### 2018-07-06 Overview.Rmd
Inital exploration of data

---
title: "Dataset Summary"
author: "Daniel Falster & Susie Zajitschek"
date: "06/07/2018"
output: 
  html_document:
    fig_height: 8
    fig_width: 10
    df_print: paged
    rows.print: 25
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE, echo=TRUE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
library(readr)
library(dplyr)
library(skimr)
library(ggplot2)
library(scales)
```

Here is an initial exploration of the mouse data we are working on.

The data is big, but not so large that we can't use our standard tools on a desktop. I'd suggest using packages from the [tidyverse](https://www.tidyverse.org/) family, in particular `readr`, `dplyr`, `ggplot2`, `skimr`, `scales`.

##  Dataset overview

Read in data, specifying variable types:

```{r cars}
data_raw <- read_csv("data/dr7.0_all_control_data.csv", 
                  col_types = cols(
                      .default = col_character(),
                      project_id = col_character(),
                      id = col_character(),
                      parameter_id = col_character(),
                      age_in_days = col_integer(),
                      date_of_experiment = col_datetime(format = ""),
                      weight = col_double(),
                      phenotyping_center_id = col_character(),
                      production_center_id = col_character(),
                      weight_date = col_datetime(format = ""),
                      date_of_birth = col_datetime(format = ""),
                      procedure_id = col_character(),
                      pipeline_id = col_character(),
                      biological_sample_id = col_character(),
                      biological_model_id = col_character(),
                      weight_days_old = col_integer(),
                      datasource_id = col_character(),
                      experiment_id = col_character(),
                      data_point = col_double(),
                      age_in_weeks = col_integer(),
                      `_version_` = col_character()
                      )
                )
```

Number of rows:

```{r}
data_raw %>% nrow()
```

Variables in the dataset:

```{r}
data_raw %>% names()
```

Lots of variables are full of NAs

```{r}
n_records <- data_raw %>% nrow()
NA_count <- data_raw %>%
  summarise_all(funs(sum(is.na(.))/n_records*100)) %>% 
  unlist() %>% sort(decreasing=TRUE)
(NA_count)

# make a plot
tibble(percent_NA = NA_count) %>% 
  ggplot(aes(percent_NA)) + geom_histogram()
```

Let's remove those variables that have all NAs and create a new variable called data:

```{r}
(all_NAs <- names(NA_count)[NA_count == 100])
data <- data_raw %>% select(-one_of(all_NAs))
```

Now we `r data %>% names() %>% length()` variables in the dataset:

```{r}
data %>% names()
```

Now use `skimr` to take a quick look of all variables:

```{r}
x <- data %>% skimr::skim()
x %>% skimr::kable()
```

Next we'll look at some specific variables of potential importance.

## Production center

Contributions by `production_center`:
```{r}
data$production_center %>% table() %>% sort()
```

## Weights

Overall distribution of weights:
```{r}
ggplot(data, aes(x=weight)) + 
  geom_histogram(bins=50)
```

Weights by center:
```{r}
ggplot(data, aes(x=weight)) + 
  geom_histogram() + 
  facet_wrap( ~ production_center, ncol=1)
```

Weights by center and sex:
```{r}
ggplot(data, aes(x=weight, fill=sex)) + 
  geom_histogram(bins=50) + 
  facet_wrap( ~ production_center, ncol=1)
```

## Procedure

Contributions by `procedure_name`:

```{r, fig_height=12}
data$procedure_name %>% table() %>% sort(decreasing = TRUE)

x <- data %>% group_by(procedure_name) %>% summarise(n=n())
ggplot(x, aes(reorder(procedure_name, n), n)) +
  geom_col() + coord_flip()
```

Procedure name by production center:

```{r}
table(data$production_center, data$procedure_name)
```

Next want to visualise the above, but so far the plot is unmanagable (need to improve):

```{r, fig.height=25}

x <- data %>% 
  group_by(production_center, procedure_name) %>% 
  summarise(n=n())

ggplot(x, aes(reorder(production_center, n), n)) +
  geom_col() + coord_flip() +
  facet_wrap( ~ procedure_name, ncol=4)
```

### 2018-07-06 Overview.Rmd
Add distributions of ages and plots of age vs weight

@@
 library(scales)
+library(viridis)
 ```
@@
 The data is big, but not so large that we can't use our standard tools on a desktop.
-I'd suggest using packages from the [tidyverse](https://www.tidyverse.org/) family, in particular `readr`, `dplyr`, `ggplot2`, `skimr`, `scales`.
+I'd suggest using packages from the [tidyverse](https://www.tidyverse.org/) family, in particular `readr`, `dplyr`, `ggplot2`, `skimr`, `scales`, `viridis`.
 
@@
 tibble(percent_NA = NA_count) %>% 
-  ggplot(aes(percent_NA)) + geom_histogram()
+  ggplot(aes(percent_NA)) + geom_histogram(bins=50)
 ```
@@
 ggplot(data, aes(x=weight)) + 
-  geom_histogram() + 
+  geom_histogram(bins=50) + 
   facet_wrap( ~ production_center, ncol=1)
@@
 
-## Procedure
+## Ages
+
+There seems to be an issue with some very negative values of age:
+```{r}
+range(data$age_in_days, na.rm=TRUE)
+ggplot(data, aes(x=age_in_days)) + 
+  geom_histogram(bins=50)
+```
+
+So for now we'll filter those out:
+
+```{r}
+data <- data %>% filter(age_in_days > 0 & age_in_days < 500)
+```
+
+Overall distribution of ages:
+```{r}
+ggplot(data, aes(x=age_in_days)) + 
+  geom_histogram(bins=50)
+```
+
+Age by center:
+```{r}
+ggplot(data, aes(x=age_in_days)) + 
+  geom_histogram(bins=50) + 
+  facet_wrap( ~ production_center, ncol=1)
+```
+
+Age by center and sex:
+```{r, fig_height=12}
+ggplot(data, aes(x=age_in_days, fill=sex)) + 
+  geom_histogram(bins=50) + 
+  facet_wrap( ~ production_center, ncol=1)
+```
+
+Age vs weight by sex:
+```{r}
+ggplot(data, aes(x=age_in_days, y=weight)) + 
+  geom_hex() + 
+  viridis::scale_fill_viridis() + 
+  coord_fixed() +
+  facet_wrap( ~ sex, ncol=1)
+```
+
+## Procedures
 
@@
 
-Next want to visualise the above, but so far the plot is unmanagable (need to improve):
+Note the uneven distribution of procdures by production_center. We can try to visualise the above (need to improve):
 

### 2018-08-02 Overview.Rmd
Cosmetic updates

--- 2018-07-06 Overview.Rmd
@@
   html_document:
-    fig_height: 8
+    fig_height: 6
     fig_width: 10
     df_print: paged
-    rows.print: 25
+    rows.print: 10
+    code_folding: hide
+    theme: yeti
+    toc: yes
+    toc_depth: 3
+    toc_float:
+      collapsed: false
+      smooth_scroll: true
 editor_options: 
@@
 library(scales)
+library(viridis)
+library(knitr)
+library(kableExtra)
 ```
@@
 The data is big, but not so large that we can't use our standard tools on a desktop.
-I'd suggest using packages from the [tidyverse](https://www.tidyverse.org/) family, in particular `readr`, `dplyr`, `ggplot2`, `skimr`, `scales`.
+I'd suggest using packages from the [tidyverse](https://www.tidyverse.org/) family, in particular `readr`, `dplyr`, `ggplot2`, `skimr`, `scales`, `viridis`.
 
-##  Dataset overview
+#  Dataset overview
 
@@
 
-Number of rows:
+Number of rows & columns:
 
 ```{r}
-data_raw %>% nrow()
+data_raw %>% dim()
 ```
 
-Variables in the dataset:
-
-```{r}
-data_raw %>% names()
-```
-
-Lots of variables are full of NAs
+Of the `r data %>% names() %>% length()` variables in the dataset, lots of variables are full of NAs:
 
@@
   summarise_all(funs(sum(is.na(.))/n_records*100)) %>% 
-  unlist() %>% sort(decreasing=TRUE)
-(NA_count)
+  unlist() %>% sort(decreasing=TRUE) %>%
+  tibble(variable=names(.), percent_NA = .)
 
 # make a plot
-tibble(percent_NA = NA_count) %>% 
-  ggplot(aes(percent_NA)) + geom_histogram()
+ggplot(NA_count, aes(percent_NA)) + geom_histogram(bins=50)
 ```
 
-Let's remove those variables that have all NAs and create a new variable called data:
+Let's remove those variables that have all NAs:
 
 ```{r}
-(all_NAs <- names(NA_count)[NA_count == 100])
+(all_NAs <- NA_count$variable[NA_count$percent_NA == 100])
 data <- data_raw %>% select(-one_of(all_NAs))
@@
 
-```{r}
+```{r, results='asis'}
 x <- data %>% skimr::skim()
-x %>% skimr::kable()
+pander::pander(x)
 ```
@@
 
-## Production center
+# Production center
 
@@
 ```{r}
-data$production_center %>% table() %>% sort()
+x <- data %>% group_by(production_center) %>% summarise(n=n())
+
+ggplot(x, aes(reorder(production_center, n), n)) +
+  geom_col() + coord_flip()
+
+x 
 ```
 
-## Weights
+# Weights
 
@@
 
-Weights by center:
-```{r}
-ggplot(data, aes(x=weight)) + 
-  geom_histogram() + 
+Weights by center and sex:
+```{r, fig.height=12}
+ggplot(data, aes(x=weight, fill=sex)) + 
+  geom_histogram(bins=50) + 
+  scale_y_log10() +
   facet_wrap( ~ production_center, ncol=1)
@@
 
-Weights by center and sex:
+# Ages
+
+There seems to be an issue with some very negative values of age. The range in the raw data is too wide:
 ```{r}
-ggplot(data, aes(x=weight, fill=sex)) + 
+range(data$age_in_days, na.rm=TRUE)
+ggplot(data, aes(x=age_in_days)) + 
+  geom_histogram(bins=50)
+```
+
+So for now we'll filter those out, to give an reasonable distribution of ages:
+
+```{r}
+data <- data %>% filter(age_in_days > 0 & age_in_days < 500)
+
+ggplot(data, aes(x=age_in_days)) + 
+  geom_histogram(bins=50)
+```
+
+Age by center and sex:
+```{r, fig.height=12}
+ggplot(data, aes(x=age_in_days, fill=sex)) + 
   geom_histogram(bins=50) + 
+  scale_y_log10() +
   facet_wrap( ~ production_center, ncol=1)
@@
 
-## Procedure
+Age vs weight by sex:
+```{r}
+data %>%
+  filter(sex %in% c("male", "female")) %>% 
+  ggplot(aes(x=age_in_days, y=weight)) + 
+  geom_hex() + 
+  viridis::scale_fill_viridis() + 
+  coord_fixed() +
+  facet_wrap( ~ sex, ncol=1)
+```
+
+# Procedures
 
@@
 
-```{r, fig_height=12}
-data$procedure_name %>% table() %>% sort(decreasing = TRUE)
-
+```{r, fig.height=12}
 x <- data %>% group_by(procedure_name) %>% summarise(n=n())
@@
 
-Procedure name by production center:
-
-```{r}
-table(data$production_center, data$procedure_name)
+```{r, results='asis'}
+data$procedure_name %>% table() %>% sort(decreasing = TRUE) %>%
+  kable() %>%
+  kable_styling() %>%
+  scroll_box(width = "500px", height = "400px")
 ```
 
-Next want to visualise the above, but so far the plot is unmanagable (need to improve):
+Note the uneven distribution of procdures by production_center:
 
@@
 ```
+
+```{r, results='asis'}
+t(table(data$production_center, data$procedure_name)) %>%
+  kable() %>%
+  kable_styling() %>%
+  scroll_box(width = "100%", height = "500px")
+```
+
+# Parameters
+
+There are a lot of unique values under the variable `parameter_name`:
+
+```{r}
+data$parameter_name %>% unique() %>% length()
+```
+
+```{r}
+data$parameter_name %>% table() %>% sort(decreasing = TRUE) %>%
+  tibble(variable=names(.), count = .) %>%
+  kable() %>%
+  kable_styling() %>%
+  scroll_box(width = "100%", height = "500px")
+```
+
+# Issues:
+
+1.  `procedure_name` are values eding in `(GMC)` different?
+2. Spelling / case differences: e.g. `Body weight` vs `Body Weight`

### 2018-08-03 Cleaning & subset.Rmd
Procedures for cleaning and exporting a subset

--- 2018-07-06 Overview.Rmd
@@
 title: "Dataset Summary"
-author: "Daniel Falster & Susie Zajitschek"
+author: "Daniel Falster"
 date: "06/07/2018"
@@
 library(dplyr)
-library(skimr)
-library(ggplot2)
-library(scales)
 ```
 
-Here is an initial exploration of the mouse data we are working on.
-
-The data is big, but not so large that we can't use our standard tools on a desktop.
-I'd suggest using packages from the [tidyverse](https://www.tidyverse.org/) family, in particular `readr`, `dplyr`, `ggplot2`, `skimr`, `scales`.
-
-##  Dataset overview
-
-Read in data, specifying variable types:
+# Load
 
@@
 
-Number of rows:
+# Cleaning:
 
 ```{r}
-data_raw %>% nrow()
+data <- data_raw %>% 
+  mutate(parameter_name = tolower(parameter_name) ) %>%
+  filter(age_in_days > 0 & age_in_days < 500) %>% 
+  select(production_center, project_name, biological_sample_id, sex, procedure_name, age_in_days, weight, parameter_name, data_point) %>% 
+  arrange(production_center, biological_sample_id, age_in_days)
 ```
 
-Variables in the dataset:
+# Export
+
+Body size only
 
 ```{r}
-data_raw %>% names()
+dir.create("export", F, F)
+data %>% filter(parameter_name == "body weight") %>%
+  saveRDS("export/body_weight.rds")
 ```
-
-Lots of variables are full of NAs
-
-```{r}
-n_records <- data_raw %>% nrow()
-NA_count <- data_raw %>%
-  summarise_all(funs(sum(is.na(.))/n_records*100)) %>% 
-  unlist() %>% sort(decreasing=TRUE)
-(NA_count)
-
-# make a plot
-tibble(percent_NA = NA_count) %>% 
-  ggplot(aes(percent_NA)) + geom_histogram()
-```
-
-Let's remove those variables that have all NAs and create a new variable called data:
-
-```{r}
-(all_NAs <- names(NA_count)[NA_count == 100])
-data <- data_raw %>% select(-one_of(all_NAs))
-```
-
-Now we `r data %>% names() %>% length()` variables in the dataset:
-
-```{r}
-data %>% names()
-```
-
-Now use `skimr` to take a quick look of all variables:
-
-```{r}
-x <- data %>% skimr::skim()
-x %>% skimr::kable()
-```
-
-Next we'll look at some specific variables of potential importance.
-
-## Production center
-
-Contributions by `production_center`:
-```{r}
-data$production_center %>% table() %>% sort()
-```
-
-## Weights
-
-Overall distribution of weights:
-```{r}
-ggplot(data, aes(x=weight)) + 
-  geom_histogram(bins=50)
-```
-
-Weights by center:
-```{r}
-ggplot(data, aes(x=weight)) + 
-  geom_histogram() + 
-  facet_wrap( ~ production_center, ncol=1)
-```
-
-Weights by center and sex:
-```{r}
-ggplot(data, aes(x=weight, fill=sex)) + 
-  geom_histogram(bins=50) + 
-  facet_wrap( ~ production_center, ncol=1)
-```
-
-## Procedure
-
-Contributions by `procedure_name`:
-
-```{r, fig_height=12}
-data$procedure_name %>% table() %>% sort(decreasing = TRUE)
-
-x <- data %>% group_by(procedure_name) %>% summarise(n=n())
-ggplot(x, aes(reorder(procedure_name, n), n)) +
-  geom_col() + coord_flip()
-```
-
-Procedure name by production center:
-
-```{r}
-table(data$production_center, data$procedure_name)
-```
-
-Next want to visualise the above, but so far the plot is unmanagable (need to improve):
-
-```{r, fig.height=25}
-
-x <- data %>% 
-  group_by(production_center, procedure_name) %>% 
-  summarise(n=n())
-
-ggplot(x, aes(reorder(production_center, n), n)) +
-  geom_col() + coord_flip() +
-  facet_wrap( ~ procedure_name, ncol=4)
-```

### 2018-08-03 Overview.Rmd
Procedures for cleaning and exporting a subset

@@
 
+# Individuals
+
+There seem to be multiple records for an individual, which is identified by the varaible `biological_sample_id`.
+Based on this there ar `r data$biological_sample_id %>% unique() %>% length()` unique individuals.
+And there are multiple records per individual.
+For example, here are records for  `biological_sample_id=107609`:
+
+```{r}
+select(filter(data, biological_sample_id == "107609"), sex, production_center, project_name, biological_sample_id, age_in_days, weight, parameter_name) %>% arrange(age_in_days) %>% data.frame()
+```
+
+```{r}
+
+data_i <- data %>% 
+  filter(parameter_name == "Body weight") %>%
+  group_by(biological_sample_id) %>% 
+  summarise(
+    production_center = production_center[1],
+    project_name = project_name[1],
+    sex = sex[1],
+    n = n(),
+    med_age= median(age_in_days)
+    )
+
+data_i
+```
+
 # Issues:

### 2018-08-03 Cleaning & subset.Rmd
Add strain into body size data; summary stats by population

@@
   filter(age_in_days > 0 & age_in_days < 500) %>% 
-  select(production_center, project_name, biological_sample_id, sex, procedure_name, age_in_days, weight, parameter_name, data_point) %>% 
+  select(production_center, strain_name, experiment_id, external_sample_id, biological_sample_id, sex, procedure_name, age_in_days, weight, parameter_name, data_point) %>% 
   arrange(production_center, biological_sample_id, age_in_days)
@@
 ```
+
+# For variance analysis
+
+- population has > 5 individuals
+
+keep age closet t0 10 
+```{r}
+
+data %>% 
+  filter(
+    age_in_days >= 98, 
+    parameter_name == "body weight") %>%
+  mutate(age_diff=abs(100-age_in_days)) %>%
+  group_by(biological_sample_id) %>%
+  filter(age_diff == min(age_diff)) %>%
+  mutate(population = sprintf("%s-%s-%s", strain_name, production_center, sex) )  -> x
+
+i <- match(unique(x$biological_sample_id), x$biological_sample_id)
+
+data2 <- x[i,] 
+```
+
+Calculate number of reocrds per population
+```{r}
+data2 %>% 
+  group_by(population) %>%
+  summarise(
+    n_records = n_distinct(biological_sample_id)
+  ) -> population_size
+hist(population_size$n_records)
+
+sum(population_size$n_records < 10)
+```
+
+```{r}
+
+data %>% 
+  filter(
+    age_in_days >= 100, 
+    parameter_name == "body weight") %>%
+  select(biological_sample_id, external_sample_id) %>%
+  arrange(external_sample_id) %>%
+  data.frame()
+
+data %>% 
+  filter(
+    age_in_days >= 100, 
+    parameter_name == "body weight") %>%
+  mutate(age_diff=abs(100-age_in_days)) %>%
+  group_by(biological_sample_id) %>%
+  filter(age_diff == min(age_diff)) -> x
+
+i <- match(unique(x$biological_sample_id), x$biological_sample_id)
+
+x[i,] -> x
+
+# check only one record per individual
+
+table(x$biological_sample_id) -> z 
+z[z!=1]
+
+```

### 2018-08-03 Overview.Rmd
Add strain into body size data; summary stats by population

@@
 ```{r}
-select(filter(data, biological_sample_id == "107609"), sex, production_center, project_name, biological_sample_id, age_in_days, weight, parameter_name) %>% arrange(age_in_days) %>% data.frame()
+select(filter(data_raw, biological_sample_id == "107609"), sex, production_center, external_sample_id, biological_sample_id, age_in_days, weight, parameter_name) %>% arrange(age_in_days) %>% data.frame()
 ```

### 2018-08-03 bodyweight_analysis_WillDan.R
Body weight analysis across age

@@ -1,0 +1,64 @@
+
+# Bring in data
+	data <- readRDS("export/body_weight.rds")
+
+# Packages
+	install.packages("patchwork")
+	install.packages("gridExtra")
+	library(gridExtra)
+
+# Subset data based on body weight
+	bw <- subset(data, parameter_name == "body weight")
+
+# Check first whether weight and data_point column match
+	any(bw$weight == bw$data_point)
+
+# Subset the data to get between 100 & 300 days
+	bw_100_300 <- subset(bw, age_in_days > 98 & age_in_days <300)
+
+# PLot and see what the distribution looks like
+	ggplot(bw_100_300, aes(x=data_point, fill = sex)) + geom_density(alpha = 0.5)
+
+# Function for cutting data into age bins and then calculating SD and CV for each sex and strain
+sd_bin <- function(data, bins, strains){
+	data$cut_age <- cut(data$age_in_days, bins)
+
+	sd <- data %>% filter(strain_name %in% strains) %>% group_by(sex, cut_age, strain_name) %>% summarise(sd = sd(data_point), cv = sd(data_point) / mean(data_point), n = n())
+
+	return(sd)
+}
+
+# Generate a new dataset containing SD and CV for the following three strains using the full data set so we don't restrict age.
+age_sd <- sd_bin(data, 10, strains = c("C57BL/6N", "C57BL/6NTac", "C57BL/6NJ"))
+
+# Check data
+print(arrange(age_sd, strain_name), n = 30)
+
+# Simple plot
+ggplot(age_sd, aes(x=cut_age, y=cv, col = sex)) + geom_point() + facet_grid(~strain_name) + theme_classic()
+
+# Main plot: PLOT THIS
+p1 <- ggplot(bw, aes(x=age_in_days, y=data_point, col = sex)) + geom_point(alpha = 0.5) + labs(x = "Age (days)", y = "Body weight")
+
+p2 <- ggplot(age_sd, aes(x=cut_age, y=sd, col = sex)) + geom_point(size=2) + facet_grid(~strain_name) +theme_bw() + theme(axis.text.x=element_text(size=rel(0.4))) + labs(x = "Age bin", y = "SD") 
+
+grid.arrange(p1, p2)
+
+
+## Simulating a power analysis - didn't get far with this....
+# Get standard deviation in two groups
[…]

### 2018-08-03 Cleaning & subset.Rmd
Meta analysis of body size at ~100 days

@@
   filter(age_in_days > 0 & age_in_days < 500) %>% 
-  select(production_center, strain_name, experiment_id, external_sample_id, biological_sample_id, sex, procedure_name, age_in_days, weight, parameter_name, data_point) %>% 
+  select(production_center, strain_name, experiment_id, external_sample_id, 
+         biological_sample_id, sex, procedure_name, age_in_days, weight, parameter_name, data_point) %>% 
   arrange(production_center, biological_sample_id, age_in_days)
@@
 
-# Export
-
-Body size only
+Export for body size only
 
@@
 
-keep age closet t0 10 
+keep age closet t=100
+
 ```{r}
@@
 
+# still some individuals with multiple records (bc appear under different procedures, so filter to one record)
 i <- match(unique(x$biological_sample_id), x$biological_sample_id)
-
 data2 <- x[i,] 
@@
 Calculate number of reocrds per population
+
 ```{r}
@@
 
-sum(population_size$n_records < 10)
+sum(population_size$n_records < 5)
+```
+
+Now calculate statsics by population:
+
+```{r}
+population_stats <- data2 %>% 
+  filter(!is.na(data_point)) %>% 
+  group_by(population, sex, strain_name, production_center) %>% 
+  summarise(
+    trait = parameter_name[1],
+    x_bar = mean(data_point),
+    x_sd = sd(data_point),
+    n_ind = n()
+  ) %>% 
+  ungroup() %>%
+  filter(n_ind > 5) %>% 
+  # Check both sexes present & filter those missing
+  group_by(strain_name, production_center) %>% 
+  mutate(
+    n_sex = n_distinct(sex)
+  ) %>% ungroup() %>%
+  filter(n_sex ==2) %>% 
+  arrange(strain_name, production_center, sex)
+```
+
+Now analyse by population data:
+
+Sanity checks
+
+```{r}
+i <- seq(1, nrow(population_stats), by=2)
+all(population_stats$sex[i] == "female")
+all(population_stats$sex[i+1] == "male")
+all(population_stats$strain_name[i+1] == population_stats$strain_name[i] )
+all(population_stats$production_center[i+1] == population_stats$production_center[i] )
+
+input <- data.frame(
+       n1i = population_stats$n_ind[i], 
+       n2i = population_stats$n_ind[i+1], 
+       x1i = population_stats$x_bar[i], 
+       x2i = population_stats$x_bar[i+1],
+       sd1i = population_stats$x_sd[i], 
+       sd2i = population_stats$x_sd[i+1])
+
+all(input > 0)
+```
+Check plot of mean vs variance
+
+```{r}
+plot(population_stats$x_bar, population_stats$x_sd, pch=16, log="xy", col = as.factor(population_stats$sex))
 ```
@@
 ```{r}
+Calc.lnCVR <- function(CMean, CSD, CN, EMean, ESD, EN){
+	S2 <- log(ESD) - log(EMean) + 1 / (2*(EN - 1)) - (log(CSD) - log(CMean) + 1 / (2*(CN - 1)))
+  return(S2)
+}
 
-data %>% 
-  filter(
-    age_in_days >= 100, 
-    parameter_name == "body weight") %>%
-  select(biological_sample_id, external_sample_id) %>%
-  arrange(external_sample_id) %>%
-  data.frame()
+Calc.var.lnCVR <- function(CMean, CSD, CN, EMean, ESD, EN, Equal.E.C.Corr=T) {
+	if(Equal.E.C.Corr==T){
+		mvcorr <- cor.test(log(c(CMean, EMean)), log(c(CSD, ESD)))$estimate
+		S2 <- CSD^2 / (CN * (CMean^2)) + 1 / (2 * (CN - 1)) - 2 * mvcorr * sqrt((CSD^2 / (CN * (CMean^2))) * (1 / (2 * (CN - 1)))) + ESD^2 / (EN * (EMean^2)) + 1 / (2 * (EN - 1)) - 2 * mvcorr * sqrt((ESD^2 / (EN * (EMean^2))) * (1 / (2 * (EN - 1))))
+	}
+	else{
+		Cmvcorr <- cor.test(log(CMean), log(CSD))$estimate
+		Emvcorr <- cor.test(log(EMean), (ESD))$estimate
+		S2 <- CSD^2 / (CN * (CMean^2)) + 1 / (2 * (CN - 1)) - 2 * Cmvcorr * sqrt((CSD^2 / (CN * (CMean^2))) * (1 / (2 * (CN - 1)))) + ESD^2 / (EN * (EMean^2)) + 1 / (2 * (EN - 1)) - 2 * Emvcorr * sqrt((ESD^2 / (EN * (EMean^2))) * (1 / (2 * (EN - 1))))
+	}
+	return(S2)
+}
 
-data %>% 
-  filter(
-    age_in_days >= 100, 
-    parameter_name == "body weight") %>%
-  mutate(age_diff=abs(100-age_in_days)) %>%
-  group_by(biological_sample_id) %>%
-  filter(age_diff == min(age_diff)) -> x
+Calc.lnVR <- function(CSD, CN, ESD, EN){
+	log(ESD) - log(CSD) + 1 / (2*(EN - 1)) - 1 / (2*(CN - 1))
+}
 
-i <- match(unique(x$biological_sample_id), x$biological_sample_id)
+Calc.var.lnVR <- function( CN,  EN) {
+	1 / (2*(EN - 1)) + 1 / (2*(CN - 1))
+}
 
-x[i,] -> x
+Calc.lnRR <- function(CMean, CSD, CN, EMean, ESD, EN) {
+	log(EMean) - log(CMean)
+}
 
-# check only one record per individual
+Calc.var.lnRR <- function(CMean, CSD, CN, EMean, ESD, EN) {
+	CSD^2/(CN * CMean^2) + ESD^2/(EN * EMean^2)
+}
+```
 
-table(x$biological_sample_id) -> z 
-z[z!=1]
+```{r}
+# library(metafor)
+#measures: CVR, VR
+# escalc(measure="CVR", 
+#       n1i = n1i, n2i = n2i, x1i = x1i, x2i = x2i, sd1i = sd1i, sd2i = sd2i, data = input)
+# not working
+
+results <- population_stats[i,] %>% 
+  select(strain_name, production_center) %>%
+  mutate(
+    effect_size_CVR = Calc.lnCVR(CMean = input$x1i, CSD = input$sd1i, CN = input$n1i, EMean = input$x2i, ESD = input$sd2i, EN = input$n2i),
+    sample_variance_CVR = Calc.var.lnCVR(CMean = input$x1i, CSD = input$sd1i, CN = input$n1i, EMean = input$x2i, ESD = input$sd2i, EN = input$n2i),
+    effect_size_VR = Calc.lnVR(CSD = input$sd1i, CN = input$n1i, ESD = input$sd2i, EN = input$n2i),
+    sample_variance_VR = Calc.var.lnVR(CN = input$n1i, EN = input$n2i),
+    effect_size_RR = Calc.lnRR(CMean = input$x1i, CSD = input$sd1i, CN = input$n1i, EMean = input$x2i, ESD = input$sd2i, EN = input$n2i),
+    sample_variance_RR = Calc.var.lnRR(CMean = input$x1i, CSD = input$sd1i, CN = input$n1i, EMean = input$x2i, ESD = input$sd2i, EN = input$n2i),
+    err = as.factor(seq_len(n()))
+    )
 
 ```
+
+## Compare CVR
+
+```{r}
+plot(results$effect_size_CVR, 1/sqrt(results$sample_variance_CVR), ylab="sample precision", xlab="effect size", pch=16, xlim=c(-0.7, 0.7), col=as.factor(results$production_center))
+abline(v=0)
+```
+
+```{r}
+metafor::rma.mv(yi = effect_size_CVR, V = sample_variance_CVR, random = list(~1| strain_name, ~1|production_center, ~1|err), data = results)
+```
+
+## Compare VR
+
+```{r}
+plot(results$effect_size_VR, 1/sqrt(results$sample_variance_VR), ylab="sample precision", xlab="effect size", pch=16, xlim=c(-0.8, 0.8), col=as.factor(results$production_center))
+abline(v=0)
+```
+
+```{r}
+metafor::rma.mv(yi = effect_size_VR, V = sample_variance_VR, random = list(~1| strain_name, ~1|production_center, ~1|err), data = results)
+```
+
+## Compare Means
+
+```{r}
+plot(results$effect_size_RR, 1/sqrt(results$sample_variance_RR), ylab="sample precision", xlab="effect size", pch=16, xlim=c(-0.5, 0.5), col=as.factor(results$production_center))
+abline(v=0)
+```
+
+```{r}
+metafor::rma.mv(yi = effect_size_RR, V = sample_variance_RR, random = list(~1| strain_name, ~1|production_center, ~1|err), data = results)
+```

### 2018-08-03 bodyweight_analysis_WillDan.R
patchwork changes

@@ -3,9 +3,11 @@
 	data <- readRDS("export/body_weight.rds")
 
 # Packages
-	install.packages("patchwork")
+	devtools::install_github("thomasp85/patchwork") # Make sure to download first in a new R session
 	install.packages("gridExtra")
 	library(gridExtra)
+	library(ggplot2)
+	library(tidyverse)
 
 # Subset data based on body weight
 	bw <- subset(data, parameter_name == "body weight")
@@ -42,16 +44,19 @@ p1 <- ggplot(bw, aes(x=age_in_days, y=data_point, col = sex)) + geom_point(alpha
 
 p2 <- ggplot(age_sd, aes(x=cut_age, y=sd, col = sex)) + geom_point(size=2) + facet_grid(~strain_name) +theme_bw() + theme(axis.text.x=element_text(size=rel(0.4))) + labs(x = "Age bin", y = "SD") 
 
+# One way
 grid.arrange(p1, p2)
 
+# Another way
+p1 / p2
 
 ## Simulating a power analysis - didn't get far with this....
 # Get standard deviation in two groups
- sd <- bw_100_300 %>% group_by(sex) %>% summarise(sd = sd(data_point))
+   sd <- bw_100_300 %>% group_by(sex) %>% summarise(sd = sd(data_point))
  mean <- bw_100_300 %>% group_by(sex) %>% summarise(mean = mean(data_point))
 
 # Sample sizes
-n <- c(5, 10, 20, 30)
+	n <- c(5, 10, 20, 30)
 
 # Means of males and females for a trait
 	m_male   <- as.numeric(mean[mean$sex == "male", "mean"])
@@ -61,4 +66,4 @@ n <- c(5, 10, 20, 30)
 	sd_male   <- as.numeric(sd[sd$sex == "male", "sd"])
 	sd_female <- as.numeric(sd[sd$sex == "female", "sd"])
 
-pwr.t2n.test
+# pwr.t2n.test

### 2018-08-03 bodyweight_analysis_WillDan.R
adding hybrids

@@ -67,3 +67,14 @@ p1 / p2
 	sd_female <- as.numeric(sd[sd$sex == "female", "sd"])
 
 # pwr.t2n.test
+
+
+#adding hybrids
+bw$hybrid<-grepl("\\\*",bw$strain_name)
+
+filter(bw,sex!="no_data")%>%
+ggplot(aes(x=age_in_days, y=data_point, col = sex)) + 
+geom_point(alpha = 0.5) + 
+labs(x = "Age (days)", y = "Body weight") +
+facet_grid(~hybrid)+
+theme_bw()-> p1

### 2018-08-03 Cleaning & subset.Rmd
Separate into functions for easier reuse across different traits

--- 2018-08-03 Cleaning & subset.Rmd
@@
 library(dplyr)
+library(metafor)
+
+source("R/meta_analysis.R")
+source("R/data_load_clean.R")
+source("R/calc_pop_stats.R")
 ```
 
-# Load
+# Setup
 
+Load data
 ```{r cars}
-data_raw <- read_csv("data/dr7.0_all_control_data.csv", 
-                  col_types = cols(
-                      .default = col_character(),
-                      project_id = col_character(),
-                      id = col_character(),
-                      parameter_id = col_character(),
-                      age_in_days = col_integer(),
-                      date_of_experiment = col_datetime(format = ""),
-                      weight = col_double(),
-                      phenotyping_center_id = col_character(),
-                      production_center_id = col_character(),
-                      weight_date = col_datetime(format = ""),
-                      date_of_birth = col_datetime(format = ""),
-                      procedure_id = col_character(),
-                      pipeline_id = col_character(),
-                      biological_sample_id = col_character(),
-                      biological_model_id = col_character(),
-                      weight_days_old = col_integer(),
-                      datasource_id = col_character(),
-                      experiment_id = col_character(),
-                      data_point = col_double(),
-                      age_in_weeks = col_integer(),
-                      `_version_` = col_character()
-                      )
-                )
+data_raw <- load_raw("data/dr7.0_all_control_data.csv") 
 ```
 
-# Cleaning:
-
+Clean data & define population variable
 ```{r}
-data <- data_raw %>% 
-  mutate(parameter_name = tolower(parameter_name) ) %>%
-  filter(age_in_days > 0 & age_in_days < 500) %>% 
-  select(production_center, project_name, biological_sample_id, sex, procedure_name, age_in_days, weight, parameter_name, data_point) %>% 
-  arrange(production_center, biological_sample_id, age_in_days)
+data <- clean_raw_data(data_raw) %>%
+  mutate(population = sprintf("%s-%s", production_center, strain_name))
 ```
 
-# Export
-
-Body size only
-
+Export copy of data for body size analysis
 ```{r}
@@
 ```
+
+Create a copy of data for variance analysis
+
+```{r}
+data_par_age <- data_subset_parameter_individual_by_age(data, "body weight", age_min = 98, age_center = 100)
+```
+
+Now calculate statistics by population:
+
+```{r}
+population_stats <- calculate_population_stats(data_par_age)
+```
+
+Now analyse by population data:
+
+Sanity checks
+
+```{r}
+# i <- seq(1, nrow(population_stats), by = 2)
+# all(population_stats$sex[i] == "female")
+# all(population_stats$sex[i + 1] == "male")
+# all(population_stats$strain_name[i + 1] == population_stats$strain_name[i])
+# all(population_stats$production_center[i + 1] == population_stats$production_center[i])
+```
+Check plot of mean vs variance
+
+```{r}
+plot(population_stats$x_bar, population_stats$x_sd, pch=16, log="xy", col = as.factor(population_stats$sex))
+```
+
+```{r}
+results <- create_meta_analysis_effect_sizes(population_stats)
+```
+
+## Compare CVR
+
+```{r}
+plot(results$effect_size_CVR, 1/sqrt(results$sample_variance_CVR), ylab="sample precision", xlab="effect size", pch=16, xlim=c(-0.7, 0.7), col=as.factor(results$production_center))
+abline(v=0)
+```
+
+```{r}
+metafor::rma.mv(yi = effect_size_CVR, V = sample_variance_CVR, random = list(~1| strain_name, ~1|production_center, ~1|err), data = results)
+```
+
+## Compare VR
+
+```{r}
+plot(results$effect_size_VR, 1/sqrt(results$sample_variance_VR), ylab="sample precision", xlab="effect size", pch=16, xlim=c(-0.8, 0.8), col=as.factor(results$production_center))
+abline(v=0)
+```
+
+```{r}
+metafor::rma.mv(yi = effect_size_VR, V = sample_variance_VR, random = list(~1| strain_name, ~1|production_center, ~1|err), data = results)
+```
+
+## Compare Means
+
+```{r}
+plot(results$effect_size_RR, 1/sqrt(results$sample_variance_RR), ylab="sample precision", xlab="effect size", pch=16, xlim=c(-0.5, 0.5), col=as.factor(results$production_center))
+abline(v=0)
+```
+
+```{r}
+metafor::rma.mv(yi = effect_size_RR, V = sample_variance_RR, random = list(~1| strain_name, ~1|production_center, ~1|err), data = results)
+```

### 2018-08-03 R/calc_pop_stats.R

@@ -1,0 +1,48 @@
+
+calculate_population_stats <- function(mydata, min_individuals = 5) {
+  mydata %>% 
+    group_by(population, strain_name, production_center, sex) %>% 
+    summarise(
+      trait = parameter_name[1],
+      x_bar = mean(data_point),
+      x_sd = sd(data_point),
+      n_ind = n()
+    ) %>% 
+    ungroup() %>%
+    filter(n_ind > min_individuals) %>% 
+    # Check both sexes present & filter those missing
+    group_by(population) %>% 
+    mutate(
+      n_sex = n_distinct(sex)
+    ) %>% 
+    ungroup() %>%
+    filter(n_sex ==2) %>% 
+    select(-n_sex) %>%
+    arrange(production_center, strain_name, population, sex)
+}
+
+
+create_meta_analysis_effect_sizes <- function(mydata) {
+  i <- seq(1, nrow(mydata), by = 2)
+  input <- data.frame(
+    n1i = mydata$n_ind[i],
+    n2i = mydata$n_ind[i + 1],
+    x1i = mydata$x_bar[i],
+    x2i = mydata$x_bar[i + 1],
+    sd1i = mydata$x_sd[i],
+    sd2i = mydata$x_sd[i + 1]
+  )
+  
+  mydata[i,] %>% 
+  select(strain_name, production_center) %>%
+    mutate(
+      effect_size_CVR = Calc.lnCVR(CMean = input$x1i, CSD = input$sd1i, CN = input$n1i, EMean = input$x2i, ESD = input$sd2i, EN = input$n2i),
+      sample_variance_CVR = Calc.var.lnCVR(CMean = input$x1i, CSD = input$sd1i, CN = input$n1i, EMean = input$x2i, ESD = input$sd2i, EN = input$n2i),
+      effect_size_VR = Calc.lnVR(CSD = input$sd1i, CN = input$n1i, ESD = input$sd2i, EN = input$n2i),
+      sample_variance_VR = Calc.var.lnVR(CN = input$n1i, EN = input$n2i),
+      effect_size_RR = Calc.lnRR(CMean = input$x1i, CSD = input$sd1i, CN = input$n1i, EMean = input$x2i, ESD = input$sd2i, EN = input$n2i),
+      sample_variance_RR = Calc.var.lnRR(CMean = input$x1i, CSD = input$sd1i, CN = input$n1i, EMean = input$x2i, ESD = input$sd2i, EN = input$n2i),
+      err = as.factor(seq_len(n()))
+    )
+
+}

### 2018-08-03 R/data_load_clean.R

@@ -1,0 +1,65 @@
+
+# loads the raw data, setting some default types for various columns
+
+load_raw <- function(filename) {
+  read_csv(filename, 
+                              col_types = cols(
+                                .default = col_character(),
+                                project_id = col_character(),
+                                id = col_character(),
+                                parameter_id = col_character(),
+                                age_in_days = col_integer(),
+                                date_of_experiment = col_datetime(format = ""),
+                                weight = col_double(),
+                                phenotyping_center_id = col_character(),
+                                production_center_id = col_character(),
+                                weight_date = col_datetime(format = ""),
+                                date_of_birth = col_datetime(format = ""),
+                                procedure_id = col_character(),
+                                pipeline_id = col_character(),
+                                biological_sample_id = col_character(),
+                                biological_model_id = col_character(),
+                                weight_days_old = col_integer(),
+                                datasource_id = col_character(),
+                                experiment_id = col_character(),
+                                data_point = col_double(),
+                                age_in_weeks = col_integer(),
+                                `_version_` = col_character()
+                              )
+  )
+}
+
+# Apply some standard cleaning to the data
+clean_raw_data <- function(mydata) {
+  mydata %>% 
+    # standardise trait names
+    mutate(parameter_name = tolower(parameter_name) ) %>%
+    
+    # remove extreme ages
+    filter(age_in_days > 0 & age_in_days < 500) %>% 
+
+    # remove NAs ages
+    filter(!is.na(data_point)) %>%
+  
+    # subset to resoanble set of variables
+    select(production_center, strain_name, biological_sample_id, sex, procedure_name, age_in_days, weight, parameter_name, data_point) %>% 
+    arrange(production_center, biological_sample_id, age_in_days)
+}
+
+
+# subset data to select data for given parameter, and taking a single record per individual, choosing the record as close as possible to 
+# age_center
+data_subset_parameter_individual_by_age <- function(mydata, parameter, age_min, age_center) {
+  tmp <- mydata %>%
+    filter(age_in_days >= age_min,
+           parameter_name == parameter) %>%
+    # take results for single individual closest to age_center
+    mutate(age_diff = abs(age_center - age_in_days)) %>%
+    group_by(biological_sample_id) %>%
+    filter(age_diff == min(age_diff)) %>%
+    select(-age_diff)
+  
+  # still some individuals with multiple records (because same individual appears under different procedures, so filter to one record)
+  i <- match(unique(tmp$biological_sample_id), tmp$biological_sample_id)
+  tmp[i, ] 
+}

### 2018-08-03 R/meta_analysis.R

@@ -1,0 +1,48 @@
+#### Calculate metanalaysis statistics
+
+#### Created by A M Senior @ the University of Otago NZ 03/01/2014
+
+#### Below are funcitons for calculating effect sizes for meta-analysis of variance. 
+#### All functions take the mean, sd and n from the control and experimental groups.
+
+#### The first function, Cal.lnCVR, calculates the the log repsonse-ratio of the coefficient of variance (lnCVR) - see Nakagawa et al 2015.
+
+#### The second function calculates the measuremnt error variance for lnCVR. As well as the aforementioned parameters, this function also takes
+#### Equal.E.C.Corr (default = T), which must be True or False. If true, the funciton assumes that the correlaiton between mean and sd (Taylor's Law) 
+#### is equal for the mean and control groups, and, thus these data are pooled. If False the mean-SD correlation for the experimental and control groups
+#### are calculated seperatley from one another.
+
+### Similar functions are then implemented for lnVR (for comparison of standard deviations) and ln RR  (for comparison of means) 
+
+Calc.lnCVR <- function(CMean, CSD, CN, EMean, ESD, EN){
+  log(ESD) - log(EMean) + 1 / (2*(EN - 1)) - (log(CSD) - log(CMean) + 1 / (2*(CN - 1)))
+}
+
+Calc.var.lnCVR <- function(CMean, CSD, CN, EMean, ESD, EN, Equal.E.C.Corr=T) {
+  if(Equal.E.C.Corr==T){
+    mvcorr <- cor.test(log(c(CMean, EMean)), log(c(CSD, ESD)))$estimate
+    S2 <- CSD^2 / (CN * (CMean^2)) + 1 / (2 * (CN - 1)) - 2 * mvcorr * sqrt((CSD^2 / (CN * (CMean^2))) * (1 / (2 * (CN - 1)))) + ESD^2 / (EN * (EMean^2)) + 1 / (2 * (EN - 1)) - 2 * mvcorr * sqrt((ESD^2 / (EN * (EMean^2))) * (1 / (2 * (EN - 1))))
+  }
+  else{
[…]

### 2018-09-18 scripts/2018.09.19-meta_analysis_prototype.Rmd
Creating a new meta-analysis Rmd

--- 2018-08-03 Cleaning & subset.Rmd
@@
 ---
-title: "Dataset Summary"
-author: "Daniel Falster"
-date: "06/07/2018"
+title: "Protoype for metaanalysis"
+author: "Daniel Falster & Alistair Senior + Shinichi messing things up"
+date: "03/07/2018"
 output: 
@@
     rows.print: 10
-    code_folding: hide
+    code_folding: show
     theme: yeti
@@
 ```{r setup, include=FALSE, echo=TRUE}
-knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
+knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE, cache=FALSE)
+knitr::opts_knit$set(root.dir =  rprojroot::find_root("README.md"))
+```
+
+```{r}
 library(readr)
@@
 
-Load data
-```{r cars}
-data_raw <- load_raw("data/dr7.0_all_control_data.csv") 
+Load data & clean data
+
+```{r, eval = FALSE}
+# Load raw data - save cleaned dataset as RDS for reuse
+data_raw <- load_raw("data/dr7.0_all_control_data.csv") %>%
+    clean_raw_data()
+dir.create("export", F, F)
+saveRDS(data_raw, "export/data_clean.rds")
 ```
 
-Clean data & define population variable
 ```{r}
-data <- clean_raw_data(data_raw) %>%
+data <- readRDS("export/data_clean.rds")
+```
+
+Define population variable
+```{r}
+data <- data %>%
   mutate(population = sprintf("%s-%s", production_center, strain_name))
@@
 
-Export copy of data for body size analysis
-```{r}
-dir.create("export", F, F)
-data %>% filter(parameter_name == "body weight") %>%
-  saveRDS("export/body_weight.rds")
-```
-
 Create a copy of data for variance analysis
-
 ```{r}

### 2018-11-02 Loop.Rmd
Add files via upload

---
title: "Loop"
author: "Susi/Felix"
date: "31 October 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

```{r}
getwd()
```

```{r}
library(readr)
library(dplyr)
library(metafor)
library(devtools)
library(patchwork)
```

#save in a folder called "export"

```{r}
source("D:/Susi/garvan/Github/mice_sex_diff/mice_sex_diff_Nov/R/meta_analysis.R")
source("D:/Susi/garvan/Github/mice_sex_diff/mice_sex_diff_Nov/R/data_load_clean2.R")
source("D:/Susi/garvan/Github/mice_sex_diff/mice_sex_diff_Nov/R/calc_pop_stats.R")
```

# Prepare data 
```{r}
# Load raw data - save cleaned dataset as RDS for reuse
#data_raw <- load_raw("data/dr7.0_all_control_data.csv") %>%
#    clean_raw_data()
#dir.create("export", F, F)
#saveRDS(data_raw, "export/data_clean.rds")

data1 <- readRDS("export/data_clean.rds")
```

CLEAN DATA: select traits with at least 2 centers
```{r}
dat1 <-
  data1 %>%
  group_by(parameter_name) %>%
  summarize(center_per_trait = length(unique(production_center, na.rm = TRUE)))
#dat1$center_per_trait

```

```{r}
dat2 <- merge(data1, dat1) #sollte auch im grossen Datensatz so funktionieren, also ohne die uebereinstimmende Variable (trait) anzugeben
dat_moreThan1center <-
  dat2  %>%
  filter(center_per_trait >= 2)
```

```{r}
data2 <- dat_moreThan1center
min(data2$center_per_trait) #=2;ok!
```

# Define population variable

```{r}
data3 <- data2 %>%
mutate(population = sprintf("%s-%s", production_center, strain_name))
```

# Assign each unique parameter_name (=trait) a unique number ('id')

```{r}
data <- transform(data3, id = match(parameter_name, unique(parameter_name)))

```

```{r}
tail(data)

```

```{r}
n <- length(unique(data$id)) #=1:232 = 232 unique traits
```

# Create matrix to store results for all traits

```{r}
results.alltraitsx <- as.data.frame(cbind(c(1:n), matrix(rep(0, n*10), ncol = 10))) #number of individual results per trait = 10
names(results.alltraitsx) <- c("id", "lnCVR", "lnCVR_lower", "lnCVR_upper", "lnVR", "lnVR_lower", "lnVR_upper", "lnRR", "lnRR_lower", "lnRR_upper" , "sampleSize")
```

# LOOP
I am removing the variable "weight", which has some missing data, got some error message before that data were excluded below, as there are "NA"s in the rows.
```{r}
data <- data[,c(1:11,13:16)]
```

```{r}

for(i in n) {

  tryCatch({

    data_par_age <- data_subset_parameterid_individual_by_age(data, i, age_min = 0, age_center = 100)

    population_stats <- calculate_population_stats(data_par_age)

    results <- create_meta_analysis_effect_sizes(population_stats)

#lnCVR,  log repsonse-ratio of the coefficient of variance    
    cvr <- metafor::rma.mv(yi = effect_size_CVR, V = sample_variance_CVR, random = list(~1| strain_name, ~1|production_center, ~1|err), control=list(optimizer="optim", optmethod="Nelder-Mead"), data = results)
    results.alltraitsx[i, 2] <- cvr$b
    results.alltraitsx[i, 3] <- cvr$ci.lb
    results.alltraitsx[i, 4] <- cvr$ci.ub

    #lnVR, comparison of standard deviations

cv <- metafor::rma.mv(yi = effect_size_VR, V = sample_variance_VR, random = list(~1| strain_name, ~1|production_center, ~1|err), control=list(optimizer="optim", optmethod="Nelder-Mead"), data = results)
    results.alltraitsx[i, 5] <- cv$b
    results.alltraitsx[i, 6] <- cv$ci.lb
    results.alltraitsx[i, 7] <- cv$ci.ub

    # for means, lnRR

means <- metafor::rma.mv(yi = effect_size_RR, V = sample_variance_RR, random = list(~1| strain_name, ~1|production_center, ~1|err), control=list(optimizer="optim", optmethod="Nelder-Mead"), data = results)
    results.alltraitsx[i, 8] <- means$b
    results.alltraitsx[i, 9] <- means$ci.lb
    results.alltraitsx[i, 10] <- means$ci.ub
      # for the associated sample sizes, i.e. number of centres contributing ? or combination centes/ strains (doesn't lookm like it)
        results.alltraitsx[i, 11] <- means$k

  }, error=function(e){cat("ERROR :",conditionMessage(e), "\n")})
}

```

 I still get the NA warnings / removals, but have extensively checked the data set - there are no more NAs present.

 I also don't understand the k<= 1, as traits that were collected by one center only had been excluded in the previous steps.
 Also, "Single-level factor(s) found in 'random' argument" is strange, as some trais that actually worked and were included have been done in one strain only. so I don't understand what's egtting thrown out here.

```{r}  
 results.alltraitsx$parameter_name <- data$parameter_name[match(results.alltraitsx$id, data$id)]
 results.alltraitsx$procedure <- data$procedure_name[match(results.alltraitsx $id, data$id)]
```

# Create matrix to store results for all traits
```{r}   
#write.csv(results.alltraitsx, file = "results.alltraitsTO CLEAN.csv")

```

### 2019-01-18 Loop.Rmd
some old changes

@@
 ```{r}
-library(readr)
-library(dplyr)
-library(metafor)
-library(devtools)
-library(patchwork)
+# library(readr)
+# library(dplyr)
+# library(metafor)
+# library(devtools)
+# library(patchwork)
+
+# loading packages - need pacman loaded
+pacman::p_load(readr, dplyr, metafor, devtools)
+devtools::install_github("thomasp85/patchwork")
+
 ```
@@
 ```{r}
-source("D:/Susi/garvan/Github/mice_sex_diff/mice_sex_diff_Nov/R/meta_analysis.R")
-source("D:/Susi/garvan/Github/mice_sex_diff/mice_sex_diff_Nov/R/data_load_clean2.R")
-source("D:/Susi/garvan/Github/mice_sex_diff/mice_sex_diff_Nov/R/calc_pop_stats.R")
+source("./R/meta_analysis.R")
+source("./R/data_load_clean.R") # we need to replcae it with data_load_clean2.R
+source("./R/calc_pop_stats.R")
 ```

### 2019-06-04 scripts/2019_4June_IMPC variance and sex difference.Rmd
Add files via upload
R script that contains the code for metaanalyses and Figures, including supplemental Heterogeneity Figure. 
Table for heterogeneity not yet finished. 
All functions (with minor corrections) are embedded in the script and do not need to be loaded separately. data still need to be linked as described.

---
title: "IMPC Mouse data - Variance in sex differences"
author: "Susanne & Felix Zajitschek"
date: "2nd April 2019"
output:
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE,
                      message = FALSE)

```

```{r, include=FALSE}
getwd()
```

# Packages

```{r}
library(readr)
library(dplyr)
library(metafor)
library(devtools)
library(purrr)
library(tidyverse)
library(tibble)
library(kableExtra)
library(robumeta)
library(ggpubr)
library(ggplot2)
```

# Loading functions that are necessary
### Preparation of raw data
1) Data loading and cleaning of the csv file
This step we have already done and provide a the cleaned up file which is less computing intensive. However, cvs
```{r}

# loads the raw data, setting some default types for various columns

load_raw <- function(filename) {
  read_csv(filename, 
                              col_types = cols(
                                .default = col_character(),
                                project_id = col_character(),
                                id = col_character(),
                                parameter_id = col_character(),
                                age_in_days = col_integer(),
                                date_of_experiment = col_datetime(format = ""),
                                weight = col_double(),
                                phenotyping_center_id = col_character(),
                                production_center_id = col_character(),
                                weight_date = col_datetime(format = ""),
                                date_of_birth = col_datetime(format = ""),
                                procedure_id = col_character(),
                                pipeline_id = col_character(),
                                biological_sample_id = col_character(),
                                biological_model_id = col_character(),
                                weight_days_old = col_integer(),
                                datasource_id = col_character(),
                                experiment_id = col_character(),
                                data_point = col_double(),
                                age_in_weeks = col_integer(),
                                `_version_` = col_character()
                              )
  )
}

# Apply some standard cleaning to the data
clean_raw_data <- function(mydata) {
  mydata %>%

    # Fileter to IMPC source (recommened by Jeremey in email to Susi on 20 Aug 2018)
    filter(datasource_name == 'IMPC') %>%

    # standardise trait names
    mutate(parameter_name = tolower(parameter_name) ) %>%

    # remove extreme ages
    filter(age_in_days > 0 & age_in_days < 500) %>%

    # remove NAs 
    filter(!is.na(data_point)) %>%

    # subset to reasonable set of variables
    # date_of_experiment: Jeremy suggested using as an indicator of batch-level effects
    select(production_center, strain_name, strain_accession_id, biological_sample_id, pipeline_stable_id, procedure_group, procedure_name, sex, date_of_experiment, age_in_days, weight, parameter_name, data_point) %>% 
    arrange(production_center, biological_sample_id, age_in_days)
}

```

2) Subsetting the data to choose only one datapoint per individual per trait
```{r}
# this is a necessary step for the loop across all traits 
data_subset_parameterid_individual_by_age <- function(mydata, parameter, age_min, age_center) {
  tmp <- mydata %>%
    filter(age_in_days >= age_min,
           id == parameter) %>%
    # take results for single individual closest to age_center
    mutate(age_diff = abs(age_center - age_in_days)) %>%
    group_by(biological_sample_id) %>%
    filter(age_diff == min(age_diff)) %>%
    select(-age_diff)

  # still some individuals with multiple records (because same individual appears under different procedures, so filter to one record)
  j <- match(unique(tmp$biological_sample_id), tmp$biological_sample_id)
  tmp[j, ] 
}
```

## Functions for preparing the data for meta analyses
3) "Population statistics"
```{r}
calculate_population_stats <- function(mydata, min_individuals = 5) {
  mydata %>% 
    group_by(population, strain_name, production_center, sex) %>% 
    summarise(
      trait = parameter_name[1],
      x_bar = mean(data_point),
      x_sd = sd(data_point),
      n_ind = n()
    ) %>% 
    ungroup() %>%
    filter(n_ind > min_individuals) %>% 
    # Check both sexes present & filter those missing
    group_by(population) %>% 
    mutate(
      n_sex = n_distinct(sex)
    ) %>% 
    ungroup() %>%
    filter(n_sex ==2) %>% 
    select(-n_sex) %>%
    arrange(production_center, strain_name, population, sex)
}
```

 4) Extraction of effect sizes and sample variances
```{r}
create_meta_analysis_effect_sizes <- function(mydata) {
  i <- seq(1, nrow(mydata), by = 2)
  input <- data.frame(
    n1i = mydata$n_ind[i],
    n2i = mydata$n_ind[i + 1],
    x1i = mydata$x_bar[i],
    x2i = mydata$x_bar[i + 1],
    sd1i = mydata$x_sd[i],
    sd2i = mydata$x_sd[i + 1]
  )

  mydata[i,] %>% 
  select(strain_name, production_center) %>%
    mutate(
      effect_size_CVR = Calc.lnCVR(CMean = input$x1i, CSD = input$sd1i, CN = input$n1i, EMean = input$x2i, ESD = input$sd2i, EN = input$n2i),
      sample_variance_CVR = Calc.var.lnCVR(CMean = input$x1i, CSD = input$sd1i, CN = input$n1i, EMean = input$x2i, ESD = input$sd2i, EN = input$n2i),
      effect_size_VR = Calc.lnVR(CSD = input$sd1i, CN = input$n1i, ESD = input$sd2i, EN = input$n2i),
      sample_variance_VR = Calc.var.lnVR(CN = input$n1i, EN = input$n2i),
      effect_size_RR = Calc.lnRR(CMean = input$x1i, CSD = input$sd1i, CN = input$n1i, EMean = input$x2i, ESD = input$sd2i, EN = input$n2i),
      sample_variance_RR = Calc.var.lnRR(CMean = input$x1i, CSD = input$sd1i, CN = input$n1i, EMean = input$x2i, ESD = input$sd2i, EN = input$n2i),
      err = as.factor(seq_len(n()))
    )

}
```

 5) Meta Analysis

 Function to calculate metanalaysis statistics. Created by A M Senior @ the University of Otago NZ 03/01/2014

Below are funcitons for calculating effect sizes for meta-analysis of variance. 
All functions take the mean, sd and n from the control and experimental groups.

The first function, Cal.lnCVR, calculates the the log repsonse-ratio of the coefficient of variance (lnCVR) - see Nakagawa et al 2015.

The second function calculates the measuremnt error variance for lnCVR. As well as the aforementioned parameters, this function also takes
Equal.E.C.Corr (default = T), which must be True or False. If true, the funciton assumes that the correlaiton between mean and sd (Taylor's Law) 
is equal for the mean and control groups, and, thus these data are pooled. If False the mean-SD correlation for the experimental and control groups
are calculated seperatley from one another.

Similar functions are then implemented for lnVR (for comparison of standard deviations) and ln RR  (for comparison of means)

```{r}

Calc.lnCVR <- function(CMean, CSD, CN, EMean, ESD, EN){
  log(ESD) - log(EMean) + 1 / (2*(EN - 1)) - (log(CSD) - log(CMean) + 1 / (2*(CN - 1)))
}

Calc.var.lnCVR <- function(CMean, CSD, CN, EMean, ESD, EN, Equal.E.C.Corr=T) {
  if(Equal.E.C.Corr==T){
    mvcorr <- 0 #cor.test(log(c(CMean, EMean)), log(c(CSD, ESD)))$estimate   old, slightly incorrect
    S2 <- CSD^2 / (CN * (CMean^2)) + 1 / (2 * (CN - 1)) - 2 * mvcorr * sqrt((CSD^2 / (CN * (CMean^2))) * (1 / (2 * (CN - 1)))) + ESD^2 / (EN * (EMean^2)) + 1 / (2 * (EN - 1)) - 2 * mvcorr * sqrt((ESD^2 / (EN * (EMean^2))) * (1 / (2 * (EN - 1))))
  }
  else{
    Cmvcorr <- cor.test(log(CMean), log(CSD))$estimate
    Emvcorr <- cor.test(log(EMean), (ESD))$estimate
    S2 <- CSD^2 / (CN * (CMean^2)) + 1 / (2 * (CN - 1)) - 2 * Cmvcorr * sqrt((CSD^2 / (CN * (CMean^2))) * (1 / (2 * (CN - 1)))) + ESD^2 / (EN * (EMean^2)) + 1 / (2 * (EN - 1)) - 2 * Emvcorr * sqrt((ESD^2 / (EN * (EMean^2))) * (1 / (2 * (EN - 1))))		
  }
  S2
}

Calc.lnVR <- function(CSD, CN, ESD, EN){
  log(ESD) - log(CSD) + 1 / (2*(EN - 1)) - 1 / (2*(CN - 1))
}

Calc.var.lnVR <- function( CN,  EN) {
  1 / (2*(EN - 1)) + 1 / (2*(CN - 1))
}

Calc.lnRR <- function(CMean, CSD, CN, EMean, ESD, EN) {
  log(EMean) - log(CMean)
}

Calc.var.lnRR <- function(CMean, CSD, CN, EMean, ESD, EN) {
  CSD^2/(CN * CMean^2) + ESD^2/(EN * EMean^2)
}

```

Having loaded the necessary functions, we can get started on the dataset.

We here provide the cleaned dataset, which we have saved in a folder called "export", as easy starting point. However, the full dataset can ve loaded and cleaned using the da cleaning function (Function 1 above), if "#" signs in the code below are removed  (created as that is much smaller than th e .csv - which we can still provide for those who absoliutely want to start from scratch?)
```{r}
## Load raw data - save cleaned dataset as RDS for reuse
#data_raw <- load_raw("data/dr7.0_all_control_data.csv") %>%
#    clean_raw_data()
#dir.create("export", F, F)
#saveRDS(data_raw, "export/data_clean.rds")

data1 <- readRDS("export/data_clean.rds")
#data1 
```

### Clean data
This requires the selection of traits that have been measured in at least 2 centers. Consequently, rare or unusual methods and procedures are being filtered out in this step.
```{r }
dat1 <-
  data1 %>%
  group_by(parameter_name) %>%
  summarize(center_per_trait = length(unique(production_center, na.rm = TRUE)))

dat2 <- merge(data1, dat1) 
dat_moreThan1center <-
  dat2  %>%
  filter(center_per_trait >= 2)

data2 <- dat_moreThan1center
#min(data2$center_per_trait)  # as a check if there indeed are no single occurences

```

## Preparation for Meta analysis
### Define population variable & add grouping variables

In this step, a grouping variable  is added (found in "Parameter.Grouping.csv")
The grouping variables were decided based on functional groups and procedures

```{r }
data3 <- data2 %>%
mutate(population = sprintf("%s-%s", production_center, strain_name))

 group <- read.csv("ParameterGrouping.csv") 
 data <- data3
 data$parameterGroup <- group$parameter[match(data$parameter_name, group$parameter_name)]

```

### Assign each unique parameter_name (=trait,use trait variable) a unique number ('id')
We add a new variable, where redundant traits are combined
[note however, at this stage the dataset still contains non-sensical traits, i.e. traits that may not contain any u=information on variance]

```{r}
#head(data)

names(data)[16] <- "parameter_group"

data <- transform(data, id = match(parameter_name, unique(parameter_name)))
n1 <- length(unique(data$parameter_name)) #232
n2 <- length(unique(data$parameter_group)) #161
n3 <- length(unique(data$procedure_name)) # 26

n <- length(unique(data$id))
#n  # just to check that the number of traits is 232
```

### Create a matrix to store results for all traits
As the current version of this script utilizes a loop instead of tidyR code, it is here necessary to create an empty matrix, in which the returning values will be stored.

```{r}
results.alltraits.grouping <- as.data.frame(cbind(c(1:n), matrix(rep(0, n*13), ncol = 13))) #number of individual results per trait = 10
names(results.alltraits.grouping) <- c("id", "lnCVR", "lnCVR_lower", "lnCVR_upper", "lnCVR_se", "lnVR", "lnVR_lower", "lnVR_upper", "lnVR_se", "lnRR", "lnRR_lower", "lnRR_upper" ,"lnRR_se" , "sampleSize")

```

## LOOP, to run meta-analysis on all traits
The loop combines the functions menationed above and fills the data matrix with results from our meta analysis. 
Error messages indicate traits that either did not reach convergence, or that did not return meaningful results in the metaanalysis, due to absence of variance. Those traits will be removed ion later steps, outlined below.

```{r}

for(t in 1:n) {

  tryCatch({

    data_par_age <- data_subset_parameterid_individual_by_age(data, t, age_min = 0, age_center = 100)

    population_stats <- calculate_population_stats(data_par_age)

    results <- create_meta_analysis_effect_sizes(population_stats)

#lnCVR,  log repsonse-ratio of the coefficient of variance    
    cvr <- metafor::rma.mv(yi = effect_size_CVR, V = sample_variance_CVR, random = list(~1| strain_name, ~1|production_center,    
                                                                                        ~1|err), control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), data = results)
    results.alltraits.grouping[t, 2] <- cvr$b
    results.alltraits.grouping[t, 3] <- cvr$ci.lb
    results.alltraits.grouping[t, 4] <- cvr$ci.ub
    results.alltraits.grouping[t, 5] <- cvr$se

    cvr

    #lnVR, comparison of standard deviations

cv <- metafor::rma.mv(yi = effect_size_VR, V = sample_variance_VR, random = list(~1| strain_name, ~1|production_center,                                                             ~1|err), control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000),  verbose=F, data = results)
    results.alltraits.grouping[t, 6] <- cv$b
    results.alltraits.grouping[t, 7] <- cv$ci.lb
    results.alltraits.grouping[t, 8] <- cv$ci.ub
    results.alltraits.grouping[t, 9] <- cv$se

    # for means, lnRR

means <- metafor::rma.mv(yi = effect_size_RR, V = sample_variance_RR, random = list(~1| strain_name, ~1|production_center,
                                                                            ~1|err),
    control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), data = results)
    results.alltraits.grouping[t, 10] <- means$b
    results.alltraits.grouping[t, 11] <- means$ci.lb
    results.alltraits.grouping[t, 12] <- means$ci.ub
    results.alltraits.grouping[t, 13] <- means$se

        results.alltraits.grouping[t, 14] <- means$k

  }, error=function(e){cat("ERROR :",conditionMessage(e), "\n")})
}

```

### Merging datasets

Procedure names, groupiung variables etc are merged back together with the results from the metafor analysis above.
This requires loading of another excel sheet, "procedures.csv"

```{r}
procedures <- read.csv("procedures.csv")

results.alltraits.grouping$parameter_group <- data$parameter_group[match(results.alltraits.grouping$id, data$id)]
results.alltraits.grouping$procedure <- data$procedure_name[match(results.alltraits.grouping$id, data$id)]

results.alltraits.grouping$GroupingTerm <-  procedures$GroupingTerm[match(results.alltraits.grouping$procedure, procedures$procedure)]
results.alltraits.grouping$parameter_name <- data$parameter_name[match(results.alltraits.grouping$id, data$id)]

meta1 <- results.alltraits.grouping
n <- length(unique(meta1$parameter_name)) # 232
```

Removal of traits that did not achieve convergence, are non-sensical for analysis of variance (such as traits that show variaton, such as number of ribs, digits, etc). 14 traits from the originally 232 that had been included are removed.

```{r}
meta_clean <- meta1[ !(meta1$id %in% c(84,144,158,160,161,162,163,165,166,167,168,221,222,231)), ]
removed <-length(unique(meta_clean$parameter_name)) #218
```

## Dealing with Correlated Paramters

This dataset contained a number of highly correlated taits, such as different kinds of cell counts (for example, hierarchichal parametrization within immunologocal assays). As those datapoints are not independent of each other,  we conducted a meta analyses on these correlated parameters to collapse the number of levels.

### Collapsing correlated parameters

Here we double check numbers of trait parameters in the dataset

```{r}

meta1 <- meta_clean 
# length(unique(meta1$procedure)) #18
# length(unique(meta1$GroupingTerm)) #9 
# length(unique(meta1$parameter_group)) # 148 levels. To be used as grouping factor for meta-meta analysis / collapsing down based on things that are classified identically in "parameter_group" but have different "parameter_name" 
length(unique(meta1$parameter_name)) #218

```

### Count of number of parameter names (correlated sub-traits) in each parameter group (par_group_size) 
This serves to idenfify and separate the traits that are correlated from the full dataset that can be preocessed as is. If the sample size (n) for a given "parameter group" equals 1, the trait is unique and uncorrelated. All instances, where there are 2 or more traits accociated with the same  parameter group (90 cases), are selected for a "mini-meta analysis", which removes the issue of correlation.

```{r}

kable(cbind (meta1 %>%  count(parameter_group) )) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "200px")

meta1b <-
  meta1 %>%
  group_by(parameter_group) %>% 
  summarize(par_group_size = length(unique(parameter_name, na.rm = TRUE)))
#this gives a summary of number of parameter names in each parameter group, now it neeeds to get merged it back together

meta1$par_group_size <- meta1b$par_group_size[match(meta1$parameter_group, meta1b$parameter_group)]

# Create subsets with > 1 count (par_group_size > 1)

meta1_sub<-subset(meta1,par_group_size >1) # 90 observations   
meta1_sub$sampleSize <- as.numeric(meta1_sub$sampleSize)

```

# Preparation for Visualization and Meta-analysis

### Perform meta-analyses on correlated sub-traits, using robumeta 
The subset of the data is prepared (nested), and in this first step the model of the meta analysis effect sizes are calculated

```{r}
# nesting
n_count <- meta1_sub %>% 
  group_by(parameter_group) %>% 
  mutate(raw_N = sum(sampleSize)) %>%  
    nest()

model_count <- n_count %>% 
  mutate(model_lnRR = map(data, ~ robu(.x$lnRR ~ 1, data= .x, studynum= .x$id, modelweights = c("CORR"), rho = 0.8, 
                                                small = TRUE, var.eff.size= (.x$lnRR_se)^2 )),
  model_lnVR = map(data, ~ robu(.x$lnVR ~ 1, data= .x, studynum= .x$id, modelweights = c("CORR"), rho = 0.8, 
                                                small = TRUE, var.eff.size= (.x$lnVR_se)^2 )),
  model_lnCVR = map(data, ~ robu(.x$lnCVR ~ 1, data= .x, studynum= .x$id, modelweights = c("CORR"), rho = 0.8, 
                                                small = TRUE, var.eff.size= (.x$lnCVR_se)^2 ))) 
```

### Extract and save parameter estimates 
Function to collect the outcomes of the "mini" meta analysis
```{r}
count_fun <- function(mod_sub)
  return(c(mod_sub$reg_table$b.r, mod_sub$reg_table$CI.L, mod_sub$reg_table$CI.U, mod_sub$reg_table$SE))   #estimate, lower ci, upper ci, SE
```

Extraction of values created during Meta analysis using robu meta
```{r}
robusub_RR <- model_count %>% 
  transmute(parameter_group, estimatelnRR = map(model_lnRR, count_fun)) %>% 
  mutate(r = map(estimatelnRR, ~ data.frame(t(.)))) %>%
  unnest(r) %>%
  select(-estimatelnRR) %>%
  purrr::set_names(c("parameter_group","lnRR","lnRR_lower","lnRR_upper","lnRR_se"))

robusub_CVR <- model_count %>% 
  transmute(parameter_group, estimatelnCVR = map(model_lnCVR, count_fun)) %>% 
  mutate(r = map(estimatelnCVR, ~ data.frame(t(.)))) %>%
  unnest(r) %>%
  select(-estimatelnCVR) %>%
  purrr::set_names(c("parameter_group","lnCVR","lnCVR_lower","lnCVR_upper","lnCVR_se"))

robusub_VR <- model_count %>% 
  transmute(parameter_group, estimatelnVR = map(model_lnVR, count_fun)) %>% 
  mutate(r = map(estimatelnVR, ~ data.frame(t(.)))) %>%
  unnest(r) %>%
  select(-estimatelnVR) %>%
  purrr::set_names(c("parameter_group","lnVR","lnVR_lower","lnVR_upper","lnVR_se"))

robu_all <- full_join(robusub_CVR, robusub_VR) %>% full_join(., robusub_RR)
kable(cbind(robu_all, robu_all)) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "200px")

```

 Merge the two data sets (the new [robu_all] and the initial [uncorrelated sub-traits with count = 1]) 
```{r}
meta_all <- meta1 %>% filter(par_group_size == 1) %>% as_tibble
#str(meta_all)
#str(robu_all)
#which(is.na(match(names(meta_all),names(robu_all))))  # check
```

Combine data 
```{r}
# Step1 
combinedmeta <- bind_rows(robu_all, meta_all)
#glimpse(combinedmeta)

# Steps 2&3
metacombo <- combinedmeta
metacombo$counts <- meta1$par_group_size[match( metacombo$parameter_group, meta1$parameter_group)]
metacombo$procedure2 <-meta1$procedure[match( metacombo$parameter_group, meta1$parameter_group)]
metacombo$GroupingTerm2 <-meta1$GroupingTerm[match( metacombo$parameter_group, meta1$parameter_group)]

kable(cbind (metacombo, metacombo)) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "200px")

```
### Clean-up and rename 
```{r}
metacombo <-metacombo[, c(1, 20:22, 2:13)] 
names(metacombo)[3] <- "procedure" 
names(metacombo)[4] <- "GroupingTerm"

# Quick pre-check before doing plots

compare <- metacombo %>%
  group_by(GroupingTerm) %>%
  dplyr::summarize(MeanCVR = mean(lnCVR),MeanVR = mean(lnVR), MeanRR = mean(lnRR) )

compare

```

## Last step: meta-meta-analysis 
### Perform meta-analyses (3 for each of the 9 grouping terms: lnCVR, lnVR, lnRR) 
This is the full result dataset
```{r}

kable(cbind (metacombo,metacombo)) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "200px")

```

### Prepare data
Nesting, calculating the number of parameters within each grouping term, and running the metaanalysis
```{r}
metacombo_final <- metacombo %>%
 group_by(GroupingTerm) %>%
 nest()

# **Calculate number of parameters per grouping term

metacombo_final <- metacombo_final  %>%  mutate(para_per_GroupingTerm = map_dbl(data, nrow))

# For all grouping terms
metacombo_final_all <- metacombo %>%
 nest()

# **Final fixed effects meta-analyses within grouping terms, with SE of the estimate

overall1 <- metacombo_final %>%

  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower)/ (2*1.96),  
				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)),
	   model_lnVR = map(data, ~ metafor::rma.uni(yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower)/ (2*1.96),  
				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)),
	   model_lnRR = map(data, ~ metafor::rma.uni(yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower)/ (2*1.96),  
				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)))

# **Final fixed effects meta-analyses ACROSS grouping terms, with SE of the estimate

overall_all1 <- metacombo_final_all %>%

  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower)/ (2*1.96),  
				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)),
	   model_lnVR = map(data, ~ metafor::rma.uni(yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower)/ (2*1.96),  
				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)),
	   model_lnRR = map(data, ~ metafor::rma.uni(yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower)/ (2*1.96),  
				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)))

```

Re-structure data for each grouping term; delete un-used variables

```{r}
Behaviour <- as.data.frame(overall1 %>% filter(., GroupingTerm == "Behaviour")    %>%  mutate(lnCVR=.[[4]][[1]]$b, lnCVR_lower=.[[4]][[1]]$ci.lb, lnCVR_upper=.[[4]][[1]]$ci.ub, lnCVR_se=.[[4]][[1]]$se,
	              lnVR=.[[5]][[1]]$b, lnVR_lower=.[[5]][[1]]$ci.lb, lnVR_upper=.[[5]][[1]]$ci.ub, lnVR_se=.[[5]][[1]]$se,
		        lnRR=.[[6]][[1]]$b, lnRR_lower=.[[6]][[1]]$ci.lb, lnRR_upper=.[[6]][[1]]$ci.ub, lnRR_se=.[[6]][[1]]$se) )[, c(1,7:18)]

Immunology <- as.data.frame(overall1 %>% filter(., GroupingTerm == "Immunology")    %>%  mutate(lnCVR=.[[4]][[1]]$b, lnCVR_lower=.[[4]][[1]]$ci.lb, lnCVR_upper=.[[4]][[1]]$ci.ub, lnCVR_se=.[[4]][[1]]$se,
	              lnVR=.[[5]][[1]]$b, lnVR_lower=.[[5]][[1]]$ci.lb, lnVR_upper=.[[5]][[1]]$ci.ub, lnVR_se=.[[5]][[1]]$se,
		        lnRR=.[[6]][[1]]$b, lnRR_lower=.[[6]][[1]]$ci.lb, lnRR_upper=.[[6]][[1]]$ci.ub, lnRR_se=.[[6]][[1]]$se) )[, c(1,7:18)]

Hematology <- as.data.frame(overall1 %>% filter(., GroupingTerm == "Hematology")    %>%  mutate(lnCVR=.[[4]][[1]]$b, lnCVR_lower=.[[4]][[1]]$ci.lb, lnCVR_upper=.[[4]][[1]]$ci.ub, lnCVR_se=.[[4]][[1]]$se,
	              lnVR=.[[5]][[1]]$b, lnVR_lower=.[[5]][[1]]$ci.lb, lnVR_upper=.[[5]][[1]]$ci.ub, lnVR_se=.[[5]][[1]]$se,
		        lnRR=.[[6]][[1]]$b, lnRR_lower=.[[6]][[1]]$ci.lb, lnRR_upper=.[[6]][[1]]$ci.ub, lnRR_se=.[[6]][[1]]$se) )[, c(1,7:18)]

Hearing <- as.data.frame(overall1 %>% filter(., GroupingTerm == "Hearing")   %>%  mutate(lnCVR=.[[4]][[1]]$b, lnCVR_lower=.[[4]][[1]]$ci.lb, lnCVR_upper=.[[4]][[1]]$ci.ub, lnCVR_se=.[[4]][[1]]$se,
	              lnVR=.[[5]][[1]]$b, lnVR_lower=.[[5]][[1]]$ci.lb, lnVR_upper=.[[5]][[1]]$ci.ub, lnVR_se=.[[5]][[1]]$se,
		        lnRR=.[[6]][[1]]$b, lnRR_lower=.[[6]][[1]]$ci.lb, lnRR_upper=.[[6]][[1]]$ci.ub, lnRR_se=.[[6]][[1]]$se) )[, c(1,7:18)]

Physiology <- as.data.frame(overall1 %>% filter(., GroupingTerm == "Physiology")  %>%  mutate(lnCVR=.[[4]][[1]]$b, lnCVR_lower=.[[4]][[1]]$ci.lb, lnCVR_upper=.[[4]][[1]]$ci.ub, lnCVR_se=.[[4]][[1]]$se,
	              lnVR=.[[5]][[1]]$b, lnVR_lower=.[[5]][[1]]$ci.lb, lnVR_upper=.[[5]][[1]]$ci.ub, lnVR_se=.[[5]][[1]]$se,
		        lnRR=.[[6]][[1]]$b, lnRR_lower=.[[6]][[1]]$ci.lb, lnRR_upper=.[[6]][[1]]$ci.ub, lnRR_se=.[[6]][[1]]$se) )[, c(1,7:18)]

Metabolism <- as.data.frame(overall1 %>% filter(., GroupingTerm == "Metabolism")  %>%  mutate(lnCVR=.[[4]][[1]]$b, lnCVR_lower=.[[4]][[1]]$ci.lb, lnCVR_upper=.[[4]][[1]]$ci.ub, lnCVR_se=.[[4]][[1]]$se,
	              lnVR=.[[5]][[1]]$b, lnVR_lower=.[[5]][[1]]$ci.lb, lnVR_upper=.[[5]][[1]]$ci.ub, lnVR_se=.[[5]][[1]]$se,
		        lnRR=.[[6]][[1]]$b, lnRR_lower=.[[6]][[1]]$ci.lb, lnRR_upper=.[[6]][[1]]$ci.ub, lnRR_se=.[[6]][[1]]$se) )[, c(1,7:18)]

Morphology <- as.data.frame(overall1 %>% filter(., GroupingTerm == "Morphology")  %>%  mutate(lnCVR=.[[4]][[1]]$b, lnCVR_lower=.[[4]][[1]]$ci.lb, lnCVR_upper=.[[4]][[1]]$ci.ub, lnCVR_se=.[[4]][[1]]$se,
	              lnVR=.[[5]][[1]]$b, lnVR_lower=.[[5]][[1]]$ci.lb, lnVR_upper=.[[5]][[1]]$ci.ub, lnVR_se=.[[5]][[1]]$se,
		        lnRR=.[[6]][[1]]$b, lnRR_lower=.[[6]][[1]]$ci.lb, lnRR_upper=.[[6]][[1]]$ci.ub, lnRR_se=.[[6]][[1]]$se) )[, c(1,7:18)]

Heart <- as.data.frame(overall1 %>% filter(., GroupingTerm == "Heart")  %>%  mutate(lnCVR=.[[4]][[1]]$b, lnCVR_lower=.[[4]][[1]]$ci.lb, lnCVR_upper=.[[4]][[1]]$ci.ub, lnCVR_se=.[[4]][[1]]$se,
	              lnVR=.[[5]][[1]]$b, lnVR_lower=.[[5]][[1]]$ci.lb, lnVR_upper=.[[5]][[1]]$ci.ub, lnVR_se=.[[5]][[1]]$se,
		        lnRR=.[[6]][[1]]$b, lnRR_lower=.[[6]][[1]]$ci.lb, lnRR_upper=.[[6]][[1]]$ci.ub, lnRR_se=.[[6]][[1]]$se) )[, c(1,7:18)]

Eye <- as.data.frame(overall1 %>% filter(., GroupingTerm == "Eye")  %>%  mutate(lnCVR=.[[4]][[1]]$b, lnCVR_lower=.[[4]][[1]]$ci.lb, lnCVR_upper=.[[4]][[1]]$ci.ub, lnCVR_se=.[[4]][[1]]$se,
	              lnVR=.[[5]][[1]]$b, lnVR_lower=.[[5]][[1]]$ci.lb, lnVR_upper=.[[5]][[1]]$ci.ub, lnVR_se=.[[5]][[1]]$se,
		        lnRR=.[[6]][[1]]$b, lnRR_lower=.[[6]][[1]]$ci.lb, lnRR_upper=.[[6]][[1]]$ci.ub, lnRR_se=.[[6]][[1]]$se) )[, c(1,7:18)]

All <- as.data.frame(overall_all1  %>%  mutate(lnCVR=.[[2]][[1]]$b, lnCVR_lower=.[[2]][[1]]$ci.lb, lnCVR_upper=.[[2]][[1]]$ci.ub, lnCVR_se=.[[2]][[1]]$se,lnVR=.[[3]][[1]]$b, lnVR_lower=.[[3]][[1]]$ci.lb, lnVR_upper=.[[3]][[1]]$ci.ub, lnVR_se=.[[3]][[1]]$se,
		        lnRR=.[[4]][[1]]$b, lnRR_lower=.[[4]][[1]]$ci.lb, lnRR_upper=.[[4]][[1]]$ci.ub, lnRR_se=.[[4]][[1]]$se) )[, c(5:16)]

All$lnCVR <- as.numeric(All$lnCVR)
All$lnVR <- as.numeric(All$lnVR)
All$lnRR <- as.numeric(All$lnRR)
All <- All %>% mutate(GroupingTerm = "All")

overall2 <- bind_rows(Behaviour, Morphology, Metabolism, Physiology, Immunology, Hematology, Heart, Hearing, Eye, All)

```

# PLOTS

## Plot FIGURE 2 (First-order meta analysis results)

Re-order grouping terms

```{r}

meta_clean$GroupingTerm <- factor(meta_clean$GroupingTerm, levels =c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye") )
meta_clean$GroupingTerm <- factor(meta_clean$GroupingTerm, rev(levels(meta_clean$GroupingTerm)))

# *Prepare data for all traits

meta.plot2.all <- meta_clean %>% select(lnCVR, lnVR, lnRR, GroupingTerm) %>% arrange(GroupingTerm)

meta.plot2.all.b <- gather(meta.plot2.all, trait, value, c(lnCVR, lnVR, lnRR))

meta.plot2.all.b$trait <- factor(meta.plot2.all.b$trait, levels =c("lnCVR","lnVR","lnRR") )

meta.plot2.all.c <- meta.plot2.all.b  %>%
				group_by_at(vars(trait, GroupingTerm)) %>%
				summarise(malebias = sum(value > 0), femalebias = sum(value<= 0), total= malebias + femalebias, 
					malepercent = malebias*100/total, femalepercent = femalebias*100/total)

meta.plot2.all.c$label <- "All traits"

# restructure to create stacked bar plots

meta.plot2.all.d <- as.data.frame(meta.plot2.all.c)
meta.plot2.all.e <- gather(meta.plot2.all.d, key = sex, value = percent, malepercent:femalepercent, factor_key = TRUE)

# create new sample size variable

meta.plot2.all.e$samplesize <- with(meta.plot2.all.e, ifelse(sex == "malepercent", malebias, femalebias) )

malebias_Fig2_alltraits <- 
ggplot(meta.plot2.all.e) +
  aes(x = GroupingTerm, y = percent, fill = sex) +
  geom_col() +
  geom_hline(yintercept = 50, linetype = "dashed", color = "gray40") +
  geom_text(data = subset(meta.plot2.all.e, samplesize != 0), aes(label = samplesize), position = position_stack(vjust = .5), 
	color = "white", size = 3.5) +
 facet_grid(cols = vars(trait), rows = vars(label),  labeller = label_wrap_gen(width = 18), 
      scales= 'free', space='free') +
 scale_fill_brewer(palette = "Set2") +
theme_bw(base_size = 18) +
  	theme(strip.text.y = element_text(angle = 270, size = 10, margin = margin(t=15, r=15, b=15, l=15)), 
	  strip.text.x = element_text(size = 12),
        strip.background = element_rect(colour = NULL,linetype = "blank", fill = "gray90"),
        text = element_text(size=14),
        panel.spacing = unit(0.5, "lines"),
        panel.border= element_blank(),
        axis.line=element_line(), 
        panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
        panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
        panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(), 
        legend.position = "none",
        axis.title.x = element_blank(),
	  axis.title.y = element_blank()  ) +
	coord_flip()

#malebias_Fig2_alltraits

```

### Prepare data for traits with CI not overlapping 0
create column with 1= different from zero, 0= zero included in CI
```{r}

meta.plot2.sig <- meta_clean %>% 
    mutate(lnCVRsig = ifelse(lnCVR_lower*lnCVR_upper >0, 1, 0), lnVRsig = ifelse(lnVR_lower*lnVR_upper >0, 1, 0), 
	     lnRRsig = ifelse(lnRR_lower*lnRR_upper > 0, 1,0))

meta.plot2.sig.b <- meta.plot2.sig[, c("lnCVR", "lnVR", "lnRR", "lnCVRsig", "lnVRsig", "lnRRsig", "GroupingTerm")]

meta.plot2.sig.c <- gather(meta.plot2.sig.b, trait, value, lnCVR:lnRR)
meta.plot2.sig.c$sig <- "placeholder"

meta.plot2.sig.c$trait <- factor(meta.plot2.sig.c$trait, levels =c("lnCVR","lnVR","lnRR") )

meta.plot2.sig.c$sig <- ifelse(meta.plot2.sig.c$trait == "lnCVR", meta.plot2.sig.c$lnCVRsig,
				ifelse(meta.plot2.sig.c$trait == "lnVR", meta.plot2.sig.c$lnVRsig, meta.plot2.sig.c$lnRRsig))

#choosing sex biased ln-ratios significantly larger than 0
meta.plot2.sig.malebias <- meta.plot2.sig.c %>%
				group_by_at(vars(trait, GroupingTerm)) %>%
				filter(sig== 1) %>%
				summarise(male_sig = sum(value > 0), female_sig = sum(value < 0), total = male_sig + female_sig)

meta.plot2.sig.malebias <- ungroup(meta.plot2.sig.malebias) %>%
				add_row(trait = "lnCVR", GroupingTerm = "Hearing", male_sig = 0, female_sig = 0, .before = 4) %>% #add "Hearing" for lnCVR (not filtered as only zeros)
				mutate(malepercent = male_sig*100 / total, femalepercent = female_sig*100 / total)

meta.plot2.sig.malebias$label <- "CI not overlapping zero"

# restructure to create stacked bar plots

meta.plot2.sig.bothsexes <- as.data.frame(meta.plot2.sig.malebias)
meta.plot2.sig.bothsexes.b <- gather(meta.plot2.sig.bothsexes, key = sex, value = percent, malepercent:femalepercent, factor_key = TRUE)

# create new sample size variable

meta.plot2.sig.bothsexes.b$samplesize <- with(meta.plot2.sig.bothsexes.b, ifelse(sex == "malepercent", male_sig, female_sig) )

# *Plot Fig2 all significant results (CI not overlapping zero): 
#     no sig. lnCVR for 'Hearing' in either sex; no sig. male-biased lnCVR for 'Immunology' and 'Eye, and no sig. male-biased lnVR for 'Eye'

malebias_Fig2_sigtraits <-  
ggplot(meta.plot2.sig.bothsexes.b) +
  aes(x = GroupingTerm, y = percent, fill = sex) +
  geom_col() +
  geom_hline(yintercept = 50, linetype = "dashed", color = "gray40") +
  geom_text(data = subset(meta.plot2.sig.bothsexes.b, samplesize != 0), aes(label = samplesize), position = position_stack(vjust = .5), 
	color = "white", size = 3.5) +
 facet_grid(cols = vars(trait), rows = vars(label),  labeller = label_wrap_gen(width = 18), 
      scales= 'free', space='free') +
 scale_fill_brewer(palette = "Set2") +
theme_bw(base_size = 18) +
  	theme(strip.text.y = element_text(angle = 270, size = 10, margin = margin(t=15, r=15, b=15, l=15)), 
	  strip.text.x = element_blank(),
        strip.background = element_rect(colour = NULL,linetype = "blank", fill = "gray90"),
        text = element_text(size=14),
        panel.spacing = unit(0.5, "lines"),
        panel.border= element_blank(),
        axis.line=element_line(), 
        panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
        panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
        panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(), 
        legend.position = "none",
        axis.title.x = element_blank(),
	  axis.title.y = element_blank()  ) +
	coord_flip()
```

Prepare data for traits with effect size ratios > 10% larger in males
```{r}
meta.plot2.over10 <- meta_clean %>% select(lnCVR, lnVR, lnRR, GroupingTerm) %>% arrange(GroupingTerm)

meta.plot2.over10.b <- gather(meta.plot2.over10, trait, value, c(lnCVR, lnVR, lnRR))

meta.plot2.over10.b$trait <- factor(meta.plot2.over10.b$trait, levels =c("lnCVR","lnVR","lnRR") )

meta.plot2.over10.c <- meta.plot2.over10.b  %>%
				group_by_at(vars(trait, GroupingTerm)) %>%
				summarise(malebias = sum(value > log(11/10)), femalebias = sum(value < log(9/10)), total= malebias + femalebias, 
					malepercent = malebias*100/total, femalepercent = femalebias*100/total)

meta.plot2.over10.c$label <- "Sex difference in m/f ratios > 10%"

# restructure to create stacked bar plots

meta.plot2.over10.c <- as.data.frame(meta.plot2.over10.c)
meta.plot2.over10.d <- gather(meta.plot2.over10.c, key = sex, value = percent, malepercent:femalepercent, factor_key = TRUE)

# create new sample size variable

meta.plot2.over10.d$samplesize <- with(meta.plot2.over10.d, ifelse(sex == "malepercent", malebias, femalebias) )

# *Plot Fig2 Sex difference in m/f ratio > 10%
malebias_Fig2_over10 <- 
ggplot(meta.plot2.over10.d) +
  aes(x = GroupingTerm, y = percent, fill = sex) +
  geom_col() +
  geom_hline(yintercept = 50, linetype = "dashed", color = "gray40") +
  geom_text(data = subset(meta.plot2.over10.d, samplesize != 0), aes(label = samplesize), position = position_stack(vjust = .5), 
	color = "white", size = 3.5) +
 facet_grid(cols = vars(trait), rows = vars(label),  labeller = label_wrap_gen(width = 18), 
      scales= 'free', space='free') +
 scale_fill_brewer(palette = "Set2") +
theme_bw(base_size = 18) +
  	theme(strip.text.y = element_text(angle = 270, size = 10, margin = margin(t=15, r=15, b=15, l=15)), 
	  strip.text.x = element_blank(),
        strip.background = element_rect(colour = NULL,linetype = "blank", fill = "gray90"),
        text = element_text(size=14),
        panel.spacing = unit(0.5, "lines"),
        panel.border= element_blank(),
        axis.line=element_line(), 
        panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
        panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
        panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(), 
        legend.position = "none",
        axis.title.x = element_blank(),
	  axis.title.y = element_blank()  ) +
	coord_flip()
#malebias_Fig2_over10

```
### Create final combined Figure (Figure 2)
```{r}

Fig2 <- ggarrange(malebias_Fig2_alltraits, malebias_Fig2_sigtraits,malebias_Fig2_over10, nrow = 3, align = "v", heights = c(1.22,1,1))
Fig2
#ggsave("Fig2.pdf", plot = Fig2, width = 6, height = 5) 
```

## Preparation, for Figure 3: Overall results of second order meta anlaysis
### Restructure data for plotting 
Data are restructred, and grouping terms are being re-ordered
```{r}
overall3 <- gather(overall2, parameter, value, c(lnCVR, lnVR, lnRR), factor_key= TRUE)

lnCVR.ci <- overall3 %>% filter(parameter == "lnCVR") %>% mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
lnVR.ci <- overall3 %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
lnRR.ci <- overall3 %>% filter(parameter == "lnRR") %>% mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)

overall4 <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)

# re-order Grouping Terms

overall4$GroupingTerm <- factor(overall4$GroupingTerm, levels =c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye", "All") )
overall4$GroupingTerm <- factor(overall4$GroupingTerm, rev(levels(overall4$GroupingTerm)))
overall4$label <- "All traits"

kable(cbind(overall4, overall4)) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "200px")

```

### Plot FIGURE 3 (Second-order meta analysis results)

Preparation: Sub-Plot  for Figure 3: all traits
```{r}

Metameta_Fig3_alltraits <- overall4 %>%

  ggplot(aes(y= GroupingTerm, x= value)) +
  geom_errorbarh(aes(xmin = ci.low, 
                     xmax = ci.high), 
			   height = 0.1, show.legend = FALSE) +
  geom_point(aes(shape = parameter), fill = 'black',
             color = 'black', size = 2.2, 
             show.legend = FALSE) +
  scale_x_continuous(limits=c(-0.24, 0.25), 
                     breaks = c(-0.2, -0.1, 0, 0.1, 0.2), 
                     name='Effect size') +
  geom_vline(xintercept=0, 
             color='black', 
             linetype='dashed')+
  facet_grid(cols = vars(parameter), rows = vars(label),
             labeller = label_wrap_gen(width = 23),
             scales= 'free', 
             space='free')+
  theme_bw()+
  theme(strip.text.y = element_text(angle = 270, size = 10, margin = margin(t=15, r=15, b=15, l=15)), 
	  strip.text.x = element_text(size = 12),
        strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
        text = element_text(size = 14),
        panel.spacing = unit(0.5, "lines"),
        panel.border= element_blank(),
        axis.line=element_line(), 
        panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
        panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
        panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(), 
        legend.title = element_blank(),
        axis.title.x = element_blank(),
	  axis.title.y = element_blank())

#Metameta_Fig3_alltraits

```

########

### Prepare data for traits with CI not overlapping 0

create column with 1= different from zero, 0= zero included in CI
Male-biased (significant) traits
```{r}
meta.male.plot3.sig <- metacombo %>% 
    	mutate(sigCVR = ifelse(lnCVR_lower > 0, 1, 0),
	sigVR = ifelse(lnVR_lower > 0, 1, 0),
	sigRR = ifelse(lnRR_lower > 0, 1, 0))

#Significant subset for lnCVR
metacombo_male.plot3.CVR <- meta.male.plot3.sig %>%
 filter(sigCVR == 1) %>%
 group_by(GroupingTerm) %>%
 nest()

metacombo_male.plot3.CVR.all <- meta.male.plot3.sig %>%
 filter(sigCVR == 1) %>%
 nest()

#Significant subset for lnVR
metacombo_male.plot3.VR <- meta.male.plot3.sig %>%
 filter(sigVR == 1) %>%
 group_by(GroupingTerm) %>%
 nest()

metacombo_male.plot3.VR.all <- meta.male.plot3.sig %>%
 filter(sigVR == 1) %>%
 nest()

#Significant subset for lnRR
metacombo_male.plot3.RR <- meta.male.plot3.sig %>%
 filter(sigRR == 1) %>%
 group_by(GroupingTerm) %>%
 nest()

metacombo_male.plot3.RR.all <- meta.male.plot3.sig %>%
 filter(sigRR == 1) %>%
 nest()

# **Final fixed effects meta-analyses within grouping terms, with SE of the estimate

plot3.male.meta.CVR <- metacombo_male.plot3.CVR %>% 
  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower)/ (2*1.96),  
				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )

plot3.male.meta.VR <- metacombo_male.plot3.VR %>% 
  mutate(model_lnVR = map(data, ~ metafor::rma.uni(yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower)/ (2*1.96),  
				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )

plot3.male.meta.RR <- metacombo_male.plot3.RR %>% 
  mutate(model_lnRR = map(data, ~ metafor::rma.uni(yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower)/ (2*1.96),  
				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )

# Across all grouping terms #

plot3.male.meta.CVR.all <- metacombo_male.plot3.CVR.all %>% 
  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower)/ (2*1.96),  
				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )

plot3.male.meta.CVR.all <- plot3.male.meta.CVR.all %>% mutate(GroupingTerm = "All")

plot3.male.meta.VR.all <- metacombo_male.plot3.VR.all %>% 
  mutate(model_lnVR = map(data, ~ metafor::rma.uni(yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower)/ (2*1.96),  
				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )

plot3.male.meta.VR.all <- plot3.male.meta.VR.all %>% mutate(GroupingTerm = "All")

plot3.male.meta.RR.all <- metacombo_male.plot3.RR.all %>% 
  mutate(model_lnRR = map(data, ~ metafor::rma.uni(yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower)/ (2*1.96),  
				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )

plot3.male.meta.RR.all <- plot3.male.meta.RR.all %>% mutate(GroupingTerm = "All")

# Combine with separate grouping term results

plot3.male.meta.CVR <- bind_rows(plot3.male.meta.CVR, plot3.male.meta.CVR.all)
plot3.male.meta.VR <- bind_rows(plot3.male.meta.VR, plot3.male.meta.VR.all)
plot3.male.meta.RR <- bind_rows(plot3.male.meta.RR, plot3.male.meta.RR.all)

# **Re-structure data for each grouping term; delete un-used variables

plot3.male.meta.CVR.b <- as.data.frame(plot3.male.meta.CVR %>% group_by(GroupingTerm) %>%  
		mutate(lnCVR = map_dbl(model_lnCVR, pluck(2)), lnCVR_lower = map_dbl(model_lnCVR, pluck(6)), 
		lnCVR_upper =map_dbl(model_lnCVR, pluck(7)), lnCVR_se =map_dbl(model_lnCVR, pluck(3))) )[, c(1,4:7)] 
add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.male.meta.CVR.b))

plot3.male.meta.CVR.b <- bind_rows(plot3.male.meta.CVR.b, add.row.hearing) 
plot3.male.meta.CVR.b <- plot3.male.meta.CVR.b[order(plot3.male.meta.CVR.b$GroupingTerm),]

plot3.male.meta.VR.b <- as.data.frame(plot3.male.meta.VR %>% group_by(GroupingTerm) %>%  
	mutate(lnVR = map_dbl(model_lnVR, pluck(2)), lnVR_lower = map_dbl(model_lnVR, pluck(6)), 
	lnVR_upper =map_dbl(model_lnVR, pluck(7)), lnVR_se =map_dbl(model_lnVR, pluck(3))) )[, c(1,4:7)] 
plot3.male.meta.VR.b <- plot3.male.meta.VR.b[order(plot3.male.meta.VR.b$GroupingTerm),]

plot3.male.meta.RR.b <- as.data.frame(plot3.male.meta.RR %>% group_by(GroupingTerm) %>%  
	mutate(lnRR = map_dbl(model_lnRR, pluck(2)), lnRR_lower = map_dbl(model_lnRR, pluck(6)), 
	lnRR_upper =map_dbl(model_lnRR, pluck(7)), lnRR_se =map_dbl(model_lnRR, pluck(3))) )[, c(1,4:7)] 
plot3.male.meta.RR.b <- plot3.male.meta.RR.b[order(plot3.male.meta.RR.b$GroupingTerm),]

overall.male.plot3 <- inner_join(plot3.male.meta.CVR.b, plot3.male.meta.VR.b) 
overall.male.plot3 <- inner_join(overall.male.plot3, plot3.male.meta.RR.b)

overall.male.plot3$GroupingTerm <- factor(overall.male.plot3$GroupingTerm, levels =c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye", "All") )
overall.male.plot3$GroupingTerm <- factor(overall.male.plot3$GroupingTerm, rev(levels(overall.male.plot3$GroupingTerm)))

#add missing GroupingTerms for plot
overall.male.plot3 <- add_row(overall.male.plot3, GroupingTerm = "Behaviour")
overall.male.plot3 <- add_row(overall.male.plot3, GroupingTerm = "Immunology")
overall.male.plot3 <- add_row(overall.male.plot3, GroupingTerm = "Eye")

overall.male.plot3$GroupingTerm <- factor(overall.male.plot3$GroupingTerm, levels =c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye", "All") )
overall.male.plot3$GroupingTerm <- factor(overall.male.plot3$GroupingTerm, rev(levels(overall.male.plot3$GroupingTerm)))

```

Restructure MALE data for plotting 
```{r}
overall3.male.sig <- gather(overall.male.plot3, parameter, value, c(lnCVR, lnVR, lnRR), factor_key= TRUE)

lnCVR.ci <- overall3.male.sig  %>% filter(parameter == "lnCVR") %>% mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
lnVR.ci <- overall3.male.sig  %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
lnRR.ci <- overall3.male.sig  %>% filter(parameter == "lnRR") %>% mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)

overall4.male.sig <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)

overall4.male.sig$label <- "CI not overlapping zero"

```

Plot Fig3 all significant results (CI not overlapping zero) for males
```{r}
######

Metameta_Fig3_male.sig <- overall4.male.sig %>%
  ggplot(aes(y= GroupingTerm, x= value)) +
  geom_errorbarh(aes(xmin = ci.low, 
                     xmax = ci.high), 
			   height = 0.1, show.legend = FALSE) +
  geom_point(aes(shape = parameter),
             fill = 'mediumaquamarine', color = 'mediumaquamarine', size = 2.2, 
               show.legend = FALSE) +
  scale_x_continuous(limits=c(0, 0.4), 
                     breaks = c(0, 0.3), 
                     name='Effect size') +
  geom_vline(xintercept=0, 
             color='black', 
             linetype='dashed')+
  facet_grid(cols = vars(parameter), rows = vars(label),
             labeller = label_wrap_gen(width = 23),
             scales= 'free', 
             space='free')+
  theme_bw()+
  theme(strip.text.y = element_text(angle = 270, size = 10, margin = margin(t=15, r=15, b=15, l=15)), 
	  strip.text.x = element_text(size = 12),
        strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
        text = element_text(size = 14),
        panel.spacing = unit(0.5, "lines"),
        panel.border= element_blank(),
        axis.line=element_line(), 
        panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
        panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
        panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(), 
        legend.title = element_blank(),
        axis.title.x = element_blank(),
	  axis.title.y = element_blank())

#Metameta_Fig3_male.sig

```

#######################
### Female Figure
Female Fig3 sig

Prepare data for traits with CI not overlapping 0
create column with 1= different from zero, 0= zero included in CI
```{r}

# female-biased traits

meta.female.plot3.sig <- metacombo %>%
              mutate(sigCVR = ifelse(lnCVR_upper < 0, 1, 0),
              sigVR = ifelse(lnVR_upper < 0, 1, 0),
              sigRR = ifelse(lnRR_upper < 0, 1, 0))

#Significant subset for lnCVR

metacombo_female.plot3.CVR <- meta.female.plot3.sig %>%
filter(sigCVR == 1) %>%
group_by(GroupingTerm) %>%
nest()

metacombo_female.plot3.CVR.all <- meta.female.plot3.sig %>%
 filter(sigCVR == 1) %>%
 nest()

#Significant subset for lnVR

metacombo_female.plot3.VR <- meta.female.plot3.sig %>%
filter(sigVR == 1) %>%
group_by(GroupingTerm) %>%
nest()

metacombo_female.plot3.VR.all <- meta.female.plot3.sig %>%
 filter(sigVR == 1) %>%
 nest()

#Significant subset for lnRR

metacombo_female.plot3.RR <- meta.female.plot3.sig %>%
filter(sigRR == 1) %>%
group_by(GroupingTerm) %>%
nest()

metacombo_female.plot3.RR.all <- meta.female.plot3.sig %>%
 filter(sigRR == 1) %>%
 nest()

# **Final fixed effects meta-analyses within grouping terms, with SE of the estimate

plot3.female.meta.CVR <- metacombo_female.plot3.CVR %>%
  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower)/ (2*1.96), 
                                 control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )

plot3.female.meta.VR <- metacombo_female.plot3.VR %>%
  mutate(model_lnVR = map(data, ~ metafor::rma.uni(yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower)/ (2*1.96), 
    					   control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )

plot3.female.meta.RR <- metacombo_female.plot3.RR %>%
  mutate(model_lnRR = map(data, ~ metafor::rma.uni(yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower)/ (2*1.96), 
                                 control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )

# Across all grouping terms #

plot3.female.meta.CVR.all <- metacombo_female.plot3.CVR.all %>% 
  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower)/ (2*1.96),  
				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )

plot3.female.meta.CVR.all <- plot3.female.meta.CVR.all %>% mutate(GroupingTerm = "All")

plot3.female.meta.VR.all <- metacombo_female.plot3.VR.all %>% 
  mutate(model_lnVR = map(data, ~ metafor::rma.uni(yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower)/ (2*1.96),  
				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )

plot3.female.meta.VR.all <- plot3.female.meta.VR.all %>% mutate(GroupingTerm = "All")

plot3.female.meta.RR.all <- metacombo_female.plot3.RR.all %>% 
  mutate(model_lnRR = map(data, ~ metafor::rma.uni(yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower)/ (2*1.96),  
				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )

plot3.female.meta.RR.all <- plot3.female.meta.RR.all %>% mutate(GroupingTerm = "All")

# Combine with separate grouping term results

plot3.female.meta.CVR <- bind_rows(plot3.female.meta.CVR, plot3.female.meta.CVR.all)
plot3.female.meta.VR <- bind_rows(plot3.female.meta.VR, plot3.female.meta.VR.all)
plot3.female.meta.RR <- bind_rows(plot3.female.meta.RR, plot3.female.meta.RR.all)

# **Re-structure data for each grouping term; delete un-used variables

plot3.female.meta.CVR.b <- as.data.frame(plot3.female.meta.CVR %>% group_by(GroupingTerm) %>% 
                             mutate(lnCVR = map_dbl(model_lnCVR, pluck(2)), lnCVR_lower = map_dbl(model_lnCVR, pluck(6)),
                             lnCVR_upper =map_dbl(model_lnCVR, pluck(7)), lnCVR_se =map_dbl(model_lnCVR, pluck(3))) )[, c(1,4:7)]

add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.female.meta.CVR.b))

plot3.female.meta.CVR.b <- bind_rows(plot3.female.meta.CVR.b, add.row.hearing)
plot3.female.meta.CVR.b <- plot3.female.meta.CVR.b[order(plot3.female.meta.CVR.b$GroupingTerm),]

plot3.female.meta.VR.b <- as.data.frame(plot3.female.meta.VR %>% group_by(GroupingTerm) %>% 
              mutate(lnVR = map_dbl(model_lnVR, pluck(2)), lnVR_lower = map_dbl(model_lnVR, pluck(6)),
              lnVR_upper =map_dbl(model_lnVR, pluck(7)), lnVR_se =map_dbl(model_lnVR, pluck(3))) )[, c(1,4:7)]

plot3.female.meta.VR.b <- plot3.female.meta.VR.b[order(plot3.female.meta.VR.b$GroupingTerm),]

plot3.female.meta.RR.b <- as.data.frame(plot3.female.meta.RR %>% group_by(GroupingTerm) %>% 
              mutate(lnRR = map_dbl(model_lnRR, pluck(2)), lnRR_lower = map_dbl(model_lnRR, pluck(6)),
              lnRR_upper =map_dbl(model_lnRR, pluck(7)), lnRR_se =map_dbl(model_lnRR, pluck(3))) )[, c(1,4:7)]

plot3.female.meta.RR.b <- plot3.female.meta.RR.b[order(plot3.female.meta.RR.b$GroupingTerm),]

overall.female.plot3 <- full_join(plot3.female.meta.CVR.b, plot3.female.meta.VR.b)
overall.female.plot3 <- full_join(overall.female.plot3, plot3.female.meta.RR.b)

overall.female.plot3$GroupingTerm <- factor(overall.female.plot3$GroupingTerm, levels =c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye", "All") )
overall.female.plot3$GroupingTerm <- factor(overall.female.plot3$GroupingTerm, rev(levels(overall.female.plot3$GroupingTerm)))

#add missing GroupingTerms for plot POYTENTIALLY DELETE
#overall.female.plot3 <- add_row(overall.female.plot3, GroupingTerm = "Morphology")
#overall.female.plot3 <- add_row(overall.female.plot3, GroupingTerm = "Metabolism")
#overall.female.plot3 <- add_row(overall.female.plot3, GroupingTerm = "Hematology")
#overall.female.plot3 <- add_row(overall.female.plot3, GroupingTerm = "Hearing")
#overall.female.plot3 <- add_row(overall.female.plot3, GroupingTerm = "Eye")

#overall.female.plot3$GroupingTerm <- factor(overall.female.plot3$GroupingTerm, levels =c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye", "All") )
#overall.female.plot3$GroupingTerm <- factor(overall.female.plot3$GroupingTerm, rev(levels(overall.female.plot3$GroupingTerm)))

```

Restructure data for plotting

```{r}
overall3.female.sig <- gather(overall.female.plot3, parameter, value, c(lnCVR, lnVR, lnRR), factor_key= TRUE)

lnCVR.ci <- overall3.female.sig  %>% filter(parameter == "lnCVR") %>% mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
lnVR.ci <- overall3.female.sig  %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
lnRR.ci <- overall3.female.sig  %>% filter(parameter == "lnRR") %>% mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)

overall4.female.sig <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)

overall4.female.sig$label <- "CI not overlapping zero"

```

### Plot Fig3 all significant results (CI not overlapping zero, female )
```{r}

Metameta_Fig3_female.sig <- overall4.female.sig %>%
  ggplot(aes(y= GroupingTerm, x= value)) +
  geom_errorbarh(aes(xmin = ci.low,
                     xmax = ci.high),
                     height = 0.1, show.legend = FALSE) +
  geom_point(aes(shape = parameter),
             fill = 'salmon1', color = 'salmon1', size = 2.2,
             show.legend = FALSE) +
  scale_x_continuous(limits=c(-0.4, 0),
                     breaks = c(-0.3 ,0),
                     name='Effect size') +
  geom_vline(xintercept=0,
             color='black',
             linetype='dashed')+
  facet_grid(cols = vars(parameter), #rows = vars(label),
             #labeller = label_wrap_gen(width = 23),
             scales= 'free',
             space='free')+
  theme_bw()+
  theme(strip.text.y = element_text(angle = 270, size = 10, margin = margin(t=15, r=15, b=15, l=15)),
                strip.text.x = element_text(size = 12),
        strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
        text = element_text(size = 14),
        panel.spacing = unit(0.5, "lines"),
        panel.border= element_blank(),
        axis.line=element_line(),
        panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
        panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
        panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(),
        legend.title = element_blank(),
        axis.title.x = element_blank(),
                axis.title.y = element_blank())

#Metameta_Fig3_female.sig
```
#######################

### Fig3 >10%

Prepare data for traits with m/f difference > 10%

create column with 1= larger, 0= diff not larger than 10%

### Male Fig 3 > 10% (male biased traits)
```{r}
meta.male.plot3.perc <- metacombo %>% 
    	mutate(percCVR = ifelse(lnCVR > log (11/10), 1, 0),			
	percVR = ifelse(lnVR > log (11/10), 1, 0),
	percRR = ifelse(lnRR > log (11/10), 1, 0))

#Significant subset for lnCVR
metacombo_male.plot3.CVR.perc <- meta.male.plot3.perc %>%
 filter(percCVR == 1) %>%
 group_by(GroupingTerm) %>%
 nest()

metacombo_male.plot3.CVR.perc.all <- meta.male.plot3.perc %>%
 filter(percCVR == 1) %>%
 nest()

#Significant subset for lnVR
metacombo_male.plot3.VR.perc <- meta.male.plot3.perc %>%
 filter(percVR == 1) %>%
 group_by(GroupingTerm) %>%
 nest()

metacombo_male.plot3.VR.perc.all <- meta.male.plot3.perc %>%
 filter(percVR == 1) %>%
 nest()

#Significant subset for lnRR
metacombo_male.plot3.RR.perc <- meta.male.plot3.perc %>%
 filter(percRR == 1) %>%
 group_by(GroupingTerm) %>%
 nest()

metacombo_male.plot3.RR.perc.all <- meta.male.plot3.perc %>%
 filter(percRR == 1) %>%
 nest()

# **Final fixed effects meta-analyses within grouping terms and across grouping terms, with SE of the estimate

plot3.male.meta.CVR.perc <- metacombo_male.plot3.CVR.perc %>% 
  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower)/ (2*1.96),  
				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )

plot3.male.meta.VR.perc <- metacombo_male.plot3.VR.perc %>% 
  mutate(model_lnVR = map(data, ~ metafor::rma.uni(yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower)/ (2*1.96),  
				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )

plot3.male.meta.RR.perc <- metacombo_male.plot3.RR.perc %>% 
  mutate(model_lnRR = map(data, ~ metafor::rma.uni(yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower)/ (2*1.96),  
				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )

# Across all grouping terms #

plot3.male.meta.CVR.perc.all <- metacombo_male.plot3.CVR.perc.all %>% 
  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower)/ (2*1.96),  
				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )

plot3.male.meta.CVR.perc.all <- plot3.male.meta.CVR.perc.all %>% mutate(GroupingTerm = "All")

plot3.male.meta.VR.perc.all <- metacombo_male.plot3.VR.perc.all %>% 
  mutate(model_lnVR = map(data, ~ metafor::rma.uni(yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower)/ (2*1.96),  
				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )

plot3.male.meta.VR.perc.all <- plot3.male.meta.VR.perc.all %>% mutate(GroupingTerm = "All")

plot3.male.meta.RR.perc.all <- metacombo_male.plot3.RR.perc.all %>% 
  mutate(model_lnRR = map(data, ~ metafor::rma.uni(yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower)/ (2*1.96),  
				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )

plot3.male.meta.RR.perc.all <- plot3.male.meta.RR.perc.all %>% mutate(GroupingTerm = "All")

# Combine with separate grouping term results

plot3.male.meta.CVR.perc <- bind_rows(plot3.male.meta.CVR.perc, plot3.male.meta.CVR.perc.all)
plot3.male.meta.VR.perc <- bind_rows(plot3.male.meta.VR.perc, plot3.male.meta.VR.perc.all)
plot3.male.meta.RR.perc <- bind_rows(plot3.male.meta.RR.perc, plot3.male.meta.RR.perc.all)

# **Re-structure data for each grouping term; delete un-used variables: "Hearing missing for all 3 parameters"

plot3.male.meta.CVR.perc.b <- as.data.frame(plot3.male.meta.CVR.perc %>% group_by(GroupingTerm) %>%  
		mutate(lnCVR = map_dbl(model_lnCVR, pluck(2)), lnCVR_lower = map_dbl(model_lnCVR, pluck(6)), 
		lnCVR_upper =map_dbl(model_lnCVR, pluck(7)), lnCVR_se =map_dbl(model_lnCVR, pluck(3))) )[, c(1,4:7)] 
add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.male.meta.CVR.perc.b))
plot3.male.meta.CVR.perc.b <- rbind(plot3.male.meta.CVR.perc.b, add.row.hearing) 
plot3.male.meta.CVR.perc.b <- plot3.male.meta.CVR.perc.b[order(plot3.male.meta.CVR.perc.b$GroupingTerm),]

plot3.male.meta.VR.perc.b <- as.data.frame(plot3.male.meta.VR.perc %>% group_by(GroupingTerm) %>%  
	mutate(lnVR = map_dbl(model_lnVR, pluck(2)), lnVR_lower = map_dbl(model_lnVR, pluck(6)), 
	lnVR_upper =map_dbl(model_lnVR, pluck(7)), lnVR_se =map_dbl(model_lnVR, pluck(3))) )[, c(1,4:7)] 
add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.male.meta.VR.perc.b))
plot3.male.meta.VR.perc.b <- rbind(plot3.male.meta.VR.perc.b, add.row.hearing) 
plot3.male.meta.VR.perc.b <- plot3.male.meta.VR.perc.b[order(plot3.male.meta.VR.perc.b$GroupingTerm),]

plot3.male.meta.RR.perc.b <- as.data.frame(plot3.male.meta.RR.perc %>% group_by(GroupingTerm) %>%  
	mutate(lnRR = map_dbl(model_lnRR, pluck(2)), lnRR_lower = map_dbl(model_lnRR, pluck(6)), 
	lnRR_upper =map_dbl(model_lnRR, pluck(7)), lnRR_se =map_dbl(model_lnRR, pluck(3))) )[, c(1,4:7)] 
add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.male.meta.RR.perc.b))
plot3.male.meta.RR.perc.b <- rbind(plot3.male.meta.RR.perc.b, add.row.hearing) 
plot3.male.meta.RR.perc.b <- plot3.male.meta.RR.perc.b[order(plot3.male.meta.RR.perc.b$GroupingTerm),]

overall.male.plot3.perc <- full_join(plot3.male.meta.CVR.perc.b, plot3.male.meta.VR.perc.b) 
overall.male.plot3.perc <- full_join(overall.male.plot3.perc, plot3.male.meta.RR.perc.b)

overall.male.plot3.perc$GroupingTerm <- factor(overall.male.plot3.perc$GroupingTerm, levels =c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye", "All") )
overall.male.plot3.perc$GroupingTerm <- factor(overall.male.plot3.perc$GroupingTerm, rev(levels(overall.male.plot3.perc$GroupingTerm)))

```

Restructure data for plotting : Male biased, 10% difference
```{r}
overall3.perc <- gather(overall.male.plot3.perc, parameter, value, c(lnCVR, lnVR, lnRR), factor_key= TRUE)

lnCVR.ci <- overall3.perc %>% filter(parameter == "lnCVR") %>% mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
lnVR.ci <- overall3.perc  %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
lnRR.ci <- overall3.perc  %>% filter(parameter == "lnRR") %>% mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)

overall4.male.perc <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)

overall4.male.perc$label <- "Sex difference in m/f ratios > 10%"

overall4.male.perc$value <- as.numeric(overall4.male.perc$value)
overall4.male.perc$ci.low  <- as.numeric(overall4.male.perc$ci.low)
overall4.male.perc$ci.high <- as.numeric(overall4.male.perc$ci.high)

```

Plot Fig3 all >10% difference (male bias)
```{r}

Metameta_Fig3_male.perc <- overall4.male.perc %>% filter(., GroupingTerm != "Hearing") %>%
  ggplot(aes(y= GroupingTerm, x= value)) +
  geom_errorbarh(aes(xmin = ci.low, 
                     xmax = ci.high), 
			   height = 0.1, show.legend = FALSE) +
  geom_point(aes(shape = parameter,
             fill = parameter), color = 'mediumaquamarine', size = 2.2, 
             show.legend = FALSE) +
  scale_x_continuous(limits=c(-0.2, 0.62), 
                     breaks = c(0, 0.3), 
                     name='Effect size') +
  geom_vline(xintercept=0, 
             color='black', 
             linetype='dashed')+
  facet_grid(cols = vars(parameter), rows = vars(label),
             labeller = label_wrap_gen(width = 23),
             scales= 'free', 
             space='free')+
  theme_bw()+
  theme(strip.text.y = element_text(angle = 270, size = 10, margin = margin(t=15, r=15, b=15, l=15)), 
	  strip.text.x = element_blank(),
        strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
        text = element_text(size = 14),
        panel.spacing = unit(0.5, "lines"),
        panel.border= element_blank(),
        axis.line=element_line(), 
        panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
        panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
        panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(), 
        legend.title = element_blank(),
        axis.title.x = element_text(hjust = 0.5, size = 14),
	  axis.title.y = element_blank())

# Metameta_Fig3_male.perc
```

##################

Female Fig 3 >10%
```{r}

meta.plot3.perc <- metacombo %>% 
    	mutate(percCVR = ifelse(lnCVR < log (9/10), 1, 0),			
	percVR = ifelse(lnVR < log (9/10), 1, 0),
	percRR = ifelse(lnRR < log (9/10), 1, 0))

#Significant subset for lnCVR
metacombo_plot3.CVR.perc <- meta.plot3.perc %>%
 filter(percCVR == 1) %>%
 group_by(GroupingTerm) %>%
 nest()

metacombo_plot3.CVR.perc.all <- meta.plot3.perc %>%
 filter(percCVR == 1) %>%
 nest()

#Significant subset for lnVR
metacombo_plot3.VR.perc <- meta.plot3.perc %>%
 filter(percVR == 1) %>%
 group_by(GroupingTerm) %>%
 nest()

metacombo_plot3.VR.perc.all <- meta.plot3.perc %>%
 filter(percVR == 1) %>%
 nest()

#Significant subset for lnRR
metacombo_plot3.RR.perc <- meta.plot3.perc %>%
 filter(percRR == 1) %>%
 group_by(GroupingTerm) %>%
 nest()

metacombo_plot3.RR.perc.all <- meta.plot3.perc %>%
 filter(percRR == 1) %>%
 nest()

# **Final fixed effects meta-analyses within grouping terms, with SE of the estimate

plot3.meta.CVR.perc <- metacombo_plot3.CVR.perc %>% 
  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower)/ (2*1.96),  
				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )

plot3.meta.VR.perc <- metacombo_plot3.VR.perc %>% 
  mutate(model_lnVR = map(data, ~ metafor::rma.uni(yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower)/ (2*1.96),  
				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )

plot3.meta.RR.perc <- metacombo_plot3.RR.perc %>% 
  mutate(model_lnRR = map(data, ~ metafor::rma.uni(yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower)/ (2*1.96),  
				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )

# Across all grouping terms #

plot3.meta.CVR.perc.all <- metacombo_plot3.CVR.perc.all %>% 
  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower)/ (2*1.96),  
				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )

plot3.meta.CVR.perc.all <- plot3.meta.CVR.perc.all %>% mutate(GroupingTerm = "All")

plot3.meta.VR.perc.all <- metacombo_plot3.VR.perc.all %>% 
  mutate(model_lnVR = map(data, ~ metafor::rma.uni(yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower)/ (2*1.96),  
				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )

plot3.meta.VR.perc.all <- plot3.meta.VR.perc.all %>% mutate(GroupingTerm = "All")

plot3.meta.RR.perc.all <- metacombo_plot3.RR.perc.all %>% 
  mutate(model_lnRR = map(data, ~ metafor::rma.uni(yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower)/ (2*1.96),  
				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )

plot3.meta.RR.perc.all <- plot3.meta.RR.perc.all %>% mutate(GroupingTerm = "All")

# Combine with separate grouping term results

plot3.meta.CVR.perc <- bind_rows(plot3.meta.CVR.perc, plot3.meta.CVR.perc.all)
plot3.meta.VR.perc <- bind_rows(plot3.meta.VR.perc, plot3.meta.VR.perc.all)
plot3.meta.RR.perc <- bind_rows(plot3.meta.RR.perc, plot3.meta.RR.perc.all)

# **Re-structure data for each grouping term; delete un-used variables: "Hearing missing for all 3 parameters"

plot3.meta.CVR.perc.b <- as.data.frame(plot3.meta.CVR.perc %>% group_by(GroupingTerm) %>%  
		mutate(lnCVR = map_dbl(model_lnCVR, pluck(2)), lnCVR_lower = map_dbl(model_lnCVR, pluck(6)), 
		lnCVR_upper =map_dbl(model_lnCVR, pluck(7)), lnCVR_se =map_dbl(model_lnCVR, pluck(3))) )[, c(1,4:7)] 
add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.meta.CVR.perc.b))
plot3.meta.CVR.perc.b <- rbind(plot3.meta.CVR.perc.b, add.row.hearing) 
plot3.meta.CVR.perc.b <- plot3.meta.CVR.perc.b[order(plot3.meta.CVR.perc.b$GroupingTerm),]

plot3.meta.VR.perc.b <- as.data.frame(plot3.meta.VR.perc %>% group_by(GroupingTerm) %>%  
	mutate(lnVR = map_dbl(model_lnVR, pluck(2)), lnVR_lower = map_dbl(model_lnVR, pluck(6)), 
	lnVR_upper =map_dbl(model_lnVR, pluck(7)), lnVR_se =map_dbl(model_lnVR, pluck(3))) )[, c(1,4:7)] 
add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.meta.VR.perc.b))
plot3.meta.VR.perc.b <- rbind(plot3.meta.VR.perc.b, add.row.hearing) 
plot3.meta.VR.perc.b <- plot3.meta.VR.perc.b[order(plot3.meta.VR.perc.b$GroupingTerm),]

plot3.meta.RR.perc.b <- as.data.frame(plot3.meta.RR.perc %>% group_by(GroupingTerm) %>%  
	mutate(lnRR = map_dbl(model_lnRR, pluck(2)), lnRR_lower = map_dbl(model_lnRR, pluck(6)), 
	lnRR_upper =map_dbl(model_lnRR, pluck(7)), lnRR_se =map_dbl(model_lnRR, pluck(3))) )[, c(1,4:7)] 
add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.meta.RR.perc.b))
plot3.meta.RR.perc.b <- rbind(plot3.meta.RR.perc.b, add.row.hearing) 
plot3.meta.RR.perc.b <- plot3.meta.RR.perc.b[order(plot3.meta.RR.perc.b$GroupingTerm),]

overall.plot3.perc <- full_join(plot3.meta.CVR.perc.b, plot3.meta.VR.perc.b) 
overall.plot3.perc <- full_join(overall.plot3.perc, plot3.meta.RR.perc.b)

overall.plot3.perc$GroupingTerm <- factor(overall.plot3.perc$GroupingTerm, levels =c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye", "All") )
overall.plot3.perc$GroupingTerm <- factor(overall.plot3.perc$GroupingTerm, rev(levels(overall.plot3.perc$GroupingTerm)))

```

### Restructure data for plotting
Female bias, 10 percent difference
```{r}
overall3.perc <- gather(overall.plot3.perc, parameter, value, c(lnCVR, lnVR, lnRR), factor_key= TRUE)

lnCVR.ci <- overall3.perc %>% filter(parameter == "lnCVR") %>% mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
lnVR.ci <- overall3.perc  %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
lnRR.ci <- overall3.perc  %>% filter(parameter == "lnRR") %>% mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)

overall4.perc <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)

overall4.perc$label <- "Sex difference in m/f ratios > 10%"

overall4.perc$value <- as.numeric(overall4.perc$value)
overall4.perc$ci.low  <- as.numeric(overall4.perc$ci.low)
overall4.perc$ci.high <- as.numeric(overall4.perc$ci.high)

```

Plot Fig3 all >10% difference (female)
```{r}
Metameta_Fig3_female.perc <- overall4.perc %>% 
  ggplot(aes(y= GroupingTerm, x= value)) +
  geom_errorbarh(aes(xmin = ci.low, 
                     xmax = ci.high), 
			   height = 0.1, show.legend = FALSE) +
  geom_point(aes(shape = parameter),
             fill = 'salmon1', color = 'salmon1', size = 2.2, 
             show.legend = FALSE) +

#scale_shape_manual(values =

  scale_x_continuous(limits=c(-0.53, 0.2), 
                     breaks = c(-0.3, 0), 
                     name='Effect size') +
  geom_vline(xintercept=0, 
             color='black', 
             linetype='dashed')+
  facet_grid(cols = vars(parameter), #rows = vars(label),
             #labeller = label_wrap_gen(width = 23),
             scales= 'free', 
             space='free')+
  theme_bw()+
  theme(strip.text.y = element_text(angle = 270, size = 10, margin = margin(t=15, r=15, b=15, l=15)), 
	  strip.text.x = element_blank(),
        strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
        text = element_text(size = 14),
        panel.spacing = unit(0.5, "lines"),
        panel.border= element_blank(),
        axis.line=element_line(), 
        panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
        panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
        panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(), 
        legend.title = element_blank(),
        axis.title.x = element_text(hjust = 0.5, size = 14),
	  axis.title.y = element_blank())

#Metameta_Fig3_female.perc

```

# Plot Fig3 all plots combined
```{r}
library(ggpubr)
Fig3.bottom <- ggarrange(Metameta_Fig3_female.sig, Metameta_Fig3_male.sig, Metameta_Fig3_female.perc, Metameta_Fig3_male.perc, 
		   ncol = 2, nrow = 2, widths = c(1, 1.20), heights = c(1, 1))

Fig3 <- ggarrange(Metameta_Fig3_alltraits, Fig3.bottom, ncol = 1, nrow = 2, heights = c(1.4, 2.5))
Fig3
#                     ggsave("Fig3.pdf", plot = Fig3, width = 9, height = 6) 
```

## Plot Supplement FIGURE S1 (Second-order meta-analysis on heterogeneity)

### Create matrix to store results for all traits
```{r}
results.allhetero.grouping <- as.data.frame(cbind(c(1:n), matrix(rep(0, n*30), ncol = 30))) 
names(results.allhetero.grouping) <- c("id", "sigma2_strain.CVR", "sigma2_center.CVR", "sigma2_error.CVR", "s.nlevels.strain.CVR", 
	"s.nlevels.center.CVR", "s.nlevels.error.CVR", "sigma2_strain.VR", "sigma2_center.VR", "sigma2_error.VR", "s.nlevels.strain.VR", 
	"s.nlevels.center.VR", "s.nlevels.error.VR", "sigma2_strain.RR", "sigma2_center.RR", "sigma2_error.RR", "s.nlevels.strain.RR", 
	"s.nlevels.center.RR", "s.nlevels.error.RR", "lnCVR", "lnCVR_lower", "lnCVR_upper", "lnCVR_se", "lnVR", "lnVR_lower", "lnVR_upper", 
	"lnVR_se", "lnRR", "lnRR_lower", "lnRR_upper" ,"lnRR_se")

```

### LOOP

```{r}

for(t in 1:n) {

  tryCatch({

    data_par_age <- data_subset_parameterid_individual_by_age(data, t, age_min = 0, age_center = 100)

    population_stats <- calculate_population_stats(data_par_age)

    results <- create_meta_analysis_effect_sizes(population_stats)

    # lnCVR, logaritm of the ratio of male and female coefficients of variance

    cvr. <- metafor::rma.mv(yi = effect_size_CVR, V = sample_variance_CVR, random = list(~1| strain_name, ~1|production_center,    
                                ~1|err), control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), data = results)
    results.allhetero.grouping[t, 2] <- cvr.$sigma2[1]
    results.allhetero.grouping[t, 3] <- cvr.$sigma2[2]
    results.allhetero.grouping[t, 4] <- cvr.$sigma2[3]
    results.allhetero.grouping[t, 5] <- cvr.$s.nlevels[1]
    results.allhetero.grouping[t, 6] <- cvr.$s.nlevels[2]
    results.allhetero.grouping[t, 7] <- cvr.$s.nlevels[3]
     results.allhetero.grouping[t, 20] <- cvr.$b
     results.allhetero.grouping[t, 21] <- cvr.$ci.lb
     results.allhetero.grouping[t, 22] <- cvr.$ci.ub
     results.allhetero.grouping[t, 23] <- cvr.$se

    # lnVR, male to female variability ratio (logarithm of male and female standard deviations)

    vr. <- metafor::rma.mv(yi = effect_size_VR, V = sample_variance_VR, random = list(~1| strain_name, ~1|production_center,    
                                ~1|err), control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), data = results)
    results.allhetero.grouping[t, 8] <- vr.$sigma2[1]
    results.allhetero.grouping[t, 9] <- vr.$sigma2[2]
    results.allhetero.grouping[t, 10] <- vr.$sigma2[3]
    results.allhetero.grouping[t, 11] <- vr.$s.nlevels[1]
    results.allhetero.grouping[t, 12] <- vr.$s.nlevels[2]
    results.allhetero.grouping[t, 13] <- vr.$s.nlevels[3]
     results.allhetero.grouping[t, 24] <- vr.$b
     results.allhetero.grouping[t, 25] <- vr.$ci.lb
     results.allhetero.grouping[t, 26] <- vr.$ci.ub
     results.allhetero.grouping[t, 27] <- vr.$se

    # lnRR, response ratio (logarithm of male and female means)

    rr. <- metafor::rma.mv(yi = effect_size_RR, V = sample_variance_RR, random = list(~1| strain_name, ~1|production_center,    
                                ~1|err), control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), data = results)
    results.allhetero.grouping[t, 14] <- rr.$sigma2[1]
    results.allhetero.grouping[t, 15] <- rr.$sigma2[2]
    results.allhetero.grouping[t, 16] <- rr.$sigma2[3]
    results.allhetero.grouping[t, 17] <- rr.$s.nlevels[1]
    results.allhetero.grouping[t, 18] <- rr.$s.nlevels[2]
    results.allhetero.grouping[t, 19] <- rr.$s.nlevels[3]
     results.allhetero.grouping[t, 28] <- rr.$b
     results.allhetero.grouping[t, 29] <- rr.$ci.lb
     results.allhetero.grouping[t, 30] <- rr.$ci.ub
     results.allhetero.grouping[t, 31] <- rr.$se

  }, error=function(e){cat("ERROR :",conditionMessage(e), "\n")})
}

```

Exclude traits
```{r}
results.allhetero.grouping2 <- results.allhetero.grouping[results.allhetero.grouping$s.nlevels.strain.VR != 0, ]
nrow(results.allhetero.grouping2) 
```

Merge data sets containing metafor results with procedure etc. names

```{r}  
procedures <- read.csv("procedures.csv")

results.allhetero.grouping2$parameter_group <- data$parameter_group[match(results.allhetero.grouping2$id, data$id)]
results.allhetero.grouping2$procedure <- data$procedure_name[match(results.allhetero.grouping2$id, data$id)]

results.allhetero.grouping2$GroupingTerm <-  procedures$GroupingTerm[match(results.allhetero.grouping2$procedure, procedures$procedure)]
results.allhetero.grouping2$parameter_name <- data$parameter_name[match(results.allhetero.grouping2$id, data$id)]

```

### Correlated parameters

```{r}
metahetero1 <- results.allhetero.grouping2 
length(unique(metahetero1$procedure)) #18    FELIX30-5-19: Komisch, ich bekomme gerade 19, und unten: 9, 152, 223; evt. wegen der neuen Formel!
length(unique(metahetero1$GroupingTerm)) #9 
length(unique(metahetero1$parameter_group)) # 148
length(unique(metahetero1$parameter_name)) #218

```

Count of number of parameter names (correlated sub-traits) in each parameter group (par_group_size)

```{r}
metahetero1b <-
  metahetero1 %>%
  group_by(parameter_group) %>% 
  mutate(par_group_size = n_distinct(parameter_name))

metahetero1$par_group_size <- metahetero1b$par_group_size[match(metahetero1$parameter_group, metahetero1b$parameter_group)]

```

Create subsets with > 1 count (par_group_size > 1)

```{r}
metahetero1_sub <- subset(metahetero1, par_group_size > 1) # 90 observations  
#str(metahetero1_sub)
# metahetero1_sub$sampleSize <- as.numeric(metahetero1_sub$sampleSize) #Felix30-5-19: delete this line
```

Nest data
```{r}
n_count. <- metahetero1_sub %>% 
  group_by(parameter_group) %>% 
  #mutate(raw_N = sum(sampleSize)) %>%  #don't think is necessary: delete in final version
  nest()

```

prepare for meta-analysis
```{r}
model_count. <- n_count. %>% 
  mutate(model_lnRR = map(data, ~ robu(.x$lnRR ~ 1, data= .x, studynum= .x$id, modelweights = c("CORR"), rho = 0.8, 
                                                small = TRUE, var.eff.size= (.x$lnRR_se)^2 )),
  model_lnVR = map(data, ~ robu(.x$lnVR ~ 1, data= .x, studynum= .x$id, modelweights = c("CORR"), rho = 0.8, 
                                                small = TRUE, var.eff.size= (.x$lnVR_se)^2 )),
  model_lnCVR = map(data, ~ robu(.x$lnCVR ~ 1, data= .x, studynum= .x$id, modelweights = c("CORR"), rho = 0.8, 
                                                small = TRUE, var.eff.size= (.x$lnCVR_se)^2 )))

#Robumeta object details:
#str(model_count.$model_lnCVR[[1]])

```

### Perform meta-analyses on correlated sub-traits, using robumeta

Extract and save parameter estimates 
```{r}
count_fun. <- function(mod_sub)
  return(c(as.numeric(mod_sub$mod_info$term1), mod_sub$N) )

```

```{r}
robusub_RR. <- model_count. %>% 
  transmute(parameter_group, estimatelnRR = map(model_lnRR, count_fun.)) %>% 
  mutate(r = map(estimatelnRR, ~ data.frame(t(.)))) %>%
  unnest(r) %>%
  select(-estimatelnRR) %>%
  purrr::set_names(c("parameter_group","var.RR","N.RR"))

robusub_CVR. <- model_count. %>% 
  transmute(parameter_group, estimatelnCVR = map(model_lnCVR, count_fun.)) %>% 
  mutate(r = map(estimatelnCVR, ~ data.frame(t(.)))) %>%
  unnest(r) %>%
  select(-estimatelnCVR) %>%
  purrr::set_names(c("parameter_group","var.CVR","N.CVR"))

robusub_VR. <- model_count. %>% 
  transmute(parameter_group, estimatelnVR = map(model_lnVR, count_fun.)) %>% 
  mutate(r = map(estimatelnVR, ~ data.frame(t(.)))) %>%
  unnest(r) %>%
  select(-estimatelnVR) %>%
  purrr::set_names(c("parameter_group","var.VR","N.VR"))

robu_all. <- full_join(robusub_CVR., robusub_VR.) %>% full_join(., robusub_RR.)

```

### Merge the two data sets (the new [robu_all] and the initial [uncorrelated sub-traits with count = 1]) 
In this step, we 	
1) put the N from robumeta and the  N from metafor (s.nlevels.error) together into the same columns (N.RR, N.VR, N.CVR)

2) calculate the total variance for metafor models as the sum of random effect variances and the residual error,
							then put them in the same columns together with the residual variances from robumeta

```{r}
metahetero_all <- metahetero1 %>% filter(par_group_size == 1) %>% as_tibble
metahetero_all$N.RR <- metahetero_all$s.nlevels.error.RR 
metahetero_all$N.CVR <- metahetero_all$s.nlevels.error.CVR 
metahetero_all$N.VR <- metahetero_all$s.nlevels.error.VR 
metahetero_all$var.RR <- log(sqrt(metahetero_all$sigma2_strain.RR + metahetero_all$sigma2_center.RR + metahetero_all$sigma2_error.RR))
metahetero_all$var.VR <- log(sqrt(metahetero_all$sigma2_strain.VR + metahetero_all$sigma2_center.VR + metahetero_all$sigma2_error.VR))
metahetero_all$var.CVR <- log(sqrt(metahetero_all$sigma2_strain.CVR + metahetero_all$sigma2_center.CVR + metahetero_all$sigma2_error.CVR))
#str(metahetero_all)
#str(robu_all.)

metahetero_all <- metahetero_all %>% mutate(var.RR = if_else(var.RR == -Inf, -7 ,var.RR),
                   	  var.VR = if_else(var.VR == -Inf, -5 ,var.VR),
				  var.CVR = if_else(var.CVR == -Inf, -6 ,var.CVR))
```

### Combine data 
in three separate steps
```{r}
combinedmetahetero <- bind_rows(robu_all., metahetero_all)
#glimpse(combinedmetahetero)

metacombohetero <- combinedmetahetero
metacombohetero$counts <- metahetero1$par_group_size[match( metacombohetero$parameter_group, metahetero1$parameter_group)]
metacombohetero$procedure2 <-metahetero1$procedure[match( metacombohetero$parameter_group, metahetero1$parameter_group)]
metacombohetero$GroupingTerm2 <-metahetero1$GroupingTerm[match( metacombohetero$parameter_group, metahetero1$parameter_group)]

```
Clean-up and rename 
```{r}
metacombohetero <- metacombohetero[, c(1:7, 43:45)] 
names(metacombohetero)[9] <- "procedure" 
names(metacombohetero)[10] <- "GroupingTerm"

#write.csv(metacombohetero, "metacombohetero.csv")
```

### Last step: Meta-meta-analysis of heterogeneity
Perform meta-meta-analysis (3 for each of the 9 grouping terms: var.CVR, var.VR, var.RR) 
```{r}
#glimpse(metacombohetero)

metacombohetero_final <- metacombohetero %>%
 group_by(GroupingTerm) %>%
 nest()

#Calculate number of parameters per grouping term : not needed; delete in final version
#metacombo_final <- metacombo_final  %>%  mutate(para_per_GroupingTerm = map_dbl(data, nrow))
```

 Final fixed effects meta-analyses within grouping terms, with SE of the estimate

```{r}
metacombohetero$var.CVR

heterog1 <- metacombohetero_final %>%

  mutate(model_heteroCVR = map(data, ~ metafor::rma.uni(yi = .x$var.CVR, sei = sqrt(1 / 2*(.x$N.CVR - 1)),  
				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 10000, stepadj=0.5), verbose=F)),
	   model_heteroVR = map(data, ~ metafor::rma.uni(yi = .x$var.VR, sei = sqrt(1 / 2*(.x$N.VR - 1)),  
				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 10000, stepadj=0.5), verbose=F)),
	   model_heteroRR = map(data, ~ metafor::rma.uni(yi = .x$var.RR, sei = sqrt(1 / 2*(.x$N.RR - 1)),  
				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 10000, stepadj=0.5), verbose=F)))

heterog1

# **Re-structure data for each grouping term; extract heterogenenity/variance terms; delete un-used variables

Behaviour. <- heterog1 %>% filter(., GroupingTerm == "Behaviour")  %>% select(., -data)  %>%  mutate(heteroCVR=.[[2]][[1]]$b, heteroCVR_lower=.[[2]][[1]]$ci.lb, heteroCVR_upper=.[[2]][[1]]$ci.ub, heteroCVR_se=.[[2]][[1]]$se,
	              heteroVR=.[[3]][[1]]$b, heteroVR_lower=.[[3]][[1]]$ci.lb, heteroVR_upper=.[[3]][[1]]$ci.ub, heteroVR_se=.[[3]][[1]]$se,
		        heteroRR=.[[4]][[1]]$b, heteroRR_lower=.[[4]][[1]]$ci.lb, heteroRR_upper=.[[4]][[1]]$ci.ub, heteroRR_se=.[[4]][[1]]$se) %>%
			  select(., GroupingTerm, heteroCVR:heteroRR_se)

Immunology. <- heterog1 %>% filter(., GroupingTerm == "Immunology") %>% select(., -data)  %>%  mutate(heteroCVR=.[[2]][[1]]$b, heteroCVR_lower=.[[2]][[1]]$ci.lb, heteroCVR_upper=.[[2]][[1]]$ci.ub, heteroCVR_se=.[[2]][[1]]$se,
	              heteroVR=.[[3]][[1]]$b, heteroVR_lower=.[[3]][[1]]$ci.lb, heteroVR_upper=.[[3]][[1]]$ci.ub, heteroVR_se=.[[3]][[1]]$se,
		        heteroRR=.[[4]][[1]]$b, heteroRR_lower=.[[4]][[1]]$ci.lb, heteroRR_upper=.[[4]][[1]]$ci.ub, heteroRR_se=.[[4]][[1]]$se) %>%
			  select(., GroupingTerm, heteroCVR:heteroRR_se)

Hematology. <- heterog1 %>% filter(., GroupingTerm == "Hematology") %>% select(., -data)  %>%  mutate(heteroCVR=.[[2]][[1]]$b, heteroCVR_lower=.[[2]][[1]]$ci.lb, heteroCVR_upper=.[[2]][[1]]$ci.ub, heteroCVR_se=.[[2]][[1]]$se,
	              heteroVR=.[[3]][[1]]$b, heteroVR_lower=.[[3]][[1]]$ci.lb, heteroVR_upper=.[[3]][[1]]$ci.ub, heteroVR_se=.[[3]][[1]]$se,
		        heteroRR=.[[4]][[1]]$b, heteroRR_lower=.[[4]][[1]]$ci.lb, heteroRR_upper=.[[4]][[1]]$ci.ub, heteroRR_se=.[[4]][[1]]$se) %>%
			  select(., GroupingTerm, heteroCVR:heteroRR_se)

Hearing. <- heterog1 %>% filter(., GroupingTerm == "Hearing")  %>% select(., -data)  %>%  mutate(heteroCVR=.[[2]][[1]]$b, heteroCVR_lower=.[[2]][[1]]$ci.lb, heteroCVR_upper=.[[2]][[1]]$ci.ub, heteroCVR_se=.[[2]][[1]]$se,
	              heteroVR=.[[3]][[1]]$b, heteroVR_lower=.[[3]][[1]]$ci.lb, heteroVR_upper=.[[3]][[1]]$ci.ub, heteroVR_se=.[[3]][[1]]$se,
		        heteroRR=.[[4]][[1]]$b, heteroRR_lower=.[[4]][[1]]$ci.lb, heteroRR_upper=.[[4]][[1]]$ci.ub, heteroRR_se=.[[4]][[1]]$se) %>%
			  select(., GroupingTerm, heteroCVR:heteroRR_se)

Physiology. <- heterog1 %>% filter(., GroupingTerm == "Physiology")  %>% select(., -data)  %>%  mutate(heteroCVR=.[[2]][[1]]$b, heteroCVR_lower=.[[2]][[1]]$ci.lb, heteroCVR_upper=.[[2]][[1]]$ci.ub, heteroCVR_se=.[[2]][[1]]$se,
	              heteroVR=.[[3]][[1]]$b, heteroVR_lower=.[[3]][[1]]$ci.lb, heteroVR_upper=.[[3]][[1]]$ci.ub, heteroVR_se=.[[3]][[1]]$se,
		        heteroRR=.[[4]][[1]]$b, heteroRR_lower=.[[4]][[1]]$ci.lb, heteroRR_upper=.[[4]][[1]]$ci.ub, heteroRR_se=.[[4]][[1]]$se) %>%
			  select(., GroupingTerm, heteroCVR:heteroRR_se)

Metabolism. <- heterog1 %>% filter(., GroupingTerm == "Metabolism")  %>% select(., -data)  %>%  mutate(heteroCVR=.[[2]][[1]]$b, heteroCVR_lower=.[[2]][[1]]$ci.lb, heteroCVR_upper=.[[2]][[1]]$ci.ub, heteroCVR_se=.[[2]][[1]]$se,
	              heteroVR=.[[3]][[1]]$b, heteroVR_lower=.[[3]][[1]]$ci.lb, heteroVR_upper=.[[3]][[1]]$ci.ub, heteroVR_se=.[[3]][[1]]$se,
		        heteroRR=.[[4]][[1]]$b, heteroRR_lower=.[[4]][[1]]$ci.lb, heteroRR_upper=.[[4]][[1]]$ci.ub, heteroRR_se=.[[4]][[1]]$se) %>%
			  select(., GroupingTerm, heteroCVR:heteroRR_se)

Morphology. <- heterog1 %>% filter(., GroupingTerm == "Morphology") %>% select(., -data)  %>%  mutate(heteroCVR=.[[2]][[1]]$b, heteroCVR_lower=.[[2]][[1]]$ci.lb, heteroCVR_upper=.[[2]][[1]]$ci.ub, heteroCVR_se=.[[2]][[1]]$se,
	              heteroVR=.[[3]][[1]]$b, heteroVR_lower=.[[3]][[1]]$ci.lb, heteroVR_upper=.[[3]][[1]]$ci.ub, heteroVR_se=.[[3]][[1]]$se,
		        heteroRR=.[[4]][[1]]$b, heteroRR_lower=.[[4]][[1]]$ci.lb, heteroRR_upper=.[[4]][[1]]$ci.ub, heteroRR_se=.[[4]][[1]]$se) %>%
			  select(., GroupingTerm, heteroCVR:heteroRR_se)

Heart. <- heterog1 %>% filter(., GroupingTerm == "Heart")  %>% select(., -data)  %>%  mutate(heteroCVR=.[[2]][[1]]$b, heteroCVR_lower=.[[2]][[1]]$ci.lb, heteroCVR_upper=.[[2]][[1]]$ci.ub, heteroCVR_se=.[[2]][[1]]$se,
	              heteroVR=.[[3]][[1]]$b, heteroVR_lower=.[[3]][[1]]$ci.lb, heteroVR_upper=.[[3]][[1]]$ci.ub, heteroVR_se=.[[3]][[1]]$se,
		        heteroRR=.[[4]][[1]]$b, heteroRR_lower=.[[4]][[1]]$ci.lb, heteroRR_upper=.[[4]][[1]]$ci.ub, heteroRR_se=.[[4]][[1]]$se) %>%
			  select(., GroupingTerm, heteroCVR:heteroRR_se)

Eye. <- heterog1 %>% filter(., GroupingTerm == "Eye")  %>% select(., -data)  %>%  mutate(heteroCVR=.[[2]][[1]]$b, heteroCVR_lower=.[[2]][[1]]$ci.lb, heteroCVR_upper=.[[2]][[1]]$ci.ub, heteroCVR_se=.[[2]][[1]]$se,
	              heteroVR=.[[3]][[1]]$b, heteroVR_lower=.[[3]][[1]]$ci.lb, heteroVR_upper=.[[3]][[1]]$ci.ub, heteroVR_se=.[[3]][[1]]$se,
		        heteroRR=.[[4]][[1]]$b, heteroRR_lower=.[[4]][[1]]$ci.lb, heteroRR_upper=.[[4]][[1]]$ci.ub, heteroRR_se=.[[4]][[1]]$se) %>%
			  select(., GroupingTerm, heteroCVR:heteroRR_se)

heterog2 <- bind_rows(Behaviour., Morphology., Metabolism., Physiology., Immunology., Hematology., Heart., Hearing., Eye.)
str(heterog2)

```

### Restructure data for plotting 
```{r}
heterog3 <- gather(heterog2, parameter, value, c(heteroCVR, heteroVR, heteroRR), factor_key= TRUE)

heteroCVR.ci <- heterog3 %>% filter(parameter == "heteroCVR") %>% mutate(ci.low = heteroCVR_lower, ci.high = heteroCVR_upper)
heteroVR.ci <- heterog3 %>% filter(parameter == "heteroVR") %>% mutate(ci.low = heteroVR_lower, ci.high = heteroVR_upper)
heteroRR.ci <- heterog3 %>% filter(parameter == "heteroRR") %>% mutate(ci.low = heteroRR_lower, ci.high = heteroRR_upper)

heterog4 <- bind_rows(heteroCVR.ci, heteroVR.ci, heteroRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)

# **Re-order grouping terms

heterog4$GroupingTerm <- factor(heterog4$GroupingTerm, levels =c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye") )
heterog4$GroupingTerm <- factor(heterog4$GroupingTerm, rev(levels(heterog4$GroupingTerm)))
heterog4$label <- "All traits"
#write.csv(heterog4, "heterog4.csv")

```

# Plot Supplement FIGURE S1 (Second-order meta analysis on heterogeneity)

### Plot FigS1 all traits
```{r}

Metameta_FigS1_alltraits <- heterog4 %>%

  ggplot(aes(y= GroupingTerm, x= value)) +
  geom_errorbarh(aes(xmin = ci.low, 
                     xmax = ci.high), 
			   height = 0.1, show.legend = FALSE) +
  geom_point(aes(shape = parameter,
             fill = parameter, color = parameter), size = 2.2, 
             show.legend = FALSE) +
  scale_x_continuous(limits=c(-7.0, 0.5), 
                     #breaks = c(-2.0, -1.5, -1.0, -0.5, 0, 0.5, 1.0, 1.5, 2.0), 
                     name='Effect size') +
  facet_grid(cols = vars(parameter), rows = vars(label),
             labeller = label_wrap_gen(width = 23),
             scales= 'free', 
             space='free')+
  theme_bw()+
  theme(strip.text.y = element_text(angle = 270, size = 10, margin = margin(t=15, r=15, b=15, l=15)), 
	  strip.text.x = element_text(size = 12),
        strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
        text = element_text(size = 14),
        panel.spacing = unit(0.5, "lines"),
        panel.border= element_blank(),
        axis.line=element_line(), 
        panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
        panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
        panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(), 
        legend.title = element_blank(),
        axis.title.x = element_blank(),
	  axis.title.y = element_blank())

Metameta_FigS1_alltraits

```

# TABLES with Heterogeneity (tau2, I2) of all the groups, following the structure of FIG3

### CVR
```{r}
heteroeach.meta.CVR.c <- as.data.frame(overall1 %>% group_by(GroupingTerm) %>%  
		mutate(tau2 = map_dbl(model_lnCVR, pluck(9)),
			 I2 = map_dbl(model_lnCVR, pluck(23))) )[, c("GroupingTerm", "tau2", "I2")]

heteroall.meta.CVR.c <- as.data.frame(overall_all1 %>% 
		mutate(tau2 = map_dbl(model_lnCVR, pluck(9)),
			 I2 = map_dbl(model_lnCVR, pluck(23))) )[, c("tau2", "I2")]

heteroall.meta.CVR.c <- heteroall.meta.CVR.c %>% mutate(GroupingTerm = "All")

overall2.CVR.c <- bind_rows(heteroeach.meta.CVR.c, heteroall.meta.CVR.c)

overall2.CVR.c <- add_column(overall2.CVR.c, var = "ln(CVR)", .before= "tau2")
overall2.CVR.c <- overall2.CVR.c[order(overall2.CVR.c$GroupingTerm),]
```

### VR

```{r}
heteroeach.meta.VR.c <- as.data.frame(overall1 %>% group_by(GroupingTerm) %>%  
		mutate(tau2 = map_dbl(model_lnVR, pluck(9)),
			 I2 = map_dbl(model_lnVR, pluck(23))) )[, c("GroupingTerm", "tau2", "I2")]

heteroall.meta.VR.c <- as.data.frame(overall_all1 %>% 
		mutate(tau2 = map_dbl(model_lnVR, pluck(9)),
			 I2 = map_dbl(model_lnVR, pluck(23))) )[, c("tau2", "I2")]

heteroall.meta.VR.c <- heteroall.meta.VR.c %>% mutate(GroupingTerm = "All")

overall2.VR.c <- bind_rows(heteroeach.meta.VR.c, heteroall.meta.VR.c)

overall2.VR.c <- add_column(overall2.VR.c, var = "ln(VR)", .before= "tau2")
overall2.VR.c <- overall2.VR.c[order(overall2.VR.c$GroupingTerm),]
```

### RR
```{r}
heteroeach.meta.RR.c <- as.data.frame(overall1 %>% group_by(GroupingTerm) %>%  
		mutate(tau2 = map_dbl(model_lnRR, pluck(9)),
			 I2 = map_dbl(model_lnRR, pluck(23))) )[, c("GroupingTerm", "tau2", "I2")]

heteroall.meta.RR.c <- as.data.frame(overall_all1 %>% 
		mutate(tau2 = map_dbl(model_lnRR, pluck(9)),
			 I2 = map_dbl(model_lnRR, pluck(23))) )[, c("tau2", "I2")]

heteroall.meta.RR.c <- heteroall.meta.RR.c %>% mutate(GroupingTerm = "All")

overall2.RR.c <- bind_rows(heteroeach.meta.RR.c, heteroall.meta.RR.c)

overall2.RR.c <- add_column(overall2.RR.c, var = "ln(RR)", .before= "tau2")
overall2.RR.c <- overall2.RR.c[order(overall2.RR.c$GroupingTerm),]

overall2.het <- full_join(overall2.CVR.c, overall2.VR.c) 
overall2.het <- full_join(overall2.het, overall2.RR.c)

for_table_overall.het <- overall2.het[order(factor(overall2.het$GroupingTerm, levels = c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye", "All"))),]
```

the following uses the same data from above (plot3.male.meta.CVR / plot3.male.meta.VR / plot3.male.meta.RR):

### Male not overlapping zero (significant)

Re-structure data for each grouping term; delete un-used variables
```{r}
#plot3.male.meta.CVR[[3]][[1]][1:30] #tau2 is at position '9', I2 is at position '23'
#plot3.male.meta.CVR[[3]][[1]][c(9, 23)]

plot3.male.meta.CVR.c <- as.data.frame(plot3.male.meta.CVR %>% group_by(GroupingTerm) %>%  
		mutate(tau2 = map_dbl(model_lnCVR, pluck(9)),
			 I2 = map_dbl(model_lnCVR, pluck(23))) )[, c(1,4,5)]
#add missing GroupingTerms for plot
plot3.male.meta.CVR.c <- add_row(plot3.male.meta.CVR.c, GroupingTerm = "Immunology")
plot3.male.meta.CVR.c <- add_row(plot3.male.meta.CVR.c, GroupingTerm = "Hearing")
plot3.male.meta.CVR.c <- add_row(plot3.male.meta.CVR.c, GroupingTerm = "Eye")
plot3.male.meta.CVR.c <- add_column(plot3.male.meta.CVR.c, var = "ln(CVR)", .before= "tau2")
plot3.male.meta.CVR.c <- plot3.male.meta.CVR.c[order(plot3.male.meta.CVR.c$GroupingTerm),]

plot3.male.meta.VR.c <- as.data.frame(plot3.male.meta.VR %>% group_by(GroupingTerm) %>%  
		mutate(tau2 = map_dbl(model_lnVR, pluck(9)),
			 I2 = map_dbl(model_lnVR, pluck(23))) )[, c(1,4,5)]
plot3.male.meta.VR.c <- add_row(plot3.male.meta.VR.c, GroupingTerm = "Immunology")
plot3.male.meta.VR.c <- add_row(plot3.male.meta.VR.c, GroupingTerm = "Eye")
plot3.male.meta.VR.c <- add_column(plot3.male.meta.VR.c, var = "ln(VR)", .before= "tau2")
plot3.male.meta.VR.c <- plot3.male.meta.VR.c[order(plot3.male.meta.VR.c$GroupingTerm),]

plot3.male.meta.RR.c <- as.data.frame(plot3.male.meta.RR %>% group_by(GroupingTerm) %>%  
		mutate(tau2 = map_dbl(model_lnRR, pluck(9)),
			 I2 = map_dbl(model_lnRR, pluck(23))) )[, c(1,4,5)]
plot3.male.meta.RR.c <- add_column(plot3.male.meta.RR.c, var = "ln(RR)", .before= "tau2")  
plot3.male.meta.RR.c <- plot3.male.meta.RR.c[order(plot3.male.meta.RR.c$GroupingTerm),]

overall.male.plot3. <- full_join(plot3.male.meta.CVR.c, plot3.male.meta.VR.c) 
overall.male.plot3. <- full_join(overall.male.plot3., plot3.male.meta.RR.c)

for_table_malesig <- overall.male.plot3.[order(factor(overall.male.plot3.$GroupingTerm, levels = c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye", "All"))),]
```
### Female not overlapping zero (significant)

Re-structure data for each grouping term; delete un-used variables
```{r}
#plot3.female.meta.CVR[[3]][[1]][1:30] #tau2 is at position '9', I2 is at position '23'
#plot3.female.meta.CVR[[3]][[1]][c(9, 23)]

plot3.female.meta.CVR.c <- as.data.frame(plot3.female.meta.CVR %>% group_by(GroupingTerm) %>%  
		mutate(tau2 = map_dbl(model_lnCVR, pluck(9)),
			 I2 = map_dbl(model_lnCVR, pluck(23))) )[, c(1,4,5)]
#add missing GroupingTerms 
plot3.female.meta.CVR.c <- add_row(plot3.female.meta.CVR.c, GroupingTerm = "Morphology")
plot3.female.meta.CVR.c <- add_row(plot3.female.meta.CVR.c, GroupingTerm = "Hearing")
plot3.female.meta.CVR.c <- add_column(plot3.female.meta.CVR.c, var = "ln(CVR)", .before= "tau2")
plot3.female.meta.CVR.c <- plot3.female.meta.CVR.c[order(plot3.female.meta.CVR.c$GroupingTerm),]

plot3.female.meta.VR.c <- as.data.frame(plot3.female.meta.VR %>% group_by(GroupingTerm) %>%  
		mutate(tau2 = map_dbl(model_lnVR, pluck(9)),
			 I2 = map_dbl(model_lnVR, pluck(23))) )[, c(1,4,5)]
plot3.female.meta.VR.c <- add_row(plot3.female.meta.VR.c, GroupingTerm = "Morphology")
plot3.female.meta.VR.c <- add_row(plot3.female.meta.VR.c, GroupingTerm = "Hearing")
plot3.female.meta.VR.c <- add_row(plot3.female.meta.VR.c, GroupingTerm = "Hematology")
plot3.female.meta.VR.c <- add_column(plot3.female.meta.VR.c, var = "ln(VR)", .before= "tau2")
plot3.female.meta.VR.c <- plot3.female.meta.VR.c[order(plot3.female.meta.VR.c$GroupingTerm),]

plot3.female.meta.RR.c <- as.data.frame(plot3.female.meta.RR %>% group_by(GroupingTerm) %>%  
		mutate(tau2 = map_dbl(model_lnRR, pluck(9)),
			 I2 = map_dbl(model_lnRR, pluck(23))) )[, c(1,4,5)]
plot3.female.meta.RR.c <- add_row(plot3.female.meta.RR.c, GroupingTerm = "Eye")
plot3.female.meta.RR.c <- add_row(plot3.female.meta.RR.c, GroupingTerm = "Metabolism")
plot3.female.meta.RR.c <- add_column(plot3.female.meta.RR.c, var = "ln(RR)", .before= "tau2")  
plot3.female.meta.RR.c <- plot3.female.meta.RR.c[order(plot3.female.meta.RR.c$GroupingTerm),]

overall.female.plot3. <- full_join(plot3.female.meta.CVR.c, plot3.female.meta.VR.c) 
overall.female.plot3. <- full_join(overall.female.plot3., plot3.female.meta.RR.c)

for_table_femsig <- overall.female.plot3.[order(factor(overall.female.plot3.$GroupingTerm, levels = c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye", "All"))),]
```

### Male-biased >10%

Re-structure data for each grouping term; delete un-used variables
```{r}
plot3.male.meta.CVR.perc.c <- as.data.frame(plot3.male.meta.CVR.perc %>% group_by(GroupingTerm) %>%  
		mutate(tau2 = map_dbl(model_lnCVR, pluck(9)),
			 I2 = map_dbl(model_lnCVR, pluck(23))) )[, c(1,4,5)]
#add missing GroupingTerms for plot
plot3.male.meta.CVR.perc.c <- add_row(plot3.male.meta.CVR.perc.c, GroupingTerm = "Hearing")
plot3.male.meta.CVR.perc.c <- add_row(plot3.male.meta.CVR.perc.c, GroupingTerm = "Eye")
plot3.male.meta.CVR.perc.c <- add_column(plot3.male.meta.CVR.perc.c, var = "ln(CVR)", .before= "tau2")
plot3.male.meta.CVR.perc.c <- plot3.male.meta.CVR.perc.c[order(plot3.male.meta.CVR.perc.c$GroupingTerm),]

plot3.male.meta.VR.perc.c <- as.data.frame(plot3.male.meta.VR.perc %>% group_by(GroupingTerm) %>%  
		mutate(tau2 = map_dbl(model_lnVR, pluck(9)),
			 I2 = map_dbl(model_lnVR, pluck(23))) )[, c(1,4,5)]
plot3.male.meta.VR.perc.c <- add_row(plot3.male.meta.VR.perc.c, GroupingTerm = "Hearing")
plot3.male.meta.VR.perc.c <- add_row(plot3.male.meta.VR.perc.c, GroupingTerm = "Eye")
plot3.male.meta.VR.perc.c <- add_column(plot3.male.meta.VR.perc.c, var = "ln(VR)", .before= "tau2")
plot3.male.meta.VR.perc.c <- plot3.male.meta.VR.perc.c[order(plot3.male.meta.VR.perc.c$GroupingTerm),]

plot3.male.meta.RR.perc.c <- as.data.frame(plot3.male.meta.RR.perc %>% group_by(GroupingTerm) %>%  
		mutate(tau2 = map_dbl(model_lnRR, pluck(9)),
			 I2 = map_dbl(model_lnRR, pluck(23))) )[, c(1,4,5)]
plot3.male.meta.RR.perc.c <- add_row(plot3.male.meta.RR.perc.c, GroupingTerm = "Hearing")
plot3.male.meta.RR.perc.c <- add_row(plot3.male.meta.RR.perc.c, GroupingTerm = "Eye")
plot3.male.meta.RR.perc.c <- add_row(plot3.male.meta.RR.perc.c, GroupingTerm = "Heart")
plot3.male.meta.RR.perc.c <- add_column(plot3.male.meta.RR.perc.c, var = "ln(RR)", .before= "tau2")  
plot3.male.meta.RR.perc.c <- plot3.male.meta.RR.perc.c[order(plot3.male.meta.RR.perc.c$GroupingTerm),]

overall.male.perc. <- full_join(plot3.male.meta.CVR.perc.c, plot3.male.meta.VR.perc.c) 
overall.male.perc. <- full_join(overall.male.perc., plot3.male.meta.RR.perc.c)

for_table_male10perc <- overall.male.perc.[order(factor(overall.male.perc.$GroupingTerm, levels = c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye", "All"))),]
```

### Female-biased >10%

Re-structure data
```{r}
#plot3.meta.CVR.perc[[3]][[1]][1:30] #tau2 is at position '9', I2 is at position '23'
#plot3.meta.CVR.perc[[3]][[1]][c(9, 23)]

plot3.female.meta.CVR.perc.c <- as.data.frame(plot3.meta.CVR.perc %>% group_by(GroupingTerm) %>%  
		mutate(tau2 = map_dbl(model_lnCVR, pluck(9)),
			 I2 = map_dbl(model_lnCVR, pluck(23))) )[, c(1,4,5)]  # all zero
#add missing GroupingTerms for plot
plot3.female.meta.CVR.perc.c <- add_row(plot3.female.meta.CVR.perc.c, GroupingTerm = "Hearing")
plot3.female.meta.CVR.perc.c <- add_row(plot3.female.meta.CVR.perc.c, GroupingTerm = "Behaviour")
plot3.female.meta.CVR.perc.c <- add_row(plot3.female.meta.CVR.perc.c, GroupingTerm = "Hematology")
plot3.female.meta.CVR.perc.c <- add_column(plot3.female.meta.CVR.perc.c, var = "ln(CVR)", .before= "tau2")
plot3.female.meta.CVR.perc.c <- plot3.female.meta.CVR.perc.c[order(plot3.female.meta.CVR.perc.c$GroupingTerm),]

plot3.female.meta.VR.perc.c <- as.data.frame(plot3.meta.VR.perc %>% group_by(GroupingTerm) %>%  
		mutate(tau2 = map_dbl(model_lnVR, pluck(9)),
			 I2 = map_dbl(model_lnVR, pluck(23))) )[, c(1,4,5)]  # all zero, except 'All'
#add missing GroupingTerms for plot
plot3.female.meta.VR.perc.c <- add_row(plot3.female.meta.VR.perc.c, GroupingTerm = "Hearing")
plot3.female.meta.VR.perc.c <- add_row(plot3.female.meta.VR.perc.c, GroupingTerm = "Hematology")
plot3.female.meta.VR.perc.c <- add_column(plot3.female.meta.VR.perc.c, var = "ln(VR)", .before= "tau2")
plot3.female.meta.VR.perc.c <- plot3.female.meta.VR.perc.c[order(plot3.female.meta.VR.perc.c$GroupingTerm),]

plot3.female.meta.RR.perc.c <- as.data.frame(plot3.meta.RR.perc %>% group_by(GroupingTerm) %>%  
		mutate(tau2 = map_dbl(model_lnRR, pluck(9)),
			 I2 = map_dbl(model_lnRR, pluck(23))) )[, c(1,4,5)]  
#add missing GroupingTerms for plot
plot3.female.meta.RR.perc.c <- add_row(plot3.female.meta.RR.perc.c, GroupingTerm = "Hearing")
plot3.female.meta.RR.perc.c <- add_row(plot3.female.meta.RR.perc.c, GroupingTerm = "Eye")
plot3.female.meta.RR.perc.c <- add_row(plot3.female.meta.RR.perc.c, GroupingTerm = "Metabolism")
plot3.female.meta.RR.perc.c <- add_row(plot3.female.meta.RR.perc.c, GroupingTerm = "Hematology")
plot3.female.meta.RR.perc.c <- add_column(plot3.female.meta.RR.perc.c, var = "ln(RR)", .before= "tau2")
plot3.female.meta.RR.perc.c <- plot3.female.meta.RR.perc.c[order(plot3.female.meta.RR.perc.c$GroupingTerm),]

overall.female.perc. <- full_join(plot3.female.meta.CVR.perc.c, plot3.female.meta.VR.perc.c) 
overall.female.perc. <- full_join(overall.female.perc., plot3.female.meta.RR.perc.c)

for_table_female10perc <- overall.female.perc.[order(factor(overall.female.perc.$GroupingTerm, levels = c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye", "All"))),]

```

### 2019-06-11 scripts/2019_4June_IMPC variance and sex difference.Rmd
Correct paths, spellcheck

@@
 
- Function to calculate metanalaysis statistics. Created by A M Senior @ the University of Otago NZ 03/01/2014
-
-Below are funcitons for calculating effect sizes for meta-analysis of variance. 
+ Function to calculate meta-analysis statistics. Created by A M Senior @ the University of Otago NZ 03/01/2014
+
+Below are functions for calculating effect sizes for meta-analysis of variance. 
 All functions take the mean, sd and n from the control and experimental groups.
 
-The first function, Cal.lnCVR, calculates the the log repsonse-ratio of the coefficient of variance (lnCVR) - see Nakagawa et al 2015.
-
-The second function calculates the measuremnt error variance for lnCVR. As well as the aforementioned parameters, this function also takes
-Equal.E.C.Corr (default = T), which must be True or False. If true, the funciton assumes that the correlaiton between mean and sd (Taylor's Law) 
+The first function, Cal.lnCVR, calculates the the log response-ratio of the coefficient of variance (lnCVR) - see Nakagawa et al 2015.
+
+The second function calculates the measurement error variance for lnCVR. As well as the aforementioned parameters, this function also takes
+Equal.E.C.Corr (default = T), which must be True or False. If true, the function assumes that the correlation between mean and sd (Taylor's Law) 
 is equal for the mean and control groups, and, thus these data are pooled. If False the mean-SD correlation for the experimental and control groups
-are calculated seperatley from one another.
+are calculated separately from one another.
 
@@
 We here provide the cleaned dataset, which we have saved in a folder called "export", as easy starting point.
-However, the full dataset can ve loaded and cleaned using the da cleaning function (Function 1 above), if "#" signs in the code below are removed  (created as that is much smaller than th e .csv - which we can still provide for those who absoliutely want to start from scratch?)
+However, the full dataset can ve loaded and cleaned using the da cleaning function (Function 1 above), if "#" signs in the code below are removed  (created as that is much smaller than th e .csv - which we can still provide for those who absolutely want to start from scratch?)
 ```{r}
@@
 
- group <- read.csv("ParameterGrouping.csv") 
+ group <- read.csv("export/ParameterGrouping.csv") 
  data <- data3
@@
 We add a new variable, where redundant traits are combined
-[note however, at this stage the dataset still contains non-sensical traits, i.e. traits that may not contain any u=information on variance]
+[note however, at this stage the dataset still contains nonsensical traits, i.e. traits that may not contain any information on variance]
 
@@
 ## LOOP, to run meta-analysis on all traits
-The loop combines the functions menationed above and fills the data matrix with results from our meta analysis. 
-Error messages indicate traits that either did not reach convergence, or that did not return meaningful results in the metaanalysis, due to absence of variance.
+The loop combines the functions mentioned above and fills the data matrix with results from our meta analysis. 
+Error messages indicate traits that either did not reach convergence, or that did not return meaningful results in the meta-analysis, due to absence of variance.
 Those traits will be removed ion later steps, outlined below.
@@
 #lnCVR,  log repsonse-ratio of the coefficient of variance    
-    cvr <- metafor::rma.mv(yi = effect_size_CVR, V = sample_variance_CVR, random = list(~1| strain_name, ~1|production_center,    
-                                                                                        ~1|err), control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), data = results)
-    results.alltraits.grouping[t, 2] <- cvr$b
+    cvr <- metafor::rma.mv(yi = effect_size_CVR, V = sample_variance_CVR, random = list(~1| strain_name, ~1|production_center, results.alltraits.grouping[t, 2] <- cvr$b
     results.alltraits.grouping[t, 3] <- cvr$ci.lb
@@
 
-Procedure names, groupiung variables etc are merged back together with the results from the metafor analysis above.
+Procedure names, grouping variables etc. are merged back together with the results from the metafor analysis above.
 This requires loading of another excel sheet, "procedures.csv"
@@
 ```{r}
-procedures <- read.csv("procedures.csv")
+procedures <- read.csv("export/procedures.csv")
 
@@
 
-Removal of traits that did not achieve convergence, are non-sensical for analysis of variance (such as traits that show variaton, such as number of ribs, digits, etc).
+Removal of traits that did not achieve convergence, are nonsensical for analysis of variance (such as traits that show variation, such as number of ribs, digits, etc).
 14 traits from the originally 232 that had been included are removed.
@@
 
-## Dealing with Correlated Paramters
-
-This dataset contained a number of highly correlated taits, such as different kinds of cell counts (for example, hierarchichal parametrization within immunologocal assays).
-As those datapoints are not independent of each other,  we conducted a meta analyses on these correlated parameters to collapse the number of levels.
+## Dealing with Correlated Parameters
+
+This dataset contained a number of highly correlated traits, such as different kinds of cell counts (for example, hierarchical parametrization within immunological assays).
+As those data-points are not independent of each other,  we conducted a meta analyses on these correlated parameters to collapse the number of levels.
 
@@
 ### Count of number of parameter names (correlated sub-traits) in each parameter group (par_group_size) 
-This serves to idenfify and separate the traits that are correlated from the full dataset that can be preocessed as is.
+This serves to identify and separate the traits that are correlated from the full dataset that can be processed as is.
 If the sample size (n) for a given "parameter group" equals 1, the trait is unique and uncorrelated.
-All instances, where there are 2 or more traits accociated with the same  parameter group (90 cases), are selected for a "mini-meta analysis", which removes the issue of correlation.
+All instances, where there are 2 or more traits associated with the same  parameter group (90 cases), are selected for a "mini-meta analysis", which removes the issue of correlation.
 
@@
 
-### Perform meta-analyses on correlated sub-traits, using robumeta 
+### Perform meta-analyses on correlated sub-traits, using `robumeta` 
 The subset of the data is prepared (nested), and in this first step the model of the meta analysis effect sizes are calculated
@@
 ### Prepare data
-Nesting, calculating the number of parameters within each grouping term, and running the metaanalysis
+Nesting, calculating the number of parameters within each grouping term, and running the meta-analysis
 ```{r}
@@
 
-Re-structure data for each grouping term; delete un-used variables
+Re-structure data for each grouping term; delete unused variables
 
@@
 ### Restructure data for plotting 
-Data are restructred, and grouping terms are being re-ordered
+Data are restructured, and grouping terms are being re-ordered
 ```{r}

### 2019-07-05 scripts/2019_4June_IMPC variance and sex difference.Rmd
Added a new Shiny app to explore meta-analytic results. Has a theme selector built in so you can check out what works and what doesn't. I can hardwire that later when people pick one and agree. I also looked through code. Fixed some small types, modified results.grouping table to include traits and added export of this table so it can be used for calculations of percent diff in shiny apps

@@
     toc_depth: 3
+runtime: shiny
 ---
@@
 1) Data loading and cleaning of the csv file
-This step we have already done and provide a the cleaned up file which is less computing intensive. However, cvs
+This step we have already done and provide a cleaned up file which is less computing intensive. However, cvs
 ```{r}
@@
   mydata[i,] %>% 
-  select(strain_name, production_center) %>%
+  select(strain_name, production_center, trait) %>%
     mutate(
@@
 We here provide the cleaned dataset, which we have saved in a folder called "export", as easy starting point.
-However, the full dataset can ve loaded and cleaned using the da cleaning function (Function 1 above), if "#" signs in the code below are removed  (created as that is much smaller than th e .csv - which we can still provide for those who absolutely want to start from scratch?)
+However, the full dataset can be loaded and cleaned using the data cleaning function (Function 1 above), if "#" signs in the code below are removed  (created as that is much smaller than the .csv - which we can still provide for those who absolutely want to start from scratch?)
 ```{r}
@@
 ```{r}
-results.alltraits.grouping <- as.data.frame(cbind(c(1:n), matrix(rep(0, n*13), ncol = 13))) #number of individual results per trait = 10
-names(results.alltraits.grouping) <- c("id", "lnCVR", "lnCVR_lower", "lnCVR_upper", "lnCVR_se", "lnVR", "lnVR_lower", "lnVR_upper", "lnVR_se", "lnRR", "lnRR_lower", "lnRR_upper" ,"lnRR_se" , "sampleSize")
-
+results.alltraits.grouping <- as.data.frame(cbind(c(1:n), matrix(rep(0, n*14), ncol = 14))) #number of individual results per trait = 10
+names(results.alltraits.grouping) <- c("id", "lnCVR", "lnCVR_lower", "lnCVR_upper", "lnCVR_se", "lnVR", "lnVR_lower", "lnVR_upper", "lnVR_se", "lnRR", "lnRR_lower", "lnRR_upper" ,"lnRR_se" , "sampleSize", "trait")
 ```
@@
 Error messages indicate traits that either did not reach convergence, or that did not return meaningful results in the meta-analysis, due to absence of variance.
-Those traits will be removed ion later steps, outlined below.
+Those traits will be removed in later steps, outlined below.
 
@@
 #lnCVR,  log repsonse-ratio of the coefficient of variance    
-    cvr <- metafor::rma.mv(yi = effect_size_CVR, V = sample_variance_CVR, random = list(~1| strain_name, ~1|production_center, results.alltraits.grouping[t, 2] <- cvr$b
+    cvr <- metafor::rma.mv(yi = effect_size_CVR, V = sample_variance_CVR, random = list(~1| strain_name, ~1|production_center, ~1|err), control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000),  verbose=F, data = results)
+
+    results.alltraits.grouping[t, 2] <- cvr$b
     results.alltraits.grouping[t, 3] <- cvr$ci.lb
@@
 
-cv <- metafor::rma.mv(yi = effect_size_VR, V = sample_variance_VR, random = list(~1| strain_name, ~1|production_center,                                                             ~1|err), control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000),  verbose=F, data = results)
+cv <- metafor::rma.mv(yi = effect_size_VR, V = sample_variance_VR, random = list(~1| strain_name, ~1|production_center,~1|err), control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000),  verbose=F, data = results)
+
     results.alltraits.grouping[t, 6] <- cv$b
@@
 
-means <- metafor::rma.mv(yi = effect_size_RR, V = sample_variance_RR, random = list(~1| strain_name, ~1|production_center,
-                                                                            ~1|err),
-    control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), data = results)
+means <- metafor::rma.mv(yi = effect_size_RR, V = sample_variance_RR, random = list(~1| strain_name, ~1|production_center, ~1|err), control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), data = results)
     results.alltraits.grouping[t, 10] <- means$b
@@
         results.alltraits.grouping[t, 14] <- means$k
+        results.alltraits.grouping[t, 15] <- unique(results$trait)
 
@@
 }
+
+# Now that we have a "results" table with each of the meta-analytic means for all effect sizes of interest, we can use this table as part of the Shint App, which will then be able to back calculate the percentage differences between males and females for mean, variance and coefficient of variance.
+We'll export and use this in the Shiny App.
+**Note that I have not dealt with convergence issues in some of these models, and so, this will need to be done down the road**
+
+trait_meta_results <- write.csv(results.alltraits.grouping, file = "export/trait_meta_results.csv")
 

### 2019-07-05 SexDifference_Shiny/app.R

@@ -1,0 +1,49 @@
+
+library(shiny)
+
+meta_results <- read.csv("export/trait_meta_results.csv")
+
+ui <- fluidPage(mainPanel(shinythemes::themeSelector()),
+    # Application title
+    titlePanel("Trait Specific Percentage Differences in Mean and Variances between the Sexes"),
+    
+    sidebarPanel(strong("Introduction"),
+        p(" This Shiny app allows users to interface with the traits present in the mouse database, and using the meta-analytic results from analyses across strains and centers, calculate the percentage difference between males and females for the given trait. This can be quite useful in understanding how different traits cary across the sexes and in conducting power analyses when designing experiments with a given trait to ensure that differences between sexes can be detected with a given experimental design"), 
+        strong("How to use:"), p("Using the app is simple. Just find your trait of interest in the dropdown menu and the table will be updated with meta-analytic results. You can read the -  Interpretation of Output - for an example trait below the table.")
+    ),
+    # Trait inputs
+   mainPanel(
+        selectInput("trait", "Trait of Interest", unique(meta_results$trait), multiple = FALSE),
+    
+    # Output Table
+    tableOutput("table")), 
+    
+    mainPanel(strong("Interpretation of output:"),p(" To interpret the above table output users need to look at the percentage increase and the direction. For example, for the trait -  % pre-pulse inhibition - global - the mean percentage tells us that males are 0.73% larger than females as the direction tells us that males are greater than females (Males >). In contrast, when we look at the variance in this trait, we see that females have 1.11% larger variance than males (Females >)")
+    )    
+)
+
+server <- function(input, output){
+    
+    output$table <- renderTable({	
+            
+        # remember log(males/females)
+            sub_trait_data <- meta_results[meta_results$trait %in% as.character(input$trait),]
+            sub_trait_data_effects <- sub_trait_data[, c("lnRR", "lnVR", "lnCVR")]
+        
+        # odds ratio: 1 = males = females; <1 = males < females; >1 = males > females
+            odds_ratio <- as.numeric(exp(sub_trait_data_effects))
+        
+        # Calculate percent diff
+            perc_difference <- ifelse(odds_ratio < 1, (1-odds_ratio)*100, (odds_ratio-1)*100)
+            direct <- ifelse(odds_ratio < 1, "Males >", "Females >") 
+            
+        # Table output
[…]

### 2019-07-05 SexDifference_Shiny/app.R
Fixed Shiny app so runs from Rstudio; added a pretty pic

@@ -1,26 +1,34 @@
 
 library(shiny)
 
-meta_results <- read.csv("export/trait_meta_results.csv")
+meta_results <- read.csv("trait_meta_results.csv")
+
 
 ui <- fluidPage(mainPanel(shinythemes::themeSelector()),
     # Application title
     titlePanel("Trait Specific Percentage Differences in Mean and Variances between the Sexes"),
     
-    sidebarPanel(strong("Introduction"),
+    sidebarPanel(
+      strong("Introduction"),
         p(" This Shiny app allows users to interface with the traits present in the mouse database, and using the meta-analytic results from analyses across strains and centers, calculate the percentage difference between males and females for the given trait. This can be quite useful in understanding how different traits cary across the sexes and in conducting power analyses when designing experiments with a given trait to ensure that differences between sexes can be detected with a given experimental design"), 
-        strong("How to use:"), p("Using the app is simple. Just find your trait of interest in the dropdown menu and the table will be updated with meta-analytic results. You can read the -  Interpretation of Output - for an example trait below the table.")
+        strong("How to use:"), 
+      p("Using the app is simple. Just find your trait of interest in the dropdown menu and the table will be updated with meta-analytic results. You can read the -  Interpretation of Output - for an example trait below the table."), 
+        strong("Interpretation of output:"), 
+        p(" To interpret the above table output users need to look at the percentage increase and the direction. For example, for the trait -  % pre-pulse inhibition - global - the mean percentage tells us that males are 0.73% larger than females as the direction tells us that males are greater than females (Males >). In contrast, when we look at the variance in this trait, we see that females have 1.11% larger variance than males (Females >)")
     ),
+    
     # Trait inputs
    mainPanel(
         selectInput("trait", "Trait of Interest", unique(meta_results$trait), multiple = FALSE),
     
-    # Output Table
-    tableOutput("table")), 
-    
-    mainPanel(strong("Interpretation of output:"),p(" To interpret the above table output users need to look at the percentage increase and the direction. For example, for the trait -  % pre-pulse inhibition - global - the mean percentage tells us that males are 0.73% larger than females as the direction tells us that males are greater than females (Males >). In contrast, when we look at the variance in this trait, we see that females have 1.11% larger variance than males (Females >)")
+      # Output Table
+      tableOutput("table")
+    ), 
+  
+    mainPanel(
[…]

### 2019-07-25 R/Heterogeneity.Rmd
Add files via upload. Need to reconcile with Heterogeneity script, which will probably now become part of the main ms, not supplement

--- 2019-06-04 scripts/2019_4June_IMPC variance and sex difference.Rmd
@@
 ---
-title: "IMPC Mouse data - Variance in sex differences"
+title: "IMPC Mouse data - Heterogeneity"
 author: "Susanne & Felix Zajitschek"
-date: "2nd April 2019"
+date: "4rth April 2019"
 output:
@@
    toc: true
-    toc_float: true
-    toc_depth: 3
+   toc_depth: 2
 ---
@@
 ```
+####################################################################################################################################
+
+# ** FIGURE 4 (Second-order meta analysis on heterogeneity)
 
 # Loading functions that are necessary
-### Preparation of raw data
+##Preparation of raw data
 1) Data loading and cleaning of the csv file
@@
   if(Equal.E.C.Corr==T){
-    mvcorr <- 0 #cor.test(log(c(CMean, EMean)), log(c(CSD, ESD)))$estimate   old, slightly incorrect
+    mvcorr <- cor.test(log(c(CMean, EMean)), log(c(CSD, ESD)))$estimate
     S2 <- CSD^2 / (CN * (CMean^2)) + 1 / (2 * (CN - 1)) - 2 * mvcorr * sqrt((CSD^2 / (CN * (CMean^2))) * (1 / (2 * (CN - 1)))) + ESD^2 / (EN * (EMean^2)) + 1 / (2 * (EN - 1)) - 2 * mvcorr * sqrt((ESD^2 / (EN * (EMean^2))) * (1 / (2 * (EN - 1))))
@@
 data1 <- readRDS("export/data_clean.rds")
-#data1 
-```
-
-### Clean data
+
+```
+
+## Clean data
 This requires the selection of traits that have been measured in at least 2 centers. Consequently, rare or unusual methods and procedures are being filtered out in this step.
@@
 data2 <- dat_moreThan1center
-#min(data2$center_per_trait)  # as a check if there indeed are no single occurences
-
-```
-
-## Preparation for Meta analysis
-### Define population variable & add grouping variables
+#min(data2$center_per_trait)  # as a check ifthere indeed are no single occurences
+
+```
+
+#Preparation for Meta analysis
+## Define population variable & add grouping variables
 
@@
 
-### Assign each unique parameter_name (=trait,use trait variable) a unique number ('id')
+## Assign each unique parameter_name (=trait,use trait variable) a unique number ('id')
 We add a new variable, where redundant traits are combined
@@
 ```{r}
-#head(data)
+head(data)
 
@@
 
-### Create a matrix to store results for all traits
-As the current version of this script utilizes a loop instead of tidyR code, it is here necessary to create an empty matrix, in which the returning values will be stored.
-
-```{r}
-results.alltraits.grouping <- as.data.frame(cbind(c(1:n), matrix(rep(0, n*13), ncol = 13))) #number of individual results per trait = 10
-names(results.alltraits.grouping) <- c("id", "lnCVR", "lnCVR_lower", "lnCVR_upper", "lnCVR_se", "lnVR", "lnVR_lower", "lnVR_upper", "lnVR_se", "lnRR", "lnRR_lower", "lnRR_upper" ,"lnRR_se" , "sampleSize")
-
-```
-
-## LOOP, to run meta-analysis on all traits
-The loop combines the functions menationed above and fills the data matrix with results from our meta analysis. 
-Error messages indicate traits that either did not reach convergence, or that did not return meaningful results in the metaanalysis, due to absence of variance.
-Those traits will be removed ion later steps, outlined below.
+## *Create matrix to store results for all traits
+```{r}
+results.allhetero.grouping <- as.data.frame(cbind(c(1:n), matrix(rep(0, n*30), ncol = 30))) 
+names(results.allhetero.grouping) <- c("id", "sigma2_strain.CVR", "sigma2_center.CVR", "sigma2_error.CVR", "s.nlevels.strain.CVR", 
+	"s.nlevels.center.CVR", "s.nlevels.error.CVR", "sigma2_strain.VR", "sigma2_center.VR", "sigma2_error.VR", "s.nlevels.strain.VR", 
+	"s.nlevels.center.VR", "s.nlevels.error.VR", "sigma2_strain.RR", "sigma2_center.RR", "sigma2_error.RR", "s.nlevels.strain.RR", 
+	"s.nlevels.center.RR", "s.nlevels.error.RR", "lnCVR", "lnCVR_lower", "lnCVR_upper", "lnCVR_se", "lnVR", "lnVR_lower", "lnVR_upper", 
+	"lnVR_se", "lnRR", "lnRR_lower", "lnRR_upper" ,"lnRR_se")
+
+```
+
+# **LOOP
+#  parameters to extract from metafor (sigma2's, s.nlevels)
 
@@
 
-#lnCVR,  log repsonse-ratio of the coefficient of variance    
-    cvr <- metafor::rma.mv(yi = effect_size_CVR, V = sample_variance_CVR, random = list(~1| strain_name, ~1|production_center,    
+    # lnCVR, logaritm of the ratio of male and female coefficients of variance
+
+    cvr. <- metafor::rma.mv(yi = effect_size_CVR, V = sample_variance_CVR, random = list(~1| strain_name, ~1|production_center,    
                                 ~1|err), control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), data = results)
-    results.alltraits.grouping[t, 2] <- cvr$b
-    results.alltraits.grouping[t, 3] <- cvr$ci.lb
-    results.alltraits.grouping[t, 4] <- cvr$ci.ub
-    results.alltraits.grouping[t, 5] <- cvr$se
-
-    cvr
-
-    #lnVR, comparison of standard deviations
-
-cv <- metafor::rma.mv(yi = effect_size_VR, V = sample_variance_VR, random = list(~1| strain_name, ~1|production_center,                                                             ~1|err), control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000),  verbose=F, data = results)
-    results.alltraits.grouping[t, 6] <- cv$b
-    results.alltraits.grouping[t, 7] <- cv$ci.lb
-    results.alltraits.grouping[t, 8] <- cv$ci.ub
-    results.alltraits.grouping[t, 9] <- cv$se
-
-    # for means, lnRR
-
-means <- metafor::rma.mv(yi = effect_size_RR, V = sample_variance_RR, random = list(~1| strain_name, ~1|production_center,
-                                                                            ~1|err),
-    control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), data = results)
-    results.alltraits.grouping[t, 10] <- means$b
-    results.alltraits.grouping[t, 11] <- means$ci.lb
-    results.alltraits.grouping[t, 12] <- means$ci.ub
-    results.alltraits.grouping[t, 13] <- means$se
-
-        results.alltraits.grouping[t, 14] <- means$k
+    results.allhetero.grouping[t, 2] <- cvr.$sigma2[1]
+    results.allhetero.grouping[t, 3] <- cvr.$sigma2[2]
+    results.allhetero.grouping[t, 4] <- cvr.$sigma2[3]
+    results.allhetero.grouping[t, 5] <- cvr.$s.nlevels[1]
+    results.allhetero.grouping[t, 6] <- cvr.$s.nlevels[2]
+    results.allhetero.grouping[t, 7] <- cvr.$s.nlevels[3]
+     results.allhetero.grouping[t, 20] <- cvr.$b
+     results.allhetero.grouping[t, 21] <- cvr.$ci.lb
+     results.allhetero.grouping[t, 22] <- cvr.$ci.ub
+     results.allhetero.grouping[t, 23] <- cvr.$se
+
+    # lnVR, male to female variability ratio (logarithm of male and female standard deviations)
+
+    vr. <- metafor::rma.mv(yi = effect_size_VR, V = sample_variance_VR, random = list(~1| strain_name, ~1|production_center,    
+                                ~1|err), control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), data = results)
+    results.allhetero.grouping[t, 8] <- vr.$sigma2[1]
+    results.allhetero.grouping[t, 9] <- vr.$sigma2[2]
+    results.allhetero.grouping[t, 10] <- vr.$sigma2[3]
+    results.allhetero.grouping[t, 11] <- vr.$s.nlevels[1]
+    results.allhetero.grouping[t, 12] <- vr.$s.nlevels[2]
+    results.allhetero.grouping[t, 13] <- vr.$s.nlevels[3]
+     results.allhetero.grouping[t, 24] <- vr.$b
+     results.allhetero.grouping[t, 25] <- vr.$ci.lb
+     results.allhetero.grouping[t, 26] <- vr.$ci.ub
+     results.allhetero.grouping[t, 27] <- vr.$se
+
+    # lnRR, response ratio (logarithm of male and female means)
+
+    rr. <- metafor::rma.mv(yi = effect_size_RR, V = sample_variance_RR, random = list(~1| strain_name, ~1|production_center,    
+                                ~1|err), control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), data = results)
+    results.allhetero.grouping[t, 14] <- rr.$sigma2[1]
+    results.allhetero.grouping[t, 15] <- rr.$sigma2[2]
+    results.allhetero.grouping[t, 16] <- rr.$sigma2[3]
+    results.allhetero.grouping[t, 17] <- rr.$s.nlevels[1]
+    results.allhetero.grouping[t, 18] <- rr.$s.nlevels[2]
+    results.allhetero.grouping[t, 19] <- rr.$s.nlevels[3]
+     results.allhetero.grouping[t, 28] <- rr.$b
+     results.allhetero.grouping[t, 29] <- rr.$ci.lb
+     results.allhetero.grouping[t, 30] <- rr.$ci.ub
+     results.allhetero.grouping[t, 31] <- rr.$se
 
@@
 
-### Merging datasets
-
-Procedure names, groupiung variables etc are merged back together with the results from the metafor analysis above.
-This requires loading of another excel sheet, "procedures.csv"
-
+## *Exclude traits
+```{r}
+results.allhetero.grouping2 <- results.allhetero.grouping[results.allhetero.grouping$s.nlevels.strain.VR != 0, ]
+nrow(results.allhetero.grouping2) #218
+```
+
+# *Merge data sets containing metafor results with procedure etc. names 
 ```{r}
@@
 
-results.alltraits.grouping$parameter_group <- data$parameter_group[match(results.alltraits.grouping$id, data$id)]
-results.alltraits.grouping$procedure <- data$procedure_name[match(results.alltraits.grouping$id, data$id)]
-
-results.alltraits.grouping$GroupingTerm <-  procedures$GroupingTerm[match(results.alltraits.grouping$procedure, procedures$procedure)]
-results.alltraits.grouping$parameter_name <- data$parameter_name[match(results.alltraits.grouping$id, data$id)]
-
-meta1 <- results.alltraits.grouping
-n <- length(unique(meta1$parameter_name)) # 232
-```
-
-Removal of traits that did not achieve convergence, are non-sensical for analysis of variance (such as traits that show variaton, such as number of ribs, digits, etc).
-14 traits from the originally 232 that had been included are removed.
-
-```{r}
-meta_clean <- meta1[ !(meta1$id %in% c(84,144,158,160,161,162,163,165,166,167,168,221,222,231)), ]
-removed <-length(unique(meta_clean$parameter_name)) #218
-```
-
-## Dealing with Correlated Paramters
-
-This dataset contained a number of highly correlated taits, such as different kinds of cell counts (for example, hierarchichal parametrization within immunologocal assays).
-As those datapoints are not independent of each other,  we conducted a meta analyses on these correlated parameters to collapse the number of levels.
-
-### Collapsing correlated parameters
-
-Here we double check numbers of trait parameters in the dataset
-
-```{r}
-
-meta1 <- meta_clean 
-# length(unique(meta1$procedure)) #18
-# length(unique(meta1$GroupingTerm)) #9 
-# length(unique(meta1$parameter_group)) # 148 levels.
-To be used as grouping factor for meta-meta analysis / collapsing down based on things that are classified identically in "parameter_group" but have different "parameter_name"
-length(unique(meta1$parameter_name)) #218
-
-```
-
-### Count of number of parameter names (correlated sub-traits) in each parameter group (par_group_size) 
-This serves to idenfify and separate the traits that are correlated from the full dataset that can be preocessed as is.
-If the sample size (n) for a given "parameter group" equals 1, the trait is unique and uncorrelated.
-All instances, where there are 2 or more traits accociated with the same  parameter group (90 cases), are selected for a "mini-meta analysis", which removes the issue of correlation.
-
-```{r}
-
-kable(cbind (meta1 %>%  count(parameter_group) )) %>%
-  kable_styling() %>%
-  scroll_box(width = "100%", height = "200px")
-
-meta1b <-
-  meta1 %>%
+results.allhetero.grouping2$parameter_group <- data$parameter_group[match(results.allhetero.grouping2$id, data$id)]
+results.allhetero.grouping2$procedure <- data$procedure_name[match(results.allhetero.grouping2$id, data$id)]
+
+results.allhetero.grouping2$GroupingTerm <-  procedures$GroupingTerm[match(results.allhetero.grouping2$procedure, procedures$procedure)]
+results.allhetero.grouping2$parameter_name <- data$parameter_name[match(results.allhetero.grouping2$id, data$id)]
+
+```
+
+## *Correlated parameters
+
+```{r}
+metahetero1 <- results.allhetero.grouping2 
+length(unique(metahetero1$procedure)) #18
+length(unique(metahetero1$GroupingTerm)) #9 
+length(unique(metahetero1$parameter_group)) # 149 levels: one more tha in effect size alanlysis, see above; CHECK!
+length(unique(metahetero1$parameter_name)) #218
+
+```
+
+# **Count of number of parameter names (correlated sub-traits) in each parameter group (par_group_size)
+
+```{r}
+metahetero1b <-
+  metahetero1 %>%
   group_by(parameter_group) %>% 
-  summarize(par_group_size = length(unique(parameter_name, na.rm = TRUE)))
-#this gives a summary of number of parameter names in each parameter group, now it neeeds to get merged it back together
-
-meta1$par_group_size <- meta1b$par_group_size[match(meta1$parameter_group, meta1b$parameter_group)]
-
-# Create subsets with > 1 count (par_group_size > 1)
-
-meta1_sub<-subset(meta1,par_group_size >1) # 90 observations   
-meta1_sub$sampleSize <- as.numeric(meta1_sub$sampleSize)
-
-```
-
-# Preparation for Visualization and Meta-analysis
-
-### Perform meta-analyses on correlated sub-traits, using robumeta 
-The subset of the data is prepared (nested), and in this first step the model of the meta analysis effect sizes are calculated
-
-```{r}
-# nesting
-n_count <- meta1_sub %>% 
+  mutate(par_group_size = n_distinct(parameter_name))
+
+metahetero1$par_group_size <- metahetero1b$par_group_size[match(metahetero1$parameter_group, metahetero1b$parameter_group)]
+
+```
+
+# **Create subsets with > 1 count (par_group_size > 1)
+
+```{r}
+metahetero1_sub <- subset(metahetero1, par_group_size > 1) # 90 observations  
+str(metahetero1_sub)
+# metahetero1_sub$sampleSize <- as.numeric(metahetero1_sub$sampleSize) #from previous analysis? don't think is used: : delete in final version
+```
+
+# **Nest data
+```{r}
+n_count. <- metahetero1_sub %>% 
   group_by(parameter_group) %>% 
-  mutate(raw_N = sum(sampleSize)) %>%  
+  #mutate(raw_N = sum(sampleSize)) %>%  #don't think is necessary: delete in final version
   nest()
 
-model_count <- n_count %>% 
+```
+
+```{r}
+model_count. <- n_count. %>% 
   mutate(model_lnRR = map(data, ~ robu(.x$lnRR ~ 1, data= .x, studynum= .x$id, modelweights = c("CORR"), rho = 0.8, 
@@
                                                 small = TRUE, var.eff.size= (.x$lnCVR_se)^2 )))
-```
-
-### Extract and save parameter estimates 
-Function to collect the outcomes of the "mini" meta analysis
-```{r}
-count_fun <- function(mod_sub)
-  return(c(mod_sub$reg_table$b.r, mod_sub$reg_table$CI.L, mod_sub$reg_table$CI.U, mod_sub$reg_table$SE))   #estimate, lower ci, upper ci, SE
-```
-
-Extraction of values created during Meta analysis using robu meta
-```{r}
-robusub_RR <- model_count %>% 
-  transmute(parameter_group, estimatelnRR = map(model_lnRR, count_fun)) %>% 
+
+```
+#Robumeta object details:
+#str(model_count.$model_lnCVR[[1]])
+
+## *Perform meta-analyses on correlated sub-traits, using robumeta
+
+# Shinichi: We think we want to use these for further analyses:
+# residual variance: as.numeric(robu_fit$mod_info$term1)     (same as 'mod_info$tau.sq')
+# sample size: robu_fit$N
+
+## **Extract and save parameter estimates 
+```{r}
+count_fun. <- function(mod_sub)
+  return(c(as.numeric(mod_sub$mod_info$term1), mod_sub$N) )
+
+```
+
+```{r}
+robusub_RR. <- model_count. %>% 
+  transmute(parameter_group, estimatelnRR = map(model_lnRR, count_fun.)) %>% 
   mutate(r = map(estimatelnRR, ~ data.frame(t(.)))) %>%
@@
   select(-estimatelnRR) %>%
-  purrr::set_names(c("parameter_group","lnRR","lnRR_lower","lnRR_upper","lnRR_se"))
-
-robusub_CVR <- model_count %>% 
-  transmute(parameter_group, estimatelnCVR = map(model_lnCVR, count_fun)) %>% 
+  purrr::set_names(c("parameter_group","var.RR","N.RR"))
+
+robusub_CVR. <- model_count. %>% 
+  transmute(parameter_group, estimatelnCVR = map(model_lnCVR, count_fun.)) %>% 
   mutate(r = map(estimatelnCVR, ~ data.frame(t(.)))) %>%
@@
   select(-estimatelnCVR) %>%
-  purrr::set_names(c("parameter_group","lnCVR","lnCVR_lower","lnCVR_upper","lnCVR_se"))
-
-robusub_VR <- model_count %>% 
-  transmute(parameter_group, estimatelnVR = map(model_lnVR, count_fun)) %>% 
+  purrr::set_names(c("parameter_group","var.CVR","N.CVR"))
+
+robusub_VR. <- model_count. %>% 
+  transmute(parameter_group, estimatelnVR = map(model_lnVR, count_fun.)) %>% 
   mutate(r = map(estimatelnVR, ~ data.frame(t(.)))) %>%
@@
   select(-estimatelnVR) %>%
-  purrr::set_names(c("parameter_group","lnVR","lnVR_lower","lnVR_upper","lnVR_se"))
-
-robu_all <- full_join(robusub_CVR, robusub_VR) %>% full_join(., robusub_RR)
-kable(cbind(robu_all, robu_all)) %>%
-  kable_styling() %>%
-  scroll_box(width = "100%", height = "200px")
-
-```
-
- Merge the two data sets (the new [robu_all] and the initial [uncorrelated sub-traits with count = 1]) 
-```{r}
-meta_all <- meta1 %>% filter(par_group_size == 1) %>% as_tibble
-#str(meta_all)
-#str(robu_all)
-#which(is.na(match(names(meta_all),names(robu_all))))  # check
-```
-
-Combine data 
-```{r}
+  purrr::set_names(c("parameter_group","var.VR","N.VR"))
+
+robu_all. <- full_join(robusub_CVR., robusub_VR.) %>% full_join(., robusub_RR.)
+
+```
+
+## **Merge the two data sets (the new [robu_all] and the initial [uncorrelated sub-traits with count = 1]) 
+##  In this step, we 	
+1) put the N from robumeta and the  N from metafor (s.nlevels.error) together into the same columns (N.RR, N.VR, N.CVR)
+
+2) calculate the total variance for metafor models as the sum of random effect variances and the residual error,
+							then put them in the same columns together with the residual variances from robumeta
+```{r}
+metahetero_all <- metahetero1 %>% filter(par_group_size == 1) %>% as_tibble
+metahetero_all$N.RR <- metahetero_all$s.nlevels.error.RR 
+metahetero_all$N.CVR <- metahetero_all$s.nlevels.error.CVR 
+metahetero_all$N.VR <- metahetero_all$s.nlevels.error.VR
+
+# log (srt( of the data to look at))
+metahetero_all$var.RR <- log(sqrt(metahetero_all$sigma2_strain.RR + metahetero_all$sigma2_center.RR + metahetero_all$sigma2_error.RR))
+metahetero_all$var.VR <- log(sqrt(metahetero_all$sigma2_strain.VR + metahetero_all$sigma2_center.VR + metahetero_all$sigma2_error.VR))
+metahetero_all$var.CVR <- log(sqrt(metahetero_all$sigma2_strain.CVR + metahetero_all$sigma2_center.CVR + metahetero_all$sigma2_error.CVR))
+#str(metahetero_all)
+#str(robu_all.)
+
+#adjust the -inf to smallest number in dataset
+metahetero_all <- metahetero_all %>% mutate(var.RR = if_else(var.RR == -Inf, -7 ,var.RR),
+                   	  var.VR = if_else(var.VR == -Inf, -5 ,var.VR),
+				  var.CVR = if_else(var.CVR == -Inf, -6 ,var.CVR))
+
+```
+
+# **Combine data 
 # Step1 
-combinedmeta <- bind_rows(robu_all, meta_all)
-#glimpse(combinedmeta)
-
+```{r}
+combinedmetahetero <- bind_rows(robu_all., metahetero_all)
+#glimpse(combinedmetahetero)
+```
 # Steps 2&3
-metacombo <- combinedmeta
-metacombo$counts <- meta1$par_group_size[match( metacombo$parameter_group, meta1$parameter_group)]
-metacombo$procedure2 <-meta1$procedure[match( metacombo$parameter_group, meta1$parameter_group)]
-metacombo$GroupingTerm2 <-meta1$GroupingTerm[match( metacombo$parameter_group, meta1$parameter_group)]
-
-kable(cbind (metacombo, metacombo)) %>%
-  kable_styling() %>%
-  scroll_box(width = "100%", height = "200px")
-
-```
-### Clean-up and rename 
-```{r}
-metacombo <-metacombo[, c(1, 20:22, 2:13)] 
-names(metacombo)[3] <- "procedure" 
-names(metacombo)[4] <- "GroupingTerm"
-
-# Quick pre-check before doing plots
-
-compare <- metacombo %>%
-  group_by(GroupingTerm) %>%
-  dplyr::summarize(MeanCVR = mean(lnCVR),MeanVR = mean(lnVR), MeanRR = mean(lnRR) )
-
-compare
-
-```
-
-## Last step: meta-meta-analysis 
-### Perform meta-analyses (3 for each of the 9 grouping terms: lnCVR, lnVR, lnRR) 
-This is the full result dataset
-```{r}
-
-kable(cbind (metacombo,metacombo)) %>%
-  kable_styling() %>%
-  scroll_box(width = "100%", height = "200px")
-
-```
-
-### Prepare data
-Nesting, calculating the number of parameters within each grouping term, and running the metaanalysis
-```{r}
-metacombo_final <- metacombo %>%
+```{r}
+metacombohetero <- combinedmetahetero
+metacombohetero$counts <- metahetero1$par_group_size[match( metacombohetero$parameter_group, metahetero1$parameter_group)]
+metacombohetero$procedure2 <-metahetero1$procedure[match( metacombohetero$parameter_group, metahetero1$parameter_group)]
+metacombohetero$GroupingTerm2 <-metahetero1$GroupingTerm[match( metacombohetero$parameter_group, metahetero1$parameter_group)]
+
+```
+# **Clean-up and rename 
+```{r}
+metacombohetero <- metacombohetero[, c(1:7, 43:45)] 
+names(metacombohetero)[9] <- "procedure" 
+names(metacombohetero)[10] <- "GroupingTerm"
+
+```
+
+```{r}
+#write.csv(metacombohetero, "metacombohetero.csv")
+
+```
+
+## *Last step: meta-meta-analysis of heterogeneity
+```{r}
+glimpse(metacombohetero)
+
+## *Perform meta-meta-analysis (3 for each of the 9 grouping terms: var.CVR, var.VR, var.RR)
+
+metacombohetero_final <- metacombohetero %>%
  group_by(GroupingTerm) %>%
@@
 
-# **Calculate number of parameters per grouping term
-
-metacombo_final <- metacombo_final  %>%  mutate(para_per_GroupingTerm = map_dbl(data, nrow))
-
-# For all grouping terms
-metacombo_final_all <- metacombo %>%
- nest()
+# **Calculate number of parameters per grouping term : not needed; delete in final version
+#metacombo_final <- metacombo_final  %>%  mutate(para_per_GroupingTerm = map_dbl(data, nrow))
 
 # **Final fixed effects meta-analyses within grouping terms, with SE of the estimate 
-
-overall1 <- metacombo_final %>%
-
-  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower)/ (2*1.96),  
-				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)),
-	   model_lnVR = map(data, ~ metafor::rma.uni(yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower)/ (2*1.96),  
-				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)),
-	   model_lnRR = map(data, ~ metafor::rma.uni(yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower)/ (2*1.96),  
-				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)))
-
-# **Final fixed effects meta-analyses ACROSS grouping terms, with SE of the estimate
-
-overall_all1 <- metacombo_final_all %>%
-
-  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower)/ (2*1.96),  
-				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)),
-	   model_lnVR = map(data, ~ metafor::rma.uni(yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower)/ (2*1.96),  
-				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)),
-	   model_lnRR = map(data, ~ metafor::rma.uni(yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower)/ (2*1.96),  
-				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)))
-
-```
-
-Re-structure data for each grouping term; delete un-used variables
-
-```{r}
-Behaviour <- as.data.frame(overall1 %>% filter(., GroupingTerm == "Behaviour")    %>%  mutate(lnCVR=.[[4]][[1]]$b, lnCVR_lower=.[[4]][[1]]$ci.lb, lnCVR_upper=.[[4]][[1]]$ci.ub, lnCVR_se=.[[4]][[1]]$se,
-	              lnVR=.[[5]][[1]]$b, lnVR_lower=.[[5]][[1]]$ci.lb, lnVR_upper=.[[5]][[1]]$ci.ub, lnVR_se=.[[5]][[1]]$se,
-		        lnRR=.[[6]][[1]]$b, lnRR_lower=.[[6]][[1]]$ci.lb, lnRR_upper=.[[6]][[1]]$ci.ub, lnRR_se=.[[6]][[1]]$se) )[, c(1,7:18)]
-
-Immunology <- as.data.frame(overall1 %>% filter(., GroupingTerm == "Immunology")    %>%  mutate(lnCVR=.[[4]][[1]]$b, lnCVR_lower=.[[4]][[1]]$ci.lb, lnCVR_upper=.[[4]][[1]]$ci.ub, lnCVR_se=.[[4]][[1]]$se,
-	              lnVR=.[[5]][[1]]$b, lnVR_lower=.[[5]][[1]]$ci.lb, lnVR_upper=.[[5]][[1]]$ci.ub, lnVR_se=.[[5]][[1]]$se,
-		        lnRR=.[[6]][[1]]$b, lnRR_lower=.[[6]][[1]]$ci.lb, lnRR_upper=.[[6]][[1]]$ci.ub, lnRR_se=.[[6]][[1]]$se) )[, c(1,7:18)]
-
-Hematology <- as.data.frame(overall1 %>% filter(., GroupingTerm == "Hematology")    %>%  mutate(lnCVR=.[[4]][[1]]$b, lnCVR_lower=.[[4]][[1]]$ci.lb, lnCVR_upper=.[[4]][[1]]$ci.ub, lnCVR_se=.[[4]][[1]]$se,
-	              lnVR=.[[5]][[1]]$b, lnVR_lower=.[[5]][[1]]$ci.lb, lnVR_upper=.[[5]][[1]]$ci.ub, lnVR_se=.[[5]][[1]]$se,
-		        lnRR=.[[6]][[1]]$b, lnRR_lower=.[[6]][[1]]$ci.lb, lnRR_upper=.[[6]][[1]]$ci.ub, lnRR_se=.[[6]][[1]]$se) )[, c(1,7:18)]
-
-Hearing <- as.data.frame(overall1 %>% filter(., GroupingTerm == "Hearing")   %>%  mutate(lnCVR=.[[4]][[1]]$b, lnCVR_lower=.[[4]][[1]]$ci.lb, lnCVR_upper=.[[4]][[1]]$ci.ub, lnCVR_se=.[[4]][[1]]$se,
-	              lnVR=.[[5]][[1]]$b, lnVR_lower=.[[5]][[1]]$ci.lb, lnVR_upper=.[[5]][[1]]$ci.ub, lnVR_se=.[[5]][[1]]$se,
-		        lnRR=.[[6]][[1]]$b, lnRR_lower=.[[6]][[1]]$ci.lb, lnRR_upper=.[[6]][[1]]$ci.ub, lnRR_se=.[[6]][[1]]$se) )[, c(1,7:18)]
-
-Physiology <- as.data.frame(overall1 %>% filter(., GroupingTerm == "Physiology")  %>%  mutate(lnCVR=.[[4]][[1]]$b, lnCVR_lower=.[[4]][[1]]$ci.lb, lnCVR_upper=.[[4]][[1]]$ci.ub, lnCVR_se=.[[4]][[1]]$se,
-	              lnVR=.[[5]][[1]]$b, lnVR_lower=.[[5]][[1]]$ci.lb, lnVR_upper=.[[5]][[1]]$ci.ub, lnVR_se=.[[5]][[1]]$se,
-		        lnRR=.[[6]][[1]]$b, lnRR_lower=.[[6]][[1]]$ci.lb, lnRR_upper=.[[6]][[1]]$ci.ub, lnRR_se=.[[6]][[1]]$se) )[, c(1,7:18)]
-
-Metabolism <- as.data.frame(overall1 %>% filter(., GroupingTerm == "Metabolism")  %>%  mutate(lnCVR=.[[4]][[1]]$b, lnCVR_lower=.[[4]][[1]]$ci.lb, lnCVR_upper=.[[4]][[1]]$ci.ub, lnCVR_se=.[[4]][[1]]$se,
-	              lnVR=.[[5]][[1]]$b, lnVR_lower=.[[5]][[1]]$ci.lb, lnVR_upper=.[[5]][[1]]$ci.ub, lnVR_se=.[[5]][[1]]$se,
-		        lnRR=.[[6]][[1]]$b, lnRR_lower=.[[6]][[1]]$ci.lb, lnRR_upper=.[[6]][[1]]$ci.ub, lnRR_se=.[[6]][[1]]$se) )[, c(1,7:18)]
-
-Morphology <- as.data.frame(overall1 %>% filter(., GroupingTerm == "Morphology")  %>%  mutate(lnCVR=.[[4]][[1]]$b, lnCVR_lower=.[[4]][[1]]$ci.lb, lnCVR_upper=.[[4]][[1]]$ci.ub, lnCVR_se=.[[4]][[1]]$se,
-	              lnVR=.[[5]][[1]]$b, lnVR_lower=.[[5]][[1]]$ci.lb, lnVR_upper=.[[5]][[1]]$ci.ub, lnVR_se=.[[5]][[1]]$se,
-		        lnRR=.[[6]][[1]]$b, lnRR_lower=.[[6]][[1]]$ci.lb, lnRR_upper=.[[6]][[1]]$ci.ub, lnRR_se=.[[6]][[1]]$se) )[, c(1,7:18)]
-
-Heart <- as.data.frame(overall1 %>% filter(., GroupingTerm == "Heart")  %>%  mutate(lnCVR=.[[4]][[1]]$b, lnCVR_lower=.[[4]][[1]]$ci.lb, lnCVR_upper=.[[4]][[1]]$ci.ub, lnCVR_se=.[[4]][[1]]$se,
-	              lnVR=.[[5]][[1]]$b, lnVR_lower=.[[5]][[1]]$ci.lb, lnVR_upper=.[[5]][[1]]$ci.ub, lnVR_se=.[[5]][[1]]$se,
-		        lnRR=.[[6]][[1]]$b, lnRR_lower=.[[6]][[1]]$ci.lb, lnRR_upper=.[[6]][[1]]$ci.ub, lnRR_se=.[[6]][[1]]$se) )[, c(1,7:18)]
-
-Eye <- as.data.frame(overall1 %>% filter(., GroupingTerm == "Eye")  %>%  mutate(lnCVR=.[[4]][[1]]$b, lnCVR_lower=.[[4]][[1]]$ci.lb, lnCVR_upper=.[[4]][[1]]$ci.ub, lnCVR_se=.[[4]][[1]]$se,
-	              lnVR=.[[5]][[1]]$b, lnVR_lower=.[[5]][[1]]$ci.lb, lnVR_upper=.[[5]][[1]]$ci.ub, lnVR_se=.[[5]][[1]]$se,
-		        lnRR=.[[6]][[1]]$b, lnRR_lower=.[[6]][[1]]$ci.lb, lnRR_upper=.[[6]][[1]]$ci.ub, lnRR_se=.[[6]][[1]]$se) )[, c(1,7:18)]
-
-All <- as.data.frame(overall_all1  %>%  mutate(lnCVR=.[[2]][[1]]$b, lnCVR_lower=.[[2]][[1]]$ci.lb, lnCVR_upper=.[[2]][[1]]$ci.ub, lnCVR_se=.[[2]][[1]]$se,lnVR=.[[3]][[1]]$b, lnVR_lower=.[[3]][[1]]$ci.lb, lnVR_upper=.[[3]][[1]]$ci.ub, lnVR_se=.[[3]][[1]]$se,
-		        lnRR=.[[4]][[1]]$b, lnRR_lower=.[[4]][[1]]$ci.lb, lnRR_upper=.[[4]][[1]]$ci.ub, lnRR_se=.[[4]][[1]]$se) )[, c(5:16)]
-
-All$lnCVR <- as.numeric(All$lnCVR)
-All$lnVR <- as.numeric(All$lnVR)
-All$lnRR <- as.numeric(All$lnRR)
-All <- All %>% mutate(GroupingTerm = "All")
-
-overall2 <- bind_rows(Behaviour, Morphology, Metabolism, Physiology, Immunology, Hematology, Heart, Hearing, Eye, All)
-
-```
-
-# PLOTS
-
-## Plot FIGURE 2 (First-order meta analysis results)
-
-Re-order grouping terms
-
-```{r}
-
-meta_clean$GroupingTerm <- factor(meta_clean$GroupingTerm, levels =c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye") )
-meta_clean$GroupingTerm <- factor(meta_clean$GroupingTerm, rev(levels(meta_clean$GroupingTerm)))
-
-# *Prepare data for all traits
-
-meta.plot2.all <- meta_clean %>% select(lnCVR, lnVR, lnRR, GroupingTerm) %>% arrange(GroupingTerm)
-
-meta.plot2.all.b <- gather(meta.plot2.all, trait, value, c(lnCVR, lnVR, lnRR))
-
-meta.plot2.all.b$trait <- factor(meta.plot2.all.b$trait, levels =c("lnCVR","lnVR","lnRR") )
-
-meta.plot2.all.c <- meta.plot2.all.b  %>%
-				group_by_at(vars(trait, GroupingTerm)) %>%
-				summarise(malebias = sum(value > 0), femalebias = sum(value<= 0), total= malebias + femalebias, 
-					malepercent = malebias*100/total, femalepercent = femalebias*100/total)
-
-meta.plot2.all.c$label <- "All traits"
-
-# restructure to create stacked bar plots
-
-meta.plot2.all.d <- as.data.frame(meta.plot2.all.c)
-meta.plot2.all.e <- gather(meta.plot2.all.d, key = sex, value = percent, malepercent:femalepercent, factor_key = TRUE)
-
-# create new sample size variable
-
-meta.plot2.all.e$samplesize <- with(meta.plot2.all.e, ifelse(sex == "malepercent", malebias, femalebias) )
-
-malebias_Fig2_alltraits <- 
-ggplot(meta.plot2.all.e) +
-  aes(x = GroupingTerm, y = percent, fill = sex) +
-  geom_col() +
-  geom_hline(yintercept = 50, linetype = "dashed", color = "gray40") +
-  geom_text(data = subset(meta.plot2.all.e, samplesize != 0), aes(label = samplesize), position = position_stack(vjust = .5), 
-	color = "white", size = 3.5) +
- facet_grid(cols = vars(trait), rows = vars(label),  labeller = label_wrap_gen(width = 18), 
-      scales= 'free', space='free') +
- scale_fill_brewer(palette = "Set2") +
-theme_bw(base_size = 18) +
-  	theme(strip.text.y = element_text(angle = 270, size = 10, margin = margin(t=15, r=15, b=15, l=15)), 
-	  strip.text.x = element_text(size = 12),
-        strip.background = element_rect(colour = NULL,linetype = "blank", fill = "gray90"),
-        text = element_text(size=14),
-        panel.spacing = unit(0.5, "lines"),
-        panel.border= element_blank(),
-        axis.line=element_line(), 
-        panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
-        panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
-        panel.grid.minor.y = element_blank(),
-        panel.grid.minor.x = element_blank(), 
-        legend.position = "none",
-        axis.title.x = element_blank(),
-	  axis.title.y = element_blank()  ) +
-	coord_flip()
-
-#malebias_Fig2_alltraits
-
-```
-
-### Prepare data for traits with CI not overlapping 0
-create column with 1= different from zero, 0= zero included in CI
-```{r}
-
-meta.plot2.sig <- meta_clean %>% 
-    mutate(lnCVRsig = ifelse(lnCVR_lower*lnCVR_upper >0, 1, 0), lnVRsig = ifelse(lnVR_lower*lnVR_upper >0, 1, 0), 
-	     lnRRsig = ifelse(lnRR_lower*lnRR_upper > 0, 1,0))
-
-meta.plot2.sig.b <- meta.plot2.sig[, c("lnCVR", "lnVR", "lnRR", "lnCVRsig", "lnVRsig", "lnRRsig", "GroupingTerm")]
-
-meta.plot2.sig.c <- gather(meta.plot2.sig.b, trait, value, lnCVR:lnRR)
-meta.plot2.sig.c$sig <- "placeholder"
-
-meta.plot2.sig.c$trait <- factor(meta.plot2.sig.c$trait, levels =c("lnCVR","lnVR","lnRR") )
-
-meta.plot2.sig.c$sig <- ifelse(meta.plot2.sig.c$trait == "lnCVR", meta.plot2.sig.c$lnCVRsig,
-				ifelse(meta.plot2.sig.c$trait == "lnVR", meta.plot2.sig.c$lnVRsig, meta.plot2.sig.c$lnRRsig))
-
-#choosing sex biased ln-ratios significantly larger than 0
-meta.plot2.sig.malebias <- meta.plot2.sig.c %>%
-				group_by_at(vars(trait, GroupingTerm)) %>%
-				filter(sig== 1) %>%
-				summarise(male_sig = sum(value > 0), female_sig = sum(value < 0), total = male_sig + female_sig)
-
-meta.plot2.sig.malebias <- ungroup(meta.plot2.sig.malebias) %>%
-				add_row(trait = "lnCVR", GroupingTerm = "Hearing", male_sig = 0, female_sig = 0, .before = 4) %>% #add "Hearing" for lnCVR (not filtered as only zeros)
-				mutate(malepercent = male_sig*100 / total, femalepercent = female_sig*100 / total)
-
-meta.plot2.sig.malebias$label <- "CI not overlapping zero"
-
-# restructure to create stacked bar plots
-
-meta.plot2.sig.bothsexes <- as.data.frame(meta.plot2.sig.malebias)
-meta.plot2.sig.bothsexes.b <- gather(meta.plot2.sig.bothsexes, key = sex, value = percent, malepercent:femalepercent, factor_key = TRUE)
-
-# create new sample size variable
-
-meta.plot2.sig.bothsexes.b$samplesize <- with(meta.plot2.sig.bothsexes.b, ifelse(sex == "malepercent", male_sig, female_sig) )
-
-# *Plot Fig2 all significant results (CI not overlapping zero): 
-#     no sig. lnCVR for 'Hearing' in either sex; no sig. male-biased lnCVR for 'Immunology' and 'Eye, and no sig. male-biased lnVR for 'Eye'
-
-malebias_Fig2_sigtraits <-  
-ggplot(meta.plot2.sig.bothsexes.b) +
-  aes(x = GroupingTerm, y = percent, fill = sex) +
-  geom_col() +
-  geom_hline(yintercept = 50, linetype = "dashed", color = "gray40") +
-  geom_text(data = subset(meta.plot2.sig.bothsexes.b, samplesize != 0), aes(label = samplesize), position = position_stack(vjust = .5), 
-	color = "white", size = 3.5) +
- facet_grid(cols = vars(trait), rows = vars(label),  labeller = label_wrap_gen(width = 18), 
-      scales= 'free', space='free') +
- scale_fill_brewer(palette = "Set2") +
-theme_bw(base_size = 18) +
-  	theme(strip.text.y = element_text(angle = 270, size = 10, margin = margin(t=15, r=15, b=15, l=15)), 
-	  strip.text.x = element_blank(),
-        strip.background = element_rect(colour = NULL,linetype = "blank", fill = "gray90"),
-        text = element_text(size=14),
-        panel.spacing = unit(0.5, "lines"),
-        panel.border= element_blank(),
-        axis.line=element_line(), 
-        panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
-        panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
-        panel.grid.minor.y = element_blank(),
-        panel.grid.minor.x = element_blank(), 
-        legend.position = "none",
-        axis.title.x = element_blank(),
-	  axis.title.y = element_blank()  ) +
-	coord_flip()
-```
-
-Prepare data for traits with effect size ratios > 10% larger in males
-```{r}
-meta.plot2.over10 <- meta_clean %>% select(lnCVR, lnVR, lnRR, GroupingTerm) %>% arrange(GroupingTerm)
-
-meta.plot2.over10.b <- gather(meta.plot2.over10, trait, value, c(lnCVR, lnVR, lnRR))
-
-meta.plot2.over10.b$trait <- factor(meta.plot2.over10.b$trait, levels =c("lnCVR","lnVR","lnRR") )
-
-meta.plot2.over10.c <- meta.plot2.over10.b  %>%
-				group_by_at(vars(trait, GroupingTerm)) %>%
-				summarise(malebias = sum(value > log(11/10)), femalebias = sum(value < log(9/10)), total= malebias + femalebias, 
-					malepercent = malebias*100/total, femalepercent = femalebias*100/total)
-
-meta.plot2.over10.c$label <- "Sex difference in m/f ratios > 10%"
-
-# restructure to create stacked bar plots
-
-meta.plot2.over10.c <- as.data.frame(meta.plot2.over10.c)
-meta.plot2.over10.d <- gather(meta.plot2.over10.c, key = sex, value = percent, malepercent:femalepercent, factor_key = TRUE)
-
-# create new sample size variable
-
-meta.plot2.over10.d$samplesize <- with(meta.plot2.over10.d, ifelse(sex == "malepercent", malebias, femalebias) )
-
-# *Plot Fig2 Sex difference in m/f ratio > 10%
-malebias_Fig2_over10 <- 
-ggplot(meta.plot2.over10.d) +
-  aes(x = GroupingTerm, y = percent, fill = sex) +
-  geom_col() +
-  geom_hline(yintercept = 50, linetype = "dashed", color = "gray40") +
-  geom_text(data = subset(meta.plot2.over10.d, samplesize != 0), aes(label = samplesize), position = position_stack(vjust = .5), 
-	color = "white", size = 3.5) +
- facet_grid(cols = vars(trait), rows = vars(label),  labeller = label_wrap_gen(width = 18), 
-      scales= 'free', space='free') +
- scale_fill_brewer(palette = "Set2") +
-theme_bw(base_size = 18) +
-  	theme(strip.text.y = element_text(angle = 270, size = 10, margin = margin(t=15, r=15, b=15, l=15)), 
-	  strip.text.x = element_blank(),
-        strip.background = element_rect(colour = NULL,linetype = "blank", fill = "gray90"),
-        text = element_text(size=14),
-        panel.spacing = unit(0.5, "lines"),
-        panel.border= element_blank(),
-        axis.line=element_line(), 
-        panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
-        panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
-        panel.grid.minor.y = element_blank(),
-        panel.grid.minor.x = element_blank(), 
-        legend.position = "none",
-        axis.title.x = element_blank(),
-	  axis.title.y = element_blank()  ) +
-	coord_flip()
-#malebias_Fig2_over10
-
-```
-### Create final combined Figure (Figure 2)
-```{r}
-
-Fig2 <- ggarrange(malebias_Fig2_alltraits, malebias_Fig2_sigtraits,malebias_Fig2_over10, nrow = 3, align = "v", heights = c(1.22,1,1))
-Fig2
-#ggsave("Fig2.pdf", plot = Fig2, width = 6, height = 5) 
-```
-
-## Preparation, for Figure 3: Overall results of second order meta anlaysis
-### Restructure data for plotting 
-Data are restructred, and grouping terms are being re-ordered
-```{r}
-overall3 <- gather(overall2, parameter, value, c(lnCVR, lnVR, lnRR), factor_key= TRUE)
-
-lnCVR.ci <- overall3 %>% filter(parameter == "lnCVR") %>% mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
-lnVR.ci <- overall3 %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
-lnRR.ci <- overall3 %>% filter(parameter == "lnRR") %>% mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
-
-overall4 <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
-
-# re-order Grouping Terms
-
-overall4$GroupingTerm <- factor(overall4$GroupingTerm, levels =c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye", "All") )
-overall4$GroupingTerm <- factor(overall4$GroupingTerm, rev(levels(overall4$GroupingTerm)))
-overall4$label <- "All traits"
-
-kable(cbind(overall4, overall4)) %>%
-  kable_styling() %>%
-  scroll_box(width = "100%", height = "200px")
-
-```
-
-### Plot FIGURE 3 (Second-order meta analysis results)
-
-Preparation: Sub-Plot  for Figure 3: all traits
-```{r}
-
-Metameta_Fig3_alltraits <- overall4 %>%
+# Shinichi: meta-analyses on heterogeneity, using  sei as below, in metafor formula
+
+heterog1 <- metacombohetero_final %>%
+
+  mutate(model_heteroCVR = map(data, ~ metafor::rma.uni(yi = .x$var.CVR, sei = sqrt(1 / 2*(.x$N.CVR - 1)),  
+				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 10000, stepadj=0.5), verbose=F)),
+	   model_heteroVR = map(data, ~ metafor::rma.uni(yi = .x$var.VR, sei = sqrt(1 / 2*(.x$N.VR - 1)),  
+				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 10000, stepadj=0.5), verbose=F)),
+	   model_heteroRR = map(data, ~ metafor::rma.uni(yi = .x$var.RR, sei = sqrt(1 / 2*(.x$N.RR - 1)),  
+				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 10000, stepadj=0.5), verbose=F)))
+
+heterog1
+
+# **Re-structure data for each grouping term; extract heterogenenity/variance terms; delete un-used variables
+
+Behaviour.
+<- heterog1 %>% filter(., GroupingTerm == "Behaviour")  %>% select(., -data)  %>%  mutate(heteroCVR=.[[2]][[1]]$b, heteroCVR_lower=.[[2]][[1]]$ci.lb, heteroCVR_upper=.[[2]][[1]]$ci.ub, heteroCVR_se=.[[2]][[1]]$se,
+	              heteroVR=.[[3]][[1]]$b, heteroVR_lower=.[[3]][[1]]$ci.lb, heteroVR_upper=.[[3]][[1]]$ci.ub, heteroVR_se=.[[3]][[1]]$se,
+		        heteroRR=.[[4]][[1]]$b, heteroRR_lower=.[[4]][[1]]$ci.lb, heteroRR_upper=.[[4]][[1]]$ci.ub, heteroRR_se=.[[4]][[1]]$se) %>%
+			  select(., GroupingTerm, heteroCVR:heteroRR_se)
+
+Immunology.
+<- heterog1 %>% filter(., GroupingTerm == "Immunology") %>% select(., -data)  %>%  mutate(heteroCVR=.[[2]][[1]]$b, heteroCVR_lower=.[[2]][[1]]$ci.lb, heteroCVR_upper=.[[2]][[1]]$ci.ub, heteroCVR_se=.[[2]][[1]]$se,
+	              heteroVR=.[[3]][[1]]$b, heteroVR_lower=.[[3]][[1]]$ci.lb, heteroVR_upper=.[[3]][[1]]$ci.ub, heteroVR_se=.[[3]][[1]]$se,
+		        heteroRR=.[[4]][[1]]$b, heteroRR_lower=.[[4]][[1]]$ci.lb, heteroRR_upper=.[[4]][[1]]$ci.ub, heteroRR_se=.[[4]][[1]]$se) %>%
+			  select(., GroupingTerm, heteroCVR:heteroRR_se)
+
+Hematology.
+<- heterog1 %>% filter(., GroupingTerm == "Hematology") %>% select(., -data)  %>%  mutate(heteroCVR=.[[2]][[1]]$b, heteroCVR_lower=.[[2]][[1]]$ci.lb, heteroCVR_upper=.[[2]][[1]]$ci.ub, heteroCVR_se=.[[2]][[1]]$se,
+	              heteroVR=.[[3]][[1]]$b, heteroVR_lower=.[[3]][[1]]$ci.lb, heteroVR_upper=.[[3]][[1]]$ci.ub, heteroVR_se=.[[3]][[1]]$se,
+		        heteroRR=.[[4]][[1]]$b, heteroRR_lower=.[[4]][[1]]$ci.lb, heteroRR_upper=.[[4]][[1]]$ci.ub, heteroRR_se=.[[4]][[1]]$se) %>%
+			  select(., GroupingTerm, heteroCVR:heteroRR_se)
+
+Hearing.
+<- heterog1 %>% filter(., GroupingTerm == "Hearing")  %>% select(., -data)  %>%  mutate(heteroCVR=.[[2]][[1]]$b, heteroCVR_lower=.[[2]][[1]]$ci.lb, heteroCVR_upper=.[[2]][[1]]$ci.ub, heteroCVR_se=.[[2]][[1]]$se,
+	              heteroVR=.[[3]][[1]]$b, heteroVR_lower=.[[3]][[1]]$ci.lb, heteroVR_upper=.[[3]][[1]]$ci.ub, heteroVR_se=.[[3]][[1]]$se,
+		        heteroRR=.[[4]][[1]]$b, heteroRR_lower=.[[4]][[1]]$ci.lb, heteroRR_upper=.[[4]][[1]]$ci.ub, heteroRR_se=.[[4]][[1]]$se) %>%
+			  select(., GroupingTerm, heteroCVR:heteroRR_se)
+
+Physiology.
+<- heterog1 %>% filter(., GroupingTerm == "Physiology")  %>% select(., -data)  %>%  mutate(heteroCVR=.[[2]][[1]]$b, heteroCVR_lower=.[[2]][[1]]$ci.lb, heteroCVR_upper=.[[2]][[1]]$ci.ub, heteroCVR_se=.[[2]][[1]]$se,
+	              heteroVR=.[[3]][[1]]$b, heteroVR_lower=.[[3]][[1]]$ci.lb, heteroVR_upper=.[[3]][[1]]$ci.ub, heteroVR_se=.[[3]][[1]]$se,
+		        heteroRR=.[[4]][[1]]$b, heteroRR_lower=.[[4]][[1]]$ci.lb, heteroRR_upper=.[[4]][[1]]$ci.ub, heteroRR_se=.[[4]][[1]]$se) %>%
+			  select(., GroupingTerm, heteroCVR:heteroRR_se)
+
+Metabolism.
+<- heterog1 %>% filter(., GroupingTerm == "Metabolism")  %>% select(., -data)  %>%  mutate(heteroCVR=.[[2]][[1]]$b, heteroCVR_lower=.[[2]][[1]]$ci.lb, heteroCVR_upper=.[[2]][[1]]$ci.ub, heteroCVR_se=.[[2]][[1]]$se,
+	              heteroVR=.[[3]][[1]]$b, heteroVR_lower=.[[3]][[1]]$ci.lb, heteroVR_upper=.[[3]][[1]]$ci.ub, heteroVR_se=.[[3]][[1]]$se,
+		        heteroRR=.[[4]][[1]]$b, heteroRR_lower=.[[4]][[1]]$ci.lb, heteroRR_upper=.[[4]][[1]]$ci.ub, heteroRR_se=.[[4]][[1]]$se) %>%
+			  select(., GroupingTerm, heteroCVR:heteroRR_se)
+
+Morphology.
+<- heterog1 %>% filter(., GroupingTerm == "Morphology") %>% select(., -data)  %>%  mutate(heteroCVR=.[[2]][[1]]$b, heteroCVR_lower=.[[2]][[1]]$ci.lb, heteroCVR_upper=.[[2]][[1]]$ci.ub, heteroCVR_se=.[[2]][[1]]$se,
+	              heteroVR=.[[3]][[1]]$b, heteroVR_lower=.[[3]][[1]]$ci.lb, heteroVR_upper=.[[3]][[1]]$ci.ub, heteroVR_se=.[[3]][[1]]$se,
+		        heteroRR=.[[4]][[1]]$b, heteroRR_lower=.[[4]][[1]]$ci.lb, heteroRR_upper=.[[4]][[1]]$ci.ub, heteroRR_se=.[[4]][[1]]$se) %>%
+			  select(., GroupingTerm, heteroCVR:heteroRR_se)
+
+Heart.
+<- heterog1 %>% filter(., GroupingTerm == "Heart")  %>% select(., -data)  %>%  mutate(heteroCVR=.[[2]][[1]]$b, heteroCVR_lower=.[[2]][[1]]$ci.lb, heteroCVR_upper=.[[2]][[1]]$ci.ub, heteroCVR_se=.[[2]][[1]]$se,
+	              heteroVR=.[[3]][[1]]$b, heteroVR_lower=.[[3]][[1]]$ci.lb, heteroVR_upper=.[[3]][[1]]$ci.ub, heteroVR_se=.[[3]][[1]]$se,
+		        heteroRR=.[[4]][[1]]$b, heteroRR_lower=.[[4]][[1]]$ci.lb, heteroRR_upper=.[[4]][[1]]$ci.ub, heteroRR_se=.[[4]][[1]]$se) %>%
+			  select(., GroupingTerm, heteroCVR:heteroRR_se)
+
+Eye.
+<- heterog1 %>% filter(., GroupingTerm == "Eye")  %>% select(., -data)  %>%  mutate(heteroCVR=.[[2]][[1]]$b, heteroCVR_lower=.[[2]][[1]]$ci.lb, heteroCVR_upper=.[[2]][[1]]$ci.ub, heteroCVR_se=.[[2]][[1]]$se,
+	              heteroVR=.[[3]][[1]]$b, heteroVR_lower=.[[3]][[1]]$ci.lb, heteroVR_upper=.[[3]][[1]]$ci.ub, heteroVR_se=.[[3]][[1]]$se,
+		        heteroRR=.[[4]][[1]]$b, heteroRR_lower=.[[4]][[1]]$ci.lb, heteroRR_upper=.[[4]][[1]]$ci.ub, heteroRR_se=.[[4]][[1]]$se) %>%
+			  select(., GroupingTerm, heteroCVR:heteroRR_se)
+
+heterog2 <- bind_rows(Behaviour., Morphology., Metabolism., Physiology., Immunology., Hematology., Heart., Hearing., Eye.)
+#str(heterog2)
+
+```
+
+####################################################################################################################################
+# *PLOTS
+
+# **Restructure data for plotting 
+```{r}
+heterog3 <- gather(heterog2, parameter, value, c(heteroCVR, heteroVR, heteroRR), factor_key= TRUE)
+
+heteroCVR.ci <- heterog3 %>% filter(parameter == "heteroCVR") %>% mutate(ci.low = heteroCVR_lower, ci.high = heteroCVR_upper)
+heteroVR.ci <- heterog3 %>% filter(parameter == "heteroVR") %>% mutate(ci.low = heteroVR_lower, ci.high = heteroVR_upper)
+heteroRR.ci <- heterog3 %>% filter(parameter == "heteroRR") %>% mutate(ci.low = heteroRR_lower, ci.high = heteroRR_upper)
+
+heterog4 <- bind_rows(heteroCVR.ci, heteroVR.ci, heteroRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
+
+# **Re-order grouping terms
+
+heterog4$GroupingTerm <- factor(heterog4$GroupingTerm, levels =c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye") )
+heterog4$GroupingTerm <- factor(heterog4$GroupingTerm, rev(levels(heterog4$GroupingTerm)))
+heterog4$label <- "All traits"
+#write.csv(heterog4, "heterog4.csv")
+
+```
+
+# *Plot FIGURE 4 (Second-order meta analysis on heterogeneity)
+
+# **Plot Fig4 all traits
+```{r}
+
+Metameta_Fig4_alltraits <- heterog4 %>%
 
@@
 			   height = 0.1, show.legend = FALSE) +
-  geom_point(aes(shape = parameter), fill = 'black',
-             color = 'black', size = 2.2, 
+  geom_point(aes(shape = parameter,
+             fill = parameter, color = parameter), size = 2.2, 
              show.legend = FALSE) +
-  scale_x_continuous(limits=c(-0.24, 0.25), 
-                     breaks = c(-0.2, -0.1, 0, 0.1, 0.2), 
+  scale_x_continuous(limits=c(-7.0, 1), 
+                     #breaks = c(-2.0, -1.5, -1.0, -0.5, 0, 0.5, 1.0, 1.5, 2.0), 
                      name='Effect size') +
-  geom_vline(xintercept=0, 
-             color='black', 
-             linetype='dashed')+
   facet_grid(cols = vars(parameter), rows = vars(label),
@@
 
-#Metameta_Fig3_alltraits
-
-```
-
-########
-
-### Prepare data for traits with CI not overlapping 0
-
-create column with 1= different from zero, 0= zero included in CI
-Male-biased (significant) traits
-```{r}
-meta.male.plot3.sig <- metacombo %>% 
-    	mutate(sigCVR = ifelse(lnCVR_lower > 0, 1, 0),
-	sigVR = ifelse(lnVR_lower > 0, 1, 0),
-	sigRR = ifelse(lnRR_lower > 0, 1, 0))
-
-#Significant subset for lnCVR
-metacombo_male.plot3.CVR <- meta.male.plot3.sig %>%
+Metameta_Fig4_alltraits
+
+```
+
+######## Not sure whether the following makes sense for Fig 4 heterogeneity!!! ###########################
+
+# *Prepare data for traits with CI not overlapping 0
+```{r}
+#create column with 1= different from zero, 0= zero included in CI
+
+meta.plot4.sig <- metacombohetero %>% 
+    	mutate(sigCVR = ifelse(heteroCVR_lower * heteroCVR_upper > 0, 1, 0),
+	sigVR = ifelse(heteroVR_lower * heteroVR_upper > 0, 1, 0),
+	sigRR = ifelse(heteroRR_lower * heteroRR_upper > 0, 1, 0))
+
+#Significant subset for heteroCVR
+metacombo_plot4.CVR <- meta.plot4.sig %>%
  filter(sigCVR == 1) %>%
@@
 
-metacombo_male.plot3.CVR.all <- meta.male.plot3.sig %>%
- filter(sigCVR == 1) %>%
- nest()
-
-#Significant subset for lnVR
-metacombo_male.plot3.VR <- meta.male.plot3.sig %>%
+#Significant subset for heteroVR
+metacombo_plot4.VR <- meta.plot4.sig %>%
  filter(sigVR == 1) %>%
@@
 
-metacombo_male.plot3.VR.all <- meta.male.plot3.sig %>%
- filter(sigVR == 1) %>%
- nest()
-
-#Significant subset for lnRR
-metacombo_male.plot3.RR <- meta.male.plot3.sig %>%
+#Significant subset for heteroRR
+metacombo_plot4.RR <- meta.plot4.sig %>%
  filter(sigRR == 1) %>%
@@
 
-metacombo_male.plot3.RR.all <- meta.male.plot3.sig %>%
- filter(sigRR == 1) %>%
- nest()
-
 # **Final fixed effects meta-analyses within grouping terms, with SE of the estimate
 
-plot3.male.meta.CVR <- metacombo_male.plot3.CVR %>% 
-  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower)/ (2*1.96),  
+plot4.meta.CVR <- metacombo_plot4.CVR %>% 
+  mutate(model_heteroCVR = map(data, ~ metafor::rma.uni(yi = .x$heteroCVR, sei = (.x$heteroCVR_upper - .x$heteroCVR_lower)/ 2*1.96,  
 				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )
 
-plot3.male.meta.VR <- metacombo_male.plot3.VR %>% 
-  mutate(model_lnVR = map(data, ~ metafor::rma.uni(yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower)/ (2*1.96),  
+plot4.meta.VR <- metacombo_plot4.VR %>% 
+  mutate(model_heteroVR = map(data, ~ metafor::rma.uni(yi = .x$heteroVR, sei = (.x$heteroVR_upper - .x$heteroVR_lower)/ 2*1.96,  
 				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )
 
-plot3.male.meta.RR <- metacombo_male.plot3.RR %>% 
-  mutate(model_lnRR = map(data, ~ metafor::rma.uni(yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower)/ (2*1.96),  
+plot4.meta.RR <- metacombo_plot4.RR %>% 
+  mutate(model_heteroRR = map(data, ~ metafor::rma.uni(yi = .x$heteroRR, sei = (.x$heteroRR_upper - .x$heteroRR_lower)/ 2*1.96,  
 				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )
 
-# Across all grouping terms #
-
-plot3.male.meta.CVR.all <- metacombo_male.plot3.CVR.all %>% 
-  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower)/ (2*1.96),  
-				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )
-
-plot3.male.meta.CVR.all <- plot3.male.meta.CVR.all %>% mutate(GroupingTerm = "All")
-
-plot3.male.meta.VR.all <- metacombo_male.plot3.VR.all %>% 
-  mutate(model_lnVR = map(data, ~ metafor::rma.uni(yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower)/ (2*1.96),  
-				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )
-
-plot3.male.meta.VR.all <- plot3.male.meta.VR.all %>% mutate(GroupingTerm = "All")
-
-plot3.male.meta.RR.all <- metacombo_male.plot3.RR.all %>% 
-  mutate(model_lnRR = map(data, ~ metafor::rma.uni(yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower)/ (2*1.96),  
-				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )
-
-plot3.male.meta.RR.all <- plot3.male.meta.RR.all %>% mutate(GroupingTerm = "All")
-
-# Combine with separate grouping term results
-
-plot3.male.meta.CVR <- bind_rows(plot3.male.meta.CVR, plot3.male.meta.CVR.all)
-plot3.male.meta.VR <- bind_rows(plot3.male.meta.VR, plot3.male.meta.VR.all)
-plot3.male.meta.RR <- bind_rows(plot3.male.meta.RR, plot3.male.meta.RR.all)
-
 # **Re-structure data for each grouping term; delete un-used variables
 
-plot3.male.meta.CVR.b <- as.data.frame(plot3.male.meta.CVR %>% group_by(GroupingTerm) %>%  
-		mutate(lnCVR = map_dbl(model_lnCVR, pluck(2)), lnCVR_lower = map_dbl(model_lnCVR, pluck(6)), 
-		lnCVR_upper =map_dbl(model_lnCVR, pluck(7)), lnCVR_se =map_dbl(model_lnCVR, pluck(3))) )[, c(1,4:7)] 
-add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.male.meta.CVR.b))
-
-plot3.male.meta.CVR.b <- bind_rows(plot3.male.meta.CVR.b, add.row.hearing) 
-plot3.male.meta.CVR.b <- plot3.male.meta.CVR.b[order(plot3.male.meta.CVR.b$GroupingTerm),]
-
-plot3.male.meta.VR.b <- as.data.frame(plot3.male.meta.VR %>% group_by(GroupingTerm) %>%  
-	mutate(lnVR = map_dbl(model_lnVR, pluck(2)), lnVR_lower = map_dbl(model_lnVR, pluck(6)), 
-	lnVR_upper =map_dbl(model_lnVR, pluck(7)), lnVR_se =map_dbl(model_lnVR, pluck(3))) )[, c(1,4:7)] 
-plot3.male.meta.VR.b <- plot3.male.meta.VR.b[order(plot3.male.meta.VR.b$GroupingTerm),]
-
-plot3.male.meta.RR.b <- as.data.frame(plot3.male.meta.RR %>% group_by(GroupingTerm) %>%  
+plot4.meta.CVR.b <- as.data.frame(plot4.meta.CVR %>% group_by(GroupingTerm) %>%  
+		mutate(heteroCVR = map_dbl(model_heteroCVR, pluck(2)), heteroCVR_lower = map_dbl(model_heteroCVR, pluck(6)), 
+		heteroCVR_upper =map_dbl(model_heteroCVR, pluck(7)), heteroCVR_se =map_dbl(model_heteroCVR, pluck(3))) )[, c(1,4:7)] 
+add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot4.meta.CVR.b))
+plot4.meta.CVR.b <- bind_rows(plot4.meta.CVR.b, add.row.hearing) 
+plot4.meta.CVR.b <- plot4.meta.CVR.b[order(plot4.meta.CVR.b$GroupingTerm),]
+
+plot4.meta.VR.b <- as.data.frame(plot4.meta.VR %>% group_by(GroupingTerm) %>%  
+	mutate(heteroVR = map_dbl(model_heteroVR, pluck(2)), heteroVR_lower = map_dbl(model_heteroVR, pluck(6)), 
+	heteroVR_upper =map_dbl(model_heteroVR, pluck(7)), heteroVR_se =map_dbl(model_heteroVR, pluck(3))) )[, c(1,4:7)] 
+plot4.meta.VR.b <- plot4.meta.VR.b[order(plot4.meta.VR.b$GroupingTerm),]
+
+plot3.meta.RR.b <- as.data.frame(plot3.meta.RR %>% group_by(GroupingTerm) %>%  
 	mutate(lnRR = map_dbl(model_lnRR, pluck(2)), lnRR_lower = map_dbl(model_lnRR, pluck(6)), 
 	lnRR_upper =map_dbl(model_lnRR, pluck(7)), lnRR_se =map_dbl(model_lnRR, pluck(3))) )[, c(1,4:7)] 
-plot3.male.meta.RR.b <- plot3.male.meta.RR.b[order(plot3.male.meta.RR.b$GroupingTerm),]
-
-overall.male.plot3 <- inner_join(plot3.male.meta.CVR.b, plot3.male.meta.VR.b) 
-overall.male.plot3 <- inner_join(overall.male.plot3, plot3.male.meta.RR.b)
-
-overall.male.plot3$GroupingTerm <- factor(overall.male.plot3$GroupingTerm, levels =c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye", "All") )
-overall.male.plot3$GroupingTerm <- factor(overall.male.plot3$GroupingTerm, rev(levels(overall.male.plot3$GroupingTerm)))
-
-#add missing GroupingTerms for plot
-overall.male.plot3 <- add_row(overall.male.plot3, GroupingTerm = "Behaviour")
-overall.male.plot3 <- add_row(overall.male.plot3, GroupingTerm = "Immunology")
-overall.male.plot3 <- add_row(overall.male.plot3, GroupingTerm = "Eye")
-
-overall.male.plot3$GroupingTerm <- factor(overall.male.plot3$GroupingTerm, levels =c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye", "All") )
-overall.male.plot3$GroupingTerm <- factor(overall.male.plot3$GroupingTerm, rev(levels(overall.male.plot3$GroupingTerm)))
-
-```
-
-Restructure MALE data for plotting 
-```{r}
-overall3.male.sig <- gather(overall.male.plot3, parameter, value, c(lnCVR, lnVR, lnRR), factor_key= TRUE)
-
-lnCVR.ci <- overall3.male.sig  %>% filter(parameter == "lnCVR") %>% mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
-lnVR.ci <- overall3.male.sig  %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
-lnRR.ci <- overall3.male.sig  %>% filter(parameter == "lnRR") %>% mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
-
-overall4.male.sig <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
-
-overall4.male.sig$label <- "CI not overlapping zero"
-
-```
-
-Plot Fig3 all significant results (CI not overlapping zero) for males
+plot3.meta.RR.b <- plot3.meta.RR.b[order(plot3.meta.RR.b$GroupingTerm),]
+
+overall.plot4 <- inner_join(plot4.meta.CVR.b, plot4.meta.VR.b) 
+overall.plot4 <- inner_join(overall.plot4, plot4.meta.RR.b)
+
+overall.plot4$GroupingTerm <- factor(overall.plot4$GroupingTerm, levels =c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye") )
+overall.plot4$GroupingTerm <- factor(overall.plot4$GroupingTerm, rev(levels(overall.plot4$GroupingTerm)))
+
+```
+
+# **Restructure data for plotting 
+```{r}
+overall4.sig <- gather(overall.plot4, parameter, value, c(heteroCVR, heteroVR, heteroRR), factor_key= TRUE)
+
+heteroCVR.ci <- overall4.sig  %>% filter(parameter == "heteroCVR") %>% mutate(ci.low = heteroCVR_lower, ci.high = heteroCVR_upper)
+heteroVR.ci <- overall4.sig  %>% filter(parameter == "heteroVR") %>% mutate(ci.low = heteroVR_lower, ci.high = heteroVR_upper)
+heteroRR.ci <- overall4.sig  %>% filter(parameter == "heteroRR") %>% mutate(ci.low = heteroRR_lower, ci.high = heteroRR_upper)
+
+overall4.sig <- bind_rows(heteroCVR.ci, heteroVR.ci, heteroRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
+
+overall4.sig$label <- "CI not overlapping zero"
+
+```
+
+# **Plot Fig4 all significant results (CI not overlapping zero)
 ```{r}
@@
 
-Metameta_Fig3_male.sig <- overall4.male.sig %>%
+Metameta_Fig4_sig <- overall4.sig %>%
   ggplot(aes(y= GroupingTerm, x= value)) +
@@
 			   height = 0.1, show.legend = FALSE) +
-  geom_point(aes(shape = parameter),
-             fill = 'mediumaquamarine', color = 'mediumaquamarine', size = 2.2, 
+  geom_point(aes(shape = parameter,
+             fill = parameter, color = parameter), size = 2.2, 
              show.legend = FALSE) +
-  scale_x_continuous(limits=c(0, 0.4), 
-                     breaks = c(0, 0.3), 
+  scale_x_continuous(limits=c(-0.52, 0.4), 
+                     breaks = c(-0.4, -0.2, 0, 0.2, 0.4), 
                      name='Effect size') +
@@
   theme(strip.text.y = element_text(angle = 270, size = 10, margin = margin(t=15, r=15, b=15, l=15)), 
-	  strip.text.x = element_text(size = 12),
+	  strip.text.x = element_blank(),
         strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
@@
 
-#Metameta_Fig3_male.sig
-
-```
+Metameta_Fig4_sig
 
 #######################
-### Female Figure
-Female Fig3 sig
-
-Prepare data for traits with CI not overlapping 0
-create column with 1= different from zero, 0= zero included in CI
-```{r}
-
-# female-biased traits
-
-meta.female.plot3.sig <- metacombo %>%
-              mutate(sigCVR = ifelse(lnCVR_upper < 0, 1, 0),
-              sigVR = ifelse(lnVR_upper < 0, 1, 0),
-              sigRR = ifelse(lnRR_upper < 0, 1, 0))
+
+# *Fig3 >10%
+
+###########
+
+########
+
+# *Prepare data for traits with m/f difference > 10%
+```{r}
+#create column with 1= larger, 0= diff not larger than 10%
+
+meta.plot3.perc <- metacombo %>% 
+    	mutate(percCVR = ifelse(lnCVR < log (9/10) | lnCVR > log (11/10), 1, 0),
+	percVR = ifelse(lnVR < log (9/10) | lnVR > log (11/10), 1, 0),
+	percRR = ifelse(lnRR < log (9/10) | lnRR > log (11/10), 1, 0))
 
 #Significant subset for lnCVR
-
-metacombo_female.plot3.CVR <- meta.female.plot3.sig %>%
-filter(sigCVR == 1) %>%
+metacombo_plot3.CVR.perc <- meta.plot3.perc %>%
+ #filter(percCVR == 1) %>%
  group_by(GroupingTerm) %>%
@@
 
-metacombo_female.plot3.CVR.all <- meta.female.plot3.sig %>%
- filter(sigCVR == 1) %>%
- nest()
-
 #Significant subset for lnVR
-
-metacombo_female.plot3.VR <- meta.female.plot3.sig %>%
-filter(sigVR == 1) %>%
-group_by(GroupingTerm) %>%
-nest()
-
-metacombo_female.plot3.VR.all <- meta.female.plot3.sig %>%
- filter(sigVR == 1) %>%
- nest()
-
-#Significant subset for lnRR
-
-metacombo_female.plot3.RR <- meta.female.plot3.sig %>%
-filter(sigRR == 1) %>%
-group_by(GroupingTerm) %>%
-nest()
-
-metacombo_female.plot3.RR.all <- meta.female.plot3.sig %>%
- filter(sigRR == 1) %>%
- nest()
-
-# **Final fixed effects meta-analyses within grouping terms, with SE of the estimate
-
-plot3.female.meta.CVR <- metacombo_female.plot3.CVR %>%
-  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower)/ (2*1.96), 
-                                 control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )
-
-plot3.female.meta.VR <- metacombo_female.plot3.VR %>%
-  mutate(model_lnVR = map(data, ~ metafor::rma.uni(yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower)/ (2*1.96), 
-    					   control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )
-
-plot3.female.meta.RR <- metacombo_female.plot3.RR %>%
-  mutate(model_lnRR = map(data, ~ metafor::rma.uni(yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower)/ (2*1.96), 
-                                 control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )
-
-# Across all grouping terms #
-
-plot3.female.meta.CVR.all <- metacombo_female.plot3.CVR.all %>% 
-  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower)/ (2*1.96),  
-				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )
-
-plot3.female.meta.CVR.all <- plot3.female.meta.CVR.all %>% mutate(GroupingTerm = "All")
-
-plot3.female.meta.VR.all <- metacombo_female.plot3.VR.all %>% 
-  mutate(model_lnVR = map(data, ~ metafor::rma.uni(yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower)/ (2*1.96),  
-				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )
-
-plot3.female.meta.VR.all <- plot3.female.meta.VR.all %>% mutate(GroupingTerm = "All")
-
-plot3.female.meta.RR.all <- metacombo_female.plot3.RR.all %>% 
-  mutate(model_lnRR = map(data, ~ metafor::rma.uni(yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower)/ (2*1.96),  
-				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )
-
-plot3.female.meta.RR.all <- plot3.female.meta.RR.all %>% mutate(GroupingTerm = "All")
-
-# Combine with separate grouping term results
-
-plot3.female.meta.CVR <- bind_rows(plot3.female.meta.CVR, plot3.female.meta.CVR.all)
-plot3.female.meta.VR <- bind_rows(plot3.female.meta.VR, plot3.female.meta.VR.all)
-plot3.female.meta.RR <- bind_rows(plot3.female.meta.RR, plot3.female.meta.RR.all)
-
-# **Re-structure data for each grouping term; delete un-used variables
-
-plot3.female.meta.CVR.b <- as.data.frame(plot3.female.meta.CVR %>% group_by(GroupingTerm) %>% 
-                             mutate(lnCVR = map_dbl(model_lnCVR, pluck(2)), lnCVR_lower = map_dbl(model_lnCVR, pluck(6)),
-                             lnCVR_upper =map_dbl(model_lnCVR, pluck(7)), lnCVR_se =map_dbl(model_lnCVR, pluck(3))) )[, c(1,4:7)]
-
-add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.female.meta.CVR.b))
-
-plot3.female.meta.CVR.b <- bind_rows(plot3.female.meta.CVR.b, add.row.hearing)
-plot3.female.meta.CVR.b <- plot3.female.meta.CVR.b[order(plot3.female.meta.CVR.b$GroupingTerm),]
-
-plot3.female.meta.VR.b <- as.data.frame(plot3.female.meta.VR %>% group_by(GroupingTerm) %>% 
-              mutate(lnVR = map_dbl(model_lnVR, pluck(2)), lnVR_lower = map_dbl(model_lnVR, pluck(6)),
-              lnVR_upper =map_dbl(model_lnVR, pluck(7)), lnVR_se =map_dbl(model_lnVR, pluck(3))) )[, c(1,4:7)]
-
-plot3.female.meta.VR.b <- plot3.female.meta.VR.b[order(plot3.female.meta.VR.b$GroupingTerm),]
-
-plot3.female.meta.RR.b <- as.data.frame(plot3.female.meta.RR %>% group_by(GroupingTerm) %>% 
-              mutate(lnRR = map_dbl(model_lnRR, pluck(2)), lnRR_lower = map_dbl(model_lnRR, pluck(6)),
-              lnRR_upper =map_dbl(model_lnRR, pluck(7)), lnRR_se =map_dbl(model_lnRR, pluck(3))) )[, c(1,4:7)]
-
-plot3.female.meta.RR.b <- plot3.female.meta.RR.b[order(plot3.female.meta.RR.b$GroupingTerm),]
-
-overall.female.plot3 <- full_join(plot3.female.meta.CVR.b, plot3.female.meta.VR.b)
-overall.female.plot3 <- full_join(overall.female.plot3, plot3.female.meta.RR.b)
-
-overall.female.plot3$GroupingTerm <- factor(overall.female.plot3$GroupingTerm, levels =c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye", "All") )
-overall.female.plot3$GroupingTerm <- factor(overall.female.plot3$GroupingTerm, rev(levels(overall.female.plot3$GroupingTerm)))
-
-#add missing GroupingTerms for plot POYTENTIALLY DELETE
-#overall.female.plot3 <- add_row(overall.female.plot3, GroupingTerm = "Morphology")
-#overall.female.plot3 <- add_row(overall.female.plot3, GroupingTerm = "Metabolism")
-#overall.female.plot3 <- add_row(overall.female.plot3, GroupingTerm = "Hematology")
-#overall.female.plot3 <- add_row(overall.female.plot3, GroupingTerm = "Hearing")
-#overall.female.plot3 <- add_row(overall.female.plot3, GroupingTerm = "Eye")
-
-#overall.female.plot3$GroupingTerm <- factor(overall.female.plot3$GroupingTerm, levels =c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye", "All") )
-#overall.female.plot3$GroupingTerm <- factor(overall.female.plot3$GroupingTerm, rev(levels(overall.female.plot3$GroupingTerm)))
-
-```
-
-Restructure data for plotting
-
-```{r}
-overall3.female.sig <- gather(overall.female.plot3, parameter, value, c(lnCVR, lnVR, lnRR), factor_key= TRUE)
-
-lnCVR.ci <- overall3.female.sig  %>% filter(parameter == "lnCVR") %>% mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
-lnVR.ci <- overall3.female.sig  %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
-lnRR.ci <- overall3.female.sig  %>% filter(parameter == "lnRR") %>% mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
-
-overall4.female.sig <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
-
-overall4.female.sig$label <- "CI not overlapping zero"
-
-```
-
-### Plot Fig3 all significant results (CI not overlapping zero, female )
-```{r}
-
-Metameta_Fig3_female.sig <- overall4.female.sig %>%
-  ggplot(aes(y= GroupingTerm, x= value)) +
-  geom_errorbarh(aes(xmin = ci.low,
-                     xmax = ci.high),
-                     height = 0.1, show.legend = FALSE) +
-  geom_point(aes(shape = parameter),
-             fill = 'salmon1', color = 'salmon1', size = 2.2,
-             show.legend = FALSE) +
-  scale_x_continuous(limits=c(-0.4, 0),
-                     breaks = c(-0.3 ,0),
-                     name='Effect size') +
-  geom_vline(xintercept=0,
-             color='black',
-             linetype='dashed')+
-  facet_grid(cols = vars(parameter), #rows = vars(label),
-             #labeller = label_wrap_gen(width = 23),
-             scales= 'free',
-             space='free')+
-  theme_bw()+
-  theme(strip.text.y = element_text(angle = 270, size = 10, margin = margin(t=15, r=15, b=15, l=15)),
-                strip.text.x = element_text(size = 12),
-        strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
-        text = element_text(size = 14),
-        panel.spacing = unit(0.5, "lines"),
-        panel.border= element_blank(),
-        axis.line=element_line(),
-        panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
-        panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
-        panel.grid.minor.y = element_blank(),
-        panel.grid.minor.x = element_blank(),
-        legend.title = element_blank(),
-        axis.title.x = element_blank(),
-                axis.title.y = element_blank())
-
-#Metameta_Fig3_female.sig
-```
-#######################
-
-### Fig3 >10%
-
-Prepare data for traits with m/f difference > 10%
-
-create column with 1= larger, 0= diff not larger than 10%
-
-### Male Fig 3 > 10% (male biased traits)
-```{r}
-meta.male.plot3.perc <- metacombo %>% 
-    	mutate(percCVR = ifelse(lnCVR > log (11/10), 1, 0),			
-	percVR = ifelse(lnVR > log (11/10), 1, 0),
-	percRR = ifelse(lnRR > log (11/10), 1, 0))
-
-#Significant subset for lnCVR
-metacombo_male.plot3.CVR.perc <- meta.male.plot3.perc %>%
- filter(percCVR == 1) %>%
- group_by(GroupingTerm) %>%
- nest()
-
-metacombo_male.plot3.CVR.perc.all <- meta.male.plot3.perc %>%
- filter(percCVR == 1) %>%
- nest()
-
-#Significant subset for lnVR
-metacombo_male.plot3.VR.perc <- meta.male.plot3.perc %>%
+metacombo_plot3.VR.perc <- meta.plot3.perc %>%
  filter(percVR == 1) %>%
@@
 
-metacombo_male.plot3.VR.perc.all <- meta.male.plot3.perc %>%
- filter(percVR == 1) %>%
- nest()
-
 #Significant subset for lnRR
-metacombo_male.plot3.RR.perc <- meta.male.plot3.perc %>%
+metacombo_plot3.RR.perc <- meta.plot3.perc %>%
  filter(percRR == 1) %>%
@@
 
-metacombo_male.plot3.RR.perc.all <- meta.male.plot3.perc %>%
- filter(percRR == 1) %>%
- nest()
-
-# **Final fixed effects meta-analyses within grouping terms and across grouping terms, with SE of the estimate
-
-plot3.male.meta.CVR.perc <- metacombo_male.plot3.CVR.perc %>% 
-  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower)/ (2*1.96),  
+# **Final fixed effects meta-analyses within grouping terms, with SE of the estimate
+
+plot3.meta.CVR.perc <- metacombo_plot3.CVR.perc %>% 
+  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower)/ 2*1.96,  
 				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )
 
-plot3.male.meta.VR.perc <- metacombo_male.plot3.VR.perc %>% 
-  mutate(model_lnVR = map(data, ~ metafor::rma.uni(yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower)/ (2*1.96),  
+plot3.meta.VR.perc <- metacombo_plot3.VR.perc %>% 
+  mutate(model_lnVR = map(data, ~ metafor::rma.uni(yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower)/ 2*1.96,  
 				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )
 
-plot3.male.meta.RR.perc <- metacombo_male.plot3.RR.perc %>% 
-  mutate(model_lnRR = map(data, ~ metafor::rma.uni(yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower)/ (2*1.96),  
+plot3.meta.RR.perc <- metacombo_plot3.RR.perc %>% 
+  mutate(model_lnRR = map(data, ~ metafor::rma.uni(yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower)/ 2*1.96,  
 				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )
 
-# Across all grouping terms #
-
-plot3.male.meta.CVR.perc.all <- metacombo_male.plot3.CVR.perc.all %>% 
-  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower)/ (2*1.96),  
-				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )
-
-plot3.male.meta.CVR.perc.all <- plot3.male.meta.CVR.perc.all %>% mutate(GroupingTerm = "All")
-
-plot3.male.meta.VR.perc.all <- metacombo_male.plot3.VR.perc.all %>% 
-  mutate(model_lnVR = map(data, ~ metafor::rma.uni(yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower)/ (2*1.96),  
-				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )
-
-plot3.male.meta.VR.perc.all <- plot3.male.meta.VR.perc.all %>% mutate(GroupingTerm = "All")
-
-plot3.male.meta.RR.perc.all <- metacombo_male.plot3.RR.perc.all %>% 
-  mutate(model_lnRR = map(data, ~ metafor::rma.uni(yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower)/ (2*1.96),  
-				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )
-
-plot3.male.meta.RR.perc.all <- plot3.male.meta.RR.perc.all %>% mutate(GroupingTerm = "All")
-
-# Combine with separate grouping term results
-
-plot3.male.meta.CVR.perc <- bind_rows(plot3.male.meta.CVR.perc, plot3.male.meta.CVR.perc.all)
-plot3.male.meta.VR.perc <- bind_rows(plot3.male.meta.VR.perc, plot3.male.meta.VR.perc.all)
-plot3.male.meta.RR.perc <- bind_rows(plot3.male.meta.RR.perc, plot3.male.meta.RR.perc.all)
-
 # **Re-structure data for each grouping term; delete un-used variables: "Hearing missing for all 3 parameters"
 
-plot3.male.meta.CVR.perc.b <- as.data.frame(plot3.male.meta.CVR.perc %>% group_by(GroupingTerm) %>%  
+plot3.meta.CVR.perc.b <- as.data.frame(plot3.meta.CVR.perc %>% group_by(GroupingTerm) %>%  
 		mutate(lnCVR = map_dbl(model_lnCVR, pluck(2)), lnCVR_lower = map_dbl(model_lnCVR, pluck(6)), 
 		lnCVR_upper =map_dbl(model_lnCVR, pluck(7)), lnCVR_se =map_dbl(model_lnCVR, pluck(3))) )[, c(1,4:7)] 
-add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.male.meta.CVR.perc.b))
-plot3.male.meta.CVR.perc.b <- rbind(plot3.male.meta.CVR.perc.b, add.row.hearing) 
-plot3.male.meta.CVR.perc.b <- plot3.male.meta.CVR.perc.b[order(plot3.male.meta.CVR.perc.b$GroupingTerm),]
-
-plot3.male.meta.VR.perc.b <- as.data.frame(plot3.male.meta.VR.perc %>% group_by(GroupingTerm) %>%  
+add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.meta.CVR.perc.b))
+plot3.meta.CVR.perc.b <- rbind(plot3.meta.CVR.perc.b, add.row.hearing) 
+plot3.meta.CVR.perc.b <- plot3.meta.CVR.perc.b[order(plot3.meta.CVR.perc.b$GroupingTerm),]
+
+plot3.meta.VR.perc.b <- as.data.frame(plot3.meta.VR.perc %>% group_by(GroupingTerm) %>%  
 	mutate(lnVR = map_dbl(model_lnVR, pluck(2)), lnVR_lower = map_dbl(model_lnVR, pluck(6)), 
 	lnVR_upper =map_dbl(model_lnVR, pluck(7)), lnVR_se =map_dbl(model_lnVR, pluck(3))) )[, c(1,4:7)] 
-add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.male.meta.VR.perc.b))
-plot3.male.meta.VR.perc.b <- rbind(plot3.male.meta.VR.perc.b, add.row.hearing) 
-plot3.male.meta.VR.perc.b <- plot3.male.meta.VR.perc.b[order(plot3.male.meta.VR.perc.b$GroupingTerm),]
-
-plot3.male.meta.RR.perc.b <- as.data.frame(plot3.male.meta.RR.perc %>% group_by(GroupingTerm) %>%  
+add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.meta.VR.perc.b))
+plot3.meta.VR.perc.b <- rbind(plot3.meta.VR.perc.b, add.row.hearing) 
+plot3.meta.VR.perc.b <- plot3.meta.VR.perc.b[order(plot3.meta.VR.perc.b$GroupingTerm),]
+
+plot3.meta.RR.perc.b <- as.data.frame(plot3.meta.RR.perc %>% group_by(GroupingTerm) %>%  
 	mutate(lnRR = map_dbl(model_lnRR, pluck(2)), lnRR_lower = map_dbl(model_lnRR, pluck(6)), 
 	lnRR_upper =map_dbl(model_lnRR, pluck(7)), lnRR_se =map_dbl(model_lnRR, pluck(3))) )[, c(1,4:7)] 
-add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.male.meta.RR.perc.b))
-plot3.male.meta.RR.perc.b <- rbind(plot3.male.meta.RR.perc.b, add.row.hearing) 
-plot3.male.meta.RR.perc.b <- plot3.male.meta.RR.perc.b[order(plot3.male.meta.RR.perc.b$GroupingTerm),]
-
-overall.male.plot3.perc <- full_join(plot3.male.meta.CVR.perc.b, plot3.male.meta.VR.perc.b) 
-overall.male.plot3.perc <- full_join(overall.male.plot3.perc, plot3.male.meta.RR.perc.b)
-
-overall.male.plot3.perc$GroupingTerm <- factor(overall.male.plot3.perc$GroupingTerm, levels =c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye", "All") )
-overall.male.plot3.perc$GroupingTerm <- factor(overall.male.plot3.perc$GroupingTerm, rev(levels(overall.male.plot3.perc$GroupingTerm)))
-
-```
-
-Restructure data for plotting : Male biased, 10% difference
-```{r}
-overall3.perc <- gather(overall.male.plot3.perc, parameter, value, c(lnCVR, lnVR, lnRR), factor_key= TRUE)
+add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.meta.RR.perc.b))
+plot3.meta.RR.perc.b <- rbind(plot3.meta.RR.perc.b, add.row.hearing) 
+plot3.meta.RR.perc.b <- plot3.meta.RR.perc.b[order(plot3.meta.RR.perc.b$GroupingTerm),]
+
+overall.plot3.perc <- inner_join(plot3.meta.CVR.perc.b, plot3.meta.VR.perc.b) 
+overall.plot3.perc <- inner_join(overall.plot3.perc, plot3.meta.RR.perc.b)
+
+overall.plot3.perc$GroupingTerm <- factor(overall.plot3.perc$GroupingTerm, levels =c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye") )
+overall.plot3.perc$GroupingTerm <- factor(overall.plot3.perc$GroupingTerm, rev(levels(overall.plot3.perc$GroupingTerm)))
+
+```
+
+# **Restructure data for plotting 
+```{r}
+overall3.perc <- gather(overall.plot3.perc, parameter, value, c(lnCVR, lnVR, lnRR), factor_key= TRUE)
 
@@
 
-overall4.male.perc <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
-
-overall4.male.perc$label <- "Sex difference in m/f ratios > 10%"
-
-overall4.male.perc$value <- as.numeric(overall4.male.perc$value)
-overall4.male.perc$ci.low  <- as.numeric(overall4.male.perc$ci.low)
-overall4.male.perc$ci.high <- as.numeric(overall4.male.perc$ci.high)
-
-```
-
-Plot Fig3 all >10% difference (male bias)
-```{r}
-
-Metameta_Fig3_male.perc <- overall4.male.perc %>% filter(., GroupingTerm != "Hearing") %>%
+overall4.perc <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
+
+overall4.perc$label <- "Sex difference in m/f ratios > 10%"
+
+overall4.perc$value <- as.numeric(overall4.perc$value)
+overall4.perc$ci.low  <- as.numeric(overall4.perc$ci.low)
+overall4.perc$ci.high <- as.numeric(overall4.perc$ci.high)
+
+```
+
+# **Plot Fig3 all >10% difference 
+```{r}
+######
+
+Metameta_Fig3_perc <- overall4.perc %>%
   ggplot(aes(y= GroupingTerm, x= value)) +
@@
   geom_point(aes(shape = parameter,
-             fill = parameter), color = 'mediumaquamarine', size = 2.2, 
+             fill = parameter, color = parameter), size = 2.2, 
              show.legend = FALSE) +
-  scale_x_continuous(limits=c(-0.2, 0.62), 
-                     breaks = c(0, 0.3), 
+  scale_x_continuous(limits=c(-0.52, 0.4), 
+                     breaks = c(-0.4, -0.2, 0, 0.2, 0.4), 
                      name='Effect size') +
@@
 
-# Metameta_Fig3_male.perc
-```
-
-##################
-
-Female Fig 3 >10%
-```{r}
-
-meta.plot3.perc <- metacombo %>% 
-    	mutate(percCVR = ifelse(lnCVR < log (9/10), 1, 0),			
-	percVR = ifelse(lnVR < log (9/10), 1, 0),
-	percRR = ifelse(lnRR < log (9/10), 1, 0))
-
-#Significant subset for lnCVR
-metacombo_plot3.CVR.perc <- meta.plot3.perc %>%
- filter(percCVR == 1) %>%
- group_by(GroupingTerm) %>%
- nest()
-
-metacombo_plot3.CVR.perc.all <- meta.plot3.perc %>%
- filter(percCVR == 1) %>%
- nest()
-
-#Significant subset for lnVR
-metacombo_plot3.VR.perc <- meta.plot3.perc %>%
- filter(percVR == 1) %>%
- group_by(GroupingTerm) %>%
- nest()
-
-metacombo_plot3.VR.perc.all <- meta.plot3.perc %>%
- filter(percVR == 1) %>%
- nest()
-
-#Significant subset for lnRR
-metacombo_plot3.RR.perc <- meta.plot3.perc %>%
- filter(percRR == 1) %>%
- group_by(GroupingTerm) %>%
- nest()
-
-metacombo_plot3.RR.perc.all <- meta.plot3.perc %>%
- filter(percRR == 1) %>%
- nest()
-
-# **Final fixed effects meta-analyses within grouping terms, with SE of the estimate
-
-plot3.meta.CVR.perc <- metacombo_plot3.CVR.perc %>% 
-  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower)/ (2*1.96),  
-				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )
-
-plot3.meta.VR.perc <- metacombo_plot3.VR.perc %>% 
-  mutate(model_lnVR = map(data, ~ metafor::rma.uni(yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower)/ (2*1.96),  
-				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )
-
-plot3.meta.RR.perc <- metacombo_plot3.RR.perc %>% 
-  mutate(model_lnRR = map(data, ~ metafor::rma.uni(yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower)/ (2*1.96),  
-				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )
-
-# Across all grouping terms #
-
-plot3.meta.CVR.perc.all <- metacombo_plot3.CVR.perc.all %>% 
-  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower)/ (2*1.96),  
-				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )
-
-plot3.meta.CVR.perc.all <- plot3.meta.CVR.perc.all %>% mutate(GroupingTerm = "All")
-
-plot3.meta.VR.perc.all <- metacombo_plot3.VR.perc.all %>% 
-  mutate(model_lnVR = map(data, ~ metafor::rma.uni(yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower)/ (2*1.96),  
-				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )
-
-plot3.meta.VR.perc.all <- plot3.meta.VR.perc.all %>% mutate(GroupingTerm = "All")
-
-plot3.meta.RR.perc.all <- metacombo_plot3.RR.perc.all %>% 
-  mutate(model_lnRR = map(data, ~ metafor::rma.uni(yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower)/ (2*1.96),  
-				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )
-
-plot3.meta.RR.perc.all <- plot3.meta.RR.perc.all %>% mutate(GroupingTerm = "All")
-
-# Combine with separate grouping term results
-
-plot3.meta.CVR.perc <- bind_rows(plot3.meta.CVR.perc, plot3.meta.CVR.perc.all)
-plot3.meta.VR.perc <- bind_rows(plot3.meta.VR.perc, plot3.meta.VR.perc.all)
-plot3.meta.RR.perc <- bind_rows(plot3.meta.RR.perc, plot3.meta.RR.perc.all)
-
-# **Re-structure data for each grouping term; delete un-used variables: "Hearing missing for all 3 parameters"
-
-plot3.meta.CVR.perc.b <- as.data.frame(plot3.meta.CVR.perc %>% group_by(GroupingTerm) %>%  
-		mutate(lnCVR = map_dbl(model_lnCVR, pluck(2)), lnCVR_lower = map_dbl(model_lnCVR, pluck(6)), 
-		lnCVR_upper =map_dbl(model_lnCVR, pluck(7)), lnCVR_se =map_dbl(model_lnCVR, pluck(3))) )[, c(1,4:7)] 
-add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.meta.CVR.perc.b))
-plot3.meta.CVR.perc.b <- rbind(plot3.meta.CVR.perc.b, add.row.hearing) 
-plot3.meta.CVR.perc.b <- plot3.meta.CVR.perc.b[order(plot3.meta.CVR.perc.b$GroupingTerm),]
-
-plot3.meta.VR.perc.b <- as.data.frame(plot3.meta.VR.perc %>% group_by(GroupingTerm) %>%  
-	mutate(lnVR = map_dbl(model_lnVR, pluck(2)), lnVR_lower = map_dbl(model_lnVR, pluck(6)), 
-	lnVR_upper =map_dbl(model_lnVR, pluck(7)), lnVR_se =map_dbl(model_lnVR, pluck(3))) )[, c(1,4:7)] 
-add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.meta.VR.perc.b))
-plot3.meta.VR.perc.b <- rbind(plot3.meta.VR.perc.b, add.row.hearing) 
-plot3.meta.VR.perc.b <- plot3.meta.VR.perc.b[order(plot3.meta.VR.perc.b$GroupingTerm),]
-
-plot3.meta.RR.perc.b <- as.data.frame(plot3.meta.RR.perc %>% group_by(GroupingTerm) %>%  
-	mutate(lnRR = map_dbl(model_lnRR, pluck(2)), lnRR_lower = map_dbl(model_lnRR, pluck(6)), 
-	lnRR_upper =map_dbl(model_lnRR, pluck(7)), lnRR_se =map_dbl(model_lnRR, pluck(3))) )[, c(1,4:7)] 
-add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.meta.RR.perc.b))
-plot3.meta.RR.perc.b <- rbind(plot3.meta.RR.perc.b, add.row.hearing) 
-plot3.meta.RR.perc.b <- plot3.meta.RR.perc.b[order(plot3.meta.RR.perc.b$GroupingTerm),]
-
-overall.plot3.perc <- full_join(plot3.meta.CVR.perc.b, plot3.meta.VR.perc.b) 
-overall.plot3.perc <- full_join(overall.plot3.perc, plot3.meta.RR.perc.b)
-
-overall.plot3.perc$GroupingTerm <- factor(overall.plot3.perc$GroupingTerm, levels =c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye", "All") )
-overall.plot3.perc$GroupingTerm <- factor(overall.plot3.perc$GroupingTerm, rev(levels(overall.plot3.perc$GroupingTerm)))
-
-```
-
-### Restructure data for plotting
-Female bias, 10 percent difference
-```{r}
-overall3.perc <- gather(overall.plot3.perc, parameter, value, c(lnCVR, lnVR, lnRR), factor_key= TRUE)
-
-lnCVR.ci <- overall3.perc %>% filter(parameter == "lnCVR") %>% mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
-lnVR.ci <- overall3.perc  %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
-lnRR.ci <- overall3.perc  %>% filter(parameter == "lnRR") %>% mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
-
-overall4.perc <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
-
-overall4.perc$label <- "Sex difference in m/f ratios > 10%"
-
-overall4.perc$value <- as.numeric(overall4.perc$value)
-overall4.perc$ci.low  <- as.numeric(overall4.perc$ci.low)
-overall4.perc$ci.high <- as.numeric(overall4.perc$ci.high)
-
-```
-
-Plot Fig3 all >10% difference (female)
-```{r}
-Metameta_Fig3_female.perc <- overall4.perc %>% 
-  ggplot(aes(y= GroupingTerm, x= value)) +
-  geom_errorbarh(aes(xmin = ci.low, 
-                     xmax = ci.high), 
-			   height = 0.1, show.legend = FALSE) +
-  geom_point(aes(shape = parameter),
-             fill = 'salmon1', color = 'salmon1', size = 2.2, 
-             show.legend = FALSE) +
-
-#scale_shape_manual(values =
-
-  scale_x_continuous(limits=c(-0.53, 0.2), 
-                     breaks = c(-0.3, 0), 
-                     name='Effect size') +
-  geom_vline(xintercept=0, 
-             color='black', 
-             linetype='dashed')+
-  facet_grid(cols = vars(parameter), #rows = vars(label),
-             #labeller = label_wrap_gen(width = 23),
-             scales= 'free', 
-             space='free')+
-  theme_bw()+
-  theme(strip.text.y = element_text(angle = 270, size = 10, margin = margin(t=15, r=15, b=15, l=15)), 
-	  strip.text.x = element_blank(),
-        strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
-        text = element_text(size = 14),
-        panel.spacing = unit(0.5, "lines"),
-        panel.border= element_blank(),
-        axis.line=element_line(), 
-        panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
-        panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
-        panel.grid.minor.y = element_blank(),
-        panel.grid.minor.x = element_blank(), 
-        legend.title = element_blank(),
-        axis.title.x = element_text(hjust = 0.5, size = 14),
-	  axis.title.y = element_blank())
-
-#Metameta_Fig3_female.perc
-
-```
-
-# Plot Fig3 all plots combined
-```{r}
+Metameta_Fig3_perc
+```
+#######################
+# *Plot Fig3 all plots together
+```{r}
+
 library(ggpubr)
-Fig3.bottom <- ggarrange(Metameta_Fig3_female.sig, Metameta_Fig3_male.sig, Metameta_Fig3_female.perc, Metameta_Fig3_male.perc, 
-		   ncol = 2, nrow = 2, widths = c(1, 1.20), heights = c(1, 1))
-
-Fig3 <- ggarrange(Metameta_Fig3_alltraits, Fig3.bottom, ncol = 1, nrow = 2, heights = c(1.4, 2.5))
-Fig3
-#                     ggsave("Fig3.pdf", plot = Fig3, width = 9, height = 6) 
-```
-
-## Plot Supplement FIGURE S1 (Second-order meta-analysis on heterogeneity)
-
-### Create matrix to store results for all traits
-```{r}
-results.allhetero.grouping <- as.data.frame(cbind(c(1:n), matrix(rep(0, n*30), ncol = 30))) 
-names(results.allhetero.grouping) <- c("id", "sigma2_strain.CVR", "sigma2_center.CVR", "sigma2_error.CVR", "s.nlevels.strain.CVR", 
-	"s.nlevels.center.CVR", "s.nlevels.error.CVR", "sigma2_strain.VR", "sigma2_center.VR", "sigma2_error.VR", "s.nlevels.strain.VR", 
-	"s.nlevels.center.VR", "s.nlevels.error.VR", "sigma2_strain.RR", "sigma2_center.RR", "sigma2_error.RR", "s.nlevels.strain.RR", 
-	"s.nlevels.center.RR", "s.nlevels.error.RR", "lnCVR", "lnCVR_lower", "lnCVR_upper", "lnCVR_se", "lnVR", "lnVR_lower", "lnVR_upper", 
-	"lnVR_se", "lnRR", "lnRR_lower", "lnRR_upper" ,"lnRR_se")
-
-```
-
-### LOOP
-
-```{r}
-
-for(t in 1:n) {
-
-  tryCatch({
-
-    data_par_age <- data_subset_parameterid_individual_by_age(data, t, age_min = 0, age_center = 100)
-
-    population_stats <- calculate_population_stats(data_par_age)
-
-    results <- create_meta_analysis_effect_sizes(population_stats)
-
-    # lnCVR, logaritm of the ratio of male and female coefficients of variance
-
-    cvr. <- metafor::rma.mv(yi = effect_size_CVR, V = sample_variance_CVR, random = list(~1| strain_name, ~1|production_center,    
-                                ~1|err), control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), data = results)
-    results.allhetero.grouping[t, 2] <- cvr.$sigma2[1]
-    results.allhetero.grouping[t, 3] <- cvr.$sigma2[2]
-    results.allhetero.grouping[t, 4] <- cvr.$sigma2[3]
-    results.allhetero.grouping[t, 5] <- cvr.$s.nlevels[1]
-    results.allhetero.grouping[t, 6] <- cvr.$s.nlevels[2]
-    results.allhetero.grouping[t, 7] <- cvr.$s.nlevels[3]
-     results.allhetero.grouping[t, 20] <- cvr.$b
-     results.allhetero.grouping[t, 21] <- cvr.$ci.lb
-     results.allhetero.grouping[t, 22] <- cvr.$ci.ub
-     results.allhetero.grouping[t, 23] <- cvr.$se
-
-    # lnVR, male to female variability ratio (logarithm of male and female standard deviations)
-
-    vr. <- metafor::rma.mv(yi = effect_size_VR, V = sample_variance_VR, random = list(~1| strain_name, ~1|production_center,    
-                                ~1|err), control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), data = results)
-    results.allhetero.grouping[t, 8] <- vr.$sigma2[1]
-    results.allhetero.grouping[t, 9] <- vr.$sigma2[2]
-    results.allhetero.grouping[t, 10] <- vr.$sigma2[3]
-    results.allhetero.grouping[t, 11] <- vr.$s.nlevels[1]
-    results.allhetero.grouping[t, 12] <- vr.$s.nlevels[2]
-    results.allhetero.grouping[t, 13] <- vr.$s.nlevels[3]
-     results.allhetero.grouping[t, 24] <- vr.$b
-     results.allhetero.grouping[t, 25] <- vr.$ci.lb
-     results.allhetero.grouping[t, 26] <- vr.$ci.ub
-     results.allhetero.grouping[t, 27] <- vr.$se
-
-    # lnRR, response ratio (logarithm of male and female means)
-
-    rr. <- metafor::rma.mv(yi = effect_size_RR, V = sample_variance_RR, random = list(~1| strain_name, ~1|production_center,    
-                                ~1|err), control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), data = results)
-    results.allhetero.grouping[t, 14] <- rr.$sigma2[1]
-    results.allhetero.grouping[t, 15] <- rr.$sigma2[2]
-    results.allhetero.grouping[t, 16] <- rr.$sigma2[3]
-    results.allhetero.grouping[t, 17] <- rr.$s.nlevels[1]
-    results.allhetero.grouping[t, 18] <- rr.$s.nlevels[2]
-    results.allhetero.grouping[t, 19] <- rr.$s.nlevels[3]
-     results.allhetero.grouping[t, 28] <- rr.$b
-     results.allhetero.grouping[t, 29] <- rr.$ci.lb
-     results.allhetero.grouping[t, 30] <- rr.$ci.ub
-     results.allhetero.grouping[t, 31] <- rr.$se
-
-  }, error=function(e){cat("ERROR :",conditionMessage(e), "\n")})
-}
-
-```
-
-Exclude traits
-```{r}
-results.allhetero.grouping2 <- results.allhetero.grouping[results.allhetero.grouping$s.nlevels.strain.VR != 0, ]
-nrow(results.allhetero.grouping2) 
-```
-
-Merge data sets containing metafor results with procedure etc. names
-
-```{r}  
-procedures <- read.csv("procedures.csv")
-
-results.allhetero.grouping2$parameter_group <- data$parameter_group[match(results.allhetero.grouping2$id, data$id)]
-results.allhetero.grouping2$procedure <- data$procedure_name[match(results.allhetero.grouping2$id, data$id)]
-
-results.allhetero.grouping2$GroupingTerm <-  procedures$GroupingTerm[match(results.allhetero.grouping2$procedure, procedures$procedure)]
-results.allhetero.grouping2$parameter_name <- data$parameter_name[match(results.allhetero.grouping2$id, data$id)]
-
-```
-
-### Correlated parameters
-
-```{r}
-metahetero1 <- results.allhetero.grouping2 
-length(unique(metahetero1$procedure)) #18    FELIX30-5-19: Komisch, ich bekomme gerade 19, und unten: 9, 152, 223; evt. wegen der neuen Formel!
-length(unique(metahetero1$GroupingTerm)) #9 
-length(unique(metahetero1$parameter_group)) # 148
-length(unique(metahetero1$parameter_name)) #218
-
-```
-
-Count of number of parameter names (correlated sub-traits) in each parameter group (par_group_size)
-
-```{r}
-metahetero1b <-
-  metahetero1 %>%
-  group_by(parameter_group) %>% 
-  mutate(par_group_size = n_distinct(parameter_name))
-
-metahetero1$par_group_size <- metahetero1b$par_group_size[match(metahetero1$parameter_group, metahetero1b$parameter_group)]
-
-```
-
-Create subsets with > 1 count (par_group_size > 1)
-
-```{r}
-metahetero1_sub <- subset(metahetero1, par_group_size > 1) # 90 observations  
-#str(metahetero1_sub)
-# metahetero1_sub$sampleSize <- as.numeric(metahetero1_sub$sampleSize) #Felix30-5-19: delete this line
-```
-
-Nest data
-```{r}
-n_count. <- metahetero1_sub %>% 
-  group_by(parameter_group) %>% 
-  #mutate(raw_N = sum(sampleSize)) %>%  #don't think is necessary: delete in final version
-  nest()
-
-```
-
-prepare for meta-analysis
-```{r}
-model_count. <- n_count. %>% 
-  mutate(model_lnRR = map(data, ~ robu(.x$lnRR ~ 1, data= .x, studynum= .x$id, modelweights = c("CORR"), rho = 0.8, 
-                                                small = TRUE, var.eff.size= (.x$lnRR_se)^2 )),
-  model_lnVR = map(data, ~ robu(.x$lnVR ~ 1, data= .x, studynum= .x$id, modelweights = c("CORR"), rho = 0.8, 
-                                                small = TRUE, var.eff.size= (.x$lnVR_se)^2 )),
-  model_lnCVR = map(data, ~ robu(.x$lnCVR ~ 1, data= .x, studynum= .x$id, modelweights = c("CORR"), rho = 0.8, 
-                                                small = TRUE, var.eff.size= (.x$lnCVR_se)^2 )))
-
-#Robumeta object details:
-#str(model_count.$model_lnCVR[[1]])
-
-```
-
-### Perform meta-analyses on correlated sub-traits, using robumeta
-
-Extract and save parameter estimates 
-```{r}
-count_fun. <- function(mod_sub)
-  return(c(as.numeric(mod_sub$mod_info$term1), mod_sub$N) )
-
-```
-
-```{r}
-robusub_RR. <- model_count. %>% 
-  transmute(parameter_group, estimatelnRR = map(model_lnRR, count_fun.)) %>% 
-  mutate(r = map(estimatelnRR, ~ data.frame(t(.)))) %>%
-  unnest(r) %>%
-  select(-estimatelnRR) %>%
-  purrr::set_names(c("parameter_group","var.RR","N.RR"))
-
-robusub_CVR. <- model_count. %>% 
-  transmute(parameter_group, estimatelnCVR = map(model_lnCVR, count_fun.)) %>% 
-  mutate(r = map(estimatelnCVR, ~ data.frame(t(.)))) %>%
-  unnest(r) %>%
-  select(-estimatelnCVR) %>%
-  purrr::set_names(c("parameter_group","var.CVR","N.CVR"))
-
-robusub_VR. <- model_count. %>% 
-  transmute(parameter_group, estimatelnVR = map(model_lnVR, count_fun.)) %>% 
-  mutate(r = map(estimatelnVR, ~ data.frame(t(.)))) %>%
-  unnest(r) %>%
-  select(-estimatelnVR) %>%
-  purrr::set_names(c("parameter_group","var.VR","N.VR"))
-
-robu_all. <- full_join(robusub_CVR., robusub_VR.) %>% full_join(., robusub_RR.)
-
-```
-
-### Merge the two data sets (the new [robu_all] and the initial [uncorrelated sub-traits with count = 1]) 
-In this step, we 	
-1) put the N from robumeta and the  N from metafor (s.nlevels.error) together into the same columns (N.RR, N.VR, N.CVR)
-
-2) calculate the total variance for metafor models as the sum of random effect variances and the residual error,
-							then put them in the same columns together with the residual variances from robumeta
-
-```{r}
-metahetero_all <- metahetero1 %>% filter(par_group_size == 1) %>% as_tibble
-metahetero_all$N.RR <- metahetero_all$s.nlevels.error.RR 
-metahetero_all$N.CVR <- metahetero_all$s.nlevels.error.CVR 
-metahetero_all$N.VR <- metahetero_all$s.nlevels.error.VR 
-metahetero_all$var.RR <- log(sqrt(metahetero_all$sigma2_strain.RR + metahetero_all$sigma2_center.RR + metahetero_all$sigma2_error.RR))
-metahetero_all$var.VR <- log(sqrt(metahetero_all$sigma2_strain.VR + metahetero_all$sigma2_center.VR + metahetero_all$sigma2_error.VR))
-metahetero_all$var.CVR <- log(sqrt(metahetero_all$sigma2_strain.CVR + metahetero_all$sigma2_center.CVR + metahetero_all$sigma2_error.CVR))
-#str(metahetero_all)
-#str(robu_all.)
-
-metahetero_all <- metahetero_all %>% mutate(var.RR = if_else(var.RR == -Inf, -7 ,var.RR),
-                   	  var.VR = if_else(var.VR == -Inf, -5 ,var.VR),
-				  var.CVR = if_else(var.CVR == -Inf, -6 ,var.CVR))
-```
-
-### Combine data 
-in three separate steps
-```{r}
-combinedmetahetero <- bind_rows(robu_all., metahetero_all)
-#glimpse(combinedmetahetero)
-
-metacombohetero <- combinedmetahetero
-metacombohetero$counts <- metahetero1$par_group_size[match( metacombohetero$parameter_group, metahetero1$parameter_group)]
-metacombohetero$procedure2 <-metahetero1$procedure[match( metacombohetero$parameter_group, metahetero1$parameter_group)]
-metacombohetero$GroupingTerm2 <-metahetero1$GroupingTerm[match( metacombohetero$parameter_group, metahetero1$parameter_group)]
-
-```
-Clean-up and rename 
-```{r}
-metacombohetero <- metacombohetero[, c(1:7, 43:45)] 
-names(metacombohetero)[9] <- "procedure" 
-names(metacombohetero)[10] <- "GroupingTerm"
-
-#write.csv(metacombohetero, "metacombohetero.csv")
-```
-
-### Last step: Meta-meta-analysis of heterogeneity
-Perform meta-meta-analysis (3 for each of the 9 grouping terms: var.CVR, var.VR, var.RR) 
-```{r}
-#glimpse(metacombohetero)
-
-metacombohetero_final <- metacombohetero %>%
- group_by(GroupingTerm) %>%
- nest()
-
-#Calculate number of parameters per grouping term : not needed; delete in final version
-#metacombo_final <- metacombo_final  %>%  mutate(para_per_GroupingTerm = map_dbl(data, nrow))
-```
-
- Final fixed effects meta-analyses within grouping terms, with SE of the estimate
-
-```{r}
-metacombohetero$var.CVR
-
-heterog1 <- metacombohetero_final %>%
-
-  mutate(model_heteroCVR = map(data, ~ metafor::rma.uni(yi = .x$var.CVR, sei = sqrt(1 / 2*(.x$N.CVR - 1)),  
-				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 10000, stepadj=0.5), verbose=F)),
-	   model_heteroVR = map(data, ~ metafor::rma.uni(yi = .x$var.VR, sei = sqrt(1 / 2*(.x$N.VR - 1)),  
-				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 10000, stepadj=0.5), verbose=F)),
-	   model_heteroRR = map(data, ~ metafor::rma.uni(yi = .x$var.RR, sei = sqrt(1 / 2*(.x$N.RR - 1)),  
-				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 10000, stepadj=0.5), verbose=F)))
-
-heterog1
-
-# **Re-structure data for each grouping term; extract heterogenenity/variance terms; delete un-used variables
-
-Behaviour.
-<- heterog1 %>% filter(., GroupingTerm == "Behaviour")  %>% select(., -data)  %>%  mutate(heteroCVR=.[[2]][[1]]$b, heteroCVR_lower=.[[2]][[1]]$ci.lb, heteroCVR_upper=.[[2]][[1]]$ci.ub, heteroCVR_se=.[[2]][[1]]$se,
-	              heteroVR=.[[3]][[1]]$b, heteroVR_lower=.[[3]][[1]]$ci.lb, heteroVR_upper=.[[3]][[1]]$ci.ub, heteroVR_se=.[[3]][[1]]$se,
-		        heteroRR=.[[4]][[1]]$b, heteroRR_lower=.[[4]][[1]]$ci.lb, heteroRR_upper=.[[4]][[1]]$ci.ub, heteroRR_se=.[[4]][[1]]$se) %>%
-			  select(., GroupingTerm, heteroCVR:heteroRR_se)
-
-Immunology.
-<- heterog1 %>% filter(., GroupingTerm == "Immunology") %>% select(., -data)  %>%  mutate(heteroCVR=.[[2]][[1]]$b, heteroCVR_lower=.[[2]][[1]]$ci.lb, heteroCVR_upper=.[[2]][[1]]$ci.ub, heteroCVR_se=.[[2]][[1]]$se,
-	              heteroVR=.[[3]][[1]]$b, heteroVR_lower=.[[3]][[1]]$ci.lb, heteroVR_upper=.[[3]][[1]]$ci.ub, heteroVR_se=.[[3]][[1]]$se,
-		        heteroRR=.[[4]][[1]]$b, heteroRR_lower=.[[4]][[1]]$ci.lb, heteroRR_upper=.[[4]][[1]]$ci.ub, heteroRR_se=.[[4]][[1]]$se) %>%
-			  select(., GroupingTerm, heteroCVR:heteroRR_se)
-
-Hematology.
-<- heterog1 %>% filter(., GroupingTerm == "Hematology") %>% select(., -data)  %>%  mutate(heteroCVR=.[[2]][[1]]$b, heteroCVR_lower=.[[2]][[1]]$ci.lb, heteroCVR_upper=.[[2]][[1]]$ci.ub, heteroCVR_se=.[[2]][[1]]$se,
-	              heteroVR=.[[3]][[1]]$b, heteroVR_lower=.[[3]][[1]]$ci.lb, heteroVR_upper=.[[3]][[1]]$ci.ub, heteroVR_se=.[[3]][[1]]$se,
-		        heteroRR=.[[4]][[1]]$b, heteroRR_lower=.[[4]][[1]]$ci.lb, heteroRR_upper=.[[4]][[1]]$ci.ub, heteroRR_se=.[[4]][[1]]$se) %>%
-			  select(., GroupingTerm, heteroCVR:heteroRR_se)
-
-Hearing.
-<- heterog1 %>% filter(., GroupingTerm == "Hearing")  %>% select(., -data)  %>%  mutate(heteroCVR=.[[2]][[1]]$b, heteroCVR_lower=.[[2]][[1]]$ci.lb, heteroCVR_upper=.[[2]][[1]]$ci.ub, heteroCVR_se=.[[2]][[1]]$se,
-	              heteroVR=.[[3]][[1]]$b, heteroVR_lower=.[[3]][[1]]$ci.lb, heteroVR_upper=.[[3]][[1]]$ci.ub, heteroVR_se=.[[3]][[1]]$se,
-		        heteroRR=.[[4]][[1]]$b, heteroRR_lower=.[[4]][[1]]$ci.lb, heteroRR_upper=.[[4]][[1]]$ci.ub, heteroRR_se=.[[4]][[1]]$se) %>%
-			  select(., GroupingTerm, heteroCVR:heteroRR_se)
-
-Physiology.
-<- heterog1 %>% filter(., GroupingTerm == "Physiology")  %>% select(., -data)  %>%  mutate(heteroCVR=.[[2]][[1]]$b, heteroCVR_lower=.[[2]][[1]]$ci.lb, heteroCVR_upper=.[[2]][[1]]$ci.ub, heteroCVR_se=.[[2]][[1]]$se,
-	              heteroVR=.[[3]][[1]]$b, heteroVR_lower=.[[3]][[1]]$ci.lb, heteroVR_upper=.[[3]][[1]]$ci.ub, heteroVR_se=.[[3]][[1]]$se,
-		        heteroRR=.[[4]][[1]]$b, heteroRR_lower=.[[4]][[1]]$ci.lb, heteroRR_upper=.[[4]][[1]]$ci.ub, heteroRR_se=.[[4]][[1]]$se) %>%
-			  select(., GroupingTerm, heteroCVR:heteroRR_se)
-
-Metabolism.
-<- heterog1 %>% filter(., GroupingTerm == "Metabolism")  %>% select(., -data)  %>%  mutate(heteroCVR=.[[2]][[1]]$b, heteroCVR_lower=.[[2]][[1]]$ci.lb, heteroCVR_upper=.[[2]][[1]]$ci.ub, heteroCVR_se=.[[2]][[1]]$se,
-	              heteroVR=.[[3]][[1]]$b, heteroVR_lower=.[[3]][[1]]$ci.lb, heteroVR_upper=.[[3]][[1]]$ci.ub, heteroVR_se=.[[3]][[1]]$se,
-		        heteroRR=.[[4]][[1]]$b, heteroRR_lower=.[[4]][[1]]$ci.lb, heteroRR_upper=.[[4]][[1]]$ci.ub, heteroRR_se=.[[4]][[1]]$se) %>%
-			  select(., GroupingTerm, heteroCVR:heteroRR_se)
-
-Morphology.
-<- heterog1 %>% filter(., GroupingTerm == "Morphology") %>% select(., -data)  %>%  mutate(heteroCVR=.[[2]][[1]]$b, heteroCVR_lower=.[[2]][[1]]$ci.lb, heteroCVR_upper=.[[2]][[1]]$ci.ub, heteroCVR_se=.[[2]][[1]]$se,
-	              heteroVR=.[[3]][[1]]$b, heteroVR_lower=.[[3]][[1]]$ci.lb, heteroVR_upper=.[[3]][[1]]$ci.ub, heteroVR_se=.[[3]][[1]]$se,
-		        heteroRR=.[[4]][[1]]$b, heteroRR_lower=.[[4]][[1]]$ci.lb, heteroRR_upper=.[[4]][[1]]$ci.ub, heteroRR_se=.[[4]][[1]]$se) %>%
-			  select(., GroupingTerm, heteroCVR:heteroRR_se)
-
-Heart.
-<- heterog1 %>% filter(., GroupingTerm == "Heart")  %>% select(., -data)  %>%  mutate(heteroCVR=.[[2]][[1]]$b, heteroCVR_lower=.[[2]][[1]]$ci.lb, heteroCVR_upper=.[[2]][[1]]$ci.ub, heteroCVR_se=.[[2]][[1]]$se,
-	              heteroVR=.[[3]][[1]]$b, heteroVR_lower=.[[3]][[1]]$ci.lb, heteroVR_upper=.[[3]][[1]]$ci.ub, heteroVR_se=.[[3]][[1]]$se,
-		        heteroRR=.[[4]][[1]]$b, heteroRR_lower=.[[4]][[1]]$ci.lb, heteroRR_upper=.[[4]][[1]]$ci.ub, heteroRR_se=.[[4]][[1]]$se) %>%
-			  select(., GroupingTerm, heteroCVR:heteroRR_se)
-
-Eye.
-<- heterog1 %>% filter(., GroupingTerm == "Eye")  %>% select(., -data)  %>%  mutate(heteroCVR=.[[2]][[1]]$b, heteroCVR_lower=.[[2]][[1]]$ci.lb, heteroCVR_upper=.[[2]][[1]]$ci.ub, heteroCVR_se=.[[2]][[1]]$se,
-	              heteroVR=.[[3]][[1]]$b, heteroVR_lower=.[[3]][[1]]$ci.lb, heteroVR_upper=.[[3]][[1]]$ci.ub, heteroVR_se=.[[3]][[1]]$se,
-		        heteroRR=.[[4]][[1]]$b, heteroRR_lower=.[[4]][[1]]$ci.lb, heteroRR_upper=.[[4]][[1]]$ci.ub, heteroRR_se=.[[4]][[1]]$se) %>%
-			  select(., GroupingTerm, heteroCVR:heteroRR_se)
-
-heterog2 <- bind_rows(Behaviour., Morphology., Metabolism., Physiology., Immunology., Hematology., Heart., Hearing., Eye.)
-str(heterog2)
-
-```
-
-### Restructure data for plotting 
-```{r}
-heterog3 <- gather(heterog2, parameter, value, c(heteroCVR, heteroVR, heteroRR), factor_key= TRUE)
-
-heteroCVR.ci <- heterog3 %>% filter(parameter == "heteroCVR") %>% mutate(ci.low = heteroCVR_lower, ci.high = heteroCVR_upper)
-heteroVR.ci <- heterog3 %>% filter(parameter == "heteroVR") %>% mutate(ci.low = heteroVR_lower, ci.high = heteroVR_upper)
-heteroRR.ci <- heterog3 %>% filter(parameter == "heteroRR") %>% mutate(ci.low = heteroRR_lower, ci.high = heteroRR_upper)
-
-heterog4 <- bind_rows(heteroCVR.ci, heteroVR.ci, heteroRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
-
-# **Re-order grouping terms
-
-heterog4$GroupingTerm <- factor(heterog4$GroupingTerm, levels =c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye") )
-heterog4$GroupingTerm <- factor(heterog4$GroupingTerm, rev(levels(heterog4$GroupingTerm)))
-heterog4$label <- "All traits"
-#write.csv(heterog4, "heterog4.csv")
-
-```
-
-# Plot Supplement FIGURE S1 (Second-order meta analysis on heterogeneity)
-
-### Plot FigS1 all traits
-```{r}
-
-Metameta_FigS1_alltraits <- heterog4 %>%
-
-  ggplot(aes(y= GroupingTerm, x= value)) +
-  geom_errorbarh(aes(xmin = ci.low, 
-                     xmax = ci.high), 
-			   height = 0.1, show.legend = FALSE) +
-  geom_point(aes(shape = parameter,
-             fill = parameter, color = parameter), size = 2.2, 
-             show.legend = FALSE) +
-  scale_x_continuous(limits=c(-7.0, 0.5), 
-                     #breaks = c(-2.0, -1.5, -1.0, -0.5, 0, 0.5, 1.0, 1.5, 2.0), 
-                     name='Effect size') +
-  facet_grid(cols = vars(parameter), rows = vars(label),
-             labeller = label_wrap_gen(width = 23),
-             scales= 'free', 
-             space='free')+
-  theme_bw()+
-  theme(strip.text.y = element_text(angle = 270, size = 10, margin = margin(t=15, r=15, b=15, l=15)), 
-	  strip.text.x = element_text(size = 12),
-        strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
-        text = element_text(size = 14),
-        panel.spacing = unit(0.5, "lines"),
-        panel.border= element_blank(),
-        axis.line=element_line(), 
-        panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
-        panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
-        panel.grid.minor.y = element_blank(),
-        panel.grid.minor.x = element_blank(), 
-        legend.title = element_blank(),
-        axis.title.x = element_blank(),
-	  axis.title.y = element_blank())
-
-Metameta_FigS1_alltraits
-
-```
-
-# TABLES with Heterogeneity (tau2, I2) of all the groups, following the structure of FIG3
-
-### CVR
-```{r}
-heteroeach.meta.CVR.c <- as.data.frame(overall1 %>% group_by(GroupingTerm) %>%  
-		mutate(tau2 = map_dbl(model_lnCVR, pluck(9)),
-			 I2 = map_dbl(model_lnCVR, pluck(23))) )[, c("GroupingTerm", "tau2", "I2")]
-
-heteroall.meta.CVR.c <- as.data.frame(overall_all1 %>% 
-		mutate(tau2 = map_dbl(model_lnCVR, pluck(9)),
-			 I2 = map_dbl(model_lnCVR, pluck(23))) )[, c("tau2", "I2")]
-
-heteroall.meta.CVR.c <- heteroall.meta.CVR.c %>% mutate(GroupingTerm = "All")
-
-overall2.CVR.c <- bind_rows(heteroeach.meta.CVR.c, heteroall.meta.CVR.c)
-
-overall2.CVR.c <- add_column(overall2.CVR.c, var = "ln(CVR)", .before= "tau2")
-overall2.CVR.c <- overall2.CVR.c[order(overall2.CVR.c$GroupingTerm),]
-```
-
-### VR
-
-```{r}
-heteroeach.meta.VR.c <- as.data.frame(overall1 %>% group_by(GroupingTerm) %>%  
-		mutate(tau2 = map_dbl(model_lnVR, pluck(9)),
-			 I2 = map_dbl(model_lnVR, pluck(23))) )[, c("GroupingTerm", "tau2", "I2")]
-
-heteroall.meta.VR.c <- as.data.frame(overall_all1 %>% 
-		mutate(tau2 = map_dbl(model_lnVR, pluck(9)),
-			 I2 = map_dbl(model_lnVR, pluck(23))) )[, c("tau2", "I2")]
-
-heteroall.meta.VR.c <- heteroall.meta.VR.c %>% mutate(GroupingTerm = "All")
-
-overall2.VR.c <- bind_rows(heteroeach.meta.VR.c, heteroall.meta.VR.c)
-
-overall2.VR.c <- add_column(overall2.VR.c, var = "ln(VR)", .before= "tau2")
-overall2.VR.c <- overall2.VR.c[order(overall2.VR.c$GroupingTerm),]
-```
-
-### RR
-```{r}
-heteroeach.meta.RR.c <- as.data.frame(overall1 %>% group_by(GroupingTerm) %>%  
-		mutate(tau2 = map_dbl(model_lnRR, pluck(9)),
-			 I2 = map_dbl(model_lnRR, pluck(23))) )[, c("GroupingTerm", "tau2", "I2")]
-
-heteroall.meta.RR.c <- as.data.frame(overall_all1 %>% 
-		mutate(tau2 = map_dbl(model_lnRR, pluck(9)),
-			 I2 = map_dbl(model_lnRR, pluck(23))) )[, c("tau2", "I2")]
-
-heteroall.meta.RR.c <- heteroall.meta.RR.c %>% mutate(GroupingTerm = "All")
-
-overall2.RR.c <- bind_rows(heteroeach.meta.RR.c, heteroall.meta.RR.c)
-
-overall2.RR.c <- add_column(overall2.RR.c, var = "ln(RR)", .before= "tau2")
-overall2.RR.c <- overall2.RR.c[order(overall2.RR.c$GroupingTerm),]
-
-overall2.het <- full_join(overall2.CVR.c, overall2.VR.c) 
-overall2.het <- full_join(overall2.het, overall2.RR.c)
-
-for_table_overall.het <- overall2.het[order(factor(overall2.het$GroupingTerm, levels = c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye", "All"))),]
-```
-
-the following uses the same data from above (plot3.male.meta.CVR / plot3.male.meta.VR / plot3.male.meta.RR):
-
-### Male not overlapping zero (significant)
-
-Re-structure data for each grouping term; delete un-used variables
-```{r}
-#plot3.male.meta.CVR[[3]][[1]][1:30] #tau2 is at position '9', I2 is at position '23'
-#plot3.male.meta.CVR[[3]][[1]][c(9, 23)]
-
-plot3.male.meta.CVR.c <- as.data.frame(plot3.male.meta.CVR %>% group_by(GroupingTerm) %>%  
-		mutate(tau2 = map_dbl(model_lnCVR, pluck(9)),
-			 I2 = map_dbl(model_lnCVR, pluck(23))) )[, c(1,4,5)]
-#add missing GroupingTerms for plot
-plot3.male.meta.CVR.c <- add_row(plot3.male.meta.CVR.c, GroupingTerm = "Immunology")
-plot3.male.meta.CVR.c <- add_row(plot3.male.meta.CVR.c, GroupingTerm = "Hearing")
-plot3.male.meta.CVR.c <- add_row(plot3.male.meta.CVR.c, GroupingTerm = "Eye")
-plot3.male.meta.CVR.c <- add_column(plot3.male.meta.CVR.c, var = "ln(CVR)", .before= "tau2")
-plot3.male.meta.CVR.c <- plot3.male.meta.CVR.c[order(plot3.male.meta.CVR.c$GroupingTerm),]
-
-plot3.male.meta.VR.c <- as.data.frame(plot3.male.meta.VR %>% group_by(GroupingTerm) %>%  
-		mutate(tau2 = map_dbl(model_lnVR, pluck(9)),
-			 I2 = map_dbl(model_lnVR, pluck(23))) )[, c(1,4,5)]
-plot3.male.meta.VR.c <- add_row(plot3.male.meta.VR.c, GroupingTerm = "Immunology")
-plot3.male.meta.VR.c <- add_row(plot3.male.meta.VR.c, GroupingTerm = "Eye")
-plot3.male.meta.VR.c <- add_column(plot3.male.meta.VR.c, var = "ln(VR)", .before= "tau2")
-plot3.male.meta.VR.c <- plot3.male.meta.VR.c[order(plot3.male.meta.VR.c$GroupingTerm),]
-
-plot3.male.meta.RR.c <- as.data.frame(plot3.male.meta.RR %>% group_by(GroupingTerm) %>%  
-		mutate(tau2 = map_dbl(model_lnRR, pluck(9)),
-			 I2 = map_dbl(model_lnRR, pluck(23))) )[, c(1,4,5)]
-plot3.male.meta.RR.c <- add_column(plot3.male.meta.RR.c, var = "ln(RR)", .before= "tau2")  
-plot3.male.meta.RR.c <- plot3.male.meta.RR.c[order(plot3.male.meta.RR.c$GroupingTerm),]
-
-overall.male.plot3. <- full_join(plot3.male.meta.CVR.c, plot3.male.meta.VR.c) 
-overall.male.plot3. <- full_join(overall.male.plot3., plot3.male.meta.RR.c)
-
-for_table_malesig <- overall.male.plot3.[order(factor(overall.male.plot3.$GroupingTerm, levels = c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye", "All"))),]
-```
-### Female not overlapping zero (significant)
-
-Re-structure data for each grouping term; delete un-used variables
-```{r}
-#plot3.female.meta.CVR[[3]][[1]][1:30] #tau2 is at position '9', I2 is at position '23'
-#plot3.female.meta.CVR[[3]][[1]][c(9, 23)]
-
-plot3.female.meta.CVR.c <- as.data.frame(plot3.female.meta.CVR %>% group_by(GroupingTerm) %>%  
-		mutate(tau2 = map_dbl(model_lnCVR, pluck(9)),
-			 I2 = map_dbl(model_lnCVR, pluck(23))) )[, c(1,4,5)]
-#add missing GroupingTerms 
-plot3.female.meta.CVR.c <- add_row(plot3.female.meta.CVR.c, GroupingTerm = "Morphology")
-plot3.female.meta.CVR.c <- add_row(plot3.female.meta.CVR.c, GroupingTerm = "Hearing")
-plot3.female.meta.CVR.c <- add_column(plot3.female.meta.CVR.c, var = "ln(CVR)", .before= "tau2")
-plot3.female.meta.CVR.c <- plot3.female.meta.CVR.c[order(plot3.female.meta.CVR.c$GroupingTerm),]
-
-plot3.female.meta.VR.c <- as.data.frame(plot3.female.meta.VR %>% group_by(GroupingTerm) %>%  
-		mutate(tau2 = map_dbl(model_lnVR, pluck(9)),
-			 I2 = map_dbl(model_lnVR, pluck(23))) )[, c(1,4,5)]
-plot3.female.meta.VR.c <- add_row(plot3.female.meta.VR.c, GroupingTerm = "Morphology")
-plot3.female.meta.VR.c <- add_row(plot3.female.meta.VR.c, GroupingTerm = "Hearing")
-plot3.female.meta.VR.c <- add_row(plot3.female.meta.VR.c, GroupingTerm = "Hematology")
-plot3.female.meta.VR.c <- add_column(plot3.female.meta.VR.c, var = "ln(VR)", .before= "tau2")
-plot3.female.meta.VR.c <- plot3.female.meta.VR.c[order(plot3.female.meta.VR.c$GroupingTerm),]
-
-plot3.female.meta.RR.c <- as.data.frame(plot3.female.meta.RR %>% group_by(GroupingTerm) %>%  
-		mutate(tau2 = map_dbl(model_lnRR, pluck(9)),
-			 I2 = map_dbl(model_lnRR, pluck(23))) )[, c(1,4,5)]
-plot3.female.meta.RR.c <- add_row(plot3.female.meta.RR.c, GroupingTerm = "Eye")
-plot3.female.meta.RR.c <- add_row(plot3.female.meta.RR.c, GroupingTerm = "Metabolism")
-plot3.female.meta.RR.c <- add_column(plot3.female.meta.RR.c, var = "ln(RR)", .before= "tau2")  
-plot3.female.meta.RR.c <- plot3.female.meta.RR.c[order(plot3.female.meta.RR.c$GroupingTerm),]
-
-overall.female.plot3. <- full_join(plot3.female.meta.CVR.c, plot3.female.meta.VR.c) 
-overall.female.plot3. <- full_join(overall.female.plot3., plot3.female.meta.RR.c)
-
-for_table_femsig <- overall.female.plot3.[order(factor(overall.female.plot3.$GroupingTerm, levels = c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye", "All"))),]
-```
-
-### Male-biased >10%
-
-Re-structure data for each grouping term; delete un-used variables
-```{r}
-plot3.male.meta.CVR.perc.c <- as.data.frame(plot3.male.meta.CVR.perc %>% group_by(GroupingTerm) %>%  
-		mutate(tau2 = map_dbl(model_lnCVR, pluck(9)),
-			 I2 = map_dbl(model_lnCVR, pluck(23))) )[, c(1,4,5)]
-#add missing GroupingTerms for plot
-plot3.male.meta.CVR.perc.c <- add_row(plot3.male.meta.CVR.perc.c, GroupingTerm = "Hearing")
-plot3.male.meta.CVR.perc.c <- add_row(plot3.male.meta.CVR.perc.c, GroupingTerm = "Eye")
-plot3.male.meta.CVR.perc.c <- add_column(plot3.male.meta.CVR.perc.c, var = "ln(CVR)", .before= "tau2")
-plot3.male.meta.CVR.perc.c <- plot3.male.meta.CVR.perc.c[order(plot3.male.meta.CVR.perc.c$GroupingTerm),]
-
-plot3.male.meta.VR.perc.c <- as.data.frame(plot3.male.meta.VR.perc %>% group_by(GroupingTerm) %>%  
-		mutate(tau2 = map_dbl(model_lnVR, pluck(9)),
-			 I2 = map_dbl(model_lnVR, pluck(23))) )[, c(1,4,5)]
-plot3.male.meta.VR.perc.c <- add_row(plot3.male.meta.VR.perc.c, GroupingTerm = "Hearing")
-plot3.male.meta.VR.perc.c <- add_row(plot3.male.meta.VR.perc.c, GroupingTerm = "Eye")
-plot3.male.meta.VR.perc.c <- add_column(plot3.male.meta.VR.perc.c, var = "ln(VR)", .before= "tau2")
-plot3.male.meta.VR.perc.c <- plot3.male.meta.VR.perc.c[order(plot3.male.meta.VR.perc.c$GroupingTerm),]
-
-plot3.male.meta.RR.perc.c <- as.data.frame(plot3.male.meta.RR.perc %>% group_by(GroupingTerm) %>%  
-		mutate(tau2 = map_dbl(model_lnRR, pluck(9)),
-			 I2 = map_dbl(model_lnRR, pluck(23))) )[, c(1,4,5)]
-plot3.male.meta.RR.perc.c <- add_row(plot3.male.meta.RR.perc.c, GroupingTerm = "Hearing")
-plot3.male.meta.RR.perc.c <- add_row(plot3.male.meta.RR.perc.c, GroupingTerm = "Eye")
-plot3.male.meta.RR.perc.c <- add_row(plot3.male.meta.RR.perc.c, GroupingTerm = "Heart")
-plot3.male.meta.RR.perc.c <- add_column(plot3.male.meta.RR.perc.c, var = "ln(RR)", .before= "tau2")  
-plot3.male.meta.RR.perc.c <- plot3.male.meta.RR.perc.c[order(plot3.male.meta.RR.perc.c$GroupingTerm),]
-
-overall.male.perc. <- full_join(plot3.male.meta.CVR.perc.c, plot3.male.meta.VR.perc.c) 
-overall.male.perc. <- full_join(overall.male.perc., plot3.male.meta.RR.perc.c)
-
-for_table_male10perc <- overall.male.perc.[order(factor(overall.male.perc.$GroupingTerm, levels = c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye", "All"))),]
-```
-
-### Female-biased >10%
-
-Re-structure data
-```{r}
-#plot3.meta.CVR.perc[[3]][[1]][1:30] #tau2 is at position '9', I2 is at position '23'
-#plot3.meta.CVR.perc[[3]][[1]][c(9, 23)]
-
-plot3.female.meta.CVR.perc.c <- as.data.frame(plot3.meta.CVR.perc %>% group_by(GroupingTerm) %>%  
-		mutate(tau2 = map_dbl(model_lnCVR, pluck(9)),
-			 I2 = map_dbl(model_lnCVR, pluck(23))) )[, c(1,4,5)]  # all zero
-#add missing GroupingTerms for plot
-plot3.female.meta.CVR.perc.c <- add_row(plot3.female.meta.CVR.perc.c, GroupingTerm = "Hearing")
-plot3.female.meta.CVR.perc.c <- add_row(plot3.female.meta.CVR.perc.c, GroupingTerm = "Behaviour")
-plot3.female.meta.CVR.perc.c <- add_row(plot3.female.meta.CVR.perc.c, GroupingTerm = "Hematology")
-plot3.female.meta.CVR.perc.c <- add_column(plot3.female.meta.CVR.perc.c, var = "ln(CVR)", .before= "tau2")
-plot3.female.meta.CVR.perc.c <- plot3.female.meta.CVR.perc.c[order(plot3.female.meta.CVR.perc.c$GroupingTerm),]
-
-plot3.female.meta.VR.perc.c <- as.data.frame(plot3.meta.VR.perc %>% group_by(GroupingTerm) %>%  
-		mutate(tau2 = map_dbl(model_lnVR, pluck(9)),
-			 I2 = map_dbl(model_lnVR, pluck(23))) )[, c(1,4,5)]  # all zero, except 'All'
-#add missing GroupingTerms for plot
-plot3.female.meta.VR.perc.c <- add_row(plot3.female.meta.VR.perc.c, GroupingTerm = "Hearing")
-plot3.female.meta.VR.perc.c <- add_row(plot3.female.meta.VR.perc.c, GroupingTerm = "Hematology")
-plot3.female.meta.VR.perc.c <- add_column(plot3.female.meta.VR.perc.c, var = "ln(VR)", .before= "tau2")
-plot3.female.meta.VR.perc.c <- plot3.female.meta.VR.perc.c[order(plot3.female.meta.VR.perc.c$GroupingTerm),]
-
-plot3.female.meta.RR.perc.c <- as.data.frame(plot3.meta.RR.perc %>% group_by(GroupingTerm) %>%  
-		mutate(tau2 = map_dbl(model_lnRR, pluck(9)),
-			 I2 = map_dbl(model_lnRR, pluck(23))) )[, c(1,4,5)]  
-#add missing GroupingTerms for plot
-plot3.female.meta.RR.perc.c <- add_row(plot3.female.meta.RR.perc.c, GroupingTerm = "Hearing")
-plot3.female.meta.RR.perc.c <- add_row(plot3.female.meta.RR.perc.c, GroupingTerm = "Eye")
-plot3.female.meta.RR.perc.c <- add_row(plot3.female.meta.RR.perc.c, GroupingTerm = "Metabolism")
-plot3.female.meta.RR.perc.c <- add_row(plot3.female.meta.RR.perc.c, GroupingTerm = "Hematology")
-plot3.female.meta.RR.perc.c <- add_column(plot3.female.meta.RR.perc.c, var = "ln(RR)", .before= "tau2")
-plot3.female.meta.RR.perc.c <- plot3.female.meta.RR.perc.c[order(plot3.female.meta.RR.perc.c$GroupingTerm),]
-
-overall.female.perc. <- full_join(plot3.female.meta.CVR.perc.c, plot3.female.meta.VR.perc.c) 
-overall.female.perc. <- full_join(overall.female.perc., plot3.female.meta.RR.perc.c)
-
-for_table_female10perc <- overall.female.perc.[order(factor(overall.female.perc.$GroupingTerm, levels = c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye", "All"))),]
-
-```
+Fig3 <- ggarrange(Metameta_Fig3_alltraits, Metameta_Fig3_sig, Metameta_Fig3_perc, nrow = 3, align = "v", heights = c(1.22,1,1))
+
+ggsave("Fig3.pdf", plot = Fig3, width = 6, height = 5)
+
+####################################################################################################################################

### 2019-08-01 scripts/2019_July_IMPC variance and sex difference.Rmd

--- 2019-07-05 scripts/2019_4June_IMPC variance and sex difference.Rmd
@@
 author: "Susanne & Felix Zajitschek"
-date: "2nd April 2019"
+date: "July 2019"
 output:
@@
 
-# Now that we have a "results" table with each of the meta-analytic means for all effect sizes of interest, we can use this table as part of the Shint App, which will then be able to back calculate the percentage differences between males and females for mean, variance and coefficient of variance.
+# Now that we have a "results" table with each of the meta-analytic means for all effect sizes of interest, we can use this table as part of the Shiny App, which will then be able to back calculate the percentage differences between males and females for mean, variance and coefficient of variance.
 We'll export and use this in the Shiny App.
 **Note that I have not dealt with convergence issues in some of these models, and so, this will need to be done down the road**
+
+## Note Susi 31/7/2019: This dataset contains dublicated values, plus no info on what the "traits" mean. I will change Dan N's to one further belwo, that have been cleaned up already
+#FILE TO USE: METACOMBO (around line 500)
 
@@
 ```
+
 ### Clean-up and rename 
 ```{r}
-metacombo <-metacombo[, c(1, 20:22, 2:13)] 
+metacombo <-metacombo[, c(1, 21:23, 2:13)] 
 names(metacombo)[3] <- "procedure" 
@@
 
+```
+
+```{r}
+# SHINY APP # Now that we have a corrected "results" table with each of the meta-analytic means for all effect sizes of interest, we can use this table as part of the Shiny App, which will then be able to back calculate the percentage differences between males and females for mean, variance and coefficient of variance.
+We'll export and use this in the Shiny App.
+**Note that I have not dealt with convergence issues in some of these models, and so, this will need to be done down the road**
+
+## Note Susi 31/7/2019: This has been cleaned up already
+#FILE TO USE: METACOMBO 
+  ### note: to use
+
+trait_meta_results <- write.csv(metacombo, file = "export/trait_meta_results.csv")
 ```
@@
 	coord_flip()
-#malebias_Fig2_over10
+# malebias_Fig2_over10
 
@@
 
-#add missing GroupingTerms for plot POYTENTIALLY DELETE
+#add missing GroupingTerms for plot POTENTIALLY DELETE
 #overall.female.plot3 <- add_row(overall.female.plot3, GroupingTerm = "Morphology")
@@
 Fig3
-#                     ggsave("Fig3.pdf", plot = Fig3, width = 9, height = 6) 
-```
-
-## Plot Supplement FIGURE S1 (Second-order meta-analysis on heterogeneity)
-
-### Create matrix to store results for all traits
+#ggsave("Fig3.pdf", plot = Fig3, width = 9, height = 6) 
+```
+
+# * Heterogeneity
+# ** FIGURE 4 (Second-order meta analysis on heterogeneity)
+## *Create matrix to store results for all traits
 ```{r}
@@
 
-### LOOP
+# **LOOP
+#  parameters to extract from metafor (sigma2's, s.nlevels)
 
@@
 
-Exclude traits
+## *Exclude traits
 ```{r}
 results.allhetero.grouping2 <- results.allhetero.grouping[results.allhetero.grouping$s.nlevels.strain.VR != 0, ]
-nrow(results.allhetero.grouping2) 
-```
-
-Merge data sets containing metafor results with procedure etc. names
-
-```{r}  
-procedures <- read.csv("procedures.csv")
+nrow(results.allhetero.grouping2) #218
+```
+
+# *Merge data sets containing metafor results with procedure etc. names 
+```{r}
+#procedures <- read.csv("procedures.csv")
 
@@
 
-### Correlated parameters
+## *Correlated parameters
 
@@
 metahetero1 <- results.allhetero.grouping2 
-length(unique(metahetero1$procedure)) #18    FELIX30-5-19: Komisch, ich bekomme gerade 19, und unten: 9, 152, 223; evt. wegen der neuen Formel!
+length(unique(metahetero1$procedure)) #18
 length(unique(metahetero1$GroupingTerm)) #9 
-length(unique(metahetero1$parameter_group)) # 148
+length(unique(metahetero1$parameter_group)) # 149 levels: one more tha in effect size alanlysis, see above; CHECK!
 length(unique(metahetero1$parameter_name)) #218
@@
 
-Count of number of parameter names (correlated sub-traits) in each parameter group (par_group_size)
+# **Count of number of parameter names (correlated sub-traits) in each parameter group (par_group_size)
 
@@
 
-Create subsets with > 1 count (par_group_size > 1)
+# **Create subsets with > 1 count (par_group_size > 1)
 
@@
 metahetero1_sub <- subset(metahetero1, par_group_size > 1) # 90 observations  
-#str(metahetero1_sub)
-# metahetero1_sub$sampleSize <- as.numeric(metahetero1_sub$sampleSize) #Felix30-5-19: delete this line
-```
-
-Nest data
+str(metahetero1_sub)
+# metahetero1_sub$sampleSize <- as.numeric(metahetero1_sub$sampleSize) #from previous analysis? don't think is used: : delete in final version
+```
+
+# **Nest data
 ```{r}
@@
 
-prepare for meta-analysis
 ```{r}
@@
 
+```
 #Robumeta object details:
@@
 
-```
-
-### Perform meta-analyses on correlated sub-traits, using robumeta
-
-Extract and save parameter estimates 
+## *Perform meta-analyses on correlated sub-traits, using robumeta
+
+# Shinichi: We think we want to use these for further analyses:
+# residual variance: as.numeric(robu_fit$mod_info$term1)     (same as 'mod_info$tau.sq')
+# sample size: robu_fit$N
+
+## **Extract and save parameter estimates 
 ```{r}
@@
 
-### Merge the two data sets (the new [robu_all] and the initial [uncorrelated sub-traits with count = 1]) 
-In this step, we 	
+## **Merge the two data sets (the new [robu_all] and the initial [uncorrelated sub-traits with count = 1]) 
+##  In this step, we 	
 1) put the N from robumeta and the  N from metafor (s.nlevels.error) together into the same columns (N.RR, N.VR, N.CVR)
@@
 							then put them in the same columns together with the residual variances from robumeta
-
 ```{r}
@@
 metahetero_all$N.VR <- metahetero_all$s.nlevels.error.VR
+
+# log (srt( of the data to look at))
 metahetero_all$var.RR <- log(sqrt(metahetero_all$sigma2_strain.RR + metahetero_all$sigma2_center.RR + metahetero_all$sigma2_error.RR))
@@
 
+#adjust the -inf to smallest number in dataset
 metahetero_all <- metahetero_all %>% mutate(var.RR = if_else(var.RR == -Inf, -7 ,var.RR),
@@
 				  var.CVR = if_else(var.CVR == -Inf, -6 ,var.CVR))
-```
-
-### Combine data 
-in three separate steps
+
+```
+
+# **Combine data 
+# Step1 
 ```{r}
@@
 #glimpse(combinedmetahetero)
-
+```
+# Steps 2&3
+```{r}
 metacombohetero <- combinedmetahetero
@@
 ```
-Clean-up and rename 
+# **Clean-up and rename 
 ```{r}
@@
 
+```
+
+```{r}
 #write.csv(metacombohetero, "metacombohetero.csv")
-```
-
-### Last step: Meta-meta-analysis of heterogeneity
-Perform meta-meta-analysis (3 for each of the 9 grouping terms: var.CVR, var.VR, var.RR) 
-```{r}
-#glimpse(metacombohetero)
+
+```
+
+## *Last step: meta-meta-analysis of heterogeneity
+```{r}
+glimpse(metacombohetero)
+
+## *Perform meta-meta-analysis (3 for each of the 9 grouping terms: var.CVR, var.VR, var.RR)
 
@@
 
-#Calculate number of parameters per grouping term : not needed; delete in final version
+# **Calculate number of parameters per grouping term : not needed; delete in final version
 #metacombo_final <- metacombo_final  %>%  mutate(para_per_GroupingTerm = map_dbl(data, nrow))
-```
-
- Final fixed effects meta-analyses within grouping terms, with SE of the estimate
-
-```{r}
-metacombohetero$var.CVR
+
+# **Final fixed effects meta-analyses within grouping terms, with SE of the estimate 
+# Shinichi: meta-analyses on heterogeneity, using  sei as below, in metafor formula
 
@@
 heterog2 <- bind_rows(Behaviour., Morphology., Metabolism., Physiology., Immunology., Hematology., Heart., Hearing., Eye.)
-str(heterog2)
-
-```
-
-### Restructure data for plotting 
+#str(heterog2)
+
+```
+
+####################################################################################################################################
+# *PLOTS
+
+# **Restructure data for plotting 
 ```{r}
@@
 
-# Plot Supplement FIGURE S1 (Second-order meta analysis on heterogeneity)
-
-### Plot FigS1 all traits
-```{r}
-
-Metameta_FigS1_alltraits <- heterog4 %>%
+# *Plot FIGURE 4 (Second-order meta analysis on heterogeneity)
+
+# **Plot Fig4 all traits
+```{r}
+
+Metameta_Fig4_alltraits <- heterog4 %>%
 
@@
              show.legend = FALSE) +
-  scale_x_continuous(limits=c(-7.0, 0.5), 
+  scale_x_continuous(limits=c(-7.0, 1), 
                      #breaks = c(-2.0, -1.5, -1.0, -0.5, 0, 0.5, 1.0, 1.5, 2.0), 
@@
 
-Metameta_FigS1_alltraits
-
-```
-
-# TABLES with Heterogeneity (tau2, I2) of all the groups, following the structure of FIG3
-
-### CVR
-```{r}
-heteroeach.meta.CVR.c <- as.data.frame(overall1 %>% group_by(GroupingTerm) %>%  
-		mutate(tau2 = map_dbl(model_lnCVR, pluck(9)),
-			 I2 = map_dbl(model_lnCVR, pluck(23))) )[, c("GroupingTerm", "tau2", "I2")]
-
-heteroall.meta.CVR.c <- as.data.frame(overall_all1 %>% 
-		mutate(tau2 = map_dbl(model_lnCVR, pluck(9)),
-			 I2 = map_dbl(model_lnCVR, pluck(23))) )[, c("tau2", "I2")]
-
-heteroall.meta.CVR.c <- heteroall.meta.CVR.c %>% mutate(GroupingTerm = "All")
-
-overall2.CVR.c <- bind_rows(heteroeach.meta.CVR.c, heteroall.meta.CVR.c)
-
-overall2.CVR.c <- add_column(overall2.CVR.c, var = "ln(CVR)", .before= "tau2")
-overall2.CVR.c <- overall2.CVR.c[order(overall2.CVR.c$GroupingTerm),]
-```
-
-### VR
-
-```{r}
-heteroeach.meta.VR.c <- as.data.frame(overall1 %>% group_by(GroupingTerm) %>%  
-		mutate(tau2 = map_dbl(model_lnVR, pluck(9)),
-			 I2 = map_dbl(model_lnVR, pluck(23))) )[, c("GroupingTerm", "tau2", "I2")]
-
-heteroall.meta.VR.c <- as.data.frame(overall_all1 %>% 
-		mutate(tau2 = map_dbl(model_lnVR, pluck(9)),
-			 I2 = map_dbl(model_lnVR, pluck(23))) )[, c("tau2", "I2")]
-
-heteroall.meta.VR.c <- heteroall.meta.VR.c %>% mutate(GroupingTerm = "All")
-
-overall2.VR.c <- bind_rows(heteroeach.meta.VR.c, heteroall.meta.VR.c)
-
-overall2.VR.c <- add_column(overall2.VR.c, var = "ln(VR)", .before= "tau2")
-overall2.VR.c <- overall2.VR.c[order(overall2.VR.c$GroupingTerm),]
-```
-
-### RR
-```{r}
-heteroeach.meta.RR.c <- as.data.frame(overall1 %>% group_by(GroupingTerm) %>%  
-		mutate(tau2 = map_dbl(model_lnRR, pluck(9)),
-			 I2 = map_dbl(model_lnRR, pluck(23))) )[, c("GroupingTerm", "tau2", "I2")]
-
-heteroall.meta.RR.c <- as.data.frame(overall_all1 %>% 
-		mutate(tau2 = map_dbl(model_lnRR, pluck(9)),
-			 I2 = map_dbl(model_lnRR, pluck(23))) )[, c("tau2", "I2")]
-
-heteroall.meta.RR.c <- heteroall.meta.RR.c %>% mutate(GroupingTerm = "All")
-
-overall2.RR.c <- bind_rows(heteroeach.meta.RR.c, heteroall.meta.RR.c)
-
-overall2.RR.c <- add_column(overall2.RR.c, var = "ln(RR)", .before= "tau2")
-overall2.RR.c <- overall2.RR.c[order(overall2.RR.c$GroupingTerm),]
-
-overall2.het <- full_join(overall2.CVR.c, overall2.VR.c) 
-overall2.het <- full_join(overall2.het, overall2.RR.c)
-
-for_table_overall.het <- overall2.het[order(factor(overall2.het$GroupingTerm, levels = c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye", "All"))),]
-```
-
-the following uses the same data from above (plot3.male.meta.CVR / plot3.male.meta.VR / plot3.male.meta.RR):
-
-### Male not overlapping zero (significant)
-
-Re-structure data for each grouping term; delete un-used variables
-```{r}
-#plot3.male.meta.CVR[[3]][[1]][1:30] #tau2 is at position '9', I2 is at position '23'
-#plot3.male.meta.CVR[[3]][[1]][c(9, 23)]
-
-plot3.male.meta.CVR.c <- as.data.frame(plot3.male.meta.CVR %>% group_by(GroupingTerm) %>%  
-		mutate(tau2 = map_dbl(model_lnCVR, pluck(9)),
-			 I2 = map_dbl(model_lnCVR, pluck(23))) )[, c(1,4,5)]
-#add missing GroupingTerms for plot
-plot3.male.meta.CVR.c <- add_row(plot3.male.meta.CVR.c, GroupingTerm = "Immunology")
-plot3.male.meta.CVR.c <- add_row(plot3.male.meta.CVR.c, GroupingTerm = "Hearing")
-plot3.male.meta.CVR.c <- add_row(plot3.male.meta.CVR.c, GroupingTerm = "Eye")
-plot3.male.meta.CVR.c <- add_column(plot3.male.meta.CVR.c, var = "ln(CVR)", .before= "tau2")
-plot3.male.meta.CVR.c <- plot3.male.meta.CVR.c[order(plot3.male.meta.CVR.c$GroupingTerm),]
-
-plot3.male.meta.VR.c <- as.data.frame(plot3.male.meta.VR %>% group_by(GroupingTerm) %>%  
-		mutate(tau2 = map_dbl(model_lnVR, pluck(9)),
-			 I2 = map_dbl(model_lnVR, pluck(23))) )[, c(1,4,5)]
-plot3.male.meta.VR.c <- add_row(plot3.male.meta.VR.c, GroupingTerm = "Immunology")
-plot3.male.meta.VR.c <- add_row(plot3.male.meta.VR.c, GroupingTerm = "Eye")
-plot3.male.meta.VR.c <- add_column(plot3.male.meta.VR.c, var = "ln(VR)", .before= "tau2")
-plot3.male.meta.VR.c <- plot3.male.meta.VR.c[order(plot3.male.meta.VR.c$GroupingTerm),]
-
-plot3.male.meta.RR.c <- as.data.frame(plot3.male.meta.RR %>% group_by(GroupingTerm) %>%  
-		mutate(tau2 = map_dbl(model_lnRR, pluck(9)),
-			 I2 = map_dbl(model_lnRR, pluck(23))) )[, c(1,4,5)]
-plot3.male.meta.RR.c <- add_column(plot3.male.meta.RR.c, var = "ln(RR)", .before= "tau2")  
-plot3.male.meta.RR.c <- plot3.male.meta.RR.c[order(plot3.male.meta.RR.c$GroupingTerm),]
-
-overall.male.plot3. <- full_join(plot3.male.meta.CVR.c, plot3.male.meta.VR.c) 
-overall.male.plot3. <- full_join(overall.male.plot3., plot3.male.meta.RR.c)
-
-for_table_malesig <- overall.male.plot3.[order(factor(overall.male.plot3.$GroupingTerm, levels = c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye", "All"))),]
-```
-### Female not overlapping zero (significant)
-
-Re-structure data for each grouping term; delete un-used variables
-```{r}
-#plot3.female.meta.CVR[[3]][[1]][1:30] #tau2 is at position '9', I2 is at position '23'
-#plot3.female.meta.CVR[[3]][[1]][c(9, 23)]
-
-plot3.female.meta.CVR.c <- as.data.frame(plot3.female.meta.CVR %>% group_by(GroupingTerm) %>%  
-		mutate(tau2 = map_dbl(model_lnCVR, pluck(9)),
-			 I2 = map_dbl(model_lnCVR, pluck(23))) )[, c(1,4,5)]
-#add missing GroupingTerms 
-plot3.female.meta.CVR.c <- add_row(plot3.female.meta.CVR.c, GroupingTerm = "Morphology")
-plot3.female.meta.CVR.c <- add_row(plot3.female.meta.CVR.c, GroupingTerm = "Hearing")
-plot3.female.meta.CVR.c <- add_column(plot3.female.meta.CVR.c, var = "ln(CVR)", .before= "tau2")
-plot3.female.meta.CVR.c <- plot3.female.meta.CVR.c[order(plot3.female.meta.CVR.c$GroupingTerm),]
-
-plot3.female.meta.VR.c <- as.data.frame(plot3.female.meta.VR %>% group_by(GroupingTerm) %>%  
-		mutate(tau2 = map_dbl(model_lnVR, pluck(9)),
-			 I2 = map_dbl(model_lnVR, pluck(23))) )[, c(1,4,5)]
-plot3.female.meta.VR.c <- add_row(plot3.female.meta.VR.c, GroupingTerm = "Morphology")
-plot3.female.meta.VR.c <- add_row(plot3.female.meta.VR.c, GroupingTerm = "Hearing")
-plot3.female.meta.VR.c <- add_row(plot3.female.meta.VR.c, GroupingTerm = "Hematology")
-plot3.female.meta.VR.c <- add_column(plot3.female.meta.VR.c, var = "ln(VR)", .before= "tau2")
-plot3.female.meta.VR.c <- plot3.female.meta.VR.c[order(plot3.female.meta.VR.c$GroupingTerm),]
-
-plot3.female.meta.RR.c <- as.data.frame(plot3.female.meta.RR %>% group_by(GroupingTerm) %>%  
-		mutate(tau2 = map_dbl(model_lnRR, pluck(9)),
-			 I2 = map_dbl(model_lnRR, pluck(23))) )[, c(1,4,5)]
-plot3.female.meta.RR.c <- add_row(plot3.female.meta.RR.c, GroupingTerm = "Eye")
-plot3.female.meta.RR.c <- add_row(plot3.female.meta.RR.c, GroupingTerm = "Metabolism")
-plot3.female.meta.RR.c <- add_column(plot3.female.meta.RR.c, var = "ln(RR)", .before= "tau2")  
-plot3.female.meta.RR.c <- plot3.female.meta.RR.c[order(plot3.female.meta.RR.c$GroupingTerm),]
-
-overall.female.plot3. <- full_join(plot3.female.meta.CVR.c, plot3.female.meta.VR.c) 
-overall.female.plot3. <- full_join(overall.female.plot3., plot3.female.meta.RR.c)
-
-for_table_femsig <- overall.female.plot3.[order(factor(overall.female.plot3.$GroupingTerm, levels = c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye", "All"))),]
-```
-
-### Male-biased >10%
-
-Re-structure data for each grouping term; delete un-used variables
-```{r}
-plot3.male.meta.CVR.perc.c <- as.data.frame(plot3.male.meta.CVR.perc %>% group_by(GroupingTerm) %>%  
-		mutate(tau2 = map_dbl(model_lnCVR, pluck(9)),
-			 I2 = map_dbl(model_lnCVR, pluck(23))) )[, c(1,4,5)]
-#add missing GroupingTerms for plot
-plot3.male.meta.CVR.perc.c <- add_row(plot3.male.meta.CVR.perc.c, GroupingTerm = "Hearing")
-plot3.male.meta.CVR.perc.c <- add_row(plot3.male.meta.CVR.perc.c, GroupingTerm = "Eye")
-plot3.male.meta.CVR.perc.c <- add_column(plot3.male.meta.CVR.perc.c, var = "ln(CVR)", .before= "tau2")
-plot3.male.meta.CVR.perc.c <- plot3.male.meta.CVR.perc.c[order(plot3.male.meta.CVR.perc.c$GroupingTerm),]
-
-plot3.male.meta.VR.perc.c <- as.data.frame(plot3.male.meta.VR.perc %>% group_by(GroupingTerm) %>%  
-		mutate(tau2 = map_dbl(model_lnVR, pluck(9)),
-			 I2 = map_dbl(model_lnVR, pluck(23))) )[, c(1,4,5)]
-plot3.male.meta.VR.perc.c <- add_row(plot3.male.meta.VR.perc.c, GroupingTerm = "Hearing")
-plot3.male.meta.VR.perc.c <- add_row(plot3.male.meta.VR.perc.c, GroupingTerm = "Eye")
-plot3.male.meta.VR.perc.c <- add_column(plot3.male.meta.VR.perc.c, var = "ln(VR)", .before= "tau2")
-plot3.male.meta.VR.perc.c <- plot3.male.meta.VR.perc.c[order(plot3.male.meta.VR.perc.c$GroupingTerm),]
-
-plot3.male.meta.RR.perc.c <- as.data.frame(plot3.male.meta.RR.perc %>% group_by(GroupingTerm) %>%  
-		mutate(tau2 = map_dbl(model_lnRR, pluck(9)),
-			 I2 = map_dbl(model_lnRR, pluck(23))) )[, c(1,4,5)]
-plot3.male.meta.RR.perc.c <- add_row(plot3.male.meta.RR.perc.c, GroupingTerm = "Hearing")
-plot3.male.meta.RR.perc.c <- add_row(plot3.male.meta.RR.perc.c, GroupingTerm = "Eye")
-plot3.male.meta.RR.perc.c <- add_row(plot3.male.meta.RR.perc.c, GroupingTerm = "Heart")
-plot3.male.meta.RR.perc.c <- add_column(plot3.male.meta.RR.perc.c, var = "ln(RR)", .before= "tau2")  
-plot3.male.meta.RR.perc.c <- plot3.male.meta.RR.perc.c[order(plot3.male.meta.RR.perc.c$GroupingTerm),]
-
-overall.male.perc. <- full_join(plot3.male.meta.CVR.perc.c, plot3.male.meta.VR.perc.c) 
-overall.male.perc. <- full_join(overall.male.perc., plot3.male.meta.RR.perc.c)
-
-for_table_male10perc <- overall.male.perc.[order(factor(overall.male.perc.$GroupingTerm, levels = c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye", "All"))),]
-```
-
-### Female-biased >10%
-
-Re-structure data
-```{r}
-#plot3.meta.CVR.perc[[3]][[1]][1:30] #tau2 is at position '9', I2 is at position '23'
-#plot3.meta.CVR.perc[[3]][[1]][c(9, 23)]
-
-plot3.female.meta.CVR.perc.c <- as.data.frame(plot3.meta.CVR.perc %>% group_by(GroupingTerm) %>%  
-		mutate(tau2 = map_dbl(model_lnCVR, pluck(9)),
-			 I2 = map_dbl(model_lnCVR, pluck(23))) )[, c(1,4,5)]  # all zero
-#add missing GroupingTerms for plot
-plot3.female.meta.CVR.perc.c <- add_row(plot3.female.meta.CVR.perc.c, GroupingTerm = "Hearing")
-plot3.female.meta.CVR.perc.c <- add_row(plot3.female.meta.CVR.perc.c, GroupingTerm = "Behaviour")
-plot3.female.meta.CVR.perc.c <- add_row(plot3.female.meta.CVR.perc.c, GroupingTerm = "Hematology")
-plot3.female.meta.CVR.perc.c <- add_column(plot3.female.meta.CVR.perc.c, var = "ln(CVR)", .before= "tau2")
-plot3.female.meta.CVR.perc.c <- plot3.female.meta.CVR.perc.c[order(plot3.female.meta.CVR.perc.c$GroupingTerm),]
-
-plot3.female.meta.VR.perc.c <- as.data.frame(plot3.meta.VR.perc %>% group_by(GroupingTerm) %>%  
-		mutate(tau2 = map_dbl(model_lnVR, pluck(9)),
-			 I2 = map_dbl(model_lnVR, pluck(23))) )[, c(1,4,5)]  # all zero, except 'All'
-#add missing GroupingTerms for plot
-plot3.female.meta.VR.perc.c <- add_row(plot3.female.meta.VR.perc.c, GroupingTerm = "Hearing")
-plot3.female.meta.VR.perc.c <- add_row(plot3.female.meta.VR.perc.c, GroupingTerm = "Hematology")
-plot3.female.meta.VR.perc.c <- add_column(plot3.female.meta.VR.perc.c, var = "ln(VR)", .before= "tau2")
-plot3.female.meta.VR.perc.c <- plot3.female.meta.VR.perc.c[order(plot3.female.meta.VR.perc.c$GroupingTerm),]
-
-plot3.female.meta.RR.perc.c <- as.data.frame(plot3.meta.RR.perc %>% group_by(GroupingTerm) %>%  
-		mutate(tau2 = map_dbl(model_lnRR, pluck(9)),
-			 I2 = map_dbl(model_lnRR, pluck(23))) )[, c(1,4,5)]  
-#add missing GroupingTerms for plot
-plot3.female.meta.RR.perc.c <- add_row(plot3.female.meta.RR.perc.c, GroupingTerm = "Hearing")
-plot3.female.meta.RR.perc.c <- add_row(plot3.female.meta.RR.perc.c, GroupingTerm = "Eye")
-plot3.female.meta.RR.perc.c <- add_row(plot3.female.meta.RR.perc.c, GroupingTerm = "Metabolism")
-plot3.female.meta.RR.perc.c <- add_row(plot3.female.meta.RR.perc.c, GroupingTerm = "Hematology")
-plot3.female.meta.RR.perc.c <- add_column(plot3.female.meta.RR.perc.c, var = "ln(RR)", .before= "tau2")
-plot3.female.meta.RR.perc.c <- plot3.female.meta.RR.perc.c[order(plot3.female.meta.RR.perc.c$GroupingTerm),]
-
-overall.female.perc. <- full_join(plot3.female.meta.CVR.perc.c, plot3.female.meta.VR.perc.c) 
-overall.female.perc. <- full_join(overall.female.perc., plot3.female.meta.RR.perc.c)
-
-for_table_female10perc <- overall.female.perc.[order(factor(overall.female.perc.$GroupingTerm, levels = c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye", "All"))),]
-
-```
+Metameta_Fig4_alltraits 
+#ggsave("Fig4.pdf", plot = Metameta_Fig4_alltraits, width = 7, height = 6) 
+```
+
+########

### 2019-08-01 scripts/old scripts/2018.07.01-Overview.Rmd
Rename scripts/2018.07.01-Overview.Rmd to scripts/old scripts/2018.07.01-Overview.Rmd

--- 2018-08-03 Overview.Rmd
@@
 ```{r setup, include=FALSE, echo=TRUE}
-knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
+knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE, cache=FALSE)
+root.dir = rprojroot::find_root("README.md")
+knitr::opts_knit$set(root.dir = root.dir)
+
 library(readr)
@@
 
+# Datasource
+
+more recently, Jeremy states: "I provided you too much data (!) which should not be included.
+A quarter to a third of the data is from legacy projects and should be excluded.
+As I mentioned, exclude anything without datasource_name = `IMPC`"
+
+By source: 
+```
+data_raw$datasource_name %>% table()
+```
+
+So reducing to IMPC reduces the data by one third.
+
+It also greatly reduces the number of parameters:
+```{r}
+filter(data_raw, datasource_name == 'IMPC') %>% pull(parameter_name) %>% unique() %>% length()
+```
+
+```
+data_raw %>% pull(parameter_name) %>% unique() %>% length()
+```
+
 # Issues:

### 2019-08-03 scripts/2019_July_IMPC variance and sex difference.Rmd
clean up

@@
     toc_depth: 3
-runtime: shiny
+  html_notebook: 
+    toc: yes
+#runtime: shiny
 ---
@@
 #saveRDS(data_raw, "export/data_clean.rds")
-
-data1 <- readRDS("export/data_clean.rds")
+getwd()
+data1 <- readRDS("/export/data_clean.rds") 
 #data1 
@@
 
- group <- read.csv("export/ParameterGrouping.csv") 
+ group <- read.csv("/export/ParameterGrouping.csv") 
  data <- data3
@@
 
-trait_meta_results <- write.csv(results.alltraits.grouping, file = "export/trait_meta_results.csv")
+#trait_meta_results <- write.csv(results.alltraits.grouping, file = "export/trait_meta_results.csv")
 
@@
 ```{r}
-procedures <- read.csv("export/procedures.csv")
+procedures <- read.csv("/export/procedures.csv")
 
@@
 
-trait_meta_results <- write.csv(metacombo, file = "export/trait_meta_results.csv")
+trait_meta_results <- write.csv(metacombo, file = "/export/trait_meta_results.csv")
 ```
@@
 
-# * Heterogeneity
-# ** FIGURE 4 (Second-order meta analysis on heterogeneity)
-## *Create matrix to store results for all traits
+# Heterogeneity
+## FIGURE 4 (Second-order meta analysis on heterogeneity)
+### Create matrix to store results for all traits
 ```{r}
@@
 
-# **LOOP
-#  parameters to extract from metafor (sigma2's, s.nlevels)
+## LOOP
+parameters to extract from metafor (sigma2's, s.nlevels)
 
@@
 
-## *Exclude traits
+### Exclude traits
 ```{r}
@@
 
-# *Merge data sets containing metafor results with procedure etc. names 
+Merge data sets containing metafor results with procedure etc. names 
 ```{r}
@@
 
-## *Correlated parameters
-
+### Dealing with correlated parameters
 ```{r}
@@
 
-```
-
-# **Count of number of parameter names (correlated sub-traits) in each parameter group (par_group_size)
-
-```{r}
+# Count of number of parameter names (correlated sub-traits) in each parameter group (par_group_size)
+
 metahetero1b <-
@@
 
-```
-
-# **Create subsets with > 1 count (par_group_size > 1)
-
-```{r}
+#Create subsets with > 1 count (par_group_size > 1)
+
 metahetero1_sub <- subset(metahetero1, par_group_size > 1) # 90 observations  
@@
 # metahetero1_sub$sampleSize <- as.numeric(metahetero1_sub$sampleSize) #from previous analysis? don't think is used: : delete in final version
-```
-
-# **Nest data
-```{r}
+
+# Nest data
+
 n_count. <- metahetero1_sub %>% 
@@
 
-```
-
-```{r}
+# meta-analysis preparation
+
 model_count. <- n_count. %>% 
@@
 
-```
 #Robumeta object details:
@@
 
-```
-
-```{r}
 robusub_RR. <- model_count. %>% 
@@
 
-## **Merge the two data sets (the new [robu_all] and the initial [uncorrelated sub-traits with count = 1]) 
-##  In this step, we 	
+### **Merge the two data sets (the new [robu_all] and the initial [uncorrelated sub-traits with count = 1]) 
+  In this step, we 	
 1) put the N from robumeta and the  N from metafor (s.nlevels.error) together into the same columns (N.RR, N.VR, N.CVR)
@@
 
-```
-
 # **Combine data 
 # Step1
-```{r}
+
 combinedmetahetero <- bind_rows(robu_all., metahetero_all)
 #glimpse(combinedmetahetero)
-```
+
 # Steps 2&3
-```{r}
+
 metacombohetero <- combinedmetahetero
@@
 
-```
 # **Clean-up and rename
-```{r}
+
 metacombohetero <- metacombohetero[, c(1:7, 43:45)] 
@@
 
-```
-
-```{r}
 #write.csv(metacombohetero, "metacombohetero.csv")
@@
 ```{r}
-glimpse(metacombohetero)
+#glimpse(metacombohetero)
 
@@
 ####################################################################################################################################
-# *PLOTS
-
-# **Restructure data for plotting 
+## Heterogeneity PLOTS
+
+Restructure data for plotting 
 ```{r}
@@
 
-# *Plot FIGURE 4 (Second-order meta analysis on heterogeneity)
-
-# **Plot Fig4 all traits
+## *Plot FIGURE 4 (Second-order meta analysis on heterogeneity)
+
+Plot Fig4 all traits
 ```{r}
@@
 ```
-
-########

### 2019-08-21 scripts/2019_July_IMPC variance and sex difference.Rmd
update

@@
 author: "Susanne & Felix Zajitschek"
-date: "July 2019"
+date: "August 2019"
 output:
@@
     code_folding: hide
-    toc: true
-    toc_float: true
-    toc_depth: 3
+    toc: yes
+    toc_depth: 4
+    toc_float: yes
   html_notebook:
     toc: yes
-#runtime: shiny
+  pdf_document:
+    toc: yes
+    toc_depth: '4'
 ---
@@
 
-# Packages
+## Set up
+### Packages
 
@@
 
-# Loading functions that are necessary
-### Preparation of raw data
+### Loading functions that are necessary
+#### Preparation of raw data
 1) Data loading and cleaning of the csv file
@@
 
-## Functions for preparing the data for meta analyses
+#### Functions for preparing the data for meta analyses
 3) "Population statistics"
@@
 getwd()
-data1 <- readRDS("/export/data_clean.rds") 
+data1 <- readRDS("../export/data_clean.rds") 
 #data1 
@@
 
-## Preparation for Meta analysis
-### Define population variable & add grouping variables
+## Meta analysis, Phase 1
+### Preparation
+#### Define population variable & add grouping variables
 
@@
 
- group <- read.csv("/export/ParameterGrouping.csv") 
+ group <- read.csv("../export/ParameterGrouping.csv") 
  data <- data3
@@
 
-### Assign each unique parameter_name (=trait,use trait variable) a unique number ('id')
+#### Assign each unique parameter_name (=trait,use trait variable) a unique number ('id')
 We add a new variable, where redundant traits are combined
@@
 
-### Create a matrix to store results for all traits
+#### Create a matrix to store results for all traits
 As the current version of this script utilizes a loop instead of tidyR code, it is here necessary to create an empty matrix, in which the returning values will be stored.
@@
 
-## LOOP, to run meta-analysis on all traits
+### LOOP, to run meta-analysis on all traits
 The loop combines the functions mentioned above and fills the data matrix with results from our meta analysis. 
@@
 ```{r}
-procedures <- read.csv("/export/procedures.csv")
+procedures <- read.csv("../export/procedures.csv")
 
@@
 
-## Dealing with Correlated Parameters
+## Meta-analysis, Phase 2
+### Dealing with Correlated Parameters, preparation
 
@@
 
-### Collapsing correlated parameters
+#### Collapsing and merging correlated parameters
 
@@
 
-### Count of number of parameter names (correlated sub-traits) in each parameter group (par_group_size) 
+#### Count of number of parameter names (correlated sub-traits) in each parameter group (par_group_size) 
 This serves to identify and separate the traits that are correlated from the full dataset that can be processed as is.
@@
 ```
-
-# Preparation for Visualization and Meta-analysis
 
@@
 
-### Extract and save parameter estimates 
+#### Extract and save parameter estimates 
 Function to collect the outcomes of the "mini" meta analysis
@@
 
-### Clean-up and rename 
+#### Clean-up and rename 
 ```{r}
@@
 
-trait_meta_results <- write.csv(metacombo, file = "/export/trait_meta_results.csv")
-```
-
-## Last step: meta-meta-analysis 
-### Perform meta-analyses (3 for each of the 9 grouping terms: lnCVR, lnVR, lnRR) 
+#trait_meta_results <- write.csv(metacombo, file = "export/trait_meta_results.csv")
+```
+
+## Meta-analysis, Phase 3
+#### Perform meta-analyses (3 for each of the 9 grouping terms: lnCVR, lnVR, lnRR) 
 This is the full result dataset
@@
 
-### Prepare data
+#### Prepare data
 Nesting, calculating the number of parameters within each grouping term, and running the meta-analysis
@@
 
-# PLOTS
-
-## Plot FIGURE 2 (First-order meta analysis results)
+### Visualisation
+
+#### Plot FIGURE 2 [4 in ms] (First-order meta analysis results)
 
@@
 
-### Prepare data for traits with CI not overlapping 0
+#### Prepare data for traits with CI not overlapping 0
 create column with 1= different from zero, 0= zero included in CI
@@
 ```
-### Create final combined Figure (Figure 2)
-```{r}
-
-Fig2 <- ggarrange(malebias_Fig2_alltraits, malebias_Fig2_sigtraits,malebias_Fig2_over10, nrow = 3, align = "v", heights = c(1.22,1,1))
+#### Create final combined Figure (Figure 2)
+```{r}
+
+Fig2 <- ggarrange(malebias_Fig2_alltraits, malebias_Fig2_sigtraits,malebias_Fig2_over10, nrow = 3, align = "v", heights = c(1.22,1,1), labels = c("A", "B", "C"))
 Fig2
-#ggsave("Fig2.pdf", plot = Fig2, width = 6, height = 5) 
-```
-
-## Preparation, for Figure 3: Overall results of second order meta anlaysis
-### Restructure data for plotting 
+ggsave("Fig2.pdf", plot = Fig2, width = 6, height = 5) 
+```
+
+###  Overall results of second order meta anlaysis (Figure 4a)
+#### Restructure data for plotting 
 Data are restructured, and grouping terms are being re-ordered
@@
 
-### Plot FIGURE 3 (Second-order meta analysis results)
+#### Plot FIGURE 4 (Second-order meta analysis results)
 
@@
 
-### Prepare data for traits with CI not overlapping 0
+#### Figure 4B:  Prepare data for traits with CI not overlapping 0
 
@@
 #######################
-### Female Figure
+#### Female Figure, significant traits
 Female Fig3 sig
@@
 
-### Plot Fig3 all significant results (CI not overlapping zero, female )
+Plot Fig3 all significant results (CI not overlapping zero, female )
 ```{r}
@@
 
-### Fig3 >10%
+#### Fig4 C >10%
 
@@
 
-### Male Fig 3 > 10% (male biased traits)
+#### Male Fig 3 > 10% (male biased traits)
 ```{r}
@@
 	lnRR_upper =map_dbl(model_lnRR, pluck(7)), lnRR_se =map_dbl(model_lnRR, pluck(3))) )[, c(1,4:7)] 
-add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.male.meta.RR.perc.b))
+add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% 
+  setNames(names(plot3.male.meta.RR.perc.b))
 plot3.male.meta.RR.perc.b <- rbind(plot3.male.meta.RR.perc.b, add.row.hearing)
+
+add.row.eye <- as.data.frame(t(c("Eye", NA, NA, NA, NA))) %>% 
+  setNames(names(plot3.male.meta.RR.perc.b))
+plot3.male.meta.RR.perc.b <- rbind(plot3.male.meta.RR.perc.b, add.row.eye)
+
 plot3.male.meta.RR.perc.b <- plot3.male.meta.RR.perc.b[order(plot3.male.meta.RR.perc.b$GroupingTerm),]
@@
 
-Metameta_Fig3_male.perc <- overall4.male.perc %>% filter(., GroupingTerm != "Hearing") %>%
+Metameta_Fig3_male.perc <- overall4.male.perc %>% #filter(., GroupingTerm != "Hearing") %>%
   ggplot(aes(y= GroupingTerm, x= value)) +
@@
 plot3.meta.RR.perc.b <- rbind(plot3.meta.RR.perc.b, add.row.hearing) 
+add.row.hematology <- as.data.frame(t(c("Hematology", NA, NA, NA, NA))) %>% 
+  setNames(names(plot3.meta.RR.perc.b))
+plot3.meta.RR.perc.b <- rbind(plot3.meta.RR.perc.b, add.row.hematology)
+
 plot3.meta.RR.perc.b <- plot3.meta.RR.perc.b[order(plot3.meta.RR.perc.b$GroupingTerm),]
@@
 
-### Restructure data for plotting
+#### Restructure data for plotting
 Female bias, 10 percent difference
@@
 
-# Plot Fig3 all plots combined
+#### Plot Fig3 all plots combined
 ```{r}
@@
 
-# Heterogeneity
-## FIGURE 4 (Second-order meta analysis on heterogeneity)
-### Create matrix to store results for all traits
+### Heterogeneity
+#### FIGURE 4 (Second-order meta analysis on heterogeneity)
+#### Create matrix to store results for all traits
 ```{r}
@@
 
-## LOOP
-parameters to extract from metafor (sigma2's, s.nlevels)
+#### LOOP
+Parameters to extract from metafor (sigma2's, s.nlevels)
 
@@
 for(t in 1:n) {
-
   tryCatch({
@@
 
-### Exclude traits
+#### Exclude traits
 ```{r}
@@
 ```{r}
-#procedures <- read.csv("procedures.csv")
+#procedures <- read.csv("../procedures.csv")
 
@@
 
-### Dealing with correlated parameters
+#### Dealing with correlated parameters
 ```{r}
@@
 ## **Extract and save parameter estimates
-```{r}
+
 count_fun. <- function(mod_sub)
@@
 robu_all. <- full_join(robusub_CVR., robusub_VR.) %>% full_join(., robusub_RR.)
-
-```
-
-### **Merge the two data sets (the new [robu_all] and the initial [uncorrelated sub-traits with count = 1]) 
+```
+
+#### Merge the two data sets (the new [robu_all.] and the initial [uncorrelated sub-traits with count = 1])
 In this step, we 	
-1) put the N from robumeta and the  N from metafor (s.nlevels.error) together into the same columns (N.RR, N.VR, N.CVR)
-
-2) calculate the total variance for metafor models as the sum of random effect variances and the residual error,
-							then put them in the same columns together with the residual variances from robumeta
+1) merge the N from robumeta and the  N from metafor (s.nlevels.error) together into the same columns (N.RR, N.VR, N.CVR)
+2) calculate the total variance for metafor models as the sum of random effect variances and the residual error, then add in the same columns together with the residual variances from robumeta
 ```{r}
@@
 metahetero_all$N.VR <- metahetero_all$s.nlevels.error.VR 
-
-# log (srt( of the data to look at))
 metahetero_all$var.RR <- log(sqrt(metahetero_all$sigma2_strain.RR + metahetero_all$sigma2_center.RR + metahetero_all$sigma2_error.RR))
@@
 
-#adjust the -inf to smallest number in dataset
 metahetero_all <- metahetero_all %>% mutate(var.RR = if_else(var.RR == -Inf, -7 ,var.RR),
@@
 # **Combine data 
-# Step1
-
+## Step1 
 combinedmetahetero <- bind_rows(robu_all., metahetero_all)
@@
 names(metacombohetero)[10] <- "GroupingTerm" 
-
-#write.csv(metacombohetero, "metacombohetero.csv")
-
-```
-
-## *Last step: meta-meta-analysis of heterogeneity
-```{r}
-#glimpse(metacombohetero)
-
+```
+
+#### Last step: meta-meta-analysis of heterogeneity
+```{r}
 ## *Perform meta-meta-analysis (3 for each of the 9 grouping terms: var.CVR, var.VR, var.RR)
@@
 
-# **Calculate number of parameters per grouping term : not needed; delete in final version
-#metacombo_final <- metacombo_final  %>%  mutate(para_per_GroupingTerm = map_dbl(data, nrow))
-
 # **Final fixed effects meta-analyses within grouping terms, with SE of the estimate
-# Shinichi: meta-analyses on heterogeneity, using  sei as below, in metafor formula
+
+metacombohetero$var.CVR
 
@@
 #str(heterog2)
-
-```
-
-####################################################################################################################################
-## Heterogeneity PLOTS
-
+```
+
+#### Heterogeneity PLOTS
 Restructure data for plotting 
@@
 
-## *Plot FIGURE 4 (Second-order meta analysis on heterogeneity)
+#### Plot FIGURE 4 (5 in ms) (Second-order meta analysis on heterogeneity)
 

### 2019-08-21 SexDifference_Shiny/app.R

@@ -1,10 +1,13 @@
 
+
 library(shiny)
 
-meta_results <- read.csv("trait_meta_results.csv")
+meta_results <- read.csv("../SexDifference_Shiny/trait_meta_results.csv")
 
 
-ui <- fluidPage(mainPanel(shinythemes::themeSelector()),
+
+
+ui <- fluidPage(mainPanel(shinythemes::themeSelector(default)),
     # Application title
     titlePanel("Trait Specific Percentage Differences in Mean and Variances between the Sexes"),
     

### 2019-11-06 Prep & old/prep and old- scrrpts/2018.07.03-bodyweight_analysis_WillDan.Rmd
rearrange

---
title: "Prototype for analysis of body weight"
author: "Will Cornwell & Dan Noble"
date: "03/07/2018"
output: 
  html_document:
    code_folding: show
    theme: yeti
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: false
      smooth_scroll: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE, echo=TRUE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE, cache=FALSE)
knitr::opts_knit$set(root.dir =  rprojroot::find_root("README.md"))
```

Packages

```{r}
#devtools::install_github("thomasp85/patchwork") # Make sure to download first in a new R session
#install.packages("gridExtra")
library(gridExtra)
library(ggplot2)
library(tidyverse)
```

Bring in data, Subset data based on body weight

```{r}
data <- readRDS("export/data_clean.rds") 
bw <- data%>%
  filter(parameter_name=="body weight")
```

Check first whether weight and data_point column match

```{r}
any(bw$weight == bw$data_point)
```

Subset the data to get between 100 & 300 days

```{r}
bw_100_300 <- subset(bw, age_in_days > 98 & age_in_days <300)
```

PLot and see what the distribution looks like

```{r}
ggplot(bw_100_300, aes(x=data_point, fill = sex)) + geom_density(alpha = 0.5)
```

Function for cutting data into age bins and then calculating SD and CV for each sex and strain

```{r}
sd_bin <- function(data, bins, strains){
	data$cut_age <- cut(data$age_in_days, bins)
	sd <- data %>% 
	  filter(strain_name %in% strains) %>% 
	  group_by(sex, cut_age, strain_name) %>% 
	  summarise(sd = sd(data_point), cv = sd(data_point) / mean(data_point), n = n())

	return(sd)
}
```

Generate a new dataset containing SD and CV for the following three strains using the full data set so we don't restrict age.

```{r}
age_sd <- sd_bin(data, 10, strains = c("C57BL/6N", "C57BL/6NTac", "C57BL/6NJ"))
```
Check data

```{r}
print(arrange(age_sd, strain_name), n = 30)
```

Simple plot

```{r}
ggplot(age_sd, aes(x=cut_age, y=cv, col = sex)) + geom_point() + facet_grid(~strain_name) + theme_classic()
```

Main plot: PLOT THIS

(**Daniel ahs no idea why these aren't showing up**)

```{r}
p1 <- ggplot(bw, aes(x=age_in_days, y=data_point, col = sex)) + geom_point(alpha = 0.5) + labs(x = "Age (days)", y = "Body weight")

p2 <- ggplot(age_sd, aes(x=cut_age, y=sd, col = sex)) + geom_point(size=2) + facet_grid(~strain_name) + theme_bw() + theme(axis.text.x=element_text(size=rel(0.4))) + labs(x = "Age bin", y = "SD") 
```

```{r}
print(p1)

print(p2)
```

```{r, eval=FALSE}
grid.arrange(p1, p2)
```

## Simulating a power analysis - didn't get far with this....

Get standard deviation in two groups

```{r}
sd <- bw_100_300 %>% group_by(sex) %>% summarise(sd = sd(data_point))
mean <- bw_100_300 %>% group_by(sex) %>% summarise(mean = mean(data_point))
```

Sample sizes

```{r}
n <- c(5, 10, 20, 30)
```

Means of males and females for a trait

```{r}
m_male   <- as.numeric(mean[mean$sex == "male", "mean"])
m_female <- as.numeric(mean[mean$sex == "female", "mean"])
```
SD of males and females for a trait

```{r}
sd_male   <- as.numeric(sd[sd$sex == "male", "sd"])
sd_female <- as.numeric(sd[sd$sex == "female", "sd"])
#pwr.t2n.test
```

### 2019-11-06 Prep & old/prep and old- scrrpts/2018.07.03-meta_analysis_prototype.Rmd
rearrange

--- 2018-09-18 scripts/2018.09.19-meta_analysis_prototype.Rmd
@@
 title: "Protoype for metaanalysis"
-author: "Daniel Falster & Alistair Senior + Shinichi messing things up"
+author: "Daniel Falster & Alistair Senior"
 date: "03/07/2018"

### 2019-11-06 Prep & old/prep and old- scrrpts/2018.08.28-Overview.Rmd
rearrange

--- 2018-08-03 Overview.Rmd
@@
 ```{r setup, include=FALSE, echo=TRUE}
-knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
+knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE, cache=FALSE)
+root.dir = rprojroot::find_root("README.md")
+knitr::opts_knit$set(root.dir = root.dir)
+```
+
+```{r}
 library(readr)
@@
 library(knitr)
+library(pander)
 library(kableExtra)
+source("R/data_load_clean.R")
 ```
 
-Here is an initial exploration of the mouse data we are working on.
+# Loading data
 
-The data is big, but not so large that we can't use our standard tools on a desktop.
-I'd suggest using packages from the [tidyverse](https://www.tidyverse.org/) family, in particular `readr`, `dplyr`, `ggplot2`, `skimr`, `scales`, `viridis`.
+Read in cleaned data, specifying variable types:
 
-#  Dataset overview
+```{r}
+data <- readRDS("export/data_clean.rds")
+```
 
-Read in data, specifying variable types:
+Note: cleaned data were generated by running
 
-```{r cars}
-data_raw <- read_csv("data/dr7.0_all_control_data.csv", 
-                  col_types = cols(
-                      .default = col_character(),
-                      project_id = col_character(),
-                      id = col_character(),
-                      parameter_id = col_character(),
-                      age_in_days = col_integer(),
-                      date_of_experiment = col_datetime(format = ""),
-                      weight = col_double(),
-                      phenotyping_center_id = col_character(),
-                      production_center_id = col_character(),
-                      weight_date = col_datetime(format = ""),
-                      date_of_birth = col_datetime(format = ""),
-                      procedure_id = col_character(),
-                      pipeline_id = col_character(),
-                      biological_sample_id = col_character(),
-                      biological_model_id = col_character(),
-                      weight_days_old = col_integer(),
-                      datasource_id = col_character(),
-                      experiment_id = col_character(),
-                      data_point = col_double(),
-                      age_in_weeks = col_integer(),
-                      `_version_` = col_character()
-                      )
-                )
+```{r, eval=FALSE}
+data <- load_raw("data/dr7.0_all_control_data.csv") %>% clean_raw_data()
 ```
+
+where using the follwing function
+```{r}
+clean_raw_data
+```
+
+# Data overview
 
@@
 ```{r}
-data_raw %>% dim()
-```
-
-Of the `r data %>% names() %>% length()` variables in the dataset, lots of variables are full of NAs:
-
-```{r}
-n_records <- data_raw %>% nrow()
-NA_count <- data_raw %>%
-  summarise_all(funs(sum(is.na(.))/n_records*100)) %>% 
-  unlist() %>% sort(decreasing=TRUE) %>%
-  tibble(variable=names(.), percent_NA = .)
-
-# make a plot
-ggplot(NA_count, aes(percent_NA)) + geom_histogram(bins=50)
-```
-
-Let's remove those variables that have all NAs:
-
-```{r}
-(all_NAs <- NA_count$variable[NA_count$percent_NA == 100])
-data <- data_raw %>% select(-one_of(all_NAs))
+data %>% dim()
 ```
@@
 x 
+```
+
+# Strains
+
+There are several strains under the variable `strain_name`:
+
+```{r}
+data$strain_name %>% unique() %>% length()
+```
+
+```{r}
+data$strain_name %>% table() %>% sort(decreasing = TRUE) %>%
+  tibble(variable=names(.), count = .) %>%
+  kable() %>%
+  kable_styling() %>%
+  scroll_box(width = "100%", height = "500px")
+```
+
+There is also a variable  several strains under the variable `strain_accession_id`:
+
+```{r}
+data$strain_accession_id %>% unique() %>% length()
+```
+
+```{r}
+data$strain_accession_id %>% table() %>% sort(decreasing = TRUE) %>%
+  tibble(variable=names(.), count = .) %>%
+  kable() %>%
+  kable_styling() %>%
+  scroll_box(width = "100%", height = "500px")
 ```
@@
 ```{r}
-select(filter(data, biological_sample_id == "107609"), sex, production_center, project_name, biological_sample_id, age_in_days, weight, parameter_name) %>% arrange(age_in_days) %>% data.frame()
+select(filter(data, biological_sample_id == "107609"), sex, production_center, biological_sample_id, age_in_days, weight, parameter_name) %>% arrange(age_in_days) %>% data.frame()
 ```
-
-```{r}
-
-data_i <- data %>% 
-  filter(parameter_name == "Body weight") %>%
-  group_by(biological_sample_id) %>% 
-  summarise(
-    production_center = production_center[1],
-    project_name = project_name[1],
-    sex = sex[1],
-    n = n(),
-    med_age= median(age_in_days)
-    )
-
-data_i
-```
-
-# Issues:
-
-1.  `procedure_name` are values eding in `(GMC)` different?
-2. Spelling / case differences: e.g. `Body weight` vs `Body Weight`

### 2019-11-06 Prep & old/prep and old- scrrpts/2019.01.17collapsing parameter_names to parameter_groups.Rmd
rearrange

17 /01/2018

```{r}
library(readr)
library(dplyr)
library(metafor)
library(devtools)
library(patchwork)
library(purrr)
library(tidyverse)
library(tibble)
```

##  test for meta-meta-analysis / collapse confounded parameters!

```{r}
meta1 <- read.csv("meta.csv") # cleaned up data/ cleaned up parameter groups. 
unique(meta1$procedure) #19. Can still get reduced.
unique(meta1$GroupingTerm) #10. sounds reasonable
unique(meta1$parameter_group) # 152 levels. To be used as random factor in meta-meta!
```

```{r meta-meta}
# use meta1 , newly loaded (as has been cleaned / checked in excel)

# need to write function to collapse the correlated parametrs down (based on parameter_groups).  For the parameter_groups that are represented more than 1, run meta analysis, the other traits stay as are.  rma(yi = estimate i.e. ln RR / ln CVR / ln VR, se = lnRR_se / lnCVR_se / lnVR_se, method = "FE" )

meta1[,"MetaMeanV"] <-meta1$lnRR_se^2
meta1[,"MetaCVRV"] <-meta1$lnCVR_se^2
meta1[,"MetaVRV"] <-meta1$lnVR_se^2
```

workflow:
count parameter_names per parameter_group, save in new list "par_group_size":
```{r}
meta1 %>%  count(parameter_group)
```
dataframe: most groups have only 1 , it;s only a couple where there's multiple parameter names.

```{r}
meta1b <-
  meta1 %>%
  group_by(parameter_group) %>% 
  summarize(par_group_size = length(unique(parameter_name, na.rm = TRUE)))
#this gives me a summary of number of parameter names in each parameter group, now I neeed to merge it back together

meta1$par_group_size <- meta1b$par_group_size[match(meta1$parameter_group, meta1b$parameter_group)]

```

create subsets: needs to use those that have more than 1 count (par_group_size)

```{r}
meta1_sub<-subset(meta1,par_group_size >1) # 86 observations
```

NEST
```{r}
n_count <- meta1_sub %>% 
  group_by(parameter_group) %>% 
  nest()
```

FIXED EFFECTS MODEL

```{r}
sub_model <- n_count %>%
  mutate(model= map(data, ~ rma(yi = lnRR, sei = lnRR_se, method = "FE", data= .)))
```

 unknot this somehow

 THIS IS NOT WORKING
```{r}

b_fun <- function(mod_sub)
  coefficients(mod_sub[[1]])

sub_model %>% transmute(parameter_group, estimate = map(model, b_fun))

```

### 2019-11-06 Prep & old/prep and old- scrrpts/data_load_clean2.R

@@ -1,0 +1,85 @@
+
+# loads the raw data, setting some default types for various columns
+
+load_raw <- function(filename) {
+  read_csv(filename, 
+                              col_types = cols(
+                                .default = col_character(),
+                                project_id = col_character(),
+                                id = col_character(),
+                                parameter_id = col_character(),
+                                age_in_days = col_integer(),
+                                date_of_experiment = col_datetime(format = ""),
+                                weight = col_double(),
+                                phenotyping_center_id = col_character(),
+                                production_center_id = col_character(),
+                                weight_date = col_datetime(format = ""),
+                                date_of_birth = col_datetime(format = ""),
+                                procedure_id = col_character(),
+                                pipeline_id = col_character(),
+                                biological_sample_id = col_character(),
+                                biological_model_id = col_character(),
+                                weight_days_old = col_integer(),
+                                datasource_id = col_character(),
+                                experiment_id = col_character(),
+                                data_point = col_double(),
+                                age_in_weeks = col_integer(),
+                                `_version_` = col_character()
+                              )
+  )
+}
+
+# Apply some standard cleaning to the data
+clean_raw_data <- function(mydata) {
+  mydata %>% 
+    
+    # Fileter to IMPC source (recommened by Jeremey in email to Susi on 20 Aug 2018)
+    filter(datasource_name == 'IMPC') %>%
+    
+    # standardise trait names
+    mutate(parameter_name = tolower(parameter_name) ) %>%
+    
+    # remove extreme ages
+    filter(age_in_days > 0 & age_in_days < 500) %>% 
+
+    # remove NAs 
+    filter(!is.na(data_point)) %>%
+  
+    # subset to reasonable set of variables
+    # date_of_experiment: Jeremy suggested using as an indicator of batch-level effects
+    select(production_center, strain_name, strain_accession_id, biological_sample_id, pipeline_stable_id, procedure_group, procedure_name, sex, date_of_experiment, age_in_days, weight, parameter_name, data_point) %>% 
+    arrange(production_center, biological_sample_id, age_in_days)
+}
+
+
+# subset data to select data for given parameter, and taking a single record per individual, choosing the record as close as possible to 
+# age_center
[…]

### 2019-11-06 Prep & old/prep and old- scrrpts/res_alltraits_FZ_4-10-2018.R

@@ -1,0 +1,141 @@
+
+# Felix laptop
+setwd("C:/Users/felix/OneDrive - UNSW/research UNSW/Project - mice sex power allometry 2018")
+
+library(readr)
+library(dplyr)
+library(metafor)
+
+#save in working directory
+source("meta_analysis.R")
+source("data_load_clean2.R") #attention: check version version
+source("calc_pop_stats.R")
+
+
+# Prepare data 
+
+# Load raw data - save cleaned dataset as RDS for reuse
+#data_raw <- load_raw("data/dr7.0_all_control_data.csv") %>%
+#    clean_raw_data()
+#dir.create("export", F, F)
+#saveRDS(data_raw, "export/data_clean.rds")
+
+data1 <- readRDS("export/data_clean.rds")
+
+# CLEAN DATA: select traits with at least 2 centers
+dat1 <-
+  data1 %>%
+  group_by(parameter_name) %>%
+  summarize(center_per_trait = length(unique(production_center, na.rm = TRUE)))
+#dat1$center_per_trait
+
+dat2 <- merge(data1, dat1) #sollte auch im grossen Datensatz so funktionieren, also ohne die uebereinstimmende Variable (trait) anzugeben
+dat_moreThan1center <-
+  dat2  %>%
+  filter(center_per_trait >= 2)
+
+data2 <- dat_moreThan1center
+min(data2$center_per_trait) #=2;ok!
+
+# Define population variable
+data3 <- data2 %>%
+mutate(population = sprintf("%s-%s", production_center, strain_name))
+
+# Assign each unique parameter_name (=trait) a unique number ('id')
+data <- transform(data3, id = match(parameter_name, unique(parameter_name)))
+tail(data)
+n <- length(unique(data$id)) #=1:232 = 232 unique traits
+
+#############################################################################################################################################
+
+# Create matrix to store results for all traits
+results.alltraits <- as.data.frame(cbind(c(1:n), matrix(rep(0, n*9), ncol = 9))) #number of individual results per trait = 9
+names(results.alltraits) <- c("id", "CVR", "CVR_lower", "CVR_upper", "CV", "CV_lower", "CV_upper", "mean", "mean_lower", "mean_upper")
+
+# LOOP
+
+for(i in 1:n) {
+
+tryCatch({
+
[…]

### 2019-11-06 scripts/prep and old/data_load_clean2.R
del

@@ -1,85 +1,0 @@
-
-# loads the raw data, setting some default types for various columns
-
-load_raw <- function(filename) {
-  read_csv(filename, 
-                              col_types = cols(
-                                .default = col_character(),
-                                project_id = col_character(),
-                                id = col_character(),
-                                parameter_id = col_character(),
-                                age_in_days = col_integer(),
-                                date_of_experiment = col_datetime(format = ""),
-                                weight = col_double(),
-                                phenotyping_center_id = col_character(),
-                                production_center_id = col_character(),
-                                weight_date = col_datetime(format = ""),
-                                date_of_birth = col_datetime(format = ""),
-                                procedure_id = col_character(),
-                                pipeline_id = col_character(),
-                                biological_sample_id = col_character(),
-                                biological_model_id = col_character(),
-                                weight_days_old = col_integer(),
-                                datasource_id = col_character(),
-                                experiment_id = col_character(),
-                                data_point = col_double(),
-                                age_in_weeks = col_integer(),
-                                `_version_` = col_character()
-                              )
-  )
-}
-
-# Apply some standard cleaning to the data
-clean_raw_data <- function(mydata) {
-  mydata %>% 
-    
-    # Fileter to IMPC source (recommened by Jeremey in email to Susi on 20 Aug 2018)
-    filter(datasource_name == 'IMPC') %>%
-    
-    # standardise trait names
-    mutate(parameter_name = tolower(parameter_name) ) %>%
-    
-    # remove extreme ages
-    filter(age_in_days > 0 & age_in_days < 500) %>% 
-
-    # remove NAs 
-    filter(!is.na(data_point)) %>%
-  
-    # subset to reasonable set of variables
-    # date_of_experiment: Jeremy suggested using as an indicator of batch-level effects
-    select(production_center, strain_name, strain_accession_id, biological_sample_id, pipeline_stable_id, procedure_group, procedure_name, sex, date_of_experiment, age_in_days, weight, parameter_name, data_point) %>% 
-    arrange(production_center, biological_sample_id, age_in_days)
-}
-
-
-# subset data to select data for given parameter, and taking a single record per individual, choosing the record as close as possible to 
-# age_center
[…]

### 2019-11-06 scripts/prep and old/res_alltraits_FZ_4-10-2018.R

@@ -1,141 +1,0 @@
-
-# Felix laptop
-setwd("C:/Users/felix/OneDrive - UNSW/research UNSW/Project - mice sex power allometry 2018")
-
-library(readr)
-library(dplyr)
-library(metafor)
-
-#save in working directory
-source("meta_analysis.R")
-source("data_load_clean2.R") #attention: check version version
-source("calc_pop_stats.R")
-
-
-# Prepare data 
-
-# Load raw data - save cleaned dataset as RDS for reuse
-#data_raw <- load_raw("data/dr7.0_all_control_data.csv") %>%
-#    clean_raw_data()
-#dir.create("export", F, F)
-#saveRDS(data_raw, "export/data_clean.rds")
-
-data1 <- readRDS("export/data_clean.rds")
-
-# CLEAN DATA: select traits with at least 2 centers
-dat1 <-
-  data1 %>%
-  group_by(parameter_name) %>%
-  summarize(center_per_trait = length(unique(production_center, na.rm = TRUE)))
-#dat1$center_per_trait
-
-dat2 <- merge(data1, dat1) #sollte auch im grossen Datensatz so funktionieren, also ohne die uebereinstimmende Variable (trait) anzugeben
-dat_moreThan1center <-
-  dat2  %>%
-  filter(center_per_trait >= 2)
-
-data2 <- dat_moreThan1center
-min(data2$center_per_trait) #=2;ok!
-
-# Define population variable
-data3 <- data2 %>%
-mutate(population = sprintf("%s-%s", production_center, strain_name))
-
-# Assign each unique parameter_name (=trait) a unique number ('id')
-data <- transform(data3, id = match(parameter_name, unique(parameter_name)))
-tail(data)
-n <- length(unique(data$id)) #=1:232 = 232 unique traits
-
-#############################################################################################################################################
-
-# Create matrix to store results for all traits
-results.alltraits <- as.data.frame(cbind(c(1:n), matrix(rep(0, n*9), ncol = 9))) #number of individual results per trait = 9
-names(results.alltraits) <- c("id", "CVR", "CVR_lower", "CVR_upper", "CV", "CV_lower", "CV_upper", "mean", "mean_lower", "mean_upper")
-
-# LOOP
-
-for(i in 1:n) {
-
-tryCatch({
-
[…]

### 2019-11-06 Prep & old/prep and old- scripts/2019_Aug30-NO_VR_IMPC_variance_and_sex_difference.Rmd
Update Nov

--- 2019-08-21 scripts/2019_July_IMPC variance and sex difference.Rmd
@@
 title: "IMPC Mouse data - Variance in sex differences"
-author: "Susanne & Felix Zajitschek"
+author: "Susanne Zajitschek,  Felix Zajitschek, Russell Bonduriansky,Robert  Brooks, Will Cornwell, Daniel Falster, Malgortaza Lagisz, Jeremy Mason, Daniel Noble, Alistair Senior & Shinichi Nakagawa"
 date: "August 2019"
@@
   html_document:
+    code_download: true
     code_folding: hide
+    depth: 4
+    number_sections: no
+    theme:  flatly
     toc: yes
@@
     toc_depth: '4'
+subtitle: Electronic Supplementary Material
 ---
@@
                       warning = FALSE,
-                      message = FALSE)
+                      message = FALSE,
+                      cache = TRUE,
+                      tidy = TRUE)
 
@@
 ## Set up
-### Packages
+#### Packages
 
@@
 
-### Loading functions that are necessary
+### Loading functions 
+#### Functions for preparing the data for meta analyses
+1) "Population statistics"
+```{r}
+calculate_population_stats <- function(mydata, min_individuals = 5) {
+  mydata %>% 
+    group_by(population, strain_name, production_center, sex) %>% 
+    summarise(
+      trait = parameter_name[1],
+      x_bar = mean(data_point),
+      x_sd = sd(data_point),
+      n_ind = n()
+    ) %>% 
+    ungroup() %>%
+    filter(n_ind > min_individuals) %>% 
+    # Check both sexes present & filter those missing
+    group_by(population) %>% 
+    mutate(
+      n_sex = n_distinct(sex)
+    ) %>% 
+    ungroup() %>%
+    filter(n_sex ==2) %>% 
+    select(-n_sex) %>%
+    arrange(production_center, strain_name, population, sex)
+}
+```
+
+2) Extraction of effect sizes and sample variances
+```{r}
+create_meta_analysis_effect_sizes <- function(mydata) {
+  i <- seq(1, nrow(mydata), by = 2)
+  input <- data.frame(
+    n1i = mydata$n_ind[i],
+    n2i = mydata$n_ind[i + 1],
+    x1i = mydata$x_bar[i],
+    x2i = mydata$x_bar[i + 1],
+    sd1i = mydata$x_sd[i],
+    sd2i = mydata$x_sd[i + 1]
+  )
+
+  mydata[i,] %>% 
+  select(strain_name, production_center, trait) %>%
+    mutate(
+      effect_size_CVR = Calc.lnCVR(CMean = input$x1i, CSD = input$sd1i, CN = input$n1i, EMean = input$x2i, ESD = input$sd2i, EN = input$n2i),
+      sample_variance_CVR = Calc.var.lnCVR(CMean = input$x1i, CSD = input$sd1i, CN = input$n1i, EMean = input$x2i, ESD = input$sd2i, EN = input$n2i),
+      effect_size_VR = Calc.lnVR(CSD = input$sd1i, CN = input$n1i, ESD = input$sd2i, EN = input$n2i),
+      sample_variance_VR = Calc.var.lnVR(CN = input$n1i, EN = input$n2i),
+      effect_size_RR = Calc.lnRR(CMean = input$x1i, CSD = input$sd1i, CN = input$n1i, EMean = input$x2i, ESD = input$sd2i, EN = input$n2i),
+      sample_variance_RR = Calc.var.lnRR(CMean = input$x1i, CSD = input$sd1i, CN = input$n1i, EMean = input$x2i, ESD = input$sd2i, EN = input$n2i),
+      err = as.factor(seq_len(n()))
+    )
+
+}
+```
+
+3) Meta Analysis
+
+ Function to calculate meta-analysis statistics. Created by A M Senior @ the University of Otago NZ 03/01/2014
+
+Below are functions for calculating effect sizes for meta-analysis of variance. 
+All functions take the mean, sd and n from the control and experimental groups.
+
+The first function, Cal.lnCVR, calculates the the log response-ratio of the coefficient of variance (lnCVR) - see Nakagawa et al 2015.
+
+The second function calculates the measurement error variance for lnCVR. As well as the aforementioned parameters, this function also takes
+Equal.E.C.Corr (default = T), which must be True or False. If true, the function assumes that the correlation between mean and sd (Taylor's Law) 
+is equal for the mean and control groups, and, thus these data are pooled. If False the mean-SD correlation for the experimental and control groups
+are calculated separately from one another.
+
+Similar functions are then implemented for lnVR (for comparison of standard deviations) and ln RR  (for comparison of means)
+
+```{r}
+
+Calc.lnCVR <- function(CMean, CSD, CN, EMean, ESD, EN){
+  log(ESD) - log(EMean) + 1 / (2*(EN - 1)) - (log(CSD) - log(CMean) + 1 / (2*(CN - 1)))
+}
+
+Calc.var.lnCVR <- function(CMean, CSD, CN, EMean, ESD, EN, Equal.E.C.Corr=T) {
+  if(Equal.E.C.Corr==T){
+    mvcorr <- 0 #cor.test(log(c(CMean, EMean)), log(c(CSD, ESD)))$estimate   old, slightly incorrect
+    S2 <- CSD^2 / (CN * (CMean^2)) + 1 / (2 * (CN - 1)) - 2 * mvcorr * sqrt((CSD^2 / (CN * (CMean^2))) * (1 / (2 * (CN - 1)))) + ESD^2 / (EN * (EMean^2)) + 1 / (2 * (EN - 1)) - 2 * mvcorr * sqrt((ESD^2 / (EN * (EMean^2))) * (1 / (2 * (EN - 1))))
+  }
+  else{
+    Cmvcorr <- cor.test(log(CMean), log(CSD))$estimate
+    Emvcorr <- cor.test(log(EMean), (ESD))$estimate
+    S2 <- CSD^2 / (CN * (CMean^2)) + 1 / (2 * (CN - 1)) - 2 * Cmvcorr * sqrt((CSD^2 / (CN * (CMean^2))) * (1 / (2 * (CN - 1)))) + ESD^2 / (EN * (EMean^2)) + 1 / (2 * (EN - 1)) - 2 * Emvcorr * sqrt((ESD^2 / (EN * (EMean^2))) * (1 / (2 * (EN - 1))))
+  }
+  S2
+}
+
+Calc.lnVR <- function(CSD, CN, ESD, EN){
+  log(ESD) - log(CSD) + 1 / (2*(EN - 1)) - 1 / (2*(CN - 1))
+}
+
+Calc.var.lnVR <- function( CN,  EN) {
+  1 / (2*(EN - 1)) + 1 / (2*(CN - 1))
+}
+
+Calc.lnRR <- function(CMean, CSD, CN, EMean, ESD, EN) {
+  log(EMean) - log(CMean)
+}
+
+Calc.var.lnRR <- function(CMean, CSD, CN, EMean, ESD, EN) {
+  CSD^2/(CN * CMean^2) + ESD^2/(EN * EMean^2)
+}
+
+```
+
+## The dataset
+
+Having loaded the necessary functions, we can get started on the dataset.
+
+We here provide the cleaned dataset, which we have saved in a folder called "export", as easy starting point.
+However, the full dataset can be loaded and cleaned using the data cleaning function (Function 1 above), if "#" signs in the code below are removed  (created as that is much smaller than the .csv - which we can still provide for those who absolutely want to start from scratch?)
+
 #### Preparation of raw data
 1) Data loading and cleaning of the csv file
-This step we have already done and provide a cleaned up file which is less computing intensive. However, cvs
-```{r}
-
+This step we have already done and provide a cleaned up file which is less computing intensive. However, the cvs is provided in case this is pereferred to be attempted, following the steps below:
+
+```{r Raw Data, eval=FALSE, include=TRUE}
 # loads the raw data, setting some default types for various columns
@@
 }
-
-```
-
-2) Subsetting the data to choose only one datapoint per individual per trait
-```{r}
+```
+2) Subsetting the data to choose only one data point per individual per trait
+```{r}
+#2) Subsetting the data to choose only one data point per individual per trait
+
 # this is a necessary step for the loop across all traits 
@@
 
-#### Functions for preparing the data for meta analyses
-3) "Population statistics"
-```{r}
-calculate_population_stats <- function(mydata, min_individuals = 5) {
-  mydata %>% 
-    group_by(population, strain_name, production_center, sex) %>% 
-    summarise(
-      trait = parameter_name[1],
-      x_bar = mean(data_point),
-      x_sd = sd(data_point),
-      n_ind = n()
-    ) %>% 
-    ungroup() %>%
-    filter(n_ind > min_individuals) %>% 
-    # Check both sexes present & filter those missing
-    group_by(population) %>% 
-    mutate(
-      n_sex = n_distinct(sex)
-    ) %>% 
-    ungroup() %>%
-    filter(n_sex ==2) %>% 
-    select(-n_sex) %>%
-    arrange(production_center, strain_name, population, sex)
-}
-```
-
- 4) Extraction of effect sizes and sample variances
-```{r}
-create_meta_analysis_effect_sizes <- function(mydata) {
-  i <- seq(1, nrow(mydata), by = 2)
-  input <- data.frame(
-    n1i = mydata$n_ind[i],
-    n2i = mydata$n_ind[i + 1],
-    x1i = mydata$x_bar[i],
-    x2i = mydata$x_bar[i + 1],
-    sd1i = mydata$x_sd[i],
-    sd2i = mydata$x_sd[i + 1]
-  )
-
-  mydata[i,] %>% 
-  select(strain_name, production_center, trait) %>%
-    mutate(
-      effect_size_CVR = Calc.lnCVR(CMean = input$x1i, CSD = input$sd1i, CN = input$n1i, EMean = input$x2i, ESD = input$sd2i, EN = input$n2i),
-      sample_variance_CVR = Calc.var.lnCVR(CMean = input$x1i, CSD = input$sd1i, CN = input$n1i, EMean = input$x2i, ESD = input$sd2i, EN = input$n2i),
-      effect_size_VR = Calc.lnVR(CSD = input$sd1i, CN = input$n1i, ESD = input$sd2i, EN = input$n2i),
-      sample_variance_VR = Calc.var.lnVR(CN = input$n1i, EN = input$n2i),
-      effect_size_RR = Calc.lnRR(CMean = input$x1i, CSD = input$sd1i, CN = input$n1i, EMean = input$x2i, ESD = input$sd2i, EN = input$n2i),
-      sample_variance_RR = Calc.var.lnRR(CMean = input$x1i, CSD = input$sd1i, CN = input$n1i, EMean = input$x2i, ESD = input$sd2i, EN = input$n2i),
-      err = as.factor(seq_len(n()))
-    )
-
-}
-```
-
- 5) Meta Analysis
-
- Function to calculate meta-analysis statistics. Created by A M Senior @ the University of Otago NZ 03/01/2014
-
-Below are functions for calculating effect sizes for meta-analysis of variance. 
-All functions take the mean, sd and n from the control and experimental groups.
-
-The first function, Cal.lnCVR, calculates the the log response-ratio of the coefficient of variance (lnCVR) - see Nakagawa et al 2015.
-
-The second function calculates the measurement error variance for lnCVR. As well as the aforementioned parameters, this function also takes
-Equal.E.C.Corr (default = T), which must be True or False. If true, the function assumes that the correlation between mean and sd (Taylor's Law) 
-is equal for the mean and control groups, and, thus these data are pooled. If False the mean-SD correlation for the experimental and control groups
-are calculated separately from one another.
-
-Similar functions are then implemented for lnVR (for comparison of standard deviations) and ln RR  (for comparison of means)
-
-```{r}
-
-Calc.lnCVR <- function(CMean, CSD, CN, EMean, ESD, EN){
-  log(ESD) - log(EMean) + 1 / (2*(EN - 1)) - (log(CSD) - log(CMean) + 1 / (2*(CN - 1)))
-}
-
-Calc.var.lnCVR <- function(CMean, CSD, CN, EMean, ESD, EN, Equal.E.C.Corr=T) {
-  if(Equal.E.C.Corr==T){
-    mvcorr <- 0 #cor.test(log(c(CMean, EMean)), log(c(CSD, ESD)))$estimate   old, slightly incorrect
-    S2 <- CSD^2 / (CN * (CMean^2)) + 1 / (2 * (CN - 1)) - 2 * mvcorr * sqrt((CSD^2 / (CN * (CMean^2))) * (1 / (2 * (CN - 1)))) + ESD^2 / (EN * (EMean^2)) + 1 / (2 * (EN - 1)) - 2 * mvcorr * sqrt((ESD^2 / (EN * (EMean^2))) * (1 / (2 * (EN - 1))))
-  }
-  else{
-    Cmvcorr <- cor.test(log(CMean), log(CSD))$estimate
-    Emvcorr <- cor.test(log(EMean), (ESD))$estimate
-    S2 <- CSD^2 / (CN * (CMean^2)) + 1 / (2 * (CN - 1)) - 2 * Cmvcorr * sqrt((CSD^2 / (CN * (CMean^2))) * (1 / (2 * (CN - 1)))) + ESD^2 / (EN * (EMean^2)) + 1 / (2 * (EN - 1)) - 2 * Emvcorr * sqrt((ESD^2 / (EN * (EMean^2))) * (1 / (2 * (EN - 1))))
-  }
-  S2
-}
-
-Calc.lnVR <- function(CSD, CN, ESD, EN){
-  log(ESD) - log(CSD) + 1 / (2*(EN - 1)) - 1 / (2*(CN - 1))
-}
-
-Calc.var.lnVR <- function( CN,  EN) {
-  1 / (2*(EN - 1)) + 1 / (2*(CN - 1))
-}
-
-Calc.lnRR <- function(CMean, CSD, CN, EMean, ESD, EN) {
-  log(EMean) - log(CMean)
-}
-
-Calc.var.lnRR <- function(CMean, CSD, CN, EMean, ESD, EN) {
-  CSD^2/(CN * CMean^2) + ESD^2/(EN * EMean^2)
-}
-
-```
-
-Having loaded the necessary functions, we can get started on the dataset.
-
-We here provide the cleaned dataset, which we have saved in a folder called "export", as easy starting point.
-However, the full dataset can be loaded and cleaned using the data cleaning function (Function 1 above), if "#" signs in the code below are removed  (created as that is much smaller than the .csv - which we can still provide for those who absolutely want to start from scratch?)
+### Load data (raw / pre-clean)
+
 ```{r}
@@
 getwd()
-data1 <- readRDS("../export/data_clean.rds") 
+data1 <- readRDS("export/data_clean.rds") 
 #data1 
@@
 
-## Meta analysis, Phase 1
+## Meta analysis, Phase 1: across all traits
 ### Preparation
-#### Define population variable & add grouping variables
+####Define population variable 
+& add grouping variables
 
@@
 
- group <- read.csv("../export/ParameterGrouping.csv") 
+ group <- read.csv("export/ParameterGrouping.csv") 
  data <- data3
  data$parameterGroup <- group$parameter[match(data$parameter_name, group$parameter_name)] 
-
-```
-
-#### Assign each unique parameter_name (=trait,use trait variable) a unique number ('id')
+```
+
+#### Assign unique IDs (per trait)
+each unique parameter_name (=trait,use trait variable) gets a unique number ('id')
+
 We add a new variable, where redundant traits are combined
@@
 
-#### Create a matrix to store results for all traits
+#### Create matrix 
 As the current version of this script utilizes a loop instead of tidyR code, it is here necessary to create an empty matrix, in which the returning values will be stored.
@@
 
-### LOOP, to run meta-analysis on all traits
+#### Loop running meta-analysis on all traits
 The loop combines the functions mentioned above and fills the data matrix with results from our meta analysis. 
@@
 
-### Merging datasets
+#### Merging datasets & removal of non-converged traits
 
@@
 ```{r}
-procedures <- read.csv("../export/procedures.csv")
+procedures <- read.csv("export/procedures.csv")
 
@@
 removed <-length(unique(meta_clean$parameter_name)) #218
-```
-
-## Meta-analysis, Phase 2
+
+meta_problem <- results.alltraits.grouping[ (results.alltraits.grouping$id %in% c(84,144,158,160,161,162,163,165,166,167,168,221,222,231)), ]
+```
+
+## Meta-analysis, Phase 2: non-independent traits
 ### Dealing with Correlated Parameters, preparation
 
-This dataset contained a number of highly correlated traits, such as different kinds of cell counts (for example, hierarchical parametrization within immunological assays).
+This dataset contained a number of highly correlated traits, such as different kinds of cell counts (for example, hierarchical parameterization within immunological assays).
 As those data-points are not independent of each other,  we conducted a meta analyses on these correlated parameters to collapse the number of levels.
@@
 To be used as grouping factor for meta-meta analysis / collapsing down based on things that are classified identically in "parameter_group" but have different "parameter_name"
-length(unique(meta1$parameter_name)) #218
+#length(unique(meta1$parameter_name)) #218
 
@@
 #### Count of number of parameter names (correlated sub-traits) in each parameter group (par_group_size)
+
 This serves to identify and separate the traits that are correlated from the full dataset that can be processed as is.
@@
 
-### Perform meta-analyses on correlated sub-traits, using `robumeta` 
+#### Meta-analyses on correlated (sub-)traits, using robumeta` 
 The subset of the data is prepared (nested), and in this first step the model of the meta analysis effect sizes are calculated
@@
 model_count <- n_count %>% 
-  mutate(model_lnRR = map(data, ~ robu(.x$lnRR ~ 1, data= .x, studynum= .x$id, modelweights = c("CORR"), rho = 0.8, 
-                                                small = TRUE, var.eff.size= (.x$lnRR_se)^2 )),
-  model_lnVR = map(data, ~ robu(.x$lnVR ~ 1, data= .x, studynum= .x$id, modelweights = c("CORR"), rho = 0.8, 
-                                                small = TRUE, var.eff.size= (.x$lnVR_se)^2 )),
-  model_lnCVR = map(data, ~ robu(.x$lnCVR ~ 1, data= .x, studynum= .x$id, modelweights = c("CORR"), rho = 0.8, 
-                                                small = TRUE, var.eff.size= (.x$lnCVR_se)^2 ))) 
-```
-
-#### Extract and save parameter estimates 
+  mutate(model_lnRR = map(data, ~ robu(.x$lnRR ~ 1, data= .x, studynum= .x$id, modelweights = c("CORR"), rho = 0.8, small = TRUE, var.eff.size= (.x$lnRR_se)^2 )),
+  model_lnVR = map(data, ~ robu(.x$lnVR ~ 1, data= .x, studynum= .x$id, modelweights = c("CORR"), rho = 0.8, small = TRUE, var.eff.size= (.x$lnVR_se)^2 )),
+  model_lnCVR = map(data, ~ robu(.x$lnCVR ~ 1, data= .x, studynum= .x$id, modelweights = c("CORR"), rho = 0.8, small = TRUE, var.eff.size= (.x$lnCVR_se)^2 ))) 
+```
+
+Extract and save parameter estimates:
 Function to collect the outcomes of the "mini" meta analysis
@@
 
-Extraction of values created during Meta analysis using robu meta
+Extraction of values created during Meta analysis using robu meta:
 ```{r}
@@
 
-Combine data 
+#### Combine data 
 ```{r}
@@
 
-#### Clean-up and rename 
+ Clean-up and rename 
 ```{r}
@@
 
-## Meta-analysis, Phase 3
+## Meta-analysis, Phase 3: Second-order meta analysis for functional groups
 #### Perform meta-analyses (3 for each of the 9 grouping terms: lnCVR, lnVR, lnRR) 
@@
 
-### Visualisation
-
-#### Plot FIGURE 2 [4 in ms] (First-order meta analysis results)
+## Visualisation
+
+#### Plot:  FIGURE 2 [Figure 4 in ms] (First-order meta analysis results)
 
@@
 
-meta.plot2.all.b <- gather(meta.plot2.all, trait, value, c(lnCVR, lnVR, lnRR))
-
-meta.plot2.all.b$trait <- factor(meta.plot2.all.b$trait, levels =c("lnCVR","lnVR","lnRR") )
+meta.plot2.all.b <- gather(meta.plot2.all, trait, value, c(lnCVR,  lnRR)) #lnVR,
+
+meta.plot2.all.b$trait <- factor(meta.plot2.all.b$trait, levels =c("lnCVR","lnRR") )#"lnVR",
 
@@
 
-meta.plot2.sig.b <- meta.plot2.sig[, c("lnCVR", "lnVR", "lnRR", "lnCVRsig", "lnVRsig", "lnRRsig", "GroupingTerm")]
+meta.plot2.sig.b <- meta.plot2.sig[, c("lnCVR",  "lnRR", "lnCVRsig", "lnVRsig", "lnRRsig", "GroupingTerm")]   #"lnVR",
 
@@
 
-meta.plot2.sig.c$trait <- factor(meta.plot2.sig.c$trait, levels =c("lnCVR","lnVR","lnRR") )
+meta.plot2.sig.c$trait <- factor(meta.plot2.sig.c$trait, levels =c("lnCVR","lnRR") ) #"lnVR",
 
@@
 ```{r}
-meta.plot2.over10 <- meta_clean %>% select(lnCVR, lnVR, lnRR, GroupingTerm) %>% arrange(GroupingTerm)
-
-meta.plot2.over10.b <- gather(meta.plot2.over10, trait, value, c(lnCVR, lnVR, lnRR))
-
-meta.plot2.over10.b$trait <- factor(meta.plot2.over10.b$trait, levels =c("lnCVR","lnVR","lnRR") )
+meta.plot2.over10 <- meta_clean %>% select(lnCVR,  lnRR, GroupingTerm) %>% arrange(GroupingTerm) #lnVR,
+
+meta.plot2.over10.b <- gather(meta.plot2.over10, trait, value, c(lnCVR,  lnRR)) #lnVR,
+
+meta.plot2.over10.b$trait <- factor(meta.plot2.over10.b$trait, levels =c("lnCVR","lnRR") ) #"lnVR",
 
@@
 Fig2
-ggsave("Fig2.pdf", plot = Fig2, width = 6, height = 5) 
-```
-
-###  Overall results of second order meta anlaysis (Figure 4a)
+ggsave("CountDataCVR_RR_only.pdf", plot = Fig2, width = 6, height = 5) 
+```
+
+###  Overall results of second order meta analysis (Figure 4a)
 #### Restructure data for plotting 
@@
 ```{r}
-overall3 <- gather(overall2, parameter, value, c(lnCVR, lnVR, lnRR), factor_key= TRUE)
+overall3 <- gather(overall2, parameter, value, c(lnCVR,  lnRR), factor_key= TRUE) #lnVR,
 
 lnCVR.ci <- overall3 %>% filter(parameter == "lnCVR") %>% mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
-lnVR.ci <- overall3 %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
+#lnVR.ci <- overall3 %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
 lnRR.ci <- overall3 %>% filter(parameter == "lnRR") %>% mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
 
-overall4 <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
+overall4 <- bind_rows(lnCVR.ci,  lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high) #lnVR.ci,
 
@@
 #### Plot FIGURE 4 (Second-order meta analysis results)
-
 Preparation: Sub-Plot  for Figure 3: all traits
@@
 
-########
-
-#### Figure 4B:  Prepare data for traits with CI not overlapping 0
-
+#### Figure 4B- traits with CI not overlapping 0 
+Prepare data 
 create column with 1= different from zero, 0= zero included in CI
@@
 #Significant subset for lnVR
-metacombo_male.plot3.VR <- meta.male.plot3.sig %>%
- filter(sigVR == 1) %>%
- group_by(GroupingTerm) %>%
- nest()
-
-metacombo_male.plot3.VR.all <- meta.male.plot3.sig %>%
- filter(sigVR == 1) %>%
- nest()
+#metacombo_male.plot3.VR <- meta.male.plot3.sig %>%
+# filter(sigVR == 1) %>%
+# group_by(GroupingTerm) %>%
+# nest()
+
+#metacombo_male.plot3.VR.all <- meta.male.plot3.sig %>%
+ #filter(sigVR == 1) %>%
+ #nest()
 
@@
 
-plot3.male.meta.VR <- metacombo_male.plot3.VR %>% 
-  mutate(model_lnVR = map(data, ~ metafor::rma.uni(yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower)/ (2*1.96),  
-				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )
+#plot3.male.meta.VR <- metacombo_male.plot3.VR %>% 
+ # mutate(model_lnVR = map(data, ~ metafor::rma.uni(yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower)/ (2*1.96),  
+#				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )
 
@@
 
-plot3.male.meta.VR.all <- metacombo_male.plot3.VR.all %>% 
-  mutate(model_lnVR = map(data, ~ metafor::rma.uni(yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower)/ (2*1.96),  
-				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )
-
-plot3.male.meta.VR.all <- plot3.male.meta.VR.all %>% mutate(GroupingTerm = "All")
+#plot3.male.meta.VR.all <- metacombo_male.plot3.VR.all %>% 
+#  mutate(model_lnVR = map(data, ~ metafor::rma.uni(yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower)/ (2*1.96),  
+#				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )
+
+#plot3.male.meta.VR.all <- plot3.male.meta.VR.all %>% mutate(GroupingTerm = "All")
 
@@
 plot3.male.meta.CVR <- bind_rows(plot3.male.meta.CVR, plot3.male.meta.CVR.all)
-plot3.male.meta.VR <- bind_rows(plot3.male.meta.VR, plot3.male.meta.VR.all)
+#plot3.male.meta.VR <- bind_rows(plot3.male.meta.VR, plot3.male.meta.VR.all)
 plot3.male.meta.RR <- bind_rows(plot3.male.meta.RR, plot3.male.meta.RR.all)
@@
 
-plot3.male.meta.VR.b <- as.data.frame(plot3.male.meta.VR %>% group_by(GroupingTerm) %>%  
-	mutate(lnVR = map_dbl(model_lnVR, pluck(2)), lnVR_lower = map_dbl(model_lnVR, pluck(6)), 
-	lnVR_upper =map_dbl(model_lnVR, pluck(7)), lnVR_se =map_dbl(model_lnVR, pluck(3))) )[, c(1,4:7)] 
-plot3.male.meta.VR.b <- plot3.male.meta.VR.b[order(plot3.male.meta.VR.b$GroupingTerm),]
+#plot3.male.meta.VR.b <- as.data.frame(plot3.male.meta.VR %>% group_by(GroupingTerm) %>%  
+#	mutate(lnVR = map_dbl(model_lnVR, pluck(2)), lnVR_lower = map_dbl(model_lnVR, pluck(6)), 
+#	lnVR_upper =map_dbl(model_lnVR, pluck(7)), lnVR_se =map_dbl(model_lnVR, pluck(3))) )[, c(1,4:7)] 
+#plot3.male.meta.VR.b <- plot3.male.meta.VR.b[order(plot3.male.meta.VR.b$GroupingTerm),]
 
@@
 
-overall.male.plot3 <- inner_join(plot3.male.meta.CVR.b, plot3.male.meta.VR.b) 
-overall.male.plot3 <- inner_join(overall.male.plot3, plot3.male.meta.RR.b)
+#overall.male.plot3 <- full_join(plot3.male.meta.CVR.b, plot3.male.meta.VR.b) 
+overall.male.plot3 <- full_join(plot3.male.meta.CVR.b, plot3.male.meta.RR.b)
 
@@
 ```{r}
-overall3.male.sig <- gather(overall.male.plot3, parameter, value, c(lnCVR, lnVR, lnRR), factor_key= TRUE)
+overall3.male.sig <- gather(overall.male.plot3, parameter, value, c(lnCVR,  lnRR), factor_key= TRUE) #lnVR,
 
 lnCVR.ci <- overall3.male.sig  %>% filter(parameter == "lnCVR") %>% mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
-lnVR.ci <- overall3.male.sig  %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
+#lnVR.ci <- overall3.male.sig  %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
 lnRR.ci <- overall3.male.sig  %>% filter(parameter == "lnRR") %>% mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
 
-overall4.male.sig <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
+overall4.male.sig <- bind_rows(lnCVR.ci,  lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high) #lnVR.ci,
 
@@
 ```{r}
-######
 
@@
 
-#######################
 #### Female Figure, significant traits
@@
 ```{r}
-overall3.female.sig <- gather(overall.female.plot3, parameter, value, c(lnCVR, lnVR, lnRR), factor_key= TRUE)
+overall3.female.sig <- gather(overall.female.plot3, parameter, value, c(lnCVR,  lnRR), factor_key= TRUE) #lnVR,
 
 lnCVR.ci <- overall3.female.sig  %>% filter(parameter == "lnCVR") %>% mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
-lnVR.ci <- overall3.female.sig  %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
+#lnVR.ci <- overall3.female.sig  %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
 lnRR.ci <- overall3.female.sig  %>% filter(parameter == "lnRR") %>% mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
 
-overall4.female.sig <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
+overall4.female.sig <- bind_rows(lnCVR.ci,  lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high) #lnVR.ci,
 
@@
 ```
-#######################
 
@@
 
-#### Male Fig 3 > 10% (male biased traits)
+#### Male Fig 4 > 10% (male biased traits)
 ```{r}
@@
 
-overall.male.plot3.perc <- full_join(plot3.male.meta.CVR.perc.b, plot3.male.meta.VR.perc.b) 
-overall.male.plot3.perc <- full_join(overall.male.plot3.perc, plot3.male.meta.RR.perc.b)
+#overall.male.plot3.perc <- full_join(plot3.male.meta.CVR.perc.b, plot3.male.meta.VR.perc.b) 
+overall.male.plot3.perc <- full_join(plot3.male.meta.CVR.perc.b, plot3.male.meta.RR.perc.b)
 
@@
 ```{r}
-overall3.perc <- gather(overall.male.plot3.perc, parameter, value, c(lnCVR, lnVR, lnRR), factor_key= TRUE)
+overall3.perc <- gather(overall.male.plot3.perc, parameter, value, c(lnCVR, lnRR), factor_key= TRUE) #lnVR,
 
 lnCVR.ci <- overall3.perc %>% filter(parameter == "lnCVR") %>% mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
-lnVR.ci <- overall3.perc  %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
+#lnVR.ci <- overall3.perc  %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
 lnRR.ci <- overall3.perc  %>% filter(parameter == "lnRR") %>% mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
 
-overall4.male.perc <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
+overall4.male.perc <- bind_rows(lnCVR.ci,  lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high) #lnVR.ci,
 
@@
 
-Plot Fig3 all >10% difference (male bias)
+Plot Fig3 (4 in ms) all >10% difference (male bias)
 ```{r}
@@
 
-##################
-
-Female Fig 3 >10%
+####Female Fig 3 >10%
 ```{r}
@@
 
-overall.plot3.perc <- full_join(plot3.meta.CVR.perc.b, plot3.meta.VR.perc.b) 
-overall.plot3.perc <- full_join(overall.plot3.perc, plot3.meta.RR.perc.b)
+#overall.plot3.perc <- full_join(plot3.meta.CVR.perc.b, plot3.meta.VR.perc.b) 
+overall.plot3.perc <- full_join(plot3.meta.CVR.perc.b, plot3.meta.RR.perc.b)
 
@@
 
-#### Restructure data for plotting
+Restructure data for plotting
 Female bias, 10 percent difference
 ```{r}
-overall3.perc <- gather(overall.plot3.perc, parameter, value, c(lnCVR, lnVR, lnRR), factor_key= TRUE)
+overall3.perc <- gather(overall.plot3.perc, parameter, value, c(lnCVR, lnRR), factor_key= TRUE) #lnVR,
 
 lnCVR.ci <- overall3.perc %>% filter(parameter == "lnCVR") %>% mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
-lnVR.ci <- overall3.perc  %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
+#lnVR.ci <- overall3.perc  %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
 lnRR.ci <- overall3.perc  %>% filter(parameter == "lnRR") %>% mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
 
-overall4.perc <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
+overall4.perc <- bind_rows(lnCVR.ci,  lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high) #lnVR.ci,
 
@@
 
-#### Plot Fig3 all plots combined
+#### Plot Fig4:  all plots combined
 ```{r}
@@
 Fig3
-#ggsave("Fig3.pdf", plot = Fig3, width = 9, height = 6) 
-```
-
-### Heterogeneity
+#ggsave("MetaResultsCVR_RR.pdf", plot = Fig3, width = 9, height = 6) 
+```
+
+## Heterogeneity
 #### FIGURE 4 (Second-order meta analysis on heterogeneity)
-#### Create matrix to store results for all traits
+Create matrix to store results for all traits
 ```{r}
@@
 
-#### LOOP
+LOOP
 Parameters to extract from metafor (sigma2's, s.nlevels)
@@
 
-#### Exclude traits
+#### Exclude traits, merge datasets
 ```{r}
@@
 
-#### Dealing with correlated parameters
+#### Correlated parameters
 ```{r}
 metahetero1 <- results.allhetero.grouping2 
-length(unique(metahetero1$procedure)) #18
-length(unique(metahetero1$GroupingTerm)) #9 
-length(unique(metahetero1$parameter_group)) # 149 levels: one more tha in effect size alanlysis, see above; CHECK!
-length(unique(metahetero1$parameter_name)) #218
+#length(unique(metahetero1$procedure)) #18
+#length(unique(metahetero1$GroupingTerm)) #9 
+#length(unique(metahetero1$parameter_group)) # 149 
+#length(unique(metahetero1$parameter_name)) #218
 
@@
 metahetero1_sub <- subset(metahetero1, par_group_size > 1) # 90 observations  
-str(metahetero1_sub)
+#str(metahetero1_sub)
 # metahetero1_sub$sampleSize <- as.numeric(metahetero1_sub$sampleSize) #from previous analysis? don't think is used: : delete in final version
@@
 
-#### Merge the two data sets (the new [robu_all.] and the initial [uncorrelated sub-traits with count = 1])
+Merge the two data sets (the new [robu_all.] and the initial [uncorrelated sub-traits with count = 1])
+
 In this step, we 	
@@
 
-#### Last step: meta-meta-analysis of heterogeneity
+#### Meta-analysis of heterogeneity
 ```{r}
@@
 
-#### Heterogeneity PLOTS
+#### Heterogeneity PLOT
 Restructure data for plotting 
@@
 
-#### Plot FIGURE 4 (5 in ms) (Second-order meta analysis on heterogeneity)
+###Plot FIGURE 4 (5 in ms) (Second-order meta analysis on heterogeneity)
 
@@
 ```
+
+## Acknowledgements
+tbd
+
+## R Session Information
+
+```{r}
+sessionInfo() 
+```

### 2019-11-06 Prep & old/prep and old- scripts/2019_Aug30_IMPC_variance_and_sex_difference.Rmd
Update Nov

--- 2019-11-06 Prep & old/prep and old- scripts/2019_Aug30-NO_VR_IMPC_variance_and_sex_difference.Rmd
@@
 
-meta.plot2.all.b <- gather(meta.plot2.all, trait, value, c(lnCVR,  lnRR)) #lnVR,
-
-meta.plot2.all.b$trait <- factor(meta.plot2.all.b$trait, levels =c("lnCVR","lnRR") )#"lnVR",
+meta.plot2.all.b <- gather(meta.plot2.all, trait, value, c(lnCVR, lnVR, lnRR))
+
+meta.plot2.all.b$trait <- factor(meta.plot2.all.b$trait, levels =c("lnCVR","lnVR","lnRR") )
 
@@
 
-meta.plot2.sig.b <- meta.plot2.sig[, c("lnCVR",  "lnRR", "lnCVRsig", "lnVRsig", "lnRRsig", "GroupingTerm")]   #"lnVR",
+meta.plot2.sig.b <- meta.plot2.sig[, c("lnCVR", "lnVR", "lnRR", "lnCVRsig", "lnVRsig", "lnRRsig", "GroupingTerm")]
 
@@
 
-meta.plot2.sig.c$trait <- factor(meta.plot2.sig.c$trait, levels =c("lnCVR","lnRR") ) #"lnVR",
+meta.plot2.sig.c$trait <- factor(meta.plot2.sig.c$trait, levels =c("lnCVR","lnVR","lnRR") )
 
@@
 ```{r}
-meta.plot2.over10 <- meta_clean %>% select(lnCVR,  lnRR, GroupingTerm) %>% arrange(GroupingTerm) #lnVR,
-
-meta.plot2.over10.b <- gather(meta.plot2.over10, trait, value, c(lnCVR,  lnRR)) #lnVR,
-
-meta.plot2.over10.b$trait <- factor(meta.plot2.over10.b$trait, levels =c("lnCVR","lnRR") ) #"lnVR",
+meta.plot2.over10 <- meta_clean %>% select(lnCVR, lnVR, lnRR, GroupingTerm) %>% arrange(GroupingTerm)
+
+meta.plot2.over10.b <- gather(meta.plot2.over10, trait, value, c(lnCVR, lnVR, lnRR))
+
+meta.plot2.over10.b$trait <- factor(meta.plot2.over10.b$trait, levels =c("lnCVR","lnVR","lnRR") )
 
@@
 Fig2
-ggsave("CountDataCVR_RR_only.pdf", plot = Fig2, width = 6, height = 5) 
+ggsave("Fig2.pdf", plot = Fig2, width = 6, height = 5) 
 ```
@@
 ```{r}
-overall3 <- gather(overall2, parameter, value, c(lnCVR,  lnRR), factor_key= TRUE) #lnVR,
+overall3 <- gather(overall2, parameter, value, c(lnCVR, lnVR, lnRR), factor_key= TRUE)
 
 lnCVR.ci <- overall3 %>% filter(parameter == "lnCVR") %>% mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
-#lnVR.ci <- overall3 %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
+lnVR.ci <- overall3 %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
 lnRR.ci <- overall3 %>% filter(parameter == "lnRR") %>% mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
 
-overall4 <- bind_rows(lnCVR.ci,  lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high) #lnVR.ci,
+overall4 <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
 
@@
 #Significant subset for lnVR
-#metacombo_male.plot3.VR <- meta.male.plot3.sig %>%
-# filter(sigVR == 1) %>%
-# group_by(GroupingTerm) %>%
-# nest()
-
-#metacombo_male.plot3.VR.all <- meta.male.plot3.sig %>%
- #filter(sigVR == 1) %>%
- #nest()
+metacombo_male.plot3.VR <- meta.male.plot3.sig %>%
+ filter(sigVR == 1) %>%
+ group_by(GroupingTerm) %>%
+ nest()
+
+metacombo_male.plot3.VR.all <- meta.male.plot3.sig %>%
+ filter(sigVR == 1) %>%
+ nest()
 
@@
 
-#plot3.male.meta.VR <- metacombo_male.plot3.VR %>% 
- # mutate(model_lnVR = map(data, ~ metafor::rma.uni(yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower)/ (2*1.96),  
-#				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )
+plot3.male.meta.VR <- metacombo_male.plot3.VR %>% 
+  mutate(model_lnVR = map(data, ~ metafor::rma.uni(yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower)/ (2*1.96),  
+				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )
 
@@
 
-#plot3.male.meta.VR.all <- metacombo_male.plot3.VR.all %>% 
-#  mutate(model_lnVR = map(data, ~ metafor::rma.uni(yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower)/ (2*1.96),  
-#				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )
-
-#plot3.male.meta.VR.all <- plot3.male.meta.VR.all %>% mutate(GroupingTerm = "All")
+plot3.male.meta.VR.all <- metacombo_male.plot3.VR.all %>% 
+  mutate(model_lnVR = map(data, ~ metafor::rma.uni(yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower)/ (2*1.96),  
+				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )
+
+plot3.male.meta.VR.all <- plot3.male.meta.VR.all %>% mutate(GroupingTerm = "All")
 
@@
 plot3.male.meta.CVR <- bind_rows(plot3.male.meta.CVR, plot3.male.meta.CVR.all)
-#plot3.male.meta.VR <- bind_rows(plot3.male.meta.VR, plot3.male.meta.VR.all)
+plot3.male.meta.VR <- bind_rows(plot3.male.meta.VR, plot3.male.meta.VR.all)
 plot3.male.meta.RR <- bind_rows(plot3.male.meta.RR, plot3.male.meta.RR.all)
@@
 
-#plot3.male.meta.VR.b <- as.data.frame(plot3.male.meta.VR %>% group_by(GroupingTerm) %>%  
-#	mutate(lnVR = map_dbl(model_lnVR, pluck(2)), lnVR_lower = map_dbl(model_lnVR, pluck(6)), 
-#	lnVR_upper =map_dbl(model_lnVR, pluck(7)), lnVR_se =map_dbl(model_lnVR, pluck(3))) )[, c(1,4:7)] 
-#plot3.male.meta.VR.b <- plot3.male.meta.VR.b[order(plot3.male.meta.VR.b$GroupingTerm),]
+plot3.male.meta.VR.b <- as.data.frame(plot3.male.meta.VR %>% group_by(GroupingTerm) %>%  
+	mutate(lnVR = map_dbl(model_lnVR, pluck(2)), lnVR_lower = map_dbl(model_lnVR, pluck(6)), 
+	lnVR_upper =map_dbl(model_lnVR, pluck(7)), lnVR_se =map_dbl(model_lnVR, pluck(3))) )[, c(1,4:7)] 
+plot3.male.meta.VR.b <- plot3.male.meta.VR.b[order(plot3.male.meta.VR.b$GroupingTerm),]
 
@@
 
-#overall.male.plot3 <- full_join(plot3.male.meta.CVR.b, plot3.male.meta.VR.b) 
-overall.male.plot3 <- full_join(plot3.male.meta.CVR.b, plot3.male.meta.RR.b)
+overall.male.plot3 <- full_join(plot3.male.meta.CVR.b, plot3.male.meta.VR.b) 
+overall.male.plot3 <- full_join(overall.male.plot3, plot3.male.meta.RR.b)
 
@@
 ```{r}
-overall3.male.sig <- gather(overall.male.plot3, parameter, value, c(lnCVR,  lnRR), factor_key= TRUE) #lnVR,
+overall3.male.sig <- gather(overall.male.plot3, parameter, value, c(lnCVR, lnVR, lnRR), factor_key= TRUE)
 
 lnCVR.ci <- overall3.male.sig  %>% filter(parameter == "lnCVR") %>% mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
-#lnVR.ci <- overall3.male.sig  %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
+lnVR.ci <- overall3.male.sig  %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
 lnRR.ci <- overall3.male.sig  %>% filter(parameter == "lnRR") %>% mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
 
-overall4.male.sig <- bind_rows(lnCVR.ci,  lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high) #lnVR.ci,
+overall4.male.sig <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
 
@@
 ```{r}
-overall3.female.sig <- gather(overall.female.plot3, parameter, value, c(lnCVR,  lnRR), factor_key= TRUE) #lnVR,
+overall3.female.sig <- gather(overall.female.plot3, parameter, value, c(lnCVR, lnVR, lnRR), factor_key= TRUE)
 
 lnCVR.ci <- overall3.female.sig  %>% filter(parameter == "lnCVR") %>% mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
-#lnVR.ci <- overall3.female.sig  %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
+lnVR.ci <- overall3.female.sig  %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
 lnRR.ci <- overall3.female.sig  %>% filter(parameter == "lnRR") %>% mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
 
-overall4.female.sig <- bind_rows(lnCVR.ci,  lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high) #lnVR.ci,
+overall4.female.sig <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
 
@@
 
-#overall.male.plot3.perc <- full_join(plot3.male.meta.CVR.perc.b, plot3.male.meta.VR.perc.b) 
-overall.male.plot3.perc <- full_join(plot3.male.meta.CVR.perc.b, plot3.male.meta.RR.perc.b)
+overall.male.plot3.perc <- full_join(plot3.male.meta.CVR.perc.b, plot3.male.meta.VR.perc.b) 
+overall.male.plot3.perc <- full_join(overall.male.plot3.perc, plot3.male.meta.RR.perc.b)
 
@@
 ```{r}
-overall3.perc <- gather(overall.male.plot3.perc, parameter, value, c(lnCVR, lnRR), factor_key= TRUE) #lnVR,
+overall3.perc <- gather(overall.male.plot3.perc, parameter, value, c(lnCVR, lnVR, lnRR), factor_key= TRUE)
 
 lnCVR.ci <- overall3.perc %>% filter(parameter == "lnCVR") %>% mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
-#lnVR.ci <- overall3.perc  %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
+lnVR.ci <- overall3.perc  %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
 lnRR.ci <- overall3.perc  %>% filter(parameter == "lnRR") %>% mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
 
-overall4.male.perc <- bind_rows(lnCVR.ci,  lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high) #lnVR.ci,
+overall4.male.perc <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
 
@@
 
-#overall.plot3.perc <- full_join(plot3.meta.CVR.perc.b, plot3.meta.VR.perc.b) 
-overall.plot3.perc <- full_join(plot3.meta.CVR.perc.b, plot3.meta.RR.perc.b)
+overall.plot3.perc <- full_join(plot3.meta.CVR.perc.b, plot3.meta.VR.perc.b) 
+overall.plot3.perc <- full_join(overall.plot3.perc, plot3.meta.RR.perc.b)
 
@@
 ```{r}
-overall3.perc <- gather(overall.plot3.perc, parameter, value, c(lnCVR, lnRR), factor_key= TRUE) #lnVR,
+overall3.perc <- gather(overall.plot3.perc, parameter, value, c(lnCVR, lnVR, lnRR), factor_key= TRUE)
 
 lnCVR.ci <- overall3.perc %>% filter(parameter == "lnCVR") %>% mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
-#lnVR.ci <- overall3.perc  %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
+lnVR.ci <- overall3.perc  %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
 lnRR.ci <- overall3.perc  %>% filter(parameter == "lnRR") %>% mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
 
-overall4.perc <- bind_rows(lnCVR.ci,  lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high) #lnVR.ci,
+overall4.perc <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
 
@@
 Fig3
-#ggsave("MetaResultsCVR_RR.pdf", plot = Fig3, width = 9, height = 6) 
+#ggsave("Fig3.pdf", plot = Fig3, width = 9, height = 6) 
 ```

### 2019-11-06 Prep & old/prep and old- scripts/2019_IMPC variance and sex difference.Rmd
Update Nov

--- 2019-11-06 Prep & old/prep and old- scripts/2019_Aug30_IMPC_variance_and_sex_difference.Rmd
@@
     number_sections: no
-    theme:  flatly
+    theme:  cosmo
     toc: yes
@@
  data$parameterGroup <- group$parameter[match(data$parameter_name, group$parameter_name)]
+
 ```
@@
 removed <-length(unique(meta_clean$parameter_name)) #218
-
-meta_problem <- results.alltraits.grouping[ (results.alltraits.grouping$id %in% c(84,144,158,160,161,162,163,165,166,167,168,221,222,231)), ]
 ```

### 2019-11-06 Prep & old/prep and old- scripts/2019_July_IMPC variance and sex difference.Rmd
Update Nov

--- 2019-08-21 scripts/2019_July_IMPC variance and sex difference.Rmd
@@
 
-2) Subsetting the data to choose only one datapoint per individual per trait
+2) Subsetting the data to choose only one data point per individual per trait
 ```{r}
@@
 
-### Heterogeneity
+## Heterogeneity
 #### FIGURE 4 (Second-order meta analysis on heterogeneity)

### 2019-11-06 Prep & old/prep and old- scripts/IMPC variance and sex difference May15_2019_FZ3-6-19.Rmd
Update Nov

--- 2019-06-04 scripts/2019_4June_IMPC variance and sex difference.Rmd
@@
 # Loading functions that are necessary
-### Preparation of raw data
+##Preparation of raw data
 1) Data loading and cleaning of the csv file
@@
   if(Equal.E.C.Corr==T){
-    mvcorr <- 0 #cor.test(log(c(CMean, EMean)), log(c(CSD, ESD)))$estimate   old, slightly incorrect
+    mvcorr <- <-0 #cor.test(log(c(CMean, EMean)), log(c(CSD, ESD)))$estimate   old, slightly incorrect
     S2 <- CSD^2 / (CN * (CMean^2)) + 1 / (2 * (CN - 1)) - 2 * mvcorr * sqrt((CSD^2 / (CN * (CMean^2))) * (1 / (2 * (CN - 1)))) + ESD^2 / (EN * (EMean^2)) + 1 / (2 * (EN - 1)) - 2 * mvcorr * sqrt((ESD^2 / (EN * (EMean^2))) * (1 / (2 * (EN - 1))))
@@
 
-### Clean data
+## Clean data
 This requires the selection of traits that have been measured in at least 2 centers. Consequently, rare or unusual methods and procedures are being filtered out in this step.
@@
 
-## Preparation for Meta analysis
-### Define population variable & add grouping variables
+#Preparation for Meta analysis
+## Define population variable & add grouping variables
 
@@
 
-### Create a matrix to store results for all traits
+## Create a matrix to store results for all traits
 As the current version of this script utilizes a loop instead of tidyR code, it is here necessary to create an empty matrix, in which the returning values will be stored.
@@
 
-## LOOP, to run meta-analysis on all traits
+# LOOP, to run meta-analysis on all traits
 The loop combines the functions menationed above and fills the data matrix with results from our meta analysis. 
@@
 
-### Merging datasets
+# Merging datasets
 
@@
 
-## Dealing with Correlated Paramters
+#Dealing with Correlated Paramters
 
@@
 
-### Collapsing correlated parameters
+## Collapsing correlated parameters
 
@@
 
-### Count of number of parameter names (correlated sub-traits) in each parameter group (par_group_size) 
+## Count of number of parameter names (correlated sub-traits) in each parameter group (par_group_size) 
 This serves to idenfify and separate the traits that are correlated from the full dataset that can be preocessed as is.
@@
 
-### Perform meta-analyses on correlated sub-traits, using robumeta 
+## Perform meta-analyses on correlated sub-traits, using robumeta 
 The subset of the data is prepared (nested), and in this first step the model of the meta analysis effect sizes are calculated
@@
 
-### Extract and save parameter estimates 
+## Extract and save parameter estimates 
 Function to collect the outcomes of the "mini" meta analysis
@@
 
-Extraction of values created during Meta analysis using robu meta
+Meta analysis using robu meta
 ```{r}
@@
 
- Merge the two data sets (the new [robu_all] and the initial [uncorrelated sub-traits with count = 1]) 
+## Merge the two data sets (the new [robu_all] and the initial [uncorrelated sub-traits with count = 1]) 
 ```{r}
@@
 
-Combine data 
+# Combine data
+
 ```{r}
@@
 ```
-### Clean-up and rename 
+
+# Clean-up and rename 
 ```{r}
@@
 
-## Last step: meta-meta-analysis 
-### Perform meta-analyses (3 for each of the 9 grouping terms: lnCVR, lnVR, lnRR) 
+# Last step: meta-meta-analysis 
+## *Perform meta-analyses (3 for each of the 9 grouping terms: lnCVR, lnVR, lnRR) 
 This is the full result dataset
@@
 
-### Prepare data
+# Prepare data
 Nesting, calculating the number of parameters within each grouping term, and running the metaanalysis
@@
 
-Re-structure data for each grouping term; delete un-used variables
+# Re-structure data for each grouping term; delete un-used variables
 
@@
 
-## Plot FIGURE 2 (First-order meta analysis results)
-
-Re-order grouping terms
+# **Plot FIGURE 2 (First-order meta analysis results)
+
+# **Re-order grouping terms
 
@@
 
-### Prepare data for traits with CI not overlapping 0
-create column with 1= different from zero, 0= zero included in CI
+# *Prepare data for traits with CI not overlapping 0
+##create column with 1= different from zero, 0= zero included in CI
 ```{r}
@@
 
-Prepare data for traits with effect size ratios > 10% larger in males
+# *Prepare data for traits with effect size ratios > 10% larger in males
 ```{r}
@@
 ```
-### Create final combined Figure (Figure 2)
+Create final combined Figure
 ```{r}
@@
 ## Preparation, for Figure 3: Overall results of second order meta anlaysis
-### Restructure data for plotting 
+## Restructure data for plotting 
 Data are restructred, and grouping terms are being re-ordered
@@
 
-### Plot FIGURE 3 (Second-order meta analysis results)
-
-Preparation: Sub-Plot  for Figure 3: all traits
+# Plot FIGURE 3 (Second-order meta analysis results)
+
+# Preparation: Sub-Plot  for Figure 3: all traits
 ```{r}
@@
 
-### Prepare data for traits with CI not overlapping 0
-
-create column with 1= different from zero, 0= zero included in CI
-Male-biased (significant) traits
+# *Prepare data for traits with CI not overlapping 0
+
+#create column with 1= different from zero, 0= zero included in CI
+# ** Male-biased traits
 ```{r}
@@
 add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.male.meta.CVR.b))    
-
 plot3.male.meta.CVR.b <- bind_rows(plot3.male.meta.CVR.b, add.row.hearing) 
@@
 
-Restructure MALE data for plotting 
+# **Restructure MALE data for plotting 
 ```{r}
@@
 
-Plot Fig3 all significant results (CI not overlapping zero) for males
+# **Plot Fig3 all significant results (CI not overlapping zero) for males
 ```{r}
@@
   geom_point(aes(shape = parameter),
-             fill = 'mediumaquamarine', color = 'mediumaquamarine', size = 2.2, 
+             fill = 'blue', color = 'blue', size = 2.2,  #needs adjustment to nicer blue, 20-5-19
                show.legend = FALSE) +
@@
 #######################
-### Female Figure
-Female Fig3 sig
-
-Prepare data for traits with CI not overlapping 0
+# **Female Fig3 sig
+
+#*Prepare data for traits with CI not overlapping 0
 create column with 1= different from zero, 0= zero included in CI
@@
 add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.female.meta.CVR.b))    
-
 plot3.female.meta.CVR.b <- bind_rows(plot3.female.meta.CVR.b, add.row.hearing)
@@
 
-overall.female.plot3 <- full_join(plot3.female.meta.CVR.b, plot3.female.meta.VR.b)
-overall.female.plot3 <- full_join(overall.female.plot3, plot3.female.meta.RR.b)
+overall.female.plot3 <- full_join(plot3.female.meta.CVR.b, plot3.female.meta.VR.b)  #FELIX: changed from inner to full
+overall.female.plot3 <- full_join(overall.female.plot3, plot3.female.meta.RR.b)   #FELIX: changed from inner to full
 
@@
 
-#add missing GroupingTerms for plot POYTENTIALLY DELETE
-#overall.female.plot3 <- add_row(overall.female.plot3, GroupingTerm = "Morphology")
-#overall.female.plot3 <- add_row(overall.female.plot3, GroupingTerm = "Metabolism")
-#overall.female.plot3 <- add_row(overall.female.plot3, GroupingTerm = "Hematology")
-#overall.female.plot3 <- add_row(overall.female.plot3, GroupingTerm = "Hearing")
-#overall.female.plot3 <- add_row(overall.female.plot3, GroupingTerm = "Eye")
-
-#overall.female.plot3$GroupingTerm <- factor(overall.female.plot3$GroupingTerm, levels =c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye", "All") )
-#overall.female.plot3$GroupingTerm <- factor(overall.female.plot3$GroupingTerm, rev(levels(overall.female.plot3$GroupingTerm)))
-
-```
-
-Restructure data for plotting
+#add missing GroupingTerms for plot: NOT NEEDED (next 5 lines)FELIX
+overall.female.plot3 <- add_row(overall.female.plot3, GroupingTerm = "Morphology")
+overall.female.plot3 <- add_row(overall.female.plot3, GroupingTerm = "Metabolism")
+overall.female.plot3 <- add_row(overall.female.plot3, GroupingTerm = "Hematology")
+overall.female.plot3 <- add_row(overall.female.plot3, GroupingTerm = "Hearing")
+overall.female.plot3 <- add_row(overall.female.plot3, GroupingTerm = "Eye")
+
+NOT NEEDED (next 2 lines)FELIX
+overall.female.plot3$GroupingTerm <- factor(overall.female.plot3$GroupingTerm, levels =c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye", "All") )
+overall.female.plot3$GroupingTerm <- factor(overall.female.plot3$GroupingTerm, rev(levels(overall.female.plot3$GroupingTerm)))
+
+```
+
+# **Restructure data for plotting
 
@@
 
-### Plot Fig3 all significant results (CI not overlapping zero, female )
+# **Plot Fig3 all significant results (CI not overlapping zero)
 ```{r}
@@
   geom_point(aes(shape = parameter),
-             fill = 'salmon1', color = 'salmon1', size = 2.2,
+             fill = 'red', color = 'red', size = 2.2,
              show.legend = FALSE) +
@@
 
-### Fig3 >10%
-
-Prepare data for traits with m/f difference > 10%
-
-create column with 1= larger, 0= diff not larger than 10%
-
-### Male Fig 3 > 10% (male biased traits)
+# *Fig3 >10%
+
+# *Prepare data for traits with m/f difference > 10%
+
+#create column with 1= larger, 0= diff not larger than 10%
+
+# Male Fig 3 > 10% (male biased traits)
 ```{r}
@@
 
-overall.male.plot3.perc <- full_join(plot3.male.meta.CVR.perc.b, plot3.male.meta.VR.perc.b) 
-overall.male.plot3.perc <- full_join(overall.male.plot3.perc, plot3.male.meta.RR.perc.b)
-
+overall.male.plot3.perc <- full_join(plot3.male.meta.CVR.perc.b, plot3.male.meta.VR.perc.b) #FELIX: changed inner to full
+overall.male.plot3.perc <- full_join(overall.male.plot3.perc, plot3.male.meta.RR.perc.b)  #FELIX: changed inner to full
+
+#FELIX: remove next 2 lines!
 overall.male.plot3.perc$GroupingTerm <- factor(overall.male.plot3.perc$GroupingTerm, levels =c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye", "All") )
@@
 
-```
-
-Restructure data for plotting : Male biased, 10% difference
+#add missing GroupingTerms for plot
+overall.male.plot3.perc <- add_row(overall.male.plot3.perc, GroupingTerm = "Heart")  #FELIX: delete this line
+overall.male.plot3.perc <- add_row(overall.male.plot3.perc, GroupingTerm = "Eye")
+
+overall.male.plot3.perc$GroupingTerm <- factor(overall.male.plot3.perc$GroupingTerm, levels =c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye", "All") )
+overall.male.plot3.perc$GroupingTerm <- factor(overall.male.plot3.perc$GroupingTerm, rev(levels(overall.male.plot3.perc$GroupingTerm)))
+
+```
+
+# **Restructure data for plotting : Male biased, 10% difference
 ```{r}
@@
 
-Plot Fig3 all >10% difference (male bias)
+# **Plot Fig3 all >10% difference (male bias)
 ```{r}
@@
   geom_point(aes(shape = parameter,
-             fill = parameter), color = 'mediumaquamarine', size = 2.2, 
+             fill = parameter), color = 'blue', size = 2.2, 
              show.legend = FALSE) +
@@
 
-Female Fig 3 >10%
+# ** Female Fig 3 >10%
 ```{r}
@@
 
-overall.plot3.perc <- full_join(plot3.meta.CVR.perc.b, plot3.meta.VR.perc.b) 
-overall.plot3.perc <- full_join(overall.plot3.perc, plot3.meta.RR.perc.b)
-
+overall.plot3.perc <- full_join(plot3.meta.CVR.perc.b, plot3.meta.VR.perc.b) #FELIX: changed inner to full
+overall.plot3.perc <- full_join(overall.plot3.perc, plot3.meta.RR.perc.b)  #FELIX: changed inner to full
+
+#FELIX: remove next 2 lines
 overall.plot3.perc$GroupingTerm <- factor(overall.plot3.perc$GroupingTerm, levels =c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye", "All") )
@@
 
-```
-
-### Restructure data for plotting
+#add missing GroupingTerms for plot
+overall.plot3.perc <- add_row(overall.plot3.perc, GroupingTerm = "Metabolism") #FELIX: delete this line
+overall.plot3.perc <- add_row(overall.plot3.perc, GroupingTerm = "Hematology")
+overall.plot3.perc <- add_row(overall.plot3.perc, GroupingTerm = "Eye")  #FELIX: delete this line
+
+overall.plot3.perc$GroupingTerm <- factor(overall.plot3.perc$GroupingTerm, levels =c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye", "All") )
+overall.plot3.perc$GroupingTerm <- factor(overall.plot3.perc$GroupingTerm, rev(levels(overall.plot3.perc$GroupingTerm)))
+
+```
+
+# **Restructure data for plotting
 Female bias, 10 percent difference
@@
 
-Plot Fig3 all >10% difference (female)
+# **Plot Fig3 all >10% difference 
 ```{r}
@@
   geom_point(aes(shape = parameter),
-             fill = 'salmon1', color = 'salmon1', size = 2.2, 
+             fill = 'red', color = 'red', size = 2.2, 
              show.legend = FALSE) +
@@
 
-# Plot Fig3 all plots combined
+# *Plot Fig3 all plots combined
 ```{r}
@@
 
-## Plot Supplement FIGURE S1 (Second-order meta-analysis on heterogeneity)
-
-### Create matrix to store results for all traits
+Plot Supplement FIGURE S1 (Second-order meta-analysis on heterogeneity)
+
+## *Create matrix to store results for all traits
 ```{r}
@@
 
-### LOOP
+# **LOOP
 
@@
 
-Exclude traits
+## *Exclude traits
 ```{r}
@@
 
-Merge data sets containing metafor results with procedure etc. names
-
+# *Merge data sets containing metafor results with procedure etc. names 
 ```{r}
 procedures <- read.csv("procedures.csv")
-
+```
+
+```{r}  
 results.allhetero.grouping2$parameter_group <- data$parameter_group[match(results.allhetero.grouping2$id, data$id)]
@@
 
+```
+
+```{r}   
 results.allhetero.grouping2$GroupingTerm <-  procedures$GroupingTerm[match(results.allhetero.grouping2$procedure, procedures$procedure)]
@@
 metahetero1_sub <- subset(metahetero1, par_group_size > 1) # 90 observations  
-#str(metahetero1_sub)
+str(metahetero1_sub)
 # metahetero1_sub$sampleSize <- as.numeric(metahetero1_sub$sampleSize) #Felix30-5-19: delete this line
@@
 
-Nest data
+# **Nest data
 ```{r}
@@
 
-### Perform meta-analyses on correlated sub-traits, using robumeta
-
-Extract and save parameter estimates 
+## *Perform meta-analyses on correlated sub-traits, using robumeta
+
+## **Extract and save parameter estimates 
 ```{r}
@@
 
-### Combine data 
-in three separate steps
+# **Combine data 
+# Step1 
 ```{r}
 combinedmetahetero <- bind_rows(robu_all., metahetero_all)
-#glimpse(combinedmetahetero)
-
+glimpse(combinedmetahetero)
+```
+# Steps 2&3
+```{r}
 metacombohetero <- combinedmetahetero
@@
 
+```
+
+```{r}
 #write.csv(metacombohetero, "metacombohetero.csv")
-```
-
-### Last step: Meta-meta-analysis of heterogeneity
-Perform meta-meta-analysis (3 for each of the 9 grouping terms: var.CVR, var.VR, var.RR) 
-```{r}
-#glimpse(metacombohetero)
-
+
+```
+
+## *Last step: Meta-meta-analysis of heterogeneity
+```{r}
+glimpse(metacombohetero)
+```
+## *Perform meta-meta-analysis (3 for each of the 9 grouping terms: var.CVR, var.VR, var.RR)
+
+```{r}
 metacombohetero_final <- metacombohetero %>%
@@
  nest()
-
-#Calculate number of parameters per grouping term : not needed; delete in final version
+```
+
+# **Calculate number of parameters per grouping term : not needed; delete in final version
 #metacombo_final <- metacombo_final  %>%  mutate(para_per_GroupingTerm = map_dbl(data, nrow))
-```
-
- Final fixed effects meta-analyses within grouping terms, with SE of the estimate
+
+# **Final fixed effects meta-analyses within grouping terms, with SE of the estimate
 
@@
 
-### Restructure data for plotting 
+####################################################################################################################################
+# *Supplement Figure S1
+
+# **Restructure data for plotting 
 ```{r}
@@
 
-# Plot Supplement FIGURE S1 (Second-order meta analysis on heterogeneity)
-
-### Plot FigS1 all traits
+# *Plot Supplement FIGURE S1 (Second-order meta analysis on heterogeneity)
+
+# **Plot FigS1 all traits
 ```{r}
@@
 ```
-
-# TABLES with Heterogeneity (tau2, I2) of all the groups, following the structure of FIG3
-
-### CVR
-```{r}
+###################################################################################################
+
+#### TABLES with Heterogeneity (tau2, I2) of all the groups in FIG3 ###
+
+#CVR
 heteroeach.meta.CVR.c <- as.data.frame(overall1 %>% group_by(GroupingTerm) %>%  
@@
 
-overall2.CVR.c <- add_column(overall2.CVR.c, var = "ln(CVR)", .before= "tau2")
-overall2.CVR.c <- overall2.CVR.c[order(overall2.CVR.c$GroupingTerm),]
-```
-
-### VR
-
-```{r}
+overall2.CVR.c <- add_column(overall2.c, var = "ln(CVR)", .before= "tau2")
+overall2.CVR.c <- overall2.c[order(overall2.c$GroupingTerm),]
+
+#VR
 heteroeach.meta.VR.c <- as.data.frame(overall1 %>% group_by(GroupingTerm) %>%  
@@
 overall2.VR.c <- overall2.VR.c[order(overall2.VR.c$GroupingTerm),]
-```
-
-### RR
-```{r}
+
+#RR
 heteroeach.meta.RR.c <- as.data.frame(overall1 %>% group_by(GroupingTerm) %>%  
@@
 for_table_overall.het <- overall2.het[order(factor(overall2.het$GroupingTerm, levels = c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye", "All"))),]
-```
-
-the following uses the same data from above (plot3.male.meta.CVR / plot3.male.meta.VR / plot3.male.meta.RR):
-
-### Male not overlapping zero (significant)
-
-Re-structure data for each grouping term; delete un-used variables
-```{r}
+
+#####################
+
+## the following uses the same data from above, right after (code in quotation marks is copied from section above):
+"
+# Combine with separate grouping term results
+
+plot3.male.meta.CVR <- bind_rows(plot3.male.meta.CVR, plot3.male.meta.CVR.all)
+plot3.male.meta.VR <- bind_rows(plot3.male.meta.VR, plot3.male.meta.VR.all)
+plot3.male.meta.RR <- bind_rows(plot3.male.meta.RR, plot3.male.meta.RR.all)
+"
+
+## Male not overlapping zero (significant)
+
+# **Re-structure data for each grouping term; delete un-used variables
+
 #plot3.male.meta.CVR[[3]][[1]][1:30] #tau2 is at position '9', I2 is at position '23'
@@
 for_table_malesig <- overall.male.plot3.[order(factor(overall.male.plot3.$GroupingTerm, levels = c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye", "All"))),]
-```
-### Female not overlapping zero (significant)
-
-Re-structure data for each grouping term; delete un-used variables
-```{r}
+
+```
+
+#NEW ADDED 3-6-2019 FZ: missing heterogeneity plots #
+
+## Female not overlapping zero (significant)
+
+# **Re-structure data for each grouping term; delete un-used variables
+
 #plot3.female.meta.CVR[[3]][[1]][1:30] #tau2 is at position '9', I2 is at position '23'
@@
 for_table_femsig <- overall.female.plot3.[order(factor(overall.female.plot3.$GroupingTerm, levels = c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye", "All"))),]
-```
-
-### Male-biased >10%
-
-Re-structure data for each grouping term; delete un-used variables
-```{r}
+
+#####
+
+plot3.male.meta.CVR.perc.b
+
+## Male-biased >10%
+
+# **Re-structure data for each grouping term; delete un-used variables
+
 plot3.male.meta.CVR.perc.c <- as.data.frame(plot3.male.meta.CVR.perc %>% group_by(GroupingTerm) %>%  
@@
 for_table_male10perc <- overall.male.perc.[order(factor(overall.male.perc.$GroupingTerm, levels = c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye", "All"))),]
-```
-
-### Female-biased >10%
-
-Re-structure data
-```{r}
+
+##
+## Female-biased >10%
+
+# **Re-structure data
+
 #plot3.meta.CVR.perc[[3]][[1]][1:30] #tau2 is at position '9', I2 is at position '23'
@@
 for_table_female10perc <- overall.female.perc.[order(factor(overall.female.perc.$GroupingTerm, levels = c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye", "All"))),]
-
-```

### 2019-11-06 Prep & old/prep and old- scripts/Loop3.Rmd
Update Nov

---
title: "Loop"
author: "Susi/Felix"
date: "5th Dec 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

```{r}
getwd()
```

```{r}
library(readr)
library(dplyr)
library(metafor)
library(devtools)
library(patchwork)
library(purrr)
library(tidyverse)
library(tibble)
```

#save in a folder called "export"

```{r}
source("D:/Susi/garvan/Github/mice_sex_diff/mice_sex_diff_Nov/R/meta_analysis_grouping.R")
source("D:/Susi/garvan/Github/mice_sex_diff/mice_sex_diff_Nov/R/data_load_clean_grouping.R")
source("D:/Susi/garvan/Github/mice_sex_diff/mice_sex_diff_Nov/R/calc_pop_stats_grouping.R")
```

# Prepare data 
```{r ignore}
# Load raw data - save cleaned dataset as RDS for reuse
#data_raw <- load_raw("data/dr7.0_all_control_data.csv") %>%
#    clean_raw_data()
#dir.create("export", F, F)
#saveRDS(data_raw, "export/data_clean.rds")

data1 <- readRDS("export/data_clean.rds")
```

CLEAN DATA: select traits with at least 2 centers
```{r ignore}
dat1 <-
  data1 %>%
  group_by(parameter_name) %>% # am keeping this here - not based on parameter groups
  summarize(center_per_trait = length(unique(production_center, na.rm = TRUE)))
#dat1$center_per_trait

```

```{r ignore}
dat2 <- merge(data1, dat1) #sollte auch im grossen Datensatz so funktionieren, also ohne die uebereinstimmende Variable (trait) anzugeben
dat_moreThan1center <-
  dat2  %>%
  filter(center_per_trait >= 2)
```

```{r ignore}
data2 <- dat_moreThan1center
min(data2$center_per_trait) #=2;ok!
```

# Define population variable

```{r ignore}
data3 <- data2 %>%
mutate(population = sprintf("%s-%s", production_center, strain_name))
```

 add grouping stuff
```{r}  
 group <- read.csv("ParemeterGrouping.csv") 
 data$parameterGroup <- group$parameter[match(data$parameter_name, group$parameter_name)] # needs to be in certain order, doesn't work if group dataset is first!
 # data4 <- merge(data, group, by="parameter_name") #alternative, works also.

```

# Assign each unique parameter_name (=trait,use trait variable) a unique number ('id')

```{r}
# newly created grouping stuff

names(data)[1] <- "parameter_name"  # this is the original parameter_name  - 232 traits
names(data)[16] <- "parameter_group"    # my new variable, where redundant traits are combined
data <- transform(data, id = match(parameter_name, unique(parameter_name)))

```

```{r}
head(data)

```

```{r}
n <- length(unique(data$id)) # 168 now
n
```

# Create matrix to store results for all traits

```{r}
results.alltraits.grouping <- as.data.frame(cbind(c(1:n), matrix(rep(0, n*13), ncol = 13))) #number of individual results per trait = 10
names(results.alltraits.grouping) <- c("id", "lnCVR", "lnCVR_lower", "lnCVR_upper", "lnCVR_se", "lnVR", "lnVR_lower", "lnVR_upper", "lnVR_se", "lnRR", "lnRR_lower", "lnRR_upper" ,"lnRR_se" , "sampleSize")
```

`

# LOOP
I am removing the variable "weight", which has some missing data, got some error message before that data were excluded below, as there are "NA"s in the rows.
```{r ignore}
#data <- data[,c(1:11,13:16)]
```

```{r}
#write.csv(unique(data$parameter_name, "parametersToCheck.csv"))
```

```{r}

for(t in 1:n) {

  tryCatch({

    data_par_age <- data_subset_parameterid_individual_by_age(data, t, age_min = 0, age_center = 100)

    population_stats <- calculate_population_stats(data_par_age)

    results <- create_meta_analysis_effect_sizes(population_stats)

#lnCVR,  log repsonse-ratio of the coefficient of variance    
    cvr <- metafor::rma.mv(yi = effect_size_CVR, V = sample_variance_CVR, random = list(~1| strain_name, ~1|production_center,    #~1|parameter_name,
                                                                                        ~1|err), control=list(optimizer="optim", optmethod="Nelder-Mead"), data = results)
    results.alltraits.grouping[t, 2] <- cvr$b
    results.alltraits.grouping[t, 3] <- cvr$ci.lb
    results.alltraits.grouping[t, 4] <- cvr$ci.ub
    results.alltraits.grouping[t, 5] <- cvr$se

    cvr

    #lnVR, comparison of standard deviations

cv <- metafor::rma.mv(yi = effect_size_VR, V = sample_variance_VR, random = list(~1| strain_name, ~1|production_center, #~1|parameter_name,
                                                                                 ~1|err), control=list(optimizer="optim", optmethod="Nelder-Mead"),  verbose=F, data = results)
    results.alltraits.grouping[t, 6] <- cv$b
    results.alltraits.grouping[t, 7] <- cv$ci.lb
    results.alltraits.grouping[t, 8] <- cv$ci.ub
    results.alltraits.grouping[t, 9] <- cv$se

    # for means, lnRR

means <- metafor::rma.mv(yi = effect_size_RR, V = sample_variance_RR, random = list(~1| strain_name, ~1|production_center,
                                                                                    #~1|parameter_name,
                                                                                    ~1|err),
    control=list(optimizer="optim", optmethod="Nelder-Mead"), data = results)
    results.alltraits.grouping[t, 10] <- means$b
    results.alltraits.grouping[t, 11] <- means$ci.lb
    results.alltraits.grouping[t, 12] <- means$ci.ub
    results.alltraits.grouping[t, 13] <- means$se

      # for the associated sample sizes, i.e. number of centres contributing ? or combination centes/ strains (doesn't lookm like it)
        results.alltraits.grouping[t, 14] <- means$k

  }, error=function(e){cat("ERROR :",conditionMessage(e), "\n")})
}

```

for those traits where convergence wasn't achieved, manual calculation, with 1000 iterations

Trait 125
```{r}

    data_par_age <- data_subset_parameterid_individual_by_age(data, 125, age_min = 0, age_center = 100)

    population_stats <- calculate_population_stats(data_par_age)

    results <- create_meta_analysis_effect_sizes(population_stats)

#lnCVR,  log repsonse-ratio of the coefficient of variance    
    cvr <- metafor::rma.mv(yi = effect_size_CVR, V = sample_variance_CVR, random = list(~1| strain_name, ~1|production_center,    #~1|parameter_name,
                                                                                        ~1|err), control=list(optimizer="optim", optmethod="Nelder-Mead",  maxit= 1000), data = results)
    results.alltraits.grouping[125, 2] <- cvr$b
    results.alltraits.grouping[125, 3] <- cvr$ci.lb
    results.alltraits.grouping[125, 4] <- cvr$ci.ub
    results.alltraits.grouping[125, 5] <- cvr$se

    cvr

    #lnVR, comparison of standard deviations

cv <- metafor::rma.mv(yi = effect_size_VR, V = sample_variance_VR, random = list(~1| strain_name, ~1|production_center, #~1|parameter_name,
                                                                                 ~1|err), control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000),  verbose=F, data = results)
    results.alltraits.grouping[125, 6] <- cv$b
    results.alltraits.grouping[125, 7] <- cv$ci.lb
    results.alltraits.grouping[125, 8] <- cv$ci.ub
    results.alltraits.grouping[125, 9] <- cv$se

    # for means, lnRR

means <- metafor::rma.mv(yi = effect_size_RR, V = sample_variance_RR, random = list(~1| strain_name, ~1|production_center,
                                                                                    #~1|parameter_name,
                                                                                    ~1|err),
    control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), data = results)
    results.alltraits.grouping[125, 10] <- means$b
    results.alltraits.grouping[125, 11] <- means$ci.lb
    results.alltraits.grouping[125, 12] <- means$ci.ub
    results.alltraits.grouping[125, 13] <- means$se

      # for the associated sample sizes, i.e. number of centres contributing ? or combination centes/ strains (doesn't lookm like it)
        results.alltraits.grouping[125, 14] <- means$k

```

  to adjust for traits 8,18,84,125,132, 144 (doesn't work), 155, 231 (doesn't work)

```{r}
data_par_age <- data_subset_parameterid_individual_by_age(data, 8, age_min = 0, age_center = 100)

    population_stats <- calculate_population_stats(data_par_age)

    results <- create_meta_analysis_effect_sizes(population_stats)

#lnCVR,  log repsonse-ratio of the coefficient of variance    
    cvr <- metafor::rma.mv(yi = effect_size_CVR, V = sample_variance_CVR, random = list(~1| strain_name, ~1|production_center,    #~1|parameter_name,
                                                                                        ~1|err), control=list(optimizer="optim", optmethod="Nelder-Mead",  maxit= 1000), data = results)
    results.alltraits.grouping[8, 2] <- cvr$b
    results.alltraits.grouping[8, 3] <- cvr$ci.lb
    results.alltraits.grouping[8, 4] <- cvr$ci.ub
    results.alltraits.grouping[8, 5] <- cvr$se

    cvr

    #lnVR, comparison of standard deviations

cv <- metafor::rma.mv(yi = effect_size_VR, V = sample_variance_VR, random = list(~1| strain_name, ~1|production_center, #~1|parameter_name,
                                                                                 ~1|err), control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000),  verbose=F, data = results)
    results.alltraits.grouping[8, 6] <- cv$b
    results.alltraits.grouping[8, 7] <- cv$ci.lb
    results.alltraits.grouping[8, 8] <- cv$ci.ub
    results.alltraits.grouping[8, 9] <- cv$se

    # for means, lnRR

means <- metafor::rma.mv(yi = effect_size_RR, V = sample_variance_RR, random = list(~1| strain_name, ~1|production_center,
                                                                                    #~1|parameter_name,
                                                                                    ~1|err),
    control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), data = results)
    results.alltraits.grouping[8, 10] <- means$b
    results.alltraits.grouping[8, 11] <- means$ci.lb
    results.alltraits.grouping[8, 12] <- means$ci.ub
    results.alltraits.grouping[8, 13] <- means$se

      # for the associated sample sizes, i.e. number of centres contributing ? or combination centes/ strains (doesn't lookm like it)
        results.alltraits.grouping[8, 14] <- means$k
```

 I still get the NA warnings / removals, but have extensively checked the data set - there are no more NAs present.

 I also don't understand the k<= 1, as traits that were collected by one center only had been excluded in the previous steps.
 Also, "Single-level factor(s) found in 'random' argument" is strange, as some trais that actually worked and were included have been done in one strain only. so I don't understand what's egtting thrown out here.
 # due to "parameter_name" being included as random factor; which  doesn't really work because for the loop the analyses are within each parameter name? 
 also, number of iterations has beeen increased to 500, so that those that disn't converge at 100 interations may be included.
 (however, this significantly affects running time! takes very long...)

 Next step is to clean the data, i.e. remove any traits that don't make sense (i.e. number of ribs / digits , numbers of events etc)

```{r}
procedures <- read.csv("procedures.csv")
```

```{r}  
 results.alltraits.grouping$parameter_group <- data$parameter_group[match(results.alltraits.grouping$id, data$id)]
 results.alltraits.grouping$procedure <- data$procedure_name[match(results.alltraits.grouping$id, data$id)]
```

```{r}   
results.alltraits.grouping$GroupingTerm <-  procedures$GroupingTerm[match(results.alltraits.grouping$procedure, procedures$procedure)]

```

check - remove traits #  144,158,160,161,162,163,165,166,167,168, 221,222,231
```{r}
meta1 <- results.alltraits.grouping
```

```{r}
meta1b <- meta1[ !(meta1$id %in% c(144,158,160,161,162,163,165,166,167,168, 221,222,231)), ]

meta1b$parameter_name <- data$parameter_name[match(meta1b$id, data$id)]

```

```{r}
write.csv(meta1b, "meta1.csv")
```

## COLLAPSING DOWN CORRELATED  PARAMETER_NAMES

```{r}
meta1 <- read.csv("meta.csv") # cleaned up data/ cleaned up parameter groups. 
unique(meta1$procedure) #19. Can still get reduced.
unique(meta1$GroupingTerm) #10. sounds reasonable
unique(meta1$parameter_group) # 152 levels. To be used as random factor in meta-meta!
##  test for meta-meta-analysis / collapse confounded parameters!
```

```{r}
meta1 <- read.csv("meta.csv") # cleaned up data/ cleaned up parameter groups. 
unique(meta1$procedure) #19. Can still get reduced.
unique(meta1$GroupingTerm) #10. sounds reasonable
unique(meta1$parameter_group) # 152 levels. To be used as random factor in meta-meta!
```

```{r meta-meta}
# use meta1 , newly loaded (as has been cleaned / checked in excel)

# need to write function to collapse the correlated parametrs down (based on parameter_groups).  For the parameter_groups that are represented more than 1, run meta analysis, the other traits stay as are.  rma(yi = estimate i.e. ln RR / ln CVR / ln VR, se = lnRR_se / lnCVR_se / lnVR_se, method = "FE" )

meta1[,"MetaMeanV"] <-meta1$lnRR_se^2
meta1[,"MetaCVRV"] <-meta1$lnCVR_se^2
meta1[,"MetaVRV"] <-meta1$lnVR_se^2
```

workflow:
count parameter_names per parameter_group, save in new list "par_group_size":
```{r}
meta1 %>%  count(parameter_group) # 152
```
dataframe: most groups have only 1 , it;s only a couple where there's multiple parameter names.

```{r}
meta1b <-
  meta1 %>%
  group_by(parameter_group) %>% 
  summarize(par_group_size = length(unique(parameter_name, na.rm = TRUE)))
#this gives me a summary of number of parameter names in each parameter group, now I neeed to merge it back together

meta1$par_group_size <- meta1b$par_group_size[match(meta1$parameter_group, meta1b$parameter_group)]

```

create subsets: needs to use those that have more than 1 count (par_group_size)

```{r}
meta1_sub<-subset(meta1,par_group_size >1) # 86 observations
```

NEST
```{r}
n_count <- meta1_sub %>% 
  group_by(parameter_group) %>% 
  mutate(raw_N = sum(sampleSize)) %>%  # get the sample sizes as well...??

  nest()
```

FIXED EFFECTS MODEL

#temporary: SE is currently *count, but really should be using the covariance matrix - CAN BE DONE IN  METAFOR??
```{r}
model_count <- n_count %>% 
  mutate(model_lnRR = map(data, ~ rma(yi = lnRR, sei= lnRR_se*par_group_size, method = "FE", data = .)),
        model_lnCVR = map(data, ~ rma(yi = lnCVR, sei= lnCVR_se*par_group_size, method = "FE", data = .)),
        model_lnVR = map(data, ~ rma(yi = lnVR, sei= lnVR_se*par_group_size, method = "FE", data = .)))

 # OLD, to check of ses have changed
sub_model3 <- n_count %>%
  mutate(model_lnRR= map(data, ~ rma(yi = lnRR, sei = lnRR_se, method = "FE", data= .)),
  model_lnCVR= map(data, ~ rma(yi = lnCVR, sei = lnCVR_se, method = "FE", data= .)),
  model_lnVR= map(data, ~ rma(yi = lnVR, sei = lnVR_se, method = "FE", data= .)))

```

 unknot this somehow

```{r}

count_fun <- function(mod_sub)
  coef(summary(mod_sub))[1, c(1,5,6, 2)]

sub_results <- model_count %>% 
  transmute(parameter_group, estimatelnCVR = map(model_lnCVR, count_fun),
            parameter_group, estimatelnVR = map(model_lnVR, count_fun),
            parameter_group, estimatelnRR = map(model_lnRR, count_fun)) %>%
   unnest()

names(sub_results) <- c("parameter_group","lnCVR","lnCVR_lower","lnCVR_upper","lnCVR_se","lnVR",
				"lnVR_lower","lnVR_upper","lnVR_se", "lnRR","lnRR_lower","lnRR_upper","lnRR_se")

########################### seems to be working.

sub3_results <- sub_model3 %>% 
  transmute(parameter_group, estimatelnCVR = map(model_lnCVR, count_fun),
            parameter_group, estimatelnVR = map(model_lnVR, count_fun),
            parameter_group, estimatelnRR = map(model_lnRR, count_fun)) %>%
   unnest()

#print(sub_model$model)

names(sub3_results) <- c("parameter_group","lnCVR","lnCVR_lower","lnCVR_upper","lnCVR_se","lnVR",
				"lnVR_lower","lnVR_upper","lnVR_se", "lnRR","lnRR_lower","lnRR_upper","lnRR_se")

# ok, what is the sample size here??? just the counts of the combined data? But the sample sizes of the single parameters is much higher then???? n_count contains the raw N as well, but don't kno how to extract it

```

merge the two (the new and the initial) datasets back together

```{r}
#5. Merge with set with count = 1
meta_all <- meta1 %>% filter(par_group_size == 1) %>% as_tibble

str(meta_all)
str(sub_results)

col.diff<- which(is.na(match(names(meta_all),names(sub_results))))
```

# combinding
```{r}
combined<-bind_rows(sub_results, meta_all)
glimpse(combined)

```

```{r}
combo <- combined
combo$counts <- meta1$par_group_size[match( combo$parameter_group, meta1$parameter_group)]

combo$procedure2 <-meta1$procedure[match( combo$parameter_group, meta1$parameter_group)]
combo$GroupingTerm2 <-meta1$GroupingTerm[match( combo$parameter_group, meta1$parameter_group)]

```

```{r}
str(combo)
head(combo)
combo <-combo[, c(1:13, 15, 16, 24:26)]
combo <-combo[, c(1, 14:18, 2:13)]
#rename
colnames(combo)[which(names(combo) == c("procedure2", "GroupingTerm2"))] <- c("procedure", "GroupingTerm")
```
# save combo, this is to be used for graphs.

```{r}
#write.csv(combo, "DataMetaCombined.csv"))
```
### PLOTS

```{r}
meta_all <- combo
str(meta_all)
head(meta_all)
```
```{r}
table(meta_all$GroupingTerm)
```

######################################################################
#Create 6 plots of lnCVR, lnCV, lnRR, separate for males and females #

# 1. Males biased (lnCVR, lnCV, lnRR > 0) #

```{r}
meta_all0 <- meta_all[, c("lnCVR", "lnVR", "lnRR", "GroupingTerm")]  
```

```{r}
meta_all1 <- gather(meta_all0, trait, value, lnCVR:lnRR)
meta_all1 <- with(meta_all1, meta_all1[order(trait, GroupingTerm),])

meta_all_malebias0 <- meta_all1 %>%
				group_by_at(vars(trait, GroupingTerm)) %>%
				summarise(malebias0= sum(value > 0), femalebias0= sum(value<= 0), total= sum(value<1000), 
					malepercent= malebias0*100/total, femalepercent= femalebias0*100/total)
print.data.frame(meta_all_malebias0)

malebias0_plot <- ggplot(meta_all_malebias0, aes(GroupingTerm, malepercent)) + 
    	geom_bar(aes(fill = trait), stat= "identity", position= "dodge") +   
	ylab("Percentage of parameters \nwith male bias")  + 
	ylim(0, 100) +
	ggtitle("Male biased sex difference (trait > 0)") + 
	theme_bw(base_size = 18) +
	theme(axis.title.x = element_blank(), panel.grid.major=element_blank(), panel.grid.minor=element_blank(), 
		axis.text.x = element_text(angle = -30), panel.border=element_blank(), axis.line = element_line(colour = "black") ) 
malebias0_plot

```

#--Save plot to pdf:
```{r}
ggsave(malebias0_plot , file="malebias0_plot .pdf", width= 10, height= 5)
```

# 2. Females biased (lnCVR, lnCV, lnRR > 0) #

```{r}
meta_all_femalebias0 <- meta_all1 %>%
				group_by_at(vars(trait, GroupingTerm)) %>%
				summarise(malebias0= sum(value > 0), femalebias0= sum(value<= 0), total= sum(value<1000), 
					malepercent= malebias0*100/total, femalepercent= femalebias0*100/total)
print.data.frame(meta_all_femalebias0)

femalebias0_plot <- ggplot(meta_all_femalebias0, aes(GroupingTerm, femalepercent)) + 
    	geom_bar(aes(fill = trait), stat= "identity", position = "dodge") +
	ylab("Percentage of parameters \nwith female bias")  + 
	ylim(0, 100) +
	ggtitle("Female biased sex difference (trait < 0)") + 
	theme_bw(base_size = 18) +
	theme(axis.title.x = element_blank(), panel.grid.major=element_blank(), panel.grid.minor=element_blank(), 
		axis.text.x = element_text(angle = -30), panel.border=element_blank(), axis.line = element_line(colour = "black") ) 
femalebias0_plot

```

#--Save plot to pdf:
```{r}
ggsave(femalebias0_plot , file="femalebias0_plot .pdf", width= 10, height= 5)

```

###########################################
# 3. Male biased ( delta lnCVR, lnCV, lnRR > 10%) #
 (as above)
meta_all0 <- meta_all[, c("lnCVR", "lnVR", "lnRR", "GroupingTerm")]  #"sampleSize",

meta_all1 <- gather(meta_all0, trait, value, lnCVR:lnRR)
meta_all1 <- with(meta_all1, meta_all1[order(trait, GroupingTerm),])

#choosing male biased ln-ratios of a larger difference in untransformed m/f ratios than 10%
```{r}
meta_all_malebias10perc <- meta_all1 %>%
				group_by_at(vars(trait, GroupingTerm)) %>%
				summarise(malebias10perc= sum(value > log(11/10)), femalebias10perc= sum(value < -log(11/10)), total= sum(value<1000), 
					malepercent= malebias10perc*100 / total, femalepercent= femalebias10perc*100 / total)
print.data.frame(meta_all_malebias10perc)

malebias10perc_plot <- ggplot(meta_all_malebias10perc, aes(GroupingTerm, malepercent)) + 
    	geom_bar(aes(fill = trait), stat= "identity", position = "dodge") +
	ylab("Percentage of parameters \nwith male bias")  + 
	ylim(0, 100) +
	ggtitle("Male biased sex difference (> 10%)") + 
	theme_bw(base_size = 18) +
	theme(axis.title.x = element_blank(), panel.grid.major=element_blank(), panel.grid.minor=element_blank(), 
		axis.text.x = element_text(angle = -30), panel.border=element_blank(), axis.line = element_line(colour = "black") ) 
malebias10perc_plot #missing bars represent 0%

#--Save plot to pdf:
ggsave(malebias10perc_plot , file="malebias10perc_plot .pdf", width= 10, height= 5)

```

###########################################
# 4. Female biased ( delta lnCVR, lnCV, lnRR > 10%) #

#choosing male biased ln-ratios of a larger difference in untransformed m/f ratios than 10%
```{r}
meta_all_malebias10perc <- meta_all1 %>%
				group_by_at(vars(trait, GroupingTerm)) %>%
				summarise(malebias10perc= sum(value > log(11/10)), femalebias10perc= sum(value < -log(11/10)), total= sum(value<1000), 
					malepercent= malebias10perc*100 / total, femalepercent= femalebias10perc*100 / total)
print.data.frame(meta_all_malebias10perc)

femalebias10perc_plot <- ggplot(meta_all_malebias10perc, aes(GroupingTerm, femalepercent)) + 
    	geom_bar(aes(fill = trait), stat= "identity", position = "dodge") +
	ylab("Percentage of parameters \nwith female bias")  + 
	ylim(0, 100) +
	ggtitle("Female biased sex difference (> 10%)") + 
	theme_bw(base_size = 18) +
	theme(axis.title.x = element_blank(), panel.grid.major=element_blank(), panel.grid.minor=element_blank(), 
		axis.text.x = element_text(angle = -30), panel.border=element_blank(), axis.line = element_line(colour = "black") ) 
femalebias10perc_plot #missing bars represent 0%

#--Save plot to pdf:
ggsave(femalebias10perc_plot , file="femalebias10perc_plot.pdf", width= 10, height= 5)
```

###########################################
# 5. Male biased ( delta lnCVR, lnCV, lnRR different from zero) #

#create column with 1= different from zero, 0= zero included in CI

```{r}
meta_all_sig <- meta_all %>% 
    mutate(lnCVRsig = ifelse(lnCVR_lower*lnCVR_upper >0, 1, 0), lnVRsig = ifelse(lnVR_lower*lnVR_upper >0, 1, 0), 
	     lnRRsig = ifelse(lnRR_lower*lnRR_upper > 0, 1,0))

meta_all_sig2 <- meta_all_sig[, c("lnCVR", "lnVR", "lnRR", "lnCVRsig", "lnVRsig", "lnRRsig", "GroupingTerm")]  #"sampleSize",

meta_all_sig3 <- gather(meta_all_sig2, trait, value, lnCVR:lnRR)
meta_all_sig4 <- with(meta_all_sig3, meta_all_sig3[order(trait, GroupingTerm),])
meta_all_sig4$sig <- "placeholder"

meta_all_sig4$sig <- ifelse(meta_all_sig4$trait == "lnCVR", meta_all_sig4$lnCVRsig,
				ifelse(meta_all_sig4$trait == "lnVR", meta_all_sig4$lnVRsig, meta_all_sig4$lnRRsig))

```

#choosing sex biased ln-ratios significantly larger than 0
```{r}
meta_all_malebiasSig0 <- meta_all_sig4 %>%
				group_by_at(vars(trait, GroupingTerm)) %>%
				filter(sig== 1) %>%
				summarise(male_sig= sum(value > 0), female_sig= sum(value < 0)) 
meta_all_malebiasSig1 <- ungroup(meta_all_malebiasSig0) %>%
				add_row(trait = "lnCVR", GroupingTerm = "Hearing", male_sig = 0, female_sig= 0, .before = 4) %>% #add "Hearing" for lnCVR (not filtered as only zeros)
				mutate(total = meta_all_malebias0$total, malepercent= male_sig*100 / total, femalepercent= female_sig*100 / total)

print.data.frame(meta_all_malebiasSig1) #check

malebiasSig1_plot <- ggplot(meta_all_malebiasSig1, aes(GroupingTerm, malepercent)) + 
    	geom_bar(aes(fill = trait), stat= "identity", position = "dodge") +
	ylab("Percentage of parameters \nwith male bias")  + 
	ylim(0, 100) + 
	ggtitle("Male biased sex difference (significant)") + 
	theme_bw(base_size = 18) +
	theme(axis.title.x = element_blank(), panel.grid.major=element_blank(), panel.grid.minor=element_blank(), 
		axis.text.x = element_text(angle = -30), panel.border=element_blank(), axis.line = element_line(colour = "black") ) 
malebiasSig1_plot #missing bars represent 0%

#--Save plot to pdf:
ggsave(malebiasSig1_plot , file="malebiasSig1_plot.pdf", width= 10, height= 5)
```

###########################################
# 6. Female biased ( delta lnCVR, lnCV, lnRR > 10%) #

```{r}
femalebiasSig1_plot <- ggplot(meta_all_malebias10perc, aes(GroupingTerm, femalepercent)) + 
    	geom_bar(aes(fill = trait), stat= "identity", position = "dodge") +
	ylab("Percentage of parameters \nwith female bias")  +
	ylim(0, 100) + 
	ggtitle("Female biased sex difference (significant)") + 
	theme_bw(base_size = 18) +
	theme(axis.title.x = element_blank(), panel.grid.major=element_blank(), panel.grid.minor=element_blank(), 
		axis.text.x = element_text(angle = -30), panel.border=element_blank(), axis.line = element_line(colour = "black") ) 
femalebiasSig1_plot #missing bars represent 0%

#--Save plot to pdf:
ggsave(femalebiasSig1_plot , file="femalebiasSig1_plot.pdf", width= 10, height= 5)

```

### 2019-11-06 scripts/2019_Nov1-FiguresRearranged_IMPC_variance_and_sex_difference.Rmd
Update Nov

--- 2019-11-06 Prep & old/prep and old- scripts/2019_Aug30-NO_VR_IMPC_variance_and_sex_difference.Rmd
@@
 #saveRDS(data_raw, "export/data_clean.rds")
-getwd()
+#getwd()
 data1 <- readRDS("export/data_clean.rds") 
@@
 ### Preparation
-####Define population variable 
+#### Define population variable 
 & add grouping variables
@@
 
-compare
+#compare
 
@@
 
-#### Plot:  FIGURE 2 [Figure 4 in ms] (First-order meta analysis results)
+#### Preparation for plots: Count data, based on First-order meta analysis results
 
@@
         legend.position = "none",
-        axis.title.x = element_blank(),
-	  axis.title.y = element_blank()  ) +
+        axis.title.x = element_blank() ,
+	    axis.title.y =  element_blank()) +
 	coord_flip()
 
-#malebias_Fig2_alltraits
+#malebias_Fig2_alltraits     #(panel A in Figure 4 in ms)
 
@@
   	theme(strip.text.y = element_text(angle = 270, size = 10, margin = margin(t=15, r=15, b=15, l=15)), 
-	  strip.text.x = element_blank(),
+	  strip.text.x = element_text(size = 12),
         strip.background = element_rect(colour = NULL,linetype = "blank", fill = "gray90"),
@@
 	coord_flip()
-# malebias_Fig2_over10
-
-```
-#### Create final combined Figure (Figure 2)
-```{r}
-
-Fig2 <- ggarrange(malebias_Fig2_alltraits, malebias_Fig2_sigtraits,malebias_Fig2_over10, nrow = 3, align = "v", heights = c(1.22,1,1), labels = c("A", "B", "C"))
-Fig2
-ggsave("CountDataCVR_RR_only.pdf", plot = Fig2, width = 6, height = 5) 
-```
-
-###  Overall results of second order meta analysis (Figure 4a)
+
+# malebias_Fig2_over10  (Panel C in Fig 5 in ms)
+
+```
+
+###  Overall results of second order meta analysis (Figure 4: overall, Figure 5: sex-bias)
 #### Restructure data for plotting 
@@
 lnCVR.ci <- overall3 %>% filter(parameter == "lnCVR") %>% mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
-#lnVR.ci <- overall3 %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
+lnVR.ci <- overall3 %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
 lnRR.ci <- overall3 %>% filter(parameter == "lnRR") %>% mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
@@
 
-#### Plot FIGURE 4 (Second-order meta analysis results)
-Preparation: Sub-Plot  for Figure 3: all traits
+#### Preparation for Plots FIGURE 4B & 5B, 5D (Second-order meta analysis results)
+Preparation: Sub-Plot  for Figure 3: all traits (4B)
 ```{r}
@@
         legend.title = element_blank(),
-        axis.title.x = element_blank(),
+        axis.title.x = element_text(hjust = 0.5, size = 14),
 	  axis.title.y = element_blank())
@@
 
-#### Figure 4B- traits with CI not overlapping 0 
+#### Figure 5 - traits with CI not overlapping 0 
 Prepare data 
@@
 
-#plot3.male.meta.VR <- metacombo_male.plot3.VR %>% 
- # mutate(model_lnVR = map(data, ~ metafor::rma.uni(yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower)/ (2*1.96),  
-#				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )
+plot3.male.meta.VR <- metacombo_male.plot3.VR %>% 
+  mutate(model_lnVR = map(data, ~ metafor::rma.uni(yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower)/ (2*1.96),  
+			control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )
 
@@
 
-#plot3.male.meta.VR.b <- as.data.frame(plot3.male.meta.VR %>% group_by(GroupingTerm) %>%  
-#	mutate(lnVR = map_dbl(model_lnVR, pluck(2)), lnVR_lower = map_dbl(model_lnVR, pluck(6)), 
-#	lnVR_upper =map_dbl(model_lnVR, pluck(7)), lnVR_se =map_dbl(model_lnVR, pluck(3))) )[, c(1,4:7)] 
-#plot3.male.meta.VR.b <- plot3.male.meta.VR.b[order(plot3.male.meta.VR.b$GroupingTerm),]
+plot3.male.meta.VR.b <- as.data.frame(plot3.male.meta.VR %>% group_by(GroupingTerm) %>%  
+mutate(lnVR = map_dbl(model_lnVR, pluck(2)), lnVR_lower = map_dbl(model_lnVR, pluck(6)), 
+lnVR_upper =map_dbl(model_lnVR, pluck(7)), lnVR_se =map_dbl(model_lnVR, pluck(3))) )[, c(1,4:7)] 
+plot3.male.meta.VR.b <- plot3.male.meta.VR.b[order(plot3.male.meta.VR.b$GroupingTerm),]
 
@@
 
+#str(overall.male.plot3)
 ```
@@
 
-Plot Fig3 all significant results (CI not overlapping zero) for males
+Plot Fig5b all significant results (CI not overlapping zero) for males
 ```{r}
@@
 #### Female Figure, significant traits
-Female Fig3 sig
+Female Fig5B sig
 
@@
 
-#add missing GroupingTerms for plot POTENTIALLY DELETE
-#overall.female.plot3 <- add_row(overall.female.plot3, GroupingTerm = "Morphology")
-#overall.female.plot3 <- add_row(overall.female.plot3, GroupingTerm = "Metabolism")
-#overall.female.plot3 <- add_row(overall.female.plot3, GroupingTerm = "Hematology")
-#overall.female.plot3 <- add_row(overall.female.plot3, GroupingTerm = "Hearing")
-#overall.female.plot3 <- add_row(overall.female.plot3, GroupingTerm = "Eye")
-
-#overall.female.plot3$GroupingTerm <- factor(overall.female.plot3$GroupingTerm, levels =c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye", "All") )
-#overall.female.plot3$GroupingTerm <- factor(overall.female.plot3$GroupingTerm, rev(levels(overall.female.plot3$GroupingTerm)))
-
 ```
@@
 
-Plot Fig3 all significant results (CI not overlapping zero, female )
+Plot Fig5B all significant results (CI not overlapping zero, female )
 ```{r}
@@
 
-#Metameta_Fig3_female.sig
-```
-
-#### Fig4 C >10%
+#Metameta_Fig3_female.sig (Figure 5B left panel)
+```
+
+#### Fig5 D >10%
 
@@
 
-#### Male Fig 4 > 10% (male biased traits)
+#### Male Fig 5D > 10% (male biased traits)
 ```{r}
@@
 
-#overall.male.plot3.perc <- full_join(plot3.male.meta.CVR.perc.b, plot3.male.meta.VR.perc.b) 
-overall.male.plot3.perc <- full_join(plot3.male.meta.CVR.perc.b, plot3.male.meta.RR.perc.b)
+plot3.male.meta.CVR.Vr.perc <- full_join(plot3.male.meta.CVR.perc.b, plot3.male.meta.VR.perc.b) 
+overall.male.plot3.perc <- full_join(plot3.male.meta.CVR.Vr.perc , plot3.male.meta.RR.perc.b)
 
@@
 
-Plot Fig3 (4 in ms) all >10% difference (male bias)
+Plot Fig5D  all >10% difference (male bias)
 ```{r}
@@
 
-# Metameta_Fig3_male.perc
-```
-
-####Female Fig 3 >10%
+# Metameta_Fig3_male.perc (Figure 5D right panel)
+```
+
+#### Female Fig 5D >10%
 ```{r}
@@
 
-#overall.plot3.perc <- full_join(plot3.meta.CVR.perc.b, plot3.meta.VR.perc.b) 
-overall.plot3.perc <- full_join(plot3.meta.CVR.perc.b, plot3.meta.RR.perc.b)
+plot3.meta.CVR.perc.c <- full_join(plot3.meta.CVR.perc.b, plot3.meta.VR.perc.b) 
+overall.plot3.perc <- full_join(plot3.meta.CVR.perc.c, plot3.meta.RR.perc.b)
 
@@
 
-Plot Fig3 all >10% difference (female)
+Plot Fig5D all >10% difference (female)
 ```{r}
@@
 
-#Metameta_Fig3_female.perc
-
-```
-
-#### Plot Fig4:  all plots combined
+#Metameta_Fig3_female.perc (Figure 5D left panel)
+
+```
+
+#### Plot Fig5:   plots combined
 ```{r}
 library(ggpubr)
-Fig3.bottom <- ggarrange(Metameta_Fig3_female.sig, Metameta_Fig3_male.sig, Metameta_Fig3_female.perc, Metameta_Fig3_male.perc, 
-		   ncol = 2, nrow = 2, widths = c(1, 1.20), heights = c(1, 1))
-
-Fig3 <- ggarrange(Metameta_Fig3_alltraits, Fig3.bottom, ncol = 1, nrow = 2, heights = c(1.4, 2.5))
-Fig3
-#ggsave("MetaResultsCVR_RR.pdf", plot = Fig3, width = 9, height = 6) 
+Fig5b <- ggarrange(Metameta_Fig3_female.sig, Metameta_Fig3_male.sig,  
+		   ncol = 2, nrow = 1, widths = c(1, 1.20), heights = c(1, 1))
+
+Fig5d <- ggarrange(Metameta_Fig3_female.perc, Metameta_Fig3_male.perc,  
+		   ncol = 2, nrow = 1, widths = c(1, 1.20), heights = c(1, 1))
+
+#end combination Figure 5
+
+Fig5 <- ggarrange(malebias_Fig2_sigtraits,  malebias_Fig2_over10, Fig5b,Fig5d,  ncol = 1, nrow = 4, heights = c(2.3,2,2.1,2), labels = c("A", " ", "B", " "))
+Fig5
+
 ```
@@
 results.allhetero.grouping2 <- results.allhetero.grouping[results.allhetero.grouping$s.nlevels.strain.VR != 0, ]
-nrow(results.allhetero.grouping2) #218
+#nrow(results.allhetero.grouping2) #218
 ```
@@
 
-# **Final fixed effects meta-analyses within grouping terms, with SE of the estimate
-
-metacombohetero$var.CVR
+# Final fixed effects meta-analyses within grouping terms, with SE of the estimate
+
+#metacombohetero$var.CVR
 
@@
 
-heterog1
-
 # **Re-structure data for each grouping term; extract heterogenenity/variance terms; delete un-used variables
@@
 
-###Plot FIGURE 4 (5 in ms) (Second-order meta analysis on heterogeneity)
+### Plot FIGURE 4 - C(Second-order meta analysis on heterogeneity)
 
@@
 ```{r}
-
-Metameta_Fig4_alltraits <- heterog4 %>%
-
-  ggplot(aes(y= GroupingTerm, x= value)) +
-  geom_errorbarh(aes(xmin = ci.low, 
-                     xmax = ci.high), 
+heterog5 <- heterog4
+heterog5$mean <- as.numeric(exp(heterog5$value))
+heterog5$ci.l <- as.numeric(exp(heterog5$ci.low))
+heterog5$ci.h <- as.numeric(exp(heterog5$ci.high))
+
+heterog6 <- heterog5
+
+Hetero4c <- 
+heterog6 %>% filter(
+  parameter ==  "heteroCVR" | parameter ==  "heteroRR") %>% 
+  ggplot(aes(y= GroupingTerm, x= mean)) +
+  geom_errorbarh(aes(xmin = ci.l, 
+                     xmax = ci.h), 
 			   height = 0.1, show.legend = FALSE) +
-  geom_point(aes(shape = parameter,
-             fill = parameter, color = parameter), size = 2.2, 
+  geom_point(aes(shape = parameter), fill = 'black',
+             color = 'black', size = 2.2, 
              show.legend = FALSE) +
-  scale_x_continuous(limits=c(-7.0, 1), 
-                     #breaks = c(-2.0, -1.5, -1.0, -0.5, 0, 0.5, 1.0, 1.5, 2.0), 
+  scale_x_continuous(limits=c( -0.1, 1.4), 
+                     #breaks = c(0, 0.1, 0.2), 
+                     name='sigma^2') +
+  #geom_vline(xintercept=0, 
+             #color='black', 
+             #linetype='dashed')+
+  facet_grid(cols = vars(parameter), rows = vars(label),
+             labeller = label_wrap_gen(width = 23),
+             scales= 'free', 
+             space='free')+
+  theme_bw()+
+  theme(strip.text.y = element_text(angle = 270, size = 10, margin = margin(t=15, r=15, b=15, l=15)), 
+	  strip.text.x = element_text(size = 12),
+        strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
+        text = element_text(size = 14),
+        panel.spacing = unit(0.5, "lines"),
+        panel.border= element_blank(),
+        axis.line=element_line(), 
+        panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
+        panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
+        panel.grid.minor.y = element_blank(),
+        panel.grid.minor.x = element_blank(), 
+        legend.title = element_blank(),
+        axis.title.x = element_text(hjust = 0.5, size = 14),
+	  axis.title.y = element_blank())
+
+#Hetero4c
+
+#ggsave("Fig4.pdf", plot = Metameta_Fig4_alltraits, width = 7, height = 6) 
+```
+
+#### Combined Figure 4: overall (Count data, Meta anlysis results, Heterogeneity)
+```{r}
+
+Fig4 <- ggarrange(malebias_Fig2_alltraits, Metameta_Fig3_alltraits, Hetero4c, nrow = 3, align = "v", heights = c(1,1,1), labels = c("A", "B", "C"))
+Fig4
+#ggsave("Fig4_OverallResults.pdf", plot = Fig4, width = 6, height = 5) 
+```
+
+## Supplemental Figures
+```{r}
+## Heterogneity, S1 C
+
+HeteroS1 <- heterog5 %>% 
+  ggplot(aes(y= GroupingTerm, x= mean)) +
+  geom_errorbarh(aes(xmin = ci.l, 
+                     xmax = ci.h), 
+			   height = 0.1, show.legend = FALSE) +
+  geom_point(aes(shape = parameter), fill = 'black',
+             color = 'black', size = 2.2, 
+             show.legend = FALSE) +
+  scale_x_continuous(limits=c( -0.1, 1.4), 
+                     #breaks = c(0, 0.1, 0.2), 
                      name='Effect size') +
+  #geom_vline(xintercept=0, 
+             #color='black', 
+             #linetype='dashed')+
   facet_grid(cols = vars(parameter), rows = vars(label),
@@
 
-Metameta_Fig4_alltraits 
+#HeteroS1
+
 #ggsave("Fig4.pdf", plot = Metameta_Fig4_alltraits, width = 7, height = 6) 
+```
+## Count data, including lnVR (Fig S1 A)
+```{r}
+# *Prepare data for all traits
+
+meta.plot2.all <- meta_clean %>% select(lnCVR, lnVR, lnRR, GroupingTerm) %>% arrange(GroupingTerm)
+
+meta.plot2.all.bS1 <- gather(meta.plot2.all, trait, value, c(lnCVR, lnVR,  lnRR))
+
+meta.plot2.all.bS1$trait <- factor(meta.plot2.all.bS1$trait, levels =c("lnCVR","lnVR", "lnRR") )
+
+meta.plot2.all.cS1 <- meta.plot2.all.bS1  %>%
+				group_by_at(vars(trait, GroupingTerm)) %>%
+				summarise(malebias = sum(value > 0), femalebias = sum(value<= 0), total= malebias + femalebias, 
+					malepercent = malebias*100/total, femalepercent = femalebias*100/total)
+
+meta.plot2.all.cS1$label <- "All traits"
+
+# restructure to create stacked bar plots
+
+meta.plot2.all.dS1 <- as.data.frame(meta.plot2.all.cS1)
+meta.plot2.all.eS1 <- gather(meta.plot2.all.dS1, key = sex, value = percent, malepercent:femalepercent, factor_key = TRUE)
+
+# create new sample size variable
+
+meta.plot2.all.eS1$samplesize <- with(meta.plot2.all.eS1, ifelse(sex == "malepercent", malebias, femalebias) )
+
+malebias_FigS1_alltraits <- 
+ggplot(meta.plot2.all.eS1) +
+  aes(x = GroupingTerm, y = percent, fill = sex) +
+  geom_col() +
+  geom_hline(yintercept = 50, linetype = "dashed", color = "gray40") +
+  geom_text(data = subset(meta.plot2.all.eS1, samplesize != 0), aes(label = samplesize), position = position_stack(vjust = .5), 
+	color = "white", size = 3.5) +
+ facet_grid(cols = vars(trait), rows = vars(label),  labeller = label_wrap_gen(width = 18), 
+      scales= 'free', space='free') +
+ scale_fill_brewer(palette = "Set2") +
+theme_bw(base_size = 18) +
+  	theme(strip.text.y = element_text(angle = 270, size = 10, margin = margin(t=15, r=15, b=15, l=15)), 
+	  strip.text.x = element_text(size = 12),
+        strip.background = element_rect(colour = NULL,linetype = "blank", fill = "gray90"),
+        text = element_text(size=14),
+        panel.spacing = unit(0.5, "lines"),
+        panel.border= element_blank(),
+        axis.line=element_line(), 
+        panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
+        panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
+        panel.grid.minor.y = element_blank(),
+        panel.grid.minor.x = element_blank(), 
+        legend.position = "none",
+        axis.title.x = element_blank() ,
+	    axis.title.y =  element_blank()) +
+	coord_flip()
+
+#malebias_FigS1_alltraits     #(panel A in Figure S1)
+```
+###  Overall results of second order meta analysis (Figure 4: overall, Figure 5: sex-bias), INCLUDING VR
+#### Restructure data for plotting 
+Restructure MALE data for plotting 
+```{r}
+overall3.male.sigS <- gather(overall.male.plot3, parameter, value, c(lnCVR, lnVR, lnRR), factor_key= TRUE)
+
+lnCVR.ci <- overall3.male.sigS  %>% filter(parameter == "lnCVR") %>% mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
+lnVR.ci <- overall3.male.sigS  %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
+lnRR.ci <- overall3.male.sigS  %>% filter(parameter == "lnRR") %>% mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
+
+overall4.male.sigS <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
+
+overall4.male.sigS$label <- "CI not overlapping zero"
+
+```
+Data are restructured, and grouping terms are being re-ordered
+```{r}
+overall3S <- gather(overall2, parameter, value, c(lnCVR, lnVR, lnRR), factor_key= TRUE)
+
+lnCVR.ci <- overall3S %>% filter(parameter == "lnCVR") %>% mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
+lnVR.ci <- overall3S %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
+lnRR.ci <- overall3S %>% filter(parameter == "lnRR") %>% mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
+
+overall4S <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
+
+# re-order Grouping Terms
+
+overall4S$GroupingTerm <- factor(overall4S$GroupingTerm, levels =c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye", "All") )
+overall4S$GroupingTerm <- factor(overall4S$GroupingTerm, rev(levels(overall4S$GroupingTerm)))
+overall4S$label <- "All traits"
+
+```
+
+#### Preparation for Plots FIGURE S1B & S2B, S2D (Second-order meta analysis results, INCL lnVR)
+Preparation: Sub-Plot  for Figure S1: all traits (S1 B)
+```{r}
+Metameta_FigS1_alltraits <- overall4S %>%
+
+  ggplot(aes(y= GroupingTerm, x= value)) +
+  geom_errorbarh(aes(xmin = ci.low, 
+                     xmax = ci.high), 
+			   height = 0.1, show.legend = FALSE) +
+  geom_point(aes(shape = parameter), fill = 'black',
+             color = 'black', size = 2.2, 
+             show.legend = FALSE) +
+  scale_x_continuous(limits=c(-0.24, 0.25), 
+                     breaks = c(-0.2, -0.1, 0, 0.1, 0.2), 
+                     name='Effect size') +
+  geom_vline(xintercept=0, 
+             color='black', 
+             linetype='dashed')+
+  facet_grid(cols = vars(parameter), rows = vars(label),
+             labeller = label_wrap_gen(width = 23),
+             scales= 'free', 
+             space='free')+
+  theme_bw()+
+  theme(strip.text.y = element_text(angle = 270, size = 10, margin = margin(t=15, r=15, b=15, l=15)), 
+	  strip.text.x = element_text(size = 12),
+        strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
+        text = element_text(size = 14),
+        panel.spacing = unit(0.5, "lines"),
+        panel.border= element_blank(),
+        axis.line=element_line(), 
+        panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
+        panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
+        panel.grid.minor.y = element_blank(),
+        panel.grid.minor.x = element_blank(), 
+        legend.title = element_blank(),
+        axis.title.x = element_text(hjust = 0.5, size = 14),
+	  axis.title.y = element_blank())
+
+#Metameta_FigS1_alltraits
+
+```
+
+#### Combined Figure S1: overall Count data, Meta anlysis results, Heterogeneity)
+```{r}
+FigS1 <- ggarrange(malebias_FigS1_alltraits + xlab("percentage sex bias"), Metameta_FigS1_alltraits, HeteroS1, nrow = 3, align = "v", heights = c(1,1,1), labels = c("A", "B", "C"))
+FigS1
+#ggsave("FigS1_OverallResults.pdf", plot = Fig4, width = 6, height = 5)
+
+```
+
+## Figure S2: sex-bias, including VR
+
+Plot FigS2 all significant results (CI not overlapping zero) for males
+```{r}
+meta.plot2.sig.bS <- meta.plot2.sig[, c("lnCVR", "lnVR", "lnRR", "lnCVRsig", "lnVRsig",  "lnRRsig", "GroupingTerm")]
+
+meta.plot2.sig.cS <- gather(meta.plot2.sig.bS, trait, value, lnCVR:lnRR)
+meta.plot2.sig.cS$sig <- "placeholder"
+
+meta.plot2.sig.cS$trait <- factor(meta.plot2.sig.cS$trait, levels =c("lnCVR","lnVR", "lnRR") )
+
+meta.plot2.sig.cS$sig <- ifelse(meta.plot2.sig.cS$trait == "lnCVR", meta.plot2.sig.cS$lnCVRsig,
+				ifelse(meta.plot2.sig.cS$trait == "lnVR", meta.plot2.sig.cS$lnVRsig, meta.plot2.sig.cS$lnRRsig))
+
+#choosing sex biased ln-ratios significantly larger than 0
+meta.plotS2.sig.malebias <- meta.plot2.sig.cS %>%
+				group_by_at(vars(trait, GroupingTerm)) %>%
+				filter(sig== 1) %>%
+				summarise(male_sig = sum(value > 0), female_sig = sum(value < 0), total = male_sig + female_sig)
+
+meta.plotS2.sig.malebias <- ungroup(meta.plotS2.sig.malebias) %>%
+				add_row(trait = "lnCVR", GroupingTerm = "Hearing", male_sig = 0, female_sig = 0, .before = 4) %>% #add "Hearing" for lnCVR (not filtered as only zeros)
+				mutate(malepercent = male_sig*100 / total, femalepercent = female_sig*100 / total)
+
+meta.plotS2.sig.malebias$label <- "CI not overlapping zero"
+
+# restructure to create stacked bar plots
+
+meta.plotS2.sig.bothsexes <- as.data.frame(meta.plotS2.sig.malebias)
+meta.plotS2.sig.bothsexes.b <- gather(meta.plotS2.sig.bothsexes, key = sex, value = percent, malepercent:femalepercent, factor_key = TRUE)
+
+# create new sample size variable
+
+meta.plotS2.sig.bothsexes.b$samplesize <- with(meta.plotS2.sig.bothsexes.b, ifelse(sex == "malepercent", male_sig, female_sig) )
+
+# *Plot Fig2 all significant results (CI not overlapping zero): 
+#     no sig. lnCVR for 'Hearing' in either sex; no sig. male-biased lnCVR for 'Immunology' and 'Eye, and no sig. male-biased lnVR for 'Eye'
+
+malebias_FigS2_sigtraits <-  
+ggplot(meta.plotS2.sig.bothsexes.b) +
+  aes(x = GroupingTerm, y = percent, fill = sex) +
+  geom_col() +
+  geom_hline(yintercept = 50, linetype = "dashed", color = "gray40") +
+  geom_text(data = subset(meta.plotS2.sig.bothsexes.b, samplesize != 0), aes(label = samplesize), position = position_stack(vjust = .5), 
+	color = "white", size = 3.5) +
+ facet_grid(cols = vars(trait), rows = vars(label),  labeller = label_wrap_gen(width = 18), 
+      scales= 'free', space='free') +
+ scale_fill_brewer(palette = "Set2") +
+theme_bw(base_size = 18) +
+  	theme(strip.text.y = element_text(angle = 270, size = 10, margin = margin(t=15, r=15, b=15, l=15)), 
+	  strip.text.x = element_text(size=12),
+        strip.background = element_rect(colour = NULL,linetype = "blank", fill = "gray90"),
+        text = element_text(size=14),
+        panel.spacing = unit(0.5, "lines"),
+        panel.border= element_blank(),
+        axis.line=element_line(), 
+        panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
+        panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
+        panel.grid.minor.y = element_blank(),
+        panel.grid.minor.x = element_blank(), 
+        legend.position = "none",
+        axis.title.x = element_blank(),
+	  axis.title.y = element_blank()  ) +
+	coord_flip()
+
+	#malebias_FigS2_sigtraits # this is Figure S2 A
+
+```
+Prepare data for traits with effect size ratios > 10% larger in males
+```{r}
+meta.plotS2.over10 <- meta_clean %>% select(lnCVR,  lnVR,lnRR, GroupingTerm) %>% arrange(GroupingTerm)
+
+meta.plotS2.over10.b <- gather(meta.plotS2.over10, trait, value, c(lnCVR,  lnVR, lnRR))
+
+meta.plotS2.over10.b$trait <- factor(meta.plotS2.over10.b$trait, levels =c("lnCVR","lnVR","lnRR") )
+
+meta.plotS2.over10.c <- meta.plotS2.over10.b  %>%
+				group_by_at(vars(trait, GroupingTerm)) %>%
+				summarise(malebias = sum(value > log(11/10)), femalebias = sum(value < log(9/10)), total= malebias + femalebias, 
+					malepercent = malebias*100/total, femalepercent = femalebias*100/total)
+
+meta.plotS2.over10.c$label <- "Sex difference in m/f ratios > 10%"
+
+# restructure to create stacked bar plots
+
+meta.plotS2.over10.c <- as.data.frame(meta.plotS2.over10.c)
+meta.plotS2.over10.d <- gather(meta.plotS2.over10.c, key = sex, value = percent, malepercent:femalepercent, factor_key = TRUE)
+
+# create new sample size variable
+
+meta.plotS2.over10.d$samplesize <- with(meta.plotS2.over10.d, ifelse(sex == "malepercent", malebias, femalebias) )
+
+# *Plot FigS2 Sex difference in m/f ratio > 10%
+malebias_FigS2_over10 <- 
+ggplot(meta.plotS2.over10.d) +
+  aes(x = GroupingTerm, y = percent, fill = sex) +
+  geom_col() +
+  geom_hline(yintercept = 50, linetype = "dashed", color = "gray40") +
+  geom_text(data = subset(meta.plot2.over10.d, samplesize != 0), aes(label = samplesize), position = position_stack(vjust = .5), 
+	color = "white", size = 3.5) +
+ facet_grid(cols = vars(trait), rows = vars(label),  labeller = label_wrap_gen(width = 18), 
+      scales= 'free', space='free') +
+ scale_fill_brewer(palette = "Set2") +
+theme_bw(base_size = 18) +
+  	theme(strip.text.y = element_text(angle = 270, size = 10, margin = margin(t=15, r=15, b=15, l=15)), 
+	  strip.text.x = element_blank(),
+        strip.background = element_rect(colour = NULL,linetype = "blank", fill = "gray90"),
+        text = element_text(size=14),
+        panel.spacing = unit(0.5, "lines"),
+        panel.border= element_blank(),
+        axis.line=element_line(), 
+        panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
+        panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
+        panel.grid.minor.y = element_blank(),
+        panel.grid.minor.x = element_blank(), 
+        legend.position = "none",
+        axis.title.x = element_blank(),
+	  axis.title.y = element_blank()  ) +
+	coord_flip()
+
+#malebias_FigS2_over10  #(Panel B in Fig S2 in ms)
+
+```
+
+#### Female Figure, significant traits
+Female FigS2 B sig
+
+Prepare data for traits with CI not overlapping 0
+create column with 1= different from zero, 0= zero included in CI
+
+Restructure data for plotting
+
+```{r}
+overall3.female.sigS <- gather(overall.female.plot3, parameter, value, c(lnCVR, lnVR, lnRR), factor_key= TRUE)
+
+lnCVR.ci <- overall3.female.sigS  %>% filter(parameter == "lnCVR") %>% mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
+lnVR.ci <- overall3.female.sigS  %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
+lnRR.ci <- overall3.female.sigS  %>% filter(parameter == "lnRR") %>% mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
+
+overall4.female.sigS <- bind_rows(lnCVR.ci,lnVR.ci,  lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
+
+overall4.female.sigS$label <- "CI not overlapping zero"
+
+##
+
+Metameta_FigS2_female.sig <- overall4.female.sigS %>%
+  ggplot(aes(y= GroupingTerm, x= value)) +
+  geom_errorbarh(aes(xmin = ci.low,
+                     xmax = ci.high),
+                     height = 0.1, show.legend = FALSE) +
+  geom_point(aes(shape = parameter),
+             fill = 'salmon1', color = 'salmon1', size = 2.2,
+             show.legend = FALSE) +
+  scale_x_continuous(limits=c(-0.4, 0),
+                     breaks = c(-0.3 ,0),
+                     name='Effect size') +
+  geom_vline(xintercept=0,
+             color='black',
+             linetype='dashed')+
+  facet_grid(cols = vars(parameter), #rows = vars(label),
+             #labeller = label_wrap_gen(width = 23),
+             scales= 'free',
+             space='free')+
+  theme_bw()+
+  theme(strip.text.y = element_text(angle = 270, size = 10, margin = margin(t=15, r=15, b=15, l=15)),
+                strip.text.x = element_text(size = 12),
+        strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
+        text = element_text(size = 14),
+        panel.spacing = unit(0.5, "lines"),
+        panel.border= element_blank(),
+        axis.line=element_line(),
+        panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
+        panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
+        panel.grid.minor.y = element_blank(),
+        panel.grid.minor.x = element_blank(),
+        legend.title = element_blank(),
+        axis.title.x = element_blank(),
+                axis.title.y = element_blank())
+
+#Metameta_FigS2_female.sig
+```
+
+#Metameta_FigS2_male.sig (Figure 5B right panel)
+
+Restructure MALE data for plotting 
+```{r}
+overall3.male.sigS <- gather(overall.male.plot3, parameter, value, c(lnCVR, lnVR, lnRR), factor_key= TRUE)
+
+lnCVR.ci <- overall3.male.sigS  %>% filter(parameter == "lnCVR") %>% mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
+lnVR.ci <- overall3.male.sigS  %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
+lnRR.ci <- overall3.male.sigS  %>% filter(parameter == "lnRR") %>% mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
+
+overall4.male.sigS <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
+
+overall4.male.sigS$label <- "CI not overlapping zero"
+
+```
+Plot FigS2 all significant results (CI not overlapping zero, male )
+```{r}
+Metameta_FigS2_male.sig <- overall4.male.sigS %>%
+  ggplot(aes(y= GroupingTerm, x= value)) +
+  geom_errorbarh(aes(xmin = ci.low, 
+                     xmax = ci.high), 
+			   height = 0.1, show.legend = FALSE) +
+  geom_point(aes(shape = parameter),
+             fill = 'mediumaquamarine', color = 'mediumaquamarine', size = 2.2, 
+               show.legend = FALSE) +
+  scale_x_continuous(limits=c(0, 0.4), 
+                     breaks = c(0, 0.3), 
+                     name='Effect size') +
+  geom_vline(xintercept=0, 
+             color='black', 
+             linetype='dashed')+
+  facet_grid(cols = vars(parameter), rows = vars(label),
+             labeller = label_wrap_gen(width = 23),
+             scales= 'free', 
+             space='free')+
+  theme_bw()+
+  theme(strip.text.y = element_text(angle = 270, size = 10, margin = margin(t=15, r=15, b=15, l=15)), 
+	  strip.text.x = element_text(size = 12),
+        strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
+        text = element_text(size = 14),
+        panel.spacing = unit(0.5, "lines"),
+        panel.border= element_blank(),
+        axis.line=element_line(), 
+        panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
+        panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
+        panel.grid.minor.y = element_blank(),
+        panel.grid.minor.x = element_blank(), 
+        legend.title = element_blank(),
+        axis.title.x = element_blank(),
+	  axis.title.y = element_blank())
+
+#Metameta_FigS2_male.sig
+
+```
+### 10 % Perc sex difference, male bias
+Restructure data for plotting : Male biased, 10% difference
+```{r}
+overall3S.perc <- gather(overall.male.plot3.perc, parameter, value, c(lnCVR, lnVR, lnRR), factor_key= TRUE) #lnVR,
+
+lnCVR.ci <- overall3S.perc %>% filter(parameter == "lnCVR") %>% mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
+lnVR.ci <- overall3S.perc  %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
+lnRR.ci <- overall3S.perc  %>% filter(parameter == "lnRR") %>% mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
+
+overall4S.male.perc <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high) #lnVR.ci,
+
+overall4S.male.perc$label <- "Sex difference in m/f ratios > 10%"
+
+overall4S.male.perc$value <- as.numeric(overall4S.male.perc$value)
+overall4S.male.perc$ci.low  <- as.numeric(overall4S.male.perc$ci.low)
+overall4S.male.perc$ci.high <- as.numeric(overall4S.male.perc$ci.high)
+
+```
+
+Plot FigS2  all >10% difference (male bias)
+```{r}
+Metameta_FigS2_male.perc <- overall4S.male.perc %>% #filter(., GroupingTerm != "Hearing") %>%
+  ggplot(aes(y= GroupingTerm, x= value)) +
+  geom_errorbarh(aes(xmin = ci.low, 
+                     xmax = ci.high), 
+			   height = 0.1, show.legend = FALSE) +
+  geom_point(aes(shape = parameter,
+             fill = parameter), color = 'mediumaquamarine', size = 2.2, 
+             show.legend = FALSE) +
+  scale_x_continuous(limits=c(-0.2, 0.62), 
+                     breaks = c(0, 0.3), 
+                     name='Effect size') +
+  geom_vline(xintercept=0, 
+             color='black', 
+             linetype='dashed')+
+  facet_grid(cols = vars(parameter), rows = vars(label),
+             labeller = label_wrap_gen(width = 23),
+             scales= 'free', 
+             space='free')+
+  theme_bw()+
+  theme(strip.text.y = element_text(angle = 270, size = 10, margin = margin(t=15, r=15, b=15, l=15)), 
+	  strip.text.x = element_blank(),
+        strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
+        text = element_text(size = 14),
+        panel.spacing = unit(0.5, "lines"),
+        panel.border= element_blank(),
+        axis.line=element_line(), 
+        panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
+        panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
+        panel.grid.minor.y = element_blank(),
+        panel.grid.minor.x = element_blank(), 
+        legend.title = element_blank(),
+        axis.title.x = element_text(hjust = 0.5, size = 14),
+	  axis.title.y = element_blank())
+
+#Metameta_FigS2_male.perc (Figure 5D right panel)
+```
+Restructure data for plotting: 
+Female bias, 10 percent difference, including VR
+```{r}
+overall3S.perc <- gather(overall.plot3.perc, parameter, value, c(lnCVR, lnVR, lnRR), factor_key= TRUE) #lnVR,
+
+lnCVR.ci <- overall3S.perc %>% filter(parameter == "lnCVR") %>% mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
+lnVR.ci <- overall3S.perc  %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
+lnRR.ci <- overall3S.perc  %>% filter(parameter == "lnRR") %>% mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
+
+overall4S.perc <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
+
+overall4S.perc$label <- "Sex difference in m/f ratios > 10%"
+
+overall4S.perc$value <- as.numeric(overall4S.perc$value)
+overall4S.perc$ci.low  <- as.numeric(overall4S.perc$ci.low)
+overall4S.perc$ci.high <- as.numeric(overall4S.perc$ci.high)
+
+```
+
+Plot Fig5D all >10% difference (female)
+```{r}
+Metameta_Fig3S_female.perc <- overall4S.perc %>% 
+  ggplot(aes(y= GroupingTerm, x= value)) +
+  geom_errorbarh(aes(xmin = ci.low, 
+                     xmax = ci.high), 
+			   height = 0.1, show.legend = FALSE) +
+  geom_point(aes(shape = parameter),
+             fill = 'salmon1', color = 'salmon1', size = 2.2, 
+             show.legend = FALSE) +
+
+#scale_shape_manual(values =
+
+  scale_x_continuous(limits=c(-0.53, 0.2), 
+                     breaks = c(-0.3, 0), 
+                     name='Effect size') +
+  geom_vline(xintercept=0, 
+             color='black', 
+             linetype='dashed')+
+  facet_grid(cols = vars(parameter), #rows = vars(label),
+             #labeller = label_wrap_gen(width = 23),
+             scales= 'free', 
+             space='free')+
+  theme_bw()+
+  theme(strip.text.y = element_text(angle = 270, size = 10, margin = margin(t=15, r=15, b=15, l=15)), 
+	  strip.text.x = element_blank(),
+        strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
+        text = element_text(size = 14),
+        panel.spacing = unit(0.5, "lines"),
+        panel.border= element_blank(),
+        axis.line=element_line(), 
+        panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
+        panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
+        panel.grid.minor.y = element_blank(),
+        panel.grid.minor.x = element_blank(), 
+        legend.title = element_blank(),
+        axis.title.x = element_text(hjust = 0.5, size = 14),
+	  axis.title.y = element_blank())
+
+#Metameta_Fig3S_female.perc (Figure 5D left panel)
+
+```
+Figure S2 
+```{r}
+FigS2c <- ggarrange(Metameta_FigS2_female.sig, Metameta_FigS2_male.sig,  
+		   ncol = 2, nrow = 1, widths = c(1, 1.20), heights = c(1, 1))
+
+FigS2d <- ggarrange(Metameta_Fig3S_female.perc, Metameta_FigS2_male.perc,  
+		   ncol = 2, nrow = 1, widths = c(1, 1.20), heights = c(1, 1))
+
+#end combination Figure 5
+
+FigS2 <- ggarrange(malebias_FigS2_sigtraits,  malebias_FigS2_over10, FigS2c,FigS2d,  ncol = 1, nrow = 4, heights = c(2.2,2,2.2,2), labels = c("A", " ", "B", " "))
+FigS2
+
 ```

### 2019-11-20 scripts/2019_Nov1-FiguresRearranged_IMPC_variance_and_sex_difference.Rmd
Ensure grouping variable is removed.
In tidyr 0.8.3, nest removes the group variable. But in tydr 1.0.0 the bahviour changes. Adding ungroup should ensure some consistency

@@
 library(ggplot2)
+
 ```
@@
   mutate(raw_N = sum(sampleSize)) %>%  
-    nest()
+  nest() %>% 
+  ungroup()
 
@@
 robu_all <- full_join(robusub_CVR, robusub_VR) %>% full_join(., robusub_RR)
+```
+
+```{r}
 kable(cbind(robu_all, robu_all)) %>%
@@
   scroll_box(width = "100%", height = "200px")
-
 ```

### 2019-11-21 scripts/2019_Nov1-FiguresRearranged_IMPC_variance_and_sex_difference.Rmd
Restyle using styler and use `here` package for rubst loading

--- 2019-11-06 Prep & old/prep and old- scripts/2019_Aug30-NO_VR_IMPC_variance_and_sex_difference.Rmd
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE,
+knitr::opts_chunk$set(
+  echo = TRUE,
   warning = FALSE,
@@
   cache = TRUE,
-                      tidy = TRUE)
-
-```
-
-```{r, include=FALSE}
-getwd()
+  tidy = TRUE
+)
+
 ```
@@
 library(ggplot2)
+library(here)
 ```
@@
     ungroup() %>%
-    filter(n_sex ==2) %>% 
+    filter(n_sex == 2) %>%
     select(-n_sex) %>%
@@
 
-  mydata[i,] %>% 
+  mydata[i, ] %>%
     select(strain_name, production_center, trait) %>%
@@
     )
-
 }
@@
 
-Calc.lnCVR <- function(CMean, CSD, CN, EMean, ESD, EN){
-  log(ESD) - log(EMean) + 1 / (2*(EN - 1)) - (log(CSD) - log(CMean) + 1 / (2*(CN - 1)))
+Calc.lnCVR <- function(CMean, CSD, CN, EMean, ESD, EN) {
+  log(ESD) - log(EMean) + 1 / (2 * (EN - 1)) - (log(CSD) - log(CMean) + 1 / (2 * (CN - 1)))
 }
 
-Calc.var.lnCVR <- function(CMean, CSD, CN, EMean, ESD, EN, Equal.E.C.Corr=T) {
-  if(Equal.E.C.Corr==T){
-    mvcorr <- 0 #cor.test(log(c(CMean, EMean)), log(c(CSD, ESD)))$estimate   old, slightly incorrect
+Calc.var.lnCVR <- function(CMean, CSD, CN, EMean, ESD, EN, Equal.E.C.Corr = T) {
+  if (Equal.E.C.Corr == T) {
+    mvcorr <- 0 # cor.test(log(c(CMean, EMean)), log(c(CSD, ESD)))$estimate   old, slightly incorrect
     S2 <- CSD^2 / (CN * (CMean^2)) + 1 / (2 * (CN - 1)) - 2 * mvcorr * sqrt((CSD^2 / (CN * (CMean^2))) * (1 / (2 * (CN - 1)))) + ESD^2 / (EN * (EMean^2)) + 1 / (2 * (EN - 1)) - 2 * mvcorr * sqrt((ESD^2 / (EN * (EMean^2))) * (1 / (2 * (EN - 1))))
   }
-  else{
+  else {
     Cmvcorr <- cor.test(log(CMean), log(CSD))$estimate
@@
 
-Calc.lnVR <- function(CSD, CN, ESD, EN){
-  log(ESD) - log(CSD) + 1 / (2*(EN - 1)) - 1 / (2*(CN - 1))
+Calc.lnVR <- function(CSD, CN, ESD, EN) {
+  log(ESD) - log(CSD) + 1 / (2 * (EN - 1)) - 1 / (2 * (CN - 1))
 }
 
-Calc.var.lnVR <- function( CN,  EN) {
-  1 / (2*(EN - 1)) + 1 / (2*(CN - 1))
+Calc.var.lnVR <- function(CN, EN) {
+  1 / (2 * (EN - 1)) + 1 / (2 * (CN - 1))
 }
@@
 Calc.var.lnRR <- function(CMean, CSD, CN, EMean, ESD, EN) {
-  CSD^2/(CN * CMean^2) + ESD^2/(EN * EMean^2)
+  CSD^2 / (CN * CMean^2) + ESD^2 / (EN * EMean^2)
 }
-
 ```
@@
     # Fileter to IMPC source (recommened by Jeremey in email to Susi on 20 Aug 2018)
-    filter(datasource_name == 'IMPC') %>%
+    filter(datasource_name == "IMPC") %>%
 
     # standardise trait names
-    mutate(parameter_name = tolower(parameter_name) ) %>%
+    mutate(parameter_name = tolower(parameter_name)) %>%
 
@@
 ```{r}
-#2) Subsetting the data to choose only one data point per individual per trait
+# 2) Subsetting the data to choose only one data point per individual per trait
 
@@
   tmp <- mydata %>%
-    filter(age_in_days >= age_min,
-           id == parameter) %>%
+    filter(
+      age_in_days >= age_min,
+      id == parameter
+    ) %>%
     # take results for single individual closest to age_center
@@
 ## Load raw data - save cleaned dataset as RDS for reuse
-#data_raw <- load_raw("data/dr7.0_all_control_data.csv") %>%
+# data_raw <- load_raw("data/dr7.0_all_control_data.csv") %>%
 #    clean_raw_data()
-#dir.create("export", F, F)
-#saveRDS(data_raw, "export/data_clean.rds")
-getwd()
-data1 <- readRDS("export/data_clean.rds") 
-#data1 
+# dir.create("export", F, F)
+# saveRDS(data_raw, "export/data_clean.rds")
+# getwd()
+data1 <- readRDS(here("export", "data_clean.rds"))
+# data1
 ```
@@
 data2 <- dat_moreThan1center
-#min(data2$center_per_trait)  # as a check if there indeed are no single occurences
-
+# min(data2$center_per_trait)  # as a check if there indeed are no single occurences
 ```
@@
 
- group <- read.csv("export/ParameterGrouping.csv") 
+group <- read.csv(here("export", "ParameterGrouping.csv"))
 data <- data3
@@
 ```{r}
-#head(data)
+# head(data)
 
@@
 data <- transform(data, id = match(parameter_name, unique(parameter_name)))
-n1 <- length(unique(data$parameter_name)) #232
-n2 <- length(unique(data$parameter_group)) #161
+n1 <- length(unique(data$parameter_name)) # 232
+n2 <- length(unique(data$parameter_group)) # 161
 n3 <- length(unique(data$procedure_name)) # 26
@@
 n <- length(unique(data$id))
-#n  # just to check that the number of traits is 232
+# n  # just to check that the number of traits is 232
 ```
@@
 ```{r}
-results.alltraits.grouping <- as.data.frame(cbind(c(1:n), matrix(rep(0, n*14), ncol = 14))) #number of individual results per trait = 10
-names(results.alltraits.grouping) <- c("id", "lnCVR", "lnCVR_lower", "lnCVR_upper", "lnCVR_se", "lnVR", "lnVR_lower", "lnVR_upper", "lnVR_se", "lnRR", "lnRR_lower", "lnRR_upper" ,"lnRR_se" , "sampleSize", "trait")
+results.alltraits.grouping <- as.data.frame(cbind(c(1:n), matrix(rep(0, n * 14), ncol = 14))) # number of individual results per trait = 10
+names(results.alltraits.grouping) <- c("id", "lnCVR", "lnCVR_lower", "lnCVR_upper", "lnCVR_se", "lnVR", "lnVR_lower", "lnVR_upper", "lnVR_se", "lnRR", "lnRR_lower", "lnRR_upper", "lnRR_se", "sampleSize", "trait")
 ```
@@
 
-for(t in 1:n) {
-
-  tryCatch({
-
+for (t in 1:n) {
+  tryCatch(
+    {
       data_par_age <- data_subset_parameterid_individual_by_age(data, t, age_min = 0, age_center = 100)
@@
 
-#lnCVR,  log repsonse-ratio of the coefficient of variance    
-    cvr <- metafor::rma.mv(yi = effect_size_CVR, V = sample_variance_CVR, random = list(~1| strain_name, ~1|production_center, ~1|err), control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000),  verbose=F, data = results)
+      # lnCVR,  log repsonse-ratio of the coefficient of variance
+      cvr <- metafor::rma.mv(yi = effect_size_CVR, V = sample_variance_CVR, 
+                             random = list(~ 1 | strain_name, ~ 1 | production_center, ~ 1 | err), control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F, data = results)
 
@@
 
-    #lnVR, comparison of standard deviations
-
-cv <- metafor::rma.mv(yi = effect_size_VR, V = sample_variance_VR, random = list(~1| strain_name, ~1|production_center,~1|err), control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000),  verbose=F, data = results)
+      # lnVR, comparison of standard deviations
+
+      cv <- metafor::rma.mv(yi = effect_size_VR, V = sample_variance_VR, random = list(~ 1 | strain_name, ~ 1 | production_center, ~ 1 | err), control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F, data = results)
 
@@
 
-means <- metafor::rma.mv(yi = effect_size_RR, V = sample_variance_RR, random = list(~1| strain_name, ~1|production_center, ~1|err), control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), data = results)
+      means <- metafor::rma.mv(yi = effect_size_RR, V = sample_variance_RR, random = list(~ 1 | strain_name, ~ 1 | production_center, ~ 1 | err), control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), data = results)
       results.alltraits.grouping[t, 10] <- means$b
@@
       results.alltraits.grouping[t, 15] <- unique(results$trait)
-
-  }, error=function(e){cat("ERROR :",conditionMessage(e), "\n")})
+    },
+    error = function(e) {
+      cat("ERROR :", conditionMessage(e), "\n")
+    }
+  )
 }
@@
 ## Note Susi 31/7/2019: This dataset contains dublicated values, plus no info on what the "traits" mean. I will change Dan N's to one further belwo, that have been cleaned up already
-#FILE TO USE: METACOMBO (around line 500)
-
-#trait_meta_results <- write.csv(results.alltraits.grouping, file = "export/trait_meta_results.csv")
-
+# FILE TO USE: METACOMBO (around line 500)
+
+# trait_meta_results <- write.csv(results.alltraits.grouping, file = "export/trait_meta_results.csv")
 ```
@@
 ```{r}
-procedures <- read.csv("export/procedures.csv")
+procedures <- read.csv(here("export", "procedures.csv"))
 
@@
 ```{r}
-meta_clean <- meta1[ !(meta1$id %in% c(84,144,158,160,161,162,163,165,166,167,168,221,222,231)), ]
-removed <-length(unique(meta_clean$parameter_name)) #218
-
-meta_problem <- results.alltraits.grouping[ (results.alltraits.grouping$id %in% c(84,144,158,160,161,162,163,165,166,167,168,221,222,231)), ]
+meta_clean <- meta1[ !(meta1$id %in% c(84, 144, 158, 160, 161, 162, 163, 165, 166, 167, 168, 221, 222, 231)), ]
+removed <- length(unique(meta_clean$parameter_name)) # 218
+
+meta_problem <- results.alltraits.grouping[ (results.alltraits.grouping$id %in% c(84, 144, 158, 160, 161, 162, 163, 165, 166, 167, 168, 221, 222, 231)), ]
 ```
@@
 To be used as grouping factor for meta-meta analysis / collapsing down based on things that are classified identically in "parameter_group" but have different "parameter_name"
-#length(unique(meta1$parameter_name)) #218
-
+# length(unique(meta1$parameter_name)) #218
 ```
@@
 
-kable(cbind (meta1 %>%  count(parameter_group) )) %>%
+kable(cbind(meta1 %>% count(parameter_group))) %>%
   kable_styling() %>%
@@
   summarize(par_group_size = length(unique(parameter_name, na.rm = TRUE)))
-#this gives a summary of number of parameter names in each parameter group, now it neeeds to get merged it back together
+# this gives a summary of number of parameter names in each parameter group, now it neeeds to get merged it back together
 
@@
 
-meta1_sub<-subset(meta1,par_group_size >1) # 90 observations   
+meta1_sub <- subset(meta1, par_group_size > 1) # 90 observations
 meta1_sub$sampleSize <- as.numeric(meta1_sub$sampleSize)
-
 ```
@@
   mutate(raw_N = sum(sampleSize)) %>%
-    nest()
+  nest() %>%
+  ungroup()
 
 model_count <- n_count %>%
-  mutate(model_lnRR = map(data, ~ robu(.x$lnRR ~ 1, data= .x, studynum= .x$id, modelweights = c("CORR"), rho = 0.8, small = TRUE, var.eff.size= (.x$lnRR_se)^2 )),
-  model_lnVR = map(data, ~ robu(.x$lnVR ~ 1, data= .x, studynum= .x$id, modelweights = c("CORR"), rho = 0.8, small = TRUE, var.eff.size= (.x$lnVR_se)^2 )),
-  model_lnCVR = map(data, ~ robu(.x$lnCVR ~ 1, data= .x, studynum= .x$id, modelweights = c("CORR"), rho = 0.8, small = TRUE, var.eff.size= (.x$lnCVR_se)^2 ))) 
+  mutate(
+    model_lnRR = map(data, ~ robu(.x$lnRR ~ 1, data = .x, studynum = .x$id, modelweights = c("CORR"), rho = 0.8, small = TRUE, var.eff.size = (.x$lnRR_se)^2)),
+    model_lnVR = map(data, ~ robu(.x$lnVR ~ 1, data = .x, studynum = .x$id, modelweights = c("CORR"), rho = 0.8, small = TRUE, var.eff.size = (.x$lnVR_se)^2)),
+    model_lnCVR = map(data, ~ robu(.x$lnCVR ~ 1, data = .x, studynum = .x$id, modelweights = c("CORR"), rho = 0.8, small = TRUE, var.eff.size = (.x$lnCVR_se)^2))
+  )
 ```
@@
 ```{r}
-count_fun <- function(mod_sub)
-  return(c(mod_sub$reg_table$b.r, mod_sub$reg_table$CI.L, mod_sub$reg_table$CI.U, mod_sub$reg_table$SE))   #estimate, lower ci, upper ci, SE
+count_fun <- function(mod_sub) {
+  return(c(mod_sub$reg_table$b.r, mod_sub$reg_table$CI.L, mod_sub$reg_table$CI.U, mod_sub$reg_table$SE))
+} # estimate, lower ci, upper ci, SE
 ```
@@
   select(-estimatelnRR) %>%
-  purrr::set_names(c("parameter_group","lnRR","lnRR_lower","lnRR_upper","lnRR_se"))
+  purrr::set_names(c("parameter_group", "lnRR", "lnRR_lower", "lnRR_upper", "lnRR_se"))
 
@@
   select(-estimatelnCVR) %>%
-  purrr::set_names(c("parameter_group","lnCVR","lnCVR_lower","lnCVR_upper","lnCVR_se"))
+  purrr::set_names(c("parameter_group", "lnCVR", "lnCVR_lower", "lnCVR_upper", "lnCVR_se"))
 
@@
   select(-estimatelnVR) %>%
-  purrr::set_names(c("parameter_group","lnVR","lnVR_lower","lnVR_upper","lnVR_se"))
+  purrr::set_names(c("parameter_group", "lnVR", "lnVR_lower", "lnVR_upper", "lnVR_se"))
 
 robu_all <- full_join(robusub_CVR, robusub_VR) %>% full_join(., robusub_RR)
+```
+
+```{r}
 kable(cbind(robu_all, robu_all)) %>%
@@
 ```{r}
-meta_all <- meta1 %>% filter(par_group_size == 1) %>% as_tibble
-#str(meta_all)
-#str(robu_all)
-#which(is.na(match(names(meta_all),names(robu_all))))  # check
+meta_all <- meta1 %>%
+  filter(par_group_size == 1) %>%
+  as_tibble()
+# str(meta_all)
+# str(robu_all)
+# which(is.na(match(names(meta_all),names(robu_all))))  # check
 ```
@@
 combinedmeta <- bind_rows(robu_all, meta_all)
-#glimpse(combinedmeta)
+# glimpse(combinedmeta)
 
@@
 metacombo <- combinedmeta
-metacombo$counts <- meta1$par_group_size[match( metacombo$parameter_group, meta1$parameter_group)]
-metacombo$procedure2 <-meta1$procedure[match( metacombo$parameter_group, meta1$parameter_group)]
-metacombo$GroupingTerm2 <-meta1$GroupingTerm[match( metacombo$parameter_group, meta1$parameter_group)]
-
-kable(cbind (metacombo, metacombo)) %>%
+metacombo$counts <- meta1$par_group_size[match(metacombo$parameter_group, meta1$parameter_group)]
+metacombo$procedure2 <- meta1$procedure[match(metacombo$parameter_group, meta1$parameter_group)]
+metacombo$GroupingTerm2 <- meta1$GroupingTerm[match(metacombo$parameter_group, meta1$parameter_group)]
+
+kable(cbind(metacombo, metacombo)) %>%
   kable_styling() %>%
   scroll_box(width = "100%", height = "200px")
-
 ```
@@
 ```{r}
-metacombo <-metacombo[, c(1, 21:23, 2:13)] 
+metacombo <- metacombo[, c(1, 21:23, 2:13)]
 names(metacombo)[3] <- "procedure"
@@
   group_by(GroupingTerm) %>%
-  dplyr::summarize(MeanCVR = mean(lnCVR),MeanVR = mean(lnVR), MeanRR = mean(lnRR) )
-
-compare
-
+  dplyr::summarize(MeanCVR = mean(lnCVR), MeanVR = mean(lnVR), MeanRR = mean(lnRR))
+
+# compare
 ```
@@
 ## Note Susi 31/7/2019: This has been cleaned up already
-#FILE TO USE: METACOMBO 
+# FILE TO USE: METACOMBO
 ### note: to use
 
-#trait_meta_results <- write.csv(metacombo, file = "export/trait_meta_results.csv")
+# trait_meta_results <- write.csv(metacombo, file = "export/trait_meta_results.csv")
 ```
@@
 
-kable(cbind (metacombo,metacombo)) %>%
+kable(cbind(metacombo, metacombo)) %>%
   kable_styling() %>%
   scroll_box(width = "100%", height = "200px")
-
 ```
@@
 
-  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower)/ (2*1.96),  
-				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)),
-	   model_lnVR = map(data, ~ metafor::rma.uni(yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower)/ (2*1.96),  
-				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)),
-	   model_lnRR = map(data, ~ metafor::rma.uni(yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower)/ (2*1.96),  
-				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)))
+  mutate(
+    model_lnCVR = map(data, ~ metafor::rma.uni(
+      yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower) / (2 * 1.96),
+      control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+    )),
+    model_lnVR = map(data, ~ metafor::rma.uni(
+      yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
+      control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+    )),
+    model_lnRR = map(data, ~ metafor::rma.uni(
+      yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
+      control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+    ))
+  )
 
@@
 
-  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower)/ (2*1.96),  
-				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)),
-	   model_lnVR = map(data, ~ metafor::rma.uni(yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower)/ (2*1.96),  
-				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)),
-	   model_lnRR = map(data, ~ metafor::rma.uni(yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower)/ (2*1.96),  
-				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)))
-
+  mutate(
+    model_lnCVR = map(data, ~ metafor::rma.uni(
+      yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower) / (2 * 1.96),
+      control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+    )),
+    model_lnVR = map(data, ~ metafor::rma.uni(
+      yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
+      control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+    )),
+    model_lnRR = map(data, ~ metafor::rma.uni(
+      yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
+      control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+    ))
+  )
 ```
@@
 ```{r}
-Behaviour <- as.data.frame(overall1 %>% filter(., GroupingTerm == "Behaviour")    %>%  mutate(lnCVR=.[[4]][[1]]$b, lnCVR_lower=.[[4]][[1]]$ci.lb, lnCVR_upper=.[[4]][[1]]$ci.ub, lnCVR_se=.[[4]][[1]]$se,
-	              lnVR=.[[5]][[1]]$b, lnVR_lower=.[[5]][[1]]$ci.lb, lnVR_upper=.[[5]][[1]]$ci.ub, lnVR_se=.[[5]][[1]]$se,
-		        lnRR=.[[6]][[1]]$b, lnRR_lower=.[[6]][[1]]$ci.lb, lnRR_upper=.[[6]][[1]]$ci.ub, lnRR_se=.[[6]][[1]]$se) )[, c(1,7:18)]
-
-Immunology <- as.data.frame(overall1 %>% filter(., GroupingTerm == "Immunology")    %>%  mutate(lnCVR=.[[4]][[1]]$b, lnCVR_lower=.[[4]][[1]]$ci.lb, lnCVR_upper=.[[4]][[1]]$ci.ub, lnCVR_se=.[[4]][[1]]$se,
-	              lnVR=.[[5]][[1]]$b, lnVR_lower=.[[5]][[1]]$ci.lb, lnVR_upper=.[[5]][[1]]$ci.ub, lnVR_se=.[[5]][[1]]$se,
-		        lnRR=.[[6]][[1]]$b, lnRR_lower=.[[6]][[1]]$ci.lb, lnRR_upper=.[[6]][[1]]$ci.ub, lnRR_se=.[[6]][[1]]$se) )[, c(1,7:18)]
-
-Hematology <- as.data.frame(overall1 %>% filter(., GroupingTerm == "Hematology")    %>%  mutate(lnCVR=.[[4]][[1]]$b, lnCVR_lower=.[[4]][[1]]$ci.lb, lnCVR_upper=.[[4]][[1]]$ci.ub, lnCVR_se=.[[4]][[1]]$se,
-	              lnVR=.[[5]][[1]]$b, lnVR_lower=.[[5]][[1]]$ci.lb, lnVR_upper=.[[5]][[1]]$ci.ub, lnVR_se=.[[5]][[1]]$se,
-		        lnRR=.[[6]][[1]]$b, lnRR_lower=.[[6]][[1]]$ci.lb, lnRR_upper=.[[6]][[1]]$ci.ub, lnRR_se=.[[6]][[1]]$se) )[, c(1,7:18)]
-
-Hearing <- as.data.frame(overall1 %>% filter(., GroupingTerm == "Hearing")   %>%  mutate(lnCVR=.[[4]][[1]]$b, lnCVR_lower=.[[4]][[1]]$ci.lb, lnCVR_upper=.[[4]][[1]]$ci.ub, lnCVR_se=.[[4]][[1]]$se,
-	              lnVR=.[[5]][[1]]$b, lnVR_lower=.[[5]][[1]]$ci.lb, lnVR_upper=.[[5]][[1]]$ci.ub, lnVR_se=.[[5]][[1]]$se,
-		        lnRR=.[[6]][[1]]$b, lnRR_lower=.[[6]][[1]]$ci.lb, lnRR_upper=.[[6]][[1]]$ci.ub, lnRR_se=.[[6]][[1]]$se) )[, c(1,7:18)]
-
-Physiology <- as.data.frame(overall1 %>% filter(., GroupingTerm == "Physiology")  %>%  mutate(lnCVR=.[[4]][[1]]$b, lnCVR_lower=.[[4]][[1]]$ci.lb, lnCVR_upper=.[[4]][[1]]$ci.ub, lnCVR_se=.[[4]][[1]]$se,
-	              lnVR=.[[5]][[1]]$b, lnVR_lower=.[[5]][[1]]$ci.lb, lnVR_upper=.[[5]][[1]]$ci.ub, lnVR_se=.[[5]][[1]]$se,
-		        lnRR=.[[6]][[1]]$b, lnRR_lower=.[[6]][[1]]$ci.lb, lnRR_upper=.[[6]][[1]]$ci.ub, lnRR_se=.[[6]][[1]]$se) )[, c(1,7:18)]
-
-Metabolism <- as.data.frame(overall1 %>% filter(., GroupingTerm == "Metabolism")  %>%  mutate(lnCVR=.[[4]][[1]]$b, lnCVR_lower=.[[4]][[1]]$ci.lb, lnCVR_upper=.[[4]][[1]]$ci.ub, lnCVR_se=.[[4]][[1]]$se,
-	              lnVR=.[[5]][[1]]$b, lnVR_lower=.[[5]][[1]]$ci.lb, lnVR_upper=.[[5]][[1]]$ci.ub, lnVR_se=.[[5]][[1]]$se,
-		        lnRR=.[[6]][[1]]$b, lnRR_lower=.[[6]][[1]]$ci.lb, lnRR_upper=.[[6]][[1]]$ci.ub, lnRR_se=.[[6]][[1]]$se) )[, c(1,7:18)]
-
-Morphology <- as.data.frame(overall1 %>% filter(., GroupingTerm == "Morphology")  %>%  mutate(lnCVR=.[[4]][[1]]$b, lnCVR_lower=.[[4]][[1]]$ci.lb, lnCVR_upper=.[[4]][[1]]$ci.ub, lnCVR_se=.[[4]][[1]]$se,
-	              lnVR=.[[5]][[1]]$b, lnVR_lower=.[[5]][[1]]$ci.lb, lnVR_upper=.[[5]][[1]]$ci.ub, lnVR_se=.[[5]][[1]]$se,
-		        lnRR=.[[6]][[1]]$b, lnRR_lower=.[[6]][[1]]$ci.lb, lnRR_upper=.[[6]][[1]]$ci.ub, lnRR_se=.[[6]][[1]]$se) )[, c(1,7:18)]
-
-Heart <- as.data.frame(overall1 %>% filter(., GroupingTerm == "Heart")  %>%  mutate(lnCVR=.[[4]][[1]]$b, lnCVR_lower=.[[4]][[1]]$ci.lb, lnCVR_upper=.[[4]][[1]]$ci.ub, lnCVR_se=.[[4]][[1]]$se,
-	              lnVR=.[[5]][[1]]$b, lnVR_lower=.[[5]][[1]]$ci.lb, lnVR_upper=.[[5]][[1]]$ci.ub, lnVR_se=.[[5]][[1]]$se,
-		        lnRR=.[[6]][[1]]$b, lnRR_lower=.[[6]][[1]]$ci.lb, lnRR_upper=.[[6]][[1]]$ci.ub, lnRR_se=.[[6]][[1]]$se) )[, c(1,7:18)]
-
-Eye <- as.data.frame(overall1 %>% filter(., GroupingTerm == "Eye")  %>%  mutate(lnCVR=.[[4]][[1]]$b, lnCVR_lower=.[[4]][[1]]$ci.lb, lnCVR_upper=.[[4]][[1]]$ci.ub, lnCVR_se=.[[4]][[1]]$se,
-	              lnVR=.[[5]][[1]]$b, lnVR_lower=.[[5]][[1]]$ci.lb, lnVR_upper=.[[5]][[1]]$ci.ub, lnVR_se=.[[5]][[1]]$se,
-		        lnRR=.[[6]][[1]]$b, lnRR_lower=.[[6]][[1]]$ci.lb, lnRR_upper=.[[6]][[1]]$ci.ub, lnRR_se=.[[6]][[1]]$se) )[, c(1,7:18)]
-
-All <- as.data.frame(overall_all1  %>%  mutate(lnCVR=.[[2]][[1]]$b, lnCVR_lower=.[[2]][[1]]$ci.lb, lnCVR_upper=.[[2]][[1]]$ci.ub, lnCVR_se=.[[2]][[1]]$se,lnVR=.[[3]][[1]]$b, lnVR_lower=.[[3]][[1]]$ci.lb, lnVR_upper=.[[3]][[1]]$ci.ub, lnVR_se=.[[3]][[1]]$se,
-		        lnRR=.[[4]][[1]]$b, lnRR_lower=.[[4]][[1]]$ci.lb, lnRR_upper=.[[4]][[1]]$ci.ub, lnRR_se=.[[4]][[1]]$se) )[, c(5:16)]
+Behaviour <- as.data.frame(overall1 %>% filter(., GroupingTerm == "Behaviour") %>% mutate(
+  lnCVR = .[[4]][[1]]$b, lnCVR_lower = .[[4]][[1]]$ci.lb, lnCVR_upper = .[[4]][[1]]$ci.ub, lnCVR_se = .[[4]][[1]]$se,
+  lnVR = .[[5]][[1]]$b, lnVR_lower = .[[5]][[1]]$ci.lb, lnVR_upper = .[[5]][[1]]$ci.ub, lnVR_se = .[[5]][[1]]$se,
+  lnRR = .[[6]][[1]]$b, lnRR_lower = .[[6]][[1]]$ci.lb, lnRR_upper = .[[6]][[1]]$ci.ub, lnRR_se = .[[6]][[1]]$se
+))[, c(1, 7:18)]
+
+Immunology <- as.data.frame(overall1 %>% filter(., GroupingTerm == "Immunology") %>% mutate(
+  lnCVR = .[[4]][[1]]$b, lnCVR_lower = .[[4]][[1]]$ci.lb, lnCVR_upper = .[[4]][[1]]$ci.ub, lnCVR_se = .[[4]][[1]]$se,
+  lnVR = .[[5]][[1]]$b, lnVR_lower = .[[5]][[1]]$ci.lb, lnVR_upper = .[[5]][[1]]$ci.ub, lnVR_se = .[[5]][[1]]$se,
+  lnRR = .[[6]][[1]]$b, lnRR_lower = .[[6]][[1]]$ci.lb, lnRR_upper = .[[6]][[1]]$ci.ub, lnRR_se = .[[6]][[1]]$se
+))[, c(1, 7:18)]
+
+Hematology <- as.data.frame(overall1 %>% filter(., GroupingTerm == "Hematology") %>% mutate(
+  lnCVR = .[[4]][[1]]$b, lnCVR_lower = .[[4]][[1]]$ci.lb, lnCVR_upper = .[[4]][[1]]$ci.ub, lnCVR_se = .[[4]][[1]]$se,
+  lnVR = .[[5]][[1]]$b, lnVR_lower = .[[5]][[1]]$ci.lb, lnVR_upper = .[[5]][[1]]$ci.ub, lnVR_se = .[[5]][[1]]$se,
+  lnRR = .[[6]][[1]]$b, lnRR_lower = .[[6]][[1]]$ci.lb, lnRR_upper = .[[6]][[1]]$ci.ub, lnRR_se = .[[6]][[1]]$se
+))[, c(1, 7:18)]
+
+Hearing <- as.data.frame(overall1 %>% filter(., GroupingTerm == "Hearing") %>% mutate(
+  lnCVR = .[[4]][[1]]$b, lnCVR_lower = .[[4]][[1]]$ci.lb, lnCVR_upper = .[[4]][[1]]$ci.ub, lnCVR_se = .[[4]][[1]]$se,
+  lnVR = .[[5]][[1]]$b, lnVR_lower = .[[5]][[1]]$ci.lb, lnVR_upper = .[[5]][[1]]$ci.ub, lnVR_se = .[[5]][[1]]$se,
+  lnRR = .[[6]][[1]]$b, lnRR_lower = .[[6]][[1]]$ci.lb, lnRR_upper = .[[6]][[1]]$ci.ub, lnRR_se = .[[6]][[1]]$se
+))[, c(1, 7:18)]
+
+Physiology <- as.data.frame(overall1 %>% filter(., GroupingTerm == "Physiology") %>% mutate(
+  lnCVR = .[[4]][[1]]$b, lnCVR_lower = .[[4]][[1]]$ci.lb, lnCVR_upper = .[[4]][[1]]$ci.ub, lnCVR_se = .[[4]][[1]]$se,
+  lnVR = .[[5]][[1]]$b, lnVR_lower = .[[5]][[1]]$ci.lb, lnVR_upper = .[[5]][[1]]$ci.ub, lnVR_se = .[[5]][[1]]$se,
+  lnRR = .[[6]][[1]]$b, lnRR_lower = .[[6]][[1]]$ci.lb, lnRR_upper = .[[6]][[1]]$ci.ub, lnRR_se = .[[6]][[1]]$se
+))[, c(1, 7:18)]
+
+Metabolism <- as.data.frame(overall1 %>% filter(., GroupingTerm == "Metabolism") %>% mutate(
+  lnCVR = .[[4]][[1]]$b, lnCVR_lower = .[[4]][[1]]$ci.lb, lnCVR_upper = .[[4]][[1]]$ci.ub, lnCVR_se = .[[4]][[1]]$se,
+  lnVR = .[[5]][[1]]$b, lnVR_lower = .[[5]][[1]]$ci.lb, lnVR_upper = .[[5]][[1]]$ci.ub, lnVR_se = .[[5]][[1]]$se,
+  lnRR = .[[6]][[1]]$b, lnRR_lower = .[[6]][[1]]$ci.lb, lnRR_upper = .[[6]][[1]]$ci.ub, lnRR_se = .[[6]][[1]]$se
+))[, c(1, 7:18)]
+
+Morphology <- as.data.frame(overall1 %>% filter(., GroupingTerm == "Morphology") %>% mutate(
+  lnCVR = .[[4]][[1]]$b, lnCVR_lower = .[[4]][[1]]$ci.lb, lnCVR_upper = .[[4]][[1]]$ci.ub, lnCVR_se = .[[4]][[1]]$se,
+  lnVR = .[[5]][[1]]$b, lnVR_lower = .[[5]][[1]]$ci.lb, lnVR_upper = .[[5]][[1]]$ci.ub, lnVR_se = .[[5]][[1]]$se,
+  lnRR = .[[6]][[1]]$b, lnRR_lower = .[[6]][[1]]$ci.lb, lnRR_upper = .[[6]][[1]]$ci.ub, lnRR_se = .[[6]][[1]]$se
+))[, c(1, 7:18)]
+
+Heart <- as.data.frame(overall1 %>% filter(., GroupingTerm == "Heart") %>% mutate(
+  lnCVR = .[[4]][[1]]$b, lnCVR_lower = .[[4]][[1]]$ci.lb, lnCVR_upper = .[[4]][[1]]$ci.ub, lnCVR_se = .[[4]][[1]]$se,
+  lnVR = .[[5]][[1]]$b, lnVR_lower = .[[5]][[1]]$ci.lb, lnVR_upper = .[[5]][[1]]$ci.ub, lnVR_se = .[[5]][[1]]$se,
+  lnRR = .[[6]][[1]]$b, lnRR_lower = .[[6]][[1]]$ci.lb, lnRR_upper = .[[6]][[1]]$ci.ub, lnRR_se = .[[6]][[1]]$se
+))[, c(1, 7:18)]
+
+Eye <- as.data.frame(overall1 %>% filter(., GroupingTerm == "Eye") %>% mutate(
+  lnCVR = .[[4]][[1]]$b, lnCVR_lower = .[[4]][[1]]$ci.lb, lnCVR_upper = .[[4]][[1]]$ci.ub, lnCVR_se = .[[4]][[1]]$se,
+  lnVR = .[[5]][[1]]$b, lnVR_lower = .[[5]][[1]]$ci.lb, lnVR_upper = .[[5]][[1]]$ci.ub, lnVR_se = .[[5]][[1]]$se,
+  lnRR = .[[6]][[1]]$b, lnRR_lower = .[[6]][[1]]$ci.lb, lnRR_upper = .[[6]][[1]]$ci.ub, lnRR_se = .[[6]][[1]]$se
+))[, c(1, 7:18)]
+
+All <- as.data.frame(overall_all1 %>% mutate(
+  lnCVR = .[[2]][[1]]$b, lnCVR_lower = .[[2]][[1]]$ci.lb, lnCVR_upper = .[[2]][[1]]$ci.ub, lnCVR_se = .[[2]][[1]]$se, lnVR = .[[3]][[1]]$b, lnVR_lower = .[[3]][[1]]$ci.lb, lnVR_upper = .[[3]][[1]]$ci.ub, lnVR_se = .[[3]][[1]]$se,
+  lnRR = .[[4]][[1]]$b, lnRR_lower = .[[4]][[1]]$ci.lb, lnRR_upper = .[[4]][[1]]$ci.ub, lnRR_se = .[[4]][[1]]$se
+))[, c(5:16)]
 
@@
 overall2 <- bind_rows(Behaviour, Morphology, Metabolism, Physiology, Immunology, Hematology, Heart, Hearing, Eye, All)
-
 ```
@@
 
-meta_clean$GroupingTerm <- factor(meta_clean$GroupingTerm, levels =c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye") )
+meta_clean$GroupingTerm <- factor(meta_clean$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye"))
 meta_clean$GroupingTerm <- factor(meta_clean$GroupingTerm, rev(levels(meta_clean$GroupingTerm)))
@@
 
-meta.plot2.all <- meta_clean %>% select(lnCVR, lnVR, lnRR, GroupingTerm) %>% arrange(GroupingTerm)
-
-meta.plot2.all.b <- gather(meta.plot2.all, trait, value, c(lnCVR,  lnRR)) #lnVR,
-
-meta.plot2.all.b$trait <- factor(meta.plot2.all.b$trait, levels =c("lnCVR","lnRR") )#"lnVR",
+meta.plot2.all <- meta_clean %>%
+  select(lnCVR, lnVR, lnRR, GroupingTerm) %>%
+  arrange(GroupingTerm)
+
+meta.plot2.all.b <- gather(meta.plot2.all, trait, value, c(lnCVR, lnRR)) # lnVR,
+
+meta.plot2.all.b$trait <- factor(meta.plot2.all.b$trait, levels = c("lnCVR", "lnRR")) # "lnVR",
 
@@
   group_by_at(vars(trait, GroupingTerm)) %>%
-				summarise(malebias = sum(value > 0), femalebias = sum(value<= 0), total= malebias + femalebias, 
-					malepercent = malebias*100/total, femalepercent = femalebias*100/total)
+  summarise(
+    malebias = sum(value > 0), femalebias = sum(value <= 0), total = malebias + femalebias,
+    malepercent = malebias * 100 / total, femalepercent = femalebias * 100 / total
+  )
 
@@
 
-meta.plot2.all.e$samplesize <- with(meta.plot2.all.e, ifelse(sex == "malepercent", malebias, femalebias) )
+meta.plot2.all.e$samplesize <- with(meta.plot2.all.e, ifelse(sex == "malepercent", malebias, femalebias))
 
@@
   geom_hline(yintercept = 50, linetype = "dashed", color = "gray40") +
-  geom_text(data = subset(meta.plot2.all.e, samplesize != 0), aes(label = samplesize), position = position_stack(vjust = .5), 
-	color = "white", size = 3.5) +
- facet_grid(cols = vars(trait), rows = vars(label),  labeller = label_wrap_gen(width = 18), 
-      scales= 'free', space='free') +
+  geom_text(
+    data = subset(meta.plot2.all.e, samplesize != 0), aes(label = samplesize), position = position_stack(vjust = .5),
+    color = "white", size = 3.5
+  ) +
+  facet_grid(
+    cols = vars(trait), rows = vars(label), labeller = label_wrap_gen(width = 18),
+    scales = "free", space = "free"
+  ) +
   scale_fill_brewer(palette = "Set2") +
   theme_bw(base_size = 18) +
-  	theme(strip.text.y = element_text(angle = 270, size = 10, margin = margin(t=15, r=15, b=15, l=15)), 
+  theme(
+    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
     strip.text.x = element_text(size = 12),
-        strip.background = element_rect(colour = NULL,linetype = "blank", fill = "gray90"),
-        text = element_text(size=14),
+    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
+    text = element_text(size = 14),
     panel.spacing = unit(0.5, "lines"),
-        panel.border= element_blank(),
-        axis.line=element_line(), 
+    panel.border = element_blank(),
+    axis.line = element_line(),
     panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
@@
     axis.title.x = element_blank(),
-	  axis.title.y = element_blank()  ) +
+    axis.title.y = element_blank()
+  ) +
   coord_flip()
 
-#malebias_Fig2_alltraits
-
+# malebias_Fig2_alltraits     #(panel A in Figure 4 in ms)
 ```
@@
 meta.plot2.sig <- meta_clean %>%
-    mutate(lnCVRsig = ifelse(lnCVR_lower*lnCVR_upper >0, 1, 0), lnVRsig = ifelse(lnVR_lower*lnVR_upper >0, 1, 0), 
-	     lnRRsig = ifelse(lnRR_lower*lnRR_upper > 0, 1,0))
-
-meta.plot2.sig.b <- meta.plot2.sig[, c("lnCVR",  "lnRR", "lnCVRsig", "lnVRsig", "lnRRsig", "GroupingTerm")]   #"lnVR",
+  mutate(
+    lnCVRsig = ifelse(lnCVR_lower * lnCVR_upper > 0, 1, 0), lnVRsig = ifelse(lnVR_lower * lnVR_upper > 0, 1, 0),
+    lnRRsig = ifelse(lnRR_lower * lnRR_upper > 0, 1, 0)
+  )
+
+meta.plot2.sig.b <- meta.plot2.sig[, c("lnCVR", "lnRR", "lnCVRsig", "lnVRsig", "lnRRsig", "GroupingTerm")] # "lnVR",
 
@@
 
-meta.plot2.sig.c$trait <- factor(meta.plot2.sig.c$trait, levels =c("lnCVR","lnRR") ) #"lnVR",
+meta.plot2.sig.c$trait <- factor(meta.plot2.sig.c$trait, levels = c("lnCVR", "lnRR")) # "lnVR",
 
 meta.plot2.sig.c$sig <- ifelse(meta.plot2.sig.c$trait == "lnCVR", meta.plot2.sig.c$lnCVRsig,
-				ifelse(meta.plot2.sig.c$trait == "lnVR", meta.plot2.sig.c$lnVRsig, meta.plot2.sig.c$lnRRsig))
-
-#choosing sex biased ln-ratios significantly larger than 0
+  ifelse(meta.plot2.sig.c$trait == "lnVR", meta.plot2.sig.c$lnVRsig, meta.plot2.sig.c$lnRRsig)
+)
+
+# choosing sex biased ln-ratios significantly larger than 0
 meta.plot2.sig.malebias <- meta.plot2.sig.c %>%
   group_by_at(vars(trait, GroupingTerm)) %>%
-				filter(sig== 1) %>%
+  filter(sig == 1) %>%
   summarise(male_sig = sum(value > 0), female_sig = sum(value < 0), total = male_sig + female_sig)
@@
 meta.plot2.sig.malebias <- ungroup(meta.plot2.sig.malebias) %>%
-				add_row(trait = "lnCVR", GroupingTerm = "Hearing", male_sig = 0, female_sig = 0, .before = 4) %>% #add "Hearing" for lnCVR (not filtered as only zeros)
-				mutate(malepercent = male_sig*100 / total, femalepercent = female_sig*100 / total)
+  add_row(trait = "lnCVR", GroupingTerm = "Hearing", male_sig = 0, female_sig = 0, .before = 4) %>% # add "Hearing" for lnCVR (not filtered as only zeros)
+  mutate(malepercent = male_sig * 100 / total, femalepercent = female_sig * 100 / total)
 
@@
 
-meta.plot2.sig.bothsexes.b$samplesize <- with(meta.plot2.sig.bothsexes.b, ifelse(sex == "malepercent", male_sig, female_sig) )
+meta.plot2.sig.bothsexes.b$samplesize <- with(meta.plot2.sig.bothsexes.b, ifelse(sex == "malepercent", male_sig, female_sig))
 
@@
   geom_hline(yintercept = 50, linetype = "dashed", color = "gray40") +
-  geom_text(data = subset(meta.plot2.sig.bothsexes.b, samplesize != 0), aes(label = samplesize), position = position_stack(vjust = .5), 
-	color = "white", size = 3.5) +
- facet_grid(cols = vars(trait), rows = vars(label),  labeller = label_wrap_gen(width = 18), 
-      scales= 'free', space='free') +
+  geom_text(
+    data = subset(meta.plot2.sig.bothsexes.b, samplesize != 0), aes(label = samplesize), position = position_stack(vjust = .5),
+    color = "white", size = 3.5
+  ) +
+  facet_grid(
+    cols = vars(trait), rows = vars(label), labeller = label_wrap_gen(width = 18),
+    scales = "free", space = "free"
+  ) +
   scale_fill_brewer(palette = "Set2") +
   theme_bw(base_size = 18) +
-  	theme(strip.text.y = element_text(angle = 270, size = 10, margin = margin(t=15, r=15, b=15, l=15)), 
-	  strip.text.x = element_blank(),
-        strip.background = element_rect(colour = NULL,linetype = "blank", fill = "gray90"),
-        text = element_text(size=14),
+  theme(
+    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
+    strip.text.x = element_text(size = 12),
+    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
+    text = element_text(size = 14),
     panel.spacing = unit(0.5, "lines"),
-        panel.border= element_blank(),
-        axis.line=element_line(), 
+    panel.border = element_blank(),
+    axis.line = element_line(),
     panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
@@
     axis.title.x = element_blank(),
-	  axis.title.y = element_blank()  ) +
+    axis.title.y = element_blank()
+  ) +
   coord_flip()
@@
 ```{r}
-meta.plot2.over10 <- meta_clean %>% select(lnCVR,  lnRR, GroupingTerm) %>% arrange(GroupingTerm) #lnVR,
-
-meta.plot2.over10.b <- gather(meta.plot2.over10, trait, value, c(lnCVR,  lnRR)) #lnVR,
-
-meta.plot2.over10.b$trait <- factor(meta.plot2.over10.b$trait, levels =c("lnCVR","lnRR") ) #"lnVR",
+meta.plot2.over10 <- meta_clean %>%
+  select(lnCVR, lnRR, GroupingTerm) %>%
+  arrange(GroupingTerm) # lnVR,
+
+meta.plot2.over10.b <- gather(meta.plot2.over10, trait, value, c(lnCVR, lnRR)) # lnVR,
+
+meta.plot2.over10.b$trait <- factor(meta.plot2.over10.b$trait, levels = c("lnCVR", "lnRR")) # "lnVR",
 
@@
   group_by_at(vars(trait, GroupingTerm)) %>%
-				summarise(malebias = sum(value > log(11/10)), femalebias = sum(value < log(9/10)), total= malebias + femalebias, 
-					malepercent = malebias*100/total, femalepercent = femalebias*100/total)
+  summarise(
+    malebias = sum(value > log(11 / 10)), femalebias = sum(value < log(9 / 10)), total = malebias + femalebias,
+    malepercent = malebias * 100 / total, femalepercent = femalebias * 100 / total
+  )
 
@@
 
-meta.plot2.over10.d$samplesize <- with(meta.plot2.over10.d, ifelse(sex == "malepercent", malebias, femalebias) )
+meta.plot2.over10.d$samplesize <- with(meta.plot2.over10.d, ifelse(sex == "malepercent", malebias, femalebias))
 
@@
   geom_hline(yintercept = 50, linetype = "dashed", color = "gray40") +
-  geom_text(data = subset(meta.plot2.over10.d, samplesize != 0), aes(label = samplesize), position = position_stack(vjust = .5), 
-	color = "white", size = 3.5) +
- facet_grid(cols = vars(trait), rows = vars(label),  labeller = label_wrap_gen(width = 18), 
-      scales= 'free', space='free') +
+  geom_text(
+    data = subset(meta.plot2.over10.d, samplesize != 0), aes(label = samplesize), position = position_stack(vjust = .5),
+    color = "white", size = 3.5
+  ) +
+  facet_grid(
+    cols = vars(trait), rows = vars(label), labeller = label_wrap_gen(width = 18),
+    scales = "free", space = "free"
+  ) +
   scale_fill_brewer(palette = "Set2") +
   theme_bw(base_size = 18) +
-  	theme(strip.text.y = element_text(angle = 270, size = 10, margin = margin(t=15, r=15, b=15, l=15)), 
+  theme(
+    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
     strip.text.x = element_blank(),
-        strip.background = element_rect(colour = NULL,linetype = "blank", fill = "gray90"),
-        text = element_text(size=14),
+    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
+    text = element_text(size = 14),
     panel.spacing = unit(0.5, "lines"),
-        panel.border= element_blank(),
-        axis.line=element_line(), 
+    panel.border = element_blank(),
+    axis.line = element_line(),
     panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
@@
     axis.title.x = element_blank(),
-	  axis.title.y = element_blank()  ) +
+    axis.title.y = element_blank()
+  ) +
   coord_flip()
-# malebias_Fig2_over10
-
-```
-#### Create final combined Figure (Figure 2)
-```{r}
-
-Fig2 <- ggarrange(malebias_Fig2_alltraits, malebias_Fig2_sigtraits,malebias_Fig2_over10, nrow = 3, align = "v", heights = c(1.22,1,1), labels = c("A", "B", "C"))
-Fig2
-ggsave("CountDataCVR_RR_only.pdf", plot = Fig2, width = 6, height = 5) 
-```
-
-###  Overall results of second order meta analysis (Figure 4a)
+
+# malebias_Fig2_over10  (Panel C in Fig 5 in ms)
+```
+
+###  Overall results of second order meta analysis (Figure 4: overall, Figure 5: sex-bias)
 #### Restructure data for plotting 
@@
 ```{r}
-overall3 <- gather(overall2, parameter, value, c(lnCVR,  lnRR), factor_key= TRUE) #lnVR,
-
-lnCVR.ci <- overall3 %>% filter(parameter == "lnCVR") %>% mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
-#lnVR.ci <- overall3 %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
-lnRR.ci <- overall3 %>% filter(parameter == "lnRR") %>% mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
-
-overall4 <- bind_rows(lnCVR.ci,  lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high) #lnVR.ci,
+overall3 <- gather(overall2, parameter, value, c(lnCVR, lnRR), factor_key = TRUE) # lnVR,
+
+lnCVR.ci <- overall3 %>%
+  filter(parameter == "lnCVR") %>%
+  mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
+lnVR.ci <- overall3 %>%
+  filter(parameter == "lnVR") %>%
+  mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
+lnRR.ci <- overall3 %>%
+  filter(parameter == "lnRR") %>%
+  mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
+
+overall4 <- bind_rows(lnCVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high) # lnVR.ci,
 
@@
 
-overall4$GroupingTerm <- factor(overall4$GroupingTerm, levels =c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye", "All") )
+overall4$GroupingTerm <- factor(overall4$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
 overall4$GroupingTerm <- factor(overall4$GroupingTerm, rev(levels(overall4$GroupingTerm)))
@@
   scroll_box(width = "100%", height = "200px")
-
-```
-
-#### Plot FIGURE 4 (Second-order meta analysis results)
-Preparation: Sub-Plot  for Figure 3: all traits
+```
+
+#### Preparation for Plots FIGURE 4B & 5B, 5D (Second-order meta analysis results)
+Preparation: Sub-Plot  for Figure 3: all traits (4B)
 ```{r}
@@
 
-  ggplot(aes(y= GroupingTerm, x= value)) +
-  geom_errorbarh(aes(xmin = ci.low, 
-                     xmax = ci.high), 
-			   height = 0.1, show.legend = FALSE) +
-  geom_point(aes(shape = parameter), fill = 'black',
-             color = 'black', size = 2.2, 
-             show.legend = FALSE) +
-  scale_x_continuous(limits=c(-0.24, 0.25), 
+  ggplot(aes(y = GroupingTerm, x = value)) +
+  geom_errorbarh(aes(
+    xmin = ci.low,
+    xmax = ci.high
+  ),
+  height = 0.1, show.legend = FALSE
+  ) +
+  geom_point(aes(shape = parameter),
+    fill = "black",
+    color = "black", size = 2.2,
+    show.legend = FALSE
+  ) +
+  scale_x_continuous(
+    limits = c(-0.24, 0.25),
     breaks = c(-0.2, -0.1, 0, 0.1, 0.2),
-                     name='Effect size') +
-  geom_vline(xintercept=0, 
-             color='black', 
-             linetype='dashed')+
-  facet_grid(cols = vars(parameter), rows = vars(label),
+    name = "Effect size"
+  ) +
+  geom_vline(
+    xintercept = 0,
+    color = "black",
+    linetype = "dashed"
+  ) +
+  facet_grid(
+    cols = vars(parameter), rows = vars(label),
     labeller = label_wrap_gen(width = 23),
-             scales= 'free', 
-             space='free')+
-  theme_bw()+
-  theme(strip.text.y = element_text(angle = 270, size = 10, margin = margin(t=15, r=15, b=15, l=15)), 
+    scales = "free",
+    space = "free"
+  ) +
+  theme_bw() +
+  theme(
+    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
     strip.text.x = element_text(size = 12),
@@
     panel.spacing = unit(0.5, "lines"),
-        panel.border= element_blank(),
-        axis.line=element_line(), 
+    panel.border = element_blank(),
+    axis.line = element_line(),
+    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
+    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
+    panel.grid.minor.y = element_blank(),
+    panel.grid.minor.x = element_blank(),
+    legend.title = element_blank(),
+    axis.title.x = element_text(hjust = 0.5, size = 14),
+    axis.title.y = element_blank()
+  )
+
+# Metameta_Fig3_alltraits
+```
+
+#### Figure 5 - traits with CI not overlapping 0 
+Prepare data 
+create column with 1= different from zero, 0= zero included in CI
+Male-biased (significant) traits
+```{r}
+meta.male.plot3.sig <- metacombo %>%
+  mutate(
+    sigCVR = ifelse(lnCVR_lower > 0, 1, 0),
+    sigVR = ifelse(lnVR_lower > 0, 1, 0),
+    sigRR = ifelse(lnRR_lower > 0, 1, 0)
+  )
+
+# Significant subset for lnCVR
+metacombo_male.plot3.CVR <- meta.male.plot3.sig %>%
+  filter(sigCVR == 1) %>%
+  group_by(GroupingTerm) %>%
+  nest()
+
+metacombo_male.plot3.CVR.all <- meta.male.plot3.sig %>%
+  filter(sigCVR == 1) %>%
+  nest()
+
+# Significant subset for lnVR
+metacombo_male.plot3.VR <- meta.male.plot3.sig %>%
+  filter(sigVR == 1) %>%
+  group_by(GroupingTerm) %>%
+  nest()
+
+metacombo_male.plot3.VR.all <- meta.male.plot3.sig %>%
+  filter(sigVR == 1) %>%
+  nest()
+
+# Significant subset for lnRR
+metacombo_male.plot3.RR <- meta.male.plot3.sig %>%
+  filter(sigRR == 1) %>%
+  group_by(GroupingTerm) %>%
+  nest()
+
+metacombo_male.plot3.RR.all <- meta.male.plot3.sig %>%
+  filter(sigRR == 1) %>%
+  nest()
+
+# **Final fixed effects meta-analyses within grouping terms, with SE of the estimate
+
+plot3.male.meta.CVR <- metacombo_male.plot3.CVR %>%
+  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+plot3.male.meta.VR <- metacombo_male.plot3.VR %>%
+  mutate(model_lnVR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+plot3.male.meta.RR <- metacombo_male.plot3.RR %>%
+  mutate(model_lnRR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+# Across all grouping terms #
+
+plot3.male.meta.CVR.all <- metacombo_male.plot3.CVR.all %>%
+  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+plot3.male.meta.CVR.all <- plot3.male.meta.CVR.all %>% mutate(GroupingTerm = "All")
+
+plot3.male.meta.VR.all <- metacombo_male.plot3.VR.all %>%
+  mutate(model_lnVR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+plot3.male.meta.VR.all <- plot3.male.meta.VR.all %>% mutate(GroupingTerm = "All")
+
+plot3.male.meta.RR.all <- metacombo_male.plot3.RR.all %>%
+  mutate(model_lnRR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+plot3.male.meta.RR.all <- plot3.male.meta.RR.all %>% mutate(GroupingTerm = "All")
+
+# Combine with separate grouping term results
+
+plot3.male.meta.CVR <- bind_rows(plot3.male.meta.CVR, plot3.male.meta.CVR.all)
+plot3.male.meta.VR <- bind_rows(plot3.male.meta.VR, plot3.male.meta.VR.all)
+plot3.male.meta.RR <- bind_rows(plot3.male.meta.RR, plot3.male.meta.RR.all)
+
+# **Re-structure data for each grouping term; delete un-used variables
+
+plot3.male.meta.CVR.b <- as.data.frame(plot3.male.meta.CVR %>% group_by(GroupingTerm) %>%
+  mutate(
+    lnCVR = map_dbl(model_lnCVR, pluck(2)), lnCVR_lower = map_dbl(model_lnCVR, pluck(6)),
+    lnCVR_upper = map_dbl(model_lnCVR, pluck(7)), lnCVR_se = map_dbl(model_lnCVR, pluck(3))
+  ))[, c(1, 4:7)]
+add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.male.meta.CVR.b))
+
+plot3.male.meta.CVR.b <- bind_rows(plot3.male.meta.CVR.b, add.row.hearing)
+plot3.male.meta.CVR.b <- plot3.male.meta.CVR.b[order(plot3.male.meta.CVR.b$GroupingTerm), ]
+
+plot3.male.meta.VR.b <- as.data.frame(plot3.male.meta.VR %>% group_by(GroupingTerm) %>%
+  mutate(
+    lnVR = map_dbl(model_lnVR, pluck(2)), lnVR_lower = map_dbl(model_lnVR, pluck(6)),
+    lnVR_upper = map_dbl(model_lnVR, pluck(7)), lnVR_se = map_dbl(model_lnVR, pluck(3))
+  ))[, c(1, 4:7)]
+plot3.male.meta.VR.b <- plot3.male.meta.VR.b[order(plot3.male.meta.VR.b$GroupingTerm), ]
+
+plot3.male.meta.RR.b <- as.data.frame(plot3.male.meta.RR %>% group_by(GroupingTerm) %>%
+  mutate(
+    lnRR = map_dbl(model_lnRR, pluck(2)), lnRR_lower = map_dbl(model_lnRR, pluck(6)),
+    lnRR_upper = map_dbl(model_lnRR, pluck(7)), lnRR_se = map_dbl(model_lnRR, pluck(3))
+  ))[, c(1, 4:7)]
+plot3.male.meta.RR.b <- plot3.male.meta.RR.b[order(plot3.male.meta.RR.b$GroupingTerm), ]
+
+overall.male.plot3 <- full_join(plot3.male.meta.CVR.b, plot3.male.meta.VR.b)
+overall.male.plot3 <- full_join(overall.male.plot3, plot3.male.meta.RR.b)
+
+overall.male.plot3$GroupingTerm <- factor(overall.male.plot3$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
+overall.male.plot3$GroupingTerm <- factor(overall.male.plot3$GroupingTerm, rev(levels(overall.male.plot3$GroupingTerm)))
+
+# add missing GroupingTerms for plot
+overall.male.plot3 <- add_row(overall.male.plot3, GroupingTerm = "Behaviour")
+overall.male.plot3 <- add_row(overall.male.plot3, GroupingTerm = "Immunology")
+overall.male.plot3 <- add_row(overall.male.plot3, GroupingTerm = "Eye")
+
+overall.male.plot3$GroupingTerm <- factor(overall.male.plot3$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
+overall.male.plot3$GroupingTerm <- factor(overall.male.plot3$GroupingTerm, rev(levels(overall.male.plot3$GroupingTerm)))
+
+# str(overall.male.plot3)
+```
+
+Restructure MALE data for plotting 
+```{r}
+overall3.male.sig <- gather(overall.male.plot3, parameter, value, c(lnCVR, lnRR), factor_key = TRUE) # lnVR,
+
+lnCVR.ci <- overall3.male.sig %>%
+  filter(parameter == "lnCVR") %>%
+  mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
+# lnVR.ci <- overall3.male.sig  %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
+lnRR.ci <- overall3.male.sig %>%
+  filter(parameter == "lnRR") %>%
+  mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
+
+overall4.male.sig <- bind_rows(lnCVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high) # lnVR.ci,
+
+overall4.male.sig$label <- "CI not overlapping zero"
+```
+
+Plot Fig5b all significant results (CI not overlapping zero) for males
+```{r}
+
+Metameta_Fig3_male.sig <- overall4.male.sig %>%
+  ggplot(aes(y = GroupingTerm, x = value)) +
+  geom_errorbarh(aes(
+    xmin = ci.low,
+    xmax = ci.high
+  ),
+  height = 0.1, show.legend = FALSE
+  ) +
+  geom_point(aes(shape = parameter),
+    fill = "mediumaquamarine", color = "mediumaquamarine", size = 2.2,
+    show.legend = FALSE
+  ) +
+  scale_x_continuous(
+    limits = c(0, 0.4),
+    breaks = c(0, 0.3),
+    name = "Effect size"
+  ) +
+  geom_vline(
+    xintercept = 0,
+    color = "black",
+    linetype = "dashed"
+  ) +
+  facet_grid(
+    cols = vars(parameter), rows = vars(label),
+    labeller = label_wrap_gen(width = 23),
+    scales = "free",
+    space = "free"
+  ) +
+  theme_bw() +
+  theme(
+    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
+    strip.text.x = element_text(size = 12),
+    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
+    text = element_text(size = 14),
+    panel.spacing = unit(0.5, "lines"),
+    panel.border = element_blank(),
+    axis.line = element_line(),
     panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
@@
     axis.title.x = element_blank(),
-	  axis.title.y = element_blank())
-
-#Metameta_Fig3_alltraits
-
-```
-
-#### Figure 4B- traits with CI not overlapping 0 
-Prepare data 
+    axis.title.y = element_blank()
+  )
+
+# Metameta_Fig3_male.sig
+```
+
+#### Female Figure, significant traits
+Female Fig5B sig
+
+Prepare data for traits with CI not overlapping 0
 create column with 1= different from zero, 0= zero included in CI
-Male-biased (significant) traits
-```{r}
-meta.male.plot3.sig <- metacombo %>% 
-    	mutate(sigCVR = ifelse(lnCVR_lower > 0, 1, 0),
-	sigVR = ifelse(lnVR_lower > 0, 1, 0),
-	sigRR = ifelse(lnRR_lower > 0, 1, 0))
-
-#Significant subset for lnCVR
-metacombo_male.plot3.CVR <- meta.male.plot3.sig %>%
+```{r}
+
+# female-biased traits
+
+meta.female.plot3.sig <- metacombo %>%
+  mutate(
+    sigCVR = ifelse(lnCVR_upper < 0, 1, 0),
+    sigVR = ifelse(lnVR_upper < 0, 1, 0),
+    sigRR = ifelse(lnRR_upper < 0, 1, 0)
+  )
+
+# Significant subset for lnCVR
+
+metacombo_female.plot3.CVR <- meta.female.plot3.sig %>%
   filter(sigCVR == 1) %>%
@@
 
-metacombo_male.plot3.CVR.all <- meta.male.plot3.sig %>%
+metacombo_female.plot3.CVR.all <- meta.female.plot3.sig %>%
   filter(sigCVR == 1) %>%
@@
 
-#Significant subset for lnVR
-#metacombo_male.plot3.VR <- meta.male.plot3.sig %>%
-# filter(sigVR == 1) %>%
-# group_by(GroupingTerm) %>%
-# nest()
-
-#metacombo_male.plot3.VR.all <- meta.male.plot3.sig %>%
- #filter(sigVR == 1) %>%
- #nest()
-
-#Significant subset for lnRR
-metacombo_male.plot3.RR <- meta.male.plot3.sig %>%
+# Significant subset for lnVR
+
+metacombo_female.plot3.VR <- meta.female.plot3.sig %>%
+  filter(sigVR == 1) %>%
+  group_by(GroupingTerm) %>%
+  nest()
+
+metacombo_female.plot3.VR.all <- meta.female.plot3.sig %>%
+  filter(sigVR == 1) %>%
+  nest()
+
+# Significant subset for lnRR
+
+metacombo_female.plot3.RR <- meta.female.plot3.sig %>%
   filter(sigRR == 1) %>%
@@
 
-metacombo_male.plot3.RR.all <- meta.male.plot3.sig %>%
+metacombo_female.plot3.RR.all <- meta.female.plot3.sig %>%
   filter(sigRR == 1) %>%
@@
 
-plot3.male.meta.CVR <- metacombo_male.plot3.CVR %>% 
-  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower)/ (2*1.96),  
-				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )
-
-#plot3.male.meta.VR <- metacombo_male.plot3.VR %>% 
- # mutate(model_lnVR = map(data, ~ metafor::rma.uni(yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower)/ (2*1.96),  
-#				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )
-
-plot3.male.meta.RR <- metacombo_male.plot3.RR %>% 
-  mutate(model_lnRR = map(data, ~ metafor::rma.uni(yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower)/ (2*1.96),  
-				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )
+plot3.female.meta.CVR <- metacombo_female.plot3.CVR %>%
+  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+plot3.female.meta.VR <- metacombo_female.plot3.VR %>%
+  mutate(model_lnVR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+plot3.female.meta.RR <- metacombo_female.plot3.RR %>%
+  mutate(model_lnRR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
 
@@
 
-plot3.male.meta.CVR.all <- metacombo_male.plot3.CVR.all %>% 
-  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower)/ (2*1.96),  
-				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )
-
-plot3.male.meta.CVR.all <- plot3.male.meta.CVR.all %>% mutate(GroupingTerm = "All")
-
-#plot3.male.meta.VR.all <- metacombo_male.plot3.VR.all %>% 
-#  mutate(model_lnVR = map(data, ~ metafor::rma.uni(yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower)/ (2*1.96),  
-#				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )
-
-#plot3.male.meta.VR.all <- plot3.male.meta.VR.all %>% mutate(GroupingTerm = "All")
-
-plot3.male.meta.RR.all <- metacombo_male.plot3.RR.all %>% 
-  mutate(model_lnRR = map(data, ~ metafor::rma.uni(yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower)/ (2*1.96),  
-				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )
-
-plot3.male.meta.RR.all <- plot3.male.meta.RR.all %>% mutate(GroupingTerm = "All")
+plot3.female.meta.CVR.all <- metacombo_female.plot3.CVR.all %>%
+  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+plot3.female.meta.CVR.all <- plot3.female.meta.CVR.all %>% mutate(GroupingTerm = "All")
+
+plot3.female.meta.VR.all <- metacombo_female.plot3.VR.all %>%
+  mutate(model_lnVR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+plot3.female.meta.VR.all <- plot3.female.meta.VR.all %>% mutate(GroupingTerm = "All")
+
+plot3.female.meta.RR.all <- metacombo_female.plot3.RR.all %>%
+  mutate(model_lnRR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+plot3.female.meta.RR.all <- plot3.female.meta.RR.all %>% mutate(GroupingTerm = "All")
 
@@
 
-plot3.male.meta.CVR <- bind_rows(plot3.male.meta.CVR, plot3.male.meta.CVR.all)
-#plot3.male.meta.VR <- bind_rows(plot3.male.meta.VR, plot3.male.meta.VR.all)
-plot3.male.meta.RR <- bind_rows(plot3.male.meta.RR, plot3.male.meta.RR.all)
+plot3.female.meta.CVR <- bind_rows(plot3.female.meta.CVR, plot3.female.meta.CVR.all)
+plot3.female.meta.VR <- bind_rows(plot3.female.meta.VR, plot3.female.meta.VR.all)
+plot3.female.meta.RR <- bind_rows(plot3.female.meta.RR, plot3.female.meta.RR.all)
 
@@
 
-plot3.male.meta.CVR.b <- as.data.frame(plot3.male.meta.CVR %>% group_by(GroupingTerm) %>%  
-		mutate(lnCVR = map_dbl(model_lnCVR, pluck(2)), lnCVR_lower = map_dbl(model_lnCVR, pluck(6)), 
-		lnCVR_upper =map_dbl(model_lnCVR, pluck(7)), lnCVR_se =map_dbl(model_lnCVR, pluck(3))) )[, c(1,4:7)] 
-add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.male.meta.CVR.b))
-
-plot3.male.meta.CVR.b <- bind_rows(plot3.male.meta.CVR.b, add.row.hearing) 
-plot3.male.meta.CVR.b <- plot3.male.meta.CVR.b[order(plot3.male.meta.CVR.b$GroupingTerm),]
-
-#plot3.male.meta.VR.b <- as.data.frame(plot3.male.meta.VR %>% group_by(GroupingTerm) %>%  
-#	mutate(lnVR = map_dbl(model_lnVR, pluck(2)), lnVR_lower = map_dbl(model_lnVR, pluck(6)), 
-#	lnVR_upper =map_dbl(model_lnVR, pluck(7)), lnVR_se =map_dbl(model_lnVR, pluck(3))) )[, c(1,4:7)] 
-#plot3.male.meta.VR.b <- plot3.male.meta.VR.b[order(plot3.male.meta.VR.b$GroupingTerm),]
-
-plot3.male.meta.RR.b <- as.data.frame(plot3.male.meta.RR %>% group_by(GroupingTerm) %>%  
-	mutate(lnRR = map_dbl(model_lnRR, pluck(2)), lnRR_lower = map_dbl(model_lnRR, pluck(6)), 
-	lnRR_upper =map_dbl(model_lnRR, pluck(7)), lnRR_se =map_dbl(model_lnRR, pluck(3))) )[, c(1,4:7)] 
-plot3.male.meta.RR.b <- plot3.male.meta.RR.b[order(plot3.male.meta.RR.b$GroupingTerm),]
-
-#overall.male.plot3 <- full_join(plot3.male.meta.CVR.b, plot3.male.meta.VR.b) 
-overall.male.plot3 <- full_join(plot3.male.meta.CVR.b, plot3.male.meta.RR.b)
-
-overall.male.plot3$GroupingTerm <- factor(overall.male.plot3$GroupingTerm, levels =c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye", "All") )
-overall.male.plot3$GroupingTerm <- factor(overall.male.plot3$GroupingTerm, rev(levels(overall.male.plot3$GroupingTerm)))
-
-#add missing GroupingTerms for plot
-overall.male.plot3 <- add_row(overall.male.plot3, GroupingTerm = "Behaviour")
-overall.male.plot3 <- add_row(overall.male.plot3, GroupingTerm = "Immunology")
-overall.male.plot3 <- add_row(overall.male.plot3, GroupingTerm = "Eye")
-
-overall.male.plot3$GroupingTerm <- factor(overall.male.plot3$GroupingTerm, levels =c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye", "All") )
-overall.male.plot3$GroupingTerm <- factor(overall.male.plot3$GroupingTerm, rev(levels(overall.male.plot3$GroupingTerm)))
-
-```
-
-Restructure MALE data for plotting 
-```{r}
-overall3.male.sig <- gather(overall.male.plot3, parameter, value, c(lnCVR,  lnRR), factor_key= TRUE) #lnVR,
-
-lnCVR.ci <- overall3.male.sig  %>% filter(parameter == "lnCVR") %>% mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
-#lnVR.ci <- overall3.male.sig  %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
-lnRR.ci <- overall3.male.sig  %>% filter(parameter == "lnRR") %>% mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
-
-overall4.male.sig <- bind_rows(lnCVR.ci,  lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high) #lnVR.ci,
-
-overall4.male.sig$label <- "CI not overlapping zero"
-
-```
-
-Plot Fig3 all significant results (CI not overlapping zero) for males
-```{r}
-
-Metameta_Fig3_male.sig <- overall4.male.sig %>%
-  ggplot(aes(y= GroupingTerm, x= value)) +
-  geom_errorbarh(aes(xmin = ci.low, 
-                     xmax = ci.high), 
-			   height = 0.1, show.legend = FALSE) +
+plot3.female.meta.CVR.b <- as.data.frame(plot3.female.meta.CVR %>% group_by(GroupingTerm) %>%
+  mutate(
+    lnCVR = map_dbl(model_lnCVR, pluck(2)), lnCVR_lower = map_dbl(model_lnCVR, pluck(6)),
+    lnCVR_upper = map_dbl(model_lnCVR, pluck(7)), lnCVR_se = map_dbl(model_lnCVR, pluck(3))
+  ))[, c(1, 4:7)]
+
+add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.female.meta.CVR.b))
+
+plot3.female.meta.CVR.b <- bind_rows(plot3.female.meta.CVR.b, add.row.hearing)
+plot3.female.meta.CVR.b <- plot3.female.meta.CVR.b[order(plot3.female.meta.CVR.b$GroupingTerm), ]
+
+plot3.female.meta.VR.b <- as.data.frame(plot3.female.meta.VR %>% group_by(GroupingTerm) %>%
+  mutate(
+    lnVR = map_dbl(model_lnVR, pluck(2)), lnVR_lower = map_dbl(model_lnVR, pluck(6)),
+    lnVR_upper = map_dbl(model_lnVR, pluck(7)), lnVR_se = map_dbl(model_lnVR, pluck(3))
+  ))[, c(1, 4:7)]
+
+plot3.female.meta.VR.b <- plot3.female.meta.VR.b[order(plot3.female.meta.VR.b$GroupingTerm), ]
+
+plot3.female.meta.RR.b <- as.data.frame(plot3.female.meta.RR %>% group_by(GroupingTerm) %>%
+  mutate(
+    lnRR = map_dbl(model_lnRR, pluck(2)), lnRR_lower = map_dbl(model_lnRR, pluck(6)),
+    lnRR_upper = map_dbl(model_lnRR, pluck(7)), lnRR_se = map_dbl(model_lnRR, pluck(3))
+  ))[, c(1, 4:7)]
+
+plot3.female.meta.RR.b <- plot3.female.meta.RR.b[order(plot3.female.meta.RR.b$GroupingTerm), ]
+
+overall.female.plot3 <- full_join(plot3.female.meta.CVR.b, plot3.female.meta.VR.b)
+overall.female.plot3 <- full_join(overall.female.plot3, plot3.female.meta.RR.b)
+
+overall.female.plot3$GroupingTerm <- factor(overall.female.plot3$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
+overall.female.plot3$GroupingTerm <- factor(overall.female.plot3$GroupingTerm, rev(levels(overall.female.plot3$GroupingTerm)))
+```
+
+Restructure data for plotting
+
+```{r}
+overall3.female.sig <- gather(overall.female.plot3, parameter, value, c(lnCVR, lnRR), factor_key = TRUE) # lnVR,
+
+lnCVR.ci <- overall3.female.sig %>%
+  filter(parameter == "lnCVR") %>%
+  mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
+# lnVR.ci <- overall3.female.sig  %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
+lnRR.ci <- overall3.female.sig %>%
+  filter(parameter == "lnRR") %>%
+  mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
+
+overall4.female.sig <- bind_rows(lnCVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high) # lnVR.ci,
+
+overall4.female.sig$label <- "CI not overlapping zero"
+```
+
+Plot Fig5B all significant results (CI not overlapping zero, female )
+```{r}
+
+Metameta_Fig3_female.sig <- overall4.female.sig %>%
+  ggplot(aes(y = GroupingTerm, x = value)) +
+  geom_errorbarh(aes(
+    xmin = ci.low,
+    xmax = ci.high
+  ),
+  height = 0.1, show.legend = FALSE
+  ) +
   geom_point(aes(shape = parameter),
-             fill = 'mediumaquamarine', color = 'mediumaquamarine', size = 2.2, 
-               show.legend = FALSE) +
-  scale_x_continuous(limits=c(0, 0.4), 
-                     breaks = c(0, 0.3), 
-                     name='Effect size') +
-  geom_vline(xintercept=0, 
-             color='black', 
-             linetype='dashed')+
-  facet_grid(cols = vars(parameter), rows = vars(label),
-             labeller = label_wrap_gen(width = 23),
-             scales= 'free', 
-             space='free')+
-  theme_bw()+
-  theme(strip.text.y = element_text(angle = 270, size = 10, margin = margin(t=15, r=15, b=15, l=15)), 
+    fill = "salmon1", color = "salmon1", size = 2.2,
+    show.legend = FALSE
+  ) +
+  scale_x_continuous(
+    limits = c(-0.4, 0),
+    breaks = c(-0.3, 0),
+    name = "Effect size"
+  ) +
+  geom_vline(
+    xintercept = 0,
+    color = "black",
+    linetype = "dashed"
+  ) +
+  facet_grid(
+    cols = vars(parameter), # rows = vars(label),
+    # labeller = label_wrap_gen(width = 23),
+    scales = "free",
+    space = "free"
+  ) +
+  theme_bw() +
+  theme(
+    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
     strip.text.x = element_text(size = 12),
@@
     panel.spacing = unit(0.5, "lines"),
-        panel.border= element_blank(),
-        axis.line=element_line(), 
+    panel.border = element_blank(),
+    axis.line = element_line(),
     panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
@@
     axis.title.x = element_blank(),
-	  axis.title.y = element_blank())
-
-#Metameta_Fig3_male.sig
-
-```
-
-#### Female Figure, significant traits
-Female Fig3 sig
-
-Prepare data for traits with CI not overlapping 0
-create column with 1= different from zero, 0= zero included in CI
-```{r}
-
-# female-biased traits
-
-meta.female.plot3.sig <- metacombo %>%
-              mutate(sigCVR = ifelse(lnCVR_upper < 0, 1, 0),
-              sigVR = ifelse(lnVR_upper < 0, 1, 0),
-              sigRR = ifelse(lnRR_upper < 0, 1, 0))
-
-#Significant subset for lnCVR
-
-metacombo_female.plot3.CVR <- meta.female.plot3.sig %>%
-filter(sigCVR == 1) %>%
-group_by(GroupingTerm) %>%
-nest()
-
-metacombo_female.plot3.CVR.all <- meta.female.plot3.sig %>%
- filter(sigCVR == 1) %>%
- nest()
-
-#Significant subset for lnVR
-
-metacombo_female.plot3.VR <- meta.female.plot3.sig %>%
-filter(sigVR == 1) %>%
-group_by(GroupingTerm) %>%
-nest()
-
-metacombo_female.plot3.VR.all <- meta.female.plot3.sig %>%
- filter(sigVR == 1) %>%
- nest()
-
-#Significant subset for lnRR
-
-metacombo_female.plot3.RR <- meta.female.plot3.sig %>%
-filter(sigRR == 1) %>%
-group_by(GroupingTerm) %>%
-nest()
-
-metacombo_female.plot3.RR.all <- meta.female.plot3.sig %>%
- filter(sigRR == 1) %>%
- nest()
-
-# **Final fixed effects meta-analyses within grouping terms, with SE of the estimate
-
-plot3.female.meta.CVR <- metacombo_female.plot3.CVR %>%
-  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower)/ (2*1.96), 
-                                 control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )
-
-plot3.female.meta.VR <- metacombo_female.plot3.VR %>%
-  mutate(model_lnVR = map(data, ~ metafor::rma.uni(yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower)/ (2*1.96), 
-    					   control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )
-
-plot3.female.meta.RR <- metacombo_female.plot3.RR %>%
-  mutate(model_lnRR = map(data, ~ metafor::rma.uni(yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower)/ (2*1.96), 
-                                 control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )
-
-# Across all grouping terms #
-
-plot3.female.meta.CVR.all <- metacombo_female.plot3.CVR.all %>% 
-  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower)/ (2*1.96),  
-				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )
-
-plot3.female.meta.CVR.all <- plot3.female.meta.CVR.all %>% mutate(GroupingTerm = "All")
-
-plot3.female.meta.VR.all <- metacombo_female.plot3.VR.all %>% 
-  mutate(model_lnVR = map(data, ~ metafor::rma.uni(yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower)/ (2*1.96),  
-				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )
-
-plot3.female.meta.VR.all <- plot3.female.meta.VR.all %>% mutate(GroupingTerm = "All")
-
-plot3.female.meta.RR.all <- metacombo_female.plot3.RR.all %>% 
-  mutate(model_lnRR = map(data, ~ metafor::rma.uni(yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower)/ (2*1.96),  
-				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )
-
-plot3.female.meta.RR.all <- plot3.female.meta.RR.all %>% mutate(GroupingTerm = "All")
-
-# Combine with separate grouping term results
-
-plot3.female.meta.CVR <- bind_rows(plot3.female.meta.CVR, plot3.female.meta.CVR.all)
-plot3.female.meta.VR <- bind_rows(plot3.female.meta.VR, plot3.female.meta.VR.all)
-plot3.female.meta.RR <- bind_rows(plot3.female.meta.RR, plot3.female.meta.RR.all)
-
-# **Re-structure data for each grouping term; delete un-used variables
-
-plot3.female.meta.CVR.b <- as.data.frame(plot3.female.meta.CVR %>% group_by(GroupingTerm) %>% 
-                             mutate(lnCVR = map_dbl(model_lnCVR, pluck(2)), lnCVR_lower = map_dbl(model_lnCVR, pluck(6)),
-                             lnCVR_upper =map_dbl(model_lnCVR, pluck(7)), lnCVR_se =map_dbl(model_lnCVR, pluck(3))) )[, c(1,4:7)]
-
-add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.female.meta.CVR.b))
-
-plot3.female.meta.CVR.b <- bind_rows(plot3.female.meta.CVR.b, add.row.hearing)
-plot3.female.meta.CVR.b <- plot3.female.meta.CVR.b[order(plot3.female.meta.CVR.b$GroupingTerm),]
-
-plot3.female.meta.VR.b <- as.data.frame(plot3.female.meta.VR %>% group_by(GroupingTerm) %>% 
-              mutate(lnVR = map_dbl(model_lnVR, pluck(2)), lnVR_lower = map_dbl(model_lnVR, pluck(6)),
-              lnVR_upper =map_dbl(model_lnVR, pluck(7)), lnVR_se =map_dbl(model_lnVR, pluck(3))) )[, c(1,4:7)]
-
-plot3.female.meta.VR.b <- plot3.female.meta.VR.b[order(plot3.female.meta.VR.b$GroupingTerm),]
-
-plot3.female.meta.RR.b <- as.data.frame(plot3.female.meta.RR %>% group_by(GroupingTerm) %>% 
-              mutate(lnRR = map_dbl(model_lnRR, pluck(2)), lnRR_lower = map_dbl(model_lnRR, pluck(6)),
-              lnRR_upper =map_dbl(model_lnRR, pluck(7)), lnRR_se =map_dbl(model_lnRR, pluck(3))) )[, c(1,4:7)]
-
-plot3.female.meta.RR.b <- plot3.female.meta.RR.b[order(plot3.female.meta.RR.b$GroupingTerm),]
-
-overall.female.plot3 <- full_join(plot3.female.meta.CVR.b, plot3.female.meta.VR.b)
-overall.female.plot3 <- full_join(overall.female.plot3, plot3.female.meta.RR.b)
-
-overall.female.plot3$GroupingTerm <- factor(overall.female.plot3$GroupingTerm, levels =c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye", "All") )
-overall.female.plot3$GroupingTerm <- factor(overall.female.plot3$GroupingTerm, rev(levels(overall.female.plot3$GroupingTerm)))
-
-#add missing GroupingTerms for plot POTENTIALLY DELETE
-#overall.female.plot3 <- add_row(overall.female.plot3, GroupingTerm = "Morphology")
-#overall.female.plot3 <- add_row(overall.female.plot3, GroupingTerm = "Metabolism")
-#overall.female.plot3 <- add_row(overall.female.plot3, GroupingTerm = "Hematology")
-#overall.female.plot3 <- add_row(overall.female.plot3, GroupingTerm = "Hearing")
-#overall.female.plot3 <- add_row(overall.female.plot3, GroupingTerm = "Eye")
-
-#overall.female.plot3$GroupingTerm <- factor(overall.female.plot3$GroupingTerm, levels =c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye", "All") )
-#overall.female.plot3$GroupingTerm <- factor(overall.female.plot3$GroupingTerm, rev(levels(overall.female.plot3$GroupingTerm)))
-
-```
-
-Restructure data for plotting
-
-```{r}
-overall3.female.sig <- gather(overall.female.plot3, parameter, value, c(lnCVR,  lnRR), factor_key= TRUE) #lnVR,
-
-lnCVR.ci <- overall3.female.sig  %>% filter(parameter == "lnCVR") %>% mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
-#lnVR.ci <- overall3.female.sig  %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
-lnRR.ci <- overall3.female.sig  %>% filter(parameter == "lnRR") %>% mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
-
-overall4.female.sig <- bind_rows(lnCVR.ci,  lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high) #lnVR.ci,
-
-overall4.female.sig$label <- "CI not overlapping zero"
-
-```
-
-Plot Fig3 all significant results (CI not overlapping zero, female )
-```{r}
-
-Metameta_Fig3_female.sig <- overall4.female.sig %>%
-  ggplot(aes(y= GroupingTerm, x= value)) +
-  geom_errorbarh(aes(xmin = ci.low,
-                     xmax = ci.high),
-                     height = 0.1, show.legend = FALSE) +
-  geom_point(aes(shape = parameter),
-             fill = 'salmon1', color = 'salmon1', size = 2.2,
-             show.legend = FALSE) +
-  scale_x_continuous(limits=c(-0.4, 0),
-                     breaks = c(-0.3 ,0),
-                     name='Effect size') +
-  geom_vline(xintercept=0,
-             color='black',
-             linetype='dashed')+
-  facet_grid(cols = vars(parameter), #rows = vars(label),
-             #labeller = label_wrap_gen(width = 23),
-             scales= 'free',
-             space='free')+
-  theme_bw()+
-  theme(strip.text.y = element_text(angle = 270, size = 10, margin = margin(t=15, r=15, b=15, l=15)),
-                strip.text.x = element_text(size = 12),
-        strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
-        text = element_text(size = 14),
-        panel.spacing = unit(0.5, "lines"),
-        panel.border= element_blank(),
-        axis.line=element_line(),
-        panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
-        panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
-        panel.grid.minor.y = element_blank(),
-        panel.grid.minor.x = element_blank(),
-        legend.title = element_blank(),
-        axis.title.x = element_blank(),
-                axis.title.y = element_blank())
-
-#Metameta_Fig3_female.sig
-```
-
-#### Fig4 C >10%
+    axis.title.y = element_blank()
+  )
+
+# Metameta_Fig3_female.sig (Figure 5B left panel)
+```
+
+#### Fig5 D >10%
 
@@
 
-#### Male Fig 4 > 10% (male biased traits)
+#### Male Fig 5D > 10% (male biased traits)
 ```{r}
 meta.male.plot3.perc <- metacombo %>%
-    	mutate(percCVR = ifelse(lnCVR > log (11/10), 1, 0),			
-	percVR = ifelse(lnVR > log (11/10), 1, 0),
-	percRR = ifelse(lnRR > log (11/10), 1, 0))
-
-#Significant subset for lnCVR
+  mutate(
+    percCVR = ifelse(lnCVR > log(11 / 10), 1, 0),
+    percVR = ifelse(lnVR > log(11 / 10), 1, 0),
+    percRR = ifelse(lnRR > log(11 / 10), 1, 0)
+  )
+
+# Significant subset for lnCVR
 metacombo_male.plot3.CVR.perc <- meta.male.plot3.perc %>%
@@
 
-#Significant subset for lnVR
+# Significant subset for lnVR
 metacombo_male.plot3.VR.perc <- meta.male.plot3.perc %>%
@@
 
-#Significant subset for lnRR
+# Significant subset for lnRR
 metacombo_male.plot3.RR.perc <- meta.male.plot3.perc %>%
@@
 plot3.male.meta.CVR.perc <- metacombo_male.plot3.CVR.perc %>%
-  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower)/ (2*1.96),  
-				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )
+  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
 
 plot3.male.meta.VR.perc <- metacombo_male.plot3.VR.perc %>%
-  mutate(model_lnVR = map(data, ~ metafor::rma.uni(yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower)/ (2*1.96),  
-				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )
+  mutate(model_lnVR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
 
 plot3.male.meta.RR.perc <- metacombo_male.plot3.RR.perc %>%
-  mutate(model_lnRR = map(data, ~ metafor::rma.uni(yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower)/ (2*1.96),  
-				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )
+  mutate(model_lnRR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
 
@@
 plot3.male.meta.CVR.perc.all <- metacombo_male.plot3.CVR.perc.all %>%
-  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower)/ (2*1.96),  
-				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )
+  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
 
@@
 plot3.male.meta.VR.perc.all <- metacombo_male.plot3.VR.perc.all %>%
-  mutate(model_lnVR = map(data, ~ metafor::rma.uni(yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower)/ (2*1.96),  
-				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )
+  mutate(model_lnVR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
 
@@
 plot3.male.meta.RR.perc.all <- metacombo_male.plot3.RR.perc.all %>%
-  mutate(model_lnRR = map(data, ~ metafor::rma.uni(yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower)/ (2*1.96),  
-				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )
+  mutate(model_lnRR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
 
@@
 plot3.male.meta.CVR.perc.b <- as.data.frame(plot3.male.meta.CVR.perc %>% group_by(GroupingTerm) %>%
-		mutate(lnCVR = map_dbl(model_lnCVR, pluck(2)), lnCVR_lower = map_dbl(model_lnCVR, pluck(6)), 
-		lnCVR_upper =map_dbl(model_lnCVR, pluck(7)), lnCVR_se =map_dbl(model_lnCVR, pluck(3))) )[, c(1,4:7)] 
+  mutate(
+    lnCVR = map_dbl(model_lnCVR, pluck(2)), lnCVR_lower = map_dbl(model_lnCVR, pluck(6)),
+    lnCVR_upper = map_dbl(model_lnCVR, pluck(7)), lnCVR_se = map_dbl(model_lnCVR, pluck(3))
+  ))[, c(1, 4:7)]
 add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.male.meta.CVR.perc.b))
 plot3.male.meta.CVR.perc.b <- rbind(plot3.male.meta.CVR.perc.b, add.row.hearing)
-plot3.male.meta.CVR.perc.b <- plot3.male.meta.CVR.perc.b[order(plot3.male.meta.CVR.perc.b$GroupingTerm),]
+plot3.male.meta.CVR.perc.b <- plot3.male.meta.CVR.perc.b[order(plot3.male.meta.CVR.perc.b$GroupingTerm), ]
 
 plot3.male.meta.VR.perc.b <- as.data.frame(plot3.male.meta.VR.perc %>% group_by(GroupingTerm) %>%
-	mutate(lnVR = map_dbl(model_lnVR, pluck(2)), lnVR_lower = map_dbl(model_lnVR, pluck(6)), 
-	lnVR_upper =map_dbl(model_lnVR, pluck(7)), lnVR_se =map_dbl(model_lnVR, pluck(3))) )[, c(1,4:7)] 
+  mutate(
+    lnVR = map_dbl(model_lnVR, pluck(2)), lnVR_lower = map_dbl(model_lnVR, pluck(6)),
+    lnVR_upper = map_dbl(model_lnVR, pluck(7)), lnVR_se = map_dbl(model_lnVR, pluck(3))
+  ))[, c(1, 4:7)]
 add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.male.meta.VR.perc.b))
 plot3.male.meta.VR.perc.b <- rbind(plot3.male.meta.VR.perc.b, add.row.hearing)
-plot3.male.meta.VR.perc.b <- plot3.male.meta.VR.perc.b[order(plot3.male.meta.VR.perc.b$GroupingTerm),]
+plot3.male.meta.VR.perc.b <- plot3.male.meta.VR.perc.b[order(plot3.male.meta.VR.perc.b$GroupingTerm), ]
 
 plot3.male.meta.RR.perc.b <- as.data.frame(plot3.male.meta.RR.perc %>% group_by(GroupingTerm) %>%
-	mutate(lnRR = map_dbl(model_lnRR, pluck(2)), lnRR_lower = map_dbl(model_lnRR, pluck(6)), 
-	lnRR_upper =map_dbl(model_lnRR, pluck(7)), lnRR_se =map_dbl(model_lnRR, pluck(3))) )[, c(1,4:7)] 
+  mutate(
+    lnRR = map_dbl(model_lnRR, pluck(2)), lnRR_lower = map_dbl(model_lnRR, pluck(6)),
+    lnRR_upper = map_dbl(model_lnRR, pluck(7)), lnRR_se = map_dbl(model_lnRR, pluck(3))
+  ))[, c(1, 4:7)]
 add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>%
@@
 
-plot3.male.meta.RR.perc.b <- plot3.male.meta.RR.perc.b[order(plot3.male.meta.RR.perc.b$GroupingTerm),]
-
-#overall.male.plot3.perc <- full_join(plot3.male.meta.CVR.perc.b, plot3.male.meta.VR.perc.b) 
-overall.male.plot3.perc <- full_join(plot3.male.meta.CVR.perc.b, plot3.male.meta.RR.perc.b)
-
-overall.male.plot3.perc$GroupingTerm <- factor(overall.male.plot3.perc$GroupingTerm, levels =c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye", "All") )
+plot3.male.meta.RR.perc.b <- plot3.male.meta.RR.perc.b[order(plot3.male.meta.RR.perc.b$GroupingTerm), ]
+
+plot3.male.meta.CVR.Vr.perc <- full_join(plot3.male.meta.CVR.perc.b, plot3.male.meta.VR.perc.b)
+overall.male.plot3.perc <- full_join(plot3.male.meta.CVR.Vr.perc, plot3.male.meta.RR.perc.b)
+
+overall.male.plot3.perc$GroupingTerm <- factor(overall.male.plot3.perc$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
 overall.male.plot3.perc$GroupingTerm <- factor(overall.male.plot3.perc$GroupingTerm, rev(levels(overall.male.plot3.perc$GroupingTerm)))
-
 ```
@@
 ```{r}
-overall3.perc <- gather(overall.male.plot3.perc, parameter, value, c(lnCVR, lnRR), factor_key= TRUE) #lnVR,
-
-lnCVR.ci <- overall3.perc %>% filter(parameter == "lnCVR") %>% mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
-#lnVR.ci <- overall3.perc  %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
-lnRR.ci <- overall3.perc  %>% filter(parameter == "lnRR") %>% mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
-
-overall4.male.perc <- bind_rows(lnCVR.ci,  lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high) #lnVR.ci,
+overall3.perc <- gather(overall.male.plot3.perc, parameter, value, c(lnCVR, lnRR), factor_key = TRUE) # lnVR,
+
+lnCVR.ci <- overall3.perc %>%
+  filter(parameter == "lnCVR") %>%
+  mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
+# lnVR.ci <- overall3.perc  %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
+lnRR.ci <- overall3.perc %>%
+  filter(parameter == "lnRR") %>%
+  mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
+
+overall4.male.perc <- bind_rows(lnCVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high) # lnVR.ci,
 
@@
 overall4.male.perc$ci.high <- as.numeric(overall4.male.perc$ci.high)
-
-```
-
-Plot Fig3 (4 in ms) all >10% difference (male bias)
-```{r}
-
-Metameta_Fig3_male.perc <- overall4.male.perc %>% #filter(., GroupingTerm != "Hearing") %>%
-  ggplot(aes(y= GroupingTerm, x= value)) +
-  geom_errorbarh(aes(xmin = ci.low, 
-                     xmax = ci.high), 
-			   height = 0.1, show.legend = FALSE) +
-  geom_point(aes(shape = parameter,
-             fill = parameter), color = 'mediumaquamarine', size = 2.2, 
-             show.legend = FALSE) +
-  scale_x_continuous(limits=c(-0.2, 0.62), 
+```
+
+Plot Fig5D  all >10% difference (male bias)
+```{r}
+
+Metameta_Fig3_male.perc <- overall4.male.perc %>% # filter(., GroupingTerm != "Hearing") %>%
+  ggplot(aes(y = GroupingTerm, x = value)) +
+  geom_errorbarh(aes(
+    xmin = ci.low,
+    xmax = ci.high
+  ),
+  height = 0.1, show.legend = FALSE
+  ) +
+  geom_point(aes(
+    shape = parameter,
+    fill = parameter
+  ),
+  color = "mediumaquamarine", size = 2.2,
+  show.legend = FALSE
+  ) +
+  scale_x_continuous(
+    limits = c(-0.2, 0.62),
     breaks = c(0, 0.3),
-                     name='Effect size') +
-  geom_vline(xintercept=0, 
-             color='black', 
-             linetype='dashed')+
-  facet_grid(cols = vars(parameter), rows = vars(label),
+    name = "Effect size"
+  ) +
+  geom_vline(
+    xintercept = 0,
+    color = "black",
+    linetype = "dashed"
+  ) +
+  facet_grid(
+    cols = vars(parameter), rows = vars(label),
     labeller = label_wrap_gen(width = 23),
-             scales= 'free', 
-             space='free')+
-  theme_bw()+
-  theme(strip.text.y = element_text(angle = 270, size = 10, margin = margin(t=15, r=15, b=15, l=15)), 
+    scales = "free",
+    space = "free"
+  ) +
+  theme_bw() +
+  theme(
+    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
     strip.text.x = element_blank(),
@@
     axis.title.x = element_text(hjust = 0.5, size = 14),
-	  axis.title.y = element_blank())
-
-# Metameta_Fig3_male.perc
-```
-
-####Female Fig 3 >10%
+    axis.title.y = element_blank()
+  )
+
+# Metameta_Fig3_male.perc (Figure 5D right panel)
+```
+
+#### Female Fig 5D >10%
 ```{r}
@@
 meta.plot3.perc <- metacombo %>%
-    	mutate(percCVR = ifelse(lnCVR < log (9/10), 1, 0),			
-	percVR = ifelse(lnVR < log (9/10), 1, 0),
-	percRR = ifelse(lnRR < log (9/10), 1, 0))
-
-#Significant subset for lnCVR
+  mutate(
+    percCVR = ifelse(lnCVR < log(9 / 10), 1, 0),
+    percVR = ifelse(lnVR < log(9 / 10), 1, 0),
+    percRR = ifelse(lnRR < log(9 / 10), 1, 0)
+  )
+
+# Significant subset for lnCVR
 metacombo_plot3.CVR.perc <- meta.plot3.perc %>%
@@
 
-#Significant subset for lnVR
+# Significant subset for lnVR
 metacombo_plot3.VR.perc <- meta.plot3.perc %>%
@@
 
-#Significant subset for lnRR
+# Significant subset for lnRR
 metacombo_plot3.RR.perc <- meta.plot3.perc %>%
@@
 plot3.meta.CVR.perc <- metacombo_plot3.CVR.perc %>%
-  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower)/ (2*1.96),  
-				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )
+  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
 
 plot3.meta.VR.perc <- metacombo_plot3.VR.perc %>%
-  mutate(model_lnVR = map(data, ~ metafor::rma.uni(yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower)/ (2*1.96),  
-				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )
+  mutate(model_lnVR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
 
 plot3.meta.RR.perc <- metacombo_plot3.RR.perc %>%
-  mutate(model_lnRR = map(data, ~ metafor::rma.uni(yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower)/ (2*1.96),  
-				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )
+  mutate(model_lnRR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
 
@@
 plot3.meta.CVR.perc.all <- metacombo_plot3.CVR.perc.all %>%
-  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower)/ (2*1.96),  
-				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )
+  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
 
@@
 plot3.meta.VR.perc.all <- metacombo_plot3.VR.perc.all %>%
-  mutate(model_lnVR = map(data, ~ metafor::rma.uni(yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower)/ (2*1.96),  
-				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )
+  mutate(model_lnVR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
 
@@
 plot3.meta.RR.perc.all <- metacombo_plot3.RR.perc.all %>%
-  mutate(model_lnRR = map(data, ~ metafor::rma.uni(yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower)/ (2*1.96),  
-				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)) )
+  mutate(model_lnRR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
 
@@
 plot3.meta.CVR.perc.b <- as.data.frame(plot3.meta.CVR.perc %>% group_by(GroupingTerm) %>%
-		mutate(lnCVR = map_dbl(model_lnCVR, pluck(2)), lnCVR_lower = map_dbl(model_lnCVR, pluck(6)), 
-		lnCVR_upper =map_dbl(model_lnCVR, pluck(7)), lnCVR_se =map_dbl(model_lnCVR, pluck(3))) )[, c(1,4:7)] 
+  mutate(
+    lnCVR = map_dbl(model_lnCVR, pluck(2)), lnCVR_lower = map_dbl(model_lnCVR, pluck(6)),
+    lnCVR_upper = map_dbl(model_lnCVR, pluck(7)), lnCVR_se = map_dbl(model_lnCVR, pluck(3))
+  ))[, c(1, 4:7)]
 add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.meta.CVR.perc.b))
 plot3.meta.CVR.perc.b <- rbind(plot3.meta.CVR.perc.b, add.row.hearing)
-plot3.meta.CVR.perc.b <- plot3.meta.CVR.perc.b[order(plot3.meta.CVR.perc.b$GroupingTerm),]
+plot3.meta.CVR.perc.b <- plot3.meta.CVR.perc.b[order(plot3.meta.CVR.perc.b$GroupingTerm), ]
 
 plot3.meta.VR.perc.b <- as.data.frame(plot3.meta.VR.perc %>% group_by(GroupingTerm) %>%
-	mutate(lnVR = map_dbl(model_lnVR, pluck(2)), lnVR_lower = map_dbl(model_lnVR, pluck(6)), 
-	lnVR_upper =map_dbl(model_lnVR, pluck(7)), lnVR_se =map_dbl(model_lnVR, pluck(3))) )[, c(1,4:7)] 
+  mutate(
+    lnVR = map_dbl(model_lnVR, pluck(2)), lnVR_lower = map_dbl(model_lnVR, pluck(6)),
+    lnVR_upper = map_dbl(model_lnVR, pluck(7)), lnVR_se = map_dbl(model_lnVR, pluck(3))
+  ))[, c(1, 4:7)]
 add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.meta.VR.perc.b))
 plot3.meta.VR.perc.b <- rbind(plot3.meta.VR.perc.b, add.row.hearing)
-plot3.meta.VR.perc.b <- plot3.meta.VR.perc.b[order(plot3.meta.VR.perc.b$GroupingTerm),]
+plot3.meta.VR.perc.b <- plot3.meta.VR.perc.b[order(plot3.meta.VR.perc.b$GroupingTerm), ]
 
 plot3.meta.RR.perc.b <- as.data.frame(plot3.meta.RR.perc %>% group_by(GroupingTerm) %>%
-	mutate(lnRR = map_dbl(model_lnRR, pluck(2)), lnRR_lower = map_dbl(model_lnRR, pluck(6)), 
-	lnRR_upper =map_dbl(model_lnRR, pluck(7)), lnRR_se =map_dbl(model_lnRR, pluck(3))) )[, c(1,4:7)] 
+  mutate(
+    lnRR = map_dbl(model_lnRR, pluck(2)), lnRR_lower = map_dbl(model_lnRR, pluck(6)),
+    lnRR_upper = map_dbl(model_lnRR, pluck(7)), lnRR_se = map_dbl(model_lnRR, pluck(3))
+  ))[, c(1, 4:7)]
 add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.meta.RR.perc.b))
@@
 
-plot3.meta.RR.perc.b <- plot3.meta.RR.perc.b[order(plot3.meta.RR.perc.b$GroupingTerm),]
-
-#overall.plot3.perc <- full_join(plot3.meta.CVR.perc.b, plot3.meta.VR.perc.b) 
-overall.plot3.perc <- full_join(plot3.meta.CVR.perc.b, plot3.meta.RR.perc.b)
-
-overall.plot3.perc$GroupingTerm <- factor(overall.plot3.perc$GroupingTerm, levels =c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye", "All") )
+plot3.meta.RR.perc.b <- plot3.meta.RR.perc.b[order(plot3.meta.RR.perc.b$GroupingTerm), ]
+
+plot3.meta.CVR.perc.c <- full_join(plot3.meta.CVR.perc.b, plot3.meta.VR.perc.b)
+overall.plot3.perc <- full_join(plot3.meta.CVR.perc.c, plot3.meta.RR.perc.b)
+
+overall.plot3.perc$GroupingTerm <- factor(overall.plot3.perc$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
 overall.plot3.perc$GroupingTerm <- factor(overall.plot3.perc$GroupingTerm, rev(levels(overall.plot3.perc$GroupingTerm)))
-
 ```
@@
 ```{r}
-overall3.perc <- gather(overall.plot3.perc, parameter, value, c(lnCVR, lnRR), factor_key= TRUE) #lnVR,
-
-lnCVR.ci <- overall3.perc %>% filter(parameter == "lnCVR") %>% mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
-#lnVR.ci <- overall3.perc  %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
-lnRR.ci <- overall3.perc  %>% filter(parameter == "lnRR") %>% mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
-
-overall4.perc <- bind_rows(lnCVR.ci,  lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high) #lnVR.ci,
+overall3.perc <- gather(overall.plot3.perc, parameter, value, c(lnCVR, lnRR), factor_key = TRUE) # lnVR,
+
+lnCVR.ci <- overall3.perc %>%
+  filter(parameter == "lnCVR") %>%
+  mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
+# lnVR.ci <- overall3.perc  %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
+lnRR.ci <- overall3.perc %>%
+  filter(parameter == "lnRR") %>%
+  mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
+
+overall4.perc <- bind_rows(lnCVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high) # lnVR.ci,
 
@@
 overall4.perc$ci.high <- as.numeric(overall4.perc$ci.high)
-
-```
-
-Plot Fig3 all >10% difference (female)
+```
+
+Plot Fig5D all >10% difference (female)
 ```{r}
 Metameta_Fig3_female.perc <- overall4.perc %>%
-  ggplot(aes(y= GroupingTerm, x= value)) +
-  geom_errorbarh(aes(xmin = ci.low, 
-                     xmax = ci.high), 
-			   height = 0.1, show.legend = FALSE) +
+  ggplot(aes(y = GroupingTerm, x = value)) +
+  geom_errorbarh(aes(
+    xmin = ci.low,
+    xmax = ci.high
+  ),
+  height = 0.1, show.legend = FALSE
+  ) +
   geom_point(aes(shape = parameter),
-             fill = 'salmon1', color = 'salmon1', size = 2.2, 
-             show.legend = FALSE) +
-
-#scale_shape_manual(values =
-
-  scale_x_continuous(limits=c(-0.53, 0.2), 
+    fill = "salmon1", color = "salmon1", size = 2.2,
+    show.legend = FALSE
+  ) +
+
+  # scale_shape_manual(values =
+
+  scale_x_continuous(
+    limits = c(-0.53, 0.2),
     breaks = c(-0.3, 0),
-                     name='Effect size') +
-  geom_vline(xintercept=0, 
-             color='black', 
-             linetype='dashed')+
-  facet_grid(cols = vars(parameter), #rows = vars(label),
-             #labeller = label_wrap_gen(width = 23),
-             scales= 'free', 
-             space='free')+
-  theme_bw()+
-  theme(strip.text.y = element_text(angle = 270, size = 10, margin = margin(t=15, r=15, b=15, l=15)), 
+    name = "Effect size"
+  ) +
+  geom_vline(
+    xintercept = 0,
+    color = "black",
+    linetype = "dashed"
+  ) +
+  facet_grid(
+    cols = vars(parameter), # rows = vars(label),
+    # labeller = label_wrap_gen(width = 23),
+    scales = "free",
+    space = "free"
+  ) +
+  theme_bw() +
+  theme(
+    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
     strip.text.x = element_blank(),
@@
     axis.title.x = element_text(hjust = 0.5, size = 14),
-	  axis.title.y = element_blank())
-
-#Metameta_Fig3_female.perc
-
-```
-
-#### Plot Fig4:  all plots combined
+    axis.title.y = element_blank()
+  )
+
+# Metameta_Fig3_female.perc (Figure 5D left panel)
+```
+
+#### Plot Fig5:   plots combined
 ```{r}
 library(ggpubr)
-Fig3.bottom <- ggarrange(Metameta_Fig3_female.sig, Metameta_Fig3_male.sig, Metameta_Fig3_female.perc, Metameta_Fig3_male.perc, 
-		   ncol = 2, nrow = 2, widths = c(1, 1.20), heights = c(1, 1))
-
-Fig3 <- ggarrange(Metameta_Fig3_alltraits, Fig3.bottom, ncol = 1, nrow = 2, heights = c(1.4, 2.5))
-Fig3
-#ggsave("MetaResultsCVR_RR.pdf", plot = Fig3, width = 9, height = 6) 
+Fig5b <- ggarrange(Metameta_Fig3_female.sig, Metameta_Fig3_male.sig,
+  ncol = 2, nrow = 1, widths = c(1, 1.20), heights = c(1, 1)
+)
+
+Fig5d <- ggarrange(Metameta_Fig3_female.perc, Metameta_Fig3_male.perc,
+  ncol = 2, nrow = 1, widths = c(1, 1.20), heights = c(1, 1)
+)
+
+# end combination Figure 5
+
+Fig5 <- ggarrange(malebias_Fig2_sigtraits, malebias_Fig2_over10, Fig5b, Fig5d, ncol = 1, nrow = 4, heights = c(2.3, 2, 2.1, 2), labels = c("A", " ", "B", " "))
+Fig5
 ```
@@
 ```{r}
-results.allhetero.grouping <- as.data.frame(cbind(c(1:n), matrix(rep(0, n*30), ncol = 30))) 
-names(results.allhetero.grouping) <- c("id", "sigma2_strain.CVR", "sigma2_center.CVR", "sigma2_error.CVR", "s.nlevels.strain.CVR", 
+results.allhetero.grouping <- as.data.frame(cbind(c(1:n), matrix(rep(0, n * 30), ncol = 30)))
+names(results.allhetero.grouping) <- c(
+  "id", "sigma2_strain.CVR", "sigma2_center.CVR", "sigma2_error.CVR", "s.nlevels.strain.CVR",
   "s.nlevels.center.CVR", "s.nlevels.error.CVR", "sigma2_strain.VR", "sigma2_center.VR", "sigma2_error.VR", "s.nlevels.strain.VR",
@@
   "s.nlevels.center.RR", "s.nlevels.error.RR", "lnCVR", "lnCVR_lower", "lnCVR_upper", "lnCVR_se", "lnVR", "lnVR_lower", "lnVR_upper",
-	"lnVR_se", "lnRR", "lnRR_lower", "lnRR_upper" ,"lnRR_se")
-
+  "lnVR_se", "lnRR", "lnRR_lower", "lnRR_upper", "lnRR_se"
+)
 ```
@@
 
-for(t in 1:n) {
-  tryCatch({
-
+for (t in 1:n) {
+  tryCatch(
+    {
       data_par_age <- data_subset_parameterid_individual_by_age(data, t, age_min = 0, age_center = 100)
@@
 
-    cvr. <- metafor::rma.mv(yi = effect_size_CVR, V = sample_variance_CVR, random = list(~1| strain_name, ~1|production_center,    
-                                ~1|err), control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), data = results)
+      cvr. <- metafor::rma.mv(yi = effect_size_CVR, V = sample_variance_CVR, random = list(
+        ~ 1 | strain_name, ~ 1 | production_center,
+        ~ 1 | err
+      ), control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), data = results)
       results.allhetero.grouping[t, 2] <- cvr.$sigma2[1]
@@
 
-    vr. <- metafor::rma.mv(yi = effect_size_VR, V = sample_variance_VR, random = list(~1| strain_name, ~1|production_center,    
-                                ~1|err), control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), data = results)
+      vr. <- metafor::rma.mv(yi = effect_size_VR, V = sample_variance_VR, random = list(
+        ~ 1 | strain_name, ~ 1 | production_center,
+        ~ 1 | err
+      ), control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), data = results)
       results.allhetero.grouping[t, 8] <- vr.$sigma2[1]
@@
 
-    rr. <- metafor::rma.mv(yi = effect_size_RR, V = sample_variance_RR, random = list(~1| strain_name, ~1|production_center,    
-                                ~1|err), control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), data = results)
+      rr. <- metafor::rma.mv(yi = effect_size_RR, V = sample_variance_RR, random = list(
+        ~ 1 | strain_name, ~ 1 | production_center,
+        ~ 1 | err
+      ), control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), data = results)
       results.allhetero.grouping[t, 14] <- rr.$sigma2[1]
@@
       results.allhetero.grouping[t, 31] <- rr.$se
-
-  }, error=function(e){cat("ERROR :",conditionMessage(e), "\n")})
+    },
+    error = function(e) {
+      cat("ERROR :", conditionMessage(e), "\n")
     }
-
+  )
+}
 ```
@@
 results.allhetero.grouping2 <- results.allhetero.grouping[results.allhetero.grouping$s.nlevels.strain.VR != 0, ]
-nrow(results.allhetero.grouping2) #218
+# nrow(results.allhetero.grouping2) #218
 ```
@@
 ```{r}
-#procedures <- read.csv("../procedures.csv")
+# procedures <- read.csv(here("export", "procedures.csv"))
 
@@
 results.allhetero.grouping2$parameter_name <- data$parameter_name[match(results.allhetero.grouping2$id, data$id)]
-
 ```
@@
 metahetero1 <- results.allhetero.grouping2
-#length(unique(metahetero1$procedure)) #18
-#length(unique(metahetero1$GroupingTerm)) #9 
-#length(unique(metahetero1$parameter_group)) # 149 
-#length(unique(metahetero1$parameter_name)) #218
+# length(unique(metahetero1$procedure)) #18
+# length(unique(metahetero1$GroupingTerm)) #9
+# length(unique(metahetero1$parameter_group)) # 149
+# length(unique(metahetero1$parameter_name)) #218
 
@@
 
-#Create subsets with > 1 count (par_group_size > 1)
+# Create subsets with > 1 count (par_group_size > 1)
 
 metahetero1_sub <- subset(metahetero1, par_group_size > 1) # 90 observations
-#str(metahetero1_sub)
+# str(metahetero1_sub)
 # metahetero1_sub$sampleSize <- as.numeric(metahetero1_sub$sampleSize) #from previous analysis? don't think is used: : delete in final version
@@
   group_by(parameter_group) %>%
-  #mutate(raw_N = sum(sampleSize)) %>%  #don't think is necessary: delete in final version
+  # mutate(raw_N = sum(sampleSize)) %>%  #don't think is necessary: delete in final version
   nest()
@@
 model_count. <- n_count. %>%
-  mutate(model_lnRR = map(data, ~ robu(.x$lnRR ~ 1, data= .x, studynum= .x$id, modelweights = c("CORR"), rho = 0.8, 
-                                                small = TRUE, var.eff.size= (.x$lnRR_se)^2 )),
-  model_lnVR = map(data, ~ robu(.x$lnVR ~ 1, data= .x, studynum= .x$id, modelweights = c("CORR"), rho = 0.8, 
-                                                small = TRUE, var.eff.size= (.x$lnVR_se)^2 )),
-  model_lnCVR = map(data, ~ robu(.x$lnCVR ~ 1, data= .x, studynum= .x$id, modelweights = c("CORR"), rho = 0.8, 
-                                                small = TRUE, var.eff.size= (.x$lnCVR_se)^2 )))
-
-#Robumeta object details:
-#str(model_count.$model_lnCVR[[1]])
+  mutate(
+    model_lnRR = map(data, ~ robu(.x$lnRR ~ 1,
+      data = .x, studynum = .x$id, modelweights = c("CORR"), rho = 0.8,
+      small = TRUE, var.eff.size = (.x$lnRR_se)^2
+    )),
+    model_lnVR = map(data, ~ robu(.x$lnVR ~ 1,
+      data = .x, studynum = .x$id, modelweights = c("CORR"), rho = 0.8,
+      small = TRUE, var.eff.size = (.x$lnVR_se)^2
+    )),
+    model_lnCVR = map(data, ~ robu(.x$lnCVR ~ 1,
+      data = .x, studynum = .x$id, modelweights = c("CORR"), rho = 0.8,
+      small = TRUE, var.eff.size = (.x$lnCVR_se)^2
+    ))
+  )
+
+# Robumeta object details:
+# str(model_count.$model_lnCVR[[1]])
 
@@
 
-count_fun. <- function(mod_sub)
-  return(c(as.numeric(mod_sub$mod_info$term1), mod_sub$N) )
+count_fun. <- function(mod_sub) {
+  return(c(as.numeric(mod_sub$mod_info$term1), mod_sub$N))
+}
 
@@
   select(-estimatelnRR) %>%
-  purrr::set_names(c("parameter_group","var.RR","N.RR"))
+  purrr::set_names(c("parameter_group", "var.RR", "N.RR"))
 
@@
   select(-estimatelnCVR) %>%
-  purrr::set_names(c("parameter_group","var.CVR","N.CVR"))
+  purrr::set_names(c("parameter_group", "var.CVR", "N.CVR"))
 
@@
   select(-estimatelnVR) %>%
-  purrr::set_names(c("parameter_group","var.VR","N.VR"))
+  purrr::set_names(c("parameter_group", "var.VR", "N.VR"))
 
@@
 ```{r}
-metahetero_all <- metahetero1 %>% filter(par_group_size == 1) %>% as_tibble
+metahetero_all <- metahetero1 %>%
+  filter(par_group_size == 1) %>%
+  as_tibble()
 metahetero_all$N.RR <- metahetero_all$s.nlevels.error.RR
@@
 metahetero_all$var.CVR <- log(sqrt(metahetero_all$sigma2_strain.CVR + metahetero_all$sigma2_center.CVR + metahetero_all$sigma2_error.CVR))
-#str(metahetero_all)
-#str(robu_all.)
-
-metahetero_all <- metahetero_all %>% mutate(var.RR = if_else(var.RR == -Inf, -7 ,var.RR),
-                   	  var.VR = if_else(var.VR == -Inf, -5 ,var.VR),
-				  var.CVR = if_else(var.CVR == -Inf, -6 ,var.CVR))
+# str(metahetero_all)
+# str(robu_all.)
+
+metahetero_all <- metahetero_all %>% mutate(
+  var.RR = if_else(var.RR == -Inf, -7, var.RR),
+  var.VR = if_else(var.VR == -Inf, -5, var.VR),
+  var.CVR = if_else(var.CVR == -Inf, -6, var.CVR)
+)
 
@@
 combinedmetahetero <- bind_rows(robu_all., metahetero_all)
-#glimpse(combinedmetahetero)
+# glimpse(combinedmetahetero)
 
@@
 metacombohetero <- combinedmetahetero
-metacombohetero$counts <- metahetero1$par_group_size[match( metacombohetero$parameter_group, metahetero1$parameter_group)]
-metacombohetero$procedure2 <-metahetero1$procedure[match( metacombohetero$parameter_group, metahetero1$parameter_group)]
-metacombohetero$GroupingTerm2 <-metahetero1$GroupingTerm[match( metacombohetero$parameter_group, metahetero1$parameter_group)]
+metacombohetero$counts <- metahetero1$par_group_size[match(metacombohetero$parameter_group, metahetero1$parameter_group)]
+metacombohetero$procedure2 <- metahetero1$procedure[match(metacombohetero$parameter_group, metahetero1$parameter_group)]
+metacombohetero$GroupingTerm2 <- metahetero1$GroupingTerm[match(metacombohetero$parameter_group, metahetero1$parameter_group)]
 
@@
 
-# **Final fixed effects meta-analyses within grouping terms, with SE of the estimate
-
-metacombohetero$var.CVR
+# Final fixed effects meta-analyses within grouping terms, with SE of the estimate
+
+# metacombohetero$var.CVR
 
@@
 
-  mutate(model_heteroCVR = map(data, ~ metafor::rma.uni(yi = .x$var.CVR, sei = sqrt(1 / 2*(.x$N.CVR - 1)),  
-				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 10000, stepadj=0.5), verbose=F)),
-	   model_heteroVR = map(data, ~ metafor::rma.uni(yi = .x$var.VR, sei = sqrt(1 / 2*(.x$N.VR - 1)),  
-				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 10000, stepadj=0.5), verbose=F)),
-	   model_heteroRR = map(data, ~ metafor::rma.uni(yi = .x$var.RR, sei = sqrt(1 / 2*(.x$N.RR - 1)),  
-				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 10000, stepadj=0.5), verbose=F)))
-
-heterog1
+  mutate(
+    model_heteroCVR = map(data, ~ metafor::rma.uni(
+      yi = .x$var.CVR, sei = sqrt(1 / 2 * (.x$N.CVR - 1)),
+      control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 10000, stepadj = 0.5), verbose = F
+    )),
+    model_heteroVR = map(data, ~ metafor::rma.uni(
+      yi = .x$var.VR, sei = sqrt(1 / 2 * (.x$N.VR - 1)),
+      control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 10000, stepadj = 0.5), verbose = F
+    )),
+    model_heteroRR = map(data, ~ metafor::rma.uni(
+      yi = .x$var.RR, sei = sqrt(1 / 2 * (.x$N.RR - 1)),
+      control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 10000, stepadj = 0.5), verbose = F
+    ))
+  )
 
@@
 
-Behaviour.
-<- heterog1 %>% filter(., GroupingTerm == "Behaviour")  %>% select(., -data)  %>%  mutate(heteroCVR=.[[2]][[1]]$b, heteroCVR_lower=.[[2]][[1]]$ci.lb, heteroCVR_upper=.[[2]][[1]]$ci.ub, heteroCVR_se=.[[2]][[1]]$se,
-	              heteroVR=.[[3]][[1]]$b, heteroVR_lower=.[[3]][[1]]$ci.lb, heteroVR_upper=.[[3]][[1]]$ci.ub, heteroVR_se=.[[3]][[1]]$se,
-		        heteroRR=.[[4]][[1]]$b, heteroRR_lower=.[[4]][[1]]$ci.lb, heteroRR_upper=.[[4]][[1]]$ci.ub, heteroRR_se=.[[4]][[1]]$se) %>%
+Behaviour. <- heterog1 %>%
+  filter(., GroupingTerm == "Behaviour") %>%
+  select(., -data) %>%
+  mutate(
+    heteroCVR = .[[2]][[1]]$b, heteroCVR_lower = .[[2]][[1]]$ci.lb, heteroCVR_upper = .[[2]][[1]]$ci.ub, heteroCVR_se = .[[2]][[1]]$se,
+    heteroVR = .[[3]][[1]]$b, heteroVR_lower = .[[3]][[1]]$ci.lb, heteroVR_upper = .[[3]][[1]]$ci.ub, heteroVR_se = .[[3]][[1]]$se,
+    heteroRR = .[[4]][[1]]$b, heteroRR_lower = .[[4]][[1]]$ci.lb, heteroRR_upper = .[[4]][[1]]$ci.ub, heteroRR_se = .[[4]][[1]]$se
+  ) %>%
   select(., GroupingTerm, heteroCVR:heteroRR_se)
 
-Immunology.
-<- heterog1 %>% filter(., GroupingTerm == "Immunology") %>% select(., -data)  %>%  mutate(heteroCVR=.[[2]][[1]]$b, heteroCVR_lower=.[[2]][[1]]$ci.lb, heteroCVR_upper=.[[2]][[1]]$ci.ub, heteroCVR_se=.[[2]][[1]]$se,
-	              heteroVR=.[[3]][[1]]$b, heteroVR_lower=.[[3]][[1]]$ci.lb, heteroVR_upper=.[[3]][[1]]$ci.ub, heteroVR_se=.[[3]][[1]]$se,
-		        heteroRR=.[[4]][[1]]$b, heteroRR_lower=.[[4]][[1]]$ci.lb, heteroRR_upper=.[[4]][[1]]$ci.ub, heteroRR_se=.[[4]][[1]]$se) %>%
+Immunology. <- heterog1 %>%
+  filter(., GroupingTerm == "Immunology") %>%
+  select(., -data) %>%
+  mutate(
+    heteroCVR = .[[2]][[1]]$b, heteroCVR_lower = .[[2]][[1]]$ci.lb, heteroCVR_upper = .[[2]][[1]]$ci.ub, heteroCVR_se = .[[2]][[1]]$se,
+    heteroVR = .[[3]][[1]]$b, heteroVR_lower = .[[3]][[1]]$ci.lb, heteroVR_upper = .[[3]][[1]]$ci.ub, heteroVR_se = .[[3]][[1]]$se,
+    heteroRR = .[[4]][[1]]$b, heteroRR_lower = .[[4]][[1]]$ci.lb, heteroRR_upper = .[[4]][[1]]$ci.ub, heteroRR_se = .[[4]][[1]]$se
+  ) %>%
   select(., GroupingTerm, heteroCVR:heteroRR_se)
 
-Hematology.
-<- heterog1 %>% filter(., GroupingTerm == "Hematology") %>% select(., -data)  %>%  mutate(heteroCVR=.[[2]][[1]]$b, heteroCVR_lower=.[[2]][[1]]$ci.lb, heteroCVR_upper=.[[2]][[1]]$ci.ub, heteroCVR_se=.[[2]][[1]]$se,
-	              heteroVR=.[[3]][[1]]$b, heteroVR_lower=.[[3]][[1]]$ci.lb, heteroVR_upper=.[[3]][[1]]$ci.ub, heteroVR_se=.[[3]][[1]]$se,
-		        heteroRR=.[[4]][[1]]$b, heteroRR_lower=.[[4]][[1]]$ci.lb, heteroRR_upper=.[[4]][[1]]$ci.ub, heteroRR_se=.[[4]][[1]]$se) %>%
+Hematology. <- heterog1 %>%
+  filter(., GroupingTerm == "Hematology") %>%
+  select(., -data) %>%
+  mutate(
+    heteroCVR = .[[2]][[1]]$b, heteroCVR_lower = .[[2]][[1]]$ci.lb, heteroCVR_upper = .[[2]][[1]]$ci.ub, heteroCVR_se = .[[2]][[1]]$se,
+    heteroVR = .[[3]][[1]]$b, heteroVR_lower = .[[3]][[1]]$ci.lb, heteroVR_upper = .[[3]][[1]]$ci.ub, heteroVR_se = .[[3]][[1]]$se,
+    heteroRR = .[[4]][[1]]$b, heteroRR_lower = .[[4]][[1]]$ci.lb, heteroRR_upper = .[[4]][[1]]$ci.ub, heteroRR_se = .[[4]][[1]]$se
+  ) %>%
   select(., GroupingTerm, heteroCVR:heteroRR_se)
 
-Hearing.
-<- heterog1 %>% filter(., GroupingTerm == "Hearing")  %>% select(., -data)  %>%  mutate(heteroCVR=.[[2]][[1]]$b, heteroCVR_lower=.[[2]][[1]]$ci.lb, heteroCVR_upper=.[[2]][[1]]$ci.ub, heteroCVR_se=.[[2]][[1]]$se,
-	              heteroVR=.[[3]][[1]]$b, heteroVR_lower=.[[3]][[1]]$ci.lb, heteroVR_upper=.[[3]][[1]]$ci.ub, heteroVR_se=.[[3]][[1]]$se,
-		        heteroRR=.[[4]][[1]]$b, heteroRR_lower=.[[4]][[1]]$ci.lb, heteroRR_upper=.[[4]][[1]]$ci.ub, heteroRR_se=.[[4]][[1]]$se) %>%
+Hearing. <- heterog1 %>%
+  filter(., GroupingTerm == "Hearing") %>%
+  select(., -data) %>%
+  mutate(
+    heteroCVR = .[[2]][[1]]$b, heteroCVR_lower = .[[2]][[1]]$ci.lb, heteroCVR_upper = .[[2]][[1]]$ci.ub, heteroCVR_se = .[[2]][[1]]$se,
+    heteroVR = .[[3]][[1]]$b, heteroVR_lower = .[[3]][[1]]$ci.lb, heteroVR_upper = .[[3]][[1]]$ci.ub, heteroVR_se = .[[3]][[1]]$se,
+    heteroRR = .[[4]][[1]]$b, heteroRR_lower = .[[4]][[1]]$ci.lb, heteroRR_upper = .[[4]][[1]]$ci.ub, heteroRR_se = .[[4]][[1]]$se
+  ) %>%
   select(., GroupingTerm, heteroCVR:heteroRR_se)
 
-Physiology.
-<- heterog1 %>% filter(., GroupingTerm == "Physiology")  %>% select(., -data)  %>%  mutate(heteroCVR=.[[2]][[1]]$b, heteroCVR_lower=.[[2]][[1]]$ci.lb, heteroCVR_upper=.[[2]][[1]]$ci.ub, heteroCVR_se=.[[2]][[1]]$se,
-	              heteroVR=.[[3]][[1]]$b, heteroVR_lower=.[[3]][[1]]$ci.lb, heteroVR_upper=.[[3]][[1]]$ci.ub, heteroVR_se=.[[3]][[1]]$se,
-		        heteroRR=.[[4]][[1]]$b, heteroRR_lower=.[[4]][[1]]$ci.lb, heteroRR_upper=.[[4]][[1]]$ci.ub, heteroRR_se=.[[4]][[1]]$se) %>%
+Physiology. <- heterog1 %>%
+  filter(., GroupingTerm == "Physiology") %>%
+  select(., -data) %>%
+  mutate(
+    heteroCVR = .[[2]][[1]]$b, heteroCVR_lower = .[[2]][[1]]$ci.lb, heteroCVR_upper = .[[2]][[1]]$ci.ub, heteroCVR_se = .[[2]][[1]]$se,
+    heteroVR = .[[3]][[1]]$b, heteroVR_lower = .[[3]][[1]]$ci.lb, heteroVR_upper = .[[3]][[1]]$ci.ub, heteroVR_se = .[[3]][[1]]$se,
+    heteroRR = .[[4]][[1]]$b, heteroRR_lower = .[[4]][[1]]$ci.lb, heteroRR_upper = .[[4]][[1]]$ci.ub, heteroRR_se = .[[4]][[1]]$se
+  ) %>%
   select(., GroupingTerm, heteroCVR:heteroRR_se)
 
-Metabolism.
-<- heterog1 %>% filter(., GroupingTerm == "Metabolism")  %>% select(., -data)  %>%  mutate(heteroCVR=.[[2]][[1]]$b, heteroCVR_lower=.[[2]][[1]]$ci.lb, heteroCVR_upper=.[[2]][[1]]$ci.ub, heteroCVR_se=.[[2]][[1]]$se,
-	              heteroVR=.[[3]][[1]]$b, heteroVR_lower=.[[3]][[1]]$ci.lb, heteroVR_upper=.[[3]][[1]]$ci.ub, heteroVR_se=.[[3]][[1]]$se,
-		        heteroRR=.[[4]][[1]]$b, heteroRR_lower=.[[4]][[1]]$ci.lb, heteroRR_upper=.[[4]][[1]]$ci.ub, heteroRR_se=.[[4]][[1]]$se) %>%
+Metabolism. <- heterog1 %>%
+  filter(., GroupingTerm == "Metabolism") %>%
+  select(., -data) %>%
+  mutate(
+    heteroCVR = .[[2]][[1]]$b, heteroCVR_lower = .[[2]][[1]]$ci.lb, heteroCVR_upper = .[[2]][[1]]$ci.ub, heteroCVR_se = .[[2]][[1]]$se,
+    heteroVR = .[[3]][[1]]$b, heteroVR_lower = .[[3]][[1]]$ci.lb, heteroVR_upper = .[[3]][[1]]$ci.ub, heteroVR_se = .[[3]][[1]]$se,
+    heteroRR = .[[4]][[1]]$b, heteroRR_lower = .[[4]][[1]]$ci.lb, heteroRR_upper = .[[4]][[1]]$ci.ub, heteroRR_se = .[[4]][[1]]$se
+  ) %>%
   select(., GroupingTerm, heteroCVR:heteroRR_se)
 
-Morphology.
-<- heterog1 %>% filter(., GroupingTerm == "Morphology") %>% select(., -data)  %>%  mutate(heteroCVR=.[[2]][[1]]$b, heteroCVR_lower=.[[2]][[1]]$ci.lb, heteroCVR_upper=.[[2]][[1]]$ci.ub, heteroCVR_se=.[[2]][[1]]$se,
-	              heteroVR=.[[3]][[1]]$b, heteroVR_lower=.[[3]][[1]]$ci.lb, heteroVR_upper=.[[3]][[1]]$ci.ub, heteroVR_se=.[[3]][[1]]$se,
-		        heteroRR=.[[4]][[1]]$b, heteroRR_lower=.[[4]][[1]]$ci.lb, heteroRR_upper=.[[4]][[1]]$ci.ub, heteroRR_se=.[[4]][[1]]$se) %>%
+Morphology. <- heterog1 %>%
+  filter(., GroupingTerm == "Morphology") %>%
+  select(., -data) %>%
+  mutate(
+    heteroCVR = .[[2]][[1]]$b, heteroCVR_lower = .[[2]][[1]]$ci.lb, heteroCVR_upper = .[[2]][[1]]$ci.ub, heteroCVR_se = .[[2]][[1]]$se,
+    heteroVR = .[[3]][[1]]$b, heteroVR_lower = .[[3]][[1]]$ci.lb, heteroVR_upper = .[[3]][[1]]$ci.ub, heteroVR_se = .[[3]][[1]]$se,
+    heteroRR = .[[4]][[1]]$b, heteroRR_lower = .[[4]][[1]]$ci.lb, heteroRR_upper = .[[4]][[1]]$ci.ub, heteroRR_se = .[[4]][[1]]$se
+  ) %>%
   select(., GroupingTerm, heteroCVR:heteroRR_se)
 
-Heart.
-<- heterog1 %>% filter(., GroupingTerm == "Heart")  %>% select(., -data)  %>%  mutate(heteroCVR=.[[2]][[1]]$b, heteroCVR_lower=.[[2]][[1]]$ci.lb, heteroCVR_upper=.[[2]][[1]]$ci.ub, heteroCVR_se=.[[2]][[1]]$se,
-	              heteroVR=.[[3]][[1]]$b, heteroVR_lower=.[[3]][[1]]$ci.lb, heteroVR_upper=.[[3]][[1]]$ci.ub, heteroVR_se=.[[3]][[1]]$se,
-		        heteroRR=.[[4]][[1]]$b, heteroRR_lower=.[[4]][[1]]$ci.lb, heteroRR_upper=.[[4]][[1]]$ci.ub, heteroRR_se=.[[4]][[1]]$se) %>%
+Heart. <- heterog1 %>%
+  filter(., GroupingTerm == "Heart") %>%
+  select(., -data) %>%
+  mutate(
+    heteroCVR = .[[2]][[1]]$b, heteroCVR_lower = .[[2]][[1]]$ci.lb, heteroCVR_upper = .[[2]][[1]]$ci.ub, heteroCVR_se = .[[2]][[1]]$se,
+    heteroVR = .[[3]][[1]]$b, heteroVR_lower = .[[3]][[1]]$ci.lb, heteroVR_upper = .[[3]][[1]]$ci.ub, heteroVR_se = .[[3]][[1]]$se,
+    heteroRR = .[[4]][[1]]$b, heteroRR_lower = .[[4]][[1]]$ci.lb, heteroRR_upper = .[[4]][[1]]$ci.ub, heteroRR_se = .[[4]][[1]]$se
+  ) %>%
   select(., GroupingTerm, heteroCVR:heteroRR_se)
 
-Eye.
-<- heterog1 %>% filter(., GroupingTerm == "Eye")  %>% select(., -data)  %>%  mutate(heteroCVR=.[[2]][[1]]$b, heteroCVR_lower=.[[2]][[1]]$ci.lb, heteroCVR_upper=.[[2]][[1]]$ci.ub, heteroCVR_se=.[[2]][[1]]$se,
-	              heteroVR=.[[3]][[1]]$b, heteroVR_lower=.[[3]][[1]]$ci.lb, heteroVR_upper=.[[3]][[1]]$ci.ub, heteroVR_se=.[[3]][[1]]$se,
-		        heteroRR=.[[4]][[1]]$b, heteroRR_lower=.[[4]][[1]]$ci.lb, heteroRR_upper=.[[4]][[1]]$ci.ub, heteroRR_se=.[[4]][[1]]$se) %>%
+Eye. <- heterog1 %>%
+  filter(., GroupingTerm == "Eye") %>%
+  select(., -data) %>%
+  mutate(
+    heteroCVR = .[[2]][[1]]$b, heteroCVR_lower = .[[2]][[1]]$ci.lb, heteroCVR_upper = .[[2]][[1]]$ci.ub, heteroCVR_se = .[[2]][[1]]$se,
+    heteroVR = .[[3]][[1]]$b, heteroVR_lower = .[[3]][[1]]$ci.lb, heteroVR_upper = .[[3]][[1]]$ci.ub, heteroVR_se = .[[3]][[1]]$se,
+    heteroRR = .[[4]][[1]]$b, heteroRR_lower = .[[4]][[1]]$ci.lb, heteroRR_upper = .[[4]][[1]]$ci.ub, heteroRR_se = .[[4]][[1]]$se
+  ) %>%
   select(., GroupingTerm, heteroCVR:heteroRR_se)
@@
 heterog2 <- bind_rows(Behaviour., Morphology., Metabolism., Physiology., Immunology., Hematology., Heart., Hearing., Eye.)
-#str(heterog2)
+# str(heterog2)
 ```
@@
 ```{r}
-heterog3 <- gather(heterog2, parameter, value, c(heteroCVR, heteroVR, heteroRR), factor_key= TRUE)
-
-heteroCVR.ci <- heterog3 %>% filter(parameter == "heteroCVR") %>% mutate(ci.low = heteroCVR_lower, ci.high = heteroCVR_upper)
-heteroVR.ci <- heterog3 %>% filter(parameter == "heteroVR") %>% mutate(ci.low = heteroVR_lower, ci.high = heteroVR_upper)
-heteroRR.ci <- heterog3 %>% filter(parameter == "heteroRR") %>% mutate(ci.low = heteroRR_lower, ci.high = heteroRR_upper)
+heterog3 <- gather(heterog2, parameter, value, c(heteroCVR, heteroVR, heteroRR), factor_key = TRUE)
+
+heteroCVR.ci <- heterog3 %>%
+  filter(parameter == "heteroCVR") %>%
+  mutate(ci.low = heteroCVR_lower, ci.high = heteroCVR_upper)
+heteroVR.ci <- heterog3 %>%
+  filter(parameter == "heteroVR") %>%
+  mutate(ci.low = heteroVR_lower, ci.high = heteroVR_upper)
+heteroRR.ci <- heterog3 %>%
+  filter(parameter == "heteroRR") %>%
+  mutate(ci.low = heteroRR_lower, ci.high = heteroRR_upper)
 
@@
 
-heterog4$GroupingTerm <- factor(heterog4$GroupingTerm, levels =c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye") )
+heterog4$GroupingTerm <- factor(heterog4$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye"))
 heterog4$GroupingTerm <- factor(heterog4$GroupingTerm, rev(levels(heterog4$GroupingTerm)))
 heterog4$label <- "All traits"
-#write.csv(heterog4, "heterog4.csv")
-
-```
-
-###Plot FIGURE 4 (5 in ms) (Second-order meta analysis on heterogeneity)
+# write.csv(heterog4, "heterog4.csv")
+```
+
+### Plot FIGURE 4 - C(Second-order meta analysis on heterogeneity)
 
@@
 ```{r}
-
-Metameta_Fig4_alltraits <- heterog4 %>%
-
-  ggplot(aes(y= GroupingTerm, x= value)) +
-  geom_errorbarh(aes(xmin = ci.low, 
-                     xmax = ci.high), 
-			   height = 0.1, show.legend = FALSE) +
-  geom_point(aes(shape = parameter,
-             fill = parameter, color = parameter), size = 2.2, 
-             show.legend = FALSE) +
-  scale_x_continuous(limits=c(-7.0, 1), 
-                     #breaks = c(-2.0, -1.5, -1.0, -0.5, 0, 0.5, 1.0, 1.5, 2.0), 
-                     name='Effect size') +
-  facet_grid(cols = vars(parameter), rows = vars(label),
+heterog5 <- heterog4
+heterog5$mean <- as.numeric(exp(heterog5$value))
+heterog5$ci.l <- as.numeric(exp(heterog5$ci.low))
+heterog5$ci.h <- as.numeric(exp(heterog5$ci.high))
+
+heterog6 <- heterog5
+
+Hetero4c <-
+  heterog6 %>%
+  filter(
+    parameter == "heteroCVR" | parameter == "heteroRR"
+  ) %>%
+  ggplot(aes(y = GroupingTerm, x = mean)) +
+  geom_errorbarh(aes(
+    xmin = ci.l,
+    xmax = ci.h
+  ),
+  height = 0.1, show.legend = FALSE
+  ) +
+  geom_point(aes(shape = parameter),
+    fill = "black",
+    color = "black", size = 2.2,
+    show.legend = FALSE
+  ) +
+  scale_x_continuous(
+    limits = c(-0.1, 1.4),
+    # breaks = c(0, 0.1, 0.2),
+    name = "sigma^2"
+  ) +
+  # geom_vline(xintercept=0,
+  # color='black',
+  # linetype='dashed')+
+  facet_grid(
+    cols = vars(parameter), rows = vars(label),
     labeller = label_wrap_gen(width = 23),
-             scales= 'free', 
-             space='free')+
-  theme_bw()+
-  theme(strip.text.y = element_text(angle = 270, size = 10, margin = margin(t=15, r=15, b=15, l=15)), 
+    scales = "free",
+    space = "free"
+  ) +
+  theme_bw() +
+  theme(
+    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
     strip.text.x = element_text(size = 12),
@@
     panel.spacing = unit(0.5, "lines"),
-        panel.border= element_blank(),
-        axis.line=element_line(), 
+    panel.border = element_blank(),
+    axis.line = element_line(),
+    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
+    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
+    panel.grid.minor.y = element_blank(),
+    panel.grid.minor.x = element_blank(),
+    legend.title = element_blank(),
+    axis.title.x = element_text(hjust = 0.5, size = 14),
+    axis.title.y = element_blank()
+  )
+
+# Hetero4c
+
+# ggsave("Fig4.pdf", plot = Metameta_Fig4_alltraits, width = 7, height = 6)
+```
+
+#### Combined Figure 4: overall (Count data, Meta anlysis results, Heterogeneity)
+```{r}
+
+Fig4 <- ggarrange(malebias_Fig2_alltraits, Metameta_Fig3_alltraits, Hetero4c, nrow = 3, align = "v", heights = c(1, 1, 1), labels = c("A", "B", "C"))
+Fig4
+# ggsave("Fig4_OverallResults.pdf", plot = Fig4, width = 6, height = 5)
+```
+
+## Supplemental Figures
+```{r}
+## Heterogneity, S1 C
+
+HeteroS1 <- heterog5 %>%
+  ggplot(aes(y = GroupingTerm, x = mean)) +
+  geom_errorbarh(aes(
+    xmin = ci.l,
+    xmax = ci.h
+  ),
+  height = 0.1, show.legend = FALSE
+  ) +
+  geom_point(aes(shape = parameter),
+    fill = "black",
+    color = "black", size = 2.2,
+    show.legend = FALSE
+  ) +
+  scale_x_continuous(
+    limits = c(-0.1, 1.4),
+    # breaks = c(0, 0.1, 0.2),
+    name = "Effect size"
+  ) +
+  # geom_vline(xintercept=0,
+  # color='black',
+  # linetype='dashed')+
+  facet_grid(
+    cols = vars(parameter), rows = vars(label),
+    labeller = label_wrap_gen(width = 23),
+    scales = "free",
+    space = "free"
+  ) +
+  theme_bw() +
+  theme(
+    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
+    strip.text.x = element_text(size = 12),
+    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
+    text = element_text(size = 14),
+    panel.spacing = unit(0.5, "lines"),
+    panel.border = element_blank(),
+    axis.line = element_line(),
     panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
@@
     axis.title.x = element_blank(),
-	  axis.title.y = element_blank())
-
-Metameta_Fig4_alltraits 
-#ggsave("Fig4.pdf", plot = Metameta_Fig4_alltraits, width = 7, height = 6) 
+    axis.title.y = element_blank()
+  )
+
+# HeteroS1
+
+# ggsave("Fig4.pdf", plot = Metameta_Fig4_alltraits, width = 7, height = 6)
+```
+## Count data, including lnVR (Fig S1 A)
+```{r}
+# *Prepare data for all traits
+
+meta.plot2.all <- meta_clean %>%
+  select(lnCVR, lnVR, lnRR, GroupingTerm) %>%
+  arrange(GroupingTerm)
+
+meta.plot2.all.bS1 <- gather(meta.plot2.all, trait, value, c(lnCVR, lnVR, lnRR))
+
+meta.plot2.all.bS1$trait <- factor(meta.plot2.all.bS1$trait, levels = c("lnCVR", "lnVR", "lnRR"))
+
+meta.plot2.all.cS1 <- meta.plot2.all.bS1 %>%
+  group_by_at(vars(trait, GroupingTerm)) %>%
+  summarise(
+    malebias = sum(value > 0), femalebias = sum(value <= 0), total = malebias + femalebias,
+    malepercent = malebias * 100 / total, femalepercent = femalebias * 100 / total
+  )
+
+meta.plot2.all.cS1$label <- "All traits"
+
+# restructure to create stacked bar plots
+
+meta.plot2.all.dS1 <- as.data.frame(meta.plot2.all.cS1)
+meta.plot2.all.eS1 <- gather(meta.plot2.all.dS1, key = sex, value = percent, malepercent:femalepercent, factor_key = TRUE)
+
+# create new sample size variable
+
+meta.plot2.all.eS1$samplesize <- with(meta.plot2.all.eS1, ifelse(sex == "malepercent", malebias, femalebias))
+
+malebias_FigS1_alltraits <-
+  ggplot(meta.plot2.all.eS1) +
+  aes(x = GroupingTerm, y = percent, fill = sex) +
+  geom_col() +
+  geom_hline(yintercept = 50, linetype = "dashed", color = "gray40") +
+  geom_text(
+    data = subset(meta.plot2.all.eS1, samplesize != 0), aes(label = samplesize), position = position_stack(vjust = .5),
+    color = "white", size = 3.5
+  ) +
+  facet_grid(
+    cols = vars(trait), rows = vars(label), labeller = label_wrap_gen(width = 18),
+    scales = "free", space = "free"
+  ) +
+  scale_fill_brewer(palette = "Set2") +
+  theme_bw(base_size = 18) +
+  theme(
+    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
+    strip.text.x = element_text(size = 12),
+    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
+    text = element_text(size = 14),
+    panel.spacing = unit(0.5, "lines"),
+    panel.border = element_blank(),
+    axis.line = element_line(),
+    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
+    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
+    panel.grid.minor.y = element_blank(),
+    panel.grid.minor.x = element_blank(),
+    legend.position = "none",
+    axis.title.x = element_blank(),
+    axis.title.y = element_blank()
+  ) +
+  coord_flip()
+
+# malebias_FigS1_alltraits     #(panel A in Figure S1)
+```
+###  Overall results of second order meta analysis (Figure 4: overall, Figure 5: sex-bias), INCLUDING VR
+#### Restructure data for plotting 
+Restructure MALE data for plotting 
+```{r}
+overall3.male.sigS <- gather(overall.male.plot3, parameter, value, c(lnCVR, lnVR, lnRR), factor_key = TRUE)
+
+lnCVR.ci <- overall3.male.sigS %>%
+  filter(parameter == "lnCVR") %>%
+  mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
+lnVR.ci <- overall3.male.sigS %>%
+  filter(parameter == "lnVR") %>%
+  mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
+lnRR.ci <- overall3.male.sigS %>%
+  filter(parameter == "lnRR") %>%
+  mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
+
+overall4.male.sigS <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
+
+overall4.male.sigS$label <- "CI not overlapping zero"
+```
+Data are restructured, and grouping terms are being re-ordered
+```{r}
+overall3S <- gather(overall2, parameter, value, c(lnCVR, lnVR, lnRR), factor_key = TRUE)
+
+lnCVR.ci <- overall3S %>%
+  filter(parameter == "lnCVR") %>%
+  mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
+lnVR.ci <- overall3S %>%
+  filter(parameter == "lnVR") %>%
+  mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
+lnRR.ci <- overall3S %>%
+  filter(parameter == "lnRR") %>%
+  mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
+
+overall4S <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
+
+# re-order Grouping Terms
+
+overall4S$GroupingTerm <- factor(overall4S$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
+overall4S$GroupingTerm <- factor(overall4S$GroupingTerm, rev(levels(overall4S$GroupingTerm)))
+overall4S$label <- "All traits"
+```
+
+#### Preparation for Plots FIGURE S1B & S2B, S2D (Second-order meta analysis results, INCL lnVR)
+Preparation: Sub-Plot  for Figure S1: all traits (S1 B)
+```{r}
+Metameta_FigS1_alltraits <- overall4S %>%
+
+  ggplot(aes(y = GroupingTerm, x = value)) +
+  geom_errorbarh(aes(
+    xmin = ci.low,
+    xmax = ci.high
+  ),
+  height = 0.1, show.legend = FALSE
+  ) +
+  geom_point(aes(shape = parameter),
+    fill = "black",
+    color = "black", size = 2.2,
+    show.legend = FALSE
+  ) +
+  scale_x_continuous(
+    limits = c(-0.24, 0.25),
+    breaks = c(-0.2, -0.1, 0, 0.1, 0.2),
+    name = "Effect size"
+  ) +
+  geom_vline(
+    xintercept = 0,
+    color = "black",
+    linetype = "dashed"
+  ) +
+  facet_grid(
+    cols = vars(parameter), rows = vars(label),
+    labeller = label_wrap_gen(width = 23),
+    scales = "free",
+    space = "free"
+  ) +
+  theme_bw() +
+  theme(
+    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
+    strip.text.x = element_text(size = 12),
+    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
+    text = element_text(size = 14),
+    panel.spacing = unit(0.5, "lines"),
+    panel.border = element_blank(),
+    axis.line = element_line(),
+    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
+    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
+    panel.grid.minor.y = element_blank(),
+    panel.grid.minor.x = element_blank(),
+    legend.title = element_blank(),
+    axis.title.x = element_text(hjust = 0.5, size = 14),
+    axis.title.y = element_blank()
+  )
+
+# Metameta_FigS1_alltraits
+```
+
+#### Combined Figure S1: overall Count data, Meta anlysis results, Heterogeneity)
+```{r}
+FigS1 <- ggarrange(malebias_FigS1_alltraits + xlab("percentage sex bias"), Metameta_FigS1_alltraits, HeteroS1, nrow = 3, align = "v", heights = c(1, 1, 1), labels = c("A", "B", "C"))
+FigS1
+# ggsave("FigS1_OverallResults.pdf", plot = Fig4, width = 6, height = 5)
+```
+
+## Figure S2: sex-bias, including VR
+
+Plot FigS2 all significant results (CI not overlapping zero) for males
+```{r}
+meta.plot2.sig.bS <- meta.plot2.sig[, c("lnCVR", "lnVR", "lnRR", "lnCVRsig", "lnVRsig", "lnRRsig", "GroupingTerm")]
+
+meta.plot2.sig.cS <- gather(meta.plot2.sig.bS, trait, value, lnCVR:lnRR)
+meta.plot2.sig.cS$sig <- "placeholder"
+
+meta.plot2.sig.cS$trait <- factor(meta.plot2.sig.cS$trait, levels = c("lnCVR", "lnVR", "lnRR"))
+
+meta.plot2.sig.cS$sig <- ifelse(meta.plot2.sig.cS$trait == "lnCVR", meta.plot2.sig.cS$lnCVRsig,
+  ifelse(meta.plot2.sig.cS$trait == "lnVR", meta.plot2.sig.cS$lnVRsig, meta.plot2.sig.cS$lnRRsig)
+)
+
+# choosing sex biased ln-ratios significantly larger than 0
+meta.plotS2.sig.malebias <- meta.plot2.sig.cS %>%
+  group_by_at(vars(trait, GroupingTerm)) %>%
+  filter(sig == 1) %>%
+  summarise(male_sig = sum(value > 0), female_sig = sum(value < 0), total = male_sig + female_sig)
+
+meta.plotS2.sig.malebias <- ungroup(meta.plotS2.sig.malebias) %>%
+  add_row(trait = "lnCVR", GroupingTerm = "Hearing", male_sig = 0, female_sig = 0, .before = 4) %>% # add "Hearing" for lnCVR (not filtered as only zeros)
+  mutate(malepercent = male_sig * 100 / total, femalepercent = female_sig * 100 / total)
+
+meta.plotS2.sig.malebias$label <- "CI not overlapping zero"
+
+# restructure to create stacked bar plots
+
+meta.plotS2.sig.bothsexes <- as.data.frame(meta.plotS2.sig.malebias)
+meta.plotS2.sig.bothsexes.b <- gather(meta.plotS2.sig.bothsexes, key = sex, value = percent, malepercent:femalepercent, factor_key = TRUE)
+
+# create new sample size variable
+
+meta.plotS2.sig.bothsexes.b$samplesize <- with(meta.plotS2.sig.bothsexes.b, ifelse(sex == "malepercent", male_sig, female_sig))
+
+# *Plot Fig2 all significant results (CI not overlapping zero):
+#     no sig. lnCVR for 'Hearing' in either sex; no sig. male-biased lnCVR for 'Immunology' and 'Eye, and no sig. male-biased lnVR for 'Eye'
+
+malebias_FigS2_sigtraits <-
+  ggplot(meta.plotS2.sig.bothsexes.b) +
+  aes(x = GroupingTerm, y = percent, fill = sex) +
+  geom_col() +
+  geom_hline(yintercept = 50, linetype = "dashed", color = "gray40") +
+  geom_text(
+    data = subset(meta.plotS2.sig.bothsexes.b, samplesize != 0), aes(label = samplesize), position = position_stack(vjust = .5),
+    color = "white", size = 3.5
+  ) +
+  facet_grid(
+    cols = vars(trait), rows = vars(label), labeller = label_wrap_gen(width = 18),
+    scales = "free", space = "free"
+  ) +
+  scale_fill_brewer(palette = "Set2") +
+  theme_bw(base_size = 18) +
+  theme(
+    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
+    strip.text.x = element_text(size = 12),
+    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
+    text = element_text(size = 14),
+    panel.spacing = unit(0.5, "lines"),
+    panel.border = element_blank(),
+    axis.line = element_line(),
+    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
+    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
+    panel.grid.minor.y = element_blank(),
+    panel.grid.minor.x = element_blank(),
+    legend.position = "none",
+    axis.title.x = element_blank(),
+    axis.title.y = element_blank()
+  ) +
+  coord_flip()
+
+# malebias_FigS2_sigtraits # this is Figure S2 A
+```
+Prepare data for traits with effect size ratios > 10% larger in males
+```{r}
+meta.plotS2.over10 <- meta_clean %>%
+  select(lnCVR, lnVR, lnRR, GroupingTerm) %>%
+  arrange(GroupingTerm)
+
+meta.plotS2.over10.b <- gather(meta.plotS2.over10, trait, value, c(lnCVR, lnVR, lnRR))
+
+meta.plotS2.over10.b$trait <- factor(meta.plotS2.over10.b$trait, levels = c("lnCVR", "lnVR", "lnRR"))
+
+meta.plotS2.over10.c <- meta.plotS2.over10.b %>%
+  group_by_at(vars(trait, GroupingTerm)) %>%
+  summarise(
+    malebias = sum(value > log(11 / 10)), femalebias = sum(value < log(9 / 10)), total = malebias + femalebias,
+    malepercent = malebias * 100 / total, femalepercent = femalebias * 100 / total
+  )
+
+meta.plotS2.over10.c$label <- "Sex difference in m/f ratios > 10%"
+
+# restructure to create stacked bar plots
+
+meta.plotS2.over10.c <- as.data.frame(meta.plotS2.over10.c)
+meta.plotS2.over10.d <- gather(meta.plotS2.over10.c, key = sex, value = percent, malepercent:femalepercent, factor_key = TRUE)
+
+# create new sample size variable
+
+meta.plotS2.over10.d$samplesize <- with(meta.plotS2.over10.d, ifelse(sex == "malepercent", malebias, femalebias))
+
+# *Plot FigS2 Sex difference in m/f ratio > 10%
+malebias_FigS2_over10 <-
+  ggplot(meta.plotS2.over10.d) +
+  aes(x = GroupingTerm, y = percent, fill = sex) +
+  geom_col() +
+  geom_hline(yintercept = 50, linetype = "dashed", color = "gray40") +
+  geom_text(
+    data = subset(meta.plot2.over10.d, samplesize != 0), aes(label = samplesize), position = position_stack(vjust = .5),
+    color = "white", size = 3.5
+  ) +
+  facet_grid(
+    cols = vars(trait), rows = vars(label), labeller = label_wrap_gen(width = 18),
+    scales = "free", space = "free"
+  ) +
+  scale_fill_brewer(palette = "Set2") +
+  theme_bw(base_size = 18) +
+  theme(
+    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
+    strip.text.x = element_blank(),
+    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
+    text = element_text(size = 14),
+    panel.spacing = unit(0.5, "lines"),
+    panel.border = element_blank(),
+    axis.line = element_line(),
+    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
+    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
+    panel.grid.minor.y = element_blank(),
+    panel.grid.minor.x = element_blank(),
+    legend.position = "none",
+    axis.title.x = element_blank(),
+    axis.title.y = element_blank()
+  ) +
+  coord_flip()
+
+# malebias_FigS2_over10  #(Panel B in Fig S2 in ms)
+```
+
+#### Female Figure, significant traits
+Female FigS2 B sig
+
+Prepare data for traits with CI not overlapping 0
+create column with 1= different from zero, 0= zero included in CI
+
+Restructure data for plotting
+
+```{r}
+overall3.female.sigS <- gather(overall.female.plot3, parameter, value, c(lnCVR, lnVR, lnRR), factor_key = TRUE)
+
+lnCVR.ci <- overall3.female.sigS %>%
+  filter(parameter == "lnCVR") %>%
+  mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
+lnVR.ci <- overall3.female.sigS %>%
+  filter(parameter == "lnVR") %>%
+  mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
+lnRR.ci <- overall3.female.sigS %>%
+  filter(parameter == "lnRR") %>%
+  mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
+
+overall4.female.sigS <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
+
+overall4.female.sigS$label <- "CI not overlapping zero"
+
+##
+
+Metameta_FigS2_female.sig <- overall4.female.sigS %>%
+  ggplot(aes(y = GroupingTerm, x = value)) +
+  geom_errorbarh(aes(
+    xmin = ci.low,
+    xmax = ci.high
+  ),
+  height = 0.1, show.legend = FALSE
+  ) +
+  geom_point(aes(shape = parameter),
+    fill = "salmon1", color = "salmon1", size = 2.2,
+    show.legend = FALSE
+  ) +
+  scale_x_continuous(
+    limits = c(-0.4, 0),
+    breaks = c(-0.3, 0),
+    name = "Effect size"
+  ) +
+  geom_vline(
+    xintercept = 0,
+    color = "black",
+    linetype = "dashed"
+  ) +
+  facet_grid(
+    cols = vars(parameter), # rows = vars(label),
+    # labeller = label_wrap_gen(width = 23),
+    scales = "free",
+    space = "free"
+  ) +
+  theme_bw() +
+  theme(
+    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
+    strip.text.x = element_text(size = 12),
+    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
+    text = element_text(size = 14),
+    panel.spacing = unit(0.5, "lines"),
+    panel.border = element_blank(),
+    axis.line = element_line(),
+    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
+    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
+    panel.grid.minor.y = element_blank(),
+    panel.grid.minor.x = element_blank(),
+    legend.title = element_blank(),
+    axis.title.x = element_blank(),
+    axis.title.y = element_blank()
+  )
+
+# Metameta_FigS2_female.sig
+```
+
+#Metameta_FigS2_male.sig (Figure 5B right panel)
+
+Restructure MALE data for plotting 
+```{r}
+overall3.male.sigS <- gather(overall.male.plot3, parameter, value, c(lnCVR, lnVR, lnRR), factor_key = TRUE)
+
+lnCVR.ci <- overall3.male.sigS %>%
+  filter(parameter == "lnCVR") %>%
+  mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
+lnVR.ci <- overall3.male.sigS %>%
+  filter(parameter == "lnVR") %>%
+  mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
+lnRR.ci <- overall3.male.sigS %>%
+  filter(parameter == "lnRR") %>%
+  mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
+
+overall4.male.sigS <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
+
+overall4.male.sigS$label <- "CI not overlapping zero"
+```
+Plot FigS2 all significant results (CI not overlapping zero, male )
+```{r}
+Metameta_FigS2_male.sig <- overall4.male.sigS %>%
+  ggplot(aes(y = GroupingTerm, x = value)) +
+  geom_errorbarh(aes(
+    xmin = ci.low,
+    xmax = ci.high
+  ),
+  height = 0.1, show.legend = FALSE
+  ) +
+  geom_point(aes(shape = parameter),
+    fill = "mediumaquamarine", color = "mediumaquamarine", size = 2.2,
+    show.legend = FALSE
+  ) +
+  scale_x_continuous(
+    limits = c(0, 0.4),
+    breaks = c(0, 0.3),
+    name = "Effect size"
+  ) +
+  geom_vline(
+    xintercept = 0,
+    color = "black",
+    linetype = "dashed"
+  ) +
+  facet_grid(
+    cols = vars(parameter), rows = vars(label),
+    labeller = label_wrap_gen(width = 23),
+    scales = "free",
+    space = "free"
+  ) +
+  theme_bw() +
+  theme(
+    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
+    strip.text.x = element_text(size = 12),
+    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
+    text = element_text(size = 14),
+    panel.spacing = unit(0.5, "lines"),
+    panel.border = element_blank(),
+    axis.line = element_line(),
+    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
+    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
+    panel.grid.minor.y = element_blank(),
+    panel.grid.minor.x = element_blank(),
+    legend.title = element_blank(),
+    axis.title.x = element_blank(),
+    axis.title.y = element_blank()
+  )
+
+# Metameta_FigS2_male.sig
+```
+### 10 % Perc sex difference, male bias
+Restructure data for plotting : Male biased, 10% difference
+```{r}
+overall3S.perc <- gather(overall.male.plot3.perc, parameter, value, c(lnCVR, lnVR, lnRR), factor_key = TRUE) # lnVR,
+
+lnCVR.ci <- overall3S.perc %>%
+  filter(parameter == "lnCVR") %>%
+  mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
+lnVR.ci <- overall3S.perc %>%
+  filter(parameter == "lnVR") %>%
+  mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
+lnRR.ci <- overall3S.perc %>%
+  filter(parameter == "lnRR") %>%
+  mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
+
+overall4S.male.perc <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high) # lnVR.ci,
+
+overall4S.male.perc$label <- "Sex difference in m/f ratios > 10%"
+
+overall4S.male.perc$value <- as.numeric(overall4S.male.perc$value)
+overall4S.male.perc$ci.low <- as.numeric(overall4S.male.perc$ci.low)
+overall4S.male.perc$ci.high <- as.numeric(overall4S.male.perc$ci.high)
+```
+
+Plot FigS2  all >10% difference (male bias)
+```{r}
+Metameta_FigS2_male.perc <- overall4S.male.perc %>% # filter(., GroupingTerm != "Hearing") %>%
+  ggplot(aes(y = GroupingTerm, x = value)) +
+  geom_errorbarh(aes(
+    xmin = ci.low,
+    xmax = ci.high
+  ),
+  height = 0.1, show.legend = FALSE
+  ) +
+  geom_point(aes(
+    shape = parameter,
+    fill = parameter
+  ),
+  color = "mediumaquamarine", size = 2.2,
+  show.legend = FALSE
+  ) +
+  scale_x_continuous(
+    limits = c(-0.2, 0.62),
+    breaks = c(0, 0.3),
+    name = "Effect size"
+  ) +
+  geom_vline(
+    xintercept = 0,
+    color = "black",
+    linetype = "dashed"
+  ) +
+  facet_grid(
+    cols = vars(parameter), rows = vars(label),
+    labeller = label_wrap_gen(width = 23),
+    scales = "free",
+    space = "free"
+  ) +
+  theme_bw() +
+  theme(
+    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
+    strip.text.x = element_blank(),
+    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
+    text = element_text(size = 14),
+    panel.spacing = unit(0.5, "lines"),
+    panel.border = element_blank(),
+    axis.line = element_line(),
+    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
+    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
+    panel.grid.minor.y = element_blank(),
+    panel.grid.minor.x = element_blank(),
+    legend.title = element_blank(),
+    axis.title.x = element_text(hjust = 0.5, size = 14),
+    axis.title.y = element_blank()
+  )
+
+# Metameta_FigS2_male.perc (Figure 5D right panel)
+```
+Restructure data for plotting: 
+Female bias, 10 percent difference, including VR
+```{r}
+overall3S.perc <- gather(overall.plot3.perc, parameter, value, c(lnCVR, lnVR, lnRR), factor_key = TRUE) # lnVR,
+
+lnCVR.ci <- overall3S.perc %>%
+  filter(parameter == "lnCVR") %>%
+  mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
+lnVR.ci <- overall3S.perc %>%
+  filter(parameter == "lnVR") %>%
+  mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
+lnRR.ci <- overall3S.perc %>%
+  filter(parameter == "lnRR") %>%
+  mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
+
+overall4S.perc <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
+
+overall4S.perc$label <- "Sex difference in m/f ratios > 10%"
+
+overall4S.perc$value <- as.numeric(overall4S.perc$value)
+overall4S.perc$ci.low <- as.numeric(overall4S.perc$ci.low)
+overall4S.perc$ci.high <- as.numeric(overall4S.perc$ci.high)
+```
+
+Plot Fig5D all >10% difference (female)
+```{r}
+Metameta_Fig3S_female.perc <- overall4S.perc %>%
+  ggplot(aes(y = GroupingTerm, x = value)) +
+  geom_errorbarh(aes(
+    xmin = ci.low,
+    xmax = ci.high
+  ),
+  height = 0.1, show.legend = FALSE
+  ) +
+  geom_point(aes(shape = parameter),
+    fill = "salmon1", color = "salmon1", size = 2.2,
+    show.legend = FALSE
+  ) +
+
+  # scale_shape_manual(values =
+
+  scale_x_continuous(
+    limits = c(-0.53, 0.2),
+    breaks = c(-0.3, 0),
+    name = "Effect size"
+  ) +
+  geom_vline(
+    xintercept = 0,
+    color = "black",
+    linetype = "dashed"
+  ) +
+  facet_grid(
+    cols = vars(parameter), # rows = vars(label),
+    # labeller = label_wrap_gen(width = 23),
+    scales = "free",
+    space = "free"
+  ) +
+  theme_bw() +
+  theme(
+    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
+    strip.text.x = element_blank(),
+    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
+    text = element_text(size = 14),
+    panel.spacing = unit(0.5, "lines"),
+    panel.border = element_blank(),
+    axis.line = element_line(),
+    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
+    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
+    panel.grid.minor.y = element_blank(),
+    panel.grid.minor.x = element_blank(),
+    legend.title = element_blank(),
+    axis.title.x = element_text(hjust = 0.5, size = 14),
+    axis.title.y = element_blank()
+  )
+
+# Metameta_Fig3S_female.perc (Figure 5D left panel)
+```
+Figure S2 
+```{r}
+FigS2c <- ggarrange(Metameta_FigS2_female.sig, Metameta_FigS2_male.sig,
+  ncol = 2, nrow = 1, widths = c(1, 1.20), heights = c(1, 1)
+)
+
+FigS2d <- ggarrange(Metameta_Fig3S_female.perc, Metameta_FigS2_male.perc,
+  ncol = 2, nrow = 1, widths = c(1, 1.20), heights = c(1, 1)
+)
+
+# end combination Figure 5
+
+FigS2 <- ggarrange(malebias_FigS2_sigtraits, malebias_FigS2_over10, FigS2c, FigS2d, ncol = 1, nrow = 4, heights = c(2.2, 2, 2.2, 2), labels = c("A", " ", "B", " "))
+FigS2
 ```

### 2019-11-21 scripts/2019_Nov1-FiguresRearranged_IMPC_variance_and_sex_difference.Rmd
Clean up: data cleaning, loading and variable naming

@@
 
-```{r setup, include=FALSE}
+# Set-up
+
+## Load packages & functions
+
+```{r, include=FALSE}
 knitr::opts_chunk$set(
@@
 ```
-
-## Set up
-#### Packages
 
@@
 
-### Loading functions 
-#### Functions for preparing the data for meta analyses
+Functions for preparing the data for meta analyses
+
 1) "Population statistics"
+
 ```{r}
@@
 2) Extraction of effect sizes and sample variances
+
 ```{r}
@@
     mutate(
-      effect_size_CVR = Calc.lnCVR(CMean = input$x1i, CSD = input$sd1i, CN = input$n1i, EMean = input$x2i, ESD = input$sd2i, EN = input$n2i),
-      sample_variance_CVR = Calc.var.lnCVR(CMean = input$x1i, CSD = input$sd1i, CN = input$n1i, EMean = input$x2i, ESD = input$sd2i, EN = input$n2i),
-      effect_size_VR = Calc.lnVR(CSD = input$sd1i, CN = input$n1i, ESD = input$sd2i, EN = input$n2i),
-      sample_variance_VR = Calc.var.lnVR(CN = input$n1i, EN = input$n2i),
-      effect_size_RR = Calc.lnRR(CMean = input$x1i, CSD = input$sd1i, CN = input$n1i, EMean = input$x2i, ESD = input$sd2i, EN = input$n2i),
-      sample_variance_RR = Calc.var.lnRR(CMean = input$x1i, CSD = input$sd1i, CN = input$n1i, EMean = input$x2i, ESD = input$sd2i, EN = input$n2i),
+      effect_size_CVR = calculate_lnCVR(CMean = input$x1i, CSD = input$sd1i, CN = input$n1i, EMean = input$x2i, ESD = input$sd2i, EN = input$n2i),
+      sample_variance_CVR = calculate_var_lnCVR(CMean = input$x1i, CSD = input$sd1i, CN = input$n1i, EMean = input$x2i, ESD = input$sd2i, EN = input$n2i),
+      effect_size_VR = calculate_lnVR(CSD = input$sd1i, CN = input$n1i, ESD = input$sd2i, EN = input$n2i),
+      sample_variance_VR = calculate_var_lnVR(CN = input$n1i, EN = input$n2i),
+      effect_size_RR = calculate_lnRR(CMean = input$x1i, CSD = input$sd1i, CN = input$n1i, EMean = input$x2i, ESD = input$sd2i, EN = input$n2i),
+      sample_variance_RR = calculate_var_lnRR(CMean = input$x1i, CSD = input$sd1i, CN = input$n1i, EMean = input$x2i, ESD = input$sd2i, EN = input$n2i),
       err = as.factor(seq_len(n()))
@@
 
-3) Meta Analysis
-
- Function to calculate meta-analysis statistics. Created by A M Senior @ the University of Otago NZ 03/01/2014
-
-Below are functions for calculating effect sizes for meta-analysis of variance. 
-All functions take the mean, sd and n from the control and experimental groups.
-
-The first function, Cal.lnCVR, calculates the the log response-ratio of the coefficient of variance (lnCVR) - see Nakagawa et al 2015.
-
-The second function calculates the measurement error variance for lnCVR. As well as the aforementioned parameters, this function also takes
-Equal.E.C.Corr (default = T), which must be True or False. If true, the function assumes that the correlation between mean and sd (Taylor's Law) 
-is equal for the mean and control groups, and, thus these data are pooled. If False the mean-SD correlation for the experimental and control groups
-are calculated separately from one another.
-
-Similar functions are then implemented for lnVR (for comparison of standard deviations) and ln RR  (for comparison of means)
-
-```{r}
-
-Calc.lnCVR <- function(CMean, CSD, CN, EMean, ESD, EN) {
+3) Calculate meta-analysis statistics
+
+Based on function created by A M Senior @ the University of Otago NZ 03/01/2014:
+
+* Calculates effect sizes for meta-analysis of variance.  All functions take the mean, sd and n from the control and experimental groups.
+* The first function, calculate_lnCVR, calculates the the log response-ratio of the coefficient of variance (lnCVR) - see Nakagawa et al 2015.
+* The second function calculates the measurement error variance for lnCVR.
+As well as the aforementioned parameters, this function also takes Equal_E_C_Corr (default = T), which must be True or False.
+If true, the function assumes that the correlation between mean and sd (Taylor's Law)  is equal for the mean and control groups, and, thus these data are pooled.
+If False the mean-SD correlation for the experimental and control groups are calculated separately from one another.
+* Similar functions are then implemented for lnVR (for comparison of standard deviations) and ln RR  (for comparison of means)
+
+```{r}
+
+calculate_lnCVR <- function(CMean, CSD, CN, EMean, ESD, EN) {
   log(ESD) - log(EMean) + 1 / (2 * (EN - 1)) - (log(CSD) - log(CMean) + 1 / (2 * (CN - 1)))
@@
 
-Calc.var.lnCVR <- function(CMean, CSD, CN, EMean, ESD, EN, Equal.E.C.Corr = T) {
-  if (Equal.E.C.Corr == T) {
+calculate_var_lnCVR <- function(CMean, CSD, CN, EMean, ESD, EN, Equal_E_C_Corr = T) {
+  if (Equal_E_C_Corr == T) {
     mvcorr <- 0 # cor.test(log(c(CMean, EMean)), log(c(CSD, ESD)))$estimate   old, slightly incorrect
@@
 
-Calc.lnVR <- function(CSD, CN, ESD, EN) {
+calculate_lnVR <- function(CSD, CN, ESD, EN) {
   log(ESD) - log(CSD) + 1 / (2 * (EN - 1)) - 1 / (2 * (CN - 1))
@@
 
-Calc.var.lnVR <- function(CN, EN) {
+calculate_var_lnVR <- function(CN, EN) {
   1 / (2 * (EN - 1)) + 1 / (2 * (CN - 1))
@@
 
-Calc.lnRR <- function(CMean, CSD, CN, EMean, ESD, EN) {
+calculate_lnRR <- function(CMean, CSD, CN, EMean, ESD, EN) {
   log(EMean) - log(CMean)
@@
 
-Calc.var.lnRR <- function(CMean, CSD, CN, EMean, ESD, EN) {
+calculate_var_lnRR <- function(CMean, CSD, CN, EMean, ESD, EN) {
   CSD^2 / (CN * CMean^2) + ESD^2 / (EN * EMean^2)
@@
 
-## The dataset
+## Load & clean data
 
@@
 
-We here provide the cleaned dataset, which we have saved in a folder called "export", as easy starting point.
-However, the full dataset can be loaded and cleaned using the data cleaning function (Function 1 above), if "#" signs in the code below are removed  (created as that is much smaller than the .csv - which we can still provide for those who absolutely want to start from scratch?)
-
-#### Preparation of raw data
+We here provide the cleaned dataset, which we have saved in a folder called `export`, as easy starting point.
+However, the full dataset can be loaded and cleaned using the data cleaning function below.
+We created this as it much smaller than the .csv.
+
 1) Data loading and cleaning of the csv file
-This step we have already done and provide a cleaned up file which is less computing intensive. However, the cvs is provided in case this is pereferred to be attempted, following the steps below:
-
-```{r Raw Data, eval=FALSE, include=TRUE}
+
+This step we have already done and provide a cleaned up file which is less computing intensive. However, the cvs is provided in case this is preferred to be attempted, following the steps below:
+
+```{r clean, eval=FALSE, include=TRUE}
 # loads the raw data, setting some default types for various columns
@@
 
-    # Fileter to IMPC source (recommened by Jeremey in email to Susi on 20 Aug 2018)
+    # Filter to IMPC source (recommend by Jeremey in email to Susi on 20 Aug 2018)
     filter(datasource_name == "IMPC") %>%
@@
     select(production_center, strain_name, strain_accession_id, biological_sample_id, pipeline_stable_id, procedure_group, procedure_name, sex, date_of_experiment, age_in_days, weight, parameter_name, data_point) %>%
-    arrange(production_center, biological_sample_id, age_in_days)
+
+    # sort
+    arrange(production_center, biological_sample_id, age_in_days) %>%
+
+    # filter to groups with > 1 centre  
+    group_by(parameter_name) %>%
+    mutate(center_per_trait = length(unique(production_center, na.rm = TRUE))) %>%
+    ungroup() %>% 
+    filter(center_per_trait >= 2) %>%
+
+    # Define population variable
+    mutate(population = sprintf("%s-%s", production_center, strain_name)) %>%
+
+    # add grouping variable: these were decided based on functional groups and procedures 
+    left_join(by="parameter_name", 
+      read_csv(here("data", "ParameterGrouping.csv")) %>%
+        select(-id)
+  ) %>% 
+  #### Assign unique IDs (per trait)
+# each unique parameter_name (=trait,use trait variable) gets a unique number ('id')
+
+# We add a new variable, where redundant traits are combined
+#[note however, at this stage the dataset still contains nonsensical traits, i.e. traits that may not contain any information on variance]
+  mutate(id = match(parameter_name, unique(parameter_name)))
 }
-```
-2) Subsetting the data to choose only one data point per individual per trait
-```{r}
-# 2) Subsetting the data to choose only one data point per individual per trait
-
-# this is a necessary step for the loop across all traits
-data_subset_parameterid_individual_by_age <- function(mydata, parameter, age_min, age_center) {
-  tmp <- mydata %>%
+
+# Load raw data - save cleaned dataset as RDS for reuse
+
+data_raw <- load_raw(here("data","dr7.0_all_control_data.csv.gz"))
+
+dir.create("export", F, F)
+
+data_raw %>% 
+  clean_raw_data() %>% 
+  saveRDS("export/data_clean.rds")
+```
+
+For analysis we load the RDS created above:
+
+```{r load}
+data <- readRDS(here("export", "data_clean.rds")) 
+```
+
+Check length of different variables:
+
+```{r}
+length(unique(data$parameter_name)) # 232
+length(unique(data$parameter_group)) # 161
+length(unique(data$procedure_name)) # 26
+
+```
+
+# Meta analysis
+
+## Phase 1: across all traits
+
+Create function for sub-setting the data to choose only one data point per individual per trait. This is a necessary step for the loop across all traits
+
+```{r}
+
+data_subset_parameterid_individual_by_age <- function(mydata, parameter, age_min=0, age_center=100) {
+  mydata %>%
     filter(
@@
     filter(age_diff == min(age_diff)) %>%
-    select(-age_diff)
-
-  # still some individuals with multiple records (because same individual appears under different procedures, so filter to one record)
-  j <- match(unique(tmp$biological_sample_id), tmp$biological_sample_id)
-  tmp[j, ]
+    select(-age_diff) %>% 
+    filter(!duplicated(biological_sample_id))
 }
@@
 
-### Load data (raw / pre-clean)
-
-```{r}
-## Load raw data - save cleaned dataset as RDS for reuse
-# data_raw <- load_raw("data/dr7.0_all_control_data.csv") %>%
-#    clean_raw_data()
-# dir.create("export", F, F)
-# saveRDS(data_raw, "export/data_clean.rds")
-# getwd()
-data1 <- readRDS(here("export", "data_clean.rds"))
-# data1
-```
-
-### Clean data
-This requires the selection of traits that have been measured in at least 2 centers. Consequently, rare or unusual methods and procedures are being filtered out in this step.
-```{r }
-dat1 <-
-  data1 %>%
-  group_by(parameter_name) %>%
-  summarize(center_per_trait = length(unique(production_center, na.rm = TRUE)))
-
-dat2 <- merge(data1, dat1)
-dat_moreThan1center <-
-  dat2 %>%
-  filter(center_per_trait >= 2)
-
-data2 <- dat_moreThan1center
-# min(data2$center_per_trait)  # as a check if there indeed are no single occurences
-```
-
-## Meta analysis, Phase 1: across all traits
-### Preparation
-#### Define population variable 
-& add grouping variables
-
-In this step, a grouping variable is added (found in "Parameter.Grouping.csv")
-The grouping variables were decided based on functional groups and procedures
-
-```{r }
-data3 <- data2 %>%
-  mutate(population = sprintf("%s-%s", production_center, strain_name))
-
-group <- read.csv(here("export", "ParameterGrouping.csv"))
-data <- data3
-data$parameterGroup <- group$parameter[match(data$parameter_name, group$parameter_name)]
-```
-
-#### Assign unique IDs (per trait)
-each unique parameter_name (=trait,use trait variable) gets a unique number ('id')
-
-We add a new variable, where redundant traits are combined
-[note however, at this stage the dataset still contains nonsensical traits, i.e. traits that may not contain any information on variance]
-
-```{r}
-# head(data)
-
-names(data)[16] <- "parameter_group"
-
-data <- transform(data, id = match(parameter_name, unique(parameter_name)))
-n1 <- length(unique(data$parameter_name)) # 232
-n2 <- length(unique(data$parameter_group)) # 161
-n3 <- length(unique(data$procedure_name)) # 26
-
-n <- length(unique(data$id))
-# n  # just to check that the number of traits is 232
-```
-
-#### Create matrix 
-As the current version of this script utilizes a loop instead of tidyR code, it is here necessary to create an empty matrix, in which the returning values will be stored.
-
-```{r}
-results.alltraits.grouping <- as.data.frame(cbind(c(1:n), matrix(rep(0, n * 14), ncol = 14))) # number of individual results per trait = 10
-names(results.alltraits.grouping) <- c("id", "lnCVR", "lnCVR_lower", "lnCVR_upper", "lnCVR_se", "lnVR", "lnVR_lower", "lnVR_upper", "lnVR_se", "lnRR", "lnRR_lower", "lnRR_upper", "lnRR_se", "sampleSize", "trait")
-```
-
-#### Loop running meta-analysis on all traits
+Loop running meta-analysis on all traits
 The loop combines the functions mentioned above and fills the data matrix with results from our meta analysis. 
@@
 
+(n <- length(unique(data$id)))
+
+#Create dataframe to store results
+
+results_alltraits_grouping <- 
+    tibble(id = 1:n, lnCVR=0, lnCVR_lower=0, lnCVR_upper=0, 
+           lnCVR_se=0, lnVR=0, lnVR_lower=0, lnVR_upper=0, 
+           lnVR_se=0, lnRR=0, lnRR_lower=0, lnRR_upper=0, lnRR_se=0, sampleSize=0, trait=0)
+
 for (t in 1:n) {
@@
     {
+
       data_par_age <- data_subset_parameterid_individual_by_age(data, t, age_min = 0, age_center = 100)
-
       population_stats <- calculate_population_stats(data_par_age)
@@
       cvr <- metafor::rma.mv(yi = effect_size_CVR, V = sample_variance_CVR, 
-                             random = list(~ 1 | strain_name, ~ 1 | production_center, ~ 1 | err), control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F, data = results)
-
-      results.alltraits.grouping[t, 2] <- cvr$b
-      results.alltraits.grouping[t, 3] <- cvr$ci.lb
-      results.alltraits.grouping[t, 4] <- cvr$ci.ub
-      results.alltraits.grouping[t, 5] <- cvr$se
+                             random = list(~ 1 | strain_name, ~ 1 | production_center, ~ 1 | err), 
+                             control = list(optimizer = "optim", optmethod = "Nelder-Mead", 
+                                            maxit = 1000), 
+                             verbose = F, data = results)
+
+      results_alltraits_grouping[t, 2] <- cvr$b
+      results_alltraits_grouping[t, 3] <- cvr$ci.lb
+      results_alltraits_grouping[t, 4] <- cvr$ci.ub
+      results_alltraits_grouping[t, 5] <- cvr$se
 
@@
 
-      cv <- metafor::rma.mv(yi = effect_size_VR, V = sample_variance_VR, random = list(~ 1 | strain_name, ~ 1 | production_center, ~ 1 | err), control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F, data = results)
-
-      results.alltraits.grouping[t, 6] <- cv$b
-      results.alltraits.grouping[t, 7] <- cv$ci.lb
-      results.alltraits.grouping[t, 8] <- cv$ci.ub
-      results.alltraits.grouping[t, 9] <- cv$se
+      cv <- metafor::rma.mv(yi = effect_size_VR, V = sample_variance_VR,
+                            random = list(~ 1 | strain_name, ~ 1 | production_center, ~ 1 | err), 
+                            control = list(optimizer = "optim", optmethod = "Nelder-Mead", 
+                                           maxit = 1000), 
+                            verbose = F, data = results)
+
+      results_alltraits_grouping[t, 6] <- cv$b
+      results_alltraits_grouping[t, 7] <- cv$ci.lb
+      results_alltraits_grouping[t, 8] <- cv$ci.ub
+      results_alltraits_grouping[t, 9] <- cv$se
 
@@
 
-      means <- metafor::rma.mv(yi = effect_size_RR, V = sample_variance_RR, random = list(~ 1 | strain_name, ~ 1 | production_center, ~ 1 | err), control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), data = results)
-      results.alltraits.grouping[t, 10] <- means$b
-      results.alltraits.grouping[t, 11] <- means$ci.lb
-      results.alltraits.grouping[t, 12] <- means$ci.ub
-      results.alltraits.grouping[t, 13] <- means$se
-
-      results.alltraits.grouping[t, 14] <- means$k
-      results.alltraits.grouping[t, 15] <- unique(results$trait)
+      means <- metafor::rma.mv(yi = effect_size_RR, V = sample_variance_RR, 
+                               random = list(~ 1 | strain_name, ~ 1 | production_center, ~ 1 | err), 
+                               control = list(optimizer = "optim", optmethod = "Nelder-Mead", 
+                                              maxit = 1000), 
+                               data = results)
+      results_alltraits_grouping[t, 10] <- means$b
+      results_alltraits_grouping[t, 11] <- means$ci.lb
+      results_alltraits_grouping[t, 12] <- means$ci.ub
+      results_alltraits_grouping[t, 13] <- means$se
+
+      results_alltraits_grouping[t, 14] <- means$k
+      results_alltraits_grouping[t, 15] <- unique(results$trait)
     },
@@
 
-# trait_meta_results <- write.csv(results.alltraits.grouping, file = "export/trait_meta_results.csv")
+# trait_meta_results <- write.csv(results_alltraits_grouping, file = "export/trait_meta_results.csv")
 ```
@@
 
-results.alltraits.grouping$parameter_group <- data$parameter_group[match(results.alltraits.grouping$id, data$id)]
-results.alltraits.grouping$procedure <- data$procedure_name[match(results.alltraits.grouping$id, data$id)]
-
-results.alltraits.grouping$GroupingTerm <- procedures$GroupingTerm[match(results.alltraits.grouping$procedure, procedures$procedure)]
-results.alltraits.grouping$parameter_name <- data$parameter_name[match(results.alltraits.grouping$id, data$id)]
-
-meta1 <- results.alltraits.grouping
+results_alltraits_grouping$parameter_group <- data$parameter_group[match(results_alltraits_grouping$id, data$id)]
+results_alltraits_grouping$procedure <- data$procedure_name[match(results_alltraits_grouping$id, data$id)]
+
+results_alltraits_grouping$GroupingTerm <- procedures$GroupingTerm[match(results_alltraits_grouping$procedure, procedures$procedure)]
+results_alltraits_grouping$parameter_name <- data$parameter_name[match(results_alltraits_grouping$id, data$id)]
+
+meta1 <- results_alltraits_grouping
 n <- length(unique(meta1$parameter_name)) # 232
@@
 
-meta_problem <- results.alltraits.grouping[ (results.alltraits.grouping$id %in% c(84, 144, 158, 160, 161, 162, 163, 165, 166, 167, 168, 221, 222, 231)), ]
+meta_problem <- results_alltraits_grouping[ (results_alltraits_grouping$id %in% c(84, 144, 158, 160, 161, 162, 163, 165, 166, 167, 168, 221, 222, 231)), ]
 ```
@@
 Function to collect the outcomes of the "mini" meta analysis
+
 ```{r}
@@
 Extraction of values created during Meta analysis using robu meta:
+
 ```{r}
@@
  Merge the two data sets (the new [robu_all] and the initial [uncorrelated sub-traits with count = 1])
+
 ```{r}
@@
 #### Combine data
+
 ```{r}
@@
  Clean-up and rename
+
 ```{r}
@@
 This is the full result dataset
+
 ```{r}
@@
 Nesting, calculating the number of parameters within each grouping term, and running the meta-analysis
+
 ```{r}
@@
 
-# **Calculate number of parameters per grouping term
+# **calculate number of parameters per grouping term
 
@@
 create column with 1= different from zero, 0= zero included in CI
+
 ```{r}
@@
 Prepare data for traits with effect size ratios > 10% larger in males
+
 ```{r}
@@
 Data are restructured, and grouping terms are being re-ordered
+
 ```{r}
@@
 Preparation: Sub-Plot  for Figure 3: all traits (4B)
+
 ```{r}
@@
 Male-biased (significant) traits
+
 ```{r}
@@
 Restructure MALE data for plotting
+
 ```{r}
@@
 Plot Fig5b all significant results (CI not overlapping zero) for males
+
 ```{r}
@@
 Plot Fig5B all significant results (CI not overlapping zero, female )
+
 ```{r}
@@
 #### Male Fig 5D > 10% (male biased traits)
+
 ```{r}
@@
 Restructure data for plotting : Male biased, 10% difference
+
 ```{r}
@@
 Plot Fig5D  all >10% difference (male bias)
+
 ```{r}
@@
 #### Female Fig 5D >10%
+
 ```{r}
@@
 Female bias, 10 percent difference
+
 ```{r}
@@
 Plot Fig5D all >10% difference (female)
+
 ```{r}
@@
 #### Plot Fig5:   plots combined
+
 ```{r}
@@
 Create matrix to store results for all traits
+
 ```{r}
@@
 #### Exclude traits, merge datasets
+
 ```{r}
@@
 Merge data sets containing metafor results with procedure etc. names
+
 ```{r}
@@
 #### Correlated parameters
+
 ```{r}
@@
 2) calculate the total variance for metafor models as the sum of random effect variances and the residual error, then add in the same columns together with the residual variances from robumeta
+
 ```{r}
@@
 #### Meta-analysis of heterogeneity
+
 ```{r}
@@
 Restructure data for plotting
+
 ```{r}
@@
 Plot Fig4 all traits
+
 ```{r}
@@
 #### Combined Figure 4: overall (Count data, Meta anlysis results, Heterogeneity)
+
 ```{r}
@@
 ## Supplemental Figures
+
 ```{r}
@@
 ```
+
 ## Count data, including lnVR (Fig S1 A)
+
 ```{r}
@@
 ```
+
 ###  Overall results of second order meta analysis (Figure 4: overall, Figure 5: sex-bias), INCLUDING VR
@@
 ```
+
 Data are restructured, and grouping terms are being re-ordered
+
 ```{r}
@@
 Preparation: Sub-Plot  for Figure S1: all traits (S1 B)
+
 ```{r}
@@
 #### Combined Figure S1: overall Count data, Meta anlysis results, Heterogeneity)
+
 ```{r}
@@
 Plot FigS2 all significant results (CI not overlapping zero) for males
+
 ```{r}
@@
 ```
+
 Prepare data for traits with effect size ratios > 10% larger in males
+
 ```{r}
@@
 ```
+
 Plot FigS2 all significant results (CI not overlapping zero, male )
+
 ```{r}
@@
 ```
+
 ### 10 % Perc sex difference, male bias
 Restructure data for plotting : Male biased, 10% difference
+
 ```{r}
@@
 Plot FigS2  all >10% difference (male bias)
+
 ```{r}
@@
 ```
+
 Restructure data for plotting: 
 Female bias, 10 percent difference, including VR
+
 ```{r}
@@
 ```
+
 Figure S2
+
 ```{r}

### 2019-11-21 scripts/2019_Nov1-FiguresRearranged_IMPC_variance_and_sex_difference.Rmd
Clean up: looping across traits

@@
 Loop running meta-analysis on all traits
-The loop combines the functions mentioned above and fills the data matrix with results from our meta analysis. 
-Error messages indicate traits that either did not reach convergence, or that did not return meaningful results in the meta-analysis, due to absence of variance.
+
+* The loop combines the functions mentioned above and fills the data matrix with results from our meta analysis. 
+* Error messages indicate traits that either did not reach convergence, or that did not return meaningful results in the meta-analysis, due to absence of variance.
 Those traits will be removed in later steps, outlined below.
@@
 
-#Create dataframe to store results
-
+# Create dataframe to store results
 results_alltraits_grouping <- 
@@
     {
-
-      data_par_age <- data_subset_parameterid_individual_by_age(data, t, age_min = 0, age_center = 100)
-      population_stats <- calculate_population_stats(data_par_age)
-
-      results <- create_meta_analysis_effect_sizes(population_stats)
+      results <- data %>% 
+        data_subset_parameterid_individual_by_age(t) %>%
+        calculate_population_stats() %>%
+        create_meta_analysis_effect_sizes()
 
@@
                              control = list(optimizer = "optim", optmethod = "Nelder-Mead", 
-                                            maxit = 1000), 
-                             verbose = F, data = results)
-
-      results_alltraits_grouping[t, 2] <- cvr$b
-      results_alltraits_grouping[t, 3] <- cvr$ci.lb
-      results_alltraits_grouping[t, 4] <- cvr$ci.ub
-      results_alltraits_grouping[t, 5] <- cvr$se
-
-      cvr
+                                            maxit = 1000), verbose = F, data = results)
 
       # lnVR, comparison of standard deviations
-
       cv <- metafor::rma.mv(yi = effect_size_VR, V = sample_variance_VR,
@@
                             control = list(optimizer = "optim", optmethod = "Nelder-Mead", 
-                                           maxit = 1000), 
-                            verbose = F, data = results)
-
-      results_alltraits_grouping[t, 6] <- cv$b
-      results_alltraits_grouping[t, 7] <- cv$ci.lb
-      results_alltraits_grouping[t, 8] <- cv$ci.ub
-      results_alltraits_grouping[t, 9] <- cv$se
+                                           maxit = 1000), verbose = F, data = results)
 
       # for means, lnRR
-
       means <- metafor::rma.mv(yi = effect_size_RR, V = sample_variance_RR, 
@@
                                control = list(optimizer = "optim", optmethod = "Nelder-Mead", 
-                                              maxit = 1000), 
-                               data = results)
-      results_alltraits_grouping[t, 10] <- means$b
-      results_alltraits_grouping[t, 11] <- means$ci.lb
-      results_alltraits_grouping[t, 12] <- means$ci.ub
-      results_alltraits_grouping[t, 13] <- means$se
-
-      results_alltraits_grouping[t, 14] <- means$k
-      results_alltraits_grouping[t, 15] <- unique(results$trait)
+                                              maxit = 1000), verbose = F, data = results)
+
+      f <- function(x) unlist(x[c("b", "ci.lb", "ci.ub", "se")])
+
+      results_alltraits_grouping2[t, 2:15] <- 
+        c(f(cvr), f(cv), f(means), means$k, unique(results$trait))
     },
@@
 }
-
-# Now that we have a "results" table with each of the meta-analytic means for all effect sizes of interest, we can use this table as part of the Shiny App, which will then be able to back calculate the percentage differences between males and females for mean, variance and coefficient of variance.
+```
+
+Now that we have a "results" table with each of the meta-analytic means for all effect sizes of interest, we can use this table as part of the Shiny App, which will then be able to back calculate the percentage differences between males and females for mean, variance and coefficient of variance.
 We'll export and use this in the Shiny App.
@@
 # trait_meta_results <- write.csv(results_alltraits_grouping, file = "export/trait_meta_results.csv")
-```
 

### 2020-04-20 Prep & old/FZ 10-12-2019.Rmd
Add files via upload

--- 2019-11-21 scripts/2019_Nov1-FiguresRearranged_IMPC_variance_and_sex_difference.Rmd
@@
 clean_raw_data <- function(mydata) {
+
+  group <- read_csv(here("data", "ParameterGrouping.csv"))
+
+  tmp <- 
     mydata %>%
@@
     # sort
-    arrange(production_center, biological_sample_id, age_in_days) %>%
+    arrange(production_center, biological_sample_id, age_in_days)
 
     # filter to groups with > 1 centre  
-    group_by(parameter_name) %>%
-    mutate(center_per_trait = length(unique(production_center, na.rm = TRUE))) %>%
-    ungroup() %>% 
+    # **Review** - retaining merge here to retain ordering of data used in previous version
+    # usually i would use mutate instead of creating sperate dataset
+    merge(tmp, 
+          tmp %>% group_by(parameter_name) %>%
+    summarise(center_per_trait = length(unique(production_center, na.rm = TRUE)))
+        )%>%
     filter(center_per_trait >= 2) %>%
@@
     # add grouping variable: these were decided based on functional groups and procedures 
-    left_join(by="parameter_name", 
-      read_csv(here("data", "ParameterGrouping.csv")) %>%
-        select(-id)
-  ) %>% 
-  #### Assign unique IDs (per trait)
+    # **Review** - retaining match here to retain ordering of data used in rpevious version
+    mutate(parameter_group = group$parameter_group[match(parameter_name, group$parameter_name)] ) %>%
+    # usually i would use left_join
+        # left_join(by="parameter_name", 
+    #   read_csv(here("data", "ParameterGrouping.csv")) %>%
+    #     select(-id)
+    # ) %>%
+
+    # Assign unique IDs (per trait)
     # each unique parameter_name (=trait,use trait variable) gets a unique number ('id')
@@
     #[note however, at this stage the dataset still contains nonsensical traits, i.e. traits that may not contain any information on variance]
-  mutate(id = match(parameter_name, unique(parameter_name)))
+    mutate(id = match(parameter_name, unique(parameter_name))) %>% 
+    as_tibble()
 }
@@
 # Load raw data - save cleaned dataset as RDS for reuse
-
 data_raw <- load_raw(here("data","dr7.0_all_control_data.csv.gz"))
-
 dir.create("export", F, F)
 
-data_raw %>% 
-  clean_raw_data() %>% 
-  saveRDS("export/data_clean.rds")
-```
-
-For analysis we load the RDS created above:
+data <- data_raw %>% 
+  clean_raw_data() 
+saveRDS(data, "export/data_clean.rds")
+```
+
+For analysis we load the RDS created above and other datasets:
 
@@
 data <- readRDS(here("export", "data_clean.rds"))
-```
-
-Check length of different variables:
-
-```{r}
-length(unique(data$parameter_name)) # 232
-length(unique(data$parameter_group)) # 161
-length(unique(data$procedure_name)) # 26
-
-```
-
-# Meta analysis
-
-## Phase 1: across all traits
+
+procedures <- read_csv(here("data", "procedures.csv"))
+
+```
+
+Check length of different variables / sample sizes:
+
+```{r}
+length(unique(data$parameter_name)) # 232 traits
+length(unique(data$parameter_group)) # 161 parameter groups
+length(unique(data$procedure_name)) # 26 procedure groups
+length(unique(data$biological_sample_id)) # 27147 individial mice   #FZ added 11-12-2019
+#number of males and females per strain per production center #FZ added 11-12-2019
+sampleSizes <-data %>% group_by(production_center, strain_name) %>% count(biological_sample_id, sex) %>% count(sex) %>% print(n = Inf)
+sampleSizes <- write.csv(sampleSizes, file = "export/sampleSizes.csv")
+length(unique(sampleSizes$strain_name)) #9
+length(unique(data$strain_name)) #9
+```
+
+# Phase 1: across all traits
 
@@
 data_subset_parameterid_individual_by_age <- function(mydata, parameter, age_min=0, age_center=100) {
-  mydata %>%
+  tmp <- mydata %>%
     filter(
@@
     filter(age_diff == min(age_diff)) %>%
-    select(-age_diff) %>% 
-    filter(!duplicated(biological_sample_id))
+    select(-age_diff)# %>% 
+#    filter(!duplicated(biological_sample_id))
+
+  # still some individuals with multiple records (because same individual appear under different procedures, so filter to one record)
+  j <- match(unique(tmp$biological_sample_id), tmp$biological_sample_id)
+  tmp[j, ] 
   }
@@
 
-for (t in 1:n) {
+for (t in 160:160) {
   tryCatch(
@@
 
-      results_alltraits_grouping2[t, 2:15] <- 
-        c(f(cvr), f(cv), f(means), means$k, unique(results$trait))
+      results_alltraits_grouping[t, 2:14] <- c(f(cvr), f(cv), f(means), means$k)
+      results_alltraits_grouping[t, 15] <- unique(results$trait)
     },
     error = function(e) {
-      cat("ERROR :", conditionMessage(e), "\n")
+      cat("ERROR :", t, conditionMessage(e), "\n")
     }
@@
 
+--------
+**REVIEW**: The above loop gives some errors, can these be fixed?
+**FZ**: In the above function, we use 'tryCatch' and 'conditionMessage' to prevent the loop from aborting when the first error at row 84 is produced.
+**FZ**  Convergence in the two listed non-converging cases can't be achieved by sensibly tweaking (other optim etc.).
+**FZ**  Since we only learn about non-convergence in the loop, it's difficult to exclude the two traits beforehand.
+**FZ**  Similarly, the 8 traits with very low variation (160, ..., 231) are hard to exclude before.
+**FZ**  Warnings are ok: indicating cases where variance components are set to zero during likelihood optimization.
+
+ERROR : 84 Optimizer (optim) did not achieve convergence (convergence = 10). 
+ERROR : 158 Optimizer (optim) did not achieve convergence (convergence = 10). 
+ERROR : 160 NA/NaN/Inf in 'y' 
+ERROR : 161 NA/NaN/Inf in 'y' 
+ERROR : 162 NA/NaN/Inf in 'y' 
+ERROR : 163 NA/NaN/Inf in 'y' 
+ERROR : 165 NA/NaN/Inf in 'y' 
+ERROR : 166 NA/NaN/Inf in 'y' 
+ERROR : 168 NA/NaN/Inf in 'y'
+ERROR : 231 NA/NaN/Inf in 'y'
+
+Also a bunch of warnings, are any of these a concern?
+
+> warnings()
+Warning messages:
+1: In metafor::rma.mv(yi = effect_size_CVR, V = sample_variance_CVR,  ... :
+  Rows with NAs omitted from model fitting.
+...
+13: In metafor::rma.mv(yi = effect_size_RR, V = sample_variance_RR,  ... :
+  There are outcomes with non-positive sampling variances.
+14: In metafor::rma.mv(yi = effect_size_RR, V = sample_variance_RR,  ... :
+  'V' appears to be not positive definite.
+16: In metafor::rma.mv(yi = effect_size_CVR, V = sample_variance_CVR,  ... :
+  Single-level factor(s) found in 'random' argument. Corresponding 'sigma2' value(s) fixed to 0.
+...
+50: In metafor::rma.mv(yi = effect_size_RR, V = sample_variance_RR,  ... :
+  'V' appears to be not positive definite
+
+------
 Now that we have a "results" table with each of the meta-analytic means for all effect sizes of interest, we can use this table as part of the Shiny App, which will then be able to back calculate the percentage differences between males and females for mean, variance and coefficient of variance.
@@
 
-## Note Susi 31/7/2019: This dataset contains dublicated values, plus no info on what the "traits" mean. I will change Dan N's to one further belwo, that have been cleaned up already
-# FILE TO USE: METACOMBO (around line 500)
-
-# trait_meta_results <- write.csv(results_alltraits_grouping, file = "export/trait_meta_results.csv")
-
-#### Merging datasets & removal of non-converged traits
-
-Procedure names, grouping variables etc. are merged back together with the results from the metafor analysis above.
-This requires loading of another excel sheet, "procedures.csv"
-
-```{r}
-procedures <- read.csv(here("export", "procedures.csv"))
-
-results_alltraits_grouping$parameter_group <- data$parameter_group[match(results_alltraits_grouping$id, data$id)]
-results_alltraits_grouping$procedure <- data$procedure_name[match(results_alltraits_grouping$id, data$id)]
-
-results_alltraits_grouping$GroupingTerm <- procedures$GroupingTerm[match(results_alltraits_grouping$procedure, procedures$procedure)]
-results_alltraits_grouping$parameter_name <- data$parameter_name[match(results_alltraits_grouping$id, data$id)]
-
-meta1 <- results_alltraits_grouping
-n <- length(unique(meta1$parameter_name)) # 232
+(Note Susi 31/7/2019: This dataset contains dublicated values, plus no info on what the "traits" mean. I will change Dan N's to one further belwo, that have been cleaned up already
+FILE TO USE: METACOMBO (around line 500))
+
+### Merging datasets & removal of non-converged traits
+
+Procedure names, grouping variables etc. are merged back together with the results from the metafor analysis above. This requires loading of another excel sheet, "procedures.csv"
+
+```{r}
+results_alltraits_grouping2 <- 
+  results_alltraits_grouping %>% 
+  left_join(by="id",
+             data %>% select(id, parameter_group, procedure = procedure_name, parameter_name) %>%
+              # REVIEW -- this bext line replciates precious code, but removes some procedures, is that right?
+		  # FZ: No. This creates the data from the complete data set ('data'), which was not carried over into 'results_alltraits_grouping'
+		  # FZ: We filter duplicated id's to get only one unique row per id (and there is one id per parameter_name)
+              filter(!duplicated(id))
+            ) %>%
+  # FZ: Below we add 'procedure' (from the previously loaded 'procedures.csv') as a variable
+  left_join(by="procedure", 
+            procedures %>% distinct()
+            )
+
+n <- length(unique(results_alltraits_grouping2$parameter_name)) # 232
 ```
@@
 
-```{r}
-meta_clean <- meta1[ !(meta1$id %in% c(84, 144, 158, 160, 161, 162, 163, 165, 166, 167, 168, 221, 222, 231)), ]
-removed <- length(unique(meta_clean$parameter_name)) # 218
-
-meta_problem <- results_alltraits_grouping[ (results_alltraits_grouping$id %in% c(84, 144, 158, 160, 161, 162, 163, 165, 166, 167, 168, 221, 222, 231)), ]
+**Review**: How did we determine this the ones with problems? 
+**FZ**: In addition to the sentence one line above, to do: add information about cause of exclusion ( 1.
+non-convergence of metafor models, or 2.
+no variation/nonsensical); reference traits to be excluded by trait name (not id number)
+**FZ**: excluded because of non-convergence: 84, 158
+**FZ**: excluded because no variation/nonsensical: 144, 158, 160,... 
+```{r}
+
+#FZ delete# has_problems <- c(84, 144, 158, 160, 161, 162, 163, 165, 166, 167, 168, 221, 222, 231)
+#FZ delete# meta_clean <- results_alltraits_grouping2 %>% filter(!id %in% has_problems)
+#FZ delete# meta_problem <- results_alltraits_grouping2 %>% filter(id %in% has_problems)
+
+#**FZ**:exclude parameter names for which metafor models didn't converge ("dp t cells", "mzb (cd21/35 high)"), and of parameters that don't harbour enough variation
+meta_clean <- results_alltraits_grouping2 %>% 
+	  filter(!parameter_name %in% c("dp t cells", "mzb (cd21/35 high)", "number of caudal vertebrae", 
+	  "number of cervical vertebrae", "number of digits", "number of lumbar vertebrae", "number of pelvic vertebrae", "number of ribs left",                       
+        "number of ribs right", "number of signals", "number of thoracic vertebrae", "total number of acquired events in panel a",
+        "total number of acquired events in panel b", "whole arena permanence"))
+
+```
+```
+
+**Reveiw**: check against old script -- identical, remove once fixed
+
+```{r, eval=FALSE}
+meta_clean.test <- readRDS("../meta_clean.test.rds")
+all.equal(meta_clean, meta_clean.test)
+all.equal(meta_clean %>% select(-parameter_group), meta_clean.test %>% mutate(id=as.integer(id), GroupingTerm = as.character(GroupingTerm)))
 ```
@@
 meta1 <- meta_clean
-# length(unique(meta1$procedure)) #18
-# length(unique(meta1$GroupingTerm)) #9
-# length(unique(meta1$parameter_group)) # 148 levels.
+length(unique(meta1$procedure)) #18
+length(unique(meta1$GroupingTerm)) #9
+# Review: next line now 155 not 148 #FZ comment: still 148 for me.
+length(unique(meta1$parameter_group)) # 148 levels.
 To be used as grouping factor for meta-meta analysis / collapsing down based on things that are classified identically in "parameter_group" but have different "parameter_name"
-# length(unique(meta1$parameter_name)) #218
+length(unique(meta1$parameter_name)) #218
 ```
@@
   scroll_box(width = "100%", height = "200px")
+```
+
+```{r}
+meta1_sub <- meta1 %>%
+  # add summary of number of parameter names in each parameter group
+  group_by(parameter_group) %>%
+  mutate(par_group_size = length(unique(parameter_name)), 
+         sampleSize = as.numeric(sampleSize)) %>% 
+  ungroup() %>% 
+  # Create subsets with > 1 count (par_group_size > 1)
+  filter(par_group_size > 1) # 90 observations
+```
+
+#### Meta-analyses on correlated (sub-)traits, using robumeta` 
+The subset of the data is prepared (nested), and in this first step the model of the meta analysis effect sizes are calculated
+
+```{r}
 
@@
   summarize(par_group_size = length(unique(parameter_name, na.rm = TRUE)))
-# this gives a summary of number of parameter names in each parameter group, now it neeeds to get merged it back together
+#this gives a summary of number of parameter names in each parameter group, now it neeeds to get merged it back together
 
@@
 
-meta1_sub <- subset(meta1, par_group_size > 1) # 90 observations
+meta1_sub<-subset(meta1,par_group_size >1) # 90 observations   
 meta1_sub$sampleSize <- as.numeric(meta1_sub$sampleSize)
-```
-
-#### Meta-analyses on correlated (sub-)traits, using robumeta` 
-The subset of the data is prepared (nested), and in this first step the model of the meta analysis effect sizes are calculated
-
-```{r}
+
 # nesting
@@
   group_by(GroupingTerm) %>%
-  nest()
+#FZ comment: changed 'nest' to 'nest_legacy' to keep old syntax/functionality
+  nest_legacy()
 
@@
 metacombo_final_all <- metacombo %>%
-  nest()
+#FZ comment: changed 'nest' to 'nest_legacy' to keep old syntax/functionality
+  nest_legacy()
 
@@
 # *Prepare data for all traits
+
+##FZ: 11-12-2019 to here!#
 

### 2020-04-20 Prep & old/SydneySexDiff WITH comments Felix & Dan.Rmd
Add files via upload

--- 2020-04-20 Prep & old/FZ 10-12-2019.Rmd
@@
 
-## Load packages & functions
+## Loading packages & custom functions
 
@@
 )
-
 ```
@@
 
-1) "Population statistics"
+1) "Population statistics": "calculate_population_stats"
+This function groups animals from the same strain and same insitiution together.
+This is done for each trait seoarately, and only for traits that have been measured in both sexes.
+Any group containing fewer than 5 individuals is excluded.
 
@@
 
-2) Extraction of effect sizes and sample variances
+2) Extraction of effect sizes and sample variances: "create_meta_analysis_effect_sizes"
 
@@
 
-Having loaded the necessary functions, we can get started on the dataset.
-
-We here provide the cleaned dataset, which we have saved in a folder called `export`, as easy starting point.
-However, the full dataset can be loaded and cleaned using the data cleaning function below.
-We created this as it much smaller than the .csv.
-
 1) Data loading and cleaning of the csv file
 
-This step we have already done and provide a cleaned up file which is less computing intensive. However, the cvs is provided in case this is preferred to be attempted, following the steps below:
+This step we have already done and provide a cleaned up file which is less computing intensive and which we have saved in a folder called `export`.
+However, the cvs is provided in case this is preferred to be attempted, following the steps below:
 
@@
     # add grouping variable: these were decided based on functional groups and procedures 
-    # **Review** - retaining match here to retain ordering of data used in rpevious version
-    mutate(parameter_group = group$parameter_group[match(parameter_name, group$parameter_name)] ) %>%
+    mutate(parameter_group = group$parameter[match(parameter_name, group$parameter_name)] ) %>%
     # usually i would use left_join
@@
 length(unique(data$biological_sample_id)) # 27147 individial mice   #FZ added 11-12-2019
-#number of males and females per strain per production center #FZ added 11-12-2019
-sampleSizes <-data %>% group_by(production_center, strain_name) %>% count(biological_sample_id, sex) %>% count(sex) %>% print(n = Inf)
-sampleSizes <- write.csv(sampleSizes, file = "export/sampleSizes.csv")
-length(unique(sampleSizes$strain_name)) #9
-length(unique(data$strain_name)) #9
+#number of males and females per strain per production center #FZ added 11-12-2019  # FOR TABLE SAMPLE SIZES
+data %>% group_by(production_center, strain_name) %>% count(biological_sample_id, sex) %>% count(sex) %>% print(n = Inf)
+
 ```
@@
 
-for (t in 160:160) {
+for (t in 1:n) {
   tryCatch(
@@
   left_join(by="id",
-             data %>% select(id, parameter_group, procedure = procedure_name, parameter_name) %>%
+             data %>% select(id, parameter_group, procedure = procedure_name, procedure_name, parameter_name) %>% #susi: check parateer group
               # REVIEW -- this bext line replciates precious code, but removes some procedures, is that right?
@@
 
-#**FZ**:exclude parameter names for which metafor models didn't converge ("dp t cells", "mzb (cd21/35 high)"), and of parameters that don't harbour enough variation
+#**FZ**: We exclude 14 parameter names for which metafor models didn't converge ("dp t cells", "mzb (cd21/35 high)"), and of parameters that don't harbour enough variation
 meta_clean <- results_alltraits_grouping2 %>% 
@@
 ```{r, eval=FALSE}
-meta_clean.test <- readRDS("../meta_clean.test.rds")
+meta_clean.test <- readRDS("../meta_clean.test.rds")  #FZ comment: doesn't work for me. '../' is for the github location?
 all.equal(meta_clean, meta_clean.test)
@@
 
-meta1_sub<-subset(meta1,par_group_size >1) # 90 observations   
+meta1_sub <- subset(meta1,par_group_size >1) # 90 observations   
 meta1_sub$sampleSize <- as.numeric(meta1_sub$sampleSize)
@@
 ```{r}
-# Step1
+# Step1 (columns are matched by name (in our case, 'parameter_group'), and any missing columns will be filled with NA) #FZ added explanation of bibd_rows
 combinedmeta <- bind_rows(robu_all, meta_all)
@@
 
-# Steps 2&3
+# Steps 2&3 (add information about number of traits in a parameter group, procedure, and grouping term) #FZ added expalnation in brackets
 metacombo <- combinedmeta
@@
 
- Clean-up and rename
-
-```{r}
-metacombo <- metacombo[, c(1, 21:23, 2:13)]
-names(metacombo)[3] <- "procedure"
-names(metacombo)[4] <- "GroupingTerm"
+Clean-up, reorder, and rename
+
+```{r}
+metacombo <- metacombo[, c(1, 21:23, 2:13)] # SUSI CHANGE TO NAMES!!!
+names(metacombo)[3] <- "procedure" #change "3" to name
+names(metacombo)[4] <- "GroupingTerm" #change "4" to name
 
@@
 
-compare <- metacombo %>%
+metacombo %>%
   group_by(GroupingTerm) %>%
@@
 
-# compare
 ```
@@
 
-Re-structure data for each grouping term; delete unused variables
+Re-structure data for each grouping term; delete unused variables  #FZ comment: referencing of cells below doesn't depend on previous oreding of the data, i.e.
+only changes if output structure from metafor::rma.uni changes
 
@@
 
-overall2 <- bind_rows(Behaviour, Morphology, Metabolism, Physiology, Immunology, Hematology, Heart, Hearing, Eye, All)
+overall2 <- bind_rows(Behaviour, Morphology, Metabolism, Physiology, Immunology, Hematology, Heart, Hearing, Eye, All) #FZ: warnings are ok
 ```
@@
 # *Prepare data for all traits
-
-##FZ: 11-12-2019 to here!#
 
@@
 
+# add summary row ('All') and re-arrange rows into correct order for plotting #FZ added
+
+meta.plot2.all.f <- meta.plot2.all.e %>% group_by(trait, sex) %>% 
+	summarise(GroupingTerm = "All", malebias = sum(malebias), femalebias = sum(femalebias), total = malebias + femalebias, 
+	label = "All traits", samplesize = sum(samplesize)) %>%
+	mutate(percent = ifelse(sex == "femalepercent", femalebias*100/(malebias+femalebias), malebias*100/(malebias+femalebias))) %>%
+	bind_rows(meta.plot2.all.e, .) %>%
+	mutate(rownumber = row_number()) %>%
+	.[c(37, 1:9, 39, 10:18, 38, 19:27, 40, 28:36), ]
+
+meta.plot2.all.f$GroupingTerm <- factor(meta.plot2.all.f$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All")) 
+meta.plot2.all.f$GroupingTerm <- factor(meta.plot2.all.f$GroupingTerm, rev(levels(meta.plot2.all.f$GroupingTerm)))
+
 malebias_Fig2_alltraits <-
-  ggplot(meta.plot2.all.e) +
+  ggplot(meta.plot2.all.f) +
   aes(x = GroupingTerm, y = percent, fill = sex) +
@@
   geom_text(
-    data = subset(meta.plot2.all.e, samplesize != 0), aes(label = samplesize), position = position_stack(vjust = .5),
+    data = subset(meta.plot2.all.f, samplesize != 0), aes(label = samplesize), position = position_stack(vjust = .5),
     color = "white", size = 3.5

### 2020-04-20 Prep & old/SydneySexDiffFelix&Dan.Rmd
Add files via upload

--- 2020-04-20 Prep & old/SydneySexDiff WITH comments Felix & Dan.Rmd
@@
 
-## Loading packages & custom functions
+## Load packages & functions
 
@@
 )
+
 ```
@@
 
-1) "Population statistics": "calculate_population_stats"
-This function groups animals from the same strain and same insitiution together.
-This is done for each trait seoarately, and only for traits that have been measured in both sexes.
-Any group containing fewer than 5 individuals is excluded.
+1) "Population statistics"
 
@@
 
-2) Extraction of effect sizes and sample variances: "create_meta_analysis_effect_sizes"
+2) Extraction of effect sizes and sample variances
 
@@
 
+Having loaded the necessary functions, we can get started on the dataset.
+
+We here provide the cleaned dataset, which we have saved in a folder called `export`, as easy starting point.
+However, the full dataset can be loaded and cleaned using the data cleaning function below.
+We created this as it much smaller than the .csv.
+
 1) Data loading and cleaning of the csv file
 
-This step we have already done and provide a cleaned up file which is less computing intensive and which we have saved in a folder called `export`.
-However, the cvs is provided in case this is preferred to be attempted, following the steps below:
+This step we have already done and provide a cleaned up file which is less computing intensive. However, the cvs is provided in case this is preferred to be attempted, following the steps below:
 
@@
     # add grouping variable: these were decided based on functional groups and procedures 
+    # **Review** - retaining match here to retain ordering of data used in rpevious version
     mutate(parameter_group = group$parameter[match(parameter_name, group$parameter_name)] ) %>%

### 2020-04-20 Prep & old/SydneySexDiff_Felix_11-2-2020TEST.Rmd
Add files via upload

--- 2020-04-20 Prep & old/SydneySexDiff WITH comments Felix & Dan.Rmd
@@
 library(tidyverse)
+library(tidyr)
 library(tibble)
@@
 
-Functions for preparing the data for meta analyses
-
-1) "Population statistics": "calculate_population_stats"
+## Functions 
+for preparing the data for meta analyses
+
+### 1) Subsetting data
+Create function for sub-setting the data to choose only one data point per individual per trait: "data_subset_parameterid_individual_by_age"
+
+```{r}
+data_subset_parameterid_individual_by_age <- function(mydata, parameter, age_min=0, age_center=100) {
+  tmp <- mydata %>%
+    filter(
+      age_in_days >= age_min,
+      id == parameter
+    ) %>%
+    # take results for single individual closest to age_center
+    mutate(age_diff = abs(age_center - age_in_days)) %>%
+    group_by(biological_sample_id) %>%
+    filter(age_diff == min(age_diff)) %>%
+    select(-age_diff)# %>% 
+#    filter(!duplicated(biological_sample_id))  #Felix 6/2/2020: this line can be deleted
+
+  # still some individuals with multiple records (because same individual appear under different procedures, so filter to one record)
+  j <- match(unique(tmp$biological_sample_id), tmp$biological_sample_id)
+  tmp[j, ] 
+  }
+```
+
+### 2) "Population statistics"
+Create function called: "calculate_population_stats"
 This function groups animals from the same strain and same insitiution together.
@@
 
-2) Extraction of effect sizes and sample variances: "create_meta_analysis_effect_sizes"
+### 3) Extraction of effect sizes and sample variances
+Function: "create_meta_analysis_effect_sizes"
 
@@
 
-3) Calculate meta-analysis statistics
-
-Based on function created by A M Senior @ the University of Otago NZ 03/01/2014:
+### 4) Calculate meta-analysis statistics
+
+Based on a function created by A M Senior @ the University of Otago NZ 03/01/2014:
 
@@
 
-1) Data loading and cleaning of the csv file
+### 1) Data loading and cleaning of the csv file
 
@@
 
-    # subset to reasonable set of variables
-    # date_of_experiment: Jeremy suggested using as an indicator of batch-level effects
+    # subset to reasonable set of variables, date_of_experiment used as an indicator of batch-level effects
     select(production_center, strain_name, strain_accession_id, biological_sample_id, pipeline_stable_id, procedure_group, procedure_name, sex, date_of_experiment, age_in_days, weight, parameter_name, data_point) %>%
@@
     # filter to groups with > 1 centre  
-    # **Review** - retaining merge here to retain ordering of data used in previous version
-    # usually i would use mutate instead of creating sperate dataset
     merge(tmp, 
@@
     mutate(parameter_group = group$parameter[match(parameter_name, group$parameter_name)] ) %>%
-    # usually i would use left_join
-        # left_join(by="parameter_name", 
-    #   read_csv(here("data", "ParameterGrouping.csv")) %>%
-    #     select(-id)
-    # ) %>%
 
@@
 
-Check length of different variables / sample sizes:
-
-```{r}
-length(unique(data$parameter_name)) # 232 traits
-length(unique(data$parameter_group)) # 161 parameter groups
-length(unique(data$procedure_name)) # 26 procedure groups
-length(unique(data$biological_sample_id)) # 27147 individial mice   #FZ added 11-12-2019
-#number of males and females per strain per production center #FZ added 11-12-2019  # FOR TABLE SAMPLE SIZES
-data %>% group_by(production_center, strain_name) %>% count(biological_sample_id, sex) %>% count(sex) %>% print(n = Inf)
-
-```
-
-# Phase 1: across all traits
-
-Create function for sub-setting the data to choose only one data point per individual per trait. This is a necessary step for the loop across all traits
-
-```{r}
-
-data_subset_parameterid_individual_by_age <- function(mydata, parameter, age_min=0, age_center=100) {
-  tmp <- mydata %>%
-    filter(
-      age_in_days >= age_min,
-      id == parameter
-    ) %>%
-    # take results for single individual closest to age_center
-    mutate(age_diff = abs(age_center - age_in_days)) %>%
-    group_by(biological_sample_id) %>%
-    filter(age_diff == min(age_diff)) %>%
-    select(-age_diff)# %>% 
-#    filter(!duplicated(biological_sample_id))
-
-  # still some individuals with multiple records (because same individual appear under different procedures, so filter to one record)
-  j <- match(unique(tmp$biological_sample_id), tmp$biological_sample_id)
-  tmp[j, ] 
-  }
-```
-
-Loop running meta-analysis on all traits
+Checking length of different variables and sample sizes.
+
+### Table 1:  "Strains and Center Sample Sizes"
+This table summarises the available numbers of male and female mice from each strain and originating institution.
+
+```{r echo = FALSE, results = 'hold'}
+#length(unique(data$parameter_name)) # 232 traits
+#length(unique(data$parameter_group)) # 161 parameter groups
+#length(unique(data$procedure_name)) # 26 procedure groups
+#length(unique(data$biological_sample_id)) # 27147 individial mice
+
+#number of males and females per strain per production center 
+kable(cbind(data %>% group_by(production_center, strain_name) %>% count(biological_sample_id, sex) %>% count(sex) %>% print(n = Inf))) %>%
+  kable_styling() %>%
+  scroll_box(width = "70%", height = "200px")
+
+## SZ: I don't understand why the tibble is showing in the knitted html
+```
+
+# Meta-analyses
+## 1. Population as analysis unit 
+(Step C, Figure 3 in main document)
+
+### Loop: Meta-analyses on all traits
 
@@
 
-(n <- length(unique(data$id)))
+n <- length(unique(data$id))
 
@@
 
---------
-**REVIEW**: The above loop gives some errors, can these be fixed?
-**FZ**: In the above function, we use 'tryCatch' and 'conditionMessage' to prevent the loop from aborting when the first error at row 84 is produced.
-**FZ**  Convergence in the two listed non-converging cases can't be achieved by sensibly tweaking (other optim etc.).
-**FZ**  Since we only learn about non-convergence in the loop, it's difficult to exclude the two traits beforehand.
-**FZ**  Similarly, the 8 traits with very low variation (160, ..., 231) are hard to exclude before.
-**FZ**  Warnings are ok: indicating cases where variance components are set to zero during likelihood optimization.
-
-ERROR : 84 Optimizer (optim) did not achieve convergence (convergence = 10). 
-ERROR : 158 Optimizer (optim) did not achieve convergence (convergence = 10). 
-ERROR : 160 NA/NaN/Inf in 'y' 
-ERROR : 161 NA/NaN/Inf in 'y' 
-ERROR : 162 NA/NaN/Inf in 'y' 
-ERROR : 163 NA/NaN/Inf in 'y' 
-ERROR : 165 NA/NaN/Inf in 'y' 
-ERROR : 166 NA/NaN/Inf in 'y' 
-ERROR : 168 NA/NaN/Inf in 'y'
-ERROR : 231 NA/NaN/Inf in 'y'
-
-Also a bunch of warnings, are any of these a concern?
-
-> warnings()
-Warning messages:
-1: In metafor::rma.mv(yi = effect_size_CVR, V = sample_variance_CVR,  ... :
-  Rows with NAs omitted from model fitting.
-...
-13: In metafor::rma.mv(yi = effect_size_RR, V = sample_variance_RR,  ... :
-  There are outcomes with non-positive sampling variances.
-14: In metafor::rma.mv(yi = effect_size_RR, V = sample_variance_RR,  ... :
-  'V' appears to be not positive definite.
-16: In metafor::rma.mv(yi = effect_size_CVR, V = sample_variance_CVR,  ... :
-  Single-level factor(s) found in 'random' argument. Corresponding 'sigma2' value(s) fixed to 0.
-...
-50: In metafor::rma.mv(yi = effect_size_RR, V = sample_variance_RR,  ... :
-  'V' appears to be not positive definite
-
-------
-Now that we have a "results" table with each of the meta-analytic means for all effect sizes of interest, we can use this table as part of the Shiny App, which will then be able to back calculate the percentage differences between males and females for mean, variance and coefficient of variance.
-We'll export and use this in the Shiny App.
-**Note that I have not dealt with convergence issues in some of these models, and so, this will need to be done down the road**
-
-(Note Susi 31/7/2019: This dataset contains dublicated values, plus no info on what the "traits" mean. I will change Dan N's to one further belwo, that have been cleaned up already
-FILE TO USE: METACOMBO (around line 500))
+In the above function, we use 'tryCatch' and 'conditionMessage' to prevent the loop from aborting when the first error at row 84 is produced.
+As convergence in the two listed non-converging cases can't be achieved by sensibly tweaking (other optim etc.), and we only learn about non-convergence in the loop, it is not possible to exclude the traits (N=2) beforehand.
+Similarly, there are 8 traits with very low variation, which can not be excluded prior to running the loop.
+
+The produced "Warnings" indicate cases where variance components are set to zero during likelihood optimization.
 
@@
 
-Procedure names, grouping variables etc. are merged back together with the results from the metafor analysis above. This requires loading of another excel sheet, "procedures.csv"
+Procedure names, grouping variables and trait names ("parameter_names") are merged back together with the results from the metafor analysis above.
 
@@
   left_join(by="id",
-             data %>% select(id, parameter_group, procedure = procedure_name, procedure_name, parameter_name) %>% #susi: check parateer group
-              # REVIEW -- this bext line replciates precious code, but removes some procedures, is that right?
-		  # FZ: No. This creates the data from the complete data set ('data'), which was not carried over into 'results_alltraits_grouping'
-		  # FZ: We filter duplicated id's to get only one unique row per id (and there is one id per parameter_name)
+             data %>% select(id, parameter_group, procedure = procedure_name, procedure_name, parameter_name) %>%   # We filter duplicated id's to get only one unique row per id (and there is one id per parameter_name)
               filter(!duplicated(id))
             ) %>%
-  # FZ: Below we add 'procedure' (from the previously loaded 'procedures.csv') as a variable
+  # Below we add 'procedure' (from the previously loaded 'procedures.csv') as a variable
   left_join(by="procedure", 
@@
 
-n <- length(unique(results_alltraits_grouping2$parameter_name)) # 232
-```
-
-Removal of traits that did not achieve convergence, are nonsensical for analysis of variance (such as traits that show variation, such as number of ribs, digits, etc).
-14 traits from the originally 232 that had been included are removed.
-
-**Review**: How did we determine this the ones with problems? 
-**FZ**: In addition to the sentence one line above, to do: add information about cause of exclusion ( 1.
-non-convergence of metafor models, or 2.
-no variation/nonsensical); reference traits to be excluded by trait name (not id number)
-**FZ**: excluded because of non-convergence: 84, 158
-**FZ**: excluded because no variation/nonsensical: 144, 158, 160,... 
-```{r}
-
-#FZ delete# has_problems <- c(84, 144, 158, 160, 161, 162, 163, 165, 166, 167, 168, 221, 222, 231)
-#FZ delete# meta_clean <- results_alltraits_grouping2 %>% filter(!id %in% has_problems)
-#FZ delete# meta_problem <- results_alltraits_grouping2 %>% filter(id %in% has_problems)
-
-#**FZ**: We exclude 14 parameter names for which metafor models didn't converge ("dp t cells", "mzb (cd21/35 high)"), and of parameters that don't harbour enough variation
+#(n <- length(unique(results_alltraits_grouping2$parameter_name))) # 232
+```
+
+### Removal of traits
+
+14 traits from the originally 232 that had been included are removed because they either did not achieve convergence or are nonsensical for analysis of variance (such as traits that show no variation, see list below).
+
+Not converged: "dp t cells", "mzb (cd21/35 high)"
+
+Not enough variation: "number of caudal vertebrae", "number of cervical vertebrae", "number of digits", "number of lumbar vertebrae", "number of pelvic vertebrae", "number of ribs left","number of ribs right", "number of signals", "number of thoracic vertebrae", "total number of acquired events in panel a","total number of acquired events in panel b", "whole arena permanence".
+
+```{r}
+# We exclude 14 parameter names for which metafor models didn't converge ("dp t cells", "mzb (cd21/35 high)"), and of parameters that don't harbour enough variation
 meta_clean <- results_alltraits_grouping2 %>% 
@@
 ```
-```
-
-**Reveiw**: check against old script -- identical, remove once fixed
-
-```{r, eval=FALSE}
-meta_clean.test <- readRDS("../meta_clean.test.rds")  #FZ comment: doesn't work for me. '../' is for the github location?
-all.equal(meta_clean, meta_clean.test)
-all.equal(meta_clean %>% select(-parameter_group), meta_clean.test %>% mutate(id=as.integer(id), GroupingTerm = as.character(GroupingTerm)))
-```
-
-## Meta-analysis, Phase 2: non-independent traits
+
+## 2. Meta-analysis: condensing non-independent traits 
+(Step F in Figure 3 in main article)
+
 ### Dealing with Correlated Parameters, preparation
 
-This dataset contained a number of highly correlated traits, such as different kinds of cell counts (for example, hierarchical parameterization within immunological assays).
-As those data-points are not independent of each other,  we conducted a meta analyses on these correlated parameters to collapse the number of levels.
+This dataset contained a number of highly correlated traits, such as different kinds of cell counts (for example hierarchical parameterization within immunological assays).
+As those data-points are not independent of each other,  we conducted meta analyses on these correlated parameters to collapse the number of levels.
 
@@
 length(unique(meta1$GroupingTerm)) #9
-# Review: next line now 155 not 148 #FZ comment: still 148 for me.
 length(unique(meta1$parameter_group)) # 148 levels.
-To be used as grouping factor for meta-meta analysis / collapsing down based on things that are classified identically in "parameter_group" but have different "parameter_name"
+To be used as grouping factor for meta-meta-analysis / collapsing down based on things that are classified identically in "parameter_group" but have different "parameter_name"
 length(unique(meta1$parameter_name)) #218
@@
 
+### Table 2: Numbers of correlated and uncorrelated traits
 This serves to identify and separate the traits that are correlated from the full dataset that can be processed as is.
@@
 ```{r}
-
 kable(cbind(meta1 %>% count(parameter_group))) %>%
   kable_styling() %>%
-  scroll_box(width = "100%", height = "200px")
+  scroll_box(width = "60%", height = "200px")
 ```
@@
 meta1_sub <- meta1 %>%
-  # add summary of number of parameter names in each parameter group
+  # Add summary of number of parameter names in each parameter group
   group_by(parameter_group) %>%
@@
 #### Meta-analyses on correlated (sub-)traits, using robumeta` 
-The subset of the data is prepared (nested), and in this first step the model of the meta analysis effect sizes are calculated
-
-```{r}
+Here we pepare the subset of the data (using nest()), and in this first step the model of the meta-analysis effect sizes are calculated
+
+```{r}
+
+# Create summary of number of parameter names in each parameter group, and merge back together
 
@@
   summarize(par_group_size = length(unique(parameter_name, na.rm = TRUE)))
-#this gives a summary of number of parameter names in each parameter group, now it neeeds to get merged it back together
 
@@
 
-# nesting
+# Nesting and meta-analyses on correlated traits, using robumeta
+
 n_count <- meta1_sub %>%
@@
 
-Extract and save parameter estimates:
-Function to collect the outcomes of the "mini" meta analysis
+#### Extracting and save parameter estimates
+Here we apply an additional Function to collect the outcomes of the 'mini-meta-analysis' that has ondensed our non-independent traits.
 
@@
 
-Extraction of values created during Meta analysis using robu meta:
+Extraction of values created during meta-analyses using robumeta
 
@@
 
-```{r}
-kable(cbind(robu_all, robu_all)) %>%
-  kable_styling() %>%
-  scroll_box(width = "100%", height = "200px")
-```
-
+#### Combining data 
 Merge the two data sets (the new [robu_all] and the initial [uncorrelated sub-traits with count = 1])
@@
   as_tibble()
-# str(meta_all)
-# str(robu_all)
-# which(is.na(match(names(meta_all),names(robu_all))))  # check
-```
-
-#### Combine data
-
-```{r}
-# Step1 (columns are matched by name (in our case, 'parameter_group'), and any missing columns will be filled with NA) #FZ added explanation of bibd_rows
+# glimpse(meta_all)
+# glimpse(robu_all)
+
+# Step 1:  Columns are matched by name (in our case, 'parameter_group'), and any missing columns will be filled with NA
 combinedmeta <- bind_rows(robu_all, meta_all)
@@
 
-# Steps 2&3 (add information about number of traits in a parameter group, procedure, and grouping term) #FZ added expalnation in brackets
+# Steps 2&3: Add information about number of traits in a parameter group, procedure, and grouping term
 metacombo <- combinedmeta
@@
 
-kable(cbind(metacombo, metacombo)) %>%
-  kable_styling() %>%
-  scroll_box(width = "100%", height = "200px")
 ```
@@
 ```{r}
-metacombo <- metacombo[, c(1, 21:23, 2:13)] # SUSI CHANGE TO NAMES!!!
-names(metacombo)[3] <- "procedure" #change "3" to name
-names(metacombo)[4] <- "GroupingTerm" #change "4" to name
+metacombo <- metacombo[c("parameter_group", "counts","procedure2","GroupingTerm2", "lnCVR","lnCVR_lower","lnCVR_upper","lnCVR_se","lnVR","lnVR_lower","lnVR_upper","lnVR_se","lnRR","lnRR_lower","lnRR_upper","lnRR_se")]
+
+names(metacombo)[names(metacombo)=="procedure2"] <- "procedure" 
+names(metacombo)[names(metacombo)=="GroupingTerm2"] <- "GroupingTerm"
 
 # Quick pre-check before doing plots
-
 metacombo %>%
@@
   dplyr::summarize(MeanCVR = mean(lnCVR), MeanVR = mean(lnVR), MeanRR = mean(lnRR))
-
-```
-
-```{r}
-# SHINY APP # Now that we have a corrected "results" table with each of the meta-analytic means for all effect sizes of interest, we can use this table as part of the Shiny App, which will then be able to back calculate the percentage differences between males and females for mean, variance and coefficient of variance.
-We'll export and use this in the Shiny App.
-**Note that I have not dealt with convergence issues in some of these models, and so, this will need to be done down the road**
-
-## Note Susi 31/7/2019: This has been cleaned up already
-# FILE TO USE: METACOMBO
-### note: to use
-
-# trait_meta_results <- write.csv(metacombo, file = "export/trait_meta_results.csv")
-```
-
-## Meta-analysis, Phase 3: Second-order meta analysis for functional groups
-#### Perform meta-analyses (3 for each of the 9 grouping terms: lnCVR, lnVR, lnRR) 
+```
+
+### Table 3: Full corrected dataset
+
+We use this corrected (for correlated traits) "results" table, which contains each of the meta-analytic means for all effect sizes of interest, for further analyses.
+We further use this table as part of the Shiny App, which is able to provide the percentage differences between males and females for mean, variance and coefficient of variance.
+
 This is the full result dataset
-
-```{r}
-
-kable(cbind(metacombo, metacombo)) %>%
+```{r}
+kable(metacombo) %>%
   kable_styling() %>%
   scroll_box(width = "100%", height = "200px")
-```
-
-#### Prepare data
-Nesting, calculating the number of parameters within each grouping term, and running the meta-analysis
+
+# trait_meta_results <- write.csv(metacombo, file = "export/trait_meta_results.csv")  #Felix 7/2/2020: I think this can be deleted for publication!
+```
+
+## 3. Second-order meta-analysis for functional groups
+(Section H in Figure 3 in main article)
+
+### Performing meta-analyses (3 for each of the 9 grouping terms: lnCVR, lnVR, lnRR)
+
+#### Preparation of data
+
+Nesting, calculating the number of parameters within each grouping term, and running the meta-analyses
 
@@
   group_by(GroupingTerm) %>%
-#FZ comment: changed 'nest' to 'nest_legacy' to keep old syntax/functionality
-  nest_legacy()
+   nest()
 
@@
 metacombo_final_all <- metacombo %>%
-#FZ comment: changed 'nest' to 'nest_legacy' to keep old syntax/functionality
-  nest_legacy()
+  nest(data = everything())
 
@@
 
-Re-structure data for each grouping term; delete unused variables  #FZ comment: referencing of cells below doesn't depend on previous oreding of the data, i.e.
-only changes if output structure from metafor::rma.uni changes
-
-```{r}
-Behaviour <- as.data.frame(overall1 %>% filter(., GroupingTerm == "Behaviour") %>% mutate(
+### Re-structuring the data for each grouping term
+We here delete unused variables, and select the respective effect sizes.
+Please note - the referencing of the cells does NOT depend on previous ordering of the data.
+This would only be affected if the output structure from metafor::rma.uni changes.
+
+```{r}
+Behaviour <- overall1 %>% 
+  filter(., GroupingTerm == "Behaviour") %>% 
+  mutate(
     lnCVR = .[[4]][[1]]$b, lnCVR_lower = .[[4]][[1]]$ci.lb, lnCVR_upper = .[[4]][[1]]$ci.ub, lnCVR_se = .[[4]][[1]]$se,
@@
     lnRR = .[[6]][[1]]$b, lnRR_lower = .[[6]][[1]]$ci.lb, lnRR_upper = .[[6]][[1]]$ci.ub, lnRR_se = .[[6]][[1]]$se
-))[, c(1, 7:18)]
-
-Immunology <- as.data.frame(overall1 %>% filter(., GroupingTerm == "Immunology") %>% mutate(
+  )  %>%
+  select(., GroupingTerm, lnCVR:lnRR_se)
+
+Immunology <- overall1 %>% 
+  filter(., GroupingTerm == "Immunology") %>% 
+  mutate(
     lnCVR = .[[4]][[1]]$b, lnCVR_lower = .[[4]][[1]]$ci.lb, lnCVR_upper = .[[4]][[1]]$ci.ub, lnCVR_se = .[[4]][[1]]$se,
@@
     lnRR = .[[6]][[1]]$b, lnRR_lower = .[[6]][[1]]$ci.lb, lnRR_upper = .[[6]][[1]]$ci.ub, lnRR_se = .[[6]][[1]]$se
-))[, c(1, 7:18)]
-
-Hematology <- as.data.frame(overall1 %>% filter(., GroupingTerm == "Hematology") %>% mutate(
+  )  %>%
+  select(., GroupingTerm, lnCVR:lnRR_se)
+
+Hematology <- overall1 %>% 
+  filter(., GroupingTerm == "Hematology") %>% 
+  mutate(
     lnCVR = .[[4]][[1]]$b, lnCVR_lower = .[[4]][[1]]$ci.lb, lnCVR_upper = .[[4]][[1]]$ci.ub, lnCVR_se = .[[4]][[1]]$se,
@@
     lnRR = .[[6]][[1]]$b, lnRR_lower = .[[6]][[1]]$ci.lb, lnRR_upper = .[[6]][[1]]$ci.ub, lnRR_se = .[[6]][[1]]$se
-))[, c(1, 7:18)]
-
-Hearing <- as.data.frame(overall1 %>% filter(., GroupingTerm == "Hearing") %>% mutate(
+  )  %>%
+  select(., GroupingTerm, lnCVR:lnRR_se)
+
+Hearing <- overall1 %>% 
+  filter(., GroupingTerm == "Hearing") %>% 
+  mutate(
     lnCVR = .[[4]][[1]]$b, lnCVR_lower = .[[4]][[1]]$ci.lb, lnCVR_upper = .[[4]][[1]]$ci.ub, lnCVR_se = .[[4]][[1]]$se,
@@
     lnRR = .[[6]][[1]]$b, lnRR_lower = .[[6]][[1]]$ci.lb, lnRR_upper = .[[6]][[1]]$ci.ub, lnRR_se = .[[6]][[1]]$se
-))[, c(1, 7:18)]
-
-Physiology <- as.data.frame(overall1 %>% filter(., GroupingTerm == "Physiology") %>% mutate(
+  )  %>%
+  select(., GroupingTerm, lnCVR:lnRR_se)
+
+Physiology <- overall1 %>% 
+  filter(., GroupingTerm == "Physiology") %>% 
+  mutate(
     lnCVR = .[[4]][[1]]$b, lnCVR_lower = .[[4]][[1]]$ci.lb, lnCVR_upper = .[[4]][[1]]$ci.ub, lnCVR_se = .[[4]][[1]]$se,
@@
     lnRR = .[[6]][[1]]$b, lnRR_lower = .[[6]][[1]]$ci.lb, lnRR_upper = .[[6]][[1]]$ci.ub, lnRR_se = .[[6]][[1]]$se
-))[, c(1, 7:18)]
-
-Metabolism <- as.data.frame(overall1 %>% filter(., GroupingTerm == "Metabolism") %>% mutate(
+  )  %>%
+  select(., GroupingTerm, lnCVR:lnRR_se)
+
+Metabolism <- overall1 %>% 
+  filter(., GroupingTerm == "Metabolism") %>% 
+  mutate(
     lnCVR = .[[4]][[1]]$b, lnCVR_lower = .[[4]][[1]]$ci.lb, lnCVR_upper = .[[4]][[1]]$ci.ub, lnCVR_se = .[[4]][[1]]$se,
@@
     lnRR = .[[6]][[1]]$b, lnRR_lower = .[[6]][[1]]$ci.lb, lnRR_upper = .[[6]][[1]]$ci.ub, lnRR_se = .[[6]][[1]]$se
-))[, c(1, 7:18)]
-
-Morphology <- as.data.frame(overall1 %>% filter(., GroupingTerm == "Morphology") %>% mutate(
+  )  %>%
+  select(., GroupingTerm, lnCVR:lnRR_se)
+
+Morphology <- overall1 %>% 
+  filter(., GroupingTerm == "Morphology") %>%
+  mutate(
     lnCVR = .[[4]][[1]]$b, lnCVR_lower = .[[4]][[1]]$ci.lb, lnCVR_upper = .[[4]][[1]]$ci.ub, lnCVR_se = .[[4]][[1]]$se,
@@
     lnRR = .[[6]][[1]]$b, lnRR_lower = .[[6]][[1]]$ci.lb, lnRR_upper = .[[6]][[1]]$ci.ub, lnRR_se = .[[6]][[1]]$se
-))[, c(1, 7:18)]
-
-Heart <- as.data.frame(overall1 %>% filter(., GroupingTerm == "Heart") %>% mutate(
+  )  %>%
+  select(., GroupingTerm, lnCVR:lnRR_se)
+
+Heart <- overall1 %>% 
+  filter(., GroupingTerm == "Heart") %>% 
+  mutate(
     lnCVR = .[[4]][[1]]$b, lnCVR_lower = .[[4]][[1]]$ci.lb, lnCVR_upper = .[[4]][[1]]$ci.ub, lnCVR_se = .[[4]][[1]]$se,
@@
     lnRR = .[[6]][[1]]$b, lnRR_lower = .[[6]][[1]]$ci.lb, lnRR_upper = .[[6]][[1]]$ci.ub, lnRR_se = .[[6]][[1]]$se
-))[, c(1, 7:18)]
-
-Eye <- as.data.frame(overall1 %>% filter(., GroupingTerm == "Eye") %>% mutate(
+  )  %>%
+  select(., GroupingTerm, lnCVR:lnRR_se)
+
+Eye <- overall1 %>% 
+  filter(., GroupingTerm == "Eye") %>% 
+  mutate(
     lnCVR = .[[4]][[1]]$b, lnCVR_lower = .[[4]][[1]]$ci.lb, lnCVR_upper = .[[4]][[1]]$ci.ub, lnCVR_se = .[[4]][[1]]$se,
@@
     lnRR = .[[6]][[1]]$b, lnRR_lower = .[[6]][[1]]$ci.lb, lnRR_upper = .[[6]][[1]]$ci.ub, lnRR_se = .[[6]][[1]]$se
-))[, c(1, 7:18)]
-
-All <- as.data.frame(overall_all1 %>% mutate(
-  lnCVR = .[[2]][[1]]$b, lnCVR_lower = .[[2]][[1]]$ci.lb, lnCVR_upper = .[[2]][[1]]$ci.ub, lnCVR_se = .[[2]][[1]]$se, lnVR = .[[3]][[1]]$b, lnVR_lower = .[[3]][[1]]$ci.lb, lnVR_upper = .[[3]][[1]]$ci.ub, lnVR_se = .[[3]][[1]]$se,
+  )  %>%
+    select(., GroupingTerm, lnCVR:lnRR_se)
+
+All <- overall_all1 %>% 
+  mutate(
+    lnCVR = .[[2]][[1]]$b, lnCVR_lower = .[[2]][[1]]$ci.lb, lnCVR_upper = .[[2]][[1]]$ci.ub, lnCVR_se = .[[2]][[1]]$se, 
+    lnVR = .[[3]][[1]]$b, lnVR_lower = .[[3]][[1]]$ci.lb, lnVR_upper = .[[3]][[1]]$ci.ub, lnVR_se = .[[3]][[1]]$se,
     lnRR = .[[4]][[1]]$b, lnRR_lower = .[[4]][[1]]$ci.lb, lnRR_upper = .[[4]][[1]]$ci.ub, lnRR_se = .[[4]][[1]]$se
-))[, c(5:16)]
-
-All$lnCVR <- as.numeric(All$lnCVR)
-All$lnVR <- as.numeric(All$lnVR)
-All$lnRR <- as.numeric(All$lnRR)
+  )  %>%
+    select(., lnCVR:lnRR_se)
+
 All <- All %>% mutate(GroupingTerm = "All")
 
-overall2 <- bind_rows(Behaviour, Morphology, Metabolism, Physiology, Immunology, Hematology, Heart, Hearing, Eye, All) #FZ: warnings are ok
-```
-
-## Visualisation
-
-#### Preparation for plots: Count data, based on First-order meta analysis results
-
-Re-order grouping terms
+overall2 <- bind_rows(Behaviour, Morphology, Metabolism, Physiology, Immunology, Hematology, Heart, Hearing, Eye, All) 
+```
+
+# Visualisation
+## Figure 4 
+#### Preparation for plots: Count data, based on First-order metamanalysis results
+This includes all separate eligible traits.
+Re-ordering of grouping terms
 
@@
 
-# *Prepare data for all traits
+# *Preparing data for all traits
 
@@
 
-meta.plot2.all.b <- gather(meta.plot2.all, trait, value, c(lnCVR, lnRR)) # lnVR,
-
-meta.plot2.all.b$trait <- factor(meta.plot2.all.b$trait, levels = c("lnCVR", "lnRR")) # "lnVR",
-
+meta.plot2.all.b <- gather(meta.plot2.all, trait, value, c(lnCVR, lnRR)) # lnVR has been removed here and in the steps below, as this is only included in the supplemental figure
+
+meta.plot2.all.b$trait <- factor(meta.plot2.all.b$trait, levels = c("lnCVR", "lnRR")) 
 meta.plot2.all.c <- meta.plot2.all.b %>%
@@
 
-# restructure to create stacked bar plots
+# Re-structure to create stacked bar plots
 
@@
 
-# create new sample size variable
+# Create new sample size variable
 
@@
 
-# add summary row ('All') and re-arrange rows into correct order for plotting #FZ added
+# Add summary row ('All') and re-arrange rows into correct order for plotting (warnings about coercing 'id' into character vector are ok)
 
@@
 	.[c(37, 1:9, 39, 10:18, 38, 19:27, 40, 28:36), ] 
+  #line references in previous code line corresponding to: 
+  #'lnCVR(male(All)), lnCVR(male('single grouping terms'), lnRR(male(All)), lnRR(male('single grouping terms')),
+  #lnCVR(female(All)), lnCVR(female('single grouping terms'), lnRR(female(All)), lnRR(female('single grouping terms'))'
 
@@
 
-#### Prepare data for traits with CI not overlapping 0
-create column with 1= different from zero, 0= zero included in CI
-
+###  Overall results of second order meta-analysis (Figure 4, Panel B)
+#### Re-structure data for plotting 
+Data are re-structured, and grouping terms are being re-ordered
+
+```{r}
+overall3 <- gather(overall2, parameter, value, c(lnCVR, lnRR), factor_key = TRUE)
+
+lnCVR.ci <- overall3 %>%
+  filter(parameter == "lnCVR") %>%
+  mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
+lnVR.ci <- overall3 %>%
+  filter(parameter == "lnVR") %>%
+  mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
+lnRR.ci <- overall3 %>%
+  filter(parameter == "lnRR") %>%
+  mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
+
+overall4 <- bind_rows(lnCVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
+
+# Re-order grouping terms
+
+overall4$GroupingTerm <- factor(overall4$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
+overall4$GroupingTerm <- factor(overall4$GroupingTerm, rev(levels(overall4$GroupingTerm)))
+overall4$label <- "All traits"
+
+kable(cbind(overall4, overall4)) %>%
+  kable_styling() %>%
+  scroll_box(width = "100%", height = "200px")
+```
+
+```{r}
+Metameta_Fig3_alltraits <- overall4 %>%
+
+  ggplot(aes(y = GroupingTerm, x = value)) +
+  geom_errorbarh(aes(
+    xmin = ci.low,
+    xmax = ci.high
+  ),
+  height = 0.1, show.legend = FALSE
+  ) +
+  geom_point(aes(shape = parameter),
+    fill = "black",
+    color = "black", size = 2.2,
+    show.legend = FALSE
+  ) +
+  scale_x_continuous(
+    limits = c(-0.24, 0.25),
+    breaks = c(-0.2, -0.1, 0, 0.1, 0.2),
+    name = "Effect size"
+  ) +
+  geom_vline(
+    xintercept = 0,
+    color = "black",
+    linetype = "dashed"
+  ) +
+  facet_grid(
+    cols = vars(parameter), rows = vars(label),
+    labeller = label_wrap_gen(width = 23),
+    scales = "free",
+    space = "free"
+  ) +
+  theme_bw() +
+  theme(
+    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
+    strip.text.x = element_text(size = 12),
+    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
+    text = element_text(size = 14),
+    panel.spacing = unit(0.5, "lines"),
+    panel.border = element_blank(),
+    axis.line = element_line(),
+    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
+    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
+    panel.grid.minor.y = element_blank(),
+    panel.grid.minor.x = element_blank(),
+    legend.title = element_blank(),
+    axis.title.x = element_text(hjust = 0.5, size = 14),
+    axis.title.y = element_blank()
+  )
+
+# Metameta_Fig3_alltraits
+```
+
+### Fig 4 # SZ STILL TO DO
+Join the different parts and  #TO DO!! add M / F symbols in Metameta_Fig3_alltraits 
+```{r}
+#Test
+#male <- readPNG(system.file("img", "male"))
+#test <- Metameta_Fig3_alltraits
+
+#library(png)
+```
+
+### Figure 4
+Panel A shows the numbers of traits across functional groups that are either male-biased (blue-green) or female-biased (orange-red), as calculated in Step D (figure 3).
+Panel B shows effect sizes and 95% CI from separate meta-analysis for each functional group (step H in Figure 3).
+Both panels represent results evaluated across all traits (Phase 3, Figure 3).
+Traits that are male biased is shown in blue, whereas female bias data is represented in orange.
+
+```{r}
+Fig4 <- ggarrange(malebias_Fig2_alltraits, Metameta_Fig3_alltraits,  nrow = 2, align = "v", heights = c(1, 1), labels = c("A", "B"))
+Fig4
+```
+
+## Figure 5
+#### Preparing data for traits with CI not overlapping 0
+To further investigate sex bias in this dataset, and in particular if the extent of sex bias differs between traits, we investigate the magnitude of male- and female bias in significantly different traits on (both for means and variability)
+
+To do this, we select only traits that have CIs that do not overlap with zero.
+The code below creates Figure 5A.
 ```{r}
@@
 
-meta.plot2.sig.b <- meta.plot2.sig[, c("lnCVR", "lnRR", "lnCVRsig", "lnVRsig", "lnRRsig", "GroupingTerm")] # "lnVR",
+meta.plot2.sig.b <- meta.plot2.sig[, c("lnCVR", "lnRR", "lnCVRsig", "lnVRsig", "lnRRsig", "GroupingTerm")]
 
@@
 
-meta.plot2.sig.c$trait <- factor(meta.plot2.sig.c$trait, levels = c("lnCVR", "lnRR")) # "lnVR",
+meta.plot2.sig.c$trait <- factor(meta.plot2.sig.c$trait, levels = c("lnCVR", "lnRR"))
 
@@
 
-# choosing sex biased ln-ratios significantly larger than 0
+# Choosing sex biased ln-ratios significantly larger than 0
 meta.plot2.sig.malebias <- meta.plot2.sig.c %>%
@@
 
-# *Plot Fig2 all significant results (CI not overlapping zero):
-#     no sig. lnCVR for 'Hearing' in either sex; no sig. male-biased lnCVR for 'Immunology' and 'Eye, and no sig. male-biased lnVR for 'Eye'
+# Add summary row ('All') and re-arrange rows into correct order for plotting
+
+meta.plot2.sig.bothsexes.c <- meta.plot2.sig.bothsexes.b %>% group_by(trait, sex) %>% 
+  summarise(GroupingTerm = "All", male_sig = sum(male_sig), female_sig = sum(female_sig), total = male_sig + female_sig, 
+            label = "CI not overlapping zero", samplesize = sum(samplesize)) %>%
+  mutate(percent = ifelse(sex == "femalepercent", female_sig*100/(male_sig+female_sig), male_sig*100/(male_sig+female_sig))) %>%
+  bind_rows(meta.plot2.sig.bothsexes.b, .) %>%
+  mutate(rownumber = row_number()) %>%
+  .[c(37, 1:9, 39, 10:18, 38, 19:27, 40, 28:36), ] 
+  #line references in previous code line corresponding to: 
+  #'lnCVR(male(All)), lnCVR(male('single grouping terms'), lnRR(male(All)), lnRR(male('single grouping terms')),
+  #lnCVR(female(All)), lnCVR(female('single grouping terms'), lnRR(female(All)), lnRR(female('single grouping terms'))'
+
+meta.plot2.sig.bothsexes.c$GroupingTerm <- factor(meta.plot2.sig.bothsexes.c$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
+meta.plot2.sig.bothsexes.c$GroupingTerm <- factor(meta.plot2.sig.bothsexes.c$GroupingTerm, rev(levels(meta.plot2.sig.bothsexes.c$GroupingTerm)))
+
+# Plot Fig2 all significant results (CI not overlapping zero)
+# Several grouping terms are added post-hoc (with no data to display): no significant lnCVR for 'Hearing' in either sex; no sig.
+male-biased lnCVR for 'Immunology' and 'Eye, and no significant female-biased lnRR for 'Eye'.
 
 malebias_Fig2_sigtraits <-
-  ggplot(meta.plot2.sig.bothsexes.b) +
+  ggplot(meta.plot2.sig.bothsexes.c) +
   aes(x = GroupingTerm, y = percent, fill = sex) +
@@
   geom_text(
-    data = subset(meta.plot2.sig.bothsexes.b, samplesize != 0), aes(label = samplesize), position = position_stack(vjust = .5),
+    data = subset(meta.plot2.sig.bothsexes.c, samplesize != 0), aes(label = samplesize), position = position_stack(vjust = .5),
     color = "white", size = 3.5
@@
 
-Prepare data for traits with effect size ratios > 10% larger in males
-
-```{r}
-meta.plot2.over10 <- meta_clean %>%
-  select(lnCVR, lnRR, GroupingTerm) %>%
-  arrange(GroupingTerm) # lnVR,
-
-meta.plot2.over10.b <- gather(meta.plot2.over10, trait, value, c(lnCVR, lnRR)) # lnVR,
-
-meta.plot2.over10.b$trait <- factor(meta.plot2.over10.b$trait, levels = c("lnCVR", "lnRR")) # "lnVR",
-
-meta.plot2.over10.c <- meta.plot2.over10.b %>%
+### Preparation for Plots on significant sex-bias (Second-order meta analysis results)
+
+#### Figure 5 B - traits with CI not overlapping 0 
+Prepare data 
+create column with 1= different from zero, 0= zero included in CI
+#### Male-biased (significant) traits
+
+```{r}
+meta.male.plot3.sig <- metacombo %>%
+  mutate(
+    sigCVR = ifelse(lnCVR_lower > 0, 1, 0),
+    sigVR = ifelse(lnVR_lower > 0, 1, 0),
+    sigRR = ifelse(lnRR_lower > 0, 1, 0)
+  )
+
+# Significant subset for lnCVR
+metacombo_male.plot3.CVR <- meta.male.plot3.sig %>%
+  filter(sigCVR == 1) %>%
+  group_by(GroupingTerm) %>%
+  nest()
+
+metacombo_male.plot3.CVR.all <- meta.male.plot3.sig %>%
+  filter(sigCVR == 1) %>%
+  nest(data = everything())    #Felix added 'data = everything()' on 4/2/2020
+
+# Significant subset for lnVR
+metacombo_male.plot3.VR <- meta.male.plot3.sig %>%
+  filter(sigVR == 1) %>%
+  group_by(GroupingTerm) %>%
+  nest()
+
+metacombo_male.plot3.VR.all <- meta.male.plot3.sig %>%
+  filter(sigVR == 1) %>%
+  nest(data = everything())
+
+# Significant subset for lnRR
+metacombo_male.plot3.RR <- meta.male.plot3.sig %>%
+  filter(sigRR == 1) %>%
+  group_by(GroupingTerm) %>%
+  nest()
+
+metacombo_male.plot3.RR.all <- meta.male.plot3.sig %>%
+  filter(sigRR == 1) %>%
+  nest(data = everything())
+
+# **Final fixed effects meta-analyses within grouping terms, with SE of the estimate
+
+plot3.male.meta.CVR <- metacombo_male.plot3.CVR %>%
+  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+plot3.male.meta.VR <- metacombo_male.plot3.VR %>%
+  mutate(model_lnVR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+plot3.male.meta.RR <- metacombo_male.plot3.RR %>%
+  mutate(model_lnRR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+# Across all grouping terms #
+
+plot3.male.meta.CVR.all <- metacombo_male.plot3.CVR.all %>%
+  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+plot3.male.meta.CVR.all <- plot3.male.meta.CVR.all %>% mutate(GroupingTerm = "All")
+
+plot3.male.meta.VR.all <- metacombo_male.plot3.VR.all %>%
+  mutate(model_lnVR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+plot3.male.meta.VR.all <- plot3.male.meta.VR.all %>% mutate(GroupingTerm = "All")
+
+plot3.male.meta.RR.all <- metacombo_male.plot3.RR.all %>%
+  mutate(model_lnRR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+plot3.male.meta.RR.all <- plot3.male.meta.RR.all %>% mutate(GroupingTerm = "All")
+
+# Combine with separate grouping term results
+
+plot3.male.meta.CVR <- bind_rows(plot3.male.meta.CVR, plot3.male.meta.CVR.all)
+plot3.male.meta.VR <- bind_rows(plot3.male.meta.VR, plot3.male.meta.VR.all)
+plot3.male.meta.RR <- bind_rows(plot3.male.meta.RR, plot3.male.meta.RR.all)
+
+# **Re-structure data for each grouping term; delete un-used variables
+
+plot3.male.meta.CVR.b <- as.data.frame(plot3.male.meta.CVR %>% group_by(GroupingTerm) %>%
+  mutate(
+    lnCVR = map_dbl(model_lnCVR, pluck(2)), lnCVR_lower = map_dbl(model_lnCVR, pluck(6)),
+    lnCVR_upper = map_dbl(model_lnCVR, pluck(7)), lnCVR_se = map_dbl(model_lnCVR, pluck(3))
+  ))[, c(1, 4:7)]
+add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.male.meta.CVR.b))
+
+plot3.male.meta.CVR.b <- bind_rows(plot3.male.meta.CVR.b, add.row.hearing)
+plot3.male.meta.CVR.b <- plot3.male.meta.CVR.b[order(plot3.male.meta.CVR.b$GroupingTerm), ]
+
+plot3.male.meta.VR.b <- as.data.frame(plot3.male.meta.VR %>% group_by(GroupingTerm) %>%
+  mutate(
+    lnVR = map_dbl(model_lnVR, pluck(2)), lnVR_lower = map_dbl(model_lnVR, pluck(6)),
+    lnVR_upper = map_dbl(model_lnVR, pluck(7)), lnVR_se = map_dbl(model_lnVR, pluck(3))
+  ))[, c(1, 4:7)]
+plot3.male.meta.VR.b <- plot3.male.meta.VR.b[order(plot3.male.meta.VR.b$GroupingTerm), ]
+
+plot3.male.meta.RR.b <- as.data.frame(plot3.male.meta.RR %>% group_by(GroupingTerm) %>%
+  mutate(
+    lnRR = map_dbl(model_lnRR, pluck(2)), lnRR_lower = map_dbl(model_lnRR, pluck(6)),
+    lnRR_upper = map_dbl(model_lnRR, pluck(7)), lnRR_se = map_dbl(model_lnRR, pluck(3))
+  ))[, c(1, 4:7)]
+plot3.male.meta.RR.b <- plot3.male.meta.RR.b[order(plot3.male.meta.RR.b$GroupingTerm), ]
+
+overall.male.plot3 <- full_join(plot3.male.meta.CVR.b, plot3.male.meta.VR.b)
+overall.male.plot3 <- full_join(overall.male.plot3, plot3.male.meta.RR.b)
+
+overall.male.plot3$GroupingTerm <- factor(overall.male.plot3$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
+overall.male.plot3$GroupingTerm <- factor(overall.male.plot3$GroupingTerm, rev(levels(overall.male.plot3$GroupingTerm)))
+
+overall.male.plot3$GroupingTerm <- factor(overall.male.plot3$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
+overall.male.plot3$GroupingTerm <- factor(overall.male.plot3$GroupingTerm, rev(levels(overall.male.plot3$GroupingTerm)))
+
+# str(overall.male.plot3)
+```
+
+Restructure MALE data for plotting
+
+```{r}
+overall3.male.sig <- gather(overall.male.plot3, parameter, value, c(lnCVR, lnRR), factor_key = TRUE)
+
+lnCVR.ci <- overall3.male.sig %>%
+  filter(parameter == "lnCVR") %>%
+  mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
+# lnVR.ci <- overall3.male.sig  %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
+lnRR.ci <- overall3.male.sig %>%
+  filter(parameter == "lnRR") %>%
+  mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
+
+overall4.male.sig <- bind_rows(lnCVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
+
+overall4.male.sig$label <- "CI not overlapping zero"
+```
+
+Plot Fig 5B all significant results (CI not overlapping zero) for males. This is the right panel in Figure 5B.
+
+```{r}
+
+Metameta_Fig3_male.sig <- overall4.male.sig %>%
+  ggplot(aes(y = GroupingTerm, x = value)) +
+  geom_errorbarh(aes(
+    xmin = ci.low,
+    xmax = ci.high
+  ),
+  height = 0.1, show.legend = FALSE
+  ) +
+  geom_point(aes(shape = parameter),
+    fill = "mediumaquamarine", color = "mediumaquamarine", size = 2.2,
+    show.legend = FALSE
+  ) +
+  scale_x_continuous(
+    limits = c(0, 0.4),
+    breaks = c(0, 0.3),
+    name = "Effect size"
+  ) +
+  geom_vline(
+    xintercept = 0,
+    color = "black",
+    linetype = "dashed"
+  ) +
+  facet_grid(
+    cols = vars(parameter), rows = vars(label),
+    labeller = label_wrap_gen(width = 23),
+    scales = "free",
+    space = "free"
+  ) +
+  theme_bw() +
+  theme(
+    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
+    strip.text.x = element_text(size = 12),
+    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
+    text = element_text(size = 14),
+    panel.spacing = unit(0.5, "lines"),
+    panel.border = element_blank(),
+    axis.line = element_line(),
+    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
+    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
+    panel.grid.minor.y = element_blank(),
+    panel.grid.minor.x = element_blank(),
+    legend.title = element_blank(),
+    axis.title.x = element_blank(),
+    axis.title.y = element_blank()
+  )
+
+# Metameta_Fig3_male.sig
+```
+
+#### Female part, significant traits
+Female Fig5B sig
+
+Prepare data for traits with CI not overlapping 0
+create column with 1= different from zero, 0= zero included in CI
+
+```{r}
+
+# Female-biased traits
+
+meta.female.plot3.sig <- metacombo %>%
+  mutate(
+    sigCVR = ifelse(lnCVR_upper < 0, 1, 0),
+    sigVR = ifelse(lnVR_upper < 0, 1, 0),
+    sigRR = ifelse(lnRR_upper < 0, 1, 0)
+  )
+
+# Significant subset for lnCVR
+
+metacombo_female.plot3.CVR <- meta.female.plot3.sig %>%
+  filter(sigCVR == 1) %>%
+  group_by(GroupingTerm) %>%
+  nest()
+
+metacombo_female.plot3.CVR.all <- meta.female.plot3.sig %>%
+  filter(sigCVR == 1) %>%
+  nest(data = everything())
+
+# Significant subset for lnVR
+
+metacombo_female.plot3.VR <- meta.female.plot3.sig %>%
+  filter(sigVR == 1) %>%
+  group_by(GroupingTerm) %>%
+  nest()
+
+metacombo_female.plot3.VR.all <- meta.female.plot3.sig %>%
+  filter(sigVR == 1) %>%
+  nest(data = everything())
+
+# Significant subset for lnRR
+
+metacombo_female.plot3.RR <- meta.female.plot3.sig %>%
+  filter(sigRR == 1) %>%
+  group_by(GroupingTerm) %>%
+  nest()
+
+#Felix added 7/2/2020: metacombo_female.plot3.RR[4,2][[1]] [[1]]$lnRR_upper; #only two data points: -0.12377263 -0.01553462; should probably be excluded?!
+
+metacombo_female.plot3.RR.all <- meta.female.plot3.sig %>%
+  filter(sigRR == 1) %>%
+  nest(data = everything())
+
+# **Final fixed effects meta-analyses within grouping terms, with SE of the estimate
+
+plot3.female.meta.CVR <- metacombo_female.plot3.CVR %>%
+  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+plot3.female.meta.VR <- metacombo_female.plot3.VR %>%
+  mutate(model_lnVR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+plot3.female.meta.RR <- metacombo_female.plot3.RR %>%
+  mutate(model_lnRR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+# Across all grouping terms #
+
+plot3.female.meta.CVR.all <- metacombo_female.plot3.CVR.all %>%
+  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+plot3.female.meta.CVR.all <- plot3.female.meta.CVR.all %>% mutate(GroupingTerm = "All")
+
+plot3.female.meta.VR.all <- metacombo_female.plot3.VR.all %>%
+  mutate(model_lnVR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+plot3.female.meta.VR.all <- plot3.female.meta.VR.all %>% mutate(GroupingTerm = "All")
+
+plot3.female.meta.RR.all <- metacombo_female.plot3.RR.all %>%
+  mutate(model_lnRR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+plot3.female.meta.RR.all <- plot3.female.meta.RR.all %>% mutate(GroupingTerm = "All")
+
+# Combine with separate grouping term results
+
+plot3.female.meta.CVR <- bind_rows(plot3.female.meta.CVR, plot3.female.meta.CVR.all)
+plot3.female.meta.VR <- bind_rows(plot3.female.meta.VR, plot3.female.meta.VR.all)
+plot3.female.meta.RR <- bind_rows(plot3.female.meta.RR, plot3.female.meta.RR.all)
+
+# **Re-structure data for each grouping term; delete un-used variables
+
+plot3.female.meta.CVR.b <- as.data.frame(plot3.female.meta.CVR %>% group_by(GroupingTerm) %>%
+  mutate(
+    lnCVR = map_dbl(model_lnCVR, pluck(2)), lnCVR_lower = map_dbl(model_lnCVR, pluck(6)),
+    lnCVR_upper = map_dbl(model_lnCVR, pluck(7)), lnCVR_se = map_dbl(model_lnCVR, pluck(3))
+  ))[, c(1, 4:7)]
+
+add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.female.meta.CVR.b))
+
+plot3.female.meta.CVR.b <- bind_rows(plot3.female.meta.CVR.b, add.row.hearing)
+plot3.female.meta.CVR.b <- plot3.female.meta.CVR.b[order(plot3.female.meta.CVR.b$GroupingTerm), ]
+
+plot3.female.meta.VR.b <- as.data.frame(plot3.female.meta.VR %>% group_by(GroupingTerm) %>%
+  mutate(
+    lnVR = map_dbl(model_lnVR, pluck(2)), lnVR_lower = map_dbl(model_lnVR, pluck(6)),
+    lnVR_upper = map_dbl(model_lnVR, pluck(7)), lnVR_se = map_dbl(model_lnVR, pluck(3))
+  ))[, c(1, 4:7)]
+
+plot3.female.meta.VR.b <- plot3.female.meta.VR.b[order(plot3.female.meta.VR.b$GroupingTerm), ]
+
+plot3.female.meta.RR.b <- as.data.frame(plot3.female.meta.RR %>% group_by(GroupingTerm) %>%
+  mutate(
+    lnRR = map_dbl(model_lnRR, pluck(2)), lnRR_lower = map_dbl(model_lnRR, pluck(6)),
+    lnRR_upper = map_dbl(model_lnRR, pluck(7)), lnRR_se = map_dbl(model_lnRR, pluck(3))
+  ))[, c(1, 4:7)]
+
+plot3.female.meta.RR.b <- plot3.female.meta.RR.b[order(plot3.female.meta.RR.b$GroupingTerm), ]
+
+overall.female.plot3 <- full_join(plot3.female.meta.CVR.b, plot3.female.meta.VR.b)
+overall.female.plot3 <- full_join(overall.female.plot3, plot3.female.meta.RR.b)
+
+overall.female.plot3$GroupingTerm <- factor(overall.female.plot3$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
+overall.female.plot3$GroupingTerm <- factor(overall.female.plot3$GroupingTerm, rev(levels(overall.female.plot3$GroupingTerm)))
+
+```
+
+Re-structure data for plotting
+
+```{r}
+overall3.female.sig <- gather(overall.female.plot3, parameter, value, c(lnCVR, lnRR), factor_key = TRUE)
+
+lnCVR.ci <- overall3.female.sig %>%
+  filter(parameter == "lnCVR") %>%
+  mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
+# lnVR.ci <- overall3.female.sig  %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
+lnRR.ci <- overall3.female.sig %>%
+  filter(parameter == "lnRR") %>%
+  mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
+
+overall4.female.sig <- bind_rows(lnCVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high) # lnVR.ci,
+
+overall4.female.sig$label <- "CI not overlapping zero"
+
+```
+
+Plotting Fig5B all significant results (CI not overlapping zero, female )
+
+```{r}
+
+Metameta_Fig3_female.sig  <- overall4.female.sig %>%
+  ggplot(aes(y = GroupingTerm, x = value)) +
+  geom_errorbarh(aes(
+    xmin = ci.low,
+    xmax = ci.high
+  ),
+  height = 0.1, show.legend = FALSE
+  ) +
+  geom_point(aes(shape = parameter),
+    fill = "salmon1", color = "salmon1", size = 2.2,
+    show.legend = FALSE
+  ) +
+  scale_x_continuous(
+    limits = c(-0.4, 0),
+    breaks = c(-0.3, 0),
+    name = "Effect size"
+  ) +
+  geom_vline(
+    xintercept = 0,
+    color = "black",
+    linetype = "dashed"
+  ) +
+  facet_grid(
+    cols = vars(parameter), # rows = vars(label),
+    # labeller = label_wrap_gen(width = 23),
+    scales = "free",
+    space = "free"
+  ) +
+  theme_bw() +
+  theme(
+    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
+    strip.text.x = element_text(size = 12),
+    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
+    text = element_text(size = 14),
+    panel.spacing = unit(0.5, "lines"),
+    panel.border = element_blank(),
+    axis.line = element_line(),
+    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
+    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
+    panel.grid.minor.y = element_blank(),
+    panel.grid.minor.x = element_blank(),
+    legend.title = element_blank(),
+    axis.title.x = element_blank(),
+    axis.title.y = element_blank()
+  )
+
+# Metameta_Fig3_female.sig #(Figure 5B left panel)
+```
+## JOIN!!! CODE MISSING??
+malebias_Fig2_sigtraits
+Metameta_Fig3_female.sig #(Figure 5B left panel)
+Metameta_Fig3_male.sig
+```{r}
+Fig5B <- ggarrange(Metameta_Fig3_female.sig, Metameta_Fig3_male.sig,
+  ncol = 2, nrow = 1, widths = c(1, 1.20), heights = c(1, 1)
+)
+
+Fig5 <- ggarrange(malebias_Fig2_sigtraits, Fig5B,
+  ncol = 1, nrow = 2, widths = c(1, 1.10), heights = c(1.10, 1),  labels = c("A", "B")
+)
+Fig5
+```
+
+# Supplemental Plots
+## Figure S1 
+### Including lnVR
+### Count data, including lnVR (Fig S1 panel A)
+
+```{r}
+# *Prepare data for all traits
+
+meta.plot2.all <- meta_clean %>%
+  select(lnCVR, lnVR, lnRR, GroupingTerm) %>%
+  arrange(GroupingTerm)
+
+meta.plot2.all.bS1 <- gather(meta.plot2.all, trait, value, c(lnCVR, lnVR, lnRR))
+
+meta.plot2.all.bS1$trait <- factor(meta.plot2.all.bS1$trait, levels = c("lnCVR", "lnVR", "lnRR"))
+
+meta.plot2.all.cS1 <- meta.plot2.all.bS1 %>%
   group_by_at(vars(trait, GroupingTerm)) %>%
   summarise(
-    malebias = sum(value > log(11 / 10)), femalebias = sum(value < log(9 / 10)), total = malebias + femalebias,
+    malebias = sum(value > 0), femalebias = sum(value <= 0), total = malebias + femalebias,
     malepercent = malebias * 100 / total, femalepercent = femalebias * 100 / total
@@
 
-meta.plot2.over10.c$label <- "Sex difference in m/f ratios > 10%"
-
-# restructure to create stacked bar plots
-
-meta.plot2.over10.c <- as.data.frame(meta.plot2.over10.c)
-meta.plot2.over10.d <- gather(meta.plot2.over10.c, key = sex, value = percent, malepercent:femalepercent, factor_key = TRUE)
-
-# create new sample size variable
-
-meta.plot2.over10.d$samplesize <- with(meta.plot2.over10.d, ifelse(sex == "malepercent", malebias, femalebias))
-
-# *Plot Fig2 Sex difference in m/f ratio > 10%
-malebias_Fig2_over10 <-
-  ggplot(meta.plot2.over10.d) +
+meta.plot2.all.cS1$label <- "All traits"
+
+# Re-structure to create stacked bar plots
+
+meta.plot2.all.dS1 <- as.data.frame(meta.plot2.all.cS1)
+meta.plot2.all.eS1 <- gather(meta.plot2.all.dS1, key = sex, value = percent, malepercent:femalepercent, factor_key = TRUE)
+
+# Create new sample size variable
+
+meta.plot2.all.eS1$samplesize <- with(meta.plot2.all.eS1, ifelse(sex == "malepercent", malebias, femalebias))
+
+# Add summary row ('All') and re-arrange rows into correct order for plotting (warnings about coercing 'id' into character vector are ok)
+
+meta.plot2.all.fS1 <- meta.plot2.all.eS1 %>% group_by(trait, sex) %>% 
+  summarise(GroupingTerm = "All", malebias = sum(malebias), femalebias = sum(femalebias), total = malebias + femalebias, 
+            label = "All traits", samplesize = sum(samplesize)) %>%
+  mutate(percent = ifelse(sex == "femalepercent", femalebias*100/(malebias+femalebias), malebias*100/(malebias+femalebias))) %>%
+  bind_rows(meta.plot2.all.eS1, .) %>%
+  mutate(rownumber = row_number()) %>%
+  .[c(55, 1:9, 57, 10:18, 59, 19:27, 56, 28:36, 58, 37:45, 60, 46:54), ]
+
+meta.plot2.all.fS1$GroupingTerm <- factor(meta.plot2.all.fS1$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
+meta.plot2.all.fS1$GroupingTerm <- factor(meta.plot2.all.fS1$GroupingTerm, rev(levels(meta.plot2.all.fS1$GroupingTerm)))
+
+malebias_FigS1_alltraits <-
+  ggplot(meta.plot2.all.fS1) +
   aes(x = GroupingTerm, y = percent, fill = sex) +
@@
   geom_text(
-    data = subset(meta.plot2.over10.d, samplesize != 0), aes(label = samplesize), position = position_stack(vjust = .5),
+    data = subset(meta.plot2.all.fS1, samplesize != 0), aes(label = samplesize), position = position_stack(vjust = .5),
     color = "white", size = 3.5
@@
     strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
-    strip.text.x = element_blank(),
+    strip.text.x = element_text(size = 12),
     strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
@@
 
-# malebias_Fig2_over10  (Panel C in Fig 5 in ms)
-```
-
-###  Overall results of second order meta analysis (Figure 4: overall, Figure 5: sex-bias)
-#### Restructure data for plotting 
-Data are restructured, and grouping terms are being re-ordered
-
-```{r}
-overall3 <- gather(overall2, parameter, value, c(lnCVR, lnRR), factor_key = TRUE) # lnVR,
-
-lnCVR.ci <- overall3 %>%
+# malebias_FigS1_alltraits     #(panel A in Figure S1)
+```
+
+###  Overall results of second order meta analysis, INCLUDING VR
+#### Re-structure data for plotting 
+Restructure MALE data for plotting
+
+```{r}
+overall3.male.sigS <- gather(overall.male.plot3, parameter, value, c(lnCVR, lnVR, lnRR), factor_key = TRUE)
+
+lnCVR.ci <- overall3.male.sigS %>%
   filter(parameter == "lnCVR") %>%
   mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
-lnVR.ci <- overall3 %>%
+lnVR.ci <- overall3.male.sigS %>%
   filter(parameter == "lnVR") %>%
   mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
-lnRR.ci <- overall3 %>%
+lnRR.ci <- overall3.male.sigS %>%
   filter(parameter == "lnRR") %>%
@@
 
-overall4 <- bind_rows(lnCVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high) # lnVR.ci,
-
-# re-order Grouping Terms
-
-overall4$GroupingTerm <- factor(overall4$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
-overall4$GroupingTerm <- factor(overall4$GroupingTerm, rev(levels(overall4$GroupingTerm)))
-overall4$label <- "All traits"
-
-kable(cbind(overall4, overall4)) %>%
-  kable_styling() %>%
-  scroll_box(width = "100%", height = "200px")
-```
-
-#### Preparation for Plots FIGURE 4B & 5B, 5D (Second-order meta analysis results)
-Preparation: Sub-Plot  for Figure 3: all traits (4B)
-
-```{r}
-
-Metameta_Fig3_alltraits <- overall4 %>%
+overall4.male.sigS <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
+
+overall4.male.sigS$label <- "CI not overlapping zero"
+
+# Data are re-structured, and grouping terms are being re-ordered
+
+overall3S <- gather(overall2, parameter, value, c(lnCVR, lnVR, lnRR), factor_key = TRUE)
+
+lnCVR.ci <- overall3S %>%
+  filter(parameter == "lnCVR") %>%
+  mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
+lnVR.ci <- overall3S %>%
+  filter(parameter == "lnVR") %>%
+  mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
+lnRR.ci <- overall3S %>%
+  filter(parameter == "lnRR") %>%
+  mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
+
+overall4S <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
+
+# Re-order grouping terms
+
+overall4S$GroupingTerm <- factor(overall4S$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
+overall4S$GroupingTerm <- factor(overall4S$GroupingTerm, rev(levels(overall4S$GroupingTerm)))
+overall4S$label <- "All traits"
+```
+
+#### Preparation for plot, including lnVR
+Preparation: Sub-Plot  for Figure S1: all traits (S1 B)
+
+```{r}
+Metameta_FigS1_alltraits <- overall4S %>%
 
@@
 
-# Metameta_Fig3_alltraits
-```
-
-#### Figure 5 - traits with CI not overlapping 0 
-Prepare data 
-create column with 1= different from zero, 0= zero included in CI
-Male-biased (significant) traits
-
-```{r}
-meta.male.plot3.sig <- metacombo %>%
-  mutate(
-    sigCVR = ifelse(lnCVR_lower > 0, 1, 0),
-    sigVR = ifelse(lnVR_lower > 0, 1, 0),
-    sigRR = ifelse(lnRR_lower > 0, 1, 0)
-  )
-
-# Significant subset for lnCVR
-metacombo_male.plot3.CVR <- meta.male.plot3.sig %>%
-  filter(sigCVR == 1) %>%
-  group_by(GroupingTerm) %>%
-  nest()
-
-metacombo_male.plot3.CVR.all <- meta.male.plot3.sig %>%
-  filter(sigCVR == 1) %>%
-  nest()
-
-# Significant subset for lnVR
-metacombo_male.plot3.VR <- meta.male.plot3.sig %>%
-  filter(sigVR == 1) %>%
-  group_by(GroupingTerm) %>%
-  nest()
-
-metacombo_male.plot3.VR.all <- meta.male.plot3.sig %>%
-  filter(sigVR == 1) %>%
-  nest()
-
-# Significant subset for lnRR
-metacombo_male.plot3.RR <- meta.male.plot3.sig %>%
-  filter(sigRR == 1) %>%
-  group_by(GroupingTerm) %>%
-  nest()
-
-metacombo_male.plot3.RR.all <- meta.male.plot3.sig %>%
-  filter(sigRR == 1) %>%
-  nest()
-
-# **Final fixed effects meta-analyses within grouping terms, with SE of the estimate
-
-plot3.male.meta.CVR <- metacombo_male.plot3.CVR %>%
-  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(
-    yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower) / (2 * 1.96),
-    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-  )))
-
-plot3.male.meta.VR <- metacombo_male.plot3.VR %>%
-  mutate(model_lnVR = map(data, ~ metafor::rma.uni(
-    yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
-    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-  )))
-
-plot3.male.meta.RR <- metacombo_male.plot3.RR %>%
-  mutate(model_lnRR = map(data, ~ metafor::rma.uni(
-    yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
-    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-  )))
-
-# Across all grouping terms #
-
-plot3.male.meta.CVR.all <- metacombo_male.plot3.CVR.all %>%
-  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(
-    yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower) / (2 * 1.96),
-    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-  )))
-
-plot3.male.meta.CVR.all <- plot3.male.meta.CVR.all %>% mutate(GroupingTerm = "All")
-
-plot3.male.meta.VR.all <- metacombo_male.plot3.VR.all %>%
-  mutate(model_lnVR = map(data, ~ metafor::rma.uni(
-    yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
-    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-  )))
-
-plot3.male.meta.VR.all <- plot3.male.meta.VR.all %>% mutate(GroupingTerm = "All")
-
-plot3.male.meta.RR.all <- metacombo_male.plot3.RR.all %>%
-  mutate(model_lnRR = map(data, ~ metafor::rma.uni(
-    yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
-    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-  )))
-
-plot3.male.meta.RR.all <- plot3.male.meta.RR.all %>% mutate(GroupingTerm = "All")
-
-# Combine with separate grouping term results
-
-plot3.male.meta.CVR <- bind_rows(plot3.male.meta.CVR, plot3.male.meta.CVR.all)
-plot3.male.meta.VR <- bind_rows(plot3.male.meta.VR, plot3.male.meta.VR.all)
-plot3.male.meta.RR <- bind_rows(plot3.male.meta.RR, plot3.male.meta.RR.all)
-
-# **Re-structure data for each grouping term; delete un-used variables
-
-plot3.male.meta.CVR.b <- as.data.frame(plot3.male.meta.CVR %>% group_by(GroupingTerm) %>%
-  mutate(
-    lnCVR = map_dbl(model_lnCVR, pluck(2)), lnCVR_lower = map_dbl(model_lnCVR, pluck(6)),
-    lnCVR_upper = map_dbl(model_lnCVR, pluck(7)), lnCVR_se = map_dbl(model_lnCVR, pluck(3))
-  ))[, c(1, 4:7)]
-add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.male.meta.CVR.b))
-
-plot3.male.meta.CVR.b <- bind_rows(plot3.male.meta.CVR.b, add.row.hearing)
-plot3.male.meta.CVR.b <- plot3.male.meta.CVR.b[order(plot3.male.meta.CVR.b$GroupingTerm), ]
-
-plot3.male.meta.VR.b <- as.data.frame(plot3.male.meta.VR %>% group_by(GroupingTerm) %>%
-  mutate(
-    lnVR = map_dbl(model_lnVR, pluck(2)), lnVR_lower = map_dbl(model_lnVR, pluck(6)),
-    lnVR_upper = map_dbl(model_lnVR, pluck(7)), lnVR_se = map_dbl(model_lnVR, pluck(3))
-  ))[, c(1, 4:7)]
-plot3.male.meta.VR.b <- plot3.male.meta.VR.b[order(plot3.male.meta.VR.b$GroupingTerm), ]
-
-plot3.male.meta.RR.b <- as.data.frame(plot3.male.meta.RR %>% group_by(GroupingTerm) %>%
-  mutate(
-    lnRR = map_dbl(model_lnRR, pluck(2)), lnRR_lower = map_dbl(model_lnRR, pluck(6)),
-    lnRR_upper = map_dbl(model_lnRR, pluck(7)), lnRR_se = map_dbl(model_lnRR, pluck(3))
-  ))[, c(1, 4:7)]
-plot3.male.meta.RR.b <- plot3.male.meta.RR.b[order(plot3.male.meta.RR.b$GroupingTerm), ]
-
-overall.male.plot3 <- full_join(plot3.male.meta.CVR.b, plot3.male.meta.VR.b)
-overall.male.plot3 <- full_join(overall.male.plot3, plot3.male.meta.RR.b)
-
-overall.male.plot3$GroupingTerm <- factor(overall.male.plot3$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
-overall.male.plot3$GroupingTerm <- factor(overall.male.plot3$GroupingTerm, rev(levels(overall.male.plot3$GroupingTerm)))
-
-# add missing GroupingTerms for plot
-overall.male.plot3 <- add_row(overall.male.plot3, GroupingTerm = "Behaviour")
-overall.male.plot3 <- add_row(overall.male.plot3, GroupingTerm = "Immunology")
-overall.male.plot3 <- add_row(overall.male.plot3, GroupingTerm = "Eye")
-
-overall.male.plot3$GroupingTerm <- factor(overall.male.plot3$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
-overall.male.plot3$GroupingTerm <- factor(overall.male.plot3$GroupingTerm, rev(levels(overall.male.plot3$GroupingTerm)))
-
-# str(overall.male.plot3)
-```
-
-Restructure MALE data for plotting
-
-```{r}
-overall3.male.sig <- gather(overall.male.plot3, parameter, value, c(lnCVR, lnRR), factor_key = TRUE) # lnVR,
-
-lnCVR.ci <- overall3.male.sig %>%
-  filter(parameter == "lnCVR") %>%
-  mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
-# lnVR.ci <- overall3.male.sig  %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
-lnRR.ci <- overall3.male.sig %>%
-  filter(parameter == "lnRR") %>%
-  mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
-
-overall4.male.sig <- bind_rows(lnCVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high) # lnVR.ci,
-
-overall4.male.sig$label <- "CI not overlapping zero"
-```
-
-Plot Fig5b all significant results (CI not overlapping zero) for males
-
-```{r}
-
-Metameta_Fig3_male.sig <- overall4.male.sig %>%
-  ggplot(aes(y = GroupingTerm, x = value)) +
-  geom_errorbarh(aes(
-    xmin = ci.low,
-    xmax = ci.high
-  ),
-  height = 0.1, show.legend = FALSE
-  ) +
-  geom_point(aes(shape = parameter),
-    fill = "mediumaquamarine", color = "mediumaquamarine", size = 2.2,
-    show.legend = FALSE
-  ) +
-  scale_x_continuous(
-    limits = c(0, 0.4),
-    breaks = c(0, 0.3),
-    name = "Effect size"
-  ) +
-  geom_vline(
-    xintercept = 0,
-    color = "black",
-    linetype = "dashed"
-  ) +
-  facet_grid(
-    cols = vars(parameter), rows = vars(label),
-    labeller = label_wrap_gen(width = 23),
-    scales = "free",
-    space = "free"
-  ) +
-  theme_bw() +
-  theme(
-    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
-    strip.text.x = element_text(size = 12),
-    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
-    text = element_text(size = 14),
-    panel.spacing = unit(0.5, "lines"),
-    panel.border = element_blank(),
-    axis.line = element_line(),
-    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
-    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
-    panel.grid.minor.y = element_blank(),
-    panel.grid.minor.x = element_blank(),
-    legend.title = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank()
-  )
-
-# Metameta_Fig3_male.sig
-```
-
-#### Female Figure, significant traits
-Female Fig5B sig
-
-Prepare data for traits with CI not overlapping 0
-create column with 1= different from zero, 0= zero included in CI
-
-```{r}
-
-# female-biased traits
-
-meta.female.plot3.sig <- metacombo %>%
-  mutate(
-    sigCVR = ifelse(lnCVR_upper < 0, 1, 0),
-    sigVR = ifelse(lnVR_upper < 0, 1, 0),
-    sigRR = ifelse(lnRR_upper < 0, 1, 0)
-  )
-
-# Significant subset for lnCVR
-
-metacombo_female.plot3.CVR <- meta.female.plot3.sig %>%
-  filter(sigCVR == 1) %>%
-  group_by(GroupingTerm) %>%
-  nest()
-
-metacombo_female.plot3.CVR.all <- meta.female.plot3.sig %>%
-  filter(sigCVR == 1) %>%
-  nest()
-
-# Significant subset for lnVR
-
-metacombo_female.plot3.VR <- meta.female.plot3.sig %>%
-  filter(sigVR == 1) %>%
-  group_by(GroupingTerm) %>%
-  nest()
-
-metacombo_female.plot3.VR.all <- meta.female.plot3.sig %>%
-  filter(sigVR == 1) %>%
-  nest()
-
-# Significant subset for lnRR
-
-metacombo_female.plot3.RR <- meta.female.plot3.sig %>%
-  filter(sigRR == 1) %>%
-  group_by(GroupingTerm) %>%
-  nest()
-
-metacombo_female.plot3.RR.all <- meta.female.plot3.sig %>%
-  filter(sigRR == 1) %>%
-  nest()
-
-# **Final fixed effects meta-analyses within grouping terms, with SE of the estimate
-
-plot3.female.meta.CVR <- metacombo_female.plot3.CVR %>%
-  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(
-    yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower) / (2 * 1.96),
-    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-  )))
-
-plot3.female.meta.VR <- metacombo_female.plot3.VR %>%
-  mutate(model_lnVR = map(data, ~ metafor::rma.uni(
-    yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
-    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-  )))
-
-plot3.female.meta.RR <- metacombo_female.plot3.RR %>%
-  mutate(model_lnRR = map(data, ~ metafor::rma.uni(
-    yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
-    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-  )))
-
-# Across all grouping terms #
-
-plot3.female.meta.CVR.all <- metacombo_female.plot3.CVR.all %>%
-  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(
-    yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower) / (2 * 1.96),
-    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-  )))
-
-plot3.female.meta.CVR.all <- plot3.female.meta.CVR.all %>% mutate(GroupingTerm = "All")
-
-plot3.female.meta.VR.all <- metacombo_female.plot3.VR.all %>%
-  mutate(model_lnVR = map(data, ~ metafor::rma.uni(
-    yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
-    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-  )))
-
-plot3.female.meta.VR.all <- plot3.female.meta.VR.all %>% mutate(GroupingTerm = "All")
-
-plot3.female.meta.RR.all <- metacombo_female.plot3.RR.all %>%
-  mutate(model_lnRR = map(data, ~ metafor::rma.uni(
-    yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
-    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-  )))
-
-plot3.female.meta.RR.all <- plot3.female.meta.RR.all %>% mutate(GroupingTerm = "All")
-
-# Combine with separate grouping term results
-
-plot3.female.meta.CVR <- bind_rows(plot3.female.meta.CVR, plot3.female.meta.CVR.all)
-plot3.female.meta.VR <- bind_rows(plot3.female.meta.VR, plot3.female.meta.VR.all)
-plot3.female.meta.RR <- bind_rows(plot3.female.meta.RR, plot3.female.meta.RR.all)
-
-# **Re-structure data for each grouping term; delete un-used variables
-
-plot3.female.meta.CVR.b <- as.data.frame(plot3.female.meta.CVR %>% group_by(GroupingTerm) %>%
-  mutate(
-    lnCVR = map_dbl(model_lnCVR, pluck(2)), lnCVR_lower = map_dbl(model_lnCVR, pluck(6)),
-    lnCVR_upper = map_dbl(model_lnCVR, pluck(7)), lnCVR_se = map_dbl(model_lnCVR, pluck(3))
-  ))[, c(1, 4:7)]
-
-add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.female.meta.CVR.b))
-
-plot3.female.meta.CVR.b <- bind_rows(plot3.female.meta.CVR.b, add.row.hearing)
-plot3.female.meta.CVR.b <- plot3.female.meta.CVR.b[order(plot3.female.meta.CVR.b$GroupingTerm), ]
-
-plot3.female.meta.VR.b <- as.data.frame(plot3.female.meta.VR %>% group_by(GroupingTerm) %>%
-  mutate(
-    lnVR = map_dbl(model_lnVR, pluck(2)), lnVR_lower = map_dbl(model_lnVR, pluck(6)),
-    lnVR_upper = map_dbl(model_lnVR, pluck(7)), lnVR_se = map_dbl(model_lnVR, pluck(3))
-  ))[, c(1, 4:7)]
-
-plot3.female.meta.VR.b <- plot3.female.meta.VR.b[order(plot3.female.meta.VR.b$GroupingTerm), ]
-
-plot3.female.meta.RR.b <- as.data.frame(plot3.female.meta.RR %>% group_by(GroupingTerm) %>%
-  mutate(
-    lnRR = map_dbl(model_lnRR, pluck(2)), lnRR_lower = map_dbl(model_lnRR, pluck(6)),
-    lnRR_upper = map_dbl(model_lnRR, pluck(7)), lnRR_se = map_dbl(model_lnRR, pluck(3))
-  ))[, c(1, 4:7)]
-
-plot3.female.meta.RR.b <- plot3.female.meta.RR.b[order(plot3.female.meta.RR.b$GroupingTerm), ]
-
-overall.female.plot3 <- full_join(plot3.female.meta.CVR.b, plot3.female.meta.VR.b)
-overall.female.plot3 <- full_join(overall.female.plot3, plot3.female.meta.RR.b)
-
-overall.female.plot3$GroupingTerm <- factor(overall.female.plot3$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
-overall.female.plot3$GroupingTerm <- factor(overall.female.plot3$GroupingTerm, rev(levels(overall.female.plot3$GroupingTerm)))
-```
-
-Restructure data for plotting
-
-```{r}
-overall3.female.sig <- gather(overall.female.plot3, parameter, value, c(lnCVR, lnRR), factor_key = TRUE) # lnVR,
-
-lnCVR.ci <- overall3.female.sig %>%
-  filter(parameter == "lnCVR") %>%
-  mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
-# lnVR.ci <- overall3.female.sig  %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
-lnRR.ci <- overall3.female.sig %>%
-  filter(parameter == "lnRR") %>%
-  mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
-
-overall4.female.sig <- bind_rows(lnCVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high) # lnVR.ci,
-
-overall4.female.sig$label <- "CI not overlapping zero"
-```
-
-Plot Fig5B all significant results (CI not overlapping zero, female )
-
-```{r}
-
-Metameta_Fig3_female.sig <- overall4.female.sig %>%
-  ggplot(aes(y = GroupingTerm, x = value)) +
-  geom_errorbarh(aes(
-    xmin = ci.low,
-    xmax = ci.high
-  ),
-  height = 0.1, show.legend = FALSE
-  ) +
-  geom_point(aes(shape = parameter),
-    fill = "salmon1", color = "salmon1", size = 2.2,
-    show.legend = FALSE
-  ) +
-  scale_x_continuous(
-    limits = c(-0.4, 0),
-    breaks = c(-0.3, 0),
-    name = "Effect size"
-  ) +
-  geom_vline(
-    xintercept = 0,
-    color = "black",
-    linetype = "dashed"
-  ) +
-  facet_grid(
-    cols = vars(parameter), # rows = vars(label),
-    # labeller = label_wrap_gen(width = 23),
-    scales = "free",
-    space = "free"
-  ) +
-  theme_bw() +
-  theme(
-    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
-    strip.text.x = element_text(size = 12),
-    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
-    text = element_text(size = 14),
-    panel.spacing = unit(0.5, "lines"),
-    panel.border = element_blank(),
-    axis.line = element_line(),
-    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
-    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
-    panel.grid.minor.y = element_blank(),
-    panel.grid.minor.x = element_blank(),
-    legend.title = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank()
-  )
-
-# Metameta_Fig3_female.sig (Figure 5B left panel)
-```
-
-#### Fig5 D >10%
-
-Prepare data for traits with m/f difference > 10%
-
-create column with 1= larger, 0= diff not larger than 10%
-
-#### Male Fig 5D > 10% (male biased traits)
-
-```{r}
-meta.male.plot3.perc <- metacombo %>%
-  mutate(
-    percCVR = ifelse(lnCVR > log(11 / 10), 1, 0),
-    percVR = ifelse(lnVR > log(11 / 10), 1, 0),
-    percRR = ifelse(lnRR > log(11 / 10), 1, 0)
-  )
-
-# Significant subset for lnCVR
-metacombo_male.plot3.CVR.perc <- meta.male.plot3.perc %>%
-  filter(percCVR == 1) %>%
-  group_by(GroupingTerm) %>%
-  nest()
-
-metacombo_male.plot3.CVR.perc.all <- meta.male.plot3.perc %>%
-  filter(percCVR == 1) %>%
-  nest()
-
-# Significant subset for lnVR
-metacombo_male.plot3.VR.perc <- meta.male.plot3.perc %>%
-  filter(percVR == 1) %>%
-  group_by(GroupingTerm) %>%
-  nest()
-
-metacombo_male.plot3.VR.perc.all <- meta.male.plot3.perc %>%
-  filter(percVR == 1) %>%
-  nest()
-
-# Significant subset for lnRR
-metacombo_male.plot3.RR.perc <- meta.male.plot3.perc %>%
-  filter(percRR == 1) %>%
-  group_by(GroupingTerm) %>%
-  nest()
-
-metacombo_male.plot3.RR.perc.all <- meta.male.plot3.perc %>%
-  filter(percRR == 1) %>%
-  nest()
-
-# **Final fixed effects meta-analyses within grouping terms and across grouping terms, with SE of the estimate
-
-plot3.male.meta.CVR.perc <- metacombo_male.plot3.CVR.perc %>%
-  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(
-    yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower) / (2 * 1.96),
-    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-  )))
-
-plot3.male.meta.VR.perc <- metacombo_male.plot3.VR.perc %>%
-  mutate(model_lnVR = map(data, ~ metafor::rma.uni(
-    yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
-    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-  )))
-
-plot3.male.meta.RR.perc <- metacombo_male.plot3.RR.perc %>%
-  mutate(model_lnRR = map(data, ~ metafor::rma.uni(
-    yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
-    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-  )))
-
-# Across all grouping terms #
-
-plot3.male.meta.CVR.perc.all <- metacombo_male.plot3.CVR.perc.all %>%
-  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(
-    yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower) / (2 * 1.96),
-    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-  )))
-
-plot3.male.meta.CVR.perc.all <- plot3.male.meta.CVR.perc.all %>% mutate(GroupingTerm = "All")
-
-plot3.male.meta.VR.perc.all <- metacombo_male.plot3.VR.perc.all %>%
-  mutate(model_lnVR = map(data, ~ metafor::rma.uni(
-    yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
-    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-  )))
-
-plot3.male.meta.VR.perc.all <- plot3.male.meta.VR.perc.all %>% mutate(GroupingTerm = "All")
-
-plot3.male.meta.RR.perc.all <- metacombo_male.plot3.RR.perc.all %>%
-  mutate(model_lnRR = map(data, ~ metafor::rma.uni(
-    yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
-    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-  )))
-
-plot3.male.meta.RR.perc.all <- plot3.male.meta.RR.perc.all %>% mutate(GroupingTerm = "All")
-
-# Combine with separate grouping term results
-
-plot3.male.meta.CVR.perc <- bind_rows(plot3.male.meta.CVR.perc, plot3.male.meta.CVR.perc.all)
-plot3.male.meta.VR.perc <- bind_rows(plot3.male.meta.VR.perc, plot3.male.meta.VR.perc.all)
-plot3.male.meta.RR.perc <- bind_rows(plot3.male.meta.RR.perc, plot3.male.meta.RR.perc.all)
-
-# **Re-structure data for each grouping term; delete un-used variables: "Hearing missing for all 3 parameters"
-
-plot3.male.meta.CVR.perc.b <- as.data.frame(plot3.male.meta.CVR.perc %>% group_by(GroupingTerm) %>%
-  mutate(
-    lnCVR = map_dbl(model_lnCVR, pluck(2)), lnCVR_lower = map_dbl(model_lnCVR, pluck(6)),
-    lnCVR_upper = map_dbl(model_lnCVR, pluck(7)), lnCVR_se = map_dbl(model_lnCVR, pluck(3))
-  ))[, c(1, 4:7)]
-add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.male.meta.CVR.perc.b))
-plot3.male.meta.CVR.perc.b <- rbind(plot3.male.meta.CVR.perc.b, add.row.hearing)
-plot3.male.meta.CVR.perc.b <- plot3.male.meta.CVR.perc.b[order(plot3.male.meta.CVR.perc.b$GroupingTerm), ]
-
-plot3.male.meta.VR.perc.b <- as.data.frame(plot3.male.meta.VR.perc %>% group_by(GroupingTerm) %>%
-  mutate(
-    lnVR = map_dbl(model_lnVR, pluck(2)), lnVR_lower = map_dbl(model_lnVR, pluck(6)),
-    lnVR_upper = map_dbl(model_lnVR, pluck(7)), lnVR_se = map_dbl(model_lnVR, pluck(3))
-  ))[, c(1, 4:7)]
-add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.male.meta.VR.perc.b))
-plot3.male.meta.VR.perc.b <- rbind(plot3.male.meta.VR.perc.b, add.row.hearing)
-plot3.male.meta.VR.perc.b <- plot3.male.meta.VR.perc.b[order(plot3.male.meta.VR.perc.b$GroupingTerm), ]
-
-plot3.male.meta.RR.perc.b <- as.data.frame(plot3.male.meta.RR.perc %>% group_by(GroupingTerm) %>%
-  mutate(
-    lnRR = map_dbl(model_lnRR, pluck(2)), lnRR_lower = map_dbl(model_lnRR, pluck(6)),
-    lnRR_upper = map_dbl(model_lnRR, pluck(7)), lnRR_se = map_dbl(model_lnRR, pluck(3))
-  ))[, c(1, 4:7)]
-add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>%
-  setNames(names(plot3.male.meta.RR.perc.b))
-plot3.male.meta.RR.perc.b <- rbind(plot3.male.meta.RR.perc.b, add.row.hearing)
-
-add.row.eye <- as.data.frame(t(c("Eye", NA, NA, NA, NA))) %>%
-  setNames(names(plot3.male.meta.RR.perc.b))
-plot3.male.meta.RR.perc.b <- rbind(plot3.male.meta.RR.perc.b, add.row.eye)
-
-plot3.male.meta.RR.perc.b <- plot3.male.meta.RR.perc.b[order(plot3.male.meta.RR.perc.b$GroupingTerm), ]
-
-plot3.male.meta.CVR.Vr.perc <- full_join(plot3.male.meta.CVR.perc.b, plot3.male.meta.VR.perc.b)
-overall.male.plot3.perc <- full_join(plot3.male.meta.CVR.Vr.perc, plot3.male.meta.RR.perc.b)
-
-overall.male.plot3.perc$GroupingTerm <- factor(overall.male.plot3.perc$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
-overall.male.plot3.perc$GroupingTerm <- factor(overall.male.plot3.perc$GroupingTerm, rev(levels(overall.male.plot3.perc$GroupingTerm)))
-```
-
-Restructure data for plotting : Male biased, 10% difference
-
-```{r}
-overall3.perc <- gather(overall.male.plot3.perc, parameter, value, c(lnCVR, lnRR), factor_key = TRUE) # lnVR,
-
-lnCVR.ci <- overall3.perc %>%
-  filter(parameter == "lnCVR") %>%
-  mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
-# lnVR.ci <- overall3.perc  %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
-lnRR.ci <- overall3.perc %>%
-  filter(parameter == "lnRR") %>%
-  mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
-
-overall4.male.perc <- bind_rows(lnCVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high) # lnVR.ci,
-
-overall4.male.perc$label <- "Sex difference in m/f ratios > 10%"
-
-overall4.male.perc$value <- as.numeric(overall4.male.perc$value)
-overall4.male.perc$ci.low <- as.numeric(overall4.male.perc$ci.low)
-overall4.male.perc$ci.high <- as.numeric(overall4.male.perc$ci.high)
-```
-
-Plot Fig5D  all >10% difference (male bias)
-
-```{r}
-
-Metameta_Fig3_male.perc <- overall4.male.perc %>% # filter(., GroupingTerm != "Hearing") %>%
-  ggplot(aes(y = GroupingTerm, x = value)) +
-  geom_errorbarh(aes(
-    xmin = ci.low,
-    xmax = ci.high
-  ),
-  height = 0.1, show.legend = FALSE
-  ) +
-  geom_point(aes(
-    shape = parameter,
-    fill = parameter
-  ),
-  color = "mediumaquamarine", size = 2.2,
-  show.legend = FALSE
-  ) +
-  scale_x_continuous(
-    limits = c(-0.2, 0.62),
-    breaks = c(0, 0.3),
-    name = "Effect size"
-  ) +
-  geom_vline(
-    xintercept = 0,
-    color = "black",
-    linetype = "dashed"
-  ) +
-  facet_grid(
-    cols = vars(parameter), rows = vars(label),
-    labeller = label_wrap_gen(width = 23),
-    scales = "free",
-    space = "free"
-  ) +
-  theme_bw() +
-  theme(
-    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
-    strip.text.x = element_blank(),
-    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
-    text = element_text(size = 14),
-    panel.spacing = unit(0.5, "lines"),
-    panel.border = element_blank(),
-    axis.line = element_line(),
-    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
-    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
-    panel.grid.minor.y = element_blank(),
-    panel.grid.minor.x = element_blank(),
-    legend.title = element_blank(),
-    axis.title.x = element_text(hjust = 0.5, size = 14),
-    axis.title.y = element_blank()
-  )
-
-# Metameta_Fig3_male.perc (Figure 5D right panel)
-```
-
-#### Female Fig 5D >10%
-
-```{r}
-
-meta.plot3.perc <- metacombo %>%
-  mutate(
-    percCVR = ifelse(lnCVR < log(9 / 10), 1, 0),
-    percVR = ifelse(lnVR < log(9 / 10), 1, 0),
-    percRR = ifelse(lnRR < log(9 / 10), 1, 0)
-  )
-
-# Significant subset for lnCVR
-metacombo_plot3.CVR.perc <- meta.plot3.perc %>%
-  filter(percCVR == 1) %>%
-  group_by(GroupingTerm) %>%
-  nest()
-
-metacombo_plot3.CVR.perc.all <- meta.plot3.perc %>%
-  filter(percCVR == 1) %>%
-  nest()
-
-# Significant subset for lnVR
-metacombo_plot3.VR.perc <- meta.plot3.perc %>%
-  filter(percVR == 1) %>%
-  group_by(GroupingTerm) %>%
-  nest()
-
-metacombo_plot3.VR.perc.all <- meta.plot3.perc %>%
-  filter(percVR == 1) %>%
-  nest()
-
-# Significant subset for lnRR
-metacombo_plot3.RR.perc <- meta.plot3.perc %>%
-  filter(percRR == 1) %>%
-  group_by(GroupingTerm) %>%
-  nest()
-
-metacombo_plot3.RR.perc.all <- meta.plot3.perc %>%
-  filter(percRR == 1) %>%
-  nest()
-
-# **Final fixed effects meta-analyses within grouping terms, with SE of the estimate
-
-plot3.meta.CVR.perc <- metacombo_plot3.CVR.perc %>%
-  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(
-    yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower) / (2 * 1.96),
-    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-  )))
-
-plot3.meta.VR.perc <- metacombo_plot3.VR.perc %>%
-  mutate(model_lnVR = map(data, ~ metafor::rma.uni(
-    yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
-    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-  )))
-
-plot3.meta.RR.perc <- metacombo_plot3.RR.perc %>%
-  mutate(model_lnRR = map(data, ~ metafor::rma.uni(
-    yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
-    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-  )))
-
-# Across all grouping terms #
-
-plot3.meta.CVR.perc.all <- metacombo_plot3.CVR.perc.all %>%
-  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(
-    yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower) / (2 * 1.96),
-    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-  )))
-
-plot3.meta.CVR.perc.all <- plot3.meta.CVR.perc.all %>% mutate(GroupingTerm = "All")
-
-plot3.meta.VR.perc.all <- metacombo_plot3.VR.perc.all %>%
-  mutate(model_lnVR = map(data, ~ metafor::rma.uni(
-    yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
-    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-  )))
-
-plot3.meta.VR.perc.all <- plot3.meta.VR.perc.all %>% mutate(GroupingTerm = "All")
-
-plot3.meta.RR.perc.all <- metacombo_plot3.RR.perc.all %>%
-  mutate(model_lnRR = map(data, ~ metafor::rma.uni(
-    yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
-    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-  )))
-
-plot3.meta.RR.perc.all <- plot3.meta.RR.perc.all %>% mutate(GroupingTerm = "All")
-
-# Combine with separate grouping term results
-
-plot3.meta.CVR.perc <- bind_rows(plot3.meta.CVR.perc, plot3.meta.CVR.perc.all)
-plot3.meta.VR.perc <- bind_rows(plot3.meta.VR.perc, plot3.meta.VR.perc.all)
-plot3.meta.RR.perc <- bind_rows(plot3.meta.RR.perc, plot3.meta.RR.perc.all)
-
-# **Re-structure data for each grouping term; delete un-used variables: "Hearing missing for all 3 parameters"
-
-plot3.meta.CVR.perc.b <- as.data.frame(plot3.meta.CVR.perc %>% group_by(GroupingTerm) %>%
-  mutate(
-    lnCVR = map_dbl(model_lnCVR, pluck(2)), lnCVR_lower = map_dbl(model_lnCVR, pluck(6)),
-    lnCVR_upper = map_dbl(model_lnCVR, pluck(7)), lnCVR_se = map_dbl(model_lnCVR, pluck(3))
-  ))[, c(1, 4:7)]
-add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.meta.CVR.perc.b))
-plot3.meta.CVR.perc.b <- rbind(plot3.meta.CVR.perc.b, add.row.hearing)
-plot3.meta.CVR.perc.b <- plot3.meta.CVR.perc.b[order(plot3.meta.CVR.perc.b$GroupingTerm), ]
-
-plot3.meta.VR.perc.b <- as.data.frame(plot3.meta.VR.perc %>% group_by(GroupingTerm) %>%
-  mutate(
-    lnVR = map_dbl(model_lnVR, pluck(2)), lnVR_lower = map_dbl(model_lnVR, pluck(6)),
-    lnVR_upper = map_dbl(model_lnVR, pluck(7)), lnVR_se = map_dbl(model_lnVR, pluck(3))
-  ))[, c(1, 4:7)]
-add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.meta.VR.perc.b))
-plot3.meta.VR.perc.b <- rbind(plot3.meta.VR.perc.b, add.row.hearing)
-plot3.meta.VR.perc.b <- plot3.meta.VR.perc.b[order(plot3.meta.VR.perc.b$GroupingTerm), ]
-
-plot3.meta.RR.perc.b <- as.data.frame(plot3.meta.RR.perc %>% group_by(GroupingTerm) %>%
-  mutate(
-    lnRR = map_dbl(model_lnRR, pluck(2)), lnRR_lower = map_dbl(model_lnRR, pluck(6)),
-    lnRR_upper = map_dbl(model_lnRR, pluck(7)), lnRR_se = map_dbl(model_lnRR, pluck(3))
-  ))[, c(1, 4:7)]
-add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.meta.RR.perc.b))
-plot3.meta.RR.perc.b <- rbind(plot3.meta.RR.perc.b, add.row.hearing)
-add.row.hematology <- as.data.frame(t(c("Hematology", NA, NA, NA, NA))) %>%
-  setNames(names(plot3.meta.RR.perc.b))
-plot3.meta.RR.perc.b <- rbind(plot3.meta.RR.perc.b, add.row.hematology)
-
-plot3.meta.RR.perc.b <- plot3.meta.RR.perc.b[order(plot3.meta.RR.perc.b$GroupingTerm), ]
-
-plot3.meta.CVR.perc.c <- full_join(plot3.meta.CVR.perc.b, plot3.meta.VR.perc.b)
-overall.plot3.perc <- full_join(plot3.meta.CVR.perc.c, plot3.meta.RR.perc.b)
-
-overall.plot3.perc$GroupingTerm <- factor(overall.plot3.perc$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
-overall.plot3.perc$GroupingTerm <- factor(overall.plot3.perc$GroupingTerm, rev(levels(overall.plot3.perc$GroupingTerm)))
-```
-
-Restructure data for plotting
-Female bias, 10 percent difference
-
-```{r}
-overall3.perc <- gather(overall.plot3.perc, parameter, value, c(lnCVR, lnRR), factor_key = TRUE) # lnVR,
-
-lnCVR.ci <- overall3.perc %>%
-  filter(parameter == "lnCVR") %>%
-  mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
-# lnVR.ci <- overall3.perc  %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
-lnRR.ci <- overall3.perc %>%
-  filter(parameter == "lnRR") %>%
-  mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
-
-overall4.perc <- bind_rows(lnCVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high) # lnVR.ci,
-
-overall4.perc$label <- "Sex difference in m/f ratios > 10%"
-
-overall4.perc$value <- as.numeric(overall4.perc$value)
-overall4.perc$ci.low <- as.numeric(overall4.perc$ci.low)
-overall4.perc$ci.high <- as.numeric(overall4.perc$ci.high)
-```
-
-Plot Fig5D all >10% difference (female)
-
-```{r}
-Metameta_Fig3_female.perc <- overall4.perc %>%
-  ggplot(aes(y = GroupingTerm, x = value)) +
-  geom_errorbarh(aes(
-    xmin = ci.low,
-    xmax = ci.high
-  ),
-  height = 0.1, show.legend = FALSE
-  ) +
-  geom_point(aes(shape = parameter),
-    fill = "salmon1", color = "salmon1", size = 2.2,
-    show.legend = FALSE
-  ) +
-
-  # scale_shape_manual(values =
-
-  scale_x_continuous(
-    limits = c(-0.53, 0.2),
-    breaks = c(-0.3, 0),
-    name = "Effect size"
-  ) +
-  geom_vline(
-    xintercept = 0,
-    color = "black",
-    linetype = "dashed"
-  ) +
-  facet_grid(
-    cols = vars(parameter), # rows = vars(label),
-    # labeller = label_wrap_gen(width = 23),
-    scales = "free",
-    space = "free"
-  ) +
-  theme_bw() +
-  theme(
-    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
-    strip.text.x = element_blank(),
-    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
-    text = element_text(size = 14),
-    panel.spacing = unit(0.5, "lines"),
-    panel.border = element_blank(),
-    axis.line = element_line(),
-    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
-    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
-    panel.grid.minor.y = element_blank(),
-    panel.grid.minor.x = element_blank(),
-    legend.title = element_blank(),
-    axis.title.x = element_text(hjust = 0.5, size = 14),
-    axis.title.y = element_blank()
-  )
-
-# Metameta_Fig3_female.perc (Figure 5D left panel)
-```
-
-#### Plot Fig5:   plots combined
-
-```{r}
-library(ggpubr)
-Fig5b <- ggarrange(Metameta_Fig3_female.sig, Metameta_Fig3_male.sig,
-  ncol = 2, nrow = 1, widths = c(1, 1.20), heights = c(1, 1)
-)
-
-Fig5d <- ggarrange(Metameta_Fig3_female.perc, Metameta_Fig3_male.perc,
-  ncol = 2, nrow = 1, widths = c(1, 1.20), heights = c(1, 1)
-)
-
-# end combination Figure 5
-
-Fig5 <- ggarrange(malebias_Fig2_sigtraits, malebias_Fig2_over10, Fig5b, Fig5d, ncol = 1, nrow = 4, heights = c(2.3, 2, 2.1, 2), labels = c("A", " ", "B", " "))
-Fig5
-```
-
-## Heterogeneity
-#### FIGURE 4 (Second-order meta analysis on heterogeneity)
-Create matrix to store results for all traits
-
-```{r}
+# Metameta_FigS1_alltraits
+```
+
+### Heterogeneity
+The analysis for heterogeneity follows the workflow of the above steps for the different meta-analyses.
+However, in the initial meta-analysis we extract sigma^2 and errors for mouse strains and centers (Institutions).
+
+```{r}
+# Create dataframe to store results
 results.allhetero.grouping <- as.data.frame(cbind(c(1:n), matrix(rep(0, n * 30), ncol = 30)))
@@
 
-#### Exclude traits, merge datasets
+#### Exclude traits without variation between mouse strains; merge datasets  #Felix added 6/2/2020
 
@@
 results.allhetero.grouping2 <- results.allhetero.grouping[results.allhetero.grouping$s.nlevels.strain.VR != 0, ]
-# nrow(results.allhetero.grouping2) #218
+# nrow(results.allhetero.grouping) #223  Felix 7/2/2020 added: not sure. Run again and it was 232?!
 ```
@@
 metahetero1 <- results.allhetero.grouping2
-# length(unique(metahetero1$procedure)) #18
+# length(unique(metahetero1$procedure)) #19
 # length(unique(metahetero1$GroupingTerm)) #9 
-# length(unique(metahetero1$parameter_group)) # 149
-# length(unique(metahetero1$parameter_name)) #218
+# length(unique(metahetero1$parameter_group)) #152
+# length(unique(metahetero1$parameter_name)) #223
 
@@
 
-metahetero1_sub <- subset(metahetero1, par_group_size > 1) # 90 observations
+metahetero1_sub <- subset(metahetero1, par_group_size > 1) # 92 observations
 # str(metahetero1_sub)
@@
   group_by(parameter_group) %>%
-  # mutate(raw_N = sum(sampleSize)) %>%  #don't think is necessary: delete in final version
+  # mutate(raw_N = sum(sampleSize)) %>%  #Felix added: don't think is necessary: delete in final version
   nest()
@@
 ## *Perform meta-analyses on correlated sub-traits, using robumeta
-
+ # Susi / FELIX: what's this below?
 # Shinichi: We think we want to use these for further analyses:
@@
 
+# Felix: doesn't work , error message:
+#!!!!!!!!!!! ERROR!!!!!!!!!!!!!!!!!!!!
+#Error: Column `parameter_group` can't be modified because it's a grouping variable
+
 count_fun. <- function(mod_sub) {
@@
 robusub_RR. <- model_count. %>%
-  transmute(parameter_group, estimatelnRR = map(model_lnRR, count_fun.)) %>%
+  transmute(estimatelnRR = map(model_lnRR, count_fun.)) %>%    #Felix 4/2/2020: deleted: 'parameter_group' (in brackets, after 'transmute')
   mutate(r = map(estimatelnRR, ~ data.frame(t(.)))) %>%
@@
 robusub_CVR. <- model_count. %>%
-  transmute(parameter_group, estimatelnCVR = map(model_lnCVR, count_fun.)) %>%
+  transmute(estimatelnCVR = map(model_lnCVR, count_fun.)) %>%
   mutate(r = map(estimatelnCVR, ~ data.frame(t(.)))) %>%
@@
 robusub_VR. <- model_count. %>%
-  transmute(parameter_group, estimatelnVR = map(model_lnVR, count_fun.)) %>%
+  transmute(estimatelnVR = map(model_lnVR, count_fun.)) %>%
   mutate(r = map(estimatelnVR, ~ data.frame(t(.)))) %>%
@@
 metahetero_all <- metahetero_all %>% mutate(
-  var.RR = if_else(var.RR == -Inf, -7, var.RR),
+  var.RR = if_else(var.RR == -Inf, -7, var.RR),   #Felix commented 6/2/2020: can't remmeber, why -7, -6, -5 in this section!
   var.VR = if_else(var.VR == -Inf, -5, var.VR),
@@
 
-metacombohetero <- metacombohetero[, c(1:7, 43:45)]
-names(metacombohetero)[9] <- "procedure"
-names(metacombohetero)[10] <- "GroupingTerm"
+metacombohetero <- metacombohetero %>% select(parameter_group, var.CVR, N.CVR, var.VR, N.VR, var.RR, N.RR, counts, procedure = procedure2, GroupingTerm = GroupingTerm2)  #Felix changed 6/2/2020: was: c(1:7, 43:45, and 2 renaming lines)
+
 ```
@@
 ```{r}
-## *Perform meta-meta-analysis (3 for each of the 9 grouping terms: var.CVR, var.VR, var.RR)
+## Perform meta-meta-analysis (3 for each of the 9 grouping terms: var.CVR, var.VR, var.RR)
 
@@
 # Final fixed effects meta-analyses within grouping terms, with SE of the estimate
-
-# metacombohetero$var.CVR
 
@@
 
-# **Re-structure data for each grouping term; extract heterogenenity/variance terms; delete un-used variables
+# Across all grouping terms
+
+metacombohetero_all_final <- metacombohetero %>%
+  nest(data = everything())
+
+# Final fixed effects meta-analyses ACROSS grouping terms, with SE of the estimate
+
+heterog1_all <- metacombohetero_all_final %>%
+
+  mutate(
+    model_heteroCVR = map(data, ~ metafor::rma.uni(
+      yi = .x$var.CVR, sei = sqrt(1 / 2 * (.x$N.CVR - 1)),
+      control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 10000, stepadj = 0.5), verbose = F
+    )),
+    model_heteroVR = map(data, ~ metafor::rma.uni(
+      yi = .x$var.VR, sei = sqrt(1 / 2 * (.x$N.VR - 1)),
+      control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 10000, stepadj = 0.5), verbose = F
+    )),
+    model_heteroRR = map(data, ~ metafor::rma.uni(
+      yi = .x$var.RR, sei = sqrt(1 / 2 * (.x$N.RR - 1)),
+      control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 10000, stepadj = 0.5), verbose = F
+    ))
+  )
+
+# Re-structure data for each grouping term; extract heterogenenity/variance terms; delete un-used variables
 
@@
 
-heterog2 <- bind_rows(Behaviour., Morphology., Metabolism., Physiology., Immunology., Hematology., Heart., Hearing., Eye.)
+#Reorder to be able to keep cell referencing 
+heterog1_all <- heterog1_all %>% mutate(GroupingTerm = "All") %>% select(GroupingTerm, everything())
+
+All. <- heterog1_all %>% 
+  select(., -data) %>%
+  mutate(
+    heteroCVR = .[[2]][[1]]$b, heteroCVR_lower = .[[2]][[1]]$ci.lb, heteroCVR_upper = .[[2]][[1]]$ci.ub, heteroCVR_se = .[[2]][[1]]$se,
+    heteroVR = .[[3]][[1]]$b, heteroVR_lower = .[[3]][[1]]$ci.lb, heteroVR_upper = .[[3]][[1]]$ci.ub, heteroVR_se = .[[3]][[1]]$se,
+    heteroRR = .[[4]][[1]]$b, heteroRR_lower = .[[4]][[1]]$ci.lb, heteroRR_upper = .[[4]][[1]]$ci.ub, heteroRR_se = .[[4]][[1]]$se
+  ) %>%
+  select(., GroupingTerm, heteroCVR:heteroRR_se)
+
+heterog2 <- bind_rows(Behaviour., Morphology., Metabolism., Physiology., Immunology., Hematology., Heart., Hearing., Eye., All.)
 # str(heterog2)
@@
 
-heterog4$GroupingTerm <- factor(heterog4$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye"))
+heterog4$GroupingTerm <- factor(heterog4$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
 heterog4$GroupingTerm <- factor(heterog4$GroupingTerm, rev(levels(heterog4$GroupingTerm)))
@@
 
-### Plot FIGURE 4 - C(Second-order meta analysis on heterogeneity)
-
-Plot Fig4 all traits
+#### Plot S1 C (Second-order meta analysis on heterogeneity)
 
@@
 
-Hetero4c <-
+HeteroS1 <-
   heterog6 %>%
-  filter(
-    parameter == "heteroCVR" | parameter == "heteroRR"
-  ) %>%
   ggplot(aes(y = GroupingTerm, x = mean)) +
@@
 
-# Hetero4c
-
-# ggsave("Fig4.pdf", plot = Metameta_Fig4_alltraits, width = 7, height = 6)
-```
-
-#### Combined Figure 4: overall (Count data, Meta anlysis results, Heterogeneity)
-
-```{r}
-
-Fig4 <- ggarrange(malebias_Fig2_alltraits, Metameta_Fig3_alltraits, Hetero4c, nrow = 3, align = "v", heights = c(1, 1, 1), labels = c("A", "B", "C"))
-Fig4
-# ggsave("Fig4_OverallResults.pdf", plot = Fig4, width = 6, height = 5)
-```
-
-## Supplemental Figures
-
-```{r}
-## Heterogneity, S1 C
-
-HeteroS1 <- heterog5 %>%
-  ggplot(aes(y = GroupingTerm, x = mean)) +
-  geom_errorbarh(aes(
-    xmin = ci.l,
-    xmax = ci.h
-  ),
-  height = 0.1, show.legend = FALSE
-  ) +
-  geom_point(aes(shape = parameter),
-    fill = "black",
-    color = "black", size = 2.2,
-    show.legend = FALSE
-  ) +
-  scale_x_continuous(
-    limits = c(-0.1, 1.4),
-    # breaks = c(0, 0.1, 0.2),
-    name = "Effect size"
-  ) +
-  # geom_vline(xintercept=0,
-  # color='black',
-  # linetype='dashed')+
-  facet_grid(
-    cols = vars(parameter), rows = vars(label),
-    labeller = label_wrap_gen(width = 23),
-    scales = "free",
-    space = "free"
-  ) +
-  theme_bw() +
-  theme(
-    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
-    strip.text.x = element_text(size = 12),
-    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
-    text = element_text(size = 14),
-    panel.spacing = unit(0.5, "lines"),
-    panel.border = element_blank(),
-    axis.line = element_line(),
-    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
-    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
-    panel.grid.minor.y = element_blank(),
-    panel.grid.minor.x = element_blank(),
-    legend.title = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank()
-  )
-
-# HeteroS1
-
-# ggsave("Fig4.pdf", plot = Metameta_Fig4_alltraits, width = 7, height = 6)
-```
-
-## Count data, including lnVR (Fig S1 A)
-
-```{r}
-# *Prepare data for all traits
-
-meta.plot2.all <- meta_clean %>%
-  select(lnCVR, lnVR, lnRR, GroupingTerm) %>%
-  arrange(GroupingTerm)
-
-meta.plot2.all.bS1 <- gather(meta.plot2.all, trait, value, c(lnCVR, lnVR, lnRR))
-
-meta.plot2.all.bS1$trait <- factor(meta.plot2.all.bS1$trait, levels = c("lnCVR", "lnVR", "lnRR"))
-
-meta.plot2.all.cS1 <- meta.plot2.all.bS1 %>%
+#HeteroS1
+
+```
+
+#### Combined Figure S1: overall Count data, Meta anlysis results, Heterogeneity)
+
+```{r}
+FigS1 <- ggarrange(malebias_FigS1_alltraits + xlab("percentage sex bias"), Metameta_FigS1_alltraits, HeteroS1, nrow = 3, align = "v", heights = c(1, 1, 1), labels = c("A", "B", "C"))
+FigS1
+# ggsave("FigS1_OverallResults.pdf", plot = Fig4, width = 6, height = 5)
+```
+
+## Figure S2
+
+Plot FigS2 all significant results (CI not overlapping zero) for males
+### FELIX:  "ALL" missing. Felix added 11/2/2020: done
+```{r}
+meta.plot2.sig.bS <- meta.plot2.sig[, c("lnCVR", "lnVR", "lnRR", "lnCVRsig", "lnVRsig", "lnRRsig", "GroupingTerm")]
+
+meta.plot2.sig.cS <- gather(meta.plot2.sig.bS, trait, value, lnCVR:lnRR)
+meta.plot2.sig.cS$sig <- "placeholder"
+
+meta.plot2.sig.cS$trait <- factor(meta.plot2.sig.cS$trait, levels = c("lnCVR", "lnVR", "lnRR"))
+
+meta.plot2.sig.cS$sig <- ifelse(meta.plot2.sig.cS$trait == "lnCVR", meta.plot2.sig.cS$lnCVRsig,
+  ifelse(meta.plot2.sig.cS$trait == "lnVR", meta.plot2.sig.cS$lnVRsig, meta.plot2.sig.cS$lnRRsig)
+)
+
+# choosing sex biased ln-ratios significantly larger than 0
+meta.plotS2.sig.malebias <- meta.plot2.sig.cS %>%
   group_by_at(vars(trait, GroupingTerm)) %>%
-  summarise(
-    malebias = sum(value > 0), femalebias = sum(value <= 0), total = malebias + femalebias,
-    malepercent = malebias * 100 / total, femalepercent = femalebias * 100 / total
-  )
-
-meta.plot2.all.cS1$label <- "All traits"
+  filter(sig == 1) %>%
+  summarise(male_sig = sum(value > 0), female_sig = sum(value < 0), total = male_sig + female_sig)
+
+meta.plotS2.sig.malebias <- ungroup(meta.plotS2.sig.malebias) %>%
+  add_row(trait = "lnCVR", GroupingTerm = "Hearing", male_sig = 0, female_sig = 0, .before = 4) %>% # add "Hearing" for lnCVR (not filtered as only zeros)
+  mutate(malepercent = male_sig * 100 / total, femalepercent = female_sig * 100 / total)
+
+meta.plotS2.sig.malebias$label <- "CI not overlapping zero"
 
@@
 
-meta.plot2.all.dS1 <- as.data.frame(meta.plot2.all.cS1)
-meta.plot2.all.eS1 <- gather(meta.plot2.all.dS1, key = sex, value = percent, malepercent:femalepercent, factor_key = TRUE)
+meta.plotS2.sig.bothsexes <- as.data.frame(meta.plotS2.sig.malebias)
+meta.plotS2.sig.bothsexes.b <- gather(meta.plotS2.sig.bothsexes, key = sex, value = percent, malepercent:femalepercent, factor_key = TRUE)
 
@@
 
-meta.plot2.all.eS1$samplesize <- with(meta.plot2.all.eS1, ifelse(sex == "malepercent", malebias, femalebias))
-
-malebias_FigS1_alltraits <-
-  ggplot(meta.plot2.all.eS1) +
+meta.plotS2.sig.bothsexes.b$samplesize <- with(meta.plotS2.sig.bothsexes.b, ifelse(sex == "malepercent", male_sig, female_sig))
+
+# Add summary row ('All') and re-arrange rows into correct order for plotting (warnings about coercing 'id' into character vector are ok)
+
+meta.plotS2.sig.bothsexes.c <- meta.plotS2.sig.bothsexes.b %>% group_by(trait, sex) %>% 
+  summarise(GroupingTerm = "All", male_sig = sum(male_sig), female_sig = sum(female_sig), total = male_sig + female_sig, 
+            label = "CI not overlapping zero", samplesize = sum(samplesize)) %>%
+  mutate(percent = ifelse(sex == "femalepercent", female_sig*100/(male_sig + female_sig), male_sig*100/(male_sig + female_sig))) %>%
+  bind_rows(meta.plotS2.sig.bothsexes.b, .) %>%
+  mutate(rownumber = row_number()) %>%
+  .[c(55, 1:9, 57, 10:18, 59, 19:27, 56, 28:36, 58, 37:45, 60, 46:54), ]
+
+meta.plotS2.sig.bothsexes.c$GroupingTerm <- factor(meta.plotS2.sig.bothsexes.c$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
+meta.plotS2.sig.bothsexes.c$GroupingTerm <- factor(meta.plotS2.sig.bothsexes.c$GroupingTerm, rev(levels(meta.plotS2.sig.bothsexes.c$GroupingTerm)))
+
+# *Plot Fig2 all significant results (CI not overlapping zero):
+#     no sig. lnCVR for 'Hearing' in either sex; no sig. male-biased lnCVR for 'Immunology' and 'Eye, and no sig. male-biased lnVR for 'Eye'
+
+malebias_FigS2_sigtraits <-
+  ggplot(meta.plotS2.sig.bothsexes.c) +
   aes(x = GroupingTerm, y = percent, fill = sex) +
@@
   geom_text(
-    data = subset(meta.plot2.all.eS1, samplesize != 0), aes(label = samplesize), position = position_stack(vjust = .5),
+    data = subset(meta.plotS2.sig.bothsexes.c, samplesize != 0), aes(label = samplesize), position = position_stack(vjust = .5),
     color = "white", size = 3.5
@@
 
-# malebias_FigS1_alltraits     #(panel A in Figure S1)
-```
-
-###  Overall results of second order meta analysis (Figure 4: overall, Figure 5: sex-bias), INCLUDING VR
-#### Restructure data for plotting 
-Restructure MALE data for plotting
-
-```{r}
-overall3.male.sigS <- gather(overall.male.plot3, parameter, value, c(lnCVR, lnVR, lnRR), factor_key = TRUE)
-
-lnCVR.ci <- overall3.male.sigS %>%
-  filter(parameter == "lnCVR") %>%
-  mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
-lnVR.ci <- overall3.male.sigS %>%
-  filter(parameter == "lnVR") %>%
-  mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
-lnRR.ci <- overall3.male.sigS %>%
-  filter(parameter == "lnRR") %>%
-  mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
-
-overall4.male.sigS <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
-
-overall4.male.sigS$label <- "CI not overlapping zero"
-```
-
-Data are restructured, and grouping terms are being re-ordered
-
-```{r}
-overall3S <- gather(overall2, parameter, value, c(lnCVR, lnVR, lnRR), factor_key = TRUE)
-
-lnCVR.ci <- overall3S %>%
-  filter(parameter == "lnCVR") %>%
-  mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
-lnVR.ci <- overall3S %>%
-  filter(parameter == "lnVR") %>%
-  mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
-lnRR.ci <- overall3S %>%
-  filter(parameter == "lnRR") %>%
-  mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
-
-overall4S <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
-
-# re-order Grouping Terms
-
-overall4S$GroupingTerm <- factor(overall4S$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
-overall4S$GroupingTerm <- factor(overall4S$GroupingTerm, rev(levels(overall4S$GroupingTerm)))
-overall4S$label <- "All traits"
-```
-
-#### Preparation for Plots FIGURE S1B & S2B, S2D (Second-order meta analysis results, INCL lnVR)
-Preparation: Sub-Plot  for Figure S1: all traits (S1 B)
-
-```{r}
-Metameta_FigS1_alltraits <- overall4S %>%
-
-  ggplot(aes(y = GroupingTerm, x = value)) +
-  geom_errorbarh(aes(
-    xmin = ci.low,
-    xmax = ci.high
-  ),
-  height = 0.1, show.legend = FALSE
-  ) +
-  geom_point(aes(shape = parameter),
-    fill = "black",
-    color = "black", size = 2.2,
-    show.legend = FALSE
-  ) +
-  scale_x_continuous(
-    limits = c(-0.24, 0.25),
-    breaks = c(-0.2, -0.1, 0, 0.1, 0.2),
-    name = "Effect size"
-  ) +
-  geom_vline(
-    xintercept = 0,
-    color = "black",
-    linetype = "dashed"
-  ) +
-  facet_grid(
-    cols = vars(parameter), rows = vars(label),
-    labeller = label_wrap_gen(width = 23),
-    scales = "free",
-    space = "free"
-  ) +
-  theme_bw() +
-  theme(
-    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
-    strip.text.x = element_text(size = 12),
-    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
-    text = element_text(size = 14),
-    panel.spacing = unit(0.5, "lines"),
-    panel.border = element_blank(),
-    axis.line = element_line(),
-    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
-    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
-    panel.grid.minor.y = element_blank(),
-    panel.grid.minor.x = element_blank(),
-    legend.title = element_blank(),
-    axis.title.x = element_text(hjust = 0.5, size = 14),
-    axis.title.y = element_blank()
-  )
-
-# Metameta_FigS1_alltraits
-```
-
-#### Combined Figure S1: overall Count data, Meta anlysis results, Heterogeneity)
-
-```{r}
-FigS1 <- ggarrange(malebias_FigS1_alltraits + xlab("percentage sex bias"), Metameta_FigS1_alltraits, HeteroS1, nrow = 3, align = "v", heights = c(1, 1, 1), labels = c("A", "B", "C"))
-FigS1
-# ggsave("FigS1_OverallResults.pdf", plot = Fig4, width = 6, height = 5)
-```
-
-## Figure S2: sex-bias, including VR
-
-Plot FigS2 all significant results (CI not overlapping zero) for males
-
-```{r}
-meta.plot2.sig.bS <- meta.plot2.sig[, c("lnCVR", "lnVR", "lnRR", "lnCVRsig", "lnVRsig", "lnRRsig", "GroupingTerm")]
-
-meta.plot2.sig.cS <- gather(meta.plot2.sig.bS, trait, value, lnCVR:lnRR)
-meta.plot2.sig.cS$sig <- "placeholder"
-
-meta.plot2.sig.cS$trait <- factor(meta.plot2.sig.cS$trait, levels = c("lnCVR", "lnVR", "lnRR"))
-
-meta.plot2.sig.cS$sig <- ifelse(meta.plot2.sig.cS$trait == "lnCVR", meta.plot2.sig.cS$lnCVRsig,
-  ifelse(meta.plot2.sig.cS$trait == "lnVR", meta.plot2.sig.cS$lnVRsig, meta.plot2.sig.cS$lnRRsig)
-)
-
-# choosing sex biased ln-ratios significantly larger than 0
-meta.plotS2.sig.malebias <- meta.plot2.sig.cS %>%
+# malebias_FigS2_sigtraits # this is Figure S2 A
+```
+### Prepare data for traits with effect size ratios > 10% larger in males, supplemental Figure S2
+### FELIX:  "ALL" missing. Felix added 11/2/2020: done
+This Figure extends Figure 4, as it includes results not only for lnCVR and lnRR but also lnCVR.
+In addition, we compare two different assessments of sex-bias, significance (CI not overlapping zero) and sex differences in male / female ratios > 10%
+
+### Over 10% male bias, count data (first- order metanalysis) 
+```{r}
+meta.plot2.over10 <- meta_clean %>%
+  select(lnCVR, lnVR, lnRR, GroupingTerm) %>%
+  arrange(GroupingTerm)
+
+meta.plot2.over10.b <- gather(meta.plot2.over10, trait, value, c(lnCVR, lnVR, lnRR))
+
+meta.plot2.over10.b$trait <- factor(meta.plot2.over10.b$trait, levels = c("lnCVR", "lnVR", "lnRR"))
+
+meta.plot2.over10.c <- meta.plot2.over10.b %>%
   group_by_at(vars(trait, GroupingTerm)) %>%
-  filter(sig == 1) %>%
-  summarise(male_sig = sum(value > 0), female_sig = sum(value < 0), total = male_sig + female_sig)
-
-meta.plotS2.sig.malebias <- ungroup(meta.plotS2.sig.malebias) %>%
-  add_row(trait = "lnCVR", GroupingTerm = "Hearing", male_sig = 0, female_sig = 0, .before = 4) %>% # add "Hearing" for lnCVR (not filtered as only zeros)
-  mutate(malepercent = male_sig * 100 / total, femalepercent = female_sig * 100 / total)
-
-meta.plotS2.sig.malebias$label <- "CI not overlapping zero"
+  summarise(
+    malebias = sum(value > log(11 / 10)), femalebias = sum(value < log(9 / 10)), total = malebias + femalebias,
+    malepercent = malebias * 100 / total, femalepercent = femalebias * 100 / total
+  )
+
+meta.plot2.over10.c$label <- "Sex difference in m/f ratios > 10%"
 
@@
 
-meta.plotS2.sig.bothsexes <- as.data.frame(meta.plotS2.sig.malebias)
-meta.plotS2.sig.bothsexes.b <- gather(meta.plotS2.sig.bothsexes, key = sex, value = percent, malepercent:femalepercent, factor_key = TRUE)
+meta.plot2.over10.c <- as.data.frame(meta.plot2.over10.c)
+meta.plot2.over10.d <- gather(meta.plot2.over10.c, key = sex, value = percent, malepercent:femalepercent, factor_key = TRUE)
 
@@
 
-meta.plotS2.sig.bothsexes.b$samplesize <- with(meta.plotS2.sig.bothsexes.b, ifelse(sex == "malepercent", male_sig, female_sig))
-
-# *Plot Fig2 all significant results (CI not overlapping zero):
-#     no sig. lnCVR for 'Hearing' in either sex; no sig. male-biased lnCVR for 'Immunology' and 'Eye, and no sig. male-biased lnVR for 'Eye'
-
-malebias_FigS2_sigtraits <-
-  ggplot(meta.plotS2.sig.bothsexes.b) +
+meta.plot2.over10.d$samplesize <- with(meta.plot2.over10.d, ifelse(sex == "malepercent", malebias, femalebias))
+
+# Add summary row ('All') and re-arrange rows into correct order for plotting (warnings about coercing 'id' into character vector are ok)
+
+meta.plot2.over10.e <- meta.plot2.over10.d %>% group_by(trait, sex) %>% 
+  summarise(GroupingTerm = "All", malebias = sum(malebias), femalebias = sum(femalebias), total = malebias + femalebias, 
+            label = "Sex difference in m/f ratios > 10%", samplesize = sum(samplesize)) %>%
+  mutate(percent = ifelse(sex == "femalepercent", femalebias*100/(malebias + femalebias), malebias*100/(malebias + femalebias))) %>%
+  bind_rows(meta.plot2.over10.d, .) %>%
+  mutate(rownumber = row_number()) %>%
+  .[c(55, 1:9, 57, 10:18, 59, 19:27, 56, 28:36, 58, 37:45, 60, 46:54), ]
+
+meta.plot2.over10.e$GroupingTerm <- factor(meta.plot2.over10.e$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
+meta.plot2.over10.e$GroupingTerm <- factor(meta.plot2.over10.e$GroupingTerm, rev(levels(meta.plot2.over10.e$GroupingTerm)))
+
+# *Plot Fig2 Sex difference in m/f ratio > 10%
+malebias_Fig2_over10 <-
+  ggplot(meta.plot2.over10.e) +
   aes(x = GroupingTerm, y = percent, fill = sex) +
@@
   geom_text(
-    data = subset(meta.plotS2.sig.bothsexes.b, samplesize != 0), aes(label = samplesize), position = position_stack(vjust = .5),
-    color = "white", size = 3.5
-  ) +
-  facet_grid(
-    cols = vars(trait), rows = vars(label), labeller = label_wrap_gen(width = 18),
-    scales = "free", space = "free"
-  ) +
-  scale_fill_brewer(palette = "Set2") +
-  theme_bw(base_size = 18) +
-  theme(
-    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
-    strip.text.x = element_text(size = 12),
-    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
-    text = element_text(size = 14),
-    panel.spacing = unit(0.5, "lines"),
-    panel.border = element_blank(),
-    axis.line = element_line(),
-    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
-    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
-    panel.grid.minor.y = element_blank(),
-    panel.grid.minor.x = element_blank(),
-    legend.position = "none",
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank()
-  ) +
-  coord_flip()
-
-# malebias_FigS2_sigtraits # this is Figure S2 A
-```
-
-Prepare data for traits with effect size ratios > 10% larger in males
-
-```{r}
-meta.plotS2.over10 <- meta_clean %>%
-  select(lnCVR, lnVR, lnRR, GroupingTerm) %>%
-  arrange(GroupingTerm)
-
-meta.plotS2.over10.b <- gather(meta.plotS2.over10, trait, value, c(lnCVR, lnVR, lnRR))
-
-meta.plotS2.over10.b$trait <- factor(meta.plotS2.over10.b$trait, levels = c("lnCVR", "lnVR", "lnRR"))
-
-meta.plotS2.over10.c <- meta.plotS2.over10.b %>%
-  group_by_at(vars(trait, GroupingTerm)) %>%
-  summarise(
-    malebias = sum(value > log(11 / 10)), femalebias = sum(value < log(9 / 10)), total = malebias + femalebias,
-    malepercent = malebias * 100 / total, femalepercent = femalebias * 100 / total
-  )
-
-meta.plotS2.over10.c$label <- "Sex difference in m/f ratios > 10%"
-
-# restructure to create stacked bar plots
-
-meta.plotS2.over10.c <- as.data.frame(meta.plotS2.over10.c)
-meta.plotS2.over10.d <- gather(meta.plotS2.over10.c, key = sex, value = percent, malepercent:femalepercent, factor_key = TRUE)
-
-# create new sample size variable
-
-meta.plotS2.over10.d$samplesize <- with(meta.plotS2.over10.d, ifelse(sex == "malepercent", malebias, femalebias))
-
-# *Plot FigS2 Sex difference in m/f ratio > 10%
-malebias_FigS2_over10 <-
-  ggplot(meta.plotS2.over10.d) +
-  aes(x = GroupingTerm, y = percent, fill = sex) +
-  geom_col() +
-  geom_hline(yintercept = 50, linetype = "dashed", color = "gray40") +
-  geom_text(
-    data = subset(meta.plot2.over10.d, samplesize != 0), aes(label = samplesize), position = position_stack(vjust = .5),
+    data = subset(meta.plot2.over10.e, samplesize != 0), aes(label = samplesize), position = position_stack(vjust = .5),
     color = "white", size = 3.5
@@
 
-# malebias_FigS2_over10  #(Panel B in Fig S2 in ms)
-```
-
+# malebias_Fig2_over10  (supplemental Figure S2)
+```
+
+#### Fig S2, second-order meta-analysis, male traits
 #### Female Figure, significant traits
@@
 
-#Metameta_FigS2_male.sig (Figure 5B right panel)
+Prepare data for traits with m/f difference > 10%
+
+Create column with 1= larger, 0= difference not larger than 10% between male/female ratios
+```{r}
+meta.male.plot3.perc <- metacombo %>%
+  mutate(
+    percCVR = ifelse(lnCVR > log(11 / 10), 1, 0),
+    percVR = ifelse(lnVR > log(11 / 10), 1, 0),
+    percRR = ifelse(lnRR > log(11 / 10), 1, 0)
+  )
+
+# Significant subset for lnCVR
+metacombo_male.plot3.CVR.perc <- meta.male.plot3.perc %>%
+  filter(percCVR == 1) %>%
+  group_by(GroupingTerm) %>%
+  nest()
+
+metacombo_male.plot3.CVR.perc.all <- meta.male.plot3.perc %>%
+  filter(percCVR == 1) %>%
+  nest(data = everything())
+
+# Significant subset for lnVR
+metacombo_male.plot3.VR.perc <- meta.male.plot3.perc %>%
+  filter(percVR == 1) %>%
+  group_by(GroupingTerm) %>%
+  nest()
+
+metacombo_male.plot3.VR.perc.all <- meta.male.plot3.perc %>%
+  filter(percVR == 1) %>%
+  nest(data = everything())
+
+# Significant subset for lnRR
+metacombo_male.plot3.RR.perc <- meta.male.plot3.perc %>%
+  filter(percRR == 1) %>%
+  group_by(GroupingTerm) %>%
+  nest()
+
+metacombo_male.plot3.RR.perc.all <- meta.male.plot3.perc %>%
+  filter(percRR == 1) %>%
+  nest(data = everything())
+
+# **Final fixed effects meta-analyses within grouping terms and across grouping terms, with SE of the estimate
+
+plot3.male.meta.CVR.perc <- metacombo_male.plot3.CVR.perc %>%
+  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+plot3.male.meta.VR.perc <- metacombo_male.plot3.VR.perc %>%
+  mutate(model_lnVR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+plot3.male.meta.RR.perc <- metacombo_male.plot3.RR.perc %>%
+  mutate(model_lnRR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+# Across all grouping terms #
+
+plot3.male.meta.CVR.perc.all <- metacombo_male.plot3.CVR.perc.all %>%
+  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+plot3.male.meta.CVR.perc.all <- plot3.male.meta.CVR.perc.all %>% mutate(GroupingTerm = "All")
+
+plot3.male.meta.VR.perc.all <- metacombo_male.plot3.VR.perc.all %>%
+  mutate(model_lnVR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+plot3.male.meta.VR.perc.all <- plot3.male.meta.VR.perc.all %>% mutate(GroupingTerm = "All")
+
+plot3.male.meta.RR.perc.all <- metacombo_male.plot3.RR.perc.all %>%
+  mutate(model_lnRR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+plot3.male.meta.RR.perc.all <- plot3.male.meta.RR.perc.all %>% mutate(GroupingTerm = "All")
+
+# Combine with separate grouping term results
+
+plot3.male.meta.CVR.perc <- bind_rows(plot3.male.meta.CVR.perc, plot3.male.meta.CVR.perc.all)
+plot3.male.meta.VR.perc <- bind_rows(plot3.male.meta.VR.perc, plot3.male.meta.VR.perc.all)
+plot3.male.meta.RR.perc <- bind_rows(plot3.male.meta.RR.perc, plot3.male.meta.RR.perc.all)
+
+# **Re-structure data for each grouping term; delete un-used variables: "Hearing missing for all 3 parameters"
+
+plot3.male.meta.CVR.perc.b <- as.data.frame(plot3.male.meta.CVR.perc %>% group_by(GroupingTerm) %>%
+  mutate(
+    lnCVR = map_dbl(model_lnCVR, pluck(2)), lnCVR_lower = map_dbl(model_lnCVR, pluck(6)),
+    lnCVR_upper = map_dbl(model_lnCVR, pluck(7)), lnCVR_se = map_dbl(model_lnCVR, pluck(3))
+  ))[, c(1, 4:7)]
+add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.male.meta.CVR.perc.b))
+plot3.male.meta.CVR.perc.b <- rbind(plot3.male.meta.CVR.perc.b, add.row.hearing)
+plot3.male.meta.CVR.perc.b <- plot3.male.meta.CVR.perc.b[order(plot3.male.meta.CVR.perc.b$GroupingTerm), ]
+
+plot3.male.meta.VR.perc.b <- as.data.frame(plot3.male.meta.VR.perc %>% group_by(GroupingTerm) %>%
+  mutate(
+    lnVR = map_dbl(model_lnVR, pluck(2)), lnVR_lower = map_dbl(model_lnVR, pluck(6)),
+    lnVR_upper = map_dbl(model_lnVR, pluck(7)), lnVR_se = map_dbl(model_lnVR, pluck(3))
+  ))[, c(1, 4:7)]
+add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.male.meta.VR.perc.b))
+plot3.male.meta.VR.perc.b <- rbind(plot3.male.meta.VR.perc.b, add.row.hearing)
+plot3.male.meta.VR.perc.b <- plot3.male.meta.VR.perc.b[order(plot3.male.meta.VR.perc.b$GroupingTerm), ]
+
+plot3.male.meta.RR.perc.b <- as.data.frame(plot3.male.meta.RR.perc %>% group_by(GroupingTerm) %>%
+  mutate(
+    lnRR = map_dbl(model_lnRR, pluck(2)), lnRR_lower = map_dbl(model_lnRR, pluck(6)),
+    lnRR_upper = map_dbl(model_lnRR, pluck(7)), lnRR_se = map_dbl(model_lnRR, pluck(3))
+  ))[, c(1, 4:7)]
+add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>%
+  setNames(names(plot3.male.meta.RR.perc.b))
+plot3.male.meta.RR.perc.b <- rbind(plot3.male.meta.RR.perc.b, add.row.hearing)
+
+add.row.eye <- as.data.frame(t(c("Eye", NA, NA, NA, NA))) %>%
+  setNames(names(plot3.male.meta.RR.perc.b))
+plot3.male.meta.RR.perc.b <- rbind(plot3.male.meta.RR.perc.b, add.row.eye)
+
+plot3.male.meta.RR.perc.b <- plot3.male.meta.RR.perc.b[order(plot3.male.meta.RR.perc.b$GroupingTerm), ]
+
+plot3.male.meta.CVR.Vr.perc <- full_join(plot3.male.meta.CVR.perc.b, plot3.male.meta.VR.perc.b)
+overall.male.plot3.perc <- full_join(plot3.male.meta.CVR.Vr.perc, plot3.male.meta.RR.perc.b)
+
+overall.male.plot3.perc$GroupingTerm <- factor(overall.male.plot3.perc$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
+overall.male.plot3.perc$GroupingTerm <- factor(overall.male.plot3.perc$GroupingTerm, rev(levels(overall.male.plot3.perc$GroupingTerm)))
+
+```
+
+Restructure data for plotting : Male biased, 10% difference
+
+```{r}
+overall3.perc <- gather(overall.male.plot3.perc, parameter, value, c(lnCVR, lnVR, lnRR), factor_key = TRUE)
+
+lnCVR.ci <- overall3.perc %>%
+  filter(parameter == "lnCVR") %>%
+  mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
+lnVR.ci <- overall3.perc  %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
+lnRR.ci <- overall3.perc %>%
+  filter(parameter == "lnRR") %>%
+  mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
+
+overall4.male.perc <- bind_rows(lnCVR.ci,lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
+
+overall4.male.perc$label <- "Sex difference in m/f ratios > 10%"
+
+overall4.male.perc$value <- as.numeric(overall4.male.perc$value)
+overall4.male.perc$ci.low <- as.numeric(overall4.male.perc$ci.low)
+overall4.male.perc$ci.high <- as.numeric(overall4.male.perc$ci.high)
+```
+
+Plot Fig S2 all >10% difference (male bias)
+S2 B, bottom right
+
+```{r}
+
+Metameta_Fig3_male.perc <- overall4.male.perc %>% # filter(., GroupingTerm != "Hearing") %>%
+  ggplot(aes(y = GroupingTerm, x = value)) +
+  geom_errorbarh(aes(
+    xmin = ci.low,
+    xmax = ci.high
+  ),
+  height = 0.1, show.legend = FALSE
+  ) +
+  geom_point(aes(
+    shape = parameter,
+    fill = parameter
+  ),
+  color = "mediumaquamarine", size = 2.2,
+  show.legend = FALSE
+  ) +
+  scale_x_continuous(
+    limits = c(-0.2, 0.62),
+    breaks = c(0, 0.3),
+    name = "Effect size"
+  ) +
+  geom_vline(
+    xintercept = 0,
+    color = "black",
+    linetype = "dashed"
+  ) +
+  facet_grid(
+    cols = vars(parameter), rows = vars(label),
+    labeller = label_wrap_gen(width = 23),
+    scales = "free",
+    space = "free"
+  ) +
+  theme_bw() +
+  theme(
+    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
+    strip.text.x = element_blank(),
+    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
+    text = element_text(size = 14),
+    panel.spacing = unit(0.5, "lines"),
+    panel.border = element_blank(),
+    axis.line = element_line(),
+    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
+    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
+    panel.grid.minor.y = element_blank(),
+    panel.grid.minor.x = element_blank(),
+    legend.title = element_blank(),
+    axis.title.x = element_text(hjust = 0.5, size = 14),
+    axis.title.y = element_blank()
+  )
+
+# Metameta_Fig3_male.perc (Figure S2 right panel)
+```
+
+#### Female Fig S2 >10%
+
+```{r}
+
+meta.plot3.perc <- metacombo %>%
+  mutate(
+    percCVR = ifelse(lnCVR < log(9 / 10), 1, 0),
+    percVR = ifelse(lnVR < log(9 / 10), 1, 0),
+    percRR = ifelse(lnRR < log(9 / 10), 1, 0)
+  )
+
+# Significant subset for lnCVR
+metacombo_plot3.CVR.perc <- meta.plot3.perc %>%
+  filter(percCVR == 1) %>%
+  group_by(GroupingTerm) %>%
+  nest()
+
+metacombo_plot3.CVR.perc.all <- meta.plot3.perc %>%
+  filter(percCVR == 1) %>%
+  nest(data = everything())
+
+# Significant subset for lnVR
+metacombo_plot3.VR.perc <- meta.plot3.perc %>%
+  filter(percVR == 1) %>%
+  group_by(GroupingTerm) %>%
+  nest()
+
+metacombo_plot3.VR.perc.all <- meta.plot3.perc %>%
+  filter(percVR == 1) %>%
+  nest(data = everything())
+
+# Significant subset for lnRR
+metacombo_plot3.RR.perc <- meta.plot3.perc %>%
+  filter(percRR == 1) %>%
+  group_by(GroupingTerm) %>%
+  nest()
+
+metacombo_plot3.RR.perc.all <- meta.plot3.perc %>%
+  filter(percRR == 1) %>%
+  nest(data = everything())
+
+# **Final fixed effects meta-analyses within grouping terms, with SE of the estimate
+
+plot3.meta.CVR.perc <- metacombo_plot3.CVR.perc %>%
+  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+plot3.meta.VR.perc <- metacombo_plot3.VR.perc %>%
+  mutate(model_lnVR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+plot3.meta.RR.perc <- metacombo_plot3.RR.perc %>%
+  mutate(model_lnRR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+# Across all grouping terms #
+
+plot3.meta.CVR.perc.all <- metacombo_plot3.CVR.perc.all %>%
+  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+plot3.meta.CVR.perc.all <- plot3.meta.CVR.perc.all %>% mutate(GroupingTerm = "All")
+
+plot3.meta.VR.perc.all <- metacombo_plot3.VR.perc.all %>%
+  mutate(model_lnVR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+plot3.meta.VR.perc.all <- plot3.meta.VR.perc.all %>% mutate(GroupingTerm = "All")
+
+plot3.meta.RR.perc.all <- metacombo_plot3.RR.perc.all %>%
+  mutate(model_lnRR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+plot3.meta.RR.perc.all <- plot3.meta.RR.perc.all %>% mutate(GroupingTerm = "All")
+
+# Combine with separate grouping term results
+
+plot3.meta.CVR.perc <- bind_rows(plot3.meta.CVR.perc, plot3.meta.CVR.perc.all)
+plot3.meta.VR.perc <- bind_rows(plot3.meta.VR.perc, plot3.meta.VR.perc.all)
+plot3.meta.RR.perc <- bind_rows(plot3.meta.RR.perc, plot3.meta.RR.perc.all)
+
+# **Re-structure data for each grouping term; delete un-used variables: "Hearing missing for all 3 parameters"
+
+plot3.meta.CVR.perc.b <- as.data.frame(plot3.meta.CVR.perc %>% group_by(GroupingTerm) %>%
+  mutate(
+    lnCVR = map_dbl(model_lnCVR, pluck(2)), lnCVR_lower = map_dbl(model_lnCVR, pluck(6)),
+    lnCVR_upper = map_dbl(model_lnCVR, pluck(7)), lnCVR_se = map_dbl(model_lnCVR, pluck(3))
+  ))[, c(1, 4:7)]
+add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.meta.CVR.perc.b))
+plot3.meta.CVR.perc.b <- rbind(plot3.meta.CVR.perc.b, add.row.hearing)
+plot3.meta.CVR.perc.b <- plot3.meta.CVR.perc.b[order(plot3.meta.CVR.perc.b$GroupingTerm), ]
+
+plot3.meta.VR.perc.b <- as.data.frame(plot3.meta.VR.perc %>% group_by(GroupingTerm) %>%
+  mutate(
+    lnVR = map_dbl(model_lnVR, pluck(2)), lnVR_lower = map_dbl(model_lnVR, pluck(6)),
+    lnVR_upper = map_dbl(model_lnVR, pluck(7)), lnVR_se = map_dbl(model_lnVR, pluck(3))
+  ))[, c(1, 4:7)]
+add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.meta.VR.perc.b))
+plot3.meta.VR.perc.b <- rbind(plot3.meta.VR.perc.b, add.row.hearing)
+plot3.meta.VR.perc.b <- plot3.meta.VR.perc.b[order(plot3.meta.VR.perc.b$GroupingTerm), ]
+
+plot3.meta.RR.perc.b <- as.data.frame(plot3.meta.RR.perc %>% group_by(GroupingTerm) %>%
+  mutate(
+    lnRR = map_dbl(model_lnRR, pluck(2)), lnRR_lower = map_dbl(model_lnRR, pluck(6)),
+    lnRR_upper = map_dbl(model_lnRR, pluck(7)), lnRR_se = map_dbl(model_lnRR, pluck(3))
+  ))[, c(1, 4:7)]
+add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.meta.RR.perc.b))
+plot3.meta.RR.perc.b <- rbind(plot3.meta.RR.perc.b, add.row.hearing)
+add.row.hematology <- as.data.frame(t(c("Hematology", NA, NA, NA, NA))) %>%
+  setNames(names(plot3.meta.RR.perc.b))
+plot3.meta.RR.perc.b <- rbind(plot3.meta.RR.perc.b, add.row.hematology)
+
+plot3.meta.RR.perc.b <- plot3.meta.RR.perc.b[order(plot3.meta.RR.perc.b$GroupingTerm), ]
+
+plot3.meta.CVR.perc.c <- full_join(plot3.meta.CVR.perc.b, plot3.meta.VR.perc.b)
+overall.plot3.perc <- full_join(plot3.meta.CVR.perc.c, plot3.meta.RR.perc.b)
+
+overall.plot3.perc$GroupingTerm <- factor(overall.plot3.perc$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
+overall.plot3.perc$GroupingTerm <- factor(overall.plot3.perc$GroupingTerm, rev(levels(overall.plot3.perc$GroupingTerm)))
+```
+
+Restructure data for plotting
+Female bias, 10 percent difference
+
+```{r}
+overall3.perc <- gather(overall.plot3.perc, parameter, value, c(lnCVR, lnVR, lnRR), factor_key = TRUE)
+
+lnCVR.ci <- overall3.perc %>%
+  filter(parameter == "lnCVR") %>%
+  mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
+lnVR.ci <- overall3.perc  %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
+lnRR.ci <- overall3.perc %>%
+  filter(parameter == "lnRR") %>%
+  mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
+
+overall4.perc <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
+
+overall4.perc$label <- "Sex difference in m/f ratios > 10%"
+
+overall4.perc$value <- as.numeric(overall4.perc$value)
+overall4.perc$ci.low <- as.numeric(overall4.perc$ci.low)
+overall4.perc$ci.high <- as.numeric(overall4.perc$ci.high)
+```
+
+Plot FigS2 all >10% difference (female)
+Figure S2B, bottom left
+
+```{r}
+Metameta_Fig3_female.perc <- overall4.perc %>%
+  ggplot(aes(y = GroupingTerm, x = value)) +
+  geom_errorbarh(aes(
+    xmin = ci.low,
+    xmax = ci.high
+  ),
+  height = 0.1, show.legend = FALSE
+  ) +
+  geom_point(aes(shape = parameter),
+    fill = "salmon1", color = "salmon1", size = 2.2,
+    show.legend = FALSE
+  ) +
+
+  # scale_shape_manual(values =
+
+  scale_x_continuous(
+    limits = c(-0.53, 0.2),
+    breaks = c(-0.3, 0),
+    name = "Effect size"
+  ) +
+  geom_vline(
+    xintercept = 0,
+    color = "black",
+    linetype = "dashed"
+  ) +
+  facet_grid(
+    cols = vars(parameter), # rows = vars(label),
+    # labeller = label_wrap_gen(width = 23),
+    scales = "free",
+    space = "free"
+  ) +
+  theme_bw() +
+  theme(
+    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
+    strip.text.x = element_blank(),
+    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
+    text = element_text(size = 14),
+    panel.spacing = unit(0.5, "lines"),
+    panel.border = element_blank(),
+    axis.line = element_line(),
+    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
+    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
+    panel.grid.minor.y = element_blank(),
+    panel.grid.minor.x = element_blank(),
+    legend.title = element_blank(),
+    axis.title.x = element_text(hjust = 0.5, size = 14),
+    axis.title.y = element_blank()
+  )
+
+# Metameta_Fig3_female.perc (Figure 5D left panel)
+```
+MISSING
+Metameta_Fig3_female.sig Metameta_Fig3_female.sig VR!!!
+# ADDED TO TEST
+#Metameta_FigS2_male.sig (Figure S2B top right panel)
 
@@
 
+#### Plot Fig S2:   plots combined
+
+Metameta_FigS2_female.sig
+```{r}
+library(ggpubr)
+FigS2b <- ggarrange(Metameta_FigS2_female.sig, Metameta_FigS2_male.sig,
+  ncol = 2, nrow = 1, widths = c(1, 1.20), heights = c(1, 1)
+)
+
+FigS2d <- ggarrange(Metameta_Fig3_female.perc, Metameta_Fig3_male.perc,
+  ncol = 2, nrow = 1, widths = c(1, 1.20), heights = c(1, 1)
+)
+
+# end combination Figure 5
+FigS2 <- ggarrange(malebias_FigS2_sigtraits, malebias_Fig2_over10, FigS2b, FigS2d, ncol = 1, nrow = 4, heights = c(2.3, 2, 2.1, 2), labels = c("A", " ", "B", " "))
+FigS2
+```
+
+## NOT SURE WHAT THIS BELOW IS?? Felix added 11/2/2020: Ich glaube, dass das von vorher war. wenn wir alles oben haben, dann unten loeschen
+
+## Figure S2: sex-bias, including VR
+
+Prepare data for traits with effect size ratios > 10% larger in males
+
+```{r}
+meta.plotS2.over10 <- meta_clean %>%
+  select(lnCVR, lnVR, lnRR, GroupingTerm) %>%
+  arrange(GroupingTerm)
+
+meta.plotS2.over10.b <- gather(meta.plotS2.over10, trait, value, c(lnCVR, lnVR, lnRR))
+
+meta.plotS2.over10.b$trait <- factor(meta.plotS2.over10.b$trait, levels = c("lnCVR", "lnVR", "lnRR"))
+
+meta.plotS2.over10.c <- meta.plotS2.over10.b %>%
+  group_by_at(vars(trait, GroupingTerm)) %>%
+  summarise(
+    malebias = sum(value > log(11 / 10)), femalebias = sum(value < log(9 / 10)), total = malebias + femalebias,
+    malepercent = malebias * 100 / total, femalepercent = femalebias * 100 / total
+  )
+
+meta.plotS2.over10.c$label <- "Sex difference in m/f ratios > 10%"
+
+# restructure to create stacked bar plots
+
+meta.plotS2.over10.c <- as.data.frame(meta.plotS2.over10.c)
+meta.plotS2.over10.d <- gather(meta.plotS2.over10.c, key = sex, value = percent, malepercent:femalepercent, factor_key = TRUE)
+
+# create new sample size variable
+
+meta.plotS2.over10.d$samplesize <- with(meta.plotS2.over10.d, ifelse(sex == "malepercent", malebias, femalebias))
+
+# *Plot FigS2 Sex difference in m/f ratio > 10%
+malebias_FigS2_over10 <-
+  ggplot(meta.plotS2.over10.d) +
+  aes(x = GroupingTerm, y = percent, fill = sex) +
+  geom_col() +
+  geom_hline(yintercept = 50, linetype = "dashed", color = "gray40") +
+  geom_text(
+    data = subset(meta.plot2.over10.d, samplesize != 0), aes(label = samplesize), position = position_stack(vjust = .5),
+    color = "white", size = 3.5
+  ) +
+  facet_grid(
+    cols = vars(trait), rows = vars(label), labeller = label_wrap_gen(width = 18),
+    scales = "free", space = "free"
+  ) +
+  scale_fill_brewer(palette = "Set2") +
+  theme_bw(base_size = 18) +
+  theme(
+    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
+    strip.text.x = element_blank(),
+    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
+    text = element_text(size = 14),
+    panel.spacing = unit(0.5, "lines"),
+    panel.border = element_blank(),
+    axis.line = element_line(),
+    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
+    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
+    panel.grid.minor.y = element_blank(),
+    panel.grid.minor.x = element_blank(),
+    legend.position = "none",
+    axis.title.x = element_blank(),
+    axis.title.y = element_blank()
+  ) +
+  coord_flip()
+
+# malebias_FigS2_over10  #(Panel B in Fig S2 in ms)
+```
+
+#Metameta_FigS2_male.sig (Figure S2B top right panel)
+
+Restructure MALE data for plotting
+
+```{r}
+overall3.male.sigS <- gather(overall.male.plot3, parameter, value, c(lnCVR, lnVR, lnRR), factor_key = TRUE)
+
+lnCVR.ci <- overall3.male.sigS %>%
+  filter(parameter == "lnCVR") %>%
+  mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
+lnVR.ci <- overall3.male.sigS %>%
+  filter(parameter == "lnVR") %>%
+  mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
+lnRR.ci <- overall3.male.sigS %>%
+  filter(parameter == "lnRR") %>%
+  mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
+
+overall4.male.sigS <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
+
+overall4.male.sigS$label <- "CI not overlapping zero"
+```
+
+Plot FigS2 all significant results (CI not overlapping zero, male )
+
+```{r}
+Metameta_FigS2_male.sig <- overall4.male.sigS %>%
+  ggplot(aes(y = GroupingTerm, x = value)) +
+  geom_errorbarh(aes(
+    xmin = ci.low,
+    xmax = ci.high
+  ),
+  height = 0.1, show.legend = FALSE
+  ) +
+  geom_point(aes(shape = parameter),
+    fill = "mediumaquamarine", color = "mediumaquamarine", size = 2.2,
+    show.legend = FALSE
+  ) +
+  scale_x_continuous(
+    limits = c(0, 0.4),
+    breaks = c(0, 0.3),
+    name = "Effect size"
+  ) +
+  geom_vline(
+    xintercept = 0,
+    color = "black",
+    linetype = "dashed"
+  ) +
+  facet_grid(
+    cols = vars(parameter), rows = vars(label),
+    labeller = label_wrap_gen(width = 23),
+    scales = "free",
+    space = "free"
+  ) +
+  theme_bw() +
+  theme(
+    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
+    strip.text.x = element_text(size = 12),
+    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
+    text = element_text(size = 14),
+    panel.spacing = unit(0.5, "lines"),
+    panel.border = element_blank(),
+    axis.line = element_line(),
+    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
+    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
+    panel.grid.minor.y = element_blank(),
+    panel.grid.minor.x = element_blank(),
+    legend.title = element_blank(),
+    axis.title.x = element_blank(),
+    axis.title.y = element_blank()
+  )
+
+# Metameta_FigS2_male.sig
+```
+
 ### 10 % Perc sex difference, male bias

### 2020-04-20 Prep & old/FZ 10-12-2019.R

@@ -1,0 +1,3144 @@
+---
+title: "IMPC Mouse data - Variance in sex differences"
+author: "Susanne Zajitschek,  Felix Zajitschek, Russell Bonduriansky,Robert  Brooks, Will Cornwell, Daniel Falster, Malgortaza Lagisz, Jeremy Mason, Daniel Noble, Alistair Senior & Shinichi Nakagawa"
+date: "August 2019"
+output:
+  html_document:
+    code_download: true
+    code_folding: hide
+    depth: 4
+    number_sections: no
+    theme:  flatly
+    toc: yes
+    toc_depth: 4
+    toc_float: yes
+  html_notebook:
+    toc: yes
+  pdf_document:
+    toc: yes
+    toc_depth: '4'
+subtitle: Electronic Supplementary Material
+---
+
+# Set-up
+
+## Load packages & functions
+
+
+```{r, include=FALSE}
+knitr::opts_chunk$set(
+  echo = TRUE,
+  warning = FALSE,
+  message = FALSE,
+  cache = TRUE,
+  tidy = TRUE
+)
+
+```
+
+```{r}
+library(readr)
+library(dplyr)
+library(metafor)
+library(devtools)
+library(purrr)
+library(tidyverse)
+library(tibble)
+library(kableExtra)
+library(robumeta)
+library(ggpubr)
+library(ggplot2)
+library(here)
+```
+
+Functions for preparing the data for meta analyses
+
+1) "Population statistics"
+
+```{r}
+calculate_population_stats <- function(mydata, min_individuals = 5) {
+  mydata %>%
+    group_by(population, strain_name, production_center, sex) %>%
+    summarise(
+      trait = parameter_name[1],
+      x_bar = mean(data_point),
+      x_sd = sd(data_point),
+      n_ind = n()
+    ) %>%
+    ungroup() %>%
+    filter(n_ind > min_individuals) %>%
+    # Check both sexes present & filter those missing
+    group_by(population) %>%
+    mutate(
+      n_sex = n_distinct(sex)
+    ) %>%
+    ungroup() %>%
+    filter(n_sex == 2) %>%
+    select(-n_sex) %>%
+    arrange(production_center, strain_name, population, sex)
+}
+```
+
+2) Extraction of effect sizes and sample variances
+
+```{r}
+create_meta_analysis_effect_sizes <- function(mydata) {
[…]

### 2020-04-20 Prep & old/FZ 30-12-2019.R

@@ -1,0 +1,3154 @@
+---
+title: "IMPC Mouse data - Variance in sex differences"
+author: "Susanne Zajitschek,  Felix Zajitschek, Russell Bonduriansky,Robert  Brooks, Will Cornwell, Daniel Falster, Malgortaza Lagisz, Jeremy Mason, Daniel Noble, Alistair Senior & Shinichi Nakagawa"
+date: "August 2019"
+output:
+  html_document:
+    code_download: true
+    code_folding: hide
+    depth: 4
+    number_sections: no
+    theme:  flatly
+    toc: yes
+    toc_depth: 4
+    toc_float: yes
+  html_notebook:
+    toc: yes
+  pdf_document:
+    toc: yes
+    toc_depth: '4'
+subtitle: Electronic Supplementary Material
+---
+
+# Set-up
+
+## Load packages & functions
+
+
+```{r, include=FALSE}
+knitr::opts_chunk$set(
+  echo = TRUE,
+  warning = FALSE,
+  message = FALSE,
+  cache = TRUE,
+  tidy = TRUE
+)
+
+```
+
+```{r}
+library(readr)
+library(dplyr)
+library(metafor)
+library(devtools)
+library(purrr)
+library(tidyverse)
+library(tibble)
+library(kableExtra)
+library(robumeta)
+library(ggpubr)
+library(ggplot2)
+library(here)
+```
+
+Functions for preparing the data for meta analyses
+
+1) "Population statistics"
+
+```{r}
+calculate_population_stats <- function(mydata, min_individuals = 5) {
+  mydata %>%
+    group_by(population, strain_name, production_center, sex) %>%
+    summarise(
+      trait = parameter_name[1],
+      x_bar = mean(data_point),
+      x_sd = sd(data_point),
+      n_ind = n()
+    ) %>%
+    ungroup() %>%
+    filter(n_ind > min_individuals) %>%
+    # Check both sexes present & filter those missing
+    group_by(population) %>%
+    mutate(
+      n_sex = n_distinct(sex)
+    ) %>%
+    ungroup() %>%
+    filter(n_sex == 2) %>%
+    select(-n_sex) %>%
+    arrange(production_center, strain_name, population, sex)
+}
+```
+
+2) Extraction of effect sizes and sample variances
+
+```{r}
+create_meta_analysis_effect_sizes <- function(mydata) {
[…]

### 2020-04-20 Prep & old/SydneySexDiff_Felix.R

@@ -1,0 +1,3056 @@
+---
+title: "IMPC Mouse data - Variance in sex differences"
+author: "Susanne Zajitschek,  Felix Zajitschek, Russell Bonduriansky,Robert  Brooks, Will Cornwell, Daniel Falster, Malgortaza Lagisz, Jeremy Mason, Daniel Noble, Alistair Senior & Shinichi Nakagawa"
+date: "August 2019"
+output:
+  html_document:
+    code_download: true
+    code_folding: hide
+    depth: 4
+    number_sections: no
+    theme:  flatly
+    toc: yes
+    toc_depth: 4
+    toc_float: yes
+  html_notebook:
+    toc: yes
+  pdf_document:
+    toc: yes
+    toc_depth: '4'
+subtitle: Electronic Supplementary Material
+---
+
+# Set-up
+
+## Loading packages & custom functions
+
+```{r, include=FALSE}
+knitr::opts_chunk$set(
+  echo = TRUE,
+  warning = FALSE,
+  message = FALSE,
+  cache = TRUE,
+  tidy = TRUE
+)
+```
+
+```{r}
+library(readr)
+library(dplyr)
+library(metafor)
+library(devtools)
+library(purrr)
+library(tidyverse)
+library(tidyr)
+library(tibble)
+library(kableExtra)
+library(robumeta)
+library(ggpubr)
+library(ggplot2)
+library(here)
+```
+
+Functions for preparing the data for meta analyses
+
+1) Create function for sub-setting the data to choose only one data point per individual per trait: "data_subset_parameterid_individual_by_age"
+
+```{r}
+data_subset_parameterid_individual_by_age <- function(mydata, parameter, age_min=0, age_center=100) {
+  tmp <- mydata %>%
+    filter(
+      age_in_days >= age_min,
+      id == parameter
+    ) %>%
+    # take results for single individual closest to age_center
+    mutate(age_diff = abs(age_center - age_in_days)) %>%
+    group_by(biological_sample_id) %>%
+    filter(age_diff == min(age_diff)) %>%
+    select(-age_diff)# %>% 
+#    filter(!duplicated(biological_sample_id))
+    
+  # still some individuals with multiple records (because same individual appear under different procedures, so filter to one record)
+  j <- match(unique(tmp$biological_sample_id), tmp$biological_sample_id)
+  tmp[j, ] 
+  }
+```
+
+2) "Population statistics": "calculate_population_stats"
[…]

### 2020-04-20 scripts/MouseSexDiffFeb20_2020.Rmd
Add files via upload

--- 2020-04-20 Prep & old/SydneySexDiff_Felix_11-2-2020TEST.Rmd
@@
 ---
-title: "IMPC Mouse data - Variance in sex differences"
-author: "Susanne Zajitschek,  Felix Zajitschek, Russell Bonduriansky,Robert  Brooks, Will Cornwell, Daniel Falster, Malgortaza Lagisz, Jeremy Mason, Daniel Noble, Alistair Senior & Shinichi Nakagawa"
-date: "August 2019"
+title: "Sex and Power: sexual dimorphism in trait variability and its eco-evolutionary and statistical implications"
+author: Susanne Zajitschek,  Felix Zajitschek, Russell Bonduriansky,Robert  Brooks,
+  Will Cornwell, Daniel Falster, Malgortaza Lagisz, Jeremy Mason, Daniel Noble, Alistair
+  Senior & Shinichi Nakagawa
+date: "March 2020"
 output:
   html_document:
-    code_download: true
+    code_download: yes
     code_folding: hide
@@
     toc: yes
+  word_document:
+    toc: yes
+    toc_depth: '4'
   pdf_document:
@@
 subtitle: Electronic Supplementary Material
+always_allow_html: yes
 ---
@@
 library(here)
+# additional packages for intergating male / female symbols in plot 4
+library(png)
+library(grid)
 ```
@@
     select(-age_diff)# %>%
-#    filter(!duplicated(biological_sample_id))  #Felix 6/2/2020: this line can be deleted
 
@@
 saveRDS(data, "export/data_clean.rds")
-```
-
-For analysis we load the RDS created above and other datasets:
-
+
+```
+
+For analysis we load the RDS created above and other datasets
 ```{r load}
@@
 
-Checking length of different variables and sample sizes.
-
-### Table 1:  "Strains and Center Sample Sizes"
+### Supplemental Table 1: "Strains and Center Sample Sizes"
 This table summarises the available numbers of male and female mice from each strain and originating institution.
 
-```{r echo = FALSE, results = 'hold'}
-#length(unique(data$parameter_name)) # 232 traits
-#length(unique(data$parameter_group)) # 161 parameter groups
-#length(unique(data$procedure_name)) # 26 procedure groups
-#length(unique(data$biological_sample_id)) # 27147 individial mice
-
-#number of males and females per strain per production center 
-kable(cbind(data %>% group_by(production_center, strain_name) %>% count(biological_sample_id, sex) %>% count(sex) %>% print(n = Inf))) %>%
+```{r include=FALSE}
+# Initial checks
+length(unique(data$parameter_name)) # 232 traits
+length(unique(data$parameter_group)) # 161 parameter groups
+length(unique(data$procedure_name)) # 26 procedure groups
+length(unique(data$biological_sample_id)) # 27147 individial mice  
+# To show a table with number of males and females per strain per production center:
+
+ST1 <- (cbind(data %>% group_by(production_center, strain_name) %>% count(biological_sample_id, sex) %>% count(sex) %>% print(n = Inf))) 
+```
+
+```{r}
+
+kable(ST1) %>%
   kable_styling() %>%
-  scroll_box(width = "70%", height = "200px")
-
-## SZ: I don't understand why the tibble is showing in the knitted html
+  scroll_box(width = "60%", height = "200px")
+
 ```
@@
 #(n <- length(unique(results_alltraits_grouping2$parameter_name))) # 232
-```
 
@@
 
-14 traits from the originally 232 that had been included are removed because they either did not achieve convergence or are nonsensical for analysis of variance (such as traits that show no variation, see list below).
-
-Not converged: "dp t cells", "mzb (cd21/35 high)"
-
-Not enough variation: "number of caudal vertebrae", "number of cervical vertebrae", "number of digits", "number of lumbar vertebrae", "number of pelvic vertebrae", "number of ribs left","number of ribs right", "number of signals", "number of thoracic vertebrae", "total number of acquired events in panel a","total number of acquired events in panel b", "whole arena permanence".
-
-```{r}
 # We exclude 14 parameter names for which metafor models didn't converge ("dp t cells", "mzb (cd21/35 high)"), and of parameters that don't harbour enough variation
@@
 ```
+ 14 traits from the originally 232 that had been included are removed because they either did not achieve convergence or are nonsensical for analysis of variance (such as traits that show no variation, see list below).
+
+Not converged: "dp t cells", "mzb (cd21/35 high)"
+
+Not enough variation: "number of caudal vertebrae", "number of cervical vertebrae", "number of digits", "number of lumbar vertebrae", "number of pelvic vertebrae", "number of ribs left","number of ribs right", "number of signals", "number of thoracic vertebrae", "total number of acquired events in panel a","total number of acquired events in panel b", "whole arena permanence".
 
@@
 #### Collapsing and merging correlated parameters
-
-Here we double check numbers of trait parameters in the dataset
-
-```{r}
-
-meta1 <- meta_clean 
-length(unique(meta1$procedure)) #18
-length(unique(meta1$GroupingTerm)) #9
-length(unique(meta1$parameter_group)) # 148 levels.
-To be used as grouping factor for meta-meta-analysis / collapsing down based on things that are classified identically in "parameter_group" but have different "parameter_name"
-length(unique(meta1$parameter_name)) #218
-```
-
-#### Count of number of parameter names (correlated sub-traits) in each parameter group (par_group_size)
-
-### Table 2: Numbers of correlated and uncorrelated traits
+Count of number of parameter names (correlated sub-traits) in each parameter group (par_group_size)
+
+### Supplemental Table 2: "Numbers of correlated and uncorrelated traits"
 This serves to identify and separate the traits that are correlated from the full dataset that can be processed as is.
@@
 ```{r}
-kable(cbind(meta1 %>% count(parameter_group))) %>%
-  kable_styling() %>%
-  scroll_box(width = "60%", height = "200px")
-```
-
-```{r}
+# Here we double check numbers of trait parameters in the dataset
+meta1 <- meta_clean 
+# length(unique(meta1$procedure)) #18
+# length(unique(meta1$GroupingTerm)) #9
+# length(unique(meta1$parameter_group)) # 148 levels.
+To be used as grouping factor for meta-meta-analysis / collapsing down based on things that are classified identically in "parameter_group" but have different "parameter_name"
+# length(unique(meta1$parameter_name)) #218
+# and prepare the dataset for second-order meta-analysis
 meta1_sub <- meta1 %>%
@@
   filter(par_group_size > 1) # 90 observations
+
+# Table detailing numbers of correlated and uncorrelated traits
+kable(cbind(meta1 %>% count(parameter_group))) %>%
+  kable_styling() %>%
+  scroll_box(width = "60%", height = "200px")
+
 ```
@@
   )
-```
 
 #### Extracting and save parameter estimates
-Here we apply an additional Function to collect the outcomes of the 'mini-meta-analysis' that has ondensed our non-independent traits.
-
-```{r}
+# Here we apply an additional Function to collect the outcomes of the 'mini-meta-analysis' that has ondensed our non-independent traits.
+Values from our second-order meta-analysis using robu-meta are extracted
+
 count_fun <- function(mod_sub) {
@@
 } # estimate, lower ci, upper ci, SE
-```
-
-Extraction of values created during meta-analyses using robumeta
-
-```{r}
+
+# Extraction of values created during meta-analyses using robumeta
+
 robusub_RR <- model_count %>%
@@
 robu_all <- full_join(robusub_CVR, robusub_VR) %>% full_join(., robusub_RR)
-```
 
 #### Combining data 
-Merge the two data sets (the new [robu_all] and the initial [uncorrelated sub-traits with count = 1])
-
-```{r}
+# Merge the two data sets (the new [robu_all] and the initial [uncorrelated sub-traits with count = 1])
+
 meta_all <- meta1 %>%
@@
 
-```
-
-Clean-up, reorder, and rename
-
-```{r}
+# Clean-up, reorder, and rename
+
 metacombo <- metacombo[c("parameter_group", "counts","procedure2","GroupingTerm2", "lnCVR","lnCVR_lower","lnCVR_upper","lnCVR_se","lnVR","lnVR_lower","lnVR_upper","lnVR_se","lnRR","lnRR_lower","lnRR_upper","lnRR_se")]
@@
 names(metacombo)[names(metacombo)=="GroupingTerm2"] <- "GroupingTerm" 
-
+```
+
+```{r include=FALSE}
 # Quick pre-check before doing plots
@@
 
-### Table 3: Full corrected dataset
+### Supplemental Table 3: "Meta-analysis results"
 
@@
 
-This is the full result dataset
 ```{r}
@@
 
-# trait_meta_results <- write.csv(metacombo, file = "export/trait_meta_results.csv")  #Felix 7/2/2020: I think this can be deleted for publication!
 ```
@@
 
-# **Final fixed effects meta-analyses within grouping terms, with SE of the estimate
+# Final fixed effects meta-analyses within grouping terms, with SE of the estimate
 
@@
 
-# **Final fixed effects meta-analyses ACROSS grouping terms, with SE of the estimate
+# Final fixed effects meta-analyses ACROSS grouping terms, with SE of the estimate
 
@@
 # Visualisation
-## Figure 4 
-#### Preparation for plots: Count data, based on First-order metamanalysis results
+## Preparation for Figure 4 
+#### Count data, based on First-order meta-analysis results
 This includes all separate eligible traits.
-Re-ordering of grouping terms
+Re-ordering of grouping terms. 
+Preparation of subplot 4A
 
@@
 
-kable(cbind(overall4, overall4)) %>%
-  kable_styling() %>%
-  scroll_box(width = "100%", height = "200px")
-```
-
-```{r}
+####  PLOT 4B
+
+#adding male / female symbols for Figure 4B
+
+male <- readPNG(here("images", "MaleAqua.png"))
+female <- readPNG(here("images", "FemaleSalmon.png"))
+
 Metameta_Fig3_alltraits <- overall4 %>%
@@
     axis.title.x = element_text(hjust = 0.5, size = 14),
-    axis.title.y = element_blank()
-  )
+    axis.title.y = element_blank()) +
+  # addition of male & female symols
+  annotation_custom(rasterGrob(female), xmin = - 0.2, xmax = -0.1, ymin = 2.3, ymax = 4) +
+  annotation_custom(rasterGrob(male), xmin = 0.1, xmax = 0.2, ymin = 2.3, ymax = 4)
 
@@
 
-### Fig 4 # SZ STILL TO DO
-Join the different parts and  #TO DO!! add M / F symbols in Metameta_Fig3_alltraits 
-```{r}
-#Test
-#male <- readPNG(system.file("img", "male"))
-#test <- Metameta_Fig3_alltraits
-
-#library(png)
-```
-
 ### Figure 4
+
 Panel A shows the numbers of traits across functional groups that are either male-biased (blue-green) or female-biased (orange-red), as calculated in Step D (figure 3).
@@
 Both panels represent results evaluated across all traits (Phase 3, Figure 3).
-Traits that are male biased is shown in blue, whereas female bias data is represented in orange.
+Traits that are male biased are shown in blue, whereas female bias data is represented in orange.
 
@@
 
-## Figure 5
+## Preparation for Figure 5: Sex bias.
 #### Preparing data for traits with CI not overlapping 0
@@
   coord_flip()
-```
 
@@
 #### Figure 5 B - traits with CI not overlapping 0 
-Prepare data 
-create column with 1= different from zero, 0= zero included in CI
-#### Male-biased (significant) traits
-
-```{r}
+# Prepare data 
+# create column with 1= different from zero, 0= zero included in CI
+
+#### Male-biased (significant) traits:
+
 meta.male.plot3.sig <- metacombo %>%
@@
   filter(sigCVR == 1) %>%
-  nest(data = everything())    #Felix added 'data = everything()' on 4/2/2020
+  nest(data = everything())
 
@@
 # str(overall.male.plot3)
-```
-
-Restructure MALE data for plotting
-
-```{r}
+
+# Restructure MALE data for plotting
+
 overall3.male.sig <- gather(overall.male.plot3, parameter, value, c(lnCVR, lnRR), factor_key = TRUE)
@@
 overall4.male.sig$label <- "CI not overlapping zero"
-```
-
-Plot Fig 5B all significant results (CI not overlapping zero) for males. This is the right panel in Figure 5B.
-
-```{r}
+
+# Plot Fig 5B all significant results (CI not overlapping zero) for males. This is the right panel in Figure 5B.
 
@@
 # Metameta_Fig3_male.sig
-```
-
-#### Female part, significant traits
-Female Fig5B sig
-
-Prepare data for traits with CI not overlapping 0
-create column with 1= different from zero, 0= zero included in CI
-
-```{r}
+
+#### Female part, significant traits: Female Fig5B sig
+
+# as above: Prepare data for traits with CI not overlapping 0
+# create column with 1= different from zero, 0= zero included in CI
 
@@
 
-#Felix added 7/2/2020: metacombo_female.plot3.RR[4,2][[1]] [[1]]$lnRR_upper; #only two data points: -0.12377263 -0.01553462; should probably be excluded?!
-
 metacombo_female.plot3.RR.all <- meta.female.plot3.sig %>%
@@
 
-# **Re-structure data for each grouping term; delete un-used variables
+# Re-structure data for each grouping term; delete un-used variables
 
@@
 
-```
-
-Re-structure data for plotting
-
-```{r}
+# Re-structuring data for plotting
+
 overall3.female.sig <- gather(overall.female.plot3, parameter, value, c(lnCVR, lnRR), factor_key = TRUE)
@@
 
-```
-
-Plotting Fig5B all significant results (CI not overlapping zero, female )
-
-```{r}
+# PLOT preparation for Fig5B: all significant results (CI not overlapping zero, female )
 
@@
 ```
-## JOIN!!! CODE MISSING??
-malebias_Fig2_sigtraits
-Metameta_Fig3_female.sig #(Figure 5B left panel)
-Metameta_Fig3_male.sig
+
+####  Figure 5
+Sex biases in trait values across trait groups (Step J in Figure 3).
+The panels in A show differences in the number of affected traits, in variance (lnCVR) and means (lnRR), where there is a significant difference between the sexes (i.e CI not overlapping zero).
+Panel B shows results for the sex bias in those traits that differ between the sexes (second-order meta-analysis).
+Triangles represent sex bias in means (response ratio) and black circles differences in the coefficient of variation ratio (mean-adjusted variability).
+The orange-red bars represent trait groups with a female bias, blue-green bars male-biased traits.
+
 ```{r}
+#Joining the Parts:
+
   Fig5B <- ggarrange(Metameta_Fig3_female.sig, Metameta_Fig3_male.sig,
@@
 
+The supplemental figures include lnVR (in addition to lnCVR and lnRR, as presented in Figures 4 and 5)
 ```{r}
@@
 # malebias_FigS1_alltraits     #(panel A in Figure S1)
-```
 
 ###  Overall results of second order meta analysis, INCLUDING VR
-#### Re-structure data for plotting 
-Restructure MALE data for plotting
-
-```{r}
+#### Re-structure MALE data for plotting
+
 overall3.male.sigS <- gather(overall.male.plot3, parameter, value, c(lnCVR, lnVR, lnRR), factor_key = TRUE)
@@
 overall4S$label <- "All traits"
-```
 
 #### Preparation for plot, including lnVR
-Preparation: Sub-Plot  for Figure S1: all traits (S1 B)
-
-```{r}
+# Sub-Plot  for Figure S1: all traits (S1 B)
+
 Metameta_FigS1_alltraits <- overall4S %>%
@@
 However, in the initial meta-analysis we extract sigma^2 and errors for mouse strains and centers (Institutions).
+As above a Loop is run and parameters extracted from metafor (sigma2's, s.nlevels)
 
@@
 
-```
-
-LOOP
-Parameters to extract from metafor (sigma2's, s.nlevels)
-
-```{r}
+#Loop
 
@@
 
-#### Exclude traits without variation between mouse strains; merge datasets  #Felix added 6/2/2020
+Exclude traits without variation between mouse strains
+Merge data sets containing metafor results with procedure etc. names. Dealing with correlated parameters, and running of second -order meta-analysis for  heterogeneity data.
 
@@
 results.allhetero.grouping2 <- results.allhetero.grouping[results.allhetero.grouping$s.nlevels.strain.VR != 0, ]
-# nrow(results.allhetero.grouping) #223  Felix 7/2/2020 added: not sure. Run again and it was 232?!
-```
-
-Merge data sets containing metafor results with procedure etc. names
-
-```{r}
+# nrow(results.allhetero.grouping) #232
+
+# Merging dataset with correct procedure names
 # procedures <- read.csv(here("export", "procedures.csv"))
@@
 results.allhetero.grouping2$parameter_name <- data$parameter_name[match(results.allhetero.grouping2$id, data$id)]
-```
-
-#### Correlated parameters
-
-```{r}
+
+#We deal with correlated parameters following the procedures described above (extraction of effects sizes).
+
 metahetero1 <- results.allhetero.grouping2
@@
 metahetero1_sub <- subset(metahetero1, par_group_size > 1) # 92 observations
-# str(metahetero1_sub)
-# metahetero1_sub$sampleSize <- as.numeric(metahetero1_sub$sampleSize) #from previous analysis? don't think is used: : delete in final version
 
@@
   group_by(parameter_group) %>%
-  # mutate(raw_N = sum(sampleSize)) %>%  #Felix added: don't think is necessary: delete in final version
   nest()
@@
 
-# Robumeta object details:
-# str(model_count.$model_lnCVR[[1]])
-
-## *Perform meta-analyses on correlated sub-traits, using robumeta
- # Susi / FELIX: what's this below?
-# Shinichi: We think we want to use these for further analyses:
-# residual variance: as.numeric(robu_fit$mod_info$term1)     (same as 'mod_info$tau.sq')
-# sample size: robu_fit$N
-
-## **Extract and save parameter estimates
-
-# Felix: doesn't work , error message:
-#!!!!!!!!!!! ERROR!!!!!!!!!!!!!!!!!!!!
-#Error: Column `parameter_group` can't be modified because it's a grouping variable
+# Robumeta object details:  str(model_count.$model_lnCVR[[1]])
+
+# Perform meta-analyses on correlated sub-traits, using robumeta
+# Extract and save parameter estimates
 
@@
 robusub_RR. <- model_count. %>%
-  transmute(estimatelnRR = map(model_lnRR, count_fun.)) %>%    #Felix 4/2/2020: deleted: 'parameter_group' (in brackets, after 'transmute')
+  transmute(estimatelnRR = map(model_lnRR, count_fun.)) %>%    
   mutate(r = map(estimatelnRR, ~ data.frame(t(.)))) %>%
@@
 robu_all. <- full_join(robusub_CVR., robusub_VR.) %>% full_join(., robusub_RR.)
-```
-
-Merge the two data sets (the new [robu_all.] and the initial [uncorrelated sub-traits with count = 1])
-
-In this step, we 	
-1) merge the N from robumeta and the  N from metafor (s.nlevels.error) together into the same columns (N.RR, N.VR, N.CVR)
-2) calculate the total variance for metafor models as the sum of random effect variances and the residual error, then add in the same columns together with the residual variances from robumeta
-
-```{r}
+
+#Merge the two data sets (the new [robu_all.] and the initial [uncorrelated sub-traits with count = 1])
+
+#In this step, we 	1) merge the N from robumeta and the  N from metafor (s.nlevels.error) together into the same columns (N.RR, N.VR, N.CVR)
+
+# 2) calculate the total variance for metafor models as the sum of random effect variances and the residual error, then add in the same columns together with the residual variances from robumeta
+
 metahetero_all <- metahetero1 %>%
@@
 metahetero_all <- metahetero_all %>% mutate(
-  var.RR = if_else(var.RR == -Inf, -7, var.RR),   #Felix commented 6/2/2020: can't remmeber, why -7, -6, -5 in this section!
+  var.RR = if_else(var.RR == -Inf, -7, var.RR),   # numbers chosen as limits; based on the values in the dataset
   var.VR = if_else(var.VR == -Inf, -5, var.VR),
@@
 
-# **Combine data
-## Step1
+# Combine data
+# Step1
+
 combinedmetahetero <- bind_rows(robu_all., metahetero_all)
@@
 
-metacombohetero <- metacombohetero %>% select(parameter_group, var.CVR, N.CVR, var.VR, N.VR, var.RR, N.RR, counts, procedure = procedure2, GroupingTerm = GroupingTerm2)  #Felix changed 6/2/2020: was: c(1:7, 43:45, and 2 renaming lines)
-
-```
+metacombohetero <- metacombohetero %>% select(parameter_group, var.CVR, N.CVR, var.VR, N.VR, var.RR, N.RR, counts, procedure = procedure2, GroupingTerm = GroupingTerm2)
+
+# Invidual table for heterogeneity across all traits
+# kable(metacombohetero) %>%
+ # kable_styling() %>%
+  #scroll_box(width = "100%", height = "200px")
 
@@
 
-```{r}
 ## Perform meta-meta-analysis (3 for each of the 9 grouping terms: var.CVR, var.VR, var.RR)
@@
 # str(heterog2)
-```
-
-#### Heterogeneity PLOT
-Restructure data for plotting
-
-```{r}
+
+#### Preparation of the Heterogeneity PLOT
+
+#Restructure data for plotting
+
 heterog3 <- gather(heterog2, parameter, value, c(heteroCVR, heteroVR, heteroRR), factor_key = TRUE)
@@
 # write.csv(heterog4, "heterog4.csv")
-```
 
@@
 
-```{r}
 heterog5 <- heterog4
@@
   )
-
-#HeteroS1
-
-```
-
-#### Combined Figure S1: overall Count data, Meta anlysis results, Heterogeneity)
-
+```
+
+## Heterogeneity Table and Plot
+### Supplemental Table 4: "Heterogeneity within groups"
+ SZ: missing a desciption so far.
 ```{r}
+kable(heterog6) %>%
+  kable_styling() %>%
+  scroll_box(width = "100%", height = "200px")
+```
+
+### Figure S1
+
+Similar to Figure 4 in the main article, this figure shows the numbers of either male (blue-green bars) or female (orange-red bars) biased traits  (Panel A) across functional groups, this time for lnCVR (left hand side), lnVR (middle) and lnRR (right hand side).
+Panel B shows effect sizes from separate meta-analysis for each functional group, and Panel C contains results of heterogeneity analyses.
+All three panels represent results evaluated across all traits (Phase 3, Figure 3).
+
+```{r}
+#### Combined Figure S1: overall Count data, Meta anlysis results, Heterogeneity
+
 FigS1 <- ggarrange(malebias_FigS1_alltraits + xlab("percentage sex bias"), Metameta_FigS1_alltraits, HeteroS1, nrow = 3, align = "v", heights = c(1, 1, 1), labels = c("A", "B", "C"))
 FigS1
-# ggsave("FigS1_OverallResults.pdf", plot = Fig4, width = 6, height = 5)
-```
-
-## Figure S2
-
-Plot FigS2 all significant results (CI not overlapping zero) for males
-### FELIX:  "ALL" missing. Felix added 11/2/2020: done
+#ggsave("FigS1_OverallResults.pdf", plot = FigS1, width = 6, height = 7)
+```
+
+### Preparations for Figure S2 A
+This Figure extends Figure 4, as it includes results not only for lnCVR and lnRR but also lnCVR.
+In addition, we compare two different assessments of sex-bias, significance (CI not overlapping zero) and sex differences in male / female ratios > 10%
 ```{r}
+# Plot FigS2 all significant results (CI not overlapping zero) for males, count data
+
 meta.plot2.sig.bS <- meta.plot2.sig[, c("lnCVR", "lnVR", "lnRR", "lnCVRsig", "lnVRsig", "lnRRsig", "GroupingTerm")]
@@
 # malebias_FigS2_sigtraits # this is Figure S2 A
-```
-### Prepare data for traits with effect size ratios > 10% larger in males, supplemental Figure S2
-### FELIX:  "ALL" missing. Felix added 11/2/2020: done
-This Figure extends Figure 4, as it includes results not only for lnCVR and lnRR but also lnCVR.
-In addition, we compare two different assessments of sex-bias, significance (CI not overlapping zero) and sex differences in male / female ratios > 10%
-
-### Over 10% male bias, count data (first- order metanalysis) 
-```{r}
+
+#Prepare data for traits with effect size ratios > 10% larger in males, supplemental Figure S2
+
+#### Over 10% male bias, count data (first- order metanalysis)
+
 meta.plot2.over10 <- meta_clean %>%
@@
 
-# *Plot Fig2 Sex difference in m/f ratio > 10%
+# PLOT:  Fig2 Sex difference in m/f ratio > 10% (Fig S2 A, lower panel)
+
 malebias_Fig2_over10 <-
@@
 
-# malebias_Fig2_over10  (supplemental Figure S2)
-```
-
-#### Fig S2, second-order meta-analysis, male traits
-#### Female Figure, significant traits
-Female FigS2 B sig
-
-Prepare data for traits with CI not overlapping 0
-create column with 1= different from zero, 0= zero included in CI
-
-Restructure data for plotting
-
+# malebias_Fig2_over10  (supplemental Figure S2 A)
+```
+
+### Preparation for Figure S2 B (second-order meta-analysis)
+#### Female Figure, significant and highly biased traits (Figure S2 B, left hand side panels)
+Preparing data for traits with CI not overlapping 0: 
+create column with 1= different from zero, 0= zero included in CI (for Figure S2 B, top left panel)
 ```{r}
+#Restructure data for plotting
+
 overall3.female.sigS <- gather(overall.female.plot3, parameter, value, c(lnCVR, lnVR, lnRR), factor_key = TRUE)
@@
 
-##
+# PLOT female-bias:  significant traits
 
@@
 # Metameta_FigS2_female.sig
-```
-
-Prepare data for traits with m/f difference > 10%
-
-Create column with 1= larger, 0= difference not larger than 10% between male/female ratios
-```{r}
-meta.male.plot3.perc <- metacombo %>%
-  mutate(
-    percCVR = ifelse(lnCVR > log(11 / 10), 1, 0),
-    percVR = ifelse(lnVR > log(11 / 10), 1, 0),
-    percRR = ifelse(lnRR > log(11 / 10), 1, 0)
+
+#### Prepare data for traits with m/f difference > 10%, Female bias (Figure S2 B, bottom left)
+
+meta.plot3.perc <- metacombo %>%
+  mutate(
+    percCVR = ifelse(lnCVR < log(9 / 10), 1, 0),
+    percVR = ifelse(lnVR < log(9 / 10), 1, 0),
+    percRR = ifelse(lnRR < log(9 / 10), 1, 0)
   )
@@
 # Significant subset for lnCVR
-metacombo_male.plot3.CVR.perc <- meta.male.plot3.perc %>%
+metacombo_plot3.CVR.perc <- meta.plot3.perc %>%
   filter(percCVR == 1) %>%
@@
 
-metacombo_male.plot3.CVR.perc.all <- meta.male.plot3.perc %>%
+metacombo_plot3.CVR.perc.all <- meta.plot3.perc %>%
   filter(percCVR == 1) %>%
@@
 # Significant subset for lnVR
-metacombo_male.plot3.VR.perc <- meta.male.plot3.perc %>%
+metacombo_plot3.VR.perc <- meta.plot3.perc %>%
   filter(percVR == 1) %>%
@@
 
-metacombo_male.plot3.VR.perc.all <- meta.male.plot3.perc %>%
+metacombo_plot3.VR.perc.all <- meta.plot3.perc %>%
   filter(percVR == 1) %>%
@@
 # Significant subset for lnRR
-metacombo_male.plot3.RR.perc <- meta.male.plot3.perc %>%
+metacombo_plot3.RR.perc <- meta.plot3.perc %>%
   filter(percRR == 1) %>%
@@
 
-metacombo_male.plot3.RR.perc.all <- meta.male.plot3.perc %>%
+metacombo_plot3.RR.perc.all <- meta.plot3.perc %>%
   filter(percRR == 1) %>%
@@
 
-# **Final fixed effects meta-analyses within grouping terms and across grouping terms, with SE of the estimate
-
-plot3.male.meta.CVR.perc <- metacombo_male.plot3.CVR.perc %>%
+# **Final fixed effects meta-analyses within grouping terms, with SE of the estimate
+
+plot3.meta.CVR.perc <- metacombo_plot3.CVR.perc %>%
   mutate(model_lnCVR = map(data, ~ metafor::rma.uni(
@@
 
-plot3.male.meta.VR.perc <- metacombo_male.plot3.VR.perc %>%
+plot3.meta.VR.perc <- metacombo_plot3.VR.perc %>%
   mutate(model_lnVR = map(data, ~ metafor::rma.uni(
@@
 
-plot3.male.meta.RR.perc <- metacombo_male.plot3.RR.perc %>%
+plot3.meta.RR.perc <- metacombo_plot3.RR.perc %>%
   mutate(model_lnRR = map(data, ~ metafor::rma.uni(
@@
 
-plot3.male.meta.CVR.perc.all <- metacombo_male.plot3.CVR.perc.all %>%
+plot3.meta.CVR.perc.all <- metacombo_plot3.CVR.perc.all %>%
   mutate(model_lnCVR = map(data, ~ metafor::rma.uni(
@@
 
-plot3.male.meta.CVR.perc.all <- plot3.male.meta.CVR.perc.all %>% mutate(GroupingTerm = "All")
-
-plot3.male.meta.VR.perc.all <- metacombo_male.plot3.VR.perc.all %>%
+plot3.meta.CVR.perc.all <- plot3.meta.CVR.perc.all %>% mutate(GroupingTerm = "All")
+
+plot3.meta.VR.perc.all <- metacombo_plot3.VR.perc.all %>%
   mutate(model_lnVR = map(data, ~ metafor::rma.uni(
@@
 
-plot3.male.meta.VR.perc.all <- plot3.male.meta.VR.perc.all %>% mutate(GroupingTerm = "All")
-
-plot3.male.meta.RR.perc.all <- metacombo_male.plot3.RR.perc.all %>%
+plot3.meta.VR.perc.all <- plot3.meta.VR.perc.all %>% mutate(GroupingTerm = "All")
+
+plot3.meta.RR.perc.all <- metacombo_plot3.RR.perc.all %>%
   mutate(model_lnRR = map(data, ~ metafor::rma.uni(
@@
 
-plot3.male.meta.RR.perc.all <- plot3.male.meta.RR.perc.all %>% mutate(GroupingTerm = "All")
+plot3.meta.RR.perc.all <- plot3.meta.RR.perc.all %>% mutate(GroupingTerm = "All")
 
@@
 
-plot3.male.meta.CVR.perc <- bind_rows(plot3.male.meta.CVR.perc, plot3.male.meta.CVR.perc.all)
-plot3.male.meta.VR.perc <- bind_rows(plot3.male.meta.VR.perc, plot3.male.meta.VR.perc.all)
-plot3.male.meta.RR.perc <- bind_rows(plot3.male.meta.RR.perc, plot3.male.meta.RR.perc.all)
+plot3.meta.CVR.perc <- bind_rows(plot3.meta.CVR.perc, plot3.meta.CVR.perc.all)
+plot3.meta.VR.perc <- bind_rows(plot3.meta.VR.perc, plot3.meta.VR.perc.all)
+plot3.meta.RR.perc <- bind_rows(plot3.meta.RR.perc, plot3.meta.RR.perc.all)
 
@@
 
-plot3.male.meta.CVR.perc.b <- as.data.frame(plot3.male.meta.CVR.perc %>% group_by(GroupingTerm) %>%
+plot3.meta.CVR.perc.b <- as.data.frame(plot3.meta.CVR.perc %>% group_by(GroupingTerm) %>%
   mutate(
@@
   ))[, c(1, 4:7)]
-add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.male.meta.CVR.perc.b))
-plot3.male.meta.CVR.perc.b <- rbind(plot3.male.meta.CVR.perc.b, add.row.hearing)
-plot3.male.meta.CVR.perc.b <- plot3.male.meta.CVR.perc.b[order(plot3.male.meta.CVR.perc.b$GroupingTerm), ]
-
-plot3.male.meta.VR.perc.b <- as.data.frame(plot3.male.meta.VR.perc %>% group_by(GroupingTerm) %>%
+add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.meta.CVR.perc.b))
+plot3.meta.CVR.perc.b <- rbind(plot3.meta.CVR.perc.b, add.row.hearing)
+plot3.meta.CVR.perc.b <- plot3.meta.CVR.perc.b[order(plot3.meta.CVR.perc.b$GroupingTerm), ]
+
+plot3.meta.VR.perc.b <- as.data.frame(plot3.meta.VR.perc %>% group_by(GroupingTerm) %>%
   mutate(
@@
   ))[, c(1, 4:7)]
-add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.male.meta.VR.perc.b))
-plot3.male.meta.VR.perc.b <- rbind(plot3.male.meta.VR.perc.b, add.row.hearing)
-plot3.male.meta.VR.perc.b <- plot3.male.meta.VR.perc.b[order(plot3.male.meta.VR.perc.b$GroupingTerm), ]
-
-plot3.male.meta.RR.perc.b <- as.data.frame(plot3.male.meta.RR.perc %>% group_by(GroupingTerm) %>%
+add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.meta.VR.perc.b))
+plot3.meta.VR.perc.b <- rbind(plot3.meta.VR.perc.b, add.row.hearing)
+plot3.meta.VR.perc.b <- plot3.meta.VR.perc.b[order(plot3.meta.VR.perc.b$GroupingTerm), ]
+
+plot3.meta.RR.perc.b <- as.data.frame(plot3.meta.RR.perc %>% group_by(GroupingTerm) %>%
   mutate(
@@
   ))[, c(1, 4:7)]
-add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>%
-  setNames(names(plot3.male.meta.RR.perc.b))
-plot3.male.meta.RR.perc.b <- rbind(plot3.male.meta.RR.perc.b, add.row.hearing)
-
-add.row.eye <- as.data.frame(t(c("Eye", NA, NA, NA, NA))) %>%
-  setNames(names(plot3.male.meta.RR.perc.b))
-plot3.male.meta.RR.perc.b <- rbind(plot3.male.meta.RR.perc.b, add.row.eye)
-
-plot3.male.meta.RR.perc.b <- plot3.male.meta.RR.perc.b[order(plot3.male.meta.RR.perc.b$GroupingTerm), ]
-
-plot3.male.meta.CVR.Vr.perc <- full_join(plot3.male.meta.CVR.perc.b, plot3.male.meta.VR.perc.b)
-overall.male.plot3.perc <- full_join(plot3.male.meta.CVR.Vr.perc, plot3.male.meta.RR.perc.b)
-
-overall.male.plot3.perc$GroupingTerm <- factor(overall.male.plot3.perc$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
-overall.male.plot3.perc$GroupingTerm <- factor(overall.male.plot3.perc$GroupingTerm, rev(levels(overall.male.plot3.perc$GroupingTerm)))
-
-```
-
-Restructure data for plotting : Male biased, 10% difference
-
-```{r}
-overall3.perc <- gather(overall.male.plot3.perc, parameter, value, c(lnCVR, lnVR, lnRR), factor_key = TRUE)
+add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.meta.RR.perc.b))
+plot3.meta.RR.perc.b <- rbind(plot3.meta.RR.perc.b, add.row.hearing)
+add.row.hematology <- as.data.frame(t(c("Hematology", NA, NA, NA, NA))) %>%
+  setNames(names(plot3.meta.RR.perc.b))
+plot3.meta.RR.perc.b <- rbind(plot3.meta.RR.perc.b, add.row.hematology)
+
+plot3.meta.RR.perc.b <- plot3.meta.RR.perc.b[order(plot3.meta.RR.perc.b$GroupingTerm), ]
+
+plot3.meta.CVR.perc.c <- full_join(plot3.meta.CVR.perc.b, plot3.meta.VR.perc.b)
+overall.plot3.perc <- full_join(plot3.meta.CVR.perc.c, plot3.meta.RR.perc.b)
+
+overall.plot3.perc$GroupingTerm <- factor(overall.plot3.perc$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
+overall.plot3.perc$GroupingTerm <- factor(overall.plot3.perc$GroupingTerm, rev(levels(overall.plot3.perc$GroupingTerm)))
+
+# Restructure data for plotting
+# Female bias, 10 percent difference
+
+overall3.perc <- gather(overall.plot3.perc, parameter, value, c(lnCVR, lnVR, lnRR), factor_key = TRUE)
 
@@
 
-overall4.male.perc <- bind_rows(lnCVR.ci,lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
-
-overall4.male.perc$label <- "Sex difference in m/f ratios > 10%"
-
-overall4.male.perc$value <- as.numeric(overall4.male.perc$value)
-overall4.male.perc$ci.low <- as.numeric(overall4.male.perc$ci.low)
-overall4.male.perc$ci.high <- as.numeric(overall4.male.perc$ci.high)
-```
-
-Plot Fig S2 all >10% difference (male bias)
-S2 B, bottom right
-
-```{r}
-
-Metameta_Fig3_male.perc <- overall4.male.perc %>% # filter(., GroupingTerm != "Hearing") %>%
+overall4.perc <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
+
+overall4.perc$label <- "Sex difference in m/f ratios > 10%"
+
+overall4.perc$value <- as.numeric(overall4.perc$value)
+overall4.perc$ci.low <- as.numeric(overall4.perc$ci.low)
+overall4.perc$ci.high <- as.numeric(overall4.perc$ci.high)
+
+# Plot FigS2 all >10% difference (female)
+# Figure S2B, bottom left
+
+Metameta_Fig3_female.perc <- overall4.perc %>%
   ggplot(aes(y = GroupingTerm, x = value)) +
@@
   ) +
-  geom_point(aes(
-    shape = parameter,
-    fill = parameter
-  ),
-  color = "mediumaquamarine", size = 2.2,
+  geom_point(aes(shape = parameter),
+    fill = "salmon1", color = "salmon1", size = 2.2,
     show.legend = FALSE
   ) +
+
+  # scale_shape_manual(values =
+
   scale_x_continuous(
-    limits = c(-0.2, 0.62),
-    breaks = c(0, 0.3),
+    limits = c(-0.53, 0.2),
+    breaks = c(-0.3, 0),
     name = "Effect size"
@@
   facet_grid(
-    cols = vars(parameter), rows = vars(label),
-    labeller = label_wrap_gen(width = 23),
+    cols = vars(parameter), # rows = vars(label),
+    # labeller = label_wrap_gen(width = 23),
     scales = "free",
@@
 
-# Metameta_Fig3_male.perc (Figure S2 right panel)
-```
-
-#### Female Fig S2 >10%
-
+# Metameta_Fig3_female.perc (Figure S2 bottom left panel)
+```
+#### Male Figure, significant and highly biased traits (Figure S2 B, right hand side panels)
+Restructuring data with significant male bias (for Figure S2 B, top right panel)
 ```{r}
-
-meta.plot3.perc <- metacombo %>%
-  mutate(
-    percCVR = ifelse(lnCVR < log(9 / 10), 1, 0),
-    percVR = ifelse(lnVR < log(9 / 10), 1, 0),
-    percRR = ifelse(lnRR < log(9 / 10), 1, 0)
+overall3.male.sigS <- gather(overall.male.plot3, parameter, value, c(lnCVR, lnVR, lnRR), factor_key = TRUE)
+
+lnCVR.ci <- overall3.male.sigS %>%
+  filter(parameter == "lnCVR") %>%
+  mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
+lnVR.ci <- overall3.male.sigS %>%
+  filter(parameter == "lnVR") %>%
+  mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
+lnRR.ci <- overall3.male.sigS %>%
+  filter(parameter == "lnRR") %>%
+  mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
+
+overall4.male.sigS <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
+
+overall4.male.sigS$label <- "CI not overlapping zero"
+
+# Plot FigS2 all significant results (CI not overlapping zero, male )
+
+Metameta_FigS2_male.sig <- overall4.male.sigS %>%
+  ggplot(aes(y = GroupingTerm, x = value)) +
+  geom_errorbarh(aes(
+    xmin = ci.low,
+    xmax = ci.high
+  ),
+  height = 0.1, show.legend = FALSE
+  ) +
+  geom_point(aes(shape = parameter),
+    fill = "mediumaquamarine", color = "mediumaquamarine", size = 2.2,
+    show.legend = FALSE
+  ) +
+  scale_x_continuous(
+    limits = c(0, 0.4),
+    breaks = c(0, 0.3),
+    name = "Effect size"
+  ) +
+  geom_vline(
+    xintercept = 0,
+    color = "black",
+    linetype = "dashed"
+  ) +
+  facet_grid(
+    cols = vars(parameter), rows = vars(label),
+    labeller = label_wrap_gen(width = 23),
+    scales = "free",
+    space = "free"
+  ) +
+  theme_bw() +
+  theme(
+    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
+    strip.text.x = element_text(size = 12),
+    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
+    text = element_text(size = 14),
+    panel.spacing = unit(0.5, "lines"),
+    panel.border = element_blank(),
+    axis.line = element_line(),
+    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
+    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
+    panel.grid.minor.y = element_blank(),
+    panel.grid.minor.x = element_blank(),
+    legend.title = element_blank(),
+    axis.title.x = element_blank(),
+    axis.title.y = element_blank()
+  )
+
+# Metameta_FigS2_male.sig
+
+## Prepare data for traits with m/f difference > 10%. Male bias
+### Create column with 1= larger, 0= difference not larger than 10% between male/female ratios
+
+meta.male.plot3.perc <- metacombo %>%
+  mutate(
+    percCVR = ifelse(lnCVR > log(11 / 10), 1, 0),
+    percVR = ifelse(lnVR > log(11 / 10), 1, 0),
+    percRR = ifelse(lnRR > log(11 / 10), 1, 0)
   )
@@
 # Significant subset for lnCVR
-metacombo_plot3.CVR.perc <- meta.plot3.perc %>%
+metacombo_male.plot3.CVR.perc <- meta.male.plot3.perc %>%
   filter(percCVR == 1) %>%
@@
 
-metacombo_plot3.CVR.perc.all <- meta.plot3.perc %>%
+metacombo_male.plot3.CVR.perc.all <- meta.male.plot3.perc %>%
   filter(percCVR == 1) %>%
@@
 # Significant subset for lnVR
-metacombo_plot3.VR.perc <- meta.plot3.perc %>%
+metacombo_male.plot3.VR.perc <- meta.male.plot3.perc %>%
   filter(percVR == 1) %>%
@@
 
-metacombo_plot3.VR.perc.all <- meta.plot3.perc %>%
+metacombo_male.plot3.VR.perc.all <- meta.male.plot3.perc %>%
   filter(percVR == 1) %>%
@@
 # Significant subset for lnRR
-metacombo_plot3.RR.perc <- meta.plot3.perc %>%
+metacombo_male.plot3.RR.perc <- meta.male.plot3.perc %>%
   filter(percRR == 1) %>%
@@
 
-metacombo_plot3.RR.perc.all <- meta.plot3.perc %>%
+metacombo_male.plot3.RR.perc.all <- meta.male.plot3.perc %>%
   filter(percRR == 1) %>%
@@
 
-# **Final fixed effects meta-analyses within grouping terms, with SE of the estimate
-
-plot3.meta.CVR.perc <- metacombo_plot3.CVR.perc %>%
+# Final fixed effects meta-analyses within grouping terms and across grouping terms, with SE of the estimate
+
+plot3.male.meta.CVR.perc <- metacombo_male.plot3.CVR.perc %>%
   mutate(model_lnCVR = map(data, ~ metafor::rma.uni(
@@
 
-plot3.meta.VR.perc <- metacombo_plot3.VR.perc %>%
+plot3.male.meta.VR.perc <- metacombo_male.plot3.VR.perc %>%
   mutate(model_lnVR = map(data, ~ metafor::rma.uni(
@@
 
-plot3.meta.RR.perc <- metacombo_plot3.RR.perc %>%
+plot3.male.meta.RR.perc <- metacombo_male.plot3.RR.perc %>%
   mutate(model_lnRR = map(data, ~ metafor::rma.uni(
@@
 
-# Across all grouping terms #
-
-plot3.meta.CVR.perc.all <- metacombo_plot3.CVR.perc.all %>%
+# Across all grouping terms
+
+plot3.male.meta.CVR.perc.all <- metacombo_male.plot3.CVR.perc.all %>%
   mutate(model_lnCVR = map(data, ~ metafor::rma.uni(
@@
 
-plot3.meta.CVR.perc.all <- plot3.meta.CVR.perc.all %>% mutate(GroupingTerm = "All")
-
-plot3.meta.VR.perc.all <- metacombo_plot3.VR.perc.all %>%
+plot3.male.meta.CVR.perc.all <- plot3.male.meta.CVR.perc.all %>% mutate(GroupingTerm = "All")
+
+plot3.male.meta.VR.perc.all <- metacombo_male.plot3.VR.perc.all %>%
   mutate(model_lnVR = map(data, ~ metafor::rma.uni(
@@
 
-plot3.meta.VR.perc.all <- plot3.meta.VR.perc.all %>% mutate(GroupingTerm = "All")
-
-plot3.meta.RR.perc.all <- metacombo_plot3.RR.perc.all %>%
+plot3.male.meta.VR.perc.all <- plot3.male.meta.VR.perc.all %>% mutate(GroupingTerm = "All")
+
+plot3.male.meta.RR.perc.all <- metacombo_male.plot3.RR.perc.all %>%
   mutate(model_lnRR = map(data, ~ metafor::rma.uni(
@@
 
-plot3.meta.RR.perc.all <- plot3.meta.RR.perc.all %>% mutate(GroupingTerm = "All")
+plot3.male.meta.RR.perc.all <- plot3.male.meta.RR.perc.all %>% mutate(GroupingTerm = "All")
 
@@
 
-plot3.meta.CVR.perc <- bind_rows(plot3.meta.CVR.perc, plot3.meta.CVR.perc.all)
-plot3.meta.VR.perc <- bind_rows(plot3.meta.VR.perc, plot3.meta.VR.perc.all)
-plot3.meta.RR.perc <- bind_rows(plot3.meta.RR.perc, plot3.meta.RR.perc.all)
+plot3.male.meta.CVR.perc <- bind_rows(plot3.male.meta.CVR.perc, plot3.male.meta.CVR.perc.all)
+plot3.male.meta.VR.perc <- bind_rows(plot3.male.meta.VR.perc, plot3.male.meta.VR.perc.all)
+plot3.male.meta.RR.perc <- bind_rows(plot3.male.meta.RR.perc, plot3.male.meta.RR.perc.all)
 
@@
 
-plot3.meta.CVR.perc.b <- as.data.frame(plot3.meta.CVR.perc %>% group_by(GroupingTerm) %>%
+plot3.male.meta.CVR.perc.b <- as.data.frame(plot3.male.meta.CVR.perc %>% group_by(GroupingTerm) %>%
   mutate(
@@
   ))[, c(1, 4:7)]
-add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.meta.CVR.perc.b))
-plot3.meta.CVR.perc.b <- rbind(plot3.meta.CVR.perc.b, add.row.hearing)
-plot3.meta.CVR.perc.b <- plot3.meta.CVR.perc.b[order(plot3.meta.CVR.perc.b$GroupingTerm), ]
-
-plot3.meta.VR.perc.b <- as.data.frame(plot3.meta.VR.perc %>% group_by(GroupingTerm) %>%
+add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.male.meta.CVR.perc.b))
+plot3.male.meta.CVR.perc.b <- rbind(plot3.male.meta.CVR.perc.b, add.row.hearing)
+plot3.male.meta.CVR.perc.b <- plot3.male.meta.CVR.perc.b[order(plot3.male.meta.CVR.perc.b$GroupingTerm), ]
+
+plot3.male.meta.VR.perc.b <- as.data.frame(plot3.male.meta.VR.perc %>% group_by(GroupingTerm) %>%
   mutate(
@@
   ))[, c(1, 4:7)]
-add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.meta.VR.perc.b))
-plot3.meta.VR.perc.b <- rbind(plot3.meta.VR.perc.b, add.row.hearing)
-plot3.meta.VR.perc.b <- plot3.meta.VR.perc.b[order(plot3.meta.VR.perc.b$GroupingTerm), ]
-
-plot3.meta.RR.perc.b <- as.data.frame(plot3.meta.RR.perc %>% group_by(GroupingTerm) %>%
+add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.male.meta.VR.perc.b))
+plot3.male.meta.VR.perc.b <- rbind(plot3.male.meta.VR.perc.b, add.row.hearing)
+plot3.male.meta.VR.perc.b <- plot3.male.meta.VR.perc.b[order(plot3.male.meta.VR.perc.b$GroupingTerm), ]
+
+plot3.male.meta.RR.perc.b <- as.data.frame(plot3.male.meta.RR.perc %>% group_by(GroupingTerm) %>%
   mutate(
@@
   ))[, c(1, 4:7)]
-add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.meta.RR.perc.b))
-plot3.meta.RR.perc.b <- rbind(plot3.meta.RR.perc.b, add.row.hearing)
-add.row.hematology <- as.data.frame(t(c("Hematology", NA, NA, NA, NA))) %>%
-  setNames(names(plot3.meta.RR.perc.b))
-plot3.meta.RR.perc.b <- rbind(plot3.meta.RR.perc.b, add.row.hematology)
-
-plot3.meta.RR.perc.b <- plot3.meta.RR.perc.b[order(plot3.meta.RR.perc.b$GroupingTerm), ]
-
-plot3.meta.CVR.perc.c <- full_join(plot3.meta.CVR.perc.b, plot3.meta.VR.perc.b)
-overall.plot3.perc <- full_join(plot3.meta.CVR.perc.c, plot3.meta.RR.perc.b)
-
-overall.plot3.perc$GroupingTerm <- factor(overall.plot3.perc$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
-overall.plot3.perc$GroupingTerm <- factor(overall.plot3.perc$GroupingTerm, rev(levels(overall.plot3.perc$GroupingTerm)))
-```
-
-Restructure data for plotting
-Female bias, 10 percent difference
-
-```{r}
-overall3.perc <- gather(overall.plot3.perc, parameter, value, c(lnCVR, lnVR, lnRR), factor_key = TRUE)
+add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>%
+  setNames(names(plot3.male.meta.RR.perc.b))
+plot3.male.meta.RR.perc.b <- rbind(plot3.male.meta.RR.perc.b, add.row.hearing)
+
+add.row.eye <- as.data.frame(t(c("Eye", NA, NA, NA, NA))) %>%
+  setNames(names(plot3.male.meta.RR.perc.b))
+plot3.male.meta.RR.perc.b <- rbind(plot3.male.meta.RR.perc.b, add.row.eye)
+
+plot3.male.meta.RR.perc.b <- plot3.male.meta.RR.perc.b[order(plot3.male.meta.RR.perc.b$GroupingTerm), ]
+
+plot3.male.meta.CVR.Vr.perc <- full_join(plot3.male.meta.CVR.perc.b, plot3.male.meta.VR.perc.b)
+overall.male.plot3.perc <- full_join(plot3.male.meta.CVR.Vr.perc, plot3.male.meta.RR.perc.b)
+
+overall.male.plot3.perc$GroupingTerm <- factor(overall.male.plot3.perc$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
+overall.male.plot3.perc$GroupingTerm <- factor(overall.male.plot3.perc$GroupingTerm, rev(levels(overall.male.plot3.perc$GroupingTerm)))
+
+# Restructure data for plotting : Male biased, 10% difference
+
+overall3.perc <- gather(overall.male.plot3.perc, parameter, value, c(lnCVR, lnVR, lnRR), factor_key = TRUE)
 
@@
 
-overall4.perc <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
-
-overall4.perc$label <- "Sex difference in m/f ratios > 10%"
-
-overall4.perc$value <- as.numeric(overall4.perc$value)
-overall4.perc$ci.low <- as.numeric(overall4.perc$ci.low)
-overall4.perc$ci.high <- as.numeric(overall4.perc$ci.high)
-```
-
-Plot FigS2 all >10% difference (female)
-Figure S2B, bottom left
-
-```{r}
-Metameta_Fig3_female.perc <- overall4.perc %>%
+overall4.male.perc <- bind_rows(lnCVR.ci,lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
+
+overall4.male.perc$label <- "Sex difference in m/f ratios > 10%"
+
+overall4.male.perc$value <- as.numeric(overall4.male.perc$value)
+overall4.male.perc$ci.low <- as.numeric(overall4.male.perc$ci.low)
+overall4.male.perc$ci.high <- as.numeric(overall4.male.perc$ci.high)
+
+# Plot Fig S2 all >10% difference (male bias)
+# S2 B, bottom right
+
+Metameta_Fig3_male.perc <- overall4.male.perc %>% # filter(., GroupingTerm != "Hearing") %>%
   ggplot(aes(y = GroupingTerm, x = value)) +
@@
   ) +
-  geom_point(aes(shape = parameter),
-    fill = "salmon1", color = "salmon1", size = 2.2,
+  geom_point(aes(
+    shape = parameter,
+    fill = parameter
+  ),
+  color = "mediumaquamarine", size = 2.2,
   show.legend = FALSE
   ) +
-
-  # scale_shape_manual(values =
-
   scale_x_continuous(
-    limits = c(-0.53, 0.2),
-    breaks = c(-0.3, 0),
+    limits = c(-0.2, 0.62),
+    breaks = c(0, 0.3),
     name = "Effect size"
@@
   facet_grid(
-    cols = vars(parameter), # rows = vars(label),
-    # labeller = label_wrap_gen(width = 23),
+    cols = vars(parameter), rows = vars(label),
+    labeller = label_wrap_gen(width = 23),
     scales = "free",
@@
 
-# Metameta_Fig3_female.perc (Figure 5D left panel)
-```
-MISSING
-Metameta_Fig3_female.sig Metameta_Fig3_female.sig VR!!!
-# ADDED TO TEST
-#Metameta_FigS2_male.sig (Figure S2B top right panel)
-
-Restructure MALE data for plotting
-
-```{r}
-overall3.male.sigS <- gather(overall.male.plot3, parameter, value, c(lnCVR, lnVR, lnRR), factor_key = TRUE)
-
-lnCVR.ci <- overall3.male.sigS %>%
-  filter(parameter == "lnCVR") %>%
-  mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
-lnVR.ci <- overall3.male.sigS %>%
-  filter(parameter == "lnVR") %>%
-  mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
-lnRR.ci <- overall3.male.sigS %>%
-  filter(parameter == "lnRR") %>%
-  mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
-
-overall4.male.sigS <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
-
-overall4.male.sigS$label <- "CI not overlapping zero"
-```
-
-Plot FigS2 all significant results (CI not overlapping zero, male )
-
-```{r}
-Metameta_FigS2_male.sig <- overall4.male.sigS %>%
-  ggplot(aes(y = GroupingTerm, x = value)) +
-  geom_errorbarh(aes(
-    xmin = ci.low,
-    xmax = ci.high
-  ),
-  height = 0.1, show.legend = FALSE
-  ) +
-  geom_point(aes(shape = parameter),
-    fill = "mediumaquamarine", color = "mediumaquamarine", size = 2.2,
-    show.legend = FALSE
-  ) +
-  scale_x_continuous(
-    limits = c(0, 0.4),
-    breaks = c(0, 0.3),
-    name = "Effect size"
-  ) +
-  geom_vline(
-    xintercept = 0,
-    color = "black",
-    linetype = "dashed"
-  ) +
-  facet_grid(
-    cols = vars(parameter), rows = vars(label),
-    labeller = label_wrap_gen(width = 23),
-    scales = "free",
-    space = "free"
-  ) +
-  theme_bw() +
-  theme(
-    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
-    strip.text.x = element_text(size = 12),
-    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
-    text = element_text(size = 14),
-    panel.spacing = unit(0.5, "lines"),
-    panel.border = element_blank(),
-    axis.line = element_line(),
-    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
-    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
-    panel.grid.minor.y = element_blank(),
-    panel.grid.minor.x = element_blank(),
-    legend.title = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank()
-  )
-
-# Metameta_FigS2_male.sig
-```
-
-#### Plot Fig S2:   plots combined
-
-Metameta_FigS2_female.sig
+# Metameta_Fig3_male.perc (Figure S2 right panel)
+```
+
+### Figure S2
+
+This figure is an extension of sex biases, as shown in Figure 5 in the main text.
+Here, we include data on lnVR (middle panel), as well as athe second method of sex-differences comparison.
+The panels in A show differences in numbers of affected traits, in variance (lnCVR and lnVR) and means (lnRR), where there’s a significant difference between the sexes (i.e CI not overlapping zero), and where the sex bias is greater than 10% difference (regardless of significance).
+Panel B depicts results for the sex bias in those traits that differ between the sexes (second-order meta-analysis).
+Triangles represent sex bias in means (response ratio) and black circles differences in the coefficient of variation ratio (mean-adjusted variability).
+The orange-red bars represent trait groups with a female bias, blue-green bars male-biased traits.
 ```{r}
@@
 FigS2b <- ggarrange(Metameta_FigS2_female.sig, Metameta_FigS2_male.sig,
-  ncol = 2, nrow = 1, widths = c(1, 1.20), heights = c(1, 1)
+  ncol = 2, nrow = 1, widths = c(1, 1.30), heights = c(1, 1)
 )
@@
 FigS2d <- ggarrange(Metameta_Fig3_female.perc, Metameta_Fig3_male.perc,
-  ncol = 2, nrow = 1, widths = c(1, 1.20), heights = c(1, 1)
+  ncol = 2, nrow = 1, widths = c(1, 1.20), heights = c(1.1, 1.1)
 )
@@
 FigS2
-```
-
-## NOT SURE WHAT THIS BELOW IS?? Felix added 11/2/2020: Ich glaube, dass das von vorher war. wenn wir alles oben haben, dann unten loeschen
-
-## Figure S2: sex-bias, including VR
-
-Prepare data for traits with effect size ratios > 10% larger in males
-
-```{r}
-meta.plotS2.over10 <- meta_clean %>%
-  select(lnCVR, lnVR, lnRR, GroupingTerm) %>%
-  arrange(GroupingTerm)
-
-meta.plotS2.over10.b <- gather(meta.plotS2.over10, trait, value, c(lnCVR, lnVR, lnRR))
-
-meta.plotS2.over10.b$trait <- factor(meta.plotS2.over10.b$trait, levels = c("lnCVR", "lnVR", "lnRR"))
-
-meta.plotS2.over10.c <- meta.plotS2.over10.b %>%
-  group_by_at(vars(trait, GroupingTerm)) %>%
-  summarise(
-    malebias = sum(value > log(11 / 10)), femalebias = sum(value < log(9 / 10)), total = malebias + femalebias,
-    malepercent = malebias * 100 / total, femalepercent = femalebias * 100 / total
-  )
-
-meta.plotS2.over10.c$label <- "Sex difference in m/f ratios > 10%"
-
-# restructure to create stacked bar plots
-
-meta.plotS2.over10.c <- as.data.frame(meta.plotS2.over10.c)
-meta.plotS2.over10.d <- gather(meta.plotS2.over10.c, key = sex, value = percent, malepercent:femalepercent, factor_key = TRUE)
-
-# create new sample size variable
-
-meta.plotS2.over10.d$samplesize <- with(meta.plotS2.over10.d, ifelse(sex == "malepercent", malebias, femalebias))
-
-# *Plot FigS2 Sex difference in m/f ratio > 10%
-malebias_FigS2_over10 <-
-  ggplot(meta.plotS2.over10.d) +
-  aes(x = GroupingTerm, y = percent, fill = sex) +
-  geom_col() +
-  geom_hline(yintercept = 50, linetype = "dashed", color = "gray40") +
-  geom_text(
-    data = subset(meta.plot2.over10.d, samplesize != 0), aes(label = samplesize), position = position_stack(vjust = .5),
-    color = "white", size = 3.5
-  ) +
-  facet_grid(
-    cols = vars(trait), rows = vars(label), labeller = label_wrap_gen(width = 18),
-    scales = "free", space = "free"
-  ) +
-  scale_fill_brewer(palette = "Set2") +
-  theme_bw(base_size = 18) +
-  theme(
-    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
-    strip.text.x = element_blank(),
-    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
-    text = element_text(size = 14),
-    panel.spacing = unit(0.5, "lines"),
-    panel.border = element_blank(),
-    axis.line = element_line(),
-    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
-    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
-    panel.grid.minor.y = element_blank(),
-    panel.grid.minor.x = element_blank(),
-    legend.position = "none",
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank()
-  ) +
-  coord_flip()
-
-# malebias_FigS2_over10  #(Panel B in Fig S2 in ms)
-```
-
-#Metameta_FigS2_male.sig (Figure S2B top right panel)
-
-Restructure MALE data for plotting
-
-```{r}
-overall3.male.sigS <- gather(overall.male.plot3, parameter, value, c(lnCVR, lnVR, lnRR), factor_key = TRUE)
-
-lnCVR.ci <- overall3.male.sigS %>%
-  filter(parameter == "lnCVR") %>%
-  mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
-lnVR.ci <- overall3.male.sigS %>%
-  filter(parameter == "lnVR") %>%
-  mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
-lnRR.ci <- overall3.male.sigS %>%
-  filter(parameter == "lnRR") %>%
-  mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
-
-overall4.male.sigS <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
-
-overall4.male.sigS$label <- "CI not overlapping zero"
-```
-
-Plot FigS2 all significant results (CI not overlapping zero, male )
-
-```{r}
-Metameta_FigS2_male.sig <- overall4.male.sigS %>%
-  ggplot(aes(y = GroupingTerm, x = value)) +
-  geom_errorbarh(aes(
-    xmin = ci.low,
-    xmax = ci.high
-  ),
-  height = 0.1, show.legend = FALSE
-  ) +
-  geom_point(aes(shape = parameter),
-    fill = "mediumaquamarine", color = "mediumaquamarine", size = 2.2,
-    show.legend = FALSE
-  ) +
-  scale_x_continuous(
-    limits = c(0, 0.4),
-    breaks = c(0, 0.3),
-    name = "Effect size"
-  ) +
-  geom_vline(
-    xintercept = 0,
-    color = "black",
-    linetype = "dashed"
-  ) +
-  facet_grid(
-    cols = vars(parameter), rows = vars(label),
-    labeller = label_wrap_gen(width = 23),
-    scales = "free",
-    space = "free"
-  ) +
-  theme_bw() +
-  theme(
-    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
-    strip.text.x = element_text(size = 12),
-    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
-    text = element_text(size = 14),
-    panel.spacing = unit(0.5, "lines"),
-    panel.border = element_blank(),
-    axis.line = element_line(),
-    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
-    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
-    panel.grid.minor.y = element_blank(),
-    panel.grid.minor.x = element_blank(),
-    legend.title = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank()
-  )
-
-# Metameta_FigS2_male.sig
-```
-
-### 10 % Perc sex difference, male bias
-Restructure data for plotting : Male biased, 10% difference
-
-```{r}
-overall3S.perc <- gather(overall.male.plot3.perc, parameter, value, c(lnCVR, lnVR, lnRR), factor_key = TRUE) # lnVR,
-
-lnCVR.ci <- overall3S.perc %>%
-  filter(parameter == "lnCVR") %>%
-  mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
-lnVR.ci <- overall3S.perc %>%
-  filter(parameter == "lnVR") %>%
-  mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
-lnRR.ci <- overall3S.perc %>%
-  filter(parameter == "lnRR") %>%
-  mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
-
-overall4S.male.perc <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high) # lnVR.ci,
-
-overall4S.male.perc$label <- "Sex difference in m/f ratios > 10%"
-
-overall4S.male.perc$value <- as.numeric(overall4S.male.perc$value)
-overall4S.male.perc$ci.low <- as.numeric(overall4S.male.perc$ci.low)
-overall4S.male.perc$ci.high <- as.numeric(overall4S.male.perc$ci.high)
-```
-
-Plot FigS2  all >10% difference (male bias)
-
-```{r}
-Metameta_FigS2_male.perc <- overall4S.male.perc %>% # filter(., GroupingTerm != "Hearing") %>%
-  ggplot(aes(y = GroupingTerm, x = value)) +
-  geom_errorbarh(aes(
-    xmin = ci.low,
-    xmax = ci.high
-  ),
-  height = 0.1, show.legend = FALSE
-  ) +
-  geom_point(aes(
-    shape = parameter,
-    fill = parameter
-  ),
-  color = "mediumaquamarine", size = 2.2,
-  show.legend = FALSE
-  ) +
-  scale_x_continuous(
-    limits = c(-0.2, 0.62),
-    breaks = c(0, 0.3),
-    name = "Effect size"
-  ) +
-  geom_vline(
-    xintercept = 0,
-    color = "black",
-    linetype = "dashed"
-  ) +
-  facet_grid(
-    cols = vars(parameter), rows = vars(label),
-    labeller = label_wrap_gen(width = 23),
-    scales = "free",
-    space = "free"
-  ) +
-  theme_bw() +
-  theme(
-    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
-    strip.text.x = element_blank(),
-    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
-    text = element_text(size = 14),
-    panel.spacing = unit(0.5, "lines"),
-    panel.border = element_blank(),
-    axis.line = element_line(),
-    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
-    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
-    panel.grid.minor.y = element_blank(),
-    panel.grid.minor.x = element_blank(),
-    legend.title = element_blank(),
-    axis.title.x = element_text(hjust = 0.5, size = 14),
-    axis.title.y = element_blank()
-  )
-
-# Metameta_FigS2_male.perc (Figure 5D right panel)
-```
-
-Restructure data for plotting: 
-Female bias, 10 percent difference, including VR
-
-```{r}
-overall3S.perc <- gather(overall.plot3.perc, parameter, value, c(lnCVR, lnVR, lnRR), factor_key = TRUE) # lnVR,
-
-lnCVR.ci <- overall3S.perc %>%
-  filter(parameter == "lnCVR") %>%
-  mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
-lnVR.ci <- overall3S.perc %>%
-  filter(parameter == "lnVR") %>%
-  mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
-lnRR.ci <- overall3S.perc %>%
-  filter(parameter == "lnRR") %>%
-  mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
-
-overall4S.perc <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
-
-overall4S.perc$label <- "Sex difference in m/f ratios > 10%"
-
-overall4S.perc$value <- as.numeric(overall4S.perc$value)
-overall4S.perc$ci.low <- as.numeric(overall4S.perc$ci.low)
-overall4S.perc$ci.high <- as.numeric(overall4S.perc$ci.high)
-```
-
-Plot Fig5D all >10% difference (female)
-
-```{r}
-Metameta_Fig3S_female.perc <- overall4S.perc %>%
-  ggplot(aes(y = GroupingTerm, x = value)) +
-  geom_errorbarh(aes(
-    xmin = ci.low,
-    xmax = ci.high
-  ),
-  height = 0.1, show.legend = FALSE
-  ) +
-  geom_point(aes(shape = parameter),
-    fill = "salmon1", color = "salmon1", size = 2.2,
-    show.legend = FALSE
-  ) +
-
-  # scale_shape_manual(values =
-
-  scale_x_continuous(
-    limits = c(-0.53, 0.2),
-    breaks = c(-0.3, 0),
-    name = "Effect size"
-  ) +
-  geom_vline(
-    xintercept = 0,
-    color = "black",
-    linetype = "dashed"
-  ) +
-  facet_grid(
-    cols = vars(parameter), # rows = vars(label),
-    # labeller = label_wrap_gen(width = 23),
-    scales = "free",
-    space = "free"
-  ) +
-  theme_bw() +
-  theme(
-    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
-    strip.text.x = element_blank(),
-    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
-    text = element_text(size = 14),
-    panel.spacing = unit(0.5, "lines"),
-    panel.border = element_blank(),
-    axis.line = element_line(),
-    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
-    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
-    panel.grid.minor.y = element_blank(),
-    panel.grid.minor.x = element_blank(),
-    legend.title = element_blank(),
-    axis.title.x = element_text(hjust = 0.5, size = 14),
-    axis.title.y = element_blank()
-  )
-
-# Metameta_Fig3S_female.perc (Figure 5D left panel)
-```
-
-Figure S2
-
-```{r}
-FigS2c <- ggarrange(Metameta_FigS2_female.sig, Metameta_FigS2_male.sig,
-  ncol = 2, nrow = 1, widths = c(1, 1.20), heights = c(1, 1)
-)
-
-FigS2d <- ggarrange(Metameta_Fig3S_female.perc, Metameta_FigS2_male.perc,
-  ncol = 2, nrow = 1, widths = c(1, 1.20), heights = c(1, 1)
-)
-
-# end combination Figure 5
-
-FigS2 <- ggarrange(malebias_FigS2_sigtraits, malebias_FigS2_over10, FigS2c, FigS2d, ncol = 1, nrow = 4, heights = c(2.2, 2, 2.2, 2), labels = c("A", " ", "B", " "))
-FigS2
+#ggsave("FigS2_Bias.pdf", plot = FigS2, width = 7, height = 8)
 ```

### 2020-04-20 Prep & old/2019_Nov1-FiguresRearranged_IMPC_variance_and_sex_difference.Rmd
move

--- 2020-04-20 Prep & old/FZ 10-12-2019.Rmd
@@
 
-Check length of different variables / sample sizes:
-
-```{r}
-length(unique(data$parameter_name)) # 232 traits
-length(unique(data$parameter_group)) # 161 parameter groups
-length(unique(data$procedure_name)) # 26 procedure groups
-length(unique(data$biological_sample_id)) # 27147 individial mice   #FZ added 11-12-2019
-#number of males and females per strain per production center #FZ added 11-12-2019
-sampleSizes <-data %>% group_by(production_center, strain_name) %>% count(biological_sample_id, sex) %>% count(sex) %>% print(n = Inf)
-sampleSizes <- write.csv(sampleSizes, file = "export/sampleSizes.csv")
-length(unique(sampleSizes$strain_name)) #9
-length(unique(data$strain_name)) #9
+Check length of different variables:
+
+```{r}
+length(unique(data$parameter_name)) # 232
+length(unique(data$parameter_group)) # 161
+length(unique(data$procedure_name)) # 26
+
 ```
@@
 
-  # still some individuals with multiple records (because same individual appear under different procedures, so filter to one record)
+  # still some individuals with multiple records (because same individual appears under different procedures, so filter to one record)
   j <- match(unique(tmp$biological_sample_id), tmp$biological_sample_id)
@@
 **REVIEW**: The above loop gives some errors, can these be fixed?
-**FZ**: In the above function, we use 'tryCatch' and 'conditionMessage' to prevent the loop from aborting when the first error at row 84 is produced.
-**FZ**  Convergence in the two listed non-converging cases can't be achieved by sensibly tweaking (other optim etc.).
-**FZ**  Since we only learn about non-convergence in the loop, it's difficult to exclude the two traits beforehand.
-**FZ**  Similarly, the 8 traits with very low variation (160, ..., 231) are hard to exclude before.
-**FZ**  Warnings are ok: indicating cases where variance components are set to zero during likelihood optimization.
 
@@
 
-Procedure names, grouping variables etc. are merged back together with the results from the metafor analysis above. This requires loading of another excel sheet, "procedures.csv"
+Procedure names, grouping variables etc. are merged back together with the results from the metafor analysis above.This requires loading of another excel sheet, "procedures.csv"
 
@@
               # REVIEW -- this bext line replciates precious code, but removes some procedures, is that right?
-		  # FZ: No. This creates the data from the complete data set ('data'), which was not carried over into 'results_alltraits_grouping'
-		  # FZ: We filter duplicated id's to get only one unique row per id (and there is one id per parameter_name)
               filter(!duplicated(id))
             ) %>%
-  # FZ: Below we add 'procedure' (from the previously loaded 'procedures.csv') as a variable
   left_join(by="procedure", 
@@
 **Review**: How did we determine this the ones with problems?
-**FZ**: In addition to the sentence one line above, to do: add information about cause of exclusion ( 1.
-non-convergence of metafor models, or 2.
-no variation/nonsensical); reference traits to be excluded by trait name (not id number)
-**FZ**: excluded because of non-convergence: 84, 158
-**FZ**: excluded because no variation/nonsensical: 144, 158, 160,... 
-```{r}
-
-#FZ delete# has_problems <- c(84, 144, 158, 160, 161, 162, 163, 165, 166, 167, 168, 221, 222, 231)
-#FZ delete# meta_clean <- results_alltraits_grouping2 %>% filter(!id %in% has_problems)
-#FZ delete# meta_problem <- results_alltraits_grouping2 %>% filter(id %in% has_problems)
-
-#**FZ**:exclude parameter names for which metafor models didn't converge ("dp t cells", "mzb (cd21/35 high)"), and of parameters that don't harbour enough variation
-meta_clean <- results_alltraits_grouping2 %>% 
-	  filter(!parameter_name %in% c("dp t cells", "mzb (cd21/35 high)", "number of caudal vertebrae", 
-	  "number of cervical vertebrae", "number of digits", "number of lumbar vertebrae", "number of pelvic vertebrae", "number of ribs left",                       
-        "number of ribs right", "number of signals", "number of thoracic vertebrae", "total number of acquired events in panel a",
-        "total number of acquired events in panel b", "whole arena permanence"))
-
-```
+
+```{r}
+
+has_problems <- c(84, 144, 158, 160, 161, 162, 163, 165, 166, 167, 168, 221, 222, 231)
+meta_clean <- results_alltraits_grouping2 %>% filter(!id %in% has_problems)
+meta_problem <- results_alltraits_grouping2 %>% filter(id %in% has_problems)
 ```
@@
 length(unique(meta1$GroupingTerm)) #9
-# Review: next line now 155 not 148 #FZ comment: still 148 for me.
+# Review: next line now 155 not 148
 length(unique(meta1$parameter_group)) # 148 levels.
@@
   group_by(GroupingTerm) %>%
-#FZ comment: changed 'nest' to 'nest_legacy' to keep old syntax/functionality
-  nest_legacy()
+  nest()
 
@@
 metacombo_final_all <- metacombo %>%
-#FZ comment: changed 'nest' to 'nest_legacy' to keep old syntax/functionality
-  nest_legacy()
+  nest()
 

### 2020-04-20 scripts/MouseSexDiffApril20_2020.Rmd
rename

--- 2020-04-20 scripts/MouseSexDiffFeb20_2020.Rmd
@@
 title: "Sex and Power: sexual dimorphism in trait variability and its eco-evolutionary and statistical implications"
-author: Susanne Zajitschek,  Felix Zajitschek, Russell Bonduriansky,Robert  Brooks,
+author: Susanne Zajitschek,  Felix Zajitschek, Russell Bonduriansky, Robert  Brooks,
   Will Cornwell, Daniel Falster, Malgortaza Lagisz, Jeremy Mason, Daniel Noble, Alistair
   Senior & Shinichi Nakagawa
-date: "March 2020"
+date: "April 2020"
 output:
@@
 
+## Packages
+
 ```{r, include=FALSE}
@@
 This step we have already done and provide a cleaned up file which is less computing intensive and which we have saved in a folder called `export`.
-However, the cvs is provided in case this is preferred to be attempted, following the steps below:
-
-```{r clean, eval=FALSE, include=TRUE}
+However, the cvs is provided in case this is preferred to be attempted, following the steps below: [This code is currently excluded from showing in this html file, but can be viewed and enabled / run in the downloadable .rmd file.
+However, it requires the .gz file containing the raw data in the "export" folder.
+Unfortuntaltely, that file can not be provided via github, as is too large (274MB).
+It will be freely accessible, uploaded on dryad.
+Link to dryad file HERE]
+
+```{r clean, eval=FALSE, include=FALSE}
 # loads the raw data, setting some default types for various columns

### 2020-04-20 scripts/MouseSexDiffApril20_2020.Rmd
Extraction of I2 during secondary meta analysis

@@
 }
+
 ```
@@
   mutate(
-    lnCVR = .[[4]][[1]]$b, lnCVR_lower = .[[4]][[1]]$ci.lb, lnCVR_upper = .[[4]][[1]]$ci.ub, lnCVR_se = .[[4]][[1]]$se,
-    lnVR = .[[5]][[1]]$b, lnVR_lower = .[[5]][[1]]$ci.lb, lnVR_upper = .[[5]][[1]]$ci.ub, lnVR_se = .[[5]][[1]]$se,
-    lnRR = .[[6]][[1]]$b, lnRR_lower = .[[6]][[1]]$ci.lb, lnRR_upper = .[[6]][[1]]$ci.ub, lnRR_se = .[[6]][[1]]$se
+    lnCVR = .[[4]][[1]]$b, lnCVR_lower = .[[4]][[1]]$ci.lb, lnCVR_upper = .[[4]][[1]]$ci.ub, lnCVR_se = .[[4]][[1]]$se,     lnCVR_I2 = .[[4]][[1]]$I2,
+    lnVR = .[[5]][[1]]$b, lnVR_lower = .[[5]][[1]]$ci.lb, lnVR_upper = .[[5]][[1]]$ci.ub, lnVR_se = .[[5]][[1]]$se, lnVR_I2 = .[[5]][[1]]$I2,
+    lnRR = .[[6]][[1]]$b, lnRR_lower = .[[6]][[1]]$ci.lb, lnRR_upper = .[[6]][[1]]$ci.ub, lnRR_se = .[[6]][[1]]$se, lnRR_I2 = .[[6]][[1]]$I2
   )  %>%
-  select(., GroupingTerm, lnCVR:lnRR_se)
+  select(., GroupingTerm, lnCVR:lnRR_I2)
 
@@
   mutate(
-    lnCVR = .[[4]][[1]]$b, lnCVR_lower = .[[4]][[1]]$ci.lb, lnCVR_upper = .[[4]][[1]]$ci.ub, lnCVR_se = .[[4]][[1]]$se,
-    lnVR = .[[5]][[1]]$b, lnVR_lower = .[[5]][[1]]$ci.lb, lnVR_upper = .[[5]][[1]]$ci.ub, lnVR_se = .[[5]][[1]]$se,
-    lnRR = .[[6]][[1]]$b, lnRR_lower = .[[6]][[1]]$ci.lb, lnRR_upper = .[[6]][[1]]$ci.ub, lnRR_se = .[[6]][[1]]$se
+   lnCVR = .[[4]][[1]]$b, lnCVR_lower = .[[4]][[1]]$ci.lb, lnCVR_upper = .[[4]][[1]]$ci.ub, lnCVR_se = .[[4]][[1]]$se,     lnCVR_I2 = .[[4]][[1]]$I2,
+    lnVR = .[[5]][[1]]$b, lnVR_lower = .[[5]][[1]]$ci.lb, lnVR_upper = .[[5]][[1]]$ci.ub, lnVR_se = .[[5]][[1]]$se,  lnVR_I2 = .[[5]][[1]]$I2,
+    lnRR = .[[6]][[1]]$b, lnRR_lower = .[[6]][[1]]$ci.lb, lnRR_upper = .[[6]][[1]]$ci.ub, lnRR_se = .[[6]][[1]]$se, lnRR_I2 = .[[6]][[1]]$I2
   )  %>%
-  select(., GroupingTerm, lnCVR:lnRR_se)
+  select(., GroupingTerm, lnCVR:lnRR_I2)
 
@@
   mutate(
-    lnCVR = .[[4]][[1]]$b, lnCVR_lower = .[[4]][[1]]$ci.lb, lnCVR_upper = .[[4]][[1]]$ci.ub, lnCVR_se = .[[4]][[1]]$se,
-    lnVR = .[[5]][[1]]$b, lnVR_lower = .[[5]][[1]]$ci.lb, lnVR_upper = .[[5]][[1]]$ci.ub, lnVR_se = .[[5]][[1]]$se,
-    lnRR = .[[6]][[1]]$b, lnRR_lower = .[[6]][[1]]$ci.lb, lnRR_upper = .[[6]][[1]]$ci.ub, lnRR_se = .[[6]][[1]]$se
+  lnCVR = .[[4]][[1]]$b, lnCVR_lower = .[[4]][[1]]$ci.lb, lnCVR_upper = .[[4]][[1]]$ci.ub, lnCVR_se = .[[4]][[1]]$se,     lnCVR_I2 = .[[4]][[1]]$I2,
+    lnVR = .[[5]][[1]]$b, lnVR_lower = .[[5]][[1]]$ci.lb, lnVR_upper = .[[5]][[1]]$ci.ub, lnVR_se = .[[5]][[1]]$se, lnVR_I2 = .[[5]][[1]]$I2,
+    lnRR = .[[6]][[1]]$b, lnRR_lower = .[[6]][[1]]$ci.lb, lnRR_upper = .[[6]][[1]]$ci.ub, lnRR_se = .[[6]][[1]]$se, lnRR_I2 = .[[6]][[1]]$I2
   )  %>%
-  select(., GroupingTerm, lnCVR:lnRR_se)
+  select(., GroupingTerm, lnCVR:lnRR_I2)
 
@@
   mutate(
-    lnCVR = .[[4]][[1]]$b, lnCVR_lower = .[[4]][[1]]$ci.lb, lnCVR_upper = .[[4]][[1]]$ci.ub, lnCVR_se = .[[4]][[1]]$se,
-    lnVR = .[[5]][[1]]$b, lnVR_lower = .[[5]][[1]]$ci.lb, lnVR_upper = .[[5]][[1]]$ci.ub, lnVR_se = .[[5]][[1]]$se,
-    lnRR = .[[6]][[1]]$b, lnRR_lower = .[[6]][[1]]$ci.lb, lnRR_upper = .[[6]][[1]]$ci.ub, lnRR_se = .[[6]][[1]]$se
+   lnCVR = .[[4]][[1]]$b, lnCVR_lower = .[[4]][[1]]$ci.lb, lnCVR_upper = .[[4]][[1]]$ci.ub, lnCVR_se = .[[4]][[1]]$se,     lnCVR_I2 = .[[4]][[1]]$I2,
+      lnVR = .[[5]][[1]]$b, lnVR_lower = .[[5]][[1]]$ci.lb, lnVR_upper = .[[5]][[1]]$ci.ub, lnVR_se = .[[5]][[1]]$se, lnVR_I2 = .[[5]][[1]]$I2,
+      lnRR = .[[6]][[1]]$b, lnRR_lower = .[[6]][[1]]$ci.lb, lnRR_upper = .[[6]][[1]]$ci.ub, lnRR_se = .[[6]][[1]]$se, lnRR_I2 = .[[6]][[1]]$I2
   )  %>%
-  select(., GroupingTerm, lnCVR:lnRR_se)
+  select(., GroupingTerm, lnCVR:lnRR_I2)
 
@@
     mutate(
-    lnCVR = .[[4]][[1]]$b, lnCVR_lower = .[[4]][[1]]$ci.lb, lnCVR_upper = .[[4]][[1]]$ci.ub, lnCVR_se = .[[4]][[1]]$se,
-    lnVR = .[[5]][[1]]$b, lnVR_lower = .[[5]][[1]]$ci.lb, lnVR_upper = .[[5]][[1]]$ci.ub, lnVR_se = .[[5]][[1]]$se,
-    lnRR = .[[6]][[1]]$b, lnRR_lower = .[[6]][[1]]$ci.lb, lnRR_upper = .[[6]][[1]]$ci.ub, lnRR_se = .[[6]][[1]]$se
+   lnCVR = .[[4]][[1]]$b, lnCVR_lower = .[[4]][[1]]$ci.lb, lnCVR_upper = .[[4]][[1]]$ci.ub, lnCVR_se = .[[4]][[1]]$se,     lnCVR_I2 = .[[4]][[1]]$I2,
+      lnVR = .[[5]][[1]]$b, lnVR_lower = .[[5]][[1]]$ci.lb, lnVR_upper = .[[5]][[1]]$ci.ub, lnVR_se = .[[5]][[1]]$se, lnVR_I2 = .[[5]][[1]]$I2,
+      lnRR = .[[6]][[1]]$b, lnRR_lower = .[[6]][[1]]$ci.lb, lnRR_upper = .[[6]][[1]]$ci.ub, lnRR_se = .[[6]][[1]]$se, lnRR_I2 = .[[6]][[1]]$I2
   )  %>%
-  select(., GroupingTerm, lnCVR:lnRR_se)
+  select(., GroupingTerm, lnCVR:lnRR_I2)
 
@@
   mutate(
-    lnCVR = .[[4]][[1]]$b, lnCVR_lower = .[[4]][[1]]$ci.lb, lnCVR_upper = .[[4]][[1]]$ci.ub, lnCVR_se = .[[4]][[1]]$se,
-    lnVR = .[[5]][[1]]$b, lnVR_lower = .[[5]][[1]]$ci.lb, lnVR_upper = .[[5]][[1]]$ci.ub, lnVR_se = .[[5]][[1]]$se,
-    lnRR = .[[6]][[1]]$b, lnRR_lower = .[[6]][[1]]$ci.lb, lnRR_upper = .[[6]][[1]]$ci.ub, lnRR_se = .[[6]][[1]]$se
+ lnCVR = .[[4]][[1]]$b, lnCVR_lower = .[[4]][[1]]$ci.lb, lnCVR_upper = .[[4]][[1]]$ci.ub, lnCVR_se = .[[4]][[1]]$se,     lnCVR_I2 = .[[4]][[1]]$I2,
+      lnVR = .[[5]][[1]]$b, lnVR_lower = .[[5]][[1]]$ci.lb, lnVR_upper = .[[5]][[1]]$ci.ub, lnVR_se = .[[5]][[1]]$se, lnVR_I2 = .[[5]][[1]]$I2,
+      lnRR = .[[6]][[1]]$b, lnRR_lower = .[[6]][[1]]$ci.lb, lnRR_upper = .[[6]][[1]]$ci.ub, lnRR_se = .[[6]][[1]]$se, lnRR_I2 = .[[6]][[1]]$I2
   )  %>%
-    select(., GroupingTerm, lnCVR:lnRR_se)
+  select(., GroupingTerm, lnCVR:lnRR_I2)
 
@@
   mutate(
-    lnCVR = .[[2]][[1]]$b, lnCVR_lower = .[[2]][[1]]$ci.lb, lnCVR_upper = .[[2]][[1]]$ci.ub, lnCVR_se = .[[2]][[1]]$se, 
-    lnVR = .[[3]][[1]]$b, lnVR_lower = .[[3]][[1]]$ci.lb, lnVR_upper = .[[3]][[1]]$ci.ub, lnVR_se = .[[3]][[1]]$se,
-    lnRR = .[[4]][[1]]$b, lnRR_lower = .[[4]][[1]]$ci.lb, lnRR_upper = .[[4]][[1]]$ci.ub, lnRR_se = .[[4]][[1]]$se
+    lnCVR = .[[2]][[1]]$b, lnCVR_lower = .[[2]][[1]]$ci.lb, lnCVR_upper = .[[2]][[1]]$ci.ub, lnCVR_se = .[[2]][[1]]$se,     lnCVR_I2 = .[[2]][[1]]$I2,
+    lnVR = .[[3]][[1]]$b, lnVR_lower = .[[3]][[1]]$ci.lb, lnVR_upper = .[[3]][[1]]$ci.ub, lnVR_se = .[[3]][[1]]$se,     lnVR_I2 = .[[3]][[1]]$I2,
+    lnRR = .[[4]][[1]]$b, lnRR_lower = .[[4]][[1]]$ci.lb, lnRR_upper = .[[4]][[1]]$ci.ub, lnRR_se = .[[4]][[1]]$se, lnRR_I2 = .[[4]][[1]]$I2,
   )  %>%
-    select(., lnCVR:lnRR_se)
+    select(., lnCVR:lnRR_I2)
 
@@
 
-```{r}
+```{r FigS1, fig.height = 8, fig.width = 7}
 #### Combined Figure S1: overall Count data, Meta anlysis results, Heterogeneity
@@
 The orange-red bars represent trait groups with a female bias, blue-green bars male-biased traits.
-```{r}
+```{r FigS2, fig.height = 8, fig.width = 7}
 library(ggpubr)

### 2020-04-21 scripts/MouseSexDiffApril20_2020.Rmd
kable clean up

@@
 ```{r}
-kable(metacombo) %>%
+kable(metacombo, digits = 3) %>%
   kable_styling() %>%
@@
 overall2 <- bind_rows(Behaviour, Morphology, Metabolism, Physiology, Immunology, Hematology, Heart, Hearing, Eye, All)
+
+```
+### Supplemental Table 4_NEW
+```{r}
+kable(overall2, , digits = 3) %>%
+ kable_styling() %>%
+  scroll_box(width = "100%", height = "200px")
+
 ```
@@
 #adding male / female symbols for Figure 4B
+# additional packages for intergating male / female symbols in plot 4
+library(png)
+library(grid)
 
@@
 # Invidual table for heterogeneity across all traits
-# kable(metacombohetero) %>%
+# kable(metacombohetero,, digits = 3) %>%
  # kable_styling() %>%
@@
 ```{r}
-kable(heterog6) %>%
+kable(heterog6, digits = 3) %>%
   kable_styling() %>%

### 2020-04-21 scripts/MouseSexDiffApril20_2020.Rmd
To do: address MISSING comments

@@
 ```
-### Supplemental Table 4_NEW
+### Supplemental Table 4
+MISSING table descpition. Refer to in ms.
 ```{r}
@@
 ## Heterogeneity Table and Plot
-### Supplemental Table 4: "Heterogeneity within groups"
- SZ: missing a desciption so far.
+### Supplemental Table 5: "Heterogeneity within groups"
+ SZ: missing a desciption so far. MISSING!! Also: rearrange table structure, what does this show??
 ```{r}

### 2020-04-24 scripts/MouseSexDiffApril20_2020.Rmd
To do: address MISSING comments
naming of chunks, removal of messages

@@
 
-```{r}
+```{r packages}
 library(readr)
@@
 
-```{r}
+```{r PopStatsFunction}
 calculate_population_stats <- function(mydata, min_individuals = 5) {
@@
 
-```{r}
+```{r EffectSizeFunction}
 create_meta_analysis_effect_sizes <- function(mydata) {
@@
 
-```{r}
+```{r MetaAnalysesFunction}
 
@@
 Unfortuntaltely, that file can not be provided via github, as is too large (274MB).
-It will be freely accessible, uploaded on dryad.
-Link to dryad file HERE]
+It is freely accessible, uploaded on zenodo.org (https://zenodo.org/deposit/3759701)
 
@@
 
-```{r include=FALSE}
+```{r Table1_prep, include=FALSE}
 # Initial checks
@@
 
-```{r}
+```{r Table1}
 
@@
 
-```{r}
+```{r loop, message=FALSE, warning=FALSE, include=FALSE}
 
@@
 
-```{r}
+```{r cleanMeta1}
 results_alltraits_grouping2 <- 
@@
 
-```{r}
+```{r Table2_Meta1}
 # Here we double check numbers of trait parameters in the dataset
@@
 
-```{r}
+```{r corrTraits}
 
@@
 
-```{r}
+```{r Table3}
 kable(metacombo, digits = 3) %>%
@@
 
-```{r}
+```{r MetaGrouping}
 metacombo_final <- metacombo %>%
@@
 
-```{r}
+```{r MetaGroup_extraction}
 Behaviour <- overall1 %>% 
@@
 MISSING table descpition. Refer to in ms.
-```{r}
+```{r Table4}
 kable(overall2, , digits = 3) %>%
@@
 
-```{r}
+```{r Fig4_prep}
 
@@
 
-```{r}
+```{r Fig4_B}
 overall3 <- gather(overall2, parameter, value, c(lnCVR, lnRR), factor_key = TRUE)
@@
 
-# Metameta_Fig3_alltraits
+#Metameta_Fig3_alltraits
 ```
@@
 
-```{r}
-Fig4 <- ggarrange(malebias_Fig2_alltraits, Metameta_Fig3_alltraits,  nrow = 2, align = "v", heights = c(1, 1), labels = c("A", "B"))
+```{r Fig4}
+Fig4 <- ggarrange(malebias_Fig2_alltraits, Metameta_Fig3_alltraits,  nrow = 2, align = "v", heights = c(8, 8), labels = c("A", "B"))
 Fig4
@@
 The code below creates Figure 5A.
-```{r}
+```{r Fig5_prep}
 
@@
 
-```{r}
+```{r Fig5}
 #Joining the Parts:
@@
 The supplemental figures include lnVR (in addition to lnCVR and lnRR, as presented in Figures 4 and 5)
-```{r}
+```{r FigS1_prep}
 # *Prepare data for all traits
@@
 
-```{r}
+```{r hetero_loop, message=FALSE, warning=FALSE, include=FALSE }
 # Create dataframe to store results
@@
 
-```{r}
+```{r hetero}
 results.allhetero.grouping2 <- results.allhetero.grouping[results.allhetero.grouping$s.nlevels.strain.VR != 0, ]
@@
 create column with 1= different from zero, 0= zero included in CI (for Figure S2 B, top left panel)
-```{r}
+```{r FigS2_B}
 #Restructure data for plotting
@@
 Restructuring data with significant male bias (for Figure S2 B, top right panel)
-```{r}
+```{r FigS2_B_right}
 overall3.male.sigS <- gather(overall.male.plot3, parameter, value, c(lnCVR, lnVR, lnRR), factor_key = TRUE)
@@
 
-```{r}
+```{r Session}
 sessionInfo()

### 2020-04-27 scripts/MouseSexDiffApril20_2020.Rmd
label Figs 4A & 5A

@@
   aes(x = GroupingTerm, y = percent, fill = sex) +
+  ylab("Percentage") +
   geom_col() +
@@
     panel.grid.minor.x = element_blank(),
-    legend.position = "none",
-    axis.title.x = element_blank(),
+    legend.position= "none",
+    #axis.title.x = Percentage,
     axis.title.y = element_blank()
@@
 
-# malebias_Fig2_alltraits     #(panel A in Figure 4 in ms)
 ```
@@
 ```{r Fig4}
-Fig4 <- ggarrange(malebias_Fig2_alltraits, Metameta_Fig3_alltraits,  nrow = 2, align = "v", heights = c(8, 8), labels = c("A", "B"))
+Fig4 <- ggarrange(malebias_Fig2_alltraits, Metameta_Fig3_alltraits,  nrow = 2, align = "v", heights = c(9, 9), labels = c("A", "B"))
 Fig4
@@
     legend.position = "none",
-    axis.title.x = element_blank(),
+    #axis.title.x = element_blank(),
     axis.title.y = element_blank()
@@
   )
+
+  Fig5B <- annotate_figure(Fig5B,
+                bottom= text_grob("Effect Size", color = "black", face = "plain", size = 14))  # SUSI NEW
 

### 2020-04-27 scripts/MouseSexDiffApril20_2020.Rmd
labels Fiure S1 and S2, panel "a"

@@
 
-FigS1 <- ggarrange(malebias_FigS1_alltraits + xlab("percentage sex bias"), Metameta_FigS1_alltraits, HeteroS1, nrow = 3, align = "v", heights = c(1, 1, 1), labels = c("A", "B", "C"))
+FigS1 <- ggarrange(malebias_FigS1_alltraits, Metameta_FigS1_alltraits, HeteroS1, nrow = 3, align = "v", heights = c(1, 1, 1), labels = c("A", "B", "C"))
 FigS1
@@
 # end combination Figure 5
-FigS2 <- ggarrange(malebias_FigS2_sigtraits, malebias_Fig2_over10, FigS2b, FigS2d, ncol = 1, nrow = 4, heights = c(2.3, 2, 2.1, 2), labels = c("A", " ", "B", " "))
+FigS2 <- ggarrange(malebias_FigS2_sigtraits, malebias_Fig2_over10, FigS2b, FigS2d, ncol = 1, nrow = 4, heights = c(2.4, 2.1, 2.1, 2), labels = c("A", " ", "B", " "))
 FigS2

### 2020-04-28 scripts/MouseSexDiffApril20_2020.Rmd
additional Table incl I2 for significant sex bias traits

@@
     lnCVR = map_dbl(model_lnCVR, pluck(2)), lnCVR_lower = map_dbl(model_lnCVR, pluck(6)),
-    lnCVR_upper = map_dbl(model_lnCVR, pluck(7)), lnCVR_se = map_dbl(model_lnCVR, pluck(3))
-  ))[, c(1, 4:7)]
-add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.male.meta.CVR.b))
+    lnCVR_upper = map_dbl(model_lnCVR, pluck(7)), lnCVR_se = map_dbl(model_lnCVR, pluck(3)), 
+    lnCVR_I2 = map_dbl(model_lnCVR, pluck("I2"))
+  ))[, c(1, 4:8)]
+add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA, NA))) %>% setNames(names(plot3.male.meta.CVR.b))
 
@@
     lnVR = map_dbl(model_lnVR, pluck(2)), lnVR_lower = map_dbl(model_lnVR, pluck(6)),
-    lnVR_upper = map_dbl(model_lnVR, pluck(7)), lnVR_se = map_dbl(model_lnVR, pluck(3))
-  ))[, c(1, 4:7)]
+    lnVR_upper = map_dbl(model_lnVR, pluck(7)), lnVR_se = map_dbl(model_lnVR, pluck(3)),
+    lnVR_I2 = map_dbl(model_lnVR, pluck("I2"))
+  ))[, c(1, 4:8)]
 plot3.male.meta.VR.b <- plot3.male.meta.VR.b[order(plot3.male.meta.VR.b$GroupingTerm), ]
@@
     lnRR = map_dbl(model_lnRR, pluck(2)), lnRR_lower = map_dbl(model_lnRR, pluck(6)),
-    lnRR_upper = map_dbl(model_lnRR, pluck(7)), lnRR_se = map_dbl(model_lnRR, pluck(3))
-  ))[, c(1, 4:7)]
+    lnRR_upper = map_dbl(model_lnRR, pluck(7)), lnRR_se = map_dbl(model_lnRR, pluck(3)),
+    lnRR_I2 = map_dbl(model_lnRR, pluck("I2"))
+  ))[, c(1, 4:8)]
 plot3.male.meta.RR.b <- plot3.male.meta.RR.b[order(plot3.male.meta.RR.b$GroupingTerm), ]
@@
     lnCVR = map_dbl(model_lnCVR, pluck(2)), lnCVR_lower = map_dbl(model_lnCVR, pluck(6)),
-    lnCVR_upper = map_dbl(model_lnCVR, pluck(7)), lnCVR_se = map_dbl(model_lnCVR, pluck(3))
-  ))[, c(1, 4:7)]
-
-add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.female.meta.CVR.b))
+    lnCVR_upper = map_dbl(model_lnCVR, pluck(7)), lnCVR_se = map_dbl(model_lnCVR, pluck(3)),
+    lnCVR_I2 = map_dbl(model_lnCVR, pluck("I2"))
+  ))[, c(1, 4:8)]
+
+add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA,NA))) %>% setNames(names(plot3.female.meta.CVR.b))
 
@@
     lnVR = map_dbl(model_lnVR, pluck(2)), lnVR_lower = map_dbl(model_lnVR, pluck(6)),
-    lnVR_upper = map_dbl(model_lnVR, pluck(7)), lnVR_se = map_dbl(model_lnVR, pluck(3))
-  ))[, c(1, 4:7)]
+    lnVR_upper = map_dbl(model_lnVR, pluck(7)), lnVR_se = map_dbl(model_lnVR, pluck(3)),
+    lnVR_I2 = map_dbl(model_lnVR, pluck("I2"))
+  ))[, c(1, 4:8)]
 
@@
     lnRR = map_dbl(model_lnRR, pluck(2)), lnRR_lower = map_dbl(model_lnRR, pluck(6)),
-    lnRR_upper = map_dbl(model_lnRR, pluck(7)), lnRR_se = map_dbl(model_lnRR, pluck(3))
-  ))[, c(1, 4:7)]
+    lnRR_upper = map_dbl(model_lnRR, pluck(7)), lnRR_se = map_dbl(model_lnRR, pluck(3)),
+    lnRR_I2 = map_dbl(model_lnRR, pluck("I2"))
+  ))[, c(1, 4:8)]
 
@@
 # Metameta_Fig3_female.sig #(Figure 5B left panel)
+```
+#### Supplemental Table 5
+Table o
+
+```{r}
+
+female <- (overall.female.plot3)
+female$Sex <- c("female")
+
+male <- (overall.male.plot3)
+male$Sex <- c("male")
+
+mf_sig <- rbind(female,male)
+mf_sig <- mf_sig [, c(1,17,2:16)]
+
+mf_sig <- mf_sig %>% arrange(desc(GroupingTerm))
+
+kable(mf_sig) %>%
+  kable_styling() %>%
+  scroll_box(width = "100%", height = "300px")
 ```

### 2020-04-28 scripts/MouseSexDiffApril20_2020.Rmd
Adding of text to tables. SHINICHI to check / change

@@
   dplyr::summarize(MeanCVR = mean(lnCVR), MeanVR = mean(lnVR), MeanRR = mean(lnRR))
-```
-
+
+```
 ### Supplemental Table 3: "Meta-analysis results"
@@
 
-### Performing meta-analyses (3 for each of the 9 grouping terms: lnCVR, lnVR, lnRR)
+### Performing meta-analyses 
+Three for each of the 9 grouping terms: lnCVR, lnVR, lnRR
 
@@
 ```
-### Supplemental Table 4
-MISSING table descpition. Refer to in ms.
+### Supplemental Table 4: "Meta-analysis on Functional Trait Groups"
+SHINICHI
+This table summarizes our overall meta-analyses on the functional trait group level ("GroupingTerm").
+Results for lnCVR, lnVR and lnRR and their respective upper and lower 95% CI's, standard error and I2 values are provided.
 ```{r Table4}
-kable(overall2, , digits = 3) %>%
+kable(overall2, digits = 3) %>%
  kable_styling() %>%
@@
 ```
-#### Supplemental Table 5
-Table o
+### Supplemental Table 5
+SHINICHI
+This table provides some of the data plotted in Figures 5 and Figure S2.
+Here, we provide an overview over meta-analysis results performed on traits that were significantly biased to either sex.
+This table summarizes findings for both sexes and the respective functional trait groups.
 
@@
 
-kable(mf_sig) %>%
+kable(mf_sig, digits = 3) %>%
   kable_styling() %>%
@@
 
-####  Figure 5
+###  Figure 5
 Sex biases in trait values across trait groups (Step J in Figure 3).
@@
 
-# Supplemental Plots
-## Figure S1 
-### Including lnVR
-### Count data, including lnVR (Fig S1 panel A)
+# Supplemental Plots and Tables
+### Figure S1 
+#### Including lnVR
+#### Count data, including lnVR (Fig S1 panel A)
 
@@
 ## Heterogeneity Table and Plot
-### Supplemental Table 5: "Heterogeneity within groups"
- SZ: missing a desciption so far. MISSING!! Also: rearrange table structure, what does this show??
+### Supplemental Table 6: "Heterogeneity within groups"
+SHINICHI
+This table summarizes our findings on heterogeneity due to institutions and mouse strains.
+These results are based on meta-analyses on sigma^2 and errors for mouse strains and centers (Institutions), following the identical workflow from above.
+
 ```{r}
-kable(heterog6, digits = 3) %>%
+
+het <- heterog6 %>%
+  pivot_wider(names_from = parameter, values_from = value:ci.h) %>%
+  rename(lnCVR = value_heteroCVR, lnCVR_lower = ci.low_heteroCVR, lnCVR_higher = ci.high_heteroCVR, 
+       lnVR = value_heteroVR, lnVR_lower = ci.low_heteroVR, lnVR_higher = ci.high_heteroVR, 
+       lnRR = value_heteroRR, lnRR_lower = ci.low_heteroRR, lnRR_higher = ci.high_heteroRR,
+       CVR = mean_heteroCVR, VR = mean_heteroVR, RR = mean_heteroRR,  CVR_lower = ci.l_heteroCVR, 
+       VR_lower = ci.l_heteroVR, RR_lower = ci.l_heteroRR, 
+       CVR_higher = ci.h_heteroCVR, VR_higher = ci.h_heteroVR, RR_higher = ci.h_heteroRR) %>%
+  select(1,2,5,8,3,6,9,4,7,10,14,17,20,15,18,21,16,19,22)
+
+kable(het, digits = 3) %>%
   kable_styling() %>%
   scroll_box(width = "100%", height = "200px")
+
 ```

### 2020-04-29 scripts/MouseSexDiffApril20_2020.Rmd
space out fig S2

@@
 ```{r Fig4}
-Fig4 <- ggarrange(malebias_Fig2_alltraits, Metameta_Fig3_alltraits,  nrow = 2, align = "v", heights = c(9, 9), labels = c("A", "B"))
+Fig4 <- ggarrange(malebias_Fig2_alltraits, Metameta_Fig3_alltraits,  nrow = 2, align = "v", heights = c(10, 9), labels = c("A", "B"))
 Fig4
@@
 
-FigS1 <- ggarrange(malebias_FigS1_alltraits, Metameta_FigS1_alltraits, HeteroS1, nrow = 3, align = "v", heights = c(1, 1, 1), labels = c("A", "B", "C"))
+FigS1 <- ggarrange(malebias_FigS1_alltraits, Metameta_FigS1_alltraits, HeteroS1, nrow = 3, align = "v", heights = c(1.1, 1, 1), labels = c("A", "B", "C"))
 FigS1
@@
 The orange-red bars represent trait groups with a female bias, blue-green bars male-biased traits.
-```{r FigS2, fig.height = 8, fig.width = 7}
+```{r FigS2, fig.height = 10, fig.width = 8}
 library(ggpubr)
 FigS2b <- ggarrange(Metameta_FigS2_female.sig, Metameta_FigS2_male.sig,
-  ncol = 2, nrow = 1, widths = c(1, 1.30), heights = c(1, 1)
+  ncol = 2, nrow = 1, widths = c(1, 1.30), heights = c(1.2, 1.2)
 )
@@
 # end combination Figure 5
-FigS2 <- ggarrange(malebias_FigS2_sigtraits, malebias_Fig2_over10, FigS2b, FigS2d, ncol = 1, nrow = 4, heights = c(2.4, 2.1, 2.1, 2), labels = c("A", " ", "B", " "))
+FigS2 <- ggarrange(malebias_FigS2_sigtraits, malebias_Fig2_over10, FigS2b, FigS2d, ncol = 1, nrow = 4, heights = c(2.5, 2.2, 2.1, 2), labels = c("A", " ", "B", " "))
 FigS2
-#ggsave("FigS2_Bias.pdf", plot = FigS2, width = 7, height = 8)
 ```

### 2020-04-30 scripts/MouseSexDiffApril20_2020.Rmd
Just trying to clean up a bit

@@
 library(here)
-# additional packages for intergating male / female symbols in plot 4
+# additional packages for incorporating male / female symbols in plot 4
 library(png)
@@
 ## Functions 
-for preparing the data for meta analyses
-
-### 1) Subsetting data
-Create function for sub-setting the data to choose only one data point per individual per trait: "data_subset_parameterid_individual_by_age"
+Functions needed for preparing the data for meta analyses
+
+### 1) Sub-setting data
+Create a function for sub-setting the data to choose only one data point per individual per trait: "data_subset_parameterid_individual_by_age"
 
@@
 ### 2) "Population statistics"
-Create function called: "calculate_population_stats"
-This function groups animals from the same strain and same insitiution together.
-This is done for each trait seoarately, and only for traits that have been measured in both sexes.
+Create a function called: "calculate_population_stats"
+This function groups animals from the same strain and institution together.
+This is done for each trait separately, and only for traits that have been measured in both sexes.
 Any group containing fewer than 5 individuals is excluded.
@@
       x_sd = sd(data_point),
-      n_ind = n()
-    ) %>%
+      n_ind = n()) %>%
     ungroup() %>%
@@
     group_by(population) %>%
-    mutate(
-      n_sex = n_distinct(sex)
-    ) %>%
+    mutate(n_sex = n_distinct(sex)) %>%
     ungroup() %>%
@@
 
-This step we have already done and provide a cleaned up file which is less computing intensive and which we have saved in a folder called `export`.
-However, the cvs is provided in case this is preferred to be attempted, following the steps below: [This code is currently excluded from showing in this html file, but can be viewed and enabled / run in the downloadable .rmd file.
+We have already done this step and provide a cleaned up file which is less computationally intensive to deal with.
+The file has been saved in a folder called `export`.
+However, the `.csv` is provided in case this is preferred and can be imported and processed using following the steps below: [This code is currently excluded from showing in this `.html` file, but can be viewed and enabled / run in the down-loadable .rmd file.
 However, it requires the .gz file containing the raw data in the "export" folder.
-Unfortuntaltely, that file can not be provided via github, as is too large (274MB).
-It is freely accessible, uploaded on zenodo.org (https://zenodo.org/deposit/3759701)
+Unfortunately, that file can not be provided via Github, as it is too large (274MB).
+However, it is freely accessible and uploaded to zenodo.org (https://zenodo.org/deposit/3759701)
 
@@
 
-### Supplemental Table 1: "Strains and Center Sample Sizes"
-This table summarises the available numbers of male and female mice from each strain and originating institution.
-
-```{r Table1_prep, include=FALSE}
-# Initial checks
-length(unique(data$parameter_name)) # 232 traits
-length(unique(data$parameter_group)) # 161 parameter groups
-length(unique(data$procedure_name)) # 26 procedure groups
-length(unique(data$biological_sample_id)) # 27147 individial mice  
-# To show a table with number of males and females per strain per production center:
-
-ST1 <- (cbind(data %>% group_by(production_center, strain_name) %>% count(biological_sample_id, sex) %>% count(sex) %>% print(n = Inf))) 
-```
-
-```{r Table1}
-
-kable(ST1) %>%
-  kable_styling() %>%
-  scroll_box(width = "60%", height = "200px")
-
-```
-
 # Meta-analyses
@@
   dplyr::summarize(MeanCVR = mean(lnCVR), MeanVR = mean(lnVR), MeanRR = mean(lnRR))
-
-```
-### Supplemental Table 3: "Meta-analysis results"
-
-We use this corrected (for correlated traits) "results" table, which contains each of the meta-analytic means for all effect sizes of interest, for further analyses.
-We further use this table as part of the Shiny App, which is able to provide the percentage differences between males and females for mean, variance and coefficient of variance.
-
-```{r Table3}
-kable(metacombo, digits = 3) %>%
-  kable_styling() %>%
-  scroll_box(width = "100%", height = "200px")
 
@@
 ```
-### Supplemental Table 5
-SHINICHI
-This table provides some of the data plotted in Figures 5 and Figure S2.
-Here, we provide an overview over meta-analysis results performed on traits that were significantly biased to either sex.
-This table summarizes findings for both sexes and the respective functional trait groups.
-
-```{r}
-
-female <- (overall.female.plot3)
-female$Sex <- c("female")
-
-male <- (overall.male.plot3)
-male$Sex <- c("male")
-
-mf_sig <- rbind(female,male)
-mf_sig <- mf_sig [, c(1,17,2:16)]
-
-mf_sig <- mf_sig %>% arrange(desc(GroupingTerm))
-
-kable(mf_sig, digits = 3) %>%
-  kable_styling() %>%
-  scroll_box(width = "100%", height = "300px")
-```
 
@@
 # Supplemental Plots and Tables
+
+### Supplemental Table S1: "Strains and Center Sample Sizes"
+This table summarises the available numbers of male and female mice from each strain and originating institution.
+
+```{r Table1_prep, include=FALSE}
+# Initial checks
+length(unique(data$parameter_name)) # 232 traits
+length(unique(data$parameter_group)) # 161 parameter groups
+length(unique(data$procedure_name)) # 26 procedure groups
+length(unique(data$biological_sample_id)) # 27147 individial mice  
+# To show a table with number of males and females per strain per production center:
+
+ST1 <- (cbind(data %>% group_by(production_center, strain_name) %>% count(biological_sample_id, sex) %>% count(sex) %>% print(n = Inf))) 
+```
+
+```{r Table1}
+
+kable(ST1) %>%
+  kable_styling() %>%
+  scroll_box(width = "60%", height = "200px")
+
+```
+
+### Supplemental Table S3: "Meta-analysis results"
+
+We use this corrected (for correlated traits) "results" table, which contains each of the meta-analytic means for all effect sizes of interest, for further analyses.
+We further use this table as part of the Shiny App, which is able to provide the percentage differences between males and females for mean, variance and coefficient of variance.
+
+```{r Table3}
+  kable(metacombo, digits = 3) %>%
+  kable_styling() %>%
+  scroll_box(width = "100%", height = "200px")
+
+```
+
+### Supplemental Table S5: "Sex-biased effect sizes"
+SHINICHI
+This table provides some of the data plotted in Figures 5 and Figure S2.
+Here, we provide an overview over meta-analysis results performed on traits that were significantly biased to either sex.
+This table summarizes findings for both sexes and the respective functional trait groups.
+
+```{r}
+
+female <- (overall.female.plot3)
+female$Sex <- c("female")
+
+male <- (overall.male.plot3)
+male$Sex <- c("male")
+
+mf_sig <- rbind(female,male)
+mf_sig <- mf_sig [, c(1,17,2:16)]
+
+mf_sig <- mf_sig %>% arrange(desc(GroupingTerm))
+
+kable(mf_sig, digits = 3) %>%
+  kable_styling() %>%
+  scroll_box(width = "100%", height = "300px")
+```
+
+### Supplemental Table S6: "Heterogeneity within groups"
+SHINICHI
+This table summarizes our findings on heterogeneity due to institutions and mouse strains.
+These results are based on meta-analyses on sigma^2 and errors for mouse strains and centers (Institutions), following the identical workflow from above.
+
+```{r}
+
+het <- heterog6 %>%
+  pivot_wider(names_from = parameter, values_from = value:ci.h) %>%
+  rename(lnCVR = value_heteroCVR, lnCVR_lower = ci.low_heteroCVR, lnCVR_higher = ci.high_heteroCVR, 
+       lnVR = value_heteroVR, lnVR_lower = ci.low_heteroVR, lnVR_higher = ci.high_heteroVR, 
+       lnRR = value_heteroRR, lnRR_lower = ci.low_heteroRR, lnRR_higher = ci.high_heteroRR,
+       CVR = mean_heteroCVR, VR = mean_heteroVR, RR = mean_heteroRR,  CVR_lower = ci.l_heteroCVR, 
+       VR_lower = ci.l_heteroVR, RR_lower = ci.l_heteroRR, 
+       CVR_higher = ci.h_heteroCVR, VR_higher = ci.h_heteroVR, RR_higher = ci.h_heteroRR) %>%
+  select(1,2,5,8,3,6,9,4,7,10,14,17,20,15,18,21,16,19,22)
+
+kable(het, digits = 3) %>%
+  kable_styling() %>%
+  scroll_box(width = "100%", height = "200px")
+
+```
+
 ### Figure S1 
@@
 
-## Heterogeneity Table and Plot
-### Supplemental Table 6: "Heterogeneity within groups"
-SHINICHI
-This table summarizes our findings on heterogeneity due to institutions and mouse strains.
-These results are based on meta-analyses on sigma^2 and errors for mouse strains and centers (Institutions), following the identical workflow from above.
-
-```{r}
-
-het <- heterog6 %>%
-  pivot_wider(names_from = parameter, values_from = value:ci.h) %>%
-  rename(lnCVR = value_heteroCVR, lnCVR_lower = ci.low_heteroCVR, lnCVR_higher = ci.high_heteroCVR, 
-       lnVR = value_heteroVR, lnVR_lower = ci.low_heteroVR, lnVR_higher = ci.high_heteroVR, 
-       lnRR = value_heteroRR, lnRR_lower = ci.low_heteroRR, lnRR_higher = ci.high_heteroRR,
-       CVR = mean_heteroCVR, VR = mean_heteroVR, RR = mean_heteroRR,  CVR_lower = ci.l_heteroCVR, 
-       VR_lower = ci.l_heteroVR, RR_lower = ci.l_heteroRR, 
-       CVR_higher = ci.h_heteroCVR, VR_higher = ci.h_heteroVR, RR_higher = ci.h_heteroRR) %>%
-  select(1,2,5,8,3,6,9,4,7,10,14,17,20,15,18,21,16,19,22)
-
-kable(het, digits = 3) %>%
-  kable_styling() %>%
-  scroll_box(width = "100%", height = "200px")
-
-```
-
 ### Figure S1

### 2020-04-30 scripts/MouseSexDiffApril20_2020.Rmd
Re-organised the structure of the supplement to make it easier to follow the general structure, and so that Tables and Figures will match and be easier to find with the MS

@@
 # Set-up
-
-## Loading packages & custom functions
-
-## Packages
+## 1. Packages
 
@@
 
-## Functions 
+## 2. Functions 
 Functions needed for preparing the data for meta analyses
@@
 
-### 2) "Population statistics"
+### 2) Population statistics
 Create a function called: "calculate_population_stats"
@@
 
-## Load & clean data
+## 3. Load & clean data
 
@@
 
-### Loop: Meta-analyses on all traits
+### 1.1: Loop: Meta-analyses on all traits
 
@@
 
-### Merging datasets & removal of non-converged traits
+### 1.2: Merging datasets & removal of non-converged traits
 
@@
 
-### Dealing with Correlated Parameters, preparation
+### 2.1: Dealing with Correlated Parameters, preparation
 
@@
 
-#### Collapsing and merging correlated parameters
-Count of number of parameter names (correlated sub-traits) in each parameter group (par_group_size)
-
-### Supplemental Table 2: "Numbers of correlated and uncorrelated traits"
+### 2.2: Collapsing and merging correlated parameters, preparation for Table S2
+Count the number of parameter names (correlated sub-traits) in each parameter group (par_group_size).
 This serves to identify and separate the traits that are correlated from the full dataset that can be processed as is.
@@
 
-# Table detailing numbers of correlated and uncorrelated traits
-kable(cbind(meta1 %>% count(parameter_group))) %>%
-  kable_styling() %>%
-  scroll_box(width = "60%", height = "200px")
-
-```
-
-#### Meta-analyses on correlated (sub-)traits, using robumeta` 
+```
+
+### 2.3: Meta-analyses on correlated (sub-)traits, using `robumeta` 
 Here we pepare the subset of the data (using nest()), and in this first step the model of the meta-analysis effect sizes are calculated
@@
 
-### Performing meta-analyses 
+### 3.1: Performing meta-analyses 
 Three for each of the 9 grouping terms: lnCVR, lnVR, lnRR
-
-#### Preparation of data
+#### 3.1.1: Preparing the data
 
@@
 
-### Re-structuring the data for each grouping term
+#### 3.1.2: Re-structuring the data for each grouping term
 We here delete unused variables, and select the respective effect sizes.
@@
 ```
-### Supplemental Table 4: "Meta-analysis on Functional Trait Groups"
-SHINICHI
-This table summarizes our overall meta-analyses on the functional trait group level ("GroupingTerm").
-Results for lnCVR, lnVR and lnRR and their respective upper and lower 95% CI's, standard error and I2 values are provided.
-```{r Table4}
-kable(overall2, digits = 3) %>%
- kable_styling() %>%
-  scroll_box(width = "100%", height = "200px")
-
-```
-
-# Visualisation
-## Preparation for Figure 4 
-#### Count data, based on First-order meta-analysis results
+
+# Visualising meta-analysis results
+## 1. Preparation for Figure 4 
+#### 1.1: Count data, based on First-order meta-analysis results
 This includes all separate eligible traits.
@@
 
-###  Overall results of second order meta-analysis (Figure 4, Panel B)
-#### Re-structure data for plotting 
+#### 1.2: Overall results of second order meta-analysis (Figure 4, Panel B)
+#### 1.3: Re-structure data for plotting 
 Data are re-structured, and grouping terms are being re-ordered
@@
 
-### Figure 4
+## 2. Figure 4
 
@@
 
-## Preparation for Figure 5: Sex bias.
-#### Preparing data for traits with CI not overlapping 0
+## 3. Preparation for Figure 5
+#### 3.1: Preparing data for traits with CI not overlapping 0
 To further investigate sex bias in this dataset, and in particular if the extent of sex bias differs between traits, we investigate the magnitude of male- and female bias in significantly different traits on (both for means and variability)
@@
 
-###  Figure 5
+## 4. Figure 5
 Sex biases in trait values across trait groups (Step J in Figure 3).
@@
 
-# Supplemental Plots and Tables
-
-### Supplemental Table S1: "Strains and Center Sample Sizes"
+# Supplemental Tables and Figures
+
+## Supplemental Tables
+#### 1. Supplemental Table S1: "Strains and Center Sample Sizes"
   This table summarises the available numbers of male and female mice from each strain and originating institution.
 
-```{r Table1_prep, include=FALSE}
+```{r Table1_prep}
   # Initial checks
@@
 ```
-
 ```{r Table1}
@@
 
-### Supplemental Table S3: "Meta-analysis results"
+#### 2. Supplemental Table S2: "Numbers of correlated and uncorrelated traits"
+
+```{r, TableS2}  
+# Table detailing numbers of correlated and uncorrelated traits
+kable(cbind(meta1 %>% count(parameter_group))) %>%
+  kable_styling() %>%
+  scroll_box(width = "60%", height = "200px")
+```
+
+#### 3. Supplemental Table S3: "Meta-analysis results"
 
@@
 
-### Supplemental Table S5: "Sex-biased effect sizes"
+#### 4. Supplemental Table S4: "Meta-analysis on Functional Trait Groups"
+  SHINICHI
+  This table summarizes our overall meta-analyses on the functional trait group level ("GroupingTerm").
+Results for lnCVR, lnVR and lnRR and their respective upper and lower 95% CI's, standard error and I2 values are provided.
+```{r Table4}
+  kable(overall2, digits = 3) %>%
+   kable_styling() %>%
+  scroll_box(width = "100%", height = "200px")
+```
+
+#### 5. Supplemental Table S5: "Sex-biased effect sizes"
   SHINICHI
@@
 
-### Supplemental Table S6: "Heterogeneity within groups"
+#### 6. Supplemental Table S6: "Heterogeneity within groups"
   SHINICHI
@@
 
-### Figure S1 
-#### Including lnVR
-#### Count data, including lnVR (Fig S1 panel A)
-
+## Supplemental Figures
+### 1. Preparation for Figure S1
+#### 1.1: Preparing the data
 The supplemental figures include lnVR (in addition to lnCVR and lnRR, as presented in Figures 4 and 5)
@@
 
-### Heterogeneity
+#### 1.2: Preparing heterogeneity
 The analysis for heterogeneity follows the workflow of the above steps for the different meta-analyses.
@@
 
-### Figure S1
+### 2. Figure S1
 
@@
 
-### Preparations for Figure S2 A
+### 3. Preparation for Figure S2
+#### 3.1: Preparation for Figure S2 A
 This Figure extends Figure 4, as it includes results not only for lnCVR and lnRR but also lnCVR.
@@
 
-### Preparation for Figure S2 B (second-order meta-analysis)
-#### Female Figure, significant and highly biased traits (Figure S2 B, left hand side panels)
+#### 3.2: Preparation for Figure S2 B (second-order meta-analysis)
+#### 3.3: Female Figure, significant and highly biased traits (Figure S2 B, left hand side panels)
 Preparing data for traits with CI not overlapping 0: 
@@
 ```
-#### Male Figure, significant and highly biased traits (Figure S2 B, right hand side panels)
+#### 3.4: Male Figure, significant and highly biased traits (Figure S2 B, right hand side panels)
 Restructuring data with significant male bias (for Figure S2 B, top right panel)
@@
 
-### Figure S2
+### 4. Figure S2
 
@@
 
-## Acknowledgements
-tbd
-
 ## R Session Information

### 2020-05-01 scripts/MouseSexDiffApril20_2020.Rmd
small change
updating app Pic and direction m/f supp table 6 moved to bottom (to allow knitting)

@@
 
-#### 6. Supplemental Table S6: "Heterogeneity within groups"
-  SHINICHI
-  This table summarizes our findings on heterogeneity due to institutions and mouse strains.
-These results are based on meta-analyses on sigma^2 and errors for mouse strains and centers (Institutions), following the identical workflow from above.
-
-```{r}
-
-  het <- heterog6 %>%
-    pivot_wider(names_from = parameter, values_from = value:ci.h) %>%
-    rename(lnCVR = value_heteroCVR, lnCVR_lower = ci.low_heteroCVR, lnCVR_higher = ci.high_heteroCVR, 
-         lnVR = value_heteroVR, lnVR_lower = ci.low_heteroVR, lnVR_higher = ci.high_heteroVR, 
-         lnRR = value_heteroRR, lnRR_lower = ci.low_heteroRR, lnRR_higher = ci.high_heteroRR,
-         CVR = mean_heteroCVR, VR = mean_heteroVR, RR = mean_heteroRR,  CVR_lower = ci.l_heteroCVR, 
-         VR_lower = ci.l_heteroVR, RR_lower = ci.l_heteroRR, 
-         CVR_higher = ci.h_heteroCVR, VR_higher = ci.h_heteroVR, RR_higher = ci.h_heteroRR) %>%
-    select(1,2,5,8,3,6,9,4,7,10,14,17,20,15,18,21,16,19,22)
-
-  kable(het, digits = 3) %>%
-    kable_styling() %>%
-    scroll_box(width = "100%", height = "200px")
-
-```
-
 ## Supplemental Figures
@@
 ```
+#### 6. Supplemental Table S6: "Heterogeneity within groups"
+  SHINICHI
+  This table summarizes our findings on heterogeneity due to institutions and mouse strains.
+These results are based on meta-analyses on sigma^2 and errors for mouse strains and centers (Institutions), following the identical workflow from above.
+
+```{r}
+
+  het <- heterog6 %>%
+    pivot_wider(names_from = parameter, values_from = value:ci.h) %>%
+    rename(lnCVR = value_heteroCVR, lnCVR_lower = ci.low_heteroCVR, lnCVR_higher = ci.high_heteroCVR, 
+         lnVR = value_heteroVR, lnVR_lower = ci.low_heteroVR, lnVR_higher = ci.high_heteroVR, 
+         lnRR = value_heteroRR, lnRR_lower = ci.low_heteroRR, lnRR_higher = ci.high_heteroRR,
+         CVR = mean_heteroCVR, VR = mean_heteroVR, RR = mean_heteroRR,  CVR_lower = ci.l_heteroCVR, 
+         VR_lower = ci.l_heteroVR, RR_lower = ci.l_heteroRR, 
+         CVR_higher = ci.h_heteroCVR, VR_higher = ci.h_heteroVR, RR_higher = ci.h_heteroRR) %>%
+    select(1,2,5,8,3,6,9,4,7,10,14,17,20,15,18,21,16,19,22)
+
+  kable(het, digits = 3) %>%
+    kable_styling() %>%
+    scroll_box(width = "100%", height = "200px")
+
+```
 

### 2020-05-01 SexDifference_Shiny/app.R

@@ -44,7 +44,7 @@ ui <- fluidPage(mainPanel(theme = shinythemes::themeSelector()),
    ),
   
     mainPanel(
-        tags$img(src = "008169.png", width = 580, height =340)
+        tags$img(src = "PCWmice1.jpg", width = 220, height =120 )
        ) 
     )    
 
@@ -61,7 +61,7 @@ server <- function(input, output){
         
         # Calculate percent diff
             perc_difference <- ifelse(odds_ratio < 1, (1-odds_ratio)*100, (odds_ratio-1)*100)
-            direct <- ifelse(odds_ratio < 1, "Males >", "Females >") 
+            direct <- ifelse(odds_ratio < 1, "Females >", "Males >") 
             
         # Table output
             table <- rbind(paste0(round(perc_difference, digits = 2), " %"), direct)
@@ -81,7 +81,7 @@ server <- function(input, output){
       
       # Calculate percent diff
       perc_difference <- ifelse(odds_ratio < 1, (1-odds_ratio)*100, (odds_ratio-1)*100)
-      direct <- ifelse(odds_ratio < 1, "Males >", "Females >") 
+      direct <- ifelse(odds_ratio < 1, "Females >", "Males >") 
       
       # Table output
       table <- rbind(paste0(round(perc_difference, digits = 2), " %"), direct)
@@ -101,7 +101,7 @@ server <- function(input, output){
       
       # Calculate percent diff
       perc_difference <- ifelse(odds_ratio < 1, (1-odds_ratio)*100, (odds_ratio-1)*100)
-      direct <- ifelse(odds_ratio < 1, "Males >", "Females >") 
+      direct <- ifelse(odds_ratio < 1, "Females >", "Males >") 
       
       # Table output
       table <- rbind(paste0(round(perc_difference, digits = 2), " %"), direct)

### 2020-05-12 scripts/MouseSexDiffApril20_2020.Rmd
Just doing some cleaning and implementing escalc instead of Al's functions

@@
   mydata %>%
-    group_by(population, strain_name, production_center, sex) %>%
-    summarise(
-      trait = parameter_name[1],
+    group_by(population, 
+             strain_name, 
+             production_center, 
+             sex) %>%
+    summarise(trait = parameter_name[1],
               x_bar = mean(data_point),
@@
 }
+
+multi_spread <- function(df, key, value) {
+    # quote key
+    keyq <- rlang::enquo(key)
+    # break value vector into quotes
+    valueq <- rlang::enquo(value)
+    s <- rlang::quos(!!valueq)
+    df %>% gather(variable, value, !!!s) %>%
+        unite(temp, !!keyq, variable) %>%
+        spread(temp, value)
+}
+
+# Will calculate population stats and exclude data that is irrelevant and not useful, it will also just convert the data straight away to wide format as opposed to long, which I think is making things more complicated when effect sizes are calculated.
+
+calculate_population_stats_new <- function(mydata, min_individuals = 5){
+    mydata %>% 
+    group_by(population,
+             production_center,  
+             strain_name,  
+             sex) %>%
+    summarise(trait  = parameter_name[1],
+              x_bar  = mean(data_point, na.rm = TRUE),
+              x_sd   =   sd(data_point, na.rm = TRUE),
+              n_ind  = n()) %>%
+    ungroup() %>%
+    filter(n_ind > min_individuals) %>%   # NOTE here that you are excluding data with 5 exactly....
+    group_by(population) %>%
+    filter(all(c("male", "female") %in% sex)) %>% # Removes any entries where only 1 sex is present
+    multi_spread(sex, c(x_bar, x_sd, n_ind))      # Spreads the data out into wide format, so sexes are beside each other which is more typical of meta-analytic data
+}
+
 ```
@@
 ```{r EffectSizeFunction}
+
+#This function should mostly replace the entire function below, but I am still not quite sure what is happening in places.
+Adding all effect sizes together (maintaining the naming), err seems to be added to each trait?
+That needs to be added.It will make use of escalc which has the correct equations for effect size calculations.
+create_meta_analysis_effect_sizes_new <- function(mydata, measure = c("CVR", "VR", "ROM")){
+  for(i in 1:length(measure)){
+    mydata <- metafor::escalc(m1i  = female_x_bar, 
+                              m2i  = male_x_bar, 
+                              sd1i = female_x_sd, 
+                              sd2i = male_x_sd, 
+                              n1i  = female_n_ind, 
+                              n2i  = male_n_ind, 
+                              data = mydata, 
+                           measure = measure[i], 
+                         var.names = c(paste0("effect_size_", measure[i]), 
+                                      paste0("sample_variance_", measure[i])),
+                            append = TRUE)
+    }
+    return(mydata)
+}
+
+## Can delete all the below ###### The above function does same thing, but uses simplified dataset and also reorganises it so no need for input dataframe.
+This also means we can remove the next section with Al's function as escalc has these built in anyway.
 create_meta_analysis_effect_sizes <- function(mydata) {
@@
     )
+
 }
@@
 results_alltraits_grouping <- 
-    tibble(id = 1:n, lnCVR=0, lnCVR_lower=0, lnCVR_upper=0, 
-           lnCVR_se=0, lnVR=0, lnVR_lower=0, lnVR_upper=0, 
-           lnVR_se=0, lnRR=0, lnRR_lower=0, lnRR_upper=0, lnRR_se=0, sampleSize=0, trait=0)
+    tibble(id = 1:n, 
+           lnCVR=0, lnCVR_lower=0, lnCVR_upper=0,lnCVR_se=0, 
+            lnVR=0,  lnVR_lower=0,  lnVR_upper=0, lnVR_se=0, 
+            lnRR=0,  lnRR_lower=0,  lnRR_upper=0, lnRR_se=0, 
+           sampleSize=0, trait=0)
 
@@
     {
-      results <- data %>% 
+
+    #NOTE: results and results 2 should now be equivalent and produce the same thing except that results 2 has the columns added in with raw effect sizes, which I think is wise if we can keep them.
+Otherwise, the naming should be the same.
+I've checked quite a few t's and all looks the same.
+results 2 just has more columns.
+      results <- data.frame(data %>% 
         data_subset_parameterid_individual_by_age(t) %>%
         calculate_population_stats() %>%
-        create_meta_analysis_effect_sizes()
+        create_meta_analysis_effect_sizes())
+
+      results2 <- data %>%
+       data_subset_parameterid_individual_by_age(t) %>%
+       calculate_population_stats_new() %>%
+       create_meta_analysis_effect_sizes_new() %>%
+       mutate(err = seq_len(n()))
 
@@
                              random = list(~ 1 | strain_name, ~ 1 | production_center, ~ 1 | err), 
-                             control = list(optimizer = "optim", optmethod = "Nelder-Mead", 
-                                            maxit = 1000), verbose = F, data = results)
+                             control = list(optimizer = "optim", 
+                                            optmethod = "Nelder-Mead", 
+                                            maxit = 1000), 
+                             verbose = F, 
+                             data = results)
 
@@
 }
-
 ```

### 2020-05-15 scripts/MouseSexDiffApril20_2020.Rmd
Just simplifying and cleaning

--- 2020-05-01 scripts/MouseSexDiffApril20_2020.Rmd
@@
 ```{r packages}
-library(readr)
-library(dplyr)
-library(metafor)
-library(devtools)
-library(purrr)
-library(tidyverse)
-library(tidyr)
-library(tibble)
-library(kableExtra)
-library(robumeta)
-library(ggpubr)
-library(ggplot2)
-library(here)
-# additional packages for incorporating male / female symbols in plot 4
-library(png)
-library(grid)
+library(pacman)
+pacman::p_load(readr, dplyr,metafor, devtools, purrr, tidyverse, tidyr, tibble, kableExtra, robumeta, ggpubr, ggplot2, png, grid, here)
 ```
@@
 ```{r PopStatsFunction}
-calculate_population_stats <- function(mydata, min_individuals = 5) {
+
+multi_spread <- function(df, key, value) {
+    # quote key
+    keyq <- rlang::enquo(key)
+    # break value vector into quotes
+    valueq <- rlang::enquo(value)
+    s <- rlang::quos(!!valueq)
+    df %>% gather(variable, value, !!!s) %>%
+        unite(temp, !!keyq, variable) %>%
+        spread(temp, value)
+}
+
+# Will calculate population stats and exclude data that is irrelevant and not useful, it will also just convert the data straight away to wide format as opposed to long, making it ready for effect size calculations
+
+calculate_population_stats <- function(mydata, min_individuals = 5){
     mydata %>% 
-    group_by(population, strain_name, production_center, sex) %>%
-    summarise(
-      trait = parameter_name[1],
-      x_bar = mean(data_point),
-      x_sd = sd(data_point),
+    group_by(population,
+             production_center,  
+             strain_name,  
+             sex) %>%
+    summarise(trait  = parameter_name[1],
+              x_bar  = mean(data_point, na.rm = TRUE),
+              x_sd   =   sd(data_point, na.rm = TRUE),
               n_ind  = n()) %>%
     ungroup() %>%
-    filter(n_ind > min_individuals) %>%
-    # Check both sexes present & filter those missing
+    filter(n_ind > min_individuals) %>%   # NOTE here that you are excluding data with 5 exactly....
     group_by(population) %>%
-    mutate(n_sex = n_distinct(sex)) %>%
-    ungroup() %>%
-    filter(n_sex == 2) %>%
-    select(-n_sex) %>%
-    arrange(production_center, strain_name, population, sex)
+    filter(all(c("male", "female") %in% sex)) %>% # Removes any entries where only 1 sex is present
+    multi_spread(sex, c(x_bar, x_sd, n_ind))      # Spreads the data out into wide format, so sexes are beside each other which is more typical of meta-analytic data
 }
+
 ```
@@
 ```{r EffectSizeFunction}
-create_meta_analysis_effect_sizes <- function(mydata) {
-  i <- seq(1, nrow(mydata), by = 2)
-  input <- data.frame(
-    n1i = mydata$n_ind[i],
-    n2i = mydata$n_ind[i + 1],
-    x1i = mydata$x_bar[i],
-    x2i = mydata$x_bar[i + 1],
-    sd1i = mydata$x_sd[i],
-    sd2i = mydata$x_sd[i + 1]
-  )
-
-  mydata[i, ] %>%
-    select(strain_name, production_center, trait) %>%
-    mutate(
-      effect_size_CVR = calculate_lnCVR(CMean = input$x1i, CSD = input$sd1i, CN = input$n1i, EMean = input$x2i, ESD = input$sd2i, EN = input$n2i),
-      sample_variance_CVR = calculate_var_lnCVR(CMean = input$x1i, CSD = input$sd1i, CN = input$n1i, EMean = input$x2i, ESD = input$sd2i, EN = input$n2i),
-      effect_size_VR = calculate_lnVR(CSD = input$sd1i, CN = input$n1i, ESD = input$sd2i, EN = input$n2i),
-      sample_variance_VR = calculate_var_lnVR(CN = input$n1i, EN = input$n2i),
-      effect_size_RR = calculate_lnRR(CMean = input$x1i, CSD = input$sd1i, CN = input$n1i, EMean = input$x2i, ESD = input$sd2i, EN = input$n2i),
-      sample_variance_RR = calculate_var_lnRR(CMean = input$x1i, CSD = input$sd1i, CN = input$n1i, EMean = input$x2i, ESD = input$sd2i, EN = input$n2i),
-      err = as.factor(seq_len(n()))
-    )
+
+#This function should mostly replace the entire function below, but I am still not quite sure what is happening in places.
+Adding all effect sizes together (maintaining the naming), err seems to be added to each trait?
+That needs to be added.It will make use of escalc which has the correct equations for effect size calculations.
+create_meta_analysis_effect_sizes <- function(mydata, measure = c("CVR", "VR", "ROM")){
+  for(i in 1:length(measure)){
+    mydata <- metafor::escalc(m1i  = male_x_bar, 
+                              m2i  = female_x_bar, 
+                              sd1i = male_x_sd, 
+                              sd2i = female_x_sd, 
+                              n1i  = male_n_ind, 
+                              n2i  = female_n_ind, 
+                              data = mydata, 
+                           measure = measure[i], 
+                         var.names = c(paste0("effect_size_", measure[i]), 
+                                      paste0("sample_variance_", measure[i])),
+                            append = TRUE)
     }
-```
-
-### 4) Calculate meta-analysis statistics
-
-Based on a function created by A M Senior @ the University of Otago NZ 03/01/2014:
-
-* Calculates effect sizes for meta-analysis of variance.  All functions take the mean, sd and n from the control and experimental groups.
-* The first function, calculate_lnCVR, calculates the the log response-ratio of the coefficient of variance (lnCVR) - see Nakagawa et al 2015.
-* The second function calculates the measurement error variance for lnCVR.
-As well as the aforementioned parameters, this function also takes Equal_E_C_Corr (default = T), which must be True or False.
-If true, the function assumes that the correlation between mean and sd (Taylor's Law)  is equal for the mean and control groups, and, thus these data are pooled.
-If False the mean-SD correlation for the experimental and control groups are calculated separately from one another.
-* Similar functions are then implemented for lnVR (for comparison of standard deviations) and ln RR  (for comparison of means)
-
-```{r MetaAnalysesFunction}
-
-calculate_lnCVR <- function(CMean, CSD, CN, EMean, ESD, EN) {
-  log(ESD) - log(EMean) + 1 / (2 * (EN - 1)) - (log(CSD) - log(CMean) + 1 / (2 * (CN - 1)))
-}
-
-calculate_var_lnCVR <- function(CMean, CSD, CN, EMean, ESD, EN, Equal_E_C_Corr = T) {
-  if (Equal_E_C_Corr == T) {
-    mvcorr <- 0 # cor.test(log(c(CMean, EMean)), log(c(CSD, ESD)))$estimate   old, slightly incorrect
-    S2 <- CSD^2 / (CN * (CMean^2)) + 1 / (2 * (CN - 1)) - 2 * mvcorr * sqrt((CSD^2 / (CN * (CMean^2))) * (1 / (2 * (CN - 1)))) + ESD^2 / (EN * (EMean^2)) + 1 / (2 * (EN - 1)) - 2 * mvcorr * sqrt((ESD^2 / (EN * (EMean^2))) * (1 / (2 * (EN - 1))))
-  }
-  else {
-    Cmvcorr <- cor.test(log(CMean), log(CSD))$estimate
-    Emvcorr <- cor.test(log(EMean), (ESD))$estimate
-    S2 <- CSD^2 / (CN * (CMean^2)) + 1 / (2 * (CN - 1)) - 2 * Cmvcorr * sqrt((CSD^2 / (CN * (CMean^2))) * (1 / (2 * (CN - 1)))) + ESD^2 / (EN * (EMean^2)) + 1 / (2 * (EN - 1)) - 2 * Emvcorr * sqrt((ESD^2 / (EN * (EMean^2))) * (1 / (2 * (EN - 1))))
-  }
-  S2
-}
-
-calculate_lnVR <- function(CSD, CN, ESD, EN) {
-  log(ESD) - log(CSD) + 1 / (2 * (EN - 1)) - 1 / (2 * (CN - 1))
-}
-
-calculate_var_lnVR <- function(CN, EN) {
-  1 / (2 * (EN - 1)) + 1 / (2 * (CN - 1))
-}
-
-calculate_lnRR <- function(CMean, CSD, CN, EMean, ESD, EN) {
-  log(EMean) - log(CMean)
-}
-
-calculate_var_lnRR <- function(CMean, CSD, CN, EMean, ESD, EN) {
-  CSD^2 / (CN * CMean^2) + ESD^2 / (EN * EMean^2)
+    return(mydata)
 }
@@
 results_alltraits_grouping <- 
-    tibble(id = 1:n, lnCVR=0, lnCVR_lower=0, lnCVR_upper=0, 
-           lnCVR_se=0, lnVR=0, lnVR_lower=0, lnVR_upper=0, 
-           lnVR_se=0, lnRR=0, lnRR_lower=0, lnRR_upper=0, lnRR_se=0, sampleSize=0, trait=0)
+    data.frame(tibble(id = 1:n, 
+           lnCVR=0, lnCVR_lower=0, lnCVR_upper=0, lnCVR_se=0, 
+            lnVR=0,  lnVR_lower=0,  lnVR_upper=0, lnVR_se=0, 
+            lnRR=0,  lnRR_lower=0,  lnRR_upper=0, lnRR_se=0, 
+           sampleSize=0, trait=0))
 
@@
     {
+
       results <- data %>%
@@
                  calculate_population_stats() %>%
-        create_meta_analysis_effect_sizes()
+                 create_meta_analysis_effect_sizes() %>%
+                 mutate(err = seq_len(n()))
 
@@
       cvr <- metafor::rma.mv(yi = effect_size_CVR, V = sample_variance_CVR, 
-                             random = list(~ 1 | strain_name, ~ 1 | production_center, ~ 1 | err), 
-                             control = list(optimizer = "optim", optmethod = "Nelder-Mead", 
-                                            maxit = 1000), verbose = F, data = results)
+                             random = list(~ 1 | strain_name, 
+                                           ~ 1 | production_center, 
+                                           ~ 1 | err), 
+                             control = list(optimizer = "optim", 
+                                            optmethod = "Nelder-Mead", 
+                                            maxit = 1000), 
+                             verbose = F, data = results)
 
@@
       cv <- metafor::rma.mv(yi = effect_size_VR, V = sample_variance_VR,
-                            random = list(~ 1 | strain_name, ~ 1 | production_center, ~ 1 | err), 
-                            control = list(optimizer = "optim", optmethod = "Nelder-Mead", 
-                                           maxit = 1000), verbose = F, data = results)
+                            random = list(~ 1 | strain_name, 
+                                          ~ 1 | production_center, 
+                                          ~ 1 | err), 
+                            control = list(optimizer = "optim", 
+                                           optmethod = "Nelder-Mead", 
+                                           maxit = 1000), 
+                            verbose = F, data = results)
 
       # for means, lnRR
-      means <- metafor::rma.mv(yi = effect_size_RR, V = sample_variance_RR, 
-                               random = list(~ 1 | strain_name, ~ 1 | production_center, ~ 1 | err), 
-                               control = list(optimizer = "optim", optmethod = "Nelder-Mead", 
-                                              maxit = 1000), verbose = F, data = results)
+      means <- metafor::rma.mv(yi = effect_size_ROM, V = sample_variance_ROM, 
+                               random = list(~ 1 | strain_name, 
+                                             ~ 1 | production_center, 
+                                             ~ 1 | err), 
+                               control = list(optimizer = "optim", 
+                                              optmethod = "Nelder-Mead", 
+                                              maxit = 1000), 
+                               verbose = F, data = results)
 
@@
 
-      results_alltraits_grouping[t, 2:14] <- c(f(cvr), f(cv), f(means), means$k)
+      results_alltraits_grouping[t, 2:14] <- c(f(cvr), f(cv), f(means), k=means$k)
       results_alltraits_grouping[t, 15]   <- unique(results$trait)
@@
 In the above function, we use 'tryCatch' and 'conditionMessage' to prevent the loop from aborting when the first error at row 84 is produced.
-As convergence in the two listed non-converging cases can't be achieved by sensibly tweaking (other optim etc.), and we only learn about non-convergence in the loop, it is not possible to exclude the traits (N=2) beforehand.
-Similarly, there are 8 traits with very low variation, which can not be excluded prior to running the loop.
-
-The produced "Warnings" indicate cases where variance components are set to zero during likelihood optimization.
+As convergence in the two listed non-converging cases can't be achieved by sensibly tweaking (other optim etc.), and we only learn about non-convergence in the loop, it is not possible to exclude the traits (N = 2) beforehand.Similarly, there are 8 traits with very low variation, which can not be excluded prior to running the loop.
+
+Any produced "Warnings" indicate cases where variance components are set to zero during likelihood optimization.
 
@@
   results_alltraits_grouping %>%
+
+  # Join data with results_alltraits_grouping. We filter duplicated id's to get only one unique row per id (and there is one id per parameter_name)
   left_join(by="id",
-             data %>% select(id, parameter_group, procedure = procedure_name, procedure_name, parameter_name) %>%   # We filter duplicated id's to get only one unique row per id (and there is one id per parameter_name)
-              filter(!duplicated(id))
-            ) %>%
-  # Below we add 'procedure' (from the previously loaded 'procedures.csv') as a variable
+             data %>% 
+             select(id, parameter_group, procedure = procedure_name, procedure_name, parameter_name) %>%  
+             filter(!duplicated(id))) %>%
+
+  # Below we add 'procedure' (from the previously loaded 'procedures.csv') as a variable; n <- length(unique(results_alltraits_grouping2$parameter_name))) should equal 232
   left_join(by="procedure", 
-            procedures %>% distinct()
-            )
-
-#(n <- length(unique(results_alltraits_grouping2$parameter_name))) # 232
-
-### Removal of traits
+            procedures %>% distinct())
 
@@
 meta_clean <- results_alltraits_grouping2 %>% 
-	  filter(!parameter_name %in% c("dp t cells", "mzb (cd21/35 high)", "number of caudal vertebrae", 
-	  "number of cervical vertebrae", "number of digits", "number of lumbar vertebrae", "number of pelvic vertebrae", "number of ribs left",                       
-        "number of ribs right", "number of signals", "number of thoracic vertebrae", "total number of acquired events in panel a",
+	            filter(!parameter_name %in% 
+	                     c("dp t cells", "mzb (cd21/35 high)", "number of caudal vertebrae", 
+	                       "number of cervical vertebrae", "number of digits", "number of lumbar vertebrae", 
+	                       "number of pelvic vertebrae", "number of ribs left","number of ribs right", 
+	                       "number of signals", "number of thoracic vertebrae", "total number of acquired events in panel a",
 	                       "total number of acquired events in panel b", "whole arena permanence"))
@@
 ```
- 14 traits from the originally 232 that had been included are removed because they either did not achieve convergence or are nonsensical for analysis of variance (such as traits that show no variation, see list below).
-
-Not converged: "dp t cells", "mzb (cd21/35 high)"
-
-Not enough variation: "number of caudal vertebrae", "number of cervical vertebrae", "number of digits", "number of lumbar vertebrae", "number of pelvic vertebrae", "number of ribs left","number of ribs right", "number of signals", "number of thoracic vertebrae", "total number of acquired events in panel a","total number of acquired events in panel b", "whole arena permanence".
+A total of 14 traits from the original 232 that had been included are removed because they either did not achieve convergence or are nonsensical for analysis of variance (such as traits that show no variation, see list below).
+
+The traits where models did not converge include: "dp t cells", "mzb (cd21/35 high)"
+
+The traits where there was not enough variation include: "number of caudal vertebrae", "number of cervical vertebrae", "number of digits", "number of lumbar vertebrae", "number of pelvic vertebrae", "number of ribs left","number of ribs right", "number of signals", "number of thoracic vertebrae", "total number of acquired events in panel a","total number of acquired events in panel b", "whole arena permanence".
 
@@
 #### Extracting and save parameter estimates
-# Here we apply an additional Function to collect the outcomes of the 'mini-meta-analysis' that has ondensed our non-independent traits.
-Values from our second-order meta-analysis using robu-meta are extracted
+# Here we apply an additional function to collect the outcomes of the 'mini-meta-analysis' that has condensed our non-independent traits.
+Values from our second-order meta-analysis using robu-meta are then extracted
 
@@
 robusub_RR <- model_count %>%
-  transmute(parameter_group, estimatelnRR = map(model_lnRR, count_fun)) %>%
-  mutate(r = map(estimatelnRR, ~ data.frame(t(.)))) %>%
+              transmute(parameter_group, 
+                        estimatelnRR = map(model_lnRR, count_fun)) %>%
+              mutate(r = map(estimatelnRR, 
+                             ~ data.frame(t(.)))) %>%
               unnest(r) %>%
@@
 robusub_CVR <- model_count %>%
-  transmute(parameter_group, estimatelnCVR = map(model_lnCVR, count_fun)) %>%
-  mutate(r = map(estimatelnCVR, ~ data.frame(t(.)))) %>%
+               transmute(parameter_group, 
+                         estimatelnCVR = map(model_lnCVR, count_fun)) %>%
+               mutate(r = map(estimatelnCVR, 
+                              ~ data.frame(t(.)))) %>%
                unnest(r) %>%
@@
 robusub_VR <- model_count %>%
-  transmute(parameter_group, estimatelnVR = map(model_lnVR, count_fun)) %>%
-  mutate(r = map(estimatelnVR, ~ data.frame(t(.)))) %>%
+              transmute(parameter_group, 
+                        estimatelnVR = map(model_lnVR, count_fun)) %>%
+              mutate(r = map(estimatelnVR, 
+                             ~ data.frame(t(.)))) %>%
               unnest(r) %>%
@@
 # Merge the two data sets (the new [robu_all] and the initial [uncorrelated sub-traits with count = 1]) 
-
 meta_all <- meta1 %>%
@@
 
-metacombo_final <- metacombo_final %>% mutate(para_per_GroupingTerm = map_dbl(data, nrow))
+metacombo_final <- metacombo_final %>% 
+                   mutate(para_per_GroupingTerm = map_dbl(data, nrow))
 
@@
 ```{r MetaGroup_extraction}
-Behaviour <- overall1 %>% 
-  filter(., GroupingTerm == "Behaviour") %>% 
-  mutate(
-    lnCVR = .[[4]][[1]]$b, lnCVR_lower = .[[4]][[1]]$ci.lb, lnCVR_upper = .[[4]][[1]]$ci.ub, lnCVR_se = .[[4]][[1]]$se,     lnCVR_I2 = .[[4]][[1]]$I2,
+
+# Function will take the averall results and extract the relevant trait of interest
+extract_trait <- function(data, trait){
+  tmp <- data %>% 
+        filter(., GroupingTerm == trait) %>% 
+        mutate(lnCVR = .[[4]][[1]]$b, lnCVR_lower = .[[4]][[1]]$ci.lb, lnCVR_upper = .[[4]][[1]]$ci.ub, lnCVR_se = .[[4]][[1]]$se, lnCVR_I2 = .[[4]][[1]]$I2,
                 lnVR = .[[5]][[1]]$b,  lnVR_lower = .[[5]][[1]]$ci.lb,  lnVR_upper = .[[5]][[1]]$ci.ub,  lnVR_se = .[[5]][[1]]$se,  lnVR_I2 = .[[5]][[1]]$I2,
-    lnRR = .[[6]][[1]]$b, lnRR_lower = .[[6]][[1]]$ci.lb, lnRR_upper = .[[6]][[1]]$ci.ub, lnRR_se = .[[6]][[1]]$se, lnRR_I2 = .[[6]][[1]]$I2
-  )  %>%
+                lnRR = .[[6]][[1]]$b,  lnRR_lower = .[[6]][[1]]$ci.lb,  lnRR_upper = .[[6]][[1]]$ci.ub,  lnRR_se = .[[6]][[1]]$se,  lnRR_I2 = .[[6]][[1]]$I2)  %>%
         select(., GroupingTerm, lnCVR:lnRR_I2)
 
-Immunology <- overall1 %>% 
-  filter(., GroupingTerm == "Immunology") %>% 
-  mutate(
-    lnCVR = .[[4]][[1]]$b, lnCVR_lower = .[[4]][[1]]$ci.lb, lnCVR_upper = .[[4]][[1]]$ci.ub, lnCVR_se = .[[4]][[1]]$se,     lnCVR_I2 = .[[4]][[1]]$I2,
-    lnVR = .[[5]][[1]]$b, lnVR_lower = .[[5]][[1]]$ci.lb, lnVR_upper = .[[5]][[1]]$ci.ub, lnVR_se = .[[5]][[1]]$se, lnVR_I2 = .[[5]][[1]]$I2,
-    lnRR = .[[6]][[1]]$b, lnRR_lower = .[[6]][[1]]$ci.lb, lnRR_upper = .[[6]][[1]]$ci.ub, lnRR_se = .[[6]][[1]]$se, lnRR_I2 = .[[6]][[1]]$I2
-  )  %>%
-  select(., GroupingTerm, lnCVR:lnRR_I2)
-
-Hematology <- overall1 %>% 
-  filter(., GroupingTerm == "Hematology") %>% 
-  mutate(
-    lnCVR = .[[4]][[1]]$b, lnCVR_lower = .[[4]][[1]]$ci.lb, lnCVR_upper = .[[4]][[1]]$ci.ub, lnCVR_se = .[[4]][[1]]$se,     lnCVR_I2 = .[[4]][[1]]$I2,
-    lnVR = .[[5]][[1]]$b, lnVR_lower = .[[5]][[1]]$ci.lb, lnVR_upper = .[[5]][[1]]$ci.ub, lnVR_se = .[[5]][[1]]$se, lnVR_I2 = .[[5]][[1]]$I2,
-    lnRR = .[[6]][[1]]$b, lnRR_lower = .[[6]][[1]]$ci.lb, lnRR_upper = .[[6]][[1]]$ci.ub, lnRR_se = .[[6]][[1]]$se, lnRR_I2 = .[[6]][[1]]$I2
-  )  %>%
-  select(., GroupingTerm, lnCVR:lnRR_I2)
-
-Hearing <- overall1 %>% 
-  filter(., GroupingTerm == "Hearing") %>% 
-  mutate(
-    lnCVR = .[[4]][[1]]$b, lnCVR_lower = .[[4]][[1]]$ci.lb, lnCVR_upper = .[[4]][[1]]$ci.ub, lnCVR_se = .[[4]][[1]]$se,     lnCVR_I2 = .[[4]][[1]]$I2,
-    lnVR = .[[5]][[1]]$b, lnVR_lower = .[[5]][[1]]$ci.lb, lnVR_upper = .[[5]][[1]]$ci.ub, lnVR_se = .[[5]][[1]]$se, lnVR_I2 = .[[5]][[1]]$I2,
-    lnRR = .[[6]][[1]]$b, lnRR_lower = .[[6]][[1]]$ci.lb, lnRR_upper = .[[6]][[1]]$ci.ub, lnRR_se = .[[6]][[1]]$se, lnRR_I2 = .[[6]][[1]]$I2
-  )  %>%
-  select(., GroupingTerm, lnCVR:lnRR_I2)
-
-Physiology <- overall1 %>% 
-  filter(., GroupingTerm == "Physiology") %>% 
-  mutate(
-   lnCVR = .[[4]][[1]]$b, lnCVR_lower = .[[4]][[1]]$ci.lb, lnCVR_upper = .[[4]][[1]]$ci.ub, lnCVR_se = .[[4]][[1]]$se,     lnCVR_I2 = .[[4]][[1]]$I2,
-    lnVR = .[[5]][[1]]$b, lnVR_lower = .[[5]][[1]]$ci.lb, lnVR_upper = .[[5]][[1]]$ci.ub, lnVR_se = .[[5]][[1]]$se,  lnVR_I2 = .[[5]][[1]]$I2,
-    lnRR = .[[6]][[1]]$b, lnRR_lower = .[[6]][[1]]$ci.lb, lnRR_upper = .[[6]][[1]]$ci.ub, lnRR_se = .[[6]][[1]]$se, lnRR_I2 = .[[6]][[1]]$I2
-  )  %>%
-  select(., GroupingTerm, lnCVR:lnRR_I2)
-
-Metabolism <- overall1 %>% 
-  filter(., GroupingTerm == "Metabolism") %>% 
-  mutate(
-  lnCVR = .[[4]][[1]]$b, lnCVR_lower = .[[4]][[1]]$ci.lb, lnCVR_upper = .[[4]][[1]]$ci.ub, lnCVR_se = .[[4]][[1]]$se,     lnCVR_I2 = .[[4]][[1]]$I2,
-    lnVR = .[[5]][[1]]$b, lnVR_lower = .[[5]][[1]]$ci.lb, lnVR_upper = .[[5]][[1]]$ci.ub, lnVR_se = .[[5]][[1]]$se, lnVR_I2 = .[[5]][[1]]$I2,
-    lnRR = .[[6]][[1]]$b, lnRR_lower = .[[6]][[1]]$ci.lb, lnRR_upper = .[[6]][[1]]$ci.ub, lnRR_se = .[[6]][[1]]$se, lnRR_I2 = .[[6]][[1]]$I2
-  )  %>%
-  select(., GroupingTerm, lnCVR:lnRR_I2)
-
-Morphology <- overall1 %>% 
-  filter(., GroupingTerm == "Morphology") %>%
-  mutate(
-   lnCVR = .[[4]][[1]]$b, lnCVR_lower = .[[4]][[1]]$ci.lb, lnCVR_upper = .[[4]][[1]]$ci.ub, lnCVR_se = .[[4]][[1]]$se,     lnCVR_I2 = .[[4]][[1]]$I2,
-      lnVR = .[[5]][[1]]$b, lnVR_lower = .[[5]][[1]]$ci.lb, lnVR_upper = .[[5]][[1]]$ci.ub, lnVR_se = .[[5]][[1]]$se, lnVR_I2 = .[[5]][[1]]$I2,
-      lnRR = .[[6]][[1]]$b, lnRR_lower = .[[6]][[1]]$ci.lb, lnRR_upper = .[[6]][[1]]$ci.ub, lnRR_se = .[[6]][[1]]$se, lnRR_I2 = .[[6]][[1]]$I2
-  )  %>%
-  select(., GroupingTerm, lnCVR:lnRR_I2)
-
-Heart <- overall1 %>% 
-  filter(., GroupingTerm == "Heart") %>% 
-    mutate(
-   lnCVR = .[[4]][[1]]$b, lnCVR_lower = .[[4]][[1]]$ci.lb, lnCVR_upper = .[[4]][[1]]$ci.ub, lnCVR_se = .[[4]][[1]]$se,     lnCVR_I2 = .[[4]][[1]]$I2,
-      lnVR = .[[5]][[1]]$b, lnVR_lower = .[[5]][[1]]$ci.lb, lnVR_upper = .[[5]][[1]]$ci.ub, lnVR_se = .[[5]][[1]]$se, lnVR_I2 = .[[5]][[1]]$I2,
-      lnRR = .[[6]][[1]]$b, lnRR_lower = .[[6]][[1]]$ci.lb, lnRR_upper = .[[6]][[1]]$ci.ub, lnRR_se = .[[6]][[1]]$se, lnRR_I2 = .[[6]][[1]]$I2
-  )  %>%
-  select(., GroupingTerm, lnCVR:lnRR_I2)
-
-Eye <- overall1 %>% 
-  filter(., GroupingTerm == "Eye") %>% 
-  mutate(
- lnCVR = .[[4]][[1]]$b, lnCVR_lower = .[[4]][[1]]$ci.lb, lnCVR_upper = .[[4]][[1]]$ci.ub, lnCVR_se = .[[4]][[1]]$se,     lnCVR_I2 = .[[4]][[1]]$I2,
-      lnVR = .[[5]][[1]]$b, lnVR_lower = .[[5]][[1]]$ci.lb, lnVR_upper = .[[5]][[1]]$ci.ub, lnVR_se = .[[5]][[1]]$se, lnVR_I2 = .[[5]][[1]]$I2,
-      lnRR = .[[6]][[1]]$b, lnRR_lower = .[[6]][[1]]$ci.lb, lnRR_upper = .[[6]][[1]]$ci.ub, lnRR_se = .[[6]][[1]]$se, lnRR_I2 = .[[6]][[1]]$I2
-  )  %>%
-  select(., GroupingTerm, lnCVR:lnRR_I2)
+  return(tmp)
+}
 
 All <- overall_all1 %>% 
-  mutate(
-    lnCVR = .[[2]][[1]]$b, lnCVR_lower = .[[2]][[1]]$ci.lb, lnCVR_upper = .[[2]][[1]]$ci.ub, lnCVR_se = .[[2]][[1]]$se,     lnCVR_I2 = .[[2]][[1]]$I2,
+       mutate(lnCVR = .[[2]][[1]]$b, lnCVR_lower = .[[2]][[1]]$ci.lb, lnCVR_upper = .[[2]][[1]]$ci.ub, lnCVR_se = .[[2]][[1]]$se, lnCVR_I2 = .[[2]][[1]]$I2,
               lnVR = .[[3]][[1]]$b,  lnVR_lower = .[[3]][[1]]$ci.lb,  lnVR_upper = .[[3]][[1]]$ci.ub,  lnVR_se = .[[3]][[1]]$se,  lnVR_I2 = .[[3]][[1]]$I2,
-    lnRR = .[[4]][[1]]$b, lnRR_lower = .[[4]][[1]]$ci.lb, lnRR_upper = .[[4]][[1]]$ci.ub, lnRR_se = .[[4]][[1]]$se, lnRR_I2 = .[[4]][[1]]$I2,
-  )  %>%
+              lnRR = .[[4]][[1]]$b,  lnRR_lower = .[[4]][[1]]$ci.lb,  lnRR_upper = .[[4]][[1]]$ci.ub,  lnRR_se = .[[4]][[1]]$se,  lnRR_I2 = .[[4]][[1]]$I2,)  %>%
        select(., lnCVR:lnRR_I2)
@@
 
-overall2 <- bind_rows(Behaviour, Morphology, Metabolism, Physiology, Immunology, Hematology, Heart, Hearing, Eye, All)
+overall2 <- bind_rows(extract_trait(overall1, "Behaviour"), 
+                      extract_trait(overall1, "Morphology"), 
+                      extract_trait(overall1, "Metabolism"), 
+                      extract_trait(overall1, "Physiology"), 
+                      extract_trait(overall1, "Immunology"), 
+                      extract_trait(overall1, "Hematology"), 
+                      extract_trait(overall1, "Heart"), 
+                      extract_trait(overall1, "Hearing"), 
+                      extract_trait(overall1, "Eye"), 
+                      All)
 
@@
 
-meta_clean$GroupingTerm <- factor(meta_clean$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye"))
-meta_clean$GroupingTerm <- factor(meta_clean$GroupingTerm, rev(levels(meta_clean$GroupingTerm)))
+meta_clean$GroupingTerm <- factor(meta_clean$GroupingTerm, 
+                                  levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye"))
+meta_clean$GroupingTerm <- factor(meta_clean$GroupingTerm, 
+                                  rev(levels(meta_clean$GroupingTerm)))
 
@@
 
-meta.plot2.all.b <- gather(meta.plot2.all, trait, value, c(lnCVR, lnRR)) # lnVR has been removed here and in the steps below, as this is only included in the supplemental figure
+# lnVR has been removed here and in the steps below, as this is only included in the supplemental figure
+      meta.plot2.all.b <- gather(meta.plot2.all, trait, value, c(lnCVR, lnRR))
 
@@
 meta.plot2.all.d <- as.data.frame(meta.plot2.all.c)
-meta.plot2.all.e <- gather(meta.plot2.all.d, key = sex, value = percent, malepercent:femalepercent, factor_key = TRUE)
+meta.plot2.all.e <- gather(meta.plot2.all.d, 
+                           key = sex, 
+                           value = percent, 
+                           malepercent:femalepercent, 
+                           factor_key = TRUE)
 
@@
 
-meta.plot2.all.e$samplesize <- with(meta.plot2.all.e, ifelse(sex == "malepercent", malebias, femalebias))
+meta.plot2.all.e$samplesize <- with(meta.plot2.all.e, 
+                                    ifelse(sex == "malepercent", 
+                                           malebias, 
+                                           femalebias))
 
@@
 
-meta.plot2.all.f <- meta.plot2.all.e %>% group_by(trait, sex) %>% 
-	summarise(GroupingTerm = "All", malebias = sum(malebias), femalebias = sum(femalebias), total = malebias + femalebias, 
-	label = "All traits", samplesize = sum(samplesize)) %>%
+meta.plot2.all.f <- meta.plot2.all.e %>% 
+                    group_by(trait, sex) %>% 
+	                  summarise(GroupingTerm = "All", 
+	                            malebias = sum(malebias),
+	                            femalebias = sum(femalebias),
+	                            total = malebias + femalebias, 
+	                            label = "All traits", 
+	                            samplesize = sum(samplesize)) %>%
 	                  mutate(percent = ifelse(sex == "femalepercent", femalebias*100/(malebias+femalebias), malebias*100/(malebias+femalebias))) %>%
@@
 
-meta.plot2.all.f$GroupingTerm <- factor(meta.plot2.all.f$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All")) 
-meta.plot2.all.f$GroupingTerm <- factor(meta.plot2.all.f$GroupingTerm, rev(levels(meta.plot2.all.f$GroupingTerm)))
+meta.plot2.all.f$GroupingTerm <- factor(meta.plot2.all.f$GroupingTerm,
+                                        levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All")) 
+meta.plot2.all.f$GroupingTerm <- factor(meta.plot2.all.f$GroupingTerm, 
+                                        rev(levels(meta.plot2.all.f$GroupingTerm)))
 
@@
 
-overall4$GroupingTerm <- factor(overall4$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
-overall4$GroupingTerm <- factor(overall4$GroupingTerm, rev(levels(overall4$GroupingTerm)))
+overall4$GroupingTerm <- factor(overall4$GroupingTerm, 
+                                levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
+overall4$GroupingTerm <- factor(overall4$GroupingTerm, 
+                                rev(levels(overall4$GroupingTerm)))
 overall4$label <- "All traits"
@@
  meta.plot2.sig <- meta_clean %>%
-  mutate(
-    lnCVRsig = ifelse(lnCVR_lower * lnCVR_upper > 0, 1, 0), lnVRsig = ifelse(lnVR_lower * lnVR_upper > 0, 1, 0),
-    lnRRsig = ifelse(lnRR_lower * lnRR_upper > 0, 1, 0)
-  )
+                   mutate(lnCVRsig = ifelse(lnCVR_lower * lnCVR_upper > 0, 1, 0), 
+                           lnVRsig = ifelse( lnVR_lower * lnVR_upper  > 0, 1, 0),
+                           lnRRsig = ifelse( lnRR_lower * lnRR_upper  > 0, 1, 0))
 
@@
 
-meta.plot2.sig.c$sig <- ifelse(meta.plot2.sig.c$trait == "lnCVR", meta.plot2.sig.c$lnCVRsig,
-  ifelse(meta.plot2.sig.c$trait == "lnVR", meta.plot2.sig.c$lnVRsig, meta.plot2.sig.c$lnRRsig)
-)
+  meta.plot2.sig.c$sig <- ifelse(meta.plot2.sig.c$trait == "lnCVR", 
+                                 meta.plot2.sig.c$lnCVRsig,
+                                 ifelse(meta.plot2.sig.c$trait == "lnVR", 
+                                        meta.plot2.sig.c$lnVRsig, 
+                                        meta.plot2.sig.c$lnRRsig))
 
@@
 meta.plot2.sig.malebias <- ungroup(meta.plot2.sig.malebias) %>%
-  add_row(trait = "lnCVR", GroupingTerm = "Hearing", male_sig = 0, female_sig = 0, .before = 4) %>% # add "Hearing" for lnCVR (not filtered as only zeros)
+                          # add "Hearing" for lnCVR (not filtered as only zeros)
+                          add_row(trait = "lnCVR", GroupingTerm = "Hearing", male_sig = 0, female_sig = 0, .before = 4) %>% 
                           mutate(malepercent = male_sig * 100 / total, femalepercent = female_sig * 100 / total)
@@
 
-meta.plot2.sig.bothsexes.c <- meta.plot2.sig.bothsexes.b %>% group_by(trait, sex) %>% 
-  summarise(GroupingTerm = "All", male_sig = sum(male_sig), female_sig = sum(female_sig), total = male_sig + female_sig, 
-            label = "CI not overlapping zero", samplesize = sum(samplesize)) %>%
-  mutate(percent = ifelse(sex == "femalepercent", female_sig*100/(male_sig+female_sig), male_sig*100/(male_sig+female_sig))) %>%
+meta.plot2.sig.bothsexes.c <- meta.plot2.sig.bothsexes.b %>% 
+                              group_by(trait, sex) %>% 
+                              summarise(GroupingTerm = "All", 
+                                        male_sig = sum(male_sig), 
+                                        female_sig = sum(female_sig), 
+                                        total = male_sig + female_sig, 
+                                        label = "CI not overlapping zero", 
+                                        samplesize = sum(samplesize)) %>%
+                              mutate(percent = ifelse(sex == "femalepercent", 
+                                                      female_sig*100/(male_sig+female_sig), 
+                                                      male_sig*100/(male_sig+female_sig))) %>%
                               bind_rows(meta.plot2.sig.bothsexes.b, .) %>%
@@
                               .[c(37, 1:9, 39, 10:18, 38, 19:27, 40, 28:36), ]
+
   #line references in previous code line corresponding to: 
@@
 
-meta.plot2.sig.bothsexes.c$GroupingTerm <- factor(meta.plot2.sig.bothsexes.c$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
-meta.plot2.sig.bothsexes.c$GroupingTerm <- factor(meta.plot2.sig.bothsexes.c$GroupingTerm, rev(levels(meta.plot2.sig.bothsexes.c$GroupingTerm)))
+meta.plot2.sig.bothsexes.c$GroupingTerm <- factor(meta.plot2.sig.bothsexes.c$GroupingTerm,
+                                                  levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", 
+                                                             "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All")) 
+meta.plot2.sig.bothsexes.c$GroupingTerm <- factor(meta.plot2.sig.bothsexes.c$GroupingTerm, 
+                                                  rev(levels(meta.plot2.sig.bothsexes.c$GroupingTerm)))
 
@@
     data = subset(meta.plot2.sig.bothsexes.c, samplesize != 0), aes(label = samplesize), position = position_stack(vjust = .5),
-    color = "white", size = 3.5
-  ) +
-  facet_grid(
-    cols = vars(trait), rows = vars(label), labeller = label_wrap_gen(width = 18),
-    scales = "free", space = "free"
-  ) +
+    color = "white", size = 3.5) +
+  facet_grid(cols = vars(trait), 
+             rows = vars(label), 
+             labeller = label_wrap_gen(width = 18),
+             scales = "free", space = "free") +
   scale_fill_brewer(palette = "Set2") +
   theme_bw(base_size = 18) +
-  theme(
-    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
+  theme(strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
         strip.text.x = element_text(size = 12),
@@
         legend.position = "none",
-    #axis.title.x = element_blank(),
-    axis.title.y = element_blank()
-  ) +
+        axis.title.y = element_blank()) +
   coord_flip()
@@
 meta.male.plot3.sig <- metacombo %>%
-  mutate(
-    sigCVR = ifelse(lnCVR_lower > 0, 1, 0),
-    sigVR = ifelse(lnVR_lower > 0, 1, 0),
-    sigRR = ifelse(lnRR_lower > 0, 1, 0)
-  )
+                       mutate(sigCVR = ifelse(lnCVR_lower > 0, 1, 0),
+                               sigVR = ifelse( lnVR_lower > 0, 1, 0),
+                               sigRR = ifelse( lnRR_lower > 0, 1, 0))
 
@@
 plot3.male.meta.CVR <- metacombo_male.plot3.CVR %>%
+                       mutate(model_lnCVR = map(data, 
+                                                ~ metafor::rma.uni(yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower) / (2 * 1.96), 
+                                              control = list(optimizer = "optim", 
+                                                             optmethod = "Nelder-Mead", 
+                                                             maxit = 1000), 
+                                              verbose = F)))
+
+plot3.male.meta.VR <- metacombo_male.plot3.VR %>%
+                      mutate(model_lnVR = map(data, 
+                                              ~ metafor::rma.uni(yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
+                                            control = list(optimizer = "optim", 
+                                                           optmethod = "Nelder-Mead", 
+                                                           maxit = 1000), 
+                                            verbose = F)))
+
+plot3.male.meta.RR <- metacombo_male.plot3.RR %>%
+                      mutate(model_lnRR = map(data, 
+                                              ~ metafor::rma.uni(yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
+                                              control = list(optimizer = "optim", 
+                                                             optmethod = "Nelder-Mead", 
+                                                             maxit = 1000), 
+                                              verbose = F)))
+
+# Across all grouping terms #
+
+plot3.male.meta.CVR.all <- metacombo_male.plot3.CVR.all %>%
+                            mutate(model_lnCVR = map(data,
+                                                     ~ metafor::rma.uni(yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower) / (2 * 1.96),
+                                                  control = list(optimizer = "optim", 
+                                                                 optmethod = "Nelder-Mead", 
+                                                                 maxit = 1000), 
+                                                  verbose = F)))
+
+plot3.male.meta.CVR.all <- plot3.male.meta.CVR.all %>% 
+                            mutate(GroupingTerm = "All")
+
+plot3.male.meta.VR.all <- metacombo_male.plot3.VR.all %>%
+                          mutate(model_lnVR = map(data, 
+                                                  ~ metafor::rma.uni(yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
+                                                  control = list(optimizer = "optim", 
+                                                                 optmethod = "Nelder-Mead", 
+                                                                 maxit = 1000), 
+                                                  verbose = F)))
+
+plot3.male.meta.VR.all <- plot3.male.meta.VR.all %>% 
+                          mutate(GroupingTerm = "All")
+
+plot3.male.meta.RR.all <- metacombo_male.plot3.RR.all %>%
+                          mutate(model_lnRR = map(data, 
+                                                  ~ metafor::rma.uni(yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
+                                                control = list(optimizer = "optim", 
+                                                               optmethod = "Nelder-Mead", 
+                                                               maxit = 1000), 
+                                                verbose = F)))
+
+plot3.male.meta.RR.all <- plot3.male.meta.RR.all %>% 
+                          mutate(GroupingTerm = "All")
+
+# Combine with separate grouping term results
+
+plot3.male.meta.CVR <- bind_rows(plot3.male.meta.CVR, plot3.male.meta.CVR.all)
+ plot3.male.meta.VR <- bind_rows(plot3.male.meta.VR,   plot3.male.meta.VR.all)
+ plot3.male.meta.RR <- bind_rows(plot3.male.meta.RR,   plot3.male.meta.RR.all)
+
+# **Re-structure data for each grouping term; delete un-used variables
+
+plot3.male.meta.CVR.b <- as.data.frame(plot3.male.meta.CVR %>% 
+                                       group_by(GroupingTerm) %>%
+                                       mutate( lnCVR = map_dbl(model_lnCVR, pluck(2)), 
+                                               lnCVR_lower = map_dbl(model_lnCVR, pluck(6)), 
+                                               lnCVR_upper = map_dbl(model_lnCVR, pluck(7)), 
+                                               lnCVR_se = map_dbl(model_lnCVR, pluck(3)), 
+                                               lnCVR_I2 = map_dbl(model_lnCVR, pluck("I2"))))[, c(1, 4:8)]
+
+add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA, NA))) %>% 
+                                  setNames(names(plot3.male.meta.CVR.b))
+
+plot3.male.meta.CVR.b <- bind_rows(plot3.male.meta.CVR.b, add.row.hearing)
+plot3.male.meta.CVR.b <- plot3.male.meta.CVR.b[order(plot3.male.meta.CVR.b$GroupingTerm), ]
+
+plot3.male.meta.VR.b <- as.data.frame(plot3.male.meta.VR %>% 
+                                      group_by(GroupingTerm) %>%
+                                      mutate(lnVR = map_dbl(model_lnVR, pluck(2)), 
+                                             lnVR_lower = map_dbl(model_lnVR, pluck(6)),
+                                             lnVR_upper = map_dbl(model_lnVR, pluck(7)), 
+                                             lnVR_se = map_dbl(model_lnVR, pluck(3)),
+                                             lnVR_I2 = map_dbl(model_lnVR, pluck("I2"))))[, c(1, 4:8)]
+
+plot3.male.meta.VR.b <- plot3.male.meta.VR.b[order(plot3.male.meta.VR.b$GroupingTerm), ]
+
+plot3.male.meta.RR.b <- as.data.frame(plot3.male.meta.RR %>% 
+                                      group_by(GroupingTerm) %>% 
+                                      mutate(lnRR = map_dbl(model_lnRR, pluck(2)), 
+                                             lnRR_lower = map_dbl(model_lnRR, pluck(6)),
+                                             lnRR_upper = map_dbl(model_lnRR, pluck(7)), 
+                                             lnRR_se = map_dbl(model_lnRR, pluck(3)),
+                                             lnRR_I2 = map_dbl(model_lnRR, pluck("I2"))))[, c(1, 4:8)]
+
+plot3.male.meta.RR.b <- plot3.male.meta.RR.b[order(plot3.male.meta.RR.b$GroupingTerm), ]
+
+overall.male.plot3 <- full_join(plot3.male.meta.CVR.b, plot3.male.meta.VR.b)
+overall.male.plot3 <- full_join(overall.male.plot3,    plot3.male.meta.RR.b)
+
+overall.male.plot3$GroupingTerm <- factor(overall.male.plot3$GroupingTerm, 
+                                          levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", 
+                                                     "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
+overall.male.plot3$GroupingTerm <- factor(overall.male.plot3$GroupingTerm, 
+                                          rev(levels(overall.male.plot3$GroupingTerm)))
+
+overall.male.plot3$GroupingTerm <- factor(overall.male.plot3$GroupingTerm, 
+                                          levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", 
+                                                     "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
+overall.male.plot3$GroupingTerm <- factor(overall.male.plot3$GroupingTerm, 
+                                          rev(levels(overall.male.plot3$GroupingTerm)))
+
+# Restructure MALE data for plotting
+
+overall3.male.sig <- gather(overall.male.plot3, parameter, value, c(lnCVR, lnRR), factor_key = TRUE)
+
+lnCVR.ci <- overall3.male.sig            %>%
+            filter(parameter == "lnCVR") %>%
+            mutate(ci.low = lnCVR_lower, 
+                   ci.high = lnCVR_upper)
+
+lnRR.ci <- overall3.male.sig           %>%
+           filter(parameter == "lnRR") %>%
+           mutate(ci.low = lnRR_lower, 
+                 ci.high = lnRR_upper)
+
+overall4.male.sig <- bind_rows(lnCVR.ci, lnRR.ci) %>% 
+                     select(GroupingTerm, 
+                            parameter, 
+                            value, 
+                            ci.low, 
+                            ci.high)
+
+overall4.male.sig$label <- "CI not overlapping zero"
+
+# Plot Fig 5B all significant results (CI not overlapping zero) for males. This is the right panel in Figure 5B.
+
+Metameta_Fig3_male.sig <- overall4.male.sig %>%
+  ggplot(aes(y = GroupingTerm, x = value)) +
+  geom_errorbarh(aes(xmin = ci.low,
+                     xmax = ci.high),
+                 height = 0.1, 
+                 show.legend = FALSE) +
+  geom_point(aes(shape = parameter),
+             fill = "mediumaquamarine", 
+             color = "mediumaquamarine", 
+             size = 2.2, 
+             show.legend = FALSE) +
+  scale_x_continuous(limits = c(0, 0.4),
+                     breaks = c(0, 0.3),
+                       name = "Effect size") +
+  geom_vline(xintercept = 0,
+                  color = "black",
+              linetype = "dashed") +
+  facet_grid(cols = vars(parameter), 
+             rows = vars(label),
+             labeller = label_wrap_gen(width = 23),
+             scales = "free",
+             space = "free") +
+  theme_bw() +
+  theme(strip.text.y = element_text(angle = 270, 
+                                    size = 10, 
+                                    margin = margin(t = 15, r = 15, b = 15, l = 15)),
+        strip.text.x = element_text(size = 12),
+        strip.background = element_rect(colour = NULL, 
+                                        linetype = "blank", 
+                                        fill = "gray90"),
+        text = element_text(size = 14),
+        panel.spacing = unit(0.5, "lines"),
+        panel.border = element_blank(),
+        axis.line = element_line(),
+        panel.grid.major.x = element_line(linetype = "solid", 
+                                          colour = "gray95"),
+        panel.grid.major.y = element_line(linetype = "solid", 
+                                          color = "gray95"),
+        panel.grid.minor.y = element_blank(),
+        panel.grid.minor.x = element_blank(),
+        legend.title = element_blank(),
+        axis.title.x = element_blank(),
+        axis.title.y = element_blank())
+
+# Metameta_Fig3_male.sig
+
+#### Female part, significant traits: Female Fig5B sig
+
+# as above: Prepare data for traits with CI not overlapping 0
+# create column with 1= different from zero, 0= zero included in CI
+
+# Female-biased traits
+
+meta.female.plot3.sig <- metacombo %>%
+  mutate(sigCVR = ifelse(lnCVR_upper < 0, 1, 0),
+          sigVR = ifelse(lnVR_upper < 0, 1, 0),
+          sigRR = ifelse(lnRR_upper < 0, 1, 0))
+
+# Significant subset for lnCVR
+
+metacombo_female.plot3.CVR <- meta.female.plot3.sig  %>%
+                              filter(sigCVR == 1)    %>%
+                              group_by(GroupingTerm) %>%
+                              nest()
+
+metacombo_female.plot3.CVR.all <- meta.female.plot3.sig %>%
+                                  filter(sigCVR == 1)   %>%
+                                  nest(data = everything())
+
+# Significant subset for lnVR
+
+metacombo_female.plot3.VR <- meta.female.plot3.sig  %>%
+                             filter(sigVR == 1)     %>%
+                             group_by(GroupingTerm) %>%
+                             nest()
+
+metacombo_female.plot3.VR.all <- meta.female.plot3.sig  %>%
+                                 filter(sigVR == 1)     %>%
+                                 nest(data = everything())
+
+# Significant subset for lnRR
+
+metacombo_female.plot3.RR <- meta.female.plot3.sig  %>%
+                             filter(sigRR == 1)     %>%
+                             group_by(GroupingTerm) %>%
+                             nest()
+
+metacombo_female.plot3.RR.all <- meta.female.plot3.sig %>%
+                                 filter(sigRR == 1)    %>%
+                                 nest(data = everything())
+
+# **Final fixed effects meta-analyses within grouping terms, with SE of the estimate
+
+plot3.female.meta.CVR <- metacombo_female.plot3.CVR %>%
+                         mutate(model_lnCVR = map(data, 
+                                                  ~ metafor::rma.uni(yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower) / (2 * 1.96),
+                                                  control = list(optimizer = "optim", 
+                                                                 optmethod = "Nelder-Mead", 
+                                                                 maxit = 1000), 
+                                                  verbose = F)))
+
+plot3.female.meta.VR <- metacombo_female.plot3.VR %>%
+  mutate(model_lnVR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+plot3.female.meta.RR <- metacombo_female.plot3.RR %>%
+  mutate(model_lnRR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+# Across all grouping terms #
+
+plot3.female.meta.CVR.all <- metacombo_female.plot3.CVR.all %>%
   mutate(model_lnCVR = map(data, ~ metafor::rma.uni(
@@
 
-plot3.male.meta.VR <- metacombo_male.plot3.VR %>%
+plot3.female.meta.CVR.all <- plot3.female.meta.CVR.all %>% mutate(GroupingTerm = "All")
+
+plot3.female.meta.VR.all <- metacombo_female.plot3.VR.all %>%
   mutate(model_lnVR = map(data, ~ metafor::rma.uni(
@@
 
-plot3.male.meta.RR <- metacombo_male.plot3.RR %>%
+plot3.female.meta.VR.all <- plot3.female.meta.VR.all %>% mutate(GroupingTerm = "All")
+
+plot3.female.meta.RR.all <- metacombo_female.plot3.RR.all %>%
   mutate(model_lnRR = map(data, ~ metafor::rma.uni(
@@
 
-# Across all grouping terms #
-
-plot3.male.meta.CVR.all <- metacombo_male.plot3.CVR.all %>%
-  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(
-    yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower) / (2 * 1.96),
-    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-  )))
-
-plot3.male.meta.CVR.all <- plot3.male.meta.CVR.all %>% mutate(GroupingTerm = "All")
-
-plot3.male.meta.VR.all <- metacombo_male.plot3.VR.all %>%
-  mutate(model_lnVR = map(data, ~ metafor::rma.uni(
-    yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
-    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-  )))
-
-plot3.male.meta.VR.all <- plot3.male.meta.VR.all %>% mutate(GroupingTerm = "All")
-
-plot3.male.meta.RR.all <- metacombo_male.plot3.RR.all %>%
-  mutate(model_lnRR = map(data, ~ metafor::rma.uni(
-    yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
-    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-  )))
-
-plot3.male.meta.RR.all <- plot3.male.meta.RR.all %>% mutate(GroupingTerm = "All")
+plot3.female.meta.RR.all <- plot3.female.meta.RR.all %>% mutate(GroupingTerm = "All")
 
@@
 
-plot3.male.meta.CVR <- bind_rows(plot3.male.meta.CVR, plot3.male.meta.CVR.all)
-plot3.male.meta.VR <- bind_rows(plot3.male.meta.VR, plot3.male.meta.VR.all)
-plot3.male.meta.RR <- bind_rows(plot3.male.meta.RR, plot3.male.meta.RR.all)
-
-# **Re-structure data for each grouping term; delete un-used variables
-
-plot3.male.meta.CVR.b <- as.data.frame(plot3.male.meta.CVR %>% group_by(GroupingTerm) %>%
+plot3.female.meta.CVR <- bind_rows(plot3.female.meta.CVR, plot3.female.meta.CVR.all)
+plot3.female.meta.VR <- bind_rows(plot3.female.meta.VR, plot3.female.meta.VR.all)
+plot3.female.meta.RR <- bind_rows(plot3.female.meta.RR, plot3.female.meta.RR.all)
+
+# Re-structure data for each grouping term; delete un-used variables
+
+plot3.female.meta.CVR.b <- as.data.frame(plot3.female.meta.CVR %>% group_by(GroupingTerm) %>%
   mutate(
@@
   ))[, c(1, 4:8)]
-add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA, NA))) %>% setNames(names(plot3.male.meta.CVR.b))
-
-plot3.male.meta.CVR.b <- bind_rows(plot3.male.meta.CVR.b, add.row.hearing)
-plot3.male.meta.CVR.b <- plot3.male.meta.CVR.b[order(plot3.male.meta.CVR.b$GroupingTerm), ]
-
-plot3.male.meta.VR.b <- as.data.frame(plot3.male.meta.VR %>% group_by(GroupingTerm) %>%
+
+add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA,NA))) %>% setNames(names(plot3.female.meta.CVR.b))
+
+plot3.female.meta.CVR.b <- bind_rows(plot3.female.meta.CVR.b, add.row.hearing)
+plot3.female.meta.CVR.b <- plot3.female.meta.CVR.b[order(plot3.female.meta.CVR.b$GroupingTerm), ]
+
+plot3.female.meta.VR.b <- as.data.frame(plot3.female.meta.VR %>% group_by(GroupingTerm) %>%
   mutate(
@@
   ))[, c(1, 4:8)]
-plot3.male.meta.VR.b <- plot3.male.meta.VR.b[order(plot3.male.meta.VR.b$GroupingTerm), ]
-
-plot3.male.meta.RR.b <- as.data.frame(plot3.male.meta.RR %>% group_by(GroupingTerm) %>%
+
+plot3.female.meta.VR.b <- plot3.female.meta.VR.b[order(plot3.female.meta.VR.b$GroupingTerm), ]
+
+plot3.female.meta.RR.b <- as.data.frame(plot3.female.meta.RR %>% group_by(GroupingTerm) %>%
   mutate(
@@
   ))[, c(1, 4:8)]
-plot3.male.meta.RR.b <- plot3.male.meta.RR.b[order(plot3.male.meta.RR.b$GroupingTerm), ]
-
-overall.male.plot3 <- full_join(plot3.male.meta.CVR.b, plot3.male.meta.VR.b)
-overall.male.plot3 <- full_join(overall.male.plot3, plot3.male.meta.RR.b)
-
-overall.male.plot3$GroupingTerm <- factor(overall.male.plot3$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
-overall.male.plot3$GroupingTerm <- factor(overall.male.plot3$GroupingTerm, rev(levels(overall.male.plot3$GroupingTerm)))
-
-overall.male.plot3$GroupingTerm <- factor(overall.male.plot3$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
-overall.male.plot3$GroupingTerm <- factor(overall.male.plot3$GroupingTerm, rev(levels(overall.male.plot3$GroupingTerm)))
-
-# str(overall.male.plot3)
-
-# Restructure MALE data for plotting
-
-overall3.male.sig <- gather(overall.male.plot3, parameter, value, c(lnCVR, lnRR), factor_key = TRUE)
-
-lnCVR.ci <- overall3.male.sig %>%
+
+plot3.female.meta.RR.b <- plot3.female.meta.RR.b[order(plot3.female.meta.RR.b$GroupingTerm), ]
+
+overall.female.plot3 <- full_join(plot3.female.meta.CVR.b, plot3.female.meta.VR.b)
+overall.female.plot3 <- full_join(overall.female.plot3, plot3.female.meta.RR.b)
+
+overall.female.plot3$GroupingTerm <- factor(overall.female.plot3$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
+overall.female.plot3$GroupingTerm <- factor(overall.female.plot3$GroupingTerm, rev(levels(overall.female.plot3$GroupingTerm)))
+
+# Re-structuring data for plotting
+
+overall3.female.sig <- gather(overall.female.plot3, parameter, value, c(lnCVR, lnRR), factor_key = TRUE)
+
+lnCVR.ci <- overall3.female.sig %>%
   filter(parameter == "lnCVR") %>%
   mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
-# lnVR.ci <- overall3.male.sig  %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
-lnRR.ci <- overall3.male.sig %>%
+# lnVR.ci <- overall3.female.sig  %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
+lnRR.ci <- overall3.female.sig %>%
   filter(parameter == "lnRR") %>%
@@
 
-overall4.male.sig <- bind_rows(lnCVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
-
-overall4.male.sig$label <- "CI not overlapping zero"
-
-# Plot Fig 5B all significant results (CI not overlapping zero) for males. This is the right panel in Figure 5B.
-
-Metameta_Fig3_male.sig <- overall4.male.sig %>%
+overall4.female.sig <- bind_rows(lnCVR.ci, lnRR.ci) %>% 
+                       select(GroupingTerm, parameter, value, ci.low, ci.high) # lnVR.ci,
+
+overall4.female.sig$label <- "CI not overlapping zero"
+
+# PLOT preparation for Fig5B: all significant results (CI not overlapping zero, female )
+
+Metameta_Fig3_female.sig  <- overall4.female.sig %>%
   ggplot(aes(y = GroupingTerm, x = value)) +
@@
     xmin = ci.low,
-    xmax = ci.high
-  ),
-  height = 0.1, show.legend = FALSE
-  ) +
+    xmax = ci.high),
+  height = 0.1, show.legend = FALSE) +
   geom_point(aes(shape = parameter),
-    fill = "mediumaquamarine", color = "mediumaquamarine", size = 2.2,
-    show.legend = FALSE
-  ) +
+    fill = "salmon1", color = "salmon1", size = 2.2,
+    show.legend = FALSE) +
   scale_x_continuous(
-    limits = c(0, 0.4),
-    breaks = c(0, 0.3),
-    name = "Effect size"
-  ) +
+    limits = c(-0.4, 0),
+    breaks = c(-0.3, 0),
+    name = "Effect size") +
   geom_vline(
@@
     color = "black",
-    linetype = "dashed"
-  ) +
+    linetype = "dashed") +
   facet_grid(
-    cols = vars(parameter), rows = vars(label),
-    labeller = label_wrap_gen(width = 23),
+    cols = vars(parameter), # rows = vars(label),
+    # labeller = label_wrap_gen(width = 23),
     scales = "free",
-    space = "free"
-  ) +
+    space = "free") +
   theme_bw() +
@@
 
-# Metameta_Fig3_male.sig
-
-#### Female part, significant traits: Female Fig5B sig
-
-# as above: Prepare data for traits with CI not overlapping 0
-# create column with 1= different from zero, 0= zero included in CI
-
-# Female-biased traits
-
-meta.female.plot3.sig <- metacombo %>%
-  mutate(
-    sigCVR = ifelse(lnCVR_upper < 0, 1, 0),
-    sigVR = ifelse(lnVR_upper < 0, 1, 0),
-    sigRR = ifelse(lnRR_upper < 0, 1, 0)
-  )
-
-# Significant subset for lnCVR
-
-metacombo_female.plot3.CVR <- meta.female.plot3.sig %>%
-  filter(sigCVR == 1) %>%
-  group_by(GroupingTerm) %>%
-  nest()
-
-metacombo_female.plot3.CVR.all <- meta.female.plot3.sig %>%
-  filter(sigCVR == 1) %>%
-  nest(data = everything())
-
-# Significant subset for lnVR
-
-metacombo_female.plot3.VR <- meta.female.plot3.sig %>%
-  filter(sigVR == 1) %>%
-  group_by(GroupingTerm) %>%
-  nest()
-
-metacombo_female.plot3.VR.all <- meta.female.plot3.sig %>%
-  filter(sigVR == 1) %>%
-  nest(data = everything())
-
-# Significant subset for lnRR
-
-metacombo_female.plot3.RR <- meta.female.plot3.sig %>%
-  filter(sigRR == 1) %>%
-  group_by(GroupingTerm) %>%
-  nest()
-
-metacombo_female.plot3.RR.all <- meta.female.plot3.sig %>%
-  filter(sigRR == 1) %>%
-  nest(data = everything())
-
-# **Final fixed effects meta-analyses within grouping terms, with SE of the estimate
-
-plot3.female.meta.CVR <- metacombo_female.plot3.CVR %>%
-  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(
-    yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower) / (2 * 1.96),
-    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-  )))
-
-plot3.female.meta.VR <- metacombo_female.plot3.VR %>%
-  mutate(model_lnVR = map(data, ~ metafor::rma.uni(
-    yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
-    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-  )))
-
-plot3.female.meta.RR <- metacombo_female.plot3.RR %>%
-  mutate(model_lnRR = map(data, ~ metafor::rma.uni(
-    yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
-    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-  )))
-
-# Across all grouping terms #
-
-plot3.female.meta.CVR.all <- metacombo_female.plot3.CVR.all %>%
-  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(
-    yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower) / (2 * 1.96),
-    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-  )))
-
-plot3.female.meta.CVR.all <- plot3.female.meta.CVR.all %>% mutate(GroupingTerm = "All")
-
-plot3.female.meta.VR.all <- metacombo_female.plot3.VR.all %>%
-  mutate(model_lnVR = map(data, ~ metafor::rma.uni(
-    yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
-    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-  )))
-
-plot3.female.meta.VR.all <- plot3.female.meta.VR.all %>% mutate(GroupingTerm = "All")
-
-plot3.female.meta.RR.all <- metacombo_female.plot3.RR.all %>%
-  mutate(model_lnRR = map(data, ~ metafor::rma.uni(
-    yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
-    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-  )))
-
-plot3.female.meta.RR.all <- plot3.female.meta.RR.all %>% mutate(GroupingTerm = "All")
-
-# Combine with separate grouping term results
-
-plot3.female.meta.CVR <- bind_rows(plot3.female.meta.CVR, plot3.female.meta.CVR.all)
-plot3.female.meta.VR <- bind_rows(plot3.female.meta.VR, plot3.female.meta.VR.all)
-plot3.female.meta.RR <- bind_rows(plot3.female.meta.RR, plot3.female.meta.RR.all)
-
-# Re-structure data for each grouping term; delete un-used variables
-
-plot3.female.meta.CVR.b <- as.data.frame(plot3.female.meta.CVR %>% group_by(GroupingTerm) %>%
-  mutate(
-    lnCVR = map_dbl(model_lnCVR, pluck(2)), lnCVR_lower = map_dbl(model_lnCVR, pluck(6)),
-    lnCVR_upper = map_dbl(model_lnCVR, pluck(7)), lnCVR_se = map_dbl(model_lnCVR, pluck(3)),
-    lnCVR_I2 = map_dbl(model_lnCVR, pluck("I2"))
-  ))[, c(1, 4:8)]
-
-add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA,NA))) %>% setNames(names(plot3.female.meta.CVR.b))
-
-plot3.female.meta.CVR.b <- bind_rows(plot3.female.meta.CVR.b, add.row.hearing)
-plot3.female.meta.CVR.b <- plot3.female.meta.CVR.b[order(plot3.female.meta.CVR.b$GroupingTerm), ]
-
-plot3.female.meta.VR.b <- as.data.frame(plot3.female.meta.VR %>% group_by(GroupingTerm) %>%
-  mutate(
-    lnVR = map_dbl(model_lnVR, pluck(2)), lnVR_lower = map_dbl(model_lnVR, pluck(6)),
-    lnVR_upper = map_dbl(model_lnVR, pluck(7)), lnVR_se = map_dbl(model_lnVR, pluck(3)),
-    lnVR_I2 = map_dbl(model_lnVR, pluck("I2"))
-  ))[, c(1, 4:8)]
-
-plot3.female.meta.VR.b <- plot3.female.meta.VR.b[order(plot3.female.meta.VR.b$GroupingTerm), ]
-
-plot3.female.meta.RR.b <- as.data.frame(plot3.female.meta.RR %>% group_by(GroupingTerm) %>%
-  mutate(
-    lnRR = map_dbl(model_lnRR, pluck(2)), lnRR_lower = map_dbl(model_lnRR, pluck(6)),
-    lnRR_upper = map_dbl(model_lnRR, pluck(7)), lnRR_se = map_dbl(model_lnRR, pluck(3)),
-    lnRR_I2 = map_dbl(model_lnRR, pluck("I2"))
-  ))[, c(1, 4:8)]
-
-plot3.female.meta.RR.b <- plot3.female.meta.RR.b[order(plot3.female.meta.RR.b$GroupingTerm), ]
-
-overall.female.plot3 <- full_join(plot3.female.meta.CVR.b, plot3.female.meta.VR.b)
-overall.female.plot3 <- full_join(overall.female.plot3, plot3.female.meta.RR.b)
-
-overall.female.plot3$GroupingTerm <- factor(overall.female.plot3$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
-overall.female.plot3$GroupingTerm <- factor(overall.female.plot3$GroupingTerm, rev(levels(overall.female.plot3$GroupingTerm)))
-
-# Re-structuring data for plotting
-
-overall3.female.sig <- gather(overall.female.plot3, parameter, value, c(lnCVR, lnRR), factor_key = TRUE)
-
-lnCVR.ci <- overall3.female.sig %>%
-  filter(parameter == "lnCVR") %>%
-  mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
-# lnVR.ci <- overall3.female.sig  %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
-lnRR.ci <- overall3.female.sig %>%
-  filter(parameter == "lnRR") %>%
-  mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
-
-overall4.female.sig <- bind_rows(lnCVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high) # lnVR.ci,
-
-overall4.female.sig$label <- "CI not overlapping zero"
-
-# PLOT preparation for Fig5B: all significant results (CI not overlapping zero, female )
-
-Metameta_Fig3_female.sig  <- overall4.female.sig %>%
-  ggplot(aes(y = GroupingTerm, x = value)) +
-  geom_errorbarh(aes(
-    xmin = ci.low,
-    xmax = ci.high
-  ),
-  height = 0.1, show.legend = FALSE
-  ) +
-  geom_point(aes(shape = parameter),
-    fill = "salmon1", color = "salmon1", size = 2.2,
-    show.legend = FALSE
-  ) +
-  scale_x_continuous(
-    limits = c(-0.4, 0),
-    breaks = c(-0.3, 0),
-    name = "Effect size"
-  ) +
-  geom_vline(
-    xintercept = 0,
-    color = "black",
-    linetype = "dashed"
-  ) +
-  facet_grid(
-    cols = vars(parameter), # rows = vars(label),
-    # labeller = label_wrap_gen(width = 23),
-    scales = "free",
-    space = "free"
-  ) +
-  theme_bw() +
-  theme(
-    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
-    strip.text.x = element_text(size = 12),
-    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
-    text = element_text(size = 14),
-    panel.spacing = unit(0.5, "lines"),
-    panel.border = element_blank(),
-    axis.line = element_line(),
-    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
-    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
-    panel.grid.minor.y = element_blank(),
-    panel.grid.minor.x = element_blank(),
-    legend.title = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank()
-  )
-
 # Metameta_Fig3_female.sig #(Figure 5B left panel)
@@
 Fig5B <- ggarrange(Metameta_Fig3_female.sig, Metameta_Fig3_male.sig,
-  ncol = 2, nrow = 1, widths = c(1, 1.20), heights = c(1, 1)
-  )
+  ncol = 2, nrow = 1, widths = c(1, 1.20), heights = c(1, 1))
 
 Fig5B <- annotate_figure(Fig5B,
-                bottom= text_grob("Effect Size", color = "black", face = "plain", size = 14))  # SUSI NEW
+                bottom= text_grob("Effect Size", color = "black", face = "plain", size = 14))
 
 Fig5 <- ggarrange(malebias_Fig2_sigtraits, Fig5B, 
-  ncol = 1, nrow = 2, widths = c(1, 1.10), heights = c(1.10, 1),  labels = c("A", "B")
-)
+                  ncol = 1, nrow = 2, widths = c(1, 1.10), 
+                  heights = c(1.10, 1),  labels = c("A", "B"))
 Fig5
@@
     percCVR = ifelse(lnCVR > log(11 / 10), 1, 0),
-    percVR = ifelse(lnVR > log(11 / 10), 1, 0),
-    percRR = ifelse(lnRR > log(11 / 10), 1, 0)
+     percVR = ifelse( lnVR > log(11 / 10), 1, 0),
+     percRR = ifelse( lnRR > log(11 / 10), 1, 0)
   )

### 2020-05-17 scripts/MouseSexDiffApril20_2020.Rmd
some minor changes (not knitting!)

@@
 author: Susanne Zajitschek,  Felix Zajitschek, Russell Bonduriansky, Robert  Brooks,
-  Will Cornwell, Daniel Falster, Malgortaza Lagisz, Jeremy Mason, Daniel Noble, Alistair
-  Senior & Shinichi Nakagawa
+  Will Cornwell, Daniel Falster, Malgortaza Lagisz, Jeremy Mason, Alistair
+  Senior Daniel Noble, , & Shinichi Nakagawa
 date: "April 2020"
@@
 library(pacman)
-pacman::p_load(readr, dplyr,metafor, devtools, purrr, tidyverse, tidyr, tibble, kableExtra, robumeta, ggpubr, ggplot2, png, grid, here)
+pacman::p_load(readr, dplyr, metafor, devtools, purrr, tidyverse, tidyr, tibble, kableExtra, robumeta, ggpubr, ggplot2, png, grid, here, pander)
 ```
@@
 
-```{r Session}
-sessionInfo()
-```
+```{r}
+sessionInfo() %>% pander()
+```

### 2020-05-17 scripts/MouseSexDiffApril20_2020.Rmd
Updating supplement

--- 2020-05-15 scripts/MouseSexDiffApril20_2020.Rmd
@@
 ---
-title: "Sex and Power: sexual dimorphism in trait variability and its eco-evolutionary and statistical implications"
+title: "Sex and Power: Sexual dimorphism in trait variability and its eco-evolutionary and statistical implications"
 author: Susanne Zajitschek,  Felix Zajitschek, Russell Bonduriansky, Robert  Brooks,
-  Will Cornwell, Daniel Falster, Malgortaza Lagisz, Jeremy Mason, Daniel Noble, Alistair
+  Will Cornwell, Daniel Falster, Malgorzata Lagisz, Jeremy Mason, Daniel Noble, Alistair
   Senior & Shinichi Nakagawa
-date: "April 2020"
+date: "`r Sys.Date()`"
 output:
-  html_document:
-    code_download: yes
+  bookdown::html_document2: 
+            toc: true
             code_folding: hide
-    depth: 4
-    number_sections: no
+            toc_depth: 6
+            toc_float: yes
+            number_sections: yes
             theme: flatly
-    toc: yes
-    toc_depth: 4
-    toc_float: yes
   html_notebook:
@@
 
+```{r packages1, echo = FALSE, eval = TRUE, messages = FALSE}
+library(pacman)
+pacman::p_load(readr, dplyr,metafor, devtools, purrr, tidyverse, tidyr, tibble, kableExtra, robumeta, ggpubr, ggplot2, png, grid, here, knitr)
+```
+
+# General Introduction
+
+Our supplementary material follows the general structure described in our methods (Figure  \@ref(fig:FigG1)).
+Generally speaking, the first few sections describe the processes by which the data were cleaned and re-organised for analysis, and how the first order and second order meta-analsyes were conducted.
+Supplemental tables and figures that are referenecd within the main manuscript can be found at the end of the document or conviently referenecd quickly using the side table of contents panel.
+
+```{r FigG1, fig.cap="Workflow of data process and meta-analysis"}
+
+include_graphics(here("images", "workflow.png"))
+```
+
 # Set-up
-## 1. Packages
+## Packages
 
@@
 
-```{r packages}
+```{r packages, echo = TRUE, eval = FALSE}
 library(pacman)
@@
 ```
-
-## 2. Functions 
+## Functions 
 Functions needed for preparing the data for meta analyses
 
-### 1) Sub-setting data
+### Sub-setting data
 Create a function for sub-setting the data to choose only one data point per individual per trait: "data_subset_parameterid_individual_by_age"
@@
 
-### 2) Population statistics
+### Population statistics
 Create a function called: "calculate_population_stats"
@@
 
-### 3) Extraction of effect sizes and sample variances
+### Extraction of effect sizes and sample variances
 Function: "create_meta_analysis_effect_sizes"
@@
 
-## 3. Load & clean data
-
-### 1) Data loading and cleaning of the csv file
+## Load & clean data
+
+### Data loading and cleaning of the csv file
 
@@
 # Meta-analyses
-## 1. Population as analysis unit 
+## Population as analysis unit 
 (Step C, Figure 3 in main document)
 
-### 1.1: Loop: Meta-analyses on all traits
+### Loop through meta-analyses on all traits
 
@@
 
-### 1.2: Merging datasets & removal of non-converged traits
+### Merging datasets & removal of non-converged traits
 
@@
 
-## 2. Meta-analysis: condensing non-independent traits 
+## Meta-analysis: condensing non-independent traits 
 (Step F in Figure 3 in main article)
 
-### 2.1: Dealing with Correlated Parameters, preparation
+### Dealing with Correlated Parameters, preparation
 
@@
 
-### 2.2: Collapsing and merging correlated parameters, preparation for Table S2
+### Collapsing and merging correlated parameters, preparation for Table S2
 Count the number of parameter names (correlated sub-traits) in each parameter group (par_group_size).
@@
 
-### 2.3: Meta-analyses on correlated (sub-)traits, using `robumeta` 
+### Meta-analyses on correlated (sub-)traits, using `robumeta` 
 Here we pepare the subset of the data (using nest()), and in this first step the model of the meta-analysis effect sizes are calculated
@@
 
-## 3. Second-order meta-analysis for functional groups
+## Second-order meta-analysis for functional groups
 (Section H in Figure 3 in main article)
 
-### 3.1: Performing meta-analyses 
+### Performing meta-analyses 
 Three for each of the 9 grouping terms: lnCVR, lnVR, lnRR
-#### 3.1.1: Preparing the data
+#### Preparing the data
 
@@
 
-#### 3.1.2: Re-structuring the data for each grouping term
+#### Re-structuring the data for each grouping term
 We here delete unused variables, and select the respective effect sizes.
@@
 # Visualising meta-analysis results
-## 1. Preparation for Figure 4 
-#### 1.1: Count data, based on First-order meta-analysis results
+## Preparation for Figure 4 
+#### Count data, based on First-order meta-analysis results
 This includes all separate eligible traits.
@@
 
-#### 1.2: Overall results of second order meta-analysis (Figure 4, Panel B)
-#### 1.3: Re-structure data for plotting 
+#### Overall results of second order meta-analysis (Figure 4, Panel B)
+#### Re-structure data for plotting 
 Data are re-structured, and grouping terms are being re-ordered
@@
 
-## 2. Figure 4
+## Figure 4
 
@@
 
-## 3. Preparation for Figure 5
-#### 3.1: Preparing data for traits with CI not overlapping 0
+## Preparation for Figure 5
+#### Preparing data for traits with CI not overlapping 0
 To further investigate sex bias in this dataset, and in particular if the extent of sex bias differs between traits, we investigate the magnitude of male- and female bias in significantly different traits on (both for means and variability)
@@
 
-## 4. Figure 5
+## Figure 5
 Sex biases in trait values across trait groups (Step J in Figure 3).
@@
 
-# Supplemental Tables and Figures
-
-## Supplemental Tables
-#### 1. Supplemental Table S1: "Strains and Center Sample Sizes"
-  This table summarises the available numbers of male and female mice from each strain and originating institution.
-
-```{r Table1_prep}
-  # Initial checks
-  length(unique(data$parameter_name)) # 232 traits
-  length(unique(data$parameter_group)) # 161 parameter groups
-  length(unique(data$procedure_name)) # 26 procedure groups
-  length(unique(data$biological_sample_id)) # 27147 individial mice  
-  # To show a table with number of males and females per strain per production center:
-
-  ST1 <- (cbind(data %>% group_by(production_center, strain_name) %>% count(biological_sample_id, sex) %>% count(sex) %>% print(n = Inf))) 
-```
-```{r Table1}
-
-  kable(ST1) %>%
-    kable_styling() %>%
-    scroll_box(width = "60%", height = "200px")
-
-```
-
-#### 2. Supplemental Table S2: "Numbers of correlated and uncorrelated traits"
-
-```{r, TableS2}  
-# Table detailing numbers of correlated and uncorrelated traits
-kable(cbind(meta1 %>% count(parameter_group))) %>%
-  kable_styling() %>%
-  scroll_box(width = "60%", height = "200px")
-```
-
-#### 3. Supplemental Table S3: "Meta-analysis results"
-
-  We use this corrected (for correlated traits) "results" table, which contains each of the meta-analytic means for all effect sizes of interest, for further analyses.
-We further use this table as part of the Shiny App, which is able to provide the percentage differences between males and females for mean, variance and coefficient of variance.
-
-```{r Table3}
-    kable(metacombo, digits = 3) %>%
-    kable_styling() %>%
-    scroll_box(width = "100%", height = "200px")
-
-```
-
-#### 4. Supplemental Table S4: "Meta-analysis on Functional Trait Groups"
-  SHINICHI
-  This table summarizes our overall meta-analyses on the functional trait group level ("GroupingTerm").
-Results for lnCVR, lnVR and lnRR and their respective upper and lower 95% CI's, standard error and I2 values are provided.
-```{r Table4}
-  kable(overall2, digits = 3) %>%
-   kable_styling() %>%
-  scroll_box(width = "100%", height = "200px")
-```
-
-#### 5. Supplemental Table S5: "Sex-biased effect sizes"
-  SHINICHI
-  This table provides some of the data plotted in Figures 5 and Figure S2.
-Here, we provide an overview over meta-analysis results performed on traits that were significantly biased to either sex.
-This table summarizes findings for both sexes and the respective functional trait groups.
-
-```{r}
-
-  female <- (overall.female.plot3)
-  female$Sex <- c("female")
-
-  male <- (overall.male.plot3)
-  male$Sex <- c("male")
-
-  mf_sig <- rbind(female,male)
-  mf_sig <- mf_sig [, c(1,17,2:16)]
-
-  mf_sig <- mf_sig %>% arrange(desc(GroupingTerm))
-
-  kable(mf_sig, digits = 3) %>%
-    kable_styling() %>%
-    scroll_box(width = "100%", height = "300px")
-```
-
-## Supplemental Figures
-### 1. Preparation for Figure S1
-#### 1.1: Preparing the data
-The supplemental figures include lnVR (in addition to lnCVR and lnRR, as presented in Figures 4 and 5)
-```{r FigS1_prep}
+# Supplemental Figures
+
+```{r FigS1_prep, echo = FALSE, eval = TRUE}
+### Preparing the data
+#The supplemental figures include lnVR (in addition to lnCVR and lnRR, as presented in Figures 4 and 5)
+
 # *Prepare data for all traits
@@
 
-#### 1.2: Preparing heterogeneity
-The analysis for heterogeneity follows the workflow of the above steps for the different meta-analyses.
+```{r hetero_loop, echo = FALSE, eval = TRUE, message=FALSE, warning=FALSE, include=FALSE, cache = TRUE}
+
+### Preparing heterogeneity
+
+#The analysis for heterogeneity follows the workflow of the above steps for the different meta-analyses.
 However, in the initial meta-analysis we extract sigma^2 and errors for mouse strains and centers (Institutions).
-As above a Loop is run and parameters extracted from metafor (sigma2's, s.nlevels)
-
-```{r hetero_loop, message=FALSE, warning=FALSE, include=FALSE }
+#As above a Loop is run and parameters extracted from metafor (sigma2's, s.nlevels)
+
 # Create dataframe to store results
@@
     {
-      data_par_age <- data_subset_parameterid_individual_by_age(data, t, age_min = 0, age_center = 100)
-
-      population_stats <- calculate_population_stats(data_par_age)
-
-      results <- create_meta_analysis_effect_sizes(population_stats)
+      results <- data %>% 
+                  data_subset_parameterid_individual_by_age(t) %>% 
+                  calculate_population_stats() %>% 
+                  create_meta_analysis_effect_sizes() %>%
+                  mutate(err = seq_len(n()))
 
@@
 
-      cvr. <- metafor::rma.mv(yi = effect_size_CVR, V = sample_variance_CVR, random = list(
-        ~ 1 | strain_name, ~ 1 | production_center,
-        ~ 1 | err
-      ), control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), data = results)
+      cvr. <- metafor::rma.mv(yi = effect_size_CVR, 
+                              V = sample_variance_CVR, 
+                              random = list(~ 1 | strain_name, ~ 1 | production_center,~ 1 | err), 
+                              control = list(optimizer = "optim", 
+                                             optmethod = "Nelder-Mead", 
+                                             maxit = 1000), 
+                              data = results)
+
       results.allhetero.grouping[t, 2] <- cvr.$sigma2[1]
@@
 
-      vr. <- metafor::rma.mv(yi = effect_size_VR, V = sample_variance_VR, random = list(
-        ~ 1 | strain_name, ~ 1 | production_center,
-        ~ 1 | err
-      ), control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), data = results)
+      vr. <- metafor::rma.mv(yi = effect_size_VR, 
+                             V = sample_variance_VR, 
+                             random = list(~ 1 | strain_name, ~ 1 | production_center, ~ 1 | err), 
+                             control = list(optimizer = "optim", 
+                                            optmethod = "Nelder-Mead", 
+                                            maxit = 1000), 
+                             data = results)
+
       results.allhetero.grouping[t, 8] <- vr.$sigma2[1]
@@
 
-      rr. <- metafor::rma.mv(yi = effect_size_RR, V = sample_variance_RR, random = list(
-        ~ 1 | strain_name, ~ 1 | production_center,
-        ~ 1 | err
-      ), control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), data = results)
+      rr. <- metafor::rma.mv(yi = effect_size_ROM, 
+                             V = sample_variance_ROM, 
+                             random = list(~ 1 | strain_name, ~ 1 | production_center, ~ 1 | err), 
+                             control = list(optimizer = "optim", 
+                                            optmethod = "Nelder-Mead", 
+                                            maxit = 1000), 
+                             data = results)
+
       results.allhetero.grouping[t, 14] <- rr.$sigma2[1]
@@
 
-Exclude traits without variation between mouse strains
-Merge data sets containing metafor results with procedure etc. names. Dealing with correlated parameters, and running of second -order meta-analysis for  heterogeneity data.
-
-```{r hetero}
+```{r hetero,eval=TRUE, echo = FALSE}
+#Exclude traits without variation between mouse strains
+#Merge data sets containing metafor results with procedure etc. names. Dealing with correlated parameters, and running of second -order meta-analysis for  heterogeneity data.
+
               results.allhetero.grouping2 <- results.allhetero.grouping[results.allhetero.grouping$s.nlevels.strain.VR != 0, ]
@@
 
-metahetero1b <-
-  metahetero1 %>%
+metahetero1b <- metahetero1                    %>%
                 group_by(parameter_group)      %>%
@@
 ```
-#### 6. Supplemental Table S6: "Heterogeneity within groups"
-  SHINICHI
-  This table summarizes our findings on heterogeneity due to institutions and mouse strains.
-These results are based on meta-analyses on sigma^2 and errors for mouse strains and centers (Institutions), following the identical workflow from above.
-
-```{r}
-
-  het <- heterog6 %>%
-    pivot_wider(names_from = parameter, values_from = value:ci.h) %>%
-    rename(lnCVR = value_heteroCVR, lnCVR_lower = ci.low_heteroCVR, lnCVR_higher = ci.high_heteroCVR, 
-         lnVR = value_heteroVR, lnVR_lower = ci.low_heteroVR, lnVR_higher = ci.high_heteroVR, 
-         lnRR = value_heteroRR, lnRR_lower = ci.low_heteroRR, lnRR_higher = ci.high_heteroRR,
-         CVR = mean_heteroCVR, VR = mean_heteroVR, RR = mean_heteroRR,  CVR_lower = ci.l_heteroCVR, 
-         VR_lower = ci.l_heteroVR, RR_lower = ci.l_heteroRR, 
-         CVR_higher = ci.h_heteroCVR, VR_higher = ci.h_heteroVR, RR_higher = ci.h_heteroRR) %>%
-    select(1,2,5,8,3,6,9,4,7,10,14,17,20,15,18,21,16,19,22)
-
-  kable(het, digits = 3) %>%
-    kable_styling() %>%
-    scroll_box(width = "100%", height = "200px")
-
-```
-
-### 2. Figure S1
-
-Similar to Figure 4 in the main article, this figure shows the numbers of either male (blue-green bars) or female (orange-red bars) biased traits  (Panel A) across functional groups, this time for lnCVR (left hand side), lnVR (middle) and lnRR (right hand side).
-Panel B shows effect sizes from separate meta-analysis for each functional group, and Panel C contains results of heterogeneity analyses.
-All three panels represent results evaluated across all traits (Phase 3, Figure 3).
-
-```{r FigS1, fig.height = 8, fig.width = 7}
-#### Combined Figure S1: overall Count data, Meta anlysis results, Heterogeneity
-
-FigS1 <- ggarrange(malebias_FigS1_alltraits, Metameta_FigS1_alltraits, HeteroS1, nrow = 3, align = "v", heights = c(1.1, 1, 1), labels = c("A", "B", "C"))
-FigS1
-#ggsave("FigS1_OverallResults.pdf", plot = FigS1, width = 6, height = 7)
-```
-
-### 3. Preparation for Figure S2
-#### 3.1: Preparation for Figure S2 A
-This Figure extends Figure 4, as it includes results not only for lnCVR and lnRR but also lnCVR.
+
+```{r, eval = TRUE, echo = FALSE}
+
+### Preparation for Figure S2
+#### Preparation for Figure S2 A
+#This Figure extends Figure 4, as it includes results not only for lnCVR and lnRR but also lnCVR.
 In addition, we compare two different assessments of sex-bias, significance (CI not overlapping zero) and sex differences in male / female ratios > 10%
-```{r}
 # Plot FigS2 all significant results (CI not overlapping zero) for males, count data
@@
 
+```{r FigS2_B, eval = TRUE, echo = FALSE}
+
 #### 3.2: Preparation for Figure S2 B (second-order meta-analysis)
 #### 3.3: Female Figure, significant and highly biased traits (Figure S2 B, left hand side panels)
-Preparing data for traits with CI not overlapping 0: 
-create column with 1= different from zero, 0= zero included in CI (for Figure S2 B, top left panel)
-```{r FigS2_B}
+#Preparing data for traits with CI not overlapping 0: 
+#create column with 1= different from zero, 0= zero included in CI (for Figure S2 B, top left panel)
+
 #Restructure data for plotting
@@
 ```
+
+```{r FigS2_B_right, eval = TRUE, echo = FALSE}
 #### 3.4: Male Figure, significant and highly biased traits (Figure S2 B, right hand side panels)
-Restructuring data with significant male bias (for Figure S2 B, top right panel)
-```{r FigS2_B_right}
+#Restructuring data with significant male bias (for Figure S2 B, top right panel)
+
 overall3.male.sigS <- gather(overall.male.plot3, parameter, value, c(lnCVR, lnVR, lnRR), factor_key = TRUE)
@@
 
-### 4. Figure S2
-
-This figure is an extension of sex biases, as shown in Figure 5 in the main text.
-Here, we include data on lnVR (middle panel), as well as athe second method of sex-differences comparison.
-The panels in A show differences in numbers of affected traits, in variance (lnCVR and lnVR) and means (lnRR), where there’s a significant difference between the sexes (i.e CI not overlapping zero), and where the sex bias is greater than 10% difference (regardless of significance).
+## Figure 5.1
+Figure \@ref(fig:FigS1) is similar to Figure 4 in the main article.
+
+```{r FigS1, fig.height = 8, fig.width = 7, fig.cap=" Numbers of either male (blue-green bars) or female (orange-red bars) biased traits  (Panel A) across functional groups, this time for lnCVR (left hand side), lnVR (middle) and lnRR (right hand side).
+Panel B shows effect sizes from separate meta-analysis for each functional group, and Panel C contains results of heterogeneity analyses.
+All three panels represent results evaluated across all traits (Phase 3, Figure 3)."}
+#### Combined Figure S1: overall Count data, Meta anlysis results, Heterogeneity
+
+FigS1 <- ggarrange(malebias_FigS1_alltraits, Metameta_FigS1_alltraits, HeteroS1, nrow = 3, align = "v", heights = c(1.1, 1, 1), labels = c("A", "B", "C"))
+FigS1
+#ggsave("FigS1_OverallResults.pdf", plot = FigS1, width = 6, height = 7)
+```
+
+## Figure 5.2
+
+Figure \@ref(fig:FigS2) is an extension of sex biases, as shown in Figure 5 in the main text. Here, we include data on lnVR (middle panel), as well as athe second method of sex-differences comparison.
+
+```{r FigS2, fig.height = 10, fig.width = 8, fig.cap=" A) Differences in numbers of affected traits, in variance (lnCVR and lnVR) and means (lnRR), where there’s a significant difference between the sexes (i.e CI not overlapping zero), and where the sex bias is greater than 10% difference (regardless of significance).
 Panel B depicts results for the sex bias in those traits that differ between the sexes (second-order meta-analysis).
 Triangles represent sex bias in means (response ratio) and black circles differences in the coefficient of variation ratio (mean-adjusted variability).
-The orange-red bars represent trait groups with a female bias, blue-green bars male-biased traits.
-```{r FigS2, fig.height = 10, fig.width = 8}
+The orange-red bars represent trait groups with a female bias, blue-green bars male-biased traits."}
 library(ggpubr)
@@
 
-## R Session Information
+# Supplemental Tables
+## Table 6.1
+
+```{r Table1_prep, echo = FALSE, eval = TRUE, results='hide'}
+  # Initial checks
+  length(unique(data$parameter_name)) # 232 traits
+  length(unique(data$parameter_group)) # 161 parameter groups
+  length(unique(data$procedure_name)) # 26 procedure groups
+  length(unique(data$biological_sample_id)) # 27147 individial mice  
+  # To show a table with number of males and females per strain per production center:
+     ST1 <- cbind(data %>% 
+                   group_by(production_center, strain_name) %>% 
+                   count(biological_sample_id, sex) %>% 
+                   count(sex) %>% 
+                   print(n = Inf))
+
+```
+```{r Table1, message=FALSE}
+
+         kable(ST1, caption = "Summary of the available numbers of male and female mice from each strain and originating institution.") %>%
+    kable_styling() %>%
+    scroll_box(width = "100%", height = "200px")
+
+```
+
+## Table 6.2
+
+```{r, TableS2}  
+# Table detailing numbers of correlated and uncorrelated traits
+kable(cbind(meta1 %>% count(parameter_group)), caption = "Trait categories (parameter_group) and the number of correlated traits within these categories. Traits were meta-analysed using robumeta") %>%
+  kable_styling() %>%
+  scroll_box(width = "100%", height = "200px")
+```
+
+## Table 6.3
+
+```{r Table3}
+    kable(metacombo, digits = 3, caption = "We use this corrected (for correlated traits) results table, which contains each of the meta-analytic means for all effect sizes of interest, for further analyses.
+We further use this table as part of the Shiny App, which is able to provide the percentage differences between males and females for mean, variance and coefficient of variance.") %>%
+    kable_styling() %>%
+    scroll_box(width = "100%", height = "200px")
+
+```
+
+## Table 6.4
+
+```{r Table4}
+  kable(overall2, digits = 3, caption = "Summary of overall meta-analyses on the functional trait group level (GroupingTerm).
+Results for lnCVR, lnVR and lnRR and their respective upper and lower 95% CI's, standard error and I2 values are provided.") %>%
+   kable_styling() %>%
+  scroll_box(width = "100%", height = "200px")
+```
+
+## Table 6.5
+
+```{r}
+
+  female <- (overall.female.plot3)
+  female$Sex <- c("female")
+
+  male <- (overall.male.plot3)
+  male$Sex <- c("male")
+
+  mf_sig <- rbind(female,male)
+  mf_sig <- mf_sig [, c(1,17,2:16)]
+
+  mf_sig <- mf_sig %>% arrange(desc(GroupingTerm))
+
+  kable(mf_sig, digits = 3, caption = "Provides an overview over meta-analysis results performed on traits that were significantly biased towards either sex.
+This table summarizes findings for both sexes and the respective functional trait groups.") %>%
+    kable_styling() %>%
+    scroll_box(width = "100%", height = "300px")
+```
+
+## Table 6.6
+
+```{r}
+
+  het <- heterog6 %>%
+    pivot_wider(names_from = parameter, values_from = value:ci.h) %>%
+    rename(lnCVR = value_heteroCVR, lnCVR_lower = ci.low_heteroCVR, lnCVR_higher = ci.high_heteroCVR, 
+         lnVR = value_heteroVR, lnVR_lower = ci.low_heteroVR, lnVR_higher = ci.high_heteroVR, 
+         lnRR = value_heteroRR, lnRR_lower = ci.low_heteroRR, lnRR_higher = ci.high_heteroRR,
+         CVR = mean_heteroCVR, VR = mean_heteroVR, RR = mean_heteroRR,  CVR_lower = ci.l_heteroCVR, 
+         VR_lower = ci.l_heteroVR, RR_lower = ci.l_heteroRR, 
+         CVR_higher = ci.h_heteroCVR, VR_higher = ci.h_heteroVR, RR_higher = ci.h_heteroRR) %>%
+    select(1,2,5,8,3,6,9,4,7,10,14,17,20,15,18,21,16,19,22)
+
+  kable(het, digits = 3, caption = "Summarizes our findings on heterogeneity due to institutions and mouse strains.
+These results are based on meta-analyses on sigma^2 and errors for mouse strains and centers (Institutions), following the identical workflow from above.") %>%
+    kable_styling() %>%
+    scroll_box(width = "100%", height = "200px")
+
+```
+
+# R Session Information
 

### 2020-05-17 scripts/MouseSexDiffApril20_2020.Rmd

@@
 author: Susanne Zajitschek,  Felix Zajitschek, Russell Bonduriansky, Robert  Brooks,
-  Will Cornwell, Daniel Falster, Malgorzata Lagisz, Jeremy Mason, Daniel Noble, Alistair
-  Senior & Shinichi Nakagawa
+  Will Cornwell, Daniel Falster, Malgorzata Lagisz, Jeremy Mason, Alistair
+  Senior, Daniel Noble, & Shinichi Nakagawa
 date: "`r Sys.Date()`"

### 2020-05-18 scripts/MouseSexDiffApril20_2020.Rmd
More major updates to Supplement, reorganising, linking with fig 1.1 and cutting down redundant code

@@
 
-Our supplementary material follows the general structure described in our methods (Figure  \@ref(fig:FigG1)).
+Our supplementary material follows the general structure described in our methods and are outlined here in Figure \@ref(fig:FigG1).
 Generally speaking, the first few sections describe the processes by which the data were cleaned and re-organised for analysis, and how the first order and second order meta-analsyes were conducted.
 Supplemental tables and figures that are referenecd within the main manuscript can be found at the end of the document or conviently referenecd quickly using the side table of contents panel.
+We will refer back to this figure as we describe the various aspects of the code and data processing.
 
@@
 
-### Sub-setting data
-Create a function for sub-setting the data to choose only one data point per individual per trait: "data_subset_parameterid_individual_by_age"
+### Loading and cleaning data
+
+These functions will load the raw and and do some cleaning to make it ready for further processing and analysis.
 
 ```{r}
-data_subset_parameterid_individual_by_age <- function(mydata, parameter, age_min=0, age_center=100) {
-  tmp <- mydata %>%
-    filter(
-      age_in_days >= age_min,
-      id == parameter
-    ) %>%
-    # take results for single individual closest to age_center
-    mutate(age_diff = abs(age_center - age_in_days)) %>%
-    group_by(biological_sample_id) %>%
-    filter(age_diff == min(age_diff)) %>%
-    select(-age_diff)# %>%
-
-  # still some individuals with multiple records (because same individual appear under different procedures, so filter to one record)
-  j <- match(unique(tmp$biological_sample_id), tmp$biological_sample_id)
-  tmp[j, ] 
-  }
-```
-
-### Population statistics
-Create a function called: "calculate_population_stats"
-This function groups animals from the same strain and institution together.
-This is done for each trait separately, and only for traits that have been measured in both sexes.
-Any group containing fewer than 5 individuals is excluded.
-
-```{r PopStatsFunction}
-
-multi_spread <- function(df, key, value) {
-    # quote key
-    keyq <- rlang::enquo(key)
-    # break value vector into quotes
-    valueq <- rlang::enquo(value)
-    s <- rlang::quos(!!valueq)
-    df %>% gather(variable, value, !!!s) %>%
-        unite(temp, !!keyq, variable) %>%
-        spread(temp, value)
-}
-
-# Will calculate population stats and exclude data that is irrelevant and not useful, it will also just convert the data straight away to wide format as opposed to long, making it ready for effect size calculations
-
-calculate_population_stats <- function(mydata, min_individuals = 5){
-    mydata %>% 
-    group_by(population,
-             production_center,  
-             strain_name,  
-             sex) %>%
-    summarise(trait  = parameter_name[1],
-              x_bar  = mean(data_point, na.rm = TRUE),
-              x_sd   =   sd(data_point, na.rm = TRUE),
-              n_ind  = n()) %>%
-    ungroup() %>%
-    filter(n_ind > min_individuals) %>%   # NOTE here that you are excluding data with 5 exactly....
-    group_by(population) %>%
-    filter(all(c("male", "female") %in% sex)) %>% # Removes any entries where only 1 sex is present
-    multi_spread(sex, c(x_bar, x_sd, n_ind))      # Spreads the data out into wide format, so sexes are beside each other which is more typical of meta-analytic data
-}
-
-```
-
-### Extraction of effect sizes and sample variances
-Function: "create_meta_analysis_effect_sizes"
-
-```{r EffectSizeFunction}
-
-#This function should mostly replace the entire function below, but I am still not quite sure what is happening in places.
-Adding all effect sizes together (maintaining the naming), err seems to be added to each trait?
-That needs to be added.It will make use of escalc which has the correct equations for effect size calculations.
-create_meta_analysis_effect_sizes <- function(mydata, measure = c("CVR", "VR", "ROM")){
-  for(i in 1:length(measure)){
-    mydata <- metafor::escalc(m1i  = male_x_bar, 
-                              m2i  = female_x_bar, 
-                              sd1i = male_x_sd, 
-                              sd2i = female_x_sd, 
-                              n1i  = male_n_ind, 
-                              n2i  = female_n_ind, 
-                              data = mydata, 
-                           measure = measure[i], 
-                         var.names = c(paste0("effect_size_", measure[i]), 
-                                      paste0("sample_variance_", measure[i])),
-                            append = TRUE)
-    }
-    return(mydata)
-}
-```
-
-## Load & clean data
-
-### Data loading and cleaning of the csv file
-
-We have already done this step and provide a cleaned up file which is less computationally intensive to deal with.
-The file has been saved in a folder called `export`.
-However, the `.csv` is provided in case this is preferred and can be imported and processed using following the steps below: [This code is currently excluded from showing in this `.html` file, but can be viewed and enabled / run in the down-loadable .rmd file.
-However, it requires the .gz file containing the raw data in the "export" folder.
-Unfortunately, that file can not be provided via Github, as it is too large (274MB).
-However, it is freely accessible and uploaded to zenodo.org (https://zenodo.org/deposit/3759701)
-
-```{r clean, eval=FALSE, include=FALSE}
 # loads the raw data, setting some default types for various columns
@@
     # subset to reasonable set of variables, date_of_experiment used as an indicator of batch-level effects
-    select(production_center, strain_name, strain_accession_id, biological_sample_id, pipeline_stable_id, procedure_group, procedure_name, sex, date_of_experiment, age_in_days, weight, parameter_name, data_point) %>%
+    select(production_center, 
+           strain_name, 
+           strain_accession_id, 
+           biological_sample_id, 
+           pipeline_stable_id, 
+           procedure_group, 
+           procedure_name, 
+           sex, 
+           date_of_experiment, 
+           age_in_days, 
+           weight, 
+           parameter_name, 
+           data_point) %>%
 
@@
 
+```
+
+### Sub-setting data
+Create a function for sub-setting the data to choose only one data point per individual per trait: "data_subset_parameterid_individual_by_age"
+
+```{r}
+data_subset_parameterid_individual_by_age <- function(mydata, parameter, age_min=0, age_center=100) {
+  tmp <- mydata %>%
+    filter(age_in_days >= age_min,
+           id == parameter) %>%
+  # Take results for single individual closest to age_center
+    mutate(age_diff = abs(age_center - age_in_days)) %>%
+    group_by(biological_sample_id) %>%
+    filter(age_diff == min(age_diff)) %>%
+    select(-age_diff)
+
+  # Still some individuals with multiple records (because same individual appears under different procedures, so filter to one record)
+  j <- match(unique(tmp$biological_sample_id), tmp$biological_sample_id)
+  tmp[j, ] 
+  }
+```
+
+### Population statistics
+Create a function called: "calculate_population_stats"
+This function groups animals from the same strain and institution together.
+This is done for each trait separately, and only for traits that have been measured in both sexes.
+Any group containing fewer than 6 individuals is excluded.
+
+```{r PopStatsFunction}
+
+# Function re-organises the data so that the male and female data are side-by-side as columns to make effect size calculations easier.
+multi_spread <- function(df, key, value) {
+    # quote key
+      keyq <- rlang::enquo(key)
+    # break value vector into quotes
+    valueq <- rlang::enquo(value)
+         s <- rlang::quos(!!valueq)
+
+         df                           %>% 
+        gather(variable, value, !!!s) %>%
+        unite(temp, !!keyq, variable) %>%
+        spread(temp, value)
+}
+
+# Function will calculate population stats and exclude data that is irrelevant and not useful, it will also just convert the data straight away to wide format making it ready for effect size calculations
+
+calculate_population_stats <- function(mydata, min_individuals = 5){
+    mydata %>% 
+    group_by(population,
+             production_center,  
+             strain_name,  
+             sex) %>%
+    summarise(trait  = parameter_name[1],
+              x_bar  = mean(data_point, na.rm = TRUE),
+              x_sd   =   sd(data_point, na.rm = TRUE),
+              n_ind  = n()) %>%
+    ungroup() %>%
+    filter(n_ind > min_individuals) %>%   # NOTE here that you are excluding data with 5 exactly....
+    group_by(population) %>%
+    filter(all(c("male", "female") %in% sex)) %>% # Removes any entries where only 1 sex is present
+    multi_spread(sex, c(x_bar, x_sd, n_ind))      # Spreads the data out into wide format, so sexes are beside each other which is more typical of meta-analytic data
+}
+
+```
+
+### Calculate effect sizes and sample variances
+Function: "create_meta_analysis_effect_sizes"
+
+```{r EffectSizeFunction}
+
+#This function takes the data and computes lnCVR, lnVR and ROM (lnRR) using male and female data to generate effect size statistics for meta-analyses
+create_meta_analysis_effect_sizes <- function(mydata, measure = c("CVR", "VR", "ROM")){
+  for(i in 1:length(measure)){
+    mydata <- metafor::escalc(m1i  = male_x_bar, 
+                              m2i  = female_x_bar, 
+                              sd1i = male_x_sd, 
+                              sd2i = female_x_sd, 
+                              n1i  = male_n_ind, 
+                              n2i  = female_n_ind, 
+                              data = mydata, 
+                           measure = measure[i], 
+                         var.names = c(paste0("effect_size_", measure[i]), 
+                                      paste0("sample_variance_", measure[i])),
+                            append = TRUE)
+    }
+    return(mydata)
+}
+```
+
+## Load & clean data
+We have already done this step and provide a cleaned up file which is less computationally intensive to deal with.
+The file has been saved in a folder called `export`.
+However, the `.csv` is provided in case this is preferred and can be imported and processed using following the steps below: [This code is currently excluded from showing in this `.html` file, but can be viewed and enabled / run in the down-loadable .rmd file.
+However, it requires the .gz file containing the raw data in the "export" folder.
+Unfortunately, that file can not be provided via Github, as it is too large (274MB).
+However, it is freely accessible and uploaded to zenodo.org (https://zenodo.org/deposit/3759701)
+
+```{r clean, eval=FALSE}
 # Load raw data - save cleaned dataset as RDS for reuse
@@
 ## Population as analysis unit
-(Step C, Figure 3 in main document)
+
+In this section, we cover the workflow described in Figure \@ref(fig:FigG1) C.
 
@@
 
-```{r loop, message=FALSE, warning=FALSE, include=FALSE}
+```{r loop, message=FALSE, warning=FALSE}
 
@@
 ## Meta-analysis: condensing non-independent traits 
-(Step F in Figure 3 in main article)
+This section describes the workflow depicted in Figure \@ref(fig:FigG1) F.
 
@@
 ## Second-order meta-analysis for functional groups
-(Section H in Figure 3 in main article)
+Here, we  describes the workflow depicted in Figure \@ref(fig:FigG1) H.
 
@@
 Three for each of the 9 grouping terms: lnCVR, lnVR, lnRR
+
 #### Preparing the data
@@
 ## Preparation for Figure 4 
-#### Count data, based on First-order meta-analysis results
+### Count data, based on First-order meta-analysis results
 This includes all separate eligible traits.
@@
 
-#### Overall results of second order meta-analysis (Figure 4, Panel B)
-#### Re-structure data for plotting 
+### Re-structure data for plotting 
 Data are re-structured, and grouping terms are being re-ordered
@@
 
-Panel A shows the numbers of traits across functional groups that are either male-biased (blue-green) or female-biased (orange-red), as calculated in Step D (figure 3).
-Panel B shows effect sizes and 95% CI from separate meta-analysis for each functional group (step H in Figure 3).
-Both panels represent results evaluated across all traits (Phase 3, Figure 3).
+Panel A shows the numbers of traits across functional groups that are either male-biased (blue-green) or female-biased (orange-red), as calculated in Figure \@ref(fig:FigG1) D.
+Panel B shows effect sizes and 95% CI from separate meta-analysis for each functional group (step H in Figure \@ref(fig:FigG1)).
+Both panels represent results evaluated across all traits (Phase 3, Figure \@ref(fig:FigG1)).
 Traits that are male biased are shown in blue, whereas female bias data is represented in orange.
@@
 ## Preparation for Figure 5
-#### Preparing data for traits with CI not overlapping 0
 To further investigate sex bias in this dataset, and in particular if the extent of sex bias differs between traits, we investigate the magnitude of male- and female bias in significantly different traits on (both for means and variability)
@@
 # Prepare data 
-# create column with 1= different from zero, 0= zero included in CI
+# create column with 1 = different from zero, 0 = zero included in CI
 
@@
 # as above: Prepare data for traits with CI not overlapping 0
-# create column with 1= different from zero, 0= zero included in CI
+# create column with 1 = different from zero, 0 = zero included in CI
 
@@
 plot3.female.meta.VR <- metacombo_female.plot3.VR %>%
-  mutate(model_lnVR = map(data, ~ metafor::rma.uni(
-    yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
-    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-  )))
+                        mutate(model_lnVR = map(data, ~ metafor::rma.uni(yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
+                                                control = list(optimizer = "optim", 
+                                                               optmethod = "Nelder-Mead", 
+                                                               maxit = 1000), 
+                                                verbose = F)))
 
 plot3.female.meta.RR <- metacombo_female.plot3.RR %>%
-  mutate(model_lnRR = map(data, ~ metafor::rma.uni(
-    yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
-    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-  )))
+                        mutate(model_lnRR = map(data, ~ metafor::rma.uni(yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
+                                                control = list(optimizer = "optim", 
+                                                               optmethod = "Nelder-Mead", 
+                                                               maxit = 1000), 
+                                                verbose = F)))
 
@@
 plot3.female.meta.CVR.all <- metacombo_female.plot3.CVR.all %>%
-  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(
-    yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower) / (2 * 1.96),
-    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-  )))
+                             mutate(model_lnCVR = map(data, ~ metafor::rma.uni(yi = .x$lnCVR, sei=(.x$lnCVR_upper-.x$lnCVR_lower)/(2 * 1.96),
+                                                       control = list(optimizer = "optim", 
+                                                                      optmethod = "Nelder-Mead", 
+                                                                      maxit = 1000),
+                                                       verbose = F)))
 
@@
 plot3.female.meta.VR.all <- metacombo_female.plot3.VR.all %>%
-  mutate(model_lnVR = map(data, ~ metafor::rma.uni(
-    yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
-    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-  )))
+  mutate(model_lnVR = map(data, ~ metafor::rma.uni(yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
+                          control = list(optimizer = "optim", 
+                                         optmethod = "Nelder-Mead", 
+                                         maxit = 1000), 
+                          verbose = F)))
 
@@
 plot3.female.meta.RR.all <- metacombo_female.plot3.RR.all %>%
-  mutate(model_lnRR = map(data, ~ metafor::rma.uni(
-    yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
-    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-  )))
-
-plot3.female.meta.RR.all <- plot3.female.meta.RR.all %>% mutate(GroupingTerm = "All")
+                            mutate(model_lnRR = map(data, 
+                                                    ~ metafor::rma.uni(yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
+                                                    control = list(optimizer = "optim", 
+                                                                   optmethod = "Nelder-Mead", 
+                                                                   maxit = 1000), 
+                                                    verbose = F)))
+
+plot3.female.meta.RR.all <- plot3.female.meta.RR.all %>% 
+                            mutate(GroupingTerm = "All")
 
@@
 
-plot3.female.meta.CVR.b <- as.data.frame(plot3.female.meta.CVR %>% group_by(GroupingTerm) %>%
-  mutate(
-    lnCVR = map_dbl(model_lnCVR, pluck(2)), lnCVR_lower = map_dbl(model_lnCVR, pluck(6)),
-    lnCVR_upper = map_dbl(model_lnCVR, pluck(7)), lnCVR_se = map_dbl(model_lnCVR, pluck(3)),
-    lnCVR_I2 = map_dbl(model_lnCVR, pluck("I2"))
-  ))[, c(1, 4:8)]
-
-add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA,NA))) %>% setNames(names(plot3.female.meta.CVR.b))
+plot3.female.meta.CVR.b <- as.data.frame(plot3.female.meta.CVR %>% 
+                                           group_by(GroupingTerm) %>%
+                                          mutate(    lnCVR = map_dbl(model_lnCVR, pluck(2)), 
+                                               lnCVR_lower = map_dbl(model_lnCVR, pluck(6)),
+                                               lnCVR_upper = map_dbl(model_lnCVR, pluck(7)), 
+                                                  lnCVR_se = map_dbl(model_lnCVR, pluck(3)),
+                                                  lnCVR_I2 = map_dbl(model_lnCVR, pluck("I2"))))[, c(1, 4:8)]
+
+add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA,NA))) %>% 
+                                 setNames(names(plot3.female.meta.CVR.b))
 
@@
 
-plot3.female.meta.VR.b <- as.data.frame(plot3.female.meta.VR %>% group_by(GroupingTerm) %>%
-  mutate(
-    lnVR = map_dbl(model_lnVR, pluck(2)), lnVR_lower = map_dbl(model_lnVR, pluck(6)),
-    lnVR_upper = map_dbl(model_lnVR, pluck(7)), lnVR_se = map_dbl(model_lnVR, pluck(3)),
-    lnVR_I2 = map_dbl(model_lnVR, pluck("I2"))
-  ))[, c(1, 4:8)]
+plot3.female.meta.VR.b <- as.data.frame(plot3.female.meta.VR %>% 
+                                        group_by(GroupingTerm) %>%
+                                        mutate(      lnVR = map_dbl(model_lnVR, pluck(2)), 
+                                               lnVR_lower = map_dbl(model_lnVR, pluck(6)),
+                                               lnVR_upper = map_dbl(model_lnVR, pluck(7)), 
+                                                  lnVR_se = map_dbl(model_lnVR, pluck(3)),
+                                                  lnVR_I2 = map_dbl(model_lnVR, pluck("I2"))))[, c(1, 4:8)]
 
@@
 
-plot3.female.meta.RR.b <- as.data.frame(plot3.female.meta.RR %>% group_by(GroupingTerm) %>%
-  mutate(
-    lnRR = map_dbl(model_lnRR, pluck(2)), lnRR_lower = map_dbl(model_lnRR, pluck(6)),
-    lnRR_upper = map_dbl(model_lnRR, pluck(7)), lnRR_se = map_dbl(model_lnRR, pluck(3)),
-    lnRR_I2 = map_dbl(model_lnRR, pluck("I2"))
-  ))[, c(1, 4:8)]
+plot3.female.meta.RR.b <- as.data.frame(plot3.female.meta.RR %>% 
+                                        group_by(GroupingTerm) %>%
+                                        mutate(      lnRR = map_dbl(model_lnRR, pluck(2)), 
+                                               lnRR_lower = map_dbl(model_lnRR, pluck(6)), 
+                                               lnRR_upper = map_dbl(model_lnRR, pluck(7)), 
+                                                  lnRR_se = map_dbl(model_lnRR, pluck(3)),
+                                                  lnRR_I2 = map_dbl(model_lnRR, pluck("I2"))))[, c(1, 4:8)]
 
@@
 
-overall.female.plot3$GroupingTerm <- factor(overall.female.plot3$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
-overall.female.plot3$GroupingTerm <- factor(overall.female.plot3$GroupingTerm, rev(levels(overall.female.plot3$GroupingTerm)))
+overall.female.plot3$GroupingTerm <- factor(overall.female.plot3$GroupingTerm, 
+                                            levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", 
+                                                       "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
+overall.female.plot3$GroupingTerm <- factor(overall.female.plot3$GroupingTerm, 
+                                            rev(levels(overall.female.plot3$GroupingTerm)))
 
@@
   filter(parameter == "lnCVR") %>%
-  mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
+  mutate(ci.low = lnCVR_lower, 
+         ci.high = lnCVR_upper)
+
 # lnVR.ci <- overall3.female.sig  %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
+
 lnRR.ci <- overall3.female.sig %>%
@@
 ## Figure 5
-Sex biases in trait values across trait groups (Step J in Figure 3).
+Sex biases in trait values across trait groups (Step J in Figure \@ref(fig:FigG1)).
 The panels in A show differences in the number of affected traits, in variance (lnCVR) and means (lnRR), where there is a significant difference between the sexes (i.e CI not overlapping zero).
@@
       yi = .x$var.CVR, sei = sqrt(1 / 2 * (.x$N.CVR - 1)),
-      control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 10000, stepadj = 0.5), verbose = F
-    )),
+      control = list(optimizer = "optim", 
+                     optmethod = "Nelder-Mead",
+                     maxit = 10000, 
+                     stepadj = 0.5), verbose = F)),
     model_heteroVR = map(data, ~ metafor::rma.uni(
       yi = .x$var.VR, sei = sqrt(1 / 2 * (.x$N.VR - 1)),
-      control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 10000, stepadj = 0.5), verbose = F
-    )),
+      control = list(optimizer = "optim", 
+                     optmethod = "Nelder-Mead", 
+                     maxit = 10000, 
+                     stepadj = 0.5), verbose = F)),
     model_heteroRR = map(data, ~ metafor::rma.uni(
       yi = .x$var.RR, sei = sqrt(1 / 2 * (.x$N.RR - 1)),
-      control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 10000, stepadj = 0.5), verbose = F
-    ))
-  )
+      control = list(optimizer = "optim", 
+                     optmethod = "Nelder-Mead", 
+                     maxit = 10000, 
+                     stepadj = 0.5), verbose = F)) )
 
@@
 
-  mutate(
-    model_heteroCVR = map(data, ~ metafor::rma.uni(
+  mutate( model_heteroCVR = map(data, ~ metafor::rma.uni(
       yi = .x$var.CVR, sei = sqrt(1 / 2 * (.x$N.CVR - 1)),
-      control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 10000, stepadj = 0.5), verbose = F
-    )),
-    model_heteroVR = map(data, ~ metafor::rma.uni(
-      yi = .x$var.VR, sei = sqrt(1 / 2 * (.x$N.VR - 1)),
-      control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 10000, stepadj = 0.5), verbose = F
-    )),
-    model_heteroRR = map(data, ~ metafor::rma.uni(
-      yi = .x$var.RR, sei = sqrt(1 / 2 * (.x$N.RR - 1)),
-      control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 10000, stepadj = 0.5), verbose = F
-    ))
-  )
+      control = list(optimizer = "optim", 
+                     optmethod = "Nelder-Mead", 
+                     maxit = 10000, 
+                     stepadj = 0.5), verbose = F)),
+    model_heteroVR = map(data, ~ metafor::rma.uni(yi = .x$var.VR, sei = sqrt(1 / 2 * (.x$N.VR - 1)),
+      control = list(optimizer = "optim", 
+                     optmethod = "Nelder-Mead", 
+                     maxit = 10000, 
+                     stepadj = 0.5), verbose = F)),
+    model_heteroRR = map(data, ~ metafor::rma.uni(yi = .x$var.RR, sei = sqrt(1 / 2 * (.x$N.RR - 1)),
+      control = list(optimizer = "optim", 
+                     optmethod = "Nelder-Mead", 
+                     maxit = 10000, 
+                     stepadj = 0.5), verbose = F)))
 
@@
 
-Behaviour. <- heterog1 %>%
-  filter(., GroupingTerm == "Behaviour") %>%
+extract_heterogeneity <- function(data, type){
+
+  tmp <- data %>%
+         filter(., GroupingTerm == type) %>%
          select(., -data) %>%
-  mutate(
-    heteroCVR = .[[2]][[1]]$b, heteroCVR_lower = .[[2]][[1]]$ci.lb, heteroCVR_upper = .[[2]][[1]]$ci.ub, heteroCVR_se = .[[2]][[1]]$se,
-    heteroVR = .[[3]][[1]]$b, heteroVR_lower = .[[3]][[1]]$ci.lb, heteroVR_upper = .[[3]][[1]]$ci.ub, heteroVR_se = .[[3]][[1]]$se,
-    heteroRR = .[[4]][[1]]$b, heteroRR_lower = .[[4]][[1]]$ci.lb, heteroRR_upper = .[[4]][[1]]$ci.ub, heteroRR_se = .[[4]][[1]]$se
-  ) %>%
+         mutate(heteroCVR       = .[[2]][[1]]$b, 
+                heteroCVR_lower = .[[2]][[1]]$ci.lb, 
+                heteroCVR_upper = .[[2]][[1]]$ci.ub, 
+                heteroCVR_se    = .[[2]][[1]]$se,
+                heteroVR        = .[[3]][[1]]$b, 
+                heteroVR_lower  = .[[3]][[1]]$ci.lb, 
+                heteroVR_upper  = .[[3]][[1]]$ci.ub, 
+                heteroVR_se     = .[[3]][[1]]$se,
+                heteroRR        = .[[4]][[1]]$b, 
+                heteroRR_lower  = .[[4]][[1]]$ci.lb, 
+                heteroRR_upper  = .[[4]][[1]]$ci.ub, 
+                heteroRR_se     = .[[4]][[1]]$se) %>%
         select(., GroupingTerm, heteroCVR:heteroRR_se)
 
-Immunology. <- heterog1 %>%
-  filter(., GroupingTerm == "Immunology") %>%
-  select(., -data) %>%
-  mutate(
-    heteroCVR = .[[2]][[1]]$b, heteroCVR_lower = .[[2]][[1]]$ci.lb, heteroCVR_upper = .[[2]][[1]]$ci.ub, heteroCVR_se = .[[2]][[1]]$se,
-    heteroVR = .[[3]][[1]]$b, heteroVR_lower = .[[3]][[1]]$ci.lb, heteroVR_upper = .[[3]][[1]]$ci.ub, heteroVR_se = .[[3]][[1]]$se,
-    heteroRR = .[[4]][[1]]$b, heteroRR_lower = .[[4]][[1]]$ci.lb, heteroRR_upper = .[[4]][[1]]$ci.ub, heteroRR_se = .[[4]][[1]]$se
-  ) %>%
-  select(., GroupingTerm, heteroCVR:heteroRR_se)
-
-Hematology. <- heterog1 %>%
-  filter(., GroupingTerm == "Hematology") %>%
-  select(., -data) %>%
-  mutate(
-    heteroCVR = .[[2]][[1]]$b, heteroCVR_lower = .[[2]][[1]]$ci.lb, heteroCVR_upper = .[[2]][[1]]$ci.ub, heteroCVR_se = .[[2]][[1]]$se,
-    heteroVR = .[[3]][[1]]$b, heteroVR_lower = .[[3]][[1]]$ci.lb, heteroVR_upper = .[[3]][[1]]$ci.ub, heteroVR_se = .[[3]][[1]]$se,
-    heteroRR = .[[4]][[1]]$b, heteroRR_lower = .[[4]][[1]]$ci.lb, heteroRR_upper = .[[4]][[1]]$ci.ub, heteroRR_se = .[[4]][[1]]$se
-  ) %>%
-  select(., GroupingTerm, heteroCVR:heteroRR_se)
-
-Hearing. <- heterog1 %>%
-  filter(., GroupingTerm == "Hearing") %>%
-  select(., -data) %>%
-  mutate(
-    heteroCVR = .[[2]][[1]]$b, heteroCVR_lower = .[[2]][[1]]$ci.lb, heteroCVR_upper = .[[2]][[1]]$ci.ub, heteroCVR_se = .[[2]][[1]]$se,
-    heteroVR = .[[3]][[1]]$b, heteroVR_lower = .[[3]][[1]]$ci.lb, heteroVR_upper = .[[3]][[1]]$ci.ub, heteroVR_se = .[[3]][[1]]$se,
-    heteroRR = .[[4]][[1]]$b, heteroRR_lower = .[[4]][[1]]$ci.lb, heteroRR_upper = .[[4]][[1]]$ci.ub, heteroRR_se = .[[4]][[1]]$se
-  ) %>%
-  select(., GroupingTerm, heteroCVR:heteroRR_se)
-
-Physiology. <- heterog1 %>%
-  filter(., GroupingTerm == "Physiology") %>%
-  select(., -data) %>%
-  mutate(
-    heteroCVR = .[[2]][[1]]$b, heteroCVR_lower = .[[2]][[1]]$ci.lb, heteroCVR_upper = .[[2]][[1]]$ci.ub, heteroCVR_se = .[[2]][[1]]$se,
-    heteroVR = .[[3]][[1]]$b, heteroVR_lower = .[[3]][[1]]$ci.lb, heteroVR_upper = .[[3]][[1]]$ci.ub, heteroVR_se = .[[3]][[1]]$se,
-    heteroRR = .[[4]][[1]]$b, heteroRR_lower = .[[4]][[1]]$ci.lb, heteroRR_upper = .[[4]][[1]]$ci.ub, heteroRR_se = .[[4]][[1]]$se
-  ) %>%
-  select(., GroupingTerm, heteroCVR:heteroRR_se)
-
-Metabolism. <- heterog1 %>%
-  filter(., GroupingTerm == "Metabolism") %>%
-  select(., -data) %>%
-  mutate(
-    heteroCVR = .[[2]][[1]]$b, heteroCVR_lower = .[[2]][[1]]$ci.lb, heteroCVR_upper = .[[2]][[1]]$ci.ub, heteroCVR_se = .[[2]][[1]]$se,
-    heteroVR = .[[3]][[1]]$b, heteroVR_lower = .[[3]][[1]]$ci.lb, heteroVR_upper = .[[3]][[1]]$ci.ub, heteroVR_se = .[[3]][[1]]$se,
-    heteroRR = .[[4]][[1]]$b, heteroRR_lower = .[[4]][[1]]$ci.lb, heteroRR_upper = .[[4]][[1]]$ci.ub, heteroRR_se = .[[4]][[1]]$se
-  ) %>%
-  select(., GroupingTerm, heteroCVR:heteroRR_se)
-
-Morphology. <- heterog1 %>%
-  filter(., GroupingTerm == "Morphology") %>%
-  select(., -data) %>%
-  mutate(
-    heteroCVR = .[[2]][[1]]$b, heteroCVR_lower = .[[2]][[1]]$ci.lb, heteroCVR_upper = .[[2]][[1]]$ci.ub, heteroCVR_se = .[[2]][[1]]$se,
-    heteroVR = .[[3]][[1]]$b, heteroVR_lower = .[[3]][[1]]$ci.lb, heteroVR_upper = .[[3]][[1]]$ci.ub, heteroVR_se = .[[3]][[1]]$se,
-    heteroRR = .[[4]][[1]]$b, heteroRR_lower = .[[4]][[1]]$ci.lb, heteroRR_upper = .[[4]][[1]]$ci.ub, heteroRR_se = .[[4]][[1]]$se
-  ) %>%
-  select(., GroupingTerm, heteroCVR:heteroRR_se)
-
-Heart. <- heterog1 %>%
-  filter(., GroupingTerm == "Heart") %>%
-  select(., -data) %>%
-  mutate(
-    heteroCVR = .[[2]][[1]]$b, heteroCVR_lower = .[[2]][[1]]$ci.lb, heteroCVR_upper = .[[2]][[1]]$ci.ub, heteroCVR_se = .[[2]][[1]]$se,
-    heteroVR = .[[3]][[1]]$b, heteroVR_lower = .[[3]][[1]]$ci.lb, heteroVR_upper = .[[3]][[1]]$ci.ub, heteroVR_se = .[[3]][[1]]$se,
-    heteroRR = .[[4]][[1]]$b, heteroRR_lower = .[[4]][[1]]$ci.lb, heteroRR_upper = .[[4]][[1]]$ci.ub, heteroRR_se = .[[4]][[1]]$se
-  ) %>%
-  select(., GroupingTerm, heteroCVR:heteroRR_se)
-
-Eye. <- heterog1 %>%
-  filter(., GroupingTerm == "Eye") %>%
-  select(., -data) %>%
-  mutate(
-    heteroCVR = .[[2]][[1]]$b, heteroCVR_lower = .[[2]][[1]]$ci.lb, heteroCVR_upper = .[[2]][[1]]$ci.ub, heteroCVR_se = .[[2]][[1]]$se,
-    heteroVR = .[[3]][[1]]$b, heteroVR_lower = .[[3]][[1]]$ci.lb, heteroVR_upper = .[[3]][[1]]$ci.ub, heteroVR_se = .[[3]][[1]]$se,
-    heteroRR = .[[4]][[1]]$b, heteroRR_lower = .[[4]][[1]]$ci.lb, heteroRR_upper = .[[4]][[1]]$ci.ub, heteroRR_se = .[[4]][[1]]$se
-  ) %>%
-  select(., GroupingTerm, heteroCVR:heteroRR_se)
+  return(tmp)
+}
+
+   Behaviour. <- extract_heterogeneity(heterog1, type = "Behaviour")
+  Immunology. <- extract_heterogeneity(heterog1, type = "Immunology")
+  Hematology. <- extract_heterogeneity(heterog1, type = "Hematology")
+     Hearing. <- extract_heterogeneity(heterog1, type = "Hearing")
+  Physiology. <- extract_heterogeneity(heterog1, type = "Physiology")
+  Metabolism. <- extract_heterogeneity(heterog1, type = "Metabolism")
+  Morphology. <- extract_heterogeneity(heterog1, type = "Morphology")
+       Heart. <- extract_heterogeneity(heterog1, type = "Heart")
+         Eye. <- extract_heterogeneity(heterog1, type = "Eye")
 
 #Reorder to be able to keep cell referencing 
-heterog1_all <- heterog1_all %>% mutate(GroupingTerm = "All") %>% select(GroupingTerm, everything())
+heterog1_all <- heterog1_all %>% 
+                mutate(GroupingTerm = "All") %>% 
+                select(GroupingTerm, everything())
 
@@
         select(., -data) %>%
-  mutate(
-    heteroCVR = .[[2]][[1]]$b, heteroCVR_lower = .[[2]][[1]]$ci.lb, heteroCVR_upper = .[[2]][[1]]$ci.ub, heteroCVR_se = .[[2]][[1]]$se,
-    heteroVR = .[[3]][[1]]$b, heteroVR_lower = .[[3]][[1]]$ci.lb, heteroVR_upper = .[[3]][[1]]$ci.ub, heteroVR_se = .[[3]][[1]]$se,
-    heteroRR = .[[4]][[1]]$b, heteroRR_lower = .[[4]][[1]]$ci.lb, heteroRR_upper = .[[4]][[1]]$ci.ub, heteroRR_se = .[[4]][[1]]$se
-  ) %>%
+        mutate(heteroCVR       = .[[2]][[1]]$b, 
+               heteroCVR_lower = .[[2]][[1]]$ci.lb, 
+               heteroCVR_upper = .[[2]][[1]]$ci.ub, 
+               heteroCVR_se    = .[[2]][[1]]$se, 
+               heteroVR        = .[[3]][[1]]$b, 
+               heteroVR_lower  = .[[3]][[1]]$ci.lb, 
+               heteroVR_upper  = .[[3]][[1]]$ci.ub, 
+               heteroVR_se     = .[[3]][[1]]$se, 
+               heteroRR        = .[[4]][[1]]$b, 
+               heteroRR_lower  = .[[4]][[1]]$ci.lb, 
+               heteroRR_upper  = .[[4]][[1]]$ci.ub, 
+               heteroRR_se     = .[[4]][[1]]$se) %>%
         select(., GroupingTerm, heteroCVR:heteroRR_se)
@@
 heterog2 <- bind_rows(Behaviour., Morphology., Metabolism., Physiology., Immunology., Hematology., Heart., Hearing., Eye., All.)
-# str(heterog2)
 
@@
                 filter(parameter == "heteroCVR") %>%
-  mutate(ci.low = heteroCVR_lower, ci.high = heteroCVR_upper)
+                mutate(ci.low = heteroCVR_lower, 
+                       ci.high = heteroCVR_upper)
 heteroVR.ci <-  heterog3 %>%
                 filter(parameter == "heteroVR") %>%
-  mutate(ci.low = heteroVR_lower, ci.high = heteroVR_upper)
+                mutate(ci.low = heteroVR_lower, 
+                       ci.high = heteroVR_upper)
 heteroRR.ci <-  heterog3 %>%
                 filter(parameter == "heteroRR") %>%
-  mutate(ci.low = heteroRR_lower, ci.high = heteroRR_upper)
+                mutate(ci.low = heteroRR_lower, 
+                       ci.high = heteroRR_upper)
 
@@
 
-heterog4$GroupingTerm <- factor(heterog4$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
-heterog4$GroupingTerm <- factor(heterog4$GroupingTerm, rev(levels(heterog4$GroupingTerm)))
+heterog4$GroupingTerm <- factor(heterog4$GroupingTerm, 
+                                levels = c("Behaviour", "Morphology", "Metabolism", 
+                                           "Physiology", "Immunology", "Hematology", "Heart", 
+                                           "Hearing", "Eye", "All"))
+
+heterog4$GroupingTerm <- factor(heterog4$GroupingTerm, 
+                                rev(levels(heterog4$GroupingTerm)))
 heterog4$label <- "All traits"
@@
     axis.title.x = element_text(hjust = 0.5, size = 14),
-    axis.title.y = element_blank()
-  )
+    axis.title.y = element_blank())
 ```
@@
 meta.plot2.sig.cS$sig <- ifelse(meta.plot2.sig.cS$trait == "lnCVR", meta.plot2.sig.cS$lnCVRsig,
-  ifelse(meta.plot2.sig.cS$trait == "lnVR", meta.plot2.sig.cS$lnVRsig, meta.plot2.sig.cS$lnRRsig)
-)
+  ifelse(meta.plot2.sig.cS$trait == "lnVR", meta.plot2.sig.cS$lnVRsig, meta.plot2.sig.cS$lnRRsig))
 
@@
                       group_by_at(vars(trait, GroupingTerm)) %>%
-  summarise(
-    malebias = sum(value > log(11 / 10)), femalebias = sum(value < log(9 / 10)), total = malebias + femalebias,
-    malepercent = malebias * 100 / total, femalepercent = femalebias * 100 / total
-  )
+                      summarise(malebias = sum(value > log(11 / 10)), 
+                                femalebias = sum(value < log(9 / 10)), 
+                                total = malebias + femalebias,
+                                malepercent = malebias * 100 / total, 
+                                femalepercent = femalebias * 100 / total)
 
@@
 
-meta.plot2.over10.e <- meta.plot2.over10.d %>% group_by(trait, sex) %>% 
-  summarise(GroupingTerm = "All", malebias = sum(malebias), femalebias = sum(femalebias), total = malebias + femalebias, 
-            label = "Sex difference in m/f ratios > 10%", samplesize = sum(samplesize)) %>%
-  mutate(percent = ifelse(sex == "femalepercent", femalebias*100/(malebias + femalebias), malebias*100/(malebias + femalebias))) %>%
+meta.plot2.over10.e <- meta.plot2.over10.d %>% 
+                      group_by(trait, sex) %>% 
+                      summarise(GroupingTerm = "All", malebias = sum(malebias), 
+                                femalebias = sum(femalebias), 
+                                total = malebias + femalebias, 
+                                label = "Sex difference in m/f ratios > 10%", 
+                                samplesize = sum(samplesize)) %>%
+                      mutate(percent = ifelse(sex == "femalepercent", 
+                                              femalebias*100/(malebias + femalebias), 
+                                              malebias*100/(malebias + femalebias))) %>%
                       bind_rows(meta.plot2.over10.d, .) %>%
@@
 Panel B shows effect sizes from separate meta-analysis for each functional group, and Panel C contains results of heterogeneity analyses.
-All three panels represent results evaluated across all traits (Phase 3, Figure 3)."}
+All three panels represent results evaluated across all traits (Phase 3, Figure 1.1)."}
+
 #### Combined Figure S1: overall Count data, Meta anlysis results, Heterogeneity
@@
 FigS2b <- ggarrange(Metameta_FigS2_female.sig, Metameta_FigS2_male.sig,
-  ncol = 2, nrow = 1, widths = c(1, 1.30), heights = c(1.2, 1.2)
-)
+  ncol = 2, nrow = 1, widths = c(1, 1.30), heights = c(1.2, 1.2))
 
 FigS2d <- ggarrange(Metameta_Fig3_female.perc, Metameta_Fig3_male.perc,
-  ncol = 2, nrow = 1, widths = c(1, 1.20), heights = c(1.1, 1.1)
-)
+  ncol = 2, nrow = 1, widths = c(1, 1.20), heights = c(1.1, 1.1))
 
@@
 
-  mf_sig <- mf_sig %>% arrange(desc(GroupingTerm))
-
-  kable(mf_sig, digits = 3, caption = "Provides an overview over meta-analysis results performed on traits that were significantly biased towards either sex.
+      mf_sig <- mf_sig %>% 
+                arrange(desc(GroupingTerm))
+
+  kable(mf_sig, digits = 3, caption = "Provides an overview of meta-analysis results performed on traits that were significantly biased towards either sex.
 This table summarizes findings for both sexes and the respective functional trait groups.") %>%
@@
     pivot_wider(names_from = parameter, values_from = value:ci.h) %>%
-    rename(lnCVR = value_heteroCVR, lnCVR_lower = ci.low_heteroCVR, lnCVR_higher = ci.high_heteroCVR, 
-         lnVR = value_heteroVR, lnVR_lower = ci.low_heteroVR, lnVR_higher = ci.high_heteroVR, 
-         lnRR = value_heteroRR, lnRR_lower = ci.low_heteroRR, lnRR_higher = ci.high_heteroRR,
-         CVR = mean_heteroCVR, VR = mean_heteroVR, RR = mean_heteroRR,  CVR_lower = ci.l_heteroCVR, 
-         VR_lower = ci.l_heteroVR, RR_lower = ci.l_heteroRR, 
-         CVR_higher = ci.h_heteroCVR, VR_higher = ci.h_heteroVR, RR_higher = ci.h_heteroRR) %>%
+    rename(lnCVR = value_heteroCVR, 
+           lnCVR_lower = ci.low_heteroCVR, 
+           lnCVR_higher = ci.high_heteroCVR, 
+           lnVR = value_heteroVR, 
+           lnVR_lower = ci.low_heteroVR, 
+           lnVR_higher = ci.high_heteroVR, 
+           lnRR = value_heteroRR, 
+           lnRR_lower = ci.low_heteroRR, 
+           lnRR_higher = ci.high_heteroRR,
+           CVR = mean_heteroCVR, 
+           VR = mean_heteroVR, 
+           RR = mean_heteroRR,  
+           CVR_lower = ci.l_heteroCVR, 
+           VR_lower = ci.l_heteroVR, 
+           RR_lower = ci.l_heteroRR, 
+           CVR_higher = ci.h_heteroCVR, 
+           VR_higher = ci.h_heteroVR, 
+           RR_higher = ci.h_heteroRR) %>%
     select(1,2,5,8,3,6,9,4,7,10,14,17,20,15,18,21,16,19,22)
@@
 ```{r}
-sessionInfo() %>% pander()
-```
+sessionInfo()
+```

### 2020-05-18 scripts/MouseSexDiffApril20_2020.Rmd
Updates

@@
 output:
+  word_document:
+    toc: yes
+    toc_depth: '4'
+  html_notebook:
+    toc: yes
+  pdf_document:
+    toc: yes
+    toc_depth: '4'
   bookdown::html_document2: 
@@
             theme: flatly
-  html_notebook:
-    toc: yes
-  word_document:
-    toc: yes
-    toc_depth: '4'
-  pdf_document:
-    toc: yes
-    toc_depth: '4'
 subtitle: Electronic Supplementary Material
@@
 
-Our supplementary material follows the general structure described in our methods and are outlined here in Figure \@ref(fig:FigG1).
-Generally speaking, the first few sections describe the processes by which the data were cleaned and re-organised for analysis, and how the first order and second order meta-analsyes were conducted.
-Supplemental tables and figures that are referenecd within the main manuscript can be found at the end of the document or conviently referenecd quickly using the side table of contents panel.
-We will refer back to this figure as we describe the various aspects of the code and data processing.
+This supplementary material follows the general structure described in our methods and is outlined here in Figure \@ref(fig:FigG1).
+Generally speaking, the first few sections describe the processes by which the data were cleaned and re-organised for analysis.
+This iss followed by how the first order and second order meta-analsyes were conducted.
+Supplemental tables and figures that are referenecd within the main manuscript can be found at the end of the document.
+Various parts of the workflow can be conviently referenecd using the side table of contents panel.
+We will refer back to this figure as we describe the various aspects of the code and data processing in relevant places.
 
@@
 
-In this section, we cover the workflow described in Figure \@ref(fig:FigG1) C.
+In this section, we cover the workflow described in Figure \@ref(fig:FigG1) C and D.
 
 ### Loop through meta-analyses on all traits
+
+This section covers Figure \@ref(fig:FigG1) C, by conducting a meta-analsyis for all traits and producing the meta-analysed effect sizes (lnVR, lnCVR and lnRR).
 
@@
 
-```{r loop, message=FALSE, warning=FALSE}
+```{r loop, message=FALSE, warning=FALSE, result = "hide"}
 
@@
 
-Procedure names, grouping variables and trait names ("parameter_names") are merged back together with the results from the metafor analysis above.
+Here we cover Figure \@ref(fig:FigG1) D, removing non-coverging model results and non-informative traits.Procedure names, grouping variables and trait names ("parameter_names") are the merged back together with the results from the metafor analysis above.
 
@@
 ## Meta-analysis: condensing non-independent traits 
-This section describes the workflow depicted in Figure \@ref(fig:FigG1) F.
-
-### Dealing with Correlated Parameters, preparation
-
 This dataset contained a number of highly correlated traits, such as different kinds of cell counts (for example hierarchical parameterization within immunological assays).
 As those data-points are not independent of each other,  we conducted meta analyses on these correlated parameters to collapse the number of levels.
+This section describes the workflow depicted in Figure \@ref(fig:FigG1) E & F.
 
@@
 All instances, where there are 2 or more traits associated with the same parameter group (90 cases), are selected for a "mini-meta analysis", which removes the issue of correlation.
+The workflow here relates to Figure \@ref(fig:FigG1) E.
 
@@
 ### Meta-analyses on correlated (sub-)traits, using `robumeta` 
-Here we pepare the subset of the data (using nest()), and in this first step the model of the meta-analysis effect sizes are calculated
+Here we pepare the subset of the data (using nest()), and in this first step the model of the meta-analysis effect sizes are calculated.
+This section specifically undertakes the workflow described in Figure \@ref(fig:FigG1) F.
 
@@
 ## Second-order meta-analysis for functional groups
-Here, we  describes the workflow depicted in Figure \@ref(fig:FigG1) H.
-
-### Performing meta-analyses 
-Three for each of the 9 grouping terms: lnCVR, lnVR, lnRR
-
-#### Preparing the data
-
-Nesting, calculating the number of parameters within each grouping term, and running the meta-analyses
+Here, we  describe the workflow depicted in Figure \@ref(fig:FigG1) H.
+We now use our uncorrelated traits from our first order meta-analysis to conduct a secondary meta-analysis by analysing the 9 functional trait groups.
+We esatimte an overall mean lnCVR, lnVR and lnRR for each functional trait group.
+
+### Preparing the data
+
+Nesting, calculating the number of parameters within each grouping term, and running the meta-analyses.
 
@@
 
-# **calculate number of parameters per grouping term
+# **Calculate number of parameters per grouping term
 
@@
                       yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower) / (2 * 1.96),
-      control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-    )),
+                      control = list(optimizer = "optim", 
+                                     optmethod = "Nelder-Mead", 
+                                     maxit = 1000), 
+                      verbose = F)),
     model_lnVR = map(data, ~ metafor::rma.uni(
                     yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
-      control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-    )),
+                    control = list(optimizer = "optim", 
+                                   optmethod = "Nelder-Mead", 
+                                   maxit = 1000), 
+                    verbose = F)),
     model_lnRR = map(data, ~ metafor::rma.uni(
                       yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
-      control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-    ))
-  )
+                      control = list(optimizer = "optim", 
+                                     optmethod = "Nelder-Mead", 
+                                     maxit = 1000), 
+                      verbose = F)))
 
@@
                       yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower) / (2 * 1.96),
-      control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-    )),
+                      control = list(optimizer = "optim", 
+                                     optmethod = "Nelder-Mead", 
+                                     maxit = 1000), 
+                      verbose = F)),
     model_lnVR = map(data, ~ metafor::rma.uni(
                     yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
-      control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-    )),
+                    control = list(optimizer = "optim", 
+                                   optmethod = "Nelder-Mead", 
+                                   maxit = 1000), 
+                    verbose = F)),
     model_lnRR = map(data, ~ metafor::rma.uni(
                     yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
-      control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-    ))
-  )
-```
-
-#### Re-structuring the data for each grouping term
-We here delete unused variables, and select the respective effect sizes.
+                    control = list(optimizer = "optim", 
+                                   optmethod = "Nelder-Mead", 
+                                   maxit = 1000), 
+                    verbose = F)))
+```
+
+### Re-structuring the data for each grouping term
+Here we delete unused variables, and select the respective effect sizes.
 Please note - the referencing of the cells does NOT depend on previous ordering of the data.
@@
         filter(., GroupingTerm == trait) %>% 
-        mutate(lnCVR = .[[4]][[1]]$b, lnCVR_lower = .[[4]][[1]]$ci.lb, lnCVR_upper = .[[4]][[1]]$ci.ub, lnCVR_se = .[[4]][[1]]$se, lnCVR_I2 = .[[4]][[1]]$I2,
-                lnVR = .[[5]][[1]]$b,  lnVR_lower = .[[5]][[1]]$ci.lb,  lnVR_upper = .[[5]][[1]]$ci.ub,  lnVR_se = .[[5]][[1]]$se,  lnVR_I2 = .[[5]][[1]]$I2,
-                lnRR = .[[6]][[1]]$b,  lnRR_lower = .[[6]][[1]]$ci.lb,  lnRR_upper = .[[6]][[1]]$ci.ub,  lnRR_se = .[[6]][[1]]$se,  lnRR_I2 = .[[6]][[1]]$I2)  %>%
+        mutate(      lnCVR = .[[4]][[1]]$b, 
+               lnCVR_lower = .[[4]][[1]]$ci.lb, 
+               lnCVR_upper = .[[4]][[1]]$ci.ub, 
+                  lnCVR_se = .[[4]][[1]]$se, 
+                  lnCVR_I2 = .[[4]][[1]]$I2,
+                      lnVR = .[[5]][[1]]$b,  
+                lnVR_lower = .[[5]][[1]]$ci.lb,  
+                lnVR_upper = .[[5]][[1]]$ci.ub,  
+                   lnVR_se = .[[5]][[1]]$se,  
+                   lnVR_I2 = .[[5]][[1]]$I2,
+                      lnRR = .[[6]][[1]]$b,  
+                lnRR_lower = .[[6]][[1]]$ci.lb,  
+                lnRR_upper = .[[6]][[1]]$ci.ub,  
+                   lnRR_se = .[[6]][[1]]$se,  
+                   lnRR_I2 = .[[6]][[1]]$I2)  %>%
         select(., GroupingTerm, lnCVR:lnRR_I2)
@@
 All <- overall_all1 %>% 
-       mutate(lnCVR = .[[2]][[1]]$b, lnCVR_lower = .[[2]][[1]]$ci.lb, lnCVR_upper = .[[2]][[1]]$ci.ub, lnCVR_se = .[[2]][[1]]$se, lnCVR_I2 = .[[2]][[1]]$I2,
-              lnVR = .[[3]][[1]]$b,  lnVR_lower = .[[3]][[1]]$ci.lb,  lnVR_upper = .[[3]][[1]]$ci.ub,  lnVR_se = .[[3]][[1]]$se,  lnVR_I2 = .[[3]][[1]]$I2,
-              lnRR = .[[4]][[1]]$b,  lnRR_lower = .[[4]][[1]]$ci.lb,  lnRR_upper = .[[4]][[1]]$ci.ub,  lnRR_se = .[[4]][[1]]$se,  lnRR_I2 = .[[4]][[1]]$I2,)  %>%
+       mutate(      lnCVR = .[[2]][[1]]$b, 
+              lnCVR_lower = .[[2]][[1]]$ci.lb, 
+              lnCVR_upper = .[[2]][[1]]$ci.ub, 
+                 lnCVR_se = .[[2]][[1]]$se, 
+                 lnCVR_I2 = .[[2]][[1]]$I2,
+                     lnVR = .[[3]][[1]]$b,  
+               lnVR_lower = .[[3]][[1]]$ci.lb,  
+               lnVR_upper = .[[3]][[1]]$ci.ub,  
+                  lnVR_se = .[[3]][[1]]$se,  
+                  lnVR_I2 = .[[3]][[1]]$I2,
+                     lnRR = .[[4]][[1]]$b,  
+               lnRR_lower = .[[4]][[1]]$ci.lb,  
+               lnRR_upper = .[[4]][[1]]$ci.ub,  
+                  lnRR_se = .[[4]][[1]]$se,  
+                  lnRR_I2 = .[[4]][[1]]$I2,)  %>%
        select(., lnCVR:lnRR_I2)
@@
 
-# Visualising meta-analysis results
+## Second-order meta-analysis of heterogenity
+
+The analysis for heterogeneity follows the workflow of the above steps for the different meta-analyses and specifically Figure \@ref(fig:FigG1) I & J.
+However, in the initial meta-analysis we extract sigma^2 and errors for mouse strains and centers (Institutions).
+As above a Loop is run and parameters extracted from metafor (sigma2's, s.nlevels)
+
+```{r hetero_loop, echo = TRUE, eval = TRUE, message=FALSE, warning=FALSE, cache = TRUE}
+
+### Preparing heterogeneity
+
+# Create dataframe to store results
+results.allhetero.grouping <- as.data.frame(cbind(c(1:n), matrix(rep(0, n * 30), ncol = 30)))
+names(results.allhetero.grouping) <- c(
+  "id", "sigma2_strain.CVR", "sigma2_center.CVR", "sigma2_error.CVR", "s.nlevels.strain.CVR",
+  "s.nlevels.center.CVR", "s.nlevels.error.CVR", "sigma2_strain.VR", "sigma2_center.VR", "sigma2_error.VR", "s.nlevels.strain.VR",
+  "s.nlevels.center.VR", "s.nlevels.error.VR", "sigma2_strain.RR", "sigma2_center.RR", "sigma2_error.RR", "s.nlevels.strain.RR",
+  "s.nlevels.center.RR", "s.nlevels.error.RR", "lnCVR", "lnCVR_lower", "lnCVR_upper", "lnCVR_se", "lnVR", "lnVR_lower", "lnVR_upper",
+  "lnVR_se", "lnRR", "lnRR_lower", "lnRR_upper", "lnRR_se"
+)
+
+#Loop
+
+for (t in 1:n) {
+  tryCatch(
+    {
+      results <- data %>% 
+                  data_subset_parameterid_individual_by_age(t) %>% 
+                  calculate_population_stats() %>% 
+                  create_meta_analysis_effect_sizes() %>%
+                  mutate(err = seq_len(n()))
+
+      # lnCVR, logaritm of the ratio of male and female coefficients of variance
+
+      cvr. <- metafor::rma.mv(yi = effect_size_CVR, 
+                              V = sample_variance_CVR, 
+                              random = list(~ 1 | strain_name, ~ 1 | production_center,~ 1 | err), 
+                              control = list(optimizer = "optim", 
+                                             optmethod = "Nelder-Mead", 
+                                             maxit = 1000), 
+                              data = results)
+
+      results.allhetero.grouping[t, 2] <- cvr.$sigma2[1]
+      results.allhetero.grouping[t, 3] <- cvr.$sigma2[2]
+      results.allhetero.grouping[t, 4] <- cvr.$sigma2[3]
+      results.allhetero.grouping[t, 5] <- cvr.$s.nlevels[1]
+      results.allhetero.grouping[t, 6] <- cvr.$s.nlevels[2]
+      results.allhetero.grouping[t, 7] <- cvr.$s.nlevels[3]
+      results.allhetero.grouping[t, 20] <- cvr.$b
+      results.allhetero.grouping[t, 21] <- cvr.$ci.lb
+      results.allhetero.grouping[t, 22] <- cvr.$ci.ub
+      results.allhetero.grouping[t, 23] <- cvr.$se
+
+      # lnVR, male to female variability ratio (logarithm of male and female standard deviations)
+
+      vr. <- metafor::rma.mv(yi = effect_size_VR, 
+                             V = sample_variance_VR, 
+                             random = list(~ 1 | strain_name, ~ 1 | production_center, ~ 1 | err), 
+                             control = list(optimizer = "optim", 
+                                            optmethod = "Nelder-Mead", 
+                                            maxit = 1000), 
+                             data = results)
+
+      results.allhetero.grouping[t, 8] <- vr.$sigma2[1]
+      results.allhetero.grouping[t, 9] <- vr.$sigma2[2]
+      results.allhetero.grouping[t, 10] <- vr.$sigma2[3]
+      results.allhetero.grouping[t, 11] <- vr.$s.nlevels[1]
+      results.allhetero.grouping[t, 12] <- vr.$s.nlevels[2]
+      results.allhetero.grouping[t, 13] <- vr.$s.nlevels[3]
+      results.allhetero.grouping[t, 24] <- vr.$b
+      results.allhetero.grouping[t, 25] <- vr.$ci.lb
+      results.allhetero.grouping[t, 26] <- vr.$ci.ub
+      results.allhetero.grouping[t, 27] <- vr.$se
+
+      # lnRR, response ratio (logarithm of male and female means)
+
+      rr. <- metafor::rma.mv(yi = effect_size_ROM, 
+                             V = sample_variance_ROM, 
+                             random = list(~ 1 | strain_name, ~ 1 | production_center, ~ 1 | err), 
+                             control = list(optimizer = "optim", 
+                                            optmethod = "Nelder-Mead", 
+                                            maxit = 1000), 
+                             data = results)
+
+      results.allhetero.grouping[t, 14] <- rr.$sigma2[1]
+      results.allhetero.grouping[t, 15] <- rr.$sigma2[2]
+      results.allhetero.grouping[t, 16] <- rr.$sigma2[3]
+      results.allhetero.grouping[t, 17] <- rr.$s.nlevels[1]
+      results.allhetero.grouping[t, 18] <- rr.$s.nlevels[2]
+      results.allhetero.grouping[t, 19] <- rr.$s.nlevels[3]
+      results.allhetero.grouping[t, 28] <- rr.$b
+      results.allhetero.grouping[t, 29] <- rr.$ci.lb
+      results.allhetero.grouping[t, 30] <- rr.$ci.ub
+      results.allhetero.grouping[t, 31] <- rr.$se
+    },
+    error = function(e) {
+      cat("ERROR :", conditionMessage(e), "\n")
+    }
+  )
+}
+```
+
+Here we exclude traits without variation between mouse strains and merge data sets containing metafor results with procedure etc.
+names.
+Dealing with the correlated parameters, and running the second -order meta-analysis for heterogeneity data (Figure \@ref(fig:FigG1) I)
+
+```{r hetero,eval=TRUE, echo = TRUE}
+
+              results.allhetero.grouping2 <- results.allhetero.grouping[results.allhetero.grouping$s.nlevels.strain.VR != 0, ]
+# nrow(results.allhetero.grouping) #232
+
+# Merging dataset with correct procedure names
+# procedures <- read.csv(here("export", "procedures.csv"))
+
+results.allhetero.grouping2$parameter_group <- data$parameter_group[match(results.allhetero.grouping2$id, data$id)]
+      results.allhetero.grouping2$procedure <- data$procedure_name[match(results.allhetero.grouping2$id, data$id)]
+
+   results.allhetero.grouping2$GroupingTerm <- procedures$GroupingTerm[match(results.allhetero.grouping2$procedure, procedures$procedure)]
+ results.allhetero.grouping2$parameter_name <- data$parameter_name[match(results.allhetero.grouping2$id, data$id)]
+
+#We deal with correlated parameters following the procedures described above (extraction of effects sizes).
+
+metahetero1 <- results.allhetero.grouping2
+# length(unique(metahetero1$procedure)) #19
+# length(unique(metahetero1$GroupingTerm)) #9 
+# length(unique(metahetero1$parameter_group)) #152
+# length(unique(metahetero1$parameter_name)) #223
+
+# Count of number of parameter names (correlated sub-traits) in each parameter group (par_group_size)
+
+metahetero1b <- metahetero1                    %>%
+                group_by(parameter_group)      %>%
+                mutate(par_group_size = n_distinct(parameter_name))
+
+metahetero1$par_group_size <- metahetero1b$par_group_size[match(metahetero1$parameter_group, metahetero1b$parameter_group)]
+
+# Create subsets with > 1 count (par_group_size > 1)
+
+metahetero1_sub <- subset(metahetero1, par_group_size > 1) # 92 observations
+
+# Nest data
+
+n_count. <- metahetero1_sub %>%
+  group_by(parameter_group) %>%
+  nest()
+
+# meta-analysis preparation
+
+model_count. <- n_count. %>%
+  mutate(
+    model_lnRR = map(data, ~ robu(.x$lnRR ~ 1,
+      data = .x, studynum = .x$id, modelweights = c("CORR"), rho = 0.8,
+      small = TRUE, var.eff.size = (.x$lnRR_se)^2
+    )),
+    model_lnVR = map(data, ~ robu(.x$lnVR ~ 1,
+      data = .x, studynum = .x$id, modelweights = c("CORR"), rho = 0.8,
+      small = TRUE, var.eff.size = (.x$lnVR_se)^2
+    )),
+    model_lnCVR = map(data, ~ robu(.x$lnCVR ~ 1,
+      data = .x, studynum = .x$id, modelweights = c("CORR"), rho = 0.8,
+      small = TRUE, var.eff.size = (.x$lnCVR_se)^2
+    ))
+  )
+
+# Robumeta object details:  str(model_count.$model_lnCVR[[1]])
+
+# Perform meta-analyses on correlated sub-traits, using robumeta
+# Extract and save parameter estimates
+
+count_fun. <- function(mod_sub) {
+  return(c(as.numeric(mod_sub$mod_info$term1), mod_sub$N))
+}
+
+robusub_RR. <- model_count. %>%
+  transmute(estimatelnRR = map(model_lnRR, count_fun.)) %>%    
+  mutate(r = map(estimatelnRR, ~ data.frame(t(.)))) %>%
+  unnest(r) %>%
+  select(-estimatelnRR) %>%
+  purrr::set_names(c("parameter_group", "var.RR", "N.RR"))
+
+robusub_CVR. <- model_count. %>%
+  transmute(estimatelnCVR = map(model_lnCVR, count_fun.)) %>%
+  mutate(r = map(estimatelnCVR, ~ data.frame(t(.)))) %>%
+  unnest(r) %>%
+  select(-estimatelnCVR) %>%
+  purrr::set_names(c("parameter_group", "var.CVR", "N.CVR"))
+
+robusub_VR. <- model_count. %>%
+  transmute(estimatelnVR = map(model_lnVR, count_fun.)) %>%
+  mutate(r = map(estimatelnVR, ~ data.frame(t(.)))) %>%
+  unnest(r) %>%
+  select(-estimatelnVR) %>%
+  purrr::set_names(c("parameter_group", "var.VR", "N.VR"))
+
+robu_all. <- full_join(robusub_CVR., robusub_VR.) %>% full_join(., robusub_RR.)
+
+#Merge the two data sets (the new [robu_all.] and the initial [uncorrelated sub-traits with count = 1])
+
+#In this step, we 	1) merge the N from robumeta and the  N from metafor (s.nlevels.error) together into the same columns (N.RR, N.VR, N.CVR)
+
+# 2) calculate the total variance for metafor models as the sum of random effect variances and the residual error, then add in the same columns together with the residual variances from robumeta
+
+metahetero_all <- metahetero1 %>%
+  filter(par_group_size == 1) %>%
+  as_tibble()
+metahetero_all$N.RR <- metahetero_all$s.nlevels.error.RR
+metahetero_all$N.CVR <- metahetero_all$s.nlevels.error.CVR
+metahetero_all$N.VR <- metahetero_all$s.nlevels.error.VR
+metahetero_all$var.RR <- log(sqrt(metahetero_all$sigma2_strain.RR + metahetero_all$sigma2_center.RR + metahetero_all$sigma2_error.RR))
+metahetero_all$var.VR <- log(sqrt(metahetero_all$sigma2_strain.VR + metahetero_all$sigma2_center.VR + metahetero_all$sigma2_error.VR))
+metahetero_all$var.CVR <- log(sqrt(metahetero_all$sigma2_strain.CVR + metahetero_all$sigma2_center.CVR + metahetero_all$sigma2_error.CVR))
+# str(metahetero_all)
+# str(robu_all.)
+
+metahetero_all <- metahetero_all %>% mutate(
+  var.RR = if_else(var.RR == -Inf, -7, var.RR),   # numbers chosen as limits; based on the values in the dataset
+  var.VR = if_else(var.VR == -Inf, -5, var.VR),
+  var.CVR = if_else(var.CVR == -Inf, -6, var.CVR)
+)
+
+# Combine data
+# Step1
+
+combinedmetahetero <- bind_rows(robu_all., metahetero_all)
+# glimpse(combinedmetahetero)
+
+# Steps 2&3
+
+              metacombohetero <- combinedmetahetero
+       metacombohetero$counts <- metahetero1$par_group_size[match(metacombohetero$parameter_group, metahetero1$parameter_group)]
+   metacombohetero$procedure2 <- metahetero1$procedure[match(metacombohetero$parameter_group, metahetero1$parameter_group)]
+metacombohetero$GroupingTerm2 <- metahetero1$GroupingTerm[match(metacombohetero$parameter_group, metahetero1$parameter_group)]
+
+# **Clean-up and rename
+
+metacombohetero <- metacombohetero %>% select(parameter_group, var.CVR, N.CVR, var.VR, N.VR, var.RR, N.RR, counts, procedure = procedure2, GroupingTerm = GroupingTerm2)
+
+# Invidual table for heterogeneity across all traits
+# kable(metacombohetero,, digits = 3) %>%
+ # kable_styling() %>%
+  #scroll_box(width = "100%", height = "200px")
+
+#### Meta-analysis of heterogeneity
+
+## Perform meta-meta-analysis (3 for each of the 9 grouping terms: var.CVR, var.VR, var.RR)
+
+metacombohetero_final <- metacombohetero %>%
+  group_by(GroupingTerm) %>%
+  nest()
+
+# Final fixed effects meta-analyses within grouping terms, with SE of the estimate
+
+heterog1 <- metacombohetero_final %>%
+
+  mutate(
+    model_heteroCVR = map(data, ~ metafor::rma.uni(
+      yi = .x$var.CVR, sei = sqrt(1 / 2 * (.x$N.CVR - 1)),
+      control = list(optimizer = "optim", 
+                     optmethod = "Nelder-Mead",
+                     maxit = 10000, 
+                     stepadj = 0.5), verbose = F)),
+    model_heteroVR = map(data, ~ metafor::rma.uni(
+      yi = .x$var.VR, sei = sqrt(1 / 2 * (.x$N.VR - 1)),
+      control = list(optimizer = "optim", 
+                     optmethod = "Nelder-Mead", 
+                     maxit = 10000, 
+                     stepadj = 0.5), verbose = F)),
+    model_heteroRR = map(data, ~ metafor::rma.uni(
+      yi = .x$var.RR, sei = sqrt(1 / 2 * (.x$N.RR - 1)),
+      control = list(optimizer = "optim", 
+                     optmethod = "Nelder-Mead", 
+                     maxit = 10000, 
+                     stepadj = 0.5), verbose = F)) )
+
+# Across all grouping terms
+
+metacombohetero_all_final <- metacombohetero %>%
+  nest(data = everything())
+
+# Final fixed effects meta-analyses ACROSS grouping terms, with SE of the estimate
+
+heterog1_all <- metacombohetero_all_final %>%
+
+  mutate( model_heteroCVR = map(data, ~ metafor::rma.uni(
+      yi = .x$var.CVR, sei = sqrt(1 / 2 * (.x$N.CVR - 1)),
+      control = list(optimizer = "optim", 
+                     optmethod = "Nelder-Mead", 
+                     maxit = 10000, 
+                     stepadj = 0.5), verbose = F)),
+    model_heteroVR = map(data, ~ metafor::rma.uni(yi = .x$var.VR, sei = sqrt(1 / 2 * (.x$N.VR - 1)),
+      control = list(optimizer = "optim", 
+                     optmethod = "Nelder-Mead", 
+                     maxit = 10000, 
+                     stepadj = 0.5), verbose = F)),
+    model_heteroRR = map(data, ~ metafor::rma.uni(yi = .x$var.RR, sei = sqrt(1 / 2 * (.x$N.RR - 1)),
+      control = list(optimizer = "optim", 
+                     optmethod = "Nelder-Mead", 
+                     maxit = 10000, 
+                     stepadj = 0.5), verbose = F)))
+
+# Re-structure data for each grouping term; extract heterogenenity/variance terms; delete un-used variables
+
+extract_heterogeneity <- function(data, type){
+
+  tmp <- data %>%
+         filter(., GroupingTerm == type) %>%
+         select(., -data) %>%
+         mutate(heteroCVR       = .[[2]][[1]]$b, 
+                heteroCVR_lower = .[[2]][[1]]$ci.lb, 
+                heteroCVR_upper = .[[2]][[1]]$ci.ub, 
+                heteroCVR_se    = .[[2]][[1]]$se,
+                heteroVR        = .[[3]][[1]]$b, 
+                heteroVR_lower  = .[[3]][[1]]$ci.lb, 
+                heteroVR_upper  = .[[3]][[1]]$ci.ub, 
+                heteroVR_se     = .[[3]][[1]]$se,
+                heteroRR        = .[[4]][[1]]$b, 
+                heteroRR_lower  = .[[4]][[1]]$ci.lb, 
+                heteroRR_upper  = .[[4]][[1]]$ci.ub, 
+                heteroRR_se     = .[[4]][[1]]$se) %>%
+        select(., GroupingTerm, heteroCVR:heteroRR_se)
+
+  return(tmp)
+}
+
+   Behaviour. <- extract_heterogeneity(heterog1, type = "Behaviour")
+  Immunology. <- extract_heterogeneity(heterog1, type = "Immunology")
+  Hematology. <- extract_heterogeneity(heterog1, type = "Hematology")
+     Hearing. <- extract_heterogeneity(heterog1, type = "Hearing")
+  Physiology. <- extract_heterogeneity(heterog1, type = "Physiology")
+  Metabolism. <- extract_heterogeneity(heterog1, type = "Metabolism")
+  Morphology. <- extract_heterogeneity(heterog1, type = "Morphology")
+       Heart. <- extract_heterogeneity(heterog1, type = "Heart")
+         Eye. <- extract_heterogeneity(heterog1, type = "Eye")
+
+#Reorder to be able to keep cell referencing 
+heterog1_all <- heterog1_all %>% 
+                mutate(GroupingTerm = "All") %>% 
+                select(GroupingTerm, everything())
+
+All. <- heterog1_all %>% 
+        select(., -data) %>%
+        mutate(heteroCVR       = .[[2]][[1]]$b, 
+               heteroCVR_lower = .[[2]][[1]]$ci.lb, 
+               heteroCVR_upper = .[[2]][[1]]$ci.ub, 
+               heteroCVR_se    = .[[2]][[1]]$se, 
+               heteroVR        = .[[3]][[1]]$b, 
+               heteroVR_lower  = .[[3]][[1]]$ci.lb, 
+               heteroVR_upper  = .[[3]][[1]]$ci.ub, 
+               heteroVR_se     = .[[3]][[1]]$se, 
+               heteroRR        = .[[4]][[1]]$b, 
+               heteroRR_lower  = .[[4]][[1]]$ci.lb, 
+               heteroRR_upper  = .[[4]][[1]]$ci.ub, 
+               heteroRR_se     = .[[4]][[1]]$se) %>%
+        select(., GroupingTerm, heteroCVR:heteroRR_se)
+
+heterog2 <- bind_rows(Behaviour., Morphology., Metabolism., Physiology., Immunology., Hematology., Heart., Hearing., Eye., All.)
+
+#### Preparation of the Heterogeneity PLOT
+
+#Restructure data for plotting
+
+heterog3 <- gather(heterog2, parameter, value, c(heteroCVR, heteroVR, heteroRR), factor_key = TRUE)
+
+heteroCVR.ci <- heterog3 %>%
+                filter(parameter == "heteroCVR") %>%
+                mutate(ci.low = heteroCVR_lower, 
+                       ci.high = heteroCVR_upper)
+heteroVR.ci <-  heterog3 %>%
+                filter(parameter == "heteroVR") %>%
+                mutate(ci.low = heteroVR_lower, 
+                       ci.high = heteroVR_upper)
+heteroRR.ci <-  heterog3 %>%
+                filter(parameter == "heteroRR") %>%
+                mutate(ci.low = heteroRR_lower, 
+                       ci.high = heteroRR_upper)
+
+heterog4 <- bind_rows(heteroCVR.ci, heteroVR.ci, heteroRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
+
+# **Re-order grouping terms
+
+heterog4$GroupingTerm <- factor(heterog4$GroupingTerm, 
+                                levels = c("Behaviour", "Morphology", "Metabolism", 
+                                           "Physiology", "Immunology", "Hematology", "Heart", 
+                                           "Hearing", "Eye", "All"))
+
+heterog4$GroupingTerm <- factor(heterog4$GroupingTerm, 
+                                rev(levels(heterog4$GroupingTerm)))
+heterog4$label <- "All traits"
+# write.csv(heterog4, "heterog4.csv")
+
+#### Plot S1 C (Second-order meta analysis on heterogeneity)
+
+heterog5 <- heterog4
+heterog5$mean <- as.numeric(exp(heterog5$value))
+heterog5$ci.l <- as.numeric(exp(heterog5$ci.low))
+heterog5$ci.h <- as.numeric(exp(heterog5$ci.high))
+
+heterog6 <- heterog5
+
+HeteroS1 <-
+  heterog6 %>%
+  ggplot(aes(y = GroupingTerm, x = mean)) +
+  geom_errorbarh(aes(
+    xmin = ci.l,
+    xmax = ci.h
+  ),
+  height = 0.1, show.legend = FALSE
+  ) +
+  geom_point(aes(shape = parameter),
+    fill = "black",
+    color = "black", size = 2.2,
+    show.legend = FALSE
+  ) +
+  scale_x_continuous(
+    limits = c(-0.1, 1.4),
+    # breaks = c(0, 0.1, 0.2),
+    name = "sigma^2"
+  ) +
+  # geom_vline(xintercept=0,
+  # color='black',
+  # linetype='dashed')+
+  facet_grid(
+    cols = vars(parameter), rows = vars(label),
+    labeller = label_wrap_gen(width = 23),
+    scales = "free",
+    space = "free"
+  ) +
+  theme_bw() +
+  theme(
+    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
+    strip.text.x = element_text(size = 12),
+    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
+    text = element_text(size = 14),
+    panel.spacing = unit(0.5, "lines"),
+    panel.border = element_blank(),
+    axis.line = element_line(),
+    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
+    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
+    panel.grid.minor.y = element_blank(),
+    panel.grid.minor.x = element_blank(),
+    legend.title = element_blank(),
+    axis.title.x = element_text(hjust = 0.5, size = 14),
+    axis.title.y = element_blank())
+```
+
+# Meta-analysis results
 ## Preparation for Figure 4 
@@
 
-```{r hetero_loop, echo = FALSE, eval = TRUE, message=FALSE, warning=FALSE, include=FALSE, cache = TRUE}
-
-### Preparing heterogeneity
-
-#The analysis for heterogeneity follows the workflow of the above steps for the different meta-analyses.
-However, in the initial meta-analysis we extract sigma^2 and errors for mouse strains and centers (Institutions).
-#As above a Loop is run and parameters extracted from metafor (sigma2's, s.nlevels)
-
-# Create dataframe to store results
-results.allhetero.grouping <- as.data.frame(cbind(c(1:n), matrix(rep(0, n * 30), ncol = 30)))
-names(results.allhetero.grouping) <- c(
-  "id", "sigma2_strain.CVR", "sigma2_center.CVR", "sigma2_error.CVR", "s.nlevels.strain.CVR",
-  "s.nlevels.center.CVR", "s.nlevels.error.CVR", "sigma2_strain.VR", "sigma2_center.VR", "sigma2_error.VR", "s.nlevels.strain.VR",
-  "s.nlevels.center.VR", "s.nlevels.error.VR", "sigma2_strain.RR", "sigma2_center.RR", "sigma2_error.RR", "s.nlevels.strain.RR",
-  "s.nlevels.center.RR", "s.nlevels.error.RR", "lnCVR", "lnCVR_lower", "lnCVR_upper", "lnCVR_se", "lnVR", "lnVR_lower", "lnVR_upper",
-  "lnVR_se", "lnRR", "lnRR_lower", "lnRR_upper", "lnRR_se"
-)
-
-#Loop
-
-for (t in 1:n) {
-  tryCatch(
-    {
-      results <- data %>% 
-                  data_subset_parameterid_individual_by_age(t) %>% 
-                  calculate_population_stats() %>% 
-                  create_meta_analysis_effect_sizes() %>%
-                  mutate(err = seq_len(n()))
-
-      # lnCVR, logaritm of the ratio of male and female coefficients of variance
-
-      cvr. <- metafor::rma.mv(yi = effect_size_CVR, 
-                              V = sample_variance_CVR, 
-                              random = list(~ 1 | strain_name, ~ 1 | production_center,~ 1 | err), 
-                              control = list(optimizer = "optim", 
-                                             optmethod = "Nelder-Mead", 
-                                             maxit = 1000), 
-                              data = results)
-
-      results.allhetero.grouping[t, 2] <- cvr.$sigma2[1]
-      results.allhetero.grouping[t, 3] <- cvr.$sigma2[2]
-      results.allhetero.grouping[t, 4] <- cvr.$sigma2[3]
-      results.allhetero.grouping[t, 5] <- cvr.$s.nlevels[1]
-      results.allhetero.grouping[t, 6] <- cvr.$s.nlevels[2]
-      results.allhetero.grouping[t, 7] <- cvr.$s.nlevels[3]
-      results.allhetero.grouping[t, 20] <- cvr.$b
-      results.allhetero.grouping[t, 21] <- cvr.$ci.lb
-      results.allhetero.grouping[t, 22] <- cvr.$ci.ub
-      results.allhetero.grouping[t, 23] <- cvr.$se
-
-      # lnVR, male to female variability ratio (logarithm of male and female standard deviations)
-
-      vr. <- metafor::rma.mv(yi = effect_size_VR, 
-                             V = sample_variance_VR, 
-                             random = list(~ 1 | strain_name, ~ 1 | production_center, ~ 1 | err), 
-                             control = list(optimizer = "optim", 
-                                            optmethod = "Nelder-Mead", 
-                                            maxit = 1000), 
-                             data = results)
-
-      results.allhetero.grouping[t, 8] <- vr.$sigma2[1]
-      results.allhetero.grouping[t, 9] <- vr.$sigma2[2]
-      results.allhetero.grouping[t, 10] <- vr.$sigma2[3]
-      results.allhetero.grouping[t, 11] <- vr.$s.nlevels[1]
-      results.allhetero.grouping[t, 12] <- vr.$s.nlevels[2]
-      results.allhetero.grouping[t, 13] <- vr.$s.nlevels[3]
-      results.allhetero.grouping[t, 24] <- vr.$b
-      results.allhetero.grouping[t, 25] <- vr.$ci.lb
-      results.allhetero.grouping[t, 26] <- vr.$ci.ub
-      results.allhetero.grouping[t, 27] <- vr.$se
-
-      # lnRR, response ratio (logarithm of male and female means)
-
-      rr. <- metafor::rma.mv(yi = effect_size_ROM, 
-                             V = sample_variance_ROM, 
-                             random = list(~ 1 | strain_name, ~ 1 | production_center, ~ 1 | err), 
-                             control = list(optimizer = "optim", 
-                                            optmethod = "Nelder-Mead", 
-                                            maxit = 1000), 
-                             data = results)
-
-      results.allhetero.grouping[t, 14] <- rr.$sigma2[1]
-      results.allhetero.grouping[t, 15] <- rr.$sigma2[2]
-      results.allhetero.grouping[t, 16] <- rr.$sigma2[3]
-      results.allhetero.grouping[t, 17] <- rr.$s.nlevels[1]
-      results.allhetero.grouping[t, 18] <- rr.$s.nlevels[2]
-      results.allhetero.grouping[t, 19] <- rr.$s.nlevels[3]
-      results.allhetero.grouping[t, 28] <- rr.$b
-      results.allhetero.grouping[t, 29] <- rr.$ci.lb
-      results.allhetero.grouping[t, 30] <- rr.$ci.ub
-      results.allhetero.grouping[t, 31] <- rr.$se
-    },
-    error = function(e) {
-      cat("ERROR :", conditionMessage(e), "\n")
-    }
-  )
-}
-```
-
-```{r hetero,eval=TRUE, echo = FALSE}
-#Exclude traits without variation between mouse strains
-#Merge data sets containing metafor results with procedure etc. names. Dealing with correlated parameters, and running of second -order meta-analysis for  heterogeneity data.
-
-              results.allhetero.grouping2 <- results.allhetero.grouping[results.allhetero.grouping$s.nlevels.strain.VR != 0, ]
-# nrow(results.allhetero.grouping) #232
-
-# Merging dataset with correct procedure names
-# procedures <- read.csv(here("export", "procedures.csv"))
-
-results.allhetero.grouping2$parameter_group <- data$parameter_group[match(results.allhetero.grouping2$id, data$id)]
-      results.allhetero.grouping2$procedure <- data$procedure_name[match(results.allhetero.grouping2$id, data$id)]
-
-   results.allhetero.grouping2$GroupingTerm <- procedures$GroupingTerm[match(results.allhetero.grouping2$procedure, procedures$procedure)]
- results.allhetero.grouping2$parameter_name <- data$parameter_name[match(results.allhetero.grouping2$id, data$id)]
-
-#We deal with correlated parameters following the procedures described above (extraction of effects sizes).
-
-metahetero1 <- results.allhetero.grouping2
-# length(unique(metahetero1$procedure)) #19
-# length(unique(metahetero1$GroupingTerm)) #9 
-# length(unique(metahetero1$parameter_group)) #152
-# length(unique(metahetero1$parameter_name)) #223
-
-# Count of number of parameter names (correlated sub-traits) in each parameter group (par_group_size)
-
-metahetero1b <- metahetero1                    %>%
-                group_by(parameter_group)      %>%
-                mutate(par_group_size = n_distinct(parameter_name))
-
-metahetero1$par_group_size <- metahetero1b$par_group_size[match(metahetero1$parameter_group, metahetero1b$parameter_group)]
-
-# Create subsets with > 1 count (par_group_size > 1)
-
-metahetero1_sub <- subset(metahetero1, par_group_size > 1) # 92 observations
-
-# Nest data
-
-n_count. <- metahetero1_sub %>%
-  group_by(parameter_group) %>%
-  nest()
-
-# meta-analysis preparation
-
-model_count. <- n_count. %>%
-  mutate(
-    model_lnRR = map(data, ~ robu(.x$lnRR ~ 1,
-      data = .x, studynum = .x$id, modelweights = c("CORR"), rho = 0.8,
-      small = TRUE, var.eff.size = (.x$lnRR_se)^2
-    )),
-    model_lnVR = map(data, ~ robu(.x$lnVR ~ 1,
-      data = .x, studynum = .x$id, modelweights = c("CORR"), rho = 0.8,
-      small = TRUE, var.eff.size = (.x$lnVR_se)^2
-    )),
-    model_lnCVR = map(data, ~ robu(.x$lnCVR ~ 1,
-      data = .x, studynum = .x$id, modelweights = c("CORR"), rho = 0.8,
-      small = TRUE, var.eff.size = (.x$lnCVR_se)^2
-    ))
-  )
-
-# Robumeta object details:  str(model_count.$model_lnCVR[[1]])
-
-# Perform meta-analyses on correlated sub-traits, using robumeta
-# Extract and save parameter estimates
-
-count_fun. <- function(mod_sub) {
-  return(c(as.numeric(mod_sub$mod_info$term1), mod_sub$N))
-}
-
-robusub_RR. <- model_count. %>%
-  transmute(estimatelnRR = map(model_lnRR, count_fun.)) %>%    
-  mutate(r = map(estimatelnRR, ~ data.frame(t(.)))) %>%
-  unnest(r) %>%
-  select(-estimatelnRR) %>%
-  purrr::set_names(c("parameter_group", "var.RR", "N.RR"))
-
-robusub_CVR. <- model_count. %>%
-  transmute(estimatelnCVR = map(model_lnCVR, count_fun.)) %>%
-  mutate(r = map(estimatelnCVR, ~ data.frame(t(.)))) %>%
-  unnest(r) %>%
-  select(-estimatelnCVR) %>%
-  purrr::set_names(c("parameter_group", "var.CVR", "N.CVR"))
-
-robusub_VR. <- model_count. %>%
-  transmute(estimatelnVR = map(model_lnVR, count_fun.)) %>%
-  mutate(r = map(estimatelnVR, ~ data.frame(t(.)))) %>%
-  unnest(r) %>%
-  select(-estimatelnVR) %>%
-  purrr::set_names(c("parameter_group", "var.VR", "N.VR"))
-
-robu_all. <- full_join(robusub_CVR., robusub_VR.) %>% full_join(., robusub_RR.)
-
-#Merge the two data sets (the new [robu_all.] and the initial [uncorrelated sub-traits with count = 1])
-
-#In this step, we 	1) merge the N from robumeta and the  N from metafor (s.nlevels.error) together into the same columns (N.RR, N.VR, N.CVR)
-
-# 2) calculate the total variance for metafor models as the sum of random effect variances and the residual error, then add in the same columns together with the residual variances from robumeta
-
-metahetero_all <- metahetero1 %>%
-  filter(par_group_size == 1) %>%
-  as_tibble()
-metahetero_all$N.RR <- metahetero_all$s.nlevels.error.RR
-metahetero_all$N.CVR <- metahetero_all$s.nlevels.error.CVR
-metahetero_all$N.VR <- metahetero_all$s.nlevels.error.VR
-metahetero_all$var.RR <- log(sqrt(metahetero_all$sigma2_strain.RR + metahetero_all$sigma2_center.RR + metahetero_all$sigma2_error.RR))
-metahetero_all$var.VR <- log(sqrt(metahetero_all$sigma2_strain.VR + metahetero_all$sigma2_center.VR + metahetero_all$sigma2_error.VR))
-metahetero_all$var.CVR <- log(sqrt(metahetero_all$sigma2_strain.CVR + metahetero_all$sigma2_center.CVR + metahetero_all$sigma2_error.CVR))
-# str(metahetero_all)
-# str(robu_all.)
-
-metahetero_all <- metahetero_all %>% mutate(
-  var.RR = if_else(var.RR == -Inf, -7, var.RR),   # numbers chosen as limits; based on the values in the dataset
-  var.VR = if_else(var.VR == -Inf, -5, var.VR),
-  var.CVR = if_else(var.CVR == -Inf, -6, var.CVR)
-)
-
-# Combine data
-# Step1
-
-combinedmetahetero <- bind_rows(robu_all., metahetero_all)
-# glimpse(combinedmetahetero)
-
-# Steps 2&3
-
-              metacombohetero <- combinedmetahetero
-       metacombohetero$counts <- metahetero1$par_group_size[match(metacombohetero$parameter_group, metahetero1$parameter_group)]
-   metacombohetero$procedure2 <- metahetero1$procedure[match(metacombohetero$parameter_group, metahetero1$parameter_group)]
-metacombohetero$GroupingTerm2 <- metahetero1$GroupingTerm[match(metacombohetero$parameter_group, metahetero1$parameter_group)]
-
-# **Clean-up and rename
-
-metacombohetero <- metacombohetero %>% select(parameter_group, var.CVR, N.CVR, var.VR, N.VR, var.RR, N.RR, counts, procedure = procedure2, GroupingTerm = GroupingTerm2)
-
-# Invidual table for heterogeneity across all traits
-# kable(metacombohetero,, digits = 3) %>%
- # kable_styling() %>%
-  #scroll_box(width = "100%", height = "200px")
-
-#### Meta-analysis of heterogeneity
-
-## Perform meta-meta-analysis (3 for each of the 9 grouping terms: var.CVR, var.VR, var.RR)
-
-metacombohetero_final <- metacombohetero %>%
-  group_by(GroupingTerm) %>%
-  nest()
-
-# Final fixed effects meta-analyses within grouping terms, with SE of the estimate
-
-heterog1 <- metacombohetero_final %>%
-
-  mutate(
-    model_heteroCVR = map(data, ~ metafor::rma.uni(
-      yi = .x$var.CVR, sei = sqrt(1 / 2 * (.x$N.CVR - 1)),
-      control = list(optimizer = "optim", 
-                     optmethod = "Nelder-Mead",
-                     maxit = 10000, 
-                     stepadj = 0.5), verbose = F)),
-    model_heteroVR = map(data, ~ metafor::rma.uni(
-      yi = .x$var.VR, sei = sqrt(1 / 2 * (.x$N.VR - 1)),
-      control = list(optimizer = "optim", 
-                     optmethod = "Nelder-Mead", 
-                     maxit = 10000, 
-                     stepadj = 0.5), verbose = F)),
-    model_heteroRR = map(data, ~ metafor::rma.uni(
-      yi = .x$var.RR, sei = sqrt(1 / 2 * (.x$N.RR - 1)),
-      control = list(optimizer = "optim", 
-                     optmethod = "Nelder-Mead", 
-                     maxit = 10000, 
-                     stepadj = 0.5), verbose = F)) )
-
-# Across all grouping terms
-
-metacombohetero_all_final <- metacombohetero %>%
-  nest(data = everything())
-
-# Final fixed effects meta-analyses ACROSS grouping terms, with SE of the estimate
-
-heterog1_all <- metacombohetero_all_final %>%
-
-  mutate( model_heteroCVR = map(data, ~ metafor::rma.uni(
-      yi = .x$var.CVR, sei = sqrt(1 / 2 * (.x$N.CVR - 1)),
-      control = list(optimizer = "optim", 
-                     optmethod = "Nelder-Mead", 
-                     maxit = 10000, 
-                     stepadj = 0.5), verbose = F)),
-    model_heteroVR = map(data, ~ metafor::rma.uni(yi = .x$var.VR, sei = sqrt(1 / 2 * (.x$N.VR - 1)),
-      control = list(optimizer = "optim", 
-                     optmethod = "Nelder-Mead", 
-                     maxit = 10000, 
-                     stepadj = 0.5), verbose = F)),
-    model_heteroRR = map(data, ~ metafor::rma.uni(yi = .x$var.RR, sei = sqrt(1 / 2 * (.x$N.RR - 1)),
-      control = list(optimizer = "optim", 
-                     optmethod = "Nelder-Mead", 
-                     maxit = 10000, 
-                     stepadj = 0.5), verbose = F)))
-
-# Re-structure data for each grouping term; extract heterogenenity/variance terms; delete un-used variables
-
-extract_heterogeneity <- function(data, type){
-
-  tmp <- data %>%
-         filter(., GroupingTerm == type) %>%
-         select(., -data) %>%
-         mutate(heteroCVR       = .[[2]][[1]]$b, 
-                heteroCVR_lower = .[[2]][[1]]$ci.lb, 
-                heteroCVR_upper = .[[2]][[1]]$ci.ub, 
-                heteroCVR_se    = .[[2]][[1]]$se,
-                heteroVR        = .[[3]][[1]]$b, 
-                heteroVR_lower  = .[[3]][[1]]$ci.lb, 
-                heteroVR_upper  = .[[3]][[1]]$ci.ub, 
-                heteroVR_se     = .[[3]][[1]]$se,
-                heteroRR        = .[[4]][[1]]$b, 
-                heteroRR_lower  = .[[4]][[1]]$ci.lb, 
-                heteroRR_upper  = .[[4]][[1]]$ci.ub, 
-                heteroRR_se     = .[[4]][[1]]$se) %>%
-        select(., GroupingTerm, heteroCVR:heteroRR_se)
-
-  return(tmp)
-}
-
-   Behaviour. <- extract_heterogeneity(heterog1, type = "Behaviour")
-  Immunology. <- extract_heterogeneity(heterog1, type = "Immunology")
-  Hematology. <- extract_heterogeneity(heterog1, type = "Hematology")
-     Hearing. <- extract_heterogeneity(heterog1, type = "Hearing")
-  Physiology. <- extract_heterogeneity(heterog1, type = "Physiology")
-  Metabolism. <- extract_heterogeneity(heterog1, type = "Metabolism")
-  Morphology. <- extract_heterogeneity(heterog1, type = "Morphology")
-       Heart. <- extract_heterogeneity(heterog1, type = "Heart")
-         Eye. <- extract_heterogeneity(heterog1, type = "Eye")
-
-#Reorder to be able to keep cell referencing 
-heterog1_all <- heterog1_all %>% 
-                mutate(GroupingTerm = "All") %>% 
-                select(GroupingTerm, everything())
-
-All. <- heterog1_all %>% 
-        select(., -data) %>%
-        mutate(heteroCVR       = .[[2]][[1]]$b, 
-               heteroCVR_lower = .[[2]][[1]]$ci.lb, 
-               heteroCVR_upper = .[[2]][[1]]$ci.ub, 
-               heteroCVR_se    = .[[2]][[1]]$se, 
-               heteroVR        = .[[3]][[1]]$b, 
-               heteroVR_lower  = .[[3]][[1]]$ci.lb, 
-               heteroVR_upper  = .[[3]][[1]]$ci.ub, 
-               heteroVR_se     = .[[3]][[1]]$se, 
-               heteroRR        = .[[4]][[1]]$b, 
-               heteroRR_lower  = .[[4]][[1]]$ci.lb, 
-               heteroRR_upper  = .[[4]][[1]]$ci.ub, 
-               heteroRR_se     = .[[4]][[1]]$se) %>%
-        select(., GroupingTerm, heteroCVR:heteroRR_se)
-
-heterog2 <- bind_rows(Behaviour., Morphology., Metabolism., Physiology., Immunology., Hematology., Heart., Hearing., Eye., All.)
-
-#### Preparation of the Heterogeneity PLOT
-
-#Restructure data for plotting
-
-heterog3 <- gather(heterog2, parameter, value, c(heteroCVR, heteroVR, heteroRR), factor_key = TRUE)
-
-heteroCVR.ci <- heterog3 %>%
-                filter(parameter == "heteroCVR") %>%
-                mutate(ci.low = heteroCVR_lower, 
-                       ci.high = heteroCVR_upper)
-heteroVR.ci <-  heterog3 %>%
-                filter(parameter == "heteroVR") %>%
-                mutate(ci.low = heteroVR_lower, 
-                       ci.high = heteroVR_upper)
-heteroRR.ci <-  heterog3 %>%
-                filter(parameter == "heteroRR") %>%
-                mutate(ci.low = heteroRR_lower, 
-                       ci.high = heteroRR_upper)
-
-heterog4 <- bind_rows(heteroCVR.ci, heteroVR.ci, heteroRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
-
-# **Re-order grouping terms
-
-heterog4$GroupingTerm <- factor(heterog4$GroupingTerm, 
-                                levels = c("Behaviour", "Morphology", "Metabolism", 
-                                           "Physiology", "Immunology", "Hematology", "Heart", 
-                                           "Hearing", "Eye", "All"))
-
-heterog4$GroupingTerm <- factor(heterog4$GroupingTerm, 
-                                rev(levels(heterog4$GroupingTerm)))
-heterog4$label <- "All traits"
-# write.csv(heterog4, "heterog4.csv")
-
-#### Plot S1 C (Second-order meta analysis on heterogeneity)
-
-heterog5 <- heterog4
-heterog5$mean <- as.numeric(exp(heterog5$value))
-heterog5$ci.l <- as.numeric(exp(heterog5$ci.low))
-heterog5$ci.h <- as.numeric(exp(heterog5$ci.high))
-
-heterog6 <- heterog5
-
-HeteroS1 <-
-  heterog6 %>%
-  ggplot(aes(y = GroupingTerm, x = mean)) +
-  geom_errorbarh(aes(
-    xmin = ci.l,
-    xmax = ci.h
-  ),
-  height = 0.1, show.legend = FALSE
-  ) +
-  geom_point(aes(shape = parameter),
-    fill = "black",
-    color = "black", size = 2.2,
-    show.legend = FALSE
-  ) +
-  scale_x_continuous(
-    limits = c(-0.1, 1.4),
-    # breaks = c(0, 0.1, 0.2),
-    name = "sigma^2"
-  ) +
-  # geom_vline(xintercept=0,
-  # color='black',
-  # linetype='dashed')+
-  facet_grid(
-    cols = vars(parameter), rows = vars(label),
-    labeller = label_wrap_gen(width = 23),
-    scales = "free",
-    space = "free"
-  ) +
-  theme_bw() +
-  theme(
-    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
-    strip.text.x = element_text(size = 12),
-    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
-    text = element_text(size = 14),
-    panel.spacing = unit(0.5, "lines"),
-    panel.border = element_blank(),
-    axis.line = element_line(),
-    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
-    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
-    panel.grid.minor.y = element_blank(),
-    panel.grid.minor.x = element_blank(),
-    legend.title = element_blank(),
-    axis.title.x = element_text(hjust = 0.5, size = 14),
-    axis.title.y = element_blank())
-```
-
 ```{r, eval = TRUE, echo = FALSE}
 
-### Preparation for Figure S2
-#### Preparation for Figure S2 A
 #This Figure extends Figure 4, as it includes results not only for lnCVR and lnRR but also lnCVR.
@@
 Panel B shows effect sizes from separate meta-analysis for each functional group, and Panel C contains results of heterogeneity analyses.
-All three panels represent results evaluated across all traits (Phase 3, Figure 1.1)."}
+All three panels represent results evaluated across all traits."}
 
@@
   kable(overall2, digits = 3, caption = "Summary of overall meta-analyses on the functional trait group level (GroupingTerm).
-Results for lnCVR, lnVR and lnRR and their respective upper and lower 95% CI's, standard error and I2 values are provided.") %>%
+Results for lnCVR, lnVR and lnRR and their respective upper and lower 95 percent CI's, standard error and I2 values are provided.") %>%
    kable_styling() %>%

### 2020-05-18 scripts/MouseSexDiffApril20_2020.tex
Updates

\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provides euro and other symbols
\else % if luatex or xelatex
  \usepackage{unicode-math}
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\usepackage{hyperref}
\hypersetup{
            pdftitle={Sex and Power: Sexual dimorphism in trait variability and its eco-evolutionary and statistical implications},
            pdfauthor={Susanne Zajitschek, Felix Zajitschek, Russell Bonduriansky, Robert Brooks, Will Cornwell, Daniel Falster, Malgorzata Lagisz, Jeremy Mason, Alistair Senior, Daniel Noble, \& Shinichi Nakagawa},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage[margin=1in]{geometry}
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

\title{Sex and Power: Sexual dimorphism in trait variability and its
eco-evolutionary and statistical implications}
\providecommand{\subtitle}[1]{}
\subtitle{Electronic Supplementary Material}
\author{Susanne Zajitschek, Felix Zajitschek, Russell Bonduriansky, Robert
Brooks, Will Cornwell, Daniel Falster, Malgorzata Lagisz, Jeremy Mason,
Alistair Senior, Daniel Noble, \& Shinichi Nakagawa}
\date{2020-05-19}

\begin{document}
\maketitle

{
\setcounter{tocdepth}{4}
\tableofcontents
}
\hypertarget{general-introduction}{%
\section{General Introduction}\label{general-introduction}}

This supplementary material follows the general structure described in
our methods and is outlined here in Figure @ref(fig:FigG1). Generally
speaking, the first few sections describe the processes by which the
data were cleaned and re-organised for analysis. This iss followed by
how the first order and second order meta-analsyes were conducted.
Supplemental tables and figures that are referenecd within the main
manuscript can be found at the end of the document. Various parts of the
workflow can be conviently referenecd using the side table of contents
panel. We will refer back to this figure as we describe the various
aspects of the code and data processing in relevant places.

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{include_graphics}\NormalTok{(}\KeywordTok{here}\NormalTok{(}\StringTok{"images"}\NormalTok{, }\StringTok{"workflow.png"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\begin{figure}
\includegraphics[width=34.94in]{/Users/danielnoble/Dropbox/1_Research/1_Manuscripts/In_Preparation/mice_sex_diff/images/workflow} \caption{Workflow of data process and meta-analysis}\label{fig:FigG1}
\end{figure}

\hypertarget{set-up}{%
\section{Set-up}\label{set-up}}

\hypertarget{packages}{%
\subsection{Packages}\label{packages}}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{library}\NormalTok{(pacman)}
\NormalTok{pacman}\OperatorTok{::}\KeywordTok{p_load}\NormalTok{(readr, dplyr, metafor, devtools, purrr, tidyverse, tidyr, tibble, }
\NormalTok{    kableExtra, robumeta, ggpubr, ggplot2, png, grid, here, pander)}
\end{Highlighting}
\end{Shaded}

\hypertarget{functions}{%
\subsection{Functions}\label{functions}}

Functions needed for preparing the data for meta analyses

\hypertarget{loading-and-cleaning-data}{%
\subsubsection{Loading and cleaning
data}\label{loading-and-cleaning-data}}

These functions will load the raw and and do some cleaning to make it
ready for further processing and analysis.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# loads the raw data, setting some default types for various columns}

\NormalTok{load_raw <-}\StringTok{ }\ControlFlowTok{function}\NormalTok{(filename) \{}
    \KeywordTok{read_csv}\NormalTok{(filename, }\DataTypeTok{col_types =} \KeywordTok{cols}\NormalTok{(}\DataTypeTok{.default =} \KeywordTok{col_character}\NormalTok{(), }\DataTypeTok{project_id =} \KeywordTok{col_character}\NormalTok{(), }
        \DataTypeTok{id =} \KeywordTok{col_character}\NormalTok{(), }\DataTypeTok{parameter_id =} \KeywordTok{col_character}\NormalTok{(), }\DataTypeTok{age_in_days =} \KeywordTok{col_integer}\NormalTok{(), }
        \DataTypeTok{date_of_experiment =} \KeywordTok{col_datetime}\NormalTok{(}\DataTypeTok{format =} \StringTok{""}\NormalTok{), }\DataTypeTok{weight =} \KeywordTok{col_double}\NormalTok{(), }\DataTypeTok{phenotyping_center_id =} \KeywordTok{col_character}\NormalTok{(), }
        \DataTypeTok{production_center_id =} \KeywordTok{col_character}\NormalTok{(), }\DataTypeTok{weight_date =} \KeywordTok{col_datetime}\NormalTok{(}\DataTypeTok{format =} \StringTok{""}\NormalTok{), }
        \DataTypeTok{date_of_birth =} \KeywordTok{col_datetime}\NormalTok{(}\DataTypeTok{format =} \StringTok{""}\NormalTok{), }\DataTypeTok{procedure_id =} \KeywordTok{col_character}\NormalTok{(), }
        \DataTypeTok{pipeline_id =} \KeywordTok{col_character}\NormalTok{(), }\DataTypeTok{biological_sample_id =} \KeywordTok{col_character}\NormalTok{(), }\DataTypeTok{biological_model_id =} \KeywordTok{col_character}\NormalTok{(), }
        \DataTypeTok{weight_days_old =} \KeywordTok{col_integer}\NormalTok{(), }\DataTypeTok{datasource_id =} \KeywordTok{col_character}\NormalTok{(), }\DataTypeTok{experiment_id =} \KeywordTok{col_character}\NormalTok{(), }
        \DataTypeTok{data_point =} \KeywordTok{col_double}\NormalTok{(), }\DataTypeTok{age_in_weeks =} \KeywordTok{col_integer}\NormalTok{(), }\StringTok{`}\DataTypeTok{_version_}\StringTok{`}\NormalTok{ =}\StringTok{ }\KeywordTok{col_character}\NormalTok{()))}
\NormalTok{\}}

\CommentTok{# Apply some standard cleaning to the data}
\NormalTok{clean_raw_data <-}\StringTok{ }\ControlFlowTok{function}\NormalTok{(mydata) \{}

\NormalTok{    group <-}\StringTok{ }\KeywordTok{read_csv}\NormalTok{(}\KeywordTok{here}\NormalTok{(}\StringTok{"data"}\NormalTok{, }\StringTok{"ParameterGrouping.csv"}\NormalTok{))}

\NormalTok{    tmp <-}\StringTok{ }\NormalTok{mydata }\OperatorTok{%>%}\StringTok{ }
\StringTok{    }\CommentTok{# Filter to IMPC source (recommend by Jeremey in email to Susi on 20 Aug 2018)}
\StringTok{    }\KeywordTok{filter}\NormalTok{(datasource_name }\OperatorTok{==}\StringTok{ "IMPC"}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{    }\CommentTok{# standardise trait names}
\StringTok{    }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{parameter_name =} \KeywordTok{tolower}\NormalTok{(parameter_name)) }\OperatorTok{%>%}\StringTok{ }
\StringTok{    }\CommentTok{# remove extreme ages}
\StringTok{    }\KeywordTok{filter}\NormalTok{(age_in_days }\OperatorTok{>}\StringTok{ }\DecValTok{0} \OperatorTok{&}\StringTok{ }\NormalTok{age_in_days }\OperatorTok{<}\StringTok{ }\DecValTok{500}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{    }\CommentTok{# remove NAs}
\StringTok{    }\KeywordTok{filter}\NormalTok{(}\OperatorTok{!}\KeywordTok{is.na}\NormalTok{(data_point)) }\OperatorTok{%>%}\StringTok{ }
\StringTok{    }\CommentTok{# subset to reasonable set of variables, date_of_experiment used as an indicator}
\StringTok{    }\CommentTok{# of batch-level effects}
\StringTok{    }\KeywordTok{select}\NormalTok{(production_center, strain_name, strain_accession_id, biological_sample_id, }
\NormalTok{        pipeline_stable_id, procedure_group, procedure_name, sex, date_of_experiment, }
\NormalTok{        age_in_days, weight, parameter_name, data_point) }\OperatorTok{%>%}\StringTok{ }
\StringTok{    }\CommentTok{# sort}
\StringTok{    }\KeywordTok{arrange}\NormalTok{(production_center, biological_sample_id, age_in_days)}

    \CommentTok{# filter to groups with > 1 centre}
    \KeywordTok{merge}\NormalTok{(tmp, tmp }\OperatorTok{%>%}\StringTok{ }\KeywordTok{group_by}\NormalTok{(parameter_name) }\OperatorTok{%>%}\StringTok{ }\KeywordTok{summarise}\NormalTok{(}\DataTypeTok{center_per_trait =} \KeywordTok{length}\NormalTok{(}\KeywordTok{unique}\NormalTok{(production_center, }
        \DataTypeTok{na.rm =} \OtherTok{TRUE}\NormalTok{)))) }\OperatorTok{%>%}\StringTok{ }\KeywordTok{filter}\NormalTok{(center_per_trait }\OperatorTok{>=}\StringTok{ }\DecValTok{2}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{    }\CommentTok{# Define population variable}
\StringTok{    }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{population =} \KeywordTok{sprintf}\NormalTok{(}\StringTok{"%s-%s"}\NormalTok{, production_center, strain_name)) }\OperatorTok{%>%}\StringTok{ }
\StringTok{    }\CommentTok{# add grouping variable: these were decided based on functional groups and}
\StringTok{    }\CommentTok{# procedures}
\StringTok{    }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{parameter_group =}\NormalTok{ group}\OperatorTok{$}\NormalTok{parameter[}\KeywordTok{match}\NormalTok{(parameter_name, group}\OperatorTok{$}\NormalTok{parameter_name)]) }\OperatorTok{%>%}\StringTok{ }
\StringTok{        }
\StringTok{    }\CommentTok{# Assign unique IDs (per trait) each unique parameter_name (=trait,use trait}
\StringTok{    }\CommentTok{# variable) gets a unique number ('id')}
\StringTok{    }
\StringTok{    }\CommentTok{# We add a new variable, where redundant traits are combined [note however, at}
\StringTok{    }\CommentTok{# this stage the dataset still contains nonsensical traits, i.e. traits that may}
\StringTok{    }\CommentTok{# not contain any information on variance]}
\StringTok{    }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{id =} \KeywordTok{match}\NormalTok{(parameter_name, }\KeywordTok{unique}\NormalTok{(parameter_name))) }\OperatorTok{%>%}\StringTok{ }\KeywordTok{as_tibble}\NormalTok{()}
\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

\hypertarget{sub-setting-data}{%
\subsubsection{Sub-setting data}\label{sub-setting-data}}

Create a function for sub-setting the data to choose only one data point
per individual per trait:
``data\_subset\_parameterid\_individual\_by\_age''

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{data_subset_parameterid_individual_by_age <-}\StringTok{ }\ControlFlowTok{function}\NormalTok{(mydata, parameter, }\DataTypeTok{age_min =} \DecValTok{0}\NormalTok{, }
    \DataTypeTok{age_center =} \DecValTok{100}\NormalTok{) \{}
\NormalTok{    tmp <-}\StringTok{ }\NormalTok{mydata }\OperatorTok{%>%}\StringTok{ }\KeywordTok{filter}\NormalTok{(age_in_days }\OperatorTok{>=}\StringTok{ }\NormalTok{age_min, id }\OperatorTok{==}\StringTok{ }\NormalTok{parameter) }\OperatorTok{%>%}\StringTok{ }\CommentTok{# Take results for single individual closest to age_center}
\StringTok{    }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{age_diff =} \KeywordTok{abs}\NormalTok{(age_center }\OperatorTok{-}\StringTok{ }\NormalTok{age_in_days)) }\OperatorTok{%>%}\StringTok{ }\KeywordTok{group_by}\NormalTok{(biological_sample_id) }\OperatorTok{%>%}\StringTok{ }
\StringTok{        }\KeywordTok{filter}\NormalTok{(age_diff }\OperatorTok{==}\StringTok{ }\KeywordTok{min}\NormalTok{(age_diff)) }\OperatorTok{%>%}\StringTok{ }\KeywordTok{select}\NormalTok{(}\OperatorTok{-}\NormalTok{age_diff)}

    \CommentTok{# Still some individuals with multiple records (because same individual appears}
    \CommentTok{# under different procedures, so filter to one record)}
\NormalTok{    j <-}\StringTok{ }\KeywordTok{match}\NormalTok{(}\KeywordTok{unique}\NormalTok{(tmp}\OperatorTok{$}\NormalTok{biological_sample_id), tmp}\OperatorTok{$}\NormalTok{biological_sample_id)}
\NormalTok{    tmp[j, ]}
\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

\hypertarget{population-statistics}{%
\subsubsection{Population statistics}\label{population-statistics}}

Create a function called: ``calculate\_population\_stats'' This function
groups animals from the same strain and institution together. This is
done for each trait separately, and only for traits that have been
measured in both sexes. Any group containing fewer than 6 individuals is
excluded.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Function re-organises the data so that the male and female data are side-by-side as columns to make effect size calculations easier.}
\NormalTok{multi_spread <-}\StringTok{ }\ControlFlowTok{function}\NormalTok{(df, key, value) \{}
    \CommentTok{# quote key}
\NormalTok{      keyq <-}\StringTok{ }\NormalTok{rlang}\OperatorTok{::}\KeywordTok{enquo}\NormalTok{(key)}
    \CommentTok{# break value vector into quotes}
\NormalTok{    valueq <-}\StringTok{ }\NormalTok{rlang}\OperatorTok{::}\KeywordTok{enquo}\NormalTok{(value)}
\NormalTok{         s <-}\StringTok{ }\NormalTok{rlang}\OperatorTok{::}\KeywordTok{quos}\NormalTok{(}\OperatorTok{!!}\NormalTok{valueq)}

\NormalTok{         df                           }\OperatorTok{%>%}\StringTok{ }
\StringTok{        }\KeywordTok{gather}\NormalTok{(variable, value, }\OperatorTok{!!!}\NormalTok{s) }\OperatorTok{%>%}
\StringTok{        }\KeywordTok{unite}\NormalTok{(temp, }\OperatorTok{!!}\NormalTok{keyq, variable) }\OperatorTok{%>%}
\StringTok{        }\KeywordTok{spread}\NormalTok{(temp, value)}
\NormalTok{\}}

\CommentTok{# Function will calculate population stats and exclude data that is irrelevant and not useful, it will also just convert the data straight away to wide format making it ready for effect size calculations}

\NormalTok{calculate_population_stats <-}\StringTok{ }\ControlFlowTok{function}\NormalTok{(mydata, }\DataTypeTok{min_individuals =} \DecValTok{5}\NormalTok{)\{}
\NormalTok{    mydata }\OperatorTok{%>%}\StringTok{ }
\StringTok{    }\KeywordTok{group_by}\NormalTok{(population,}
\NormalTok{             production_center,  }
\NormalTok{             strain_name,  }
\NormalTok{             sex) }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{summarise}\NormalTok{(}\DataTypeTok{trait  =}\NormalTok{ parameter_name[}\DecValTok{1}\NormalTok{],}
              \DataTypeTok{x_bar  =} \KeywordTok{mean}\NormalTok{(data_point, }\DataTypeTok{na.rm =} \OtherTok{TRUE}\NormalTok{),}
              \DataTypeTok{x_sd   =}   \KeywordTok{sd}\NormalTok{(data_point, }\DataTypeTok{na.rm =} \OtherTok{TRUE}\NormalTok{),}
              \DataTypeTok{n_ind  =} \KeywordTok{n}\NormalTok{()) }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{ungroup}\NormalTok{() }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{filter}\NormalTok{(n_ind }\OperatorTok{>}\StringTok{ }\NormalTok{min_individuals) }\OperatorTok{%>%}\StringTok{   }\CommentTok{# }\AlertTok{NOTE}\CommentTok{ here that you are excluding data with 5 exactly....}
\StringTok{    }\KeywordTok{group_by}\NormalTok{(population) }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{filter}\NormalTok{(}\KeywordTok{all}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"male"}\NormalTok{, }\StringTok{"female"}\NormalTok{) }\OperatorTok{%in%}\StringTok{ }\NormalTok{sex)) }\OperatorTok{%>%}\StringTok{ }\CommentTok{# Removes any entries where only 1 sex is present}
\StringTok{    }\KeywordTok{multi_spread}\NormalTok{(sex, }\KeywordTok{c}\NormalTok{(x_bar, x_sd, n_ind))      }\CommentTok{# Spreads the data out into wide format, so sexes are beside each other which is more typical of meta-analytic data}
\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

\hypertarget{calculate-effect-sizes-and-sample-variances}{%
\subsubsection{Calculate effect sizes and sample
variances}\label{calculate-effect-sizes-and-sample-variances}}

Function: ``create\_meta\_analysis\_effect\_sizes''

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# This function takes the data and computes lnCVR, lnVR and ROM (lnRR) using male}
\CommentTok{# and female data to generate effect size statistics for meta-analyses}
\NormalTok{create_meta_analysis_effect_sizes <-}\StringTok{ }\ControlFlowTok{function}\NormalTok{(mydata, }\DataTypeTok{measure =} \KeywordTok{c}\NormalTok{(}\StringTok{"CVR"}\NormalTok{, }\StringTok{"VR"}\NormalTok{, }\StringTok{"ROM"}\NormalTok{)) \{}
    \ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{1}\OperatorTok{:}\KeywordTok{length}\NormalTok{(measure)) \{}
\NormalTok{        mydata <-}\StringTok{ }\NormalTok{metafor}\OperatorTok{::}\KeywordTok{escalc}\NormalTok{(}\DataTypeTok{m1i =}\NormalTok{ male_x_bar, }\DataTypeTok{m2i =}\NormalTok{ female_x_bar, }\DataTypeTok{sd1i =}\NormalTok{ male_x_sd, }
            \DataTypeTok{sd2i =}\NormalTok{ female_x_sd, }\DataTypeTok{n1i =}\NormalTok{ male_n_ind, }\DataTypeTok{n2i =}\NormalTok{ female_n_ind, }\DataTypeTok{data =}\NormalTok{ mydata, }
            \DataTypeTok{measure =}\NormalTok{ measure[i], }\DataTypeTok{var.names =} \KeywordTok{c}\NormalTok{(}\KeywordTok{paste0}\NormalTok{(}\StringTok{"effect_size_"}\NormalTok{, measure[i]), }
                \KeywordTok{paste0}\NormalTok{(}\StringTok{"sample_variance_"}\NormalTok{, measure[i])), }\DataTypeTok{append =} \OtherTok{TRUE}\NormalTok{)}
\NormalTok{    \}}
    \KeywordTok{return}\NormalTok{(mydata)}
\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

\hypertarget{load-clean-data}{%
\subsection{Load \& clean data}\label{load-clean-data}}

We have already done this step and provide a cleaned up file which is
less computationally intensive to deal with. The file has been saved in
a folder called \texttt{export}. However, the \texttt{.csv} is provided
in case this is preferred and can be imported and processed using
following the steps below: {[}This code is currently excluded from
showing in this \texttt{.html} file, but can be viewed and enabled / run
in the down-loadable .rmd file. However, it requires the .gz file
containing the raw data in the ``export'' folder. Unfortunately, that
file can not be provided via Github, as it is too large (274MB).
However, it is freely accessible and uploaded to zenodo.org
(\url{https://zenodo.org/deposit/3759701})

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Load raw data - save cleaned dataset as RDS for reuse}
\NormalTok{data_raw <-}\StringTok{ }\KeywordTok{load_raw}\NormalTok{(}\KeywordTok{here}\NormalTok{(}\StringTok{"data"}\NormalTok{, }\StringTok{"dr7.0_all_control_data.csv.gz"}\NormalTok{))}
\KeywordTok{dir.create}\NormalTok{(}\StringTok{"export"}\NormalTok{, F, F)}

\NormalTok{data <-}\StringTok{ }\NormalTok{data_raw }\OperatorTok{%>%}\StringTok{ }\KeywordTok{clean_raw_data}\NormalTok{()}
\KeywordTok{saveRDS}\NormalTok{(data, }\StringTok{"export/data_clean.rds"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

For analysis we load the RDS created above and other datasets

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{data <-}\StringTok{ }\KeywordTok{readRDS}\NormalTok{(}\KeywordTok{here}\NormalTok{(}\StringTok{"export"}\NormalTok{, }\StringTok{"data_clean.rds"}\NormalTok{))}

\NormalTok{procedures <-}\StringTok{ }\KeywordTok{read_csv}\NormalTok{(}\KeywordTok{here}\NormalTok{(}\StringTok{"data"}\NormalTok{, }\StringTok{"procedures.csv"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\hypertarget{meta-analyses}{%
\section{Meta-analyses}\label{meta-analyses}}

\hypertarget{population-as-analysis-unit}{%
\subsection{Population as analysis
unit}\label{population-as-analysis-unit}}

In this section, we cover the workflow described in Figure
@ref(fig:FigG1) C and D.

\hypertarget{loop-through-meta-analyses-on-all-traits}{%
\subsubsection{Loop through meta-analyses on all
traits}\label{loop-through-meta-analyses-on-all-traits}}

This section covers Figure @ref(fig:FigG1) C, by conducting a
meta-analsyis for all traits and producing the meta-analysed effect
sizes (lnVR, lnCVR and lnRR).

\begin{itemize}
\tightlist
\item
  The loop combines the functions mentioned above and fills the data
  matrix with results from our meta analysis.
\item
  Error messages indicate traits that either did not reach convergence,
  or that did not return meaningful results in the meta-analysis, due to
  absence of variance. Those traits will be removed in later steps,
  outlined below.
\end{itemize}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{n <-}\StringTok{ }\KeywordTok{length}\NormalTok{(}\KeywordTok{unique}\NormalTok{(data}\OperatorTok{$}\NormalTok{id))}

\CommentTok{# Create dataframe to store results}
\NormalTok{results_alltraits_grouping <-}\StringTok{ }\KeywordTok{data.frame}\NormalTok{(}\KeywordTok{tibble}\NormalTok{(}\DataTypeTok{id =} \DecValTok{1}\OperatorTok{:}\NormalTok{n, }\DataTypeTok{lnCVR =} \DecValTok{0}\NormalTok{, }\DataTypeTok{lnCVR_lower =} \DecValTok{0}\NormalTok{, }
    \DataTypeTok{lnCVR_upper =} \DecValTok{0}\NormalTok{, }\DataTypeTok{lnCVR_se =} \DecValTok{0}\NormalTok{, }\DataTypeTok{lnVR =} \DecValTok{0}\NormalTok{, }\DataTypeTok{lnVR_lower =} \DecValTok{0}\NormalTok{, }\DataTypeTok{lnVR_upper =} \DecValTok{0}\NormalTok{, }\DataTypeTok{lnVR_se =} \DecValTok{0}\NormalTok{, }
    \DataTypeTok{lnRR =} \DecValTok{0}\NormalTok{, }\DataTypeTok{lnRR_lower =} \DecValTok{0}\NormalTok{, }\DataTypeTok{lnRR_upper =} \DecValTok{0}\NormalTok{, }\DataTypeTok{lnRR_se =} \DecValTok{0}\NormalTok{, }\DataTypeTok{sampleSize =} \DecValTok{0}\NormalTok{, }\DataTypeTok{trait =} \DecValTok{0}\NormalTok{))}

\ControlFlowTok{for}\NormalTok{ (t }\ControlFlowTok{in} \DecValTok{1}\OperatorTok{:}\NormalTok{n) \{}
    \KeywordTok{tryCatch}\NormalTok{(\{}

\NormalTok{        results <-}\StringTok{ }\NormalTok{data }\OperatorTok{%>%}\StringTok{ }\KeywordTok{data_subset_parameterid_individual_by_age}\NormalTok{(t) }\OperatorTok{%>%}\StringTok{ }\KeywordTok{calculate_population_stats}\NormalTok{() }\OperatorTok{%>%}\StringTok{ }
\StringTok{            }\KeywordTok{create_meta_analysis_effect_sizes}\NormalTok{() }\OperatorTok{%>%}\StringTok{ }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{err =} \KeywordTok{seq_len}\NormalTok{(}\KeywordTok{n}\NormalTok{()))}

        \CommentTok{# lnCVR, log repsonse-ratio of the coefficient of variance}
\NormalTok{        cvr <-}\StringTok{ }\NormalTok{metafor}\OperatorTok{::}\KeywordTok{rma.mv}\NormalTok{(}\DataTypeTok{yi =}\NormalTok{ effect_size_CVR, }\DataTypeTok{V =}\NormalTok{ sample_variance_CVR, }\DataTypeTok{random =} \KeywordTok{list}\NormalTok{(}\OperatorTok{~}\DecValTok{1} \OperatorTok{|}\StringTok{ }
\StringTok{            }\NormalTok{strain_name, }\OperatorTok{~}\DecValTok{1} \OperatorTok{|}\StringTok{ }\NormalTok{production_center, }\OperatorTok{~}\DecValTok{1} \OperatorTok{|}\StringTok{ }\NormalTok{err), }\DataTypeTok{control =} \KeywordTok{list}\NormalTok{(}\DataTypeTok{optimizer =} \StringTok{"optim"}\NormalTok{, }
            \DataTypeTok{optmethod =} \StringTok{"Nelder-Mead"}\NormalTok{, }\DataTypeTok{maxit =} \DecValTok{1000}\NormalTok{), }\DataTypeTok{verbose =}\NormalTok{ F, }\DataTypeTok{data =}\NormalTok{ results)}

        \CommentTok{# lnVR, comparison of standard deviations}
\NormalTok{        cv <-}\StringTok{ }\NormalTok{metafor}\OperatorTok{::}\KeywordTok{rma.mv}\NormalTok{(}\DataTypeTok{yi =}\NormalTok{ effect_size_VR, }\DataTypeTok{V =}\NormalTok{ sample_variance_VR, }\DataTypeTok{random =} \KeywordTok{list}\NormalTok{(}\OperatorTok{~}\DecValTok{1} \OperatorTok{|}\StringTok{ }
\StringTok{            }\NormalTok{strain_name, }\OperatorTok{~}\DecValTok{1} \OperatorTok{|}\StringTok{ }\NormalTok{production_center, }\OperatorTok{~}\DecValTok{1} \OperatorTok{|}\StringTok{ }\NormalTok{err), }\DataTypeTok{control =} \KeywordTok{list}\NormalTok{(}\DataTypeTok{optimizer =} \StringTok{"optim"}\NormalTok{, }
            \DataTypeTok{optmethod =} \StringTok{"Nelder-Mead"}\NormalTok{, }\DataTypeTok{maxit =} \DecValTok{1000}\NormalTok{), }\DataTypeTok{verbose =}\NormalTok{ F, }\DataTypeTok{data =}\NormalTok{ results)}

        \CommentTok{# for means, lnRR}
\NormalTok{        means <-}\StringTok{ }\NormalTok{metafor}\OperatorTok{::}\KeywordTok{rma.mv}\NormalTok{(}\DataTypeTok{yi =}\NormalTok{ effect_size_ROM, }\DataTypeTok{V =}\NormalTok{ sample_variance_ROM, }\DataTypeTok{random =} \KeywordTok{list}\NormalTok{(}\OperatorTok{~}\DecValTok{1} \OperatorTok{|}\StringTok{ }
\StringTok{            }\NormalTok{strain_name, }\OperatorTok{~}\DecValTok{1} \OperatorTok{|}\StringTok{ }\NormalTok{production_center, }\OperatorTok{~}\DecValTok{1} \OperatorTok{|}\StringTok{ }\NormalTok{err), }\DataTypeTok{control =} \KeywordTok{list}\NormalTok{(}\DataTypeTok{optimizer =} \StringTok{"optim"}\NormalTok{, }
            \DataTypeTok{optmethod =} \StringTok{"Nelder-Mead"}\NormalTok{, }\DataTypeTok{maxit =} \DecValTok{1000}\NormalTok{), }\DataTypeTok{verbose =}\NormalTok{ F, }\DataTypeTok{data =}\NormalTok{ results)}

\NormalTok{        f <-}\StringTok{ }\ControlFlowTok{function}\NormalTok{(x) }\KeywordTok{unlist}\NormalTok{(x[}\KeywordTok{c}\NormalTok{(}\StringTok{"b"}\NormalTok{, }\StringTok{"ci.lb"}\NormalTok{, }\StringTok{"ci.ub"}\NormalTok{, }\StringTok{"se"}\NormalTok{)])}

\NormalTok{        results_alltraits_grouping[t, }\DecValTok{2}\OperatorTok{:}\DecValTok{14}\NormalTok{] <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\KeywordTok{f}\NormalTok{(cvr), }\KeywordTok{f}\NormalTok{(cv), }\KeywordTok{f}\NormalTok{(means), }\DataTypeTok{k =}\NormalTok{ means}\OperatorTok{$}\NormalTok{k)}
\NormalTok{        results_alltraits_grouping[t, }\DecValTok{15}\NormalTok{] <-}\StringTok{ }\KeywordTok{unique}\NormalTok{(results}\OperatorTok{$}\NormalTok{trait)}
\NormalTok{    \}, }\DataTypeTok{error =} \ControlFlowTok{function}\NormalTok{(e) \{}
        \KeywordTok{cat}\NormalTok{(}\StringTok{"ERROR :"}\NormalTok{, t, }\KeywordTok{conditionMessage}\NormalTok{(e), }\StringTok{"}\CharTok{\textbackslash{}n}\StringTok{"}\NormalTok{)}
\NormalTok{    \})}
\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## ERROR : 84 Optimizer (optim) did not achieve convergence (convergence = 10). 
## ERROR : 160 Processing terminated since k <= 1. 
## ERROR : 168 Processing terminated since k <= 1.
\end{verbatim}

In the above function, we use `tryCatch' and `conditionMessage' to
prevent the loop from aborting when the first error at row 84 is
produced. As convergence in the two listed non-converging cases can't be
achieved by sensibly tweaking (other optim etc.), and we only learn
about non-convergence in the loop, it is not possible to exclude the
traits (N = 2) beforehand.Similarly, there are 8 traits with very low
variation, which can not be excluded prior to running the loop.

Any produced ``Warnings'' indicate cases where variance components are
set to zero during likelihood optimization.

\hypertarget{merging-datasets-removal-of-non-converged-traits}{%
\subsubsection{Merging datasets \& removal of non-converged
traits}\label{merging-datasets-removal-of-non-converged-traits}}

Here we cover Figure @ref(fig:FigG1) D, removing non-coverging model
results and non-informative traits.Procedure names, grouping variables
and trait names (``parameter\_names'') are the merged back together with
the results from the metafor analysis above.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{results_alltraits_grouping2 <-}\StringTok{ }\NormalTok{results_alltraits_grouping }\OperatorTok{%>%}\StringTok{ }
\CommentTok{# Join data with results_alltraits_grouping. We filter duplicated id's to get}
\CommentTok{# only one unique row per id (and there is one id per parameter_name)}
\KeywordTok{left_join}\NormalTok{(}\DataTypeTok{by =} \StringTok{"id"}\NormalTok{, data }\OperatorTok{%>%}\StringTok{ }\KeywordTok{select}\NormalTok{(id, parameter_group, }\DataTypeTok{procedure =}\NormalTok{ procedure_name, }
\NormalTok{    procedure_name, parameter_name) }\OperatorTok{%>%}\StringTok{ }\KeywordTok{filter}\NormalTok{(}\OperatorTok{!}\KeywordTok{duplicated}\NormalTok{(id))) }\OperatorTok{%>%}\StringTok{ }
\CommentTok{# Below we add 'procedure' (from the previously loaded 'procedures.csv') as a}
\CommentTok{# variable; n <- length(unique(results_alltraits_grouping2$parameter_name)))}
\CommentTok{# should equal 232}
\KeywordTok{left_join}\NormalTok{(}\DataTypeTok{by =} \StringTok{"procedure"}\NormalTok{, procedures }\OperatorTok{%>%}\StringTok{ }\KeywordTok{distinct}\NormalTok{())}

\CommentTok{# We exclude 14 parameter names for which metafor models didn't converge ('dp t}
\CommentTok{# cells', 'mzb (cd21/35 high)'), and of parameters that don't harbour enough}
\CommentTok{# variation}
\NormalTok{meta_clean <-}\StringTok{ }\NormalTok{results_alltraits_grouping2 }\OperatorTok{%>%}\StringTok{ }\KeywordTok{filter}\NormalTok{(}\OperatorTok{!}\NormalTok{parameter_name }\OperatorTok{%in%}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"dp t cells"}\NormalTok{, }
    \StringTok{"mzb (cd21/35 high)"}\NormalTok{, }\StringTok{"number of caudal vertebrae"}\NormalTok{, }\StringTok{"number of cervical vertebrae"}\NormalTok{, }
    \StringTok{"number of digits"}\NormalTok{, }\StringTok{"number of lumbar vertebrae"}\NormalTok{, }\StringTok{"number of pelvic vertebrae"}\NormalTok{, }
    \StringTok{"number of ribs left"}\NormalTok{, }\StringTok{"number of ribs right"}\NormalTok{, }\StringTok{"number of signals"}\NormalTok{, }\StringTok{"number of thoracic vertebrae"}\NormalTok{, }
    \StringTok{"total number of acquired events in panel a"}\NormalTok{, }\StringTok{"total number of acquired events in panel b"}\NormalTok{, }
    \StringTok{"whole arena permanence"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

A total of 14 traits from the original 232 that had been included are
removed because they either did not achieve convergence or are
nonsensical for analysis of variance (such as traits that show no
variation, see list below).

The traits where models did not converge include: ``dp t cells'', ``mzb
(cd21/35 high)''

The traits where there was not enough variation include: ``number of
caudal vertebrae'', ``number of cervical vertebrae'', ``number of
digits'', ``number of lumbar vertebrae'', ``number of pelvic
vertebrae'', ``number of ribs left'',``number of ribs right'', ``number
of signals'', ``number of thoracic vertebrae'', ``total number of
acquired events in panel a'',``total number of acquired events in panel
b'', ``whole arena permanence''.

\hypertarget{meta-analysis-condensing-non-independent-traits}{%
\subsection{Meta-analysis: condensing non-independent
traits}\label{meta-analysis-condensing-non-independent-traits}}

This dataset contained a number of highly correlated traits, such as
different kinds of cell counts (for example hierarchical
parameterization within immunological assays). As those data-points are
not independent of each other, we conducted meta analyses on these
correlated parameters to collapse the number of levels. This section
describes the workflow depicted in Figure @ref(fig:FigG1) E \& F.

\hypertarget{collapsing-and-merging-correlated-parameters-preparation-for-table-s2}{%
\subsubsection{Collapsing and merging correlated parameters, preparation
for Table
S2}\label{collapsing-and-merging-correlated-parameters-preparation-for-table-s2}}

Count the number of parameter names (correlated sub-traits) in each
parameter group (par\_group\_size). This serves to identify and separate
the traits that are correlated from the full dataset that can be
processed as is. If the sample size (n) for a given ``parameter group''
equals 1, the trait is unique and uncorrelated. All instances, where
there are 2 or more traits associated with the same parameter group (90
cases), are selected for a ``mini-meta analysis'', which removes the
issue of correlation. The workflow here relates to Figure
@ref(fig:FigG1) E.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Here we double check numbers of trait parameters in the dataset}
\NormalTok{meta1 <-}\StringTok{ }\NormalTok{meta_clean}
\CommentTok{# length(unique(meta1$procedure)) #18 length(unique(meta1$GroupingTerm)) #9}
\CommentTok{# length(unique(meta1$parameter_group)) # 148 levels. To be used as grouping}
\CommentTok{# factor for meta-meta-analysis / collapsing down based on things that are}
\CommentTok{# classified identically in 'parameter_group' but have different 'parameter_name'}
\CommentTok{# length(unique(meta1$parameter_name)) #218 and prepare the dataset for}
\CommentTok{# second-order meta-analysis}
\NormalTok{meta1_sub <-}\StringTok{ }\NormalTok{meta1 }\OperatorTok{%>%}\StringTok{ }\CommentTok{# Add summary of number of parameter names in each parameter group}
\KeywordTok{group_by}\NormalTok{(parameter_group) }\OperatorTok{%>%}\StringTok{ }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{par_group_size =} \KeywordTok{length}\NormalTok{(}\KeywordTok{unique}\NormalTok{(parameter_name)), }
    \DataTypeTok{sampleSize =} \KeywordTok{as.numeric}\NormalTok{(sampleSize)) }\OperatorTok{%>%}\StringTok{ }\KeywordTok{ungroup}\NormalTok{() }\OperatorTok{%>%}\StringTok{ }\CommentTok{# Create subsets with > 1 count (par_group_size > 1)}
\KeywordTok{filter}\NormalTok{(par_group_size }\OperatorTok{>}\StringTok{ }\DecValTok{1}\NormalTok{)  }\CommentTok{# 90 observations}
\end{Highlighting}
\end{Shaded}

\hypertarget{meta-analyses-on-correlated-sub-traits-using-robumeta}{%
\subsubsection{\texorpdfstring{Meta-analyses on correlated (sub-)traits,
using
\texttt{robumeta}}{Meta-analyses on correlated (sub-)traits, using robumeta}}\label{meta-analyses-on-correlated-sub-traits-using-robumeta}}

Here we pepare the subset of the data (using nest()), and in this first
step the model of the meta-analysis effect sizes are calculated. This
section specifically undertakes the workflow described in Figure
@ref(fig:FigG1) F.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Create summary of number of parameter names in each parameter group, and merge}
\CommentTok{# back together}

\NormalTok{meta1b <-}\StringTok{ }\NormalTok{meta1 }\OperatorTok{%>%}\StringTok{ }\KeywordTok{group_by}\NormalTok{(parameter_group) }\OperatorTok{%>%}\StringTok{ }\KeywordTok{summarize}\NormalTok{(}\DataTypeTok{par_group_size =} \KeywordTok{length}\NormalTok{(}\KeywordTok{unique}\NormalTok{(parameter_name, }
    \DataTypeTok{na.rm =} \OtherTok{TRUE}\NormalTok{)))}

\NormalTok{meta1}\OperatorTok{$}\NormalTok{par_group_size <-}\StringTok{ }\NormalTok{meta1b}\OperatorTok{$}\NormalTok{par_group_size[}\KeywordTok{match}\NormalTok{(meta1}\OperatorTok{$}\NormalTok{parameter_group, meta1b}\OperatorTok{$}\NormalTok{parameter_group)]}

\CommentTok{# Create subsets with > 1 count (par_group_size > 1)}

\NormalTok{meta1_sub <-}\StringTok{ }\KeywordTok{subset}\NormalTok{(meta1, par_group_size }\OperatorTok{>}\StringTok{ }\DecValTok{1}\NormalTok{)  }\CommentTok{# 90 observations   }
\NormalTok{meta1_sub}\OperatorTok{$}\NormalTok{sampleSize <-}\StringTok{ }\KeywordTok{as.numeric}\NormalTok{(meta1_sub}\OperatorTok{$}\NormalTok{sampleSize)}

\CommentTok{# Nesting and meta-analyses on correlated traits, using robumeta}

\NormalTok{n_count <-}\StringTok{ }\NormalTok{meta1_sub }\OperatorTok{%>%}\StringTok{ }\KeywordTok{group_by}\NormalTok{(parameter_group) }\OperatorTok{%>%}\StringTok{ }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{raw_N =} \KeywordTok{sum}\NormalTok{(sampleSize)) }\OperatorTok{%>%}\StringTok{ }
\StringTok{    }\KeywordTok{nest}\NormalTok{() }\OperatorTok{%>%}\StringTok{ }\KeywordTok{ungroup}\NormalTok{()}

\NormalTok{model_count <-}\StringTok{ }\NormalTok{n_count }\OperatorTok{%>%}\StringTok{ }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{model_lnRR =} \KeywordTok{map}\NormalTok{(data, }\OperatorTok{~}\KeywordTok{robu}\NormalTok{(.x}\OperatorTok{$}\NormalTok{lnRR }\OperatorTok{~}\StringTok{ }\DecValTok{1}\NormalTok{, }\DataTypeTok{data =}\NormalTok{ .x, }
    \DataTypeTok{studynum =}\NormalTok{ .x}\OperatorTok{$}\NormalTok{id, }\DataTypeTok{modelweights =} \KeywordTok{c}\NormalTok{(}\StringTok{"CORR"}\NormalTok{), }\DataTypeTok{rho =} \FloatTok{0.8}\NormalTok{, }\DataTypeTok{small =} \OtherTok{TRUE}\NormalTok{, }\DataTypeTok{var.eff.size =}\NormalTok{ (.x}\OperatorTok{$}\NormalTok{lnRR_se)}\OperatorTok{^}\DecValTok{2}\NormalTok{)), }
    \DataTypeTok{model_lnVR =} \KeywordTok{map}\NormalTok{(data, }\OperatorTok{~}\KeywordTok{robu}\NormalTok{(.x}\OperatorTok{$}\NormalTok{lnVR }\OperatorTok{~}\StringTok{ }\DecValTok{1}\NormalTok{, }\DataTypeTok{data =}\NormalTok{ .x, }\DataTypeTok{studynum =}\NormalTok{ .x}\OperatorTok{$}\NormalTok{id, }\DataTypeTok{modelweights =} \KeywordTok{c}\NormalTok{(}\StringTok{"CORR"}\NormalTok{), }
        \DataTypeTok{rho =} \FloatTok{0.8}\NormalTok{, }\DataTypeTok{small =} \OtherTok{TRUE}\NormalTok{, }\DataTypeTok{var.eff.size =}\NormalTok{ (.x}\OperatorTok{$}\NormalTok{lnVR_se)}\OperatorTok{^}\DecValTok{2}\NormalTok{)), }\DataTypeTok{model_lnCVR =} \KeywordTok{map}\NormalTok{(data, }
        \OperatorTok{~}\KeywordTok{robu}\NormalTok{(.x}\OperatorTok{$}\NormalTok{lnCVR }\OperatorTok{~}\StringTok{ }\DecValTok{1}\NormalTok{, }\DataTypeTok{data =}\NormalTok{ .x, }\DataTypeTok{studynum =}\NormalTok{ .x}\OperatorTok{$}\NormalTok{id, }\DataTypeTok{modelweights =} \KeywordTok{c}\NormalTok{(}\StringTok{"CORR"}\NormalTok{), }
            \DataTypeTok{rho =} \FloatTok{0.8}\NormalTok{, }\DataTypeTok{small =} \OtherTok{TRUE}\NormalTok{, }\DataTypeTok{var.eff.size =}\NormalTok{ (.x}\OperatorTok{$}\NormalTok{lnCVR_se)}\OperatorTok{^}\DecValTok{2}\NormalTok{)))}

\CommentTok{#### Extracting and save parameter estimates Here we apply an additional function to}
\CommentTok{#### collect the outcomes of the 'mini-meta-analysis' that has condensed our}
\CommentTok{#### non-independent traits. Values from our second-order meta-analysis using}
\CommentTok{#### robu-meta are then extracted}

\NormalTok{count_fun <-}\StringTok{ }\ControlFlowTok{function}\NormalTok{(mod_sub) \{}
    \KeywordTok{return}\NormalTok{(}\KeywordTok{c}\NormalTok{(mod_sub}\OperatorTok{$}\NormalTok{reg_table}\OperatorTok{$}\NormalTok{b.r, mod_sub}\OperatorTok{$}\NormalTok{reg_table}\OperatorTok{$}\NormalTok{CI.L, mod_sub}\OperatorTok{$}\NormalTok{reg_table}\OperatorTok{$}\NormalTok{CI.U, }
\NormalTok{        mod_sub}\OperatorTok{$}\NormalTok{reg_table}\OperatorTok{$}\NormalTok{SE))}
\NormalTok{\}  }\CommentTok{# estimate, lower ci, upper ci, SE}

\CommentTok{# Extraction of values created during meta-analyses using robumeta}

\NormalTok{robusub_RR <-}\StringTok{ }\NormalTok{model_count }\OperatorTok{%>%}\StringTok{ }\KeywordTok{transmute}\NormalTok{(parameter_group, }\DataTypeTok{estimatelnRR =} \KeywordTok{map}\NormalTok{(model_lnRR, }
\NormalTok{    count_fun)) }\OperatorTok{%>%}\StringTok{ }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{r =} \KeywordTok{map}\NormalTok{(estimatelnRR, }\OperatorTok{~}\KeywordTok{data.frame}\NormalTok{(}\KeywordTok{t}\NormalTok{(.)))) }\OperatorTok{%>%}\StringTok{ }\KeywordTok{unnest}\NormalTok{(r) }\OperatorTok{%>%}\StringTok{ }
\StringTok{    }\KeywordTok{select}\NormalTok{(}\OperatorTok{-}\NormalTok{estimatelnRR) }\OperatorTok{%>%}\StringTok{ }\NormalTok{purrr}\OperatorTok{::}\KeywordTok{set_names}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"parameter_group"}\NormalTok{, }\StringTok{"lnRR"}\NormalTok{, }\StringTok{"lnRR_lower"}\NormalTok{, }
    \StringTok{"lnRR_upper"}\NormalTok{, }\StringTok{"lnRR_se"}\NormalTok{))}

\NormalTok{robusub_CVR <-}\StringTok{ }\NormalTok{model_count }\OperatorTok{%>%}\StringTok{ }\KeywordTok{transmute}\NormalTok{(parameter_group, }\DataTypeTok{estimatelnCVR =} \KeywordTok{map}\NormalTok{(model_lnCVR, }
\NormalTok{    count_fun)) }\OperatorTok{%>%}\StringTok{ }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{r =} \KeywordTok{map}\NormalTok{(estimatelnCVR, }\OperatorTok{~}\KeywordTok{data.frame}\NormalTok{(}\KeywordTok{t}\NormalTok{(.)))) }\OperatorTok{%>%}\StringTok{ }\KeywordTok{unnest}\NormalTok{(r) }\OperatorTok{%>%}\StringTok{ }
\StringTok{    }\KeywordTok{select}\NormalTok{(}\OperatorTok{-}\NormalTok{estimatelnCVR) }\OperatorTok{%>%}\StringTok{ }\NormalTok{purrr}\OperatorTok{::}\KeywordTok{set_names}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"parameter_group"}\NormalTok{, }\StringTok{"lnCVR"}\NormalTok{, }\StringTok{"lnCVR_lower"}\NormalTok{, }
    \StringTok{"lnCVR_upper"}\NormalTok{, }\StringTok{"lnCVR_se"}\NormalTok{))}

\NormalTok{robusub_VR <-}\StringTok{ }\NormalTok{model_count }\OperatorTok{%>%}\StringTok{ }\KeywordTok{transmute}\NormalTok{(parameter_group, }\DataTypeTok{estimatelnVR =} \KeywordTok{map}\NormalTok{(model_lnVR, }
\NormalTok{    count_fun)) }\OperatorTok{%>%}\StringTok{ }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{r =} \KeywordTok{map}\NormalTok{(estimatelnVR, }\OperatorTok{~}\KeywordTok{data.frame}\NormalTok{(}\KeywordTok{t}\NormalTok{(.)))) }\OperatorTok{%>%}\StringTok{ }\KeywordTok{unnest}\NormalTok{(r) }\OperatorTok{%>%}\StringTok{ }
\StringTok{    }\KeywordTok{select}\NormalTok{(}\OperatorTok{-}\NormalTok{estimatelnVR) }\OperatorTok{%>%}\StringTok{ }\NormalTok{purrr}\OperatorTok{::}\KeywordTok{set_names}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"parameter_group"}\NormalTok{, }\StringTok{"lnVR"}\NormalTok{, }\StringTok{"lnVR_lower"}\NormalTok{, }
    \StringTok{"lnVR_upper"}\NormalTok{, }\StringTok{"lnVR_se"}\NormalTok{))}

\NormalTok{robu_all <-}\StringTok{ }\KeywordTok{full_join}\NormalTok{(robusub_CVR, robusub_VR) }\OperatorTok{%>%}\StringTok{ }\KeywordTok{full_join}\NormalTok{(., robusub_RR)}

\CommentTok{#### Combining data Merge the two data sets (the new [robu_all] and the initial}
\CommentTok{#### [uncorrelated sub-traits with count = 1])}
\NormalTok{meta_all <-}\StringTok{ }\NormalTok{meta1 }\OperatorTok{%>%}\StringTok{ }\KeywordTok{filter}\NormalTok{(par_group_size }\OperatorTok{==}\StringTok{ }\DecValTok{1}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }\KeywordTok{as_tibble}\NormalTok{()}
\CommentTok{# glimpse(meta_all) glimpse(robu_all)}

\CommentTok{# Step 1: Columns are matched by name (in our case, 'parameter_group'), and any}
\CommentTok{# missing columns will be filled with NA}
\NormalTok{combinedmeta <-}\StringTok{ }\KeywordTok{bind_rows}\NormalTok{(robu_all, meta_all)}
\CommentTok{# glimpse(combinedmeta)}

\CommentTok{# Steps 2&3: Add information about number of traits in a parameter group,}
\CommentTok{# procedure, and grouping term}
\NormalTok{metacombo <-}\StringTok{ }\NormalTok{combinedmeta}
\NormalTok{metacombo}\OperatorTok{$}\NormalTok{counts <-}\StringTok{ }\NormalTok{meta1}\OperatorTok{$}\NormalTok{par_group_size[}\KeywordTok{match}\NormalTok{(metacombo}\OperatorTok{$}\NormalTok{parameter_group, meta1}\OperatorTok{$}\NormalTok{parameter_group)]}
\NormalTok{metacombo}\OperatorTok{$}\NormalTok{procedure2 <-}\StringTok{ }\NormalTok{meta1}\OperatorTok{$}\NormalTok{procedure[}\KeywordTok{match}\NormalTok{(metacombo}\OperatorTok{$}\NormalTok{parameter_group, meta1}\OperatorTok{$}\NormalTok{parameter_group)]}
\NormalTok{metacombo}\OperatorTok{$}\NormalTok{GroupingTerm2 <-}\StringTok{ }\NormalTok{meta1}\OperatorTok{$}\NormalTok{GroupingTerm[}\KeywordTok{match}\NormalTok{(metacombo}\OperatorTok{$}\NormalTok{parameter_group, meta1}\OperatorTok{$}\NormalTok{parameter_group)]}

\CommentTok{# Clean-up, reorder, and rename}

\NormalTok{metacombo <-}\StringTok{ }\NormalTok{metacombo[}\KeywordTok{c}\NormalTok{(}\StringTok{"parameter_group"}\NormalTok{, }\StringTok{"counts"}\NormalTok{, }\StringTok{"procedure2"}\NormalTok{, }\StringTok{"GroupingTerm2"}\NormalTok{, }
    \StringTok{"lnCVR"}\NormalTok{, }\StringTok{"lnCVR_lower"}\NormalTok{, }\StringTok{"lnCVR_upper"}\NormalTok{, }\StringTok{"lnCVR_se"}\NormalTok{, }\StringTok{"lnVR"}\NormalTok{, }\StringTok{"lnVR_lower"}\NormalTok{, }\StringTok{"lnVR_upper"}\NormalTok{, }
    \StringTok{"lnVR_se"}\NormalTok{, }\StringTok{"lnRR"}\NormalTok{, }\StringTok{"lnRR_lower"}\NormalTok{, }\StringTok{"lnRR_upper"}\NormalTok{, }\StringTok{"lnRR_se"}\NormalTok{)]}

\KeywordTok{names}\NormalTok{(metacombo)[}\KeywordTok{names}\NormalTok{(metacombo) }\OperatorTok{==}\StringTok{ "procedure2"}\NormalTok{] <-}\StringTok{ "procedure"}
\KeywordTok{names}\NormalTok{(metacombo)[}\KeywordTok{names}\NormalTok{(metacombo) }\OperatorTok{==}\StringTok{ "GroupingTerm2"}\NormalTok{] <-}\StringTok{ "GroupingTerm"}
\end{Highlighting}
\end{Shaded}

\hypertarget{second-order-meta-analysis-for-functional-groups}{%
\subsection{Second-order meta-analysis for functional
groups}\label{second-order-meta-analysis-for-functional-groups}}

Here, we describe the workflow depicted in Figure @ref(fig:FigG1) H. We
now use our uncorrelated traits from our first order meta-analysis to
conduct a secondary meta-analysis by analysing the 9 functional trait
groups. We esatimte an overall mean lnCVR, lnVR and lnRR for each
functional trait group.

\hypertarget{preparing-the-data}{%
\subsubsection{Preparing the data}\label{preparing-the-data}}

Nesting, calculating the number of parameters within each grouping term,
and running the meta-analyses.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{metacombo_final <-}\StringTok{ }\NormalTok{metacombo }\OperatorTok{%>%}\StringTok{ }\KeywordTok{group_by}\NormalTok{(GroupingTerm) }\OperatorTok{%>%}\StringTok{ }\KeywordTok{nest}\NormalTok{()}

\CommentTok{# **Calculate number of parameters per grouping term}

\NormalTok{metacombo_final <-}\StringTok{ }\NormalTok{metacombo_final }\OperatorTok{%>%}\StringTok{ }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{para_per_GroupingTerm =} \KeywordTok{map_dbl}\NormalTok{(data, }
\NormalTok{    nrow))}

\CommentTok{# For all grouping terms}
\NormalTok{metacombo_final_all <-}\StringTok{ }\NormalTok{metacombo }\OperatorTok{%>%}\StringTok{ }\KeywordTok{nest}\NormalTok{(}\DataTypeTok{data =} \KeywordTok{everything}\NormalTok{())}

\CommentTok{# Final fixed effects meta-analyses within grouping terms, with SE of the}
\CommentTok{# estimate}

\NormalTok{overall1 <-}\StringTok{ }\NormalTok{metacombo_final }\OperatorTok{%>%}\StringTok{ }
\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{model_lnCVR =} \KeywordTok{map}\NormalTok{(data, }\OperatorTok{~}\NormalTok{metafor}\OperatorTok{::}\KeywordTok{rma.uni}\NormalTok{(}\DataTypeTok{yi =}\NormalTok{ .x}\OperatorTok{$}\NormalTok{lnCVR, }\DataTypeTok{sei =}\NormalTok{ (.x}\OperatorTok{$}\NormalTok{lnCVR_upper }\OperatorTok{-}\StringTok{ }
\StringTok{    }\NormalTok{.x}\OperatorTok{$}\NormalTok{lnCVR_lower)}\OperatorTok{/}\NormalTok{(}\DecValTok{2} \OperatorTok{*}\StringTok{ }\FloatTok{1.96}\NormalTok{), }\DataTypeTok{control =} \KeywordTok{list}\NormalTok{(}\DataTypeTok{optimizer =} \StringTok{"optim"}\NormalTok{, }\DataTypeTok{optmethod =} \StringTok{"Nelder-Mead"}\NormalTok{, }
    \DataTypeTok{maxit =} \DecValTok{1000}\NormalTok{), }\DataTypeTok{verbose =}\NormalTok{ F)), }\DataTypeTok{model_lnVR =} \KeywordTok{map}\NormalTok{(data, }\OperatorTok{~}\NormalTok{metafor}\OperatorTok{::}\KeywordTok{rma.uni}\NormalTok{(}\DataTypeTok{yi =}\NormalTok{ .x}\OperatorTok{$}\NormalTok{lnVR, }
    \DataTypeTok{sei =}\NormalTok{ (.x}\OperatorTok{$}\NormalTok{lnVR_upper }\OperatorTok{-}\StringTok{ }\NormalTok{.x}\OperatorTok{$}\NormalTok{lnVR_lower)}\OperatorTok{/}\NormalTok{(}\DecValTok{2} \OperatorTok{*}\StringTok{ }\FloatTok{1.96}\NormalTok{), }\DataTypeTok{control =} \KeywordTok{list}\NormalTok{(}\DataTypeTok{optimizer =} \StringTok{"optim"}\NormalTok{, }
        \DataTypeTok{optmethod =} \StringTok{"Nelder-Mead"}\NormalTok{, }\DataTypeTok{maxit =} \DecValTok{1000}\NormalTok{), }\DataTypeTok{verbose =}\NormalTok{ F)), }\DataTypeTok{model_lnRR =} \KeywordTok{map}\NormalTok{(data, }
    \OperatorTok{~}\NormalTok{metafor}\OperatorTok{::}\KeywordTok{rma.uni}\NormalTok{(}\DataTypeTok{yi =}\NormalTok{ .x}\OperatorTok{$}\NormalTok{lnRR, }\DataTypeTok{sei =}\NormalTok{ (.x}\OperatorTok{$}\NormalTok{lnRR_upper }\OperatorTok{-}\StringTok{ }\NormalTok{.x}\OperatorTok{$}\NormalTok{lnRR_lower)}\OperatorTok{/}\NormalTok{(}\DecValTok{2} \OperatorTok{*}\StringTok{ }\FloatTok{1.96}\NormalTok{), }
        \DataTypeTok{control =} \KeywordTok{list}\NormalTok{(}\DataTypeTok{optimizer =} \StringTok{"optim"}\NormalTok{, }\DataTypeTok{optmethod =} \StringTok{"Nelder-Mead"}\NormalTok{, }\DataTypeTok{maxit =} \DecValTok{1000}\NormalTok{), }
        \DataTypeTok{verbose =}\NormalTok{ F)))}

\CommentTok{# Final fixed effects meta-analyses ACROSS grouping terms, with SE of the}
\CommentTok{# estimate}

\NormalTok{overall_all1 <-}\StringTok{ }\NormalTok{metacombo_final_all }\OperatorTok{%>%}\StringTok{ }
\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{model_lnCVR =} \KeywordTok{map}\NormalTok{(data, }\OperatorTok{~}\NormalTok{metafor}\OperatorTok{::}\KeywordTok{rma.uni}\NormalTok{(}\DataTypeTok{yi =}\NormalTok{ .x}\OperatorTok{$}\NormalTok{lnCVR, }\DataTypeTok{sei =}\NormalTok{ (.x}\OperatorTok{$}\NormalTok{lnCVR_upper }\OperatorTok{-}\StringTok{ }
\StringTok{    }\NormalTok{.x}\OperatorTok{$}\NormalTok{lnCVR_lower)}\OperatorTok{/}\NormalTok{(}\DecValTok{2} \OperatorTok{*}\StringTok{ }\FloatTok{1.96}\NormalTok{), }\DataTypeTok{control =} \KeywordTok{list}\NormalTok{(}\DataTypeTok{optimizer =} \StringTok{"optim"}\NormalTok{, }\DataTypeTok{optmethod =} \StringTok{"Nelder-Mead"}\NormalTok{, }
    \DataTypeTok{maxit =} \DecValTok{1000}\NormalTok{), }\DataTypeTok{verbose =}\NormalTok{ F)), }\DataTypeTok{model_lnVR =} \KeywordTok{map}\NormalTok{(data, }\OperatorTok{~}\NormalTok{metafor}\OperatorTok{::}\KeywordTok{rma.uni}\NormalTok{(}\DataTypeTok{yi =}\NormalTok{ .x}\OperatorTok{$}\NormalTok{lnVR, }
    \DataTypeTok{sei =}\NormalTok{ (.x}\OperatorTok{$}\NormalTok{lnVR_upper }\OperatorTok{-}\StringTok{ }\NormalTok{.x}\OperatorTok{$}\NormalTok{lnVR_lower)}\OperatorTok{/}\NormalTok{(}\DecValTok{2} \OperatorTok{*}\StringTok{ }\FloatTok{1.96}\NormalTok{), }\DataTypeTok{control =} \KeywordTok{list}\NormalTok{(}\DataTypeTok{optimizer =} \StringTok{"optim"}\NormalTok{, }
        \DataTypeTok{optmethod =} \StringTok{"Nelder-Mead"}\NormalTok{, }\DataTypeTok{maxit =} \DecValTok{1000}\NormalTok{), }\DataTypeTok{verbose =}\NormalTok{ F)), }\DataTypeTok{model_lnRR =} \KeywordTok{map}\NormalTok{(data, }
    \OperatorTok{~}\NormalTok{metafor}\OperatorTok{::}\KeywordTok{rma.uni}\NormalTok{(}\DataTypeTok{yi =}\NormalTok{ .x}\OperatorTok{$}\NormalTok{lnRR, }\DataTypeTok{sei =}\NormalTok{ (.x}\OperatorTok{$}\NormalTok{lnRR_upper }\OperatorTok{-}\StringTok{ }\NormalTok{.x}\OperatorTok{$}\NormalTok{lnRR_lower)}\OperatorTok{/}\NormalTok{(}\DecValTok{2} \OperatorTok{*}\StringTok{ }\FloatTok{1.96}\NormalTok{), }
        \DataTypeTok{control =} \KeywordTok{list}\NormalTok{(}\DataTypeTok{optimizer =} \StringTok{"optim"}\NormalTok{, }\DataTypeTok{optmethod =} \StringTok{"Nelder-Mead"}\NormalTok{, }\DataTypeTok{maxit =} \DecValTok{1000}\NormalTok{), }
        \DataTypeTok{verbose =}\NormalTok{ F)))}
\end{Highlighting}
\end{Shaded}

\hypertarget{re-structuring-the-data-for-each-grouping-term}{%
\subsubsection{Re-structuring the data for each grouping
term}\label{re-structuring-the-data-for-each-grouping-term}}

Here we delete unused variables, and select the respective effect sizes.
Please note - the referencing of the cells does NOT depend on previous
ordering of the data. This would only be affected if the output
structure from metafor::rma.uni changes.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Function will take the averall results and extract the relevant trait of}
\CommentTok{# interest}
\NormalTok{extract_trait <-}\StringTok{ }\ControlFlowTok{function}\NormalTok{(data, trait) \{}
\NormalTok{    tmp <-}\StringTok{ }\NormalTok{data }\OperatorTok{%>%}\StringTok{ }\KeywordTok{filter}\NormalTok{(., GroupingTerm }\OperatorTok{==}\StringTok{ }\NormalTok{trait) }\OperatorTok{%>%}\StringTok{ }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{lnCVR =}\NormalTok{ .[[}\DecValTok{4}\NormalTok{]][[}\DecValTok{1}\NormalTok{]]}\OperatorTok{$}\NormalTok{b, }
        \DataTypeTok{lnCVR_lower =}\NormalTok{ .[[}\DecValTok{4}\NormalTok{]][[}\DecValTok{1}\NormalTok{]]}\OperatorTok{$}\NormalTok{ci.lb, }\DataTypeTok{lnCVR_upper =}\NormalTok{ .[[}\DecValTok{4}\NormalTok{]][[}\DecValTok{1}\NormalTok{]]}\OperatorTok{$}\NormalTok{ci.ub, }\DataTypeTok{lnCVR_se =}\NormalTok{ .[[}\DecValTok{4}\NormalTok{]][[}\DecValTok{1}\NormalTok{]]}\OperatorTok{$}\NormalTok{se, }
        \DataTypeTok{lnCVR_I2 =}\NormalTok{ .[[}\DecValTok{4}\NormalTok{]][[}\DecValTok{1}\NormalTok{]]}\OperatorTok{$}\NormalTok{I2, }\DataTypeTok{lnVR =}\NormalTok{ .[[}\DecValTok{5}\NormalTok{]][[}\DecValTok{1}\NormalTok{]]}\OperatorTok{$}\NormalTok{b, }\DataTypeTok{lnVR_lower =}\NormalTok{ .[[}\DecValTok{5}\NormalTok{]][[}\DecValTok{1}\NormalTok{]]}\OperatorTok{$}\NormalTok{ci.lb, }
        \DataTypeTok{lnVR_upper =}\NormalTok{ .[[}\DecValTok{5}\NormalTok{]][[}\DecValTok{1}\NormalTok{]]}\OperatorTok{$}\NormalTok{ci.ub, }\DataTypeTok{lnVR_se =}\NormalTok{ .[[}\DecValTok{5}\NormalTok{]][[}\DecValTok{1}\NormalTok{]]}\OperatorTok{$}\NormalTok{se, }\DataTypeTok{lnVR_I2 =}\NormalTok{ .[[}\DecValTok{5}\NormalTok{]][[}\DecValTok{1}\NormalTok{]]}\OperatorTok{$}\NormalTok{I2, }
        \DataTypeTok{lnRR =}\NormalTok{ .[[}\DecValTok{6}\NormalTok{]][[}\DecValTok{1}\NormalTok{]]}\OperatorTok{$}\NormalTok{b, }\DataTypeTok{lnRR_lower =}\NormalTok{ .[[}\DecValTok{6}\NormalTok{]][[}\DecValTok{1}\NormalTok{]]}\OperatorTok{$}\NormalTok{ci.lb, }\DataTypeTok{lnRR_upper =}\NormalTok{ .[[}\DecValTok{6}\NormalTok{]][[}\DecValTok{1}\NormalTok{]]}\OperatorTok{$}\NormalTok{ci.ub, }
        \DataTypeTok{lnRR_se =}\NormalTok{ .[[}\DecValTok{6}\NormalTok{]][[}\DecValTok{1}\NormalTok{]]}\OperatorTok{$}\NormalTok{se, }\DataTypeTok{lnRR_I2 =}\NormalTok{ .[[}\DecValTok{6}\NormalTok{]][[}\DecValTok{1}\NormalTok{]]}\OperatorTok{$}\NormalTok{I2) }\OperatorTok{%>%}\StringTok{ }\KeywordTok{select}\NormalTok{(., GroupingTerm, }
\NormalTok{        lnCVR}\OperatorTok{:}\NormalTok{lnRR_I2)}

    \KeywordTok{return}\NormalTok{(tmp)}
\NormalTok{\}}

\NormalTok{All <-}\StringTok{ }\NormalTok{overall_all1 }\OperatorTok{%>%}\StringTok{ }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{lnCVR =}\NormalTok{ .[[}\DecValTok{2}\NormalTok{]][[}\DecValTok{1}\NormalTok{]]}\OperatorTok{$}\NormalTok{b, }\DataTypeTok{lnCVR_lower =}\NormalTok{ .[[}\DecValTok{2}\NormalTok{]][[}\DecValTok{1}\NormalTok{]]}\OperatorTok{$}\NormalTok{ci.lb, }
    \DataTypeTok{lnCVR_upper =}\NormalTok{ .[[}\DecValTok{2}\NormalTok{]][[}\DecValTok{1}\NormalTok{]]}\OperatorTok{$}\NormalTok{ci.ub, }\DataTypeTok{lnCVR_se =}\NormalTok{ .[[}\DecValTok{2}\NormalTok{]][[}\DecValTok{1}\NormalTok{]]}\OperatorTok{$}\NormalTok{se, }\DataTypeTok{lnCVR_I2 =}\NormalTok{ .[[}\DecValTok{2}\NormalTok{]][[}\DecValTok{1}\NormalTok{]]}\OperatorTok{$}\NormalTok{I2, }
    \DataTypeTok{lnVR =}\NormalTok{ .[[}\DecValTok{3}\NormalTok{]][[}\DecValTok{1}\NormalTok{]]}\OperatorTok{$}\NormalTok{b, }\DataTypeTok{lnVR_lower =}\NormalTok{ .[[}\DecValTok{3}\NormalTok{]][[}\DecValTok{1}\NormalTok{]]}\OperatorTok{$}\NormalTok{ci.lb, }\DataTypeTok{lnVR_upper =}\NormalTok{ .[[}\DecValTok{3}\NormalTok{]][[}\DecValTok{1}\NormalTok{]]}\OperatorTok{$}\NormalTok{ci.ub, }
    \DataTypeTok{lnVR_se =}\NormalTok{ .[[}\DecValTok{3}\NormalTok{]][[}\DecValTok{1}\NormalTok{]]}\OperatorTok{$}\NormalTok{se, }\DataTypeTok{lnVR_I2 =}\NormalTok{ .[[}\DecValTok{3}\NormalTok{]][[}\DecValTok{1}\NormalTok{]]}\OperatorTok{$}\NormalTok{I2, }\DataTypeTok{lnRR =}\NormalTok{ .[[}\DecValTok{4}\NormalTok{]][[}\DecValTok{1}\NormalTok{]]}\OperatorTok{$}\NormalTok{b, }\DataTypeTok{lnRR_lower =}\NormalTok{ .[[}\DecValTok{4}\NormalTok{]][[}\DecValTok{1}\NormalTok{]]}\OperatorTok{$}\NormalTok{ci.lb, }
    \DataTypeTok{lnRR_upper =}\NormalTok{ .[[}\DecValTok{4}\NormalTok{]][[}\DecValTok{1}\NormalTok{]]}\OperatorTok{$}\NormalTok{ci.ub, }\DataTypeTok{lnRR_se =}\NormalTok{ .[[}\DecValTok{4}\NormalTok{]][[}\DecValTok{1}\NormalTok{]]}\OperatorTok{$}\NormalTok{se, }\DataTypeTok{lnRR_I2 =}\NormalTok{ .[[}\DecValTok{4}\NormalTok{]][[}\DecValTok{1}\NormalTok{]]}\OperatorTok{$}\NormalTok{I2, }
\NormalTok{    ) }\OperatorTok{%>%}\StringTok{ }\KeywordTok{select}\NormalTok{(., lnCVR}\OperatorTok{:}\NormalTok{lnRR_I2)}

\NormalTok{All <-}\StringTok{ }\NormalTok{All }\OperatorTok{%>%}\StringTok{ }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{GroupingTerm =} \StringTok{"All"}\NormalTok{)}

\NormalTok{overall2 <-}\StringTok{ }\KeywordTok{bind_rows}\NormalTok{(}\KeywordTok{extract_trait}\NormalTok{(overall1, }\StringTok{"Behaviour"}\NormalTok{), }\KeywordTok{extract_trait}\NormalTok{(overall1, }
    \StringTok{"Morphology"}\NormalTok{), }\KeywordTok{extract_trait}\NormalTok{(overall1, }\StringTok{"Metabolism"}\NormalTok{), }\KeywordTok{extract_trait}\NormalTok{(overall1, }
    \StringTok{"Physiology"}\NormalTok{), }\KeywordTok{extract_trait}\NormalTok{(overall1, }\StringTok{"Immunology"}\NormalTok{), }\KeywordTok{extract_trait}\NormalTok{(overall1, }
    \StringTok{"Hematology"}\NormalTok{), }\KeywordTok{extract_trait}\NormalTok{(overall1, }\StringTok{"Heart"}\NormalTok{), }\KeywordTok{extract_trait}\NormalTok{(overall1, }\StringTok{"Hearing"}\NormalTok{), }
    \KeywordTok{extract_trait}\NormalTok{(overall1, }\StringTok{"Eye"}\NormalTok{), All)}
\end{Highlighting}
\end{Shaded}

\hypertarget{second-order-meta-analysis-of-heterogenity}{%
\subsection{Second-order meta-analysis of
heterogenity}\label{second-order-meta-analysis-of-heterogenity}}

The analysis for heterogeneity follows the workflow of the above steps
for the different meta-analyses and specifically Figure @ref(fig:FigG1)
I \& J. However, in the initial meta-analysis we extract sigma\^{}2 and
errors for mouse strains and centers (Institutions). As above a Loop is
run and parameters extracted from metafor (sigma2's, s.nlevels)

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{### Preparing heterogeneity}

\CommentTok{# Create dataframe to store results}
\NormalTok{results.allhetero.grouping <-}\StringTok{ }\KeywordTok{as.data.frame}\NormalTok{(}\KeywordTok{cbind}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\DecValTok{1}\OperatorTok{:}\NormalTok{n), }\KeywordTok{matrix}\NormalTok{(}\KeywordTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{, n }\OperatorTok{*}\StringTok{ }\DecValTok{30}\NormalTok{), }
    \DataTypeTok{ncol =} \DecValTok{30}\NormalTok{)))}
\KeywordTok{names}\NormalTok{(results.allhetero.grouping) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"sigma2_strain.CVR"}\NormalTok{, }\StringTok{"sigma2_center.CVR"}\NormalTok{, }
    \StringTok{"sigma2_error.CVR"}\NormalTok{, }\StringTok{"s.nlevels.strain.CVR"}\NormalTok{, }\StringTok{"s.nlevels.center.CVR"}\NormalTok{, }\StringTok{"s.nlevels.error.CVR"}\NormalTok{, }
    \StringTok{"sigma2_strain.VR"}\NormalTok{, }\StringTok{"sigma2_center.VR"}\NormalTok{, }\StringTok{"sigma2_error.VR"}\NormalTok{, }\StringTok{"s.nlevels.strain.VR"}\NormalTok{, }
    \StringTok{"s.nlevels.center.VR"}\NormalTok{, }\StringTok{"s.nlevels.error.VR"}\NormalTok{, }\StringTok{"sigma2_strain.RR"}\NormalTok{, }\StringTok{"sigma2_center.RR"}\NormalTok{, }
    \StringTok{"sigma2_error.RR"}\NormalTok{, }\StringTok{"s.nlevels.strain.RR"}\NormalTok{, }\StringTok{"s.nlevels.center.RR"}\NormalTok{, }\StringTok{"s.nlevels.error.RR"}\NormalTok{, }
    \StringTok{"lnCVR"}\NormalTok{, }\StringTok{"lnCVR_lower"}\NormalTok{, }\StringTok{"lnCVR_upper"}\NormalTok{, }\StringTok{"lnCVR_se"}\NormalTok{, }\StringTok{"lnVR"}\NormalTok{, }\StringTok{"lnVR_lower"}\NormalTok{, }\StringTok{"lnVR_upper"}\NormalTok{, }
    \StringTok{"lnVR_se"}\NormalTok{, }\StringTok{"lnRR"}\NormalTok{, }\StringTok{"lnRR_lower"}\NormalTok{, }\StringTok{"lnRR_upper"}\NormalTok{, }\StringTok{"lnRR_se"}\NormalTok{)}

\CommentTok{# Loop}

\ControlFlowTok{for}\NormalTok{ (t }\ControlFlowTok{in} \DecValTok{1}\OperatorTok{:}\NormalTok{n) \{}
    \KeywordTok{tryCatch}\NormalTok{(\{}
\NormalTok{        results <-}\StringTok{ }\NormalTok{data }\OperatorTok{%>%}\StringTok{ }\KeywordTok{data_subset_parameterid_individual_by_age}\NormalTok{(t) }\OperatorTok{%>%}\StringTok{ }\KeywordTok{calculate_population_stats}\NormalTok{() }\OperatorTok{%>%}\StringTok{ }
\StringTok{            }\KeywordTok{create_meta_analysis_effect_sizes}\NormalTok{() }\OperatorTok{%>%}\StringTok{ }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{err =} \KeywordTok{seq_len}\NormalTok{(}\KeywordTok{n}\NormalTok{()))}

        \CommentTok{# lnCVR, logaritm of the ratio of male and female coefficients of variance}

\NormalTok{        cvr. <-}\StringTok{ }\NormalTok{metafor}\OperatorTok{::}\KeywordTok{rma.mv}\NormalTok{(}\DataTypeTok{yi =}\NormalTok{ effect_size_CVR, }\DataTypeTok{V =}\NormalTok{ sample_variance_CVR, }\DataTypeTok{random =} \KeywordTok{list}\NormalTok{(}\OperatorTok{~}\DecValTok{1} \OperatorTok{|}\StringTok{ }
\StringTok{            }\NormalTok{strain_name, }\OperatorTok{~}\DecValTok{1} \OperatorTok{|}\StringTok{ }\NormalTok{production_center, }\OperatorTok{~}\DecValTok{1} \OperatorTok{|}\StringTok{ }\NormalTok{err), }\DataTypeTok{control =} \KeywordTok{list}\NormalTok{(}\DataTypeTok{optimizer =} \StringTok{"optim"}\NormalTok{, }
            \DataTypeTok{optmethod =} \StringTok{"Nelder-Mead"}\NormalTok{, }\DataTypeTok{maxit =} \DecValTok{1000}\NormalTok{), }\DataTypeTok{data =}\NormalTok{ results)}

\NormalTok{        results.allhetero.grouping[t, }\DecValTok{2}\NormalTok{] <-}\StringTok{ }\NormalTok{cvr.}\OperatorTok{$}\NormalTok{sigma2[}\DecValTok{1}\NormalTok{]}
\NormalTok{        results.allhetero.grouping[t, }\DecValTok{3}\NormalTok{] <-}\StringTok{ }\NormalTok{cvr.}\OperatorTok{$}\NormalTok{sigma2[}\DecValTok{2}\NormalTok{]}
\NormalTok{        results.allhetero.grouping[t, }\DecValTok{4}\NormalTok{] <-}\StringTok{ }\NormalTok{cvr.}\OperatorTok{$}\NormalTok{sigma2[}\DecValTok{3}\NormalTok{]}
\NormalTok{        results.allhetero.grouping[t, }\DecValTok{5}\NormalTok{] <-}\StringTok{ }\NormalTok{cvr.}\OperatorTok{$}\NormalTok{s.nlevels[}\DecValTok{1}\NormalTok{]}
\NormalTok{        results.allhetero.grouping[t, }\DecValTok{6}\NormalTok{] <-}\StringTok{ }\NormalTok{cvr.}\OperatorTok{$}\NormalTok{s.nlevels[}\DecValTok{2}\NormalTok{]}
\NormalTok{        results.allhetero.grouping[t, }\DecValTok{7}\NormalTok{] <-}\StringTok{ }\NormalTok{cvr.}\OperatorTok{$}\NormalTok{s.nlevels[}\DecValTok{3}\NormalTok{]}
\NormalTok{        results.allhetero.grouping[t, }\DecValTok{20}\NormalTok{] <-}\StringTok{ }\NormalTok{cvr.}\OperatorTok{$}\NormalTok{b}
\NormalTok{        results.allhetero.grouping[t, }\DecValTok{21}\NormalTok{] <-}\StringTok{ }\NormalTok{cvr.}\OperatorTok{$}\NormalTok{ci.lb}
\NormalTok{        results.allhetero.grouping[t, }\DecValTok{22}\NormalTok{] <-}\StringTok{ }\NormalTok{cvr.}\OperatorTok{$}\NormalTok{ci.ub}
\NormalTok{        results.allhetero.grouping[t, }\DecValTok{23}\NormalTok{] <-}\StringTok{ }\NormalTok{cvr.}\OperatorTok{$}\NormalTok{se}

        \CommentTok{# lnVR, male to female variability ratio (logarithm of male and female standard}
        \CommentTok{# deviations)}

\NormalTok{        vr. <-}\StringTok{ }\NormalTok{metafor}\OperatorTok{::}\KeywordTok{rma.mv}\NormalTok{(}\DataTypeTok{yi =}\NormalTok{ effect_size_VR, }\DataTypeTok{V =}\NormalTok{ sample_variance_VR, }\DataTypeTok{random =} \KeywordTok{list}\NormalTok{(}\OperatorTok{~}\DecValTok{1} \OperatorTok{|}\StringTok{ }
\StringTok{            }\NormalTok{strain_name, }\OperatorTok{~}\DecValTok{1} \OperatorTok{|}\StringTok{ }\NormalTok{production_center, }\OperatorTok{~}\DecValTok{1} \OperatorTok{|}\StringTok{ }\NormalTok{err), }\DataTypeTok{control =} \KeywordTok{list}\NormalTok{(}\DataTypeTok{optimizer =} \StringTok{"optim"}\NormalTok{, }
            \DataTypeTok{optmethod =} \StringTok{"Nelder-Mead"}\NormalTok{, }\DataTypeTok{maxit =} \DecValTok{1000}\NormalTok{), }\DataTypeTok{data =}\NormalTok{ results)}

\NormalTok{        results.allhetero.grouping[t, }\DecValTok{8}\NormalTok{] <-}\StringTok{ }\NormalTok{vr.}\OperatorTok{$}\NormalTok{sigma2[}\DecValTok{1}\NormalTok{]}
\NormalTok{        results.allhetero.grouping[t, }\DecValTok{9}\NormalTok{] <-}\StringTok{ }\NormalTok{vr.}\OperatorTok{$}\NormalTok{sigma2[}\DecValTok{2}\NormalTok{]}
\NormalTok{        results.allhetero.grouping[t, }\DecValTok{10}\NormalTok{] <-}\StringTok{ }\NormalTok{vr.}\OperatorTok{$}\NormalTok{sigma2[}\DecValTok{3}\NormalTok{]}
\NormalTok{        results.allhetero.grouping[t, }\DecValTok{11}\NormalTok{] <-}\StringTok{ }\NormalTok{vr.}\OperatorTok{$}\NormalTok{s.nlevels[}\DecValTok{1}\NormalTok{]}
\NormalTok{        results.allhetero.grouping[t, }\DecValTok{12}\NormalTok{] <-}\StringTok{ }\NormalTok{vr.}\OperatorTok{$}\NormalTok{s.nlevels[}\DecValTok{2}\NormalTok{]}
\NormalTok{        results.allhetero.grouping[t, }\DecValTok{13}\NormalTok{] <-}\StringTok{ }\NormalTok{vr.}\OperatorTok{$}\NormalTok{s.nlevels[}\DecValTok{3}\NormalTok{]}
\NormalTok{        results.allhetero.grouping[t, }\DecValTok{24}\NormalTok{] <-}\StringTok{ }\NormalTok{vr.}\OperatorTok{$}\NormalTok{b}
\NormalTok{        results.allhetero.grouping[t, }\DecValTok{25}\NormalTok{] <-}\StringTok{ }\NormalTok{vr.}\OperatorTok{$}\NormalTok{ci.lb}
\NormalTok{        results.allhetero.grouping[t, }\DecValTok{26}\NormalTok{] <-}\StringTok{ }\NormalTok{vr.}\OperatorTok{$}\NormalTok{ci.ub}
\NormalTok{        results.allhetero.grouping[t, }\DecValTok{27}\NormalTok{] <-}\StringTok{ }\NormalTok{vr.}\OperatorTok{$}\NormalTok{se}

        \CommentTok{# lnRR, response ratio (logarithm of male and female means)}

\NormalTok{        rr. <-}\StringTok{ }\NormalTok{metafor}\OperatorTok{::}\KeywordTok{rma.mv}\NormalTok{(}\DataTypeTok{yi =}\NormalTok{ effect_size_ROM, }\DataTypeTok{V =}\NormalTok{ sample_variance_ROM, }\DataTypeTok{random =} \KeywordTok{list}\NormalTok{(}\OperatorTok{~}\DecValTok{1} \OperatorTok{|}\StringTok{ }
\StringTok{            }\NormalTok{strain_name, }\OperatorTok{~}\DecValTok{1} \OperatorTok{|}\StringTok{ }\NormalTok{production_center, }\OperatorTok{~}\DecValTok{1} \OperatorTok{|}\StringTok{ }\NormalTok{err), }\DataTypeTok{control =} \KeywordTok{list}\NormalTok{(}\DataTypeTok{optimizer =} \StringTok{"optim"}\NormalTok{, }
            \DataTypeTok{optmethod =} \StringTok{"Nelder-Mead"}\NormalTok{, }\DataTypeTok{maxit =} \DecValTok{1000}\NormalTok{), }\DataTypeTok{data =}\NormalTok{ results)}

\NormalTok{        results.allhetero.grouping[t, }\DecValTok{14}\NormalTok{] <-}\StringTok{ }\NormalTok{rr.}\OperatorTok{$}\NormalTok{sigma2[}\DecValTok{1}\NormalTok{]}
\NormalTok{        results.allhetero.grouping[t, }\DecValTok{15}\NormalTok{] <-}\StringTok{ }\NormalTok{rr.}\OperatorTok{$}\NormalTok{sigma2[}\DecValTok{2}\NormalTok{]}
\NormalTok{        results.allhetero.grouping[t, }\DecValTok{16}\NormalTok{] <-}\StringTok{ }\NormalTok{rr.}\OperatorTok{$}\NormalTok{sigma2[}\DecValTok{3}\NormalTok{]}
\NormalTok{        results.allhetero.grouping[t, }\DecValTok{17}\NormalTok{] <-}\StringTok{ }\NormalTok{rr.}\OperatorTok{$}\NormalTok{s.nlevels[}\DecValTok{1}\NormalTok{]}
\NormalTok{        results.allhetero.grouping[t, }\DecValTok{18}\NormalTok{] <-}\StringTok{ }\NormalTok{rr.}\OperatorTok{$}\NormalTok{s.nlevels[}\DecValTok{2}\NormalTok{]}
\NormalTok{        results.allhetero.grouping[t, }\DecValTok{19}\NormalTok{] <-}\StringTok{ }\NormalTok{rr.}\OperatorTok{$}\NormalTok{s.nlevels[}\DecValTok{3}\NormalTok{]}
\NormalTok{        results.allhetero.grouping[t, }\DecValTok{28}\NormalTok{] <-}\StringTok{ }\NormalTok{rr.}\OperatorTok{$}\NormalTok{b}
\NormalTok{        results.allhetero.grouping[t, }\DecValTok{29}\NormalTok{] <-}\StringTok{ }\NormalTok{rr.}\OperatorTok{$}\NormalTok{ci.lb}
\NormalTok{        results.allhetero.grouping[t, }\DecValTok{30}\NormalTok{] <-}\StringTok{ }\NormalTok{rr.}\OperatorTok{$}\NormalTok{ci.ub}
\NormalTok{        results.allhetero.grouping[t, }\DecValTok{31}\NormalTok{] <-}\StringTok{ }\NormalTok{rr.}\OperatorTok{$}\NormalTok{se}
\NormalTok{    \}, }\DataTypeTok{error =} \ControlFlowTok{function}\NormalTok{(e) \{}
        \KeywordTok{cat}\NormalTok{(}\StringTok{"ERROR :"}\NormalTok{, }\KeywordTok{conditionMessage}\NormalTok{(e), }\StringTok{"}\CharTok{\textbackslash{}n}\StringTok{"}\NormalTok{)}
\NormalTok{    \})}
\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## ERROR : Optimizer (optim) did not achieve convergence (convergence = 10). 
## ERROR : Processing terminated since k <= 1. 
## ERROR : Processing terminated since k <= 1.
\end{verbatim}

Here we exclude traits without variation between mouse strains and merge
data sets containing metafor results with procedure etc. names. Dealing
with the correlated parameters, and running the second -order
meta-analysis for heterogeneity data (Figure @ref(fig:FigG1) I)

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{              results.allhetero.grouping2 <-}\StringTok{ }\NormalTok{results.allhetero.grouping[results.allhetero.grouping}\OperatorTok{$}\NormalTok{s.nlevels.strain.VR }\OperatorTok{!=}\StringTok{ }\DecValTok{0}\NormalTok{, ]}
\CommentTok{# nrow(results.allhetero.grouping) #232  }

\CommentTok{# Merging dataset with correct procedure names}
\CommentTok{# procedures <- read.csv(here("export", "procedures.csv"))}

\NormalTok{results.allhetero.grouping2}\OperatorTok{$}\NormalTok{parameter_group <-}\StringTok{ }\NormalTok{data}\OperatorTok{$}\NormalTok{parameter_group[}\KeywordTok{match}\NormalTok{(results.allhetero.grouping2}\OperatorTok{$}\NormalTok{id, data}\OperatorTok{$}\NormalTok{id)]}
\NormalTok{      results.allhetero.grouping2}\OperatorTok{$}\NormalTok{procedure <-}\StringTok{ }\NormalTok{data}\OperatorTok{$}\NormalTok{procedure_name[}\KeywordTok{match}\NormalTok{(results.allhetero.grouping2}\OperatorTok{$}\NormalTok{id, data}\OperatorTok{$}\NormalTok{id)]}

\NormalTok{   results.allhetero.grouping2}\OperatorTok{$}\NormalTok{GroupingTerm <-}\StringTok{ }\NormalTok{procedures}\OperatorTok{$}\NormalTok{GroupingTerm[}\KeywordTok{match}\NormalTok{(results.allhetero.grouping2}\OperatorTok{$}\NormalTok{procedure, procedures}\OperatorTok{$}\NormalTok{procedure)]}
\NormalTok{ results.allhetero.grouping2}\OperatorTok{$}\NormalTok{parameter_name <-}\StringTok{ }\NormalTok{data}\OperatorTok{$}\NormalTok{parameter_name[}\KeywordTok{match}\NormalTok{(results.allhetero.grouping2}\OperatorTok{$}\NormalTok{id, data}\OperatorTok{$}\NormalTok{id)]}

\CommentTok{#We deal with correlated parameters following the procedures described above (extraction of effects sizes).}

\NormalTok{metahetero1 <-}\StringTok{ }\NormalTok{results.allhetero.grouping2}
\CommentTok{# length(unique(metahetero1$procedure)) #19}
\CommentTok{# length(unique(metahetero1$GroupingTerm)) #9 }
\CommentTok{# length(unique(metahetero1$parameter_group)) #152}
\CommentTok{# length(unique(metahetero1$parameter_name)) #223}

\CommentTok{# Count of number of parameter names (correlated sub-traits) in each parameter group (par_group_size)}

\NormalTok{metahetero1b <-}\StringTok{ }\NormalTok{metahetero1                    }\OperatorTok{%>%}
\StringTok{                }\KeywordTok{group_by}\NormalTok{(parameter_group)      }\OperatorTok{%>%}
\StringTok{                }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{par_group_size =} \KeywordTok{n_distinct}\NormalTok{(parameter_name))}

\NormalTok{metahetero1}\OperatorTok{$}\NormalTok{par_group_size <-}\StringTok{ }\NormalTok{metahetero1b}\OperatorTok{$}\NormalTok{par_group_size[}\KeywordTok{match}\NormalTok{(metahetero1}\OperatorTok{$}\NormalTok{parameter_group, metahetero1b}\OperatorTok{$}\NormalTok{parameter_group)]}

\CommentTok{# Create subsets with > 1 count (par_group_size > 1)}

\NormalTok{metahetero1_sub <-}\StringTok{ }\KeywordTok{subset}\NormalTok{(metahetero1, par_group_size }\OperatorTok{>}\StringTok{ }\DecValTok{1}\NormalTok{) }\CommentTok{# 92 observations}

\CommentTok{# Nest data}

\NormalTok{n_count. <-}\StringTok{ }\NormalTok{metahetero1_sub }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{group_by}\NormalTok{(parameter_group) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{nest}\NormalTok{()}

\CommentTok{# meta-analysis preparation}

\NormalTok{model_count. <-}\StringTok{ }\NormalTok{n_count. }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}
    \DataTypeTok{model_lnRR =} \KeywordTok{map}\NormalTok{(data, }\OperatorTok{~}\StringTok{ }\KeywordTok{robu}\NormalTok{(.x}\OperatorTok{$}\NormalTok{lnRR }\OperatorTok{~}\StringTok{ }\DecValTok{1}\NormalTok{,}
      \DataTypeTok{data =}\NormalTok{ .x, }\DataTypeTok{studynum =}\NormalTok{ .x}\OperatorTok{$}\NormalTok{id, }\DataTypeTok{modelweights =} \KeywordTok{c}\NormalTok{(}\StringTok{"CORR"}\NormalTok{), }\DataTypeTok{rho =} \FloatTok{0.8}\NormalTok{,}
      \DataTypeTok{small =} \OtherTok{TRUE}\NormalTok{, }\DataTypeTok{var.eff.size =}\NormalTok{ (.x}\OperatorTok{$}\NormalTok{lnRR_se)}\OperatorTok{^}\DecValTok{2}
\NormalTok{    )),}
    \DataTypeTok{model_lnVR =} \KeywordTok{map}\NormalTok{(data, }\OperatorTok{~}\StringTok{ }\KeywordTok{robu}\NormalTok{(.x}\OperatorTok{$}\NormalTok{lnVR }\OperatorTok{~}\StringTok{ }\DecValTok{1}\NormalTok{,}
      \DataTypeTok{data =}\NormalTok{ .x, }\DataTypeTok{studynum =}\NormalTok{ .x}\OperatorTok{$}\NormalTok{id, }\DataTypeTok{modelweights =} \KeywordTok{c}\NormalTok{(}\StringTok{"CORR"}\NormalTok{), }\DataTypeTok{rho =} \FloatTok{0.8}\NormalTok{,}
      \DataTypeTok{small =} \OtherTok{TRUE}\NormalTok{, }\DataTypeTok{var.eff.size =}\NormalTok{ (.x}\OperatorTok{$}\NormalTok{lnVR_se)}\OperatorTok{^}\DecValTok{2}
\NormalTok{    )),}
    \DataTypeTok{model_lnCVR =} \KeywordTok{map}\NormalTok{(data, }\OperatorTok{~}\StringTok{ }\KeywordTok{robu}\NormalTok{(.x}\OperatorTok{$}\NormalTok{lnCVR }\OperatorTok{~}\StringTok{ }\DecValTok{1}\NormalTok{,}
      \DataTypeTok{data =}\NormalTok{ .x, }\DataTypeTok{studynum =}\NormalTok{ .x}\OperatorTok{$}\NormalTok{id, }\DataTypeTok{modelweights =} \KeywordTok{c}\NormalTok{(}\StringTok{"CORR"}\NormalTok{), }\DataTypeTok{rho =} \FloatTok{0.8}\NormalTok{,}
      \DataTypeTok{small =} \OtherTok{TRUE}\NormalTok{, }\DataTypeTok{var.eff.size =}\NormalTok{ (.x}\OperatorTok{$}\NormalTok{lnCVR_se)}\OperatorTok{^}\DecValTok{2}
\NormalTok{    ))}
\NormalTok{  )}

\CommentTok{# Robumeta object details:  str(model_count.$model_lnCVR[[1]])}

\CommentTok{# Perform meta-analyses on correlated sub-traits, using robumeta}
\CommentTok{# Extract and save parameter estimates}

\NormalTok{count_fun. <-}\StringTok{ }\ControlFlowTok{function}\NormalTok{(mod_sub) \{}
  \KeywordTok{return}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\KeywordTok{as.numeric}\NormalTok{(mod_sub}\OperatorTok{$}\NormalTok{mod_info}\OperatorTok{$}\NormalTok{term1), mod_sub}\OperatorTok{$}\NormalTok{N))}
\NormalTok{\}}

\NormalTok{robusub_RR. <-}\StringTok{ }\NormalTok{model_count. }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{transmute}\NormalTok{(}\DataTypeTok{estimatelnRR =} \KeywordTok{map}\NormalTok{(model_lnRR, count_fun.)) }\OperatorTok{%>%}\StringTok{    }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{r =} \KeywordTok{map}\NormalTok{(estimatelnRR, }\OperatorTok{~}\StringTok{ }\KeywordTok{data.frame}\NormalTok{(}\KeywordTok{t}\NormalTok{(.)))) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{unnest}\NormalTok{(r) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{select}\NormalTok{(}\OperatorTok{-}\NormalTok{estimatelnRR) }\OperatorTok{%>%}
\StringTok{  }\NormalTok{purrr}\OperatorTok{::}\KeywordTok{set_names}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"parameter_group"}\NormalTok{, }\StringTok{"var.RR"}\NormalTok{, }\StringTok{"N.RR"}\NormalTok{))}

\NormalTok{robusub_CVR. <-}\StringTok{ }\NormalTok{model_count. }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{transmute}\NormalTok{(}\DataTypeTok{estimatelnCVR =} \KeywordTok{map}\NormalTok{(model_lnCVR, count_fun.)) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{r =} \KeywordTok{map}\NormalTok{(estimatelnCVR, }\OperatorTok{~}\StringTok{ }\KeywordTok{data.frame}\NormalTok{(}\KeywordTok{t}\NormalTok{(.)))) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{unnest}\NormalTok{(r) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{select}\NormalTok{(}\OperatorTok{-}\NormalTok{estimatelnCVR) }\OperatorTok{%>%}
\StringTok{  }\NormalTok{purrr}\OperatorTok{::}\KeywordTok{set_names}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"parameter_group"}\NormalTok{, }\StringTok{"var.CVR"}\NormalTok{, }\StringTok{"N.CVR"}\NormalTok{))}

\NormalTok{robusub_VR. <-}\StringTok{ }\NormalTok{model_count. }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{transmute}\NormalTok{(}\DataTypeTok{estimatelnVR =} \KeywordTok{map}\NormalTok{(model_lnVR, count_fun.)) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{r =} \KeywordTok{map}\NormalTok{(estimatelnVR, }\OperatorTok{~}\StringTok{ }\KeywordTok{data.frame}\NormalTok{(}\KeywordTok{t}\NormalTok{(.)))) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{unnest}\NormalTok{(r) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{select}\NormalTok{(}\OperatorTok{-}\NormalTok{estimatelnVR) }\OperatorTok{%>%}
\StringTok{  }\NormalTok{purrr}\OperatorTok{::}\KeywordTok{set_names}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"parameter_group"}\NormalTok{, }\StringTok{"var.VR"}\NormalTok{, }\StringTok{"N.VR"}\NormalTok{))}

\NormalTok{robu_all. <-}\StringTok{ }\KeywordTok{full_join}\NormalTok{(robusub_CVR., robusub_VR.) }\OperatorTok{%>%}\StringTok{ }\KeywordTok{full_join}\NormalTok{(., robusub_RR.)}

\CommentTok{#Merge the two data sets (the new [robu_all.] and the initial [uncorrelated sub-traits with count = 1])}

\CommentTok{#In this step, we   1) merge the N from robumeta and the  N from metafor (s.nlevels.error) together into the same columns (N.RR, N.VR, N.CVR)}

\CommentTok{# 2) calculate the total variance for metafor models as the sum of random effect variances and the residual error, then add in the same columns together with the residual variances from robumeta }

\NormalTok{metahetero_all <-}\StringTok{ }\NormalTok{metahetero1 }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{filter}\NormalTok{(par_group_size }\OperatorTok{==}\StringTok{ }\DecValTok{1}\NormalTok{) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{as_tibble}\NormalTok{()}
\NormalTok{metahetero_all}\OperatorTok{$}\NormalTok{N.RR <-}\StringTok{ }\NormalTok{metahetero_all}\OperatorTok{$}\NormalTok{s.nlevels.error.RR}
\NormalTok{metahetero_all}\OperatorTok{$}\NormalTok{N.CVR <-}\StringTok{ }\NormalTok{metahetero_all}\OperatorTok{$}\NormalTok{s.nlevels.error.CVR}
\NormalTok{metahetero_all}\OperatorTok{$}\NormalTok{N.VR <-}\StringTok{ }\NormalTok{metahetero_all}\OperatorTok{$}\NormalTok{s.nlevels.error.VR}
\NormalTok{metahetero_all}\OperatorTok{$}\NormalTok{var.RR <-}\StringTok{ }\KeywordTok{log}\NormalTok{(}\KeywordTok{sqrt}\NormalTok{(metahetero_all}\OperatorTok{$}\NormalTok{sigma2_strain.RR }\OperatorTok{+}\StringTok{ }\NormalTok{metahetero_all}\OperatorTok{$}\NormalTok{sigma2_center.RR }\OperatorTok{+}\StringTok{ }\NormalTok{metahetero_all}\OperatorTok{$}\NormalTok{sigma2_error.RR))}
\NormalTok{metahetero_all}\OperatorTok{$}\NormalTok{var.VR <-}\StringTok{ }\KeywordTok{log}\NormalTok{(}\KeywordTok{sqrt}\NormalTok{(metahetero_all}\OperatorTok{$}\NormalTok{sigma2_strain.VR }\OperatorTok{+}\StringTok{ }\NormalTok{metahetero_all}\OperatorTok{$}\NormalTok{sigma2_center.VR }\OperatorTok{+}\StringTok{ }\NormalTok{metahetero_all}\OperatorTok{$}\NormalTok{sigma2_error.VR))}
\NormalTok{metahetero_all}\OperatorTok{$}\NormalTok{var.CVR <-}\StringTok{ }\KeywordTok{log}\NormalTok{(}\KeywordTok{sqrt}\NormalTok{(metahetero_all}\OperatorTok{$}\NormalTok{sigma2_strain.CVR }\OperatorTok{+}\StringTok{ }\NormalTok{metahetero_all}\OperatorTok{$}\NormalTok{sigma2_center.CVR }\OperatorTok{+}\StringTok{ }\NormalTok{metahetero_all}\OperatorTok{$}\NormalTok{sigma2_error.CVR))}
\CommentTok{# str(metahetero_all)}
\CommentTok{# str(robu_all.)}

\NormalTok{metahetero_all <-}\StringTok{ }\NormalTok{metahetero_all }\OperatorTok{%>%}\StringTok{ }\KeywordTok{mutate}\NormalTok{(}
  \DataTypeTok{var.RR =} \KeywordTok{if_else}\NormalTok{(var.RR }\OperatorTok{==}\StringTok{ }\OperatorTok{-}\OtherTok{Inf}\NormalTok{, }\DecValTok{-7}\NormalTok{, var.RR),   }\CommentTok{# numbers chosen as limits; based on the values in the dataset}
  \DataTypeTok{var.VR =} \KeywordTok{if_else}\NormalTok{(var.VR }\OperatorTok{==}\StringTok{ }\OperatorTok{-}\OtherTok{Inf}\NormalTok{, }\DecValTok{-5}\NormalTok{, var.VR),}
  \DataTypeTok{var.CVR =} \KeywordTok{if_else}\NormalTok{(var.CVR }\OperatorTok{==}\StringTok{ }\OperatorTok{-}\OtherTok{Inf}\NormalTok{, }\DecValTok{-6}\NormalTok{, var.CVR)}
\NormalTok{)}

\CommentTok{# Combine data}
\CommentTok{# Step1}

\NormalTok{combinedmetahetero <-}\StringTok{ }\KeywordTok{bind_rows}\NormalTok{(robu_all., metahetero_all)}
\CommentTok{# glimpse(combinedmetahetero)}

\CommentTok{# Steps 2&3}

\NormalTok{              metacombohetero <-}\StringTok{ }\NormalTok{combinedmetahetero}
\NormalTok{       metacombohetero}\OperatorTok{$}\NormalTok{counts <-}\StringTok{ }\NormalTok{metahetero1}\OperatorTok{$}\NormalTok{par_group_size[}\KeywordTok{match}\NormalTok{(metacombohetero}\OperatorTok{$}\NormalTok{parameter_group, metahetero1}\OperatorTok{$}\NormalTok{parameter_group)]}
\NormalTok{   metacombohetero}\OperatorTok{$}\NormalTok{procedure2 <-}\StringTok{ }\NormalTok{metahetero1}\OperatorTok{$}\NormalTok{procedure[}\KeywordTok{match}\NormalTok{(metacombohetero}\OperatorTok{$}\NormalTok{parameter_group, metahetero1}\OperatorTok{$}\NormalTok{parameter_group)]}
\NormalTok{metacombohetero}\OperatorTok{$}\NormalTok{GroupingTerm2 <-}\StringTok{ }\NormalTok{metahetero1}\OperatorTok{$}\NormalTok{GroupingTerm[}\KeywordTok{match}\NormalTok{(metacombohetero}\OperatorTok{$}\NormalTok{parameter_group, metahetero1}\OperatorTok{$}\NormalTok{parameter_group)]}

\CommentTok{# **Clean-up and rename}

\NormalTok{metacombohetero <-}\StringTok{ }\NormalTok{metacombohetero }\OperatorTok{%>%}\StringTok{ }\KeywordTok{select}\NormalTok{(parameter_group, var.CVR, N.CVR, var.VR, N.VR, var.RR, N.RR, counts, }\DataTypeTok{procedure =}\NormalTok{ procedure2, }\DataTypeTok{GroupingTerm =}\NormalTok{ GroupingTerm2)  }

\CommentTok{# Invidual table for heterogeneity across all traits}
\CommentTok{# kable(metacombohetero,, digits = 3) %>%}
 \CommentTok{# kable_styling() %>%}
  \CommentTok{#scroll_box(width = "100%", height = "200px")}

\CommentTok{#### Meta-analysis of heterogeneity}

\CommentTok{## Perform meta-meta-analysis (3 for each of the 9 grouping terms: var.CVR, var.VR, var.RR)}

\NormalTok{metacombohetero_final <-}\StringTok{ }\NormalTok{metacombohetero }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{group_by}\NormalTok{(GroupingTerm) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{nest}\NormalTok{()}

\CommentTok{# Final fixed effects meta-analyses within grouping terms, with SE of the estimate}

\NormalTok{heterog1 <-}\StringTok{ }\NormalTok{metacombohetero_final }\OperatorTok{%>%}

\StringTok{  }\KeywordTok{mutate}\NormalTok{(}
    \DataTypeTok{model_heteroCVR =} \KeywordTok{map}\NormalTok{(data, }\OperatorTok{~}\StringTok{ }\NormalTok{metafor}\OperatorTok{::}\KeywordTok{rma.uni}\NormalTok{(}
      \DataTypeTok{yi =}\NormalTok{ .x}\OperatorTok{$}\NormalTok{var.CVR, }\DataTypeTok{sei =} \KeywordTok{sqrt}\NormalTok{(}\DecValTok{1} \OperatorTok{/}\StringTok{ }\DecValTok{2} \OperatorTok{*}\StringTok{ }\NormalTok{(.x}\OperatorTok{$}\NormalTok{N.CVR }\OperatorTok{-}\StringTok{ }\DecValTok{1}\NormalTok{)),}
      \DataTypeTok{control =} \KeywordTok{list}\NormalTok{(}\DataTypeTok{optimizer =} \StringTok{"optim"}\NormalTok{, }
                     \DataTypeTok{optmethod =} \StringTok{"Nelder-Mead"}\NormalTok{,}
                     \DataTypeTok{maxit =} \DecValTok{10000}\NormalTok{, }
                     \DataTypeTok{stepadj =} \FloatTok{0.5}\NormalTok{), }\DataTypeTok{verbose =}\NormalTok{ F)),}
    \DataTypeTok{model_heteroVR =} \KeywordTok{map}\NormalTok{(data, }\OperatorTok{~}\StringTok{ }\NormalTok{metafor}\OperatorTok{::}\KeywordTok{rma.uni}\NormalTok{(}
      \DataTypeTok{yi =}\NormalTok{ .x}\OperatorTok{$}\NormalTok{var.VR, }\DataTypeTok{sei =} \KeywordTok{sqrt}\NormalTok{(}\DecValTok{1} \OperatorTok{/}\StringTok{ }\DecValTok{2} \OperatorTok{*}\StringTok{ }\NormalTok{(.x}\OperatorTok{$}\NormalTok{N.VR }\OperatorTok{-}\StringTok{ }\DecValTok{1}\NormalTok{)),}
      \DataTypeTok{control =} \KeywordTok{list}\NormalTok{(}\DataTypeTok{optimizer =} \StringTok{"optim"}\NormalTok{, }
                     \DataTypeTok{optmethod =} \StringTok{"Nelder-Mead"}\NormalTok{, }
                     \DataTypeTok{maxit =} \DecValTok{10000}\NormalTok{, }
                     \DataTypeTok{stepadj =} \FloatTok{0.5}\NormalTok{), }\DataTypeTok{verbose =}\NormalTok{ F)),}
    \DataTypeTok{model_heteroRR =} \KeywordTok{map}\NormalTok{(data, }\OperatorTok{~}\StringTok{ }\NormalTok{metafor}\OperatorTok{::}\KeywordTok{rma.uni}\NormalTok{(}
      \DataTypeTok{yi =}\NormalTok{ .x}\OperatorTok{$}\NormalTok{var.RR, }\DataTypeTok{sei =} \KeywordTok{sqrt}\NormalTok{(}\DecValTok{1} \OperatorTok{/}\StringTok{ }\DecValTok{2} \OperatorTok{*}\StringTok{ }\NormalTok{(.x}\OperatorTok{$}\NormalTok{N.RR }\OperatorTok{-}\StringTok{ }\DecValTok{1}\NormalTok{)),}
      \DataTypeTok{control =} \KeywordTok{list}\NormalTok{(}\DataTypeTok{optimizer =} \StringTok{"optim"}\NormalTok{, }
                     \DataTypeTok{optmethod =} \StringTok{"Nelder-Mead"}\NormalTok{, }
                     \DataTypeTok{maxit =} \DecValTok{10000}\NormalTok{, }
                     \DataTypeTok{stepadj =} \FloatTok{0.5}\NormalTok{), }\DataTypeTok{verbose =}\NormalTok{ F)) )}

\CommentTok{# Across all grouping terms   }

\NormalTok{metacombohetero_all_final <-}\StringTok{ }\NormalTok{metacombohetero }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{nest}\NormalTok{(}\DataTypeTok{data =} \KeywordTok{everything}\NormalTok{()) }

\CommentTok{# Final fixed effects meta-analyses ACROSS grouping terms, with SE of the estimate}

\NormalTok{heterog1_all <-}\StringTok{ }\NormalTok{metacombohetero_all_final }\OperatorTok{%>%}
\StringTok{  }
\StringTok{  }\KeywordTok{mutate}\NormalTok{( }\DataTypeTok{model_heteroCVR =} \KeywordTok{map}\NormalTok{(data, }\OperatorTok{~}\StringTok{ }\NormalTok{metafor}\OperatorTok{::}\KeywordTok{rma.uni}\NormalTok{(}
      \DataTypeTok{yi =}\NormalTok{ .x}\OperatorTok{$}\NormalTok{var.CVR, }\DataTypeTok{sei =} \KeywordTok{sqrt}\NormalTok{(}\DecValTok{1} \OperatorTok{/}\StringTok{ }\DecValTok{2} \OperatorTok{*}\StringTok{ }\NormalTok{(.x}\OperatorTok{$}\NormalTok{N.CVR }\OperatorTok{-}\StringTok{ }\DecValTok{1}\NormalTok{)),}
      \DataTypeTok{control =} \KeywordTok{list}\NormalTok{(}\DataTypeTok{optimizer =} \StringTok{"optim"}\NormalTok{, }
                     \DataTypeTok{optmethod =} \StringTok{"Nelder-Mead"}\NormalTok{, }
                     \DataTypeTok{maxit =} \DecValTok{10000}\NormalTok{, }
                     \DataTypeTok{stepadj =} \FloatTok{0.5}\NormalTok{), }\DataTypeTok{verbose =}\NormalTok{ F)),}
    \DataTypeTok{model_heteroVR =} \KeywordTok{map}\NormalTok{(data, }\OperatorTok{~}\StringTok{ }\NormalTok{metafor}\OperatorTok{::}\KeywordTok{rma.uni}\NormalTok{(}\DataTypeTok{yi =}\NormalTok{ .x}\OperatorTok{$}\NormalTok{var.VR, }\DataTypeTok{sei =} \KeywordTok{sqrt}\NormalTok{(}\DecValTok{1} \OperatorTok{/}\StringTok{ }\DecValTok{2} \OperatorTok{*}\StringTok{ }\NormalTok{(.x}\OperatorTok{$}\NormalTok{N.VR }\OperatorTok{-}\StringTok{ }\DecValTok{1}\NormalTok{)),}
      \DataTypeTok{control =} \KeywordTok{list}\NormalTok{(}\DataTypeTok{optimizer =} \StringTok{"optim"}\NormalTok{, }
                     \DataTypeTok{optmethod =} \StringTok{"Nelder-Mead"}\NormalTok{, }
                     \DataTypeTok{maxit =} \DecValTok{10000}\NormalTok{, }
                     \DataTypeTok{stepadj =} \FloatTok{0.5}\NormalTok{), }\DataTypeTok{verbose =}\NormalTok{ F)),}
    \DataTypeTok{model_heteroRR =} \KeywordTok{map}\NormalTok{(data, }\OperatorTok{~}\StringTok{ }\NormalTok{metafor}\OperatorTok{::}\KeywordTok{rma.uni}\NormalTok{(}\DataTypeTok{yi =}\NormalTok{ .x}\OperatorTok{$}\NormalTok{var.RR, }\DataTypeTok{sei =} \KeywordTok{sqrt}\NormalTok{(}\DecValTok{1} \OperatorTok{/}\StringTok{ }\DecValTok{2} \OperatorTok{*}\StringTok{ }\NormalTok{(.x}\OperatorTok{$}\NormalTok{N.RR }\OperatorTok{-}\StringTok{ }\DecValTok{1}\NormalTok{)),}
      \DataTypeTok{control =} \KeywordTok{list}\NormalTok{(}\DataTypeTok{optimizer =} \StringTok{"optim"}\NormalTok{, }
                     \DataTypeTok{optmethod =} \StringTok{"Nelder-Mead"}\NormalTok{, }
                     \DataTypeTok{maxit =} \DecValTok{10000}\NormalTok{, }
                     \DataTypeTok{stepadj =} \FloatTok{0.5}\NormalTok{), }\DataTypeTok{verbose =}\NormalTok{ F)))}

\CommentTok{# Re-structure data for each grouping term; extract heterogenenity/variance terms; delete un-used variables}

\NormalTok{extract_heterogeneity <-}\StringTok{ }\ControlFlowTok{function}\NormalTok{(data, type)\{}

\NormalTok{  tmp <-}\StringTok{ }\NormalTok{data }\OperatorTok{%>%}
\StringTok{         }\KeywordTok{filter}\NormalTok{(., GroupingTerm }\OperatorTok{==}\StringTok{ }\NormalTok{type) }\OperatorTok{%>%}
\StringTok{         }\KeywordTok{select}\NormalTok{(., }\OperatorTok{-}\NormalTok{data) }\OperatorTok{%>%}
\StringTok{         }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{heteroCVR       =}\NormalTok{ .[[}\DecValTok{2}\NormalTok{]][[}\DecValTok{1}\NormalTok{]]}\OperatorTok{$}\NormalTok{b, }
                \DataTypeTok{heteroCVR_lower =}\NormalTok{ .[[}\DecValTok{2}\NormalTok{]][[}\DecValTok{1}\NormalTok{]]}\OperatorTok{$}\NormalTok{ci.lb, }
                \DataTypeTok{heteroCVR_upper =}\NormalTok{ .[[}\DecValTok{2}\NormalTok{]][[}\DecValTok{1}\NormalTok{]]}\OperatorTok{$}\NormalTok{ci.ub, }
                \DataTypeTok{heteroCVR_se    =}\NormalTok{ .[[}\DecValTok{2}\NormalTok{]][[}\DecValTok{1}\NormalTok{]]}\OperatorTok{$}\NormalTok{se,}
                \DataTypeTok{heteroVR        =}\NormalTok{ .[[}\DecValTok{3}\NormalTok{]][[}\DecValTok{1}\NormalTok{]]}\OperatorTok{$}\NormalTok{b, }
                \DataTypeTok{heteroVR_lower  =}\NormalTok{ .[[}\DecValTok{3}\NormalTok{]][[}\DecValTok{1}\NormalTok{]]}\OperatorTok{$}\NormalTok{ci.lb, }
                \DataTypeTok{heteroVR_upper  =}\NormalTok{ .[[}\DecValTok{3}\NormalTok{]][[}\DecValTok{1}\NormalTok{]]}\OperatorTok{$}\NormalTok{ci.ub, }
                \DataTypeTok{heteroVR_se     =}\NormalTok{ .[[}\DecValTok{3}\NormalTok{]][[}\DecValTok{1}\NormalTok{]]}\OperatorTok{$}\NormalTok{se,}
                \DataTypeTok{heteroRR        =}\NormalTok{ .[[}\DecValTok{4}\NormalTok{]][[}\DecValTok{1}\NormalTok{]]}\OperatorTok{$}\NormalTok{b, }
                \DataTypeTok{heteroRR_lower  =}\NormalTok{ .[[}\DecValTok{4}\NormalTok{]][[}\DecValTok{1}\NormalTok{]]}\OperatorTok{$}\NormalTok{ci.lb, }
                \DataTypeTok{heteroRR_upper  =}\NormalTok{ .[[}\DecValTok{4}\NormalTok{]][[}\DecValTok{1}\NormalTok{]]}\OperatorTok{$}\NormalTok{ci.ub, }
                \DataTypeTok{heteroRR_se     =}\NormalTok{ .[[}\DecValTok{4}\NormalTok{]][[}\DecValTok{1}\NormalTok{]]}\OperatorTok{$}\NormalTok{se) }\OperatorTok{%>%}
\StringTok{        }\KeywordTok{select}\NormalTok{(., GroupingTerm, heteroCVR}\OperatorTok{:}\NormalTok{heteroRR_se)}

  \KeywordTok{return}\NormalTok{(tmp)}
\NormalTok{\}}

\NormalTok{   Behaviour. <-}\StringTok{ }\KeywordTok{extract_heterogeneity}\NormalTok{(heterog1, }\DataTypeTok{type =} \StringTok{"Behaviour"}\NormalTok{)}
\NormalTok{  Immunology. <-}\StringTok{ }\KeywordTok{extract_heterogeneity}\NormalTok{(heterog1, }\DataTypeTok{type =} \StringTok{"Immunology"}\NormalTok{)}
\NormalTok{  Hematology. <-}\StringTok{ }\KeywordTok{extract_heterogeneity}\NormalTok{(heterog1, }\DataTypeTok{type =} \StringTok{"Hematology"}\NormalTok{)}
\NormalTok{     Hearing. <-}\StringTok{ }\KeywordTok{extract_heterogeneity}\NormalTok{(heterog1, }\DataTypeTok{type =} \StringTok{"Hearing"}\NormalTok{)}
\NormalTok{  Physiology. <-}\StringTok{ }\KeywordTok{extract_heterogeneity}\NormalTok{(heterog1, }\DataTypeTok{type =} \StringTok{"Physiology"}\NormalTok{)}
\NormalTok{  Metabolism. <-}\StringTok{ }\KeywordTok{extract_heterogeneity}\NormalTok{(heterog1, }\DataTypeTok{type =} \StringTok{"Metabolism"}\NormalTok{)}
\NormalTok{  Morphology. <-}\StringTok{ }\KeywordTok{extract_heterogeneity}\NormalTok{(heterog1, }\DataTypeTok{type =} \StringTok{"Morphology"}\NormalTok{)}
\NormalTok{       Heart. <-}\StringTok{ }\KeywordTok{extract_heterogeneity}\NormalTok{(heterog1, }\DataTypeTok{type =} \StringTok{"Heart"}\NormalTok{)}
\NormalTok{         Eye. <-}\StringTok{ }\KeywordTok{extract_heterogeneity}\NormalTok{(heterog1, }\DataTypeTok{type =} \StringTok{"Eye"}\NormalTok{)}

\CommentTok{#Reorder to be able to keep cell referencing }
\NormalTok{heterog1_all <-}\StringTok{ }\NormalTok{heterog1_all }\OperatorTok{%>%}\StringTok{ }
\StringTok{                }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{GroupingTerm =} \StringTok{"All"}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{                }\KeywordTok{select}\NormalTok{(GroupingTerm, }\KeywordTok{everything}\NormalTok{())}

\NormalTok{All. <-}\StringTok{ }\NormalTok{heterog1_all }\OperatorTok{%>%}\StringTok{ }
\StringTok{        }\KeywordTok{select}\NormalTok{(., }\OperatorTok{-}\NormalTok{data) }\OperatorTok{%>%}
\StringTok{        }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{heteroCVR       =}\NormalTok{ .[[}\DecValTok{2}\NormalTok{]][[}\DecValTok{1}\NormalTok{]]}\OperatorTok{$}\NormalTok{b, }
               \DataTypeTok{heteroCVR_lower =}\NormalTok{ .[[}\DecValTok{2}\NormalTok{]][[}\DecValTok{1}\NormalTok{]]}\OperatorTok{$}\NormalTok{ci.lb, }
               \DataTypeTok{heteroCVR_upper =}\NormalTok{ .[[}\DecValTok{2}\NormalTok{]][[}\DecValTok{1}\NormalTok{]]}\OperatorTok{$}\NormalTok{ci.ub, }
               \DataTypeTok{heteroCVR_se    =}\NormalTok{ .[[}\DecValTok{2}\NormalTok{]][[}\DecValTok{1}\NormalTok{]]}\OperatorTok{$}\NormalTok{se, }
               \DataTypeTok{heteroVR        =}\NormalTok{ .[[}\DecValTok{3}\NormalTok{]][[}\DecValTok{1}\NormalTok{]]}\OperatorTok{$}\NormalTok{b, }
               \DataTypeTok{heteroVR_lower  =}\NormalTok{ .[[}\DecValTok{3}\NormalTok{]][[}\DecValTok{1}\NormalTok{]]}\OperatorTok{$}\NormalTok{ci.lb, }
               \DataTypeTok{heteroVR_upper  =}\NormalTok{ .[[}\DecValTok{3}\NormalTok{]][[}\DecValTok{1}\NormalTok{]]}\OperatorTok{$}\NormalTok{ci.ub, }
               \DataTypeTok{heteroVR_se     =}\NormalTok{ .[[}\DecValTok{3}\NormalTok{]][[}\DecValTok{1}\NormalTok{]]}\OperatorTok{$}\NormalTok{se, }
               \DataTypeTok{heteroRR        =}\NormalTok{ .[[}\DecValTok{4}\NormalTok{]][[}\DecValTok{1}\NormalTok{]]}\OperatorTok{$}\NormalTok{b, }
               \DataTypeTok{heteroRR_lower  =}\NormalTok{ .[[}\DecValTok{4}\NormalTok{]][[}\DecValTok{1}\NormalTok{]]}\OperatorTok{$}\NormalTok{ci.lb, }
               \DataTypeTok{heteroRR_upper  =}\NormalTok{ .[[}\DecValTok{4}\NormalTok{]][[}\DecValTok{1}\NormalTok{]]}\OperatorTok{$}\NormalTok{ci.ub, }
               \DataTypeTok{heteroRR_se     =}\NormalTok{ .[[}\DecValTok{4}\NormalTok{]][[}\DecValTok{1}\NormalTok{]]}\OperatorTok{$}\NormalTok{se) }\OperatorTok{%>%}
\StringTok{        }\KeywordTok{select}\NormalTok{(., GroupingTerm, heteroCVR}\OperatorTok{:}\NormalTok{heteroRR_se)}

\NormalTok{heterog2 <-}\StringTok{ }\KeywordTok{bind_rows}\NormalTok{(Behaviour., Morphology., Metabolism., Physiology., Immunology., Hematology., Heart., Hearing., Eye., All.)}

\CommentTok{#### Preparation of the Heterogeneity PLOT}

\CommentTok{#Restructure data for plotting}

\NormalTok{heterog3 <-}\StringTok{ }\KeywordTok{gather}\NormalTok{(heterog2, parameter, value, }\KeywordTok{c}\NormalTok{(heteroCVR, heteroVR, heteroRR), }\DataTypeTok{factor_key =} \OtherTok{TRUE}\NormalTok{)}

\NormalTok{heteroCVR.ci <-}\StringTok{ }\NormalTok{heterog3 }\OperatorTok{%>%}
\StringTok{                }\KeywordTok{filter}\NormalTok{(parameter }\OperatorTok{==}\StringTok{ "heteroCVR"}\NormalTok{) }\OperatorTok{%>%}
\StringTok{                }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{ci.low =}\NormalTok{ heteroCVR_lower, }
                       \DataTypeTok{ci.high =}\NormalTok{ heteroCVR_upper)}
\NormalTok{heteroVR.ci <-}\StringTok{  }\NormalTok{heterog3 }\OperatorTok{%>%}
\StringTok{                }\KeywordTok{filter}\NormalTok{(parameter }\OperatorTok{==}\StringTok{ "heteroVR"}\NormalTok{) }\OperatorTok{%>%}
\StringTok{                }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{ci.low =}\NormalTok{ heteroVR_lower, }
                       \DataTypeTok{ci.high =}\NormalTok{ heteroVR_upper)}
\NormalTok{heteroRR.ci <-}\StringTok{  }\NormalTok{heterog3 }\OperatorTok{%>%}
\StringTok{                }\KeywordTok{filter}\NormalTok{(parameter }\OperatorTok{==}\StringTok{ "heteroRR"}\NormalTok{) }\OperatorTok{%>%}
\StringTok{                }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{ci.low =}\NormalTok{ heteroRR_lower, }
                       \DataTypeTok{ci.high =}\NormalTok{ heteroRR_upper)}

\NormalTok{heterog4 <-}\StringTok{ }\KeywordTok{bind_rows}\NormalTok{(heteroCVR.ci, heteroVR.ci, heteroRR.ci) }\OperatorTok{%>%}\StringTok{ }\KeywordTok{select}\NormalTok{(GroupingTerm, parameter, value, ci.low, ci.high)}

\CommentTok{# **Re-order grouping terms}

\NormalTok{heterog4}\OperatorTok{$}\NormalTok{GroupingTerm <-}\StringTok{ }\KeywordTok{factor}\NormalTok{(heterog4}\OperatorTok{$}\NormalTok{GroupingTerm, }
                                \DataTypeTok{levels =} \KeywordTok{c}\NormalTok{(}\StringTok{"Behaviour"}\NormalTok{, }\StringTok{"Morphology"}\NormalTok{, }\StringTok{"Metabolism"}\NormalTok{, }
                                           \StringTok{"Physiology"}\NormalTok{, }\StringTok{"Immunology"}\NormalTok{, }\StringTok{"Hematology"}\NormalTok{, }\StringTok{"Heart"}\NormalTok{, }
                                           \StringTok{"Hearing"}\NormalTok{, }\StringTok{"Eye"}\NormalTok{, }\StringTok{"All"}\NormalTok{))}

\NormalTok{heterog4}\OperatorTok{$}\NormalTok{GroupingTerm <-}\StringTok{ }\KeywordTok{factor}\NormalTok{(heterog4}\OperatorTok{$}\NormalTok{GroupingTerm, }
                                \KeywordTok{rev}\NormalTok{(}\KeywordTok{levels}\NormalTok{(heterog4}\OperatorTok{$}\NormalTok{GroupingTerm)))}
\NormalTok{heterog4}\OperatorTok{$}\NormalTok{label <-}\StringTok{ "All traits"}
\CommentTok{# write.csv(heterog4, "heterog4.csv")}

\CommentTok{#### Plot S1 C (Second-order meta analysis on heterogeneity)}

\NormalTok{heterog5 <-}\StringTok{ }\NormalTok{heterog4}
\NormalTok{heterog5}\OperatorTok{$}\NormalTok{mean <-}\StringTok{ }\KeywordTok{as.numeric}\NormalTok{(}\KeywordTok{exp}\NormalTok{(heterog5}\OperatorTok{$}\NormalTok{value))}
\NormalTok{heterog5}\OperatorTok{$}\NormalTok{ci.l <-}\StringTok{ }\KeywordTok{as.numeric}\NormalTok{(}\KeywordTok{exp}\NormalTok{(heterog5}\OperatorTok{$}\NormalTok{ci.low))}
\NormalTok{heterog5}\OperatorTok{$}\NormalTok{ci.h <-}\StringTok{ }\KeywordTok{as.numeric}\NormalTok{(}\KeywordTok{exp}\NormalTok{(heterog5}\OperatorTok{$}\NormalTok{ci.high))}

\NormalTok{heterog6 <-}\StringTok{ }\NormalTok{heterog5}

\NormalTok{HeteroS1 <-}
\StringTok{  }\NormalTok{heterog6 }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{ggplot}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{y =}\NormalTok{ GroupingTerm, }\DataTypeTok{x =}\NormalTok{ mean)) }\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_errorbarh}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}
    \DataTypeTok{xmin =}\NormalTok{ ci.l,}
    \DataTypeTok{xmax =}\NormalTok{ ci.h}
\NormalTok{  ),}
  \DataTypeTok{height =} \FloatTok{0.1}\NormalTok{, }\DataTypeTok{show.legend =} \OtherTok{FALSE}
\NormalTok{  ) }\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_point}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{shape =}\NormalTok{ parameter),}
    \DataTypeTok{fill =} \StringTok{"black"}\NormalTok{,}
    \DataTypeTok{color =} \StringTok{"black"}\NormalTok{, }\DataTypeTok{size =} \FloatTok{2.2}\NormalTok{,}
    \DataTypeTok{show.legend =} \OtherTok{FALSE}
\NormalTok{  ) }\OperatorTok{+}
\StringTok{  }\KeywordTok{scale_x_continuous}\NormalTok{(}
    \DataTypeTok{limits =} \KeywordTok{c}\NormalTok{(}\OperatorTok{-}\FloatTok{0.1}\NormalTok{, }\FloatTok{1.4}\NormalTok{),}
    \CommentTok{# breaks = c(0, 0.1, 0.2),}
    \DataTypeTok{name =} \StringTok{"sigma^2"}
\NormalTok{  ) }\OperatorTok{+}
\StringTok{  }\CommentTok{# geom_vline(xintercept=0,}
\StringTok{  }\CommentTok{# color='black',}
\StringTok{  }\CommentTok{# linetype='dashed')+}
\StringTok{  }\KeywordTok{facet_grid}\NormalTok{(}
    \DataTypeTok{cols =} \KeywordTok{vars}\NormalTok{(parameter), }\DataTypeTok{rows =} \KeywordTok{vars}\NormalTok{(label),}
    \DataTypeTok{labeller =} \KeywordTok{label_wrap_gen}\NormalTok{(}\DataTypeTok{width =} \DecValTok{23}\NormalTok{),}
    \DataTypeTok{scales =} \StringTok{"free"}\NormalTok{,}
    \DataTypeTok{space =} \StringTok{"free"}
\NormalTok{  ) }\OperatorTok{+}
\StringTok{  }\KeywordTok{theme_bw}\NormalTok{() }\OperatorTok{+}
\StringTok{  }\KeywordTok{theme}\NormalTok{(}
    \DataTypeTok{strip.text.y =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{angle =} \DecValTok{270}\NormalTok{, }\DataTypeTok{size =} \DecValTok{10}\NormalTok{, }\DataTypeTok{margin =} \KeywordTok{margin}\NormalTok{(}\DataTypeTok{t =} \DecValTok{15}\NormalTok{, }\DataTypeTok{r =} \DecValTok{15}\NormalTok{, }\DataTypeTok{b =} \DecValTok{15}\NormalTok{, }\DataTypeTok{l =} \DecValTok{15}\NormalTok{)),}
    \DataTypeTok{strip.text.x =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{size =} \DecValTok{12}\NormalTok{),}
    \DataTypeTok{strip.background =} \KeywordTok{element_rect}\NormalTok{(}\DataTypeTok{colour =} \OtherTok{NULL}\NormalTok{, }\DataTypeTok{linetype =} \StringTok{"blank"}\NormalTok{, }\DataTypeTok{fill =} \StringTok{"gray90"}\NormalTok{),}
    \DataTypeTok{text =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{size =} \DecValTok{14}\NormalTok{),}
    \DataTypeTok{panel.spacing =} \KeywordTok{unit}\NormalTok{(}\FloatTok{0.5}\NormalTok{, }\StringTok{"lines"}\NormalTok{),}
    \DataTypeTok{panel.border =} \KeywordTok{element_blank}\NormalTok{(),}
    \DataTypeTok{axis.line =} \KeywordTok{element_line}\NormalTok{(),}
    \DataTypeTok{panel.grid.major.x =} \KeywordTok{element_line}\NormalTok{(}\DataTypeTok{linetype =} \StringTok{"solid"}\NormalTok{, }\DataTypeTok{colour =} \StringTok{"gray95"}\NormalTok{),}
    \DataTypeTok{panel.grid.major.y =} \KeywordTok{element_line}\NormalTok{(}\DataTypeTok{linetype =} \StringTok{"solid"}\NormalTok{, }\DataTypeTok{color =} \StringTok{"gray95"}\NormalTok{),}
    \DataTypeTok{panel.grid.minor.y =} \KeywordTok{element_blank}\NormalTok{(),}
    \DataTypeTok{panel.grid.minor.x =} \KeywordTok{element_blank}\NormalTok{(),}
    \DataTypeTok{legend.title =} \KeywordTok{element_blank}\NormalTok{(),}
    \DataTypeTok{axis.title.x =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{hjust =} \FloatTok{0.5}\NormalTok{, }\DataTypeTok{size =} \DecValTok{14}\NormalTok{),}
    \DataTypeTok{axis.title.y =} \KeywordTok{element_blank}\NormalTok{())}
\end{Highlighting}
\end{Shaded}

\hypertarget{meta-analysis-results}{%
\section{Meta-analysis results}\label{meta-analysis-results}}

\hypertarget{preparation-for-figure-4}{%
\subsection{Preparation for Figure 4}\label{preparation-for-figure-4}}

\hypertarget{count-data-based-on-first-order-meta-analysis-results}{%
\subsubsection{Count data, based on First-order meta-analysis
results}\label{count-data-based-on-first-order-meta-analysis-results}}

This includes all separate eligible traits. Re-ordering of grouping
terms. Preparation of subplot 4A

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{meta_clean}\OperatorTok{$}\NormalTok{GroupingTerm <-}\StringTok{ }\KeywordTok{factor}\NormalTok{(meta_clean}\OperatorTok{$}\NormalTok{GroupingTerm, }
                                  \DataTypeTok{levels =} \KeywordTok{c}\NormalTok{(}\StringTok{"Behaviour"}\NormalTok{, }\StringTok{"Morphology"}\NormalTok{, }\StringTok{"Metabolism"}\NormalTok{, }\StringTok{"Physiology"}\NormalTok{, }\StringTok{"Immunology"}\NormalTok{, }\StringTok{"Hematology"}\NormalTok{, }\StringTok{"Heart"}\NormalTok{, }\StringTok{"Hearing"}\NormalTok{, }\StringTok{"Eye"}\NormalTok{))}
\NormalTok{meta_clean}\OperatorTok{$}\NormalTok{GroupingTerm <-}\StringTok{ }\KeywordTok{factor}\NormalTok{(meta_clean}\OperatorTok{$}\NormalTok{GroupingTerm, }
                                  \KeywordTok{rev}\NormalTok{(}\KeywordTok{levels}\NormalTok{(meta_clean}\OperatorTok{$}\NormalTok{GroupingTerm)))}

\CommentTok{# *Preparing data for all traits}

\NormalTok{meta.plot2.all <-}\StringTok{ }\NormalTok{meta_clean }\OperatorTok{%>%}
\StringTok{                  }\KeywordTok{select}\NormalTok{(lnCVR, lnVR, lnRR, GroupingTerm) }\OperatorTok{%>%}
\StringTok{                  }\KeywordTok{arrange}\NormalTok{(GroupingTerm)}

\CommentTok{# lnVR has been removed here and in the steps below, as this is only included in the supplemental figure}
\NormalTok{      meta.plot2.all.b <-}\StringTok{ }\KeywordTok{gather}\NormalTok{(meta.plot2.all, trait, value, }\KeywordTok{c}\NormalTok{(lnCVR, lnRR)) }

\NormalTok{meta.plot2.all.b}\OperatorTok{$}\NormalTok{trait <-}\StringTok{ }\KeywordTok{factor}\NormalTok{(meta.plot2.all.b}\OperatorTok{$}\NormalTok{trait, }\DataTypeTok{levels =} \KeywordTok{c}\NormalTok{(}\StringTok{"lnCVR"}\NormalTok{, }\StringTok{"lnRR"}\NormalTok{)) }
\NormalTok{      meta.plot2.all.c <-}\StringTok{ }\NormalTok{meta.plot2.all.b }\OperatorTok{%>%}
\StringTok{                          }\KeywordTok{group_by_at}\NormalTok{(}\KeywordTok{vars}\NormalTok{(trait, GroupingTerm)) }\OperatorTok{%>%}
\StringTok{                          }\KeywordTok{summarise}\NormalTok{(}
                            \DataTypeTok{malebias =} \KeywordTok{sum}\NormalTok{(value }\OperatorTok{>}\StringTok{ }\DecValTok{0}\NormalTok{), }\DataTypeTok{femalebias =} \KeywordTok{sum}\NormalTok{(value }\OperatorTok{<=}\StringTok{ }\DecValTok{0}\NormalTok{), }\DataTypeTok{total =}\NormalTok{ malebias }\OperatorTok{+}\StringTok{ }\NormalTok{femalebias,}
                            \DataTypeTok{malepercent =}\NormalTok{ malebias }\OperatorTok{*}\StringTok{ }\DecValTok{100} \OperatorTok{/}\StringTok{ }\NormalTok{total, }\DataTypeTok{femalepercent =}\NormalTok{ femalebias }\OperatorTok{*}\StringTok{ }\DecValTok{100} \OperatorTok{/}\StringTok{ }\NormalTok{total}
\NormalTok{                          )}

\NormalTok{meta.plot2.all.c}\OperatorTok{$}\NormalTok{label <-}\StringTok{ "All traits"}

\CommentTok{# Re-structure to create stacked bar plots}

\NormalTok{meta.plot2.all.d <-}\StringTok{ }\KeywordTok{as.data.frame}\NormalTok{(meta.plot2.all.c)}
\NormalTok{meta.plot2.all.e <-}\StringTok{ }\KeywordTok{gather}\NormalTok{(meta.plot2.all.d, }
                           \DataTypeTok{key =}\NormalTok{ sex, }
                           \DataTypeTok{value =}\NormalTok{ percent, }
\NormalTok{                           malepercent}\OperatorTok{:}\NormalTok{femalepercent, }
                           \DataTypeTok{factor_key =} \OtherTok{TRUE}\NormalTok{)}

\CommentTok{# Create new sample size variable}

\NormalTok{meta.plot2.all.e}\OperatorTok{$}\NormalTok{samplesize <-}\StringTok{ }\KeywordTok{with}\NormalTok{(meta.plot2.all.e, }
                                    \KeywordTok{ifelse}\NormalTok{(sex }\OperatorTok{==}\StringTok{ "malepercent"}\NormalTok{, }
\NormalTok{                                           malebias, }
\NormalTok{                                           femalebias))}

\CommentTok{# Add summary row ('All') and re-arrange rows into correct order for plotting (warnings about coercing 'id' into character vector are ok)}

\NormalTok{meta.plot2.all.f <-}\StringTok{ }\NormalTok{meta.plot2.all.e }\OperatorTok{%>%}\StringTok{ }
\StringTok{                    }\KeywordTok{group_by}\NormalTok{(trait, sex) }\OperatorTok{%>%}\StringTok{ }
\StringTok{                      }\KeywordTok{summarise}\NormalTok{(}\DataTypeTok{GroupingTerm =} \StringTok{"All"}\NormalTok{, }
                                \DataTypeTok{malebias =} \KeywordTok{sum}\NormalTok{(malebias),}
                                \DataTypeTok{femalebias =} \KeywordTok{sum}\NormalTok{(femalebias),}
                                \DataTypeTok{total =}\NormalTok{ malebias }\OperatorTok{+}\StringTok{ }\NormalTok{femalebias, }
                                \DataTypeTok{label =} \StringTok{"All traits"}\NormalTok{, }
                                \DataTypeTok{samplesize =} \KeywordTok{sum}\NormalTok{(samplesize)) }\OperatorTok{%>%}
\StringTok{                      }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{percent =} \KeywordTok{ifelse}\NormalTok{(sex }\OperatorTok{==}\StringTok{ "femalepercent"}\NormalTok{, femalebias}\OperatorTok{*}\DecValTok{100}\OperatorTok{/}\NormalTok{(malebias}\OperatorTok{+}\NormalTok{femalebias), malebias}\OperatorTok{*}\DecValTok{100}\OperatorTok{/}\NormalTok{(malebias}\OperatorTok{+}\NormalTok{femalebias))) }\OperatorTok{%>%}
\StringTok{                      }\KeywordTok{bind_rows}\NormalTok{(meta.plot2.all.e, .) }\OperatorTok{%>%}
\StringTok{                      }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{rownumber =} \KeywordTok{row_number}\NormalTok{()) }\OperatorTok{%>%}
\StringTok{                      }\NormalTok{.[}\KeywordTok{c}\NormalTok{(}\DecValTok{37}\NormalTok{, }\DecValTok{1}\OperatorTok{:}\DecValTok{9}\NormalTok{, }\DecValTok{39}\NormalTok{, }\DecValTok{10}\OperatorTok{:}\DecValTok{18}\NormalTok{, }\DecValTok{38}\NormalTok{, }\DecValTok{19}\OperatorTok{:}\DecValTok{27}\NormalTok{, }\DecValTok{40}\NormalTok{, }\DecValTok{28}\OperatorTok{:}\DecValTok{36}\NormalTok{), ] }
  \CommentTok{#line references in previous code line corresponding to: }
  \CommentTok{#'lnCVR(male(All)), lnCVR(male('single grouping terms'), lnRR(male(All)), lnRR(male('single grouping terms')),}
  \CommentTok{#lnCVR(female(All)), lnCVR(female('single grouping terms'), lnRR(female(All)), lnRR(female('single grouping terms'))'}

\NormalTok{meta.plot2.all.f}\OperatorTok{$}\NormalTok{GroupingTerm <-}\StringTok{ }\KeywordTok{factor}\NormalTok{(meta.plot2.all.f}\OperatorTok{$}\NormalTok{GroupingTerm,}
                                        \DataTypeTok{levels =} \KeywordTok{c}\NormalTok{(}\StringTok{"Behaviour"}\NormalTok{, }\StringTok{"Morphology"}\NormalTok{, }\StringTok{"Metabolism"}\NormalTok{, }\StringTok{"Physiology"}\NormalTok{, }\StringTok{"Immunology"}\NormalTok{, }\StringTok{"Hematology"}\NormalTok{, }\StringTok{"Heart"}\NormalTok{, }\StringTok{"Hearing"}\NormalTok{, }\StringTok{"Eye"}\NormalTok{, }\StringTok{"All"}\NormalTok{)) }
\NormalTok{meta.plot2.all.f}\OperatorTok{$}\NormalTok{GroupingTerm <-}\StringTok{ }\KeywordTok{factor}\NormalTok{(meta.plot2.all.f}\OperatorTok{$}\NormalTok{GroupingTerm, }
                                        \KeywordTok{rev}\NormalTok{(}\KeywordTok{levels}\NormalTok{(meta.plot2.all.f}\OperatorTok{$}\NormalTok{GroupingTerm)))}

\NormalTok{malebias_Fig2_alltraits <-}
\StringTok{    }\KeywordTok{ggplot}\NormalTok{(meta.plot2.all.f) }\OperatorTok{+}
\StringTok{    }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ GroupingTerm, }\DataTypeTok{y =}\NormalTok{ percent, }\DataTypeTok{fill =}\NormalTok{ sex) }\OperatorTok{+}
\StringTok{    }\KeywordTok{ylab}\NormalTok{(}\StringTok{"Percentage"}\NormalTok{) }\OperatorTok{+}
\StringTok{    }\KeywordTok{geom_col}\NormalTok{() }\OperatorTok{+}
\StringTok{    }\KeywordTok{geom_hline}\NormalTok{(}\DataTypeTok{yintercept =} \DecValTok{50}\NormalTok{, }\DataTypeTok{linetype =} \StringTok{"dashed"}\NormalTok{, }\DataTypeTok{color =} \StringTok{"gray40"}\NormalTok{) }\OperatorTok{+}
\StringTok{    }\KeywordTok{geom_text}\NormalTok{(}
      \DataTypeTok{data =} \KeywordTok{subset}\NormalTok{(meta.plot2.all.f, samplesize }\OperatorTok{!=}\StringTok{ }\DecValTok{0}\NormalTok{), }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{label =}\NormalTok{ samplesize), }\DataTypeTok{position =} \KeywordTok{position_stack}\NormalTok{(}\DataTypeTok{vjust =} \FloatTok{.5}\NormalTok{),}
      \DataTypeTok{color =} \StringTok{"white"}\NormalTok{, }\DataTypeTok{size =} \FloatTok{3.5}
\NormalTok{    ) }\OperatorTok{+}
\StringTok{    }\KeywordTok{facet_grid}\NormalTok{(}
      \DataTypeTok{cols =} \KeywordTok{vars}\NormalTok{(trait), }\DataTypeTok{rows =} \KeywordTok{vars}\NormalTok{(label), }\DataTypeTok{labeller =} \KeywordTok{label_wrap_gen}\NormalTok{(}\DataTypeTok{width =} \DecValTok{18}\NormalTok{),}
      \DataTypeTok{scales =} \StringTok{"free"}\NormalTok{, }\DataTypeTok{space =} \StringTok{"free"}
\NormalTok{    ) }\OperatorTok{+}\StringTok{  }
\StringTok{    }\KeywordTok{scale_fill_brewer}\NormalTok{(}\DataTypeTok{palette =} \StringTok{"Set2"}\NormalTok{) }\OperatorTok{+}
\StringTok{    }\KeywordTok{theme_bw}\NormalTok{(}\DataTypeTok{base_size =} \DecValTok{18}\NormalTok{) }\OperatorTok{+}
\StringTok{    }\KeywordTok{theme}\NormalTok{(}
      \DataTypeTok{strip.text.y =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{angle =} \DecValTok{270}\NormalTok{, }\DataTypeTok{size =} \DecValTok{10}\NormalTok{, }\DataTypeTok{margin =} \KeywordTok{margin}\NormalTok{(}\DataTypeTok{t =} \DecValTok{15}\NormalTok{, }\DataTypeTok{r =} \DecValTok{15}\NormalTok{, }\DataTypeTok{b =} \DecValTok{15}\NormalTok{, }\DataTypeTok{l =} \DecValTok{15}\NormalTok{)),}
      \DataTypeTok{strip.text.x =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{size =} \DecValTok{12}\NormalTok{),}
      \DataTypeTok{strip.background =} \KeywordTok{element_rect}\NormalTok{(}\DataTypeTok{colour =} \OtherTok{NULL}\NormalTok{, }\DataTypeTok{linetype =} \StringTok{"blank"}\NormalTok{, }\DataTypeTok{fill =} \StringTok{"gray90"}\NormalTok{),}
      \DataTypeTok{text =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{size =} \DecValTok{14}\NormalTok{),}
      \DataTypeTok{panel.spacing =} \KeywordTok{unit}\NormalTok{(}\FloatTok{0.5}\NormalTok{, }\StringTok{"lines"}\NormalTok{),}
      \DataTypeTok{panel.border =} \KeywordTok{element_blank}\NormalTok{(),}
      \DataTypeTok{axis.line =} \KeywordTok{element_line}\NormalTok{(),}
      \DataTypeTok{panel.grid.major.x =} \KeywordTok{element_line}\NormalTok{(}\DataTypeTok{linetype =} \StringTok{"solid"}\NormalTok{, }\DataTypeTok{colour =} \StringTok{"gray95"}\NormalTok{),}
      \DataTypeTok{panel.grid.major.y =} \KeywordTok{element_line}\NormalTok{(}\DataTypeTok{linetype =} \StringTok{"solid"}\NormalTok{, }\DataTypeTok{color =} \StringTok{"gray95"}\NormalTok{),}
      \DataTypeTok{panel.grid.minor.y =} \KeywordTok{element_blank}\NormalTok{(),}
      \DataTypeTok{panel.grid.minor.x =} \KeywordTok{element_blank}\NormalTok{(),}
      \DataTypeTok{legend.position=} \StringTok{"none"}\NormalTok{,}
      \CommentTok{#axis.title.x = Percentage,}
      \DataTypeTok{axis.title.y =} \KeywordTok{element_blank}\NormalTok{()}
\NormalTok{    ) }\OperatorTok{+}
\StringTok{    }\KeywordTok{coord_flip}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\hypertarget{re-structure-data-for-plotting}{%
\subsubsection{Re-structure data for
plotting}\label{re-structure-data-for-plotting}}

Data are re-structured, and grouping terms are being re-ordered

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{overall3 <-}\StringTok{ }\KeywordTok{gather}\NormalTok{(overall2, parameter, value, }\KeywordTok{c}\NormalTok{(lnCVR, lnRR), }\DataTypeTok{factor_key =} \OtherTok{TRUE}\NormalTok{)}

\NormalTok{lnCVR.ci <-}\StringTok{ }\NormalTok{overall3 }\OperatorTok{%>%}\StringTok{ }\KeywordTok{filter}\NormalTok{(parameter }\OperatorTok{==}\StringTok{ "lnCVR"}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{ci.low =}\NormalTok{ lnCVR_lower, }
    \DataTypeTok{ci.high =}\NormalTok{ lnCVR_upper)}
\NormalTok{lnVR.ci <-}\StringTok{ }\NormalTok{overall3 }\OperatorTok{%>%}\StringTok{ }\KeywordTok{filter}\NormalTok{(parameter }\OperatorTok{==}\StringTok{ "lnVR"}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{ci.low =}\NormalTok{ lnVR_lower, }
    \DataTypeTok{ci.high =}\NormalTok{ lnVR_upper)}
\NormalTok{lnRR.ci <-}\StringTok{ }\NormalTok{overall3 }\OperatorTok{%>%}\StringTok{ }\KeywordTok{filter}\NormalTok{(parameter }\OperatorTok{==}\StringTok{ "lnRR"}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{ci.low =}\NormalTok{ lnRR_lower, }
    \DataTypeTok{ci.high =}\NormalTok{ lnRR_upper)}

\NormalTok{overall4 <-}\StringTok{ }\KeywordTok{bind_rows}\NormalTok{(lnCVR.ci, lnRR.ci) }\OperatorTok{%>%}\StringTok{ }\KeywordTok{select}\NormalTok{(GroupingTerm, parameter, value, }
\NormalTok{    ci.low, ci.high)}

\CommentTok{# Re-order grouping terms}

\NormalTok{overall4}\OperatorTok{$}\NormalTok{GroupingTerm <-}\StringTok{ }\KeywordTok{factor}\NormalTok{(overall4}\OperatorTok{$}\NormalTok{GroupingTerm, }\DataTypeTok{levels =} \KeywordTok{c}\NormalTok{(}\StringTok{"Behaviour"}\NormalTok{, }\StringTok{"Morphology"}\NormalTok{, }
    \StringTok{"Metabolism"}\NormalTok{, }\StringTok{"Physiology"}\NormalTok{, }\StringTok{"Immunology"}\NormalTok{, }\StringTok{"Hematology"}\NormalTok{, }\StringTok{"Heart"}\NormalTok{, }\StringTok{"Hearing"}\NormalTok{, }\StringTok{"Eye"}\NormalTok{, }
    \StringTok{"All"}\NormalTok{))}
\NormalTok{overall4}\OperatorTok{$}\NormalTok{GroupingTerm <-}\StringTok{ }\KeywordTok{factor}\NormalTok{(overall4}\OperatorTok{$}\NormalTok{GroupingTerm, }\KeywordTok{rev}\NormalTok{(}\KeywordTok{levels}\NormalTok{(overall4}\OperatorTok{$}\NormalTok{GroupingTerm)))}
\NormalTok{overall4}\OperatorTok{$}\NormalTok{label <-}\StringTok{ "All traits"}

\CommentTok{#### PLOT 4B}

\CommentTok{# adding male / female symbols for Figure 4B additional packages for intergating}
\CommentTok{# male / female symbols in plot 4}
\KeywordTok{library}\NormalTok{(png)}
\KeywordTok{library}\NormalTok{(grid)}

\NormalTok{male <-}\StringTok{ }\KeywordTok{readPNG}\NormalTok{(}\KeywordTok{here}\NormalTok{(}\StringTok{"images"}\NormalTok{, }\StringTok{"MaleAqua.png"}\NormalTok{))}
\NormalTok{female <-}\StringTok{ }\KeywordTok{readPNG}\NormalTok{(}\KeywordTok{here}\NormalTok{(}\StringTok{"images"}\NormalTok{, }\StringTok{"FemaleSalmon.png"}\NormalTok{))}

\NormalTok{Metameta_Fig3_alltraits <-}\StringTok{ }\NormalTok{overall4 }\OperatorTok{%>%}\StringTok{ }
\KeywordTok{ggplot}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{y =}\NormalTok{ GroupingTerm, }\DataTypeTok{x =}\NormalTok{ value)) }\OperatorTok{+}\StringTok{ }\KeywordTok{geom_errorbarh}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{xmin =}\NormalTok{ ci.low, }\DataTypeTok{xmax =}\NormalTok{ ci.high), }
    \DataTypeTok{height =} \FloatTok{0.1}\NormalTok{, }\DataTypeTok{show.legend =} \OtherTok{FALSE}\NormalTok{) }\OperatorTok{+}\StringTok{ }\KeywordTok{geom_point}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{shape =}\NormalTok{ parameter), }\DataTypeTok{fill =} \StringTok{"black"}\NormalTok{, }
    \DataTypeTok{color =} \StringTok{"black"}\NormalTok{, }\DataTypeTok{size =} \FloatTok{2.2}\NormalTok{, }\DataTypeTok{show.legend =} \OtherTok{FALSE}\NormalTok{) }\OperatorTok{+}\StringTok{ }\KeywordTok{scale_x_continuous}\NormalTok{(}\DataTypeTok{limits =} \KeywordTok{c}\NormalTok{(}\OperatorTok{-}\FloatTok{0.24}\NormalTok{, }
    \FloatTok{0.25}\NormalTok{), }\DataTypeTok{breaks =} \KeywordTok{c}\NormalTok{(}\OperatorTok{-}\FloatTok{0.2}\NormalTok{, }\FloatTok{-0.1}\NormalTok{, }\DecValTok{0}\NormalTok{, }\FloatTok{0.1}\NormalTok{, }\FloatTok{0.2}\NormalTok{), }\DataTypeTok{name =} \StringTok{"Effect size"}\NormalTok{) }\OperatorTok{+}\StringTok{ }\KeywordTok{geom_vline}\NormalTok{(}\DataTypeTok{xintercept =} \DecValTok{0}\NormalTok{, }
    \DataTypeTok{color =} \StringTok{"black"}\NormalTok{, }\DataTypeTok{linetype =} \StringTok{"dashed"}\NormalTok{) }\OperatorTok{+}\StringTok{ }\KeywordTok{facet_grid}\NormalTok{(}\DataTypeTok{cols =} \KeywordTok{vars}\NormalTok{(parameter), }\DataTypeTok{rows =} \KeywordTok{vars}\NormalTok{(label), }
    \DataTypeTok{labeller =} \KeywordTok{label_wrap_gen}\NormalTok{(}\DataTypeTok{width =} \DecValTok{23}\NormalTok{), }\DataTypeTok{scales =} \StringTok{"free"}\NormalTok{, }\DataTypeTok{space =} \StringTok{"free"}\NormalTok{) }\OperatorTok{+}\StringTok{ }\KeywordTok{theme_bw}\NormalTok{() }\OperatorTok{+}\StringTok{ }
\StringTok{    }\KeywordTok{theme}\NormalTok{(}\DataTypeTok{strip.text.y =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{angle =} \DecValTok{270}\NormalTok{, }\DataTypeTok{size =} \DecValTok{10}\NormalTok{, }\DataTypeTok{margin =} \KeywordTok{margin}\NormalTok{(}\DataTypeTok{t =} \DecValTok{15}\NormalTok{, }
        \DataTypeTok{r =} \DecValTok{15}\NormalTok{, }\DataTypeTok{b =} \DecValTok{15}\NormalTok{, }\DataTypeTok{l =} \DecValTok{15}\NormalTok{)), }\DataTypeTok{strip.text.x =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{size =} \DecValTok{12}\NormalTok{), }\DataTypeTok{strip.background =} \KeywordTok{element_rect}\NormalTok{(}\DataTypeTok{colour =} \OtherTok{NULL}\NormalTok{, }
        \DataTypeTok{linetype =} \StringTok{"blank"}\NormalTok{, }\DataTypeTok{fill =} \StringTok{"gray90"}\NormalTok{), }\DataTypeTok{text =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{size =} \DecValTok{14}\NormalTok{), }\DataTypeTok{panel.spacing =} \KeywordTok{unit}\NormalTok{(}\FloatTok{0.5}\NormalTok{, }
        \StringTok{"lines"}\NormalTok{), }\DataTypeTok{panel.border =} \KeywordTok{element_blank}\NormalTok{(), }\DataTypeTok{axis.line =} \KeywordTok{element_line}\NormalTok{(), }\DataTypeTok{panel.grid.major.x =} \KeywordTok{element_line}\NormalTok{(}\DataTypeTok{linetype =} \StringTok{"solid"}\NormalTok{, }
        \DataTypeTok{colour =} \StringTok{"gray95"}\NormalTok{), }\DataTypeTok{panel.grid.major.y =} \KeywordTok{element_line}\NormalTok{(}\DataTypeTok{linetype =} \StringTok{"solid"}\NormalTok{, }
        \DataTypeTok{color =} \StringTok{"gray95"}\NormalTok{), }\DataTypeTok{panel.grid.minor.y =} \KeywordTok{element_blank}\NormalTok{(), }\DataTypeTok{panel.grid.minor.x =} \KeywordTok{element_blank}\NormalTok{(), }
        \DataTypeTok{legend.title =} \KeywordTok{element_blank}\NormalTok{(), }\DataTypeTok{axis.title.x =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{hjust =} \FloatTok{0.5}\NormalTok{, }
            \DataTypeTok{size =} \DecValTok{14}\NormalTok{), }\DataTypeTok{axis.title.y =} \KeywordTok{element_blank}\NormalTok{()) }\OperatorTok{+}\StringTok{ }\CommentTok{# addition of male & female symols}
\KeywordTok{annotation_custom}\NormalTok{(}\KeywordTok{rasterGrob}\NormalTok{(female), }\DataTypeTok{xmin =} \FloatTok{-0.2}\NormalTok{, }\DataTypeTok{xmax =} \FloatTok{-0.1}\NormalTok{, }\DataTypeTok{ymin =} \FloatTok{2.3}\NormalTok{, }\DataTypeTok{ymax =} \DecValTok{4}\NormalTok{) }\OperatorTok{+}\StringTok{ }
\StringTok{    }\KeywordTok{annotation_custom}\NormalTok{(}\KeywordTok{rasterGrob}\NormalTok{(male), }\DataTypeTok{xmin =} \FloatTok{0.1}\NormalTok{, }\DataTypeTok{xmax =} \FloatTok{0.2}\NormalTok{, }\DataTypeTok{ymin =} \FloatTok{2.3}\NormalTok{, }\DataTypeTok{ymax =} \DecValTok{4}\NormalTok{)}

\CommentTok{# Metameta_Fig3_alltraits}
\end{Highlighting}
\end{Shaded}

\hypertarget{figure-4}{%
\subsection{Figure 4}\label{figure-4}}

Panel A shows the numbers of traits across functional groups that are
either male-biased (blue-green) or female-biased (orange-red), as
calculated in Figure @ref(fig:FigG1) D. Panel B shows effect sizes and
95\% CI from separate meta-analysis for each functional group (step H in
Figure @ref(fig:FigG1)). Both panels represent results evaluated across
all traits (Phase 3, Figure @ref(fig:FigG1)). Traits that are male
biased are shown in blue, whereas female bias data is represented in
orange.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{Fig4 <-}\StringTok{ }\KeywordTok{ggarrange}\NormalTok{(malebias_Fig2_alltraits, Metameta_Fig3_alltraits, }\DataTypeTok{nrow =} \DecValTok{2}\NormalTok{, }\DataTypeTok{align =} \StringTok{"v"}\NormalTok{, }
    \DataTypeTok{heights =} \KeywordTok{c}\NormalTok{(}\DecValTok{10}\NormalTok{, }\DecValTok{9}\NormalTok{), }\DataTypeTok{labels =} \KeywordTok{c}\NormalTok{(}\StringTok{"A"}\NormalTok{, }\StringTok{"B"}\NormalTok{))}
\NormalTok{Fig4}
\end{Highlighting}
\end{Shaded}

\includegraphics{MouseSexDiffApril20_2020_files/figure-latex/Fig4-1.pdf}

\hypertarget{preparation-for-figure-5}{%
\subsection{Preparation for Figure 5}\label{preparation-for-figure-5}}

To further investigate sex bias in this dataset, and in particular if
the extent of sex bias differs between traits, we investigate the
magnitude of male- and female bias in significantly different traits on
(both for means and variability)

To do this, we select only traits that have CIs that do not overlap with
zero. The code below creates Figure 5A.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{ meta.plot2.sig <-}\StringTok{ }\NormalTok{meta_clean }\OperatorTok{%>%}
\StringTok{                   }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{lnCVRsig =} \KeywordTok{ifelse}\NormalTok{(lnCVR_lower }\OperatorTok{*}\StringTok{ }\NormalTok{lnCVR_upper }\OperatorTok{>}\StringTok{ }\DecValTok{0}\NormalTok{, }\DecValTok{1}\NormalTok{, }\DecValTok{0}\NormalTok{), }
                           \DataTypeTok{lnVRsig =} \KeywordTok{ifelse}\NormalTok{( lnVR_lower }\OperatorTok{*}\StringTok{ }\NormalTok{lnVR_upper  }\OperatorTok{>}\StringTok{ }\DecValTok{0}\NormalTok{, }\DecValTok{1}\NormalTok{, }\DecValTok{0}\NormalTok{),}
                           \DataTypeTok{lnRRsig =} \KeywordTok{ifelse}\NormalTok{( lnRR_lower }\OperatorTok{*}\StringTok{ }\NormalTok{lnRR_upper  }\OperatorTok{>}\StringTok{ }\DecValTok{0}\NormalTok{, }\DecValTok{1}\NormalTok{, }\DecValTok{0}\NormalTok{))}

\NormalTok{meta.plot2.sig.b <-}\StringTok{ }\NormalTok{meta.plot2.sig[, }\KeywordTok{c}\NormalTok{(}\StringTok{"lnCVR"}\NormalTok{, }\StringTok{"lnRR"}\NormalTok{, }\StringTok{"lnCVRsig"}\NormalTok{, }\StringTok{"lnVRsig"}\NormalTok{, }\StringTok{"lnRRsig"}\NormalTok{, }\StringTok{"GroupingTerm"}\NormalTok{)] }

\NormalTok{    meta.plot2.sig.c <-}\StringTok{ }\KeywordTok{gather}\NormalTok{(meta.plot2.sig.b, trait, value, lnCVR}\OperatorTok{:}\NormalTok{lnRR)}
\NormalTok{meta.plot2.sig.c}\OperatorTok{$}\NormalTok{sig <-}\StringTok{ "placeholder"}

\NormalTok{meta.plot2.sig.c}\OperatorTok{$}\NormalTok{trait <-}\StringTok{ }\KeywordTok{factor}\NormalTok{(meta.plot2.sig.c}\OperatorTok{$}\NormalTok{trait, }\DataTypeTok{levels =} \KeywordTok{c}\NormalTok{(}\StringTok{"lnCVR"}\NormalTok{, }\StringTok{"lnRR"}\NormalTok{)) }

\NormalTok{  meta.plot2.sig.c}\OperatorTok{$}\NormalTok{sig <-}\StringTok{ }\KeywordTok{ifelse}\NormalTok{(meta.plot2.sig.c}\OperatorTok{$}\NormalTok{trait }\OperatorTok{==}\StringTok{ "lnCVR"}\NormalTok{, }
\NormalTok{                                 meta.plot2.sig.c}\OperatorTok{$}\NormalTok{lnCVRsig,}
                                 \KeywordTok{ifelse}\NormalTok{(meta.plot2.sig.c}\OperatorTok{$}\NormalTok{trait }\OperatorTok{==}\StringTok{ "lnVR"}\NormalTok{, }
\NormalTok{                                        meta.plot2.sig.c}\OperatorTok{$}\NormalTok{lnVRsig, }
\NormalTok{                                        meta.plot2.sig.c}\OperatorTok{$}\NormalTok{lnRRsig))}

\CommentTok{# Choosing sex biased ln-ratios significantly larger than 0}
\NormalTok{meta.plot2.sig.malebias <-}\StringTok{ }\NormalTok{meta.plot2.sig.c }\OperatorTok{%>%}
\StringTok{                           }\KeywordTok{group_by_at}\NormalTok{(}\KeywordTok{vars}\NormalTok{(trait, GroupingTerm)) }\OperatorTok{%>%}
\StringTok{                           }\KeywordTok{filter}\NormalTok{(sig }\OperatorTok{==}\StringTok{ }\DecValTok{1}\NormalTok{) }\OperatorTok{%>%}
\StringTok{                           }\KeywordTok{summarise}\NormalTok{(}\DataTypeTok{male_sig =} \KeywordTok{sum}\NormalTok{(value }\OperatorTok{>}\StringTok{ }\DecValTok{0}\NormalTok{), }\DataTypeTok{female_sig =} \KeywordTok{sum}\NormalTok{(value }\OperatorTok{<}\StringTok{ }\DecValTok{0}\NormalTok{), }\DataTypeTok{total =}\NormalTok{ male_sig }\OperatorTok{+}\StringTok{ }\NormalTok{female_sig)}

\NormalTok{meta.plot2.sig.malebias <-}\StringTok{ }\KeywordTok{ungroup}\NormalTok{(meta.plot2.sig.malebias) }\OperatorTok{%>%}
\StringTok{                          }\CommentTok{# add "Hearing" for lnCVR (not filtered as only zeros)}
\StringTok{                          }\KeywordTok{add_row}\NormalTok{(}\DataTypeTok{trait =} \StringTok{"lnCVR"}\NormalTok{, }\DataTypeTok{GroupingTerm =} \StringTok{"Hearing"}\NormalTok{, }\DataTypeTok{male_sig =} \DecValTok{0}\NormalTok{, }\DataTypeTok{female_sig =} \DecValTok{0}\NormalTok{, }\DataTypeTok{.before =} \DecValTok{4}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{                          }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{malepercent =}\NormalTok{ male_sig }\OperatorTok{*}\StringTok{ }\DecValTok{100} \OperatorTok{/}\StringTok{ }\NormalTok{total, }\DataTypeTok{femalepercent =}\NormalTok{ female_sig }\OperatorTok{*}\StringTok{ }\DecValTok{100} \OperatorTok{/}\StringTok{ }\NormalTok{total)}

\NormalTok{meta.plot2.sig.malebias}\OperatorTok{$}\NormalTok{label <-}\StringTok{ "CI not overlapping zero"}

\CommentTok{# Re-structure to create stacked bar plots}

\NormalTok{  meta.plot2.sig.bothsexes <-}\StringTok{ }\KeywordTok{as.data.frame}\NormalTok{(meta.plot2.sig.malebias)}
\NormalTok{meta.plot2.sig.bothsexes.b <-}\StringTok{ }\KeywordTok{gather}\NormalTok{(meta.plot2.sig.bothsexes, }\DataTypeTok{key =}\NormalTok{ sex, }\DataTypeTok{value =}\NormalTok{ percent, malepercent}\OperatorTok{:}\NormalTok{femalepercent, }\DataTypeTok{factor_key =} \OtherTok{TRUE}\NormalTok{)}

\CommentTok{# create new sample size variable}

\NormalTok{meta.plot2.sig.bothsexes.b}\OperatorTok{$}\NormalTok{samplesize <-}\StringTok{ }\KeywordTok{with}\NormalTok{(meta.plot2.sig.bothsexes.b, }\KeywordTok{ifelse}\NormalTok{(sex }\OperatorTok{==}\StringTok{ "malepercent"}\NormalTok{, male_sig, female_sig))}

\CommentTok{# Add summary row ('All') and re-arrange rows into correct order for plotting }

\NormalTok{meta.plot2.sig.bothsexes.c <-}\StringTok{ }\NormalTok{meta.plot2.sig.bothsexes.b }\OperatorTok{%>%}\StringTok{ }
\StringTok{                              }\KeywordTok{group_by}\NormalTok{(trait, sex) }\OperatorTok{%>%}\StringTok{ }
\StringTok{                              }\KeywordTok{summarise}\NormalTok{(}\DataTypeTok{GroupingTerm =} \StringTok{"All"}\NormalTok{, }
                                        \DataTypeTok{male_sig =} \KeywordTok{sum}\NormalTok{(male_sig), }
                                        \DataTypeTok{female_sig =} \KeywordTok{sum}\NormalTok{(female_sig), }
                                        \DataTypeTok{total =}\NormalTok{ male_sig }\OperatorTok{+}\StringTok{ }\NormalTok{female_sig, }
                                        \DataTypeTok{label =} \StringTok{"CI not overlapping zero"}\NormalTok{, }
                                        \DataTypeTok{samplesize =} \KeywordTok{sum}\NormalTok{(samplesize)) }\OperatorTok{%>%}
\StringTok{                              }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{percent =} \KeywordTok{ifelse}\NormalTok{(sex }\OperatorTok{==}\StringTok{ "femalepercent"}\NormalTok{, }
\NormalTok{                                                      female_sig}\OperatorTok{*}\DecValTok{100}\OperatorTok{/}\NormalTok{(male_sig}\OperatorTok{+}\NormalTok{female_sig), }
\NormalTok{                                                      male_sig}\OperatorTok{*}\DecValTok{100}\OperatorTok{/}\NormalTok{(male_sig}\OperatorTok{+}\NormalTok{female_sig))) }\OperatorTok{%>%}
\StringTok{                              }\KeywordTok{bind_rows}\NormalTok{(meta.plot2.sig.bothsexes.b, .) }\OperatorTok{%>%}
\StringTok{                              }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{rownumber =} \KeywordTok{row_number}\NormalTok{()) }\OperatorTok{%>%}
\StringTok{                              }\NormalTok{.[}\KeywordTok{c}\NormalTok{(}\DecValTok{37}\NormalTok{, }\DecValTok{1}\OperatorTok{:}\DecValTok{9}\NormalTok{, }\DecValTok{39}\NormalTok{, }\DecValTok{10}\OperatorTok{:}\DecValTok{18}\NormalTok{, }\DecValTok{38}\NormalTok{, }\DecValTok{19}\OperatorTok{:}\DecValTok{27}\NormalTok{, }\DecValTok{40}\NormalTok{, }\DecValTok{28}\OperatorTok{:}\DecValTok{36}\NormalTok{), ] }

  \CommentTok{#line references in previous code line corresponding to: }
  \CommentTok{#'lnCVR(male(All)), lnCVR(male('single grouping terms'), lnRR(male(All)), lnRR(male('single grouping terms')),}
  \CommentTok{#lnCVR(female(All)), lnCVR(female('single grouping terms'), lnRR(female(All)), lnRR(female('single grouping terms'))'}

\NormalTok{meta.plot2.sig.bothsexes.c}\OperatorTok{$}\NormalTok{GroupingTerm <-}\StringTok{ }\KeywordTok{factor}\NormalTok{(meta.plot2.sig.bothsexes.c}\OperatorTok{$}\NormalTok{GroupingTerm,}
                                                  \DataTypeTok{levels =} \KeywordTok{c}\NormalTok{(}\StringTok{"Behaviour"}\NormalTok{, }\StringTok{"Morphology"}\NormalTok{, }\StringTok{"Metabolism"}\NormalTok{, }\StringTok{"Physiology"}\NormalTok{, }
                                                             \StringTok{"Immunology"}\NormalTok{, }\StringTok{"Hematology"}\NormalTok{, }\StringTok{"Heart"}\NormalTok{, }\StringTok{"Hearing"}\NormalTok{, }\StringTok{"Eye"}\NormalTok{, }\StringTok{"All"}\NormalTok{)) }
\NormalTok{meta.plot2.sig.bothsexes.c}\OperatorTok{$}\NormalTok{GroupingTerm <-}\StringTok{ }\KeywordTok{factor}\NormalTok{(meta.plot2.sig.bothsexes.c}\OperatorTok{$}\NormalTok{GroupingTerm, }
                                                  \KeywordTok{rev}\NormalTok{(}\KeywordTok{levels}\NormalTok{(meta.plot2.sig.bothsexes.c}\OperatorTok{$}\NormalTok{GroupingTerm)))}

\CommentTok{# Plot Fig2 all significant results (CI not overlapping zero)}
\CommentTok{# Several grouping terms are added post-hoc (with no data to display): no significant lnCVR for 'Hearing' in either sex; no sig. male-biased lnCVR for 'Immunology' and 'Eye, and no significant female-biased lnRR for 'Eye'.}

\NormalTok{malebias_Fig2_sigtraits <-}
\StringTok{  }\KeywordTok{ggplot}\NormalTok{(meta.plot2.sig.bothsexes.c) }\OperatorTok{+}
\StringTok{  }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ GroupingTerm, }\DataTypeTok{y =}\NormalTok{ percent, }\DataTypeTok{fill =}\NormalTok{ sex) }\OperatorTok{+}
\StringTok{  }\KeywordTok{ylab}\NormalTok{(}\StringTok{"Percentage"}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_col}\NormalTok{() }\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_hline}\NormalTok{(}\DataTypeTok{yintercept =} \DecValTok{50}\NormalTok{, }\DataTypeTok{linetype =} \StringTok{"dashed"}\NormalTok{, }\DataTypeTok{color =} \StringTok{"gray40"}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_text}\NormalTok{(}
    \DataTypeTok{data =} \KeywordTok{subset}\NormalTok{(meta.plot2.sig.bothsexes.c, samplesize }\OperatorTok{!=}\StringTok{ }\DecValTok{0}\NormalTok{), }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{label =}\NormalTok{ samplesize), }\DataTypeTok{position =} \KeywordTok{position_stack}\NormalTok{(}\DataTypeTok{vjust =} \FloatTok{.5}\NormalTok{),}
    \DataTypeTok{color =} \StringTok{"white"}\NormalTok{, }\DataTypeTok{size =} \FloatTok{3.5}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{facet_grid}\NormalTok{(}\DataTypeTok{cols =} \KeywordTok{vars}\NormalTok{(trait), }
             \DataTypeTok{rows =} \KeywordTok{vars}\NormalTok{(label), }
             \DataTypeTok{labeller =} \KeywordTok{label_wrap_gen}\NormalTok{(}\DataTypeTok{width =} \DecValTok{18}\NormalTok{),}
             \DataTypeTok{scales =} \StringTok{"free"}\NormalTok{, }\DataTypeTok{space =} \StringTok{"free"}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{scale_fill_brewer}\NormalTok{(}\DataTypeTok{palette =} \StringTok{"Set2"}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{theme_bw}\NormalTok{(}\DataTypeTok{base_size =} \DecValTok{18}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{theme}\NormalTok{(}\DataTypeTok{strip.text.y =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{angle =} \DecValTok{270}\NormalTok{, }\DataTypeTok{size =} \DecValTok{10}\NormalTok{, }\DataTypeTok{margin =} \KeywordTok{margin}\NormalTok{(}\DataTypeTok{t =} \DecValTok{15}\NormalTok{, }\DataTypeTok{r =} \DecValTok{15}\NormalTok{, }\DataTypeTok{b =} \DecValTok{15}\NormalTok{, }\DataTypeTok{l =} \DecValTok{15}\NormalTok{)),}
        \DataTypeTok{strip.text.x =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{size =} \DecValTok{12}\NormalTok{),}
        \DataTypeTok{strip.background =} \KeywordTok{element_rect}\NormalTok{(}\DataTypeTok{colour =} \OtherTok{NULL}\NormalTok{, }\DataTypeTok{linetype =} \StringTok{"blank"}\NormalTok{, }\DataTypeTok{fill =} \StringTok{"gray90"}\NormalTok{),}
        \DataTypeTok{text =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{size =} \DecValTok{14}\NormalTok{),}
        \DataTypeTok{panel.spacing =} \KeywordTok{unit}\NormalTok{(}\FloatTok{0.5}\NormalTok{, }\StringTok{"lines"}\NormalTok{),}
        \DataTypeTok{panel.border =} \KeywordTok{element_blank}\NormalTok{(),}
        \DataTypeTok{axis.line =} \KeywordTok{element_line}\NormalTok{(),}
        \DataTypeTok{panel.grid.major.x =} \KeywordTok{element_line}\NormalTok{(}\DataTypeTok{linetype =} \StringTok{"solid"}\NormalTok{, }\DataTypeTok{colour =} \StringTok{"gray95"}\NormalTok{),}
        \DataTypeTok{panel.grid.major.y =} \KeywordTok{element_line}\NormalTok{(}\DataTypeTok{linetype =} \StringTok{"solid"}\NormalTok{, }\DataTypeTok{color =} \StringTok{"gray95"}\NormalTok{),}
        \DataTypeTok{panel.grid.minor.y =} \KeywordTok{element_blank}\NormalTok{(),}
        \DataTypeTok{panel.grid.minor.x =} \KeywordTok{element_blank}\NormalTok{(),}
        \DataTypeTok{legend.position =} \StringTok{"none"}\NormalTok{,}
        \DataTypeTok{axis.title.y =} \KeywordTok{element_blank}\NormalTok{()) }\OperatorTok{+}
\StringTok{  }\KeywordTok{coord_flip}\NormalTok{()}

\CommentTok{### Preparation for Plots on significant sex-bias (Second-order meta analysis results)}

\CommentTok{#### Figure 5 B - traits with CI not overlapping 0 }
\CommentTok{# Prepare data }
\CommentTok{# create column with 1 = different from zero, 0 = zero included in CI}

\CommentTok{#### Male-biased (significant) traits:}

\NormalTok{meta.male.plot3.sig <-}\StringTok{ }\NormalTok{metacombo }\OperatorTok{%>%}
\StringTok{                       }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{sigCVR =} \KeywordTok{ifelse}\NormalTok{(lnCVR_lower }\OperatorTok{>}\StringTok{ }\DecValTok{0}\NormalTok{, }\DecValTok{1}\NormalTok{, }\DecValTok{0}\NormalTok{),}
                               \DataTypeTok{sigVR =} \KeywordTok{ifelse}\NormalTok{( lnVR_lower }\OperatorTok{>}\StringTok{ }\DecValTok{0}\NormalTok{, }\DecValTok{1}\NormalTok{, }\DecValTok{0}\NormalTok{),}
                               \DataTypeTok{sigRR =} \KeywordTok{ifelse}\NormalTok{( lnRR_lower }\OperatorTok{>}\StringTok{ }\DecValTok{0}\NormalTok{, }\DecValTok{1}\NormalTok{, }\DecValTok{0}\NormalTok{))}

\CommentTok{# Significant subset for lnCVR}
\NormalTok{metacombo_male.plot3.CVR <-}\StringTok{ }\NormalTok{meta.male.plot3.sig    }\OperatorTok{%>%}
\StringTok{                            }\KeywordTok{filter}\NormalTok{(sigCVR }\OperatorTok{==}\StringTok{ }\DecValTok{1}\NormalTok{)    }\OperatorTok{%>%}
\StringTok{                            }\KeywordTok{group_by}\NormalTok{(GroupingTerm) }\OperatorTok{%>%}
\StringTok{                            }\KeywordTok{nest}\NormalTok{()}

\NormalTok{metacombo_male.plot3.CVR.all <-}\StringTok{ }\NormalTok{meta.male.plot3.sig }\OperatorTok{%>%}
\StringTok{                                }\KeywordTok{filter}\NormalTok{(sigCVR }\OperatorTok{==}\StringTok{ }\DecValTok{1}\NormalTok{) }\OperatorTok{%>%}
\StringTok{                                }\KeywordTok{nest}\NormalTok{(}\DataTypeTok{data =} \KeywordTok{everything}\NormalTok{())   }

\CommentTok{# Significant subset for lnVR}
\NormalTok{metacombo_male.plot3.VR <-}\StringTok{ }\NormalTok{meta.male.plot3.sig    }\OperatorTok{%>%}
\StringTok{                           }\KeywordTok{filter}\NormalTok{(sigVR }\OperatorTok{==}\StringTok{ }\DecValTok{1}\NormalTok{)     }\OperatorTok{%>%}
\StringTok{                           }\KeywordTok{group_by}\NormalTok{(GroupingTerm) }\OperatorTok{%>%}
\StringTok{                           }\KeywordTok{nest}\NormalTok{()}

\NormalTok{metacombo_male.plot3.VR.all <-}\StringTok{ }\NormalTok{meta.male.plot3.sig    }\OperatorTok{%>%}
\StringTok{                               }\KeywordTok{filter}\NormalTok{(sigVR }\OperatorTok{==}\StringTok{ }\DecValTok{1}\NormalTok{)     }\OperatorTok{%>%}
\StringTok{                               }\KeywordTok{nest}\NormalTok{(}\DataTypeTok{data =} \KeywordTok{everything}\NormalTok{())    }

\CommentTok{# Significant subset for lnRR}
\NormalTok{metacombo_male.plot3.RR <-}\StringTok{ }\NormalTok{meta.male.plot3.sig    }\OperatorTok{%>%}
\StringTok{                           }\KeywordTok{filter}\NormalTok{(sigRR }\OperatorTok{==}\StringTok{ }\DecValTok{1}\NormalTok{)     }\OperatorTok{%>%}
\StringTok{                           }\KeywordTok{group_by}\NormalTok{(GroupingTerm) }\OperatorTok{%>%}
\StringTok{                           }\KeywordTok{nest}\NormalTok{()}

\NormalTok{metacombo_male.plot3.RR.all <-}\StringTok{ }\NormalTok{meta.male.plot3.sig }\OperatorTok{%>%}
\StringTok{                               }\KeywordTok{filter}\NormalTok{(sigRR }\OperatorTok{==}\StringTok{ }\DecValTok{1}\NormalTok{)  }\OperatorTok{%>%}
\StringTok{                               }\KeywordTok{nest}\NormalTok{(}\DataTypeTok{data =} \KeywordTok{everything}\NormalTok{())   }

\CommentTok{# **Final fixed effects meta-analyses within grouping terms, with SE of the estimate}

\NormalTok{plot3.male.meta.CVR <-}\StringTok{ }\NormalTok{metacombo_male.plot3.CVR }\OperatorTok{%>%}
\StringTok{                       }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{model_lnCVR =} \KeywordTok{map}\NormalTok{(data, }
                                                \OperatorTok{~}\StringTok{ }\NormalTok{metafor}\OperatorTok{::}\KeywordTok{rma.uni}\NormalTok{(}\DataTypeTok{yi =}\NormalTok{ .x}\OperatorTok{$}\NormalTok{lnCVR, }\DataTypeTok{sei =}\NormalTok{ (.x}\OperatorTok{$}\NormalTok{lnCVR_upper }\OperatorTok{-}\StringTok{ }\NormalTok{.x}\OperatorTok{$}\NormalTok{lnCVR_lower) }\OperatorTok{/}\StringTok{ }\NormalTok{(}\DecValTok{2} \OperatorTok{*}\StringTok{ }\FloatTok{1.96}\NormalTok{), }
                                              \DataTypeTok{control =} \KeywordTok{list}\NormalTok{(}\DataTypeTok{optimizer =} \StringTok{"optim"}\NormalTok{, }
                                                             \DataTypeTok{optmethod =} \StringTok{"Nelder-Mead"}\NormalTok{, }
                                                             \DataTypeTok{maxit =} \DecValTok{1000}\NormalTok{), }
                                              \DataTypeTok{verbose =}\NormalTok{ F)))}

\NormalTok{plot3.male.meta.VR <-}\StringTok{ }\NormalTok{metacombo_male.plot3.VR }\OperatorTok{%>%}
\StringTok{                      }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{model_lnVR =} \KeywordTok{map}\NormalTok{(data, }
                                              \OperatorTok{~}\StringTok{ }\NormalTok{metafor}\OperatorTok{::}\KeywordTok{rma.uni}\NormalTok{(}\DataTypeTok{yi =}\NormalTok{ .x}\OperatorTok{$}\NormalTok{lnVR, }\DataTypeTok{sei =}\NormalTok{ (.x}\OperatorTok{$}\NormalTok{lnVR_upper }\OperatorTok{-}\StringTok{ }\NormalTok{.x}\OperatorTok{$}\NormalTok{lnVR_lower) }\OperatorTok{/}\StringTok{ }\NormalTok{(}\DecValTok{2} \OperatorTok{*}\StringTok{ }\FloatTok{1.96}\NormalTok{),}
                                            \DataTypeTok{control =} \KeywordTok{list}\NormalTok{(}\DataTypeTok{optimizer =} \StringTok{"optim"}\NormalTok{, }
                                                           \DataTypeTok{optmethod =} \StringTok{"Nelder-Mead"}\NormalTok{, }
                                                           \DataTypeTok{maxit =} \DecValTok{1000}\NormalTok{), }
                                            \DataTypeTok{verbose =}\NormalTok{ F)))}

\NormalTok{plot3.male.meta.RR <-}\StringTok{ }\NormalTok{metacombo_male.plot3.RR }\OperatorTok{%>%}
\StringTok{                      }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{model_lnRR =} \KeywordTok{map}\NormalTok{(data, }
                                              \OperatorTok{~}\StringTok{ }\NormalTok{metafor}\OperatorTok{::}\KeywordTok{rma.uni}\NormalTok{(}\DataTypeTok{yi =}\NormalTok{ .x}\OperatorTok{$}\NormalTok{lnRR, }\DataTypeTok{sei =}\NormalTok{ (.x}\OperatorTok{$}\NormalTok{lnRR_upper }\OperatorTok{-}\StringTok{ }\NormalTok{.x}\OperatorTok{$}\NormalTok{lnRR_lower) }\OperatorTok{/}\StringTok{ }\NormalTok{(}\DecValTok{2} \OperatorTok{*}\StringTok{ }\FloatTok{1.96}\NormalTok{),}
                                              \DataTypeTok{control =} \KeywordTok{list}\NormalTok{(}\DataTypeTok{optimizer =} \StringTok{"optim"}\NormalTok{, }
                                                             \DataTypeTok{optmethod =} \StringTok{"Nelder-Mead"}\NormalTok{, }
                                                             \DataTypeTok{maxit =} \DecValTok{1000}\NormalTok{), }
                                              \DataTypeTok{verbose =}\NormalTok{ F)))}

\CommentTok{# Across all grouping terms #}

\NormalTok{plot3.male.meta.CVR.all <-}\StringTok{ }\NormalTok{metacombo_male.plot3.CVR.all }\OperatorTok{%>%}
\StringTok{                            }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{model_lnCVR =} \KeywordTok{map}\NormalTok{(data,}
                                                     \OperatorTok{~}\StringTok{ }\NormalTok{metafor}\OperatorTok{::}\KeywordTok{rma.uni}\NormalTok{(}\DataTypeTok{yi =}\NormalTok{ .x}\OperatorTok{$}\NormalTok{lnCVR, }\DataTypeTok{sei =}\NormalTok{ (.x}\OperatorTok{$}\NormalTok{lnCVR_upper }\OperatorTok{-}\StringTok{ }\NormalTok{.x}\OperatorTok{$}\NormalTok{lnCVR_lower) }\OperatorTok{/}\StringTok{ }\NormalTok{(}\DecValTok{2} \OperatorTok{*}\StringTok{ }\FloatTok{1.96}\NormalTok{),}
                                                  \DataTypeTok{control =} \KeywordTok{list}\NormalTok{(}\DataTypeTok{optimizer =} \StringTok{"optim"}\NormalTok{, }
                                                                 \DataTypeTok{optmethod =} \StringTok{"Nelder-Mead"}\NormalTok{, }
                                                                 \DataTypeTok{maxit =} \DecValTok{1000}\NormalTok{), }
                                                  \DataTypeTok{verbose =}\NormalTok{ F)))}

\NormalTok{plot3.male.meta.CVR.all <-}\StringTok{ }\NormalTok{plot3.male.meta.CVR.all }\OperatorTok{%>%}\StringTok{ }
\StringTok{                            }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{GroupingTerm =} \StringTok{"All"}\NormalTok{)}

\NormalTok{plot3.male.meta.VR.all <-}\StringTok{ }\NormalTok{metacombo_male.plot3.VR.all }\OperatorTok{%>%}
\StringTok{                          }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{model_lnVR =} \KeywordTok{map}\NormalTok{(data, }
                                                  \OperatorTok{~}\StringTok{ }\NormalTok{metafor}\OperatorTok{::}\KeywordTok{rma.uni}\NormalTok{(}\DataTypeTok{yi =}\NormalTok{ .x}\OperatorTok{$}\NormalTok{lnVR, }\DataTypeTok{sei =}\NormalTok{ (.x}\OperatorTok{$}\NormalTok{lnVR_upper }\OperatorTok{-}\StringTok{ }\NormalTok{.x}\OperatorTok{$}\NormalTok{lnVR_lower) }\OperatorTok{/}\StringTok{ }\NormalTok{(}\DecValTok{2} \OperatorTok{*}\StringTok{ }\FloatTok{1.96}\NormalTok{),}
                                                  \DataTypeTok{control =} \KeywordTok{list}\NormalTok{(}\DataTypeTok{optimizer =} \StringTok{"optim"}\NormalTok{, }
                                                                 \DataTypeTok{optmethod =} \StringTok{"Nelder-Mead"}\NormalTok{, }
                                                                 \DataTypeTok{maxit =} \DecValTok{1000}\NormalTok{), }
                                                  \DataTypeTok{verbose =}\NormalTok{ F)))}

\NormalTok{plot3.male.meta.VR.all <-}\StringTok{ }\NormalTok{plot3.male.meta.VR.all }\OperatorTok{%>%}\StringTok{ }
\StringTok{                          }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{GroupingTerm =} \StringTok{"All"}\NormalTok{)}

\NormalTok{plot3.male.meta.RR.all <-}\StringTok{ }\NormalTok{metacombo_male.plot3.RR.all }\OperatorTok{%>%}
\StringTok{                          }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{model_lnRR =} \KeywordTok{map}\NormalTok{(data, }
                                                  \OperatorTok{~}\StringTok{ }\NormalTok{metafor}\OperatorTok{::}\KeywordTok{rma.uni}\NormalTok{(}\DataTypeTok{yi =}\NormalTok{ .x}\OperatorTok{$}\NormalTok{lnRR, }\DataTypeTok{sei =}\NormalTok{ (.x}\OperatorTok{$}\NormalTok{lnRR_upper }\OperatorTok{-}\StringTok{ }\NormalTok{.x}\OperatorTok{$}\NormalTok{lnRR_lower) }\OperatorTok{/}\StringTok{ }\NormalTok{(}\DecValTok{2} \OperatorTok{*}\StringTok{ }\FloatTok{1.96}\NormalTok{),}
                                                \DataTypeTok{control =} \KeywordTok{list}\NormalTok{(}\DataTypeTok{optimizer =} \StringTok{"optim"}\NormalTok{, }
                                                               \DataTypeTok{optmethod =} \StringTok{"Nelder-Mead"}\NormalTok{, }
                                                               \DataTypeTok{maxit =} \DecValTok{1000}\NormalTok{), }
                                                \DataTypeTok{verbose =}\NormalTok{ F)))}

\NormalTok{plot3.male.meta.RR.all <-}\StringTok{ }\NormalTok{plot3.male.meta.RR.all }\OperatorTok{%>%}\StringTok{ }
\StringTok{                          }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{GroupingTerm =} \StringTok{"All"}\NormalTok{)}

\CommentTok{# Combine with separate grouping term results}

\NormalTok{plot3.male.meta.CVR <-}\StringTok{ }\KeywordTok{bind_rows}\NormalTok{(plot3.male.meta.CVR, plot3.male.meta.CVR.all)}
\NormalTok{ plot3.male.meta.VR <-}\StringTok{ }\KeywordTok{bind_rows}\NormalTok{(plot3.male.meta.VR,   plot3.male.meta.VR.all)}
\NormalTok{ plot3.male.meta.RR <-}\StringTok{ }\KeywordTok{bind_rows}\NormalTok{(plot3.male.meta.RR,   plot3.male.meta.RR.all)}

\CommentTok{# **Re-structure data for each grouping term; delete un-used variables}

\NormalTok{plot3.male.meta.CVR.b <-}\StringTok{ }\KeywordTok{as.data.frame}\NormalTok{(plot3.male.meta.CVR }\OperatorTok{%>%}\StringTok{ }
\StringTok{                                       }\KeywordTok{group_by}\NormalTok{(GroupingTerm) }\OperatorTok{%>%}
\StringTok{                                       }\KeywordTok{mutate}\NormalTok{( }\DataTypeTok{lnCVR =} \KeywordTok{map_dbl}\NormalTok{(model_lnCVR, }\KeywordTok{pluck}\NormalTok{(}\DecValTok{2}\NormalTok{)), }
                                               \DataTypeTok{lnCVR_lower =} \KeywordTok{map_dbl}\NormalTok{(model_lnCVR, }\KeywordTok{pluck}\NormalTok{(}\DecValTok{6}\NormalTok{)), }
                                               \DataTypeTok{lnCVR_upper =} \KeywordTok{map_dbl}\NormalTok{(model_lnCVR, }\KeywordTok{pluck}\NormalTok{(}\DecValTok{7}\NormalTok{)), }
                                               \DataTypeTok{lnCVR_se =} \KeywordTok{map_dbl}\NormalTok{(model_lnCVR, }\KeywordTok{pluck}\NormalTok{(}\DecValTok{3}\NormalTok{)), }
                                               \DataTypeTok{lnCVR_I2 =} \KeywordTok{map_dbl}\NormalTok{(model_lnCVR, }\KeywordTok{pluck}\NormalTok{(}\StringTok{"I2"}\NormalTok{))))[, }\KeywordTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{, }\DecValTok{4}\OperatorTok{:}\DecValTok{8}\NormalTok{)]}

\NormalTok{add.row.hearing <-}\StringTok{ }\KeywordTok{as.data.frame}\NormalTok{(}\KeywordTok{t}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"Hearing"}\NormalTok{, }\OtherTok{NA}\NormalTok{, }\OtherTok{NA}\NormalTok{, }\OtherTok{NA}\NormalTok{, }\OtherTok{NA}\NormalTok{, }\OtherTok{NA}\NormalTok{))) }\OperatorTok{%>%}\StringTok{ }
\StringTok{                                  }\KeywordTok{setNames}\NormalTok{(}\KeywordTok{names}\NormalTok{(plot3.male.meta.CVR.b))}

\NormalTok{plot3.male.meta.CVR.b <-}\StringTok{ }\KeywordTok{bind_rows}\NormalTok{(plot3.male.meta.CVR.b, add.row.hearing)}
\NormalTok{plot3.male.meta.CVR.b <-}\StringTok{ }\NormalTok{plot3.male.meta.CVR.b[}\KeywordTok{order}\NormalTok{(plot3.male.meta.CVR.b}\OperatorTok{$}\NormalTok{GroupingTerm), ]}

\NormalTok{plot3.male.meta.VR.b <-}\StringTok{ }\KeywordTok{as.data.frame}\NormalTok{(plot3.male.meta.VR }\OperatorTok{%>%}\StringTok{ }
\StringTok{                                      }\KeywordTok{group_by}\NormalTok{(GroupingTerm) }\OperatorTok{%>%}
\StringTok{                                      }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{lnVR =} \KeywordTok{map_dbl}\NormalTok{(model_lnVR, }\KeywordTok{pluck}\NormalTok{(}\DecValTok{2}\NormalTok{)), }
                                             \DataTypeTok{lnVR_lower =} \KeywordTok{map_dbl}\NormalTok{(model_lnVR, }\KeywordTok{pluck}\NormalTok{(}\DecValTok{6}\NormalTok{)),}
                                             \DataTypeTok{lnVR_upper =} \KeywordTok{map_dbl}\NormalTok{(model_lnVR, }\KeywordTok{pluck}\NormalTok{(}\DecValTok{7}\NormalTok{)), }
                                             \DataTypeTok{lnVR_se =} \KeywordTok{map_dbl}\NormalTok{(model_lnVR, }\KeywordTok{pluck}\NormalTok{(}\DecValTok{3}\NormalTok{)),}
                                             \DataTypeTok{lnVR_I2 =} \KeywordTok{map_dbl}\NormalTok{(model_lnVR, }\KeywordTok{pluck}\NormalTok{(}\StringTok{"I2"}\NormalTok{))))[, }\KeywordTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{, }\DecValTok{4}\OperatorTok{:}\DecValTok{8}\NormalTok{)]}

\NormalTok{plot3.male.meta.VR.b <-}\StringTok{ }\NormalTok{plot3.male.meta.VR.b[}\KeywordTok{order}\NormalTok{(plot3.male.meta.VR.b}\OperatorTok{$}\NormalTok{GroupingTerm), ]}

\NormalTok{plot3.male.meta.RR.b <-}\StringTok{ }\KeywordTok{as.data.frame}\NormalTok{(plot3.male.meta.RR }\OperatorTok{%>%}\StringTok{ }
\StringTok{                                      }\KeywordTok{group_by}\NormalTok{(GroupingTerm) }\OperatorTok{%>%}\StringTok{ }
\StringTok{                                      }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{lnRR =} \KeywordTok{map_dbl}\NormalTok{(model_lnRR, }\KeywordTok{pluck}\NormalTok{(}\DecValTok{2}\NormalTok{)), }
                                             \DataTypeTok{lnRR_lower =} \KeywordTok{map_dbl}\NormalTok{(model_lnRR, }\KeywordTok{pluck}\NormalTok{(}\DecValTok{6}\NormalTok{)),}
                                             \DataTypeTok{lnRR_upper =} \KeywordTok{map_dbl}\NormalTok{(model_lnRR, }\KeywordTok{pluck}\NormalTok{(}\DecValTok{7}\NormalTok{)), }
                                             \DataTypeTok{lnRR_se =} \KeywordTok{map_dbl}\NormalTok{(model_lnRR, }\KeywordTok{pluck}\NormalTok{(}\DecValTok{3}\NormalTok{)),}
                                             \DataTypeTok{lnRR_I2 =} \KeywordTok{map_dbl}\NormalTok{(model_lnRR, }\KeywordTok{pluck}\NormalTok{(}\StringTok{"I2"}\NormalTok{))))[, }\KeywordTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{, }\DecValTok{4}\OperatorTok{:}\DecValTok{8}\NormalTok{)]}

\NormalTok{plot3.male.meta.RR.b <-}\StringTok{ }\NormalTok{plot3.male.meta.RR.b[}\KeywordTok{order}\NormalTok{(plot3.male.meta.RR.b}\OperatorTok{$}\NormalTok{GroupingTerm), ]}

\NormalTok{overall.male.plot3 <-}\StringTok{ }\KeywordTok{full_join}\NormalTok{(plot3.male.meta.CVR.b, plot3.male.meta.VR.b)}
\NormalTok{overall.male.plot3 <-}\StringTok{ }\KeywordTok{full_join}\NormalTok{(overall.male.plot3,    plot3.male.meta.RR.b)}

\NormalTok{overall.male.plot3}\OperatorTok{$}\NormalTok{GroupingTerm <-}\StringTok{ }\KeywordTok{factor}\NormalTok{(overall.male.plot3}\OperatorTok{$}\NormalTok{GroupingTerm, }
                                          \DataTypeTok{levels =} \KeywordTok{c}\NormalTok{(}\StringTok{"Behaviour"}\NormalTok{, }\StringTok{"Morphology"}\NormalTok{, }\StringTok{"Metabolism"}\NormalTok{, }\StringTok{"Physiology"}\NormalTok{, }
                                                     \StringTok{"Immunology"}\NormalTok{, }\StringTok{"Hematology"}\NormalTok{, }\StringTok{"Heart"}\NormalTok{, }\StringTok{"Hearing"}\NormalTok{, }\StringTok{"Eye"}\NormalTok{, }\StringTok{"All"}\NormalTok{))}
\NormalTok{overall.male.plot3}\OperatorTok{$}\NormalTok{GroupingTerm <-}\StringTok{ }\KeywordTok{factor}\NormalTok{(overall.male.plot3}\OperatorTok{$}\NormalTok{GroupingTerm, }
                                          \KeywordTok{rev}\NormalTok{(}\KeywordTok{levels}\NormalTok{(overall.male.plot3}\OperatorTok{$}\NormalTok{GroupingTerm)))}

\NormalTok{overall.male.plot3}\OperatorTok{$}\NormalTok{GroupingTerm <-}\StringTok{ }\KeywordTok{factor}\NormalTok{(overall.male.plot3}\OperatorTok{$}\NormalTok{GroupingTerm, }
                                          \DataTypeTok{levels =} \KeywordTok{c}\NormalTok{(}\StringTok{"Behaviour"}\NormalTok{, }\StringTok{"Morphology"}\NormalTok{, }\StringTok{"Metabolism"}\NormalTok{, }\StringTok{"Physiology"}\NormalTok{, }
                                                     \StringTok{"Immunology"}\NormalTok{, }\StringTok{"Hematology"}\NormalTok{, }\StringTok{"Heart"}\NormalTok{, }\StringTok{"Hearing"}\NormalTok{, }\StringTok{"Eye"}\NormalTok{, }\StringTok{"All"}\NormalTok{))}
\NormalTok{overall.male.plot3}\OperatorTok{$}\NormalTok{GroupingTerm <-}\StringTok{ }\KeywordTok{factor}\NormalTok{(overall.male.plot3}\OperatorTok{$}\NormalTok{GroupingTerm, }
                                          \KeywordTok{rev}\NormalTok{(}\KeywordTok{levels}\NormalTok{(overall.male.plot3}\OperatorTok{$}\NormalTok{GroupingTerm)))}

\CommentTok{# Restructure MALE data for plotting }

\NormalTok{overall3.male.sig <-}\StringTok{ }\KeywordTok{gather}\NormalTok{(overall.male.plot3, parameter, value, }\KeywordTok{c}\NormalTok{(lnCVR, lnRR), }\DataTypeTok{factor_key =} \OtherTok{TRUE}\NormalTok{) }

\NormalTok{lnCVR.ci <-}\StringTok{ }\NormalTok{overall3.male.sig            }\OperatorTok{%>%}
\StringTok{            }\KeywordTok{filter}\NormalTok{(parameter }\OperatorTok{==}\StringTok{ "lnCVR"}\NormalTok{) }\OperatorTok{%>%}
\StringTok{            }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{ci.low =}\NormalTok{ lnCVR_lower, }
                   \DataTypeTok{ci.high =}\NormalTok{ lnCVR_upper)}

\NormalTok{lnRR.ci <-}\StringTok{ }\NormalTok{overall3.male.sig           }\OperatorTok{%>%}
\StringTok{           }\KeywordTok{filter}\NormalTok{(parameter }\OperatorTok{==}\StringTok{ "lnRR"}\NormalTok{) }\OperatorTok{%>%}
\StringTok{           }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{ci.low =}\NormalTok{ lnRR_lower, }
                 \DataTypeTok{ci.high =}\NormalTok{ lnRR_upper)}

\NormalTok{overall4.male.sig <-}\StringTok{ }\KeywordTok{bind_rows}\NormalTok{(lnCVR.ci, lnRR.ci) }\OperatorTok{%>%}\StringTok{ }
\StringTok{                     }\KeywordTok{select}\NormalTok{(GroupingTerm, }
\NormalTok{                            parameter, }
\NormalTok{                            value, }
\NormalTok{                            ci.low, }
\NormalTok{                            ci.high) }

\NormalTok{overall4.male.sig}\OperatorTok{$}\NormalTok{label <-}\StringTok{ "CI not overlapping zero"}

\CommentTok{# Plot Fig 5B all significant results (CI not overlapping zero) for males. This is the right panel in Figure 5B.}

\NormalTok{Metameta_Fig3_male.sig <-}\StringTok{ }\NormalTok{overall4.male.sig }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{ggplot}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{y =}\NormalTok{ GroupingTerm, }\DataTypeTok{x =}\NormalTok{ value)) }\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_errorbarh}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{xmin =}\NormalTok{ ci.low,}
                     \DataTypeTok{xmax =}\NormalTok{ ci.high),}
                 \DataTypeTok{height =} \FloatTok{0.1}\NormalTok{, }
                 \DataTypeTok{show.legend =} \OtherTok{FALSE}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_point}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{shape =}\NormalTok{ parameter),}
             \DataTypeTok{fill =} \StringTok{"mediumaquamarine"}\NormalTok{, }
             \DataTypeTok{color =} \StringTok{"mediumaquamarine"}\NormalTok{, }
             \DataTypeTok{size =} \FloatTok{2.2}\NormalTok{, }
             \DataTypeTok{show.legend =} \OtherTok{FALSE}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{scale_x_continuous}\NormalTok{(}\DataTypeTok{limits =} \KeywordTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }\FloatTok{0.4}\NormalTok{),}
                     \DataTypeTok{breaks =} \KeywordTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }\FloatTok{0.3}\NormalTok{),}
                       \DataTypeTok{name =} \StringTok{"Effect size"}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_vline}\NormalTok{(}\DataTypeTok{xintercept =} \DecValTok{0}\NormalTok{,}
                  \DataTypeTok{color =} \StringTok{"black"}\NormalTok{,}
              \DataTypeTok{linetype =} \StringTok{"dashed"}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{facet_grid}\NormalTok{(}\DataTypeTok{cols =} \KeywordTok{vars}\NormalTok{(parameter), }
             \DataTypeTok{rows =} \KeywordTok{vars}\NormalTok{(label),}
             \DataTypeTok{labeller =} \KeywordTok{label_wrap_gen}\NormalTok{(}\DataTypeTok{width =} \DecValTok{23}\NormalTok{),}
             \DataTypeTok{scales =} \StringTok{"free"}\NormalTok{,}
             \DataTypeTok{space =} \StringTok{"free"}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{theme_bw}\NormalTok{() }\OperatorTok{+}
\StringTok{  }\KeywordTok{theme}\NormalTok{(}\DataTypeTok{strip.text.y =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{angle =} \DecValTok{270}\NormalTok{, }
                                    \DataTypeTok{size =} \DecValTok{10}\NormalTok{, }
                                    \DataTypeTok{margin =} \KeywordTok{margin}\NormalTok{(}\DataTypeTok{t =} \DecValTok{15}\NormalTok{, }\DataTypeTok{r =} \DecValTok{15}\NormalTok{, }\DataTypeTok{b =} \DecValTok{15}\NormalTok{, }\DataTypeTok{l =} \DecValTok{15}\NormalTok{)),}
        \DataTypeTok{strip.text.x =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{size =} \DecValTok{12}\NormalTok{),}
        \DataTypeTok{strip.background =} \KeywordTok{element_rect}\NormalTok{(}\DataTypeTok{colour =} \OtherTok{NULL}\NormalTok{, }
                                        \DataTypeTok{linetype =} \StringTok{"blank"}\NormalTok{, }
                                        \DataTypeTok{fill =} \StringTok{"gray90"}\NormalTok{),}
        \DataTypeTok{text =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{size =} \DecValTok{14}\NormalTok{),}
        \DataTypeTok{panel.spacing =} \KeywordTok{unit}\NormalTok{(}\FloatTok{0.5}\NormalTok{, }\StringTok{"lines"}\NormalTok{),}
        \DataTypeTok{panel.border =} \KeywordTok{element_blank}\NormalTok{(),}
        \DataTypeTok{axis.line =} \KeywordTok{element_line}\NormalTok{(),}
        \DataTypeTok{panel.grid.major.x =} \KeywordTok{element_line}\NormalTok{(}\DataTypeTok{linetype =} \StringTok{"solid"}\NormalTok{, }
                                          \DataTypeTok{colour =} \StringTok{"gray95"}\NormalTok{),}
        \DataTypeTok{panel.grid.major.y =} \KeywordTok{element_line}\NormalTok{(}\DataTypeTok{linetype =} \StringTok{"solid"}\NormalTok{, }
                                          \DataTypeTok{color =} \StringTok{"gray95"}\NormalTok{),}
        \DataTypeTok{panel.grid.minor.y =} \KeywordTok{element_blank}\NormalTok{(),}
        \DataTypeTok{panel.grid.minor.x =} \KeywordTok{element_blank}\NormalTok{(),}
        \DataTypeTok{legend.title =} \KeywordTok{element_blank}\NormalTok{(),}
        \DataTypeTok{axis.title.x =} \KeywordTok{element_blank}\NormalTok{(),}
        \DataTypeTok{axis.title.y =} \KeywordTok{element_blank}\NormalTok{())}

\CommentTok{# Metameta_Fig3_male.sig}

\CommentTok{#### Female part, significant traits: Female Fig5B sig}

\CommentTok{# as above: Prepare data for traits with CI not overlapping 0}
\CommentTok{# create column with 1 = different from zero, 0 = zero included in CI}

\CommentTok{# Female-biased traits}

\NormalTok{meta.female.plot3.sig <-}\StringTok{ }\NormalTok{metacombo }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{sigCVR =} \KeywordTok{ifelse}\NormalTok{(lnCVR_upper }\OperatorTok{<}\StringTok{ }\DecValTok{0}\NormalTok{, }\DecValTok{1}\NormalTok{, }\DecValTok{0}\NormalTok{),}
          \DataTypeTok{sigVR =} \KeywordTok{ifelse}\NormalTok{(lnVR_upper }\OperatorTok{<}\StringTok{ }\DecValTok{0}\NormalTok{, }\DecValTok{1}\NormalTok{, }\DecValTok{0}\NormalTok{),}
          \DataTypeTok{sigRR =} \KeywordTok{ifelse}\NormalTok{(lnRR_upper }\OperatorTok{<}\StringTok{ }\DecValTok{0}\NormalTok{, }\DecValTok{1}\NormalTok{, }\DecValTok{0}\NormalTok{))}

\CommentTok{# Significant subset for lnCVR}

\NormalTok{metacombo_female.plot3.CVR <-}\StringTok{ }\NormalTok{meta.female.plot3.sig  }\OperatorTok{%>%}
\StringTok{                              }\KeywordTok{filter}\NormalTok{(sigCVR }\OperatorTok{==}\StringTok{ }\DecValTok{1}\NormalTok{)    }\OperatorTok{%>%}
\StringTok{                              }\KeywordTok{group_by}\NormalTok{(GroupingTerm) }\OperatorTok{%>%}
\StringTok{                              }\KeywordTok{nest}\NormalTok{()}

\NormalTok{metacombo_female.plot3.CVR.all <-}\StringTok{ }\NormalTok{meta.female.plot3.sig }\OperatorTok{%>%}
\StringTok{                                  }\KeywordTok{filter}\NormalTok{(sigCVR }\OperatorTok{==}\StringTok{ }\DecValTok{1}\NormalTok{)   }\OperatorTok{%>%}
\StringTok{                                  }\KeywordTok{nest}\NormalTok{(}\DataTypeTok{data =} \KeywordTok{everything}\NormalTok{())   }

\CommentTok{# Significant subset for lnVR}

\NormalTok{metacombo_female.plot3.VR <-}\StringTok{ }\NormalTok{meta.female.plot3.sig  }\OperatorTok{%>%}
\StringTok{                             }\KeywordTok{filter}\NormalTok{(sigVR }\OperatorTok{==}\StringTok{ }\DecValTok{1}\NormalTok{)     }\OperatorTok{%>%}
\StringTok{                             }\KeywordTok{group_by}\NormalTok{(GroupingTerm) }\OperatorTok{%>%}
\StringTok{                             }\KeywordTok{nest}\NormalTok{()}

\NormalTok{metacombo_female.plot3.VR.all <-}\StringTok{ }\NormalTok{meta.female.plot3.sig  }\OperatorTok{%>%}
\StringTok{                                 }\KeywordTok{filter}\NormalTok{(sigVR }\OperatorTok{==}\StringTok{ }\DecValTok{1}\NormalTok{)     }\OperatorTok{%>%}
\StringTok{                                 }\KeywordTok{nest}\NormalTok{(}\DataTypeTok{data =} \KeywordTok{everything}\NormalTok{())   }

\CommentTok{# Significant subset for lnRR}

\NormalTok{metacombo_female.plot3.RR <-}\StringTok{ }\NormalTok{meta.female.plot3.sig  }\OperatorTok{%>%}
\StringTok{                             }\KeywordTok{filter}\NormalTok{(sigRR }\OperatorTok{==}\StringTok{ }\DecValTok{1}\NormalTok{)     }\OperatorTok{%>%}
\StringTok{                             }\KeywordTok{group_by}\NormalTok{(GroupingTerm) }\OperatorTok{%>%}
\StringTok{                             }\KeywordTok{nest}\NormalTok{()}

\NormalTok{metacombo_female.plot3.RR.all <-}\StringTok{ }\NormalTok{meta.female.plot3.sig }\OperatorTok{%>%}
\StringTok{                                 }\KeywordTok{filter}\NormalTok{(sigRR }\OperatorTok{==}\StringTok{ }\DecValTok{1}\NormalTok{)    }\OperatorTok{%>%}
\StringTok{                                 }\KeywordTok{nest}\NormalTok{(}\DataTypeTok{data =} \KeywordTok{everything}\NormalTok{())   }

\CommentTok{# **Final fixed effects meta-analyses within grouping terms, with SE of the estimate}

\NormalTok{plot3.female.meta.CVR <-}\StringTok{ }\NormalTok{metacombo_female.plot3.CVR }\OperatorTok{%>%}
\StringTok{                         }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{model_lnCVR =} \KeywordTok{map}\NormalTok{(data, }
                                                  \OperatorTok{~}\StringTok{ }\NormalTok{metafor}\OperatorTok{::}\KeywordTok{rma.uni}\NormalTok{(}\DataTypeTok{yi =}\NormalTok{ .x}\OperatorTok{$}\NormalTok{lnCVR, }\DataTypeTok{sei =}\NormalTok{ (.x}\OperatorTok{$}\NormalTok{lnCVR_upper }\OperatorTok{-}\StringTok{ }\NormalTok{.x}\OperatorTok{$}\NormalTok{lnCVR_lower) }\OperatorTok{/}\StringTok{ }\NormalTok{(}\DecValTok{2} \OperatorTok{*}\StringTok{ }\FloatTok{1.96}\NormalTok{),}
                                                  \DataTypeTok{control =} \KeywordTok{list}\NormalTok{(}\DataTypeTok{optimizer =} \StringTok{"optim"}\NormalTok{, }
                                                                 \DataTypeTok{optmethod =} \StringTok{"Nelder-Mead"}\NormalTok{, }
                                                                 \DataTypeTok{maxit =} \DecValTok{1000}\NormalTok{), }
                                                  \DataTypeTok{verbose =}\NormalTok{ F)))}

\NormalTok{plot3.female.meta.VR <-}\StringTok{ }\NormalTok{metacombo_female.plot3.VR }\OperatorTok{%>%}
\StringTok{                        }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{model_lnVR =} \KeywordTok{map}\NormalTok{(data, }\OperatorTok{~}\StringTok{ }\NormalTok{metafor}\OperatorTok{::}\KeywordTok{rma.uni}\NormalTok{(}\DataTypeTok{yi =}\NormalTok{ .x}\OperatorTok{$}\NormalTok{lnVR, }\DataTypeTok{sei =}\NormalTok{ (.x}\OperatorTok{$}\NormalTok{lnVR_upper }\OperatorTok{-}\StringTok{ }\NormalTok{.x}\OperatorTok{$}\NormalTok{lnVR_lower) }\OperatorTok{/}\StringTok{ }\NormalTok{(}\DecValTok{2} \OperatorTok{*}\StringTok{ }\FloatTok{1.96}\NormalTok{),}
                                                \DataTypeTok{control =} \KeywordTok{list}\NormalTok{(}\DataTypeTok{optimizer =} \StringTok{"optim"}\NormalTok{, }
                                                               \DataTypeTok{optmethod =} \StringTok{"Nelder-Mead"}\NormalTok{, }
                                                               \DataTypeTok{maxit =} \DecValTok{1000}\NormalTok{), }
                                                \DataTypeTok{verbose =}\NormalTok{ F)))}

\NormalTok{plot3.female.meta.RR <-}\StringTok{ }\NormalTok{metacombo_female.plot3.RR }\OperatorTok{%>%}
\StringTok{                        }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{model_lnRR =} \KeywordTok{map}\NormalTok{(data, }\OperatorTok{~}\StringTok{ }\NormalTok{metafor}\OperatorTok{::}\KeywordTok{rma.uni}\NormalTok{(}\DataTypeTok{yi =}\NormalTok{ .x}\OperatorTok{$}\NormalTok{lnRR, }\DataTypeTok{sei =}\NormalTok{ (.x}\OperatorTok{$}\NormalTok{lnRR_upper }\OperatorTok{-}\StringTok{ }\NormalTok{.x}\OperatorTok{$}\NormalTok{lnRR_lower) }\OperatorTok{/}\StringTok{ }\NormalTok{(}\DecValTok{2} \OperatorTok{*}\StringTok{ }\FloatTok{1.96}\NormalTok{),}
                                                \DataTypeTok{control =} \KeywordTok{list}\NormalTok{(}\DataTypeTok{optimizer =} \StringTok{"optim"}\NormalTok{, }
                                                               \DataTypeTok{optmethod =} \StringTok{"Nelder-Mead"}\NormalTok{, }
                                                               \DataTypeTok{maxit =} \DecValTok{1000}\NormalTok{), }
                                                \DataTypeTok{verbose =}\NormalTok{ F)))}

\CommentTok{# Across all grouping terms #}

\NormalTok{plot3.female.meta.CVR.all <-}\StringTok{ }\NormalTok{metacombo_female.plot3.CVR.all }\OperatorTok{%>%}
\StringTok{                             }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{model_lnCVR =} \KeywordTok{map}\NormalTok{(data, }\OperatorTok{~}\StringTok{ }\NormalTok{metafor}\OperatorTok{::}\KeywordTok{rma.uni}\NormalTok{(}\DataTypeTok{yi =}\NormalTok{ .x}\OperatorTok{$}\NormalTok{lnCVR, }\DataTypeTok{sei=}\NormalTok{(.x}\OperatorTok{$}\NormalTok{lnCVR_upper}\OperatorTok{-}\NormalTok{.x}\OperatorTok{$}\NormalTok{lnCVR_lower)}\OperatorTok{/}\NormalTok{(}\DecValTok{2} \OperatorTok{*}\StringTok{ }\FloatTok{1.96}\NormalTok{),}
                                                       \DataTypeTok{control =} \KeywordTok{list}\NormalTok{(}\DataTypeTok{optimizer =} \StringTok{"optim"}\NormalTok{, }
                                                                      \DataTypeTok{optmethod =} \StringTok{"Nelder-Mead"}\NormalTok{, }
                                                                      \DataTypeTok{maxit =} \DecValTok{1000}\NormalTok{),}
                                                       \DataTypeTok{verbose =}\NormalTok{ F)))}

\NormalTok{plot3.female.meta.CVR.all <-}\StringTok{ }\NormalTok{plot3.female.meta.CVR.all }\OperatorTok{%>%}\StringTok{ }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{GroupingTerm =} \StringTok{"All"}\NormalTok{)}

\NormalTok{plot3.female.meta.VR.all <-}\StringTok{ }\NormalTok{metacombo_female.plot3.VR.all }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{model_lnVR =} \KeywordTok{map}\NormalTok{(data, }\OperatorTok{~}\StringTok{ }\NormalTok{metafor}\OperatorTok{::}\KeywordTok{rma.uni}\NormalTok{(}\DataTypeTok{yi =}\NormalTok{ .x}\OperatorTok{$}\NormalTok{lnVR, }\DataTypeTok{sei =}\NormalTok{ (.x}\OperatorTok{$}\NormalTok{lnVR_upper }\OperatorTok{-}\StringTok{ }\NormalTok{.x}\OperatorTok{$}\NormalTok{lnVR_lower) }\OperatorTok{/}\StringTok{ }\NormalTok{(}\DecValTok{2} \OperatorTok{*}\StringTok{ }\FloatTok{1.96}\NormalTok{),}
                          \DataTypeTok{control =} \KeywordTok{list}\NormalTok{(}\DataTypeTok{optimizer =} \StringTok{"optim"}\NormalTok{, }
                                         \DataTypeTok{optmethod =} \StringTok{"Nelder-Mead"}\NormalTok{, }
                                         \DataTypeTok{maxit =} \DecValTok{1000}\NormalTok{), }
                          \DataTypeTok{verbose =}\NormalTok{ F)))}

\NormalTok{plot3.female.meta.VR.all <-}\StringTok{ }\NormalTok{plot3.female.meta.VR.all }\OperatorTok{%>%}\StringTok{ }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{GroupingTerm =} \StringTok{"All"}\NormalTok{)}

\NormalTok{plot3.female.meta.RR.all <-}\StringTok{ }\NormalTok{metacombo_female.plot3.RR.all }\OperatorTok{%>%}
\StringTok{                            }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{model_lnRR =} \KeywordTok{map}\NormalTok{(data, }
                                                    \OperatorTok{~}\StringTok{ }\NormalTok{metafor}\OperatorTok{::}\KeywordTok{rma.uni}\NormalTok{(}\DataTypeTok{yi =}\NormalTok{ .x}\OperatorTok{$}\NormalTok{lnRR, }\DataTypeTok{sei =}\NormalTok{ (.x}\OperatorTok{$}\NormalTok{lnRR_upper }\OperatorTok{-}\StringTok{ }\NormalTok{.x}\OperatorTok{$}\NormalTok{lnRR_lower) }\OperatorTok{/}\StringTok{ }\NormalTok{(}\DecValTok{2} \OperatorTok{*}\StringTok{ }\FloatTok{1.96}\NormalTok{),}
                                                    \DataTypeTok{control =} \KeywordTok{list}\NormalTok{(}\DataTypeTok{optimizer =} \StringTok{"optim"}\NormalTok{, }
                                                                   \DataTypeTok{optmethod =} \StringTok{"Nelder-Mead"}\NormalTok{, }
                                                                   \DataTypeTok{maxit =} \DecValTok{1000}\NormalTok{), }
                                                    \DataTypeTok{verbose =}\NormalTok{ F)))}

\NormalTok{plot3.female.meta.RR.all <-}\StringTok{ }\NormalTok{plot3.female.meta.RR.all }\OperatorTok{%>%}\StringTok{ }
\StringTok{                            }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{GroupingTerm =} \StringTok{"All"}\NormalTok{)}

\CommentTok{# Combine with separate grouping term results}

\NormalTok{plot3.female.meta.CVR <-}\StringTok{ }\KeywordTok{bind_rows}\NormalTok{(plot3.female.meta.CVR, plot3.female.meta.CVR.all)}
\NormalTok{ plot3.female.meta.VR <-}\StringTok{ }\KeywordTok{bind_rows}\NormalTok{(plot3.female.meta.VR,   plot3.female.meta.VR.all)}
\NormalTok{ plot3.female.meta.RR <-}\StringTok{ }\KeywordTok{bind_rows}\NormalTok{(plot3.female.meta.RR,   plot3.female.meta.RR.all)}

\CommentTok{# Re-structure data for each grouping term; delete un-used variables}

\NormalTok{plot3.female.meta.CVR.b <-}\StringTok{ }\KeywordTok{as.data.frame}\NormalTok{(plot3.female.meta.CVR }\OperatorTok{%>%}\StringTok{ }
\StringTok{                                           }\KeywordTok{group_by}\NormalTok{(GroupingTerm) }\OperatorTok{%>%}
\StringTok{                                          }\KeywordTok{mutate}\NormalTok{(    }\DataTypeTok{lnCVR =} \KeywordTok{map_dbl}\NormalTok{(model_lnCVR, }\KeywordTok{pluck}\NormalTok{(}\DecValTok{2}\NormalTok{)), }
                                               \DataTypeTok{lnCVR_lower =} \KeywordTok{map_dbl}\NormalTok{(model_lnCVR, }\KeywordTok{pluck}\NormalTok{(}\DecValTok{6}\NormalTok{)),}
                                               \DataTypeTok{lnCVR_upper =} \KeywordTok{map_dbl}\NormalTok{(model_lnCVR, }\KeywordTok{pluck}\NormalTok{(}\DecValTok{7}\NormalTok{)), }
                                                  \DataTypeTok{lnCVR_se =} \KeywordTok{map_dbl}\NormalTok{(model_lnCVR, }\KeywordTok{pluck}\NormalTok{(}\DecValTok{3}\NormalTok{)),}
                                                  \DataTypeTok{lnCVR_I2 =} \KeywordTok{map_dbl}\NormalTok{(model_lnCVR, }\KeywordTok{pluck}\NormalTok{(}\StringTok{"I2"}\NormalTok{))))[, }\KeywordTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{, }\DecValTok{4}\OperatorTok{:}\DecValTok{8}\NormalTok{)]}

\NormalTok{add.row.hearing <-}\StringTok{ }\KeywordTok{as.data.frame}\NormalTok{(}\KeywordTok{t}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"Hearing"}\NormalTok{, }\OtherTok{NA}\NormalTok{, }\OtherTok{NA}\NormalTok{, }\OtherTok{NA}\NormalTok{, }\OtherTok{NA}\NormalTok{,}\OtherTok{NA}\NormalTok{))) }\OperatorTok{%>%}\StringTok{ }
\StringTok{                                 }\KeywordTok{setNames}\NormalTok{(}\KeywordTok{names}\NormalTok{(plot3.female.meta.CVR.b))}

\NormalTok{plot3.female.meta.CVR.b <-}\StringTok{ }\KeywordTok{bind_rows}\NormalTok{(plot3.female.meta.CVR.b, add.row.hearing)}
\NormalTok{plot3.female.meta.CVR.b <-}\StringTok{ }\NormalTok{plot3.female.meta.CVR.b[}\KeywordTok{order}\NormalTok{(plot3.female.meta.CVR.b}\OperatorTok{$}\NormalTok{GroupingTerm), ]}

\NormalTok{plot3.female.meta.VR.b <-}\StringTok{ }\KeywordTok{as.data.frame}\NormalTok{(plot3.female.meta.VR }\OperatorTok{%>%}\StringTok{ }
\StringTok{                                        }\KeywordTok{group_by}\NormalTok{(GroupingTerm) }\OperatorTok{%>%}
\StringTok{                                        }\KeywordTok{mutate}\NormalTok{(      }\DataTypeTok{lnVR =} \KeywordTok{map_dbl}\NormalTok{(model_lnVR, }\KeywordTok{pluck}\NormalTok{(}\DecValTok{2}\NormalTok{)), }
                                               \DataTypeTok{lnVR_lower =} \KeywordTok{map_dbl}\NormalTok{(model_lnVR, }\KeywordTok{pluck}\NormalTok{(}\DecValTok{6}\NormalTok{)),}
                                               \DataTypeTok{lnVR_upper =} \KeywordTok{map_dbl}\NormalTok{(model_lnVR, }\KeywordTok{pluck}\NormalTok{(}\DecValTok{7}\NormalTok{)), }
                                                  \DataTypeTok{lnVR_se =} \KeywordTok{map_dbl}\NormalTok{(model_lnVR, }\KeywordTok{pluck}\NormalTok{(}\DecValTok{3}\NormalTok{)),}
                                                  \DataTypeTok{lnVR_I2 =} \KeywordTok{map_dbl}\NormalTok{(model_lnVR, }\KeywordTok{pluck}\NormalTok{(}\StringTok{"I2"}\NormalTok{))))[, }\KeywordTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{, }\DecValTok{4}\OperatorTok{:}\DecValTok{8}\NormalTok{)]}

\NormalTok{plot3.female.meta.VR.b <-}\StringTok{ }\NormalTok{plot3.female.meta.VR.b[}\KeywordTok{order}\NormalTok{(plot3.female.meta.VR.b}\OperatorTok{$}\NormalTok{GroupingTerm), ]}

\NormalTok{plot3.female.meta.RR.b <-}\StringTok{ }\KeywordTok{as.data.frame}\NormalTok{(plot3.female.meta.RR }\OperatorTok{%>%}\StringTok{ }
\StringTok{                                        }\KeywordTok{group_by}\NormalTok{(GroupingTerm) }\OperatorTok{%>%}
\StringTok{                                        }\KeywordTok{mutate}\NormalTok{(      }\DataTypeTok{lnRR =} \KeywordTok{map_dbl}\NormalTok{(model_lnRR, }\KeywordTok{pluck}\NormalTok{(}\DecValTok{2}\NormalTok{)), }
                                               \DataTypeTok{lnRR_lower =} \KeywordTok{map_dbl}\NormalTok{(model_lnRR, }\KeywordTok{pluck}\NormalTok{(}\DecValTok{6}\NormalTok{)), }
                                               \DataTypeTok{lnRR_upper =} \KeywordTok{map_dbl}\NormalTok{(model_lnRR, }\KeywordTok{pluck}\NormalTok{(}\DecValTok{7}\NormalTok{)), }
                                                  \DataTypeTok{lnRR_se =} \KeywordTok{map_dbl}\NormalTok{(model_lnRR, }\KeywordTok{pluck}\NormalTok{(}\DecValTok{3}\NormalTok{)),}
                                                  \DataTypeTok{lnRR_I2 =} \KeywordTok{map_dbl}\NormalTok{(model_lnRR, }\KeywordTok{pluck}\NormalTok{(}\StringTok{"I2"}\NormalTok{))))[, }\KeywordTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{, }\DecValTok{4}\OperatorTok{:}\DecValTok{8}\NormalTok{)]}

\NormalTok{plot3.female.meta.RR.b <-}\StringTok{ }\NormalTok{plot3.female.meta.RR.b[}\KeywordTok{order}\NormalTok{(plot3.female.meta.RR.b}\OperatorTok{$}\NormalTok{GroupingTerm), ]}

\NormalTok{overall.female.plot3 <-}\StringTok{ }\KeywordTok{full_join}\NormalTok{(plot3.female.meta.CVR.b, plot3.female.meta.VR.b)}
\NormalTok{overall.female.plot3 <-}\StringTok{ }\KeywordTok{full_join}\NormalTok{(overall.female.plot3, plot3.female.meta.RR.b)}

\NormalTok{overall.female.plot3}\OperatorTok{$}\NormalTok{GroupingTerm <-}\StringTok{ }\KeywordTok{factor}\NormalTok{(overall.female.plot3}\OperatorTok{$}\NormalTok{GroupingTerm, }
                                            \DataTypeTok{levels =} \KeywordTok{c}\NormalTok{(}\StringTok{"Behaviour"}\NormalTok{, }\StringTok{"Morphology"}\NormalTok{, }\StringTok{"Metabolism"}\NormalTok{, }\StringTok{"Physiology"}\NormalTok{, }
                                                       \StringTok{"Immunology"}\NormalTok{, }\StringTok{"Hematology"}\NormalTok{, }\StringTok{"Heart"}\NormalTok{, }\StringTok{"Hearing"}\NormalTok{, }\StringTok{"Eye"}\NormalTok{, }\StringTok{"All"}\NormalTok{))}
\NormalTok{overall.female.plot3}\OperatorTok{$}\NormalTok{GroupingTerm <-}\StringTok{ }\KeywordTok{factor}\NormalTok{(overall.female.plot3}\OperatorTok{$}\NormalTok{GroupingTerm, }
                                            \KeywordTok{rev}\NormalTok{(}\KeywordTok{levels}\NormalTok{(overall.female.plot3}\OperatorTok{$}\NormalTok{GroupingTerm)))}

\CommentTok{# Re-structuring data for plotting}

\NormalTok{overall3.female.sig <-}\StringTok{ }\KeywordTok{gather}\NormalTok{(overall.female.plot3, parameter, value, }\KeywordTok{c}\NormalTok{(lnCVR, lnRR), }\DataTypeTok{factor_key =} \OtherTok{TRUE}\NormalTok{) }

\NormalTok{lnCVR.ci <-}\StringTok{ }\NormalTok{overall3.female.sig }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{filter}\NormalTok{(parameter }\OperatorTok{==}\StringTok{ "lnCVR"}\NormalTok{) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{ci.low =}\NormalTok{ lnCVR_lower, }
         \DataTypeTok{ci.high =}\NormalTok{ lnCVR_upper)}

\CommentTok{# lnVR.ci <- overall3.female.sig  %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)}

\NormalTok{lnRR.ci <-}\StringTok{ }\NormalTok{overall3.female.sig }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{filter}\NormalTok{(parameter }\OperatorTok{==}\StringTok{ "lnRR"}\NormalTok{) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{ci.low =}\NormalTok{ lnRR_lower, }\DataTypeTok{ci.high =}\NormalTok{ lnRR_upper)}

\NormalTok{overall4.female.sig <-}\StringTok{ }\KeywordTok{bind_rows}\NormalTok{(lnCVR.ci, lnRR.ci) }\OperatorTok{%>%}\StringTok{ }
\StringTok{                       }\KeywordTok{select}\NormalTok{(GroupingTerm, parameter, value, ci.low, ci.high) }\CommentTok{# lnVR.ci,}

\NormalTok{overall4.female.sig}\OperatorTok{$}\NormalTok{label <-}\StringTok{ "CI not overlapping zero"}

\CommentTok{# PLOT preparation for Fig5B: all significant results (CI not overlapping zero, female )}

\NormalTok{Metameta_Fig3_female.sig  <-}\StringTok{ }\NormalTok{overall4.female.sig }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{ggplot}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{y =}\NormalTok{ GroupingTerm, }\DataTypeTok{x =}\NormalTok{ value)) }\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_errorbarh}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}
    \DataTypeTok{xmin =}\NormalTok{ ci.low,}
    \DataTypeTok{xmax =}\NormalTok{ ci.high),}
  \DataTypeTok{height =} \FloatTok{0.1}\NormalTok{, }\DataTypeTok{show.legend =} \OtherTok{FALSE}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_point}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{shape =}\NormalTok{ parameter),}
    \DataTypeTok{fill =} \StringTok{"salmon1"}\NormalTok{, }\DataTypeTok{color =} \StringTok{"salmon1"}\NormalTok{, }\DataTypeTok{size =} \FloatTok{2.2}\NormalTok{,}
    \DataTypeTok{show.legend =} \OtherTok{FALSE}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{scale_x_continuous}\NormalTok{(}
    \DataTypeTok{limits =} \KeywordTok{c}\NormalTok{(}\OperatorTok{-}\FloatTok{0.4}\NormalTok{, }\DecValTok{0}\NormalTok{),}
    \DataTypeTok{breaks =} \KeywordTok{c}\NormalTok{(}\OperatorTok{-}\FloatTok{0.3}\NormalTok{, }\DecValTok{0}\NormalTok{),}
    \DataTypeTok{name =} \StringTok{"Effect size"}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_vline}\NormalTok{(}
    \DataTypeTok{xintercept =} \DecValTok{0}\NormalTok{,}
    \DataTypeTok{color =} \StringTok{"black"}\NormalTok{,}
    \DataTypeTok{linetype =} \StringTok{"dashed"}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{facet_grid}\NormalTok{(}
    \DataTypeTok{cols =} \KeywordTok{vars}\NormalTok{(parameter), }\CommentTok{# rows = vars(label),}
    \CommentTok{# labeller = label_wrap_gen(width = 23),}
    \DataTypeTok{scales =} \StringTok{"free"}\NormalTok{,}
    \DataTypeTok{space =} \StringTok{"free"}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{theme_bw}\NormalTok{() }\OperatorTok{+}
\StringTok{  }\KeywordTok{theme}\NormalTok{(}
    \DataTypeTok{strip.text.y =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{angle =} \DecValTok{270}\NormalTok{, }\DataTypeTok{size =} \DecValTok{10}\NormalTok{, }\DataTypeTok{margin =} \KeywordTok{margin}\NormalTok{(}\DataTypeTok{t =} \DecValTok{15}\NormalTok{, }\DataTypeTok{r =} \DecValTok{15}\NormalTok{, }\DataTypeTok{b =} \DecValTok{15}\NormalTok{, }\DataTypeTok{l =} \DecValTok{15}\NormalTok{)),}
    \DataTypeTok{strip.text.x =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{size =} \DecValTok{12}\NormalTok{),}
    \DataTypeTok{strip.background =} \KeywordTok{element_rect}\NormalTok{(}\DataTypeTok{colour =} \OtherTok{NULL}\NormalTok{, }\DataTypeTok{linetype =} \StringTok{"blank"}\NormalTok{, }\DataTypeTok{fill =} \StringTok{"gray90"}\NormalTok{),}
    \DataTypeTok{text =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{size =} \DecValTok{14}\NormalTok{),}
    \DataTypeTok{panel.spacing =} \KeywordTok{unit}\NormalTok{(}\FloatTok{0.5}\NormalTok{, }\StringTok{"lines"}\NormalTok{),}
    \DataTypeTok{panel.border =} \KeywordTok{element_blank}\NormalTok{(),}
    \DataTypeTok{axis.line =} \KeywordTok{element_line}\NormalTok{(),}
    \DataTypeTok{panel.grid.major.x =} \KeywordTok{element_line}\NormalTok{(}\DataTypeTok{linetype =} \StringTok{"solid"}\NormalTok{, }\DataTypeTok{colour =} \StringTok{"gray95"}\NormalTok{),}
    \DataTypeTok{panel.grid.major.y =} \KeywordTok{element_line}\NormalTok{(}\DataTypeTok{linetype =} \StringTok{"solid"}\NormalTok{, }\DataTypeTok{color =} \StringTok{"gray95"}\NormalTok{),}
    \DataTypeTok{panel.grid.minor.y =} \KeywordTok{element_blank}\NormalTok{(),}
    \DataTypeTok{panel.grid.minor.x =} \KeywordTok{element_blank}\NormalTok{(),}
    \DataTypeTok{legend.title =} \KeywordTok{element_blank}\NormalTok{(),}
    \DataTypeTok{axis.title.x =} \KeywordTok{element_blank}\NormalTok{(),}
    \DataTypeTok{axis.title.y =} \KeywordTok{element_blank}\NormalTok{()}
\NormalTok{  )}

\CommentTok{# Metameta_Fig3_female.sig #(Figure 5B left panel)}
\end{Highlighting}
\end{Shaded}

\hypertarget{figure-5}{%
\subsection{Figure 5}\label{figure-5}}

Sex biases in trait values across trait groups (Step J in Figure
@ref(fig:FigG1)). The panels in A show differences in the number of
affected traits, in variance (lnCVR) and means (lnRR), where there is a
significant difference between the sexes (i.e CI not overlapping zero).
Panel B shows results for the sex bias in those traits that differ
between the sexes (second-order meta-analysis). Triangles represent sex
bias in means (response ratio) and black circles differences in the
coefficient of variation ratio (mean-adjusted variability). The
orange-red bars represent trait groups with a female bias, blue-green
bars male-biased traits.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Joining the Parts:}

\NormalTok{Fig5B <-}\StringTok{ }\KeywordTok{ggarrange}\NormalTok{(Metameta_Fig3_female.sig, Metameta_Fig3_male.sig, }\DataTypeTok{ncol =} \DecValTok{2}\NormalTok{, }\DataTypeTok{nrow =} \DecValTok{1}\NormalTok{, }
    \DataTypeTok{widths =} \KeywordTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{, }\FloatTok{1.2}\NormalTok{), }\DataTypeTok{heights =} \KeywordTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{, }\DecValTok{1}\NormalTok{))}

\NormalTok{Fig5B <-}\StringTok{ }\KeywordTok{annotate_figure}\NormalTok{(Fig5B, }\DataTypeTok{bottom =} \KeywordTok{text_grob}\NormalTok{(}\StringTok{"Effect Size"}\NormalTok{, }\DataTypeTok{color =} \StringTok{"black"}\NormalTok{, }
    \DataTypeTok{face =} \StringTok{"plain"}\NormalTok{, }\DataTypeTok{size =} \DecValTok{14}\NormalTok{))}

\NormalTok{Fig5 <-}\StringTok{ }\KeywordTok{ggarrange}\NormalTok{(malebias_Fig2_sigtraits, Fig5B, }\DataTypeTok{ncol =} \DecValTok{1}\NormalTok{, }\DataTypeTok{nrow =} \DecValTok{2}\NormalTok{, }\DataTypeTok{widths =} \KeywordTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{, }
    \FloatTok{1.1}\NormalTok{), }\DataTypeTok{heights =} \KeywordTok{c}\NormalTok{(}\FloatTok{1.1}\NormalTok{, }\DecValTok{1}\NormalTok{), }\DataTypeTok{labels =} \KeywordTok{c}\NormalTok{(}\StringTok{"A"}\NormalTok{, }\StringTok{"B"}\NormalTok{))}
\NormalTok{Fig5}
\end{Highlighting}
\end{Shaded}

\includegraphics{MouseSexDiffApril20_2020_files/figure-latex/Fig5-1.pdf}

\hypertarget{supplemental-figures}{%
\section{Supplemental Figures}\label{supplemental-figures}}

\hypertarget{figure-5.1}{%
\subsection{Figure 5.1}\label{figure-5.1}}

Figure @ref(fig:FigS1) is similar to Figure 4 in the main article.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{#### Combined Figure S1: overall Count data, Meta anlysis results, Heterogeneity}

\NormalTok{FigS1 <-}\StringTok{ }\KeywordTok{ggarrange}\NormalTok{(malebias_FigS1_alltraits, Metameta_FigS1_alltraits, HeteroS1, }
    \DataTypeTok{nrow =} \DecValTok{3}\NormalTok{, }\DataTypeTok{align =} \StringTok{"v"}\NormalTok{, }\DataTypeTok{heights =} \KeywordTok{c}\NormalTok{(}\FloatTok{1.1}\NormalTok{, }\DecValTok{1}\NormalTok{, }\DecValTok{1}\NormalTok{), }\DataTypeTok{labels =} \KeywordTok{c}\NormalTok{(}\StringTok{"A"}\NormalTok{, }\StringTok{"B"}\NormalTok{, }\StringTok{"C"}\NormalTok{))}
\NormalTok{FigS1}
\end{Highlighting}
\end{Shaded}

\begin{figure}
\centering
\includegraphics{MouseSexDiffApril20_2020_files/figure-latex/FigS1-1.pdf}
\caption{Numbers of either male (blue-green bars) or female (orange-red
bars) biased traits (Panel A) across functional groups, this time for
lnCVR (left hand side), lnVR (middle) and lnRR (right hand side). Panel
B shows effect sizes from separate meta-analysis for each functional
group, and Panel C contains results of heterogeneity analyses. All three
panels represent results evaluated across all traits.}
\end{figure}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# ggsave('FigS1_OverallResults.pdf', plot = FigS1, width = 6, height = 7)}
\end{Highlighting}
\end{Shaded}

\hypertarget{figure-5.2}{%
\subsection{Figure 5.2}\label{figure-5.2}}

Figure @ref(fig:FigS2) is an extension of sex biases, as shown in Figure
5 in the main text. Here, we include data on lnVR (middle panel), as
well as athe second method of sex-differences comparison.

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{library}\NormalTok{(ggpubr)}
\NormalTok{FigS2b <-}\StringTok{ }\KeywordTok{ggarrange}\NormalTok{(Metameta_FigS2_female.sig, Metameta_FigS2_male.sig, }\DataTypeTok{ncol =} \DecValTok{2}\NormalTok{, }
    \DataTypeTok{nrow =} \DecValTok{1}\NormalTok{, }\DataTypeTok{widths =} \KeywordTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{, }\FloatTok{1.3}\NormalTok{), }\DataTypeTok{heights =} \KeywordTok{c}\NormalTok{(}\FloatTok{1.2}\NormalTok{, }\FloatTok{1.2}\NormalTok{))}

\NormalTok{FigS2d <-}\StringTok{ }\KeywordTok{ggarrange}\NormalTok{(Metameta_Fig3_female.perc, Metameta_Fig3_male.perc, }\DataTypeTok{ncol =} \DecValTok{2}\NormalTok{, }
    \DataTypeTok{nrow =} \DecValTok{1}\NormalTok{, }\DataTypeTok{widths =} \KeywordTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{, }\FloatTok{1.2}\NormalTok{), }\DataTypeTok{heights =} \KeywordTok{c}\NormalTok{(}\FloatTok{1.1}\NormalTok{, }\FloatTok{1.1}\NormalTok{))}

\CommentTok{# end combination Figure 5}
\NormalTok{FigS2 <-}\StringTok{ }\KeywordTok{ggarrange}\NormalTok{(malebias_FigS2_sigtraits, malebias_Fig2_over10, FigS2b, FigS2d, }
    \DataTypeTok{ncol =} \DecValTok{1}\NormalTok{, }\DataTypeTok{nrow =} \DecValTok{4}\NormalTok{, }\DataTypeTok{heights =} \KeywordTok{c}\NormalTok{(}\FloatTok{2.5}\NormalTok{, }\FloatTok{2.2}\NormalTok{, }\FloatTok{2.1}\NormalTok{, }\DecValTok{2}\NormalTok{), }\DataTypeTok{labels =} \KeywordTok{c}\NormalTok{(}\StringTok{"A"}\NormalTok{, }\StringTok{" "}\NormalTok{, }\StringTok{"B"}\NormalTok{, }
        \StringTok{" "}\NormalTok{))}
\NormalTok{FigS2}
\end{Highlighting}
\end{Shaded}

\begin{figure}
\centering
\includegraphics{MouseSexDiffApril20_2020_files/figure-latex/FigS2-1.pdf}
\caption{A) Differences in numbers of affected traits, in variance
(lnCVR and lnVR) and means (lnRR), where there's a significant
difference between the sexes (i.e CI not overlapping zero), and where
the sex bias is greater than 10\% difference (regardless of
significance). Panel B depicts results for the sex bias in those traits
that differ between the sexes (second-order meta-analysis). Triangles
represent sex bias in means (response ratio) and black circles
differences in the coefficient of variation ratio (mean-adjusted
variability). The orange-red bars represent trait groups with a female
bias, blue-green bars male-biased traits.}
\end{figure}

\hypertarget{supplemental-tables}{%
\section{Supplemental Tables}\label{supplemental-tables}}

\hypertarget{table-6.1}{%
\subsection{Table 6.1}\label{table-6.1}}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{kable}\NormalTok{(ST1, }\DataTypeTok{caption =} \StringTok{"Summary of the available numbers of male and female mice from each strain and originating institution."}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{    }\KeywordTok{kable_styling}\NormalTok{() }\OperatorTok{%>%}\StringTok{ }\KeywordTok{scroll_box}\NormalTok{(}\DataTypeTok{width =} \StringTok{"100%"}\NormalTok{, }\DataTypeTok{height =} \StringTok{"200px"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{table}

\caption{\label{tab:Table1}Summary of the available numbers of male and female mice from each strain and originating institution.}
\centering
\begin{tabular}[t]{l|l|l|r}
\hline
production\_center &amp; strain\_name &amp; sex &amp; n\\
\hline
BCM &amp; C57BL/6N &amp; female &amp; 653\\
\hline
BCM &amp; C57BL/6N &amp; male &amp; 639\\
\hline
BCM &amp; C57BL/6N;C57BL/6NTac &amp; female &amp; 47\\
\hline
BCM &amp; C57BL/6N;C57BL/6NTac &amp; male &amp; 52\\
\hline
BCM &amp; C57BL/6NCrl &amp; female &amp; 4\\
\hline
BCM &amp; C57BL/6NCrl &amp; male &amp; 2\\
\hline
BCM &amp; C57BL/6NJ &amp; female &amp; 6\\
\hline
BCM &amp; C57BL/6NJ &amp; male &amp; 6\\
\hline
BCM &amp; C57BL/6NTac &amp; female &amp; 1\\
\hline
BCM &amp; C57BL/6NTac &amp; male &amp; 5\\
\hline
HMGU &amp; C57BL/6NCrl &amp; female &amp; 313\\
\hline
HMGU &amp; C57BL/6NCrl &amp; male &amp; 311\\
\hline
HMGU &amp; C57BL/6NTac &amp; female &amp; 1045\\
\hline
HMGU &amp; C57BL/6NTac &amp; male &amp; 1062\\
\hline
ICS &amp; C57BL/6N &amp; female &amp; 1025\\
\hline
ICS &amp; C57BL/6N &amp; male &amp; 1050\\
\hline
JAX &amp; C57BL/6NJ &amp; female &amp; 2025\\
\hline
JAX &amp; C57BL/6NJ &amp; male &amp; 2022\\
\hline
KMPC &amp; C57BL/6N;C57BL/6NTac &amp; female &amp; 271\\
\hline
KMPC &amp; C57BL/6N;C57BL/6NTac &amp; male &amp; 266\\
\hline
MARC &amp; C57BL/6N &amp; female &amp; 936\\
\hline
MARC &amp; C57BL/6N &amp; male &amp; 926\\
\hline
MRC Harwell &amp; C57BL/6NTac &amp; female &amp; 2639\\
\hline
MRC Harwell &amp; C57BL/6NTac &amp; male &amp; 2661\\
\hline
MRC Harwell &amp; C57BL/6NTac &amp; no\_data &amp; 3\\
\hline
RBRC &amp; C57BL/6NJcl &amp; female &amp; 222\\
\hline
RBRC &amp; C57BL/6NJcl &amp; male &amp; 222\\
\hline
RBRC &amp; C57BL/6NTac &amp; female &amp; 526\\
\hline
RBRC &amp; C57BL/6NTac &amp; male &amp; 523\\
\hline
TCP &amp; C57BL/6NCrl &amp; female &amp; 552\\
\hline
TCP &amp; C57BL/6NCrl &amp; male &amp; 524\\
\hline
TCP &amp; C57BL6/NCrl &amp; female &amp; 2\\
\hline
TCP &amp; C57BL6/NCrl &amp; male &amp; 2\\
\hline
UC Davis &amp; C57BL/6N &amp; male &amp; 1\\
\hline
UC Davis &amp; C57BL/6NCrl &amp; female &amp; 1155\\
\hline
UC Davis &amp; C57BL/6NCrl &amp; male &amp; 1158\\
\hline
WTSI &amp; B6Brd;B6Dnk;B6N-Tyr<c-brd> &amp; female &amp; 97\\
\hline
WTSI &amp; B6Brd;B6Dnk;B6N-Tyr<c-brd> &amp; male &amp; 87\\
\hline
WTSI &amp; C57BL/6J-Tyr<c-brd> or C57BL/6NTac/USA &amp; male &amp; 3\\
\hline
WTSI &amp; C57BL/6N &amp; female &amp; 1951\\
\hline
WTSI &amp; C57BL/6N &amp; male &amp; 2008\\
\hline
WTSI &amp; C57BL/6N;C57BL/6NTac &amp; female &amp; 41\\
\hline
WTSI &amp; C57BL/6N;C57BL/6NTac &amp; male &amp; 7\\
\hline
WTSI &amp; C57BL/6NCrl &amp; male &amp; 13\\
\hline
WTSI &amp; C57BL/6NTac &amp; female &amp; 49\\
\hline
WTSI &amp; C57BL/6NTac &amp; male &amp; 34\\
\hline
\end{tabular}
\end{table}

\hypertarget{table-6.2}{%
\subsection{Table 6.2}\label{table-6.2}}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Table detailing numbers of correlated and uncorrelated traits}
\KeywordTok{kable}\NormalTok{(}\KeywordTok{cbind}\NormalTok{(meta1 }\OperatorTok{%>%}\StringTok{ }\KeywordTok{count}\NormalTok{(parameter_group)), }\DataTypeTok{caption =} \StringTok{"Trait categories (parameter_group) and the number of correlated traits within these categories. Traits were meta-analysed using robumeta"}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{    }\KeywordTok{kable_styling}\NormalTok{() }\OperatorTok{%>%}\StringTok{ }\KeywordTok{scroll_box}\NormalTok{(}\DataTypeTok{width =} \StringTok{"100%"}\NormalTok{, }\DataTypeTok{height =} \StringTok{"200px"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\textbackslash{}begin\{table\}

\textbackslash{}caption\{\label{tab:TableS2}Trait categories
(parameter\_group) and the number of correlated traits within these
categories. Traits were meta-analysed using robumeta\} \centering

\begin{tabular}[t]{l|r}
\hline
parameter\_group &amp; n\\
\hline
12khz-evoked abr threshold &amp; 1\\
\hline
18khz-evoked abr threshold &amp; 1\\
\hline
24khz-evoked abr threshold &amp; 1\\
\hline
30khz-evoked abr threshold &amp; 1\\
\hline
6khz-evoked abr threshold &amp; 1\\
\hline
alanine aminotransferase &amp; 1\\
\hline
albumin &amp; 1\\
\hline
alkaline phosphatase &amp; 1\\
\hline
alpha-amylase &amp; 1\\
\hline
area under glucose response curve &amp; 1\\
\hline
aspartate aminotransferase &amp; 1\\
\hline
B cells &amp; 4\\
\hline
basophil cell count &amp; 1\\
\hline
basophil differential count &amp; 1\\
\hline
bmc/body weight &amp; 1\\
\hline
body length &amp; 1\\
\hline
body temp &amp; 1\\
\hline
body weight &amp; 1\\
\hline
body weight after experiment &amp; 1\\
\hline
body weight before experiment &amp; 1\\
\hline
bone area &amp; 1\\
\hline
bone mineral content (excluding skull) &amp; 1\\
\hline
bone mineral density (excluding skull) &amp; 1\\
\hline
calcium &amp; 1\\
\hline
cardiac output &amp; 1\\
\hline
cd4 nkt &amp; 6\\
\hline
cd4 t &amp; 7\\
\hline
cd8 nkt &amp; 6\\
\hline
cd8 t &amp; 7\\
\hline
cdcs &amp; 2\\
\hline
center average speed &amp; 1\\
\hline
center distance travelled &amp; 1\\
\hline
center permanence time &amp; 1\\
\hline
center resting time &amp; 1\\
\hline
chloride &amp; 1\\
\hline
click-evoked abr threshold &amp; 1\\
\hline
creatine kinase &amp; 1\\
\hline
creatinine &amp; 1\\
\hline
cv &amp; 1\\
\hline
distance travelled - total &amp; 1\\
\hline
dn nkt &amp; 6\\
\hline
dn t &amp; 7\\
\hline
ejection fraction &amp; 1\\
\hline
end-diastolic diameter &amp; 1\\
\hline
end-systolic diameter &amp; 1\\
\hline
eosinophils &amp; 3\\
\hline
fasted blood glucose concentration &amp; 1\\
\hline
fat mass &amp; 1\\
\hline
fat/body weight &amp; 1\\
\hline
follicular b cells &amp; 2\\
\hline
forelimb and hindlimb grip strength measurement mean &amp; 1\\
\hline
forelimb grip strength measurement mean &amp; 1\\
\hline
fractional shortening &amp; 1\\
\hline
free fatty acids &amp; 1\\
\hline
fructosamine &amp; 1\\
\hline
glucose &amp; 1\\
\hline
hdl-cholesterol &amp; 1\\
\hline
heart weight &amp; 1\\
\hline
heart weight normalised against body weight &amp; 1\\
\hline
hematocrit &amp; 1\\
\hline
hemoglobin &amp; 1\\
\hline
hr &amp; 1\\
\hline
hrv &amp; 1\\
\hline
initial response to glucose challenge &amp; 1\\
\hline
insulin &amp; 1\\
\hline
iron &amp; 1\\
\hline
lactate dehydrogenase &amp; 1\\
\hline
latency to center entry &amp; 1\\
\hline
ldl-cholesterol &amp; 1\\
\hline
lean mass &amp; 1\\
\hline
lean/body weight &amp; 1\\
\hline
left anterior chamber depth &amp; 1\\
\hline
left corneal thickness &amp; 1\\
\hline
left inner nuclear layer &amp; 1\\
\hline
left outer nuclear layer &amp; 1\\
\hline
left posterior chamber depth &amp; 1\\
\hline
left total retinal thickness &amp; 1\\
\hline
locomotor activity &amp; 1\\
\hline
luc &amp; 2\\
\hline
lvawd &amp; 1\\
\hline
lvaws &amp; 1\\
\hline
lvidd &amp; 1\\
\hline
lvids &amp; 1\\
\hline
lvpwd &amp; 1\\
\hline
lvpws &amp; 1\\
\hline
lymphocytes &amp; 2\\
\hline
magnesium &amp; 1\\
\hline
mean cell hemoglobin concentration &amp; 1\\
\hline
mean cell volume &amp; 1\\
\hline
mean corpuscular hemoglobin &amp; 1\\
\hline
mean platelet volume &amp; 1\\
\hline
mean r amplitude &amp; 1\\
\hline
mean sr amplitude &amp; 1\\
\hline
monocytes &amp; 3\\
\hline
neutrophils &amp; 3\\
\hline
nk cells &amp; 6\\
\hline
nkt cells &amp; 4\\
\hline
number of center entries &amp; 1\\
\hline
number of rears - total &amp; 1\\
\hline
others &amp; 1\\
\hline
pdcs &amp; 1\\
\hline
percentage center time &amp; 1\\
\hline
percentage of live gated events &amp; 2\\
\hline
periphery average speed &amp; 1\\
\hline
periphery distance travelled &amp; 1\\
\hline
periphery permanence time &amp; 1\\
\hline
periphery resting time &amp; 1\\
\hline
phosphorus &amp; 1\\
\hline
platelet count &amp; 1\\
\hline
pnn5(6&gt;ms) &amp; 1\\
\hline
potassium &amp; 1\\
\hline
pq &amp; 1\\
\hline
pr &amp; 1\\
\hline
pre-pulse inhibition &amp; 5\\
\hline
qrs &amp; 1\\
\hline
qtc &amp; 1\\
\hline
qtc dispersion &amp; 1\\
\hline
red blood cell count &amp; 1\\
\hline
red blood cell distribution width &amp; 1\\
\hline
respiration rate &amp; 1\\
\hline
respiratory exchange ratio &amp; 1\\
\hline
response amplitude &amp; 10\\
\hline
right anterior chamber depth &amp; 1\\
\hline
right corneal thickness &amp; 1\\
\hline
right inner nuclear layer &amp; 1\\
\hline
right outer nuclear layer &amp; 1\\
\hline
right posterior chamber depth &amp; 1\\
\hline
right total retinal thickness &amp; 1\\
\hline
rmssd &amp; 1\\
\hline
rp macrophage (cd19-  cd11c-) &amp; 1\\
\hline
rr &amp; 1\\
\hline
sodium &amp; 1\\
\hline
spleen weight &amp; 1\\
\hline
st &amp; 1\\
\hline
stroke volume &amp; 1\\
\hline
t cells &amp; 3\\
\hline
tibia length &amp; 1\\
\hline
total bilirubin &amp; 1\\
\hline
total cholesterol &amp; 1\\
\hline
total food intake &amp; 1\\
\hline
total protein &amp; 1\\
\hline
total water intake &amp; 1\\
\hline
triglycerides &amp; 1\\
\hline
urea (blood urea nitrogen - bun) &amp; 1\\
\hline
uric acid &amp; 1\\
\hline
white blood cell count &amp; 1\\
\hline
whole arena average speed &amp; 1\\
\hline
whole arena resting time &amp; 1\\
\hline
\end{tabular}

\textbackslash{}end\{table\}

\hypertarget{table-6.3}{%
\subsection{Table 6.3}\label{table-6.3}}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{kable}\NormalTok{(metacombo, }\DataTypeTok{digits =} \DecValTok{3}\NormalTok{, }\DataTypeTok{caption =} \StringTok{"We use this corrected (for correlated traits) results table, which contains each of the meta-analytic means for all effect sizes of interest, for further analyses.  We further use this table as part of the Shiny App, which is able to provide the percentage differences between males and females for mean, variance and coefficient of variance."}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{    }\KeywordTok{kable_styling}\NormalTok{() }\OperatorTok{%>%}\StringTok{ }\KeywordTok{scroll_box}\NormalTok{(}\DataTypeTok{width =} \StringTok{"100%"}\NormalTok{, }\DataTypeTok{height =} \StringTok{"200px"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{table}

\caption{\label{tab:Table3}We use this corrected (for correlated traits) results table, which contains each of the meta-analytic means for all effect sizes of interest, for further analyses.  We further use this table as part of the Shiny App, which is able to provide the percentage differences between males and females for mean, variance and coefficient of variance.}
\centering
\begin{tabular}[t]{l|r|l|l|r|r|r|r|r|r|r|r|r|r|r|r}
\hline
parameter\_group &amp; counts &amp; procedure &amp; GroupingTerm &amp; lnCVR &amp; lnCVR\_lower &amp; lnCVR\_upper &amp; lnCVR\_se &amp; lnVR &amp; lnVR\_lower &amp; lnVR\_upper &amp; lnVR\_se &amp; lnRR &amp; lnRR\_lower &amp; lnRR\_upper &amp; lnRR\_se\\
\hline
pre-pulse inhibition &amp; 5 &amp; Acoustic Startle and Pre-pulse Inhibition (PPI) &amp; Behaviour &amp; 0.023 &amp; -0.080 &amp; 0.127 &amp; 0.037 &amp; 0.009 &amp; -0.036 &amp; 0.055 &amp; 0.014 &amp; -0.005 &amp; -0.043 &amp; 0.032 &amp; 0.013\\
\hline
B cells &amp; 4 &amp; Immunophenotyping &amp; Immunology &amp; -0.094 &amp; -0.250 &amp; 0.062 &amp; 0.043 &amp; -0.100 &amp; -0.207 &amp; 0.008 &amp; 0.025 &amp; -0.003 &amp; -0.130 &amp; 0.125 &amp; 0.039\\
\hline
cd4 nkt &amp; 6 &amp; Immunophenotyping &amp; Immunology &amp; -0.029 &amp; -0.057 &amp; -0.001 &amp; 0.010 &amp; -0.202 &amp; -0.310 &amp; -0.094 &amp; 0.033 &amp; -0.234 &amp; -0.401 &amp; -0.068 &amp; 0.063\\
\hline
cd4 t &amp; 7 &amp; Immunophenotyping &amp; Immunology &amp; -0.151 &amp; -0.243 &amp; -0.059 &amp; 0.036 &amp; -0.170 &amp; -0.263 &amp; -0.077 &amp; 0.035 &amp; -0.003 &amp; -0.041 &amp; 0.035 &amp; 0.015\\
\hline
cd8 nkt &amp; 6 &amp; Immunophenotyping &amp; Immunology &amp; -0.042 &amp; -0.078 &amp; -0.007 &amp; 0.012 &amp; -0.030 &amp; -0.182 &amp; 0.122 &amp; 0.053 &amp; 0.004 &amp; -0.057 &amp; 0.064 &amp; 0.021\\
\hline
cd8 t &amp; 7 &amp; Immunophenotyping &amp; Immunology &amp; -0.122 &amp; -0.218 &amp; -0.027 &amp; 0.036 &amp; -0.158 &amp; -0.234 &amp; -0.082 &amp; 0.027 &amp; -0.042 &amp; -0.051 &amp; -0.032 &amp; 0.002\\
\hline
cdcs &amp; 2 &amp; Immunophenotyping &amp; Immunology &amp; -0.036 &amp; -0.359 &amp; 0.286 &amp; 0.025 &amp; 0.108 &amp; -0.057 &amp; 0.273 &amp; 0.013 &amp; 0.164 &amp; -0.170 &amp; 0.499 &amp; 0.026\\
\hline
dn nkt &amp; 6 &amp; Immunophenotyping &amp; Immunology &amp; -0.062 &amp; -0.136 &amp; 0.012 &amp; 0.026 &amp; -0.157 &amp; -0.281 &amp; -0.033 &amp; 0.045 &amp; -0.173 &amp; -0.291 &amp; -0.055 &amp; 0.044\\
\hline
dn t &amp; 7 &amp; Immunophenotyping &amp; Immunology &amp; -0.080 &amp; -0.184 &amp; 0.025 &amp; 0.042 &amp; -0.242 &amp; -0.343 &amp; -0.141 &amp; 0.041 &amp; -0.230 &amp; -0.252 &amp; -0.208 &amp; 0.007\\
\hline
eosinophils &amp; 3 &amp; Hematology &amp; Hematology &amp; -0.066 &amp; -0.281 &amp; 0.148 &amp; 0.033 &amp; -0.015 &amp; -0.405 &amp; 0.374 &amp; 0.087 &amp; -0.004 &amp; -0.241 &amp; 0.232 &amp; 0.051\\
\hline
follicular b cells &amp; 2 &amp; Immunophenotyping &amp; Immunology &amp; -0.116 &amp; -0.726 &amp; 0.494 &amp; 0.048 &amp; -0.105 &amp; -0.695 &amp; 0.485 &amp; 0.046 &amp; 0.005 &amp; -0.187 &amp; 0.198 &amp; 0.015\\
\hline
luc &amp; 2 &amp; Hematology &amp; Hematology &amp; 0.018 &amp; -0.204 &amp; 0.240 &amp; 0.017 &amp; 0.266 &amp; -1.225 &amp; 1.757 &amp; 0.117 &amp; 0.222 &amp; -1.414 &amp; 1.857 &amp; 0.129\\
\hline
lymphocytes &amp; 2 &amp; Hematology &amp; Hematology &amp; 0.081 &amp; -2.262 &amp; 2.423 &amp; 0.184 &amp; 0.155 &amp; -1.089 &amp; 1.399 &amp; 0.098 &amp; 0.060 &amp; -1.013 &amp; 1.134 &amp; 0.084\\
\hline
monocytes &amp; 3 &amp; Hematology &amp; Hematology &amp; -0.021 &amp; -0.203 &amp; 0.160 &amp; 0.042 &amp; 0.078 &amp; -0.181 &amp; 0.338 &amp; 0.059 &amp; 0.103 &amp; -0.148 &amp; 0.353 &amp; 0.057\\
\hline
neutrophils &amp; 3 &amp; Hematology &amp; Hematology &amp; 0.259 &amp; 0.013 &amp; 0.504 &amp; 0.056 &amp; 0.380 &amp; -0.206 &amp; 0.966 &amp; 0.132 &amp; 0.132 &amp; -0.267 &amp; 0.531 &amp; 0.092\\
\hline
nk cells &amp; 6 &amp; Immunophenotyping &amp; Immunology &amp; -0.041 &amp; -0.096 &amp; 0.013 &amp; 0.020 &amp; 0.016 &amp; -0.070 &amp; 0.102 &amp; 0.032 &amp; 0.047 &amp; -0.016 &amp; 0.111 &amp; 0.023\\
\hline
nkt cells &amp; 4 &amp; Immunophenotyping &amp; Immunology &amp; 0.003 &amp; -0.107 &amp; 0.114 &amp; 0.029 &amp; -0.246 &amp; -0.445 &amp; -0.047 &amp; 0.043 &amp; -0.182 &amp; -0.323 &amp; -0.041 &amp; 0.031\\
\hline
percentage of live gated events &amp; 2 &amp; Immunophenotyping &amp; Immunology &amp; -0.093 &amp; -0.304 &amp; 0.117 &amp; 0.017 &amp; -0.041 &amp; -0.141 &amp; 0.059 &amp; 0.008 &amp; 0.050 &amp; 0.008 &amp; 0.092 &amp; 0.003\\
\hline
response amplitude &amp; 10 &amp; Acoustic Startle and Pre-pulse Inhibition (PPI) &amp; Behaviour &amp; 0.033 &amp; -0.013 &amp; 0.079 &amp; 0.020 &amp; 0.255 &amp; 0.197 &amp; 0.313 &amp; 0.026 &amp; 0.202 &amp; 0.111 &amp; 0.292 &amp; 0.040\\
\hline
t cells &amp; 3 &amp; Immunophenotyping &amp; Immunology &amp; -0.134 &amp; -0.275 &amp; 0.007 &amp; 0.033 &amp; -0.124 &amp; -0.412 &amp; 0.164 &amp; 0.067 &amp; -0.001 &amp; -0.166 &amp; 0.165 &amp; 0.037\\
\hline
12khz-evoked abr threshold &amp; 1 &amp; Auditory Brain Stem Response &amp; Hearing &amp; 0.054 &amp; -0.006 &amp; 0.113 &amp; 0.030 &amp; 0.087 &amp; 0.007 &amp; 0.167 &amp; 0.041 &amp; 0.002 &amp; -0.021 &amp; 0.026 &amp; 0.012\\
\hline
18khz-evoked abr threshold &amp; 1 &amp; Auditory Brain Stem Response &amp; Hearing &amp; 0.024 &amp; -0.033 &amp; 0.081 &amp; 0.029 &amp; 0.025 &amp; -0.049 &amp; 0.099 &amp; 0.038 &amp; -0.020 &amp; -0.043 &amp; 0.003 &amp; 0.012\\
\hline
24khz-evoked abr threshold &amp; 1 &amp; Auditory Brain Stem Response &amp; Hearing &amp; 0.052 &amp; -0.015 &amp; 0.118 &amp; 0.034 &amp; -0.089 &amp; -0.332 &amp; 0.154 &amp; 0.124 &amp; -0.022 &amp; -0.044 &amp; 0.000 &amp; 0.011\\
\hline
30khz-evoked abr threshold &amp; 1 &amp; Auditory Brain Stem Response &amp; Hearing &amp; 0.017 &amp; -0.053 &amp; 0.088 &amp; 0.036 &amp; -0.034 &amp; -0.102 &amp; 0.033 &amp; 0.034 &amp; -0.050 &amp; -0.075 &amp; -0.025 &amp; 0.013\\
\hline
6khz-evoked abr threshold &amp; 1 &amp; Auditory Brain Stem Response &amp; Hearing &amp; -0.008 &amp; -0.042 &amp; 0.026 &amp; 0.017 &amp; 0.014 &amp; -0.019 &amp; 0.047 &amp; 0.017 &amp; 0.018 &amp; 0.006 &amp; 0.031 &amp; 0.006\\
\hline
alanine aminotransferase &amp; 1 &amp; Clinical Chemistry &amp; Physiology &amp; -0.068 &amp; -0.190 &amp; 0.053 &amp; 0.062 &amp; 0.059 &amp; -0.132 &amp; 0.249 &amp; 0.097 &amp; 0.107 &amp; 0.032 &amp; 0.182 &amp; 0.038\\
\hline
albumin &amp; 1 &amp; Clinical Chemistry &amp; Physiology &amp; 0.113 &amp; 0.045 &amp; 0.181 &amp; 0.035 &amp; 0.056 &amp; -0.008 &amp; 0.120 &amp; 0.033 &amp; -0.057 &amp; -0.073 &amp; -0.040 &amp; 0.008\\
\hline
alkaline phosphatase &amp; 1 &amp; Clinical Chemistry &amp; Physiology &amp; 0.104 &amp; 0.045 &amp; 0.164 &amp; 0.030 &amp; -0.311 &amp; -0.398 &amp; -0.224 &amp; 0.044 &amp; -0.422 &amp; -0.469 &amp; -0.374 &amp; 0.024\\
\hline
alpha-amylase &amp; 1 &amp; Clinical Chemistry &amp; Physiology &amp; 0.038 &amp; -0.042 &amp; 0.119 &amp; 0.041 &amp; 0.280 &amp; 0.162 &amp; 0.398 &amp; 0.060 &amp; 0.225 &amp; 0.179 &amp; 0.270 &amp; 0.023\\
\hline
area under glucose response curve &amp; 1 &amp; Intraperitoneal glucose tolerance test (IPGTT) &amp; Metabolism &amp; -0.153 &amp; -0.221 &amp; -0.085 &amp; 0.035 &amp; 0.275 &amp; 0.195 &amp; 0.355 &amp; 0.041 &amp; 0.436 &amp; 0.366 &amp; 0.506 &amp; 0.036\\
\hline
aspartate aminotransferase &amp; 1 &amp; Clinical Chemistry &amp; Physiology &amp; 0.012 &amp; -0.123 &amp; 0.147 &amp; 0.069 &amp; -0.057 &amp; -0.246 &amp; 0.132 &amp; 0.096 &amp; -0.059 &amp; -0.133 &amp; 0.016 &amp; 0.038\\
\hline
basophil cell count &amp; 1 &amp; Hematology &amp; Hematology &amp; -0.092 &amp; -0.202 &amp; 0.019 &amp; 0.056 &amp; 0.203 &amp; -0.013 &amp; 0.419 &amp; 0.110 &amp; 0.268 &amp; 0.064 &amp; 0.471 &amp; 0.104\\
\hline
basophil differential count &amp; 1 &amp; Hematology &amp; Hematology &amp; -0.093 &amp; -0.179 &amp; -0.008 &amp; 0.044 &amp; -0.064 &amp; -0.283 &amp; 0.155 &amp; 0.112 &amp; -0.016 &amp; -0.110 &amp; 0.079 &amp; 0.048\\
\hline
bmc/body weight &amp; 1 &amp; Body Composition (DEXA lean/fat) &amp; Morphology &amp; 0.131 &amp; 0.033 &amp; 0.230 &amp; 0.050 &amp; -0.045 &amp; -0.134 &amp; 0.044 &amp; 0.045 &amp; -0.172 &amp; -0.221 &amp; -0.124 &amp; 0.025\\
\hline
body length &amp; 1 &amp; Body Composition (DEXA lean/fat) &amp; Morphology &amp; -0.035 &amp; -0.082 &amp; 0.013 &amp; 0.024 &amp; -0.006 &amp; -0.053 &amp; 0.041 &amp; 0.024 &amp; 0.028 &amp; 0.023 &amp; 0.033 &amp; 0.003\\
\hline
body temp &amp; 1 &amp; Echo &amp; Heart &amp; -0.033 &amp; -0.107 &amp; 0.042 &amp; 0.038 &amp; -0.030 &amp; -0.104 &amp; 0.044 &amp; 0.038 &amp; 0.002 &amp; -0.001 &amp; 0.004 &amp; 0.001\\
\hline
body weight &amp; 1 &amp; Body Weight &amp; Morphology &amp; 0.025 &amp; -0.042 &amp; 0.091 &amp; 0.034 &amp; 0.234 &amp; 0.169 &amp; 0.298 &amp; 0.033 &amp; 0.210 &amp; 0.194 &amp; 0.225 &amp; 0.008\\
\hline
body weight after experiment &amp; 1 &amp; Indirect Calorimetry &amp; Metabolism &amp; 0.085 &amp; 0.030 &amp; 0.141 &amp; 0.028 &amp; 0.285 &amp; 0.233 &amp; 0.337 &amp; 0.027 &amp; 0.203 &amp; 0.186 &amp; 0.220 &amp; 0.009\\
\hline
body weight before experiment &amp; 1 &amp; Indirect Calorimetry &amp; Metabolism &amp; 0.105 &amp; 0.041 &amp; 0.169 &amp; 0.033 &amp; 0.304 &amp; 0.244 &amp; 0.364 &amp; 0.031 &amp; 0.201 &amp; 0.182 &amp; 0.220 &amp; 0.010\\
\hline
bone area &amp; 1 &amp; Body Composition (DEXA lean/fat) &amp; Morphology &amp; 0.098 &amp; 0.027 &amp; 0.169 &amp; 0.036 &amp; 0.129 &amp; 0.053 &amp; 0.204 &amp; 0.038 &amp; 0.032 &amp; 0.000 &amp; 0.063 &amp; 0.016\\
\hline
bone mineral content (excluding skull) &amp; 1 &amp; Body Composition (DEXA lean/fat) &amp; Morphology &amp; 0.171 &amp; 0.063 &amp; 0.279 &amp; 0.055 &amp; 0.209 &amp; 0.102 &amp; 0.317 &amp; 0.055 &amp; 0.037 &amp; -0.013 &amp; 0.088 &amp; 0.026\\
\hline
bone mineral density (excluding skull) &amp; 1 &amp; Body Composition (DEXA lean/fat) &amp; Morphology &amp; 0.054 &amp; -0.088 &amp; 0.197 &amp; 0.073 &amp; 0.049 &amp; -0.109 &amp; 0.207 &amp; 0.081 &amp; 0.001 &amp; -0.019 &amp; 0.021 &amp; 0.010\\
\hline
calcium &amp; 1 &amp; Clinical Chemistry &amp; Physiology &amp; 0.010 &amp; -0.046 &amp; 0.066 &amp; 0.029 &amp; 0.014 &amp; -0.042 &amp; 0.070 &amp; 0.029 &amp; 0.004 &amp; 0.000 &amp; 0.007 &amp; 0.002\\
\hline
cardiac output &amp; 1 &amp; Echo &amp; Heart &amp; 0.013 &amp; -0.080 &amp; 0.107 &amp; 0.048 &amp; 0.102 &amp; 0.021 &amp; 0.183 &amp; 0.041 &amp; 0.093 &amp; 0.058 &amp; 0.129 &amp; 0.018\\
\hline
center average speed &amp; 1 &amp; Open Field &amp; Behaviour &amp; 0.017 &amp; -0.040 &amp; 0.074 &amp; 0.029 &amp; -0.059 &amp; -0.100 &amp; -0.017 &amp; 0.021 &amp; -0.072 &amp; -0.115 &amp; -0.030 &amp; 0.022\\
\hline
center distance travelled &amp; 1 &amp; Open Field &amp; Behaviour &amp; -0.016 &amp; -0.073 &amp; 0.041 &amp; 0.029 &amp; -0.106 &amp; -0.202 &amp; -0.010 &amp; 0.049 &amp; -0.094 &amp; -0.195 &amp; 0.007 &amp; 0.051\\
\hline
center permanence time &amp; 1 &amp; Open Field &amp; Behaviour &amp; -0.025 &amp; -0.083 &amp; 0.032 &amp; 0.029 &amp; -0.026 &amp; -0.101 &amp; 0.050 &amp; 0.039 &amp; -0.004 &amp; -0.090 &amp; 0.083 &amp; 0.044\\
\hline
center resting time &amp; 1 &amp; Open Field &amp; Behaviour &amp; 0.024 &amp; -0.074 &amp; 0.123 &amp; 0.050 &amp; -0.023 &amp; -0.155 &amp; 0.109 &amp; 0.067 &amp; -0.063 &amp; -0.222 &amp; 0.095 &amp; 0.081\\
\hline
chloride &amp; 1 &amp; Clinical Chemistry &amp; Physiology &amp; 0.032 &amp; -0.127 &amp; 0.191 &amp; 0.081 &amp; 0.024 &amp; -0.144 &amp; 0.192 &amp; 0.086 &amp; -0.013 &amp; -0.018 &amp; -0.008 &amp; 0.003\\
\hline
click-evoked abr threshold &amp; 1 &amp; Auditory Brain Stem Response &amp; Hearing &amp; -0.053 &amp; -0.153 &amp; 0.048 &amp; 0.051 &amp; -0.056 &amp; -0.183 &amp; 0.071 &amp; 0.065 &amp; -0.015 &amp; -0.058 &amp; 0.027 &amp; 0.022\\
\hline
creatine kinase &amp; 1 &amp; Clinical Chemistry &amp; Physiology &amp; 0.024 &amp; -0.107 &amp; 0.155 &amp; 0.067 &amp; -0.132 &amp; -0.397 &amp; 0.133 &amp; 0.135 &amp; -0.134 &amp; -0.384 &amp; 0.115 &amp; 0.127\\
\hline
creatinine &amp; 1 &amp; Clinical Chemistry &amp; Physiology &amp; 0.035 &amp; -0.023 &amp; 0.093 &amp; 0.030 &amp; 0.107 &amp; -0.220 &amp; 0.433 &amp; 0.167 &amp; -0.084 &amp; -0.132 &amp; -0.037 &amp; 0.024\\
\hline
cv &amp; 1 &amp; Electrocardiogram (ECG) &amp; Heart &amp; 0.187 &amp; 0.072 &amp; 0.303 &amp; 0.059 &amp; -0.090 &amp; -0.248 &amp; 0.069 &amp; 0.081 &amp; -0.240 &amp; -0.341 &amp; -0.139 &amp; 0.051\\
\hline
distance travelled - total &amp; 1 &amp; Open Field &amp; Behaviour &amp; -0.019 &amp; -0.086 &amp; 0.048 &amp; 0.034 &amp; -0.127 &amp; -0.200 &amp; -0.055 &amp; 0.037 &amp; -0.112 &amp; -0.182 &amp; -0.043 &amp; 0.035\\
\hline
ejection fraction &amp; 1 &amp; Echo &amp; Heart &amp; -0.030 &amp; -0.135 &amp; 0.074 &amp; 0.053 &amp; -0.053 &amp; -0.148 &amp; 0.043 &amp; 0.049 &amp; -0.028 &amp; -0.049 &amp; -0.008 &amp; 0.011\\
\hline
end-diastolic diameter &amp; 1 &amp; Echo &amp; Heart &amp; 0.112 &amp; 0.043 &amp; 0.181 &amp; 0.035 &amp; 0.174 &amp; 0.088 &amp; 0.261 &amp; 0.044 &amp; 0.060 &amp; 0.035 &amp; 0.085 &amp; 0.013\\
\hline
end-systolic diameter &amp; 1 &amp; Echo &amp; Heart &amp; -0.008 &amp; -0.078 &amp; 0.061 &amp; 0.036 &amp; 0.067 &amp; -0.002 &amp; 0.135 &amp; 0.035 &amp; 0.076 &amp; 0.045 &amp; 0.108 &amp; 0.016\\
\hline
fasted blood glucose concentration &amp; 1 &amp; Intraperitoneal glucose tolerance test (IPGTT) &amp; Metabolism &amp; -0.018 &amp; -0.126 &amp; 0.090 &amp; 0.055 &amp; 0.070 &amp; -0.030 &amp; 0.171 &amp; 0.051 &amp; 0.087 &amp; 0.049 &amp; 0.124 &amp; 0.019\\
\hline
fat mass &amp; 1 &amp; Body Composition (DEXA lean/fat) &amp; Morphology &amp; 0.041 &amp; -0.043 &amp; 0.125 &amp; 0.043 &amp; 0.371 &amp; 0.270 &amp; 0.473 &amp; 0.052 &amp; 0.328 &amp; 0.267 &amp; 0.390 &amp; 0.031\\
\hline
fat/body weight &amp; 1 &amp; Body Composition (DEXA lean/fat) &amp; Morphology &amp; 0.078 &amp; -0.012 &amp; 0.167 &amp; 0.046 &amp; 0.202 &amp; 0.108 &amp; 0.296 &amp; 0.048 &amp; 0.124 &amp; 0.064 &amp; 0.183 &amp; 0.030\\
\hline
forelimb and hindlimb grip strength measurement mean &amp; 1 &amp; Grip Strength &amp; Morphology &amp; 0.058 &amp; 0.004 &amp; 0.112 &amp; 0.027 &amp; 0.115 &amp; 0.053 &amp; 0.176 &amp; 0.031 &amp; 0.054 &amp; 0.029 &amp; 0.079 &amp; 0.013\\
\hline
forelimb grip strength measurement mean &amp; 1 &amp; Grip Strength &amp; Morphology &amp; 0.027 &amp; -0.019 &amp; 0.072 &amp; 0.023 &amp; 0.100 &amp; 0.054 &amp; 0.145 &amp; 0.023 &amp; 0.070 &amp; 0.044 &amp; 0.096 &amp; 0.013\\
\hline
fractional shortening &amp; 1 &amp; Echo &amp; Heart &amp; -0.015 &amp; -0.116 &amp; 0.086 &amp; 0.052 &amp; -0.058 &amp; -0.156 &amp; 0.041 &amp; 0.050 &amp; -0.041 &amp; -0.057 &amp; -0.026 &amp; 0.008\\
\hline
free fatty acids &amp; 1 &amp; Clinical Chemistry &amp; Physiology &amp; 0.028 &amp; -0.100 &amp; 0.157 &amp; 0.066 &amp; 0.055 &amp; -0.074 &amp; 0.185 &amp; 0.066 &amp; 0.019 &amp; -0.009 &amp; 0.048 &amp; 0.015\\
\hline
fructosamine &amp; 1 &amp; Clinical Chemistry &amp; Physiology &amp; -0.040 &amp; -0.120 &amp; 0.040 &amp; 0.041 &amp; -0.068 &amp; -0.151 &amp; 0.016 &amp; 0.043 &amp; -0.028 &amp; -0.069 &amp; 0.013 &amp; 0.021\\
\hline
glucose &amp; 1 &amp; Clinical Chemistry &amp; Physiology &amp; 0.069 &amp; 0.018 &amp; 0.120 &amp; 0.026 &amp; 0.128 &amp; 0.042 &amp; 0.214 &amp; 0.044 &amp; 0.065 &amp; 0.022 &amp; 0.108 &amp; 0.022\\
\hline
hdl-cholesterol &amp; 1 &amp; Clinical Chemistry &amp; Physiology &amp; -0.065 &amp; -0.126 &amp; -0.004 &amp; 0.031 &amp; 0.172 &amp; 0.070 &amp; 0.275 &amp; 0.052 &amp; 0.261 &amp; 0.218 &amp; 0.303 &amp; 0.022\\
\hline
heart weight &amp; 1 &amp; Heart Weight &amp; Morphology &amp; 0.177 &amp; 0.067 &amp; 0.286 &amp; 0.056 &amp; 0.365 &amp; 0.217 &amp; 0.513 &amp; 0.076 &amp; 0.174 &amp; 0.141 &amp; 0.207 &amp; 0.017\\
\hline
heart weight normalised against body weight &amp; 1 &amp; Heart Weight &amp; Morphology &amp; 0.079 &amp; -0.006 &amp; 0.165 &amp; 0.044 &amp; 0.036 &amp; -0.097 &amp; 0.168 &amp; 0.068 &amp; -0.050 &amp; -0.084 &amp; -0.016 &amp; 0.017\\
\hline
hematocrit &amp; 1 &amp; Hematology &amp; Hematology &amp; 0.057 &amp; -0.052 &amp; 0.165 &amp; 0.055 &amp; 0.074 &amp; -0.033 &amp; 0.180 &amp; 0.054 &amp; 0.017 &amp; 0.004 &amp; 0.031 &amp; 0.007\\
\hline
hemoglobin &amp; 1 &amp; Hematology &amp; Hematology &amp; 0.087 &amp; 0.027 &amp; 0.146 &amp; 0.030 &amp; 0.087 &amp; 0.019 &amp; 0.154 &amp; 0.034 &amp; 0.005 &amp; -0.008 &amp; 0.018 &amp; 0.007\\
\hline
hr &amp; 1 &amp; Electrocardiogram (ECG) &amp; Heart &amp; -0.063 &amp; -0.173 &amp; 0.047 &amp; 0.056 &amp; -0.014 &amp; -0.149 &amp; 0.121 &amp; 0.069 &amp; 0.041 &amp; -0.014 &amp; 0.095 &amp; 0.028\\
\hline
hrv &amp; 1 &amp; Electrocardiogram (ECG) &amp; Heart &amp; 0.172 &amp; 0.109 &amp; 0.235 &amp; 0.032 &amp; -0.081 &amp; -0.213 &amp; 0.050 &amp; 0.067 &amp; -0.250 &amp; -0.366 &amp; -0.135 &amp; 0.059\\
\hline
initial response to glucose challenge &amp; 1 &amp; Intraperitoneal glucose tolerance test (IPGTT) &amp; Metabolism &amp; -0.097 &amp; -0.150 &amp; -0.043 &amp; 0.027 &amp; 0.043 &amp; 0.014 &amp; 0.072 &amp; 0.015 &amp; 0.118 &amp; 0.085 &amp; 0.151 &amp; 0.017\\
\hline
insulin &amp; 1 &amp; Insulin Blood Level &amp; Metabolism &amp; -0.099 &amp; -0.372 &amp; 0.174 &amp; 0.139 &amp; 0.177 &amp; -0.194 &amp; 0.549 &amp; 0.189 &amp; 0.445 &amp; 0.094 &amp; 0.795 &amp; 0.179\\
\hline
iron &amp; 1 &amp; Clinical Chemistry &amp; Physiology &amp; -0.097 &amp; -0.214 &amp; 0.019 &amp; 0.060 &amp; -0.253 &amp; -0.396 &amp; -0.111 &amp; 0.073 &amp; -0.153 &amp; -0.193 &amp; -0.113 &amp; 0.021\\
\hline
lactate dehydrogenase &amp; 1 &amp; Clinical Chemistry &amp; Physiology &amp; 0.094 &amp; -0.021 &amp; 0.210 &amp; 0.059 &amp; 0.141 &amp; -0.062 &amp; 0.344 &amp; 0.104 &amp; 0.032 &amp; -0.141 &amp; 0.205 &amp; 0.088\\
\hline
latency to center entry &amp; 1 &amp; Open Field &amp; Behaviour &amp; 0.125 &amp; 0.033 &amp; 0.218 &amp; 0.047 &amp; 0.364 &amp; 0.206 &amp; 0.523 &amp; 0.081 &amp; 0.273 &amp; 0.074 &amp; 0.473 &amp; 0.102\\
\hline
ldl-cholesterol &amp; 1 &amp; Clinical Chemistry &amp; Physiology &amp; 0.423 &amp; 0.155 &amp; 0.691 &amp; 0.137 &amp; 0.267 &amp; -0.096 &amp; 0.630 &amp; 0.185 &amp; -0.162 &amp; -0.601 &amp; 0.278 &amp; 0.224\\
\hline
lean mass &amp; 1 &amp; Body Composition (DEXA lean/fat) &amp; Morphology &amp; 0.144 &amp; 0.076 &amp; 0.211 &amp; 0.035 &amp; 0.338 &amp; 0.266 &amp; 0.410 &amp; 0.037 &amp; 0.193 &amp; 0.175 &amp; 0.211 &amp; 0.009\\
\hline
lean/body weight &amp; 1 &amp; Body Composition (DEXA lean/fat) &amp; Morphology &amp; 0.195 &amp; 0.091 &amp; 0.300 &amp; 0.053 &amp; 0.184 &amp; 0.086 &amp; 0.282 &amp; 0.050 &amp; -0.012 &amp; -0.026 &amp; 0.001 &amp; 0.007\\
\hline
left anterior chamber depth &amp; 1 &amp; Eye Morphology &amp; Eye &amp; -0.185 &amp; -0.431 &amp; 0.060 &amp; 0.125 &amp; -0.153 &amp; -0.401 &amp; 0.094 &amp; 0.126 &amp; 0.033 &amp; 0.028 &amp; 0.038 &amp; 0.002\\
\hline
left corneal thickness &amp; 1 &amp; Eye Morphology &amp; Eye &amp; -0.145 &amp; -0.234 &amp; -0.055 &amp; 0.046 &amp; -0.135 &amp; -0.223 &amp; -0.047 &amp; 0.045 &amp; 0.008 &amp; -0.006 &amp; 0.021 &amp; 0.007\\
\hline
left inner nuclear layer &amp; 1 &amp; Eye Morphology &amp; Eye &amp; 0.048 &amp; -0.036 &amp; 0.132 &amp; 0.043 &amp; 0.049 &amp; -0.035 &amp; 0.132 &amp; 0.043 &amp; 0.001 &amp; -0.010 &amp; 0.011 &amp; 0.005\\
\hline
left outer nuclear layer &amp; 1 &amp; Eye Morphology &amp; Eye &amp; -0.068 &amp; -0.151 &amp; 0.016 &amp; 0.043 &amp; -0.062 &amp; -0.145 &amp; 0.022 &amp; 0.043 &amp; 0.006 &amp; 0.001 &amp; 0.012 &amp; 0.003\\
\hline
left posterior chamber depth &amp; 1 &amp; Eye Morphology &amp; Eye &amp; -0.263 &amp; -0.473 &amp; -0.053 &amp; 0.107 &amp; -0.269 &amp; -0.479 &amp; -0.058 &amp; 0.107 &amp; -0.003 &amp; -0.015 &amp; 0.009 &amp; 0.006\\
\hline
left total retinal thickness &amp; 1 &amp; Eye Morphology &amp; Eye &amp; -0.198 &amp; -0.439 &amp; 0.044 &amp; 0.123 &amp; -0.193 &amp; -0.427 &amp; 0.040 &amp; 0.119 &amp; 0.003 &amp; -0.003 &amp; 0.009 &amp; 0.003\\
\hline
locomotor activity &amp; 1 &amp; Combined SHIRPA and Dysmorphology &amp; Behaviour &amp; 0.096 &amp; 0.022 &amp; 0.170 &amp; 0.038 &amp; -0.016 &amp; -0.058 &amp; 0.026 &amp; 0.021 &amp; -0.111 &amp; -0.176 &amp; -0.045 &amp; 0.033\\
\hline
lvawd &amp; 1 &amp; Echo &amp; Heart &amp; 0.023 &amp; -0.025 &amp; 0.070 &amp; 0.024 &amp; 0.045 &amp; -0.001 &amp; 0.092 &amp; 0.024 &amp; 0.025 &amp; 0.011 &amp; 0.038 &amp; 0.007\\
\hline
lvaws &amp; 1 &amp; Echo &amp; Heart &amp; -0.002 &amp; -0.252 &amp; 0.248 &amp; 0.128 &amp; 0.023 &amp; -0.178 &amp; 0.224 &amp; 0.103 &amp; 0.011 &amp; -0.031 &amp; 0.053 &amp; 0.021\\
\hline
lvidd &amp; 1 &amp; Echo &amp; Heart &amp; 0.045 &amp; -0.024 &amp; 0.115 &amp; 0.035 &amp; 0.098 &amp; 0.021 &amp; 0.175 &amp; 0.039 &amp; 0.053 &amp; 0.038 &amp; 0.068 &amp; 0.008\\
\hline
lvids &amp; 1 &amp; Echo &amp; Heart &amp; -0.064 &amp; -0.199 &amp; 0.072 &amp; 0.069 &amp; 0.008 &amp; -0.134 &amp; 0.150 &amp; 0.072 &amp; 0.076 &amp; 0.053 &amp; 0.099 &amp; 0.012\\
\hline
lvpwd &amp; 1 &amp; Echo &amp; Heart &amp; -0.032 &amp; -0.126 &amp; 0.062 &amp; 0.048 &amp; -0.010 &amp; -0.127 &amp; 0.106 &amp; 0.060 &amp; 0.030 &amp; 0.013 &amp; 0.047 &amp; 0.009\\
\hline
lvpws &amp; 1 &amp; Echo &amp; Heart &amp; -0.019 &amp; -0.101 &amp; 0.063 &amp; 0.042 &amp; 0.009 &amp; -0.082 &amp; 0.100 &amp; 0.047 &amp; 0.027 &amp; 0.006 &amp; 0.047 &amp; 0.010\\
\hline
magnesium &amp; 1 &amp; Urinalysis &amp; Physiology &amp; 0.016 &amp; -0.023 &amp; 0.055 &amp; 0.020 &amp; -0.051 &amp; -0.117 &amp; 0.014 &amp; 0.033 &amp; -0.041 &amp; -0.114 &amp; 0.031 &amp; 0.037\\
\hline
mean cell hemoglobin concentration &amp; 1 &amp; Hematology &amp; Hematology &amp; 0.038 &amp; -0.088 &amp; 0.164 &amp; 0.064 &amp; 0.025 &amp; -0.109 &amp; 0.159 &amp; 0.068 &amp; -0.011 &amp; -0.015 &amp; -0.008 &amp; 0.002\\
\hline
mean cell volume &amp; 1 &amp; Hematology &amp; Hematology &amp; 0.004 &amp; -0.096 &amp; 0.104 &amp; 0.051 &amp; -0.003 &amp; -0.096 &amp; 0.090 &amp; 0.048 &amp; -0.006 &amp; -0.010 &amp; -0.003 &amp; 0.002\\
\hline
mean corpuscular hemoglobin &amp; 1 &amp; Hematology &amp; Hematology &amp; -0.003 &amp; -0.065 &amp; 0.060 &amp; 0.032 &amp; -0.019 &amp; -0.082 &amp; 0.044 &amp; 0.032 &amp; -0.017 &amp; -0.020 &amp; -0.014 &amp; 0.001\\
\hline
mean platelet volume &amp; 1 &amp; Hematology &amp; Hematology &amp; 0.049 &amp; -0.004 &amp; 0.102 &amp; 0.027 &amp; 0.035 &amp; -0.021 &amp; 0.092 &amp; 0.029 &amp; -0.017 &amp; -0.028 &amp; -0.007 &amp; 0.005\\
\hline
mean r amplitude &amp; 1 &amp; Electrocardiogram (ECG) &amp; Heart &amp; 0.008 &amp; -0.028 &amp; 0.045 &amp; 0.019 &amp; -0.095 &amp; -0.163 &amp; -0.027 &amp; 0.035 &amp; -0.084 &amp; -0.150 &amp; -0.017 &amp; 0.034\\
\hline
mean sr amplitude &amp; 1 &amp; Electrocardiogram (ECG) &amp; Heart &amp; 0.028 &amp; -0.013 &amp; 0.070 &amp; 0.021 &amp; -0.088 &amp; -0.127 &amp; -0.048 &amp; 0.020 &amp; -0.113 &amp; -0.156 &amp; -0.070 &amp; 0.022\\
\hline
number of center entries &amp; 1 &amp; Open Field &amp; Behaviour &amp; 0.015 &amp; -0.053 &amp; 0.084 &amp; 0.035 &amp; -0.036 &amp; -0.095 &amp; 0.023 &amp; 0.030 &amp; -0.059 &amp; -0.168 &amp; 0.050 &amp; 0.056\\
\hline
number of rears - total &amp; 1 &amp; Open Field &amp; Behaviour &amp; -0.001 &amp; -0.114 &amp; 0.112 &amp; 0.058 &amp; 0.187 &amp; -0.039 &amp; 0.413 &amp; 0.115 &amp; 0.179 &amp; 0.057 &amp; 0.302 &amp; 0.063\\
\hline
others &amp; 1 &amp; Immunophenotyping &amp; Immunology &amp; -0.168 &amp; -0.260 &amp; -0.077 &amp; 0.047 &amp; -0.152 &amp; -0.244 &amp; -0.059 &amp; 0.047 &amp; 0.020 &amp; 0.005 &amp; 0.034 &amp; 0.007\\
\hline
pdcs &amp; 1 &amp; Immunophenotyping &amp; Immunology &amp; -0.173 &amp; -0.400 &amp; 0.054 &amp; 0.116 &amp; -0.257 &amp; -0.719 &amp; 0.204 &amp; 0.235 &amp; -0.092 &amp; -0.252 &amp; 0.069 &amp; 0.082\\
\hline
percentage center time &amp; 1 &amp; Open Field &amp; Behaviour &amp; -0.022 &amp; -0.086 &amp; 0.042 &amp; 0.033 &amp; -0.019 &amp; -0.091 &amp; 0.053 &amp; 0.037 &amp; -0.006 &amp; -0.097 &amp; 0.085 &amp; 0.046\\
\hline
periphery average speed &amp; 1 &amp; Open Field &amp; Behaviour &amp; -0.044 &amp; -0.108 &amp; 0.019 &amp; 0.033 &amp; -0.140 &amp; -0.212 &amp; -0.068 &amp; 0.037 &amp; -0.096 &amp; -0.145 &amp; -0.048 &amp; 0.025\\
\hline
periphery distance travelled &amp; 1 &amp; Open Field &amp; Behaviour &amp; -0.031 &amp; -0.092 &amp; 0.029 &amp; 0.031 &amp; -0.134 &amp; -0.187 &amp; -0.081 &amp; 0.027 &amp; -0.104 &amp; -0.171 &amp; -0.036 &amp; 0.035\\
\hline
periphery permanence time &amp; 1 &amp; Open Field &amp; Behaviour &amp; -0.037 &amp; -0.128 &amp; 0.054 &amp; 0.046 &amp; -0.029 &amp; -0.101 &amp; 0.042 &amp; 0.036 &amp; 0.008 &amp; -0.014 &amp; 0.029 &amp; 0.011\\
\hline
periphery resting time &amp; 1 &amp; Open Field &amp; Behaviour &amp; -0.054 &amp; -0.127 &amp; 0.019 &amp; 0.037 &amp; -0.057 &amp; -0.107 &amp; -0.007 &amp; 0.025 &amp; 0.003 &amp; -0.056 &amp; 0.061 &amp; 0.030\\
\hline
phosphorus &amp; 1 &amp; Clinical Chemistry &amp; Physiology &amp; -0.049 &amp; -0.084 &amp; -0.013 &amp; 0.018 &amp; -0.083 &amp; -0.158 &amp; -0.008 &amp; 0.038 &amp; -0.042 &amp; -0.081 &amp; -0.003 &amp; 0.020\\
\hline
platelet count &amp; 1 &amp; Hematology &amp; Hematology &amp; 0.074 &amp; 0.021 &amp; 0.127 &amp; 0.027 &amp; 0.242 &amp; 0.187 &amp; 0.296 &amp; 0.028 &amp; 0.164 &amp; 0.137 &amp; 0.191 &amp; 0.014\\
\hline
pnn5(6&gt;ms) &amp; 1 &amp; Electrocardiogram (ECG) &amp; Heart &amp; 0.291 &amp; 0.172 &amp; 0.410 &amp; 0.061 &amp; -0.293 &amp; -0.527 &amp; -0.058 &amp; 0.120 &amp; -0.600 &amp; -0.924 &amp; -0.277 &amp; 0.165\\
\hline
potassium &amp; 1 &amp; Clinical Chemistry &amp; Physiology &amp; -0.071 &amp; -0.221 &amp; 0.080 &amp; 0.077 &amp; -0.007 &amp; -0.173 &amp; 0.158 &amp; 0.084 &amp; 0.070 &amp; 0.048 &amp; 0.093 &amp; 0.012\\
\hline
pq &amp; 1 &amp; Electrocardiogram (ECG) &amp; Heart &amp; -0.065 &amp; -0.154 &amp; 0.024 &amp; 0.045 &amp; -0.065 &amp; -0.127 &amp; -0.003 &amp; 0.032 &amp; 0.002 &amp; -0.026 &amp; 0.029 &amp; 0.014\\
\hline
pr &amp; 1 &amp; Electrocardiogram (ECG) &amp; Heart &amp; -0.056 &amp; -0.105 &amp; -0.008 &amp; 0.025 &amp; -0.075 &amp; -0.124 &amp; -0.027 &amp; 0.025 &amp; -0.018 &amp; -0.032 &amp; -0.005 &amp; 0.007\\
\hline
qrs &amp; 1 &amp; Electrocardiogram (ECG) &amp; Heart &amp; 0.073 &amp; 0.035 &amp; 0.110 &amp; 0.019 &amp; 0.068 &amp; 0.030 &amp; 0.106 &amp; 0.019 &amp; -0.005 &amp; -0.015 &amp; 0.005 &amp; 0.005\\
\hline
qtc &amp; 1 &amp; Electrocardiogram (ECG) &amp; Heart &amp; 0.033 &amp; -0.010 &amp; 0.076 &amp; 0.022 &amp; 0.031 &amp; -0.021 &amp; 0.083 &amp; 0.026 &amp; -0.001 &amp; -0.009 &amp; 0.008 &amp; 0.004\\
\hline
qtc dispersion &amp; 1 &amp; Electrocardiogram (ECG) &amp; Heart &amp; 0.003 &amp; -0.052 &amp; 0.059 &amp; 0.028 &amp; -0.005 &amp; -0.106 &amp; 0.097 &amp; 0.052 &amp; -0.008 &amp; -0.051 &amp; 0.036 &amp; 0.022\\
\hline
red blood cell count &amp; 1 &amp; Hematology &amp; Hematology &amp; 0.077 &amp; 0.007 &amp; 0.147 &amp; 0.036 &amp; 0.100 &amp; 0.032 &amp; 0.168 &amp; 0.035 &amp; 0.023 &amp; 0.009 &amp; 0.037 &amp; 0.007\\
\hline
red blood cell distribution width &amp; 1 &amp; Hematology &amp; Hematology &amp; 0.125 &amp; -0.004 &amp; 0.253 &amp; 0.065 &amp; 0.135 &amp; -0.004 &amp; 0.274 &amp; 0.071 &amp; 0.010 &amp; -0.003 &amp; 0.024 &amp; 0.007\\
\hline
respiration rate &amp; 1 &amp; Echo &amp; Heart &amp; -0.138 &amp; -0.218 &amp; -0.059 &amp; 0.041 &amp; -0.070 &amp; -0.180 &amp; 0.039 &amp; 0.056 &amp; 0.061 &amp; 0.023 &amp; 0.099 &amp; 0.020\\
\hline
respiratory exchange ratio &amp; 1 &amp; Indirect Calorimetry &amp; Metabolism &amp; -0.012 &amp; -0.090 &amp; 0.066 &amp; 0.040 &amp; -0.011 &amp; -0.088 &amp; 0.067 &amp; 0.039 &amp; 0.002 &amp; -0.006 &amp; 0.009 &amp; 0.004\\
\hline
right anterior chamber depth &amp; 1 &amp; Eye Morphology &amp; Eye &amp; -0.449 &amp; -1.329 &amp; 0.431 &amp; 0.449 &amp; -0.416 &amp; -1.292 &amp; 0.460 &amp; 0.447 &amp; 0.032 &amp; 0.026 &amp; 0.037 &amp; 0.003\\
\hline
right corneal thickness &amp; 1 &amp; Eye Morphology &amp; Eye &amp; -0.036 &amp; -0.228 &amp; 0.157 &amp; 0.098 &amp; -0.031 &amp; -0.196 &amp; 0.135 &amp; 0.085 &amp; -0.001 &amp; -0.024 &amp; 0.021 &amp; 0.011\\
\hline
right inner nuclear layer &amp; 1 &amp; Eye Morphology &amp; Eye &amp; -0.255 &amp; -0.763 &amp; 0.254 &amp; 0.260 &amp; -0.279 &amp; -0.837 &amp; 0.280 &amp; 0.285 &amp; -0.018 &amp; -0.066 &amp; 0.031 &amp; 0.025\\
\hline
right outer nuclear layer &amp; 1 &amp; Eye Morphology &amp; Eye &amp; 0.006 &amp; -0.078 &amp; 0.090 &amp; 0.043 &amp; 0.011 &amp; -0.073 &amp; 0.095 &amp; 0.043 &amp; 0.006 &amp; 0.000 &amp; 0.011 &amp; 0.003\\
\hline
right posterior chamber depth &amp; 1 &amp; Eye Morphology &amp; Eye &amp; -0.078 &amp; -0.291 &amp; 0.135 &amp; 0.109 &amp; -0.076 &amp; -0.289 &amp; 0.136 &amp; 0.109 &amp; 0.007 &amp; -0.018 &amp; 0.032 &amp; 0.013\\
\hline
right total retinal thickness &amp; 1 &amp; Eye Morphology &amp; Eye &amp; -0.199 &amp; -0.646 &amp; 0.248 &amp; 0.228 &amp; -0.193 &amp; -0.629 &amp; 0.243 &amp; 0.222 &amp; 0.005 &amp; -0.005 &amp; 0.015 &amp; 0.005\\
\hline
rmssd &amp; 1 &amp; Electrocardiogram (ECG) &amp; Heart &amp; 0.180 &amp; -0.088 &amp; 0.448 &amp; 0.137 &amp; -0.016 &amp; -0.411 &amp; 0.379 &amp; 0.202 &amp; -0.118 &amp; -0.245 &amp; 0.009 &amp; 0.065\\
\hline
rp macrophage (cd19-  cd11c-) &amp; 1 &amp; Immunophenotyping &amp; Immunology &amp; -0.077 &amp; -0.340 &amp; 0.187 &amp; 0.134 &amp; -0.075 &amp; -0.335 &amp; 0.186 &amp; 0.133 &amp; -0.075 &amp; -0.207 &amp; 0.058 &amp; 0.068\\
\hline
rr &amp; 1 &amp; Electrocardiogram (ECG) &amp; Heart &amp; -0.076 &amp; -0.188 &amp; 0.035 &amp; 0.057 &amp; -0.090 &amp; -0.206 &amp; 0.027 &amp; 0.060 &amp; -0.013 &amp; -0.021 &amp; -0.004 &amp; 0.005\\
\hline
sodium &amp; 1 &amp; Clinical Chemistry &amp; Physiology &amp; 0.026 &amp; -0.117 &amp; 0.170 &amp; 0.073 &amp; 0.034 &amp; -0.134 &amp; 0.201 &amp; 0.085 &amp; 0.010 &amp; 0.007 &amp; 0.013 &amp; 0.002\\
\hline
spleen weight &amp; 1 &amp; Immunophenotyping &amp; Immunology &amp; 0.187 &amp; -0.050 &amp; 0.425 &amp; 0.121 &amp; 0.113 &amp; -0.160 &amp; 0.387 &amp; 0.140 &amp; -0.154 &amp; -0.210 &amp; -0.098 &amp; 0.029\\
\hline
st &amp; 1 &amp; Electrocardiogram (ECG) &amp; Heart &amp; 0.003 &amp; -0.054 &amp; 0.061 &amp; 0.029 &amp; -0.005 &amp; -0.081 &amp; 0.070 &amp; 0.039 &amp; -0.003 &amp; -0.018 &amp; 0.011 &amp; 0.007\\
\hline
stroke volume &amp; 1 &amp; Echo &amp; Heart &amp; 0.059 &amp; -0.078 &amp; 0.197 &amp; 0.070 &amp; 0.157 &amp; 0.009 &amp; 0.306 &amp; 0.076 &amp; 0.094 &amp; 0.078 &amp; 0.110 &amp; 0.008\\
\hline
tibia length &amp; 1 &amp; Heart Weight &amp; Morphology &amp; -0.148 &amp; -0.440 &amp; 0.145 &amp; 0.149 &amp; -0.137 &amp; -0.426 &amp; 0.151 &amp; 0.147 &amp; 0.010 &amp; 0.006 &amp; 0.013 &amp; 0.002\\
\hline
total bilirubin &amp; 1 &amp; Clinical Chemistry &amp; Physiology &amp; 0.061 &amp; -0.010 &amp; 0.131 &amp; 0.036 &amp; 0.002 &amp; -0.086 &amp; 0.091 &amp; 0.045 &amp; -0.055 &amp; -0.098 &amp; -0.012 &amp; 0.022\\
\hline
total cholesterol &amp; 1 &amp; Clinical Chemistry &amp; Physiology &amp; 0.094 &amp; -0.075 &amp; 0.264 &amp; 0.086 &amp; 0.314 &amp; 0.113 &amp; 0.516 &amp; 0.103 &amp; 0.203 &amp; 0.175 &amp; 0.230 &amp; 0.014\\
\hline
total food intake &amp; 1 &amp; Indirect Calorimetry &amp; Metabolism &amp; -0.119 &amp; -0.254 &amp; 0.016 &amp; 0.069 &amp; -0.096 &amp; -0.256 &amp; 0.064 &amp; 0.082 &amp; 0.027 &amp; -0.023 &amp; 0.077 &amp; 0.026\\
\hline
total protein &amp; 1 &amp; Clinical Chemistry &amp; Physiology &amp; -0.042 &amp; -0.062 &amp; -0.022 &amp; 0.010 &amp; -0.036 &amp; -0.062 &amp; -0.009 &amp; 0.013 &amp; 0.009 &amp; -0.001 &amp; 0.019 &amp; 0.005\\
\hline
total water intake &amp; 1 &amp; Indirect Calorimetry &amp; Metabolism &amp; -0.146 &amp; -0.237 &amp; -0.054 &amp; 0.047 &amp; -0.210 &amp; -0.268 &amp; -0.151 &amp; 0.030 &amp; -0.065 &amp; -0.137 &amp; 0.007 &amp; 0.037\\
\hline
triglycerides &amp; 1 &amp; Clinical Chemistry &amp; Physiology &amp; -0.032 &amp; -0.123 &amp; 0.059 &amp; 0.047 &amp; 0.327 &amp; 0.209 &amp; 0.445 &amp; 0.060 &amp; 0.347 &amp; 0.259 &amp; 0.436 &amp; 0.045\\
\hline
urea (blood urea nitrogen - bun) &amp; 1 &amp; Clinical Chemistry &amp; Physiology &amp; -0.141 &amp; -0.266 &amp; -0.015 &amp; 0.064 &amp; -0.095 &amp; -0.251 &amp; 0.061 &amp; 0.079 &amp; 0.040 &amp; 0.005 &amp; 0.075 &amp; 0.018\\
\hline
uric acid &amp; 1 &amp; Clinical Chemistry &amp; Physiology &amp; 0.037 &amp; -0.066 &amp; 0.139 &amp; 0.052 &amp; 0.363 &amp; 0.091 &amp; 0.634 &amp; 0.138 &amp; 0.447 &amp; -0.080 &amp; 0.975 &amp; 0.269\\
\hline
white blood cell count &amp; 1 &amp; Hematology &amp; Hematology &amp; -0.091 &amp; -0.170 &amp; -0.011 &amp; 0.041 &amp; 0.117 &amp; -0.002 &amp; 0.236 &amp; 0.061 &amp; 0.198 &amp; 0.137 &amp; 0.259 &amp; 0.031\\
\hline
whole arena average speed &amp; 1 &amp; Open Field &amp; Behaviour &amp; -0.016 &amp; -0.086 &amp; 0.054 &amp; 0.036 &amp; -0.114 &amp; -0.184 &amp; -0.044 &amp; 0.036 &amp; -0.100 &amp; -0.152 &amp; -0.048 &amp; 0.027\\
\hline
whole arena resting time &amp; 1 &amp; Open Field &amp; Behaviour &amp; -0.053 &amp; -0.101 &amp; -0.005 &amp; 0.025 &amp; -0.059 &amp; -0.108 &amp; -0.011 &amp; 0.025 &amp; 0.005 &amp; -0.051 &amp; 0.061 &amp; 0.029\\
\hline
\end{tabular}
\end{table}

\hypertarget{table-6.4}{%
\subsection{Table 6.4}\label{table-6.4}}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{kable}\NormalTok{(overall2, }\DataTypeTok{digits =} \DecValTok{3}\NormalTok{, }\DataTypeTok{caption =} \StringTok{"Summary of overall meta-analyses on the functional trait group level (GroupingTerm). Results for lnCVR, lnVR and lnRR and their respective upper and lower 95 percent CI's, standard error and I2 values are provided."}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{    }\KeywordTok{kable_styling}\NormalTok{()  }\CommentTok{#%>%}
\end{Highlighting}
\end{Shaded}

\begin{table}

\caption{\label{tab:Table4}Summary of overall meta-analyses on the functional trait group level (GroupingTerm). Results for lnCVR, lnVR and lnRR and their respective upper and lower 95 percent CI's, standard error and I2 values are provided.}
\centering
\begin{tabular}[t]{l|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r}
\hline
GroupingTerm & lnCVR & lnCVR\_lower & lnCVR\_upper & lnCVR\_se & lnCVR\_I2 & lnVR & lnVR\_lower & lnVR\_upper & lnVR\_se & lnVR\_I2 & lnRR & lnRR\_lower & lnRR\_upper & lnRR\_se & lnRR\_I2\\
\hline
Behaviour & -0.004 & -0.024 & 0.017 & 0.010 & 39.033 & -0.018 & -0.074 & 0.038 & 0.029 & 92.799 & -0.020 & -0.063 & 0.024 & 0.022 & 89.238\\
\hline
Morphology & 0.077 & 0.041 & 0.113 & 0.018 & 67.282 & 0.151 & 0.082 & 0.221 & 0.035 & 90.626 & 0.068 & 0.007 & 0.128 & 0.031 & 99.698\\
\hline
Metabolism & -0.043 & -0.113 & 0.026 & 0.035 & 84.801 & 0.091 & -0.034 & 0.216 & 0.064 & 96.783 & 0.142 & 0.036 & 0.248 & 0.054 & 99.377\\
\hline
Physiology & 0.013 & -0.014 & 0.039 & 0.014 & 70.566 & 0.036 & -0.028 & 0.100 & 0.033 & 90.643 & 0.016 & -0.044 & 0.077 & 0.031 & 99.817\\
\hline
Immunology & -0.068 & -0.098 & -0.038 & 0.015 & 40.769 & -0.111 & -0.162 & -0.060 & 0.026 & 58.020 & -0.057 & -0.107 & -0.008 & 0.025 & 96.148\\
\hline
Hematology & 0.022 & -0.017 & 0.060 & 0.020 & 60.753 & 0.080 & 0.032 & 0.129 & 0.025 & 64.943 & 0.039 & -0.002 & 0.080 & 0.021 & 99.630\\
\hline
Heart & 0.018 & -0.013 & 0.050 & 0.016 & 81.298 & -0.005 & -0.036 & 0.026 & 0.016 & 74.058 & -0.005 & -0.032 & 0.023 & 0.014 & 98.985\\
\hline
Hearing & 0.016 & -0.011 & 0.043 & 0.014 & 21.756 & 0.011 & -0.023 & 0.044 & 0.017 & 22.797 & -0.013 & -0.034 & 0.007 & 0.010 & 79.486\\
\hline
Eye & -0.082 & -0.148 & -0.016 & 0.034 & 49.810 & -0.074 & -0.138 & -0.011 & 0.032 & 48.309 & 0.009 & 0.001 & 0.017 & 0.004 & 90.528\\
\hline
All & 0.005 & -0.009 & 0.018 & 0.007 & 76.486 & 0.016 & -0.008 & 0.039 & 0.012 & 90.760 & 0.012 & -0.006 & 0.031 & 0.009 & 99.716\\
\hline
\end{tabular}
\end{table}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# scroll_box(width = '100%', height = '200px')}
\end{Highlighting}
\end{Shaded}

\hypertarget{table-6.5}{%
\subsection{Table 6.5}\label{table-6.5}}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{female <-}\StringTok{ }\NormalTok{(overall.female.plot3)}
\NormalTok{female}\OperatorTok{$}\NormalTok{Sex <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"female"}\NormalTok{)}

\NormalTok{male <-}\StringTok{ }\NormalTok{(overall.male.plot3)}
\NormalTok{male}\OperatorTok{$}\NormalTok{Sex <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"male"}\NormalTok{)}

\NormalTok{mf_sig <-}\StringTok{ }\KeywordTok{rbind}\NormalTok{(female, male)}
\NormalTok{mf_sig <-}\StringTok{ }\NormalTok{mf_sig[, }\KeywordTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{, }\DecValTok{17}\NormalTok{, }\DecValTok{2}\OperatorTok{:}\DecValTok{16}\NormalTok{)]}

\NormalTok{mf_sig <-}\StringTok{ }\NormalTok{mf_sig }\OperatorTok{%>%}\StringTok{ }\KeywordTok{arrange}\NormalTok{(}\KeywordTok{desc}\NormalTok{(GroupingTerm))}

\KeywordTok{kable}\NormalTok{(mf_sig, }\DataTypeTok{digits =} \DecValTok{3}\NormalTok{, }\DataTypeTok{caption =} \StringTok{"Provides an overview of meta-analysis results performed on traits that were significantly biased towards either sex. This table summarizes findings for both sexes and the respective functional trait groups."}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{    }\KeywordTok{kable_styling}\NormalTok{()  }\CommentTok{#%>%}
\end{Highlighting}
\end{Shaded}

\begin{table}

\caption{\label{tab:unnamed-chunk-6}Provides an overview of meta-analysis results performed on traits that were significantly biased towards either sex. This table summarizes findings for both sexes and the respective functional trait groups.}
\centering
\begin{tabular}[t]{l|l|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r}
\hline
GroupingTerm & Sex & lnCVR & lnCVR\_lower & lnCVR\_upper & lnCVR\_se & lnCVR\_I2 & lnVR & lnVR\_lower & lnVR\_upper & lnVR\_se & lnVR\_I2 & lnRR & lnRR\_lower & lnRR\_upper & lnRR\_se & lnRR\_I2\\
\hline
Behaviour & female & -0.053 & -0.101 & -0.005 & 0.025 & 0.000 & -0.093 & -0.120 & -0.066 & 0.014 & 42.139 & -0.094 & -0.117 & -0.072 & 0.011 & 0.000\\
\hline
Behaviour & male & 0.107 & 0.050 & 0.165 & 0.029 & 0.000 & 0.284 & 0.189 & 0.378 & 0.048 & 37.808 & 0.203 & 0.135 & 0.272 & 0.035 & 0.000\\
\hline
Morphology & female & NA & NA & NA & NA & NA & NA & NA & NA & NA & NA & -0.110 & -0.230 & 0.011 & 0.061 & 93.935\\
\hline
Morphology & male & 0.127 & 0.086 & 0.168 & 0.021 & 41.546 & 0.217 & 0.155 & 0.280 & 0.032 & 84.378 & 0.120 & 0.058 & 0.183 & 0.032 & 99.674\\
\hline
Metabolism & female & -0.125 & -0.166 & -0.083 & 0.021 & 13.324 & -0.210 & -0.268 & -0.151 & 0.030 & 0.000 & NA & NA & NA & NA & NA\\
\hline
Metabolism & male & 0.094 & 0.052 & 0.136 & 0.021 & 0.000 & 0.224 & 0.100 & 0.348 & 0.063 & 95.761 & 0.223 & 0.110 & 0.335 & 0.058 & 98.647\\
\hline
Physiology & female & -0.047 & -0.064 & -0.030 & 0.009 & 0.610 & -0.163 & -0.296 & -0.030 & 0.068 & 92.843 & -0.117 & -0.221 & -0.014 & 0.053 & 99.301\\
\hline
Physiology & male & 0.096 & 0.063 & 0.130 & 0.017 & 0.109 & 0.240 & 0.159 & 0.320 & 0.041 & 56.006 & 0.145 & 0.071 & 0.218 & 0.038 & 98.518\\
\hline
Immunology & female & -0.090 & -0.148 & -0.032 & 0.030 & 81.548 & -0.180 & -0.218 & -0.141 & 0.020 & 0.000 & -0.159 & -0.229 & -0.090 & 0.035 & 94.729\\
\hline
Immunology & male & NA & NA & NA & NA & NA & NA & NA & NA & NA & NA & 0.028 & 0.001 & 0.055 & 0.014 & 44.587\\
\hline
Hematology & female & -0.092 & -0.150 & -0.034 & 0.030 & 0.000 & NA & NA & NA & NA & NA & -0.013 & -0.018 & -0.007 & 0.003 & 84.990\\
\hline
Hematology & male & 0.082 & 0.048 & 0.117 & 0.017 & 0.089 & 0.144 & 0.046 & 0.243 & 0.050 & 86.350 & 0.116 & 0.027 & 0.205 & 0.046 & 98.445\\
\hline
Heart & female & -0.091 & -0.171 & -0.012 & 0.041 & 66.548 & -0.084 & -0.109 & -0.059 & 0.013 & 0.528 & -0.108 & -0.179 & -0.036 & 0.036 & 98.814\\
\hline
Heart & male & 0.154 & 0.085 & 0.223 & 0.035 & 78.699 & 0.104 & 0.062 & 0.146 & 0.022 & 36.412 & 0.058 & 0.041 & 0.075 & 0.009 & 84.650\\
\hline
Hearing & female & NA & NA & NA & NA & NA & NA & NA & NA & NA & NA & -0.035 & -0.062 & -0.009 & 0.014 & 61.362\\
\hline
Hearing & male & NA & NA & NA & NA & NA & 0.087 & 0.007 & 0.167 & 0.041 & 0.000 & 0.018 & 0.006 & 0.031 & 0.006 & 0.000\\
\hline
Eye & female & -0.164 & -0.250 & -0.078 & 0.044 & 3.071 & -0.166 & -0.277 & -0.056 & 0.057 & 24.076 & NA & NA & NA & NA & NA\\
\hline
Eye & male & NA & NA & NA & NA & NA & NA & NA & NA & NA & NA & 0.019 & 0.004 & 0.034 & 0.008 & 97.046\\
\hline
All & female & -0.087 & -0.109 & -0.064 & 0.012 & 66.479 & -0.130 & -0.157 & -0.103 & 0.014 & 75.919 & -0.098 & -0.129 & -0.068 & 0.016 & 99.612\\
\hline
All & male & 0.111 & 0.093 & 0.130 & 0.009 & 34.070 & 0.198 & 0.162 & 0.233 & 0.018 & 86.497 & 0.111 & 0.083 & 0.138 & 0.014 & 99.639\\
\hline
\end{tabular}
\end{table}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# scroll_box(width = '100%', height = '300px')}
\end{Highlighting}
\end{Shaded}

\hypertarget{table-6.6}{%
\subsection{Table 6.6}\label{table-6.6}}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{het <-}\StringTok{ }\NormalTok{heterog6 }\OperatorTok{%>%}\StringTok{ }\KeywordTok{pivot_wider}\NormalTok{(}\DataTypeTok{names_from =}\NormalTok{ parameter, }\DataTypeTok{values_from =}\NormalTok{ value}\OperatorTok{:}\NormalTok{ci.h) }\OperatorTok{%>%}\StringTok{ }
\StringTok{    }\KeywordTok{rename}\NormalTok{(}\DataTypeTok{lnCVR =}\NormalTok{ value_heteroCVR, }\DataTypeTok{lnCVR_lower =}\NormalTok{ ci.low_heteroCVR, }\DataTypeTok{lnCVR_higher =}\NormalTok{ ci.high_heteroCVR, }
        \DataTypeTok{lnVR =}\NormalTok{ value_heteroVR, }\DataTypeTok{lnVR_lower =}\NormalTok{ ci.low_heteroVR, }\DataTypeTok{lnVR_higher =}\NormalTok{ ci.high_heteroVR, }
        \DataTypeTok{lnRR =}\NormalTok{ value_heteroRR, }\DataTypeTok{lnRR_lower =}\NormalTok{ ci.low_heteroRR, }\DataTypeTok{lnRR_higher =}\NormalTok{ ci.high_heteroRR, }
        \DataTypeTok{CVR =}\NormalTok{ mean_heteroCVR, }\DataTypeTok{VR =}\NormalTok{ mean_heteroVR, }\DataTypeTok{RR =}\NormalTok{ mean_heteroRR, }\DataTypeTok{CVR_lower =}\NormalTok{ ci.l_heteroCVR, }
        \DataTypeTok{VR_lower =}\NormalTok{ ci.l_heteroVR, }\DataTypeTok{RR_lower =}\NormalTok{ ci.l_heteroRR, }\DataTypeTok{CVR_higher =}\NormalTok{ ci.h_heteroCVR, }
        \DataTypeTok{VR_higher =}\NormalTok{ ci.h_heteroVR, }\DataTypeTok{RR_higher =}\NormalTok{ ci.h_heteroRR) }\OperatorTok{%>%}\StringTok{ }\KeywordTok{select}\NormalTok{(}\DecValTok{1}\NormalTok{, }\DecValTok{2}\NormalTok{, }\DecValTok{5}\NormalTok{, }
    \DecValTok{8}\NormalTok{, }\DecValTok{3}\NormalTok{, }\DecValTok{6}\NormalTok{, }\DecValTok{9}\NormalTok{, }\DecValTok{4}\NormalTok{, }\DecValTok{7}\NormalTok{, }\DecValTok{10}\NormalTok{, }\DecValTok{14}\NormalTok{, }\DecValTok{17}\NormalTok{, }\DecValTok{20}\NormalTok{, }\DecValTok{15}\NormalTok{, }\DecValTok{18}\NormalTok{, }\DecValTok{21}\NormalTok{, }\DecValTok{16}\NormalTok{, }\DecValTok{19}\NormalTok{, }\DecValTok{22}\NormalTok{)}

\KeywordTok{kable}\NormalTok{(het, }\DataTypeTok{digits =} \DecValTok{3}\NormalTok{, }\DataTypeTok{caption =} \StringTok{"Summarizes our findings on heterogeneity due to institutions and mouse strains. These results are based on meta-analyses on sigma^2 and errors for mouse strains and centers (Institutions), following the identical workflow from above."}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{    }\KeywordTok{kable_styling}\NormalTok{()  }\CommentTok{#%>%}
\end{Highlighting}
\end{Shaded}

\begin{table}

\caption{\label{tab:unnamed-chunk-7}Summarizes our findings on heterogeneity due to institutions and mouse strains. These results are based on meta-analyses on sigma^2 and errors for mouse strains and centers (Institutions), following the identical workflow from above.}
\centering
\begin{tabular}[t]{l|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r}
\hline
GroupingTerm & lnCVR & lnCVR\_lower & lnCVR\_higher & lnVR & lnVR\_lower & lnVR\_higher & lnRR & lnRR\_lower & lnRR\_higher & CVR & CVR\_lower & CVR\_higher & VR & VR\_lower & VR\_higher & RR & RR\_lower & RR\_higher\\
\hline
Behaviour & -1.649 & -2.464 & -0.835 & -1.545 & -2.359 & -0.730 & -2.640 & -4.135 & -1.145 & 0.192 & 0.085 & 0.434 & 0.213 & 0.094 & 0.482 & 0.071 & 0.016 & 0.318\\
\hline
Morphology & -1.745 & -2.424 & -1.066 & -1.725 & -2.404 & -1.046 & -7.277 & -10.004 & -4.549 & 0.175 & 0.089 & 0.344 & 0.178 & 0.090 & 0.351 & 0.001 & 0.000 & 0.011\\
\hline
Metabolism & -2.404 & -3.567 & -1.240 & -2.897 & -4.260 & -1.534 & -2.970 & -4.134 & -1.806 & 0.090 & 0.028 & 0.289 & 0.055 & 0.014 & 0.216 & 0.051 & 0.016 & 0.164\\
\hline
Physiology & -2.899 & -3.762 & -2.037 & -1.922 & -2.688 & -1.155 & -2.664 & -3.430 & -1.898 & 0.055 & 0.023 & 0.130 & 0.146 & 0.068 & 0.315 & 0.070 & 0.032 & 0.150\\
\hline
Immunology & -0.291 & -0.795 & 0.213 & -0.231 & -0.735 & 0.273 & -0.895 & -1.790 & 0.001 & 0.748 & 0.452 & 1.238 & 0.793 & 0.479 & 1.313 & 0.409 & 0.167 & 1.001\\
\hline
Hematology & -0.463 & -1.120 & 0.193 & -0.369 & -1.026 & 0.287 & -1.287 & -2.220 & -0.354 & 0.629 & 0.326 & 1.213 & 0.691 & 0.359 & 1.333 & 0.276 & 0.109 & 0.702\\
\hline
Heart & -3.573 & -4.272 & -2.874 & -2.980 & -3.549 & -2.411 & -3.877 & -4.443 & -3.311 & 0.028 & 0.014 & 0.056 & 0.051 & 0.029 & 0.090 & 0.021 & 0.012 & 0.036\\
\hline
Hearing & -3.059 & -5.049 & -1.068 & -2.361 & -4.352 & -0.370 & -3.602 & -5.592 & -1.611 & 0.047 & 0.006 & 0.344 & 0.094 & 0.013 & 0.690 & 0.027 & 0.004 & 0.200\\
\hline
Eye & -3.707 & -5.102 & -2.312 & -3.228 & -4.331 & -2.125 & -5.773 & -6.574 & -4.972 & 0.025 & 0.006 & 0.099 & 0.040 & 0.013 & 0.119 & 0.003 & 0.001 & 0.007\\
\hline
All & -2.290 & -2.648 & -1.932 & -1.936 & -2.254 & -1.619 & -3.452 & -3.944 & -2.960 & 0.101 & 0.071 & 0.145 & 0.144 & 0.105 & 0.198 & 0.032 & 0.019 & 0.052\\
\hline
\end{tabular}
\end{table}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# scroll_box(width = '100%', height = '200px')}
\end{Highlighting}
\end{Shaded}

\hypertarget{r-session-information}{%
\section{R Session Information}\label{r-session-information}}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{sessionInfo}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## R version 3.6.0 (2019-04-26)
## Platform: x86_64-apple-darwin15.6.0 (64-bit)
## Running under: macOS  10.15.4
## 
## Matrix products: default
## BLAS:   /Library/Frameworks/R.framework/Versions/3.6/Resources/lib/libRblas.0.dylib
## LAPACK: /Library/Frameworks/R.framework/Versions/3.6/Resources/lib/libRlapack.dylib
## 
## locale:
## [1] en_AU.UTF-8/en_AU.UTF-8/en_AU.UTF-8/C/en_AU.UTF-8/en_AU.UTF-8
## 
## attached base packages:
## [1] grid      stats     graphics  grDevices utils     datasets  methods  
## [8] base     
## 
## other attached packages:
##  [1] knitr_1.28       here_0.1         png_0.1-7        ggpubr_0.3.0    
##  [5] robumeta_2.0     kableExtra_1.1.0 forcats_0.5.0    stringr_1.4.0   
##  [9] tidyr_1.0.3      tibble_3.0.1     ggplot2_3.3.0    tidyverse_1.3.0 
## [13] purrr_0.3.4      devtools_2.3.0   usethis_1.6.1    metafor_2.4-0   
## [17] Matrix_1.2-18    dplyr_0.8.5      readr_1.3.1      pacman_0.5.1    
## 
## loaded via a namespace (and not attached):
##  [1] nlme_3.1-147      fs_1.4.1          lubridate_1.7.8   webshot_0.5.2    
##  [5] httr_1.4.1        rprojroot_1.3-2   tools_3.6.0       backports_1.1.6  
##  [9] R6_2.4.1          DBI_1.1.0         colorspace_1.4-1  withr_2.2.0      
## [13] tidyselect_1.1.0  prettyunits_1.1.1 processx_3.4.2    curl_4.3         
## [17] compiler_3.6.0    cli_2.0.2         rvest_0.3.5       formatR_1.7      
## [21] xml2_1.3.2        desc_1.2.0        scales_1.1.1      callr_3.4.3      
## [25] digest_0.6.25     foreign_0.8-71    rmarkdown_2.1     rio_0.5.16       
## [29] pkgconfig_2.0.3   htmltools_0.4.0   sessioninfo_1.1.1 dbplyr_1.4.3     
## [33] rlang_0.4.6       readxl_1.3.1      rstudioapi_0.11   generics_0.0.2   
## [37] jsonlite_1.6.1    zip_2.0.4         car_3.0-7         magrittr_1.5     
## [41] Rcpp_1.0.4.6      munsell_0.5.0     fansi_0.4.1       abind_1.4-5      
## [45] lifecycle_0.2.0   stringi_1.4.6     yaml_2.2.1        carData_3.0-3    
## [49] pkgbuild_1.0.8    crayon_1.3.4      lattice_0.20-41   haven_2.2.0      
## [53] hms_0.5.3         ps_1.3.3          pillar_1.4.4      ggsignif_0.6.0   
## [57] codetools_0.2-16  pkgload_1.0.2     reprex_0.3.0      glue_1.4.0       
## [61] evaluate_0.14     data.table_1.12.8 remotes_2.1.1     modelr_0.1.7     
## [65] vctrs_0.3.0       testthat_2.3.2    cellranger_1.1.0  gtable_0.3.0     
## [69] assertthat_0.2.1  xfun_0.13         openxlsx_4.1.5    broom_0.5.6      
## [73] rstatix_0.5.0     viridisLite_0.3.0 memoise_1.1.0     ellipsis_0.3.0
\end{verbatim}

\end{document}

### 2020-05-19 scripts/MouseSexDiffApril20_2020.Rmd
More supplements stuff. Added in mean-variance relationships

@@
 ---
-title: "Sex and Power: Sexual dimorphism in trait variability and its eco-evolutionary and statistical implications"
+title: 'Sex and Power: Sexual dimorphism in trait variability and its eco-evolutionary
+  and statistical implications'
 author: Susanne Zajitschek,  Felix Zajitschek, Russell Bonduriansky, Robert  Brooks,
-  Will Cornwell, Daniel Falster, Malgorzata Lagisz, Jeremy Mason, Alistair
-  Senior, Daniel Noble, & Shinichi Nakagawa
+  Will Cornwell, Daniel Falster, Malgorzata Lagisz, Jeremy Mason, Alistair Senior,
+  Daniel Noble, & Shinichi Nakagawa
 date: "`r Sys.Date()`"
 output:
+  bookdown::html_document2:
+    code_folding: hide
+    number_sections: yes
+    theme: flatly
+    toc: yes
+    toc_depth: 6
+    toc_float: yes
   word_document:
@@
     toc_depth: '4'
-  bookdown::html_document2: 
-            toc: true
-            code_folding: hide
-            toc_depth: 6
-            toc_float: yes
-            number_sections: yes
-            theme: flatly
+  html_document:
+    df_print: paged
+    toc: yes
+    toc_depth: '4'
 subtitle: Electronic Supplementary Material
@@
 library(pacman)
-pacman::p_load(readr, dplyr,metafor, devtools, purrr, tidyverse, tidyr, tibble, kableExtra, robumeta, ggpubr, ggplot2, png, grid, here, knitr)
+pacman::p_load(readr, dplyr,metafor, devtools, purrr, tidyverse, tidyr, tibble, kableExtra, robumeta, ggpubr, ggplot2, png, grid, here, knitr, pander, splus2R)
 ```
@@
 Generally speaking, the first few sections describe the processes by which the data were cleaned and re-organised for analysis.
-This iss followed by how the first order and second order meta-analsyes were conducted.
-Supplemental tables and figures that are referenecd within the main manuscript can be found at the end of the document.
-Various parts of the workflow can be conviently referenecd using the side table of contents panel.
+This is followed by how the first order and second order meta-analyses were conducted.
+Supplemental tables and figures that are referenced within the main manuscript can be found at the end of the document.
+Various parts of the workflow can be conveniently referenced using the table of contents panel (located along the side).
 We will refer back to this figure as we describe the various aspects of the code and data processing in relevant places.
 
-```{r FigG1, fig.cap="Workflow of data process and meta-analysis"}
+```{r FigG1, fig.width = 4, fig.height = 8, fig.cap="Workflow of data process and meta-analysis"}
 
@@
     ungroup() %>%
-    filter(n_ind > min_individuals) %>%   # NOTE here that you are excluding data with 5 exactly....
+    filter(n_ind > min_individuals) %>%   
     group_by(population) %>%
@@
 ```
+## Mean-variance relationships
+We can also have a look at the mean-variance relationships in these data (Figure \@ref(fig:FigCor)).
+Note that these data have not been filtered to the same extent that the data is that is used in the meta-analyses, but this is simply here to demonstrate that mean-variance relationships exist and are strong providing strong justification for using the log coefficient of variation ratio (lnCVR).
+
+```{r FigCor, fig.height=3, message = FALSE, fig.cap= "Mean-variance relationships (log(Mean) vs log(SD, standard deviation)) across all traits for males (A) and females (B)."}
+
+# First, clean up the data
+
+ results <- data %>%
+            group_by(population,
+             production_center,  
+             strain_name,  
+             parameter_name,
+             sex) %>%
+    summarise(trait  = parameter_name[1],
+              x_bar  = mean(data_point, na.rm = TRUE),
+              x_sd   =   sd(data_point, na.rm = TRUE),
+              n_ind  = n()) %>%
+    ungroup() %>%
+    filter(n_ind > 5) %>%   # NOTE here that you are excluding data with 5 exactly....
+    group_by(population) %>%
+    filter(all(c("male", "female") %in% sex)) %>% # Removes any entries where only 1 sex is present
+    multi_spread(sex, c(x_bar, x_sd, n_ind)) %>%
+    mutate(lnMean_m = log(male_x_bar),
+           logSD_m  = log(male_x_sd),
+           lnMean_f = log(female_x_bar),
+           lnSD_f   = log(female_x_sd)) %>%
+    filter(!is.na(logSD_m) & !is.inf(logSD_m)) %>%
+    filter(!is.na(lnSD_f) & !is.inf(lnSD_f))
+
+male <- ggplot(results, aes(x = lnMean_m, y = logSD_m)) +
+    geom_point(color = "blue", size = 2) +
+   geom_smooth(method = "lm", se = FALSE, color="black") + 
+    labs(x = "log (Mean)",
+         y = "log (SD)") + 
+    theme_classic()
+
+female <- ggplot(results, aes(x = lnMean_f, y = lnSD_f)) +
+    geom_point(color = "pink", size = 2) +
+  geom_smooth(method = "lm", se = FALSE, color="black")+
+    labs(x = "log (Mean)",
+         y = "log (SD)") + 
+    theme_classic()
+
+ggarrange(male, female, ncol = 2, nrow = 1, labels = c("A", "B"))
+
+```
+
+We can see that there are strong relationships between the log transformed means and standard deviations for both males (Figure \@ref(fig:FigCor)A) and females (Figure \@ref(fig:FigCor)B), with the Person's correlation coefficient being `r round(stats::cor(results$lnMean_m,results$logSD_m, use = "complete.obs"), digits = 3) ` and `r round(cor(results$lnMean_f, results$lnSD_f, use = "complete.obs"), digits = 3) `, respectively.
 
@@
 
-In this section, we cover the workflow described in Figure \@ref(fig:FigG1) C and D.
+In this section, we cover the workflow described in Figure \@ref(fig:FigG1)C and D.
 
@@
 
-This section covers Figure \@ref(fig:FigG1) C, by conducting a meta-analsyis for all traits and producing the meta-analysed effect sizes (lnVR, lnCVR and lnRR).
+This section covers Figure \@ref(fig:FigG1) C, by conducting a meta-analysis for all traits and producing the meta-analysed effect sizes (lnVR, lnCVR and lnRR).
 
@@
 
-Here we cover Figure \@ref(fig:FigG1) D, removing non-coverging model results and non-informative traits.Procedure names, grouping variables and trait names ("parameter_names") are the merged back together with the results from the metafor analysis above.
+Here we cover Figure \@ref(fig:FigG1)D, removing non-coverging model results and non-informative traits.
+Procedure names, grouping variables and trait names ("parameter_names") are the merged back together with the results from the metafor analysis above.
 
@@
 As those data-points are not independent of each other,  we conducted meta analyses on these correlated parameters to collapse the number of levels.
-This section describes the workflow depicted in Figure \@ref(fig:FigG1) E & F.
-
-### Collapsing and merging correlated parameters, preparation for Table S2
+This section describes the workflow depicted in Figure \@ref(fig:FigG1)E & F.
+
+### Collapsing and merging correlated parameters
 Count the number of parameter names (correlated sub-traits) in each parameter group (par_group_size).
@@
 All instances, where there are 2 or more traits associated with the same parameter group (90 cases), are selected for a "mini-meta analysis", which removes the issue of correlation.
-The workflow here relates to Figure \@ref(fig:FigG1) E.
+The workflow here relates to Figure \@ref(fig:FigG1)E.
 
@@
 ## Second-order meta-analysis for functional groups
-Here, we  describe the workflow depicted in Figure \@ref(fig:FigG1) H.
+Here, we describe the workflow depicted in Figure \@ref(fig:FigG1)H.
 We now use our uncorrelated traits from our first order meta-analysis to conduct a secondary meta-analysis by analysing the 9 functional trait groups.
-We esatimte an overall mean lnCVR, lnVR and lnRR for each functional trait group.
+We estimate an overall mean lnCVR, lnVR and lnRR for each functional trait group.
 
@@
 
-The analysis for heterogeneity follows the workflow of the above steps for the different meta-analyses and specifically Figure \@ref(fig:FigG1) I & J.
+To see how much heterogeneity there is for each trait across different populations on average (for different functional groups and overall), we also conducted secondary meta-analyses by combining the total heterogeneities.
+More specifically, we combined the logarithm of the sum of the three variance components (Strain, Location and Unit; see above) with 1/2(N[effect size] - 1) as the sampling variance via the random effect model.
+That is, we conducted 3 sets of 10 secondary meta-analyses as with those of mean effect sizes for each trait, i.e.
+meta-analyzing log(total heterogeneities) for 9 functional groups and all the groups combined (Figure \@ref(fig:FigG1)I).
+The analysis for heterogeneity follows the workflow of the above steps for the different meta-analyses and specifically Figure \@ref(fig:FigG1)I & J.
 However, in the initial meta-analysis we extract sigma^2 and errors for mouse strains and centers (Institutions).
@@
 names.
-Dealing with the correlated parameters, and running the second -order meta-analysis for heterogeneity data (Figure \@ref(fig:FigG1) I)
+Dealing with the correlated parameters, and running the second -order meta-analysis for heterogeneity data (Figure \@ref(fig:FigG1)I)
 
@@
 # Meta-analysis results
-## Preparation for Figure 4 
+## Preparing: Figure 3 
 ### Count data, based on First-order meta-analysis results
@@
 
-## Figure 4
-
-Panel A shows the numbers of traits across functional groups that are either male-biased (blue-green) or female-biased (orange-red), as calculated in Figure \@ref(fig:FigG1) D.
-Panel B shows effect sizes and 95% CI from separate meta-analysis for each functional group (step H in Figure \@ref(fig:FigG1)).
-Both panels represent results evaluated across all traits (Phase 3, Figure \@ref(fig:FigG1)).
-Traits that are male biased are shown in blue, whereas female bias data is represented in orange.
-
-```{r Fig4}
+## Main Manuscript: Figure 3
+
+```{r Fig3, fig.cap = "Panel A shows the numbers of traits across functional groups that are either male-biased (blue-green) or female-biased (orange-red), as calculated in Figure 1.1D.
+Panel B shows effect sizes and 95% CI from separate meta-analysis for each functional group (step H in Figure1.1).
+Both panels represent results evaluated across all traits.
+Traits that are male biased are shown in blue, whereas female bias data is represented in orange."}
 Fig4 <- ggarrange(malebias_Fig2_alltraits, Metameta_Fig3_alltraits,  nrow = 2, align = "v", heights = c(10, 9), labels = c("A", "B"))
@@
 
-## Preparation for Figure 5
-To further investigate sex bias in this dataset, and in particular if the extent of sex bias differs between traits, we investigate the magnitude of male- and female bias in significantly different traits on (both for means and variability)
-
-To do this, we select only traits that have CIs that do not overlap with zero.
-The code below creates Figure 5A.
-```{r Fig5_prep}
-
+# Supplemental Figures
+
+```{r FigS1_prep, echo = FALSE, eval = TRUE}
+### Preparing the data
+#The supplemental figures include lnVR (in addition to lnCVR and lnRR, as presented in Figures 4 and 5)
+
+# *Prepare data for all traits
+
+meta.plot2.all <- meta_clean %>%
+  select(lnCVR, lnVR, lnRR, GroupingTerm) %>%
+  arrange(GroupingTerm)
+
+meta.plot2.all.bS1 <- gather(meta.plot2.all, trait, value, c(lnCVR, lnVR, lnRR))
+
+meta.plot2.all.bS1$trait <- factor(meta.plot2.all.bS1$trait, levels = c("lnCVR", "lnVR", "lnRR"))
+
+meta.plot2.all.cS1 <- meta.plot2.all.bS1 %>%
+  group_by_at(vars(trait, GroupingTerm)) %>%
+  summarise(
+    malebias = sum(value > 0), femalebias = sum(value <= 0), total = malebias + femalebias,
+    malepercent = malebias * 100 / total, femalepercent = femalebias * 100 / total
+  )
+
+meta.plot2.all.cS1$label <- "All traits"
+
+# Re-structure to create stacked bar plots
+
+meta.plot2.all.dS1 <- as.data.frame(meta.plot2.all.cS1)
+meta.plot2.all.eS1 <- gather(meta.plot2.all.dS1, key = sex, value = percent, malepercent:femalepercent, factor_key = TRUE)
+
+# Create new sample size variable
+
+meta.plot2.all.eS1$samplesize <- with(meta.plot2.all.eS1, ifelse(sex == "malepercent", malebias, femalebias))
+
+# Add summary row ('All') and re-arrange rows into correct order for plotting (warnings about coercing 'id' into character vector are ok)
+
+meta.plot2.all.fS1 <- meta.plot2.all.eS1 %>% group_by(trait, sex) %>% 
+  summarise(GroupingTerm = "All", malebias = sum(malebias), femalebias = sum(femalebias), total = malebias + femalebias, 
+            label = "All traits", samplesize = sum(samplesize)) %>%
+  mutate(percent = ifelse(sex == "femalepercent", femalebias*100/(malebias+femalebias), malebias*100/(malebias+femalebias))) %>%
+  bind_rows(meta.plot2.all.eS1, .) %>%
+  mutate(rownumber = row_number()) %>%
+  .[c(55, 1:9, 57, 10:18, 59, 19:27, 56, 28:36, 58, 37:45, 60, 46:54), ]
+
+meta.plot2.all.fS1$GroupingTerm <- factor(meta.plot2.all.fS1$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
+meta.plot2.all.fS1$GroupingTerm <- factor(meta.plot2.all.fS1$GroupingTerm, rev(levels(meta.plot2.all.fS1$GroupingTerm)))
+
+malebias_FigS1_alltraits <-
+  ggplot(meta.plot2.all.fS1) +
+  aes(x = GroupingTerm, y = percent, fill = sex) +
+  ylab("Percentage") +
+  geom_col() +
+  geom_hline(yintercept = 50, linetype = "dashed", color = "gray40") +
+  geom_text(
+    data = subset(meta.plot2.all.fS1, samplesize != 0), aes(label = samplesize), position = position_stack(vjust = .5),
+    color = "white", size = 3.5
+  ) +
+  facet_grid(
+    cols = vars(trait), rows = vars(label), labeller = label_wrap_gen(width = 18),
+    scales = "free", space = "free"
+  ) +
+  scale_fill_brewer(palette = "Set2") +
+  theme_bw(base_size = 18) +
+  theme(
+    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
+    strip.text.x = element_text(size = 12),
+    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
+    text = element_text(size = 14),
+    panel.spacing = unit(0.5, "lines"),
+    panel.border = element_blank(),
+    axis.line = element_line(),
+    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
+    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
+    panel.grid.minor.y = element_blank(),
+    panel.grid.minor.x = element_blank(),
+    legend.position = "none",
+    #axis.title.x = element_blank(),
+    axis.title.y = element_blank()
+  ) +
+  coord_flip()
+
+# malebias_FigS1_alltraits     #(panel A in Figure S1)
+
+###  Overall results of second order meta analysis, INCLUDING VR
+#### Re-structure MALE data for plotting
+
+overall3.male.sigS <- gather(overall.male.plot3, parameter, value, c(lnCVR, lnVR, lnRR), factor_key = TRUE)
+
+lnCVR.ci <- overall3.male.sigS %>%
+  filter(parameter == "lnCVR") %>%
+  mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
+lnVR.ci <- overall3.male.sigS %>%
+  filter(parameter == "lnVR") %>%
+  mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
+lnRR.ci <- overall3.male.sigS %>%
+  filter(parameter == "lnRR") %>%
+  mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
+
+overall4.male.sigS <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
+
+overall4.male.sigS$label <- "CI not overlapping zero"
+
+# Data are re-structured, and grouping terms are being re-ordered
+
+overall3S <- gather(overall2, parameter, value, c(lnCVR, lnVR, lnRR), factor_key = TRUE)
+
+lnCVR.ci <- overall3S %>%
+  filter(parameter == "lnCVR") %>%
+  mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
+lnVR.ci <- overall3S %>%
+  filter(parameter == "lnVR") %>%
+  mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
+lnRR.ci <- overall3S %>%
+  filter(parameter == "lnRR") %>%
+  mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
+
+overall4S <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
+
+# Re-order grouping terms
+
+overall4S$GroupingTerm <- factor(overall4S$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
+overall4S$GroupingTerm <- factor(overall4S$GroupingTerm, rev(levels(overall4S$GroupingTerm)))
+overall4S$label <- "All traits"
+
+#### Preparation for plot, including lnVR
+# Sub-Plot  for Figure S1: all traits (S1 B)
+
+Metameta_FigS1_alltraits <- overall4S %>%
+
+  ggplot(aes(y = GroupingTerm, x = value)) +
+  geom_errorbarh(aes(
+    xmin = ci.low,
+    xmax = ci.high
+  ),
+  height = 0.1, show.legend = FALSE
+  ) +
+  geom_point(aes(shape = parameter),
+    fill = "black",
+    color = "black", size = 2.2,
+    show.legend = FALSE
+  ) +
+  scale_x_continuous(
+    limits = c(-0.24, 0.25),
+    breaks = c(-0.2, -0.1, 0, 0.1, 0.2),
+    name = "Effect size"
+  ) +
+  geom_vline(
+    xintercept = 0,
+    color = "black",
+    linetype = "dashed"
+  ) +
+  facet_grid(
+    cols = vars(parameter), rows = vars(label),
+    labeller = label_wrap_gen(width = 23),
+    scales = "free",
+    space = "free"
+  ) +
+  theme_bw() +
+  theme(
+    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
+    strip.text.x = element_text(size = 12),
+    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
+    text = element_text(size = 14),
+    panel.spacing = unit(0.5, "lines"),
+    panel.border = element_blank(),
+    axis.line = element_line(),
+    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
+    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
+    panel.grid.minor.y = element_blank(),
+    panel.grid.minor.x = element_blank(),
+    legend.title = element_blank(),
+    axis.title.x = element_text(hjust = 0.5, size = 14),
+    axis.title.y = element_blank()
+  )
+
+# Metameta_FigS1_alltraits
+```
+
+```{r, eval = TRUE, echo = FALSE}
+
+#This Figure extends Figure 4, as it includes results not only for lnCVR and lnRR but also lnCVR.
+In addition, we compare two different assessments of sex-bias, significance (CI not overlapping zero) and sex differences in male / female ratios > 10%
+# Plot FigS2 all significant results (CI not overlapping zero) for males, count data
+
+meta.plot2.sig.bS <- meta.plot2.sig[, c("lnCVR", "lnVR", "lnRR", "lnCVRsig", "lnVRsig", "lnRRsig", "GroupingTerm")]
+
+meta.plot2.sig.cS <- gather(meta.plot2.sig.bS, trait, value, lnCVR:lnRR)
+meta.plot2.sig.cS$sig <- "placeholder"
+
+meta.plot2.sig.cS$trait <- factor(meta.plot2.sig.cS$trait, levels = c("lnCVR", "lnVR", "lnRR"))
+
+meta.plot2.sig.cS$sig <- ifelse(meta.plot2.sig.cS$trait == "lnCVR", meta.plot2.sig.cS$lnCVRsig,
+  ifelse(meta.plot2.sig.cS$trait == "lnVR", meta.plot2.sig.cS$lnVRsig, meta.plot2.sig.cS$lnRRsig))
+
+# choosing sex biased ln-ratios significantly larger than 0
+meta.plotS2.sig.malebias <- meta.plot2.sig.cS %>%
+  group_by_at(vars(trait, GroupingTerm)) %>%
+  filter(sig == 1) %>%
+  summarise(male_sig = sum(value > 0), female_sig = sum(value < 0), total = male_sig + female_sig)
+
+meta.plotS2.sig.malebias <- ungroup(meta.plotS2.sig.malebias) %>%
+  add_row(trait = "lnCVR", GroupingTerm = "Hearing", male_sig = 0, female_sig = 0, .before = 4) %>% # add "Hearing" for lnCVR (not filtered as only zeros)
+  mutate(malepercent = male_sig * 100 / total, femalepercent = female_sig * 100 / total)
+
+meta.plotS2.sig.malebias$label <- "CI not overlapping zero"
+
+# restructure to create stacked bar plots
+
+meta.plotS2.sig.bothsexes <- as.data.frame(meta.plotS2.sig.malebias)
+meta.plotS2.sig.bothsexes.b <- gather(meta.plotS2.sig.bothsexes, key = sex, value = percent, malepercent:femalepercent, factor_key = TRUE)
+
+# create new sample size variable
+
+meta.plotS2.sig.bothsexes.b$samplesize <- with(meta.plotS2.sig.bothsexes.b, ifelse(sex == "malepercent", male_sig, female_sig))
+
+# Add summary row ('All') and re-arrange rows into correct order for plotting (warnings about coercing 'id' into character vector are ok)
+
+meta.plotS2.sig.bothsexes.c <- meta.plotS2.sig.bothsexes.b %>% group_by(trait, sex) %>% 
+  summarise(GroupingTerm = "All", male_sig = sum(male_sig), female_sig = sum(female_sig), total = male_sig + female_sig, 
+            label = "CI not overlapping zero", samplesize = sum(samplesize)) %>%
+  mutate(percent = ifelse(sex == "femalepercent", female_sig*100/(male_sig + female_sig), male_sig*100/(male_sig + female_sig))) %>%
+  bind_rows(meta.plotS2.sig.bothsexes.b, .) %>%
+  mutate(rownumber = row_number()) %>%
+  .[c(55, 1:9, 57, 10:18, 59, 19:27, 56, 28:36, 58, 37:45, 60, 46:54), ]
+
+meta.plotS2.sig.bothsexes.c$GroupingTerm <- factor(meta.plotS2.sig.bothsexes.c$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
+meta.plotS2.sig.bothsexes.c$GroupingTerm <- factor(meta.plotS2.sig.bothsexes.c$GroupingTerm, rev(levels(meta.plotS2.sig.bothsexes.c$GroupingTerm)))
+
+# *Plot Fig2 all significant results (CI not overlapping zero):
+#     no sig. lnCVR for 'Hearing' in either sex; no sig. male-biased lnCVR for 'Immunology' and 'Eye, and no sig. male-biased lnVR for 'Eye'
+
+malebias_FigS2_sigtraits <-
+  ggplot(meta.plotS2.sig.bothsexes.c) +
+  aes(x = GroupingTerm, y = percent, fill = sex) +
+  ylab("Percentage") +
+  geom_col() +
+  geom_hline(yintercept = 50, linetype = "dashed", color = "gray40") +
+  geom_text(
+    data = subset(meta.plotS2.sig.bothsexes.c, samplesize != 0), aes(label = samplesize), position = position_stack(vjust = .5),
+    color = "white", size = 3.5
+  ) +
+  facet_grid(
+    cols = vars(trait), rows = vars(label), labeller = label_wrap_gen(width = 18),
+    scales = "free", space = "free"
+  ) +
+  scale_fill_brewer(palette = "Set2") +
+  theme_bw(base_size = 18) +
+  theme(
+    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
+    strip.text.x = element_text(size = 12),
+    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
+    text = element_text(size = 14),
+    panel.spacing = unit(0.5, "lines"),
+    panel.border = element_blank(),
+    axis.line = element_line(),
+    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
+    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
+    panel.grid.minor.y = element_blank(),
+    panel.grid.minor.x = element_blank(),
+    legend.position = "none",
+    #axis.title.x = element_blank(),
+    axis.title.y = element_blank()
+  ) +
+  coord_flip()
+
+# malebias_FigS2_sigtraits # this is Figure S2 A
+
+#Prepare data for traits with effect size ratios > 10% larger in males, supplemental Figure S2
+
+#### Over 10% male bias, count data (first- order metanalysis)
+
+meta.plot2.over10 <- meta_clean %>%
+                    select(lnCVR, lnVR, lnRR, GroupingTerm) %>%
+                    arrange(GroupingTerm)
+
+meta.plot2.over10.b <- gather(meta.plot2.over10, trait, value, c(lnCVR, lnVR, lnRR))
+
+meta.plot2.over10.b$trait <- factor(meta.plot2.over10.b$trait, levels = c("lnCVR", "lnVR", "lnRR"))
+
+meta.plot2.over10.c <- meta.plot2.over10.b %>%
+                      group_by_at(vars(trait, GroupingTerm)) %>%
+                      summarise(malebias = sum(value > log(11 / 10)), 
+                                femalebias = sum(value < log(9 / 10)), 
+                                total = malebias + femalebias,
+                                malepercent = malebias * 100 / total, 
+                                femalepercent = femalebias * 100 / total)
+
+meta.plot2.over10.c$label <- "Sex difference in m/f ratios > 10%"
+
+# restructure to create stacked bar plots
+
+meta.plot2.over10.c <- as.data.frame(meta.plot2.over10.c)
+meta.plot2.over10.d <- gather(meta.plot2.over10.c, key = sex, value = percent, malepercent:femalepercent, factor_key = TRUE)
+
+# create new sample size variable
+
+meta.plot2.over10.d$samplesize <- with(meta.plot2.over10.d, ifelse(sex == "malepercent", malebias, femalebias))
+
+# Add summary row ('All') and re-arrange rows into correct order for plotting (warnings about coercing 'id' into character vector are ok)
+
+meta.plot2.over10.e <- meta.plot2.over10.d %>% 
+                      group_by(trait, sex) %>% 
+                      summarise(GroupingTerm = "All", malebias = sum(malebias), 
+                                femalebias = sum(femalebias), 
+                                total = malebias + femalebias, 
+                                label = "Sex difference in m/f ratios > 10%", 
+                                samplesize = sum(samplesize)) %>%
+                      mutate(percent = ifelse(sex == "femalepercent", 
+                                              femalebias*100/(malebias + femalebias), 
+                                              malebias*100/(malebias + femalebias))) %>%
+                      bind_rows(meta.plot2.over10.d, .) %>%
+                      mutate(rownumber = row_number()) %>%
+                      .[c(55, 1:9, 57, 10:18, 59, 19:27, 56, 28:36, 58, 37:45, 60, 46:54), ]
+
+meta.plot2.over10.e$GroupingTerm <- factor(meta.plot2.over10.e$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
+meta.plot2.over10.e$GroupingTerm <- factor(meta.plot2.over10.e$GroupingTerm, rev(levels(meta.plot2.over10.e$GroupingTerm)))
+
+# PLOT:  Fig2 Sex difference in m/f ratio > 10% (Fig S2 A, lower panel)
+
+malebias_Fig2_over10 <-
+  ggplot(meta.plot2.over10.e) +
+  aes(x = GroupingTerm, y = percent, fill = sex) +
+  ylab("Percentage") +
+  geom_col() +
+  geom_hline(yintercept = 50, linetype = "dashed", color = "gray40") +
+  geom_text(
+    data = subset(meta.plot2.over10.e, samplesize != 0), aes(label = samplesize), position = position_stack(vjust = .5),
+    color = "white", size = 3.5
+  ) +
+  facet_grid(
+    cols = vars(trait), rows = vars(label), labeller = label_wrap_gen(width = 18),
+    scales = "free", space = "free"
+  ) +
+  scale_fill_brewer(palette = "Set2") +
+  theme_bw(base_size = 18) +
+  theme(
+    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
+    strip.text.x = element_blank(),
+    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
+    text = element_text(size = 14),
+    panel.spacing = unit(0.5, "lines"),
+    panel.border = element_blank(),
+    axis.line = element_line(),
+    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
+    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
+    panel.grid.minor.y = element_blank(),
+    panel.grid.minor.x = element_blank(),
+    legend.position = "none",
+    #axis.title.x = element_blank(),
+    axis.title.y = element_blank()
+  ) +
+  coord_flip()
+
+# malebias_Fig2_over10  (supplemental Figure S2 A)
+```
+
+```{r FigS2_B, eval = TRUE, echo = FALSE}
+
+#### 3.2: Preparation for Figure S2 B (second-order meta-analysis)
+#### 3.3: Female Figure, significant and highly biased traits (Figure S2 B, left hand side panels)
+#Preparing data for traits with CI not overlapping 0: 
+#create column with 1= different from zero, 0= zero included in CI (for Figure S2 B, top left panel)
+
+#Restructure data for plotting
+
+overall3.female.sigS <- gather(overall.female.plot3, parameter, value, c(lnCVR, lnVR, lnRR), factor_key = TRUE)
+
+lnCVR.ci <- overall3.female.sigS %>%
+  filter(parameter == "lnCVR") %>%
+  mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
+lnVR.ci <- overall3.female.sigS %>%
+  filter(parameter == "lnVR") %>%
+  mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
+lnRR.ci <- overall3.female.sigS %>%
+  filter(parameter == "lnRR") %>%
+  mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
+
+overall4.female.sigS <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
+
+overall4.female.sigS$label <- "CI not overlapping zero"
+
+# PLOT female-bias:  significant traits
+
+Metameta_FigS2_female.sig <- overall4.female.sigS %>%
+  ggplot(aes(y = GroupingTerm, x = value)) +
+  geom_errorbarh(aes(
+    xmin = ci.low,
+    xmax = ci.high
+  ),
+  height = 0.1, show.legend = FALSE
+  ) +
+  geom_point(aes(shape = parameter),
+    fill = "salmon1", color = "salmon1", size = 2.2,
+    show.legend = FALSE
+  ) +
+  scale_x_continuous(
+    limits = c(-0.4, 0),
+    breaks = c(-0.3, 0),
+    name = "Effect size"
+  ) +
+  geom_vline(
+    xintercept = 0,
+    color = "black",
+    linetype = "dashed"
+  ) +
+  facet_grid(
+    cols = vars(parameter), # rows = vars(label),
+    # labeller = label_wrap_gen(width = 23),
+    scales = "free",
+    space = "free"
+  ) +
+  theme_bw() +
+  theme(
+    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
+    strip.text.x = element_text(size = 12),
+    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
+    text = element_text(size = 14),
+    panel.spacing = unit(0.5, "lines"),
+    panel.border = element_blank(),
+    axis.line = element_line(),
+    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
+    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
+    panel.grid.minor.y = element_blank(),
+    panel.grid.minor.x = element_blank(),
+    legend.title = element_blank(),
+    axis.title.x = element_blank(),
+    axis.title.y = element_blank()
+  )
+
+# Metameta_FigS2_female.sig
+
+#### Prepare data for traits with m/f difference > 10%, Female bias (Figure S2 B, bottom left)
+
+meta.plot3.perc <- metacombo %>%
+  mutate(
+    percCVR = ifelse(lnCVR < log(9 / 10), 1, 0),
+    percVR = ifelse(lnVR < log(9 / 10), 1, 0),
+    percRR = ifelse(lnRR < log(9 / 10), 1, 0)
+  )
+
+# Significant subset for lnCVR
+metacombo_plot3.CVR.perc <- meta.plot3.perc %>%
+  filter(percCVR == 1) %>%
+  group_by(GroupingTerm) %>%
+  nest()
+
+metacombo_plot3.CVR.perc.all <- meta.plot3.perc %>%
+  filter(percCVR == 1) %>%
+  nest(data = everything())
+
+# Significant subset for lnVR
+metacombo_plot3.VR.perc <- meta.plot3.perc %>%
+  filter(percVR == 1) %>%
+  group_by(GroupingTerm) %>%
+  nest()
+
+metacombo_plot3.VR.perc.all <- meta.plot3.perc %>%
+  filter(percVR == 1) %>%
+  nest(data = everything())
+
+# Significant subset for lnRR
+metacombo_plot3.RR.perc <- meta.plot3.perc %>%
+  filter(percRR == 1) %>%
+  group_by(GroupingTerm) %>%
+  nest()
+
+metacombo_plot3.RR.perc.all <- meta.plot3.perc %>%
+  filter(percRR == 1) %>%
+  nest(data = everything())
+
+# **Final fixed effects meta-analyses within grouping terms, with SE of the estimate
+
+plot3.meta.CVR.perc <- metacombo_plot3.CVR.perc %>%
+  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+plot3.meta.VR.perc <- metacombo_plot3.VR.perc %>%
+  mutate(model_lnVR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+plot3.meta.RR.perc <- metacombo_plot3.RR.perc %>%
+  mutate(model_lnRR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+# Across all grouping terms #
+
+plot3.meta.CVR.perc.all <- metacombo_plot3.CVR.perc.all %>%
+  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+plot3.meta.CVR.perc.all <- plot3.meta.CVR.perc.all %>% mutate(GroupingTerm = "All")
+
+plot3.meta.VR.perc.all <- metacombo_plot3.VR.perc.all %>%
+  mutate(model_lnVR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+plot3.meta.VR.perc.all <- plot3.meta.VR.perc.all %>% mutate(GroupingTerm = "All")
+
+plot3.meta.RR.perc.all <- metacombo_plot3.RR.perc.all %>%
+  mutate(model_lnRR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+plot3.meta.RR.perc.all <- plot3.meta.RR.perc.all %>% mutate(GroupingTerm = "All")
+
+# Combine with separate grouping term results
+
+plot3.meta.CVR.perc <- bind_rows(plot3.meta.CVR.perc, plot3.meta.CVR.perc.all)
+plot3.meta.VR.perc <- bind_rows(plot3.meta.VR.perc, plot3.meta.VR.perc.all)
+plot3.meta.RR.perc <- bind_rows(plot3.meta.RR.perc, plot3.meta.RR.perc.all)
+
+# **Re-structure data for each grouping term; delete un-used variables: "Hearing missing for all 3 parameters"
+
+plot3.meta.CVR.perc.b <- as.data.frame(plot3.meta.CVR.perc %>% group_by(GroupingTerm) %>%
+  mutate(
+    lnCVR = map_dbl(model_lnCVR, pluck(2)), lnCVR_lower = map_dbl(model_lnCVR, pluck(6)),
+    lnCVR_upper = map_dbl(model_lnCVR, pluck(7)), lnCVR_se = map_dbl(model_lnCVR, pluck(3))
+  ))[, c(1, 4:7)]
+add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.meta.CVR.perc.b))
+plot3.meta.CVR.perc.b <- rbind(plot3.meta.CVR.perc.b, add.row.hearing)
+plot3.meta.CVR.perc.b <- plot3.meta.CVR.perc.b[order(plot3.meta.CVR.perc.b$GroupingTerm), ]
+
+plot3.meta.VR.perc.b <- as.data.frame(plot3.meta.VR.perc %>% group_by(GroupingTerm) %>%
+  mutate(
+    lnVR = map_dbl(model_lnVR, pluck(2)), lnVR_lower = map_dbl(model_lnVR, pluck(6)),
+    lnVR_upper = map_dbl(model_lnVR, pluck(7)), lnVR_se = map_dbl(model_lnVR, pluck(3))
+  ))[, c(1, 4:7)]
+add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.meta.VR.perc.b))
+plot3.meta.VR.perc.b <- rbind(plot3.meta.VR.perc.b, add.row.hearing)
+plot3.meta.VR.perc.b <- plot3.meta.VR.perc.b[order(plot3.meta.VR.perc.b$GroupingTerm), ]
+
+plot3.meta.RR.perc.b <- as.data.frame(plot3.meta.RR.perc %>% group_by(GroupingTerm) %>%
+  mutate(
+    lnRR = map_dbl(model_lnRR, pluck(2)), lnRR_lower = map_dbl(model_lnRR, pluck(6)),
+    lnRR_upper = map_dbl(model_lnRR, pluck(7)), lnRR_se = map_dbl(model_lnRR, pluck(3))
+  ))[, c(1, 4:7)]
+add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.meta.RR.perc.b))
+plot3.meta.RR.perc.b <- rbind(plot3.meta.RR.perc.b, add.row.hearing)
+add.row.hematology <- as.data.frame(t(c("Hematology", NA, NA, NA, NA))) %>%
+  setNames(names(plot3.meta.RR.perc.b))
+plot3.meta.RR.perc.b <- rbind(plot3.meta.RR.perc.b, add.row.hematology)
+
+plot3.meta.RR.perc.b <- plot3.meta.RR.perc.b[order(plot3.meta.RR.perc.b$GroupingTerm), ]
+
+plot3.meta.CVR.perc.c <- full_join(plot3.meta.CVR.perc.b, plot3.meta.VR.perc.b)
+overall.plot3.perc <- full_join(plot3.meta.CVR.perc.c, plot3.meta.RR.perc.b)
+
+overall.plot3.perc$GroupingTerm <- factor(overall.plot3.perc$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
+overall.plot3.perc$GroupingTerm <- factor(overall.plot3.perc$GroupingTerm, rev(levels(overall.plot3.perc$GroupingTerm)))
+
+# Restructure data for plotting
+# Female bias, 10 percent difference
+
+overall3.perc <- gather(overall.plot3.perc, parameter, value, c(lnCVR, lnVR, lnRR), factor_key = TRUE)
+
+lnCVR.ci <- overall3.perc %>%
+  filter(parameter == "lnCVR") %>%
+  mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
+lnVR.ci <- overall3.perc  %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
+lnRR.ci <- overall3.perc %>%
+  filter(parameter == "lnRR") %>%
+  mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
+
+overall4.perc <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
+
+overall4.perc$label <- "Sex difference in m/f ratios > 10%"
+
+overall4.perc$value <- as.numeric(overall4.perc$value)
+overall4.perc$ci.low <- as.numeric(overall4.perc$ci.low)
+overall4.perc$ci.high <- as.numeric(overall4.perc$ci.high)
+
+# Plot FigS2 all >10% difference (female)
+# Figure S2B, bottom left
+
+Metameta_Fig3_female.perc <- overall4.perc %>%
+  ggplot(aes(y = GroupingTerm, x = value)) +
+  geom_errorbarh(aes(
+    xmin = ci.low,
+    xmax = ci.high
+  ),
+  height = 0.1, show.legend = FALSE
+  ) +
+  geom_point(aes(shape = parameter),
+    fill = "salmon1", color = "salmon1", size = 2.2,
+    show.legend = FALSE
+  ) +
+
+  # scale_shape_manual(values =
+
+  scale_x_continuous(
+    limits = c(-0.53, 0.2),
+    breaks = c(-0.3, 0),
+    name = "Effect size"
+  ) +
+  geom_vline(
+    xintercept = 0,
+    color = "black",
+    linetype = "dashed"
+  ) +
+  facet_grid(
+    cols = vars(parameter), # rows = vars(label),
+    # labeller = label_wrap_gen(width = 23),
+    scales = "free",
+    space = "free"
+  ) +
+  theme_bw() +
+  theme(
+    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
+    strip.text.x = element_blank(),
+    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
+    text = element_text(size = 14),
+    panel.spacing = unit(0.5, "lines"),
+    panel.border = element_blank(),
+    axis.line = element_line(),
+    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
+    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
+    panel.grid.minor.y = element_blank(),
+    panel.grid.minor.x = element_blank(),
+    legend.title = element_blank(),
+    axis.title.x = element_text(hjust = 0.5, size = 14),
+    axis.title.y = element_blank()
+  )
+
+# Metameta_Fig3_female.perc (Figure S2 bottom left panel)
+```
+
+```{r FigS2_B_right, eval = TRUE, echo = FALSE}
+#### 3.4: Male Figure, significant and highly biased traits (Figure S2 B, right hand side panels)
+#Restructuring data with significant male bias (for Figure S2 B, top right panel)
+
+overall3.male.sigS <- gather(overall.male.plot3, parameter, value, c(lnCVR, lnVR, lnRR), factor_key = TRUE)
+
+lnCVR.ci <- overall3.male.sigS %>%
+  filter(parameter == "lnCVR") %>%
+  mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
+lnVR.ci <- overall3.male.sigS %>%
+  filter(parameter == "lnVR") %>%
+  mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
+lnRR.ci <- overall3.male.sigS %>%
+  filter(parameter == "lnRR") %>%
+  mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
+
+overall4.male.sigS <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
+
+overall4.male.sigS$label <- "CI not overlapping zero"
+
+# Plot FigS2 all significant results (CI not overlapping zero, male )
+
+Metameta_FigS2_male.sig <- overall4.male.sigS %>%
+  ggplot(aes(y = GroupingTerm, x = value)) +
+  geom_errorbarh(aes(
+    xmin = ci.low,
+    xmax = ci.high
+  ),
+  height = 0.1, show.legend = FALSE
+  ) +
+  geom_point(aes(shape = parameter),
+    fill = "mediumaquamarine", color = "mediumaquamarine", size = 2.2,
+    show.legend = FALSE
+  ) +
+  scale_x_continuous(
+    limits = c(0, 0.4),
+    breaks = c(0, 0.3),
+    name = "Effect size"
+  ) +
+  geom_vline(
+    xintercept = 0,
+    color = "black",
+    linetype = "dashed"
+  ) +
+  facet_grid(
+    cols = vars(parameter), rows = vars(label),
+    labeller = label_wrap_gen(width = 23),
+    scales = "free",
+    space = "free"
+  ) +
+  theme_bw() +
+  theme(
+    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
+    strip.text.x = element_text(size = 12),
+    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
+    text = element_text(size = 14),
+    panel.spacing = unit(0.5, "lines"),
+    panel.border = element_blank(),
+    axis.line = element_line(),
+    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
+    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
+    panel.grid.minor.y = element_blank(),
+    panel.grid.minor.x = element_blank(),
+    legend.title = element_blank(),
+    axis.title.x = element_blank(),
+    axis.title.y = element_blank()
+  )
+
+# Metameta_FigS2_male.sig
+
+## Prepare data for traits with m/f difference > 10%. Male bias
+### Create column with 1= larger, 0= difference not larger than 10% between male/female ratios
+
+meta.male.plot3.perc <- metacombo %>%
+  mutate(
+    percCVR = ifelse(lnCVR > log(11 / 10), 1, 0),
+     percVR = ifelse( lnVR > log(11 / 10), 1, 0),
+     percRR = ifelse( lnRR > log(11 / 10), 1, 0)
+  )
+
+# Significant subset for lnCVR
+metacombo_male.plot3.CVR.perc <- meta.male.plot3.perc %>%
+                                filter(percCVR == 1) %>%
+                                group_by(GroupingTerm) %>%
+                                nest()
+
+metacombo_male.plot3.CVR.perc.all <- meta.male.plot3.perc %>%
+                filter(percCVR == 1) %>%
+  nest(data = everything())
+
+# Significant subset for lnVR
+metacombo_male.plot3.VR.perc <- meta.male.plot3.perc %>%
+  filter(percVR == 1) %>%
+  group_by(GroupingTerm) %>%
+  nest()
+
+metacombo_male.plot3.VR.perc.all <- meta.male.plot3.perc %>%
+  filter(percVR == 1) %>%
+  nest(data = everything())
+
+# Significant subset for lnRR
+metacombo_male.plot3.RR.perc <- meta.male.plot3.perc %>%
+  filter(percRR == 1) %>%
+  group_by(GroupingTerm) %>%
+  nest()
+
+metacombo_male.plot3.RR.perc.all <- meta.male.plot3.perc %>%
+  filter(percRR == 1) %>%
+  nest(data = everything())
+
+# Final fixed effects meta-analyses within grouping terms and across grouping terms, with SE of the estimate
+
+plot3.male.meta.CVR.perc <- metacombo_male.plot3.CVR.perc %>%
+  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+plot3.male.meta.VR.perc <- metacombo_male.plot3.VR.perc %>%
+  mutate(model_lnVR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+plot3.male.meta.RR.perc <- metacombo_male.plot3.RR.perc %>%
+  mutate(model_lnRR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+# Across all grouping terms
+
+plot3.male.meta.CVR.perc.all <- metacombo_male.plot3.CVR.perc.all %>%
+  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+plot3.male.meta.CVR.perc.all <- plot3.male.meta.CVR.perc.all %>% mutate(GroupingTerm = "All")
+
+plot3.male.meta.VR.perc.all <- metacombo_male.plot3.VR.perc.all %>%
+  mutate(model_lnVR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+plot3.male.meta.VR.perc.all <- plot3.male.meta.VR.perc.all %>% mutate(GroupingTerm = "All")
+
+plot3.male.meta.RR.perc.all <- metacombo_male.plot3.RR.perc.all %>%
+  mutate(model_lnRR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+plot3.male.meta.RR.perc.all <- plot3.male.meta.RR.perc.all %>% mutate(GroupingTerm = "All")
+
+# Combine with separate grouping term results
+
+plot3.male.meta.CVR.perc <- bind_rows(plot3.male.meta.CVR.perc, plot3.male.meta.CVR.perc.all)
+plot3.male.meta.VR.perc <- bind_rows(plot3.male.meta.VR.perc, plot3.male.meta.VR.perc.all)
+plot3.male.meta.RR.perc <- bind_rows(plot3.male.meta.RR.perc, plot3.male.meta.RR.perc.all)
+
+# **Re-structure data for each grouping term; delete un-used variables: "Hearing missing for all 3 parameters"
+
+plot3.male.meta.CVR.perc.b <- as.data.frame(plot3.male.meta.CVR.perc %>% group_by(GroupingTerm) %>%
+  mutate(
+    lnCVR = map_dbl(model_lnCVR, pluck(2)), lnCVR_lower = map_dbl(model_lnCVR, pluck(6)),
+    lnCVR_upper = map_dbl(model_lnCVR, pluck(7)), lnCVR_se = map_dbl(model_lnCVR, pluck(3))
+  ))[, c(1, 4:7)]
+add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.male.meta.CVR.perc.b))
+plot3.male.meta.CVR.perc.b <- rbind(plot3.male.meta.CVR.perc.b, add.row.hearing)
+plot3.male.meta.CVR.perc.b <- plot3.male.meta.CVR.perc.b[order(plot3.male.meta.CVR.perc.b$GroupingTerm), ]
+
+plot3.male.meta.VR.perc.b <- as.data.frame(plot3.male.meta.VR.perc %>% group_by(GroupingTerm) %>%
+  mutate(
+    lnVR = map_dbl(model_lnVR, pluck(2)), lnVR_lower = map_dbl(model_lnVR, pluck(6)),
+    lnVR_upper = map_dbl(model_lnVR, pluck(7)), lnVR_se = map_dbl(model_lnVR, pluck(3))
+  ))[, c(1, 4:7)]
+add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.male.meta.VR.perc.b))
+plot3.male.meta.VR.perc.b <- rbind(plot3.male.meta.VR.perc.b, add.row.hearing)
+plot3.male.meta.VR.perc.b <- plot3.male.meta.VR.perc.b[order(plot3.male.meta.VR.perc.b$GroupingTerm), ]
+
+plot3.male.meta.RR.perc.b <- as.data.frame(plot3.male.meta.RR.perc %>% group_by(GroupingTerm) %>%
+  mutate(
+    lnRR = map_dbl(model_lnRR, pluck(2)), lnRR_lower = map_dbl(model_lnRR, pluck(6)),
+    lnRR_upper = map_dbl(model_lnRR, pluck(7)), lnRR_se = map_dbl(model_lnRR, pluck(3))
+  ))[, c(1, 4:7)]
+add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>%
+  setNames(names(plot3.male.meta.RR.perc.b))
+plot3.male.meta.RR.perc.b <- rbind(plot3.male.meta.RR.perc.b, add.row.hearing)
+
+add.row.eye <- as.data.frame(t(c("Eye", NA, NA, NA, NA))) %>%
+  setNames(names(plot3.male.meta.RR.perc.b))
+plot3.male.meta.RR.perc.b <- rbind(plot3.male.meta.RR.perc.b, add.row.eye)
+
+plot3.male.meta.RR.perc.b <- plot3.male.meta.RR.perc.b[order(plot3.male.meta.RR.perc.b$GroupingTerm), ]
+
+plot3.male.meta.CVR.Vr.perc <- full_join(plot3.male.meta.CVR.perc.b, plot3.male.meta.VR.perc.b)
+overall.male.plot3.perc <- full_join(plot3.male.meta.CVR.Vr.perc, plot3.male.meta.RR.perc.b)
+
+overall.male.plot3.perc$GroupingTerm <- factor(overall.male.plot3.perc$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
+overall.male.plot3.perc$GroupingTerm <- factor(overall.male.plot3.perc$GroupingTerm, rev(levels(overall.male.plot3.perc$GroupingTerm)))
+
+# Restructure data for plotting : Male biased, 10% difference
+
+overall3.perc <- gather(overall.male.plot3.perc, parameter, value, c(lnCVR, lnVR, lnRR), factor_key = TRUE)
+
+lnCVR.ci <- overall3.perc %>%
+  filter(parameter == "lnCVR") %>%
+  mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
+lnVR.ci <- overall3.perc  %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
+lnRR.ci <- overall3.perc %>%
+  filter(parameter == "lnRR") %>%
+  mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
+
+overall4.male.perc <- bind_rows(lnCVR.ci,lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
+
+overall4.male.perc$label <- "Sex difference in m/f ratios > 10%"
+
+overall4.male.perc$value <- as.numeric(overall4.male.perc$value)
+overall4.male.perc$ci.low <- as.numeric(overall4.male.perc$ci.low)
+overall4.male.perc$ci.high <- as.numeric(overall4.male.perc$ci.high)
+
+# Plot Fig S2 all >10% difference (male bias)
+# S2 B, bottom right
+
+Metameta_Fig3_male.perc <- overall4.male.perc %>% # filter(., GroupingTerm != "Hearing") %>%
+  ggplot(aes(y = GroupingTerm, x = value)) +
+  geom_errorbarh(aes(
+    xmin = ci.low,
+    xmax = ci.high
+  ),
+  height = 0.1, show.legend = FALSE
+  ) +
+  geom_point(aes(
+    shape = parameter,
+    fill = parameter
+  ),
+  color = "mediumaquamarine", size = 2.2,
+  show.legend = FALSE
+  ) +
+  scale_x_continuous(
+    limits = c(-0.2, 0.62),
+    breaks = c(0, 0.3),
+    name = "Effect size"
+  ) +
+  geom_vline(
+    xintercept = 0,
+    color = "black",
+    linetype = "dashed"
+  ) +
+  facet_grid(
+    cols = vars(parameter), rows = vars(label),
+    labeller = label_wrap_gen(width = 23),
+    scales = "free",
+    space = "free"
+  ) +
+  theme_bw() +
+  theme(
+    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
+    strip.text.x = element_blank(),
+    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
+    text = element_text(size = 14),
+    panel.spacing = unit(0.5, "lines"),
+    panel.border = element_blank(),
+    axis.line = element_line(),
+    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
+    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
+    panel.grid.minor.y = element_blank(),
+    panel.grid.minor.x = element_blank(),
+    legend.title = element_blank(),
+    axis.title.x = element_text(hjust = 0.5, size = 14),
+    axis.title.y = element_blank()
+  )
+
+# Metameta_Fig3_male.perc (Figure S2 right panel)
+```
+
+## Figure
+Figure \@ref(fig:FigS1) is similar to Figure 3 in the main article.
+
+```{r FigS1, fig.height = 8, fig.width = 7, fig.cap=" Numbers of either male (blue-green bars) or female (orange-red bars) biased traits  (Panel A) across functional groups, this time for lnCVR (left hand side), lnVR (middle) and lnRR (right hand side).
+Panel B shows effect sizes from separate meta-analysis for each functional group, and Panel C contains results of heterogeneity analyses.
+All three panels represent results evaluated across all traits."}
+
+#### Combined Figure S1: overall Count data, Meta anlysis results, Heterogeneity
+
+FigS1 <- ggarrange(malebias_FigS1_alltraits, Metameta_FigS1_alltraits, HeteroS1, nrow = 3, align = "v", heights = c(1.1, 1, 1), labels = c("A", "B", "C"))
+FigS1
+#ggsave("FigS1_OverallResults.pdf", plot = FigS1, width = 6, height = 7)
+```
+
+## Figure
+
+### Sex-bias in traits: Methods and results
+
+#### Methods
+Among the 147 traits (i.e.
+with ‘first-order’ meta-analytic results), we found 31 traits to be significantly male-biased and 30 female-biased for lnCVR (47 male-biased and 39 female- biased for lnRR; 74 male and 55 female-biased for lnVR).
+We used this statistical significance to categorize traits into two groups: male-based and female-biased traits.
+For each set of these sex-biased traits, we conducted second-order meta-analyses with trait as the unit of analysis in the same way as those using lnRR, lnVR and lnCVR (Figure \@ref(fig:FigG1)J).
+As sensitivity analyses, we also employed another way of separating male- and female-biased traits.
+We quantified traits that were more than 10% biased towards either of the sexes, regardless of significance (N[male-biased] = 31, & N[female-biased] = 36 for lnCVR,  N[male-biased] = 56, & N[female-biased] = 57 for lnVR , N[male-biased] = 42, & N[female-biased] = 33  for lnRR; see Supplemental Figure S\@ref(fig:FigS2), Supplemental Table 7.3).
+
+#### Results
+Having established that different sex-biases were present across trait functional groups, we explored specific patterns in male and female bias by categorizing traits into either male or female-biased, and then, quantifying the degree of sex bias.
+To do this, we focused on only those traits that were significantly biased towards one sex (as indicated by “CI not overlapping 0” in Figure S\@ref(fig:FigS2).
+Selecting significantly sex-biased traits reduced the number of traits substantially (Figure S\@ref(fig:FigS2)A; compared to all traits, Figure \@ref(fig:Fig3) and Figure \@ref(fig:FigS1)), and returned similar numbers of traits with either significant male- or female-bias for lnCVR (Figure S\@ref(fig:FigS2)A).
+
+Looking only at traits with significant male-bias, trait variability tended to be higher in males than in females overall (11.77% male bias, lnCVR = 0.111, CI = [0.093 to 0.129]; compared to 8.3% female-bias, lnCVR = -0.087, CI = [-0.109 to (-0.064)]; Figure S\@ref(fig:FigS2)B).
+The degree of sex-bias varied across the functional trait groups, ranging from 4.6 % (Physiology, lnCVR = -0.047, CI = [-0.064 to (-0.030)] to 15.13 % (Eye morphology, lnCVR = -0.164, CI = [-0.249 to (-0.250)] in females, and from 8.6 % (Hematology, lnCVR = 0.082, CI = [0.048 to 0.117]) and 16.66 % (Heart, lnCVR = 0.154, CI = [0.085 to 0.223]) in males (Figure S\@ref(fig:FigS2)B).
+
+To put sex biases (sexual dimorphisms) in variability into perspective, we also quantify the degree of sexual dimorphism in significantly sex-biased traits (i.e., the extent of sexual dimorphisms).
+There were more traits that were significantly biased in mean trait value in males compared to females (Figure S\@ref(fig:FigS2)A, lnRR).
+These traits were 11.73 % biased towards males (Figure S\@ref(fig:FigS2)B; lnRR = 0.111, CI = [0.083 – 0.138]) while 9.38 % towards females (lnRR = -0.094, CI = [-0.129 – (-0.068)].
+The overall pattern for lnRR was more varied among the functional trait groups than for lnCVR, ranging from 1.2% (Hematology, lnRR = -0.013, CI = [-0.017 – (-0.007)] to 14.72 % (Immunology, lnRR = -0.159, CI = [-0.229 – (-0.089)] in female-based traits (Figure S\@ref(fig:FigS2)B) whereas in males-based traits from 1.8 % (Hearing, lnRR = 0.018, CI = [0.006 – 0.031]) to 25 % (Metabolism, lnRR = 0.223, CI = [0.110 – 0.335])  (Figure S\@ref(fig:FigS2)B).
+
+```{r FigS2, fig.height = 10, fig.width = 8, fig.cap=" A) Differences in numbers of affected traits, in variance (lnCVR and lnVR) and means (lnRR), where there’s a significant difference between the sexes (i.e CI not overlapping zero), and where the sex bias is greater than 10% difference (regardless of significance).
+Panel B depicts results for the sex bias in those traits that differ between the sexes (second-order meta-analysis).
+Triangles represent sex bias in means (response ratio) and black circles differences in the coefficient of variation ratio (mean-adjusted variability).
+The orange-red bars represent trait groups with a female bias, blue-green bars male-biased traits."}
+library(ggpubr)
+FigS2b <- ggarrange(Metameta_FigS2_female.sig, Metameta_FigS2_male.sig,
+  ncol = 2, nrow = 1, widths = c(1, 1.30), heights = c(1.2, 1.2))
+
+FigS2d <- ggarrange(Metameta_Fig3_female.perc, Metameta_Fig3_male.perc,
+  ncol = 2, nrow = 1, widths = c(1, 1.20), heights = c(1.1, 1.1))
+
+# end combination Figure 5
+FigS2 <- ggarrange(malebias_FigS2_sigtraits, malebias_Fig2_over10, FigS2b, FigS2d, ncol = 1, nrow = 4, heights = c(2.5, 2.2, 2.1, 2), labels = c("A", " ", "B", " "))
+FigS2
+```
+
+# Supplemental Tables
+## Table
+
+```{r Fig5_prep, echo = FALSE, eval = TRUE}
  meta.plot2.sig <- meta_clean %>%
@@
                            lnRRsig = ifelse( lnRR_lower * lnRR_upper  > 0, 1, 0))
-
 meta.plot2.sig.b <- meta.plot2.sig[, c("lnCVR", "lnRR", "lnCVRsig", "lnVRsig", "lnRRsig", "GroupingTerm")] 
-
     meta.plot2.sig.c <- gather(meta.plot2.sig.b, trait, value, lnCVR:lnRR)
 meta.plot2.sig.c$sig <- "placeholder"
-
 meta.plot2.sig.c$trait <- factor(meta.plot2.sig.c$trait, levels = c("lnCVR", "lnRR")) 
-
   meta.plot2.sig.c$sig <- ifelse(meta.plot2.sig.c$trait == "lnCVR", 
@@
                                         meta.plot2.sig.c$lnRRsig))
-
 # Choosing sex biased ln-ratios significantly larger than 0
@@
                            summarise(male_sig = sum(value > 0), female_sig = sum(value < 0), total = male_sig + female_sig)
-
 meta.plot2.sig.malebias <- ungroup(meta.plot2.sig.malebias) %>%
@@
                           mutate(malepercent = male_sig * 100 / total, femalepercent = female_sig * 100 / total)
-
 meta.plot2.sig.malebias$label <- "CI not overlapping zero"
-
 # Re-structure to create stacked bar plots
-
   meta.plot2.sig.bothsexes <- as.data.frame(meta.plot2.sig.malebias)
 meta.plot2.sig.bothsexes.b <- gather(meta.plot2.sig.bothsexes, key = sex, value = percent, malepercent:femalepercent, factor_key = TRUE)
-
 # create new sample size variable
-
 meta.plot2.sig.bothsexes.b$samplesize <- with(meta.plot2.sig.bothsexes.b, ifelse(sex == "malepercent", male_sig, female_sig))
-
 # Add summary row ('All') and re-arrange rows into correct order for plotting 
-
 meta.plot2.sig.bothsexes.c <- meta.plot2.sig.bothsexes.b %>% 
@@
                               .[c(37, 1:9, 39, 10:18, 38, 19:27, 40, 28:36), ] 
-
   #line references in previous code line corresponding to: 
@@
   #lnCVR(female(All)), lnCVR(female('single grouping terms'), lnRR(female(All)), lnRR(female('single grouping terms'))'
-
 meta.plot2.sig.bothsexes.c$GroupingTerm <- factor(meta.plot2.sig.bothsexes.c$GroupingTerm,
@@
                                                   rev(levels(meta.plot2.sig.bothsexes.c$GroupingTerm)))
-
 # Plot Fig2 all significant results (CI not overlapping zero)
@@
 male-biased lnCVR for 'Immunology' and 'Eye, and no significant female-biased lnRR for 'Eye'.
-
 malebias_Fig2_sigtraits <-
@@
   coord_flip()
-
 ### Preparation for Plots on significant sex-bias (Second-order meta analysis results)
-
 #### Figure 5 B - traits with CI not overlapping 0 
@@
 # create column with 1 = different from zero, 0 = zero included in CI
-
 #### Male-biased (significant) traits:
-
 meta.male.plot3.sig <- metacombo %>%
@@
                                sigRR = ifelse( lnRR_lower > 0, 1, 0))
-
 # Significant subset for lnCVR
@@
                             nest()
-
 metacombo_male.plot3.CVR.all <- meta.male.plot3.sig %>%
@@
                                 nest(data = everything())   
-
 # Significant subset for lnVR
@@
                            nest()
-
 metacombo_male.plot3.VR.all <- meta.male.plot3.sig    %>%
@@
                                nest(data = everything())    
-
 # Significant subset for lnRR
@@
                            nest()
-
 metacombo_male.plot3.RR.all <- meta.male.plot3.sig %>%
@@
                                nest(data = everything())   
-
 # **Final fixed effects meta-analyses within grouping terms, with SE of the estimate
-
 plot3.male.meta.CVR <- metacombo_male.plot3.CVR %>%
@@
                                               verbose = F)))
-
 plot3.male.meta.VR <- metacombo_male.plot3.VR %>%
@@
                                             verbose = F)))
-
 plot3.male.meta.RR <- metacombo_male.plot3.RR %>%
@@
                                               verbose = F)))
-
 # Across all grouping terms #
-
 plot3.male.meta.CVR.all <- metacombo_male.plot3.CVR.all %>%
@@
                                                   verbose = F)))
-
 plot3.male.meta.CVR.all <- plot3.male.meta.CVR.all %>% 
                             mutate(GroupingTerm = "All")
-
 plot3.male.meta.VR.all <- metacombo_male.plot3.VR.all %>%
@@
                                                   verbose = F)))
-
 plot3.male.meta.VR.all <- plot3.male.meta.VR.all %>% 
                           mutate(GroupingTerm = "All")
-
 plot3.male.meta.RR.all <- metacombo_male.plot3.RR.all %>%
@@
                                                 verbose = F)))
-
 plot3.male.meta.RR.all <- plot3.male.meta.RR.all %>% 
                           mutate(GroupingTerm = "All")
-
 # Combine with separate grouping term results
-
 plot3.male.meta.CVR <- bind_rows(plot3.male.meta.CVR, plot3.male.meta.CVR.all)
@@
  plot3.male.meta.RR <- bind_rows(plot3.male.meta.RR,   plot3.male.meta.RR.all)
-
 # **Re-structure data for each grouping term; delete un-used variables
-
 plot3.male.meta.CVR.b <- as.data.frame(plot3.male.meta.CVR %>% 
@@
                                                lnCVR_I2 = map_dbl(model_lnCVR, pluck("I2"))))[, c(1, 4:8)]
-
 add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA, NA))) %>% 
                                   setNames(names(plot3.male.meta.CVR.b))
-
 plot3.male.meta.CVR.b <- bind_rows(plot3.male.meta.CVR.b, add.row.hearing)
 plot3.male.meta.CVR.b <- plot3.male.meta.CVR.b[order(plot3.male.meta.CVR.b$GroupingTerm), ]
-
 plot3.male.meta.VR.b <- as.data.frame(plot3.male.meta.VR %>% 
@@
                                              lnVR_I2 = map_dbl(model_lnVR, pluck("I2"))))[, c(1, 4:8)]
-
 plot3.male.meta.VR.b <- plot3.male.meta.VR.b[order(plot3.male.meta.VR.b$GroupingTerm), ]
-
 plot3.male.meta.RR.b <- as.data.frame(plot3.male.meta.RR %>% 
@@
                                              lnRR_I2 = map_dbl(model_lnRR, pluck("I2"))))[, c(1, 4:8)]
-
 plot3.male.meta.RR.b <- plot3.male.meta.RR.b[order(plot3.male.meta.RR.b$GroupingTerm), ]
-
 overall.male.plot3 <- full_join(plot3.male.meta.CVR.b, plot3.male.meta.VR.b)
 overall.male.plot3 <- full_join(overall.male.plot3,    plot3.male.meta.RR.b)
-
 overall.male.plot3$GroupingTerm <- factor(overall.male.plot3$GroupingTerm, 
@@
                                           rev(levels(overall.male.plot3$GroupingTerm)))
-
 overall.male.plot3$GroupingTerm <- factor(overall.male.plot3$GroupingTerm, 
@@
                                           rev(levels(overall.male.plot3$GroupingTerm)))
-
 # Restructure MALE data for plotting 
-
 overall3.male.sig <- gather(overall.male.plot3, parameter, value, c(lnCVR, lnRR), factor_key = TRUE) 
-
 lnCVR.ci <- overall3.male.sig            %>%
@@
                    ci.high = lnCVR_upper)
-
 lnRR.ci <- overall3.male.sig           %>%
@@
                  ci.high = lnRR_upper)
-
 overall4.male.sig <- bind_rows(lnCVR.ci, lnRR.ci) %>% 
@@
                             ci.high) 
-
 overall4.male.sig$label <- "CI not overlapping zero"
-
 # Plot Fig 5B all significant results (CI not overlapping zero) for males. This is the right panel in Figure 5B.
-
 Metameta_Fig3_male.sig <- overall4.male.sig %>%
@@
         axis.title.y = element_blank())
-
 # Metameta_Fig3_male.sig
-
 #### Female part, significant traits: Female Fig5B sig
-
 # as above: Prepare data for traits with CI not overlapping 0
 # create column with 1 = different from zero, 0 = zero included in CI
-
 # Female-biased traits
-
 meta.female.plot3.sig <- metacombo %>%
@@
           sigRR = ifelse(lnRR_upper < 0, 1, 0))
-
 # Significant subset for lnCVR
-
 metacombo_female.plot3.CVR <- meta.female.plot3.sig  %>%
@@
                               nest()
-
 metacombo_female.plot3.CVR.all <- meta.female.plot3.sig %>%
@@
                                   nest(data = everything())   
-
 # Significant subset for lnVR
-
 metacombo_female.plot3.VR <- meta.female.plot3.sig  %>%
@@
                              nest()
-
 metacombo_female.plot3.VR.all <- meta.female.plot3.sig  %>%
@@
                                  nest(data = everything())   
-
 # Significant subset for lnRR
-
 metacombo_female.plot3.RR <- meta.female.plot3.sig  %>%
@@
                              nest()
-
 metacombo_female.plot3.RR.all <- meta.female.plot3.sig %>%
@@
                                  nest(data = everything())   
-
 # **Final fixed effects meta-analyses within grouping terms, with SE of the estimate
-
 plot3.female.meta.CVR <- metacombo_female.plot3.CVR %>%
@@
                                                   verbose = F)))
-
 plot3.female.meta.VR <- metacombo_female.plot3.VR %>%
@@
                                                 verbose = F)))
-
 plot3.female.meta.RR <- metacombo_female.plot3.RR %>%
@@
                                                 verbose = F)))
-
 # Across all grouping terms #
-
 plot3.female.meta.CVR.all <- metacombo_female.plot3.CVR.all %>%
@@
                                                        verbose = F)))
-
 plot3.female.meta.CVR.all <- plot3.female.meta.CVR.all %>% mutate(GroupingTerm = "All")
-
 plot3.female.meta.VR.all <- metacombo_female.plot3.VR.all %>%
@@
                           verbose = F)))
-
 plot3.female.meta.VR.all <- plot3.female.meta.VR.all %>% mutate(GroupingTerm = "All")
-
 plot3.female.meta.RR.all <- metacombo_female.plot3.RR.all %>%
@@
                                                     verbose = F)))
-
 plot3.female.meta.RR.all <- plot3.female.meta.RR.all %>% 
                             mutate(GroupingTerm = "All")
-
 # Combine with separate grouping term results
-
 plot3.female.meta.CVR <- bind_rows(plot3.female.meta.CVR, plot3.female.meta.CVR.all)
@@
  plot3.female.meta.RR <- bind_rows(plot3.female.meta.RR,   plot3.female.meta.RR.all)
-
 # Re-structure data for each grouping term; delete un-used variables
-
 plot3.female.meta.CVR.b <- as.data.frame(plot3.female.meta.CVR %>% 
@@
                                                   lnCVR_I2 = map_dbl(model_lnCVR, pluck("I2"))))[, c(1, 4:8)]
-
 add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA,NA))) %>% 
                                  setNames(names(plot3.female.meta.CVR.b))
-
 plot3.female.meta.CVR.b <- bind_rows(plot3.female.meta.CVR.b, add.row.hearing)
 plot3.female.meta.CVR.b <- plot3.female.meta.CVR.b[order(plot3.female.meta.CVR.b$GroupingTerm), ]
-
 plot3.female.meta.VR.b <- as.data.frame(plot3.female.meta.VR %>% 
@@
                                                   lnVR_I2 = map_dbl(model_lnVR, pluck("I2"))))[, c(1, 4:8)]
-
 plot3.female.meta.VR.b <- plot3.female.meta.VR.b[order(plot3.female.meta.VR.b$GroupingTerm), ]
-
 plot3.female.meta.RR.b <- as.data.frame(plot3.female.meta.RR %>% 
@@
                                                   lnRR_I2 = map_dbl(model_lnRR, pluck("I2"))))[, c(1, 4:8)]
-
 plot3.female.meta.RR.b <- plot3.female.meta.RR.b[order(plot3.female.meta.RR.b$GroupingTerm), ]
-
 overall.female.plot3 <- full_join(plot3.female.meta.CVR.b, plot3.female.meta.VR.b)
 overall.female.plot3 <- full_join(overall.female.plot3, plot3.female.meta.RR.b)
-
 overall.female.plot3$GroupingTerm <- factor(overall.female.plot3$GroupingTerm, 
@@
                                             rev(levels(overall.female.plot3$GroupingTerm)))
-
 # Re-structuring data for plotting
-
 overall3.female.sig <- gather(overall.female.plot3, parameter, value, c(lnCVR, lnRR), factor_key = TRUE) 
-
 lnCVR.ci <- overall3.female.sig %>%
@@
          ci.high = lnCVR_upper)
-
 # lnVR.ci <- overall3.female.sig  %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
-
 lnRR.ci <- overall3.female.sig %>%
@@
   mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
-
 overall4.female.sig <- bind_rows(lnCVR.ci, lnRR.ci) %>% 
                        select(GroupingTerm, parameter, value, ci.low, ci.high) # lnVR.ci,
-
 overall4.female.sig$label <- "CI not overlapping zero"
-
 # PLOT preparation for Fig5B: all significant results (CI not overlapping zero, female )
-
 Metameta_Fig3_female.sig  <- overall4.female.sig %>%
@@
   )
-
 # Metameta_Fig3_female.sig #(Figure 5B left panel)
 ```
-
-## Figure 5
-Sex biases in trait values across trait groups (Step J in Figure \@ref(fig:FigG1)).
-The panels in A show differences in the number of affected traits, in variance (lnCVR) and means (lnRR), where there is a significant difference between the sexes (i.e CI not overlapping zero).
-Panel B shows results for the sex bias in those traits that differ between the sexes (second-order meta-analysis).
-Triangles represent sex bias in means (response ratio) and black circles differences in the coefficient of variation ratio (mean-adjusted variability).
-The orange-red bars represent trait groups with a female bias, blue-green bars male-biased traits.
-
-```{r Fig5}
-#Joining the Parts:
-
-Fig5B <- ggarrange(Metameta_Fig3_female.sig, Metameta_Fig3_male.sig,
-  ncol = 2, nrow = 1, widths = c(1, 1.20), heights = c(1, 1))
-
-Fig5B <- annotate_figure(Fig5B,
-                bottom= text_grob("Effect Size", color = "black", face = "plain", size = 14))
-
-Fig5 <- ggarrange(malebias_Fig2_sigtraits, Fig5B, 
-                  ncol = 1, nrow = 2, widths = c(1, 1.10), 
-                  heights = c(1.10, 1),  labels = c("A", "B"))
-Fig5
-```
-
-# Supplemental Figures
-
-```{r FigS1_prep, echo = FALSE, eval = TRUE}
-### Preparing the data
-#The supplemental figures include lnVR (in addition to lnCVR and lnRR, as presented in Figures 4 and 5)
-
-# *Prepare data for all traits
-
-meta.plot2.all <- meta_clean %>%
-  select(lnCVR, lnVR, lnRR, GroupingTerm) %>%
-  arrange(GroupingTerm)
-
-meta.plot2.all.bS1 <- gather(meta.plot2.all, trait, value, c(lnCVR, lnVR, lnRR))
-
-meta.plot2.all.bS1$trait <- factor(meta.plot2.all.bS1$trait, levels = c("lnCVR", "lnVR", "lnRR"))
-
-meta.plot2.all.cS1 <- meta.plot2.all.bS1 %>%
-  group_by_at(vars(trait, GroupingTerm)) %>%
-  summarise(
-    malebias = sum(value > 0), femalebias = sum(value <= 0), total = malebias + femalebias,
-    malepercent = malebias * 100 / total, femalepercent = femalebias * 100 / total
-  )
-
-meta.plot2.all.cS1$label <- "All traits"
-
-# Re-structure to create stacked bar plots
-
-meta.plot2.all.dS1 <- as.data.frame(meta.plot2.all.cS1)
-meta.plot2.all.eS1 <- gather(meta.plot2.all.dS1, key = sex, value = percent, malepercent:femalepercent, factor_key = TRUE)
-
-# Create new sample size variable
-
-meta.plot2.all.eS1$samplesize <- with(meta.plot2.all.eS1, ifelse(sex == "malepercent", malebias, femalebias))
-
-# Add summary row ('All') and re-arrange rows into correct order for plotting (warnings about coercing 'id' into character vector are ok)
-
-meta.plot2.all.fS1 <- meta.plot2.all.eS1 %>% group_by(trait, sex) %>% 
-  summarise(GroupingTerm = "All", malebias = sum(malebias), femalebias = sum(femalebias), total = malebias + femalebias, 
-            label = "All traits", samplesize = sum(samplesize)) %>%
-  mutate(percent = ifelse(sex == "femalepercent", femalebias*100/(malebias+femalebias), malebias*100/(malebias+femalebias))) %>%
-  bind_rows(meta.plot2.all.eS1, .) %>%
-  mutate(rownumber = row_number()) %>%
-  .[c(55, 1:9, 57, 10:18, 59, 19:27, 56, 28:36, 58, 37:45, 60, 46:54), ]
-
-meta.plot2.all.fS1$GroupingTerm <- factor(meta.plot2.all.fS1$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
-meta.plot2.all.fS1$GroupingTerm <- factor(meta.plot2.all.fS1$GroupingTerm, rev(levels(meta.plot2.all.fS1$GroupingTerm)))
-
-malebias_FigS1_alltraits <-
-  ggplot(meta.plot2.all.fS1) +
-  aes(x = GroupingTerm, y = percent, fill = sex) +
-  ylab("Percentage") +
-  geom_col() +
-  geom_hline(yintercept = 50, linetype = "dashed", color = "gray40") +
-  geom_text(
-    data = subset(meta.plot2.all.fS1, samplesize != 0), aes(label = samplesize), position = position_stack(vjust = .5),
-    color = "white", size = 3.5
-  ) +
-  facet_grid(
-    cols = vars(trait), rows = vars(label), labeller = label_wrap_gen(width = 18),
-    scales = "free", space = "free"
-  ) +
-  scale_fill_brewer(palette = "Set2") +
-  theme_bw(base_size = 18) +
-  theme(
-    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
-    strip.text.x = element_text(size = 12),
-    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
-    text = element_text(size = 14),
-    panel.spacing = unit(0.5, "lines"),
-    panel.border = element_blank(),
-    axis.line = element_line(),
-    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
-    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
-    panel.grid.minor.y = element_blank(),
-    panel.grid.minor.x = element_blank(),
-    legend.position = "none",
-    #axis.title.x = element_blank(),
-    axis.title.y = element_blank()
-  ) +
-  coord_flip()
-
-# malebias_FigS1_alltraits     #(panel A in Figure S1)
-
-###  Overall results of second order meta analysis, INCLUDING VR
-#### Re-structure MALE data for plotting
-
-overall3.male.sigS <- gather(overall.male.plot3, parameter, value, c(lnCVR, lnVR, lnRR), factor_key = TRUE)
-
-lnCVR.ci <- overall3.male.sigS %>%
-  filter(parameter == "lnCVR") %>%
-  mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
-lnVR.ci <- overall3.male.sigS %>%
-  filter(parameter == "lnVR") %>%
-  mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
-lnRR.ci <- overall3.male.sigS %>%
-  filter(parameter == "lnRR") %>%
-  mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
-
-overall4.male.sigS <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
-
-overall4.male.sigS$label <- "CI not overlapping zero"
-
-# Data are re-structured, and grouping terms are being re-ordered
-
-overall3S <- gather(overall2, parameter, value, c(lnCVR, lnVR, lnRR), factor_key = TRUE)
-
-lnCVR.ci <- overall3S %>%
-  filter(parameter == "lnCVR") %>%
-  mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
-lnVR.ci <- overall3S %>%
-  filter(parameter == "lnVR") %>%
-  mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
-lnRR.ci <- overall3S %>%
-  filter(parameter == "lnRR") %>%
-  mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
-
-overall4S <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
-
-# Re-order grouping terms
-
-overall4S$GroupingTerm <- factor(overall4S$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
-overall4S$GroupingTerm <- factor(overall4S$GroupingTerm, rev(levels(overall4S$GroupingTerm)))
-overall4S$label <- "All traits"
-
-#### Preparation for plot, including lnVR
-# Sub-Plot  for Figure S1: all traits (S1 B)
-
-Metameta_FigS1_alltraits <- overall4S %>%
-
-  ggplot(aes(y = GroupingTerm, x = value)) +
-  geom_errorbarh(aes(
-    xmin = ci.low,
-    xmax = ci.high
-  ),
-  height = 0.1, show.legend = FALSE
-  ) +
-  geom_point(aes(shape = parameter),
-    fill = "black",
-    color = "black", size = 2.2,
-    show.legend = FALSE
-  ) +
-  scale_x_continuous(
-    limits = c(-0.24, 0.25),
-    breaks = c(-0.2, -0.1, 0, 0.1, 0.2),
-    name = "Effect size"
-  ) +
-  geom_vline(
-    xintercept = 0,
-    color = "black",
-    linetype = "dashed"
-  ) +
-  facet_grid(
-    cols = vars(parameter), rows = vars(label),
-    labeller = label_wrap_gen(width = 23),
-    scales = "free",
-    space = "free"
-  ) +
-  theme_bw() +
-  theme(
-    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
-    strip.text.x = element_text(size = 12),
-    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
-    text = element_text(size = 14),
-    panel.spacing = unit(0.5, "lines"),
-    panel.border = element_blank(),
-    axis.line = element_line(),
-    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
-    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
-    panel.grid.minor.y = element_blank(),
-    panel.grid.minor.x = element_blank(),
-    legend.title = element_blank(),
-    axis.title.x = element_text(hjust = 0.5, size = 14),
-    axis.title.y = element_blank()
-  )
-
-# Metameta_FigS1_alltraits
-```
-
-```{r, eval = TRUE, echo = FALSE}
-
-#This Figure extends Figure 4, as it includes results not only for lnCVR and lnRR but also lnCVR.
-In addition, we compare two different assessments of sex-bias, significance (CI not overlapping zero) and sex differences in male / female ratios > 10%
-# Plot FigS2 all significant results (CI not overlapping zero) for males, count data
-
-meta.plot2.sig.bS <- meta.plot2.sig[, c("lnCVR", "lnVR", "lnRR", "lnCVRsig", "lnVRsig", "lnRRsig", "GroupingTerm")]
-
-meta.plot2.sig.cS <- gather(meta.plot2.sig.bS, trait, value, lnCVR:lnRR)
-meta.plot2.sig.cS$sig <- "placeholder"
-
-meta.plot2.sig.cS$trait <- factor(meta.plot2.sig.cS$trait, levels = c("lnCVR", "lnVR", "lnRR"))
-
-meta.plot2.sig.cS$sig <- ifelse(meta.plot2.sig.cS$trait == "lnCVR", meta.plot2.sig.cS$lnCVRsig,
-  ifelse(meta.plot2.sig.cS$trait == "lnVR", meta.plot2.sig.cS$lnVRsig, meta.plot2.sig.cS$lnRRsig))
-
-# choosing sex biased ln-ratios significantly larger than 0
-meta.plotS2.sig.malebias <- meta.plot2.sig.cS %>%
-  group_by_at(vars(trait, GroupingTerm)) %>%
-  filter(sig == 1) %>%
-  summarise(male_sig = sum(value > 0), female_sig = sum(value < 0), total = male_sig + female_sig)
-
-meta.plotS2.sig.malebias <- ungroup(meta.plotS2.sig.malebias) %>%
-  add_row(trait = "lnCVR", GroupingTerm = "Hearing", male_sig = 0, female_sig = 0, .before = 4) %>% # add "Hearing" for lnCVR (not filtered as only zeros)
-  mutate(malepercent = male_sig * 100 / total, femalepercent = female_sig * 100 / total)
-
-meta.plotS2.sig.malebias$label <- "CI not overlapping zero"
-
-# restructure to create stacked bar plots
-
-meta.plotS2.sig.bothsexes <- as.data.frame(meta.plotS2.sig.malebias)
-meta.plotS2.sig.bothsexes.b <- gather(meta.plotS2.sig.bothsexes, key = sex, value = percent, malepercent:femalepercent, factor_key = TRUE)
-
-# create new sample size variable
-
-meta.plotS2.sig.bothsexes.b$samplesize <- with(meta.plotS2.sig.bothsexes.b, ifelse(sex == "malepercent", male_sig, female_sig))
-
-# Add summary row ('All') and re-arrange rows into correct order for plotting (warnings about coercing 'id' into character vector are ok)
-
-meta.plotS2.sig.bothsexes.c <- meta.plotS2.sig.bothsexes.b %>% group_by(trait, sex) %>% 
-  summarise(GroupingTerm = "All", male_sig = sum(male_sig), female_sig = sum(female_sig), total = male_sig + female_sig, 
-            label = "CI not overlapping zero", samplesize = sum(samplesize)) %>%
-  mutate(percent = ifelse(sex == "femalepercent", female_sig*100/(male_sig + female_sig), male_sig*100/(male_sig + female_sig))) %>%
-  bind_rows(meta.plotS2.sig.bothsexes.b, .) %>%
-  mutate(rownumber = row_number()) %>%
-  .[c(55, 1:9, 57, 10:18, 59, 19:27, 56, 28:36, 58, 37:45, 60, 46:54), ]
-
-meta.plotS2.sig.bothsexes.c$GroupingTerm <- factor(meta.plotS2.sig.bothsexes.c$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
-meta.plotS2.sig.bothsexes.c$GroupingTerm <- factor(meta.plotS2.sig.bothsexes.c$GroupingTerm, rev(levels(meta.plotS2.sig.bothsexes.c$GroupingTerm)))
-
-# *Plot Fig2 all significant results (CI not overlapping zero):
-#     no sig. lnCVR for 'Hearing' in either sex; no sig. male-biased lnCVR for 'Immunology' and 'Eye, and no sig. male-biased lnVR for 'Eye'
-
-malebias_FigS2_sigtraits <-
-  ggplot(meta.plotS2.sig.bothsexes.c) +
-  aes(x = GroupingTerm, y = percent, fill = sex) +
-  ylab("Percentage") +
-  geom_col() +
-  geom_hline(yintercept = 50, linetype = "dashed", color = "gray40") +
-  geom_text(
-    data = subset(meta.plotS2.sig.bothsexes.c, samplesize != 0), aes(label = samplesize), position = position_stack(vjust = .5),
-    color = "white", size = 3.5
-  ) +
-  facet_grid(
-    cols = vars(trait), rows = vars(label), labeller = label_wrap_gen(width = 18),
-    scales = "free", space = "free"
-  ) +
-  scale_fill_brewer(palette = "Set2") +
-  theme_bw(base_size = 18) +
-  theme(
-    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
-    strip.text.x = element_text(size = 12),
-    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
-    text = element_text(size = 14),
-    panel.spacing = unit(0.5, "lines"),
-    panel.border = element_blank(),
-    axis.line = element_line(),
-    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
-    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
-    panel.grid.minor.y = element_blank(),
-    panel.grid.minor.x = element_blank(),
-    legend.position = "none",
-    #axis.title.x = element_blank(),
-    axis.title.y = element_blank()
-  ) +
-  coord_flip()
-
-# malebias_FigS2_sigtraits # this is Figure S2 A
-
-#Prepare data for traits with effect size ratios > 10% larger in males, supplemental Figure S2
-
-#### Over 10% male bias, count data (first- order metanalysis)
-
-meta.plot2.over10 <- meta_clean %>%
-                    select(lnCVR, lnVR, lnRR, GroupingTerm) %>%
-                    arrange(GroupingTerm)
-
-meta.plot2.over10.b <- gather(meta.plot2.over10, trait, value, c(lnCVR, lnVR, lnRR))
-
-meta.plot2.over10.b$trait <- factor(meta.plot2.over10.b$trait, levels = c("lnCVR", "lnVR", "lnRR"))
-
-meta.plot2.over10.c <- meta.plot2.over10.b %>%
-                      group_by_at(vars(trait, GroupingTerm)) %>%
-                      summarise(malebias = sum(value > log(11 / 10)), 
-                                femalebias = sum(value < log(9 / 10)), 
-                                total = malebias + femalebias,
-                                malepercent = malebias * 100 / total, 
-                                femalepercent = femalebias * 100 / total)
-
-meta.plot2.over10.c$label <- "Sex difference in m/f ratios > 10%"
-
-# restructure to create stacked bar plots
-
-meta.plot2.over10.c <- as.data.frame(meta.plot2.over10.c)
-meta.plot2.over10.d <- gather(meta.plot2.over10.c, key = sex, value = percent, malepercent:femalepercent, factor_key = TRUE)
-
-# create new sample size variable
-
-meta.plot2.over10.d$samplesize <- with(meta.plot2.over10.d, ifelse(sex == "malepercent", malebias, femalebias))
-
-# Add summary row ('All') and re-arrange rows into correct order for plotting (warnings about coercing 'id' into character vector are ok)
-
-meta.plot2.over10.e <- meta.plot2.over10.d %>% 
-                      group_by(trait, sex) %>% 
-                      summarise(GroupingTerm = "All", malebias = sum(malebias), 
-                                femalebias = sum(femalebias), 
-                                total = malebias + femalebias, 
-                                label = "Sex difference in m/f ratios > 10%", 
-                                samplesize = sum(samplesize)) %>%
-                      mutate(percent = ifelse(sex == "femalepercent", 
-                                              femalebias*100/(malebias + femalebias), 
-                                              malebias*100/(malebias + femalebias))) %>%
-                      bind_rows(meta.plot2.over10.d, .) %>%
-                      mutate(rownumber = row_number()) %>%
-                      .[c(55, 1:9, 57, 10:18, 59, 19:27, 56, 28:36, 58, 37:45, 60, 46:54), ]
-
-meta.plot2.over10.e$GroupingTerm <- factor(meta.plot2.over10.e$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
-meta.plot2.over10.e$GroupingTerm <- factor(meta.plot2.over10.e$GroupingTerm, rev(levels(meta.plot2.over10.e$GroupingTerm)))
-
-# PLOT:  Fig2 Sex difference in m/f ratio > 10% (Fig S2 A, lower panel)
-
-malebias_Fig2_over10 <-
-  ggplot(meta.plot2.over10.e) +
-  aes(x = GroupingTerm, y = percent, fill = sex) +
-  ylab("Percentage") +
-  geom_col() +
-  geom_hline(yintercept = 50, linetype = "dashed", color = "gray40") +
-  geom_text(
-    data = subset(meta.plot2.over10.e, samplesize != 0), aes(label = samplesize), position = position_stack(vjust = .5),
-    color = "white", size = 3.5
-  ) +
-  facet_grid(
-    cols = vars(trait), rows = vars(label), labeller = label_wrap_gen(width = 18),
-    scales = "free", space = "free"
-  ) +
-  scale_fill_brewer(palette = "Set2") +
-  theme_bw(base_size = 18) +
-  theme(
-    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
-    strip.text.x = element_blank(),
-    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
-    text = element_text(size = 14),
-    panel.spacing = unit(0.5, "lines"),
-    panel.border = element_blank(),
-    axis.line = element_line(),
-    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
-    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
-    panel.grid.minor.y = element_blank(),
-    panel.grid.minor.x = element_blank(),
-    legend.position = "none",
-    #axis.title.x = element_blank(),
-    axis.title.y = element_blank()
-  ) +
-  coord_flip()
-
-# malebias_Fig2_over10  (supplemental Figure S2 A)
-```
-
-```{r FigS2_B, eval = TRUE, echo = FALSE}
-
-#### 3.2: Preparation for Figure S2 B (second-order meta-analysis)
-#### 3.3: Female Figure, significant and highly biased traits (Figure S2 B, left hand side panels)
-#Preparing data for traits with CI not overlapping 0: 
-#create column with 1= different from zero, 0= zero included in CI (for Figure S2 B, top left panel)
-
-#Restructure data for plotting
-
-overall3.female.sigS <- gather(overall.female.plot3, parameter, value, c(lnCVR, lnVR, lnRR), factor_key = TRUE)
-
-lnCVR.ci <- overall3.female.sigS %>%
-  filter(parameter == "lnCVR") %>%
-  mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
-lnVR.ci <- overall3.female.sigS %>%
-  filter(parameter == "lnVR") %>%
-  mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
-lnRR.ci <- overall3.female.sigS %>%
-  filter(parameter == "lnRR") %>%
-  mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
-
-overall4.female.sigS <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
-
-overall4.female.sigS$label <- "CI not overlapping zero"
-
-# PLOT female-bias:  significant traits
-
-Metameta_FigS2_female.sig <- overall4.female.sigS %>%
-  ggplot(aes(y = GroupingTerm, x = value)) +
-  geom_errorbarh(aes(
-    xmin = ci.low,
-    xmax = ci.high
-  ),
-  height = 0.1, show.legend = FALSE
-  ) +
-  geom_point(aes(shape = parameter),
-    fill = "salmon1", color = "salmon1", size = 2.2,
-    show.legend = FALSE
-  ) +
-  scale_x_continuous(
-    limits = c(-0.4, 0),
-    breaks = c(-0.3, 0),
-    name = "Effect size"
-  ) +
-  geom_vline(
-    xintercept = 0,
-    color = "black",
-    linetype = "dashed"
-  ) +
-  facet_grid(
-    cols = vars(parameter), # rows = vars(label),
-    # labeller = label_wrap_gen(width = 23),
-    scales = "free",
-    space = "free"
-  ) +
-  theme_bw() +
-  theme(
-    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
-    strip.text.x = element_text(size = 12),
-    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
-    text = element_text(size = 14),
-    panel.spacing = unit(0.5, "lines"),
-    panel.border = element_blank(),
-    axis.line = element_line(),
-    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
-    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
-    panel.grid.minor.y = element_blank(),
-    panel.grid.minor.x = element_blank(),
-    legend.title = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank()
-  )
-
-# Metameta_FigS2_female.sig
-
-#### Prepare data for traits with m/f difference > 10%, Female bias (Figure S2 B, bottom left)
-
-meta.plot3.perc <- metacombo %>%
-  mutate(
-    percCVR = ifelse(lnCVR < log(9 / 10), 1, 0),
-    percVR = ifelse(lnVR < log(9 / 10), 1, 0),
-    percRR = ifelse(lnRR < log(9 / 10), 1, 0)
-  )
-
-# Significant subset for lnCVR
-metacombo_plot3.CVR.perc <- meta.plot3.perc %>%
-  filter(percCVR == 1) %>%
-  group_by(GroupingTerm) %>%
-  nest()
-
-metacombo_plot3.CVR.perc.all <- meta.plot3.perc %>%
-  filter(percCVR == 1) %>%
-  nest(data = everything())
-
-# Significant subset for lnVR
-metacombo_plot3.VR.perc <- meta.plot3.perc %>%
-  filter(percVR == 1) %>%
-  group_by(GroupingTerm) %>%
-  nest()
-
-metacombo_plot3.VR.perc.all <- meta.plot3.perc %>%
-  filter(percVR == 1) %>%
-  nest(data = everything())
-
-# Significant subset for lnRR
-metacombo_plot3.RR.perc <- meta.plot3.perc %>%
-  filter(percRR == 1) %>%
-  group_by(GroupingTerm) %>%
-  nest()
-
-metacombo_plot3.RR.perc.all <- meta.plot3.perc %>%
-  filter(percRR == 1) %>%
-  nest(data = everything())
-
-# **Final fixed effects meta-analyses within grouping terms, with SE of the estimate
-
-plot3.meta.CVR.perc <- metacombo_plot3.CVR.perc %>%
-  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(
-    yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower) / (2 * 1.96),
-    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-  )))
-
-plot3.meta.VR.perc <- metacombo_plot3.VR.perc %>%
-  mutate(model_lnVR = map(data, ~ metafor::rma.uni(
-    yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
-    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-  )))
-
-plot3.meta.RR.perc <- metacombo_plot3.RR.perc %>%
-  mutate(model_lnRR = map(data, ~ metafor::rma.uni(
-    yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
-    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-  )))
-
-# Across all grouping terms #
-
-plot3.meta.CVR.perc.all <- metacombo_plot3.CVR.perc.all %>%
-  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(
-    yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower) / (2 * 1.96),
-    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-  )))
-
-plot3.meta.CVR.perc.all <- plot3.meta.CVR.perc.all %>% mutate(GroupingTerm = "All")
-
-plot3.meta.VR.perc.all <- metacombo_plot3.VR.perc.all %>%
-  mutate(model_lnVR = map(data, ~ metafor::rma.uni(
-    yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
-    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-  )))
-
-plot3.meta.VR.perc.all <- plot3.meta.VR.perc.all %>% mutate(GroupingTerm = "All")
-
-plot3.meta.RR.perc.all <- metacombo_plot3.RR.perc.all %>%
-  mutate(model_lnRR = map(data, ~ metafor::rma.uni(
-    yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
-    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-  )))
-
-plot3.meta.RR.perc.all <- plot3.meta.RR.perc.all %>% mutate(GroupingTerm = "All")
-
-# Combine with separate grouping term results
-
-plot3.meta.CVR.perc <- bind_rows(plot3.meta.CVR.perc, plot3.meta.CVR.perc.all)
-plot3.meta.VR.perc <- bind_rows(plot3.meta.VR.perc, plot3.meta.VR.perc.all)
-plot3.meta.RR.perc <- bind_rows(plot3.meta.RR.perc, plot3.meta.RR.perc.all)
-
-# **Re-structure data for each grouping term; delete un-used variables: "Hearing missing for all 3 parameters"
-
-plot3.meta.CVR.perc.b <- as.data.frame(plot3.meta.CVR.perc %>% group_by(GroupingTerm) %>%
-  mutate(
-    lnCVR = map_dbl(model_lnCVR, pluck(2)), lnCVR_lower = map_dbl(model_lnCVR, pluck(6)),
-    lnCVR_upper = map_dbl(model_lnCVR, pluck(7)), lnCVR_se = map_dbl(model_lnCVR, pluck(3))
-  ))[, c(1, 4:7)]
-add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.meta.CVR.perc.b))
-plot3.meta.CVR.perc.b <- rbind(plot3.meta.CVR.perc.b, add.row.hearing)
-plot3.meta.CVR.perc.b <- plot3.meta.CVR.perc.b[order(plot3.meta.CVR.perc.b$GroupingTerm), ]
-
-plot3.meta.VR.perc.b <- as.data.frame(plot3.meta.VR.perc %>% group_by(GroupingTerm) %>%
-  mutate(
-    lnVR = map_dbl(model_lnVR, pluck(2)), lnVR_lower = map_dbl(model_lnVR, pluck(6)),
-    lnVR_upper = map_dbl(model_lnVR, pluck(7)), lnVR_se = map_dbl(model_lnVR, pluck(3))
-  ))[, c(1, 4:7)]
-add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.meta.VR.perc.b))
-plot3.meta.VR.perc.b <- rbind(plot3.meta.VR.perc.b, add.row.hearing)
-plot3.meta.VR.perc.b <- plot3.meta.VR.perc.b[order(plot3.meta.VR.perc.b$GroupingTerm), ]
-
-plot3.meta.RR.perc.b <- as.data.frame(plot3.meta.RR.perc %>% group_by(GroupingTerm) %>%
-  mutate(
-    lnRR = map_dbl(model_lnRR, pluck(2)), lnRR_lower = map_dbl(model_lnRR, pluck(6)),
-    lnRR_upper = map_dbl(model_lnRR, pluck(7)), lnRR_se = map_dbl(model_lnRR, pluck(3))
-  ))[, c(1, 4:7)]
-add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.meta.RR.perc.b))
-plot3.meta.RR.perc.b <- rbind(plot3.meta.RR.perc.b, add.row.hearing)
-add.row.hematology <- as.data.frame(t(c("Hematology", NA, NA, NA, NA))) %>%
-  setNames(names(plot3.meta.RR.perc.b))
-plot3.meta.RR.perc.b <- rbind(plot3.meta.RR.perc.b, add.row.hematology)
-
-plot3.meta.RR.perc.b <- plot3.meta.RR.perc.b[order(plot3.meta.RR.perc.b$GroupingTerm), ]
-
-plot3.meta.CVR.perc.c <- full_join(plot3.meta.CVR.perc.b, plot3.meta.VR.perc.b)
-overall.plot3.perc <- full_join(plot3.meta.CVR.perc.c, plot3.meta.RR.perc.b)
-
-overall.plot3.perc$GroupingTerm <- factor(overall.plot3.perc$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
-overall.plot3.perc$GroupingTerm <- factor(overall.plot3.perc$GroupingTerm, rev(levels(overall.plot3.perc$GroupingTerm)))
-
-# Restructure data for plotting
-# Female bias, 10 percent difference
-
-overall3.perc <- gather(overall.plot3.perc, parameter, value, c(lnCVR, lnVR, lnRR), factor_key = TRUE)
-
-lnCVR.ci <- overall3.perc %>%
-  filter(parameter == "lnCVR") %>%
-  mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
-lnVR.ci <- overall3.perc  %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
-lnRR.ci <- overall3.perc %>%
-  filter(parameter == "lnRR") %>%
-  mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
-
-overall4.perc <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
-
-overall4.perc$label <- "Sex difference in m/f ratios > 10%"
-
-overall4.perc$value <- as.numeric(overall4.perc$value)
-overall4.perc$ci.low <- as.numeric(overall4.perc$ci.low)
-overall4.perc$ci.high <- as.numeric(overall4.perc$ci.high)
-
-# Plot FigS2 all >10% difference (female)
-# Figure S2B, bottom left
-
-Metameta_Fig3_female.perc <- overall4.perc %>%
-  ggplot(aes(y = GroupingTerm, x = value)) +
-  geom_errorbarh(aes(
-    xmin = ci.low,
-    xmax = ci.high
-  ),
-  height = 0.1, show.legend = FALSE
-  ) +
-  geom_point(aes(shape = parameter),
-    fill = "salmon1", color = "salmon1", size = 2.2,
-    show.legend = FALSE
-  ) +
-
-  # scale_shape_manual(values =
-
-  scale_x_continuous(
-    limits = c(-0.53, 0.2),
-    breaks = c(-0.3, 0),
-    name = "Effect size"
-  ) +
-  geom_vline(
-    xintercept = 0,
-    color = "black",
-    linetype = "dashed"
-  ) +
-  facet_grid(
-    cols = vars(parameter), # rows = vars(label),
-    # labeller = label_wrap_gen(width = 23),
-    scales = "free",
-    space = "free"
-  ) +
-  theme_bw() +
-  theme(
-    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
-    strip.text.x = element_blank(),
-    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
-    text = element_text(size = 14),
-    panel.spacing = unit(0.5, "lines"),
-    panel.border = element_blank(),
-    axis.line = element_line(),
-    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
-    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
-    panel.grid.minor.y = element_blank(),
-    panel.grid.minor.x = element_blank(),
-    legend.title = element_blank(),
-    axis.title.x = element_text(hjust = 0.5, size = 14),
-    axis.title.y = element_blank()
-  )
-
-# Metameta_Fig3_female.perc (Figure S2 bottom left panel)
-```
-
-```{r FigS2_B_right, eval = TRUE, echo = FALSE}
-#### 3.4: Male Figure, significant and highly biased traits (Figure S2 B, right hand side panels)
-#Restructuring data with significant male bias (for Figure S2 B, top right panel)
-
-overall3.male.sigS <- gather(overall.male.plot3, parameter, value, c(lnCVR, lnVR, lnRR), factor_key = TRUE)
-
-lnCVR.ci <- overall3.male.sigS %>%
-  filter(parameter == "lnCVR") %>%
-  mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
-lnVR.ci <- overall3.male.sigS %>%
-  filter(parameter == "lnVR") %>%
-  mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
-lnRR.ci <- overall3.male.sigS %>%
-  filter(parameter == "lnRR") %>%
-  mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
-
-overall4.male.sigS <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
-
-overall4.male.sigS$label <- "CI not overlapping zero"
-
-# Plot FigS2 all significant results (CI not overlapping zero, male )
-
-Metameta_FigS2_male.sig <- overall4.male.sigS %>%
-  ggplot(aes(y = GroupingTerm, x = value)) +
-  geom_errorbarh(aes(
-    xmin = ci.low,
-    xmax = ci.high
-  ),
-  height = 0.1, show.legend = FALSE
-  ) +
-  geom_point(aes(shape = parameter),
-    fill = "mediumaquamarine", color = "mediumaquamarine", size = 2.2,
-    show.legend = FALSE
-  ) +
-  scale_x_continuous(
-    limits = c(0, 0.4),
-    breaks = c(0, 0.3),
-    name = "Effect size"
-  ) +
-  geom_vline(
-    xintercept = 0,
-    color = "black",
-    linetype = "dashed"
-  ) +
-  facet_grid(
-    cols = vars(parameter), rows = vars(label),
-    labeller = label_wrap_gen(width = 23),
-    scales = "free",
-    space = "free"
-  ) +
-  theme_bw() +
-  theme(
-    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
-    strip.text.x = element_text(size = 12),
-    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
-    text = element_text(size = 14),
-    panel.spacing = unit(0.5, "lines"),
-    panel.border = element_blank(),
-    axis.line = element_line(),
-    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
-    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
-    panel.grid.minor.y = element_blank(),
-    panel.grid.minor.x = element_blank(),
-    legend.title = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank()
-  )
-
-# Metameta_FigS2_male.sig
-
-## Prepare data for traits with m/f difference > 10%. Male bias
-### Create column with 1= larger, 0= difference not larger than 10% between male/female ratios
-
-meta.male.plot3.perc <- metacombo %>%
-  mutate(
-    percCVR = ifelse(lnCVR > log(11 / 10), 1, 0),
-     percVR = ifelse( lnVR > log(11 / 10), 1, 0),
-     percRR = ifelse( lnRR > log(11 / 10), 1, 0)
-  )
-
-# Significant subset for lnCVR
-metacombo_male.plot3.CVR.perc <- meta.male.plot3.perc %>%
-                                filter(percCVR == 1) %>%
-                                group_by(GroupingTerm) %>%
-                                nest()
-
-metacombo_male.plot3.CVR.perc.all <- meta.male.plot3.perc %>%
-                filter(percCVR == 1) %>%
-  nest(data = everything())
-
-# Significant subset for lnVR
-metacombo_male.plot3.VR.perc <- meta.male.plot3.perc %>%
-  filter(percVR == 1) %>%
-  group_by(GroupingTerm) %>%
-  nest()
-
-metacombo_male.plot3.VR.perc.all <- meta.male.plot3.perc %>%
-  filter(percVR == 1) %>%
-  nest(data = everything())
-
-# Significant subset for lnRR
-metacombo_male.plot3.RR.perc <- meta.male.plot3.perc %>%
-  filter(percRR == 1) %>%
-  group_by(GroupingTerm) %>%
-  nest()
-
-metacombo_male.plot3.RR.perc.all <- meta.male.plot3.perc %>%
-  filter(percRR == 1) %>%
-  nest(data = everything())
-
-# Final fixed effects meta-analyses within grouping terms and across grouping terms, with SE of the estimate
-
-plot3.male.meta.CVR.perc <- metacombo_male.plot3.CVR.perc %>%
-  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(
-    yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower) / (2 * 1.96),
-    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-  )))
-
-plot3.male.meta.VR.perc <- metacombo_male.plot3.VR.perc %>%
-  mutate(model_lnVR = map(data, ~ metafor::rma.uni(
-    yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
-    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-  )))
-
-plot3.male.meta.RR.perc <- metacombo_male.plot3.RR.perc %>%
-  mutate(model_lnRR = map(data, ~ metafor::rma.uni(
-    yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
-    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-  )))
-
-# Across all grouping terms
-
-plot3.male.meta.CVR.perc.all <- metacombo_male.plot3.CVR.perc.all %>%
-  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(
-    yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower) / (2 * 1.96),
-    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-  )))
-
-plot3.male.meta.CVR.perc.all <- plot3.male.meta.CVR.perc.all %>% mutate(GroupingTerm = "All")
-
-plot3.male.meta.VR.perc.all <- metacombo_male.plot3.VR.perc.all %>%
-  mutate(model_lnVR = map(data, ~ metafor::rma.uni(
-    yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
-    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-  )))
-
-plot3.male.meta.VR.perc.all <- plot3.male.meta.VR.perc.all %>% mutate(GroupingTerm = "All")
-
-plot3.male.meta.RR.perc.all <- metacombo_male.plot3.RR.perc.all %>%
-  mutate(model_lnRR = map(data, ~ metafor::rma.uni(
-    yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
-    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-  )))
-
-plot3.male.meta.RR.perc.all <- plot3.male.meta.RR.perc.all %>% mutate(GroupingTerm = "All")
-
-# Combine with separate grouping term results
-
-plot3.male.meta.CVR.perc <- bind_rows(plot3.male.meta.CVR.perc, plot3.male.meta.CVR.perc.all)
-plot3.male.meta.VR.perc <- bind_rows(plot3.male.meta.VR.perc, plot3.male.meta.VR.perc.all)
-plot3.male.meta.RR.perc <- bind_rows(plot3.male.meta.RR.perc, plot3.male.meta.RR.perc.all)
-
-# **Re-structure data for each grouping term; delete un-used variables: "Hearing missing for all 3 parameters"
-
-plot3.male.meta.CVR.perc.b <- as.data.frame(plot3.male.meta.CVR.perc %>% group_by(GroupingTerm) %>%
-  mutate(
-    lnCVR = map_dbl(model_lnCVR, pluck(2)), lnCVR_lower = map_dbl(model_lnCVR, pluck(6)),
-    lnCVR_upper = map_dbl(model_lnCVR, pluck(7)), lnCVR_se = map_dbl(model_lnCVR, pluck(3))
-  ))[, c(1, 4:7)]
-add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.male.meta.CVR.perc.b))
-plot3.male.meta.CVR.perc.b <- rbind(plot3.male.meta.CVR.perc.b, add.row.hearing)
-plot3.male.meta.CVR.perc.b <- plot3.male.meta.CVR.perc.b[order(plot3.male.meta.CVR.perc.b$GroupingTerm), ]
-
-plot3.male.meta.VR.perc.b <- as.data.frame(plot3.male.meta.VR.perc %>% group_by(GroupingTerm) %>%
-  mutate(
-    lnVR = map_dbl(model_lnVR, pluck(2)), lnVR_lower = map_dbl(model_lnVR, pluck(6)),
-    lnVR_upper = map_dbl(model_lnVR, pluck(7)), lnVR_se = map_dbl(model_lnVR, pluck(3))
-  ))[, c(1, 4:7)]
-add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.male.meta.VR.perc.b))
-plot3.male.meta.VR.perc.b <- rbind(plot3.male.meta.VR.perc.b, add.row.hearing)
-plot3.male.meta.VR.perc.b <- plot3.male.meta.VR.perc.b[order(plot3.male.meta.VR.perc.b$GroupingTerm), ]
-
-plot3.male.meta.RR.perc.b <- as.data.frame(plot3.male.meta.RR.perc %>% group_by(GroupingTerm) %>%
-  mutate(
-    lnRR = map_dbl(model_lnRR, pluck(2)), lnRR_lower = map_dbl(model_lnRR, pluck(6)),
-    lnRR_upper = map_dbl(model_lnRR, pluck(7)), lnRR_se = map_dbl(model_lnRR, pluck(3))
-  ))[, c(1, 4:7)]
-add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>%
-  setNames(names(plot3.male.meta.RR.perc.b))
-plot3.male.meta.RR.perc.b <- rbind(plot3.male.meta.RR.perc.b, add.row.hearing)
-
-add.row.eye <- as.data.frame(t(c("Eye", NA, NA, NA, NA))) %>%
-  setNames(names(plot3.male.meta.RR.perc.b))
-plot3.male.meta.RR.perc.b <- rbind(plot3.male.meta.RR.perc.b, add.row.eye)
-
-plot3.male.meta.RR.perc.b <- plot3.male.meta.RR.perc.b[order(plot3.male.meta.RR.perc.b$GroupingTerm), ]
-
-plot3.male.meta.CVR.Vr.perc <- full_join(plot3.male.meta.CVR.perc.b, plot3.male.meta.VR.perc.b)
-overall.male.plot3.perc <- full_join(plot3.male.meta.CVR.Vr.perc, plot3.male.meta.RR.perc.b)
-
-overall.male.plot3.perc$GroupingTerm <- factor(overall.male.plot3.perc$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
-overall.male.plot3.perc$GroupingTerm <- factor(overall.male.plot3.perc$GroupingTerm, rev(levels(overall.male.plot3.perc$GroupingTerm)))
-
-# Restructure data for plotting : Male biased, 10% difference
-
-overall3.perc <- gather(overall.male.plot3.perc, parameter, value, c(lnCVR, lnVR, lnRR), factor_key = TRUE)
-
-lnCVR.ci <- overall3.perc %>%
-  filter(parameter == "lnCVR") %>%
-  mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
-lnVR.ci <- overall3.perc  %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
-lnRR.ci <- overall3.perc %>%
-  filter(parameter == "lnRR") %>%
-  mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
-
-overall4.male.perc <- bind_rows(lnCVR.ci,lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
-
-overall4.male.perc$label <- "Sex difference in m/f ratios > 10%"
-
-overall4.male.perc$value <- as.numeric(overall4.male.perc$value)
-overall4.male.perc$ci.low <- as.numeric(overall4.male.perc$ci.low)
-overall4.male.perc$ci.high <- as.numeric(overall4.male.perc$ci.high)
-
-# Plot Fig S2 all >10% difference (male bias)
-# S2 B, bottom right
-
-Metameta_Fig3_male.perc <- overall4.male.perc %>% # filter(., GroupingTerm != "Hearing") %>%
-  ggplot(aes(y = GroupingTerm, x = value)) +
-  geom_errorbarh(aes(
-    xmin = ci.low,
-    xmax = ci.high
-  ),
-  height = 0.1, show.legend = FALSE
-  ) +
-  geom_point(aes(
-    shape = parameter,
-    fill = parameter
-  ),
-  color = "mediumaquamarine", size = 2.2,
-  show.legend = FALSE
-  ) +
-  scale_x_continuous(
-    limits = c(-0.2, 0.62),
-    breaks = c(0, 0.3),
-    name = "Effect size"
-  ) +
-  geom_vline(
-    xintercept = 0,
-    color = "black",
-    linetype = "dashed"
-  ) +
-  facet_grid(
-    cols = vars(parameter), rows = vars(label),
-    labeller = label_wrap_gen(width = 23),
-    scales = "free",
-    space = "free"
-  ) +
-  theme_bw() +
-  theme(
-    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
-    strip.text.x = element_blank(),
-    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
-    text = element_text(size = 14),
-    panel.spacing = unit(0.5, "lines"),
-    panel.border = element_blank(),
-    axis.line = element_line(),
-    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
-    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
-    panel.grid.minor.y = element_blank(),
-    panel.grid.minor.x = element_blank(),
-    legend.title = element_blank(),
-    axis.title.x = element_text(hjust = 0.5, size = 14),
-    axis.title.y = element_blank()
-  )
-
-# Metameta_Fig3_male.perc (Figure S2 right panel)
-```
-
-## Figure 5.1
-Figure \@ref(fig:FigS1) is similar to Figure 4 in the main article.
-
-```{r FigS1, fig.height = 8, fig.width = 7, fig.cap=" Numbers of either male (blue-green bars) or female (orange-red bars) biased traits  (Panel A) across functional groups, this time for lnCVR (left hand side), lnVR (middle) and lnRR (right hand side).
-Panel B shows effect sizes from separate meta-analysis for each functional group, and Panel C contains results of heterogeneity analyses.
-All three panels represent results evaluated across all traits."}
-
-#### Combined Figure S1: overall Count data, Meta anlysis results, Heterogeneity
-
-FigS1 <- ggarrange(malebias_FigS1_alltraits, Metameta_FigS1_alltraits, HeteroS1, nrow = 3, align = "v", heights = c(1.1, 1, 1), labels = c("A", "B", "C"))
-FigS1
-#ggsave("FigS1_OverallResults.pdf", plot = FigS1, width = 6, height = 7)
-```
-
-## Figure 5.2
-
-Figure \@ref(fig:FigS2) is an extension of sex biases, as shown in Figure 5 in the main text. Here, we include data on lnVR (middle panel), as well as athe second method of sex-differences comparison.
-
-```{r FigS2, fig.height = 10, fig.width = 8, fig.cap=" A) Differences in numbers of affected traits, in variance (lnCVR and lnVR) and means (lnRR), where there’s a significant difference between the sexes (i.e CI not overlapping zero), and where the sex bias is greater than 10% difference (regardless of significance).
-Panel B depicts results for the sex bias in those traits that differ between the sexes (second-order meta-analysis).
-Triangles represent sex bias in means (response ratio) and black circles differences in the coefficient of variation ratio (mean-adjusted variability).
-The orange-red bars represent trait groups with a female bias, blue-green bars male-biased traits."}
-library(ggpubr)
-FigS2b <- ggarrange(Metameta_FigS2_female.sig, Metameta_FigS2_male.sig,
-  ncol = 2, nrow = 1, widths = c(1, 1.30), heights = c(1.2, 1.2))
-
-FigS2d <- ggarrange(Metameta_Fig3_female.perc, Metameta_Fig3_male.perc,
-  ncol = 2, nrow = 1, widths = c(1, 1.20), heights = c(1.1, 1.1))
-
-# end combination Figure 5
-FigS2 <- ggarrange(malebias_FigS2_sigtraits, malebias_Fig2_over10, FigS2b, FigS2d, ncol = 1, nrow = 4, heights = c(2.5, 2.2, 2.1, 2), labels = c("A", " ", "B", " "))
-FigS2
-```
-
-# Supplemental Tables
-## Table 6.1
 
@@
 
-         kable(ST1, caption = "Summary of the available numbers of male and female mice from each strain and originating institution.") %>%
-    kable_styling() %>%
-    scroll_box(width = "100%", height = "200px")
-
-```
-
-## Table 6.2
+   pander(ST1, caption = "Table 6.1: Summary of the available numbers of male and female mice from each strain and originating institution.")
+
+    #kable(ST1, caption = "Summary of the available numbers of male and female mice from each strain and originating institution.") %>%
+    #kable_styling() %>%
+    #pander()
+    #scroll_box(width = "100%", height = "200px")
+
+```
+
+## Table
 
@@
 # Table detailing numbers of correlated and uncorrelated traits
-kable(cbind(meta1 %>% count(parameter_group)), caption = "Trait categories (parameter_group) and the number of correlated traits within these categories. Traits were meta-analysed using robumeta") %>%
-  kable_styling() %>%
-  scroll_box(width = "100%", height = "200px")
-```
-
-## Table 6.3
+
+pander(cbind(meta1 %>% count(parameter_group)), caption = "Table 6.2: Trait categories (parameter_group) and the number of correlated traits within these categories.
+Traits were meta-analysed using robumeta")
+
+#kable(cbind(meta1 %>% count(parameter_group)), caption = "Trait categories (parameter_group) and the number of correlated traits within these categories.
+Traits were meta-analysed using robumeta") %>%
+  #kable_styling() %>%
+  #scroll_box(width = "100%", height = "200px")
+```
+
+## Table
 
 ```{r Table3}
-    kable(metacombo, digits = 3, caption = "We use this corrected (for correlated traits) results table, which contains each of the meta-analytic means for all effect sizes of interest, for further analyses.
+
+pander(metacombo, caption = "Table 6.3: We use this corrected (for correlated traits) results table, which contains each of the meta-analytic means for all effect sizes of interest, for further analyses.
+We further use this table as part of the Shiny App, which is able to provide the percentage differences between males and females for mean, variance and coefficient of variance.")
+
+#kable(metacombo, digits = 3, caption = "We use this corrected (for correlated traits) results table, which contains each of the meta-analytic means for all effect sizes of interest, for further analyses.
 We further use this table as part of the Shiny App, which is able to provide the percentage differences between males and females for mean, variance and coefficient of variance.") %>%
-    kable_styling() %>%
-    scroll_box(width = "100%", height = "200px")
-
-```
-
-## Table 6.4
+  #kable_styling() %>%
+  #scroll_box(width = "100%", height = "200px")
+
+```
+
+## Table
 
 ```{r Table4}
-  kable(overall2, digits = 3, caption = "Summary of overall meta-analyses on the functional trait group level (GroupingTerm).
+
+pander(overall2, caption = "Table 6.4: Summary of overall meta-analyses on the functional trait group level (GroupingTerm).
+Results for lnCVR, lnVR and lnRR and their respective upper and lower 95 percent CI's, standard error and I2 values are provided.")
+
+#kable(overall2, digits = 3, caption = "Summary of overall meta-analyses on the functional trait group level (GroupingTerm).
 Results for lnCVR, lnVR and lnRR and their respective upper and lower 95 percent CI's, standard error and I2 values are provided.") %>%
-   kable_styling() %>%
-  scroll_box(width = "100%", height = "200px")
-```
-
-## Table 6.5
+ #  kable_styling() %>%
+#  scroll_box(width = "100%", height = "200px")
+```
+
+## Table
 
@@
 
-  kable(mf_sig, digits = 3, caption = "Provides an overview of meta-analysis results performed on traits that were significantly biased towards either sex.
+    pander(mf_sig, caption = "Table 6.5: Provides an overview of meta-analysis results performed on traits that were significantly biased towards either sex.
+This table summarizes findings for both sexes and the respective functional trait groups.")
+
+  #kable(mf_sig, digits = 3, caption = "Provides an overview of meta-analysis results performed on traits that were significantly biased towards either sex.
 This table summarizes findings for both sexes and the respective functional trait groups.") %>%
-    kable_styling() %>%
-    scroll_box(width = "100%", height = "300px")
-```
-
-## Table 6.6
+   # kable_styling() %>%
+  # scroll_box(width = "100%", height = "300px")
+```
+
+## Table
 
@@
 
-  kable(het, digits = 3, caption = "Summarizes our findings on heterogeneity due to institutions and mouse strains.
+  pander(het, caption = "Table 6.6: Summarizes our findings on heterogeneity due to institutions and mouse strains.
+These results are based on meta-analyses on sigma^2 and errors for mouse strains and centers (Institutions), following the identical workflow from above.")
+
+  #kable(het, digits = 3, caption = "Summarizes our findings on heterogeneity due to institutions and mouse strains.
 These results are based on meta-analyses on sigma^2 and errors for mouse strains and centers (Institutions), following the identical workflow from above.") %>%
-    kable_styling() %>%
-    scroll_box(width = "100%", height = "200px")
+   # kable_styling() %>%
+    #scroll_box(width = "100%", height = "200px")
 
@@
 ```{r}
-sessionInfo()
-```
+sessionInfo() %>% pander()
+```

### 2020-05-19 scripts/MouseSexDiffApril20_2020.Rmd
Small corrections:

@@
 
-```{r FigG1, fig.width = 4, fig.height = 8, fig.cap="Workflow of data process and meta-analysis"}
+```{r FigG1, echo = FALSE, fig.width = 4, fig.height = 8, fig.cap="Workflow of data process and meta-analysis"}
 
@@
 ## Figure
-Figure \@ref(fig:FigS1) is similar to Figure 3 in the main article.
+Figure \@ref(fig:FigS1) is similar to Figure 3 in the main article except that lnVR has been added to the plot for comparison with lnCVR and lnRR.
 
@@
 
-### Sex-bias in traits: Methods and results
+### Sex-bias in traits sub-analysis
 

### 2020-05-19 scripts/MouseSexDiffApril20_2020.Rmd
Fixes

@@
 male <- ggplot(results, aes(x = lnMean_m, y = logSD_m)) +
-    geom_point(color = "blue", size = 2) +
+    geom_point(color = "turquoise", size = 2) +
    geom_smooth(method = "lm", se = FALSE, color="black") + 
@@
 female <- ggplot(results, aes(x = lnMean_f, y = lnSD_f)) +
-    geom_point(color = "pink", size = 2) +
+    geom_point(color = "orange", size = 2) +
   geom_smooth(method = "lm", se = FALSE, color="black")+

### 2020-05-19 scripts/MouseSexDiffApril20_2020.Rmd
Updated colour scheme for mean-var

--- 2020-05-19 scripts/MouseSexDiffApril20_2020.Rmd
@@
 male <- ggplot(results, aes(x = lnMean_m, y = logSD_m)) +
-    geom_point(color = "blue", size = 2) +
+    geom_point(color = "#66C2A5", size = 2) +
    geom_smooth(method = "lm", se = FALSE, color="black") + 
@@
 female <- ggplot(results, aes(x = lnMean_f, y = lnSD_f)) +
-    geom_point(color = "pink", size = 2) +
+    geom_point(color = "#FC8D62", size = 2) +
   geom_smooth(method = "lm", se = FALSE, color="black")+

### 2020-05-19 scripts/MouseSexDiffApril20_2020.Rmd
Small fixes for renderinga nd trying abunch of stuff tos ee ifw e can sort PDF, no luck

@@
 output:
+  bookdown::pdf_document2:
+    toc: yes
+    toc_depth: 6
+    number_sections: true
+    theme: flatly
+  word_document:
+    toc: yes
+    toc_depth: '4'
+  html_notebook:
+    toc: yes
   bookdown::html_document2:
@@
     toc_float: yes
-  word_document:
-    toc: yes
-    toc_depth: '4'
-  html_notebook:
-    toc: yes
-  pdf_document:
-    toc: yes
-    toc_depth: '4'
   html_document:
@@
   cache = TRUE,
-  tidy = TRUE
+  tidy = TRUE,
+  tidy.opts=list(width.cutoff=80)
 )
@@
 This includes all separate eligible traits.
-Re-ordering of grouping terms. 
-Preparation of subplot 4A
+Re-ordering of grouping terms. Preparation of subplot 3A
 
@@
 # Supplemental Figures
-
-```{r FigS1_prep, echo = FALSE, eval = TRUE}
-### Preparing the data
-#The supplemental figures include lnVR (in addition to lnCVR and lnRR, as presented in Figures 4 and 5)
-
-# *Prepare data for all traits
-
-meta.plot2.all <- meta_clean %>%
-  select(lnCVR, lnVR, lnRR, GroupingTerm) %>%
-  arrange(GroupingTerm)
-
-meta.plot2.all.bS1 <- gather(meta.plot2.all, trait, value, c(lnCVR, lnVR, lnRR))
-
-meta.plot2.all.bS1$trait <- factor(meta.plot2.all.bS1$trait, levels = c("lnCVR", "lnVR", "lnRR"))
-
-meta.plot2.all.cS1 <- meta.plot2.all.bS1 %>%
-  group_by_at(vars(trait, GroupingTerm)) %>%
-  summarise(
-    malebias = sum(value > 0), femalebias = sum(value <= 0), total = malebias + femalebias,
-    malepercent = malebias * 100 / total, femalepercent = femalebias * 100 / total
-  )
-
-meta.plot2.all.cS1$label <- "All traits"
-
-# Re-structure to create stacked bar plots
-
-meta.plot2.all.dS1 <- as.data.frame(meta.plot2.all.cS1)
-meta.plot2.all.eS1 <- gather(meta.plot2.all.dS1, key = sex, value = percent, malepercent:femalepercent, factor_key = TRUE)
-
-# Create new sample size variable
-
-meta.plot2.all.eS1$samplesize <- with(meta.plot2.all.eS1, ifelse(sex == "malepercent", malebias, femalebias))
-
-# Add summary row ('All') and re-arrange rows into correct order for plotting (warnings about coercing 'id' into character vector are ok)
-
-meta.plot2.all.fS1 <- meta.plot2.all.eS1 %>% group_by(trait, sex) %>% 
-  summarise(GroupingTerm = "All", malebias = sum(malebias), femalebias = sum(femalebias), total = malebias + femalebias, 
-            label = "All traits", samplesize = sum(samplesize)) %>%
-  mutate(percent = ifelse(sex == "femalepercent", femalebias*100/(malebias+femalebias), malebias*100/(malebias+femalebias))) %>%
-  bind_rows(meta.plot2.all.eS1, .) %>%
-  mutate(rownumber = row_number()) %>%
-  .[c(55, 1:9, 57, 10:18, 59, 19:27, 56, 28:36, 58, 37:45, 60, 46:54), ]
-
-meta.plot2.all.fS1$GroupingTerm <- factor(meta.plot2.all.fS1$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
-meta.plot2.all.fS1$GroupingTerm <- factor(meta.plot2.all.fS1$GroupingTerm, rev(levels(meta.plot2.all.fS1$GroupingTerm)))
-
-malebias_FigS1_alltraits <-
-  ggplot(meta.plot2.all.fS1) +
-  aes(x = GroupingTerm, y = percent, fill = sex) +
-  ylab("Percentage") +
-  geom_col() +
-  geom_hline(yintercept = 50, linetype = "dashed", color = "gray40") +
-  geom_text(
-    data = subset(meta.plot2.all.fS1, samplesize != 0), aes(label = samplesize), position = position_stack(vjust = .5),
-    color = "white", size = 3.5
-  ) +
-  facet_grid(
-    cols = vars(trait), rows = vars(label), labeller = label_wrap_gen(width = 18),
-    scales = "free", space = "free"
-  ) +
-  scale_fill_brewer(palette = "Set2") +
-  theme_bw(base_size = 18) +
-  theme(
-    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
-    strip.text.x = element_text(size = 12),
-    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
-    text = element_text(size = 14),
-    panel.spacing = unit(0.5, "lines"),
-    panel.border = element_blank(),
-    axis.line = element_line(),
-    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
-    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
-    panel.grid.minor.y = element_blank(),
-    panel.grid.minor.x = element_blank(),
-    legend.position = "none",
-    #axis.title.x = element_blank(),
-    axis.title.y = element_blank()
-  ) +
-  coord_flip()
-
-# malebias_FigS1_alltraits     #(panel A in Figure S1)
-
-###  Overall results of second order meta analysis, INCLUDING VR
-#### Re-structure MALE data for plotting
-
-overall3.male.sigS <- gather(overall.male.plot3, parameter, value, c(lnCVR, lnVR, lnRR), factor_key = TRUE)
-
-lnCVR.ci <- overall3.male.sigS %>%
-  filter(parameter == "lnCVR") %>%
-  mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
-lnVR.ci <- overall3.male.sigS %>%
-  filter(parameter == "lnVR") %>%
-  mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
-lnRR.ci <- overall3.male.sigS %>%
-  filter(parameter == "lnRR") %>%
-  mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
-
-overall4.male.sigS <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
-
-overall4.male.sigS$label <- "CI not overlapping zero"
-
-# Data are re-structured, and grouping terms are being re-ordered
-
-overall3S <- gather(overall2, parameter, value, c(lnCVR, lnVR, lnRR), factor_key = TRUE)
-
-lnCVR.ci <- overall3S %>%
-  filter(parameter == "lnCVR") %>%
-  mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
-lnVR.ci <- overall3S %>%
-  filter(parameter == "lnVR") %>%
-  mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
-lnRR.ci <- overall3S %>%
-  filter(parameter == "lnRR") %>%
-  mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
-
-overall4S <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
-
-# Re-order grouping terms
-
-overall4S$GroupingTerm <- factor(overall4S$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
-overall4S$GroupingTerm <- factor(overall4S$GroupingTerm, rev(levels(overall4S$GroupingTerm)))
-overall4S$label <- "All traits"
-
-#### Preparation for plot, including lnVR
-# Sub-Plot  for Figure S1: all traits (S1 B)
-
-Metameta_FigS1_alltraits <- overall4S %>%
-
-  ggplot(aes(y = GroupingTerm, x = value)) +
-  geom_errorbarh(aes(
-    xmin = ci.low,
-    xmax = ci.high
-  ),
-  height = 0.1, show.legend = FALSE
-  ) +
-  geom_point(aes(shape = parameter),
-    fill = "black",
-    color = "black", size = 2.2,
-    show.legend = FALSE
-  ) +
-  scale_x_continuous(
-    limits = c(-0.24, 0.25),
-    breaks = c(-0.2, -0.1, 0, 0.1, 0.2),
-    name = "Effect size"
-  ) +
-  geom_vline(
-    xintercept = 0,
-    color = "black",
-    linetype = "dashed"
-  ) +
-  facet_grid(
-    cols = vars(parameter), rows = vars(label),
-    labeller = label_wrap_gen(width = 23),
-    scales = "free",
-    space = "free"
-  ) +
-  theme_bw() +
-  theme(
-    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
-    strip.text.x = element_text(size = 12),
-    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
-    text = element_text(size = 14),
-    panel.spacing = unit(0.5, "lines"),
-    panel.border = element_blank(),
-    axis.line = element_line(),
-    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
-    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
-    panel.grid.minor.y = element_blank(),
-    panel.grid.minor.x = element_blank(),
-    legend.title = element_blank(),
-    axis.title.x = element_text(hjust = 0.5, size = 14),
-    axis.title.y = element_blank()
-  )
-
-# Metameta_FigS1_alltraits
-```
-
-```{r, eval = TRUE, echo = FALSE}
-
-#This Figure extends Figure 4, as it includes results not only for lnCVR and lnRR but also lnCVR.
-In addition, we compare two different assessments of sex-bias, significance (CI not overlapping zero) and sex differences in male / female ratios > 10%
-# Plot FigS2 all significant results (CI not overlapping zero) for males, count data
-
-meta.plot2.sig.bS <- meta.plot2.sig[, c("lnCVR", "lnVR", "lnRR", "lnCVRsig", "lnVRsig", "lnRRsig", "GroupingTerm")]
-
-meta.plot2.sig.cS <- gather(meta.plot2.sig.bS, trait, value, lnCVR:lnRR)
-meta.plot2.sig.cS$sig <- "placeholder"
-
-meta.plot2.sig.cS$trait <- factor(meta.plot2.sig.cS$trait, levels = c("lnCVR", "lnVR", "lnRR"))
-
-meta.plot2.sig.cS$sig <- ifelse(meta.plot2.sig.cS$trait == "lnCVR", meta.plot2.sig.cS$lnCVRsig,
-  ifelse(meta.plot2.sig.cS$trait == "lnVR", meta.plot2.sig.cS$lnVRsig, meta.plot2.sig.cS$lnRRsig))
-
-# choosing sex biased ln-ratios significantly larger than 0
-meta.plotS2.sig.malebias <- meta.plot2.sig.cS %>%
-  group_by_at(vars(trait, GroupingTerm)) %>%
-  filter(sig == 1) %>%
-  summarise(male_sig = sum(value > 0), female_sig = sum(value < 0), total = male_sig + female_sig)
-
-meta.plotS2.sig.malebias <- ungroup(meta.plotS2.sig.malebias) %>%
-  add_row(trait = "lnCVR", GroupingTerm = "Hearing", male_sig = 0, female_sig = 0, .before = 4) %>% # add "Hearing" for lnCVR (not filtered as only zeros)
-  mutate(malepercent = male_sig * 100 / total, femalepercent = female_sig * 100 / total)
-
-meta.plotS2.sig.malebias$label <- "CI not overlapping zero"
-
-# restructure to create stacked bar plots
-
-meta.plotS2.sig.bothsexes <- as.data.frame(meta.plotS2.sig.malebias)
-meta.plotS2.sig.bothsexes.b <- gather(meta.plotS2.sig.bothsexes, key = sex, value = percent, malepercent:femalepercent, factor_key = TRUE)
-
-# create new sample size variable
-
-meta.plotS2.sig.bothsexes.b$samplesize <- with(meta.plotS2.sig.bothsexes.b, ifelse(sex == "malepercent", male_sig, female_sig))
-
-# Add summary row ('All') and re-arrange rows into correct order for plotting (warnings about coercing 'id' into character vector are ok)
-
-meta.plotS2.sig.bothsexes.c <- meta.plotS2.sig.bothsexes.b %>% group_by(trait, sex) %>% 
-  summarise(GroupingTerm = "All", male_sig = sum(male_sig), female_sig = sum(female_sig), total = male_sig + female_sig, 
-            label = "CI not overlapping zero", samplesize = sum(samplesize)) %>%
-  mutate(percent = ifelse(sex == "femalepercent", female_sig*100/(male_sig + female_sig), male_sig*100/(male_sig + female_sig))) %>%
-  bind_rows(meta.plotS2.sig.bothsexes.b, .) %>%
-  mutate(rownumber = row_number()) %>%
-  .[c(55, 1:9, 57, 10:18, 59, 19:27, 56, 28:36, 58, 37:45, 60, 46:54), ]
-
-meta.plotS2.sig.bothsexes.c$GroupingTerm <- factor(meta.plotS2.sig.bothsexes.c$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
-meta.plotS2.sig.bothsexes.c$GroupingTerm <- factor(meta.plotS2.sig.bothsexes.c$GroupingTerm, rev(levels(meta.plotS2.sig.bothsexes.c$GroupingTerm)))
-
-# *Plot Fig2 all significant results (CI not overlapping zero):
-#     no sig. lnCVR for 'Hearing' in either sex; no sig. male-biased lnCVR for 'Immunology' and 'Eye, and no sig. male-biased lnVR for 'Eye'
-
-malebias_FigS2_sigtraits <-
-  ggplot(meta.plotS2.sig.bothsexes.c) +
-  aes(x = GroupingTerm, y = percent, fill = sex) +
-  ylab("Percentage") +
-  geom_col() +
-  geom_hline(yintercept = 50, linetype = "dashed", color = "gray40") +
-  geom_text(
-    data = subset(meta.plotS2.sig.bothsexes.c, samplesize != 0), aes(label = samplesize), position = position_stack(vjust = .5),
-    color = "white", size = 3.5
-  ) +
-  facet_grid(
-    cols = vars(trait), rows = vars(label), labeller = label_wrap_gen(width = 18),
-    scales = "free", space = "free"
-  ) +
-  scale_fill_brewer(palette = "Set2") +
-  theme_bw(base_size = 18) +
-  theme(
-    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
-    strip.text.x = element_text(size = 12),
-    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
-    text = element_text(size = 14),
-    panel.spacing = unit(0.5, "lines"),
-    panel.border = element_blank(),
-    axis.line = element_line(),
-    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
-    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
-    panel.grid.minor.y = element_blank(),
-    panel.grid.minor.x = element_blank(),
-    legend.position = "none",
-    #axis.title.x = element_blank(),
-    axis.title.y = element_blank()
-  ) +
-  coord_flip()
-
-# malebias_FigS2_sigtraits # this is Figure S2 A
-
-#Prepare data for traits with effect size ratios > 10% larger in males, supplemental Figure S2
-
-#### Over 10% male bias, count data (first- order metanalysis)
-
-meta.plot2.over10 <- meta_clean %>%
-                    select(lnCVR, lnVR, lnRR, GroupingTerm) %>%
-                    arrange(GroupingTerm)
-
-meta.plot2.over10.b <- gather(meta.plot2.over10, trait, value, c(lnCVR, lnVR, lnRR))
-
-meta.plot2.over10.b$trait <- factor(meta.plot2.over10.b$trait, levels = c("lnCVR", "lnVR", "lnRR"))
-
-meta.plot2.over10.c <- meta.plot2.over10.b %>%
-                      group_by_at(vars(trait, GroupingTerm)) %>%
-                      summarise(malebias = sum(value > log(11 / 10)), 
-                                femalebias = sum(value < log(9 / 10)), 
-                                total = malebias + femalebias,
-                                malepercent = malebias * 100 / total, 
-                                femalepercent = femalebias * 100 / total)
-
-meta.plot2.over10.c$label <- "Sex difference in m/f ratios > 10%"
-
-# restructure to create stacked bar plots
-
-meta.plot2.over10.c <- as.data.frame(meta.plot2.over10.c)
-meta.plot2.over10.d <- gather(meta.plot2.over10.c, key = sex, value = percent, malepercent:femalepercent, factor_key = TRUE)
-
-# create new sample size variable
-
-meta.plot2.over10.d$samplesize <- with(meta.plot2.over10.d, ifelse(sex == "malepercent", malebias, femalebias))
-
-# Add summary row ('All') and re-arrange rows into correct order for plotting (warnings about coercing 'id' into character vector are ok)
-
-meta.plot2.over10.e <- meta.plot2.over10.d %>% 
-                      group_by(trait, sex) %>% 
-                      summarise(GroupingTerm = "All", malebias = sum(malebias), 
-                                femalebias = sum(femalebias), 
-                                total = malebias + femalebias, 
-                                label = "Sex difference in m/f ratios > 10%", 
-                                samplesize = sum(samplesize)) %>%
-                      mutate(percent = ifelse(sex == "femalepercent", 
-                                              femalebias*100/(malebias + femalebias), 
-                                              malebias*100/(malebias + femalebias))) %>%
-                      bind_rows(meta.plot2.over10.d, .) %>%
-                      mutate(rownumber = row_number()) %>%
-                      .[c(55, 1:9, 57, 10:18, 59, 19:27, 56, 28:36, 58, 37:45, 60, 46:54), ]
-
-meta.plot2.over10.e$GroupingTerm <- factor(meta.plot2.over10.e$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
-meta.plot2.over10.e$GroupingTerm <- factor(meta.plot2.over10.e$GroupingTerm, rev(levels(meta.plot2.over10.e$GroupingTerm)))
-
-# PLOT:  Fig2 Sex difference in m/f ratio > 10% (Fig S2 A, lower panel)
-
-malebias_Fig2_over10 <-
-  ggplot(meta.plot2.over10.e) +
-  aes(x = GroupingTerm, y = percent, fill = sex) +
-  ylab("Percentage") +
-  geom_col() +
-  geom_hline(yintercept = 50, linetype = "dashed", color = "gray40") +
-  geom_text(
-    data = subset(meta.plot2.over10.e, samplesize != 0), aes(label = samplesize), position = position_stack(vjust = .5),
-    color = "white", size = 3.5
-  ) +
-  facet_grid(
-    cols = vars(trait), rows = vars(label), labeller = label_wrap_gen(width = 18),
-    scales = "free", space = "free"
-  ) +
-  scale_fill_brewer(palette = "Set2") +
-  theme_bw(base_size = 18) +
-  theme(
-    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
-    strip.text.x = element_blank(),
-    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
-    text = element_text(size = 14),
-    panel.spacing = unit(0.5, "lines"),
-    panel.border = element_blank(),
-    axis.line = element_line(),
-    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
-    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
-    panel.grid.minor.y = element_blank(),
-    panel.grid.minor.x = element_blank(),
-    legend.position = "none",
-    #axis.title.x = element_blank(),
-    axis.title.y = element_blank()
-  ) +
-  coord_flip()
-
-# malebias_Fig2_over10  (supplemental Figure S2 A)
-```
-
-```{r FigS2_B, eval = TRUE, echo = FALSE}
-
-#### 3.2: Preparation for Figure S2 B (second-order meta-analysis)
-#### 3.3: Female Figure, significant and highly biased traits (Figure S2 B, left hand side panels)
-#Preparing data for traits with CI not overlapping 0: 
-#create column with 1= different from zero, 0= zero included in CI (for Figure S2 B, top left panel)
-
-#Restructure data for plotting
-
-overall3.female.sigS <- gather(overall.female.plot3, parameter, value, c(lnCVR, lnVR, lnRR), factor_key = TRUE)
-
-lnCVR.ci <- overall3.female.sigS %>%
-  filter(parameter == "lnCVR") %>%
-  mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
-lnVR.ci <- overall3.female.sigS %>%
-  filter(parameter == "lnVR") %>%
-  mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
-lnRR.ci <- overall3.female.sigS %>%
-  filter(parameter == "lnRR") %>%
-  mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
-
-overall4.female.sigS <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
-
-overall4.female.sigS$label <- "CI not overlapping zero"
-
-# PLOT female-bias:  significant traits
-
-Metameta_FigS2_female.sig <- overall4.female.sigS %>%
-  ggplot(aes(y = GroupingTerm, x = value)) +
-  geom_errorbarh(aes(
-    xmin = ci.low,
-    xmax = ci.high
-  ),
-  height = 0.1, show.legend = FALSE
-  ) +
-  geom_point(aes(shape = parameter),
-    fill = "salmon1", color = "salmon1", size = 2.2,
-    show.legend = FALSE
-  ) +
-  scale_x_continuous(
-    limits = c(-0.4, 0),
-    breaks = c(-0.3, 0),
-    name = "Effect size"
-  ) +
-  geom_vline(
-    xintercept = 0,
-    color = "black",
-    linetype = "dashed"
-  ) +
-  facet_grid(
-    cols = vars(parameter), # rows = vars(label),
-    # labeller = label_wrap_gen(width = 23),
-    scales = "free",
-    space = "free"
-  ) +
-  theme_bw() +
-  theme(
-    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
-    strip.text.x = element_text(size = 12),
-    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
-    text = element_text(size = 14),
-    panel.spacing = unit(0.5, "lines"),
-    panel.border = element_blank(),
-    axis.line = element_line(),
-    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
-    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
-    panel.grid.minor.y = element_blank(),
-    panel.grid.minor.x = element_blank(),
-    legend.title = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank()
-  )
-
-# Metameta_FigS2_female.sig
-
-#### Prepare data for traits with m/f difference > 10%, Female bias (Figure S2 B, bottom left)
-
-meta.plot3.perc <- metacombo %>%
-  mutate(
-    percCVR = ifelse(lnCVR < log(9 / 10), 1, 0),
-    percVR = ifelse(lnVR < log(9 / 10), 1, 0),
-    percRR = ifelse(lnRR < log(9 / 10), 1, 0)
-  )
-
-# Significant subset for lnCVR
-metacombo_plot3.CVR.perc <- meta.plot3.perc %>%
-  filter(percCVR == 1) %>%
-  group_by(GroupingTerm) %>%
-  nest()
-
-metacombo_plot3.CVR.perc.all <- meta.plot3.perc %>%
-  filter(percCVR == 1) %>%
-  nest(data = everything())
-
-# Significant subset for lnVR
-metacombo_plot3.VR.perc <- meta.plot3.perc %>%
-  filter(percVR == 1) %>%
-  group_by(GroupingTerm) %>%
-  nest()
-
-metacombo_plot3.VR.perc.all <- meta.plot3.perc %>%
-  filter(percVR == 1) %>%
-  nest(data = everything())
-
-# Significant subset for lnRR
-metacombo_plot3.RR.perc <- meta.plot3.perc %>%
-  filter(percRR == 1) %>%
-  group_by(GroupingTerm) %>%
-  nest()
-
-metacombo_plot3.RR.perc.all <- meta.plot3.perc %>%
-  filter(percRR == 1) %>%
-  nest(data = everything())
-
-# **Final fixed effects meta-analyses within grouping terms, with SE of the estimate
-
-plot3.meta.CVR.perc <- metacombo_plot3.CVR.perc %>%
-  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(
-    yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower) / (2 * 1.96),
-    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-  )))
-
-plot3.meta.VR.perc <- metacombo_plot3.VR.perc %>%
-  mutate(model_lnVR = map(data, ~ metafor::rma.uni(
-    yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
-    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-  )))
-
-plot3.meta.RR.perc <- metacombo_plot3.RR.perc %>%
-  mutate(model_lnRR = map(data, ~ metafor::rma.uni(
-    yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
-    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-  )))
-
-# Across all grouping terms #
-
-plot3.meta.CVR.perc.all <- metacombo_plot3.CVR.perc.all %>%
-  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(
-    yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower) / (2 * 1.96),
-    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-  )))
-
-plot3.meta.CVR.perc.all <- plot3.meta.CVR.perc.all %>% mutate(GroupingTerm = "All")
-
-plot3.meta.VR.perc.all <- metacombo_plot3.VR.perc.all %>%
-  mutate(model_lnVR = map(data, ~ metafor::rma.uni(
-    yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
-    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-  )))
-
-plot3.meta.VR.perc.all <- plot3.meta.VR.perc.all %>% mutate(GroupingTerm = "All")
-
-plot3.meta.RR.perc.all <- metacombo_plot3.RR.perc.all %>%
-  mutate(model_lnRR = map(data, ~ metafor::rma.uni(
-    yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
-    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-  )))
-
-plot3.meta.RR.perc.all <- plot3.meta.RR.perc.all %>% mutate(GroupingTerm = "All")
-
-# Combine with separate grouping term results
-
-plot3.meta.CVR.perc <- bind_rows(plot3.meta.CVR.perc, plot3.meta.CVR.perc.all)
-plot3.meta.VR.perc <- bind_rows(plot3.meta.VR.perc, plot3.meta.VR.perc.all)
-plot3.meta.RR.perc <- bind_rows(plot3.meta.RR.perc, plot3.meta.RR.perc.all)
-
-# **Re-structure data for each grouping term; delete un-used variables: "Hearing missing for all 3 parameters"
-
-plot3.meta.CVR.perc.b <- as.data.frame(plot3.meta.CVR.perc %>% group_by(GroupingTerm) %>%
-  mutate(
-    lnCVR = map_dbl(model_lnCVR, pluck(2)), lnCVR_lower = map_dbl(model_lnCVR, pluck(6)),
-    lnCVR_upper = map_dbl(model_lnCVR, pluck(7)), lnCVR_se = map_dbl(model_lnCVR, pluck(3))
-  ))[, c(1, 4:7)]
-add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.meta.CVR.perc.b))
-plot3.meta.CVR.perc.b <- rbind(plot3.meta.CVR.perc.b, add.row.hearing)
-plot3.meta.CVR.perc.b <- plot3.meta.CVR.perc.b[order(plot3.meta.CVR.perc.b$GroupingTerm), ]
-
-plot3.meta.VR.perc.b <- as.data.frame(plot3.meta.VR.perc %>% group_by(GroupingTerm) %>%
-  mutate(
-    lnVR = map_dbl(model_lnVR, pluck(2)), lnVR_lower = map_dbl(model_lnVR, pluck(6)),
-    lnVR_upper = map_dbl(model_lnVR, pluck(7)), lnVR_se = map_dbl(model_lnVR, pluck(3))
-  ))[, c(1, 4:7)]
-add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.meta.VR.perc.b))
-plot3.meta.VR.perc.b <- rbind(plot3.meta.VR.perc.b, add.row.hearing)
-plot3.meta.VR.perc.b <- plot3.meta.VR.perc.b[order(plot3.meta.VR.perc.b$GroupingTerm), ]
-
-plot3.meta.RR.perc.b <- as.data.frame(plot3.meta.RR.perc %>% group_by(GroupingTerm) %>%
-  mutate(
-    lnRR = map_dbl(model_lnRR, pluck(2)), lnRR_lower = map_dbl(model_lnRR, pluck(6)),
-    lnRR_upper = map_dbl(model_lnRR, pluck(7)), lnRR_se = map_dbl(model_lnRR, pluck(3))
-  ))[, c(1, 4:7)]
-add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.meta.RR.perc.b))
-plot3.meta.RR.perc.b <- rbind(plot3.meta.RR.perc.b, add.row.hearing)
-add.row.hematology <- as.data.frame(t(c("Hematology", NA, NA, NA, NA))) %>%
-  setNames(names(plot3.meta.RR.perc.b))
-plot3.meta.RR.perc.b <- rbind(plot3.meta.RR.perc.b, add.row.hematology)
-
-plot3.meta.RR.perc.b <- plot3.meta.RR.perc.b[order(plot3.meta.RR.perc.b$GroupingTerm), ]
-
-plot3.meta.CVR.perc.c <- full_join(plot3.meta.CVR.perc.b, plot3.meta.VR.perc.b)
-overall.plot3.perc <- full_join(plot3.meta.CVR.perc.c, plot3.meta.RR.perc.b)
-
-overall.plot3.perc$GroupingTerm <- factor(overall.plot3.perc$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
-overall.plot3.perc$GroupingTerm <- factor(overall.plot3.perc$GroupingTerm, rev(levels(overall.plot3.perc$GroupingTerm)))
-
-# Restructure data for plotting
-# Female bias, 10 percent difference
-
-overall3.perc <- gather(overall.plot3.perc, parameter, value, c(lnCVR, lnVR, lnRR), factor_key = TRUE)
-
-lnCVR.ci <- overall3.perc %>%
-  filter(parameter == "lnCVR") %>%
-  mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
-lnVR.ci <- overall3.perc  %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
-lnRR.ci <- overall3.perc %>%
-  filter(parameter == "lnRR") %>%
-  mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
-
-overall4.perc <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
-
-overall4.perc$label <- "Sex difference in m/f ratios > 10%"
-
-overall4.perc$value <- as.numeric(overall4.perc$value)
-overall4.perc$ci.low <- as.numeric(overall4.perc$ci.low)
-overall4.perc$ci.high <- as.numeric(overall4.perc$ci.high)
-
-# Plot FigS2 all >10% difference (female)
-# Figure S2B, bottom left
-
-Metameta_Fig3_female.perc <- overall4.perc %>%
-  ggplot(aes(y = GroupingTerm, x = value)) +
-  geom_errorbarh(aes(
-    xmin = ci.low,
-    xmax = ci.high
-  ),
-  height = 0.1, show.legend = FALSE
-  ) +
-  geom_point(aes(shape = parameter),
-    fill = "salmon1", color = "salmon1", size = 2.2,
-    show.legend = FALSE
-  ) +
-
-  # scale_shape_manual(values =
-
-  scale_x_continuous(
-    limits = c(-0.53, 0.2),
-    breaks = c(-0.3, 0),
-    name = "Effect size"
-  ) +
-  geom_vline(
-    xintercept = 0,
-    color = "black",
-    linetype = "dashed"
-  ) +
-  facet_grid(
-    cols = vars(parameter), # rows = vars(label),
-    # labeller = label_wrap_gen(width = 23),
-    scales = "free",
-    space = "free"
-  ) +
-  theme_bw() +
-  theme(
-    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
-    strip.text.x = element_blank(),
-    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
-    text = element_text(size = 14),
-    panel.spacing = unit(0.5, "lines"),
-    panel.border = element_blank(),
-    axis.line = element_line(),
-    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
-    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
-    panel.grid.minor.y = element_blank(),
-    panel.grid.minor.x = element_blank(),
-    legend.title = element_blank(),
-    axis.title.x = element_text(hjust = 0.5, size = 14),
-    axis.title.y = element_blank()
-  )
-
-# Metameta_Fig3_female.perc (Figure S2 bottom left panel)
-```
-
-```{r FigS2_B_right, eval = TRUE, echo = FALSE}
-#### 3.4: Male Figure, significant and highly biased traits (Figure S2 B, right hand side panels)
-#Restructuring data with significant male bias (for Figure S2 B, top right panel)
-
-overall3.male.sigS <- gather(overall.male.plot3, parameter, value, c(lnCVR, lnVR, lnRR), factor_key = TRUE)
-
-lnCVR.ci <- overall3.male.sigS %>%
-  filter(parameter == "lnCVR") %>%
-  mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
-lnVR.ci <- overall3.male.sigS %>%
-  filter(parameter == "lnVR") %>%
-  mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
-lnRR.ci <- overall3.male.sigS %>%
-  filter(parameter == "lnRR") %>%
-  mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
-
-overall4.male.sigS <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
-
-overall4.male.sigS$label <- "CI not overlapping zero"
-
-# Plot FigS2 all significant results (CI not overlapping zero, male )
-
-Metameta_FigS2_male.sig <- overall4.male.sigS %>%
-  ggplot(aes(y = GroupingTerm, x = value)) +
-  geom_errorbarh(aes(
-    xmin = ci.low,
-    xmax = ci.high
-  ),
-  height = 0.1, show.legend = FALSE
-  ) +
-  geom_point(aes(shape = parameter),
-    fill = "mediumaquamarine", color = "mediumaquamarine", size = 2.2,
-    show.legend = FALSE
-  ) +
-  scale_x_continuous(
-    limits = c(0, 0.4),
-    breaks = c(0, 0.3),
-    name = "Effect size"
-  ) +
-  geom_vline(
-    xintercept = 0,
-    color = "black",
-    linetype = "dashed"
-  ) +
-  facet_grid(
-    cols = vars(parameter), rows = vars(label),
-    labeller = label_wrap_gen(width = 23),
-    scales = "free",
-    space = "free"
-  ) +
-  theme_bw() +
-  theme(
-    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
-    strip.text.x = element_text(size = 12),
-    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
-    text = element_text(size = 14),
-    panel.spacing = unit(0.5, "lines"),
-    panel.border = element_blank(),
-    axis.line = element_line(),
-    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
-    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
-    panel.grid.minor.y = element_blank(),
-    panel.grid.minor.x = element_blank(),
-    legend.title = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank()
-  )
-
-# Metameta_FigS2_male.sig
-
-## Prepare data for traits with m/f difference > 10%. Male bias
-### Create column with 1= larger, 0= difference not larger than 10% between male/female ratios
-
-meta.male.plot3.perc <- metacombo %>%
-  mutate(
-    percCVR = ifelse(lnCVR > log(11 / 10), 1, 0),
-     percVR = ifelse( lnVR > log(11 / 10), 1, 0),
-     percRR = ifelse( lnRR > log(11 / 10), 1, 0)
-  )
-
-# Significant subset for lnCVR
-metacombo_male.plot3.CVR.perc <- meta.male.plot3.perc %>%
-                                filter(percCVR == 1) %>%
-                                group_by(GroupingTerm) %>%
-                                nest()
-
-metacombo_male.plot3.CVR.perc.all <- meta.male.plot3.perc %>%
-                filter(percCVR == 1) %>%
-  nest(data = everything())
-
-# Significant subset for lnVR
-metacombo_male.plot3.VR.perc <- meta.male.plot3.perc %>%
-  filter(percVR == 1) %>%
-  group_by(GroupingTerm) %>%
-  nest()
-
-metacombo_male.plot3.VR.perc.all <- meta.male.plot3.perc %>%
-  filter(percVR == 1) %>%
-  nest(data = everything())
-
-# Significant subset for lnRR
-metacombo_male.plot3.RR.perc <- meta.male.plot3.perc %>%
-  filter(percRR == 1) %>%
-  group_by(GroupingTerm) %>%
-  nest()
-
-metacombo_male.plot3.RR.perc.all <- meta.male.plot3.perc %>%
-  filter(percRR == 1) %>%
-  nest(data = everything())
-
-# Final fixed effects meta-analyses within grouping terms and across grouping terms, with SE of the estimate
-
-plot3.male.meta.CVR.perc <- metacombo_male.plot3.CVR.perc %>%
-  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(
-    yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower) / (2 * 1.96),
-    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-  )))
-
-plot3.male.meta.VR.perc <- metacombo_male.plot3.VR.perc %>%
-  mutate(model_lnVR = map(data, ~ metafor::rma.uni(
-    yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
-    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-  )))
-
-plot3.male.meta.RR.perc <- metacombo_male.plot3.RR.perc %>%
-  mutate(model_lnRR = map(data, ~ metafor::rma.uni(
-    yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
-    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-  )))
-
-# Across all grouping terms
-
-plot3.male.meta.CVR.perc.all <- metacombo_male.plot3.CVR.perc.all %>%
-  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(
-    yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower) / (2 * 1.96),
-    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-  )))
-
-plot3.male.meta.CVR.perc.all <- plot3.male.meta.CVR.perc.all %>% mutate(GroupingTerm = "All")
-
-plot3.male.meta.VR.perc.all <- metacombo_male.plot3.VR.perc.all %>%
-  mutate(model_lnVR = map(data, ~ metafor::rma.uni(
-    yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
-    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-  )))
-
-plot3.male.meta.VR.perc.all <- plot3.male.meta.VR.perc.all %>% mutate(GroupingTerm = "All")
-
-plot3.male.meta.RR.perc.all <- metacombo_male.plot3.RR.perc.all %>%
-  mutate(model_lnRR = map(data, ~ metafor::rma.uni(
-    yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
-    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
-  )))
-
-plot3.male.meta.RR.perc.all <- plot3.male.meta.RR.perc.all %>% mutate(GroupingTerm = "All")
-
-# Combine with separate grouping term results
-
-plot3.male.meta.CVR.perc <- bind_rows(plot3.male.meta.CVR.perc, plot3.male.meta.CVR.perc.all)
-plot3.male.meta.VR.perc <- bind_rows(plot3.male.meta.VR.perc, plot3.male.meta.VR.perc.all)
-plot3.male.meta.RR.perc <- bind_rows(plot3.male.meta.RR.perc, plot3.male.meta.RR.perc.all)
-
-# **Re-structure data for each grouping term; delete un-used variables: "Hearing missing for all 3 parameters"
-
-plot3.male.meta.CVR.perc.b <- as.data.frame(plot3.male.meta.CVR.perc %>% group_by(GroupingTerm) %>%
-  mutate(
-    lnCVR = map_dbl(model_lnCVR, pluck(2)), lnCVR_lower = map_dbl(model_lnCVR, pluck(6)),
-    lnCVR_upper = map_dbl(model_lnCVR, pluck(7)), lnCVR_se = map_dbl(model_lnCVR, pluck(3))
-  ))[, c(1, 4:7)]
-add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.male.meta.CVR.perc.b))
-plot3.male.meta.CVR.perc.b <- rbind(plot3.male.meta.CVR.perc.b, add.row.hearing)
-plot3.male.meta.CVR.perc.b <- plot3.male.meta.CVR.perc.b[order(plot3.male.meta.CVR.perc.b$GroupingTerm), ]
-
-plot3.male.meta.VR.perc.b <- as.data.frame(plot3.male.meta.VR.perc %>% group_by(GroupingTerm) %>%
-  mutate(
-    lnVR = map_dbl(model_lnVR, pluck(2)), lnVR_lower = map_dbl(model_lnVR, pluck(6)),
-    lnVR_upper = map_dbl(model_lnVR, pluck(7)), lnVR_se = map_dbl(model_lnVR, pluck(3))
-  ))[, c(1, 4:7)]
-add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.male.meta.VR.perc.b))
-plot3.male.meta.VR.perc.b <- rbind(plot3.male.meta.VR.perc.b, add.row.hearing)
-plot3.male.meta.VR.perc.b <- plot3.male.meta.VR.perc.b[order(plot3.male.meta.VR.perc.b$GroupingTerm), ]
-
-plot3.male.meta.RR.perc.b <- as.data.frame(plot3.male.meta.RR.perc %>% group_by(GroupingTerm) %>%
-  mutate(
-    lnRR = map_dbl(model_lnRR, pluck(2)), lnRR_lower = map_dbl(model_lnRR, pluck(6)),
-    lnRR_upper = map_dbl(model_lnRR, pluck(7)), lnRR_se = map_dbl(model_lnRR, pluck(3))
-  ))[, c(1, 4:7)]
-add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>%
-  setNames(names(plot3.male.meta.RR.perc.b))
-plot3.male.meta.RR.perc.b <- rbind(plot3.male.meta.RR.perc.b, add.row.hearing)
-
-add.row.eye <- as.data.frame(t(c("Eye", NA, NA, NA, NA))) %>%
-  setNames(names(plot3.male.meta.RR.perc.b))
-plot3.male.meta.RR.perc.b <- rbind(plot3.male.meta.RR.perc.b, add.row.eye)
-
-plot3.male.meta.RR.perc.b <- plot3.male.meta.RR.perc.b[order(plot3.male.meta.RR.perc.b$GroupingTerm), ]
-
-plot3.male.meta.CVR.Vr.perc <- full_join(plot3.male.meta.CVR.perc.b, plot3.male.meta.VR.perc.b)
-overall.male.plot3.perc <- full_join(plot3.male.meta.CVR.Vr.perc, plot3.male.meta.RR.perc.b)
-
-overall.male.plot3.perc$GroupingTerm <- factor(overall.male.plot3.perc$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
-overall.male.plot3.perc$GroupingTerm <- factor(overall.male.plot3.perc$GroupingTerm, rev(levels(overall.male.plot3.perc$GroupingTerm)))
-
-# Restructure data for plotting : Male biased, 10% difference
-
-overall3.perc <- gather(overall.male.plot3.perc, parameter, value, c(lnCVR, lnVR, lnRR), factor_key = TRUE)
-
-lnCVR.ci <- overall3.perc %>%
-  filter(parameter == "lnCVR") %>%
-  mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
-lnVR.ci <- overall3.perc  %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
-lnRR.ci <- overall3.perc %>%
-  filter(parameter == "lnRR") %>%
-  mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
-
-overall4.male.perc <- bind_rows(lnCVR.ci,lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
-
-overall4.male.perc$label <- "Sex difference in m/f ratios > 10%"
-
-overall4.male.perc$value <- as.numeric(overall4.male.perc$value)
-overall4.male.perc$ci.low <- as.numeric(overall4.male.perc$ci.low)
-overall4.male.perc$ci.high <- as.numeric(overall4.male.perc$ci.high)
-
-# Plot Fig S2 all >10% difference (male bias)
-# S2 B, bottom right
-
-Metameta_Fig3_male.perc <- overall4.male.perc %>% # filter(., GroupingTerm != "Hearing") %>%
-  ggplot(aes(y = GroupingTerm, x = value)) +
-  geom_errorbarh(aes(
-    xmin = ci.low,
-    xmax = ci.high
-  ),
-  height = 0.1, show.legend = FALSE
-  ) +
-  geom_point(aes(
-    shape = parameter,
-    fill = parameter
-  ),
-  color = "mediumaquamarine", size = 2.2,
-  show.legend = FALSE
-  ) +
-  scale_x_continuous(
-    limits = c(-0.2, 0.62),
-    breaks = c(0, 0.3),
-    name = "Effect size"
-  ) +
-  geom_vline(
-    xintercept = 0,
-    color = "black",
-    linetype = "dashed"
-  ) +
-  facet_grid(
-    cols = vars(parameter), rows = vars(label),
-    labeller = label_wrap_gen(width = 23),
-    scales = "free",
-    space = "free"
-  ) +
-  theme_bw() +
-  theme(
-    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
-    strip.text.x = element_blank(),
-    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
-    text = element_text(size = 14),
-    panel.spacing = unit(0.5, "lines"),
-    panel.border = element_blank(),
-    axis.line = element_line(),
-    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
-    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
-    panel.grid.minor.y = element_blank(),
-    panel.grid.minor.x = element_blank(),
-    legend.title = element_blank(),
-    axis.title.x = element_text(hjust = 0.5, size = 14),
-    axis.title.y = element_blank()
-  )
-
-# Metameta_Fig3_male.perc (Figure S2 right panel)
-```
-
-## Figure
-Figure \@ref(fig:FigS1) is similar to Figure 3 in the main article except that lnVR has been added to the plot for comparison with lnCVR and lnRR.
-
-```{r FigS1, fig.height = 8, fig.width = 7, fig.cap=" Numbers of either male (blue-green bars) or female (orange-red bars) biased traits  (Panel A) across functional groups, this time for lnCVR (left hand side), lnVR (middle) and lnRR (right hand side).
-Panel B shows effect sizes from separate meta-analysis for each functional group, and Panel C contains results of heterogeneity analyses.
-All three panels represent results evaluated across all traits."}
-
-#### Combined Figure S1: overall Count data, Meta anlysis results, Heterogeneity
-
-FigS1 <- ggarrange(malebias_FigS1_alltraits, Metameta_FigS1_alltraits, HeteroS1, nrow = 3, align = "v", heights = c(1.1, 1, 1), labels = c("A", "B", "C"))
-FigS1
-#ggsave("FigS1_OverallResults.pdf", plot = FigS1, width = 6, height = 7)
-```
-
-## Figure
-
-### Sex-bias in traits sub-analysis
-
-#### Methods
-Among the 147 traits (i.e.
-with ‘first-order’ meta-analytic results), we found 31 traits to be significantly male-biased and 30 female-biased for lnCVR (47 male-biased and 39 female- biased for lnRR; 74 male and 55 female-biased for lnVR).
-We used this statistical significance to categorize traits into two groups: male-based and female-biased traits.
-For each set of these sex-biased traits, we conducted second-order meta-analyses with trait as the unit of analysis in the same way as those using lnRR, lnVR and lnCVR (Figure \@ref(fig:FigG1)J).
-As sensitivity analyses, we also employed another way of separating male- and female-biased traits.
-We quantified traits that were more than 10% biased towards either of the sexes, regardless of significance (N[male-biased] = 31, & N[female-biased] = 36 for lnCVR,  N[male-biased] = 56, & N[female-biased] = 57 for lnVR , N[male-biased] = 42, & N[female-biased] = 33  for lnRR; see Supplemental Figure S\@ref(fig:FigS2), Supplemental Table 7.3).
-
-#### Results
-Having established that different sex-biases were present across trait functional groups, we explored specific patterns in male and female bias by categorizing traits into either male or female-biased, and then, quantifying the degree of sex bias.
-To do this, we focused on only those traits that were significantly biased towards one sex (as indicated by “CI not overlapping 0” in Figure S\@ref(fig:FigS2).
-Selecting significantly sex-biased traits reduced the number of traits substantially (Figure S\@ref(fig:FigS2)A; compared to all traits, Figure \@ref(fig:Fig3) and Figure \@ref(fig:FigS1)), and returned similar numbers of traits with either significant male- or female-bias for lnCVR (Figure S\@ref(fig:FigS2)A).
-
-Looking only at traits with significant male-bias, trait variability tended to be higher in males than in females overall (11.77% male bias, lnCVR = 0.111, CI = [0.093 to 0.129]; compared to 8.3% female-bias, lnCVR = -0.087, CI = [-0.109 to (-0.064)]; Figure S\@ref(fig:FigS2)B).
-The degree of sex-bias varied across the functional trait groups, ranging from 4.6 % (Physiology, lnCVR = -0.047, CI = [-0.064 to (-0.030)] to 15.13 % (Eye morphology, lnCVR = -0.164, CI = [-0.249 to (-0.250)] in females, and from 8.6 % (Hematology, lnCVR = 0.082, CI = [0.048 to 0.117]) and 16.66 % (Heart, lnCVR = 0.154, CI = [0.085 to 0.223]) in males (Figure S\@ref(fig:FigS2)B).
-
-To put sex biases (sexual dimorphisms) in variability into perspective, we also quantify the degree of sexual dimorphism in significantly sex-biased traits (i.e., the extent of sexual dimorphisms).
-There were more traits that were significantly biased in mean trait value in males compared to females (Figure S\@ref(fig:FigS2)A, lnRR).
-These traits were 11.73 % biased towards males (Figure S\@ref(fig:FigS2)B; lnRR = 0.111, CI = [0.083 – 0.138]) while 9.38 % towards females (lnRR = -0.094, CI = [-0.129 – (-0.068)].
-The overall pattern for lnRR was more varied among the functional trait groups than for lnCVR, ranging from 1.2% (Hematology, lnRR = -0.013, CI = [-0.017 – (-0.007)] to 14.72 % (Immunology, lnRR = -0.159, CI = [-0.229 – (-0.089)] in female-based traits (Figure S\@ref(fig:FigS2)B) whereas in males-based traits from 1.8 % (Hearing, lnRR = 0.018, CI = [0.006 – 0.031]) to 25 % (Metabolism, lnRR = 0.223, CI = [0.110 – 0.335])  (Figure S\@ref(fig:FigS2)B).
-
-```{r FigS2, fig.height = 10, fig.width = 8, fig.cap=" A) Differences in numbers of affected traits, in variance (lnCVR and lnVR) and means (lnRR), where there’s a significant difference between the sexes (i.e CI not overlapping zero), and where the sex bias is greater than 10% difference (regardless of significance).
-Panel B depicts results for the sex bias in those traits that differ between the sexes (second-order meta-analysis).
-Triangles represent sex bias in means (response ratio) and black circles differences in the coefficient of variation ratio (mean-adjusted variability).
-The orange-red bars represent trait groups with a female bias, blue-green bars male-biased traits."}
-library(ggpubr)
-FigS2b <- ggarrange(Metameta_FigS2_female.sig, Metameta_FigS2_male.sig,
-  ncol = 2, nrow = 1, widths = c(1, 1.30), heights = c(1.2, 1.2))
-
-FigS2d <- ggarrange(Metameta_Fig3_female.perc, Metameta_Fig3_male.perc,
-  ncol = 2, nrow = 1, widths = c(1, 1.20), heights = c(1.1, 1.1))
-
-# end combination Figure 5
-FigS2 <- ggarrange(malebias_FigS2_sigtraits, malebias_Fig2_over10, FigS2b, FigS2d, ncol = 1, nrow = 4, heights = c(2.5, 2.2, 2.1, 2), labels = c("A", " ", "B", " "))
-FigS2
-```
-
-# Supplemental Tables
-## Table
-
 ```{r Fig5_prep, echo = FALSE, eval = TRUE}
@@
 
+```{r FigS1_prep, echo = FALSE, eval = TRUE}
+### Preparing the data
+#The supplemental figures include lnVR (in addition to lnCVR and lnRR, as presented in Figures 4 and 5)
+
+# *Prepare data for all traits
+
+meta.plot2.all <- meta_clean %>%
+  select(lnCVR, lnVR, lnRR, GroupingTerm) %>%
+  arrange(GroupingTerm)
+
+meta.plot2.all.bS1 <- gather(meta.plot2.all, trait, value, c(lnCVR, lnVR, lnRR))
+
+meta.plot2.all.bS1$trait <- factor(meta.plot2.all.bS1$trait, levels = c("lnCVR", "lnVR", "lnRR"))
+
+meta.plot2.all.cS1 <- meta.plot2.all.bS1 %>%
+  group_by_at(vars(trait, GroupingTerm)) %>%
+  summarise(
+    malebias = sum(value > 0), femalebias = sum(value <= 0), total = malebias + femalebias,
+    malepercent = malebias * 100 / total, femalepercent = femalebias * 100 / total
+  )
+
+meta.plot2.all.cS1$label <- "All traits"
+
+# Re-structure to create stacked bar plots
+
+meta.plot2.all.dS1 <- as.data.frame(meta.plot2.all.cS1)
+meta.plot2.all.eS1 <- gather(meta.plot2.all.dS1, key = sex, value = percent, malepercent:femalepercent, factor_key = TRUE)
+
+# Create new sample size variable
+
+meta.plot2.all.eS1$samplesize <- with(meta.plot2.all.eS1, ifelse(sex == "malepercent", malebias, femalebias))
+
+# Add summary row ('All') and re-arrange rows into correct order for plotting (warnings about coercing 'id' into character vector are ok)
+
+meta.plot2.all.fS1 <- meta.plot2.all.eS1 %>% group_by(trait, sex) %>% 
+  summarise(GroupingTerm = "All", malebias = sum(malebias), femalebias = sum(femalebias), total = malebias + femalebias, 
+            label = "All traits", samplesize = sum(samplesize)) %>%
+  mutate(percent = ifelse(sex == "femalepercent", femalebias*100/(malebias+femalebias), malebias*100/(malebias+femalebias))) %>%
+  bind_rows(meta.plot2.all.eS1, .) %>%
+  mutate(rownumber = row_number()) %>%
+  .[c(55, 1:9, 57, 10:18, 59, 19:27, 56, 28:36, 58, 37:45, 60, 46:54), ]
+
+meta.plot2.all.fS1$GroupingTerm <- factor(meta.plot2.all.fS1$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
+meta.plot2.all.fS1$GroupingTerm <- factor(meta.plot2.all.fS1$GroupingTerm, rev(levels(meta.plot2.all.fS1$GroupingTerm)))
+
+malebias_FigS1_alltraits <-
+  ggplot(meta.plot2.all.fS1) +
+  aes(x = GroupingTerm, y = percent, fill = sex) +
+  ylab("Percentage") +
+  geom_col() +
+  geom_hline(yintercept = 50, linetype = "dashed", color = "gray40") +
+  geom_text(
+    data = subset(meta.plot2.all.fS1, samplesize != 0), aes(label = samplesize), position = position_stack(vjust = .5),
+    color = "white", size = 3.5
+  ) +
+  facet_grid(
+    cols = vars(trait), rows = vars(label), labeller = label_wrap_gen(width = 18),
+    scales = "free", space = "free"
+  ) +
+  scale_fill_brewer(palette = "Set2") +
+  theme_bw(base_size = 18) +
+  theme(
+    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
+    strip.text.x = element_text(size = 12),
+    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
+    text = element_text(size = 14),
+    panel.spacing = unit(0.5, "lines"),
+    panel.border = element_blank(),
+    axis.line = element_line(),
+    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
+    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
+    panel.grid.minor.y = element_blank(),
+    panel.grid.minor.x = element_blank(),
+    legend.position = "none",
+    #axis.title.x = element_blank(),
+    axis.title.y = element_blank()
+  ) +
+  coord_flip()
+
+# malebias_FigS1_alltraits     #(panel A in Figure S1)
+
+###  Overall results of second order meta analysis, INCLUDING VR
+#### Re-structure MALE data for plotting
+
+overall3.male.sigS <- gather(overall.male.plot3, parameter, value, c(lnCVR, lnVR, lnRR), factor_key = TRUE)
+
+lnCVR.ci <- overall3.male.sigS %>%
+  filter(parameter == "lnCVR") %>%
+  mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
+lnVR.ci <- overall3.male.sigS %>%
+  filter(parameter == "lnVR") %>%
+  mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
+lnRR.ci <- overall3.male.sigS %>%
+  filter(parameter == "lnRR") %>%
+  mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
+
+overall4.male.sigS <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
+
+overall4.male.sigS$label <- "CI not overlapping zero"
+
+# Data are re-structured, and grouping terms are being re-ordered
+
+overall3S <- gather(overall2, parameter, value, c(lnCVR, lnVR, lnRR), factor_key = TRUE)
+
+lnCVR.ci <- overall3S %>%
+  filter(parameter == "lnCVR") %>%
+  mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
+lnVR.ci <- overall3S %>%
+  filter(parameter == "lnVR") %>%
+  mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
+lnRR.ci <- overall3S %>%
+  filter(parameter == "lnRR") %>%
+  mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
+
+overall4S <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
+
+# Re-order grouping terms
+
+overall4S$GroupingTerm <- factor(overall4S$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
+overall4S$GroupingTerm <- factor(overall4S$GroupingTerm, rev(levels(overall4S$GroupingTerm)))
+overall4S$label <- "All traits"
+
+#### Preparation for plot, including lnVR
+# Sub-Plot  for Figure S1: all traits (S1 B)
+
+Metameta_FigS1_alltraits <- overall4S %>%
+
+  ggplot(aes(y = GroupingTerm, x = value)) +
+  geom_errorbarh(aes(
+    xmin = ci.low,
+    xmax = ci.high
+  ),
+  height = 0.1, show.legend = FALSE
+  ) +
+  geom_point(aes(shape = parameter),
+    fill = "black",
+    color = "black", size = 2.2,
+    show.legend = FALSE
+  ) +
+  scale_x_continuous(
+    limits = c(-0.24, 0.25),
+    breaks = c(-0.2, -0.1, 0, 0.1, 0.2),
+    name = "Effect size"
+  ) +
+  geom_vline(
+    xintercept = 0,
+    color = "black",
+    linetype = "dashed"
+  ) +
+  facet_grid(
+    cols = vars(parameter), rows = vars(label),
+    labeller = label_wrap_gen(width = 23),
+    scales = "free",
+    space = "free"
+  ) +
+  theme_bw() +
+  theme(
+    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
+    strip.text.x = element_text(size = 12),
+    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
+    text = element_text(size = 14),
+    panel.spacing = unit(0.5, "lines"),
+    panel.border = element_blank(),
+    axis.line = element_line(),
+    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
+    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
+    panel.grid.minor.y = element_blank(),
+    panel.grid.minor.x = element_blank(),
+    legend.title = element_blank(),
+    axis.title.x = element_text(hjust = 0.5, size = 14),
+    axis.title.y = element_blank()
+  )
+
+# Metameta_FigS1_alltraits
+```
+
+```{r, eval = TRUE, echo = FALSE}
+
+#This Figure extends Figure 4, as it includes results not only for lnCVR and lnRR but also lnCVR.
+In addition, we compare two different assessments of sex-bias, significance (CI not overlapping zero) and sex differences in male / female ratios > 10%
+# Plot FigS2 all significant results (CI not overlapping zero) for males, count data
+
+meta.plot2.sig.bS <- meta.plot2.sig[, c("lnCVR", "lnVR", "lnRR", "lnCVRsig", "lnVRsig", "lnRRsig", "GroupingTerm")]
+
+meta.plot2.sig.cS <- gather(meta.plot2.sig.bS, trait, value, lnCVR:lnRR)
+meta.plot2.sig.cS$sig <- "placeholder"
+
+meta.plot2.sig.cS$trait <- factor(meta.plot2.sig.cS$trait, levels = c("lnCVR", "lnVR", "lnRR"))
+
+meta.plot2.sig.cS$sig <- ifelse(meta.plot2.sig.cS$trait == "lnCVR", meta.plot2.sig.cS$lnCVRsig,
+  ifelse(meta.plot2.sig.cS$trait == "lnVR", meta.plot2.sig.cS$lnVRsig, meta.plot2.sig.cS$lnRRsig))
+
+# choosing sex biased ln-ratios significantly larger than 0
+meta.plotS2.sig.malebias <- meta.plot2.sig.cS %>%
+  group_by_at(vars(trait, GroupingTerm)) %>%
+  filter(sig == 1) %>%
+  summarise(male_sig = sum(value > 0), female_sig = sum(value < 0), total = male_sig + female_sig)
+
+meta.plotS2.sig.malebias <- ungroup(meta.plotS2.sig.malebias) %>%
+  add_row(trait = "lnCVR", GroupingTerm = "Hearing", male_sig = 0, female_sig = 0, .before = 4) %>% # add "Hearing" for lnCVR (not filtered as only zeros)
+  mutate(malepercent = male_sig * 100 / total, femalepercent = female_sig * 100 / total)
+
+meta.plotS2.sig.malebias$label <- "CI not overlapping zero"
+
+# restructure to create stacked bar plots
+
+meta.plotS2.sig.bothsexes <- as.data.frame(meta.plotS2.sig.malebias)
+meta.plotS2.sig.bothsexes.b <- gather(meta.plotS2.sig.bothsexes, key = sex, value = percent, malepercent:femalepercent, factor_key = TRUE)
+
+# create new sample size variable
+
+meta.plotS2.sig.bothsexes.b$samplesize <- with(meta.plotS2.sig.bothsexes.b, ifelse(sex == "malepercent", male_sig, female_sig))
+
+# Add summary row ('All') and re-arrange rows into correct order for plotting (warnings about coercing 'id' into character vector are ok)
+
+meta.plotS2.sig.bothsexes.c <- meta.plotS2.sig.bothsexes.b %>% group_by(trait, sex) %>% 
+  summarise(GroupingTerm = "All", male_sig = sum(male_sig), female_sig = sum(female_sig), total = male_sig + female_sig, 
+            label = "CI not overlapping zero", samplesize = sum(samplesize)) %>%
+  mutate(percent = ifelse(sex == "femalepercent", female_sig*100/(male_sig + female_sig), male_sig*100/(male_sig + female_sig))) %>%
+  bind_rows(meta.plotS2.sig.bothsexes.b, .) %>%
+  mutate(rownumber = row_number()) %>%
+  .[c(55, 1:9, 57, 10:18, 59, 19:27, 56, 28:36, 58, 37:45, 60, 46:54), ]
+
+meta.plotS2.sig.bothsexes.c$GroupingTerm <- factor(meta.plotS2.sig.bothsexes.c$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
+meta.plotS2.sig.bothsexes.c$GroupingTerm <- factor(meta.plotS2.sig.bothsexes.c$GroupingTerm, rev(levels(meta.plotS2.sig.bothsexes.c$GroupingTerm)))
+
+# *Plot Fig2 all significant results (CI not overlapping zero):
+#     no sig. lnCVR for 'Hearing' in either sex; no sig. male-biased lnCVR for 'Immunology' and 'Eye, and no sig. male-biased lnVR for 'Eye'
+
+malebias_FigS2_sigtraits <-
+  ggplot(meta.plotS2.sig.bothsexes.c) +
+  aes(x = GroupingTerm, y = percent, fill = sex) +
+  ylab("Percentage") +
+  geom_col() +
+  geom_hline(yintercept = 50, linetype = "dashed", color = "gray40") +
+  geom_text(
+    data = subset(meta.plotS2.sig.bothsexes.c, samplesize != 0), aes(label = samplesize), position = position_stack(vjust = .5),
+    color = "white", size = 3.5
+  ) +
+  facet_grid(
+    cols = vars(trait), rows = vars(label), labeller = label_wrap_gen(width = 18),
+    scales = "free", space = "free"
+  ) +
+  scale_fill_brewer(palette = "Set2") +
+  theme_bw(base_size = 18) +
+  theme(
+    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
+    strip.text.x = element_text(size = 12),
+    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
+    text = element_text(size = 14),
+    panel.spacing = unit(0.5, "lines"),
+    panel.border = element_blank(),
+    axis.line = element_line(),
+    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
+    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
+    panel.grid.minor.y = element_blank(),
+    panel.grid.minor.x = element_blank(),
+    legend.position = "none",
+    #axis.title.x = element_blank(),
+    axis.title.y = element_blank()
+  ) +
+  coord_flip()
+
+# malebias_FigS2_sigtraits # this is Figure S2 A
+
+#Prepare data for traits with effect size ratios > 10% larger in males, supplemental Figure S2
+
+#### Over 10% male bias, count data (first- order metanalysis)
+
+meta.plot2.over10 <- meta_clean %>%
+                    select(lnCVR, lnVR, lnRR, GroupingTerm) %>%
+                    arrange(GroupingTerm)
+
+meta.plot2.over10.b <- gather(meta.plot2.over10, trait, value, c(lnCVR, lnVR, lnRR))
+
+meta.plot2.over10.b$trait <- factor(meta.plot2.over10.b$trait, levels = c("lnCVR", "lnVR", "lnRR"))
+
+meta.plot2.over10.c <- meta.plot2.over10.b %>%
+                      group_by_at(vars(trait, GroupingTerm)) %>%
+                      summarise(malebias = sum(value > log(11 / 10)), 
+                                femalebias = sum(value < log(9 / 10)), 
+                                total = malebias + femalebias,
+                                malepercent = malebias * 100 / total, 
+                                femalepercent = femalebias * 100 / total)
+
+meta.plot2.over10.c$label <- "Sex difference in m/f ratios > 10%"
+
+# restructure to create stacked bar plots
+
+meta.plot2.over10.c <- as.data.frame(meta.plot2.over10.c)
+meta.plot2.over10.d <- gather(meta.plot2.over10.c, key = sex, value = percent, malepercent:femalepercent, factor_key = TRUE)
+
+# create new sample size variable
+
+meta.plot2.over10.d$samplesize <- with(meta.plot2.over10.d, ifelse(sex == "malepercent", malebias, femalebias))
+
+# Add summary row ('All') and re-arrange rows into correct order for plotting (warnings about coercing 'id' into character vector are ok)
+
+meta.plot2.over10.e <- meta.plot2.over10.d %>% 
+                      group_by(trait, sex) %>% 
+                      summarise(GroupingTerm = "All", malebias = sum(malebias), 
+                                femalebias = sum(femalebias), 
+                                total = malebias + femalebias, 
+                                label = "Sex difference in m/f ratios > 10%", 
+                                samplesize = sum(samplesize)) %>%
+                      mutate(percent = ifelse(sex == "femalepercent", 
+                                              femalebias*100/(malebias + femalebias), 
+                                              malebias*100/(malebias + femalebias))) %>%
+                      bind_rows(meta.plot2.over10.d, .) %>%
+                      mutate(rownumber = row_number()) %>%
+                      .[c(55, 1:9, 57, 10:18, 59, 19:27, 56, 28:36, 58, 37:45, 60, 46:54), ]
+
+meta.plot2.over10.e$GroupingTerm <- factor(meta.plot2.over10.e$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
+meta.plot2.over10.e$GroupingTerm <- factor(meta.plot2.over10.e$GroupingTerm, rev(levels(meta.plot2.over10.e$GroupingTerm)))
+
+# PLOT:  Fig2 Sex difference in m/f ratio > 10% (Fig S2 A, lower panel)
+
+malebias_Fig2_over10 <-
+  ggplot(meta.plot2.over10.e) +
+  aes(x = GroupingTerm, y = percent, fill = sex) +
+  ylab("Percentage") +
+  geom_col() +
+  geom_hline(yintercept = 50, linetype = "dashed", color = "gray40") +
+  geom_text(
+    data = subset(meta.plot2.over10.e, samplesize != 0), aes(label = samplesize), position = position_stack(vjust = .5),
+    color = "white", size = 3.5
+  ) +
+  facet_grid(
+    cols = vars(trait), rows = vars(label), labeller = label_wrap_gen(width = 18),
+    scales = "free", space = "free"
+  ) +
+  scale_fill_brewer(palette = "Set2") +
+  theme_bw(base_size = 18) +
+  theme(
+    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
+    strip.text.x = element_blank(),
+    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
+    text = element_text(size = 14),
+    panel.spacing = unit(0.5, "lines"),
+    panel.border = element_blank(),
+    axis.line = element_line(),
+    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
+    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
+    panel.grid.minor.y = element_blank(),
+    panel.grid.minor.x = element_blank(),
+    legend.position = "none",
+    #axis.title.x = element_blank(),
+    axis.title.y = element_blank()
+  ) +
+  coord_flip()
+
+# malebias_Fig2_over10  (supplemental Figure S2 A)
+```
+
+```{r FigS2_B, eval = TRUE, echo = FALSE}
+
+#### 3.2: Preparation for Figure S2 B (second-order meta-analysis)
+#### 3.3: Female Figure, significant and highly biased traits (Figure S2 B, left hand side panels)
+#Preparing data for traits with CI not overlapping 0: 
+#create column with 1= different from zero, 0= zero included in CI (for Figure S2 B, top left panel)
+
+#Restructure data for plotting
+
+overall3.female.sigS <- gather(overall.female.plot3, parameter, value, c(lnCVR, lnVR, lnRR), factor_key = TRUE)
+
+lnCVR.ci <- overall3.female.sigS %>%
+  filter(parameter == "lnCVR") %>%
+  mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
+lnVR.ci <- overall3.female.sigS %>%
+  filter(parameter == "lnVR") %>%
+  mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
+lnRR.ci <- overall3.female.sigS %>%
+  filter(parameter == "lnRR") %>%
+  mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
+
+overall4.female.sigS <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
+
+overall4.female.sigS$label <- "CI not overlapping zero"
+
+# PLOT female-bias:  significant traits
+
+Metameta_FigS2_female.sig <- overall4.female.sigS %>%
+  ggplot(aes(y = GroupingTerm, x = value)) +
+  geom_errorbarh(aes(
+    xmin = ci.low,
+    xmax = ci.high
+  ),
+  height = 0.1, show.legend = FALSE
+  ) +
+  geom_point(aes(shape = parameter),
+    fill = "salmon1", color = "salmon1", size = 2.2,
+    show.legend = FALSE
+  ) +
+  scale_x_continuous(
+    limits = c(-0.4, 0),
+    breaks = c(-0.3, 0),
+    name = "Effect size"
+  ) +
+  geom_vline(
+    xintercept = 0,
+    color = "black",
+    linetype = "dashed"
+  ) +
+  facet_grid(
+    cols = vars(parameter), # rows = vars(label),
+    # labeller = label_wrap_gen(width = 23),
+    scales = "free",
+    space = "free"
+  ) +
+  theme_bw() +
+  theme(
+    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
+    strip.text.x = element_text(size = 12),
+    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
+    text = element_text(size = 14),
+    panel.spacing = unit(0.5, "lines"),
+    panel.border = element_blank(),
+    axis.line = element_line(),
+    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
+    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
+    panel.grid.minor.y = element_blank(),
+    panel.grid.minor.x = element_blank(),
+    legend.title = element_blank(),
+    axis.title.x = element_blank(),
+    axis.title.y = element_blank()
+  )
+
+# Metameta_FigS2_female.sig
+
+#### Prepare data for traits with m/f difference > 10%, Female bias (Figure S2 B, bottom left)
+
+meta.plot3.perc <- metacombo %>%
+  mutate(
+    percCVR = ifelse(lnCVR < log(9 / 10), 1, 0),
+    percVR = ifelse(lnVR < log(9 / 10), 1, 0),
+    percRR = ifelse(lnRR < log(9 / 10), 1, 0)
+  )
+
+# Significant subset for lnCVR
+metacombo_plot3.CVR.perc <- meta.plot3.perc %>%
+  filter(percCVR == 1) %>%
+  group_by(GroupingTerm) %>%
+  nest()
+
+metacombo_plot3.CVR.perc.all <- meta.plot3.perc %>%
+  filter(percCVR == 1) %>%
+  nest(data = everything())
+
+# Significant subset for lnVR
+metacombo_plot3.VR.perc <- meta.plot3.perc %>%
+  filter(percVR == 1) %>%
+  group_by(GroupingTerm) %>%
+  nest()
+
+metacombo_plot3.VR.perc.all <- meta.plot3.perc %>%
+  filter(percVR == 1) %>%
+  nest(data = everything())
+
+# Significant subset for lnRR
+metacombo_plot3.RR.perc <- meta.plot3.perc %>%
+  filter(percRR == 1) %>%
+  group_by(GroupingTerm) %>%
+  nest()
+
+metacombo_plot3.RR.perc.all <- meta.plot3.perc %>%
+  filter(percRR == 1) %>%
+  nest(data = everything())
+
+# **Final fixed effects meta-analyses within grouping terms, with SE of the estimate
+
+plot3.meta.CVR.perc <- metacombo_plot3.CVR.perc %>%
+  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+plot3.meta.VR.perc <- metacombo_plot3.VR.perc %>%
+  mutate(model_lnVR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+plot3.meta.RR.perc <- metacombo_plot3.RR.perc %>%
+  mutate(model_lnRR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+# Across all grouping terms #
+
+plot3.meta.CVR.perc.all <- metacombo_plot3.CVR.perc.all %>%
+  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+plot3.meta.CVR.perc.all <- plot3.meta.CVR.perc.all %>% mutate(GroupingTerm = "All")
+
+plot3.meta.VR.perc.all <- metacombo_plot3.VR.perc.all %>%
+  mutate(model_lnVR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+plot3.meta.VR.perc.all <- plot3.meta.VR.perc.all %>% mutate(GroupingTerm = "All")
+
+plot3.meta.RR.perc.all <- metacombo_plot3.RR.perc.all %>%
+  mutate(model_lnRR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+plot3.meta.RR.perc.all <- plot3.meta.RR.perc.all %>% mutate(GroupingTerm = "All")
+
+# Combine with separate grouping term results
+
+plot3.meta.CVR.perc <- bind_rows(plot3.meta.CVR.perc, plot3.meta.CVR.perc.all)
+plot3.meta.VR.perc <- bind_rows(plot3.meta.VR.perc, plot3.meta.VR.perc.all)
+plot3.meta.RR.perc <- bind_rows(plot3.meta.RR.perc, plot3.meta.RR.perc.all)
+
+# **Re-structure data for each grouping term; delete un-used variables: "Hearing missing for all 3 parameters"
+
+plot3.meta.CVR.perc.b <- as.data.frame(plot3.meta.CVR.perc %>% group_by(GroupingTerm) %>%
+  mutate(
+    lnCVR = map_dbl(model_lnCVR, pluck(2)), lnCVR_lower = map_dbl(model_lnCVR, pluck(6)),
+    lnCVR_upper = map_dbl(model_lnCVR, pluck(7)), lnCVR_se = map_dbl(model_lnCVR, pluck(3))
+  ))[, c(1, 4:7)]
+add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.meta.CVR.perc.b))
+plot3.meta.CVR.perc.b <- rbind(plot3.meta.CVR.perc.b, add.row.hearing)
+plot3.meta.CVR.perc.b <- plot3.meta.CVR.perc.b[order(plot3.meta.CVR.perc.b$GroupingTerm), ]
+
+plot3.meta.VR.perc.b <- as.data.frame(plot3.meta.VR.perc %>% group_by(GroupingTerm) %>%
+  mutate(
+    lnVR = map_dbl(model_lnVR, pluck(2)), lnVR_lower = map_dbl(model_lnVR, pluck(6)),
+    lnVR_upper = map_dbl(model_lnVR, pluck(7)), lnVR_se = map_dbl(model_lnVR, pluck(3))
+  ))[, c(1, 4:7)]
+add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.meta.VR.perc.b))
+plot3.meta.VR.perc.b <- rbind(plot3.meta.VR.perc.b, add.row.hearing)
+plot3.meta.VR.perc.b <- plot3.meta.VR.perc.b[order(plot3.meta.VR.perc.b$GroupingTerm), ]
+
+plot3.meta.RR.perc.b <- as.data.frame(plot3.meta.RR.perc %>% group_by(GroupingTerm) %>%
+  mutate(
+    lnRR = map_dbl(model_lnRR, pluck(2)), lnRR_lower = map_dbl(model_lnRR, pluck(6)),
+    lnRR_upper = map_dbl(model_lnRR, pluck(7)), lnRR_se = map_dbl(model_lnRR, pluck(3))
+  ))[, c(1, 4:7)]
+add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.meta.RR.perc.b))
+plot3.meta.RR.perc.b <- rbind(plot3.meta.RR.perc.b, add.row.hearing)
+add.row.hematology <- as.data.frame(t(c("Hematology", NA, NA, NA, NA))) %>%
+  setNames(names(plot3.meta.RR.perc.b))
+plot3.meta.RR.perc.b <- rbind(plot3.meta.RR.perc.b, add.row.hematology)
+
+plot3.meta.RR.perc.b <- plot3.meta.RR.perc.b[order(plot3.meta.RR.perc.b$GroupingTerm), ]
+
+plot3.meta.CVR.perc.c <- full_join(plot3.meta.CVR.perc.b, plot3.meta.VR.perc.b)
+overall.plot3.perc <- full_join(plot3.meta.CVR.perc.c, plot3.meta.RR.perc.b)
+
+overall.plot3.perc$GroupingTerm <- factor(overall.plot3.perc$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
+overall.plot3.perc$GroupingTerm <- factor(overall.plot3.perc$GroupingTerm, rev(levels(overall.plot3.perc$GroupingTerm)))
+
+# Restructure data for plotting
+# Female bias, 10 percent difference
+
+overall3.perc <- gather(overall.plot3.perc, parameter, value, c(lnCVR, lnVR, lnRR), factor_key = TRUE)
+
+lnCVR.ci <- overall3.perc %>%
+  filter(parameter == "lnCVR") %>%
+  mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
+lnVR.ci <- overall3.perc  %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
+lnRR.ci <- overall3.perc %>%
+  filter(parameter == "lnRR") %>%
+  mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
+
+overall4.perc <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
+
+overall4.perc$label <- "Sex difference in m/f ratios > 10%"
+
+overall4.perc$value <- as.numeric(overall4.perc$value)
+overall4.perc$ci.low <- as.numeric(overall4.perc$ci.low)
+overall4.perc$ci.high <- as.numeric(overall4.perc$ci.high)
+
+# Plot FigS2 all >10% difference (female)
+# Figure S2B, bottom left
+
+Metameta_Fig3_female.perc <- overall4.perc %>%
+  ggplot(aes(y = GroupingTerm, x = value)) +
+  geom_errorbarh(aes(
+    xmin = ci.low,
+    xmax = ci.high
+  ),
+  height = 0.1, show.legend = FALSE
+  ) +
+  geom_point(aes(shape = parameter),
+    fill = "salmon1", color = "salmon1", size = 2.2,
+    show.legend = FALSE
+  ) +
+
+  # scale_shape_manual(values =
+
+  scale_x_continuous(
+    limits = c(-0.53, 0.2),
+    breaks = c(-0.3, 0),
+    name = "Effect size"
+  ) +
+  geom_vline(
+    xintercept = 0,
+    color = "black",
+    linetype = "dashed"
+  ) +
+  facet_grid(
+    cols = vars(parameter), # rows = vars(label),
+    # labeller = label_wrap_gen(width = 23),
+    scales = "free",
+    space = "free"
+  ) +
+  theme_bw() +
+  theme(
+    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
+    strip.text.x = element_blank(),
+    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
+    text = element_text(size = 14),
+    panel.spacing = unit(0.5, "lines"),
+    panel.border = element_blank(),
+    axis.line = element_line(),
+    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
+    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
+    panel.grid.minor.y = element_blank(),
+    panel.grid.minor.x = element_blank(),
+    legend.title = element_blank(),
+    axis.title.x = element_text(hjust = 0.5, size = 14),
+    axis.title.y = element_blank()
+  )
+
+# Metameta_Fig3_female.perc (Figure S2 bottom left panel)
+```
+
+```{r FigS2_B_right, eval = TRUE, echo = FALSE}
+#### 3.4: Male Figure, significant and highly biased traits (Figure S2 B, right hand side panels)
+#Restructuring data with significant male bias (for Figure S2 B, top right panel)
+
+overall3.male.sigS <- gather(overall.male.plot3, parameter, value, c(lnCVR, lnVR, lnRR), factor_key = TRUE)
+
+lnCVR.ci <- overall3.male.sigS %>%
+  filter(parameter == "lnCVR") %>%
+  mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
+lnVR.ci <- overall3.male.sigS %>%
+  filter(parameter == "lnVR") %>%
+  mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
+lnRR.ci <- overall3.male.sigS %>%
+  filter(parameter == "lnRR") %>%
+  mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
+
+overall4.male.sigS <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
+
+overall4.male.sigS$label <- "CI not overlapping zero"
+
+# Plot FigS2 all significant results (CI not overlapping zero, male )
+
+Metameta_FigS2_male.sig <- overall4.male.sigS %>%
+  ggplot(aes(y = GroupingTerm, x = value)) +
+  geom_errorbarh(aes(
+    xmin = ci.low,
+    xmax = ci.high
+  ),
+  height = 0.1, show.legend = FALSE
+  ) +
+  geom_point(aes(shape = parameter),
+    fill = "mediumaquamarine", color = "mediumaquamarine", size = 2.2,
+    show.legend = FALSE
+  ) +
+  scale_x_continuous(
+    limits = c(0, 0.4),
+    breaks = c(0, 0.3),
+    name = "Effect size"
+  ) +
+  geom_vline(
+    xintercept = 0,
+    color = "black",
+    linetype = "dashed"
+  ) +
+  facet_grid(
+    cols = vars(parameter), rows = vars(label),
+    labeller = label_wrap_gen(width = 23),
+    scales = "free",
+    space = "free"
+  ) +
+  theme_bw() +
+  theme(
+    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
+    strip.text.x = element_text(size = 12),
+    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
+    text = element_text(size = 14),
+    panel.spacing = unit(0.5, "lines"),
+    panel.border = element_blank(),
+    axis.line = element_line(),
+    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
+    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
+    panel.grid.minor.y = element_blank(),
+    panel.grid.minor.x = element_blank(),
+    legend.title = element_blank(),
+    axis.title.x = element_blank(),
+    axis.title.y = element_blank()
+  )
+
+# Metameta_FigS2_male.sig
+
+## Prepare data for traits with m/f difference > 10%. Male bias
+### Create column with 1= larger, 0= difference not larger than 10% between male/female ratios
+
+meta.male.plot3.perc <- metacombo %>%
+  mutate(
+    percCVR = ifelse(lnCVR > log(11 / 10), 1, 0),
+     percVR = ifelse( lnVR > log(11 / 10), 1, 0),
+     percRR = ifelse( lnRR > log(11 / 10), 1, 0)
+  )
+
+# Significant subset for lnCVR
+metacombo_male.plot3.CVR.perc <- meta.male.plot3.perc %>%
+                                filter(percCVR == 1) %>%
+                                group_by(GroupingTerm) %>%
+                                nest()
+
+metacombo_male.plot3.CVR.perc.all <- meta.male.plot3.perc %>%
+                filter(percCVR == 1) %>%
+  nest(data = everything())
+
+# Significant subset for lnVR
+metacombo_male.plot3.VR.perc <- meta.male.plot3.perc %>%
+  filter(percVR == 1) %>%
+  group_by(GroupingTerm) %>%
+  nest()
+
+metacombo_male.plot3.VR.perc.all <- meta.male.plot3.perc %>%
+  filter(percVR == 1) %>%
+  nest(data = everything())
+
+# Significant subset for lnRR
+metacombo_male.plot3.RR.perc <- meta.male.plot3.perc %>%
+  filter(percRR == 1) %>%
+  group_by(GroupingTerm) %>%
+  nest()
+
+metacombo_male.plot3.RR.perc.all <- meta.male.plot3.perc %>%
+  filter(percRR == 1) %>%
+  nest(data = everything())
+
+# Final fixed effects meta-analyses within grouping terms and across grouping terms, with SE of the estimate
+
+plot3.male.meta.CVR.perc <- metacombo_male.plot3.CVR.perc %>%
+  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+plot3.male.meta.VR.perc <- metacombo_male.plot3.VR.perc %>%
+  mutate(model_lnVR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+plot3.male.meta.RR.perc <- metacombo_male.plot3.RR.perc %>%
+  mutate(model_lnRR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+# Across all grouping terms
+
+plot3.male.meta.CVR.perc.all <- metacombo_male.plot3.CVR.perc.all %>%
+  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+plot3.male.meta.CVR.perc.all <- plot3.male.meta.CVR.perc.all %>% mutate(GroupingTerm = "All")
+
+plot3.male.meta.VR.perc.all <- metacombo_male.plot3.VR.perc.all %>%
+  mutate(model_lnVR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+plot3.male.meta.VR.perc.all <- plot3.male.meta.VR.perc.all %>% mutate(GroupingTerm = "All")
+
+plot3.male.meta.RR.perc.all <- metacombo_male.plot3.RR.perc.all %>%
+  mutate(model_lnRR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+plot3.male.meta.RR.perc.all <- plot3.male.meta.RR.perc.all %>% mutate(GroupingTerm = "All")
+
+# Combine with separate grouping term results
+
+plot3.male.meta.CVR.perc <- bind_rows(plot3.male.meta.CVR.perc, plot3.male.meta.CVR.perc.all)
+plot3.male.meta.VR.perc <- bind_rows(plot3.male.meta.VR.perc, plot3.male.meta.VR.perc.all)
+plot3.male.meta.RR.perc <- bind_rows(plot3.male.meta.RR.perc, plot3.male.meta.RR.perc.all)
+
+# **Re-structure data for each grouping term; delete un-used variables: "Hearing missing for all 3 parameters"
+
+plot3.male.meta.CVR.perc.b <- as.data.frame(plot3.male.meta.CVR.perc %>% group_by(GroupingTerm) %>%
+  mutate(
+    lnCVR = map_dbl(model_lnCVR, pluck(2)), lnCVR_lower = map_dbl(model_lnCVR, pluck(6)),
+    lnCVR_upper = map_dbl(model_lnCVR, pluck(7)), lnCVR_se = map_dbl(model_lnCVR, pluck(3))
+  ))[, c(1, 4:7)]
+add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.male.meta.CVR.perc.b))
+plot3.male.meta.CVR.perc.b <- rbind(plot3.male.meta.CVR.perc.b, add.row.hearing)
+plot3.male.meta.CVR.perc.b <- plot3.male.meta.CVR.perc.b[order(plot3.male.meta.CVR.perc.b$GroupingTerm), ]
+
+plot3.male.meta.VR.perc.b <- as.data.frame(plot3.male.meta.VR.perc %>% group_by(GroupingTerm) %>%
+  mutate(
+    lnVR = map_dbl(model_lnVR, pluck(2)), lnVR_lower = map_dbl(model_lnVR, pluck(6)),
+    lnVR_upper = map_dbl(model_lnVR, pluck(7)), lnVR_se = map_dbl(model_lnVR, pluck(3))
+  ))[, c(1, 4:7)]
+add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.male.meta.VR.perc.b))
+plot3.male.meta.VR.perc.b <- rbind(plot3.male.meta.VR.perc.b, add.row.hearing)
+plot3.male.meta.VR.perc.b <- plot3.male.meta.VR.perc.b[order(plot3.male.meta.VR.perc.b$GroupingTerm), ]
+
+plot3.male.meta.RR.perc.b <- as.data.frame(plot3.male.meta.RR.perc %>% group_by(GroupingTerm) %>%
+  mutate(
+    lnRR = map_dbl(model_lnRR, pluck(2)), lnRR_lower = map_dbl(model_lnRR, pluck(6)),
+    lnRR_upper = map_dbl(model_lnRR, pluck(7)), lnRR_se = map_dbl(model_lnRR, pluck(3))
+  ))[, c(1, 4:7)]
+add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>%
+  setNames(names(plot3.male.meta.RR.perc.b))
+plot3.male.meta.RR.perc.b <- rbind(plot3.male.meta.RR.perc.b, add.row.hearing)
+
+add.row.eye <- as.data.frame(t(c("Eye", NA, NA, NA, NA))) %>%
+  setNames(names(plot3.male.meta.RR.perc.b))
+plot3.male.meta.RR.perc.b <- rbind(plot3.male.meta.RR.perc.b, add.row.eye)
+
+plot3.male.meta.RR.perc.b <- plot3.male.meta.RR.perc.b[order(plot3.male.meta.RR.perc.b$GroupingTerm), ]
+
+plot3.male.meta.CVR.Vr.perc <- full_join(plot3.male.meta.CVR.perc.b, plot3.male.meta.VR.perc.b)
+overall.male.plot3.perc <- full_join(plot3.male.meta.CVR.Vr.perc, plot3.male.meta.RR.perc.b)
+
+overall.male.plot3.perc$GroupingTerm <- factor(overall.male.plot3.perc$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
+overall.male.plot3.perc$GroupingTerm <- factor(overall.male.plot3.perc$GroupingTerm, rev(levels(overall.male.plot3.perc$GroupingTerm)))
+
+# Restructure data for plotting : Male biased, 10% difference
+
+overall3.perc <- gather(overall.male.plot3.perc, parameter, value, c(lnCVR, lnVR, lnRR), factor_key = TRUE)
+
+lnCVR.ci <- overall3.perc %>%
+  filter(parameter == "lnCVR") %>%
+  mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
+lnVR.ci <- overall3.perc  %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
+lnRR.ci <- overall3.perc %>%
+  filter(parameter == "lnRR") %>%
+  mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
+
+overall4.male.perc <- bind_rows(lnCVR.ci,lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
+
+overall4.male.perc$label <- "Sex difference in m/f ratios > 10%"
+
+overall4.male.perc$value <- as.numeric(overall4.male.perc$value)
+overall4.male.perc$ci.low <- as.numeric(overall4.male.perc$ci.low)
+overall4.male.perc$ci.high <- as.numeric(overall4.male.perc$ci.high)
+
+# Plot Fig S2 all >10% difference (male bias)
+# S2 B, bottom right
+
+Metameta_Fig3_male.perc <- overall4.male.perc %>% # filter(., GroupingTerm != "Hearing") %>%
+  ggplot(aes(y = GroupingTerm, x = value)) +
+  geom_errorbarh(aes(
+    xmin = ci.low,
+    xmax = ci.high
+  ),
+  height = 0.1, show.legend = FALSE
+  ) +
+  geom_point(aes(
+    shape = parameter,
+    fill = parameter
+  ),
+  color = "mediumaquamarine", size = 2.2,
+  show.legend = FALSE
+  ) +
+  scale_x_continuous(
+    limits = c(-0.2, 0.62),
+    breaks = c(0, 0.3),
+    name = "Effect size"
+  ) +
+  geom_vline(
+    xintercept = 0,
+    color = "black",
+    linetype = "dashed"
+  ) +
+  facet_grid(
+    cols = vars(parameter), rows = vars(label),
+    labeller = label_wrap_gen(width = 23),
+    scales = "free",
+    space = "free"
+  ) +
+  theme_bw() +
+  theme(
+    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
+    strip.text.x = element_blank(),
+    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
+    text = element_text(size = 14),
+    panel.spacing = unit(0.5, "lines"),
+    panel.border = element_blank(),
+    axis.line = element_line(),
+    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
+    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
+    panel.grid.minor.y = element_blank(),
+    panel.grid.minor.x = element_blank(),
+    legend.title = element_blank(),
+    axis.title.x = element_text(hjust = 0.5, size = 14),
+    axis.title.y = element_blank()
+  )
+
+# Metameta_Fig3_male.perc (Figure S2 right panel)
+```
+
+## Figure 5.1
+Figure \@ref(fig:FigS1) is similar to Figure 3 in the main article except that lnVR has been added to the plot for comparison with lnCVR and lnRR.
+
+```{r FigS1, fig.height = 8, fig.width = 7, fig.cap=" Numbers of either male (blue-green bars) or female (orange-red bars) biased traits  (Panel A) across functional groups, this time for lnCVR (left hand side), lnVR (middle) and lnRR (right hand side).
+Panel B shows effect sizes from separate meta-analysis for each functional group, and Panel C contains results of heterogeneity analyses.
+All three panels represent results evaluated across all traits."}
+
+#### Combined Figure S1: overall Count data, Meta anlysis results, Heterogeneity
+
+FigS1 <- ggarrange(malebias_FigS1_alltraits, Metameta_FigS1_alltraits, HeteroS1, nrow = 3, align = "v", heights = c(1.1, 1, 1), labels = c("A", "B", "C"))
+FigS1
+#ggsave("FigS1_OverallResults.pdf", plot = FigS1, width = 6, height = 7)
+```
+
+## Figure 5.2
+
+### Sex-bias in traits sub-analysis
+
+#### Methods
+Among the 147 traits (i.e.
+with ‘first-order’ meta-analytic results), we found 31 traits to be significantly male-biased and 30 female-biased for lnCVR (47 male-biased and 39 female- biased for lnRR; 74 male and 55 female-biased for lnVR).
+We used this statistical significance to categorize traits into two groups: male-based and female-biased traits.
+For each set of these sex-biased traits, we conducted second-order meta-analyses with trait as the unit of analysis in the same way as those using lnRR, lnVR and lnCVR (Figure \@ref(fig:FigG1)J).
+As sensitivity analyses, we also employed another way of separating male- and female-biased traits.
+We quantified traits that were more than 10% biased towards either of the sexes, regardless of significance (N[male-biased] = 31, & N[female-biased] = 36 for lnCVR,  N[male-biased] = 56, & N[female-biased] = 57 for lnVR , N[male-biased] = 42, & N[female-biased] = 33  for lnRR; see Supplemental Figure S\@ref(fig:FigS2), Supplemental Table 7.3).
+
+#### Results
+Having established that different sex-biases were present across trait functional groups, we explored specific patterns in male and female bias by categorizing traits into either male or female-biased, and then, quantifying the degree of sex bias.
+To do this, we focused on only those traits that were significantly biased towards one sex (as indicated by “CI not overlapping 0” in Figure S\@ref(fig:FigS2).
+Selecting significantly sex-biased traits reduced the number of traits substantially (Figure S\@ref(fig:FigS2)A; compared to all traits, Figure \@ref(fig:Fig3) and Figure \@ref(fig:FigS1)), and returned similar numbers of traits with either significant male- or female-bias for lnCVR (Figure S\@ref(fig:FigS2)A).
+
+Looking only at traits with significant male-bias, trait variability tended to be higher in males than in females overall (11.77% male bias, lnCVR = 0.111, CI = [0.093 to 0.129]; compared to 8.3% female-bias, lnCVR = -0.087, CI = [-0.109 to (-0.064)]; Figure S\@ref(fig:FigS2)B).
+The degree of sex-bias varied across the functional trait groups, ranging from 4.6 % (Physiology, lnCVR = -0.047, CI = [-0.064 to (-0.030)] to 15.13 % (Eye morphology, lnCVR = -0.164, CI = [-0.249 to (-0.250)] in females, and from 8.6 % (Hematology, lnCVR = 0.082, CI = [0.048 to 0.117]) and 16.66 % (Heart, lnCVR = 0.154, CI = [0.085 to 0.223]) in males (Figure S\@ref(fig:FigS2)B).
+
+To put sex biases (sexual dimorphisms) in variability into perspective, we also quantify the degree of sexual dimorphism in significantly sex-biased traits (i.e., the extent of sexual dimorphisms).
+There were more traits that were significantly biased in mean trait value in males compared to females (Figure S\@ref(fig:FigS2)A, lnRR).
+These traits were 11.73 % biased towards males (Figure S\@ref(fig:FigS2)B; lnRR = 0.111, CI = [0.083 – 0.138]) while 9.38 % towards females (lnRR = -0.094, CI = [-0.129 – (-0.068)].
+The overall pattern for lnRR was more varied among the functional trait groups than for lnCVR, ranging from 1.2% (Hematology, lnRR = -0.013, CI = [-0.017 – (-0.007)] to 14.72 % (Immunology, lnRR = -0.159, CI = [-0.229 – (-0.089)] in female-based traits (Figure S\@ref(fig:FigS2)B) whereas in males-based traits from 1.8 % (Hearing, lnRR = 0.018, CI = [0.006 – 0.031]) to 25 % (Metabolism, lnRR = 0.223, CI = [0.110 – 0.335])  (Figure S\@ref(fig:FigS2)B).
+
+```{r FigS2, fig.height = 10, fig.width = 8, fig.cap=" A) Differences in numbers of affected traits, in variance (lnCVR and lnVR) and means (lnRR), where there’s a significant difference between the sexes (i.e CI not overlapping zero), and where the sex bias is greater than 10% difference (regardless of significance).
+Panel B depicts results for the sex bias in those traits that differ between the sexes (second-order meta-analysis).
+Triangles represent sex bias in means (response ratio) and black circles differences in the coefficient of variation ratio (mean-adjusted variability).
+The orange-red bars represent trait groups with a female bias, blue-green bars male-biased traits."}
+library(ggpubr)
+FigS2b <- ggarrange(Metameta_FigS2_female.sig, Metameta_FigS2_male.sig,
+  ncol = 2, nrow = 1, widths = c(1, 1.30), heights = c(1.2, 1.2))
+
+FigS2d <- ggarrange(Metameta_Fig3_female.perc, Metameta_Fig3_male.perc,
+  ncol = 2, nrow = 1, widths = c(1, 1.20), heights = c(1.1, 1.1))
+
+# end combination Figure 5
+FigS2 <- ggarrange(malebias_FigS2_sigtraits, malebias_Fig2_over10, FigS2b, FigS2d, ncol = 1, nrow = 4, heights = c(2.5, 2.2, 2.1, 2), labels = c("A", " ", "B", " "))
+FigS2
+```
+
+# Supplemental Tables
+## Table 6.1
+
 ```{r Table1_prep, echo = FALSE, eval = TRUE, results='hide'}
@@
 
+  #PDF
  pander(ST1, caption = "Table 6.1: Summary of the available numbers of male and female mice from each strain and originating institution.")
-
+  #HTML
     #kable(ST1, caption = "Summary of the available numbers of male and female mice from each strain and originating institution.") %>%
     #kable_styling() %>%
-    #pander()
     #scroll_box(width = "100%", height = "200px")
@@
 
-## Table
+## Table 6.2
 
@@
 
+#PDF
 pander(cbind(meta1 %>% count(parameter_group)), caption = "Table 6.2: Trait categories (parameter_group) and the number of correlated traits within these categories.
@@
 
-## Table
+## Table 6.3
 
@@
 
+# PDF
 pander(metacombo, caption = "Table 6.3: We use this corrected (for correlated traits) results table, which contains each of the meta-analytic means for all effect sizes of interest, for further analyses.
@@
 
+#HTML
 #kable(metacombo, digits = 3, caption = "We use this corrected (for correlated traits) results table, which contains each of the meta-analytic means for all effect sizes of interest, for further analyses.
@@
 
-## Table
+## Table 6.4
 
@@
 
+#PDF
 pander(overall2, caption = "Table 6.4: Summary of overall meta-analyses on the functional trait group level (GroupingTerm).
@@
 
+#HTML
 #kable(overall2, digits = 3, caption = "Summary of overall meta-analyses on the functional trait group level (GroupingTerm).
 Results for lnCVR, lnVR and lnRR and their respective upper and lower 95 percent CI's, standard error and I2 values are provided.") %>%
- #  kable_styling() %>%
-#  scroll_box(width = "100%", height = "200px")
-```
-
-## Table
+#kable_styling() %>%
+#scroll_box(width = "100%", height = "200px")
+```
+
+## Table 6.5
 
@@
 
+        #PDF
     pander(mf_sig, caption = "Table 6.5: Provides an overview of meta-analysis results performed on traits that were significantly biased towards either sex.
 This table summarizes findings for both sexes and the respective functional trait groups.")
-
+      #HTML
   #kable(mf_sig, digits = 3, caption = "Provides an overview of meta-analysis results performed on traits that were significantly biased towards either sex.
 This table summarizes findings for both sexes and the respective functional trait groups.") %>%
-   # kable_styling() %>%
-  # scroll_box(width = "100%", height = "300px")
-```
-
-## Table
+  #kable_styling() %>%
+  #scroll_box(width = "100%", height = "300px")
+```
+
+## Table 6.6
 
@@
 
+  # PDF
   pander(het, caption = "Table 6.6: Summarizes our findings on heterogeneity due to institutions and mouse strains.
@@
 
+  # HTML
   #kable(het, digits = 3, caption = "Summarizes our findings on heterogeneity due to institutions and mouse strains.
 These results are based on meta-analyses on sigma^2 and errors for mouse strains and centers (Institutions), following the identical workflow from above.") %>%
-   # kable_styling() %>%
+   #kable_styling() %>%
     #scroll_box(width = "100%", height = "200px")

### 2020-05-21 scripts/MouseSexDiffApril20_2020.Rmd
Added new word yaml for bookdown; renders it much closer to html and just some manually tweaking to match legend names

@@
 output:
+  bookdown::word_document2:
+    toc: yes
+    toc_depth: 6
+    number_sections: true
+    theme: flatly
   bookdown::pdf_document2:

### 2020-08-25 scripts/MouseSexDiffVar_05_2020.Rmd

--- 2020-05-19 scripts/MouseSexDiffApril20_2020.Rmd
@@
 output:
+  html_document:
+    df_print: paged
+    toc: yes
+    toc_depth: '4'
   bookdown::pdf_document2:
@@
     toc_float: yes
-  html_document:
-    df_print: paged
+  bookdown::word_document2:
     toc: yes
-    toc_depth: '4'
+    toc_depth: 6
+    number_sections: true
+    theme: flatly
 subtitle: Electronic Supplementary Material

### 2020-09-08 scripts/MouseSexDiffVar_05_2020.Rmd
Added some ne descriptive stats to the very first trait based 218 meta-analysis table. Just added rows. Problems rendering though in places of script that I've not touched. Not sure whats up L2647 mark

--- 2020-05-19 scripts/MouseSexDiffApril20_2020.Rmd
@@
 output:
+  bookdown::html_document2:
+    code_folding: hide
+    number_sections: yes
+    theme: flatly
+    toc: yes
+    toc_depth: 6
+    toc_float: yes
   bookdown::pdf_document2:
@@
     toc: yes
-  bookdown::html_document2:
-    code_folding: hide
-    number_sections: yes
-    theme: flatly
-    toc: yes
-    toc_depth: 6
-    toc_float: yes
   html_document:
@@
     toc_depth: '4'
+  bookdown::word_document2:
+    toc: yes
+    toc_depth: 6
+    number_sections: true
+    theme: flatly
 subtitle: Electronic Supplementary Material
@@
 
-```{r packages1, echo = FALSE, eval = TRUE, messages = FALSE}
+```{r packages1, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE, messages=FALSE, paged.print=FALSE}
 library(pacman)
@@
     data.frame(tibble(id = 1:n, 
-           lnCVR=0, lnCVR_lower=0, lnCVR_upper=0, lnCVR_se=0, 
-            lnVR=0,  lnVR_lower=0,  lnVR_upper=0, lnVR_se=0, 
-            lnRR=0,  lnRR_lower=0,  lnRR_upper=0, lnRR_se=0, 
-           sampleSize=0, trait=0))
+           lnCVR=0, lnCVR_lower=0, lnCVR_upper=0, lnCVR_se=0, lnCVR_I2=0,
+            lnVR=0,  lnVR_lower=0,  lnVR_upper=0, lnVR_se=0, lnVR_I2=0,
+            lnRR=0,  lnRR_lower=0,  lnRR_upper=0, lnRR_se=0, lnRR_I2=0,
+           k=0, trait=0, male_N = 0, female_N=0, min_male_N = 0, max_male_N = 0, mean_male_N = 0,
+              min_female_N = 0, max_female_N = 0, mean_female_N = 0))
 
@@
 
-      results_alltraits_grouping[t, 2:14] <- c(f(cvr), f(cv), f(means), k=means$k)
-      results_alltraits_grouping[t, 15]   <- unique(results$trait)
+      extract_I2 <- function(mod){
+                  sigma2 <- mod$sigma2
+                       w <- mod$vi
+                       k <- mod$k
+
+                  sigmaM <- sum(w * (k-1)) / (sum(w)^2 - sum(w^2))
+
+                    I2_tot <- round(sum(sigma2) / sum(sigma2 + sigmaM), digits = 3)*100
+                  return(I2_tot)
+      }
+
+      results_alltraits_grouping[t, c(2:17,19:26)] <- c(f(cvr),lnCVR_I2 = extract_I2(cvr), f(cv), lnVR_I2 = extract_I2(cv), f(means), lnRR_I2 = extract_I2(means), k=means$k, male_N = sum(results$male_n_ind), female_N = sum(results$female_n_ind), min_male_N = min(results$male_n_ind), max_male_N = max(results$male_n_ind), mean_male_N = mean(results$male_n_ind),
+                                                        min_female_N = min(results$female_n_ind), max_female_N = max(results$female_n_ind), mean_female_N = mean(results$female_n_ind))
+      results_alltraits_grouping[t, 18]   <- unique(results$trait)
     },
@@
 
-```{r cleanMeta1}
+```{r cleanMeta1, results='hide'}
 results_alltraits_grouping2 <- 
@@
 	                       "total number of acquired events in panel b", "whole arena permanence"))
+
+# Summary of the cleaned data for 218 traits
+  range(meta_clean$male_N)
+  range(meta_clean$female_N)
+  range(meta_clean$lnCVR_I2)
+  range(meta_clean$lnVR_I2)
+  range(meta_clean$lnRR_I2)
+  range(meta_clean$k)
+  mean(meta_clean$mean_male_N)
+  range(meta_clean$min_male_N)
+  median(meta_clean$mean_male_N)
+  sd(meta_clean$mean_male_N)
+  sd(meta_clean$mean_male_N) / sqrt(length(meta_clean$mean_male_N))
+  mean(meta_clean$mean_female_N)
+  median(meta_clean$mean_female_N)
+  range(meta_clean$min_female_N)
+  sd(meta_clean$mean_female_N)
+  sd(meta_clean$mean_female_N) / sqrt(length(meta_clean$mean_female_N))
 
@@
   mutate(par_group_size = length(unique(parameter_name)), 
-         sampleSize = as.numeric(sampleSize)) %>% 
+         sampleSize = as.numeric(k)) %>% 
   ungroup() %>% 
@@
            meta1_sub <- subset(meta1,par_group_size >1) # 90 observations   
-meta1_sub$sampleSize <- as.numeric(meta1_sub$sampleSize)
+meta1_sub$sampleSize <- as.numeric(meta1_sub$k)
 
@@
 
-# Final fixed effects meta-analyses within grouping terms, with SE of the estimate
+# Final random effects meta-analyses within grouping terms, with SE of the estimate
 
@@
 
-# Final fixed effects meta-analyses ACROSS grouping terms, with SE of the estimate
+# Final random effects meta-analyses ACROSS grouping terms, with SE of the estimate
 
@@
 
-overall2 <- bind_rows(extract_trait(overall1, "Behaviour"), 
+overall2 <- rbind(extract_trait(overall1, "Behaviour"), 
                       extract_trait(overall1, "Morphology"), 
@@
 
-heterog4 <- bind_rows(heteroCVR.ci, heteroVR.ci, heteroRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
+heterog4 <- rbind(heteroCVR.ci, heteroVR.ci, heteroRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
 
@@
                                nest(data = everything())   
-# **Final fixed effects meta-analyses within grouping terms, with SE of the estimate
+# **Final random effects meta-analyses within grouping terms, with SE of the estimate
 plot3.male.meta.CVR <- metacombo_male.plot3.CVR %>%
@@
                                   setNames(names(plot3.male.meta.CVR.b))
-plot3.male.meta.CVR.b <- bind_rows(plot3.male.meta.CVR.b, add.row.hearing)
+plot3.male.meta.CVR.b <- rbind(plot3.male.meta.CVR.b, add.row.hearing)
 plot3.male.meta.CVR.b <- plot3.male.meta.CVR.b[order(plot3.male.meta.CVR.b$GroupingTerm), ]
@@
                  ci.high = lnRR_upper)
-overall4.male.sig <- bind_rows(lnCVR.ci, lnRR.ci) %>% 
+overall4.male.sig <- rbind(lnCVR.ci, lnRR.ci) %>% 
                      select(GroupingTerm, 
@@
                                  nest(data = everything())   
-# **Final fixed effects meta-analyses within grouping terms, with SE of the estimate
+# **Final random effects meta-analyses within grouping terms, with SE of the estimate
 plot3.female.meta.CVR <- metacombo_female.plot3.CVR %>%
@@
                                  setNames(names(plot3.female.meta.CVR.b))
-plot3.female.meta.CVR.b <- bind_rows(plot3.female.meta.CVR.b, add.row.hearing)
+plot3.female.meta.CVR.b <- rbind(plot3.female.meta.CVR.b, add.row.hearing)
 plot3.female.meta.CVR.b <- plot3.female.meta.CVR.b[order(plot3.female.meta.CVR.b$GroupingTerm), ]
@@
   mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
-overall4.female.sig <- bind_rows(lnCVR.ci, lnRR.ci) %>% 
+overall4.female.sig <- rbind(lnCVR.ci, lnRR.ci) %>% 
                        select(GroupingTerm, parameter, value, ci.low, ci.high) # lnVR.ci,
@@
 
-overall4.male.sigS <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
+overall4.male.sigS <- rbind(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
 
@@
 
-overall4.female.sigS <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
+overall4.female.sigS <- rbind(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
 
@@
 
-# **Final fixed effects meta-analyses within grouping terms, with SE of the estimate
+# **Final random effects meta-analyses within grouping terms, with SE of the estimate
 
@@
 
-overall4.perc <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
+overall4.perc <- rbind(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
 
@@
 
-# Final fixed effects meta-analyses within grouping terms and across grouping terms, with SE of the estimate
+# Final random effects meta-analyses within grouping terms and across grouping terms, with SE of the estimate
 
@@
 
-overall4.male.perc <- bind_rows(lnCVR.ci,lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
+overall4.male.perc <- rbind(lnCVR.ci,lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
 

### 2020-09-08 scripts/MouseSexDiffVar_05_2020.Rmd
Small update to get SD for k

@@
 # Summary of the cleaned data for 218 traits
+  sd(meta_clean$k)
   range(meta_clean$male_N)

### 2020-09-08 scripts/MouseSexDiffVar_05_2020.Rmd
Fixed some input data problems for code. Class was character when should be numeric. Not sure why this issues popped up as it was never a problem for me in the past

@@
 overall4.female.sigS <- rbind(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
-
+overall4.female.sigS <- overall4.female.sigS %>%
+                          mutate(value = as.numeric(value),
+                                 ci.low = as.numeric(ci.low),
+                                 ci.high = as.numeric(ci.low))
 overall4.female.sigS$label <- "CI not overlapping zero"
@@
 
-overall4.male.sigS <- rbind(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
+overall4.male.sigS <- rbind(lnCVR.ci, lnVR.ci, lnRR.ci) %>% 
+                      select(GroupingTerm, parameter, value, ci.low, ci.high) %>%
+                      mutate(value = as.numeric(value), ci.low = as.numeric(ci.low), ci.high = as.numeric(ci.high))
 

### 2020-09-09 scripts/MouseSexDiffVar_05_2020.Rmd
Still not sure why rendering is failing. Seems to be some issue with gather. Works fine when I run on it's own, but ony when knitting does it fail

@@
 output:
-  bookdown::html_document2:
-    code_folding: hide
-    number_sections: yes
-    theme: flatly
+  html_document:
+    df_print: paged
     toc: yes
-    toc_depth: 6
-    toc_float: yes
+    toc_depth: '4'
   bookdown::pdf_document2:
@@
     toc: yes
-  html_document:
-    df_print: paged
+  bookdown::html_document2:
+    code_folding: hide
+    number_sections: yes
+    theme: flatly
     toc: yes
-    toc_depth: '4'
+    toc_depth: 6
+    toc_float: yes
   bookdown::word_document2:

### 2020-09-12 scripts/MouseSexDiffVar_Sept_2020.Rmd
latest 05/2020 wouldn't run / knit, seems like issues between version / rbind didn't work, reverted to bind_rows

--- 2020-09-08 scripts/MouseSexDiffVar_05_2020.Rmd
@@
       }
-
       results_alltraits_grouping[t, c(2:17,19:26)] <- c(f(cvr),lnCVR_I2 = extract_I2(cvr), f(cv), lnVR_I2 = extract_I2(cv), f(means), lnRR_I2 = extract_I2(means), k=means$k, male_N = sum(results$male_n_ind), female_N = sum(results$female_n_ind), min_male_N = min(results$male_n_ind), max_male_N = max(results$male_n_ind), mean_male_N = mean(results$male_n_ind),
@@
 
-```{r cleanMeta1, results='hide'}
+```{r cleanMeta1, results = "hide"}
 results_alltraits_grouping2 <- 
@@
 
-overall2 <- rbind(extract_trait(overall1, "Behaviour"), 
+overall2 <- bind_rows(extract_trait(overall1, "Behaviour"), 
                       extract_trait(overall1, "Morphology"), 
@@
 # Invidual table for heterogeneity across all traits
-# kable(metacombohetero,, digits = 3) %>%
- # kable_styling() %>%
-  #scroll_box(width = "100%", height = "200px")
+ kable(metacombohetero,, digits = 3) %>%
+  kable_styling() %>%
+  scroll_box(width = "100%", height = "200px")
 
@@
 
-heterog4 <- rbind(heteroCVR.ci, heteroVR.ci, heteroRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
+heterog4 <- bind_rows(heteroCVR.ci, heteroVR.ci, heteroRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
 
@@
                                   setNames(names(plot3.male.meta.CVR.b))
-plot3.male.meta.CVR.b <- rbind(plot3.male.meta.CVR.b, add.row.hearing)
+plot3.male.meta.CVR.b <- bind_rows(plot3.male.meta.CVR.b, add.row.hearing)
 plot3.male.meta.CVR.b <- plot3.male.meta.CVR.b[order(plot3.male.meta.CVR.b$GroupingTerm), ]
@@
                  ci.high = lnRR_upper)
-overall4.male.sig <- rbind(lnCVR.ci, lnRR.ci) %>% 
+overall4.male.sig <- bind_rows(lnCVR.ci, lnRR.ci) %>% 
                      select(GroupingTerm, 
@@
                                  setNames(names(plot3.female.meta.CVR.b))
-plot3.female.meta.CVR.b <- rbind(plot3.female.meta.CVR.b, add.row.hearing)
+plot3.female.meta.CVR.b <- bind_rows(plot3.female.meta.CVR.b, add.row.hearing)
 plot3.female.meta.CVR.b <- plot3.female.meta.CVR.b[order(plot3.female.meta.CVR.b$GroupingTerm), ]
@@
   mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
-overall4.female.sig <- rbind(lnCVR.ci, lnRR.ci) %>% 
+overall4.female.sig <- bind_rows(lnCVR.ci, lnRR.ci) %>% 
                        select(GroupingTerm, parameter, value, ci.low, ci.high) # lnVR.ci,
@@
 
-overall4.male.sigS <- rbind(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
+overall4.male.sigS <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
 
@@
 
-overall4.female.sigS <- rbind(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
+overall4.female.sigS <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high) # Note: bind_rows may need to be replaced by rbind
+
+overall4.female.sigS <- overall4.female.sigS %>%
+                          mutate(value = as.numeric(value),
+                                 ci.low = as.numeric(ci.low),
+                                 ci.high = as.numeric(ci.low))
 
@@
 
-overall4.perc <- rbind(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
+overall4.perc <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
 
@@
 
-overall4.male.sigS <- rbind(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
+overall4.male.sigS <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
+# may require: 	 %>% mutate(value = as.numeric(value), ci.low = as.numeric(ci.low), ci.high = as.numeric(ci.high))
 
@@
 
-overall4.male.perc <- rbind(lnCVR.ci,lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
+overall4.male.perc <- bind_rows(lnCVR.ci,lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
 
@@
 ```{r Table1_prep, echo = FALSE, eval = TRUE, results='hide'}
-  # Initial checks
-  length(unique(data$parameter_name)) # 232 traits
-  length(unique(data$parameter_group)) # 161 parameter groups
-  length(unique(data$procedure_name)) # 26 procedure groups
-  length(unique(data$biological_sample_id)) # 27147 individial mice  
+#Initial checks
+  #length(unique(data$parameter_name)) # 232 traits
+  #length(unique(data$parameter_group)) # 161 parameter groups
+ # length(unique(data$procedure_name)) # 26 procedure groups
+  #length(unique(data$biological_sample_id)) # 27147 individial mice
 # To show a table with number of males and females per strain per production center:
@@
                    print(n = Inf)) 
-
-```
+```
+
 ```{r Table1, message=FALSE}
@@
   #PDF
- pander(ST1, caption = "Table 6.1: Summary of the available numbers of male and female mice from each strain and originating institution.")
+ #pander(ST1, caption = "Table 6.1: Summary of the available numbers of male and female mice from each strain and originating institution.")
   #HTML
-    #kable(ST1, caption = "Summary of the available numbers of male and female mice from each strain and originating institution.") %>%
-    #kable_styling() %>%
-    #scroll_box(width = "100%", height = "200px")
+    kable(ST1, caption = "Summary of the available numbers of male and female mice from each strain and originating institution.") %>%
+    kable_styling() %>%
+    scroll_box(width = "100%", height = "200px")
 
@@
 #PDF
-pander(cbind(meta1 %>% count(parameter_group)), caption = "Table 6.2: Trait categories (parameter_group) and the number of correlated traits within these categories.
+#pander(cbind(meta1 %>% count(parameter_group)), caption = "Table 6.2: Trait categories (parameter_group) and the number of correlated traits within these categories.
 Traits were meta-analysed using robumeta")
 
-#kable(cbind(meta1 %>% count(parameter_group)), caption = "Trait categories (parameter_group) and the number of correlated traits within these categories.
-Traits were meta-analysed using robumeta") %>%
-  #kable_styling() %>%
-  #scroll_box(width = "100%", height = "200px")
+kable(cbind(meta1 %>% count(parameter_group)), caption = "Trait categories (parameter_group) and the number of correlated traits within these categories. Traits were meta-analysed using robumeta") %>%
+  kable_styling() %>%
+  scroll_box(width = "100%", height = "200px")
 ```
@@
 # PDF
-pander(metacombo, caption = "Table 6.3: We use this corrected (for correlated traits) results table, which contains each of the meta-analytic means for all effect sizes of interest, for further analyses.
+#pander(metacombo, caption = "Table 6.3: We use this corrected (for correlated traits) results table, which contains each of the meta-analytic means for all effect sizes of interest, for further analyses.
 We further use this table as part of the Shiny App, which is able to provide the percentage differences between males and females for mean, variance and coefficient of variance.")
@@
 #HTML
-#kable(metacombo, digits = 3, caption = "We use this corrected (for correlated traits) results table, which contains each of the meta-analytic means for all effect sizes of interest, for further analyses.
+kable(metacombo, digits = 3, caption = "We use this corrected (for correlated traits) results table, which contains each of the meta-analytic means for all effect sizes of interest, for further analyses.
 We further use this table as part of the Shiny App, which is able to provide the percentage differences between males and females for mean, variance and coefficient of variance.") %>%
-  #kable_styling() %>%
-  #scroll_box(width = "100%", height = "200px")
+  kable_styling() %>%
+  scroll_box(width = "100%", height = "200px")
 
@@
 #PDF
-pander(overall2, caption = "Table 6.4: Summary of overall meta-analyses on the functional trait group level (GroupingTerm).
+#pander(overall2, caption = "Table 6.4: Summary of overall meta-analyses on the functional trait group level (GroupingTerm).
 Results for lnCVR, lnVR and lnRR and their respective upper and lower 95 percent CI's, standard error and I2 values are provided.")
@@
 #HTML
-#kable(overall2, digits = 3, caption = "Summary of overall meta-analyses on the functional trait group level (GroupingTerm).
+kable(overall2, digits = 3, caption = "Summary of overall meta-analyses on the functional trait group level (GroupingTerm).
 Results for lnCVR, lnVR and lnRR and their respective upper and lower 95 percent CI's, standard error and I2 values are provided.") %>%
-#kable_styling() %>%
-#scroll_box(width = "100%", height = "200px")
+ kable_styling() %>%
+ scroll_box(width = "100%", height = "200px")
 ```
@@
         #PDF
-    pander(mf_sig, caption = "Table 6.5: Provides an overview of meta-analysis results performed on traits that were significantly biased towards either sex.
+    #pander(mf_sig, caption = "Table 6.5: Provides an overview of meta-analysis results performed on traits that were significantly biased towards either sex.
 This table summarizes findings for both sexes and the respective functional trait groups.")
       #HTML
-  #kable(mf_sig, digits = 3, caption = "Provides an overview of meta-analysis results performed on traits that were significantly biased towards either sex.
+  kable(mf_sig, digits = 3, caption = "Provides an overview of meta-analysis results performed on traits that were significantly biased towards either sex.
 This table summarizes findings for both sexes and the respective functional trait groups.") %>%
-  #kable_styling() %>%
-  #scroll_box(width = "100%", height = "300px")
+  kable_styling() %>%
+  scroll_box(width = "100%", height = "300px")
 ```
@@
   # PDF
-  pander(het, caption = "Table 6.6: Summarizes our findings on heterogeneity due to institutions and mouse strains.
+  #pander(het, caption = "Table 6.6: Summarizes our findings on heterogeneity due to institutions and mouse strains.
 These results are based on meta-analyses on sigma^2 and errors for mouse strains and centers (Institutions), following the identical workflow from above.")
@@
   # HTML
-  #kable(het, digits = 3, caption = "Summarizes our findings on heterogeneity due to institutions and mouse strains.
+  kable(het, digits = 3, caption = "Summarizes our findings on heterogeneity due to institutions and mouse strains.
 These results are based on meta-analyses on sigma^2 and errors for mouse strains and centers (Institutions), following the identical workflow from above.") %>%
-   #kable_styling() %>%
-    #scroll_box(width = "100%", height = "200px")
+   kable_styling() %>%
+    scroll_box(width = "100%", height = "200px")
 

### 2020-10-28 scripts/MouseSexDiffVar_Oct_2020.Rmd
reverting to rbind, with R version 4.0 / associated dplyr version; Changed Figure names to match the manuscriot files. Added doi for the knitted version

--- 2020-09-12 scripts/MouseSexDiffVar_Sept_2020.Rmd
@@
 ---
-title: 'Sex and Power: Sexual dimorphism in trait variability and its eco-evolutionary
+title: 'Sexual dimorphism in trait variability and its eco-evolutionary
   and statistical implications'
@@
     toc_float: yes
+  html_document:
+    df_print: paged
+    toc: yes
+    toc_depth: '4'
+  word_document:
+    toc: yes
+    toc_depth: '4'
+  html_notebook:
+    toc: yes
   bookdown::pdf_document2:
@@
     theme: flatly
-  word_document:
-    toc: yes
-    toc_depth: '4'
-  html_notebook:
-    toc: yes
-  html_document:
-    df_print: paged
-    toc: yes
-    toc_depth: '4'
   bookdown::word_document2:
@@
     theme: flatly
-subtitle: Electronic Supplementary Material
+subtitle: Electronic Supporting File (doi:10.5281/zenodo.4146948)
 always_allow_html: yes
@@
 
-```{r FigG1, echo = FALSE, fig.width = 4, fig.height = 8, fig.cap="Workflow of data process and meta-analysis"}
+```{r FigG1, echo = FALSE, fig.width = 4, fig.height = 8, fig.cap="Workflow of data processing and meta-analysis [Figure 3 in manuscipt]"}
 
@@
 
-```{r FigCor, fig.height=3, message = FALSE, fig.cap= "Mean-variance relationships (log(Mean) vs log(SD, standard deviation)) across all traits for males (A) and females (B)."}
+```{r FigCor, fig.height=3, message = FALSE, fig.cap= "Mean-variance relationships (log(Mean) vs log(SD, standard deviation)) across all traits for males (A) and females (B).[Figure 1-figure supplement 1 in manuscript]"}
 
@@
 # Meta-analysis results
-## Preparing: Figure 3 
+## Preparing: Figure 4 
 ### Count data, based on First-order meta-analysis results
@@
 
-## Main Manuscript: Figure 3
+## Main Manuscript: Figure 4
 
@@
 Both panels represent results evaluated across all traits.
-Traits that are male biased are shown in blue, whereas female bias data is represented in orange."}
+Traits that are male biased are shown in blue, whereas female bias data is represented in orange.[Figure 4 in manuscript]"}
 Fig4 <- ggarrange(malebias_Fig2_alltraits, Metameta_Fig3_alltraits,  nrow = 2, align = "v", heights = c(10, 9), labels = c("A", "B"))
 Fig4
+ggsave("Figure4.pdf", plot = Fig4, width = 6, height = 7)
 ```
@@
                                   setNames(names(plot3.male.meta.CVR.b))
-plot3.male.meta.CVR.b <- bind_rows(plot3.male.meta.CVR.b, add.row.hearing)
+plot3.male.meta.CVR.b <- rbind(plot3.male.meta.CVR.b, add.row.hearing) #bind_rows
 plot3.male.meta.CVR.b <- plot3.male.meta.CVR.b[order(plot3.male.meta.CVR.b$GroupingTerm), ]
@@
                  ci.high = lnRR_upper)
-overall4.male.sig <- bind_rows(lnCVR.ci, lnRR.ci) %>% 
+overall4.male.sig <- rbind(lnCVR.ci, lnRR.ci) %>%  #bind_rows
                      select(GroupingTerm, 
@@
 # Combine with separate grouping term results
-plot3.female.meta.CVR <- bind_rows(plot3.female.meta.CVR, plot3.female.meta.CVR.all)
+plot3.female.meta.CVR <- bind_rows(plot3.female.meta.CVR, plot3.female.meta.CVR.all) #bind_rows
  plot3.female.meta.VR <- bind_rows(plot3.female.meta.VR,   plot3.female.meta.VR.all)
@@
                                  setNames(names(plot3.female.meta.CVR.b))
-plot3.female.meta.CVR.b <- bind_rows(plot3.female.meta.CVR.b, add.row.hearing)
+plot3.female.meta.CVR.b <- rbind(plot3.female.meta.CVR.b, add.row.hearing) #bind_rows
 plot3.female.meta.CVR.b <- plot3.female.meta.CVR.b[order(plot3.female.meta.CVR.b$GroupingTerm), ]
@@
   mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
-overall4.female.sig <- bind_rows(lnCVR.ci, lnRR.ci) %>% 
+overall4.female.sig <- rbind(lnCVR.ci, lnRR.ci) %>%  #bind_rows
                        select(GroupingTerm, parameter, value, ci.low, ci.high) # lnVR.ci,
@@
 
-overall4.male.sigS <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
+overall4.male.sigS <- rbind(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high) #bind_rows
 
@@
 
-overall4.female.sigS <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high) # Note: bind_rows may need to be replaced by rbind
+overall4.female.sigS <- rbind(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high) # Note: bind_rows may need to be replaced by rbind
 
@@
 
-overall4.male.sigS <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
-# may require: 	 %>% mutate(value = as.numeric(value), ci.low = as.numeric(ci.low), ci.high = as.numeric(ci.high))
-
+overall4.male.sigS <- rbind(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high) %>% 
+  mutate(value = as.numeric(value), ci.low = as.numeric(ci.low), ci.high = as.numeric(ci.high))
+# may require: 	
 overall4.male.sigS$label <- "CI not overlapping zero"
@@
 ## Figure 5.1
-Figure \@ref(fig:FigS1) is similar to Figure 3 in the main article except that lnVR has been added to the plot for comparison with lnCVR and lnRR.
+This Figure is similar to Figure 4 in the main article except that lnVR has been added to the plot for comparison with lnCVR and lnRR.
 
@@
 Panel B shows effect sizes from separate meta-analysis for each functional group, and Panel C contains results of heterogeneity analyses.
-All three panels represent results evaluated across all traits."}
+All three panels represent results evaluated across all traits.[Figure 4 – figure supplement 1 in manuscript]"}
 
@@
 FigS1
-#ggsave("FigS1_OverallResults.pdf", plot = FigS1, width = 6, height = 7)
+ggsave("Figure4_1.pdf", plot = FigS1, width = 6, height = 7)
 ```
@@
 As sensitivity analyses, we also employed another way of separating male- and female-biased traits.
-We quantified traits that were more than 10% biased towards either of the sexes, regardless of significance (N[male-biased] = 31, & N[female-biased] = 36 for lnCVR,  N[male-biased] = 56, & N[female-biased] = 57 for lnVR , N[male-biased] = 42, & N[female-biased] = 33  for lnRR; see Supplemental Figure S\@ref(fig:FigS2), Supplemental Table 7.3).
+We quantified traits that were more than 10% biased towards either of the sexes, regardless of significance (N[male-biased] = 31, & N[female-biased] = 36 for lnCVR,  N[male-biased] = 56, & N[female-biased] = 57 for lnVR , N[male-biased] = 42, & N[female-biased] = 33  for lnRR; see Figure 4 – figure supplement 1, Supplemental Table 3).
 
@@
 Having established that different sex-biases were present across trait functional groups, we explored specific patterns in male and female bias by categorizing traits into either male or female-biased, and then, quantifying the degree of sex bias.
-To do this, we focused on only those traits that were significantly biased towards one sex (as indicated by “CI not overlapping 0” in Figure S\@ref(fig:FigS2).
-Selecting significantly sex-biased traits reduced the number of traits substantially (Figure S\@ref(fig:FigS2)A; compared to all traits, Figure \@ref(fig:Fig3) and Figure \@ref(fig:FigS1)), and returned similar numbers of traits with either significant male- or female-bias for lnCVR (Figure S\@ref(fig:FigS2)A).
-
-Looking only at traits with significant male-bias, trait variability tended to be higher in males than in females overall (11.77% male bias, lnCVR = 0.111, CI = [0.093 to 0.129]; compared to 8.3% female-bias, lnCVR = -0.087, CI = [-0.109 to (-0.064)]; Figure S\@ref(fig:FigS2)B).
-The degree of sex-bias varied across the functional trait groups, ranging from 4.6 % (Physiology, lnCVR = -0.047, CI = [-0.064 to (-0.030)] to 15.13 % (Eye morphology, lnCVR = -0.164, CI = [-0.249 to (-0.250)] in females, and from 8.6 % (Hematology, lnCVR = 0.082, CI = [0.048 to 0.117]) and 16.66 % (Heart, lnCVR = 0.154, CI = [0.085 to 0.223]) in males (Figure S\@ref(fig:FigS2)B).
+To do this, we focused on only those traits that were significantly biased towards one sex (as indicated by “CI not overlapping 0” in Figure Figure 4 – figure supplement 2).
+Selecting significantly sex-biased traits reduced the number of traits substantially (Figure 4 – figure supplement 2A; compared to all traits, Figure 4 and Figure 4 – figure supplement 1), and returned similar numbers of traits with either significant male- or female-bias for lnCVR (Figure 4 – figure supplement 2A).
+
+Looking only at traits with significant male-bias, trait variability tended to be higher in males than in females overall (11.77% male bias, lnCVR = 0.111, CI = [0.093 to 0.129]; compared to 8.3% female-bias, lnCVR = -0.087, CI = [-0.109 to (-0.064)]; Figure 4 – figure supplement 2B).
+The degree of sex-bias varied across the functional trait groups, ranging from 4.6 % (Physiology, lnCVR = -0.047, CI = [-0.064 to (-0.030)] to 15.13 % (Eye morphology, lnCVR = -0.164, CI = [-0.249 to (-0.250)] in females, and from 8.6 % (Hematology, lnCVR = 0.082, CI = [0.048 to 0.117]) and 16.66 % (Heart, lnCVR = 0.154, CI = [0.085 to 0.223]) in males (Figure 4 – figure supplement 2B).
 
 To put sex biases (sexual dimorphisms) in variability into perspective, we also quantify the degree of sexual dimorphism in significantly sex-biased traits (i.e., the extent of sexual dimorphisms).
-There were more traits that were significantly biased in mean trait value in males compared to females (Figure S\@ref(fig:FigS2)A, lnRR).
-These traits were 11.73 % biased towards males (Figure S\@ref(fig:FigS2)B; lnRR = 0.111, CI = [0.083 – 0.138]) while 9.38 % towards females (lnRR = -0.094, CI = [-0.129 – (-0.068)].
-The overall pattern for lnRR was more varied among the functional trait groups than for lnCVR, ranging from 1.2% (Hematology, lnRR = -0.013, CI = [-0.017 – (-0.007)] to 14.72 % (Immunology, lnRR = -0.159, CI = [-0.229 – (-0.089)] in female-based traits (Figure S\@ref(fig:FigS2)B) whereas in males-based traits from 1.8 % (Hearing, lnRR = 0.018, CI = [0.006 – 0.031]) to 25 % (Metabolism, lnRR = 0.223, CI = [0.110 – 0.335])  (Figure S\@ref(fig:FigS2)B).
-
-```{r FigS2, fig.height = 10, fig.width = 8, fig.cap=" A) Differences in numbers of affected traits, in variance (lnCVR and lnVR) and means (lnRR), where there’s a significant difference between the sexes (i.e CI not overlapping zero), and where the sex bias is greater than 10% difference (regardless of significance).
+There were more traits that were significantly biased in mean trait value in males compared to females (Figure 4 – figure supplement 2A, lnRR).
+These traits were 11.73 % biased towards males Figure 4 – figure supplement 2B; lnRR = 0.111, CI = [0.083 – 0.138]) while 9.38 % towards females (lnRR = -0.094, CI = [-0.129 – (-0.068)].
+The overall pattern for lnRR was more varied among the functional trait groups than for lnCVR, ranging from 1.2% (Hematology, lnRR = -0.013, CI = [-0.017 – (-0.007)] to 14.72 % (Immunology, lnRR = -0.159, CI = [-0.229 – (-0.089)] in female-based traits Figure 4 – figure supplement 2B, whereas in males-based traits from 1.8 % (Hearing, lnRR = 0.018, CI = [0.006 – 0.031]) to 25 % (Metabolism, lnRR = 0.223, CI = [0.110 – 0.335])  (Figure 4 – figure supplement 2B).
+
+```{r FigS2, fig.height = 10, fig.width = 8, fig.cap=" A) Differences in numbers of affected traits, in variance (lnCVR and lnVR) and means (lnRR), where there is a significant difference between the sexes (i.e CI not overlapping zero), and where the sex bias is greater than 10% difference (regardless of significance).
 Panel B depicts results for the sex bias in those traits that differ between the sexes (second-order meta-analysis).
 Triangles represent sex bias in means (response ratio) and black circles differences in the coefficient of variation ratio (mean-adjusted variability).
-The orange-red bars represent trait groups with a female bias, blue-green bars male-biased traits."}
+The orange-red bars represent trait groups with a female bias, blue-green bars male-biased traits.[Figure 4 – figure supplement 2 in manuscript]"}
 library(ggpubr)
@@
 FigS2
-```
-
-# Supplemental Tables
-## Table 6.1
+ggsave("Figure4_2.pdf", plot = FigS2, width = 6, height = 7)
+```
+
+# .Supplemental Tables
+## Table 1
 
@@
 
-## Table 6.2
+## Table 2
 
@@
 
-## Table 6.3
+## Table 3
 
@@
 
-## Table 6.4
+## Table 4
 
@@
 
-## Table 6.5
+## Table 5
 
@@
 
-## Table 6.6
+## Table 6
 

### 2020-11-19 scripts/MouseSexDiffVar_Oct_2020.Rmd
typo in Suppl Fig

@@
                                   setNames(names(plot3.male.meta.CVR.b))
-plot3.male.meta.CVR.b <- rbind(plot3.male.meta.CVR.b, add.row.hearing) #bind_rows
+plot3.male.meta.CVR.b <- rbind(plot3.male.meta.CVR.b, add.row.hearing) #use bind_rows in R3.6
 plot3.male.meta.CVR.b <- plot3.male.meta.CVR.b[order(plot3.male.meta.CVR.b$GroupingTerm), ]
@@
                  ci.high = lnRR_upper)
-overall4.male.sig <- rbind(lnCVR.ci, lnRR.ci) %>%  #bind_rows
+overall4.male.sig <- rbind(lnCVR.ci, lnRR.ci) %>%  #use bind_rows in R3.6
                      select(GroupingTerm, 
@@
 # Combine with separate grouping term results
-plot3.female.meta.CVR <- bind_rows(plot3.female.meta.CVR, plot3.female.meta.CVR.all) #bind_rows
+plot3.female.meta.CVR <- bind_rows(plot3.female.meta.CVR, plot3.female.meta.CVR.all) #use bind_rows in R3.6
  plot3.female.meta.VR <- bind_rows(plot3.female.meta.VR,   plot3.female.meta.VR.all)
@@
                                  setNames(names(plot3.female.meta.CVR.b))
-plot3.female.meta.CVR.b <- rbind(plot3.female.meta.CVR.b, add.row.hearing) #bind_rows
+plot3.female.meta.CVR.b <- rbind(plot3.female.meta.CVR.b, add.row.hearing) #use bind_rows in R3.6
 plot3.female.meta.CVR.b <- plot3.female.meta.CVR.b[order(plot3.female.meta.CVR.b$GroupingTerm), ]
@@
   mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
-overall4.female.sig <- rbind(lnCVR.ci, lnRR.ci) %>%  #bind_rows
+overall4.female.sig <- rbind(lnCVR.ci, lnRR.ci) %>%  #use bind_rows in R3.6
                        select(GroupingTerm, parameter, value, ci.low, ci.high) # lnVR.ci,
@@
 
-overall4.male.sigS <- rbind(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high) #bind_rows
+overall4.male.sigS <- rbind(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high) #use bind_rows in R3.6
 
@@
   mutate(value = as.numeric(value), ci.low = as.numeric(ci.low), ci.high = as.numeric(ci.high))
-# may require: 	
+# R 3.6: do not use "%>% mutate(value = as.numeric(value), ci.low = as.numeric(ci.low), ci.high = as.numeric(ci.high))"
 overall4.male.sigS$label <- "CI not overlapping zero"

### 2020-11-19 scripts/MouseSexDiffVar_Oct_2020.Rmd

@@
                                  ci.low = as.numeric(ci.low),
-                                 ci.high = as.numeric(ci.low))
+                                 ci.high = as.numeric(ci.high))
 
@@
 FigS2
-ggsave("Figure4_2.pdf", plot = FigS2, width = 6, height = 7)
+ggsave("Figure4_2.pdf", plot = FigS2, width = 8, height = 9)
 ```

### 2021-04-05 executableMS/ms_v1.rmd
Rename ms_v1.md to ms_v1.rmd

---
authors:
  - Susanne RK Zajitschek
  - Felix Zajitschek
  - Russell Bonduriansky
  - Robert C Brooks
  - Will Cornwell
  - Daniel S Falster
  - Malgorzata Lagisz
  - Jeremy Mason
  - Alistair M Senior
  - Daniel WA Noble
  - Shinichi Nakagawa
  - Evolution & Ecology Research Center, School of Biological, Earth, and Environmental Sciences, University of New South Wales, Sydney, Australia; 
  - Liverpool John Moores University, School of Biological and Environmental Sciences, Liverpool, United Kingdom; 
  - European Bioinformatics Institute (EMBL- EBI), European Molecular Biology Laboratory, Wellcome Trust Genome Campus, Hinxton, United Kingdom; 
  - University of Sydney, Charles Perkins Centre, School of Life and Environmental Sciences, School of Mathematics and Statistics, Sydney, Australia; 
  - Division of Ecology and Evolution, Research School of Biology, Australian National University, Canberra, Australia

bibilography: SexDiffBib.bib

---

# Sexual dimorphism in trait variability and its eco-evolutionary and statistical implications

## Abstract 
Biomedical and clinical sciences are experiencing a renewed interest in the fact that males and females differ in many anatomic, physiological, and behavioural traits. Sex differences in trait variability, however, are yet to receive similar recognition. In medical science, mammalian females are assumed to have higher trait variability due to estrous cycles (the ‘estrus-mediated variability hypothesis’); historically in biomedical research, females have been excluded for this reason. Contrastingly, evolutionary theory and associated data support the ‘greater male variability hypothesis’. Here, we test these competing hypotheses in 218 traits measured in >26,900 mice, using meta-analysis methods. Neither hypothesis could universally explain patterns in trait variability. Sex bias in variability was trait-dependent. While greater male variability was found in morphological traits, females were much more variable in immunological traits. Sex-specific variability has eco-evolutionary ramifications, including sex-dependent responses to climate change, as well as statistical implications including power analysis considering sex difference in variance.

## Introduction
Sex differences arise because selection acts on the two sexes differently, especially on traits associ- ated with mating and reproduction (Darwin, 1871). Therefore, sex differences are widespread, a fact which is unsurprising to any evolutionary biologist. However, scientists in many (bio-)medical fields have not necessarily regarded sex as a biological factor of intrinsic interest (Clayton, 2016; Flanagan, 2014; Karp et al., 2017; Klein et al., 2015; Prendergast et al., 2014; Shansky and Woolley, 2016). Therefore, many (bio-)medical studies have only been conducted with male sub- jects. Consequently, our knowledge is biased. For example, we know far more about drug efficacy in male compared to female subjects, contributing to a poor understanding of how the sexes respond differently to medical interventions (Nowogrodzki, 2017). This gap in knowledge is predicted to lead to overmedication and adverse drug reactions in women (Zucker and Prendergast, 2020). Only recently have (bio-)medical scientists started considering sex differences in their research (Dorris et al., 2015; Ingvorsen et al., 2017; Robinson et al., 2017; Smarr et al., 2017;Ahmad et al., 2017; Foltin and Evans, 2018; Thompson et al., 2018). Indeed, the National Insti- tutes of Health (NIH) have now implemented new guidelines for animal and human research study designs, requiring that sex be included as a biological variable (Clayton, 2016; Clayton and Collins, 2014; NIH, 2015a). [@moore2001]
When comparing the sexes, biologists generally focus on mean differences in trait values, placing little or no emphasis on sex differences in trait variability (see Figure 1 for a diagram explaining differences in means and variances). Despite this, two hypotheses exist that explain why trait variability might be expected to differ between the sexes. Interestingly, these two hypotheses make opposing predictions.

 this stupid figure has to get embedded Fig1 (./executableMS/Figures/Figure 1.png).

First, the ‘estrus-mediated variability hypothesis’ (Figure 2), which emerged in the (bio-)medical research field, assumes that the female estrous cycle (see e.g. Prendergast et al., 2014; Beery and Zucker, 2011) causes higher variability across traits in female subjects. A wide range of labile traits are presumed to co-vary with physiological changes that are induced by reproductive hormones. High variability is, therefore, expected to be particularly prominent when the stage of the estrous cycle is unknown and unaccounted for. This higher trait variability, resulting from females being at different stages of their estrous cycle, is the main reason for why female research subjects are often excluded from biomedical research trials, especially in the fields of neuroscience, physiology and pharmacology (NIH, 2015a). Female exclusion has traditionally been justified based on the grounds that including females in empirical research leads to a loss of statistical power, or that animals must be sampled across the estrous cycle for one to make valid conclusions, requiring more time and resources.

Fig2(./executableMS/Figures/Figure 2.png)

Second, the ‘greater male variability hypothesis’ suggests males exhibit higher trait variability because of two different mechanisms. The first mechanism is based on males being the heteroga- metic sex in mammals. Mammalian females possess two X chromosomes, leading to an ‘averaging’ of trait expression across the genes on each chromosome. In contrast, males exhibit greater variance because expression of genes on a single X chromosome is likely to lead to more extreme trait values (Reinhold and Engqvist, 2013). The second mechanism is based on males being under stronger sex- ual selection (Pomiankowski and Moller, 1995; Cuervo and Møller, 1999; Cuervo and Møller,2001). Empirical evidence supports higher variability of traits that are sexually selected, often har- bouring high genetic variance and being condition-dependent, which makes sense as ‘condition’ as a trait is likely to be based on numerous loci (Rowe and Houle, 1996; Tomkins et al., 2004). Thus, higher genetic and, thus, phenotypic variance resulting from sexual selection is expected to charac- terise sexually selected traits. In mammals, it is likely that both mechanisms are operating concomi- tantly. So far, the ‘greater male variability hypothesis’ has gained some support in the evolutionary and psychological literature (Reinhold and Engqvist, 2013; Lehre et al., 2009).
Here, we conduct the first comprehensive test of the greater male variability and estrus-mediated variability hypotheses in mice (Figure 2; Reinhold and Engqvist, 2013; Johnson et al., 2008;Hedges and Nowell, 1995; Itoh and Arnold, 2015; Becker et al., 2016; Beery, 2018), examining sex differences in variance across 218 traits in 26,916 animals. To this end, we carry out a series of meta-analyses in two steps (Figure 3). First, we quantify the natural logarithm of the male to female coefficients of variation, CV, or relative variance (lnCVR) for each cohort (population) of mice, for dif- ferent traits, along with the variability ratio of male to female standard deviations, SD, on the log scale (lnVR, following Nakagawa et al., 2015, see Figure 1). Then, we analyse these effect sizes to quantify sex bias in variance for each trait using meta-analytic methods. To better understand our results, and match them to previously reported sex differences in trait means (Karp et al., 2017), we also quantify and analyse the log response ratio (lnRR). Next, we statistically amalgamate the trait- level results to test our hypotheses and to quantify the degree of sex bias in and across nine functional trait groups (for details on the grouping, see below). Our meta-analytic approach allows easy interpretation and comparison with earlier and future studies. Further, the proposed method using lnCVR (and lnVR) is probably the only practical method to compare variability between two sexes within and across studies (Nakagawa et al., 2015; Senior et al., 2020), as far as we are aware. Also, the use of a ratio (i.e. lnRR, lnVR, lnCVR) between two groups (males and females) naturally controls for different units (e.g. cm, g, ml) as well as for changes in traits over time and space.

## Results
Data characteristics and workflow
We used a dataset compiled by the International Mouse Phenotyping Consortium (Dickinson et al., 2016) (IMPC, dataset acquired 6/2018). To gain insight into systematic sex differences, we only included data of wildtype-strain adult mice, between 100 and 500 days of age. We removed cases with missing data, and selected measurements that were closest to 100 days of age (young adult) when multiple measurements of the same trait were available. To obtain robust estimates of sex dif- ferences, we only used data on traits that were measured in at least two different institutions (see workflow diagram, Figure 3).
Our dataset comprised 218 continuous traits (after initial data cleaning and pre-processing; Fig- ure 3). It contains information from 26,916 mice from nine wildtype strains that were studied across 11 institutions. We combined mouse strain/institution information to create a biological grouping variable (referred to as ‘population’ in Figure 3B; see also Supplementary file 1, Table 1 for details), and the mean and variance of a trait for each population was quantified. We assigned traits accord- ing to related procedures into functionally and/or procedurally related trait groups to enhance interpretability (referred to as ‘functional groups’ hereafter; see also Figure 3G). Our nine functional trait groups were: behaviour, morphology, metabolism, physiology, immunology, hematology, heart, hearing and eye (for the rationale of these functional groups and related details, see Methods and Supplementary file 1, Table 3).

### Testing the two hypotheses
We found that some means and variabilities of traits were biased towards males (i.e. ‘male-biased’, hereafter; turquoise shaded traits, Figure 4), but others towards females (i.e. ‘female-biased’, here- after; orange shading, Figure 4) within all functional groups. These sex-specific biases occur in mean trait sizes and also in our measures of trait variability. There were strong positive relationships between mean and variance across traits (r > 0.94 on the log scale; Figure 1—figure supplement 1), and therefore, we report the results of lnCVR, which controls for differences in means, in the main text. Results on lnVR are presented as figure supplements (Figure 4—figure supplements 1 and 2).
There was no consistent pattern in which sex has more variability (lnCVR) in the examined traits (left panel in Figure 4A). Our meta-analytic results also did not support a consistent pattern of either higher male variability or higher female variability (see Figure 4B, left panel: ‘All’ indicates that across all traits and functional groups, there was no significant sex bias in variances; lnCVR = 0.005, 95% confidence interval, 95% CI = [-0.009 to 0.018]). However, there was high heterogeneity among traits (I2 = 76.5%, Supplementary file 1, Table 4 and see also Table 5), indicating sex differ- ences in variability are trait-dependent, corroborating our general observation that variability in some traits was male-biased but others female-biased (Figure 4A).
As expected, specific functional trait groups showed significant sex-specific bias in variability (Figure 4B). The variability among traits within a functional group was lower than that of all the traits combined (Supplementary file 1, Table 4). For example, males exhibited an 8.05% increase in CV relative to females for morphological traits (lnCVR = 0.077; CI = [0.041 to 0.113], I2 = 67.3%), but CV was female-biased for immunological traits (6.59% higher in females, lnCVR = -0.068, CI = [-0.098 to 0.038], I2 = 40.8%) and eye morphology (7.85% higher in females, lnCVR = -0.081, CI = [-0.147 to (-0.016)], I2 = 49.8%).
The pattern was similar for overall sexual dimorphism in mean trait values (here, a slight male bias is indicated by larger ‘turquoise’ than ‘orange’ areas; Figure 4B, right and Figure 4B, lnRR: ‘All’, lnRR = 0.012, CI = [-0.006 to 0.31]). Trait means (lnRR) were 7% larger for males (lnRR = 0.067; CI =[0.007 to 0.128]) in morphological traits and 15.3% larger in males for metabolic traits (lnRR = 0.142; CI = [0.036 to 0.248]). In contrast, females had 5.59% (lnRR = 0.057, CI = [-0.107 to (-0.007)]) larger means than those of males for immunological traits. We note that these meta-analytic estimates were accompanied by very large between-trait heterogeneity values (morphology I2 = 99.7%, metabolism I2 = 99.4%, immunology I2 = 96.2; see Supplementary file 1, Table 4), indicating that even within the same functional groups, the degree and direction of sex bias in the mean was not consistent among traits.

## Discussion
We tested competing predictions from two hypotheses explaining why sex biases in trait variability exist. Neither the ‘greater male variability’ hypothesis nor the ‘estrus-mediated variability’ hypothesis explain the observed patterns in sex-biased trait variation on their own. Therefore, our results add further empirical weight to calls that question the basis for the routine exclusion of one sex in bio- medical research based on the estrus-mediated variability hypothesis (Flanagan, 2014; Klein et al., 2015; Prendergast et al., 2014; Shansky and Woolley, 2016; Becker et al., 2016). It is important to know that for each trait we estimated the mean effect size (i.e. lnCVR) over strains and locations. As such, our results may not necessarily apply to every group of mice, which may or may not result in stronger support for either of the two hypotheses.
Greater male variability vs. estrus-mediated variability?
Evolutionary biologists commonly expect greater variability in the heterogametic sex than the homo- gametic sex. In mammals, males are heterogametic, and hence are expected to exhibit higher trait variability compared to females, which is also consistent with an expectation from sexual selection theory (Reinhold and Engqvist, 2013). Our results provide only partial support for the greater male variability hypothesis, because the expected pattern only manifested for morphological traits (see Figures 4 and 5). This result corroborates a previous analysis across animals, which found that the heterogametic sex was more variable in body size (Reinhold and Engqvist, 2013). However, our data do not support the conclusion that higher variability in males occurs across all traits, including for many other morphological traits.
The estrus-mediated variability hypothesis was, at least until recently (Prendergast et al., 2014; Smarr et al., 2017), regularly used as a rationale for including only male subjects in many biomedical studies. So far, we know very little about the relationship between hormonal fluctuations and general trait variability within and among female subjects. Our results are consistent with the estrus-medi- ated variability hypothesis for immunological traits only. Immune responses can strongly depend on sex hormones (Zuk and McKean, 1996; Grossman, 1989), which may explain higher female variabil- ity in these traits. However, if estrus status affects traits through variation in hormone levels, we would expect to also find higher female variability in physiological and hematological traits. This was not the case in our dataset. Interestingly, however, eye morphology (structural traits, which should fluctuate little across the estrous cycle) also appeared to be more variable in females than males, but little is known about sex differences in ocular traits in general (Wagner et al., 2008; Shaqiri et al., 2018). Overall, we find no consistent support for the female estrus-mediated variability hypothesis.
In line with our findings, recent studies have refuted the prediction of higher female variability (Prendergast et al., 2014; Smarr et al., 2017; Beery and Zucker, 2011; Becker et al., 2016; Beery, 2018). For example, several rodent studies have found that males are more variable than females (Prendergast et al., 2014; Smarr et al., 2017; Becker et al., 2016; Beery, 2018; Fritz et al., 2017; Mogil and Chanda, 2005). Further studies should investigate whether higher female variability in immunological traits is indeed due to the estrous cycle, or generally because of greater between-individual variation (Figure 2).
In general, we found many traits to be sexually dimorphic (Figure 5) in accordance with the previ- ous study, which used the same database (Karp et al., 2017). Although the original study also pro- vided estimates for sex differences in traits both with and without controlling for weight (we did not control for weight; Nakagawa et al., 2017). More specifically, males are larger than females, while females have higher immunological parameters (see Figure 5). Notably, the most sexually dimorphic trait means also show the greatest differences in trait variance (Figures 4 and 5). Indeed, theory pre- dicts that sexually selected traits (e.g. larger body size for males due to male-male competition) are likely more variable, as these traits are often condition-dependent (Rowe and Houle, 1996). There- fore, this sex difference in variability could be more pronounced under natural conditions compared to laboratory settings. This relationship may explain why male-biased morphological traits are larger and more variable.

### Eco-evolutionary implications
We have used lnCVR values to compare phenotypic variability (CV) between the sexes. When lnCVR is used for fitness-related traits, it can signify sex differences in the ‘opportunity for selection’ between females and males (Rowe and Houle, 1996). If we assume that phenotypic variation (i.e. variability in traits) has a heritable basis, then large ratios of lnCVR may indicate differences in the evolutionary potential of each sex to respond to selection, at least in the short term (Hansen and Houle, 2008). For example, more variable morphological traits of males could potentially provide them with better capacity than females to adapt morphologically to a changing climate. We note, however, that in our study, lnCVR reflects sex differences in trait variability within strains, such that the variability differences we observe between the sexes may be partially the result of phenotypic plasticity.
Demographic parameters, such as age-dependent mortality rate (Lemaıˆtre et al., 2020) can often be different for each sex. For example, a study on European sparrowhawks found that variability in mortality was higher in females compared to males (Colchero et al., 2017). In this species, sex-spe- cific variation affects age-dependent mortality and results in higher average female life expectancy. Therefore, population dynamic models, which make predictions about how populations change in their size over time, should take sex differences in variability into account to produce more accurate predictions (Caswell and Weeks, 1986; Lindstro ̈m and Kokko, 1998). In our rapidly changing world, better predictions on population dynamics are vital for understanding whether climate change is likely to result in population extinction and lead to further biodiversity loss.

### Statistical and practical implications
It is now mandatory to include both sexes in biomedical experiments and clinical trials funded by the NIH, unless there exists strong justification against the inclusion of both sexes (NIH, 2015a; NIH, 2015b). In order to conduct meaningful research and make sound clinical recommendations for both male and female patients, it is necessary to understand both how trait means and variances dif- fer between the sexes. If one sex is systematically more variable in a trait of interest than the other, then experiments should be designed to accommodate relative differences in statistical power between the sexes (which has not been considered before, see Flanagan, 2014; Klein et al., 2015; Prendergast et al., 2014; Shansky and Woolley, 2016). For example, female immunological traits are generally more variable (i.e. having higher CV and SD). Therefore, in an experiment measuring immunological traits, we would need to include a larger sample (N) of females than males (N[female] > N[male]; N[total] = N[female] + N[male]) to achieve the same power as when the experiment only includes males (N[total*] = 2N[male]). In other words, in an experiment with both sexes we would need a larger sample size than the same experiment with males only (N[total] > N[total*]).
To help researchers adjust their sex-specific sample size to achieve optimal statistical power, we provide an online tool (ShinyApp; https://bit.ly/sex-difference). This tool may serve as a starting point for checking baseline variability for each sex in mice. The sex bias (indicated by the % differ- ence between the sexes) is provided for separate traits, procedures, and functional groups. These meta-analytic results are based on our analyses of more than 2 million rodent data points, from 26,916 individual mice. We note, however, that variability in a trait measured in untreated individuals maintained under carefully standardized environmental conditions, as reported here, may not directly translate into the same variability when measured in experimentally treated individuals, or individuals exposed to a range of environments (i.e. natural populations or human cohorts). Further, these estimates are overall mean differences across strains and locations. Therefore, these may not be particularly informative if one’s experiment only includes one specific strain. Nonetheless, we point out that our estimates may be useful in the light of a recent recommendation of using ‘hetero- genization’ where many different strains are systematically included (i.e. randomized complete block design) to increase the robustness of experimental results (Voelkl et al., 2020). However, note that an experiment with heterogenization might only include a few strains with several animals per strain. Even in such a case, using just a few strains, our tool could provide potentially useful benchmarks. Incidentally, heterogenization would be key to making one’s experimental outcome more generaliz- able (Webster and Rutz, 2020).
Importantly, when two groups (e.g. males and females) show differences in variability, we violate homogeneity of variance or homoscedasticity assumptions. Such a violation is detrimental because it leads to a higher Type I error rate. Therefore, we should consider incorporating heteroscedasticity (different variances) explicitly or using robust estimators of variance (also known as ‘the sandwich variance estimator’) to prevent an inflated Type I error rate (Cleasby and Nakagawa, 2011), espe- cially when we compare traits between the sexes.

## Conclusion
We have shown that sex biases in variability occur in many mouse traits, but that the directions of those biases differ between traits. Neither the ‘greater male variability’ nor the ‘estrus-mediated var- iability’ hypothesis provides a general explanation for sex differences in trait variability. Instead, we have found that the direction of the sex bias varies across traits and among trait types (Figures 4 and 5). Our findings have important ecological and evolutionary ramifications. If the differences in variability correspond to the potential of each sex to respond to changes in specific environments, this sex difference needs to be incorporated into demographic and population dynamic modelling. Moreover, in the (bio-)medical field, our results should inform decisions during study design by pro- viding more rigorous power analyses that allow researchers to incorporate sex-specific differences for sample size. We believe that taking sex differences in trait variability into account will help avoid misleading conclusions and provide new insights into sex differences across many areas of biological and bio-medical research. Ultimately, such considerations will not only better our knowledge, but also close the current gaps in our biased knowledge (Tannenbaum et al., 2019).

## Materials and methods
### Data selection and process
The IMPC (International Mouse Phenotyping Consortium) provides a comprehensive catalogue of mammalian gene function for investigating the genetics of health and disease, by systematically col- lecting phenotypes of knock-out and wildtype mice. To investigate differences in trait variability between the sexes, we only considered the data for wildtype control mice. We retrieved the dataset from the IMPC server in June 2018 and filtered it to contain non-categorical traits for wildtype mice. The initial dataset comprised over 2,500,000 data points for 340 traits. In cases where multiple meas- urements were taken over time, data cleaning started with selecting single measurements for each individual and trait. In these cases, we selected the measurement closest to ‘100 days of age’. All data are from unstaged females (with no information about the stage of their estrous cycle). We excluded data for juvenile and unsexed mice (Figure 3A; this dataset and scripts can be found on https://rpubs.com/SusZaj/ESF; https://bit.ly/code-mice-sex-diff; raw data: https://doi.org/10.5281/ zenodo.3759701).

### Grouping and effect-size calculation
We created a grouping variable called ‘population’ (Figure 3B). A population comprised a group of individuals belonging to a distinct wildtype strain maintained at one particular location (institution); populations were identified for every trait of interest. Our data were derived from 11 different loca- tions/institutions, and a given location/institution could provide data on multiple populations (see Supplementary file 1, Table 1 for details on numbers of strains and institutions). We included only populations that contained data points for at least six individuals, and which had information for members of both sexes; further, populations for a particular trait had to come from at least two insti- tutions to be eligible for inclusion. After this selection process, the dataset contained 2,300,000 data points across 232 traits. Overall, we meta-analysed traits with between 2–18 effect sizes (mean = 9.09 effects, SD = 4.47). However, each meta-analysis contained a total number of individ- ual mice that ranged from 83/91 to 13467/13449 (males/females). While a minimum of N = 6 mice were used to create effect sizes for any given group (male or female), in reality samples sizes of male/female groups were much larger (males: mean = 396.66 (SD = 238.23), median = 465.56;females: mean = 407.35 (SD = 240.31), median = 543.89). We used the function escalc in the R pack- age, metafor (Viechtbauer, 2010) to obtain lnCVR, lnVR and lnRR and their corresponding sampling variance for each trait for each population; we worked in the R environment for data cleaning, proc- essing and analyses (R Development Core Team, 2017, version 3.6.0; for the versions of all the soft- ware packages used for this article and all the details and code for the statistical analyses, see the Source code 1 and repositories). As mentioned above, the use of ratio-based effect sizes, such as lnCVR, lnVR and lnRR, controls for baseline changes over time and space, assuming that these changes affect males and females similarly. However, we acknowledge that we could not test this assumption.

### Meta-analyses: overview
We conducted meta-analyses at two different levels (Figure 3C–J). First, we conducted a meta-anal- ysis for each trait for all three effect-size types (lnRR, lnVR and lnCVR), calculated at the ‘population’ level (i.e. using population as a unit of analysis). Second, we statistically amalgamated overall effect sizes estimated at each trait (i.e. overall trait means as a unit of analysis) after accounting for depen- dence among traits. In other words, we conducted second-order meta-analyses (Nakagawa et al., 2019). We used the second-order meta-analyses for three different purposes: (A) estimating overall sex biases in variance (lnCVR and lnVR) and mean (lnRR) in the nine functional groups (for details, see below) and in all these groups combined (the overall estimates); (B) visualizing heterogeneities across populations for the three types of effect size in the nine functional trait groups, which comple- mented the first set of analyses (Figure 3I, Table 6 in Supplementary file 1); and (C) when traits were found to be significantly sex-biased, grouping such traits into either male-biased and female- biased traits, and then, estimating overall magnitudes of sex bias for both sexes again for the nine functional trait groups. Only the first second-order meta-analysis (A) directly related to the testing of our hypotheses, results of B and C are found in Supplementary file 1 and figures and reported in our freely accessible code.

### Meta-analyses: population as an analysis unit
To obtain degree of sex bias for each trait mean and variance (Figure 3C), we used the function rma.mv in the R package metafor (Viechtbauer, 2010) by fitting the following multilevel meta-ana- lytic model, an extension of random-effects models (sensu Nakagawa and Santos, 2012):
ESi ~ 1 + (1 | Strainj) + (1 | Locationk) + (1 | Uniti) + Errori, where ‘ESi’ is the ith effect size (i.e. lnCVR, lnVR and lnRR) for each of 232 traits, the ‘1’ is the overall intercept (other ‘1’s are random intercepts for the following random effects), ‘Strainj’ is a random effect for the jth strain of mice (among nine strains), ‘Locationk’ is a random effect for the kth location (among 11 institutions), ‘Uniti’ is a residual (or effect-size level or ‘population-level’ random effect) for the ith effect size, ‘Errori’ is a random effect of the known sampling error for the ith effect size. Given the model above, meta-ana- lytic results had two components: (1) overall means with standard errors (95% confidence intervals), and (2) total heterogeneity (the sum of the three variance components, which is estimated for the random effects). Note that overall means indicate average (marginalised) effect sizes over different strains and locations, and total heterogeneities reflect variation around overall means due to differ- ent strains and locations.
We excluded traits which did not carry useful information for this study (i.e. fixed traits, such as number of vertebrae, digits, ribs and other traits that were not variable across wildtype mice; note that this may be different for knock-down mutant strains) or where the meta-analytic model for the trait of interest did not converge, most likely due to small sample size from the dataset (14 traits, see SI Appendix, for details: Meta-analyses; 1. Population as analysis unit). We therefore obtained a dataset containing meta-analytic results for 218 traits, at this stage, to use for our second-order meta-analyses (Figure 3D).

### Meta-analyses: accounting for correlated traits
Our dataset of meta-analytic results included a large number of non-independent traits. To account for dependence, we identified 90 out of 218 traits, and organized them into 19 trait sub-groups (containing 2–10 correlated traits, see Figure 3E). For example, many measurements (i.e. traits) from hematological and immunological assays were hierarchically clustered or overlapped with each other (e.g. cell type A, B and A+B). We combined the meta-analytic results from 90 traits into 19 meta- analytic results (Figure 3F) using the function robu in the R package robumeta with the assumption of sampling errors being correlated with the default value of r = 0.8 (Fisher et al., 2017). Conse- quently, our final dataset for secondary meta-analyses contained 147 traits (i.e. the newly condensed 19 plus the remaining 128 independent traits, see Figure 3, Supplementary file 1, Table 2), which we assume to be independent of each other.
Second-order meta-analyses: trait as an analysis unit
We created our nine overarching functional groups of traits (Figure 3G) by condensing the IMPC’s 26 procedural categories (‘procedures’) into related clusters. The categories were based on proce- dures that were biologically related, in conjunction with measurement techniques and the number of available traits in each category (see Supplementary file 1, Table 3 for a list of clustered traits, procedures and grouping terms). To test our two hypotheses about how trait variability changes in relation to sex, we estimated overall effect sizes for nine functional groups by aggregating meta-ana- lytic results via ‘classical’ random-effect models using the function rma.uni in the R package metafor (Viechtbauer, 2010). In other words, we conducted three sets of 10 second-order meta-analyses (i.e. meta-analyzing 3 types of effect size: lnRR, lnVR and lnCVR for nine functional groups and one for all the groups combined, Figure 3H). Although we present the frequencies of male- and female- biased traits in Figure 4A, we did not run inferential statistical tests on these counts because such tests would be considered as vote-counting, which has been severely criticised in the meta-analytic literature (Higgins, 2019).

### Acknowledgements
SRKZ and ML were supported by the Australian (ARC) Discovery Grant (DP180100818) awarded to SN. JM was supported by EMBL core funding and the NIH Common Fund (UM1-H G006370). AMS was supported by an ARC fellowship (DE180101520).

## References
Ahmad AA, Randall MD, Roberts RE. 2017. Sex differences in the role of phospholipase A2 -dependent arachidonic acid pathway in the perivascular adipose tissue function in pigs. The Journal of Physiology 595:6623–6634. DOI: https://doi.org/10.1113/JP274831, PMID: 28877347.

Becker JB, Prendergast BJ, Liang JW. 2016. Female rats are not more variable than male rats: a meta-analysis of neuroscience studies. Biology of Sex Differences 7:34. DOI: https://doi.org/10.1186/s13293-016-0087-5, PMID: 27468347.

Beery AK. 2018. Inclusion of females does not increase variability in rodent research studies. Current Opinion in Behavioral Sciences 23:143–149. DOI: https://doi.org/10.1016/j.cobeha.2018.06.016.

Beery AK, Zucker I. 2011. Sex bias in neuroscience and biomedical research. Neuroscience & Biobehavioral Reviews 35:565–572. DOI: https://doi.org/10.1016/j.neubiorev.2010.07.002, PMID: 20620164.

Caswell H, Weeks DE. 1986. Two-Sex models: chaos, extinction, and other dynamic consequences of sex. The American Naturalist 128:707–735. DOI: https://doi.org/10.1086/284598.

Clayton JA. 2016. Studying both sexes: a guiding principle for biomedicine. The FASEB Journal 30:519–524. DOI: https://doi.org/10.1096/fj.15-279554.

Clayton JA, Collins FS. 2014. Policy: NIH to balance sex in cell and animal studies. Nature 509:282–283. DOI: https://doi.org/10.1038/509282a, PMID: 24834516.

Cleasby IR, Nakagawa S. 2011. Neglected biological patterns in the residuals. Behavioral Ecology and Sociobiology 65:2361–2372. DOI:https://doi.org/10.1007/s00265-011-1254-7.

Colchero F, Aliaga AE, Jones OR, Conde DA. 2017. Individual heterogeneity determines sex differences in mortality in a monogamous bird with reversed sexual dimorphism. Journal of Animal Ecology 86:899–907. DOI: https://doi.org/10.1111/1365-2656.12677, PMID: 28393353.

Cuervo JJ, Møller AP. 1999. Phenotypic variation and fluctuating asymmetry in sexually dimorphic feather ornaments in relation to sex and mating system. Biological Journal of the Linnean Society 68:505–529. DOI: https://doi.org/10.1111/j.1095-8312.1999.tb01186.x.

Cuervo JJ, Møller AP. 2001. Components of phenotypic variation in avian ornamental and non-ornamental feathers. Evolutionary Ecology 15:53–72. DOI: https://doi.org/10.1023/A:1011913804309.

Darwin C. 1871. The descent of man and Selection in Relation to Sex. Journal of Anatomy and Physiology 5:363– 372.

Dickinson ME, Flenniken AM, Ji X, Teboul L, Wong MD, White JK, Meehan TF, Weninger WJ, Westerberg H, Adissu H, Baker CN, Bower L, Brown JM, Caddle LB, Chiani F, Clary D, Cleak J, Daly MJ, Denegre JM, Doe B, et al. 2016. High-throughput discovery of novel developmental phenotypes. Nature 537:508–514. DOI: https:// doi.org/10.1038/nature19356.

Dorris DM, Cao J, Willett JA, Hauser CA, Meitzen J. 2015. Intrinsic excitability varies by sex in prepubertal striatal medium spiny neurons. Journal of Neurophysiology 113:720–729. DOI: https://doi.org/10.1152/jn. 00687.2014, PMID: 25376786.

Fisher Z, Tipton E, Zhipeng H, Fisher MZ. 2017. robumeta. 2.0. Robust Variance Meta-Regression. https://cran.r- project.org/web/packages/robumeta/index.html. 
Flanagan KL. 2014. Sexual dimorphism in biomedical research: a call to analyse by sex. Transactions of the Royal Society of Tropical Medicine and Hygiene 108:385–387. DOI: https://doi.org/10.1093/trstmh/tru079, PMID: 24 934286.

Foltin RW, Evans SM. 2018. Sex differences in the anorexigenic effects of dexfenfluramine and amphetamine in baboons. Experimental and Clinical Psychopharmacology 26:335–340. DOI: https://doi.org/10.1037/ pha0000201, PMID: 29792471.

Fritz A, Amrein I, Wolfer DP. 2017. Similar reliability and equivalent performance of female and male mice in the open field and water-maze place navigation task. American Journal of Medical Genetics Part C: Seminars in Medical Genetics 175:380–391. DOI: https://doi.org/10.1002/ajmg.c.31565.

Grossman C. 1989. Possible underlying mechanisms of sexual dimorphism in the immune response, fact and hypothesis. Journal of Steroid Biochemistry 34:241–251. DOI: https://doi.org/10.1016/0022-4731(89)90088-5, PMID: 2696846.

Hansen TF, Houle D. 2008. Measuring and comparing evolvability and constraint in multivariate characters. Journal of Evolutionary Biology 21:1201–1219. DOI: https://doi.org/10.1111/j.1420-9101.2008.01573.x, PMID: 18662244.

Hedges LV, Nowell A. 1995. Sex differences in mental test scores, variability, and numbers of high-scoring individuals. Science 269:41–45. DOI: https://doi.org/10.1126/science.7604277, PMID: 7604277.

Higgins JP. 2019. Cochrane Handbook for Systematic Reviews of Interventions. John Wiley & Sons. DOI: https:// doi.org/10.1002/9781119536604.

Ingvorsen C, Karp NA, Lelliott CJ. 2017. The role of sex and body weight on the metabolic effects of high-fat diet in C57BL/6N mice. Nutrition & Diabetes 7:e261. DOI: https://doi.org/10.1038/nutd.2017.6, PMID: 283 94359.

Itoh Y, Arnold AP. 2015. Are females more variable than males in gene expression? Meta-analysis of microarray datasets. Biology of Sex Differences 6:8. DOI: https://doi.org/10.1186/s13293-015-0036-8, PMID: 26557976.

Johnson W, Carothers A, Deary IJ. 2008. Sex differences in variability in general intelligence: a new look at theold question. Perspectives on Psychological Science 3:518–531. DOI: https://doi.org/10.1111/j.1745-6924.2008.00096.x, PMID: 26158978.

Karp NA, Mason J, Beaudet AL, Benjamini Y, Bower L, Braun RE, Brown SDM, Chesler EJ, Dickinson ME,Flenniken AM, Fuchs H, Angelis MH, Gao X, Guo S, Greenaway S, Heller R, Herault Y, Justice MJ, Kurbatova N, Lelliott CJ, et al. 2017. Prevalence of sexual dimorphism in mammalian phenotypic traits. Nature Communications 8:15475. DOI: https://doi.org/10.1038/ncomms15475, PMID: 28650954.

Klein SL, Schiebinger L, Stefanick ML, Cahill L, Danska J, de Vries GJ, Kibbe MR, McCarthy MM, Mogil JS, Woodruff TK, Zucker I. 2015. Opinion: sex inclusion in basic research drives discovery. Proceedings of the National Academy of Sciences 112:5257–5258. DOI: https://doi.org/10.1073/pnas.1502843112, PMID: 25 902532. 
Lehre AC, Lehre KP, Laake P, Danbolt NC. 2009. Greater intrasex phenotype variability in males than in females is a fundamental aspect of the gender differences in humans. Developmental Psychobiology 51:198–206. DOI: https://doi.org/10.1002/dev.20358, PMID: 19031491.

Lemaˆıtre JF, Ronget V, Tidie` re M, Allaine ́ D, Berger V, Cohas A, Colchero F, Conde DA, Garratt M, Liker A, Marais GAB, Scheuerlein A, Sze ́ kely T, Gaillard JM. 2020. Sex differences in adult lifespan and aging rates of mortality across wild mammals. Proceedings of the National Academy of Sciences 117:8546–8553.
DOI: https://doi.org/10.1073/pnas.1911999117, PMID: 32205429.

Lindstrom J, Kokko H. 1998. Sexual reproduction and population dynamics: the role of polygyny and demographic sex differences. Proceedings of the Royal Society of London. Series B: Biological Sciences 265: 483–488. DOI: https://doi.org/10.1098/rspb.1998.0320.

Mogil JS, Chanda ML. 2005. The case for the inclusion of female subjects in basic science studies of pain. Pain 117:1–5. DOI: https://doi.org/10.1016/j.pain.2005.06.020, PMID: 16098670.

Nakagawa S, Poulin R, Mengersen K, Reinhold K, Engqvist L, Lagisz M, Senior AM. 2015. Meta-analysis of variation: ecological and evolutionary applications and beyond. Methods in Ecology and Evolution 6:143–152. DOI: https://doi.org/10.1111/2041-210X.12309.

Nakagawa S, Noble DW, Senior AM, Lagisz M. 2017. Meta-evaluation of meta-analysis: ten appraisal questions for biologists. BMC Biology 15:18. DOI: https://doi.org/10.1186/s12915-017-0357-7, PMID: 28257642.

Nakagawa S, Samarasinghe G, Haddaway NR, Westgate MJ, O’Dea RE, Noble DWA, Lagisz M. 2019. Research weaving: visualizing the future of research synthesis. Trends in Ecology & Evolution 34:224–238. DOI: https:// doi.org/10.1016/j.tree.2018.11.007, PMID: 30580972.

Nakagawa S, Santos ESA. 2012. Methodological issues and advances in biological meta-analysis. Evolutionary Ecology 26:1253–1274. DOI: https://doi.org/10.1007/s10682-012-9555-5.

NIH. 2015a. Consideration of Sex as a Biological Variable in NIH-Funded Research, Notice NOT-OD-102: National Institutes of Health.

NIH. 2015b. Enhancing Reproducibility Through Rigor and Transparency, Notice NOT-OD-103: National Institutes of Health.

Nowogrodzki A. 2017. Inequality in medicine. Nature 550:S18–S19. DOI: https://doi.org/10.1038/550S18a Pomiankowski A, Moller AP. 1995. A resolution of the lek paradox. Proceedings of the Royal Society of London. Series B, Containing Papers of a Biological Character 260:21–29. DOI: https://doi.org/10.1098/rspb.1995.0054.

Prendergast BJ, Onishi KG, Zucker I. 2014. Female mice liberated for inclusion in neuroscience and biomedical research. Neuroscience & Biobehavioral Reviews 40:1–5. DOI: https://doi.org/10.1016/j.neubiorev.2014.01.001, PMID: 24456941.

R Development Core Team. 2017. R: A Language and Environment for Statistical Computing. Vienna, Austria, R Foundation for Statistical Computing. http://www.r-project.org.

Reinhold K, Engqvist L. 2013. The variability is in the sex chromosomes. Evolution 67:3662–3668. DOI: https:// doi.org/10.1111/evo.12224. 
Robinson CM, Wang Y, Pfeiffer JK. 2017. Sex-Dependent intestinal replication of an enteric virus. Journal of Virology 91:e02101-16. DOI: https://doi.org/10.1128/JVI.02101-16, PMID: 28100612.

Rowe L, Houle D. 1996. The lek paradox and the capture of genetic variance by condition dependent traits. Proceedings of the Royal Society B: Biological Sciences 263:1415–1421. DOI: https://doi.org/10.1098/rspb. 1996.0207.

Senior AM, Viechtbauer W, Nakagawa S. 2020. Revisiting and expanding the meta-analysis of variation: the log coefficient of variation ratio. Research Synthesis Methods 11:1423:553–567. DOI: https://doi.org/10.1002/jrsm. 1423.

Shansky RM, Woolley CS. 2016. Considering sex as a biological variable will be valuable for neuroscience research. The Journal of Neuroscience 36:11817–11822. DOI: https://doi.org/10.1523/JNEUROSCI.1390-16. 2016, PMID: 27881768.

Shaqiri A, Roinishvili M, Grzeczkowski L, Chkonia E, Pilz K, Mohr C, Brand A, Kunchulia M, Herzog MH. 2018. Sex-related differences in vision are heterogeneous. Scientific Reports 8:8. DOI: https://doi.org/10.1038/ s41598-018-25298-8, PMID: 29760400.

Smarr BL, Grant AD, Zucker I, Prendergast BJ, Kriegsfeld LJ. 2017. Sex differences in variability across timescales in BALB/c mice. Biology of Sex Differences 8:3. DOI: https://doi.org/10.1186/s13293-016-0125-3, PMID: 2 8203366.

Tannenbaum C, Ellis RP, Eyssel F, Zou J, Schiebinger L. 2019. Sex and gender analysis improves science and engineering. Nature 575:137–146. DOI: https://doi.org/10.1038/s41586-019-1657-6, PMID: 31695204.

Thompson LP, Chen L, Polster BM, Pinkas G, Song H. 2018. Prenatal hypoxia impairs cardiac mitochondrial and ventricular function in guinea pig offspring in a sex-related manner. American Journal of Physiology. Regulatory, Integrative and Comparative Physiology 315:R1232–R1241. DOI: https://doi.org/10.1152/ajpregu. 00224.2018, PMID: 30365351.

Tomkins JL, Radwan J, Kotiaho JS, Tregenza T. 2004. Genic capture and resolving the lek paradox. Trends in Ecology & Evolution 19:323–328. DOI: https://doi.org/10.1016/j.tree.2004.03.029, PMID: 16701278.

Viechtbauer W. 2010. Conducting Meta-Analyses in R with the metafor Package. Journal of Statistical Software 36:i03. DOI: https://doi.org/10.18637/jss.v036.i03. 
Voelkl B, Altman NS, Forsman A, Forstmeier W, Gurevitch J, Jaric I, Karp NA, Kas MJ, Schielzeth H, Van de Casteele T, Wu ̈ rbel H. 2020. Reproducibility of animal research in light of biological variation. Nature Reviews Neuroscience 21:384–393. DOI: https://doi.org/10.1038/s41583-020-0313-3.

Wagner H, Fink BA, Zadnik K. 2008. Sex- and gender-based differences in healthy and diseased eyes. Optometry - Journal of the American Optometric Association 79:636–652. DOI: https://doi.org/10.1016/j.optm.2008.01. 024, PMID: 19811761.

Webster MM, Rutz C. 2020. How STRANGE are your study animals? Nature 582:337–340. DOI: https://doi.org/ 10.1038/d41586-020-01751-5, PMID: 32541916.

Zucker I, Prendergast BJ. 2020. Sex differences in pharmacokinetics predict adverse drug reactions in women. Biology of Sex Differences 11:32. DOI: https://doi.org/10.1186/s13293-020-00308-5, PMID: 32503637.

Zuk M, McKean KA. 1996. Sex differences in parasite infections: patterns and processes. International Journal for Parasitology 26:1009–1024. DOI: https://doi.org/10.1016/S0020-7519(96)80001-4, PMID: 8982783.

### 2021-04-05 executableMS/ms_v1.rmd
Update ms_v1.rmd

@@
   - Division of Ecology and Evolution, Research School of Biology, Australian National University, Canberra, Australia
-
-bibilography: SexDiffBib.bib
-
 ---
@@
 Indeed, the National Insti- tutes of Health (NIH) have now implemented new guidelines for animal and human research study designs, requiring that sex be included as a biological variable (Clayton, 2016; Clayton and Collins, 2014; NIH, 2015a).
-[@moore2001]
 When comparing the sexes, biologists generally focus on mean differences in trait values, placing little or no emphasis on sex differences in trait variability (see Figure 1 for a diagram explaining differences in means and variances).
@@
 
- this stupid figure has to get embedded Fig1 (./executableMS/Figures/Figure 1.png).
+ this stupid figure has to get embedded    
+ ![Fig1](./executableMS/Figures/Figure 1.png)
 
@@
 
-Fig2(./executableMS/Figures/Figure 2.png)
+![Fig2](./executableMS/Figures/Figure 2.png)
 

### 2021-04-05 executableMS/ms_v1.rmd
Update ms_v1.rmd

@@
  this stupid figure has to get embedded    
- ![Fig1](./executableMS/Figures/Figure 1.png)
+ Fig (/Figures/Figure 1.png)
+
+```{r Fig1, echo = FALSE, fig.width = 4, fig.height = 8, fig.cap=Figure 1]"}
+include_graphics(here("Figures", "Figure 1.png"))
+```
 
@@
 
-![Fig2](./executableMS/Figures/Figure 2.png)
+ (/Figures/Figure 2.png)
+ ```{r Fig2, echo = FALSE, fig.width = 4, fig.height = 4, fig.cap=Figure 2]"}
+include_graphics(here("Figures", "Figure 2.png"))
+```
 

### 2021-04-05 executableMS/ms_v1.rmd
Update ms_v1.rmd

@@
  this stupid figure has to get embedded    
- Fig (/Figures/Figure 1.png)
+ ![Fig1](https://github.com/itchyshin/mice_sex_diff/edit/master/executableMS/Figures/Figure 1.png)
 
@@
 
- (/Figures/Figure 2.png)
+ ![Fig2](https://github.com/itchyshin/mice_sex_diff/edit/master/executableMS/Figures/Figure 2.png)
  ```{r Fig2, echo = FALSE, fig.width = 4, fig.height = 4, fig.cap=Figure 2]"}

### 2021-04-05 executableMS/ms_v1.rmd
Update ms_v1.rmd

--- 2021-04-05 executableMS/ms_v1.rmd
@@
  this stupid figure has to get embedded    
- ![Fig1](./executableMS/Figures/Figure 1.png)
+ ![Fig1](https://github.com/itchyshin/mice_sex_diff/edit/master/executableMS/Figures/Figure%201..png)
 
@@
 
-![Fig2](./executableMS/Figures/Figure 2.png)
+ ![Fig2](https://github.com/itchyshin/mice_sex_diff/edit/master/executableMS/Figures/Figure%202.png)
 
@@
 To obtain robust estimates of sex dif- ferences, we only used data on traits that were measured in at least two different institutions (see workflow diagram, Figure 3).
-Our dataset comprised 218 continuous traits (after initial data cleaning and pre-processing; Fig- ure 3).
+
+ ![Fig3](https://github.com/itchyshin/mice_sex_diff/edit/master/executableMS/Figures/Figure%203.png)
+
+Our dataset comprised 218 continuous traits (after initial data cleaning and pre-processing; Figure 3).
 It contains information from 26,916 mice from nine wildtype strains that were studied across 11 institutions.

### 2021-04-05 executableMS/ms_v1.rmd
Update ms_v1.rmd

@@
  this stupid figure has to get embedded    
- ![Fig1](https://github.com/itchyshin/mice_sex_diff/edit/master/executableMS/Figures/Figure%201..png)
+ ![Fig1](/Figures/Figure%201.png)
 
@@
 
- ![Fig2](https://github.com/itchyshin/mice_sex_diff/edit/master/executableMS/Figures/Figure%202.png)
+ ![Fig2](./Figures/Figure%202.png)
 

### 2021-04-05 executableMS/ms_v1.rmd
Update ms_v1.rmd

@@
 ## Introduction
-Sex differences arise because selection acts on the two sexes differently, especially on traits associ- ated with mating and reproduction (Darwin, 1871).
+Sex differences arise because selection acts on the two sexes differently, especially on traits associated with mating and reproduction (Darwin, 1871).
 Therefore, sex differences are widespread, a fact which is unsurprising to any evolutionary biologist.
@@
  this stupid figure has to get embedded    
- ![Fig1](/Figures/Figure%201.png)
+ ![Fig1](/Figures/Figure1.png)
 
@@
 
- ![Fig2](./Figures/Figure%202.png)
+ ![Fig2](/Figures/Figure2.png)
 
@@
 
- ![Fig3](https://github.com/itchyshin/mice_sex_diff/edit/master/executableMS/Figures/Figure%203.png)
+ ![Fig3](/Figures/Figure3.png)
 

### 2021-04-05 executableMS/ms_v1.rmd
Rename ms_v1.md to ms_v1.rmd

@@
 However, scientists in many (bio-)medical fields have not necessarily regarded sex as a biological factor of intrinsic interest (Clayton, 2016; Flanagan, 2014; Karp et al., 2017; Klein et al., 2015; Prendergast et al., 2014; Shansky and Woolley, 2016).
-Therefore, many (bio-)medical studies have only been conducted with male sub- jects.
+Therefore, many (bio-)medical studies have only been conducted with male subjects.
 Consequently, our knowledge is biased.
@@
  this stupid figure has to get embedded    
- ![Fig1](/Figures/Figure1.png)
+ ![Fig1](./Figures/Figure1.png)
 
@@
 
- ![Fig2](/Figures/Figure2.png)
+ ![Fig2](./Figures/Figure2.png)
 
@@
 
- ![Fig3](/Figures/Figure3.png)
+ ![Fig3](./Figures/Figure3.png)
 

### 2021-04-05 executableMS/ms_v1.rmd
Update ms_v1.rmd
Update and rename ms_v1.md to ms_v1.rmd

@@
 We combined mouse strain/institution information to create a biological grouping variable (referred to as ‘population’ in Figure 3B; see also Supplementary file 1, Table 1 for details), and the mean and variance of a trait for each population was quantified.
-We assigned traits accord- ing to related procedures into functionally and/or procedurally related trait groups to enhance interpretability (referred to as ‘functional groups’ hereafter; see also Figure 3G).
+We assigned traits according to related procedures into functionally and/or procedurally related trait groups to enhance interpretability (referred to as ‘functional groups’ hereafter; see also Figure 3G).
 Our nine functional trait groups were: behaviour, morphology, metabolism, physiology, immunology, hematology, heart, hearing and eye (for the rationale of these functional groups and related details, see Methods and Supplementary file 1, Table 3).
+
+```{r packages1, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE, messages=FALSE, paged.print=FALSE}
+library(pacman)
+pacman::p_load(readr, dplyr,metafor, devtools, purrr, tidyverse, tidyr, tibble, kableExtra, robumeta, ggpubr, ggplot2, png, grid, here, knitr, pander, splus2R)
+data <- readRDS(here("export", "data_clean.rds")) 
+procedures <- read_csv(here("data", "procedures.csv"))
+
+n <- length(unique(data$id))
+# Create dataframe to store results
+results_alltraits_grouping <- 
+    data.frame(tibble(id = 1:n, 
+           lnCVR=0, lnCVR_lower=0, lnCVR_upper=0, lnCVR_se=0, lnCVR_I2=0,
+            lnVR=0,  lnVR_lower=0,  lnVR_upper=0, lnVR_se=0, lnVR_I2=0,
+            lnRR=0,  lnRR_lower=0,  lnRR_upper=0, lnRR_se=0, lnRR_I2=0,
+           k=0, trait=0, male_N = 0, female_N=0, min_male_N = 0, max_male_N = 0, mean_male_N = 0,
+              min_female_N = 0, max_female_N = 0, mean_female_N = 0))
+for (t in 1:n) {
+  tryCatch(
+    {
+      results <- data %>%
+                 data_subset_parameterid_individual_by_age(t) %>%
+                 calculate_population_stats()                 %>%
+                 create_meta_analysis_effect_sizes()          %>%
+                 mutate(err = seq_len(n()))
+      # lnCVR,  log repsonse-ratio of the coefficient of variance
+      cvr <- metafor::rma.mv(yi = effect_size_CVR, V = sample_variance_CVR, 
+                             random = list(~ 1 | strain_name, 
+                                           ~ 1 | production_center, 
+                                           ~ 1 | err), 
+                             control = list(optimizer = "optim", 
+                                            optmethod = "Nelder-Mead", 
+                                            maxit = 1000), 
+                             verbose = F, data = results)
+
+# lnVR, comparison of standard deviations
+      cv <- metafor::rma.mv(yi = effect_size_VR, V = sample_variance_VR,
+                            random = list(~ 1 | strain_name, 
+                                          ~ 1 | production_center, 
+                                          ~ 1 | err), 
+                            control = list(optimizer = "optim", 
+                                           optmethod = "Nelder-Mead", 
+                                           maxit = 1000), 
+                            verbose = F, data = results)
+      # for means, lnRR
+      means <- metafor::rma.mv(yi = effect_size_ROM, V = sample_variance_ROM, 
+                               random = list(~ 1 | strain_name, 
+                                             ~ 1 | production_center, 
+                                             ~ 1 | err), 
+                               control = list(optimizer = "optim", 
+                                              optmethod = "Nelder-Mead", 
+                                              maxit = 1000), 
+                               verbose = F, data = results)
+
+      f <- function(x) unlist(x[c("b", "ci.lb", "ci.ub", "se")])
+
+      extract_I2 <- function(mod){
+                  sigma2 <- mod$sigma2
+                       w <- mod$vi
+                       k <- mod$k
+
+                  sigmaM <- sum(w * (k-1)) / (sum(w)^2 - sum(w^2))
+
+                    I2_tot <- round(sum(sigma2) / sum(sigma2 + sigmaM), digits = 3)*100
+                  return(I2_tot)
+      }
+      results_alltraits_grouping[t, c(2:17,19:26)] <- c(f(cvr),lnCVR_I2 = extract_I2(cvr), f(cv), lnVR_I2 = extract_I2(cv), f(means), lnRR_I2 = extract_I2(means), k=means$k, male_N = sum(results$male_n_ind), female_N = sum(results$female_n_ind), min_male_N = min(results$male_n_ind), max_male_N = max(results$male_n_ind), mean_male_N = mean(results$male_n_ind),
+                                                        min_female_N = min(results$female_n_ind), max_female_N = max(results$female_n_ind), mean_female_N = mean(results$female_n_ind))
+      results_alltraits_grouping[t, 18]   <- unique(results$trait)
+    },
+    error = function(e) {
+      cat("ERROR :", t, conditionMessage(e), "\n")
+    }
+  )
+}
+
+results_alltraits_grouping2 <- 
+  results_alltraits_grouping %>%
+
+  # Join data with results_alltraits_grouping. We filter duplicated id's to get only one unique row per id (and there is one id per parameter_name)
+  left_join(by="id",
+             data %>% 
+             select(id, parameter_group, procedure = procedure_name, procedure_name, parameter_name) %>%  
+             filter(!duplicated(id))) %>%
+
+  # Below we add 'procedure' (from the previously loaded 'procedures.csv') as a variable; n <- length(unique(results_alltraits_grouping2$parameter_name))) should equal 232
+  left_join(by="procedure", 
+            procedures %>% distinct())
+# We exclude 14 parameter names for which metafor models didn't converge ("dp t cells", "mzb (cd21/35 high)"), and of parameters that don't harbour enough variation
+meta_clean <- results_alltraits_grouping2 %>% 
+	            filter(!parameter_name %in% 
+	                     c("dp t cells", "mzb (cd21/35 high)", "number of caudal vertebrae", 
+	                       "number of cervical vertebrae", "number of digits", "number of lumbar vertebrae", 
+	                       "number of pelvic vertebrae", "number of ribs left","number of ribs right", 
+	                       "number of signals", "number of thoracic vertebrae", "total number of acquired events in panel a",
+	                       "total number of acquired events in panel b", "whole arena permanence"))
+# Summary of the cleaned data for 218 traits
+  sd(meta_clean$k)
+  range(meta_clean$male_N)
+  range(meta_clean$female_N)
+  range(meta_clean$lnCVR_I2)
+  range(meta_clean$lnVR_I2)
+  range(meta_clean$lnRR_I2)
+  range(meta_clean$k)
+  mean(meta_clean$mean_male_N)
+  range(meta_clean$min_male_N)
+  median(meta_clean$mean_male_N)
+  sd(meta_clean$mean_male_N)
+  sd(meta_clean$mean_male_N) / sqrt(length(meta_clean$mean_male_N))
+  mean(meta_clean$mean_female_N)
+  median(meta_clean$mean_female_N)
+  range(meta_clean$min_female_N)
+  sd(meta_clean$mean_female_N)
+  sd(meta_clean$mean_female_N) / sqrt(length(meta_clean$mean_female_N))
+
+  meta1_sub <- meta_clean %>%
+  # Add summary of number of parameter names in each parameter group
+  group_by(parameter_group) %>%
+  mutate(par_group_size = length(unique(parameter_name)), 
+         sampleSize = as.numeric(k)) %>% 
+  ungroup() %>% 
+  # Create subsets with > 1 count (par_group_size > 1)
+  filter(par_group_size > 1) # 90 observations
+
+  # Create summary of number of parameter names in each parameter group, and merge back together
+meta1b <-
+  meta1 %>%
+  group_by(parameter_group) %>% 
+  summarize(par_group_size = length(unique(parameter_name, na.rm = TRUE)))
+meta1$par_group_size <- meta1b$par_group_size[match(meta1$parameter_group, meta1b$parameter_group)]
+# Create subsets with > 1 count (par_group_size > 1) 
+           meta1_sub <- subset(meta1,par_group_size >1) # 90 observations   
+meta1_sub$sampleSize <- as.numeric(meta1_sub$k)
+# Nesting and meta-analyses on correlated traits, using robumeta
+n_count <- meta1_sub %>%
+           group_by(parameter_group) %>%
+           mutate(raw_N = sum(sampleSize)) %>%
+           nest() %>%
+           ungroup()
+model_count <- n_count %>%
+  mutate(
+     model_lnRR = map(data, ~ robu(.x$lnRR ~ 1,  data = .x, studynum = .x$id, modelweights = c("CORR"), rho = 0.8, small = TRUE, var.eff.size = (.x$lnRR_se)^2)),
+     model_lnVR = map(data, ~ robu(.x$lnVR ~ 1,  data = .x, studynum = .x$id, modelweights = c("CORR"), rho = 0.8, small = TRUE, var.eff.size = (.x$lnVR_se)^2)),
+    model_lnCVR = map(data, ~ robu(.x$lnCVR ~ 1, data = .x, studynum = .x$id, modelweights = c("CORR"), rho = 0.8, small = TRUE, var.eff.size = (.x$lnCVR_se)^2))
+  )
+#### Extracting and save parameter estimates
+# Here we apply an additional function to collect the outcomes of the 'mini-meta-analysis' that has condensed our non-independent traits.
+Values from our second-order meta-analysis using robu-meta are then extracted
+count_fun <- function(mod_sub) {
+  return(c(mod_sub$reg_table$b.r, mod_sub$reg_table$CI.L, mod_sub$reg_table$CI.U, mod_sub$reg_table$SE))
+} # estimate, lower ci, upper ci, SE
+
+# Extraction of values created during meta-analyses using robumeta
+robusub_RR <- model_count %>%
+              transmute(parameter_group, 
+                        estimatelnRR = map(model_lnRR, count_fun)) %>%
+              mutate(r = map(estimatelnRR, 
+                             ~ data.frame(t(.)))) %>%
+              unnest(r) %>%
+              select(-estimatelnRR) %>%
+              purrr::set_names(c("parameter_group", "lnRR", "lnRR_lower", "lnRR_upper", "lnRR_se"))
+robusub_CVR <- model_count %>%
+               transmute(parameter_group, 
+                         estimatelnCVR = map(model_lnCVR, count_fun)) %>%
+               mutate(r = map(estimatelnCVR, 
+                              ~ data.frame(t(.)))) %>%
+               unnest(r) %>%
+               select(-estimatelnCVR) %>%
+               purrr::set_names(c("parameter_group", "lnCVR", "lnCVR_lower", "lnCVR_upper", "lnCVR_se"))
+robusub_VR <- model_count %>%
+              transmute(parameter_group, 
+                        estimatelnVR = map(model_lnVR, count_fun)) %>%
+              mutate(r = map(estimatelnVR, 
+                             ~ data.frame(t(.)))) %>%
+              unnest(r) %>%
+              select(-estimatelnVR) %>%
+              purrr::set_names(c("parameter_group", "lnVR", "lnVR_lower", "lnVR_upper", "lnVR_se"))
+robu_all <- full_join(robusub_CVR, robusub_VR) %>% full_join(., robusub_RR)
+#### Combining data 
+# Merge the two data sets (the new [robu_all] and the initial [uncorrelated sub-traits with count = 1]) 
+meta_all <- meta1 %>%
+            filter(par_group_size == 1) %>%
+            as_tibble()
+# Step 1:  Columns are matched by name (in our case, 'parameter_group'), and any missing columns will be filled with NA
+  combinedmeta <- bind_rows(robu_all, meta_all)
+# glimpse(combinedmeta)
+# Steps 2&3: Add information about number of traits in a parameter group, procedure, and grouping term
+              metacombo <- combinedmeta
+       metacombo$counts <- meta1$par_group_size[match(metacombo$parameter_group, meta1$parameter_group)] 
+   metacombo$procedure2 <- meta1$procedure[match(metacombo$parameter_group, meta1$parameter_group)]
+metacombo$GroupingTerm2 <- meta1$GroupingTerm[match(metacombo$parameter_group, meta1$parameter_group)]
+# Clean-up, reorder, and rename 
+metacombo <- metacombo[c("parameter_group", "counts","procedure2","GroupingTerm2", "lnCVR","lnCVR_lower","lnCVR_upper","lnCVR_se","lnVR","lnVR_lower","lnVR_upper","lnVR_se","lnRR","lnRR_lower","lnRR_upper","lnRR_se")]
+   names(metacombo)[names(metacombo)=="procedure2"] <- "procedure" 
+names(metacombo)[names(metacombo)=="GroupingTerm2"] <- "GroupingTerm"
+
+metacombo_final <- metacombo %>%
+                   group_by(GroupingTerm) %>%
+                   nest()
+
+metacombo_final <- metacombo_final %>% 
+                   mutate(para_per_GroupingTerm = map_dbl(data, nrow))
+# For all grouping terms
+metacombo_final_all <- metacombo %>%
+                       nest(data = everything())
+# Final random effects meta-analyses within grouping terms, with SE of the estimate
+overall1 <- metacombo_final %>%
+  mutate(
+    model_lnCVR = map(data, ~ metafor::rma.uni(
+                      yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower) / (2 * 1.96),
+                      control = list(optimizer = "optim", 
+                                     optmethod = "Nelder-Mead", 
+                                     maxit = 1000), 
+                      verbose = F)),
+    model_lnVR = map(data, ~ metafor::rma.uni(
+                    yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
+                    control = list(optimizer = "optim", 
+                                   optmethod = "Nelder-Mead", 
+                                   maxit = 1000), 
+                    verbose = F)),
+    model_lnRR = map(data, ~ metafor::rma.uni(
+                      yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
+                      control = list(optimizer = "optim", 
+                                     optmethod = "Nelder-Mead", 
+                                     maxit = 1000), 
+                      verbose = F)))
+# Final random effects meta-analyses ACROSS grouping terms, with SE of the estimate
+overall_all1 <- metacombo_final_all %>%
+  mutate(
+    model_lnCVR = map(data, ~ metafor::rma.uni(
+                      yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower) / (2 * 1.96),
+                      control = list(optimizer = "optim", 
+                                     optmethod = "Nelder-Mead", 
+                                     maxit = 1000), 
+                      verbose = F)),
+    model_lnVR = map(data, ~ metafor::rma.uni(
+                    yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
+                    control = list(optimizer = "optim", 
+                                   optmethod = "Nelder-Mead", 
+                                   maxit = 1000), 
+                    verbose = F)),
+    model_lnRR = map(data, ~ metafor::rma.uni(
+                    yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
+                    control = list(optimizer = "optim", 
+                                   optmethod = "Nelder-Mead", 
+                                   maxit = 1000), 
+                    verbose = F)))
+
+  # Function will take the averall results and extract the relevant trait of interest
+extract_trait <- function(data, trait){
+  tmp <- data %>% 
+        filter(., GroupingTerm == trait) %>% 
+        mutate(      lnCVR = .[[4]][[1]]$b, 
+               lnCVR_lower = .[[4]][[1]]$ci.lb, 
+               lnCVR_upper = .[[4]][[1]]$ci.ub, 
+                  lnCVR_se = .[[4]][[1]]$se, 
+                  lnCVR_I2 = .[[4]][[1]]$I2,
+                      lnVR = .[[5]][[1]]$b,  
+                lnVR_lower = .[[5]][[1]]$ci.lb,  
+                lnVR_upper = .[[5]][[1]]$ci.ub,  
+                   lnVR_se = .[[5]][[1]]$se,  
+                   lnVR_I2 = .[[5]][[1]]$I2,
+                      lnRR = .[[6]][[1]]$b,  
+                lnRR_lower = .[[6]][[1]]$ci.lb,  
+                lnRR_upper = .[[6]][[1]]$ci.ub,  
+                   lnRR_se = .[[6]][[1]]$se,  
+                   lnRR_I2 = .[[6]][[1]]$I2)  %>%
+        select(., GroupingTerm, lnCVR:lnRR_I2)
+
+  return(tmp)
+}
+All <- overall_all1 %>% 
+       mutate(      lnCVR = .[[2]][[1]]$b, 
+              lnCVR_lower = .[[2]][[1]]$ci.lb, 
+              lnCVR_upper = .[[2]][[1]]$ci.ub, 
+                 lnCVR_se = .[[2]][[1]]$se, 
+                 lnCVR_I2 = .[[2]][[1]]$I2,
+                     lnVR = .[[3]][[1]]$b,  
+               lnVR_lower = .[[3]][[1]]$ci.lb,  
+               lnVR_upper = .[[3]][[1]]$ci.ub,  
+                  lnVR_se = .[[3]][[1]]$se,  
+                  lnVR_I2 = .[[3]][[1]]$I2,
+                     lnRR = .[[4]][[1]]$b,  
+               lnRR_lower = .[[4]][[1]]$ci.lb,  
+               lnRR_upper = .[[4]][[1]]$ci.ub,  
+                  lnRR_se = .[[4]][[1]]$se,  
+                  lnRR_I2 = .[[4]][[1]]$I2,)  %>%
+       select(., lnCVR:lnRR_I2)
+
+All <- All %>% mutate(GroupingTerm = "All")
+
+overall2 <- bind_rows(extract_trait(overall1, "Behaviour"), 
+                      extract_trait(overall1, "Morphology"), 
+                      extract_trait(overall1, "Metabolism"), 
+                      extract_trait(overall1, "Physiology"), 
+                      extract_trait(overall1, "Immunology"), 
+                      extract_trait(overall1, "Hematology"), 
+                      extract_trait(overall1, "Heart"), 
+                      extract_trait(overall1, "Hearing"), 
+                      extract_trait(overall1, "Eye"), 
+                      All)
+
+meta_clean$GroupingTerm <- factor(meta_clean$GroupingTerm, 
+                                  levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye"))
+meta_clean$GroupingTerm <- factor(meta_clean$GroupingTerm, 
+                                  rev(levels(meta_clean$GroupingTerm)))
+#Preparing data for all traits
+meta.plot2.all <- meta_clean %>%
+                  select(lnCVR, lnVR, lnRR, GroupingTerm) %>%
+                  arrange(GroupingTerm)
+#lnVR has been removed here and in the steps below, as this is only included in the supplemental figure
+      meta.plot2.all.b <- gather(meta.plot2.all, trait, value, c(lnCVR, lnRR)) 
+meta.plot2.all.b$trait <- factor(meta.plot2.all.b$trait, levels = c("lnCVR", "lnRR")) 
+      meta.plot2.all.c <- meta.plot2.all.b %>%
+                          group_by_at(vars(trait, GroupingTerm)) %>%
+                          summarise(
+                            malebias = sum(value > 0), femalebias = sum(value <= 0), total = malebias + femalebias,
+                            malepercent = malebias * 100 / total, femalepercent = femalebias * 100 / total
+                          )
+meta.plot2.all.c$label <- "All traits"
+# Re-structure to create stacked bar plots
+meta.plot2.all.d <- as.data.frame(meta.plot2.all.c)
+meta.plot2.all.e <- gather(meta.plot2.all.d, 
+                           key = sex, 
+                           value = percent, 
+                           malepercent:femalepercent, 
+                           factor_key = TRUE)
+# Create new sample size variable
+meta.plot2.all.e$samplesize <- with(meta.plot2.all.e, 
+                                    ifelse(sex == "malepercent", 
+                                           malebias, 
+                                           femalebias))
+# Add summary row ('All') and re-arrange rows into correct order for plotting (warnings about coercing 'id' into character vector are ok)
+meta.plot2.all.f <- meta.plot2.all.e %>% 
+                    group_by(trait, sex) %>% 
+	                  summarise(GroupingTerm = "All", 
+	                            malebias = sum(malebias),
+	                            femalebias = sum(femalebias),
+	                            total = malebias + femalebias, 
+	                            label = "All traits", 
+	                            samplesize = sum(samplesize)) %>%
+	                  mutate(percent = ifelse(sex == "femalepercent", femalebias*100/(malebias+femalebias), malebias*100/(malebias+femalebias))) %>%
+	                  bind_rows(meta.plot2.all.e, .) %>%
+	                  mutate(rownumber = row_number()) %>%
+	                  .[c(37, 1:9, 39, 10:18, 38, 19:27, 40, 28:36), ] 
+  #line references in previous code line corresponding to: 
+  #'lnCVR(male(All)), lnCVR(male('single grouping terms'), lnRR(male(All)), lnRR(male('single grouping terms')),
+  #lnCVR(female(All)), lnCVR(female('single grouping terms'), lnRR(female(All)), lnRR(female('single grouping terms'))'
+meta.plot2.all.f$GroupingTerm <- factor(meta.plot2.all.f$GroupingTerm,
+                                        levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All")) 
+meta.plot2.all.f$GroupingTerm <- factor(meta.plot2.all.f$GroupingTerm, 
+                                        rev(levels(meta.plot2.all.f$GroupingTerm)))
+malebias_Fig2_alltraits <-
+    ggplot(meta.plot2.all.f) +
+    aes(x = GroupingTerm, y = percent, fill = sex) +
+    ylab("Percentage") +
+    geom_col() +
+    geom_hline(yintercept = 50, linetype = "dashed", color = "gray40") +
+    geom_text(
+      data = subset(meta.plot2.all.f, samplesize != 0), aes(label = samplesize), position = position_stack(vjust = .5),
+      color = "white", size = 3.5
+    ) +
+    facet_grid(
+      cols = vars(trait), rows = vars(label), labeller = label_wrap_gen(width = 18),
+      scales = "free", space = "free"
+    ) +  
+    scale_fill_brewer(palette = "Set2") +
+    theme_bw(base_size = 18) +
+    theme(
+      strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
+      strip.text.x = element_text(size = 12),
+      strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
+      text = element_text(size = 14),
+      panel.spacing = unit(0.5, "lines"),
+      panel.border = element_blank(),
+      axis.line = element_line(),
+      panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
+      panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
+      panel.grid.minor.y = element_blank(),
+      panel.grid.minor.x = element_blank(),
+      legend.position= "none",
+      #axis.title.x = Percentage,
+      axis.title.y = element_blank()
+    ) +
+    coord_flip()
+    overall3 <- gather(overall2, parameter, value, c(lnCVR, lnRR), factor_key = TRUE) 
+lnCVR.ci <- overall3 %>%
+           filter(parameter == "lnCVR") %>%
+           mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
+lnVR.ci <- overall3 %>%
+          filter(parameter == "lnVR") %>%
+          mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
+lnRR.ci <- overall3 %>%
+          filter(parameter == "lnRR") %>%
+          mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
+overall4 <- bind_rows(lnCVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high) 
+# Re-order grouping terms
+overall4$GroupingTerm <- factor(overall4$GroupingTerm, 
+                                levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
+overall4$GroupingTerm <- factor(overall4$GroupingTerm, 
+                                rev(levels(overall4$GroupingTerm)))
+overall4$label <- "All traits"
+####  PLOT 4B
+#adding male / female symbols for Figure 4B
+# additional packages for intergating male / female symbols in plot 4
+library(png)
+library(grid)
+  male <- readPNG(here("images", "MaleAqua.png"))
+female <- readPNG(here("images", "FemaleSalmon.png"))
+Metameta_Fig3_alltraits <- overall4 %>%
+  ggplot(aes(y = GroupingTerm, x = value)) +
+  geom_errorbarh(aes(
+    xmin = ci.low,
+    xmax = ci.high
+  ),
+  height = 0.1, show.legend = FALSE
+  ) +
+  geom_point(aes(shape = parameter),
+    fill = "black",
+    color = "black", size = 2.2,
+    show.legend = FALSE
+  ) +
+  scale_x_continuous(
+    limits = c(-0.24, 0.25),
+    breaks = c(-0.2, -0.1, 0, 0.1, 0.2),
+    name = "Effect size"
+  ) +
+  geom_vline(
+    xintercept = 0,
+    color = "black",
+    linetype = "dashed"
+  ) +
+  facet_grid(
+    cols = vars(parameter), rows = vars(label),
+    labeller = label_wrap_gen(width = 23),
+    scales = "free",
+    space = "free"
+  ) +
+  theme_bw() +
+  theme(
+    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
+    strip.text.x = element_text(size = 12),
+    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
+    text = element_text(size = 14),
+    panel.spacing = unit(0.5, "lines"),
+    panel.border = element_blank(),
+    axis.line = element_line(),
+    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
+    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
+    panel.grid.minor.y = element_blank(),
+    panel.grid.minor.x = element_blank(),
+    legend.title = element_blank(),
+    axis.title.x = element_text(hjust = 0.5, size = 14),
+    axis.title.y = element_blank()) +
+  # addition of male & female symols
+  annotation_custom(rasterGrob(female), xmin = - 0.2, xmax = -0.1, ymin = 2.3, ymax = 4) +
+  annotation_custom(rasterGrob(male), xmin = 0.1, xmax = 0.2, ymin = 2.3, ymax = 4)
+
+```
+
+blah blah
+
+```{r Fig3, fig.cap = "Panel A shows the numbers of traits across functional groups that are either male-biased (blue-green) or female-biased (orange-red), as calculated in Figure 1.1D.
+Panel B shows effect sizes and 95% CI from separate meta-analysis for each functional group (step H in Figure1.1).
+Both panels represent results evaluated across all traits.
+Traits that are male biased are shown in blue, whereas female bias data is represented in orange.[Figure 4 in manuscript]"}
+Fig4 <- ggarrange(malebias_Fig2_alltraits, Metameta_Fig3_alltraits,  nrow = 2, align = "v", heights = c(10, 9), labels = c("A", "B"))
+Fig4
+```
 
@@
 
-Lemaˆıtre JF, Ronget V, Tidie` re M, Allaine ́ D, Berger V, Cohas A, Colchero F, Conde DA, Garratt M, Liker A, Marais GAB, Scheuerlein A, Sze ́ kely T, Gaillard JM.
+Lemaˆıtre JF, Ronget V, Tidiere M, Allaine ́ D, Berger V, Cohas A, Colchero F, Conde DA, Garratt M, Liker A, Marais GAB, Scheuerlein A, Sze ́ kely T, Gaillard JM.
 2020.

### 2021-04-07 executableMS/ms_v1.rmd
Update ms_v1.rmd

@@
   - Division of Ecology and Evolution, Research School of Biology, Australian National University, Canberra, Australia
+bibliography: SexDiff.bib
 ---
@@
 ## Introduction
-Sex differences arise because selection acts on the two sexes differently, especially on traits associated with mating and reproduction (Darwin, 1871).
+Sex differences arise because selection acts on the two sexes differently, especially on traits associated with mating and reproduction (@darwin1871) (Darwin, 1871).
 Therefore, sex differences are widespread, a fact which is unsurprising to any evolutionary biologist.
-However, scientists in many (bio-)medical fields have not necessarily regarded sex as a biological factor of intrinsic interest (Clayton, 2016; Flanagan, 2014; Karp et al., 2017; Klein et al., 2015; Prendergast et al., 2014; Shansky and Woolley, 2016).
+However, scientists in many (bio-)medical fields have not necessarily regarded sex as a biological factor of intrinsic interest (@clayton2016; @flanagan2014; @karp2017; @klein2015; @prendergast2014; @shansky2016) (Clayton, 2016; Flanagan, 2014; Karp et al., 2017; Klein et al., 2015; Prendergast et al., 2014; Shansky and Woolley, 2016).
 Therefore, many (bio-)medical studies have only been conducted with male subjects.
 Consequently, our knowledge is biased.
-For example, we know far more about drug efficacy in male compared to female subjects, contributing to a poor understanding of how the sexes respond differently to medical interventions (Nowogrodzki, 2017).
-This gap in knowledge is predicted to lead to overmedication and adverse drug reactions in women (Zucker and Prendergast, 2020).
-Only recently have (bio-)medical scientists started considering sex differences in their research (Dorris et al., 2015; Ingvorsen et al., 2017; Robinson et al., 2017; Smarr et al., 2017;Ahmad et al., 2017; Foltin and Evans, 2018; Thompson et al., 2018).
-Indeed, the National Insti- tutes of Health (NIH) have now implemented new guidelines for animal and human research study designs, requiring that sex be included as a biological variable (Clayton, 2016; Clayton and Collins, 2014; NIH, 2015a).
+For example, we know far more about drug efficacy in male compared to female subjects, contributing to a poor understanding of how the sexes respond differently to medical interventions (@nowogrodzki2017)(Nowogrodzki, 2017).
+This gap in knowledge is predicted to lead to overmedication and adverse drug reactions in women (@zucker2020) (Zucker and Prendergast, 2020).
+Only recently have (bio-)medical scientists started considering sex differences in their research (@dorris2015; @ingvorsen2017; @robinson2017; @smarr2017; @ahmad2017; @foltin2018; @thompson2018)(Dorris et al., 2015; Ingvorsen et al., 2017; Robinson et al., 2017; Smarr et al., 2017;Ahmad et al., 2017; Foltin and Evans, 2018; Thompson et al., 2018).
+Indeed, the National Insti- tutes of Health (NIH) have now implemented new guidelines for animal and human research study designs, requiring that sex be included as a biological variable (@clayton2016; @clayton2014; @nih2015a) (NIH, 2015a(Clayton, 2016; Clayton and Collins, 2014; NIH, 2015a).
 When comparing the sexes, biologists generally focus on mean differences in trait values, placing little or no emphasis on sex differences in trait variability (see Figure 1 for a diagram explaining differences in means and variances).
@@
 
- this stupid figure has to get embedded    
+## Figure 1
  ![Fig1](./Figures/Figure1.png)
+
+### Overview of meta-analytic methods used to detect differences in means and variances in any given trait (e.g. body size in mice).
+The orange shading represents females (F), turquoise shading stands for males (M).
+The solid circle represents a mean trait value within the respective group.
+Solid lines represent standard deviation, with upper and lower bounds indicated by diamond shapes.
+Below, we present three types of effect sizes that can be used for comparing two groups, along with the respective formulas and interpretations.
+Compared to lnVR (the ratio of SD), lnCVR (the ratio of CV or relative variance) provides a more general measure of the difference in variability between two groups (mean-adjusted variability ratio).
+
+ ## Figure 1—figure supplement 1 
+ this code doesn't make sense here - as it needs all the code that's introduced later
+ ```{r FigCor, fig.height=3, message = FALSE, fig.cap= "Mean-variance relationships (log(Mean) vs log(SD, standard deviation)) across all traits for males (A) and females (B).[Figure 1-figure supplement 1 in manuscript]"}
+# First, clean up the data
+ results <- data %>%
+            group_by(population,
+             production_center,  
+             strain_name,  
+             parameter_name,
+             sex) %>%
+    summarise(trait  = parameter_name[1],
+              x_bar  = mean(data_point, na.rm = TRUE),
+              x_sd   =   sd(data_point, na.rm = TRUE),
+              n_ind  = n()) %>%
+    ungroup() %>%
+    filter(n_ind > 5) %>%   # NOTE here that you are excluding data with 5 exactly....
+    group_by(population) %>%
+    filter(all(c("male", "female") %in% sex)) %>% # Removes any entries where only 1 sex is present
+    multi_spread(sex, c(x_bar, x_sd, n_ind)) %>%
+    mutate(lnMean_m = log(male_x_bar),
+           logSD_m  = log(male_x_sd),
+           lnMean_f = log(female_x_bar),
+           lnSD_f   = log(female_x_sd)) %>%
+    filter(!is.na(logSD_m) & !is.inf(logSD_m)) %>%
+    filter(!is.na(lnSD_f) & !is.inf(lnSD_f))
+
+male <- ggplot(results, aes(x = lnMean_m, y = logSD_m)) +
+    geom_point(color = "#66C2A5", size = 2) +
+   geom_smooth(method = "lm", se = FALSE, color="black") + 
+    labs(x = "log (Mean)",
+         y = "log (SD)") + 
+    theme_classic()
+female <- ggplot(results, aes(x = lnMean_f, y = lnSD_f)) +
+    geom_point(color = "#FC8D62", size = 2) +
+  geom_smooth(method = "lm", se = FALSE, color="black")+
+    labs(x = "log (Mean)",
+         y = "log (SD)") + 
+    theme_classic()
+ggarrange(male, female, ncol = 2, nrow = 1, labels = c("A", "B"))
+```
+ ![Fig1sup](./Figures/Figure1sup.png)
+
+ ### Mean-variance relationships (log(Mean) vs log(SD, standard deviation)) across all traits for males (A) and females (B).
 
@@
 
+## Figure 2
  ![Fig2](./Figures/Figure2.png)
+
+## The two hypotheses (‘greater male variability’ versus ‘estrus-mediated variability’) have different predictions on how variabilities influence total observed phenotypic variance (Vtotal in the figure).
+For greater male variability, the within-subject (or within-trait) variation Vwithin could be potentially negligible or is equal in males and females.
+This is illustrated as the shaded distributions around each individual mean (dashed vertical lines), which are of equal area for the males (turquoise) and females (orange).
+The greater value of Vtotal is driven by wider distribution of mean trait values in males compared to females (i.e.
+Vbetween, represented by a thick horizontal bar).
+The estrus-mediated variability hypothesis, in contrast, assumes that within-subject [or within-trait] variability is much higher in females than in males (broader orange-shaded trait distributions than turquoise distributions), while the variability of the means between individuals stays the same (thick horizontal bars).
 
@@
 
+## Figure 3
+ ![Fig3](./Figures/Figure3.png)
+
+### Workflow of data processing and meta-analysis.
+
 ## Results
@@
 
- ![Fig3](./Figures/Figure3.png)
-
 Our dataset comprised 218 continuous traits (after initial data cleaning and pre-processing; Figure 3).
@@
 ```{r packages1, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE, messages=FALSE, paged.print=FALSE}
-library(pacman)
-pacman::p_load(readr, dplyr,metafor, devtools, purrr, tidyverse, tidyr, tibble, kableExtra, robumeta, ggpubr, ggplot2, png, grid, here, knitr, pander, splus2R)
-data <- readRDS(here("export", "data_clean.rds")) 
-procedures <- read_csv(here("data", "procedures.csv"))
-
+library(readr)
+library(dplyr)
+library(devtools)
+library(purrr)
+library(tidyverse)
+library(tidyr)
+library(tibble)
+library(kableExtra)
+library(ggpubr)
+library(ggplot2)
+library(png)
+library(grid)
+library(splus2R)
+
+# missing for meta-analysis: metafor, robumeta
+# pacman::p_load(readr, dplyr,metafor, devtools, purrr, tidyverse, tidyr, tibble, kableExtra, robumeta, ggpubr, ggplot2, png, grid, here, knitr, pander, splus2R)
+```
+Loading data & functions
+```{r}
+data <- readRDS(github://itchyshin/mice_sex_diff/export/data_clean.rds) 
+procedures <- read_csv(github://itchyshin/mice_sex_diff/export/procedures.csv)
 n <- length(unique(data$id))
+
+# loads the raw data, setting some default types for various columns
+load_raw <- function(filename) {
+  read_csv(filename,
+    col_types = cols(
+      .default = col_character(),
+      project_id = col_character(),
+      id = col_character(),
+      parameter_id = col_character(),
+      age_in_days = col_integer(),
+      date_of_experiment = col_datetime(format = ""),
+      weight = col_double(),
+      phenotyping_center_id = col_character(),
+      production_center_id = col_character(),
+      weight_date = col_datetime(format = ""),
+      date_of_birth = col_datetime(format = ""),
+      procedure_id = col_character(),
+      pipeline_id = col_character(),
+      biological_sample_id = col_character(),
+      biological_model_id = col_character(),
+      weight_days_old = col_integer(),
+      datasource_id = col_character(),
+      experiment_id = col_character(),
+      data_point = col_double(),
+      age_in_weeks = col_integer(),
+      `_version_` = col_character()
+    )
+  )
+}
+# Apply some standard cleaning to the data
+clean_raw_data <- function(mydata) {
+
+  group <- read_csv(here("data", "ParameterGrouping.csv"))
+
+  tmp <- 
+    mydata %>%
+    # Filter to IMPC source (recommend by Jeremey in email to Susi on 20 Aug 2018)
+    filter(datasource_name == "IMPC") %>%
+
+# standardise trait names
+    mutate(parameter_name = tolower(parameter_name)) %>%
+    # remove extreme ages
+    filter(age_in_days > 0 & age_in_days < 500) %>%
+    # remove NAs
+    filter(!is.na(data_point)) %>%
+    # subset to reasonable set of variables, date_of_experiment used as an indicator of batch-level effects
+    select(production_center, 
+           strain_name, 
+           strain_accession_id, 
+           biological_sample_id, 
+           pipeline_stable_id, 
+           procedure_group, 
+           procedure_name, 
+           sex, 
+           date_of_experiment, 
+           age_in_days, 
+           weight, 
+           parameter_name, 
+           data_point) %>% 
+    # sort
+    arrange(production_center, biological_sample_id, age_in_days)
+
+    # filter to groups with > 1 centre  
+    merge(tmp, 
+          tmp %>% group_by(parameter_name) %>%
+    summarise(center_per_trait = length(unique(production_center, na.rm = TRUE)))
+        )%>%
+    filter(center_per_trait >= 2) %>% 
+    # Define population variable
+    mutate(population = sprintf("%s-%s", production_center, strain_name)) %>% 
+    # add grouping variable: these were decided based on functional groups and procedures 
+    mutate(parameter_group = group$parameter[match(parameter_name, group$parameter_name)] ) %>%
+
+    # Assign unique IDs (per trait)
+    # each unique parameter_name (=trait,use trait variable) gets a unique number ('id')
+    # We add a new variable, where redundant traits are combined
+    #[note however, at this stage the dataset still contains nonsensical traits, i.e. traits that may not contain any information on variance]
+    mutate(id = match(parameter_name, unique(parameter_name))) %>% 
+    as_tibble()
+    }
+
+    data_subset_parameterid_individual_by_age <- function(mydata, parameter, age_min=0, age_center=100) {
+  tmp <- mydata %>%
+    filter(age_in_days >= age_min,
+           id == parameter) %>%
+  # Take results for single individual closest to age_center
+    mutate(age_diff = abs(age_center - age_in_days)) %>%
+    group_by(biological_sample_id) %>%
+    filter(age_diff == min(age_diff)) %>%
+    select(-age_diff)
+
+  # Still some individuals with multiple records (because same individual appears under different procedures, so filter to one record)
+  j <- match(unique(tmp$biological_sample_id), tmp$biological_sample_id)
+  tmp[j, ] 
+  }
+
+  # Function re-organises the data so that the male and female data are side-by-side as columns to make effect size calculations easier.
+multi_spread <- function(df, key, value) {
+    # quote key
+      keyq <- rlang::enquo(key)
+    # break value vector into quotes
+    valueq <- rlang::enquo(value)
+         s <- rlang::quos(!!valueq)
+
+         df                           %>% 
+        gather(variable, value, !!!s) %>%
+        unite(temp, !!keyq, variable) %>%
+        spread(temp, value)
+}
+# Function will calculate population stats and exclude data that is irrelevant and not useful, it will also just convert the data straight away to wide format making it ready for effect size calculations
+calculate_population_stats <- function(mydata, min_individuals = 5){
+    mydata %>% 
+    group_by(population,
+             production_center,  
+             strain_name,  
+             sex) %>%
+    summarise(trait  = parameter_name[1],
+              x_bar  = mean(data_point, na.rm = TRUE),
+              x_sd   =   sd(data_point, na.rm = TRUE),
+              n_ind  = n()) %>%
+    ungroup() %>%
+    filter(n_ind > min_individuals) %>%   
+    group_by(population) %>%
+    filter(all(c("male", "female") %in% sex)) %>% # Removes any entries where only 1 sex is present
+    multi_spread(sex, c(x_bar, x_sd, n_ind))      # Spreads the data out into wide format, so sexes are beside each other which is more typical of meta-analytic data
+}
+
+#This function takes the data and computes lnCVR, lnVR and ROM (lnRR) using male and female data to generate effect size statistics for meta-analyses
+create_meta_analysis_effect_sizes <- function(mydata, measure = c("CVR", "VR", "ROM")){
+  for(i in 1:length(measure)){
+    mydata <- metafor::escalc(m1i  = male_x_bar, 
+                              m2i  = female_x_bar, 
+                              sd1i = male_x_sd, 
+                              sd2i = female_x_sd, 
+                              n1i  = male_n_ind, 
+                              n2i  = female_n_ind, 
+                              data = mydata, 
+                           measure = measure[i], 
+                         var.names = c(paste0("effect_size_", measure[i]), 
+                                      paste0("sample_variance_", measure[i])),
+                            append = TRUE)
+    }
+    return(mydata)
+}
+
+```
+
+```{r metaanlysis prep, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE, messages=FALSE, paged.print=FALSE}
 # Create dataframe to store results
@@
   )
+ ```
+Additional meta-analyses and preparation for plots
+
+ ```{r extracting estimates}
 #### Extracting and save parameter estimates
@@
 robu_all <- full_join(robusub_CVR, robusub_VR) %>% full_join(., robusub_RR)
+
 #### Combining data 
@@
 
-blah blah
-
-```{r Fig3, fig.cap = "Panel A shows the numbers of traits across functional groups that are either male-biased (blue-green) or female-biased (orange-red), as calculated in Figure 1.1D.
-Panel B shows effect sizes and 95% CI from separate meta-analysis for each functional group (step H in Figure1.1).
-Both panels represent results evaluated across all traits.
-Traits that are male biased are shown in blue, whereas female bias data is represented in orange.[Figure 4 in manuscript]"}
+## Figure 4
+
+```{r  fig.cap = "Sex bias in trait groups.
+Panel (A) shows the numbers of traits that are either male-biased (turquoise) or female-biased (orange) across functional groups.
+The x-axes in Panel A represents the overall percentages of traits with a given direction of sex bias: orange shading when meta-analytic mean < 0 (female-biased), turquoise shading when meta-analytic mean > 0 (male-biased).
+White numbers inside the turquoise bars represent numbers of traits that show male bias within a given group of traits, numbers inside the orange bars represent the number of female-biased traits.
+Panel (B) shows effect sizes and 95% CI from separate meta-analysis for each functional group (Figure 3H).
+Traits that are male-biased in Panel B are shifted towards the righthand side of the zero-midline (near the turquoise male symbol), whereas female-biased traits are shifted towards the left (near the orange female symbol)."}
+
 Fig4 <- ggarrange(malebias_Fig2_alltraits, Metameta_Fig3_alltraits,  nrow = 2, align = "v", heights = c(10, 9), labels = c("A", "B"))
 Fig4
+```
+## Figure 4—figure supplement 1
+```{r code for heterogeneity}
+### Preparing heterogeneity
+# Create dataframe to store results
+results.allhetero.grouping <- as.data.frame(cbind(c(1:n), matrix(rep(0, n * 30), ncol = 30)))
+names(results.allhetero.grouping) <- c(
+  "id", "sigma2_strain.CVR", "sigma2_center.CVR", "sigma2_error.CVR", "s.nlevels.strain.CVR",
+  "s.nlevels.center.CVR", "s.nlevels.error.CVR", "sigma2_strain.VR", "sigma2_center.VR", "sigma2_error.VR", "s.nlevels.strain.VR",
+  "s.nlevels.center.VR", "s.nlevels.error.VR", "sigma2_strain.RR", "sigma2_center.RR", "sigma2_error.RR", "s.nlevels.strain.RR",
+  "s.nlevels.center.RR", "s.nlevels.error.RR", "lnCVR", "lnCVR_lower", "lnCVR_upper", "lnCVR_se", "lnVR", "lnVR_lower", "lnVR_upper",
+  "lnVR_se", "lnRR", "lnRR_lower", "lnRR_upper", "lnRR_se"
+)
+
+#Loop
+for (t in 1:n) {
+  tryCatch(
+    {
+      results <- data %>% 
+                  data_subset_parameterid_individual_by_age(t) %>% 
+                  calculate_population_stats() %>% 
+                  create_meta_analysis_effect_sizes() %>%
+                  mutate(err = seq_len(n()))
+
+      # lnCVR, logaritm of the ratio of male and female coefficients of variance
+      cvr. <- metafor::rma.mv(yi = effect_size_CVR, 
+                              V = sample_variance_CVR, 
+                              random = list(~ 1 | strain_name, ~ 1 | production_center,~ 1 | err), 
+                              control = list(optimizer = "optim", 
+                                             optmethod = "Nelder-Mead", 
+                                             maxit = 1000), 
+                              data = results)
+
+      results.allhetero.grouping[t, 2] <- cvr.$sigma2[1]
+      results.allhetero.grouping[t, 3] <- cvr.$sigma2[2]
+      results.allhetero.grouping[t, 4] <- cvr.$sigma2[3]
+      results.allhetero.grouping[t, 5] <- cvr.$s.nlevels[1]
+      results.allhetero.grouping[t, 6] <- cvr.$s.nlevels[2]
+      results.allhetero.grouping[t, 7] <- cvr.$s.nlevels[3]
+      results.allhetero.grouping[t, 20] <- cvr.$b
+      results.allhetero.grouping[t, 21] <- cvr.$ci.lb
+      results.allhetero.grouping[t, 22] <- cvr.$ci.ub
+      results.allhetero.grouping[t, 23] <- cvr.$se
+
+       # lnVR, male to female variability ratio (logarithm of male and female standard deviations)
+      vr. <- metafor::rma.mv(yi = effect_size_VR, 
+                             V = sample_variance_VR, 
+                             random = list(~ 1 | strain_name, ~ 1 | production_center, ~ 1 | err), 
+                             control = list(optimizer = "optim", 
+                                            optmethod = "Nelder-Mead", 
+                                            maxit = 1000), 
+                             data = results)
+
+      results.allhetero.grouping[t, 8] <- vr.$sigma2[1]
+      results.allhetero.grouping[t, 9] <- vr.$sigma2[2]
+      results.allhetero.grouping[t, 10] <- vr.$sigma2[3]
+      results.allhetero.grouping[t, 11] <- vr.$s.nlevels[1]
+      results.allhetero.grouping[t, 12] <- vr.$s.nlevels[2]
+      results.allhetero.grouping[t, 13] <- vr.$s.nlevels[3]
+      results.allhetero.grouping[t, 24] <- vr.$b
+      results.allhetero.grouping[t, 25] <- vr.$ci.lb
+      results.allhetero.grouping[t, 26] <- vr.$ci.ub
+      results.allhetero.grouping[t, 27] <- vr.$se
+      # lnRR, response ratio (logarithm of male and female means)
+      rr. <- metafor::rma.mv(yi = effect_size_ROM, 
+                             V = sample_variance_ROM, 
+                             random = list(~ 1 | strain_name, ~ 1 | production_center, ~ 1 | err), 
+                             control = list(optimizer = "optim", 
+                                            optmethod = "Nelder-Mead", 
+                                            maxit = 1000), 
+                             data = results)
+
+      results.allhetero.grouping[t, 14] <- rr.$sigma2[1]
+      results.allhetero.grouping[t, 15] <- rr.$sigma2[2]
+      results.allhetero.grouping[t, 16] <- rr.$sigma2[3]
+      results.allhetero.grouping[t, 17] <- rr.$s.nlevels[1]
+      results.allhetero.grouping[t, 18] <- rr.$s.nlevels[2]
+      results.allhetero.grouping[t, 19] <- rr.$s.nlevels[3]
+      results.allhetero.grouping[t, 28] <- rr.$b
+      results.allhetero.grouping[t, 29] <- rr.$ci.lb
+      results.allhetero.grouping[t, 30] <- rr.$ci.ub
+      results.allhetero.grouping[t, 31] <- rr.$se
+    },
+    error = function(e) {
+      cat("ERROR :", conditionMessage(e), "\n")
+    }
+     )
+}
+
+              results.allhetero.grouping2 <- results.allhetero.grouping[results.allhetero.grouping$s.nlevels.strain.VR != 0, ]
+# nrow(results.allhetero.grouping) #232  
+# Merging dataset with correct procedure names
+# procedures <- read.csv(here("export", "procedures.csv"))
+results.allhetero.grouping2$parameter_group <- data$parameter_group[match(results.allhetero.grouping2$id, data$id)]
+      results.allhetero.grouping2$procedure <- data$procedure_name[match(results.allhetero.grouping2$id, data$id)]
+   results.allhetero.grouping2$GroupingTerm <- procedures$GroupingTerm[match(results.allhetero.grouping2$procedure, procedures$procedure)]
+ results.allhetero.grouping2$parameter_name <- data$parameter_name[match(results.allhetero.grouping2$id, data$id)]
+#We deal with correlated parameters following the procedures described above (extraction of effects sizes).
+metahetero1 <- results.allhetero.grouping2
+# length(unique(metahetero1$procedure)) #19
+# length(unique(metahetero1$GroupingTerm)) #9 
+# length(unique(metahetero1$parameter_group)) #152
+# length(unique(metahetero1$parameter_name)) #223
+# Count of number of parameter names (correlated sub-traits) in each parameter group (par_group_size)
+metahetero1b <- metahetero1                    %>%
+                group_by(parameter_group)      %>%
+                mutate(par_group_size = n_distinct(parameter_name))
+metahetero1$par_group_size <- metahetero1b$par_group_size[match(metahetero1$parameter_group, metahetero1b$parameter_group)]
+# Create subsets with > 1 count (par_group_size > 1)
+metahetero1_sub <- subset(metahetero1, par_group_size > 1) # 92 observations
+# Nest data
+n_count. <- metahetero1_sub %>%
+  group_by(parameter_group) %>%
+  nest()
+
+# meta-analysis preparation
+model_count. <- n_count. %>%
+  mutate(
+    model_lnRR = map(data, ~ robu(.x$lnRR ~ 1,
+      data = .x, studynum = .x$id, modelweights = c("CORR"), rho = 0.8,
+      small = TRUE, var.eff.size = (.x$lnRR_se)^2
+    )),
+    model_lnVR = map(data, ~ robu(.x$lnVR ~ 1,
+      data = .x, studynum = .x$id, modelweights = c("CORR"), rho = 0.8,
+      small = TRUE, var.eff.size = (.x$lnVR_se)^2
+    )),
+    model_lnCVR = map(data, ~ robu(.x$lnCVR ~ 1,
+      data = .x, studynum = .x$id, modelweights = c("CORR"), rho = 0.8,
+      small = TRUE, var.eff.size = (.x$lnCVR_se)^2
+    ))
+  )
+# Robumeta object details:  str(model_count.$model_lnCVR[[1]])
+# Perform meta-analyses on correlated sub-traits, using robumeta
+# Extract and save parameter estimates
+count_fun. <- function(mod_sub) {
+  return(c(as.numeric(mod_sub$mod_info$term1), mod_sub$N))
+}
+robusub_RR. <- model_count. %>%
+  transmute(estimatelnRR = map(model_lnRR, count_fun.)) %>%    
+  mutate(r = map(estimatelnRR, ~ data.frame(t(.)))) %>%
+  unnest(r) %>%
+  select(-estimatelnRR) %>%
+  purrr::set_names(c("parameter_group", "var.RR", "N.RR"))
+robusub_CVR. <- model_count. %>%
+  transmute(estimatelnCVR = map(model_lnCVR, count_fun.)) %>%
+  mutate(r = map(estimatelnCVR, ~ data.frame(t(.)))) %>%
+  unnest(r) %>%
+  select(-estimatelnCVR) %>%
+  purrr::set_names(c("parameter_group", "var.CVR", "N.CVR"))
+robusub_VR. <- model_count. %>%
+  transmute(estimatelnVR = map(model_lnVR, count_fun.)) %>%
+  mutate(r = map(estimatelnVR, ~ data.frame(t(.)))) %>%
+  unnest(r) %>%
+   select(-estimatelnVR) %>%
+  purrr::set_names(c("parameter_group", "var.VR", "N.VR"))
+robu_all. <- full_join(robusub_CVR., robusub_VR.) %>% full_join(., robusub_RR.)
+#Merge the two data sets (the new [robu_all.] and the initial [uncorrelated sub-traits with count = 1])
+#In this step, we 	1) merge the N from robumeta and the  N from metafor (s.nlevels.error) together into the same columns (N.RR, N.VR, N.CVR)
+# 2) calculate the total variance for metafor models as the sum of random effect variances and the residual error, then add in the same columns together with the residual variances from robumeta
+
+metahetero_all <- metahetero1 %>%
+  filter(par_group_size == 1) %>%
+  as_tibble()
+metahetero_all$N.RR <- metahetero_all$s.nlevels.error.RR
+metahetero_all$N.CVR <- metahetero_all$s.nlevels.error.CVR
+metahetero_all$N.VR <- metahetero_all$s.nlevels.error.VR
+metahetero_all$var.RR <- log(sqrt(metahetero_all$sigma2_strain.RR + metahetero_all$sigma2_center.RR + metahetero_all$sigma2_error.RR))
+metahetero_all$var.VR <- log(sqrt(metahetero_all$sigma2_strain.VR + metahetero_all$sigma2_center.VR + metahetero_all$sigma2_error.VR))
+metahetero_all$var.CVR <- log(sqrt(metahetero_all$sigma2_strain.CVR + metahetero_all$sigma2_center.CVR + metahetero_all$sigma2_error.CVR))
+# str(metahetero_all)
+# str(robu_all.)
+
+metahetero_all <- metahetero_all %>% mutate(
+  var.RR = if_else(var.RR == -Inf, -7, var.RR),   # numbers chosen as limits; based on the values in the dataset
+  var.VR = if_else(var.VR == -Inf, -5, var.VR),
+  var.CVR = if_else(var.CVR == -Inf, -6, var.CVR)
+)
+# Combine data
+# Step1
+combinedmetahetero <- bind_rows(robu_all., metahetero_all)
+# glimpse(combinedmetahetero)
+# Steps 2&3
+              metacombohetero <- combinedmetahetero
+       metacombohetero$counts <- metahetero1$par_group_size[match(metacombohetero$parameter_group, metahetero1$parameter_group)]
+   metacombohetero$procedure2 <- metahetero1$procedure[match(metacombohetero$parameter_group, metahetero1$parameter_group)]
+metacombohetero$GroupingTerm2 <- metahetero1$GroupingTerm[match(metacombohetero$parameter_group, metahetero1$parameter_group)]
+# **Clean-up and rename
+metacombohetero <- metacombohetero %>% select(parameter_group, var.CVR, N.CVR, var.VR, N.VR, var.RR, N.RR, counts, procedure = procedure2, GroupingTerm = GroupingTerm2)  
+# Invidual table for heterogeneity across all traits
+ kable(metacombohetero,, digits = 3) %>%
+  kable_styling() %>%
+  scroll_box(width = "100%", height = "200px")
+#### Meta-analysis of heterogeneity
+## Perform meta-meta-analysis (3 for each of the 9 grouping terms: var.CVR, var.VR, var.RR)
+metacombohetero_final <- metacombohetero %>%
+  group_by(GroupingTerm) %>%
+  nest()
+# Final random effects meta-analyses within grouping terms, with SE of the estimate
+heterog1 <- metacombohetero_final %>%
+  mutate(
+    model_heteroCVR = map(data, ~ metafor::rma.uni(
+      yi = .x$var.CVR, sei = sqrt(1 / 2 * (.x$N.CVR - 1)),
+      control = list(optimizer = "optim", 
+                     optmethod = "Nelder-Mead",
+		                          maxit = 10000, 
+                     stepadj = 0.5), verbose = F)),
+    model_heteroVR = map(data, ~ metafor::rma.uni(
+      yi = .x$var.VR, sei = sqrt(1 / 2 * (.x$N.VR - 1)),
+      control = list(optimizer = "optim", 
+                     optmethod = "Nelder-Mead", 
+                     maxit = 10000, 
+                     stepadj = 0.5), verbose = F)),
+    model_heteroRR = map(data, ~ metafor::rma.uni(
+      yi = .x$var.RR, sei = sqrt(1 / 2 * (.x$N.RR - 1)),
+      control = list(optimizer = "optim", 
+                     optmethod = "Nelder-Mead", 
+                     maxit = 10000, 
+                     stepadj = 0.5), verbose = F)) )
+# Across all grouping terms   
+metacombohetero_all_final <- metacombohetero %>%
+  nest(data = everything()) 
+# Final random effects meta-analyses ACROSS grouping terms, with SE of the estimate
+heterog1_all <- metacombohetero_all_final %>%
+
+  mutate( model_heteroCVR = map(data, ~ metafor::rma.uni(
+      yi = .x$var.CVR, sei = sqrt(1 / 2 * (.x$N.CVR - 1)),
+      control = list(optimizer = "optim", 
+                     optmethod = "Nelder-Mead", 
+                     maxit = 10000, 
+                     stepadj = 0.5), verbose = F)),
+    model_heteroVR = map(data, ~ metafor::rma.uni(yi = .x$var.VR, sei = sqrt(1 / 2 * (.x$N.VR - 1)),
+      control = list(optimizer = "optim", 
+                     optmethod = "Nelder-Mead", 
+                     maxit = 10000, 
+                     stepadj = 0.5), verbose = F)),
+    model_heteroRR = map(data, ~ metafor::rma.uni(yi = .x$var.RR, sei = sqrt(1 / 2 * (.x$N.RR - 1)),
+      control = list(optimizer = "optim", 
+                     optmethod = "Nelder-Mead", 
+                     maxit = 10000, 
+                     stepadj = 0.5), verbose = F)))
+
+# Re-structure data for each grouping term; extract heterogenenity/variance terms; delete un-used variables
+extract_heterogeneity <- function(data, type){
+
+  tmp <- data %>%
+         filter(., GroupingTerm == type) %>%
+         select(., -data) %>%
+         mutate(heteroCVR       = .[[2]][[1]]$b, 
+                heteroCVR_lower = .[[2]][[1]]$ci.lb, 
+                heteroCVR_upper = .[[2]][[1]]$ci.ub, 
+                heteroCVR_se    = .[[2]][[1]]$se,
+                heteroVR        = .[[3]][[1]]$b, 
+                heteroVR_lower  = .[[3]][[1]]$ci.lb, 
+                heteroVR_upper  = .[[3]][[1]]$ci.ub, 
+                heteroVR_se     = .[[3]][[1]]$se,
+                heteroRR        = .[[4]][[1]]$b, 
+                heteroRR_lower  = .[[4]][[1]]$ci.lb, 
+                heteroRR_upper  = .[[4]][[1]]$ci.ub, 
+                heteroRR_se     = .[[4]][[1]]$se) %>%
+        select(., GroupingTerm, heteroCVR:heteroRR_se)
+
+  return(tmp)
+}
+   Behaviour. <- extract_heterogeneity(heterog1, type = "Behaviour")
+  Immunology. <- extract_heterogeneity(heterog1, type = "Immunology")
+  Hematology. <- extract_heterogeneity(heterog1, type = "Hematology")
+     Hearing. <- extract_heterogeneity(heterog1, type = "Hearing")
+  Physiology. <- extract_heterogeneity(heterog1, type = "Physiology")
+  Metabolism. <- extract_heterogeneity(heterog1, type = "Metabolism")
+  Morphology. <- extract_heterogeneity(heterog1, type = "Morphology")
+       Heart. <- extract_heterogeneity(heterog1, type = "Heart")
+         Eye. <- extract_heterogeneity(heterog1, type = "Eye")
+#Reorder to be able to keep cell referencing 
+heterog1_all <- heterog1_all %>% 
+                mutate(GroupingTerm = "All") %>% 
+                select(GroupingTerm, everything())
+
+		All. <- heterog1_all %>% 
+        select(., -data) %>%
+        mutate(heteroCVR       = .[[2]][[1]]$b, 
+               heteroCVR_lower = .[[2]][[1]]$ci.lb, 
+               heteroCVR_upper = .[[2]][[1]]$ci.ub, 
+               heteroCVR_se    = .[[2]][[1]]$se, 
+               heteroVR        = .[[3]][[1]]$b, 
+               heteroVR_lower  = .[[3]][[1]]$ci.lb, 
+               heteroVR_upper  = .[[3]][[1]]$ci.ub, 
+               heteroVR_se     = .[[3]][[1]]$se, 
+               heteroRR        = .[[4]][[1]]$b, 
+               heteroRR_lower  = .[[4]][[1]]$ci.lb, 
+               heteroRR_upper  = .[[4]][[1]]$ci.ub, 
+               heteroRR_se     = .[[4]][[1]]$se) %>%
+        select(., GroupingTerm, heteroCVR:heteroRR_se)
+
+heterog2 <- bind_rows(Behaviour., Morphology., Metabolism., Physiology., Immunology., Hematology., Heart., Hearing., Eye., All.)
+
+#### Preparation of the Heterogeneity PLOT
+#Restructure data for plotting
+heterog3 <- gather(heterog2, parameter, value, c(heteroCVR, heteroVR, heteroRR), factor_key = TRUE)
+heteroCVR.ci <- heterog3 %>%
+                filter(parameter == "heteroCVR") %>%
+                mutate(ci.low = heteroCVR_lower, 
+                       ci.high = heteroCVR_upper)
+heteroVR.ci <-  heterog3 %>%
+                filter(parameter == "heteroVR") %>%
+                mutate(ci.low = heteroVR_lower, 
+                       ci.high = heteroVR_upper)
+heteroRR.ci <-  heterog3 %>%
+                filter(parameter == "heteroRR") %>%
+                mutate(ci.low = heteroRR_lower, 
+                       ci.high = heteroRR_upper)
+heterog4 <- bind_rows(heteroCVR.ci, heteroVR.ci, heteroRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
+# **Re-order grouping terms
+heterog4$GroupingTerm <- factor(heterog4$GroupingTerm, 
+                                levels = c("Behaviour", "Morphology", "Metabolism", 
+                                           "Physiology", "Immunology", "Hematology", "Heart", 
+                                           "Hearing", "Eye", "All"))
+heterog4$GroupingTerm <- factor(heterog4$GroupingTerm, 
+                                rev(levels(heterog4$GroupingTerm)))
+heterog4$label <- "All traits"
+# write.csv(heterog4, "heterog4.csv")
+#### Plot S1 C (Second-order meta analysis on heterogeneity)
+heterog5 <- heterog4
+heterog5$mean <- as.numeric(exp(heterog5$value))
+heterog5$ci.l <- as.numeric(exp(heterog5$ci.low))
+heterog5$ci.h <- as.numeric(exp(heterog5$ci.high))
+heterog6 <- heterog5
+HeteroS1 <-
+  heterog6 %>%
+  ggplot(aes(y = GroupingTerm, x = mean)) +
+  geom_errorbarh(aes(
+    xmin = ci.l,
+    xmax = ci.h
+  ),
+  height = 0.1, show.legend = FALSE
+  ) +
+  geom_point(aes(shape = parameter),
+    fill = "black",
+    color = "black", size = 2.2,
+    show.legend = FALSE
+  ) +
+  scale_x_continuous(
+    limits = c(-0.1, 1.4),
+    # breaks = c(0, 0.1, 0.2),
+    name = "sigma^2"
+  ) +
+  # geom_vline(xintercept=0,
+  # color='black',
+  # linetype='dashed')+
+  facet_grid(
+    cols = vars(parameter), rows = vars(label),
+        labeller = label_wrap_gen(width = 23),
+    scales = "free",
+    space = "free"
+  ) +
+  theme_bw() +
+  theme(
+    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
+    strip.text.x = element_text(size = 12),
+    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
+    text = element_text(size = 14),
+    panel.spacing = unit(0.5, "lines"),
+    panel.border = element_blank(),
+    axis.line = element_line(),
+    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
+    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
+    panel.grid.minor.y = element_blank(),
+    panel.grid.minor.x = element_blank(),
+    legend.title = element_blank(),
+    axis.title.x = element_text(hjust = 0.5, size = 14),
+    axis.title.y = element_blank())
+```
+
+```{r fig.cap = "Percentages and numbers of either male (turqoise bars) or female (orange bars) biased traits (Panel A) across functional groups, this time for lnCVR (left hand side), lnVR (middle) and lnRR (right hand side).
+Panel B shows effect sizes from separate meta-analysis for each functional group, and Panel C contains results of heterogeneity analyses.
+All three panels represent results evaluated across all traits."}
+
+```
+
+#HERE
+ add code for supplemental figs
+
+## Figure 4—figure supplement 2
+```{r code for sex bias}
+
+```
+
+```{r fig.cap = "**Sex bias in trait groups for lnCVR, lnVR and lnRR.**
+(A) Percentages and numbers of affected traits, for variance (lnCVR and lnVR) and means (lnRR), where there is a significant difference between the sexes (i.e.
+CI not overlapping zero), and where the sex bias is greater than 10% difference (regardless of significance).
+Panel B depicts results for the effect size magnitudes in those traits that differ between the sexes (second-order meta-analysis).
+Triangles represent sex bias in means (response ratio) and black circles differences in the coefficient of variation ratio (mean-adjusted variability).
+The orange bars represent trait groups with a female bias, turqouise bars male-biased traits."}
+
 ```

### 2021-04-07 executableMS/ms_v1.rmd
Update ms_v1.rmd

@@
 
-```{r fig.cap = "Percentages and numbers of either male (turqoise bars) or female (orange bars) biased traits (Panel A) across functional groups, this time for lnCVR (left hand side), lnVR (middle) and lnRR (right hand side).
+```{r Fig4S1, fig.height = 8, fig.width = 7, fig.cap = "Percentages and numbers of either male (turqoise bars) or female (orange bars) biased traits (Panel A) across functional groups, this time for lnCVR (left hand side), lnVR (middle) and lnRR (right hand side).
 Panel B shows effect sizes from separate meta-analysis for each functional group, and Panel C contains results of heterogeneity analyses.
@@
 
+#### Combined Figure 4S1: overall Count data, Meta anlysis results, Heterogeneity
+
+Fig4S1 <- ggarrange(malebias_FigS1_alltraits, Metameta_FigS1_alltraits, HeteroS1, nrow = 3, align = "v", heights = c(1.1, 1, 1), labels = c("A", "B", "C"))
+Fig4S1
+
 ```
 
-#HERE
- add code for supplemental figs
+## ## Figure 4—figure supplement 2
+```{r Fig4S2_prep, echo = FALSE, eval = TRUE}
+ meta.plot2.sig <- meta_clean %>%
+                   mutate(lnCVRsig = ifelse(lnCVR_lower * lnCVR_upper > 0, 1, 0), 
+                           lnVRsig = ifelse( lnVR_lower * lnVR_upper  > 0, 1, 0),
+                           lnRRsig = ifelse( lnRR_lower * lnRR_upper  > 0, 1, 0))
+meta.plot2.sig.b <- meta.plot2.sig[, c("lnCVR", "lnRR", "lnCVRsig", "lnVRsig", "lnRRsig", "GroupingTerm")] 
+    meta.plot2.sig.c <- gather(meta.plot2.sig.b, trait, value, lnCVR:lnRR)
+meta.plot2.sig.c$sig <- "placeholder"
+meta.plot2.sig.c$trait <- factor(meta.plot2.sig.c$trait, levels = c("lnCVR", "lnRR")) 
+  meta.plot2.sig.c$sig <- ifelse(meta.plot2.sig.c$trait == "lnCVR", 
+                                 meta.plot2.sig.c$lnCVRsig,
+                                 ifelse(meta.plot2.sig.c$trait == "lnVR", 
+                                        meta.plot2.sig.c$lnVRsig, 
+                                        meta.plot2.sig.c$lnRRsig))
+# Choosing sex biased ln-ratios significantly larger than 0
+meta.plot2.sig.malebias <- meta.plot2.sig.c %>%
+                           group_by_at(vars(trait, GroupingTerm)) %>%
+                           filter(sig == 1) %>%
+                           summarise(male_sig = sum(value > 0), female_sig = sum(value < 0), total = male_sig + female_sig)
+meta.plot2.sig.malebias <- ungroup(meta.plot2.sig.malebias) %>%
+                          # add "Hearing" for lnCVR (not filtered as only zeros)
+                          add_row(trait = "lnCVR", GroupingTerm = "Hearing", male_sig = 0, female_sig = 0, .before = 4) %>% 
+                          mutate(malepercent = male_sig * 100 / total, femalepercent = female_sig * 100 / total)
+meta.plot2.sig.malebias$label <- "CI not overlapping zero"
+# Re-structure to create stacked bar plots
+  meta.plot2.sig.bothsexes <- as.data.frame(meta.plot2.sig.malebias)
+meta.plot2.sig.bothsexes.b <- gather(meta.plot2.sig.bothsexes, key = sex, value = percent, malepercent:femalepercent, factor_key = TRUE)
+# create new sample size variable
+meta.plot2.sig.bothsexes.b$samplesize <- with(meta.plot2.sig.bothsexes.b, ifelse(sex == "malepercent", male_sig, female_sig))
+# Add summary row ('All') and re-arrange rows into correct order for plotting 
+meta.plot2.sig.bothsexes.c <- meta.plot2.sig.bothsexes.b %>% 
+                              group_by(trait, sex) %>% 
+                              summarise(GroupingTerm = "All", 
+                                        male_sig = sum(male_sig), 
+                                        female_sig = sum(female_sig), 
+                                        total = male_sig + female_sig, 
+                                        label = "CI not overlapping zero", 
+                                        samplesize = sum(samplesize)) %>%
+                              mutate(percent = ifelse(sex == "femalepercent", 
+                                                      female_sig*100/(male_sig+female_sig), 
+                                                      male_sig*100/(male_sig+female_sig))) %>%
+                              bind_rows(meta.plot2.sig.bothsexes.b, .) %>%
+                              mutate(rownumber = row_number()) %>%
+                              .[c(37, 1:9, 39, 10:18, 38, 19:27, 40, 28:36), ] 
+  #line references in previous code line corresponding to: 
+  #'lnCVR(male(All)), lnCVR(male('single grouping terms'), lnRR(male(All)), lnRR(male('single grouping terms')),
+  #lnCVR(female(All)), lnCVR(female('single grouping terms'), lnRR(female(All)), lnRR(female('single grouping terms'))'
+meta.plot2.sig.bothsexes.c$GroupingTerm <- factor(meta.plot2.sig.bothsexes.c$GroupingTerm,
+                                                  levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", 
+                                                             "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All")) 
+meta.plot2.sig.bothsexes.c$GroupingTerm <- factor(meta.plot2.sig.bothsexes.c$GroupingTerm, 
+                                                  rev(levels(meta.plot2.sig.bothsexes.c$GroupingTerm)))
+# Plot Fig2 all significant results (CI not overlapping zero)
+# Several grouping terms are added post-hoc (with no data to display): no significant lnCVR for 'Hearing' in either sex; no sig.
+male-biased lnCVR for 'Immunology' and 'Eye, and no significant female-biased lnRR for 'Eye'.
+malebias_Fig2_sigtraits <-
+  ggplot(meta.plot2.sig.bothsexes.c) +
+  aes(x = GroupingTerm, y = percent, fill = sex) +
+  ylab("Percentage") +
+  geom_col() +
+  geom_hline(yintercept = 50, linetype = "dashed", color = "gray40") +
+  geom_text(
+    data = subset(meta.plot2.sig.bothsexes.c, samplesize != 0), aes(label = samplesize), position = position_stack(vjust = .5),
+    color = "white", size = 3.5) +
+  facet_grid(cols = vars(trait), 
+             rows = vars(label), 
+             labeller = label_wrap_gen(width = 18),
+             scales = "free", space = "free") +
+  scale_fill_brewer(palette = "Set2") +
+  theme_bw(base_size = 18) +
+  theme(strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
+        strip.text.x = element_text(size = 12),
+        strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
+        text = element_text(size = 14),
+        panel.spacing = unit(0.5, "lines"),
+        panel.border = element_blank(),
+        axis.line = element_line(),
+        panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
+        panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
+        panel.grid.minor.y = element_blank(),
+        panel.grid.minor.x = element_blank(),
+        legend.position = "none",
+        axis.title.y = element_blank()) +
+  coord_flip()
+### Preparation for Plots on significant sex-bias (Second-order meta analysis results)
+#### Figure 5 B - traits with CI not overlapping 0 
+# Prepare data 
+# create column with 1 = different from zero, 0 = zero included in CI
+#### Male-biased (significant) traits:
+meta.male.plot3.sig <- metacombo %>%
+                       mutate(sigCVR = ifelse(lnCVR_lower > 0, 1, 0),
+                               sigVR = ifelse( lnVR_lower > 0, 1, 0),
+                               sigRR = ifelse( lnRR_lower > 0, 1, 0))
+# Significant subset for lnCVR
+metacombo_male.plot3.CVR <- meta.male.plot3.sig    %>%
+                            filter(sigCVR == 1)    %>%
+                            group_by(GroupingTerm) %>%
+                            nest()
+metacombo_male.plot3.CVR.all <- meta.male.plot3.sig %>%
+                                filter(sigCVR == 1) %>%
+                                nest(data = everything())   
+# Significant subset for lnVR
+metacombo_male.plot3.VR <- meta.male.plot3.sig    %>%
+                           filter(sigVR == 1)     %>%
+                           group_by(GroupingTerm) %>%
+                           nest()
+metacombo_male.plot3.VR.all <- meta.male.plot3.sig    %>%
+                               filter(sigVR == 1)     %>%
+                               nest(data = everything())    
+# Significant subset for lnRR
+metacombo_male.plot3.RR <- meta.male.plot3.sig    %>%
+                           filter(sigRR == 1)     %>%
+                           group_by(GroupingTerm) %>%
+                           nest()
+metacombo_male.plot3.RR.all <- meta.male.plot3.sig %>%
+                               filter(sigRR == 1)  %>%
+                               nest(data = everything())   
+# **Final random effects meta-analyses within grouping terms, with SE of the estimate
+plot3.male.meta.CVR <- metacombo_male.plot3.CVR %>%
+                       mutate(model_lnCVR = map(data, 
+                                                ~ metafor::rma.uni(yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower) / (2 * 1.96), 
+                                              control = list(optimizer = "optim", 
+                                                             optmethod = "Nelder-Mead", 
+                                                             maxit = 1000), 
+                                              verbose = F)))
+plot3.male.meta.VR <- metacombo_male.plot3.VR %>%
+                      mutate(model_lnVR = map(data, 
+                                              ~ metafor::rma.uni(yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
+                                            control = list(optimizer = "optim", 
+                                                           optmethod = "Nelder-Mead", 
+                                                           maxit = 1000), 
+                                            verbose = F)))
+plot3.male.meta.RR <- metacombo_male.plot3.RR %>%
+                      mutate(model_lnRR = map(data, 
+                                              ~ metafor::rma.uni(yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
+                                              control = list(optimizer = "optim", 
+                                                             optmethod = "Nelder-Mead", 
+                                                             maxit = 1000), 
+                                              verbose = F)))
+# Across all grouping terms #
+plot3.male.meta.CVR.all <- metacombo_male.plot3.CVR.all %>%
+                            mutate(model_lnCVR = map(data,
+                                                     ~ metafor::rma.uni(yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower) / (2 * 1.96),
+                                                  control = list(optimizer = "optim", 
+                                                                 optmethod = "Nelder-Mead", 
+                                                                 maxit = 1000), 
+                                                  verbose = F)))
+plot3.male.meta.CVR.all <- plot3.male.meta.CVR.all %>% 
+                            mutate(GroupingTerm = "All")
+plot3.male.meta.VR.all <- metacombo_male.plot3.VR.all %>%
+                          mutate(model_lnVR = map(data, 
+                                                  ~ metafor::rma.uni(yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
+                                                  control = list(optimizer = "optim", 
+                                                                 optmethod = "Nelder-Mead", 
+                                                                 maxit = 1000), 
+                                                  verbose = F)))
+plot3.male.meta.VR.all <- plot3.male.meta.VR.all %>% 
+                          mutate(GroupingTerm = "All")
+plot3.male.meta.RR.all <- metacombo_male.plot3.RR.all %>%
+                          mutate(model_lnRR = map(data, 
+                                                  ~ metafor::rma.uni(yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
+                                                control = list(optimizer = "optim", 
+                                                               optmethod = "Nelder-Mead", 
+                                                               maxit = 1000), 
+                                                verbose = F)))
+plot3.male.meta.RR.all <- plot3.male.meta.RR.all %>% 
+                          mutate(GroupingTerm = "All")
+# Combine with separate grouping term results
+plot3.male.meta.CVR <- bind_rows(plot3.male.meta.CVR, plot3.male.meta.CVR.all)
+ plot3.male.meta.VR <- bind_rows(plot3.male.meta.VR,   plot3.male.meta.VR.all)
+ plot3.male.meta.RR <- bind_rows(plot3.male.meta.RR,   plot3.male.meta.RR.all)
+# **Re-structure data for each grouping term; delete un-used variables
+plot3.male.meta.CVR.b <- as.data.frame(plot3.male.meta.CVR %>% 
+                                       group_by(GroupingTerm) %>%
+                                       mutate( lnCVR = map_dbl(model_lnCVR, pluck(2)), 
+                                               lnCVR_lower = map_dbl(model_lnCVR, pluck(6)), 
+                                               lnCVR_upper = map_dbl(model_lnCVR, pluck(7)), 
+                                               lnCVR_se = map_dbl(model_lnCVR, pluck(3)), 
+                                               lnCVR_I2 = map_dbl(model_lnCVR, pluck("I2"))))[, c(1, 4:8)]
+add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA, NA))) %>% 
+                                  setNames(names(plot3.male.meta.CVR.b))
+plot3.male.meta.CVR.b <- rbind(plot3.male.meta.CVR.b, add.row.hearing) #use bind_rows in R3.6
+plot3.male.meta.CVR.b <- plot3.male.meta.CVR.b[order(plot3.male.meta.CVR.b$GroupingTerm), ]
+plot3.male.meta.VR.b <- as.data.frame(plot3.male.meta.VR %>% 
+                                      group_by(GroupingTerm) %>%
+                                      mutate(lnVR = map_dbl(model_lnVR, pluck(2)), 
+                                             lnVR_lower = map_dbl(model_lnVR, pluck(6)),
+                                             lnVR_upper = map_dbl(model_lnVR, pluck(7)), 
+                                             lnVR_se = map_dbl(model_lnVR, pluck(3)),
+                                             lnVR_I2 = map_dbl(model_lnVR, pluck("I2"))))[, c(1, 4:8)]
+plot3.male.meta.VR.b <- plot3.male.meta.VR.b[order(plot3.male.meta.VR.b$GroupingTerm), ]
+plot3.male.meta.RR.b <- as.data.frame(plot3.male.meta.RR %>% 
+                                      group_by(GroupingTerm) %>% 
+                                      mutate(lnRR = map_dbl(model_lnRR, pluck(2)), 
+                                             lnRR_lower = map_dbl(model_lnRR, pluck(6)),
+                                             lnRR_upper = map_dbl(model_lnRR, pluck(7)), 
+                                             lnRR_se = map_dbl(model_lnRR, pluck(3)),
+                                             lnRR_I2 = map_dbl(model_lnRR, pluck("I2"))))[, c(1, 4:8)]
+plot3.male.meta.RR.b <- plot3.male.meta.RR.b[order(plot3.male.meta.RR.b$GroupingTerm), ]
+overall.male.plot3 <- full_join(plot3.male.meta.CVR.b, plot3.male.meta.VR.b)
+overall.male.plot3 <- full_join(overall.male.plot3,    plot3.male.meta.RR.b)
+overall.male.plot3$GroupingTerm <- factor(overall.male.plot3$GroupingTerm, 
+                                          levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", 
+                                                     "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
+overall.male.plot3$GroupingTerm <- factor(overall.male.plot3$GroupingTerm, 
+                                          rev(levels(overall.male.plot3$GroupingTerm)))
+overall.male.plot3$GroupingTerm <- factor(overall.male.plot3$GroupingTerm, 
+                                          levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", 
+                                                     "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
+overall.male.plot3$GroupingTerm <- factor(overall.male.plot3$GroupingTerm, 
+                                          rev(levels(overall.male.plot3$GroupingTerm)))
+# Restructure MALE data for plotting 
+overall3.male.sig <- gather(overall.male.plot3, parameter, value, c(lnCVR, lnRR), factor_key = TRUE) 
+lnCVR.ci <- overall3.male.sig            %>%
+            filter(parameter == "lnCVR") %>%
+            mutate(ci.low = lnCVR_lower, 
+                   ci.high = lnCVR_upper)
+lnRR.ci <- overall3.male.sig           %>%
+           filter(parameter == "lnRR") %>%
+           mutate(ci.low = lnRR_lower, 
+                 ci.high = lnRR_upper)
+overall4.male.sig <- rbind(lnCVR.ci, lnRR.ci) %>%  #use bind_rows in R3.6
+                     select(GroupingTerm, 
+                            parameter, 
+                            value, 
+                            ci.low, 
+                            ci.high) 
+overall4.male.sig$label <- "CI not overlapping zero"
+# Plot Fig 5B all significant results (CI not overlapping zero) for males. This is the right panel in Figure 5B.
+Metameta_Fig3_male.sig <- overall4.male.sig %>%
+  ggplot(aes(y = GroupingTerm, x = value)) +
+  geom_errorbarh(aes(xmin = ci.low,
+                     xmax = ci.high),
+                 height = 0.1, 
+                 show.legend = FALSE) +
+  geom_point(aes(shape = parameter),
+             fill = "mediumaquamarine", 
+             color = "mediumaquamarine", 
+             size = 2.2, 
+             show.legend = FALSE) +
+  scale_x_continuous(limits = c(0, 0.4),
+                     breaks = c(0, 0.3),
+                       name = "Effect size") +
+  geom_vline(xintercept = 0,
+                  color = "black",
+              linetype = "dashed") +
+  facet_grid(cols = vars(parameter), 
+             rows = vars(label),
+             labeller = label_wrap_gen(width = 23),
+             scales = "free",
+             space = "free") +
+  theme_bw() +
+  theme(strip.text.y = element_text(angle = 270, 
+                                    size = 10, 
+                                    margin = margin(t = 15, r = 15, b = 15, l = 15)),
+        strip.text.x = element_text(size = 12),
+        strip.background = element_rect(colour = NULL, 
+                                        linetype = "blank", 
+                                        fill = "gray90"),
+        text = element_text(size = 14),
+        panel.spacing = unit(0.5, "lines"),
+        panel.border = element_blank(),
+        axis.line = element_line(),
+        panel.grid.major.x = element_line(linetype = "solid", 
+                                          colour = "gray95"),
+        panel.grid.major.y = element_line(linetype = "solid", 
+                                          color = "gray95"),
+        panel.grid.minor.y = element_blank(),
+        panel.grid.minor.x = element_blank(),
+        legend.title = element_blank(),
+        axis.title.x = element_blank(),
+        axis.title.y = element_blank())
+# Metameta_Fig3_male.sig
+#### Female part, significant traits: Female Fig5B sig
+# as above: Prepare data for traits with CI not overlapping 0
+# create column with 1 = different from zero, 0 = zero included in CI
+# Female-biased traits
+meta.female.plot3.sig <- metacombo %>%
+  mutate(sigCVR = ifelse(lnCVR_upper < 0, 1, 0),
+          sigVR = ifelse(lnVR_upper < 0, 1, 0),
+          sigRR = ifelse(lnRR_upper < 0, 1, 0))
+# Significant subset for lnCVR
+metacombo_female.plot3.CVR <- meta.female.plot3.sig  %>%
+                              filter(sigCVR == 1)    %>%
+                              group_by(GroupingTerm) %>%
+                              nest()
+metacombo_female.plot3.CVR.all <- meta.female.plot3.sig %>%
+                                  filter(sigCVR == 1)   %>%
+                                  nest(data = everything())   
+# Significant subset for lnVR
+metacombo_female.plot3.VR <- meta.female.plot3.sig  %>%
+                             filter(sigVR == 1)     %>%
+                             group_by(GroupingTerm) %>%
+                             nest()
+metacombo_female.plot3.VR.all <- meta.female.plot3.sig  %>%
+                                 filter(sigVR == 1)     %>%
+                                 nest(data = everything())   
+# Significant subset for lnRR
+metacombo_female.plot3.RR <- meta.female.plot3.sig  %>%
+                             filter(sigRR == 1)     %>%
+                             group_by(GroupingTerm) %>%
+                             nest()
+metacombo_female.plot3.RR.all <- meta.female.plot3.sig %>%
+                                 filter(sigRR == 1)    %>%
+                                 nest(data = everything())   
+# **Final random effects meta-analyses within grouping terms, with SE of the estimate
+plot3.female.meta.CVR <- metacombo_female.plot3.CVR %>%
+                         mutate(model_lnCVR = map(data, 
+                                                  ~ metafor::rma.uni(yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower) / (2 * 1.96),
+                                                  control = list(optimizer = "optim", 
+                                                                 optmethod = "Nelder-Mead", 
+                                                                 maxit = 1000), 
+                                                  verbose = F)))
+plot3.female.meta.VR <- metacombo_female.plot3.VR %>%
+                        mutate(model_lnVR = map(data, ~ metafor::rma.uni(yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
+                                                control = list(optimizer = "optim", 
+                                                               optmethod = "Nelder-Mead", 
+                                                               maxit = 1000), 
+                                                verbose = F)))
+plot3.female.meta.RR <- metacombo_female.plot3.RR %>%
+                        mutate(model_lnRR = map(data, ~ metafor::rma.uni(yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
+                                                control = list(optimizer = "optim", 
+                                                               optmethod = "Nelder-Mead", 
+                                                               maxit = 1000), 
+                                                verbose = F)))
+# Across all grouping terms #
+plot3.female.meta.CVR.all <- metacombo_female.plot3.CVR.all %>%
+                             mutate(model_lnCVR = map(data, ~ metafor::rma.uni(yi = .x$lnCVR, sei=(.x$lnCVR_upper-.x$lnCVR_lower)/(2 * 1.96),
+                                                       control = list(optimizer = "optim", 
+                                                                      optmethod = "Nelder-Mead", 
+                                                                      maxit = 1000),
+                                                       verbose = F)))
+plot3.female.meta.CVR.all <- plot3.female.meta.CVR.all %>% mutate(GroupingTerm = "All")
+plot3.female.meta.VR.all <- metacombo_female.plot3.VR.all %>%
+  mutate(model_lnVR = map(data, ~ metafor::rma.uni(yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
+                          control = list(optimizer = "optim", 
+                                         optmethod = "Nelder-Mead", 
+                                         maxit = 1000), 
+                          verbose = F)))
+plot3.female.meta.VR.all <- plot3.female.meta.VR.all %>% mutate(GroupingTerm = "All")
+plot3.female.meta.RR.all <- metacombo_female.plot3.RR.all %>%
+                            mutate(model_lnRR = map(data, 
+                                                    ~ metafor::rma.uni(yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
+                                                    control = list(optimizer = "optim", 
+                                                                   optmethod = "Nelder-Mead", 
+                                                                   maxit = 1000), 
+                                                    verbose = F)))
+plot3.female.meta.RR.all <- plot3.female.meta.RR.all %>% 
+                            mutate(GroupingTerm = "All")
+# Combine with separate grouping term results
+plot3.female.meta.CVR <- bind_rows(plot3.female.meta.CVR, plot3.female.meta.CVR.all) #use bind_rows in R3.6
+ plot3.female.meta.VR <- bind_rows(plot3.female.meta.VR,   plot3.female.meta.VR.all)
+ plot3.female.meta.RR <- bind_rows(plot3.female.meta.RR,   plot3.female.meta.RR.all)
+# Re-structure data for each grouping term; delete un-used variables
+plot3.female.meta.CVR.b <- as.data.frame(plot3.female.meta.CVR %>% 
+                                           group_by(GroupingTerm) %>%
+                                          mutate(    lnCVR = map_dbl(model_lnCVR, pluck(2)), 
+                                               lnCVR_lower = map_dbl(model_lnCVR, pluck(6)),
+                                               lnCVR_upper = map_dbl(model_lnCVR, pluck(7)), 
+                                                  lnCVR_se = map_dbl(model_lnCVR, pluck(3)),
+                                                  lnCVR_I2 = map_dbl(model_lnCVR, pluck("I2"))))[, c(1, 4:8)]
+add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA,NA))) %>% 
+                                 setNames(names(plot3.female.meta.CVR.b))
+plot3.female.meta.CVR.b <- rbind(plot3.female.meta.CVR.b, add.row.hearing) #use bind_rows in R3.6
+plot3.female.meta.CVR.b <- plot3.female.meta.CVR.b[order(plot3.female.meta.CVR.b$GroupingTerm), ]
+plot3.female.meta.VR.b <- as.data.frame(plot3.female.meta.VR %>% 
+                                        group_by(GroupingTerm) %>%
+                                        mutate(      lnVR = map_dbl(model_lnVR, pluck(2)), 
+                                               lnVR_lower = map_dbl(model_lnVR, pluck(6)),
+                                               lnVR_upper = map_dbl(model_lnVR, pluck(7)), 
+                                                  lnVR_se = map_dbl(model_lnVR, pluck(3)),
+                                                  lnVR_I2 = map_dbl(model_lnVR, pluck("I2"))))[, c(1, 4:8)]
+plot3.female.meta.VR.b <- plot3.female.meta.VR.b[order(plot3.female.meta.VR.b$GroupingTerm), ]
+plot3.female.meta.RR.b <- as.data.frame(plot3.female.meta.RR %>% 
+                                        group_by(GroupingTerm) %>%
+                                        mutate(      lnRR = map_dbl(model_lnRR, pluck(2)), 
+                                               lnRR_lower = map_dbl(model_lnRR, pluck(6)), 
+                                               lnRR_upper = map_dbl(model_lnRR, pluck(7)), 
+                                                  lnRR_se = map_dbl(model_lnRR, pluck(3)),
+                                                  lnRR_I2 = map_dbl(model_lnRR, pluck("I2"))))[, c(1, 4:8)]
+plot3.female.meta.RR.b <- plot3.female.meta.RR.b[order(plot3.female.meta.RR.b$GroupingTerm), ]
+overall.female.plot3 <- full_join(plot3.female.meta.CVR.b, plot3.female.meta.VR.b)
+overall.female.plot3 <- full_join(overall.female.plot3, plot3.female.meta.RR.b)
+overall.female.plot3$GroupingTerm <- factor(overall.female.plot3$GroupingTerm, 
+                                            levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", 
+                                                       "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
+overall.female.plot3$GroupingTerm <- factor(overall.female.plot3$GroupingTerm, 
+                                            rev(levels(overall.female.plot3$GroupingTerm)))
+# Re-structuring data for plotting
+overall3.female.sig <- gather(overall.female.plot3, parameter, value, c(lnCVR, lnRR), factor_key = TRUE) 
+lnCVR.ci <- overall3.female.sig %>%
+  filter(parameter == "lnCVR") %>%
+  mutate(ci.low = lnCVR_lower, 
+         ci.high = lnCVR_upper)
+# lnVR.ci <- overall3.female.sig  %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
+lnRR.ci <- overall3.female.sig %>%
+  filter(parameter == "lnRR") %>%
+  mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
+overall4.female.sig <- rbind(lnCVR.ci, lnRR.ci) %>%  #use bind_rows in R3.6
+                       select(GroupingTerm, parameter, value, ci.low, ci.high) # lnVR.ci,
+overall4.female.sig$label <- "CI not overlapping zero"
+# PLOT preparation for Fig5B: all significant results (CI not overlapping zero, female )
+Metameta_Fig3_female.sig  <- overall4.female.sig %>%
+  ggplot(aes(y = GroupingTerm, x = value)) +
+  geom_errorbarh(aes(
+    xmin = ci.low,
+    xmax = ci.high),
+  height = 0.1, show.legend = FALSE) +
+  geom_point(aes(shape = parameter),
+    fill = "salmon1", color = "salmon1", size = 2.2,
+    show.legend = FALSE) +
+  scale_x_continuous(
+    limits = c(-0.4, 0),
+    breaks = c(-0.3, 0),
+    name = "Effect size") +
+  geom_vline(
+    xintercept = 0,
+    color = "black",
+    linetype = "dashed") +
+  facet_grid(
+    cols = vars(parameter), # rows = vars(label),
+    # labeller = label_wrap_gen(width = 23),
+    scales = "free",
+    space = "free") +
+  theme_bw() +
+  theme(
+    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
+    strip.text.x = element_text(size = 12),
+    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
+    text = element_text(size = 14),
+    panel.spacing = unit(0.5, "lines"),
+    panel.border = element_blank(),
+    axis.line = element_line(),
+    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
+    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
+    panel.grid.minor.y = element_blank(),
+    panel.grid.minor.x = element_blank(),
+    legend.title = element_blank(),
+    axis.title.x = element_blank(),
+    axis.title.y = element_blank()
+  )
+# Metameta_Fig3_female.sig #(Figure 5B left panel)
+```
+
+```{r FigS1_prep, echo = FALSE, eval = TRUE}
+### Preparing the data
+#The supplemental figures include lnVR (in addition to lnCVR and lnRR, as presented in Figures 4 and 5)
+
+# *Prepare data for all traits
+
+meta.plot2.all <- meta_clean %>%
+  select(lnCVR, lnVR, lnRR, GroupingTerm) %>%
+  arrange(GroupingTerm)
+
+meta.plot2.all.bS1 <- gather(meta.plot2.all, trait, value, c(lnCVR, lnVR, lnRR))
+
+meta.plot2.all.bS1$trait <- factor(meta.plot2.all.bS1$trait, levels = c("lnCVR", "lnVR", "lnRR"))
+
+meta.plot2.all.cS1 <- meta.plot2.all.bS1 %>%
+  group_by_at(vars(trait, GroupingTerm)) %>%
+  summarise(
+    malebias = sum(value > 0), femalebias = sum(value <= 0), total = malebias + femalebias,
+    malepercent = malebias * 100 / total, femalepercent = femalebias * 100 / total
+  )
+
+meta.plot2.all.cS1$label <- "All traits"
+
+# Re-structure to create stacked bar plots
+
+meta.plot2.all.dS1 <- as.data.frame(meta.plot2.all.cS1)
+meta.plot2.all.eS1 <- gather(meta.plot2.all.dS1, key = sex, value = percent, malepercent:femalepercent, factor_key = TRUE)
+
+# Create new sample size variable
+
+meta.plot2.all.eS1$samplesize <- with(meta.plot2.all.eS1, ifelse(sex == "malepercent", malebias, femalebias))
+
+# Add summary row ('All') and re-arrange rows into correct order for plotting (warnings about coercing 'id' into character vector are ok)
+
+meta.plot2.all.fS1 <- meta.plot2.all.eS1 %>% group_by(trait, sex) %>% 
+  summarise(GroupingTerm = "All", malebias = sum(malebias), femalebias = sum(femalebias), total = malebias + femalebias, 
+            label = "All traits", samplesize = sum(samplesize)) %>%
+  mutate(percent = ifelse(sex == "femalepercent", femalebias*100/(malebias+femalebias), malebias*100/(malebias+femalebias))) %>%
+  bind_rows(meta.plot2.all.eS1, .) %>%
+  mutate(rownumber = row_number()) %>%
+  .[c(55, 1:9, 57, 10:18, 59, 19:27, 56, 28:36, 58, 37:45, 60, 46:54), ]
+
+meta.plot2.all.fS1$GroupingTerm <- factor(meta.plot2.all.fS1$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
+meta.plot2.all.fS1$GroupingTerm <- factor(meta.plot2.all.fS1$GroupingTerm, rev(levels(meta.plot2.all.fS1$GroupingTerm)))
+
+malebias_FigS1_alltraits <-
+  ggplot(meta.plot2.all.fS1) +
+  aes(x = GroupingTerm, y = percent, fill = sex) +
+  ylab("Percentage") +
+  geom_col() +
+  geom_hline(yintercept = 50, linetype = "dashed", color = "gray40") +
+  geom_text(
+    data = subset(meta.plot2.all.fS1, samplesize != 0), aes(label = samplesize), position = position_stack(vjust = .5),
+    color = "white", size = 3.5
+  ) +
+  facet_grid(
+    cols = vars(trait), rows = vars(label), labeller = label_wrap_gen(width = 18),
+    scales = "free", space = "free"
+  ) +
+  scale_fill_brewer(palette = "Set2") +
+  theme_bw(base_size = 18) +
+  theme(
+    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
+    strip.text.x = element_text(size = 12),
+    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
+    text = element_text(size = 14),
+    panel.spacing = unit(0.5, "lines"),
+    panel.border = element_blank(),
+    axis.line = element_line(),
+    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
+    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
+    panel.grid.minor.y = element_blank(),
+    panel.grid.minor.x = element_blank(),
+    legend.position = "none",
+    #axis.title.x = element_blank(),
+    axis.title.y = element_blank()
+  ) +
+  coord_flip()
+
+# malebias_FigS1_alltraits     #(panel A in Figure S1)
+
+###  Overall results of second order meta analysis, INCLUDING VR
+#### Re-structure MALE data for plotting
+
+overall3.male.sigS <- gather(overall.male.plot3, parameter, value, c(lnCVR, lnVR, lnRR), factor_key = TRUE)
+
+lnCVR.ci <- overall3.male.sigS %>%
+  filter(parameter == "lnCVR") %>%
+  mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
+lnVR.ci <- overall3.male.sigS %>%
+  filter(parameter == "lnVR") %>%
+  mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
+lnRR.ci <- overall3.male.sigS %>%
+  filter(parameter == "lnRR") %>%
+  mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
+
+overall4.male.sigS <- rbind(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high) #use bind_rows in R3.6
+
+overall4.male.sigS$label <- "CI not overlapping zero"
+
+# Data are re-structured, and grouping terms are being re-ordered
+
+overall3S <- gather(overall2, parameter, value, c(lnCVR, lnVR, lnRR), factor_key = TRUE)
+
+lnCVR.ci <- overall3S %>%
+  filter(parameter == "lnCVR") %>%
+  mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
+lnVR.ci <- overall3S %>%
+  filter(parameter == "lnVR") %>%
+  mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
+lnRR.ci <- overall3S %>%
+  filter(parameter == "lnRR") %>%
+  mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
+
+overall4S <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
+
+# Re-order grouping terms
+
+overall4S$GroupingTerm <- factor(overall4S$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
+overall4S$GroupingTerm <- factor(overall4S$GroupingTerm, rev(levels(overall4S$GroupingTerm)))
+overall4S$label <- "All traits"
+
+#### Preparation for plot, including lnVR
+# Sub-Plot  for Figure S1: all traits (S1 B)
+
+Metameta_FigS1_alltraits <- overall4S %>%
+
+  ggplot(aes(y = GroupingTerm, x = value)) +
+  geom_errorbarh(aes(
+    xmin = ci.low,
+    xmax = ci.high
+  ),
+  height = 0.1, show.legend = FALSE
+  ) +
+  geom_point(aes(shape = parameter),
+    fill = "black",
+    color = "black", size = 2.2,
+    show.legend = FALSE
+  ) +
+  scale_x_continuous(
+    limits = c(-0.24, 0.25),
+    breaks = c(-0.2, -0.1, 0, 0.1, 0.2),
+    name = "Effect size"
+  ) +
+  geom_vline(
+    xintercept = 0,
+    color = "black",
+    linetype = "dashed"
+  ) +
+  facet_grid(
+    cols = vars(parameter), rows = vars(label),
+    labeller = label_wrap_gen(width = 23),
+    scales = "free",
+    space = "free"
+  ) +
+  theme_bw() +
+  theme(
+    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
+    strip.text.x = element_text(size = 12),
+    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
+    text = element_text(size = 14),
+    panel.spacing = unit(0.5, "lines"),
+    panel.border = element_blank(),
+    axis.line = element_line(),
+    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
+    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
+    panel.grid.minor.y = element_blank(),
+    panel.grid.minor.x = element_blank(),
+    legend.title = element_blank(),
+    axis.title.x = element_text(hjust = 0.5, size = 14),
+    axis.title.y = element_blank()
+  )
+
+#This Figure extends Figure 4, as it includes results not only for lnCVR and lnRR but also lnCVR.
+In addition, we compare two different assessments of sex-bias, significance (CI not overlapping zero) and sex differences in male / female ratios > 10%
+# Plot FigS2 all significant results (CI not overlapping zero) for males, count data
+
+meta.plot2.sig.bS <- meta.plot2.sig[, c("lnCVR", "lnVR", "lnRR", "lnCVRsig", "lnVRsig", "lnRRsig", "GroupingTerm")]
+
+meta.plot2.sig.cS <- gather(meta.plot2.sig.bS, trait, value, lnCVR:lnRR)
+meta.plot2.sig.cS$sig <- "placeholder"
+
+meta.plot2.sig.cS$trait <- factor(meta.plot2.sig.cS$trait, levels = c("lnCVR", "lnVR", "lnRR"))
+
+meta.plot2.sig.cS$sig <- ifelse(meta.plot2.sig.cS$trait == "lnCVR", meta.plot2.sig.cS$lnCVRsig,
+  ifelse(meta.plot2.sig.cS$trait == "lnVR", meta.plot2.sig.cS$lnVRsig, meta.plot2.sig.cS$lnRRsig))
+
+# choosing sex biased ln-ratios significantly larger than 0
+meta.plotS2.sig.malebias <- meta.plot2.sig.cS %>%
+  group_by_at(vars(trait, GroupingTerm)) %>%
+  filter(sig == 1) %>%
+  summarise(male_sig = sum(value > 0), female_sig = sum(value < 0), total = male_sig + female_sig)
+
+meta.plotS2.sig.malebias <- ungroup(meta.plotS2.sig.malebias) %>%
+  add_row(trait = "lnCVR", GroupingTerm = "Hearing", male_sig = 0, female_sig = 0, .before = 4) %>% # add "Hearing" for lnCVR (not filtered as only zeros)
+  mutate(malepercent = male_sig * 100 / total, femalepercent = female_sig * 100 / total)
+
+meta.plotS2.sig.malebias$label <- "CI not overlapping zero"
+
+# restructure to create stacked bar plots
+
+meta.plotS2.sig.bothsexes <- as.data.frame(meta.plotS2.sig.malebias)
+meta.plotS2.sig.bothsexes.b <- gather(meta.plotS2.sig.bothsexes, key = sex, value = percent, malepercent:femalepercent, factor_key = TRUE)
+
+# create new sample size variable
+
+meta.plotS2.sig.bothsexes.b$samplesize <- with(meta.plotS2.sig.bothsexes.b, ifelse(sex == "malepercent", male_sig, female_sig))
+
+# Add summary row ('All') and re-arrange rows into correct order for plotting (warnings about coercing 'id' into character vector are ok)
+
+meta.plotS2.sig.bothsexes.c <- meta.plotS2.sig.bothsexes.b %>% group_by(trait, sex) %>% 
+  summarise(GroupingTerm = "All", male_sig = sum(male_sig), female_sig = sum(female_sig), total = male_sig + female_sig, 
+            label = "CI not overlapping zero", samplesize = sum(samplesize)) %>%
+  mutate(percent = ifelse(sex == "femalepercent", female_sig*100/(male_sig + female_sig), male_sig*100/(male_sig + female_sig))) %>%
+  bind_rows(meta.plotS2.sig.bothsexes.b, .) %>%
+  mutate(rownumber = row_number()) %>%
+  .[c(55, 1:9, 57, 10:18, 59, 19:27, 56, 28:36, 58, 37:45, 60, 46:54), ]
+
+meta.plotS2.sig.bothsexes.c$GroupingTerm <- factor(meta.plotS2.sig.bothsexes.c$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
+meta.plotS2.sig.bothsexes.c$GroupingTerm <- factor(meta.plotS2.sig.bothsexes.c$GroupingTerm, rev(levels(meta.plotS2.sig.bothsexes.c$GroupingTerm)))
+
+# *Plot Fig2 all significant results (CI not overlapping zero):
+#     no sig. lnCVR for 'Hearing' in either sex; no sig. male-biased lnCVR for 'Immunology' and 'Eye, and no sig. male-biased lnVR for 'Eye'
+
+malebias_FigS2_sigtraits <-
+  ggplot(meta.plotS2.sig.bothsexes.c) +
+  aes(x = GroupingTerm, y = percent, fill = sex) +
+  ylab("Percentage") +
+  geom_col() +
+  geom_hline(yintercept = 50, linetype = "dashed", color = "gray40") +
+  geom_text(
+    data = subset(meta.plotS2.sig.bothsexes.c, samplesize != 0), aes(label = samplesize), position = position_stack(vjust = .5),
+    color = "white", size = 3.5
+  ) +
+  facet_grid(
+    cols = vars(trait), rows = vars(label), labeller = label_wrap_gen(width = 18),
+    scales = "free", space = "free"
+  ) +
+  scale_fill_brewer(palette = "Set2") +
+  theme_bw(base_size = 18) +
+  theme(
+    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
+    strip.text.x = element_text(size = 12),
+    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
+    text = element_text(size = 14),
+    panel.spacing = unit(0.5, "lines"),
+    panel.border = element_blank(),
+    axis.line = element_line(),
+    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
+    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
+    panel.grid.minor.y = element_blank(),
+    panel.grid.minor.x = element_blank(),
+    legend.position = "none",
+    #axis.title.x = element_blank(),
+    axis.title.y = element_blank()
+  ) +
+  coord_flip()
+
+# malebias_FigS2_sigtraits # this is Figure S2 A
+
+#Prepare data for traits with effect size ratios > 10% larger in males, supplemental Figure S2
+
+#### Over 10% male bias, count data (first- order metanalysis)
+
+meta.plot2.over10 <- meta_clean %>%
+                    select(lnCVR, lnVR, lnRR, GroupingTerm) %>%
+                    arrange(GroupingTerm)
+
+meta.plot2.over10.b <- gather(meta.plot2.over10, trait, value, c(lnCVR, lnVR, lnRR))
+
+meta.plot2.over10.b$trait <- factor(meta.plot2.over10.b$trait, levels = c("lnCVR", "lnVR", "lnRR"))
+
+meta.plot2.over10.c <- meta.plot2.over10.b %>%
+                      group_by_at(vars(trait, GroupingTerm)) %>%
+                      summarise(malebias = sum(value > log(11 / 10)), 
+                                femalebias = sum(value < log(9 / 10)), 
+                                total = malebias + femalebias,
+                                malepercent = malebias * 100 / total, 
+                                femalepercent = femalebias * 100 / total)
+
+meta.plot2.over10.c$label <- "Sex difference in m/f ratios > 10%"
+
+# restructure to create stacked bar plots
+
+meta.plot2.over10.c <- as.data.frame(meta.plot2.over10.c)
+meta.plot2.over10.d <- gather(meta.plot2.over10.c, key = sex, value = percent, malepercent:femalepercent, factor_key = TRUE)
+
+# create new sample size variable
+
+meta.plot2.over10.d$samplesize <- with(meta.plot2.over10.d, ifelse(sex == "malepercent", malebias, femalebias))
+
+# Add summary row ('All') and re-arrange rows into correct order for plotting (warnings about coercing 'id' into character vector are ok)
+
+meta.plot2.over10.e <- meta.plot2.over10.d %>% 
+                      group_by(trait, sex) %>% 
+                      summarise(GroupingTerm = "All", malebias = sum(malebias), 
+                                femalebias = sum(femalebias), 
+                                total = malebias + femalebias, 
+                                label = "Sex difference in m/f ratios > 10%", 
+                                samplesize = sum(samplesize)) %>%
+                      mutate(percent = ifelse(sex == "femalepercent", 
+                                              femalebias*100/(malebias + femalebias), 
+                                              malebias*100/(malebias + femalebias))) %>%
+                      bind_rows(meta.plot2.over10.d, .) %>%
+                      mutate(rownumber = row_number()) %>%
+                      .[c(55, 1:9, 57, 10:18, 59, 19:27, 56, 28:36, 58, 37:45, 60, 46:54), ]
+
+meta.plot2.over10.e$GroupingTerm <- factor(meta.plot2.over10.e$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
+meta.plot2.over10.e$GroupingTerm <- factor(meta.plot2.over10.e$GroupingTerm, rev(levels(meta.plot2.over10.e$GroupingTerm)))
+
+# PLOT:  Fig2 Sex difference in m/f ratio > 10% (Fig S2 A, lower panel)
+
+malebias_Fig2_over10 <-
+  ggplot(meta.plot2.over10.e) +
+  aes(x = GroupingTerm, y = percent, fill = sex) +
+  ylab("Percentage") +
+  geom_col() +
+  geom_hline(yintercept = 50, linetype = "dashed", color = "gray40") +
+  geom_text(
+    data = subset(meta.plot2.over10.e, samplesize != 0), aes(label = samplesize), position = position_stack(vjust = .5),
+    color = "white", size = 3.5
+  ) +
+  facet_grid(
+    cols = vars(trait), rows = vars(label), labeller = label_wrap_gen(width = 18),
+    scales = "free", space = "free"
+  ) +
+  scale_fill_brewer(palette = "Set2") +
+  theme_bw(base_size = 18) +
+  theme(
+    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
+    strip.text.x = element_blank(),
+    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
+    text = element_text(size = 14),
+    panel.spacing = unit(0.5, "lines"),
+    panel.border = element_blank(),
+    axis.line = element_line(),
+    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
+    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
+    panel.grid.minor.y = element_blank(),
+    panel.grid.minor.x = element_blank(),
+    legend.position = "none",
+    #axis.title.x = element_blank(),
+    axis.title.y = element_blank()
+  ) +
+  coord_flip()
+
+#### 3.2: Preparation for Figure 4S2 B (second-order meta-analysis)
+#### 3.3: Female Figure, significant and highly biased traits (Figure S2 B, left hand side panels)
+#Preparing data for traits with CI not overlapping 0: 
+#create column with 1= different from zero, 0= zero included in CI (for Figure S2 B, top left panel)
+
+#Restructure data for plotting
+
+overall3.female.sigS <- gather(overall.female.plot3, parameter, value, c(lnCVR, lnVR, lnRR), factor_key = TRUE)
+
+lnCVR.ci <- overall3.female.sigS %>%
+  filter(parameter == "lnCVR") %>%
+  mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
+lnVR.ci <- overall3.female.sigS %>%
+  filter(parameter == "lnVR") %>%
+  mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
+lnRR.ci <- overall3.female.sigS %>%
+  filter(parameter == "lnRR") %>%
+  mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
+
+overall4.female.sigS <- rbind(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high) # Note: bind_rows may need to be replaced by rbind
+
+overall4.female.sigS <- overall4.female.sigS %>%
+                          mutate(value = as.numeric(value),
+                                 ci.low = as.numeric(ci.low),
+                                 ci.high = as.numeric(ci.high))
+
+overall4.female.sigS$label <- "CI not overlapping zero"
+
+# PLOT female-bias:  significant traits
+
+Metameta_FigS2_female.sig <- overall4.female.sigS %>%
+  ggplot(aes(y = GroupingTerm, x = value)) +
+  geom_errorbarh(aes(
+    xmin = ci.low,
+    xmax = ci.high
+  ),
+  height = 0.1, show.legend = FALSE
+  ) +
+  geom_point(aes(shape = parameter),
+    fill = "salmon1", color = "salmon1", size = 2.2,
+    show.legend = FALSE
+  ) +
+  scale_x_continuous(
+    limits = c(-0.4, 0),
+    breaks = c(-0.3, 0),
+    name = "Effect size"
+  ) +
+  geom_vline(
+    xintercept = 0,
+    color = "black",
+    linetype = "dashed"
+  ) +
+  facet_grid(
+    cols = vars(parameter), # rows = vars(label),
+    # labeller = label_wrap_gen(width = 23),
+    scales = "free",
+    space = "free"
+  ) +
+  theme_bw() +
+  theme(
+    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
+    strip.text.x = element_text(size = 12),
+    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
+    text = element_text(size = 14),
+    panel.spacing = unit(0.5, "lines"),
+    panel.border = element_blank(),
+    axis.line = element_line(),
+    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
+    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
+    panel.grid.minor.y = element_blank(),
+    panel.grid.minor.x = element_blank(),
+    legend.title = element_blank(),
+    axis.title.x = element_blank(),
+    axis.title.y = element_blank()
+  )
+
+#### Prepare data for traits with m/f difference > 10%, Female bias (Figure 4S2 B, bottom left)
+
+meta.plot3.perc <- metacombo %>%
+  mutate(
+    percCVR = ifelse(lnCVR < log(9 / 10), 1, 0),
+    percVR = ifelse(lnVR < log(9 / 10), 1, 0),
+    percRR = ifelse(lnRR < log(9 / 10), 1, 0)
+  )
+
+# Significant subset for lnCVR
+metacombo_plot3.CVR.perc <- meta.plot3.perc %>%
+  filter(percCVR == 1) %>%
+  group_by(GroupingTerm) %>%
+  nest()
+
+metacombo_plot3.CVR.perc.all <- meta.plot3.perc %>%
+  filter(percCVR == 1) %>%
+  nest(data = everything())
+
+# Significant subset for lnVR
+metacombo_plot3.VR.perc <- meta.plot3.perc %>%
+  filter(percVR == 1) %>%
+  group_by(GroupingTerm) %>%
+  nest()
+
+metacombo_plot3.VR.perc.all <- meta.plot3.perc %>%
+  filter(percVR == 1) %>%
+  nest(data = everything())
+
+# Significant subset for lnRR
+metacombo_plot3.RR.perc <- meta.plot3.perc %>%
+  filter(percRR == 1) %>%
+  group_by(GroupingTerm) %>%
+  nest()
+
+metacombo_plot3.RR.perc.all <- meta.plot3.perc %>%
+  filter(percRR == 1) %>%
+  nest(data = everything())
+
+# **Final random effects meta-analyses within grouping terms, with SE of the estimate
+
+plot3.meta.CVR.perc <- metacombo_plot3.CVR.perc %>%
+  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+plot3.meta.VR.perc <- metacombo_plot3.VR.perc %>%
+  mutate(model_lnVR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+plot3.meta.RR.perc <- metacombo_plot3.RR.perc %>%
+  mutate(model_lnRR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+# Across all grouping terms #
+
+plot3.meta.CVR.perc.all <- metacombo_plot3.CVR.perc.all %>%
+  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+plot3.meta.CVR.perc.all <- plot3.meta.CVR.perc.all %>% mutate(GroupingTerm = "All")
+
+plot3.meta.VR.perc.all <- metacombo_plot3.VR.perc.all %>%
+  mutate(model_lnVR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+plot3.meta.VR.perc.all <- plot3.meta.VR.perc.all %>% mutate(GroupingTerm = "All")
+
+plot3.meta.RR.perc.all <- metacombo_plot3.RR.perc.all %>%
+  mutate(model_lnRR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+plot3.meta.RR.perc.all <- plot3.meta.RR.perc.all %>% mutate(GroupingTerm = "All")
+
+# Combine with separate grouping term results
+
+plot3.meta.CVR.perc <- bind_rows(plot3.meta.CVR.perc, plot3.meta.CVR.perc.all)
+plot3.meta.VR.perc <- bind_rows(plot3.meta.VR.perc, plot3.meta.VR.perc.all)
+plot3.meta.RR.perc <- bind_rows(plot3.meta.RR.perc, plot3.meta.RR.perc.all)
+
+# **Re-structure data for each grouping term; delete un-used variables: "Hearing missing for all 3 parameters"
+
+plot3.meta.CVR.perc.b <- as.data.frame(plot3.meta.CVR.perc %>% group_by(GroupingTerm) %>%
+  mutate(
+    lnCVR = map_dbl(model_lnCVR, pluck(2)), lnCVR_lower = map_dbl(model_lnCVR, pluck(6)),
+    lnCVR_upper = map_dbl(model_lnCVR, pluck(7)), lnCVR_se = map_dbl(model_lnCVR, pluck(3))
+  ))[, c(1, 4:7)]
+add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.meta.CVR.perc.b))
+plot3.meta.CVR.perc.b <- rbind(plot3.meta.CVR.perc.b, add.row.hearing)
+plot3.meta.CVR.perc.b <- plot3.meta.CVR.perc.b[order(plot3.meta.CVR.perc.b$GroupingTerm), ]
+
+plot3.meta.VR.perc.b <- as.data.frame(plot3.meta.VR.perc %>% group_by(GroupingTerm) %>%
+  mutate(
+    lnVR = map_dbl(model_lnVR, pluck(2)), lnVR_lower = map_dbl(model_lnVR, pluck(6)),
+    lnVR_upper = map_dbl(model_lnVR, pluck(7)), lnVR_se = map_dbl(model_lnVR, pluck(3))
+  ))[, c(1, 4:7)]
+add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.meta.VR.perc.b))
+plot3.meta.VR.perc.b <- rbind(plot3.meta.VR.perc.b, add.row.hearing)
+plot3.meta.VR.perc.b <- plot3.meta.VR.perc.b[order(plot3.meta.VR.perc.b$GroupingTerm), ]
+
+plot3.meta.RR.perc.b <- as.data.frame(plot3.meta.RR.perc %>% group_by(GroupingTerm) %>%
+  mutate(
+    lnRR = map_dbl(model_lnRR, pluck(2)), lnRR_lower = map_dbl(model_lnRR, pluck(6)),
+    lnRR_upper = map_dbl(model_lnRR, pluck(7)), lnRR_se = map_dbl(model_lnRR, pluck(3))
+  ))[, c(1, 4:7)]
+add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.meta.RR.perc.b))
+plot3.meta.RR.perc.b <- rbind(plot3.meta.RR.perc.b, add.row.hearing)
+add.row.hematology <- as.data.frame(t(c("Hematology", NA, NA, NA, NA))) %>%
+  setNames(names(plot3.meta.RR.perc.b))
+plot3.meta.RR.perc.b <- rbind(plot3.meta.RR.perc.b, add.row.hematology)
+
+plot3.meta.RR.perc.b <- plot3.meta.RR.perc.b[order(plot3.meta.RR.perc.b$GroupingTerm), ]
+
+plot3.meta.CVR.perc.c <- full_join(plot3.meta.CVR.perc.b, plot3.meta.VR.perc.b)
+overall.plot3.perc <- full_join(plot3.meta.CVR.perc.c, plot3.meta.RR.perc.b)
+
+overall.plot3.perc$GroupingTerm <- factor(overall.plot3.perc$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
+overall.plot3.perc$GroupingTerm <- factor(overall.plot3.perc$GroupingTerm, rev(levels(overall.plot3.perc$GroupingTerm)))
+
+# Restructure data for plotting
+# Female bias, 10 percent difference
+
+overall3.perc <- gather(overall.plot3.perc, parameter, value, c(lnCVR, lnVR, lnRR), factor_key = TRUE)
+
+lnCVR.ci <- overall3.perc %>%
+  filter(parameter == "lnCVR") %>%
+  mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
+lnVR.ci <- overall3.perc  %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
+lnRR.ci <- overall3.perc %>%
+  filter(parameter == "lnRR") %>%
+  mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
+
+overall4.perc <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
+
+overall4.perc$label <- "Sex difference in m/f ratios > 10%"
+
+overall4.perc$value <- as.numeric(overall4.perc$value)
+overall4.perc$ci.low <- as.numeric(overall4.perc$ci.low)
+overall4.perc$ci.high <- as.numeric(overall4.perc$ci.high)
+
+# Plot FigS2 all >10% difference (female)
+# Figure S2B, bottom left
+
+Metameta_Fig3_female.perc <- overall4.perc %>%
+  ggplot(aes(y = GroupingTerm, x = value)) +
+  geom_errorbarh(aes(
+    xmin = ci.low,
+    xmax = ci.high
+  ),
+  height = 0.1, show.legend = FALSE
+  ) +
+  geom_point(aes(shape = parameter),
+    fill = "salmon1", color = "salmon1", size = 2.2,
+    show.legend = FALSE
+  ) +
+
+  # scale_shape_manual(values =
+
+  scale_x_continuous(
+    limits = c(-0.53, 0.2),
+    breaks = c(-0.3, 0),
+    name = "Effect size"
+  ) +
+  geom_vline(
+    xintercept = 0,
+    color = "black",
+    linetype = "dashed"
+  ) +
+  facet_grid(
+    cols = vars(parameter), # rows = vars(label),
+    # labeller = label_wrap_gen(width = 23),
+    scales = "free",
+    space = "free"
+  ) +
+  theme_bw() +
+  theme(
+    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
+    strip.text.x = element_blank(),
+    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
+    text = element_text(size = 14),
+    panel.spacing = unit(0.5, "lines"),
+    panel.border = element_blank(),
+    axis.line = element_line(),
+    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
+    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
+    panel.grid.minor.y = element_blank(),
+    panel.grid.minor.x = element_blank(),
+    legend.title = element_blank(),
+    axis.title.x = element_text(hjust = 0.5, size = 14),
+    axis.title.y = element_blank()
+  )
+
+#### 3.4: Male Figure, significant and highly biased traits (Figure 4S2 B, right hand side panels)
+#Restructuring data with significant male bias (for Figure 4S2 B, top right panel)
+
+overall3.male.sigS <- gather(overall.male.plot3, parameter, value, c(lnCVR, lnVR, lnRR), factor_key = TRUE)
+
+lnCVR.ci <- overall3.male.sigS %>%
+  filter(parameter == "lnCVR") %>%
+  mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
+lnVR.ci <- overall3.male.sigS %>%
+  filter(parameter == "lnVR") %>%
+  mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
+lnRR.ci <- overall3.male.sigS %>%
+  filter(parameter == "lnRR") %>%
+  mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
+
+overall4.male.sigS <- rbind(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high) %>% 
+  mutate(value = as.numeric(value), ci.low = as.numeric(ci.low), ci.high = as.numeric(ci.high))
+# R 3.6: do not use "%>% mutate(value = as.numeric(value), ci.low = as.numeric(ci.low), ci.high = as.numeric(ci.high))"
+overall4.male.sigS$label <- "CI not overlapping zero"
+
+# Plot FigS2 all significant results (CI not overlapping zero, male )
+
+Metameta_FigS2_male.sig <- overall4.male.sigS %>%
+  ggplot(aes(y = GroupingTerm, x = value)) +
+  geom_errorbarh(aes(
+    xmin = ci.low,
+    xmax = ci.high
+  ),
+  height = 0.1, show.legend = FALSE
+  ) +
+  geom_point(aes(shape = parameter),
+    fill = "mediumaquamarine", color = "mediumaquamarine", size = 2.2,
+    show.legend = FALSE
+  ) +
+  scale_x_continuous(
+    limits = c(0, 0.4),
+    breaks = c(0, 0.3),
+    name = "Effect size"
+  ) +
+  geom_vline(
+    xintercept = 0,
+    color = "black",
+    linetype = "dashed"
+  ) +
+  facet_grid(
+    cols = vars(parameter), rows = vars(label),
+    labeller = label_wrap_gen(width = 23),
+    scales = "free",
+    space = "free"
+  ) +
+  theme_bw() +
+  theme(
+    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
+    strip.text.x = element_text(size = 12),
+    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
+    text = element_text(size = 14),
+    panel.spacing = unit(0.5, "lines"),
+    panel.border = element_blank(),
+    axis.line = element_line(),
+    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
+    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
+    panel.grid.minor.y = element_blank(),
+    panel.grid.minor.x = element_blank(),
+    legend.title = element_blank(),
+    axis.title.x = element_blank(),
+    axis.title.y = element_blank()
+  )
+
+# Metameta_FigS2_male.sig
+
+## Prepare data for traits with m/f difference > 10%. Male bias
+### Create column with 1= larger, 0= difference not larger than 10% between male/female ratios
+
+meta.male.plot3.perc <- metacombo %>%
+  mutate(
+    percCVR = ifelse(lnCVR > log(11 / 10), 1, 0),
+     percVR = ifelse( lnVR > log(11 / 10), 1, 0),
+     percRR = ifelse( lnRR > log(11 / 10), 1, 0)
+  )
+
+# Significant subset for lnCVR
+metacombo_male.plot3.CVR.perc <- meta.male.plot3.perc %>%
+                                filter(percCVR == 1) %>%
+                                group_by(GroupingTerm) %>%
+                                nest()
+
+metacombo_male.plot3.CVR.perc.all <- meta.male.plot3.perc %>%
+                filter(percCVR == 1) %>%
+  nest(data = everything())
+
+# Significant subset for lnVR
+metacombo_male.plot3.VR.perc <- meta.male.plot3.perc %>%
+  filter(percVR == 1) %>%
+  group_by(GroupingTerm) %>%
+  nest()
+
+metacombo_male.plot3.VR.perc.all <- meta.male.plot3.perc %>%
+  filter(percVR == 1) %>%
+  nest(data = everything())
+
+# Significant subset for lnRR
+metacombo_male.plot3.RR.perc <- meta.male.plot3.perc %>%
+  filter(percRR == 1) %>%
+  group_by(GroupingTerm) %>%
+  nest()
+
+metacombo_male.plot3.RR.perc.all <- meta.male.plot3.perc %>%
+  filter(percRR == 1) %>%
+  nest(data = everything())
+
+# Final random effects meta-analyses within grouping terms and across grouping terms, with SE of the estimate
+
+plot3.male.meta.CVR.perc <- metacombo_male.plot3.CVR.perc %>%
+  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+plot3.male.meta.VR.perc <- metacombo_male.plot3.VR.perc %>%
+  mutate(model_lnVR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+plot3.male.meta.RR.perc <- metacombo_male.plot3.RR.perc %>%
+  mutate(model_lnRR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+# Across all grouping terms
+
+plot3.male.meta.CVR.perc.all <- metacombo_male.plot3.CVR.perc.all %>%
+  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+plot3.male.meta.CVR.perc.all <- plot3.male.meta.CVR.perc.all %>% mutate(GroupingTerm = "All")
+
+plot3.male.meta.VR.perc.all <- metacombo_male.plot3.VR.perc.all %>%
+  mutate(model_lnVR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+plot3.male.meta.VR.perc.all <- plot3.male.meta.VR.perc.all %>% mutate(GroupingTerm = "All")
+
+plot3.male.meta.RR.perc.all <- metacombo_male.plot3.RR.perc.all %>%
+  mutate(model_lnRR = map(data, ~ metafor::rma.uni(
+    yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
+    control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
+  )))
+
+plot3.male.meta.RR.perc.all <- plot3.male.meta.RR.perc.all %>% mutate(GroupingTerm = "All")
+
+# Combine with separate grouping term results
+
+plot3.male.meta.CVR.perc <- bind_rows(plot3.male.meta.CVR.perc, plot3.male.meta.CVR.perc.all)
+plot3.male.meta.VR.perc <- bind_rows(plot3.male.meta.VR.perc, plot3.male.meta.VR.perc.all)
+plot3.male.meta.RR.perc <- bind_rows(plot3.male.meta.RR.perc, plot3.male.meta.RR.perc.all)
+
+# **Re-structure data for each grouping term; delete un-used variables: "Hearing missing for all 3 parameters"
+
+plot3.male.meta.CVR.perc.b <- as.data.frame(plot3.male.meta.CVR.perc %>% group_by(GroupingTerm) %>%
+  mutate(
+    lnCVR = map_dbl(model_lnCVR, pluck(2)), lnCVR_lower = map_dbl(model_lnCVR, pluck(6)),
+    lnCVR_upper = map_dbl(model_lnCVR, pluck(7)), lnCVR_se = map_dbl(model_lnCVR, pluck(3))
+  ))[, c(1, 4:7)]
+add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.male.meta.CVR.perc.b))
+plot3.male.meta.CVR.perc.b <- rbind(plot3.male.meta.CVR.perc.b, add.row.hearing)
+plot3.male.meta.CVR.perc.b <- plot3.male.meta.CVR.perc.b[order(plot3.male.meta.CVR.perc.b$GroupingTerm), ]
+
+plot3.male.meta.VR.perc.b <- as.data.frame(plot3.male.meta.VR.perc %>% group_by(GroupingTerm) %>%
+  mutate(
+    lnVR = map_dbl(model_lnVR, pluck(2)), lnVR_lower = map_dbl(model_lnVR, pluck(6)),
+    lnVR_upper = map_dbl(model_lnVR, pluck(7)), lnVR_se = map_dbl(model_lnVR, pluck(3))
+  ))[, c(1, 4:7)]
+add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.male.meta.VR.perc.b))
+plot3.male.meta.VR.perc.b <- rbind(plot3.male.meta.VR.perc.b, add.row.hearing)
+plot3.male.meta.VR.perc.b <- plot3.male.meta.VR.perc.b[order(plot3.male.meta.VR.perc.b$GroupingTerm), ]
+
+plot3.male.meta.RR.perc.b <- as.data.frame(plot3.male.meta.RR.perc %>% group_by(GroupingTerm) %>%
+  mutate(
+    lnRR = map_dbl(model_lnRR, pluck(2)), lnRR_lower = map_dbl(model_lnRR, pluck(6)),
+    lnRR_upper = map_dbl(model_lnRR, pluck(7)), lnRR_se = map_dbl(model_lnRR, pluck(3))
+  ))[, c(1, 4:7)]
+add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>%
+  setNames(names(plot3.male.meta.RR.perc.b))
+plot3.male.meta.RR.perc.b <- rbind(plot3.male.meta.RR.perc.b, add.row.hearing)
+
+add.row.eye <- as.data.frame(t(c("Eye", NA, NA, NA, NA))) %>%
+  setNames(names(plot3.male.meta.RR.perc.b))
+plot3.male.meta.RR.perc.b <- rbind(plot3.male.meta.RR.perc.b, add.row.eye)
+
+plot3.male.meta.RR.perc.b <- plot3.male.meta.RR.perc.b[order(plot3.male.meta.RR.perc.b$GroupingTerm), ]
+
+plot3.male.meta.CVR.Vr.perc <- full_join(plot3.male.meta.CVR.perc.b, plot3.male.meta.VR.perc.b)
+overall.male.plot3.perc <- full_join(plot3.male.meta.CVR.Vr.perc, plot3.male.meta.RR.perc.b)
+
+overall.male.plot3.perc$GroupingTerm <- factor(overall.male.plot3.perc$GroupingTerm, levels = c("Behaviour", "Morphology", "Metabolism", "Physiology", "Immunology", "Hematology", "Heart", "Hearing", "Eye", "All"))
+overall.male.plot3.perc$GroupingTerm <- factor(overall.male.plot3.perc$GroupingTerm, rev(levels(overall.male.plot3.perc$GroupingTerm)))
+
+# Restructure data for plotting : Male biased, 10% difference
+
+overall3.perc <- gather(overall.male.plot3.perc, parameter, value, c(lnCVR, lnVR, lnRR), factor_key = TRUE)
+
+lnCVR.ci <- overall3.perc %>%
+  filter(parameter == "lnCVR") %>%
+  mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
+lnVR.ci <- overall3.perc  %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
+lnRR.ci <- overall3.perc %>%
+  filter(parameter == "lnRR") %>%
+  mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)
+
+overall4.male.perc <- bind_rows(lnCVR.ci,lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
+
+overall4.male.perc$label <- "Sex difference in m/f ratios > 10%"
+
+overall4.male.perc$value <- as.numeric(overall4.male.perc$value)
+overall4.male.perc$ci.low <- as.numeric(overall4.male.perc$ci.low)
+overall4.male.perc$ci.high <- as.numeric(overall4.male.perc$ci.high)
+
+# Plot Fig S2 all >10% difference (male bias)
+# S2 B, bottom right
+
+Metameta_Fig3_male.perc <- overall4.male.perc %>% # filter(., GroupingTerm != "Hearing") %>%
+  ggplot(aes(y = GroupingTerm, x = value)) +
+  geom_errorbarh(aes(
+    xmin = ci.low,
+    xmax = ci.high
+  ),
+  height = 0.1, show.legend = FALSE
+  ) +
+  geom_point(aes(
+    shape = parameter,
+    fill = parameter
+  ),
+  color = "mediumaquamarine", size = 2.2,
+  show.legend = FALSE
+  ) +
+  scale_x_continuous(
+    limits = c(-0.2, 0.62),
+    breaks = c(0, 0.3),
+    name = "Effect size"
+  ) +
+  geom_vline(
+    xintercept = 0,
+    color = "black",
+    linetype = "dashed"
+  ) +
+  facet_grid(
+    cols = vars(parameter), rows = vars(label),
+    labeller = label_wrap_gen(width = 23),
+    scales = "free",
+    space = "free"
+  ) +
+  theme_bw() +
+  theme(
+    strip.text.y = element_text(angle = 270, size = 10, margin = margin(t = 15, r = 15, b = 15, l = 15)),
+    strip.text.x = element_blank(),
+    strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
+    text = element_text(size = 14),
+    panel.spacing = unit(0.5, "lines"),
+    panel.border = element_blank(),
+    axis.line = element_line(),
+    panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
+    panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
+    panel.grid.minor.y = element_blank(),
+    panel.grid.minor.x = element_blank(),
+    legend.title = element_blank(),
+    axis.title.x = element_text(hjust = 0.5, size = 14),
+    axis.title.y = element_blank()
+  )
+
+# Metameta_Fig3_male.perc (Figure S2 right panel)
+```
+
+```{r Fig4S1, fig.height = 8, fig.width = 7, fig.cap=" Percentages and numbers of either male (turqoise bars) or female (orange bars) biased traits (Panel A) across functional groups, this time for lnCVR (left hand side), lnVR (middle) and lnRR (right hand side).
+Panel B shows effect sizes from separate meta-analysis for each functional group, and Panel C contains results of heterogeneity analyses.
+All three panels represent results evaluated across all traits.}
+
+#### Combined Figure 4S1: overall Count data, Meta anlysis results, Heterogeneity
+
+Fig4S1 <- ggarrange(malebias_FigS1_alltraits, Metameta_FigS1_alltraits, HeteroS1, nrow = 3, align = "v", heights = c(1.1, 1, 1), labels = c("A", "B", "C"))
+Fig4S1
+
+```
 
@@
 As such, our results may not necessarily apply to every group of mice, which may or may not result in stronger support for either of the two hypotheses.
-Greater male variability vs. estrus-mediated variability?
+
+### Greater male variability vs. estrus-mediated variability?
 Evolutionary biologists commonly expect greater variability in the heterogametic sex than the homo- gametic sex.
@@
 However, our data do not support the conclusion that higher variability in males occurs across all traits, including for many other morphological traits.
+
+## Figure 5
+ ![Fig5](./Figures/Figure5.png)
+
+### Summary of sex differences in the mean trait values (lnRR) and variances (lnCVR) across nine functional trait groups, and overall.
+
 The estrus-mediated variability hypothesis was, at least until recently (Prendergast et al., 2014; Smarr et al., 2017), regularly used as a rationale for including only male subjects in many biomedical studies.

### 2021-04-07 executableMS/ms_v1.rmd
Update ms_v1.rmd

@@
  ## Figure 1—figure supplement 1
- this code doesn't make sense here - as it needs all the code that's introduced later
- ```{r FigCor, fig.height=3, message = FALSE, fig.cap= "Mean-variance relationships (log(Mean) vs log(SD, standard deviation)) across all traits for males (A) and females (B).[Figure 1-figure supplement 1 in manuscript]"}
-# First, clean up the data
- results <- data %>%
-            group_by(population,
-             production_center,  
-             strain_name,  
-             parameter_name,
-             sex) %>%
-    summarise(trait  = parameter_name[1],
-              x_bar  = mean(data_point, na.rm = TRUE),
-              x_sd   =   sd(data_point, na.rm = TRUE),
-              n_ind  = n()) %>%
-    ungroup() %>%
-    filter(n_ind > 5) %>%   # NOTE here that you are excluding data with 5 exactly....
-    group_by(population) %>%
-    filter(all(c("male", "female") %in% sex)) %>% # Removes any entries where only 1 sex is present
-    multi_spread(sex, c(x_bar, x_sd, n_ind)) %>%
-    mutate(lnMean_m = log(male_x_bar),
-           logSD_m  = log(male_x_sd),
-           lnMean_f = log(female_x_bar),
-           lnSD_f   = log(female_x_sd)) %>%
-    filter(!is.na(logSD_m) & !is.inf(logSD_m)) %>%
-    filter(!is.na(lnSD_f) & !is.inf(lnSD_f))
-
-male <- ggplot(results, aes(x = lnMean_m, y = logSD_m)) +
-    geom_point(color = "#66C2A5", size = 2) +
-   geom_smooth(method = "lm", se = FALSE, color="black") + 
-    labs(x = "log (Mean)",
-         y = "log (SD)") + 
-    theme_classic()
-female <- ggplot(results, aes(x = lnMean_f, y = lnSD_f)) +
-    geom_point(color = "#FC8D62", size = 2) +
-  geom_smooth(method = "lm", se = FALSE, color="black")+
-    labs(x = "log (Mean)",
-         y = "log (SD)") + 
-    theme_classic()
-ggarrange(male, female, ncol = 2, nrow = 1, labels = c("A", "B"))
-```
+
  ![Fig1sup](./Figures/Figure1sup.png)
@@
 
-## The two hypotheses (‘greater male variability’ versus ‘estrus-mediated variability’) have different predictions on how variabilities influence total observed phenotypic variance (Vtotal in the figure).
+### The two hypotheses (‘greater male variability’ versus ‘estrus-mediated variability’) have different predictions on how variabilities influence total observed phenotypic variance (Vtotal in the figure).
 For greater male variability, the within-subject (or within-trait) variation Vwithin could be potentially negligible or is equal in males and females.
@@
 library(splus2R)
-
-# missing for meta-analysis: metafor, robumeta
+library(metafor)
+library(robumeta)
+
 # pacman::p_load(readr, dplyr,metafor, devtools, purrr, tidyverse, tidyr, tibble, kableExtra, robumeta, ggpubr, ggplot2, png, grid, here, knitr, pander, splus2R)
@@
 ```{r}
-data <- readRDS(github://itchyshin/mice_sex_diff/export/data_clean.rds) 
+data <- readRDS(data_clean.rds) 
 procedures <- read_csv(github://itchyshin/mice_sex_diff/export/procedures.csv)
@@
 
-```{r metaanlysis prep, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE, messages=FALSE, paged.print=FALSE}
+```{r metaanalysis prep, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE, messages=FALSE, paged.print=FALSE}
 # Create dataframe to store results
@@
 Fig4
+
 ```
+
 ## Figure 4—figure supplement 1
@@
 
-## ## Figure 4—figure supplement 2
+## Figure 4—figure supplement 2
+
 ```{r Fig4S2_prep, echo = FALSE, eval = TRUE}
@@
   )
-# Metameta_Fig3_female.sig #(Figure 5B left panel)
-```
-
-```{r FigS1_prep, echo = FALSE, eval = TRUE}
+
 ### Preparing the data
@@
 
-```{r Fig4S1, fig.height = 8, fig.width = 7, fig.cap=" Percentages and numbers of either male (turqoise bars) or female (orange bars) biased traits (Panel A) across functional groups, this time for lnCVR (left hand side), lnVR (middle) and lnRR (right hand side).
-Panel B shows effect sizes from separate meta-analysis for each functional group, and Panel C contains results of heterogeneity analyses.
-All three panels represent results evaluated across all traits.}
-
-#### Combined Figure 4S1: overall Count data, Meta anlysis results, Heterogeneity
-
-Fig4S1 <- ggarrange(malebias_FigS1_alltraits, Metameta_FigS1_alltraits, HeteroS1, nrow = 3, align = "v", heights = c(1.1, 1, 1), labels = c("A", "B", "C"))
-Fig4S1
-
-```
-
-## Figure 4—figure supplement 2
-```{r code for sex bias}
-
-```
-
-```{r fig.cap = "**Sex bias in trait groups for lnCVR, lnVR and lnRR.**
+```{r Fig4S1, fig.height = 8, fig.width = 7, fig.cap=" "**Sex bias in trait groups for lnCVR, lnVR and lnRR.**
 (A) Percentages and numbers of affected traits, for variance (lnCVR and lnVR) and means (lnRR), where there is a significant difference between the sexes (i.e.
@@
 The orange bars represent trait groups with a female bias, turqouise bars male-biased traits."}
+
+#### Combined Figure 4S1: overall Count data, Meta anlysis results, Heterogeneity
+
+Fig4S1 <- ggarrange(malebias_FigS1_alltraits, Metameta_FigS1_alltraits, HeteroS1, nrow = 3, align = "v", heights = c(1.1, 1, 1), labels = c("A", "B", "C"))
+Fig4S1
 

### 2021-04-07 executableMS/ms_v1.rmd
Update ms_v1.rmd

@@
 ```{r}
-data <- readRDS(data_clean.rds) 
+data <- readRDS(github://itchyshin/mice_sex_diff/export/data_clean.rds) 
 procedures <- read_csv(github://itchyshin/mice_sex_diff/export/procedures.csv)

### 2021-04-07 executableMS/ms_v1.rmd
Update ms_v1.rmd

--- 2021-04-07 executableMS/ms_v1.rmd
@@
 ```{r}
-data <- readRDS(data_clean.rds) 
-procedures <- read_csv(github://itchyshin/mice_sex_diff/export/procedures.csv)
+data <- readRDS(github://itchyshin/mice_sex_diff/export/data_clean.rds) 
+procedures <- read_csv(github://itchyshin/mice_sex_diff/data/procedures.csv)
 n <- length(unique(data$id))
@@
 
-  group <- read_csv(here("data", "ParameterGrouping.csv"))
+  group <- read_csv((github://itchyshin/mice_sex_diff/data/ParameterGrouping.csv)
 
